### 2023-03-04 carbon_paper/main.tex
added tex source for paper

% mnras_template.tex 
%
% LaTeX template for creating an MNRAS paper
%
% v3.0 released 14 May 2015
% (version numbers match those of mnras.cls)
%
% Copyright (C) Royal Astronomical Society 2015
% Authors:
% Keith T. Smith (Royal Astronomical Society)

% Change log
%
% v3.0 May 2015
%    Renamed to match the new package name
%    Version number matches mnras.cls
%    A few minor tweaks to wording
% v1.0 September 2013
%    Beta testing only - never publicly released
%    First version: a simple (ish) template for creating an MNRAS paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Basic setup. Most papers should leave these options alone.
\documentclass[fleqn,usenatbib]{mnras}

% MNRAS is set in Times font. If you don't have this installed (most LaTeX
% installations will be fine) or prefer the old Computer Modern fonts, comment
% out the following line
\usepackage{newtxtext,newtxmath}
% Depending on your LaTeX fonts installation, you might get better results with one of these:
%\usepackage{mathptmx}
%\usepackage{txfonts}

% Use vector fonts, so it zooms properly in on-screen viewing software
% Don't change these lines unless you know what you are doing
\usepackage[T1]{fontenc}

% Allow "Thomas van Noord" and "Simon de Laguarde" and alike to be sorted by "N" and "L" etc. in the bibliography.
% Write the name in the bibliography as "\VAN{Noord}{Van}{van} Noord, Thomas"
\DeclareRobustCommand{\VAN}[3]{#2}
\let\VANthebibliography\thebibliography
\def\thebibliography{\DeclareRobustCommand{\VAN}[3]{##3}\VANthebibliography}

%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%

% Only include extra packages if you really need them. Common packages are:
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
% \usepackage{amssymb}	% Extra maths symbols

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%
\defcitealias{2011ApJS..197...17C}{C11}
\defcitealias{2015ApJS..219...40C}{C15}

\newcommand{\cristallo}{\citetalias{2011ApJS..197...17C}+\citetalias{2015ApJS..219...40C}}

% Please keep new commands to a minimum, and use \newcommand not \def to avoid
% overwriting existing commands. Example:
% \newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared
\newcommand{\VICE}{\texttt{VICE}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[Constraining carbon yields]{The galactic chemical evolution of carbon: Constraining stellar nucleosynthesis}

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[D. A. Boyea et al.]{
Daniel A. Boyea,$^{1}$\
et al.
% James W. Johnson,$^{1}$
% David Weinberg
% Jack Roberts
% Jennifer Johnson
% ?
\\
% List of institutions
$^{1}$Department of Astronomy, The Ohio State University\\
$^{2}$Department, Institution, Street Address, City Postal Code, Country\\
$^{3}$Another Department, Different Institution, Street Address, City Postal Code, Country
}

% These dates will be filled out by the publisher
\date{Accepted XXX. Received YYY; in original form ZZZ}

% Enter the current year, for the copyright statements etc.
\pubyear{2023}

% Don't change these lines
\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle

% Abstract of the paper
\begin{abstract}
Stellar evolution models provide highly uncertain predictions for elemental yields due to our limited understanding of stellar physics. In this paper, we aim to estimate the nucleosynthetic yields of carbon using galactic chemical evolution models.

We find that the AGB stars make up a fraction $0.20_{-20}^{+80}$ of total carbon production at late times. 
\end{abstract}

% Select between one and six entries from the list of approved keywords.
% Don't make up new ones.
\begin{keywords}
Need to find some...
\end{keywords}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%% BODY OF PAPER %%%%%%%%%%%%%%%%%%

\section{Introduction}

A fundamental question of Galactic Chemical Evolution (GCE) is understanding the physical processes which make each element. Stellar evolution models can be used to predict how much of each element stars with a variety of physical properties produce. However, these models are rife with uncertainties, limited by our understanding of critical physical processes such as nuclear reaction rates, convection, opacity, and mass loss (CITE, e.g. stellar physics reviews).

Carbon and nitrogen are the only lighter elements produced significantly by low mass stars, so*****, reasons WHY this study.

Asymptotic Giant Branch (AGB) stars are known to be importaint (cite) from stellar model predictions, previous GCE, and evidence from abundance patterns. (are there detections in PN?)

CCSNe are also important (.... SN reminant measurments)

We also know that there is evidence for non-monatonic carbon yield patterns. 
pattern where carbon is more readily produced by both high metallicity and very low metallicity stars (CEMPS, early GCE results), but our picture.

Additionally, stellar models are computationally expensive, even in one dimension, so while there are grids of predictions, these are not always fine enough to make accurate chemical evolution models.

Previous models (CIte). We use \VICE (CITE) to create multi-zone models of GCE enabling us to account for the effects of migration on our predicted yields.

\citet{2018MNRAS.476.3432P}
\citep{2017ApJ...837..183W}
\citep{2021MNRAS.508.4484J}
\citep{2021arXiv210603912V}

\citep[e.g.][]{2022arXiv220204666J}

Carbon abundances are strongly affected by CNO cycle processing in stars. The CNO cycle is one of two series of nuclear reactions( $^{12}$C(p, $\gamma$)$^{13}$N($\beta^+ \nu_e$)$^{14}$N(p, $\gamma$)$^{15}$O($\beta^+\nu_e$)$^{15}$N(p,$\alpha$)$^{12}$C

Because the $^{14}$N(p, $\alpha$) proton capture is the slowest component of the CNO cycle ****, the CNO cycle, to first order, converts all $^{12}$C into $^{14}N$.

One challenge of measuring abundances of carbon in star is that when a star becomes a RGB star, material from the CNO-processed core. Since this core-processed material is now carbon depleted and nitrogen enhanced, measurments of this star's atmosphere will no longer reflect the birth abundances of the star.

In Figure \ref{fig:sum} we present a sample of APOGEE subgiants. These subgiants were chosen based on their location in the HR diagram based on criteria in \citet{jack_subgiant} replicated in Appendix \ref{sec:jack}. Because subgiants have not undergone FDU, their surface abundances are an accurate reflection of the birth abundances (CITATION).

\begin{equation}
\begin{cases}
\text{[Mg/Fe]} >0.12-0.13\text{[Fe/H]}, & \text{[Fe/H]}<0\\
\text{[Mg/Fe]} >0.12, & \text{[Fe/H]}>0\\
\end{cases}
\end{equation}

\begin{figure*}
    \centering
    \includegraphics[]{figures/subgiants_mgh.pdf}
    \includegraphics[]{figures/subgiants_mgfe.pdf}
    \caption{Chemical abundance relationships of our sample of APOGEE subgiants (see Jack et al. 2023). Left panel shows }
    \label{fig:sum}
\end{figure*}
\section{Nucleosynthesis}

Galactic chemical evolution are fundamentally intertwined with our understanding of stellar nucleosynthesis. In this paper, we are concerned with three major nucleosynthetic pathways: AGB stars, CCSNe, and Supernovae type Ia. While only AGB stars and CCSNe are producers of carbon, SNeIa Fe can be used to compare with the AGB delayed carbon component.

\VICE allows us to explore the nucleosynthesis of various models, as it includes AGB tables for C11, et.c

We discuss carbon nucleosythesis in more detail in the next two sections. We assume that the only dominant sources of carbon are from AGB stars and CCSNe/massive star winds. ***JUSTIFY***. Below  is a brief overview of our  nucleosythetic assumptions of other elements.

Let $y_{\rm X}^{\rm proc}(M, Z)$ be the fractional yield of element X by a process proc for stars of a mass $M$ (in solar masses) and at metallicity $Z$ defined as: 
\begin{equation}
    y_{\rm X} = \frac{M_{\rm X,\ ej} - M_{\rm X,\ birth}}{M}   
\end{equation}

Where $M_{\rm X,\ ej}$ and $M_{\rm X,\ birth}$ are the mass of element X ejected and initially present in the star. 
We define the IMF-integrated yield of X with: 
\begin{equation}
Y_{\rm X}^{\rm proc}(Z) = \int_{M_{\rm min}}^{M_{\rm max}} y_{\rm X}^{\rm proc}(M, Z)\ \Phi(M)  \ dM
\end{equation}
Where $\Phi(M) = \frac{dN}{dM}/ \int_{M_{\rm min}}^{M_{\rm max}} \frac{dN}{dM}\ dM$ is the normalized IMF, $M_{\rm min}$ and $M_{\rm max}$ are the minimum and maximum mass of stars, which we take to be $0.08 M_{\sun}$ and $100 M_{\sun}$ respectively; and $\frac{dN}{dM}$ is the initial mass function, the frequency of stars born between $M$ and $M+dM$.

There are two $\alpha$-elements we care about: Mg and O. Stellar observations of magnesium are more reliable but oxygen abundances are easier to measure in HII regions. We assume that both Mg and O are produced entirely in CCSNe with constant, metallicity-independent yields. Thus $\text{[Mg/H]} = \text{[O/H]} = [\alpha/\text{H}]$ in our models

\begin{itemize}
    \item observational validation
\end{itemize}
For carbon, the dominant producer is from massive stars which eject carbon fused in their cores during CCSNe.

Taken from J21 and J22, we make the following yield assumptions:
\begin{itemize}
    \item $Y_\text{O}^\text{CC} = 0.015$
    \item $Y_\text{O}^\text{Ia} = 0$
    \item $Y_\text{Fe}^\text{Ia} = 0.00214?$
    \item $Y_\text{Fe}^\text{CC} = 0.0012$
    \item $Y_\text{N}^\text{CC} = 0.00036$
    \item $y_\text{N}^\text{AGB}(M, Z) = 9\times 10^{-4} M \left(\frac{Z}{Z_\odot}\right)$
\end{itemize}
Also following J21/J22, we take the SNeIa Delay Time distribution to be a $t^{-1.1}$ law based on the observations by \citet{2012MNRAS.426.3282M}.

We leave consistent throughout the paper. While different CCSNe models predict different absolute values for $y_\text{O}^\text{CC}$, they also predict that the yield is metallicity-independent within the uncertainties of the model.

\subsection{Asymptotic giant branch carbon}

An AGB star is a low mass ($\lesssim 8 M_{\sun}$) star during the final phases of evolution. The star has already completed Hydrogen core burning, Hydrogen shell burning during the red giant branch phase, and Helium core burning. So, the structure consists of an inert core of carbon and oxygen surrounded by a Helium burning shell and a Hydrogen burning shell. The double shell burning leads to thermal instabilities which drive off the outer layers of the star in a series of violent pulsations, ejecting the envelope and leaving behind a C/O white dwarf.

In an AGB star, TDU and HBB are two major processes involved in carbon production and destruction. TDU occurs during thermal pulsations, where the convective layer of the star passes into the inner layers with He-burning products which mixes in C and O into the envelope. In contrast, HBB may happen if the base of the convective envelope reaches about 50MK, initiating the CNO cycle, converting most C12 into N14.

The differences in yields between AGB models depend on the mass loss rate, treatment of convection, and nuclear reaction rates.

In this work, we explore four different sets of AGB star yields representative of the variety of options which also provide reasonably well sampled grids in metallicity and mass necessary for chemical evolution studies.
\begin{itemize}
    \item~\VICE~\VICE~\VICE
    \item \citetalias{2015ApJS..219...40C}
    \item \cristallo
    \item \cite[C11][Hi]{2011ApJS..197...17C}: \citet{2011ApJS..197...17C, 2015ApJS..219...40C}
    \item K10: \citet{2010MNRAS.403.1413K}
    \item V13: \citet{2013MNRAS.431.3642V}
    \item K16: \citet{2016ApJ...825...26K}
\end{itemize}
Unless otherwise noted, C11 is the model we choose as our fiducial AGB yield.

Figure \ref{fig:y_agb} compares the net fractional AGB carbon yield, $m_\text{C}^\text{AGB}(M, Z)$ for each AGB model we consider. Note that the yields may be negative when the birth abundance is higher than the carbon abundance of the material ejected back to the ISM.

Most models agree on the qualitative shape of the net fractional AGB carbon yield. The stars with the highest fractional carbon yields are between 2 to 4 solar masses, depending on the metallicity and model. Both lower and higher mass stars produce less carbon, and high mass stars may even destroy carbon at high metallicity due to highly efficient HBB. And all models agree that the carbon yield generally decreases with metallicity.

Metallicity dependence:
V13 is the only model that stands out, showing a non-monotonic metallicity dependence, however this effect is only for models with [M/H]$\leq -1$. Otherwise the major differences between the models are the precise amount of carbon and the slope of the metallicity dependence. For example, the three models C11, K10, and K16 predict $y_\text{C}^\text{AGB}$ to be between 0.006 and 0.008 at solar metallicity, but C11 has a much shallower metallicity dependence than the K10 and K16 models. And at solar, V13 predicts a value at around 0.004 so the models are all within about a factor of 2.

Another difference is the speed at which equilibrium is reached. K10 and K16 weight carbon production more heavily towards massive stars resulting in a faster time to equilibrium, whereas the C11 and V13 models predict a slightly longer timescale with order 1Gyr, but little to no carbon is produced more than 2Gyr after a star formation event. This is in contrast to iron which is still produced by SNeIa up to 10Gyr after a star formation event.

\begin{figure*}
    \centering
 	    \includegraphics[scale=1]{figures/agb_yields.pdf}\\

    \caption{The net fraction carbon yield ($M_\text{C}$, the amount of carbon produced by the star divided by $M$) plotted as a function of mass, $M$. Lighter colors represent higher values of metalicity ([M/H]). Each panel represents a different AGB model. K10 reports stars at MoverH -3, -2, etc. I can reproduce C11 and K10 but not other V13 and KL16 :(((}

    \label{fig:y_agb}
\end{figure*}

\begin{figure*}
    \centering

    \includegraphics[scale=1]{figures/y_agb_vs_z-1.pdf}
    \includegraphics[scale=1]{figures/y_agb_vs_t-1.pdf}

    \caption{On the left, we plot the IMF weighted net fractional carbon yields of each AGB model as a function of metalicity.The right panel plots the normalized net carbon AGB yield as a function of time for a population of stars born at the same time at solar metallicity. We note that for the right panel, the minimum of the DTD for V13 is }

\end{figure*}

\subsection{CCSNe carbon}

While there are many stellar models providing predictions of CCSNe yields, the results of these models are highly uncertain due to the many stellar modeling uncertainties.

We summarise many of the predictions of stellar models in Figure \ref{fig:y_cc}. Pink squares represent \citep{2013ARA&A..51..457N}, etc. etc.
\citep{2018ApJS..237...13L}
\citep{2016ApJ...821...38S}
\citep{1995ApJS..101..181W}

On the right, we plot the expected CCSNe abundance ratio of each model as a function of metallicity, defining
\begin{equation}
    {\rm [C/O]^{CC}} = \log_{10}\left( \frac{y_{\rm C}^{\rm CC}}{y_{\rm O}^{\rm CC}}\right) - \log_{10} \left( \frac{Z_{C, \sun }}{Z_{O, \sun }} \right)
\end{equation}
Notice how even these ratios 
\begin{figure*}
    \includegraphics[scale=0.9]{figures/y_c_cc-2.pdf}
    \includegraphics[scale=0.9]{figures/y_co_cc.pdf}
    \caption{The fist plot shows IMF-weighted net fractional CCSNe yield of carbon, $y_C^{cc}$ against metalicity, [M/H], for different studies. The right plot instead shows [C/O]$^\text{CC}$, the logarithm of the abundance ratio of carbon to oxygen if CCSNe were the only carbon source, also as a function of metallicity for the same set of studies. The black line represents the carbon yield of the fiducial model, $y_C^{CC} = 0.004? (Z/Z_{\sun})^{0.3}$, and becomes dashed over regions where we have not tested our model. }
    \label{fig:y_cc}
\end{figure*}

    \begin{itemize}
        \item Wide range in predictions, exacerbated to 1 dex range when including variance in oxygen predictions
        \item (explain) most models have a near-metallicity independent oxygen yield, so we choose the fiducial value of 0.015 despite varience in $y_O^{cc}$
        \item The fiducial value, where we choose the carbon yield from Sukhbold+16, may be above most predictions of carbon yields but is within the range of yield ratios
        \item the fiducial value would reach an equilibrium carbon yield of -0.1 without AGB stars
        \item Rotation in LC18 appears to increase metallicity dependence of carbon production (read this paper more carefully)
        \item NKT and LC agree in positive metallicity depenent yields
    \end{itemize}

\section{The Multizone Model}

To simulate the chemical evolution of a Milky way like galaxy, we use the Versitile Integrator for Chemical Evolution (\VICE ) published in \citet{2021MNRAS.508.4484J} and also briefly described in \citet{2022arXiv220204666J}. 
As a multi-zone model, the galaxy is divided into 200 rings of 0.1kpc, each with separate gas supplies with outflow and inflow rates.

\VICE\ accounts for radial migration by using the results of the \texttt{h277} hydrodynamical simulation. Each VICE SSP is matched to a random nearby star particle \textit{analogue} in \texttt{H277}. VICE approximates the migration of this particle by using a $\sqrt{\text{time}}$-diffusion approximation where the change in galactic radius of a star, $\Delta R$, is $\Delta R \propto \sqrt{\text{t}}$. 
VICE does not account for radial gas flows.

Other approaches have used dynamical arguments to implement their stellar mirgrations. We note that our approach does not introduce more free parameters which may bias conclusions. However, we only consider one dynamic history, and it is still unknown how variations in the dynamic history of a galaxy impact its chemical evolution.

We initially assume an "inside-out" SFH where the star formation rate peaks in the early evolution of the galaxy and is higher closer to the galactic center. The star formation rate, $\Sigma_\star$, for our fiducial model is parameterized by
\begin{equation}
    \dot{\Sigma}_\star \propto \left(1-e^{-t/\tau_{\rm rise}}\right) e^{-t/\tau_{\rm sfh}}
\end{equation}
where $\tau_\text{rise}=2$Gyr is the
and $\tau_{sfh}$ is the rate of decline of the star formation rate, which is based on *****.

We also explore a "lateburst" model which is parameterized with a normal distribution multiplying our fiducial "inside-out" SFH as
\begin{equation}
    \dot{\Sigma}_{\rm lateburst} \propto \dot{\Sigma}_{\rm insideout} \left(1 + A e^{-(t-\tau_{\rm burst})^2/2\sigma^2_{\rm burst}} \right)
\end{equation}

$A=1.5$ represents the amplitude of the birth, $\tau_\text{burst}=10.8$Gyr is the time where the burst is strongest, and $\sigma_\text{burst}=1$Gyr is the width of the burst. We do explore the effects of variations of this parameterization in section ****.

VICE normalizes the total mass of star formation against observations from ******.
The gas inflow is calculated based on our star formation parameterization by using a schmit law 
\begin{equation}
    dM_g \propto \dot{\Sigma}^{1/n}
\end{equation}
where we take $n$ to be ****

Salpeter IMF.

\subsection{Yield Parameterization}
  Because of the large uncertainties in CCSNe carbon yields, we choose to explore an analytic expression of the yield enabling us to easily explore how variations of CCSNe carbon yields affect abundance tracks. We find that a powerlaw yield with a metallicity-dependent constant minimum is able to match the observations well while remaining a simple parameterization (see below). Our expression is:
    \begin{equation}
   y_\text{C}^\text{CC}(Z) =  \alpha\ Z^\beta y_\text{O}^\text{CC} + y_\text{C, 0}^\text{CC}
    \end{equation}
   	Where we estimate $\alpha = 0.02$ and $\beta = 0.25$ (See Section \ref{equilibrium} ). Our second model uses $\alpha = 0.44$ and $\beta = 0.63$ with K16 yields and reduced $\eta \rightarrow 1/2 \eta$

    As an overall scaling of yields does not significantly affect our models, we choose to fix the total equilibrium value of the total carbon yield at solar at $Y_{\text{C},\ \sun} = 0.005$, and then scale the yields relative to this value.

\section{Multizone model results}

\subsection{Data Selection}

We use data from APOGEE DR17 processed with APOSCAP. Since subgiant stars have yet to experience FDU, their atmospheric carbon and nitrogen abundances are still reflective of their birth abundances and do not need mixing corrections.

To select for subgiants, we use the following cut in $\log g$ and $T_{\rm eff}$ which selects stars at the base of the red giant turnoff (FIGURE and \cite{jack_subgiant})

Because the star formation history is left in a simple inside-out form, this multizone model does not reproduce the high-$\alpha$ sequence, therefore we make the following cut to the V21 data to remove the high alpha sequence. (do we?)

See Appendix \ref{sec:jack} for further discussion of our sample and comparison to FIORENZO.

\subsection{The Evolution of carbon across the galaxy and through time}

The GCE of carbon is complicated by metallicity dependencies and delayed contributions.

We note the following features of our model:

\begin{enumerate}
    \item Carbon comes predominantly ($\sim80\%$) from CCSNe but the rest is from AGB stars
    \item The CCSNe carbon production is more efficient at higher metallicities
    \item AGB stars produce less carbon at higher metallicities.
\end{enumerate}

The combination of these features leads to an evolution that proceeds as follows
\begin{enumerate}
    \item Initially, CCSNe dominate production before AGB stars can contribute their enrichment, but because CCSNe is highly metalliticy dependent, the C/$\alpha$ ratio increases with time.
    \item AGB stars begin contributing their carbon, increasing the $C/\alpha$ ratio more steeply as the gas begins to reach its equilibrium metallicity
    \item When $Z$ reaches equilibrium, the $C/\alpha$ ratio stops increasing or may even decline, as AGB stars formed at higher metallicities reduce the net carbon yields.
\end{enumerate}

We plot time evolution tracks in Figure \ref{fig:c_evo} for $[C/\alpha]-[\alpha/H]$ and $[C/\alpha]-[Fe/H]$ for our fiducial model. Each colored track corresponds to a different galactic radius and 1Gyr time steps are marked with crosses on the lines.

Comparing [C/$\alpha$] against [Fe/H] enables us to see late time evolution of carbon more clearly. Because [Fe/H] takes longer to reach equilibrium as half of iron production comes from type-Ia supernovae, the late time evolution is not clustered as tightly horizontally as for [$\alpha$/H].

This is even more evident in the lower part of Figure \ref{fig:c_evo}, where we instead plot snapshots of the galactic radial trend at different times for our model. While the [C/$\alpha$]-[$\alpha$/H] trend reaches almost equilibrium at 5Gyr, the [C/$\alpha$]-[$\alpha$/Fe] trend continues to evolve even until the present day, exposing the effect of the delayed contribution from AGB stars on the evolutionary history.

\begin{figure*}
\label{fig:c_evo}
\includegraphics{figures/evo_tracks-9.pdf}
\includegraphics{figures/evo_slices-2.pdf}
\caption{The top set of panes show the time evolution of the gas phase of our fiducial model, plotted as tracks through [C/O]-[O/H] and [C/O]-[O/Fe] where each colored line corresponds to the evolution at that galactic radius. 
The bottom set instead shows the galaxies gas-phase [C/O]-[O/H] and [C/O]-[O/Fe] trend at 5 different time slices. 
}
\end{figure*}

\subsection{Effects of AGB Yields}
\begin{figure*}
\includegraphics[scale=0.6]{figures/oob_agb-1.pdf}

\caption{Abundance tracks for 4 different choices of AGB models. Each panel has different abundance ratios on the axis but is otherwise the same. The black points are Jack Roberts selection of APOGEE subgiants. Each model is plotted as a line representing the mean stellar abundance in each bin on x.}
\label{fig:stars_abundances}
\end{figure*}

How much does the choice of AGB model affect chemical evolution? 
Short description of effects of AGB model choices, and how we can rule out models like V21.  Maybe point to appendex B?

Our next exploration is to adjust the relative fraction of AGB star yields. To do this, we hold the total carbon yield at solar metallicity fixed, so for a desired AGB fraction (assuming equilibrium),

\begin{equation}
    \alpha_{AGB} = f_{agb} \frac{y_{desired}}{y_0^{agb}}
\end{equation}
\begin{equation}
    \alpha_{CC} = (1 - f_{agb}) \frac{y_{desired}}{y_0^{cc}}
\end{equation}

\begin{table}
	\centering
	\caption{For each AGB yield set, our calculation of the effective SFH- and IMF-weighted carbon AGB yield, along with the multiplicative factor to reach an AGB contribution of 20.}
	\label{tab:alpha_agb}
	\begin{tabular}{lcr} % four columns, alignment for each
		\hline
		Study & $y_{\rm C, 0}^{\rm agb}$ & $\alpha_{\rm agb, 20}$\\
		\hline
		C11 & 0.000405 & 3.6\\
		K10 & 0.000643 & 2.3\\
		V13 & 0.000214 & 6.8\\
		K16 & 0.000404 & 3.6\\
		\hline
	\end{tabular}
\end{table}

\subsection{Star Formation History}

We do run models with an alternate "lateburst" stars formation history.

equation of lateburst

However, we find that the star formation history has a negligable effect on the shape of the mean track. More drastic changes in SFH could explain the high alpha/low alpha seperation but we leave further exploration of SFH to future work.

% \begin{figure*}
% \includegraphics[width=1.5\columnwidth]{figures/cooh_lateburst.pdf}
% \caption{Same as Fig. \ref{fig:stars_abundances} but with different model choices.}
% \end{figure*}

\begin{figure*}
\includegraphics[scale=0.6]{figures/beta-1.pdf}
\includegraphics[scale=0.6]{figures/f_agb-1.pdf}

\caption{Similar to \ref{fig:stars_abundances} except the top plot shows the fiducial model with lower and higher values of $\beta$, the C-CCSNe metallicity dependence. The bottom plot is the same except shows varying AGB fractions.}
\end{figure*}

\begin{figure*}
\includegraphics[scale=0.6]{figures/lateburst_eta-1.pdf}

\caption{Same as Figure \ref{fig:stars_abundances} but comparing the fiducial model to the reduced outlow model and a lateburst model. (okay, need to totally change approach...)}
\end{figure*}

\subsection{Adjusted CCSNe Yields}

\begin{figure}
    \includegraphics[scale=0.6]{figures/cooh_scatter.pdf}
    \caption{The simulated stars of our model at present day plotted on [C/O]-[O/H] and colored such that lighter colors represent stars born at greater galactric radii.}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[scale=0.6]{figures/cnoh.pdf}
    \caption{Caption}
    \label{fig:cnofe}
\end{figure}

\begin{figure*}
\centering
\includegraphics[]{figures/summary-2.pdf}
\caption{Present-day gas phase tracks of the fiducial model in [C/O]-[O/H] space. M101 is valid comparison to MW ...(van Dokkum et al. 2014)}
\label{fig:gas_phase}
\end{figure*}
\subsection{The AGB Fraction }
One potential tension with data is our models predict a low value for the AGB fraction of stars.

Our model with Z-dependent CCSNe yields has $f_\text{agb} = 0.05$ which implies that CCSNe overwhelms AGB production and there should not be a seperation between low and high alpha sequences. However, V21 observes a significant seperation implying a more substantial delayed-time source.

Even changing the AGB model does not affect the conclusion significantly.

An alternate solution is to reduce the outflows and core collapse yields similarly, consistent with a model where more large stars collapse directly into black holes. This leaves the $y_\text{C}^\text{CC}/y_\text{O}^\text{CC}$ ratio unchanged, but because $y_\text{C}^\text{CC}$ is unchanged, the relative size of the AGB contribution is larger.

Increasing the relative AGB production lowers the magnitude of  $y_\text{C}^\text{CC}/y_\text{O}^\text{CC}$, but the metallicity dependence of the ratio must increase to compensate for the inverse metallicity dependence of AGB carbon yields.

We find that we can adjust both the outflows and scale down the yields if we change our model for $y_\text{C}^\text{CC}/y_\text{O}^\text{CC}$. For example, reducing outflows and CCSNe yields by a factor of two requires the modified parameters
$\alpha = 0.033$ and $\beta = 0.625$, which results in a slightly lower value at solar but nearly a doubling of the metallicity dependence.

These models are indistinguishable in the [C/O]-[O/H] plane from our adjusted CCSNe model, so future work investigating the SFH and carbon isotopic ratios in more depth may be able to provide more insight. In the next section, we develop the analytic tools to explore this problem in more depth.

\subsection{Outflows}
A common degeneracy in chemical evolution models is the yield-outflow degeneracy. An increase in stellar yields has a near-identical effect as a decrease in outflows. However, reducing the outflows reduces the evolution timescale of the system.

The theoretical motivation for decreasing outflows is due to the uncertainty in the explodability landscape---if less massive stars explode, then both the yields and outflows will be reduced by some factor. So, when we explore reduced outflow models, we consider models where both the outflows and yields are reduced by approximately the same factor, to leave the equilibrium abundances of a pure CCSNe unchanged.

The effect of reducing outflows is then increasing the relative contributions of non-CCSNe processes. For carbon, this increases the AGB fraction.

We have found that the [C/O]-[O/Fe] relationship may provide insight into this issue. [O/Fe] is a tracer of the relative contributions of CCSNe and delayed-time sources in chemical evolution. So, the appearance of a slope in [O/Fe] implies that there is a substantial delay-time process in carbon evolution. 
The metallicity-dependence of carbon yields complicates this picture because younger stars have higher [O/Fe] as the SNeIa contributions take up to 10Gyr, so metal-poor young stars will naturally have lower [C/O], agreeing with the slope observed in [C/O]-[O/Fe]. However, a pure CCSNe carbon model cannot reproduce the slope accurately as

\subsection{Comparison to HII Region Observations}
In Figure \ref{fig:gas_phase}, we plot our two favorite models against HII-region measured carbon abundances from **********

Our model appears to be broadly consistant with the gas phase data, however these imply if anything that the slope should be increased.

Are HII regions a good approximation?

Short discussion of measurment challenges in extragalactic galaxies, how other galaxies and dwarf SFH may come into play, why this relation is notecably steeper.

\section{The Equilibrium Approximation}\label{equilibrium}
If we assume that the median track is an equilibrium phenomenon, we can calculate the total carbon to oxygen yield ratio. Additionally, assuming an AGB yield set enables us to predict the CCSNe carbon yield.  
We begin with the model, which underlies the multizone simulations, that the change in mass of an element is a sum of production, outflows, recycling, and mass left in reminants. We write this as
\begin{equation}
M_\text{C} = y_\text{C} \dot{M}_\star - (1 + \eta - r) Z_\text{C} \dot{M}_\star
\end{equation}

In the case that carbon
\begin{equation}
Z_c^{eq}(R) = \frac{y_c^{cc} + \langle y_c^{agb} \rangle }{1 + \eta(R) - r - \tau_\star / \tau_{sfh}}
\end{equation}Where
\begin{equation}
\langle y_c^{agb} \rangle = \frac{\int_0^T y_c^{agb}(M, Z) \dot{M}_\star(T - t) \frac{dN}{dM} \frac{dM}{dt} dt  }{ \dot{M}_\star \int_0^T \frac{dN}{dM} \frac{dM}{dt} dt}
\end{equation}

Likewise for oxygen:
\begin{equation}
Z_O^{eq}(R) = \frac{y_O^{cc}}{1 + \eta(R) - r - \tau_\star / \tau_{sfh}}
\end{equation}

However, for the yield ratio, the denominator cancles with that of oxygen, so the ratio is fixed.
\begin{equation}
\frac{Z_c^{eq}}{Z_o^{eq}} = \frac{y_c^{cc} + \langle y_c^{agb} \rangle }{y_o^{cc}}
\end{equation}

For this analysis, we let $y_c^{agb}$ represent the default AGB yields from a given yield set, but add a process factor $\alpha_{agb}$ which multaplicatively increases the AGB fraction. See Table \ref{tab:alpha_agb}.

\begin{equation}
    y_{\rm C}^{\rm CC} \rightarrow \alpha_{agb}  y_{\rm C}^{\rm CC}
\end{equation}

With these definitions, we can calculate the core collapse yields of carbon as a function of metallicity:
\begin{equation}
    y_\text{C}^\text{CC} =  y_\text{O}^\text{CC} \frac{Z_\text{C,eq}}{Z_\text{O,eq}} - \alpha_{agb} \langle y_c^{agb} \rangle
\end{equation}

Rewriting in terms of the observed abundance ratio and dividing by $y_\text{O}^\text{CC}$. So, given the outflows or CCSNe oxygen yields, the carbon AGB yield, and the [C/O]-[O/H] mean abundance track, we can estimate the CCSNe carbon yield. Written as a relative yield:
\begin{equation}
    \frac{y_\text{C}^\text{CC}}{y_\text{O}^\text{CC}} = \frac{Z_{C, \sun}}{Z_{O, \sun}} 10^{[C/O]} - \frac{\alpha_{agb} \langle y_c^{agb} \rangle}{ y_\text{O}^\text{CC}}
\end{equation}

This equation corroberates what we have explored earlier in the paper, and provides our analytic estimates of the CCSNe carbon yields. Since the AGB term is subtracted, a negative AGB Z-dependence will correspond to a positive CC Z-dependence. And as we reduce outflows, the AGB factor increases, steepening the required slope of the carbon yields. So, while the AGB yields may agree with eachother, the uncertainties in the oxygen CC yields and outflows leads to a substantial uncertainty in the AGB fraction.

\begin{figure}
    \centering
    \includegraphics[scale=0.3]{figures/analytic_y-4.pdf}
    \caption{Our reverse fitting method to determine total CCSNe contribution}
\end{figure}

% y_c^cc = (0.0148 +- 0.00016) Z^{0.154 +- 0.0053}
\begin{equation}
    y_C = (0.004 \pm 0.00002) + (0.008 \pm 0.0001) \text{[M/H]} 
\end{equation}

\subsection{Uncertainties}

We only perform this analysis on the C11/15 yields because the range of metallicities of the data (about [M/H] = -0.4, 0.4) only represents about 2 AGB models, relying heavily on our choice of extrapolation. C11/C15 have a finer model grid, allowing us to have 5 theoretical predicted points within this metallicity range, allowing us to be more certain of our conclusion.

We do note that this analysis fails to take into account selection effects and biases in APOGEE, and a more robust determination of the carbon yield.

This formulation is degenerate in $\varpi$ until we estimate a better AGB fraction. As the seperation between the low and high alpha sequences can be used to estimate the delayed time contribution to carbon, using the model to estimate this value relies heavaly on the details of the SFH in addition to the 
We do give an estimate of the CCSNe yields, however this is dependent on our choice of $\eta$. Other choices of $\eta$ vary the value significantly in both magnitude and slope (as AGB contributions increase, we need less CCSNe carbon, however the CCSNe carbon must have a higher metallicity dependence to replicate the V21 data).

\section{Modeling extragalactic carbon trends}
Can we use our yield estimations and apply them to extragalactic sources successfully?

Explain Berg+19,

Bursty SFH may not be needed to explain scatter as the C/O slope + differet evolutionary timescales is capable alone of reproducing this scatter.

While the extragalactic trend appears to be more steeply sloped than our models, this is because of ***e.g. mass-dependent outflow rates/differening SFH between galaxies.

\section{Conclusions}

The last numbered section should briefly summarise what has been done, and describe
the final conclusions which the authors draw from their work.

\section*{Acknowledgements}

The Acknowledgements section is not numbered. Here you can thank helpful
colleagues, acknowledge funding agencies, telescopes and facilities used etc.
Try to keep it short.

Numpy, pandas, scipy, VICE, matplotlib
\cite{numpy, matplotlib}

\cite{OhioSupercomputerCenter1987}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Data Availability}

The inclusion of a Data Availability Statement is a requirement for articles published in MNRAS. Data Availability Statements provide a standardised format for readers to understand the availability of data underlying the research results described in the article. The statement may refer to original data generated in the course of the study or to third-party data analysed in the article. The statement should describe and provide means of access, where possible, by linking to the data or providing the required accession numbers for the relevant databases or DOIs.

%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%

% The best way to enter references is to use BibTeX:

\bibliographystyle{mnras}
\bibliography{main} % if your bibtex file is called example.bib

% Alternatively you could enter them by hand, like this:
% This method is tedious and prone to error if you have lots of references
%\begin{thebibliography}{99}
%\bibitem[\protect\citeauthoryear{Author}{2012}]{Author2012}
%Author A.~N., 2013, Journal of Improbable Astronomy, 1, 1
%\bibitem[\protect\citeauthoryear{Others}{2013}]{Others2013}
%Others S., 2012, Journal of Interesting Stuff, 17, 198
%\end{thebibliography}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%

\appendix

\section{Validating the APOGEE Subgiant Sample}\label{sec:jack}
Our APOGEE subgiant sample excludes stars marked with the following flags:
\begin{itemize}
\item \texttt{ancillary young embedded cluster}
\item \texttt{ancillary emission line star}
\item \texttt{MIR-deected candidate cluster member}
\item \texttt{selected as part of the EB program}
\item \texttt{selected as part of the young cluster study (in-SYNC)}
\item \texttt{W3/4/5 star forming complex}
\end{itemize}

To select stars only in the subgiant branch, we select stars in a polygon in $\log g$-$T_\text{eff}$ space described by the following cuts:
\begin{equation}
\begin{cases}
\log g \geq 3.5 \\
\log g \leq 0.004\ T_\text{eff} - 15.7 \\
\log g \leq 0.00070588\ T_\text{eff} + 0.358836 \\
\log g \leq -0.0015\ T_\text{eff} + 12.05 \\
\log g \geq 0.0012\ T_\text{eff} - 2.8 \\
\end{cases}
\end{equation}

Instead of excluding stars which have experienced FDU and thus modified carbon abundances as JACK's subgiant sample does, another approach to predict the birth abundances of carbon and nitrogen in stars is to model the predicted abundance effects of dredge up and then correct the measured abundances, as is done in V21.

In the first panel, both V13 and the subgiant sample predict similar trends in [C/Mg]-[Mg/H] but there appears to be a systematic offset of about 0.2dex. Reproducing the trend is promising as V21's mixing corrections were metallicity-dependent so the uncorrected sample of APOGEE giants does not match the subgiant trend.

The systematic offset could be explained by overpredicting the effects of FDU or other *** in V21's stellar evolution models??? or other subgiant physics???

In the second panel, agreement appears to be better. Both the MDF and the slope are nearly identical,
There is a slight deviation in slope between the models, and this could again be a systematic such as underestimation of **8some stellar effect**** at higher metallicities.

We compare both of **** in Figure \ref{fig:fiorenzo_jack}.

\begin{figure*}
    \centering
    \includegraphics[scale=0.5]{figures/fiorenzo_vs_jack_c-1.pdf}
    \includegraphics[scale=0.5]{figures/fiorenzo_vs_jack_n-1.pdf}
    \caption{A comparison of estimated stellar birth abundance trends from the subgiant sample and \citet{2021arXiv210603912V}
    }
    \label{fig:fiorenzo_jack}
\end{figure*}

\section{Effects of Alternate AGB Models}\label{sec:alt_agb}

While we focus the main discussion of the paper on the C11 model, other AGB models can have notable effects on abundance trends at ***

Because the predictions of the AGB yield models we consider are dwarfed by the required CCSNe carbon production to match observations (see Figure ***), we briefly explore here the effects of variations in AGB models affect abundance trend predictions when these models are amplified to match observational [C/MG]-[Mg/Fe] trends.

While most models are well represented by our AGB-fraction formalism, V13 presents a challenge as the predicted solar yield is much lower than the lower metallicity predictions, requiring the solar value to be a certain fraction forces us to amplify the yields by an unreasonable about (of order 10-30times) to reach the same $f_{\rm AGB}$ as other models. Thus, we instead calculate $f_{\rm AGB}$ at a metallicity of ... for this model.

V13 is also interesting as at high metallicity, the yields quickly become strongly negative. This causes a reversal of the [C/Mg]-[Mg/Fe] trend at high [Mg/H] slices (figure ...). As our set of observations do not appear to reverse, this indicates that carbon yields likely stay positive even at slightly super-solar, so models like V13 are a poor match to observations. 
Plot of age metallicity relationship?

\begin{figure*}
\includegraphics[scale=0.45]{figures/agb_adj-2.pdf}
\includegraphics[scale=0.45]{figures/abg_adj_z-1.pdf}

\caption{Same as \ref{fig:stars_abundances} but comparing our fiducial model to our recommended z-dependent $y_\text{C}^\text{CC}$ model. A plot of the stars of our favored CCSNe model colored by radius. The contours represent the density of V+21 data. The model is given Gaussian scatter equivalent to the mean error in the abundances reported by APOGEE. }
\end{figure*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Don't change these lines
\bsp	% typesetting comment
\label{lastpage}
\end{document}

% End of mnras_template.tex

### 2023-03-04 carbon_paper/agb_yields.py

@@ -6,6 +6,7 @@ import matplotlib as mpl
 import plot_style
 
 
+
 cmap = mpl.cm.viridis
 Z_max = 0.02
 Z_min = 0.0001

### 2023-03-04 carbon_paper/figure2b.py

@@ -1,89 +1,0 @@
-import matplotlib.pyplot as plt
-import vice
-import numpy as np
-import matplotlib as mpl
-import sys
-sys.path.append("../")
-from plotting_utils import fig_saver
-import rc_params
-
-sf = fig_saver()
-
-colors = ['#0072B2', '#009E73', '#D55E00', '#CC79A7', '#F0E442', '#56B4E9']
-
-allowed_MoverH = {
-    "LC18": [-3, -2, -1, 0],
-    "S16/N20": [0],
-    #"CL13": [0],
-    "NKT13": [-np.inf, -1.15, -0.54, -0.24, 0.15, 0.55],
-    #"CL04": [-np.inf, -4, -2, -1, -0.37, 0.15],
-    "WW95": [-np.inf, -4, -2, -1, 0]
-    }
-allowed_rotations = {
-    "LC18": [0, 150, 300],
-    "S16/N20": [0],
-    "CL13": [0, 300],
-    "NKT13": [0],
-    "CL04": [0],
-    "WW95": [0]
-}
-
-ccsne_studies = ["LC18", "S16/N20", "WW95","NKT13"]
-cmap = plt.get_cmap("jet")
-N = len(ccsne_studies)
-
-for i in range(len(ccsne_studies)):
-    study=ccsne_studies[i]
-    metalicities = allowed_MoverH[study]
-    rotations = allowed_rotations[study]
-    
-    for j in range(len(rotations)):
-        rotation = rotations[j]
-        yc = [vice.yields.ccsne.fractional('c', study=study, MoverH=metalicity, rotation=rotation)[0]
-             for metalicity in metalicities]
-        yo = [vice.yields.ccsne.fractional('o', study=study, MoverH=metalicity, rotation=rotation)[0]
-              for metalicity in metalicities]
-        y = np.log10(np.array(yc)/yo) - np.log10(vice.solar_z("c")/vice.solar_z("o"))
-        
-        Z = list(map(lambda x: 10**x, metalicities))
-        if rotation == 0:
-            marker = ["v", "o", "*", "s"][i]
-        elif rotation == 150:
-            marker=">"
-        elif rotation == 300:
-            marker="^"
[…]

### 2023-03-04 carbon_paper/figure3.py

@@ -1,22 +1,0 @@
-import matplotlib.pyplot as plt
-import vice
-import numpy as np
-import matplotlib as mpl
-import sys
-
-sys.path.append("/home/daniel")
-from python_packages.plotting import rc_params
-
-import os
-
-os.chdir("../..")
-
-sys.path.append(".")
-from model_comparer import ModelComparer
-from plotting_utils import fig_saver
-
-sf = fig_saver("carbon_paper/figures")
-
-mc = ModelComparer(["cristallo11"], sf=".")
-
-mc.plot_all_mean_stars(filename="figure3")

### 2023-03-04 carbon_paper/plot_style.py

@@ -3,6 +3,7 @@ import matplotlib.style as style
 import matplotlib.pyplot as plt
 import inspect
 from os import path
+from mpl_toolkits.axes_grid1 import Divider, Size
 
 
 def init():
@@ -41,7 +42,28 @@ def clear():
     style.use("./journal.mplstyle")
     plt.style.reload_library()
 
+def double_fig():
+    fig = plt.figure(figsize=(3,3))
+    h = [Size.Fixed(1.), Size.Fixed(WIDTH)]
+    v = [Size.Fixed(1.), Size.Fixed(WIDTH)]
+    divider = Divider(fig, (0,0,1,1), h, v)
+    ax = fig.add_axes(divider.get_position(),
+                      axes_locator=divider.new_locator(nx=1,ny=1))
+
+    return fig, ax
+
+def get_plot():
+    fig = plt.figure(figsize=(3,3))
+    h = [Size.Fixed(1.), Size.Fixed(WIDTH)]
+    v = [Size.Fixed(1.), Size.Fixed(WIDTH)]
+    divider = Divider(fig, (0,0,1,1), h, v)
+    ax = fig.add_axes(divider.get_position(),
+                      axes_locator=divider.new_locator(nx=1,ny=1))
+
+    return fig, ax
+
+
 init()
 
+WIDTH = 2.362 #inches
 COLORS = plt.rcParams['axes.prop_cycle'].by_key()['color']
-WIDTH = 3.15 #inches

### 2023-03-04 carbon_paper/subgiants_mgfe.py

@@ -10,13 +10,16 @@ import plot_style
 
 fig, (ax, ax_cb) = plt.subplots(1, 2)
 
-width = 3
+width = plot_style.WIDTH
 height = width
-padding = 0.1
-cbar_width = 0.05 # relative
-divider = SubplotDivider(fig, 111,
-                         horizontal=[Size.Fixed(width),Size.Fixed(padding), Size.Fixed(width * cbar_width)],
-                         vertical=[Size.Fixed(height)])
+padding = 0.05*width
+cbar_width = 0.05*width
+
+divider = SubplotDivider(fig, 111)
+divider.set_horizontal( [Size.Fixed(width),Size.Fixed(padding),
+                         Size.Fixed(cbar_width)])
+divider.set_vertical([divider.get_horizontal()[0]])
+                    
 
 plt.sca(ax)
 

### 2023-03-04 carbon_paper/subgiants_mgh.py

@@ -14,18 +14,20 @@ params = {
             "s": 0.5
             }
 
+fig, ax = plot_style.get_plot()
+
 df = subgiants[~ha]
-plt.scatter(df["MG_H"], df["C_MG"], label="low $\\alpha$", **params)
+ax.scatter(df["MG_H"], df["C_MG"], label="low $\\alpha$", **params)
 
 df = subgiants[ha]
-plt.scatter(df["MG_H"], df["C_MG"], label="high $\\alpha$", zorder=2,
+ax.scatter(df["MG_H"], df["C_MG"], label="high $\\alpha$", zorder=2,
          **params)
 
-pluto.fancy_legend(colors=[pluto.COLORS[0], pluto.COLORS[1]])
+pluto.fancy_legend(ax=ax, colors=[pluto.COLORS[0], pluto.COLORS[1]])
 
-plt.xlim(-0.6, 0.6)
-plt.ylim(-0.5, 0.2)
-plt.xlabel("[Mg/H]")
-plt.ylabel("[C/Mg]")
+ax.set_xlim(-0.6, 0.6)
+ax.set_ylim(-0.5, 0.2)
+ax.set_xlabel("[Mg/H]")
+ax.set_ylabel("[C/Mg]")
 
 plot_style.save()

### 2023-03-04 sciplot/src/plotting/figure.py

@@ -1,0 +1,30 @@
+import matplotlib as mpl
+
+import pyplot as plt
+
+class figure:
+    """
+    This class is designed to 
+    make modifications and handeling MPL's
+    figure class easier
+    """
+    __init__(**kwargs):
+        self.create_fig()
+
+    create_fig(self, **kwargs):
+        self.fig, self.ax = mpl.figure(**kwargs)
+
+    resize_fig(self):
+        ax_width
+
+
+    @property
+    def ax_width(self):
+        return (self.fig.subplotpars.right -
+                self.fig.subplotpars.left)*self.fig.get_figwidth()
+
+    @property
+    def ax_heighth(self):
+        return (self.fig.subplotpars.top -
+                self.fig.subplotpars.bottom)*self.fig.get_figheighth()
+

### 2023-03-13 carbon_paper/tex/main.tex
better reference names for paper

--- 2023-03-04 carbon_paper/main.tex
@@
 % \usepackage{amssymb}	% Extra maths symbols
+\graphicspath{{../figures/}}
 
@@
 %%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%
-\defcitealias{2011ApJS..197...17C}{C11}
-\defcitealias{2015ApJS..219...40C}{C15}
+\defcitealias{cristallo+11}{C11}
+\defcitealias{cristallo+15}{C15}
+\defcitealias{ventura+13}{V13}
 
-\newcommand{\cristallo}{\citetalias{2011ApJS..197...17C}+\citetalias{2015ApJS..219...40C}}
+\newcommand{\cristallo}{\citetalias{cristallo+11}+\citetalias{cristallo+15}}
 
@@
 
-\citet{2018MNRAS.476.3432P}
-\citep{2017ApJ...837..183W}
-\citep{2021MNRAS.508.4484J}
-\citep{2021arXiv210603912V}
+\citet{prantzos+18}
+\citep{WAF17}
+\citep{james+21}
+\citep{fiorenzo+21}
 
-\citep[e.g.][]{2022arXiv220204666J}
+\citep[e.g.][]{james+22}
 
@@
 
-\begin{equation}
-\begin{cases}
-\text{[Mg/Fe]} >0.12-0.13\text{[Fe/H]}, & \text{[Fe/H]}<0\\
-\text{[Mg/Fe]} >0.12, & \text{[Fe/H]}>0\\
-\end{cases}
-\end{equation}
-
 \begin{figure*}
     \centering
-    \includegraphics[]{figures/subgiants_mgh.pdf}
-    \includegraphics[]{figures/subgiants_mgfe.pdf}
+    \includegraphics[]{subgiants_mgh.pdf}
+    \includegraphics[]{subgiants_mgfe.pdf}
     \caption{Chemical abundance relationships of our sample of APOGEE subgiants (see Jack et al. 2023). Left panel shows }
@@
 \end{itemize}
-Also following J21/J22, we take the SNeIa Delay Time distribution to be a $t^{-1.1}$ law based on the observations by \citet{2012MNRAS.426.3282M}.
+Also following J21/J22, we take the SNeIa Delay Time distribution to be a $t^{-1.1}$ law based on
+the observations by \citet{maoz+12}.
 
@@
 \begin{itemize}
-    \item~\VICE~\VICE~\VICE
-    \item \citetalias{2015ApJS..219...40C}
+    \item \citetalias{cristallo+11}
     \item \cristallo
-    \item \cite[C11][Hi]{2011ApJS..197...17C}: \citet{2011ApJS..197...17C, 2015ApJS..219...40C}
-    \item K10: \citet{2010MNRAS.403.1413K}
-    \item V13: \citet{2013MNRAS.431.3642V}
-    \item K16: \citet{2016ApJ...825...26K}
+    \item \cite[C11][Hi]{cristallo+11}: \citet{cristallo+11}
+    \item K10: \citet{karakas10}
+    \item V13: \citet{ventura+13}
+    \item K16: \citet{KL16}
 \end{itemize}
@@
     \centering
- 	    \includegraphics[scale=1]{figures/agb_yields.pdf}\\
+ 	    \includegraphics[scale=1]{agb_yields.pdf}\\
 
@@
 
-    \includegraphics[scale=1]{figures/y_agb_vs_z-1.pdf}
-    \includegraphics[scale=1]{figures/y_agb_vs_t-1.pdf}
+    \includegraphics[scale=1]{y_agb_vs_z-1.pdf}
+    \includegraphics[scale=1]{y_agb_vs_t-1.pdf}
 
@@
 
-We summarise many of the predictions of stellar models in Figure \ref{fig:y_cc}. Pink squares represent \citep{2013ARA&A..51..457N}, etc. etc.
-\citep{2018ApJS..237...13L}
-\citep{2016ApJ...821...38S}
-\citep{1995ApJS..101..181W}
+We summarise many of the predictions of stellar models in Figure \ref{fig:y_cc}. Pink squares
+represent \citep{NKT13}, etc. etc.
+\citep{LC18}
+\citep{sukhbold+16}
+\citep{WW95}
 
@@
 \begin{figure*}
-    \includegraphics[scale=0.9]{figures/y_c_cc-2.pdf}
-    \includegraphics[scale=0.9]{figures/y_co_cc.pdf}
+    \includegraphics[scale=0.9]{y_c_cc-2.pdf}
+    \includegraphics[scale=0.9]{y_co_cc.pdf}
     \caption{The fist plot shows IMF-weighted net fractional CCSNe yield of carbon, $y_C^{cc}$ against metalicity, [M/H], for different studies.
@@
 
-To simulate the chemical evolution of a Milky way like galaxy, we use the Versitile Integrator for Chemical Evolution (\VICE ) published in \citet{2021MNRAS.508.4484J} and also briefly described in \citet{2022arXiv220204666J}.
+To simulate the chemical evolution of a Milky way like galaxy, we use the Versitile Integrator for
+Chemical Evolution (\VICE\footnote{\VICE~is available at \url{https://github.com/giganano/VICE}}) published in \citet{james+21} and also briefly described in
+\citet{james+22}. 
 As a multi-zone model, the galaxy is divided into 200 rings of 0.1kpc, each with separate gas supplies with outflow and inflow rates.
@@
 Because the star formation history is left in a simple inside-out form, this multizone model does not reproduce the high-$\alpha$ sequence, therefore we make the following cut to the V21 data to remove the high alpha sequence.
-(do we?)
+
+\begin{equation}
+\begin{cases}
+\text{[Mg/Fe]} >0.12-0.13\text{[Fe/H]}, & \text{[Fe/H]}<0\\
+\text{[Mg/Fe]} >0.12, & \text{[Fe/H]}>0\\
+\end{cases}
+\end{equation}
 
@@
 \label{fig:c_evo}
-\includegraphics{figures/evo_tracks-9.pdf}
-\includegraphics{figures/evo_slices-2.pdf}
+\includegraphics{evo_tracks-9.pdf}
+\includegraphics{evo_slices-2.pdf}
 \caption{The top set of panes show the time evolution of the gas phase of our fiducial model, plotted as tracks through [C/O]-[O/H] and [C/O]-[O/Fe] where each colored line corresponds to the evolution at that galactic radius.
@@
 \begin{figure*}
-\includegraphics[scale=0.6]{figures/oob_agb-1.pdf}
+\includegraphics[scale=0.6]{oob_agb-1.pdf}
 
@@
 
-\begin{table}
-	\centering
-	\caption{For each AGB yield set, our calculation of the effective SFH- and IMF-weighted carbon AGB yield, along with the multiplicative factor to reach an AGB contribution of 20.}
-	\label{tab:alpha_agb}
-	\begin{tabular}{lcr} % four columns, alignment for each
-		\hline
-		Study & $y_{\rm C, 0}^{\rm agb}$ & $\alpha_{\rm agb, 20}$\\
-		\hline
-		C11 & 0.000405 & 3.6\\
-		K10 & 0.000643 & 2.3\\
-		V13 & 0.000214 & 6.8\\
-		K16 & 0.000404 & 3.6\\
-		\hline
-	\end{tabular}
-\end{table}
-
 \subsection{Star Formation History}
@@
 % \begin{figure*}
-% \includegraphics[width=1.5\columnwidth]{figures/cooh_lateburst.pdf}
+% \includegraphics[width=1.5\columnwidth]{cooh_lateburst.pdf}
 % \caption{Same as Fig. \ref{fig:stars_abundances} but with different model choices.}
@@
 \begin{figure*}
-\includegraphics[scale=0.6]{figures/beta-1.pdf}
-\includegraphics[scale=0.6]{figures/f_agb-1.pdf}
+\includegraphics[scale=0.6]{beta-1.pdf}
+\includegraphics[scale=0.6]{f_agb-1.pdf}
 
@@
 \begin{figure*}
-\includegraphics[scale=0.6]{figures/lateburst_eta-1.pdf}
+\includegraphics[scale=0.6]{lateburst_eta-1.pdf}
 
@@
 \begin{figure}
-    \includegraphics[scale=0.6]{figures/cooh_scatter.pdf}
+    \includegraphics[scale=0.6]{cooh_scatter.pdf}
     \caption{The simulated stars of our model at present day plotted on [C/O]-[O/H] and colored such that lighter colors represent stars born at greater galactric radii.}
@@
     \centering
-    \includegraphics[scale=0.6]{figures/cnoh.pdf}
+    \includegraphics[scale=0.6]{cnoh.pdf}
     \caption{Caption}
@@
 \centering
-\includegraphics[]{figures/summary-2.pdf}
+\includegraphics[]{summary-2.pdf}
 \caption{Present-day gas phase tracks of the fiducial model in [C/O]-[O/H] space. M101 is valid comparison to MW ...(van Dokkum et al. 2014)}
@@
     \centering
-    \includegraphics[scale=0.3]{figures/analytic_y-4.pdf}
+    \includegraphics[scale=0.3]{analytic_y-4.pdf}
     \caption{Our reverse fitting method to determine total CCSNe contribution}
@@
     \centering
-    \includegraphics[scale=0.5]{figures/fiorenzo_vs_jack_c-1.pdf}
-    \includegraphics[scale=0.5]{figures/fiorenzo_vs_jack_n-1.pdf}
-    \caption{A comparison of estimated stellar birth abundance trends from the subgiant sample and \citet{2021arXiv210603912V}
+    \includegraphics[scale=0.5]{fiorenzo_vs_jack_c-1.pdf}
+    \includegraphics[scale=0.5]{fiorenzo_vs_jack_n-1.pdf}
+    \caption{A comparison of estimated stellar birth abundance trends from the subgiant sample and
+        \citet{fiorenzo+21}
     }
@@
 \section{Effects of Alternate AGB Models}\label{sec:alt_agb}
+
+\begin{table}
+	\centering
+	\caption{For each AGB yield set, our calculation of the effective SFH- and IMF-weighted carbon AGB yield, along with the multiplicative factor to reach an AGB contribution of 20.}
+	\label{tab:alpha_agb}
+	\begin{tabular}{lcr} % four columns, alignment for each
+		\hline
+		Study & $y_{\rm C, 0}^{\rm agb}$ & $\alpha_{\rm agb, 20}$\\
+		\hline
+		C11 & 0.000347 & 2.9\\
+		K10 & 0.000585 & 1.7\\
+		V13 & 0.000060 & 16.5\\
+		K16 & 0.000421 & 2.4\\
+		\hline
+	\end{tabular}
+\end{table}
 
@@
 \begin{figure*}
-\includegraphics[scale=0.45]{figures/agb_adj-2.pdf}
-\includegraphics[scale=0.45]{figures/abg_adj_z-1.pdf}
+\includegraphics[scale=0.45]{agb_adj-2.pdf}
+\includegraphics[scale=0.45]{abg_adj_z-1.pdf}
 

### 2023-03-13 sciplot/src/plotting/figure.py

@@ -1,30 +1,0 @@
-import matplotlib as mpl
-
-import pyplot as plt
-
-class figure:
-    """
-    This class is designed to 
-    make modifications and handeling MPL's
-    figure class easier
-    """
-    __init__(**kwargs):
-        self.create_fig()
-
-    create_fig(self, **kwargs):
-        self.fig, self.ax = mpl.figure(**kwargs)
-
-    resize_fig(self):
-        ax_width
-
-
-    @property
-    def ax_width(self):
-        return (self.fig.subplotpars.right -
-                self.fig.subplotpars.left)*self.fig.get_figwidth()
-
-    @property
-    def ax_heighth(self):
-        return (self.fig.subplotpars.top -
-                self.fig.subplotpars.bottom)*self.fig.get_figheighth()
-

### 2023-03-13 src/analysis/plotting_utils.py

@@ -37,8 +37,7 @@ def fancy_legend(ax=None, colors=COLORS, **kwargs):
     if ax is None:
         ax = plt.gca()
        
-    leg = ax.legend(frameon = False, handlelength = 0, columnspacing = 0.8, 
-                    **kwargs)
+    leg = ax.legend(frameon = False, handlelength = 0, columnspacing = 0.8, **kwargs)
     for i in range(len(leg.get_texts())):
         leg.get_texts()[i].set_color(colors[i % len(colors)])
         leg.legendHandles[i].set_visible(False)

### 2023-03-15 carbon_paper/tex/main.tex
paper updates

@@
 \usepackage{amsmath}	% Advanced maths commands
+\usepackage{abbrevs}
 % \usepackage{amssymb}	% Extra maths symbols
@@
 \defcitealias{ventura+13}{V13}
+\defcitealias{karakas10}{K10}
+\defcitealias{KL16}{KL16}
+\defcitealias{karakas+18}{K18}
 
 \newcommand{\cristallo}{\citetalias{cristallo+11}+\citetalias{cristallo+15}}
+\newcommand{\karakas}{\citetalias{karakas10}}
+\newcommand{\kl}{\citetalias{KL16}+\citetalias{karakas+18}}
+\newcommand{\ventura}{\citetalias{ventura+13}}
 
-% Please keep new commands to a minimum, and use \newcommand not \def to avoid
-% overwriting existing commands. Example:
-% \newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared
+\newabbrev\CC{Core Collapse Supernovae (CCSNe)}[CCSNe]
+
 \newcommand{\VICE}{\texttt{VICE}}
+\newcommand{\caah}{[C/Mg]-[Mg/H]}
+\newcommand{\caafe}{[C/Mg]-[Mg/Fe]}
+
+\newcommand{\zoo}{\ensuremath{Z/Z_{\sun }}}
+\newcommand{\Ycc}{\ensuremath{Y_{\rm C}^{\rm cc}}}
+\newcommand{\Yct}{\ensuremath{Y_{\rm C, 0}^{\rm tot}}}
+\newcommand{\Yoc}{\ensuremath{Y_{\rm O}^{\rm cc}}}
+\newcommand{\Ycagb}{\ensuremath{Y_{\rm C}^{\rm agb}}}
 
@@
 
-Asymptotic Giant Branch (AGB) stars are known to be importaint (cite) from stellar model predictions, previous GCE, and evidence from abundance patterns. (are there detections in PN?)
+AGB stars are known to be importaint (cite) from stellar model predictions, previous GCE, and evidence from abundance patterns. (are there detections in PN?)
 
-CCSNe are also important (.... SN reminant measurments)
+\CC are also important (.... SN reminant measurments)
 
@@
 
-In Figure \ref{fig:sum} we present a sample of APOGEE subgiants.
+In Fig.
+\ref{fig:subgiants} we present a sample of APOGEE subgiants.
 These subgiants were chosen based on their location in the HR diagram based on criteria in \citet{jack_subgiant} replicated in Appendix \ref{sec:jack}.
@@
     \caption{Chemical abundance relationships of our sample of APOGEE subgiants (see Jack et al. 2023). Left panel shows }
-    \label{fig:sum}
+    \label{fig:subgiants}
 \end{figure*}
@@
 
-Galactic chemical evolution are fundamentally intertwined with our understanding of stellar nucleosynthesis.
-In this paper, we are concerned with three major nucleosynthetic pathways: AGB stars, CCSNe, and Supernovae type Ia.
-While only AGB stars and CCSNe are producers of carbon, SNeIa Fe can be used to compare with the AGB delayed carbon component.
+Galactic chemical evolution are fundamentally intertwined with our
+understanding of stellar nucleosynthesis. In this paper, we are concerned with
+three major nucleosynthetic pathways: AGB stars, \CC, and Supernovae type Ia.
+While only AGB stars and \CC are producers of carbon, SNeIa Fe can be used to
+compare with the AGB delayed carbon component.
 
-\VICE allows us to explore the nucleosynthesis of various models, as it includes AGB tables for C11, et.c
+\VICE allows us to explore the nucleosynthesis of various models, as it
+includes AGB tables for C11, et.c
 
-We discuss carbon nucleosythesis in more detail in the next two sections.
-We assume that the only dominant sources of carbon are from AGB stars and CCSNe/massive star winds.
-***JUSTIFY***.
-Below  is a brief overview of our  nucleosythetic assumptions of other elements.
+We discuss carbon nucleosythesis in more detail in the next two sections. We
+assume that the only dominant sources of carbon are from AGB stars and CCSNe/massive star winds. ***JUSTIFY***. Below  is a brief overview of our  nucleosythetic assumptions of other elements.
 
@@
 \begin{itemize}
-    \item \citetalias{cristallo+11}
-    \item \cristallo
-    \item \cite[C11][Hi]{cristallo+11}: \citet{cristallo+11}
-    \item K10: \citet{karakas10}
-    \item V13: \citet{ventura+13}
-    \item K16: \citet{KL16}
+    \item \citet{cristallo+11} and \citet{cristallo+15} (\cristallo).
+    \item \citet{karakas10} (\karakas)
+    \item \citet{ventura+13} \ventura
+    \item \citet{KL16} \citet{karakas+18} \kl
 \end{itemize}
@@
 
-Figure \ref{fig:y_agb} compares the net fractional AGB carbon yield, $m_\text{C}^\text{AGB}(M, Z)$ for each AGB model we consider.
+Fig.
+\ref{fig:y_agb} compares the net fractional AGB carbon yield, $m_\text{C}^\text{AGB}(M, Z)$ for each AGB model we consider.
 Note that the yields may be negative when the birth abundance is higher than the carbon abundance of the material ejected back to the ISM.
@@
 
-We summarise many of the predictions of stellar models in Figure \ref{fig:y_cc}. Pink squares
+We summarise many of the predictions of stellar models in Fig. \ref{fig:y_cc}. Pink squares
 represent \citep{NKT13}, etc. etc.
@@
 
-To simulate the chemical evolution of a Milky way like galaxy, we use the Versitile Integrator for
-Chemical Evolution (\VICE\footnote{\VICE~is available at \url{https://github.com/giganano/VICE}}) published in \citet{james+21} and also briefly described in
-\citet{james+22}. 
+To simulate the chemical evolution of a Milky-Way-like galaxy, we use the Versitile Integrator for Chemical Evolution (\VICE\footnote{\VICE~is available at \url{https://github.com/giganano/VICE}}) published in \citet{james+21} and also briefly described in \citet{james+22}.
 As a multi-zone model, the galaxy is divided into 200 rings of 0.1kpc, each with separate gas supplies with outflow and inflow rates.
@@
 We also explore a "lateburst" model which is parameterized with a normal distribution multiplying our fiducial "inside-out" SFH as
-\begin{equation}
+\begin{equation}\label{eq:lateburst}
     \dot{\Sigma}_{\rm lateburst} \propto \dot{\Sigma}_{\rm insideout} \left(1 + A e^{-(t-\tau_{\rm burst})^2/2\sigma^2_{\rm burst}} \right)
@@
 
-\subsection{Yield Parameterization}
+\subsection{Model Stellar Yields}
+We define a parameterization of a \CC~yield
   Because of the large uncertainties in CCSNe carbon yields, we choose to explore an analytic expression of the yield enabling us to easily explore how variations of CCSNe carbon yields affect abundance tracks.
@@
 Our expression is:
-    \begin{equation}
-   y_\text{C}^\text{CC}(Z) =  \alpha\ Z^\beta y_\text{O}^\text{CC} + y_\text{C, 0}^\text{CC}
+  \begin{equation}\label{eq:y_yields}
+   Y_\text{C}^\text{CC}(Z) =  \alpha\ Z^\beta Y_\text{O}^\text{CC} + Y_\text{C, 0}^\text{CC}
     \end{equation}
-   	Where we estimate $\alpha = 0.02$ and $\beta = 0.25$ (See Section \ref{equilibrium} ).
+   	Where we estimate $\alpha = 0.02$ and $\beta = 0.25$ (See Section \ref{sec:equilibrium} ).
 Our second model uses $\alpha = 0.44$ and $\beta = 0.63$ with K16 yields and reduced $\eta \rightarrow 1/2 \eta$
@@
 
-We use data from APOGEE DR17 processed with APOSCAP.
+We use data from APOGEE DR17 \citep{apogee17} processed with APOSCAP.
 Since subgiant stars have yet to experience FDU, their atmospheric carbon and nitrogen abundances are still reflective of their birth abundances and do not need mixing corrections.
 
-To select for subgiants, we use the following cut in $\log g$ and $T_{\rm eff}$ which selects stars at the base of the red giant turnoff (FIGURE and \cite{jack_subgiant})
+To select for subgiants, we use the following cut in $\log g$ and $T_{\rm eff}$
+which selects stars at the base of the red giant turnoff (FIGURE and
+\cite{jack_subgiant}). We describe our selection criteria along with a 
+comparison to \citet{fiorenzo+21} in Appendix \ref{sec:jack}.
 
@@
 
-See Appendix \ref{sec:jack} for further discussion of our sample and comparison to FIORENZO.
+While we show the entire dataset in Fig. \ref{fig:subgiants}, we chose to compare the
+binned data to our models as black points with dashes representing the 1-sigma
+spread, as in e.g. Fig. \ref{fig:agb_sims}.
 
@@
 
-We plot time evolution tracks in Figure \ref{fig:c_evo} for $[C/\alpha]-[\alpha/H]$ and $[C/\alpha]-[Fe/H]$ for our fiducial model.
+We plot time evolution tracks in Fig.
+\ref{fig:c_evo} for \caah and \caafe for our fiducial model.
 Each colored track corresponds to a different galactic radius and 1Gyr time steps are marked with crosses on the lines.
@@
 
-This is even more evident in the lower part of Figure \ref{fig:c_evo}, where we instead plot snapshots of the galactic radial trend at different times for our model.
-While the [C/$\alpha$]-[$\alpha$/H] trend reaches almost equilibrium at 5Gyr, the [C/$\alpha$]-[$\alpha$/Fe] trend continues to evolve even until the present day, exposing the effect of the delayed contribution from AGB stars on the evolutionary history.
+This is even more evident in the lower part of Fig. \ref{fig:c_evo}, where we
+instead plot snapshots of the galactic radial trend at different times for our
+model.
+While the \caah trend reaches almost equilibrium at 5Gyr, the \caafe trend continues to evolve even until the present day, exposing the effect of the delayed contribution from AGB stars on the evolutionary history.
 
@@
 \includegraphics{evo_slices-2.pdf}
-\caption{The top set of panes show the time evolution of the gas phase of our fiducial model, plotted as tracks through [C/O]-[O/H] and [C/O]-[O/Fe] where each colored line corresponds to the evolution at that galactic radius.
-The bottom set instead shows the galaxies gas-phase [C/O]-[O/H] and [C/O]-[O/Fe] trend at 5 different time slices. 
+\caption{The top set of panes show the time evolution of the gas phase of our
+    fiducial model, plotted as tracks through \caah and \caafe where each colored line corresponds to the evolution at that galactic radius. 
+The bottom set instead shows the galaxies gas-phase \caah and \caafe trend at 5 different time slices. 
 }
@@
 \subsection{Effects of AGB Yields}
+
 \begin{figure*}
@@
 
-\caption{Abundance tracks for 4 different choices of AGB models.
-Each panel has different abundance ratios on the axis but is otherwise the same.
-The black points are Jack Roberts selection of APOGEE subgiants.
-Each model is plotted as a line representing the mean stellar abundance in each bin on x.}
-\label{fig:stars_abundances}
+\caption{Left: the \caah~ \textbf{median} present-day stellar tracks for four different
+AGB models (\cristallo, \karakas, \kl, and \ventura ). The median bin [C/Mg] values from \citet{jack_subgiant} are
+plotted as black points with 1-std errors marked by horizontal grey dashes.
+Right: same as left but for \caafe. While each AGB yield model may
+differ in detail, there is minimal effect on the overall [C/Mg] trends. }
+\label{fig:agb_sims}
 \end{figure*}
 
-How much does the choice of AGB model affect chemical evolution? 
-Short description of effects of AGB model choices, and how we can rule out models like V21.  Maybe point to appendex B?
+What happens as we change our choice of AGB stellar yields? We consider four models
+using the published yields in \cristallo, \karakas, \kl, and \ventura~in Fig.
+\ref{fig:agb_sims}.
+
+As we chose to leave $Y_{\rm C}^{\rm CC}$ in a functional form, we chose to
+leave the total IMF-averaged carbon yield to be constant. The magnitude of
+$Y_{\rm C}^{\rm CC}$
+\begin{equation}
+    Y_{\rm C}^{0}  = 0.005  =  Y_{\rm C}^{\rm cc} + Y_{\rm C}^{\rm agb}
+\Big \rvert_{Z=Z_\odot}
+\end{equation}
+where we are choosing to evaluate the total IMF \CC and AGB yields at solar
+metallicity. We show our calculations of $Y_{\rm C}^{\rm agb}(Z=Z_{\sun })$  in
+Table \ref{tab:alpha_agb}.
+
+This choice of total carbon yield with our fixed choice of oxygen gives an
+equilibrium value of $Z_{\rm C}/Z_{\rm O} = Y_{\rm C}/Y_{\rm O} = 0.333$ which
+is reasonably consistant with the value in \citet{asplund+09} of $Z_{\rm
+C}/Z_{\rm O}=0.413$ and was chosen as to match the median value of our sample
+at $Z=Z_{\sun }$.
+
+As the highest AGB yield at solar is from our \karakas~model at $Y_{\rm C}^{\rm
+agb} = 0.000585$ is only 11.7 percent of our required total carbon production,
+each of these models is dominated by \CC production of carbon. As a result,
+while the metallicity dependence of the \caah may vary, the
+\caafe diagnostic shows how this small AGB fraction makes the details of
+the AGB model and delay-time-distribution unchange the galaxy production of
+carbon.
+
+Appendix \ref{sec:alt_agb} describes the effects of increasing the AGB model on
+resulting abundance trends. However, we use the \cristallo AGB yields for the
+rest of the main discussion.
 
@@
 
+\begin{table}
+	\centering
+	\caption{For each AGB yield set, our calculation of the effective SFH- and IMF-weighted carbon AGB yield, along with the multiplicative factor to reach an AGB contribution of 20.}
+	\label{tab:alpha_agb}
+	\begin{tabular}{lcr} % four columns, alignment for each
+		\hline
+		Study & $y_{\rm C, 0}^{\rm agb}$ & $\alpha_{\rm agb, 20}$\\
+		\hline
+		C11 & 0.000347 & 2.9\\
+		K10 & 0.000585 & 1.7\\
+		V13 & 0.000060 & 16.5\\
+		K16 & 0.000421 & 2.4\\
+		\hline
+	\end{tabular}
+\end{table}
+
 \begin{equation}
-    \alpha_{AGB} = f_{agb} \frac{y_{desired}}{y_0^{agb}}
+    \alpha_{\rm agb} = f_{\rm agb} \frac{\Yct}{\Ycagb}
 \end{equation}
 \begin{equation}
-    \alpha_{CC} = (1 - f_{agb}) \frac{y_{desired}}{y_0^{cc}}
+    \alpha_{\rm CC} = (1 - f_{\rm agb}) \frac{\Yct}{\Ycc}
 \end{equation}
 
-\subsection{Star Formation History}
+\subsection{Metallicity dependence and the AGB Fraction}
+The next question is how does changing the CCSNe carbon yield affect the model?
+We now consider variations of our fiducial model:
+\begin{itemize}
+    \item $f_{\rm agb} = 0.2$
+    \item AGB model: \cristallo
+    \item $Z_{\rm C}^{\rm cc} = 0.004 (Z/Z_{\sun })^{0.4}$ ($\beta = 4$)
+\end{itemize}
 
-We do run models with an alternate "lateburst" stars formation history.
+We could chose to vary the value of $\alpha$; however, the overall scaling of
+yields is unknown so our constraint is really that $Y_{\rm C}/Y_{\rm O} =
+0.dfsjkhld$, based on binning from our data. As discussed in the previous
+section, we chose to leave the total value of the IMF integrated yield fixed,
+and then assert the AGB fraction (next section) and scale the AGB yields from
+literature appropriety. As such,
 
-equation of lateburst
+As we display in Fig. \ref{fig:beta_f}, we observe that changes in $\beta$ are
+approprietly reflected in the resulting \caah~trend. As the metallicity
+dependence steepens with higher $\beta$, the [C/Mg] ratio becomes
+correspondingly more dependent on [Mg/H].
 
-However, we find that the star formation history has a negligable effect on the shape of the mean track.
-More drastic changes in SFH could explain the high alpha/low alpha seperation but we leave further exploration of SFH to future work.
+Wow! Equilibrium!! See section \ref{sec:equilibrium}
 
-% \begin{figure*}
-% \includegraphics[width=1.5\columnwidth]{cooh_lateburst.pdf}
-% \caption{Same as Fig. \ref{fig:stars_abundances} but with different model choices.}
-% \end{figure*}
+Importantly, the \caafe trend is mostly unaffected by choosing a different
+CCSNe yield. As all CCSNe enrichment happens at the same, rapid timescale, by
+taking a slice in [Mg/H], this metallicity dependence is effectively ignored as
+the only effect can be a vertical offset if the slice is narrow enough.
 
-\begin{figure*}
-\includegraphics[scale=0.6]{beta-1.pdf}
-\includegraphics[scale=0.6]{f_agb-1.pdf}
+So, the scaling of the trend and metallicity dependence of carbon (as seen in
+the \caah~trend) gives information on the total carbon yield and the behavior
+of CCSNe (as the dominating producer of carbon);
+the \caafe trend exposes the delayed effect of carbon from AGB contribution.
 
-\caption{Similar to \ref{fig:stars_abundances} except the top plot shows the fiducial model with lower and higher values of $\beta$, the C-CCSNe metallicity dependence.
-The bottom plot is the same except shows varying AGB fractions.}
-\end{figure*}
-
-\begin{figure*}
-\includegraphics[scale=0.6]{lateburst_eta-1.pdf}
-
-\caption{Same as Figure \ref{fig:stars_abundances} but comparing the fiducial model to the reduced outlow model and a lateburst model. (okay, need to totally change approach...)}
-\end{figure*}
-
-\subsection{Adjusted CCSNe Yields}
-
-\begin{figure}
-    \includegraphics[scale=0.6]{cooh_scatter.pdf}
-    \caption{The simulated stars of our model at present day plotted on [C/O]-[O/H] and colored such that lighter colors represent stars born at greater galactric radii.}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[scale=0.6]{cnoh.pdf}
-    \caption{Caption}
-    \label{fig:cnofe}
-\end{figure}
-
-\begin{figure*}
-\centering
-\includegraphics[]{summary-2.pdf}
-\caption{Present-day gas phase tracks of the fiducial model in [C/O]-[O/H] space. M101 is valid comparison to MW ...(van Dokkum et al. 2014)}
-\label{fig:gas_phase}
-\end{figure*}
 \subsection{The AGB Fraction }
@@
 
-We find that we can adjust both the outflows and scale down the yields if we change our model for $y_\text{C}^\text{CC}/y_\text{O}^\text{CC}$.
-For example, reducing outflows and CCSNe yields by a factor of two requires the modified parameters
-$\alpha = 0.033$ and $\beta = 0.625$, which results in a slightly lower value at solar but nearly a doubling of the metallicity dependence.
-
-These models are indistinguishable in the [C/O]-[O/H] plane from our adjusted CCSNe model, so future work investigating the SFH and carbon isotopic ratios in more depth may be able to provide more insight.
+These models are indistinguishable in the \caah~plane from our adjusted CCSNe model, so future work investigating the SFH and carbon isotopic ratios in more depth may be able to provide more insight.
 In the next section, we develop the analytic tools to explore this problem in more depth.
 
+\subsection{Star Formation History}
+
+We consider a simple modification of our SFH described by our lateburst model
+(see Equation \ref{eq:lateburst})
+
+equation of lateburst
+
+However, we find that the star formation history has a negligable effect on the shape of the mean track.
+More drastic changes in SFH could explain the high alpha/low alpha seperation but we leave further exploration of SFH to future work.
+
+\begin{figure*}\label{fig:beta_f}
+\includegraphics[scale=0.6]{beta-1.pdf}
+\includegraphics[scale=0.6]{f_agb-1.pdf}
+
+\caption{Similar to \ref{fig:agb_sims} except the top plot shows the fiducial model with lower and higher values of $\beta$, the C-CCSNe metallicity dependence.
+The bottom plot is the same except shows varying AGB fractions.}
+\end{figure*}
+
+\begin{figure*}
+\includegraphics[scale=0.6]{lateburst_eta-1.pdf}
+
+\caption{Same as Fig. \ref{fig:agb_sims} but comparing the fiducial model to the reduced outlow model and a lateburst model. (okay, need to totally change approach...)}
+\end{figure*}
+
+\begin{figure}
+    \includegraphics[scale=0.6]{cooh_scatter.pdf}
+    \caption{The simulated stars of our model at present day plotted on \caah~and colored such that lighter colors represent stars born at greater galactric radii.}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[scale=0.6]{cnoh.pdf}
+    \caption{Caption}
+    \label{fig:cnofe}
+\end{figure}
+
+\begin{figure*}
+\centering
+\includegraphics[]{summary-2.pdf}
+\caption{Present-day gas phase tracks of the fiducial model in \caah~space. M101 is valid comparison to MW ...(van Dokkum et al. 2014)}
+\label{fig:gas_phase}
+\end{figure*}
 \subsection{Outflows}
@@
 
-We have found that the [C/O]-[O/Fe] relationship may provide insight into this issue.
+We have found that the \caah~relationship may provide insight into this issue.
 [O/Fe] is a tracer of the relative contributions of CCSNe and delayed-time sources in chemical evolution.
 So, the appearance of a slope in [O/Fe] implies that there is a substantial delay-time process in carbon evolution.
-The metallicity-dependence of carbon yields complicates this picture because younger stars have higher [O/Fe] as the SNeIa contributions take up to 10Gyr, so metal-poor young stars will naturally have lower [C/O], agreeing with the slope observed in [C/O]-[O/Fe].
-However, a pure CCSNe carbon model cannot reproduce the slope accurately as
+The metallicity-dependence of carbon yields complicates this picture because
+younger stars have higher [O/Fe] as the SNeIa contributions take up to 10Gyr,
+so metal-poor young stars will naturally have lower [C/O], agreeing with the
+slope observed in\caafe. However, a pure CCSNe carbon model cannot reproduce the slope accurately as
 
-\subsection{Comparison to HII Region Observations}
-In Figure \ref{fig:gas_phase}, we plot our two favorite models against HII-region measured carbon abundances from **********
+We find that we can adjust both the outflows and scale down the yields if we change our model for $y_\text{C}^\text{CC}/y_\text{O}^\text{CC}$.
+For example, reducing outflows and CCSNe yields by a factor of two requires the modified parameters
+$\alpha = 0.033$ and $\beta = 0.625$, which results in a slightly lower value at solar but nearly a doubling of the metallicity dependence.
+
+\subsection{Comparison to Observations}
+
+Beyond Milky Way stars, astronomers have observed carbon to oxygen ratios in
+HII-regions through either Recombination Lines or (OTHER TEchnique0), enabling
+us to probe gas-phase abundances of carbon in our galaxy and other types of
+galaxies from dwarf to elliptical.
+
+In Fig. \ref{fig:gas_phase}, we plot our fiducial model's gas phase abundances
+at present day and 2Gyr compared to C/O
+abundances measured in both stars, our subgiant sample, halo stars, galaxies,
+and even Damped Lynman Alpha (DLA) systems.
 
@@
 
+Measuring carbon in the gas phase is challenging. Carbon emission lines are
+very weak compared to other common lines, (visible/etc.).
+Temperature/modelining limitations. Lack of strong HII calibration.
+
 Short discussion of measurment challenges in extragalactic galaxies, how other galaxies and dwarf SFH may come into play, why this relation is notecably steeper.
 
-\section{The Equilibrium Approximation}\label{equilibrium}
+Our model fails to capture the trend past [$\alpha$/H]$=-1$. As our knowledge
+of stellar evolution is limited, our knowledge of extremely metal poor stellar
+evolution is extremely limited. (despite a pure H/He born star appearing
+simpler lolol). A variety of explanation for the increasing relative carbon
+enrichments for metal-poor stars have been proposed (e.g. ...). The likely case
+that Population III star supernovae produced high abundances of carbon seems
+most plausable, especially given our uncertainty in the carbon yields and the
+short timescales required to create this enhancement (e.g. $z\sim 2$ DLA,
+dwarfs, etc.) make it unlikely that AGB stars could be the culprit.
+
+As any constraints in this regieme are poor, we choose to only qualitatively
+conclude that CCSNe carbon production increases at extremely low metallicity
+but the details of this remains an open question.
+
+Can we use our yield estimations and apply them to extragalactic sources successfully?
+
+Explain Berg+19,
+
+Bursty SFH may not be needed to explain scatter as the C/O slope + differet evolutionary timescales is capable alone of reproducing this scatter.
+
+While the extragalactic trend appears to be more steeply sloped than our models, this is because of ***e.g. mass-dependent outflow rates/differening SFH between galaxies.
+
+\section{The Equilibrium Approximation}\label{sec:equilibrium}
 If we assume that the median track is an equilibrium phenomenon, we can calculate the total carbon to oxygen yield ratio.
@@
 
-Rewriting in terms of the observed abundance ratio and dividing by $y_\text{O}^\text{CC}$.
-So, given the outflows or CCSNe oxygen yields, the carbon AGB yield, and the [C/O]-[O/H] mean abundance track, we can estimate the CCSNe carbon yield.
-Written as a relative yield:
+Rewriting in terms of the observed abundance ratio and dividing by
+$y_\text{O}^\text{CC}$. So, given the outflows or CCSNe oxygen yields, the
+carbon AGB yield, and the \caah mean abundance track, we can estimate the CCSNe carbon yield. Written as a relative yield:
 \begin{equation}
@@
 
-\section{Modeling extragalactic carbon trends}
-Can we use our yield estimations and apply them to extragalactic sources successfully?
-
-Explain Berg+19,
-
-Bursty SFH may not be needed to explain scatter as the C/O slope + differet evolutionary timescales is capable alone of reproducing this scatter.
-
-While the extragalactic trend appears to be more steeply sloped than our models, this is because of ***e.g. mass-dependent outflow rates/differening SFH between galaxies.
-
 \section{Conclusions}
 
-The last numbered section should briefly summarise what has been done, and describe
-the final conclusions which the authors draw from their work.
+Directions-->SneIa/AGB trends as a constraint on DTD.
+Observations of Carbon in metal poor stars, extragalactic (call out any
+existing surveys in e.g. APOGEE/DESI?)
+Abundance ratios (e.g.C12/C13) as additional constraints
 
@@
 
-We compare both of **** in Figure \ref{fig:fiorenzo_jack}.
+We compare both of **** in Fig. \ref{fig:fiorenzo_jack}.
 
@@
 
-\begin{table}
-	\centering
-	\caption{For each AGB yield set, our calculation of the effective SFH- and IMF-weighted carbon AGB yield, along with the multiplicative factor to reach an AGB contribution of 20.}
-	\label{tab:alpha_agb}
-	\begin{tabular}{lcr} % four columns, alignment for each
-		\hline
-		Study & $y_{\rm C, 0}^{\rm agb}$ & $\alpha_{\rm agb, 20}$\\
-		\hline
-		C11 & 0.000347 & 2.9\\
-		K10 & 0.000585 & 1.7\\
-		V13 & 0.000060 & 16.5\\
-		K16 & 0.000421 & 2.4\\
-		\hline
-	\end{tabular}
-\end{table}
-
 While we focus the main discussion of the paper on the C11 model, other AGB models can have notable effects on abundance trends at ***
 
-Because the predictions of the AGB yield models we consider are dwarfed by the required CCSNe carbon production to match observations (see Figure ***), we briefly explore here the effects of variations in AGB models affect abundance trend predictions when these models are amplified to match observational [C/MG]-[Mg/Fe] trends.
+Because the predictions of the AGB yield models we consider are dwarfed by the
+required CCSNe carbon production to match observations (see Fig.
+***), we briefly explore here the effects of variations in AGB models affect abundance trend predictions when these models are amplified to match observational [C/MG]-[Mg/Fe] trends.
 
@@
 
-\caption{Same as \ref{fig:stars_abundances} but comparing our fiducial model to our recommended z-dependent $y_\text{C}^\text{CC}$ model.
+\caption{Same as \ref{fig:agb_sims} but comparing our fiducial model to our recommended z-dependent $y_\text{C}^\text{CC}$ model.
 A plot of the stars of our favored CCSNe model colored by radius.

### 2023-03-15 __init__.py

@@ -1,0 +1,4 @@
+
+from . import src
+from .src import analysis
+from .src import simulation

### 2023-03-15 src/__init__.py

@@ -1,0 +1,3 @@
+__all__ = ["simulation", "analysis"]
+from . import simulation
+from . import analysis

### 2023-03-15 src/analysis/__init__.py

@@ -1,0 +1,6 @@
+__all__ = ["apogee_analysis", "carbon_yield_plots", "plotting_utils", "vice_model"]
+
+from . import apogee_analysis
+from . import carbon_yield_plots
+from . import plotting_utils
+from . import vice_model

### 2023-03-15 src/analysis/carbon_yield_plots.py

@@ -1,7 +1,7 @@
 import matplotlib.pyplot as plt
 import numpy as np
 import vice
-import apogee_analysis as aah
+from . import apogee_analysis as aah
 
 
 def plot_c_table(study = "cristallo11", ax=None, fig=None, **kwargs):

### 2023-03-15 src/simulation/__init__.py

@@ -1,0 +1,4 @@
+__all__ = ["multizone_sim.py", "vice_to_json.py"]
+
+from . import multizone_sim
+from . import vice_to_json

### 2023-03-21 __init__.py
line plot

@@ -1,5 +1,4 @@
 from .figure import Figure, Subplot, save_at, Legend, JoinPlot, SubFigure, Length
-from .plotting import Scatter, Colorbar
+from .plotting import Scatter, Colorbar, Line
 from .style import style
 
-# from .plotting import Plot, Scatter, Line

### 2023-03-21 figure/legend.py

@@ -1,10 +1,11 @@
 from matplotlib import pyplot as plt
 
 class Legend:
-    def __init__(self, subplot):
+    def __init__(self, subplot, **kwargs):
         self.labels = subplot.labels
+        
 
-        self.mpl_leg = subplot.mpl_ax.legend(subplot.handles, self.labels, frameon=False)
+        self.mpl_leg = subplot.mpl_ax.legend(subplot.handles, self.labels, frameon=False, **kwargs)
         subplot.add_legend(self)
 
     @property
@@ -39,7 +40,7 @@ class Legend:
             h.set_visible(False)
 
         self.mpl_leg.handlelength = 0
-        self.mpl_leg.columnspacing = 0
+        self.mpl_leg.columnspacing = 0.8
 
     def color_labels(self, alpha=None):
         texts = self.mpl_leg.get_texts()
@@ -48,10 +49,19 @@ class Legend:
 
     @property
     def colors(self):
-        if len(self.handles[0].get_color()) != 4:
-            return [h.get_color()[0] for h in self.handles]
-        else:
-            return [h.get_color() for h in self.handles]
+        cs = []
+        for handle in self.handles:
+            c = handle.get_color()
+            if isinstance(c, str):
+                cs.append(c)
+            elif isinstance(c, list):
+                if isinstance(c[0], (str, float)):
+                    cs.append(c)
+                elif isinstance(c, list):
+                    cs.append(c[0])
+                else:
+                    print("not implemented")
+        return cs
 
     @colors.setter
     def colors(self, cs):

### 2023-03-21 figure/subplot.py

@@ -32,13 +32,14 @@ class Subplot():
         self._layers = []
 
         self.lc_cycle = cycle(COLORS)
+        self.ls_cycle = cycle(["-", ":", "--", "--."])
         self.mc_cycle = cycle(COLORS)
         self.ms_cycle = cycle(MARKERS)
 
 
 
     def next_linesty(self):
-        return next(self.lc_cycle)
+        return next(self.lc_cycle), next(self.ls_cycle)
 
     def next_marksty(self):
         return next(self.mc_cycle), next(self.ms_cycle)
@@ -67,11 +68,19 @@ class Subplot():
 
     @property
     def labels(self):
-        return [lay.label for lay in self.layers]
+        ls = []
+        for lay in self.layers:
+            if lay.label != "":
+                ls.append(lay.label)
+        return ls
 
     @property
     def handles(self):
-        return [lay.handle for lay in self.layers]
+        hs = []
+        for lay in self.layers:
+            if lay.label != "":
+                hs.append(lay.handle)
+        return hs
 
     @property
     def figure(self):

### 2023-03-21 plotting/__init__.py

@@ -1,4 +1,5 @@
 from .scatter import Scatter
 from .data import PlotData
 from .colorbar import Colorbar
+from .line import Line
 

### 2023-03-21 plotting/colorbar.py

@@ -6,11 +6,14 @@ from ..figure.axis import Axis
 class Colorbar(Subplot):
     cmin = 0
     cmax = 1
-    def __init__(self, layer, figure=None, row=None, col=None):
+    def __init__(self, layer=None, subplot=None, mappable=None, figure=None, 
+                 row=None, col=None, width=None):
 
         self.layer = layer
 
-        self._sp = layer.subplot
+        if subplot is None:
+            subplot = layer.subplot
+        self._sp = subplot
 
         if figure is None:
             figure = self._sp.figure
@@ -21,10 +24,16 @@ class Colorbar(Subplot):
 
         self.figure = figure
 
-        self._width = self._sp.width * 0.05
+        if width is None:
+            self._width = self._sp.width * 0.05
+        else:
+            self._width = width
+
         self._height = self._sp.height
 
-        self.map = self.layer.mpl_map
+        if mappable is None:
+            mappable = self.layer.mpl_map
+        self.map = mappable
 
         self.mpl_ax = self.figure.mpl_fig.add_subplot()
 

### 2023-03-21 plotting/layer.py

@@ -6,7 +6,7 @@ from .. import Figure
 class Layer:
     def __init__(self, subplot=None):
         if subplot is None:
-            fig = Figure()
+            fig = Figure(add_subplot=True)
             subplot = fig.children[0][0]
 
         self.subplot = subplot

### 2023-03-21 plotting/line.py

@@ -1,0 +1,120 @@
+import matplotlib.pyplot as plt
+from matplotlib.lines import Line2D
+import matplotlib as mpl
+import numpy as np
+
+from ..figure import Figure
+from .data import PlotData
+from .layer import Layer
+
+
+class Line(Layer):
+    ls = "-"
+    def __init__(self, x, y, color=None, linewidth=None, subplot=None, linestyle=None, 
+                 size=None, **kwargs):
+        """
+        A simple line plot
+
+        Parameters
+        ----------
+        x: array-like
+        y:
+        subplot: [Defaut=None]
+        color: [None]
+        """
+
+        super().__init__(subplot)
+        self.set(x=x, y=y, lw=linewidth, color=color, ls=linestyle)
+
+        self.plot(**kwargs)
+
+
+    def set(self, x, y, ls, color, lw):
+        self.mpl_plot = None
+
+        self.color = color
+        self.linestyle = ls
+        self.linewidth = lw
+
+        # only use subplot cycler if needed
+        # so we don't increment otherwise
+        if (ls is None) or (color is None):
+            lcolor, lsty = self.subplot.next_linesty()
+            if ls is None:
+                self.linestyle = ls
+            if color is None:
+                self.color = lcolor
+
+        self.data = PlotData(x=x, y=y)
+
+        return self
+
+
+    def plot(self, **kwargs):
+        self.mpl_plot = self.mpl_ax.plot(self.data.x, self.data.y, lw=self.linewidth, 
+                                         color=self.color, ls=self.linestyle, **kwargs)
+
+        self.update()
+
+    def update(self):
+        pass
+
+    # ------------- class properties --------------
+
+
+    @property
+    def x(self):
+        return self.data.x
+
+    @x.setter 
+    def x(self, a):
+        self.data.x = x
+        self.mpl_plot.set_offsets(self.data.x, self.data.y)
+
+    @property
+    def color(self):
+        return self._color
+
+    @color.setter
+    def color(self, c):
+        if self.mpl_plot is not None:
+            self.mpl_plot.set_color(c)
+        self._color = c
+
+
+    @property
+    def label(self):
+        return self._label
+
+    @label.setter
+    def label(self, label):
+        self._label = label
+
+    @property
+    def linewidth(self):
+        return self._lw
+
+    @linewidth.setter
+    def linewidth(self, w):
+        if w is not None and self.mpl_plot is not None:
+            self.mpl_plot.set_linewidth(w)
[…]

### 2023-03-21 plotting/scatter.py

@@ -87,7 +87,7 @@ class Scatter(Layer):
         self._clim = clh
 
         norm = mpl.colors.Normalize(*self.clim)
-        cmap = mpl.cm.get_cmap()
+        cmap = mpl.colormaps["plasma"]
         self.mpl_map = mpl.cm.ScalarMappable(norm, cmap)
 
         self.update()

### 2023-03-21 style/style.py

@@ -5,6 +5,7 @@ import os
 
 COLORS = ['#0173b2', '#de8f05', '#029e73', '#d55e00', '#cc78bc', 
           '#ca9161', '#fbafe4', '#949494', '#ece133', '#56b4e9']
+COLORS = ['#648FFF', '#DC267F', '#FFB000', '#785EF0', '#FE6100']
 MARKERS = ['o', '+', '^', '*', 's', 
            'd', 'o', 'x', '1']
 FILL =    [True,  True,  True,  True,

### 2023-03-21 carbon_paper/tex/main.tex
more plot fixes

@@
 
-A fundamental question of Galactic Chemical Evolution (GCE) is understanding the physical processes which make each element.
+Where does each chemical element come from?
+
 Stellar evolution models can be used to predict how much of each element stars with a variety of physical properties produce.
@@
 
-Galactic chemical evolution are fundamentally intertwined with our
-understanding of stellar nucleosynthesis. In this paper, we are concerned with
-three major nucleosynthetic pathways: AGB stars, \CC, and Supernovae type Ia.
-While only AGB stars and \CC are producers of carbon, SNeIa Fe can be used to
-compare with the AGB delayed carbon component.
+Modern theoretical nucleosynthesis provides our starting point for our models.
+We focus on three primary nucleosynthetic pathways: AGB stars, CCSne, and SNeIa.
+Each process has unique timescales and element production which we can trace through the tools of GCE.
+While carbon is only known to be produced in AGB stars and CCSNe, comparing carbon to iron production (from SNeIa) adds a valuable constraint to our models and insight into the delay-time production of carbon.
 
-\VICE allows us to explore the nucleosynthesis of various models, as it
-includes AGB tables for C11, et.c
+After a group of stars are formed, CCSNe from massive stars are the first enrichment, providing light elements such as C, O, and Mg and heavier elements such as Fe and beyond.
+Importaintly, $\alpha$ elements like O and Mg are only formed in CCSNe (in significant quantities).
+Next, low mass stars begin to reach the end of their lives.
+The dying breaths of AGB stars are known to be importaint sources of C, N, and a smattering of heavier elements.
+Finally, the white dwarfs, including formation and time to collide/over-eat, explode, releasing much of Fe and nearby elements.
 
-We discuss carbon nucleosythesis in more detail in the next two sections. We
-assume that the only dominant sources of carbon are from AGB stars and CCSNe/massive star winds. ***JUSTIFY***. Below  is a brief overview of our  nucleosythetic assumptions of other elements.
+We focus on O and Mg as $\alpha$ elements only formed in CCSNe, and use Fe to
+trace delayed enrichment from SNeIa. C and N are both formed in AGB and CCSNe.
 
-Let $y_{\rm X}^{\rm proc}(M, Z)$ be the fractional yield of element X by a process proc for stars of a mass $M$ (in solar masses) and at metallicity $Z$ defined as: 
+We use IMF-Integrated yields calculated with \VICE~throughout this paper (see
+section \ref{sec:vice}, \citet{james+21, james+22}). For an element X and star
+with mass $M$, the stellar yield $y$ is defined as the net production of X relative 
+to $M$, or
 \begin{equation}
-    y_{\rm X} = \frac{M_{\rm X,\ ej} - M_{\rm X,\ birth}}{M}   
+    y_{\rm X} = \frac{M_{\rm X,\ ejected} - Z_{0, X} M_{\rm ejected}}{M}   
 \end{equation}
+where we let $M_{\rm ejected}$ and $M_{\rm X, ejected}$ be the total ejected
+stellar mass (through winds and supernovae ejecta) and the ejected mass of X,
+and $Z_{0, X}$ was the birth mass fraction of element X.
 
-Where $M_{\rm X,\ ej}$ and $M_{\rm X,\ birth}$ are the mass of element X ejected and initially present in the star. 
+More useful for GCE are Initial Mass Function (IMF) yields, where we sum up the
+contributions of all stars which produce an element.
 We define the IMF-integrated yield of X with: 
@@
 
-There are two $\alpha$-elements we care about: Mg and O.
-Stellar observations of magnesium are more reliable but oxygen abundances are easier to measure in HII regions.
-We assume that both Mg and O are produced entirely in CCSNe with constant, metallicity-independent yields.
-Thus $\text{[Mg/H]} = \text{[O/H]} = [\alpha/\text{H}]$ in our models
+There are two $\alpha$-elements we care about: Mg and O. Stellar observations
+of magnesium are more reliable but oxygen abundances are easier to measure in
+HII regions. We assume that both Mg and O are produced entirely in CCSNe with
+constant, metallicity-independent yields. Thus $\text{[Mg/H]} = \text{[O/H]} =
+[\alpha/\text{H}]$ in our models. (Observational validation?)
 
-\begin{itemize}
-    \item observational validation
-\end{itemize}
 For carbon, the dominant producer is from massive stars which eject carbon fused in their cores during CCSNe.
 
-Taken from J21 and J22, we make the following yield assumptions:
+As we focus on the yields of carbon, we keep yields for other elements fixed in
+most models. Taken from \citet{james+21, james+22}, we let
 \begin{itemize}
@@
 \end{itemize}
-Also following J21/J22, we take the SNeIa Delay Time distribution to be a $t^{-1.1}$ law based on
-the observations by \citet{maoz+12}.
-
-We leave consistent throughout the paper.
-While different CCSNe models predict different absolute values for $y_\text{O}^\text{CC}$, they also predict that the yield is metallicity-independent within the uncertainties of the model.
+Also following \citet{james+21, james+22}, we take the SNeIa Delay Time distribution to be a
+$t^{-1.1}$ law suggested by the observations of \citet{maoz+12}.
 
@@
 
+\begin{figure*}
+    \centering
+ 	    \includegraphics[scale=1]{agb_yields.pdf}\\
+
+    \caption{The net fraction carbon yield ($M_\text{C}$, the amount of carbon produced by the star divided by $M$) plotted as a function of mass, $M$.
+Lighter colors represent higher values of metalicity ([M/H]).
+Each panel represents a different AGB model.
+K10 reports stars at MoverH -3, -2, etc.
+I can reproduce C11 and K10 but not other V13 and KL16 :(((}
+
+    \label{fig:y_agb}
+\end{figure*}
+
+\begin{figure*}
+    \centering
+
+    \includegraphics[scale=1]{y_agb_vs_z.pdf}
+    \includegraphics[scale=1]{y_agb_vs_t.pdf}
+
+    \caption{On the left, we plot the IMF weighted net fractional carbon yields of each AGB model as a function of metalicity.The right panel plots the normalized net carbon AGB yield as a function of time for a population of stars born at the same time at solar metallicity.
+We note that for the right panel, the minimum of the DTD for V13 is }
+
+\end{figure*}
+
 An AGB star is a low mass ($\lesssim 8 M_{\sun}$) star during the final phases of evolution.
-The star has already completed Hydrogen core burning, Hydrogen shell burning during the red giant branch phase, and Helium core burning.
-So, the structure consists of an inert core of carbon and oxygen surrounded by a Helium burning shell and a Hydrogen burning shell.
+The star has already completed hydrogen core burning, Hydrogen shell burning during the red giant branch phase, and helium core burning.
+So, the structure consists of an inert core of carbon and oxygen surrounded by a helium burning shell and a hydrogen burning shell.
 The double shell burning leads to thermal instabilities which drive off the outer layers of the star in a series of violent pulsations, ejecting the envelope and leaving behind a C/O white dwarf.
 
-In an AGB star, TDU and HBB are two major processes involved in carbon production and destruction.
+In an AGB star, two competing processes determine the outcome of carbon production.
+Third Dredge Up (TDU) is needed to eject carbon from the star, enriching the surface with helium-burning-processed material from the core.
+But Hot Bottom Burning (HBB) at the base of the convection layer changes carbon into nitrogen.
 TDU occurs during thermal pulsations, where the convective layer of the star passes into the inner layers with He-burning products which mixes in C and O into the envelope.
@@
 
-\begin{figure*}
-    \centering
- 	    \includegraphics[scale=1]{agb_yields.pdf}\\
-
-    \caption{The net fraction carbon yield ($M_\text{C}$, the amount of carbon produced by the star divided by $M$) plotted as a function of mass, $M$.
-Lighter colors represent higher values of metalicity ([M/H]).
-Each panel represents a different AGB model.
-K10 reports stars at MoverH -3, -2, etc.
-I can reproduce C11 and K10 but not other V13 and KL16 :(((}
-
-    \label{fig:y_agb}
-\end{figure*}
+\subsection{CCSNe carbon}
 
 \begin{figure*}
-    \centering
-
-    \includegraphics[scale=1]{y_agb_vs_z-1.pdf}
-    \includegraphics[scale=1]{y_agb_vs_t-1.pdf}
-
-    \caption{On the left, we plot the IMF weighted net fractional carbon yields of each AGB model as a function of metalicity.The right panel plots the normalized net carbon AGB yield as a function of time for a population of stars born at the same time at solar metallicity.
-We note that for the right panel, the minimum of the DTD for V13 is }
-
+    \includegraphics[scale=0.9]{y_c_cc-2.pdf}
+    \includegraphics[scale=0.9]{y_co_cc.pdf}
+    \caption{The fist plot shows IMF-weighted net fractional CCSNe yield of
+        carbon, $y_C^{cc}$ against metalicity, [M/H], for different studies.
+        The right plot instead shows [C/O]$^\text{CC}$, the logarithm of the
+        abundance ratio of carbon to oxygen if CCSNe were the only carbon
+        source, also as a function of metallicity for the same set of studies.
+        The black line represents the carbon yield of the fiducial model,
+        $y_C^{CC} = 0.004? (Z/Z_{\sun})^{0.3}$, and becomes dashed over regions
+        where we have not tested our model.\citep{NKT13}, \citep{LC18},
+        \citep{sukhbold+16}, \citep{WW95}
+ }
+    \label{fig:y_cc}
 \end{figure*}
-
-\subsection{CCSNe carbon}
 
@@
 
-We summarise many of the predictions of stellar models in Fig. \ref{fig:y_cc}. Pink squares
-represent \citep{NKT13}, etc. etc.
-\citep{LC18}
-\citep{sukhbold+16}
-\citep{WW95}
-
-On the right, we plot the expected CCSNe abundance ratio of each model as a function of metallicity, defining
+We summarise many of the predictions of stellar models in Fig. \ref{fig:y_cc}. 
 \begin{equation}
@@
 Notice how even these ratios
-\begin{figure*}
-    \includegraphics[scale=0.9]{y_c_cc-2.pdf}
-    \includegraphics[scale=0.9]{y_co_cc.pdf}
-    \caption{The fist plot shows IMF-weighted net fractional CCSNe yield of carbon, $y_C^{cc}$ against metalicity, [M/H], for different studies.
-The right plot instead shows [C/O]$^\text{CC}$, the logarithm of the abundance ratio of carbon to oxygen if CCSNe were the only carbon source, also as a function of metallicity for the same set of studies.
-The black line represents the carbon yield of the fiducial model, $y_C^{CC} = 0.004?
-(Z/Z_{\sun})^{0.3}$, and becomes dashed over regions where we have not tested our model.
-}
-    \label{fig:y_cc}
-\end{figure*}
 
@@
 
-\section{The Multizone Model}
+    \section{The Multizone Model}\label{sec:vice}
 
@@
 
+\begin{figure*}
+\label{fig:c_evo}
+\includegraphics{evo_tracks-9.pdf}
+\includegraphics{evo_slices-2.pdf}
+\caption{The top set of panes show the time evolution of the gas phase of our
+    fiducial model, plotted as tracks through \caah and \caafe where each colored line corresponds to the evolution at that galactic radius. 
+The bottom set instead shows the galaxies gas-phase \caah and \caafe trend at 5 different time slices. 
+}
+\end{figure*}
+
 The GCE of carbon is complicated by metallicity dependencies and delayed contributions.
@@
 While the \caah trend reaches almost equilibrium at 5Gyr, the \caafe trend continues to evolve even until the present day, exposing the effect of the delayed contribution from AGB stars on the evolutionary history.
-
-\begin{figure*}
-\label{fig:c_evo}
-\includegraphics{evo_tracks-9.pdf}
-\includegraphics{evo_slices-2.pdf}
-\caption{The top set of panes show the time evolution of the gas phase of our
-    fiducial model, plotted as tracks through \caah and \caafe where each colored line corresponds to the evolution at that galactic radius. 
-The bottom set instead shows the galaxies gas-phase \caah and \caafe trend at 5 different time slices. 
-}
-\end{figure*}
 
@@
 \subsection{Metallicity dependence and the AGB Fraction}
+
+\begin{figure*}\label{fig:beta_f}
+\includegraphics[scale=0.6]{beta-1.pdf}
+\includegraphics[scale=0.6]{f_agb-1.pdf}
+
+\caption{Similar to \ref{fig:agb_sims} except the top plot shows the fiducial model with lower and higher values of $\beta$, the C-CCSNe metallicity dependence.
+The bottom plot is the same except shows varying AGB fractions.}
+\end{figure*}
+
 The next question is how does changing the CCSNe carbon yield affect the model?
@@
 
+\begin{figure*}
+\includegraphics[scale=0.6]{lateburst_eta-1.pdf}
+
+\caption{Same as Fig. \ref{fig:agb_sims} but comparing the fiducial model to the reduced outlow model and a lateburst model. (okay, need to totally change approach...)}
+\end{figure*}
+
 We consider a simple modification of our SFH described by our lateburst model
@@
 
-\begin{figure*}\label{fig:beta_f}
-\includegraphics[scale=0.6]{beta-1.pdf}
-\includegraphics[scale=0.6]{f_agb-1.pdf}
-
-\caption{Similar to \ref{fig:agb_sims} except the top plot shows the fiducial model with lower and higher values of $\beta$, the C-CCSNe metallicity dependence.
-The bottom plot is the same except shows varying AGB fractions.}
-\end{figure*}
-
-\begin{figure*}
-\includegraphics[scale=0.6]{lateburst_eta-1.pdf}
-
-\caption{Same as Fig. \ref{fig:agb_sims} but comparing the fiducial model to the reduced outlow model and a lateburst model. (okay, need to totally change approach...)}
-\end{figure*}
-
-\begin{figure}
-    \includegraphics[scale=0.6]{cooh_scatter.pdf}
-    \caption{The simulated stars of our model at present day plotted on \caah~and colored such that lighter colors represent stars born at greater galactric radii.}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[scale=0.6]{cnoh.pdf}
-    \caption{Caption}
-    \label{fig:cnofe}
-\end{figure}
-
-\begin{figure*}
-\centering
-\includegraphics[]{summary-2.pdf}
-\caption{Present-day gas phase tracks of the fiducial model in \caah~space. M101 is valid comparison to MW ...(van Dokkum et al. 2014)}
-\label{fig:gas_phase}
-\end{figure*}
 \subsection{Outflows}
@@
 
+\subsection{Understanding Scatter}
+
+\begin{figure}
+    \includegraphics[scale=0.6]{cooh_scatter.pdf}
+    \caption{The simulated stars of our model at present day plotted on \caah~and colored such that lighter colors represent stars born at greater galactric radii.}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[scale=0.6]{cnoh.pdf}
+    \caption{Caption}
+    \label{fig:cnofe}
+\end{figure}
+
+Beyond simply comparing median trends, we can compare the distribution 
+shape of our distribution to observations.
+
 \subsection{Comparison to Observations}
+
+\begin{figure*}
+\centering
+\includegraphics[]{summary-2.pdf}
+\caption{Present-day gas phase tracks of the fiducial model in \caah~space. M101 is valid comparison to MW ...(van Dokkum et al. 2014)}
+\label{fig:gas_phase}
+\end{figure*}
 

### 2023-03-21 carbon_paper/agb_yields.py

@@ -35,7 +35,7 @@ def plot_c_table(study = "cristallo11", ax=None, fig=None, **kwargs):
     return f
 
 
-fig, axs = plt.subplots(2, 2, figsize=(2*plot_style.WIDTH, 4/3*plot_style.WIDTH), sharex=True, sharey=True)
+fig, axs = plt.subplots(2, 2, figsize=((np.sqrt(5) + 1)*plot_style.WIDTH, 2*plot_style.WIDTH), sharex=True, sharey=True)
 plt.subplots_adjust(hspace=0, wspace=0)
 # plt.minorticks_off()
 

### 2023-03-26 thesis/tex/main.tex
initial thesis commit

--- 2023-03-21 carbon_paper/tex/main.tex
@@
-% mnras_template.tex 
-%
-% LaTeX template for creating an MNRAS paper
-%
-% v3.0 released 14 May 2015
-% (version numbers match those of mnras.cls)
-%
-% Copyright (C) Royal Astronomical Society 2015
-% Authors:
-% Keith T. Smith (Royal Astronomical Society)
+\documentclass[12pt,oneside]{book}
 
-% Change log
-%
-% v3.0 May 2015
-%    Renamed to match the new package name
-%    Version number matches mnras.cls
-%    A few minor tweaks to wording
-% v1.0 September 2013
-%    Beta testing only - never publicly released
-%    First version: a simple (ish) template for creating an MNRAS paper
+% \AddToHook{cmd/section/before}{\clearpage}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Basic setup. Most papers should leave these options alone.
-\documentclass[fleqn,usenatbib]{mnras}
-
-% MNRAS is set in Times font. If you don't have this installed (most LaTeX
-% installations will be fine) or prefer the old Computer Modern fonts, comment
-% out the following line
-\usepackage{newtxtext,newtxmath}
-% Depending on your LaTeX fonts installation, you might get better results with one of these:
-%\usepackage{mathptmx}
-%\usepackage{txfonts}
-
-% Use vector fonts, so it zooms properly in on-screen viewing software
-% Don't change these lines unless you know what you are doing
 \usepackage[T1]{fontenc}
 
-% Allow "Thomas van Noord" and "Simon de Laguarde" and alike to be sorted by "N" and "L" etc. in the bibliography.
-% Write the name in the bibliography as "\VAN{Noord}{Van}{van} Noord, Thomas"
-\DeclareRobustCommand{\VAN}[3]{#2}
-\let\VANthebibliography\thebibliography
-\def\thebibliography{\DeclareRobustCommand{\VAN}[3]{##3}\VANthebibliography}
+\usepackage{aas_macros}
+\usepackage[letterpaper, top=1in]{geometry}
+\usepackage{titlesec}
 
-%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%
+\titleformat{\chapter}{\normalfont\normalsize\centering}{Chapter \thechapter:}{1em}{}
+\titleformat{\section}{\normalfont\normalsize\centering}{\thesection}{1em}{}
+\titleformat{\subsection}{\normalfont\normalsize\centering}{\thesubsection}{1em}{}
+\titlespacing*{\chapter}{0pt}{-15pt}{40pt} \titlespacing*{\section}{0pt}{0pt}{20pt}
+\renewcommand{\contentsname}{Table of Contents}
 
-% Only include extra packages if you really need them. Common packages are:
+\usepackage{setspace}
+
+\usepackage{amsmath}	% Advanced maths commands
+\usepackage{txfonts}
+\usepackage{hyperref}
+\hypersetup{
+    colorlinks=true,
+    linkcolor=blue,
+    filecolor=blue,
+    urlcolor=blue,
+    pdftitle={Thesis},
+    pdfpagemode=FullScreen,
+}
+% \usepackage{amssymb}	% Extra maths symbols
+
 \usepackage{graphicx}	% Including figure files
-\usepackage{amsmath}	% Advanced maths commands
-\usepackage{abbrevs}
-% \usepackage{amssymb}	% Extra maths symbols
 \graphicspath{{../figures/}}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\usepackage{natbib}
+\usepackage[nottoc,numbib]{tocbibind}
 
-%%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%
+% \usepackage{fancyhdr}
+% \pagestyle{fancy}
+% \fancyhead{}
+% \fancyhead[RO,RE]{Carbon Galactic Nucleosynthesis}
+\pagestyle{plain}
+
 \defcitealias{cristallo+11}{C11}
@@
 
-\newabbrev\CC{Core Collapse Supernovae (CCSNe)}[CCSNe]
-
 \newcommand{\VICE}{\texttt{VICE}}
@@
 \newcommand{\zoo}{\ensuremath{Z/Z_{\sun }}}
-\newcommand{\Ycc}{\ensuremath{Y_{\rm C}^{\rm cc}}}
-\newcommand{\Yct}{\ensuremath{Y_{\rm C, 0}^{\rm tot}}}
-\newcommand{\Yoc}{\ensuremath{Y_{\rm O}^{\rm cc}}}
-\newcommand{\Ycagb}{\ensuremath{Y_{\rm C}^{\rm agb}}}
+\newcommand{\Ycc}{\ensuremath{y_{\rm C}^{\rm cc}}}
+\newcommand{\Yct}{\ensuremath{y_{\rm C, 0}^{\rm tot}}}
+\newcommand{\Yoc}{\ensuremath{y_{\rm O}^{\rm cc}}}
+\newcommand{\Ycagb}{\ensuremath{y_{\rm C}^{\rm agb}}}
+\newcommand{\sun}{\ensuremath{\odot}}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%
-
-% Title of the paper, and the short title which is used in the headers.
-% Keep the title short and informative.
-\title[Constraining carbon yields]{The galactic chemical evolution of carbon: Constraining stellar nucleosynthesis}
-
+\title{Carbon Nucleosynthesis}
 % The list of authors, and the short list which is used in the headers.
 % If you need two or more lines of authors, add an extra line using \newauthor
-\author[D. A. Boyea et al.]{
-Daniel A. Boyea,$^{1}$\
-et al.
-% James W. Johnson,$^{1}$
-% David Weinberg
-% Jack Roberts
-% Jennifer Johnson
-% ?
-\\
-% List of institutions
-$^{1}$Department of Astronomy, The Ohio State University\\
-$^{2}$Department, Institution, Street Address, City Postal Code, Country\\
-$^{3}$Another Department, Different Institution, Street Address, City Postal Code, Country
-}
+\author{Daniel A. Boyea}
 
 % These dates will be filled out by the publisher
-\date{Accepted XXX. Received YYY; in original form ZZZ}
+\date{\today}
 
-% Enter the current year, for the copyright statements etc.
-\pubyear{2023}
+\pagenumbering{roman}
 
-% Don't change these lines
 \begin{document}
-\label{firstpage}
-\pagerange{\pageref{firstpage}--\pageref{lastpage}}
-\maketitle
+
+%\doublespacing
+
+\begin{titlepage}
+   \begin{center}
+       \vfill
+       \textbf{The Galactic Chemical Evolution of Carbon} \\
+        Implications for nucleosynthesis
+        \vfill
+        Research Thesis
+        \vfill
+        Presented in partial fulfillment of the requirements for graduation \textit{with research distinction} in Astronomy and Astrophysics in the College of Arts and Sciences of The Ohio State University.
+        \vfill
+        by 
+        \vfill
+       {Daniel A. Boyea}\\
+       \vfill
+       Department of Astronomy\\
+       The Ohio State University\\
+       \vfill
+       April 2023
+       \vfill
+       Thesis Committee:\\
+       David Weinberg, Advisor \\
+       Jennifer Johnson \\
+       Rolando Vald\'es Aguilar\\
+       \vfill
+
+   \end{center}
+\end{titlepage}
 
 % Abstract of the paper
-\begin{abstract}
+\chapter*{Abstract}
+\begin{center}
 Stellar evolution models provide highly uncertain predictions for elemental yields due to our limited understanding of stellar physics.
@@
 We find that the AGB stars make up a fraction $0.20_{-20}^{+80}$ of total carbon production at late times. 
-\end{abstract}
+\end{center}
 
-% Select between one and six entries from the list of approved keywords.
-% Don't make up new ones.
-\begin{keywords}
-Need to find some...
-\end{keywords}
+\chapter*{Acknowledgements}
+
+Many thanks to
+
+%% Lists
+
+\tableofcontents
+\listoffigures
+\listoftables
+\newpage
+\pagenumbering{arabic}
 
@@
 
-\section{Introduction}
+\chapter{Introduction}
 
@@
 
-Carbon and nitrogen are the only lighter elements produced significantly by low mass stars, so*****, reasons WHY this study.
+Carbon and nitrogen are well studied elements as they are easy to observe (Citations...).
+Additionally, carbon and nitrogen are used as age indicators for giant branch stars (citations, e.g.
+\cite{fiorenzo+21}), and are the only light elements known to be produced significantly in Asymptotic Giant Branch Stars (AGB) (cite).
+
+However, theoretical interpretations of the trends of
+
+While easily visible in many stars, determining birth abundances of carbon and nitrogen are
+
+One challenge of measuring abundances of carbon in star is that when a star becomes a RGB star, material from the CNO-processed core.
+Since this core-processed material is now carbon depleted and nitrogen enhanced, measurments of this star's atmosphere will no longer reflect the birth abundances of the star.
+Additionaly, carbon is extremelt challenging to measure gas-phase abundances for because the strongest visible line is ...., e.g. carbon unreliable in GALAH, low detections.
 
@@
 
-\CC are also important (.... SN reminant measurments)
+CCSne are also important (.... SN reminant measurments)
 
@@
 
-Previous models (CIte). We use \VICE (CITE) to create multi-zone models of GCE enabling us to account for the effects of migration on our predicted yields.
-
-\citet{prantzos+18}
-\citep{WAF17}
-\citep{james+21}
-\citep{fiorenzo+21}
-
-\citep[e.g.][]{james+22}
-
-Carbon abundances are strongly affected by CNO cycle processing in stars.
-The CNO cycle is one of two series of nuclear reactions( $^{12}$C(p, $\gamma$)$^{13}$N($\beta^+ \nu_e$)$^{14}$N(p, $\gamma$)$^{15}$O($\beta^+\nu_e$)$^{15}$N(p,$\alpha$)$^{12}$C
-
-Because the $^{14}$N(p, $\alpha$) proton capture is the slowest component of the CNO cycle ****, the CNO cycle, to first order, converts all $^{12}$C into $^{14}N$.
-
-One challenge of measuring abundances of carbon in star is that when a star becomes a RGB star, material from the CNO-processed core.
-Since this core-processed material is now carbon depleted and nitrogen enhanced, measurments of this star's atmosphere will no longer reflect the birth abundances of the star.
-
 In Fig.
@@
 
-\begin{figure*}
+\begin{figure}[htp]
     \centering
-    \includegraphics[]{subgiants_mgh.pdf}
-    \includegraphics[]{subgiants_mgfe.pdf}
-    \caption{Chemical abundance relationships of our sample of APOGEE subgiants (see Jack et al. 2023). Left panel shows }
+    \includegraphics[scale=0.85]{subgiants_mgh.pdf}
+    \includegraphics[scale=0.85]{subgiants_mgfe.pdf}
+    \caption[APOGEE Subgiants]{The [C/Mg] ratio against [Mg/H] (left) and [Mg/Fe] (right).
+The left panel uses blue and orange to represent high and low $\alpha$ sequences respectively.
+On the right, we plot more metal rich ([Mh/H]) stars with darker colors.}
     \label{fig:subgiants}
-\end{figure*}
-\section{Nucleosynthesis}
+\end{figure}
+\chapter{Nucleosynthesis}
 
@@
 trace delayed enrichment from SNeIa. C and N are both formed in AGB and CCSNe.
-
-We use IMF-Integrated yields calculated with \VICE~throughout this paper (see
-section \ref{sec:vice}, \citet{james+21, james+22}). For an element X and star
-with mass $M$, the stellar yield $y$ is defined as the net production of X relative 
-to $M$, or
-\begin{equation}
-    y_{\rm X} = \frac{M_{\rm X,\ ejected} - Z_{0, X} M_{\rm ejected}}{M}   
-\end{equation}
-where we let $M_{\rm ejected}$ and $M_{\rm X, ejected}$ be the total ejected
-stellar mass (through winds and supernovae ejecta) and the ejected mass of X,
-and $Z_{0, X}$ was the birth mass fraction of element X.
-
-More useful for GCE are Initial Mass Function (IMF) yields, where we sum up the
-contributions of all stars which produce an element.
-We define the IMF-integrated yield of X with: 
-\begin{equation}
-Y_{\rm X}^{\rm proc}(Z) = \int_{M_{\rm min}}^{M_{\rm max}} y_{\rm X}^{\rm proc}(M, Z)\ \Phi(M)  \ dM
-\end{equation}
-Where $\Phi(M) = \frac{dN}{dM}/ \int_{M_{\rm min}}^{M_{\rm max}} \frac{dN}{dM}\ dM$ is the normalized IMF, $M_{\rm min}$ and $M_{\rm max}$ are the minimum and maximum mass of stars, which we take to be $0.08 M_{\sun}$ and $100 M_{\sun}$ respectively; and $\frac{dN}{dM}$ is the initial mass function, the frequency of stars born between $M$ and $M+dM$.
 
@@
 
-\subsection{Asymptotic giant branch carbon}
+\section{Asymptotic giant branch carbon}
 
@@
 
-An AGB star is a low mass ($\lesssim 8 M_{\sun}$) star during the final phases of evolution.
-The star has already completed hydrogen core burning, Hydrogen shell burning during the red giant branch phase, and helium core burning.
-So, the structure consists of an inert core of carbon and oxygen surrounded by a helium burning shell and a hydrogen burning shell.
-The double shell burning leads to thermal instabilities which drive off the outer layers of the star in a series of violent pulsations, ejecting the envelope and leaving behind a C/O white dwarf.
-
-In an AGB star, two competing processes determine the outcome of carbon production.
+An AGB star is a low mass ($\lesssim 8 M_{\sun}$) star during the final phases of evolution.  In an AGB star, two competing processes determine the outcome of carbon production.
 Third Dredge Up (TDU) is needed to eject carbon from the star, enriching the surface with helium-burning-processed material from the core.
@@
 In contrast, HBB may happen if the base of the convective envelope reaches about 50MK, initiating the CNO cycle, converting most C12 into N14.
+
+Carbon abundances are strongly affected by CNO cycle processing in stars.
+The CNO cycle is one of two series of nuclear reactions( $^{12}$C(p, $\gamma$)$^{13}$N($\beta^+ \nu_e$)$^{14}$N(p, $\gamma$)$^{15}$O($\beta^+\nu_e$)$^{15}$N(p,$\alpha$)$^{12}$C
+
+Because the $^{14}$N(p, $\alpha$) proton capture is the slowest component of the CNO cycle ****, the CNO cycle, to first order, converts all $^{12}$C into $^{14}N$.
 
@@
 Unless otherwise noted, C11 is the model we choose as our fiducial AGB yield.
+
+We use IMF-Integrated yields calculated with \VICE~throughout this paper (see
+section \ref{sec:vice}, \citet{james+21, james+22}). For an element X and star
+with mass $M$, the stellar yield $y$ is defined as the net production of X relative 
+to $M$, or
+\begin{equation}
+    y_{\rm X} = \frac{M_{\rm X,\ ejected} - Z_{0, X} M_{\rm ejected}}{M}   
+\end{equation}
+where we let $M_{\rm ejected}$ and $M_{\rm X, ejected}$ be the total ejected
+stellar mass (through winds and supernovae ejecta) and the ejected mass of X,
+and $Z_{0, X}$ was the birth mass fraction of element X.
+
+More useful for GCE are Initial Mass Function (IMF) yields, where we sum up the
+contributions of all stars which produce an element.
+We define the IMF-integrated yield of X with: 
+\begin{equation}
+Y_{\rm X}^{\rm proc}(Z) = \int_{M_{\rm min}}^{M_{\rm max}} y_{\rm X}^{\rm proc}(M, Z)\ \Phi(M)  \ dM
+\end{equation}
+Where $\Phi(M) = \frac{dN}{dM}/ \int_{M_{\rm min}}^{M_{\rm max}} \frac{dN}{dM}\ dM$ is the normalized IMF, $M_{\rm min}$ and $M_{\rm max}$ are the minimum and maximum mass of stars, which we take to be $0.08 M_{\sun}$ and $100 M_{\sun}$ respectively; and $\frac{dN}{dM}$ is the initial mass function, the frequency of stars born between $M$ and $M+dM$.
 
@@
 
-\subsection{CCSNe carbon}
+\section{CCSNe carbon}
 
-\begin{figure*}
-    \includegraphics[scale=0.9]{y_c_cc-2.pdf}
-    \includegraphics[scale=0.9]{y_co_cc.pdf}
+\begin{figure}[htp]
+    \includegraphics[scale=0.8]{y_c_cc-2.pdf}
+    \includegraphics[scale=0.8]{y_co_cc.pdf}
     \caption{The fist plot shows IMF-weighted net fractional CCSNe yield of
@@
     \label{fig:y_cc}
-\end{figure*}
+\end{figure}
 
@@
 
-    \section{The Multizone Model}\label{sec:vice}
+\chapter{The Multizone Model}\label{sec:vice}
 
@@
 
-\subsection{Model Stellar Yields}
-We define a parameterization of a \CC~yield
+\section{Model Stellar Yields}
+We define a parameterization of a CC~yield
   Because of the large uncertainties in CCSNe carbon yields, we choose to explore an analytic expression of the yield enabling us to easily explore how variations of CCSNe carbon yields affect abundance tracks.
@@
 
-\section{Multizone model results}
-
-\subsection{Data Selection}
+\chapter{Multizone model results}
+\section{Data Selection}
 
@@
 
-\subsection{The Evolution of carbon across the galaxy and through time}
+\section{The Evolution of carbon across the galaxy and through time}
 
@@
 \label{fig:c_evo}
-\includegraphics{evo_tracks-9.pdf}
-\includegraphics{evo_slices-2.pdf}
+\includegraphics{evo_tracks.pdf}
+\includegraphics{evo_slices.pdf}
 \caption{The top set of panes show the time evolution of the gas phase of our
@@
 
-\subsection{Effects of AGB Yields}
+\section{Effects of AGB Yields}
 
 \begin{figure*}
-\includegraphics[scale=0.6]{oob_agb-1.pdf}
+\includegraphics[scale=0.9]{oob_agb.pdf}
 
@@
 \end{equation}
-where we are choosing to evaluate the total IMF \CC and AGB yields at solar
+where we are choosing to evaluate the total IMF CC and AGB yields at solar
 metallicity. We show our calculations of $Y_{\rm C}^{\rm agb}(Z=Z_{\sun })$  in
@@
 agb} = 0.000585$ is only 11.7 percent of our required total carbon production,
-each of these models is dominated by \CC production of carbon. As a result,
+each of these models is dominated by CC production of carbon. As a result,
 while the metallicity dependence of the \caah may vary, the
@@
 
-\subsection{Metallicity dependence and the AGB Fraction}
+\section{Metallicity dependence and the AGB Fraction}
 
 \begin{figure*}\label{fig:beta_f}
-\includegraphics[scale=0.6]{beta-1.pdf}
-\includegraphics[scale=0.6]{f_agb-1.pdf}
+\includegraphics{beta.pdf}
+\includegraphics{f_agb.pdf}
 
@@
 
-\subsection{The AGB Fraction }
+One caveat is that the slope of this trend is also determined by the ratio of delayed iron to CCSNe iron production as well.
+If the SNeIa iron fraction is increased, then more iron enters later reducing the slope of the trend as AGB becomes a more rapid mechanism than Fe comparatively.
+The difference however is that changing the Fe franction mostly affects the tail of the distribution as this controls the speed of descent off the high $\alpha$ sequence, but the AGB fraction even changes the behavior for the low $\alpha$ sequence.
+
+\section{The AGB Fraction }
 One potential tension with data is our models predict a low value for the AGB fraction of stars.
@@
 
-\subsection{Star Formation History}
+\section{Star Formation History}
 
 \begin{figure*}
-\includegraphics[scale=0.6]{lateburst_eta-1.pdf}
+\includegraphics[]{lateburst_eta.pdf}
 
@@
 
-\subsection{Outflows}
+\section{Outflows}
 A common degeneracy in chemical evolution models is the yield-outflow degeneracy.
@@
 
-\subsection{Understanding Scatter}
+\section{Understanding Scatter}
 
-\begin{figure}
-    \includegraphics[scale=0.6]{cooh_scatter.pdf}
+\begin{figure*}
+    \includegraphics[scale=0.9]{cooh_scatter.pdf}
+    \includegraphics[scale=0.9]{cnoh_scatter.pdf}
     \caption{The simulated stars of our model at present day plotted on \caah~and colored such that lighter colors represent stars born at greater galactric radii.}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[scale=0.6]{cnoh.pdf}
-    \caption{Caption}
-    \label{fig:cnofe}
-\end{figure}
+\end{figure*}
 
@@
 
-\subsection{Comparison to Observations}
+\section{Comparison to Observations}
 
@@
 
-\section{The Equilibrium Approximation}\label{sec:equilibrium}
+\chapter{The Equilibrium Approximation}\label{sec:equilibrium}
 If we assume that the median track is an equilibrium phenomenon, we can calculate the total carbon to oxygen yield ratio.
@@
     \centering
-    \includegraphics[scale=0.3]{analytic_y-4.pdf}
+    \includegraphics[]{analytic.pdf}
     \caption{Our reverse fitting method to determine total CCSNe contribution}
@@
 
-\subsection{Uncertainties}
+\section{Uncertainties}
 
@@
 
-\section{Conclusions}
+\chapter{Conclusions}
 
@@
 Abundance ratios (e.g.C12/C13) as additional constraints
-
-\section*{Acknowledgements}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Data Availability}
+\chapter*{Data Availability}
 
@@
 
-\bibliographystyle{mnras}
+\bibliographystyle{aasjournal}
 \bibliography{main} % if your bibtex file is called example.bib
@@
 
-\section{Validating the APOGEE Subgiant Sample}\label{sec:jack}
+\chapter{Validating the APOGEE Subgiant Sample}\label{sec:jack}
 Our APOGEE subgiant sample excludes stars marked with the following flags:
@@
 
-In the first panel, both V13 and the subgiant sample predict similar trends in [C/Mg]-[Mg/H] but there appears to be a systematic offset of about 0.2dex.
-Reproducing the trend is promising as V21's mixing corrections were metallicity-dependent so the uncorrected sample of APOGEE giants does not match the subgiant trend.
-
-The systematic offset could be explained by overpredicting the effects of FDU or other *** in V21's stellar evolution models??? or other subgiant physics???
-
-In the second panel, agreement appears to be better. Both the MDF and the slope are nearly identical,
-There is a slight deviation in slope between the models, and this could again be a systematic such as underestimation of **8some stellar effect**** at higher metallicities.
-
-We compare both of **** in Fig. \ref{fig:fiorenzo_jack}.
-
-\begin{figure*}
-    \centering
-    \includegraphics[scale=0.5]{fiorenzo_vs_jack_c-1.pdf}
-    \includegraphics[scale=0.5]{fiorenzo_vs_jack_n-1.pdf}
-    \caption{A comparison of estimated stellar birth abundance trends from the subgiant sample and
-        \citet{fiorenzo+21}
-    }
-    \label{fig:fiorenzo_jack}
-\end{figure*}
-
-\section{Effects of Alternate AGB Models}\label{sec:alt_agb}
+\chapter{Effects of Alternate AGB Models}\label{sec:alt_agb}
 
@@
 \begin{figure*}
-\includegraphics[scale=0.45]{agb_adj-2.pdf}
-\includegraphics[scale=0.45]{abg_adj_z-1.pdf}
+    \includegraphics{coofe_agb_extra.pdf}
+    \includegraphics{coofe_agb_extra_0.2.pdf}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% Don't change these lines
-\bsp	% typesetting comment
 \label{lastpage}
 \end{document}
-
-% End of mnras_template.tex

### 2023-03-30 thesis/tex/main.tex
better yield plots

@@
-\documentclass[12pt,oneside]{book}
+\documentclass[12pt,oneside]{report}
 
@@
 \titleformat{\subsection}{\normalfont\normalsize\centering}{\thesubsection}{1em}{}
-\titlespacing*{\chapter}{0pt}{-15pt}{40pt} \titlespacing*{\section}{0pt}{0pt}{20pt}
+\titlespacing*{\chapter}{0pt}{0pt}{40pt} \titlespacing*{\section}{0pt}{0pt}{20pt}
 \renewcommand{\contentsname}{Table of Contents}
+\AtBeginDocument{
+      \renewcommand{\bibsection}{\chapter*{\bibname}}
+  }
 
 \usepackage{setspace}
+
+\usepackage{etoolbox}% http://ctan.org/pkg/etoolbox
+\makeatletter
+% \patchcmd{<cmd>}{<search>}{<replace>}{<succes>}{<failure>}
+\patchcmd{\@chapter}{\addtocontents{lof}{\protect\addvspace{10\p@}}}{}{}{}% LoF
+\patchcmd{\@chapter}{\addtocontents{lot}{\protect\addvspace{10\p@}}}{}{}{}% LoT
+\makeatother
 
@@
     urlcolor=blue,
+    citecolor=blue,
     pdftitle={Thesis},
@@
 \usepackage[nottoc,numbib]{tocbibind}
+\usepackage[titles]{tocloft} % fig titles
+\renewcommand{\cftfigpresnum}{\figurename\enspace}
+\setlength{\cftfignumwidth}{5em}
+\renewcommand{\cfttabpresnum}{\tablename\enspace}
+\setlength{\cfttabnumwidth}{5em}
 
@@
 \pagestyle{plain}
+\counterwithout{figure}{chapter}
+\counterwithout{table}{chapter}
 
@@
         \vfill
-       {Daniel A. Boyea}\\
+       {Daniel Alexandra Boyea}\\
        \vfill
@@
 \chapter*{Abstract}
-\begin{center}
+\addcontentsline{toc}{chapter}{Abstract}
 Stellar evolution models provide highly uncertain predictions for elemental yields due to our limited understanding of stellar physics.
@@
 We find that the AGB stars make up a fraction $0.20_{-20}^{+80}$ of total carbon production at late times.
-\end{center}
 
 \chapter*{Acknowledgements}
+\addcontentsline{toc}{chapter}{Acknowledgements}
 
-Many thanks to
+James Johnson, for guiding me through this project and through my last year of undergraduate.
+Wayne Schlingman, for everything you do for everyone. You are the glue holding together our department.
+David Weinberg and Jennifer Johnson, for listening to my earlier drafts of this work and providing excellent suggestions.
+
+I also would not have made it here without all the additional support from my friends and family.
+Eric, even across the country, you have always been a point of support and stability, and I am always happy to be around you.
+Anya, you are a wonderful friend and I cannot thank you enough for your support this year.
+I love so many people in our department who have just been friends and positive support: Kaia, Maria, Autumn, Simon, Mary, Bailee, Aaliyah, Sanskruti, Alyssa, Harrison, Denis, and so many others. 
+My Family (and Arya, my lovely labrodoodle).
 
@@
 
-Where does each chemical element come from?
+Astronomy is unique among sciences in that we can determine the history of chemical elements.
+While stable on earth, the churning gasses and firery stars can dramatically transform elements into new materials.
+However, we still have much to learn about how each chemical element is made.
+In this work, we will hope to clarify how the chemical element carbon, the basis of life, is made in the universe.
 
-Stellar evolution models can be used to predict how much of each element stars with a variety of physical properties produce.
+As the universe just began to cool following the big bang, the only elements around were hydrogen, helium, and trace amounts of lithium and berylium.
+All other elements were formed afterwords with the help of stars.
+Stars of different masses, ages, and metalicities have substantially different interior stuctures.
+Different stars produce vastly different amounts of different chemical elements depending on their properties.
+
+Stellar evolution, at the basis of galactical chemical evolution, predict the elemental production of different stellar processes. 
 However, these models are rife with uncertainties, limited by our understanding of critical physical processes such as nuclear reaction rates, convection, opacity, and mass loss (CITE, e.g.
@@
 
-However, theoretical interpretations of the trends of
+However, our theoretical understanding of the producion sources of carbon are still uncertain.
 
@@
 \begin{figure}[htp]
-    \centering
-    \includegraphics[scale=0.85]{subgiants_mgh.pdf}
-    \includegraphics[scale=0.85]{subgiants_mgfe.pdf}
-    \caption[APOGEE Subgiants]{The [C/Mg] ratio against [Mg/H] (left) and [Mg/Fe] (right).
+    \includegraphics{subgiants_mgh.pdf}
+    \includegraphics{subgiants_mgfe.pdf}
+    \caption[APOGEE Subgiants]{The [C/Mg] ratio against [Mg/H] (left) and [Mg/Fe] (right) for the sample of subgiants as in \cite{jack_subgiant}.
 The left panel uses blue and orange to represent high and low $\alpha$ sequences respectively.
@@
 
+Nucleosynthetic predictions 
 Modern theoretical nucleosynthesis provides our starting point for our models.
@@
 
-    \caption{The net fraction carbon yield ($M_\text{C}$, the amount of carbon produced by the star divided by $M$) plotted as a function of mass, $M$.
+        \caption[AGB carbon yields]{The net fraction carbon yield ($M_\text{C}$, the amount of carbon produced by the star divided by $M$) plotted as a function of mass, $M$.
 Lighter colors represent higher values of metalicity ([M/H]).
@@
 
-    \caption{On the left, we plot the IMF weighted net fractional carbon yields of each AGB model as a function of metalicity.The right panel plots the normalized net carbon AGB yield as a function of time for a population of stars born at the same time at solar metallicity.
+    \caption[SSP AGB carbon]{On the left, we plot the IMF weighted net fractional carbon yields of each AGB model as a function of metalicity.The right panel plots the normalized net carbon AGB yield as a function of time for a population of stars born at the same time at solar metallicity.
 We note that for the right panel, the minimum of the DTD for V13 is }
@@
 \begin{figure}[htp]
-    \includegraphics[scale=0.8]{y_c_cc-2.pdf}
-    \includegraphics[scale=0.8]{y_co_cc.pdf}
-    \caption{The fist plot shows IMF-weighted net fractional CCSNe yield of
+    \centering
+    \includegraphics{y_c_cc.pdf}
+    \caption[CCSNe carbon yields]{The fist plot shows IMF-weighted net fractional CCSNe yield of
         carbon, $y_C^{cc}$ against metalicity, [M/H], for different studies.
@@
 
+Massive stars form $^{12}$C through the triple--$\alpha$ process. However, the carbon has to get out of the star to be useful. 
 While there are many stellar models providing predictions of CCSNe yields, the results of these models are highly uncertain due to the many stellar modeling uncertainties.
@@
 \includegraphics{evo_slices.pdf}
-\caption{The top set of panes show the time evolution of the gas phase of our
+\caption[Carbon chemical evolution tracks]{The top set of panes show the time evolution of the gas phase of our
     fiducial model, plotted as tracks through \caah and \caafe where each colored line corresponds to the evolution at that galactic radius. 
@@
 
-\begin{figure*}
-\includegraphics[scale=0.9]{oob_agb.pdf}
+\begin{figure}
+\centering
+\includegraphics{oob_agb.pdf}
 
-\caption{Left: the \caah~ \textbf{median} present-day stellar tracks for four different
+\caption[AGB GCE Models]{Left: the \caah~ \textbf{median} present-day stellar tracks for four different
 AGB models (\cristallo, \karakas, \kl, and \ventura ). The median bin [C/Mg] values from \citet{jack_subgiant} are
@@
 \label{fig:agb_sims}
-\end{figure*}
+\end{figure}
 
@@
 	\centering
-	\caption{For each AGB yield set, our calculation of the effective SFH- and IMF-weighted carbon AGB yield, along with the multiplicative factor to reach an AGB contribution of 20.}
+    \caption[AGB net solar IMF yields]{For each AGB yield set, our calculation of the effective SFH- and IMF-weighted carbon AGB yield, along with the multiplicative factor to reach an AGB contribution of 20.}
 	\label{tab:alpha_agb}
@@
 
-\begin{figure*}\label{fig:beta_f}
+\begin{figure}\label{fig:beta_f}
+\centering
 \includegraphics{beta.pdf}
@@
 
-\caption{Similar to \ref{fig:agb_sims} except the top plot shows the fiducial model with lower and higher values of $\beta$, the C-CCSNe metallicity dependence.
+\caption[Adjusted yield models]{Similar to \ref{fig:agb_sims} except the top plot shows the fiducial model with lower and higher values of $\beta$, the C-CCSNe metallicity dependence.
 The bottom plot is the same except shows varying AGB fractions.}
-\end{figure*}
+\end{figure}
 
@@
 
-\begin{figure*}
+\begin{figure}
+\centering
 \includegraphics[]{lateburst_eta.pdf}
 
-\caption{Same as Fig. \ref{fig:agb_sims} but comparing the fiducial model to the reduced outlow model and a lateburst model. (okay, need to totally change approach...)}
-\end{figure*}
+\caption[Lateburst and reduced-outflow models]{Same as Fig.
+\ref{fig:agb_sims} but comparing the fiducial model to the reduced outlow model and a lateburst model.
+(okay, need to totally change approach...)}
+\end{figure}
 
@@
     \includegraphics[scale=0.9]{cnoh_scatter.pdf}
-    \caption{The simulated stars of our model at present day plotted on \caah~and colored such that lighter colors represent stars born at greater galactric radii.}
+    \caption[Scatter agreement]{The simulated stars of our model at present day plotted on \caah~and colored such that lighter colors represent stars born at greater galactric radii.}
 \end{figure*}
@@
 \includegraphics[]{summary-2.pdf}
-\caption{Present-day gas phase tracks of the fiducial model in \caah~space. M101 is valid comparison to MW ...(van Dokkum et al. 2014)}
+\caption[Gas phase abundances]{Present-day gas phase tracks of the fiducial model in \caah~space. M101 is valid comparison to MW ...(van Dokkum et al. 2014)}
 \label{fig:gas_phase}
@@
     \includegraphics[]{analytic.pdf}
-    \caption{Our reverse fitting method to determine total CCSNe contribution}
+    \caption[Reverse fit yields]{Our reverse fitting method to determine total CCSNe contribution}
 \end{figure}
@@
 \chapter*{Data Availability}
+\addcontentsline{toc}{chapter}{Data Availability}
 
@@
 
+\newpage
 \bibliographystyle{aasjournal}
+\addcontentsline{toc}{chapter}{Bibliography}
 \bibliography{main} % if your bibtex file is called example.bib
@@
 \appendix
+\chapter*{Appendix}
+\addcontentsline{toc}{chapter}{Appendix}
+\renewcommand{\thesection}{A.\arabic{section}}
+\renewcommand\thefigure{A.\arabic{figure}}    
+\setcounter{figure}{0}
 
-\chapter{Validating the APOGEE Subgiant Sample}\label{sec:jack}
+\section{Validating the APOGEE Subgiant Sample}\label{sec:jack}
 Our APOGEE subgiant sample excludes stars marked with the following flags:
@@
 
-\chapter{Effects of Alternate AGB Models}\label{sec:alt_agb}
+\newpage
+\section{Effects of Alternate AGB Models}\label{sec:alt_agb}
 
@@
 
-\begin{figure*}
+\begin{figure}[htp]
     \includegraphics{coofe_agb_extra.pdf}
@@
 
-\caption{Same as \ref{fig:agb_sims} but comparing our fiducial model to our recommended z-dependent $y_\text{C}^\text{CC}$ model.
+    \caption[Alternate AGB models]{Same as \ref{fig:agb_sims} but comparing our fiducial model to our recommended z-dependent $y_\text{C}^\text{CC}$ model.
 A plot of the stars of our favored CCSNe model colored by radius.
@@
 }
-\end{figure*}
+\end{figure}
 

### 2023-03-30 src/analysis/apogee_analysis.py

@@ -309,7 +309,7 @@ def plot_contour(x, y, ax=None, bins=50,exclude_high_alpha=True,  **kwargs):
 
     if exclude_high_alpha:
         v21 = v21[~v21["high_alpha"]]
-    sns.kdeplot(v21[x], v21[y], color="black", linewidths=1, **kwargs)
+    sns.kdeplot(v21, x=x, y=y, color="black", linewidths=1, **kwargs)
 
 def plot_cooh():
     df = subgiants

### 2023-04-01 thesis/tex/main.tex
thesis work

@@
     colorlinks=true,
-    linkcolor=blue,
-    filecolor=blue,
-    urlcolor=blue,
-    citecolor=blue,
+    linkcolor=black,
+    filecolor=black,
+    urlcolor=black,
+    citecolor=black,
     pdftitle={Thesis},
@@
 }
+\urlstyle{same}
 % \usepackage{amssymb}	% Extra maths symbols
@@
 \usepackage[nottoc,numbib]{tocbibind}
-\usepackage[titles]{tocloft} % fig titles
-\renewcommand{\cftfigpresnum}{\figurename\enspace}
-\setlength{\cftfignumwidth}{5em}
-\renewcommand{\cfttabpresnum}{\tablename\enspace}
-\setlength{\cfttabnumwidth}{5em}
+% \usepackage[titles]{tocloft} % fig titles
+% \renewcommand{\cftfigpresnum}{\figurename\enspace}
+% \setlength{\cftfignumwidth}{5em}
+% \renewcommand{\cfttabpresnum}{\tablename\enspace}
+% \setlength{\cfttabnumwidth}{5em}
 
@@
     \end{itemize}
+
+\chapter{The Equilibrium Approximation}\label{sec:equilibrium}
+
+Chemical abundances reach an equilibrium.
+New elements produced in stars balance the elements lost to galactic winds and inside stellar reminants.
+At the present day, our galaxy has evolved long enough to be well approximated by the chemical equilibriums.
+
+In equilibrium, if we know the yields, than the largest uncertainty is the rate of outflows. This determines the final abundances of evolutionary ... \cite{WAF17}.
+
+If we assume that the median track is an equilibrium phenomenon, we can calculate the total carbon to oxygen yield ratio.
+Additionally, assuming an AGB yield set enables us to predict the CCSNe carbon yield.
+We begin with the model, which underlies the multizone simulations, that the change in mass of an element is a sum of production, outflows, recycling, and mass left in reminants. We write this as
+\begin{equation}
+M_\text{C} = y_\text{C} \dot{M}_\star - (1 + \eta - r) Z_\text{C} \dot{M}_\star
+\end{equation}
+
+In the case that carbon
+\begin{equation}
+Z_c^{eq}(R) = \frac{y_c^{cc} + \langle y_c^{agb} \rangle }{1 + \eta(R) - r - \tau_\star / \tau_{sfh}}
+\end{equation}Where
+\begin{equation}
+\langle y_c^{agb} \rangle = \frac{\int_0^T y_c^{agb}(M, Z) \dot{M}_\star(T - t) \frac{dN}{dM} \frac{dM}{dt} dt  }{ \dot{M}_\star \int_0^T \frac{dN}{dM} \frac{dM}{dt} dt}
+\end{equation}
+
+Likewise for oxygen:
+\begin{equation}
+Z_O^{eq}(R) = \frac{y_O^{cc}}{1 + \eta(R) - r - \tau_\star / \tau_{sfh}}
+\end{equation}
+
+However, for the yield ratio, the denominator cancles with that of oxygen, so the ratio is fixed.
+\begin{equation}
+\frac{Z_c^{eq}}{Z_o^{eq}} = \frac{y_c^{cc} + \langle y_c^{agb} \rangle }{y_o^{cc}}
+\end{equation}
+
+For this analysis, we let $y_c^{agb}$ represent the default AGB yields from a given yield set, but add a process factor $\alpha_{agb}$ which multaplicatively increases the AGB fraction.
+See Table \ref{tab:alpha_agb}.
+
+\begin{equation}
+    y_{\rm C}^{\rm CC} \rightarrow \alpha_{agb}  y_{\rm C}^{\rm CC}
+\end{equation}
+
+With these definitions, we can calculate the core collapse yields of carbon as a function of metallicity:
+\begin{equation}
+    y_\text{C}^\text{CC} =  y_\text{O}^\text{CC} \frac{Z_\text{C,eq}}{Z_\text{O,eq}} - \alpha_{agb} \langle y_c^{agb} \rangle
+\end{equation}
+
+Rewriting in terms of the observed abundance ratio and dividing by
+$y_\text{O}^\text{CC}$. So, given the outflows or CCSNe oxygen yields, the
+carbon AGB yield, and the \caah mean abundance track, we can estimate the CCSNe carbon yield. Written as a relative yield:
+\begin{equation}
+    \frac{y_\text{C}^\text{CC}}{y_\text{O}^\text{CC}} = \frac{Z_{C, \sun}}{Z_{O, \sun}} 10^{[C/O]} - \frac{\alpha_{agb} \langle y_c^{agb} \rangle}{ y_\text{O}^\text{CC}}
+\end{equation}
+
+This equation corroberates what we have explored earlier in the paper, and provides our analytic estimates of the CCSNe carbon yields.
+Since the AGB term is subtracted, a negative AGB Z-dependence will correspond to a positive CC Z-dependence.
+And as we reduce outflows, the AGB factor increases, steepening the required slope of the carbon yields.
+So, while the AGB yields may agree with eachother, the uncertainties in the oxygen CC yields and outflows leads to a substantial uncertainty in the AGB fraction.
+
+\begin{figure}
+    \centering
+    \includegraphics[]{analytic.pdf}
+    \caption[Reverse fit yields]{Our reverse fitting method to determine total CCSNe contribution}
+\end{figure}
+
+% y_c^cc = (0.0148 +- 0.00016) Z^{0.154 +- 0.0053}
+\begin{equation}
+    y_C = (0.0029 \pm 0.0005) + (0.001 \pm 0.0004) \left(\frac{Z}{Z_\odot}\right)
+\end{equation}
+
+With uncertainties 
+
+\section{Uncertainties}
+
+We only perform this analysis on the C11/15 yields because the range of metallicities of the data (about [M/H] = -0.4, 0.4) only represents about 2 AGB models, relying heavily on our choice of extrapolation.
+C11/C15 have a finer model grid, allowing us to have 5 theoretical predicted points within this metallicity range, allowing us to be more certain of our conclusion.
+
+We do note that this analysis fails to take into account selection effects and biases in APOGEE, and a more robust determination of the carbon yield.
+
+This formulation is degenerate in $\varpi$ until we estimate a better AGB fraction.
+As the seperation between the low and high alpha sequences can be used to estimate the delayed time contribution to carbon, using the model to estimate this value relies heavaly on the details of the SFH in addition to the
+We do give an estimate of the CCSNe yields, however this is dependent on our choice of $\eta$.
+Other choices of $\eta$ vary the value significantly in both magnitude and slope (as AGB contributions increase, we need less CCSNe carbon, however the CCSNe carbon must have a higher metallicity dependence to replicate the V21 data).
 
@@
 
-\chapter{The Equilibrium Approximation}\label{sec:equilibrium}
-If we assume that the median track is an equilibrium phenomenon, we can calculate the total carbon to oxygen yield ratio.
-Additionally, assuming an AGB yield set enables us to predict the CCSNe carbon yield.
-We begin with the model, which underlies the multizone simulations, that the change in mass of an element is a sum of production, outflows, recycling, and mass left in reminants. We write this as
-\begin{equation}
-M_\text{C} = y_\text{C} \dot{M}_\star - (1 + \eta - r) Z_\text{C} \dot{M}_\star
-\end{equation}
-
-In the case that carbon
-\begin{equation}
-Z_c^{eq}(R) = \frac{y_c^{cc} + \langle y_c^{agb} \rangle }{1 + \eta(R) - r - \tau_\star / \tau_{sfh}}
-\end{equation}Where
-\begin{equation}
-\langle y_c^{agb} \rangle = \frac{\int_0^T y_c^{agb}(M, Z) \dot{M}_\star(T - t) \frac{dN}{dM} \frac{dM}{dt} dt  }{ \dot{M}_\star \int_0^T \frac{dN}{dM} \frac{dM}{dt} dt}
-\end{equation}
-
-Likewise for oxygen:
-\begin{equation}
-Z_O^{eq}(R) = \frac{y_O^{cc}}{1 + \eta(R) - r - \tau_\star / \tau_{sfh}}
-\end{equation}
-
-However, for the yield ratio, the denominator cancles with that of oxygen, so the ratio is fixed.
-\begin{equation}
-\frac{Z_c^{eq}}{Z_o^{eq}} = \frac{y_c^{cc} + \langle y_c^{agb} \rangle }{y_o^{cc}}
-\end{equation}
-
-For this analysis, we let $y_c^{agb}$ represent the default AGB yields from a given yield set, but add a process factor $\alpha_{agb}$ which multaplicatively increases the AGB fraction.
-See Table \ref{tab:alpha_agb}.
-
-\begin{equation}
-    y_{\rm C}^{\rm CC} \rightarrow \alpha_{agb}  y_{\rm C}^{\rm CC}
-\end{equation}
-
-With these definitions, we can calculate the core collapse yields of carbon as a function of metallicity:
-\begin{equation}
-    y_\text{C}^\text{CC} =  y_\text{O}^\text{CC} \frac{Z_\text{C,eq}}{Z_\text{O,eq}} - \alpha_{agb} \langle y_c^{agb} \rangle
-\end{equation}
-
-Rewriting in terms of the observed abundance ratio and dividing by
-$y_\text{O}^\text{CC}$. So, given the outflows or CCSNe oxygen yields, the
-carbon AGB yield, and the \caah mean abundance track, we can estimate the CCSNe carbon yield. Written as a relative yield:
-\begin{equation}
-    \frac{y_\text{C}^\text{CC}}{y_\text{O}^\text{CC}} = \frac{Z_{C, \sun}}{Z_{O, \sun}} 10^{[C/O]} - \frac{\alpha_{agb} \langle y_c^{agb} \rangle}{ y_\text{O}^\text{CC}}
-\end{equation}
-
-This equation corroberates what we have explored earlier in the paper, and provides our analytic estimates of the CCSNe carbon yields.
-Since the AGB term is subtracted, a negative AGB Z-dependence will correspond to a positive CC Z-dependence.
-And as we reduce outflows, the AGB factor increases, steepening the required slope of the carbon yields.
-So, while the AGB yields may agree with eachother, the uncertainties in the oxygen CC yields and outflows leads to a substantial uncertainty in the AGB fraction.
-
-\begin{figure}
-    \centering
-    \includegraphics[]{analytic.pdf}
-    \caption[Reverse fit yields]{Our reverse fitting method to determine total CCSNe contribution}
-\end{figure}
-
-% y_c^cc = (0.0148 +- 0.00016) Z^{0.154 +- 0.0053}
-\begin{equation}
-    y_C = (0.004 \pm 0.00002) + (0.008 \pm 0.0001) \text{[M/H]} 
-\end{equation}
-
-\section{Uncertainties}
-
-We only perform this analysis on the C11/15 yields because the range of metallicities of the data (about [M/H] = -0.4, 0.4) only represents about 2 AGB models, relying heavily on our choice of extrapolation.
-C11/C15 have a finer model grid, allowing us to have 5 theoretical predicted points within this metallicity range, allowing us to be more certain of our conclusion.
-
-We do note that this analysis fails to take into account selection effects and biases in APOGEE, and a more robust determination of the carbon yield.
-
-This formulation is degenerate in $\varpi$ until we estimate a better AGB fraction.
-As the seperation between the low and high alpha sequences can be used to estimate the delayed time contribution to carbon, using the model to estimate this value relies heavaly on the details of the SFH in addition to the
-We do give an estimate of the CCSNe yields, however this is dependent on our choice of $\eta$.
-Other choices of $\eta$ vary the value significantly in both magnitude and slope (as AGB contributions increase, we need less CCSNe carbon, however the CCSNe carbon must have a higher metallicity dependence to replicate the V21 data).
-
 \chapter{Conclusions}
@@
 \cite{OhioSupercomputerCenter1987}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\chapter*{Data Availability}
-\addcontentsline{toc}{chapter}{Data Availability}
-
-The inclusion of a Data Availability Statement is a requirement for articles published in MNRAS.
-Data Availability Statements provide a standardised format for readers to understand the availability of data underlying the research results described in the article.
-The statement may refer to original data generated in the course of the study or to third-party data analysed in the article.
-The statement should describe and provide means of access, where possible, by linking to the data or providing the required accession numbers for the relevant databases or DOIs.
 

### 2023-04-04 osc/simulate.py
plots for new set of models

@@ -10,7 +10,7 @@ y_c_0 = 0.005
 y_c_cc_0 = 0.0029
 zeta_n = 9e-4
 y_cc_n = 3.6e-4
-y_n_0 = 3.6e-4
+y_n_0 = 9e-4
 
 Z_Sun = 0.014
 
@@ -72,13 +72,14 @@ def set_yields(args):
     alpha_agb, alpha_cc = calc_alpha(args)
 
 
-    def y_c_cc(Z):
-        prefactor = y_c_0 * alpha_cc / (y_c_cc_0 + args.beta)
-
-        return prefactor * (y_c_cc_0 + args.beta*(Z/Z_Sun)) 
 
     vice.yields.agb.settings["N"] = lambda M, Z: (zeta_n * (Z/Z_Sun) * M 
                                                   + y_n_0 * M)
+
+    print("alpha_cc = ", alpha_cc)
+    def y_c_cc(Z):
+        prefactor = y_c_0 * alpha_cc / (y_c_cc_0 + args.beta)
+        return prefactor * (y_c_cc_0 + args.beta*(Z/Z_Sun)) 
     vice.yields.ccsne.settings["C"] = y_c_cc
 
 
@@ -96,7 +97,7 @@ def calc_alpha(args):
     }
     y_agb = y_agbs[agb_model]
 
-    y_c = 0.005*args.eta
+    y_c = y_c_0*args.eta
 
     oob = args.out_of_box_agb
 
@@ -105,7 +106,7 @@ def calc_alpha(args):
     else:
         alpha_agb = args.agb_fraction*y_c/y_agb
 
-    alpha_cc = (y_c - alpha_agb*y_agb)/y_c
+    alpha_cc = args.eta * (1 - args.agb_fraction)
 
     return alpha_agb, alpha_cc
 

### 2023-04-04 src/simulation/multizone_sim.py

@@ -17,8 +17,8 @@ MAX_SF_RADIUS = 15.5 #kpc
 END_TIME = 13.2
 
 def run_model(name, migration_mode="diffusion", spec="insideout", n_stars=2, agb_yields="cristallo11", 
-              seed=None, multithread=False, dt=0.01, n_yields=None, burst_size=1.5, eta_factor=1, 
-              isotopic=False, ratio_reduce=False, agb_factor=1, prefix=None):
+              seed=None, multithread=False, dt=0.01, burst_size=1.5, eta_factor=1, 
+              ratio_reduce=False, agb_factor=1, prefix=None):
     """
     This function wraps various settings to make running VICE multizone models
     easier for the carbon paper investigation
@@ -53,9 +53,6 @@ def run_model(name, migration_mode="diffusion", spec="insideout", n_stars=2, agb
         - "karakas16"
         Look at VICE for more details
 
-    seed: ``int?`` [default: None]
-        The seed to use for the model
-
     multithread: ``bool`` [default: False]
         If true, runs the multithreaded version of the model.
         The maximum number of threads is currently 8
@@ -64,11 +61,6 @@ def run_model(name, migration_mode="diffusion", spec="insideout", n_stars=2, agb
     dt: ``float`` [default: 0.01]
         The timestep of the simulation, measured in Gyr.
         Decreasing this value can significantly speed up results
-
-    n_yields: ``str`` [defalt: None]
-        Only acceptable value is "J22", which sets the
-        AGB N yields to the analytic form in
-        Johnson, et. al. 2022 (Emperical constraints of N)
 
     burst_size: ``float`` [default: 1.5]
         The size of the SFH burst for lateburst model.
@@ -122,20 +114,13 @@ def run_model(name, migration_mode="diffusion", spec="insideout", n_stars=2, agb
 
 
     # we use au and ag for c12 and c13 respectively
-    if isotopic:
-        model.elements = ("fe", "o", "n", "au", "ag")
-    else:
-        model.elements = ("fe", "o", "n", "c")
+    # if isotopic:
+    #     model.elements = ("fe", "o", "n", "au", "ag")
+    # else:
+    model.elements = ("fe", "o", "n", "c")
 
     model.mode = "sfr"
 
-    # multithreading may or may not work
-    # if multithread:
-    #     model.setup_nthreads = 8
-    #     model.nthreads = 4
-    # else:
-    #     model.setup_nthreads = 1
[…]

### 2023-04-04 submit_model.sh

@@ -2,18 +2,13 @@
 
 for f_agb in 0.2 # 0.4 0.1
 do
-  for beta in 0 # 0.002 0.0005
+  for beta in 0.001 # 0.002 0.0005
   do
-    for model in "C11"  "K10" "V13" "K16"
+    for model in "C11"  #"K10" "V13" "K16"
     do
-      for eta in 1 # 0.3
+      for eta in 0.6 0.3 # 1
       do
-        echo "f_agb = $f_agb"
-        echo "eta/eta_0 = $eta"
-        echo "beta = $beta"
-        echo "model = $model"
-
-        bash osc/run.sh -f $f_agb -b $beta -m $model -e $eta -o
+        bash osc/run.sh -f $f_agb -b $beta -m $model -e $eta
       done
     done
   done

### 2023-04-04 thesis/tex/main.tex
thesis again

@@
 Anya, you are a wonderful friend and I cannot thank you enough for your support this year.
-I love so many people in our department who have just been friends and positive support: Kaia, Maria, Autumn, Simon, Mary, Bailee, Aaliyah, Sanskruti, Alyssa, Harrison, Denis, and so many others. 
-My Family (and Arya, my lovely labrodoodle).
+I love so many people in our department who have just been friends and positive support: Kaia, Maria, Autumn, Simon, Mary, Aaliyah, Sanskruti, Alyssa, Harrison, Denis, and so many others. 
+My Family (and Arya, our lovely doodle).
 
@@
 
+\begin{figure}
+    \includegraphics[scale=1]{y_agb_t2.pdf}
+
+    \caption[AGB DTD]{
+    The Delay Time Distribution for AGB STars}
+
+\end{figure}
+
 \begin{figure*}
@@
     \includegraphics[scale=1]{y_agb_vs_z.pdf}
-    \includegraphics[scale=1]{y_agb_vs_t.pdf}
 
@@
 
-With uncertainties 
+With uncertainties
+
+\section{Model Stellar Yields}
+We define a parameterization of a CC~yield
+  Because of the large uncertainties in CCSNe carbon yields, we choose to explore an analytic expression of the yield enabling us to easily explore how variations of CCSNe carbon yields affect abundance tracks.
+We find that a powerlaw yield with a metallicity-dependent constant minimum is able to match the observations well while remaining a simple parameterization (see below).
+Our expression is:
+  \begin{equation}\label{eq:y_yields}
+   Y_\text{C}^\text{CC}(Z) =  \alpha\ Z^\beta Y_\text{O}^\text{CC} + Y_\text{C, 0}^\text{CC}
+    \end{equation}
+   	Where we estimate $\alpha = 0.02$ and $\beta = 0.25$ (See Section \ref{sec:equilibrium} ).
+Our second model uses $\alpha = 0.44$ and $\beta = 0.63$ with K16 yields and reduced $\eta \rightarrow 1/2 \eta$
+
+    As an overall scaling of yields does not significantly affect our models, we choose to fix the total equilibrium value of the total carbon yield at solar at $Y_{\text{C},\ \sun} = 0.005$, and then scale the yields relative to this value.
 
@@
 
-\section{Model Stellar Yields}
-We define a parameterization of a CC~yield
-  Because of the large uncertainties in CCSNe carbon yields, we choose to explore an analytic expression of the yield enabling us to easily explore how variations of CCSNe carbon yields affect abundance tracks.
-We find that a powerlaw yield with a metallicity-dependent constant minimum is able to match the observations well while remaining a simple parameterization (see below).
-Our expression is:
-  \begin{equation}\label{eq:y_yields}
-   Y_\text{C}^\text{CC}(Z) =  \alpha\ Z^\beta Y_\text{O}^\text{CC} + Y_\text{C, 0}^\text{CC}
-    \end{equation}
-   	Where we estimate $\alpha = 0.02$ and $\beta = 0.25$ (See Section \ref{sec:equilibrium} ).
-Our second model uses $\alpha = 0.44$ and $\beta = 0.63$ with K16 yields and reduced $\eta \rightarrow 1/2 \eta$
-
-    As an overall scaling of yields does not significantly affect our models, we choose to fix the total equilibrium value of the total carbon yield at solar at $Y_{\text{C},\ \sun} = 0.005$, and then scale the yields relative to this value.
-
 \chapter{Multizone model results}
@@
 
-While we show the entire dataset in Fig. \ref{fig:subgiants}, we chose to compare the
-binned data to our models as black points with dashes representing the 1-sigma
-spread, as in e.g. Fig. \ref{fig:agb_sims}.
-
 \section{The Evolution of carbon across the galaxy and through time}
@@
 \end{figure*}
+
+Here, we present our fiducial model which we will later show aggrees well with APOGEE. We will later investigate the effects of alterations to this model.
+
+In this model, we use the following yields:
 
@@
 \ref{fig:c_evo} for \caah and \caafe for our fiducial model.
-Each colored track corresponds to a different galactic radius and 1Gyr time steps are marked with crosses on the lines.
-
 Comparing [C/$\alpha$] against [Fe/H] enables us to see late time evolution of carbon more clearly.
 Because [Fe/H] takes longer to reach equilibrium as half of iron production comes from type-Ia supernovae, the late time evolution is not clustered as tightly horizontally as for [$\alpha$/H].
-
-This is even more evident in the lower part of Fig. \ref{fig:c_evo}, where we
-instead plot snapshots of the galactic radial trend at different times for our
-model.
+This is even more evident in the lower part of Fig.
+\ref{fig:c_evo}.
 While the \caah trend reaches almost equilibrium at 5Gyr, the \caafe trend continues to evolve even until the present day, exposing the effect of the delayed contribution from AGB stars on the evolutionary history.
 
-\section{Effects of AGB Yields}
+\begin{itemize}
+    \item Describe definition of $f$ /etc.
+    \item How we match the figures, DTD vs $\zeta$
+
+\end{itemize}
 
@@
 Right: same as left but for \caafe. While each AGB yield model may
-differ in detail, there is minimal effect on the overall [C/Mg] trends. }
-\label{fig:agb_sims}
+differ in detail, there is minimal effect on the overall [C/Mg] trends.
+
+While we show the entire dataset in Fig. \ref{fig:subgiants}, we chose to compare the
+binned data to our models as black points with dashes representing the 1-sigma
+spread, as in e.g. Fig. \ref{fig:agb_sims}. \label{fig:agb_sims}
+}
 \end{figure}
+
+\section{Alternate Models}
 
@@
 
-\section{Metallicity dependence and the AGB Fraction}
-
 \begin{figure}\label{fig:beta_f}
@@
 
-\section{The AGB Fraction }
 One potential tension with data is our models predict a low value for the AGB fraction of stars.
@@
 In the next section, we develop the analytic tools to explore this problem in more depth.
-
-\section{Star Formation History}
 
@@
 \section{Outflows}
+
+In GCE there are models requiring significant mass loading, but other approaches neglect outlows altogether. (Minchev, Chiappini and Martig (13, 14), Spitoni ++ 19,20,21).
+
+We can modify our model to account for this by $\eta=0$.
+
 A common degeneracy in chemical evolution models is the yield-outflow degeneracy.
@@
 \begin{figure*}
+    \centering
     \includegraphics[scale=0.9]{cooh_scatter.pdf}
-    \includegraphics[scale=0.9]{cnoh_scatter.pdf}
     \caption[Scatter agreement]{The simulated stars of our model at present day plotted on \caah~and colored such that lighter colors represent stars born at greater galactric radii.}
@@
 \centering
-\includegraphics[]{summary-2.pdf}
+\includegraphics[]{summary.pdf}
 \caption[Gas phase abundances]{Present-day gas phase tracks of the fiducial model in \caah~space. M101 is valid comparison to MW ...(van Dokkum et al. 2014)}
@@
 \end{figure*}
+
+Carbon measurments in stars are difficult. There are measurments which can however be used to test.
+
+We don't predict low metallicity but we are in agreement, substantial error bars.
+
+Pop III stars from Cooke++.
 
@@
 \chapter{Conclusions}
+
+\begin{itemize}
+    \item James ++23 Nitrogen,
+    \item J++ found yield ratios, APOGEE -> yield assumptions
+    \item SFH and eta don't matter too much.
+
+        \item
+        \item Variations in f and beta
+        \item Evolutionary history
+        \item Gas phase and Pop III
+        \item Implications in Stellar evolution
+        \item Continuing to work on neutron-capture e.t.c., 
+        \item MWM and value of this work
+\end{itemize}
 

### 2023-04-05 thesis/tex/main.tex
thesis updates

@@
 \titleformat{\subsection}{\normalfont\normalsize\centering}{\thesubsection}{1em}{}
-\titlespacing*{\chapter}{0pt}{0pt}{40pt} \titlespacing*{\section}{0pt}{0pt}{20pt}
+% \titlespacing*{\chapter}{0pt}{0pt}{40pt} 
+% \titlespacing*{\section}{0pt}{0pt}{20pt}
 \renewcommand{\contentsname}{Table of Contents}
@@
 \usepackage{graphicx}	% Including figure files
-\graphicspath{{../figures/}}
-
-\usepackage{natbib}
+\graphicspath{{../figures/}} \usepackage{natbib}
 \usepackage[nottoc,numbib]{tocbibind}
@@
 \begin{itemize}
-    \item $Y_\text{O}^\text{CC} = 0.015$
-    \item $Y_\text{O}^\text{Ia} = 0$
-    \item $Y_\text{Fe}^\text{Ia} = 0.00214?$
-    \item $Y_\text{Fe}^\text{CC} = 0.0012$
-    \item $Y_\text{N}^\text{CC} = 0.00036$
-    \item $y_\text{N}^\text{AGB}(M, Z) = 9\times 10^{-4} M \left(\frac{Z}{Z_\odot}\right)$
+    \item $y_\text{Mg}^\text{CC} = 0.00185$
+    \item $y_\text{Mg}^\text{Ia} = 0$
+    \item $y_\text{Fe}^\text{Ia} = 0.00214$
+    \item $y_\text{Fe}^\text{CC} = 0.0012$
+    \item $y_\text{N}^\text{CC} = 0.00036$
+    \item $\tilde{y}_\text{N}^\text{AGB}(M, Z) = 9\times 10^{-4} M \left(\frac{Z}{Z_\odot}\right)$
 \end{itemize}
+
 Also following \citet{james+21, james+22}, we take the SNeIa Delay Time distribution to be a
@@
 
-    \caption[AGB DTD]{
+    \caption[AGB yields delayed-time-distribution]{
     The Delay Time Distribution for AGB STars}
@@
 
-    \caption[SSP AGB carbon]{On the left, we plot the IMF weighted net fractional carbon yields of each AGB model as a function of metalicity.The right panel plots the normalized net carbon AGB yield as a function of time for a population of stars born at the same time at solar metallicity.
+    \caption[AGB yield metallicity dependence]{On the left, we plot the IMF weighted net fractional carbon yields of each AGB model as a function of metalicity.The right panel plots the normalized net carbon AGB yield as a function of time for a population of stars born at the same time at solar metallicity.
 We note that for the right panel, the minimum of the DTD for V13 is }
@@
 \begin{itemize}
-    \item \citet{cristallo+11} and \citet{cristallo+15} (\cristallo).
-    \item \citet{karakas10} (\karakas)
-    \item \citet{ventura+13} \ventura
-    \item \citet{KL16} \citet{karakas+18} \kl
+    \item C11: \citet{cristallo+11} and \citet{cristallo+15}
+    \item K10: \citet{karakas10}
+    \item V13: \citet{ventura+13}
+    \item K16: \citet{KL16} \citet{karakas+18}
 \end{itemize}
@@
 Chemical abundances reach an equilibrium.
-New elements produced in stars balance the elements lost to galactic winds and inside stellar reminants.
-At the present day, our galaxy has evolved long enough to be well approximated by the chemical equilibriums.
+At least with simple enough assumptions.
+The new elements synthesized in stars balance against elements lost to galactic winds and locked in stellar reminants.
+While our galaxy is likely not in perfect equilibrium or described by a single, homogenous chemical region, we can still use an equilibrium approximation to understand total yields.
+\cite{WAF17}. \cite{james_dwarf}, \cite{james+22}
 
-In equilibrium, if we know the yields, than the largest uncertainty is the rate of outflows. This determines the final abundances of evolutionary ... \cite{WAF17}.
+Here, we assume a simple one-zone chemical evolution model.
+A one zone model is essentially zero-dimensional---the gas and stars are considered to be homogenously mixed, so we can represent all quantaties as scalars.
+We use $M_{X}$ to represent the mass of element X
 
@@
 \begin{equation}
-    y_{\rm C}^{\rm CC} \rightarrow \alpha_{agb}  y_{\rm C}^{\rm CC}
+    \Ycagb \rightarrow \alpha_{agb}  \Ycagb
 \end{equation}
@@
 \begin{equation}
-    y_C = (0.0029 \pm 0.0005) + (0.001 \pm 0.0004) \left(\frac{Z}{Z_\odot}\right)
+    \Ycc = y_{\rm C,~0}^{\rm CC} + \zeta \left(\frac{Z}{Z_\odot}\right)
 \end{equation}
+where we estimate $y_{\rm C,~0}^{\rm CC} = 0.0029\pm 0.0005$ and $\zeta = 0.001\pm0.0004$.
 
@@
 
-We only perform this analysis on the C11/15 yields because the range of metallicities of the data (about [M/H] = -0.4, 0.4) only represents about 2 AGB models, relying heavily on our choice of extrapolation.
-C11/C15 have a finer model grid, allowing us to have 5 theoretical predicted points within this metallicity range, allowing us to be more certain of our conclusion.
+We only perform this analysis on the C11yields because the range of metallicities of the data (about [M/H] = -0.4, 0.4) only represents about 2 AGB models, relying heavily on our choice of extrapolation.
+C11 have a finer model grid, allowing us to have 5 theoretical predicted points within this metallicity range, allowing us to be more certain of our conclusion.
 
@@
 
-To simulate the chemical evolution of a Milky-Way-like galaxy, we use the Versitile Integrator for Chemical Evolution (\VICE\footnote{\VICE~is available at \url{https://github.com/giganano/VICE}}) published in \citet{james+21} and also briefly described in \citet{james+22}.
+Unfortunantly, a simple and tidy one-zone model is a poor approximation for our galaxy.
+The galaxy evolves ``inside out''---where star formation is higher towards the center and in the early universe \citep{bird+13}.
+Additionally, stars can migrate several kpc over their lifetimes, mixing together different chemical environments across the galaxy \citep{bird+12,sellwood+binney02}.
+For the rest of this paper, we focus on multizone models, which divide the galaxy into seperate zones and account for stellar migration.
+Our models are created with the Versitile Integrator for Chemical Evolution (\VICE\footnote{\VICE~is available at \url{https://github.com/giganano/VICE}}).
+\VICE~is published and extensively described in \citet{james+21}.
+\citet{james+22} include an additional summary.
+We briefly describe the importaint characteristics of \VICE~here.
+
 As a multi-zone model, the galaxy is divided into 200 rings of 0.1kpc, each with separate gas supplies with outflow and inflow rates.
-
-\VICE\ accounts for radial migration by using the results of the \texttt{h277} hydrodynamical simulation.
-Each VICE SSP is matched to a random nearby star particle \textit{analogue} in \texttt{H277}.
-VICE approximates the migration of this particle by using a $\sqrt{\text{time}}$-diffusion approximation where the change in galactic radius of a star, $\Delta R$, is $\Delta R \propto \sqrt{\text{t}}$.
-VICE does not account for radial gas flows.
-
-Other approaches have used dynamical arguments to implement their stellar mirgrations.
-We note that our approach does not introduce more free parameters which may bias conclusions.
-However, we only consider one dynamic history, and it is still unknown how variations in the dynamic history of a galaxy impact its chemical evolution.
-
-We initially assume an "inside-out" SFH where the star formation rate peaks in the early evolution of the galaxy and is higher closer to the galactic center.
-The star formation rate, $\Sigma_\star$, for our fiducial model is parameterized by
+Star formation truncates after 15.5kpc.
+We initially assume an ``inside-out'' Star Formation History (SFH), where the star formation rate (SFR) $\Sigma_\star$ is given by
 \begin{equation}
-    \dot{\Sigma}_\star \propto \left(1-e^{-t/\tau_{\rm rise}}\right) e^{-t/\tau_{\rm sfh}}
+    \dot{\Sigma}_\star \propto \left(1-e^{-t/\tau_{\rm rise}}\right) e^{-t/\tau_{\rm sfh}}.
 \end{equation}
-where $\tau_\text{rise}=2$Gyr is the
-and $\tau_{sfh}$ is the rate of decline of the star formation rate, which is based on *****.
+The SFR reaches a maximum around $\tau_\text{rise}=2$ Gyr, and $\tau{\rm sfh}$ describes the decay timescale of star formation as a function of radius $R$.
+\VICE~derives $\tau_{\rm sfh}(R)$ from data of MaNGA galaxies in \cite{sanches20}.
 
@@
 
-VICE normalizes the total mass of star formation against observations from ******.
-The gas inflow is calculated based on our star formation parameterization by using a schmit law 
+The gas inflow is calculated based on an extension of a Kennicutt-Schmidt law (e.g. \cite{kennicutt98}), motivated by 
 \begin{equation}
-    dM_g \propto \dot{\Sigma}^{1/n}
+\dot{\Sigma}_{\star} \propto \\
+\begin{cases}
+    {\Sigma}_{\rm gas} & 2\times 10^7 \leq \Sigma_{\rm gas} \\ 
+    {(\Sigma}_{\rm gas})^{3.6} & 5\times 10^6 \leq \Sigma_{\rm gas} < 2\times10^7 \\ 
+    {(\Sigma}_{\rm gas})^{1.7} & \Sigma_{\rm gas} < 5\times10^6 \\ 
+\end{cases}
 \end{equation}
-where we take $n$ to be ****
 
-Salpeter IMF.
+Help? allowing $\tau_\star = \Sigma_{\rm gas}/\dot{\Sigma}_{\star}$, the depletion timescale, to vary as a function of radius and time??
+
+VICE normalizes the total mass of star formation against observations from \cite{LM15}, and uses a double exponential disk profile for the distribution of star formation.
+We use a Kroupa IMF \cite{kroupa01}.
+
+\VICE\ accounts for radial migration by using the results of the \texttt{h277} hydrodynamical simulation.
+Each VICE SSP is matched to a random nearby star particle \textit{analogue} in \texttt{H277}.
+VICE approximates the migration of this particle by using a $\sqrt{\text{time}}$-diffusion approximation where the change in galactic radius of a star, $\Delta R$, is $\Delta R \propto \sqrt{\text{t}}$.
+VICE does not account for radial gas flows. 
+Using the results of a hydrodynamical simulation without modification limits the free parameters in \VICE; however we do not explore different dynamic histories.
+It is still unknown what role dynamic structure and history plays in chemical evolution.
+
+As the strength of outflows controls the resulting $\alpha$ abundances, \VICE~creates a metallicity gradienty by defining
+\begin{equation}
+\eta(R) = \frac{y_{\alpha}^{\rm CC}}{Z_{\alpha, \odot}} 10^{(-0.08\text{ kpc}^{-1})(R-4\text{ kpc})+0.3} + r - 1.
+\end{equation}
+We do explore uniformly scaling yields and outflows in Section REF.
+While we can constrain relative yields, the absolute scaling of yields and outflows is unknown and chemical evolution models are insensitive to this overal scalling (e.g.
+\cite{james_dwarf}).
 
@@
 		\hline
-		Study & $y_{\rm C, 0}^{\rm agb}$ & $\alpha_{\rm agb, 20}$\\
+		AGB Model & $y_{\rm C, 0}^{\rm AGB}$ & $\alpha_{\rm AGB, 20}$\\
 		\hline
@@
 
-\section{Validating the APOGEE Subgiant Sample}\label{sec:jack}
-Our APOGEE subgiant sample excludes stars marked with the following flags:
-\begin{itemize}
-\item \texttt{ancillary young embedded cluster}
-\item \texttt{ancillary emission line star}
-\item \texttt{MIR-deected candidate cluster member}
-\item \texttt{selected as part of the EB program}
-\item \texttt{selected as part of the young cluster study (in-SYNC)}
-\item \texttt{W3/4/5 star forming complex}
-\end{itemize}
+\section{The APOGEE Subgiant Sample}\label{sec:jack}
 
-To select stars only in the subgiant branch, we select stars in a polygon in $\log g$-$T_\text{eff}$ space described by the following cuts:
+We use the criteria outlined in \cite{jack_subgiant} to create a sample of subgiants from APOGEE DR17 \cite{apogee17} as our primary observational constraint. 
+\cite{jack_subgiant} selects a region of stars in $\log g$-$T_\text{eff}$ space described by the following polyhedron
 \begin{equation}
@@
 
-Instead of excluding stars which have experienced FDU and thus modified carbon abundances as JACK's subgiant sample does, another approach to predict the birth abundances of carbon and nitrogen in stars is to model the predicted abundance effects of dredge up and then correct the measured abundances, as is done in V21.
+This cut isolates a clean sample of subgiants.
+As First Dredge Up, which affects carbon and nitrogen abundances, only occurs during the ascent onto the red giant branch, subgiant stars are unaffected by this enrichment.
+
+Additionally, we exclued stars in APOGEE marked by the following flags.
+\begin{itemize}
+\item \texttt{ancillary young embedded cluster}
+\item \texttt{ancillary emission line star}
+\item \texttt{MIR-deected candidate cluster member}
+\item \texttt{selected as part of the EB program}
+\item \texttt{selected as part of the young cluster study (in-SYNC)}
+\item \texttt{W3/4/5 star forming complex}
+\end{itemize}
+
+A second approach in determining birth abundances in stars is to correct the surface abundance effects of FDU, as in \cite{fiorenzo+21}.
+We do note that there is a slight difference in the yields found through \cite{fiorenzo+21} and \cite{jack_subgiant}.
+As o
+
+We choose to use \cite{jack_subgiant}'s sample as this does not rely on additional layers of modeling, providing a more direct constraint to our model and limiting our systematic uncertainties.
 
 \newpage
-\section{Effects of Alternate AGB Models}\label{sec:alt_agb}
+\section{Additional Considerations of Yields}\label{sec:alt_agb}
 
@@
 
-    \caption[Alternate AGB models]{Same as \ref{fig:agb_sims} but comparing our fiducial model to our recommended z-dependent $y_\text{C}^\text{CC}$ model.
-A plot of the stars of our favored CCSNe model colored by radius.
-The contours represent the density of V+21 data.
-The model is given Gaussian scatter equivalent to the mean error in the abundances reported by APOGEE.
-}
+    \caption[Alternate AGB models]{Comparisons of our 4 different AGB models except with $f_{\rm agb} = 0.2$, and a metallicity dependent CCSNe yield.
+Both panels plot [C/Mg]-[Mg/Fe], except the left has a bin centered at 0, and the right at [Mg/H]$=0.2$.
+The higher metallicity bin exposes how many of the AGB models predict downturns near solar metallicity which are not present in our data.}
+\end{figure}
+
+\begin{figure}
+    \includegraphics{y_mg.pdf}
+\end{figure}
+
+\begin{figure}
+    \includegraphics{fe_ia.pdf}
 \end{figure}

### 2023-04-06 osc/run.sh
new models and plots

@@ -1,125 +1,0 @@
-#!/bin/bash
-
-# Default values
-eta=1
-beta=0.001
-lateburst=false
-agb_fraction=0.2
-out_of_box_agb=false
-agb_model="C11"
-lateburst_amplitude=1.5
-fe_ia_factor=""
-filename=""
-
-# Function to generate filename
-function generate_filename {
-  # Extract command line arguments
-  local eta="$1"
-  local beta="$2"
-  local lateburst="$3"
-  local agb_fraction="$4"
-  local out_of_box_agb="$5"
-  local agb_model="$6"
-  local lateburst_amplitude="$7"
-  local fe_ia_factor="$8"
-
-  # Generate filename
-  local filename="${agb_model}_f${agb_fraction}"
-  if [ "$out_of_box_agb" = true ]; then
-    filename="${filename}_OOB"
-  fi
-  filename="${filename}_eta${eta}_beta${beta}"
-  if [ "$lateburst" = true ]; then
-    filename="${filename}_lateburst${lateburst_amplitude}"
-  fi
-  if [ "$fe_ia_factor" != "" ]; then
-    filename="${filename}_Fe${fe_ia_factor}"
-  fi
-  filename="${filename}"
-
-  # Return filename
-  echo "$filename"
-}
-
-
-while [[ $# -gt 0 ]]
-do
-  key="$1"
-  case $key in
-    -e|--eta)
-      eta="$2"
-      shift
-      shift
-      ;;
-    -b|--beta)
-      beta="$2"
-      shift
-      shift
-      ;;
-    -l|--lateburst)
-      lateburst=true
-      shift
-      ;;
-    -f|--agb_fraction)
-      agb_fraction="$2"
-      shift
-      shift
-      ;;
-    -o|--out_of_box_agb)
-      out_of_box_agb=true
-      shift
-      ;;
-    -m|--agb_model)
-      agb_model="$2"
-      shift
-      shift
-      ;;
-    -n|--filename)
-      filename="$2"
-      shift
-      shift
-      ;;
-    -A|--lateburst_amplitude)
-      lateburst_amplitude="$2"
-      shift
-      shift
-      ;;
-    -i|--fe_ia_factor)
-      fe_ia_factor="$2"
-      shift
-      shift
-      ;;
-    -h|--help)
-      display_help
-      exit 0
-      ;;
-    *)
-      echo "Unknown option: $key"
-      exit 1
-      ;;
[…]

### 2023-04-06 osc/simulate.py

@@ -1,93 +1,145 @@
 import sys
 import vice
 
-import argparse
+import surp.src.yields
+from surp.src.yields import amplified_yields
 
+import surp.src.simulation.multizone_sim
 from surp.src.simulation.multizone_sim import run_model
 from surp import __version__
 
 y_c_0 = 0.005
-y_c_cc_0 = 0.0029
+
 zeta_n = 9e-4
-y_cc_n = 3.6e-4
-y_n_0 = 9e-4
+y_n_flat = 7.1e-4
 
 Z_Sun = 0.014
 
 
-def main():
-    print("Loaded")
-    args = parse_args()
-    f_agb = args.agb_fraction
-    beta = args.beta
-    eta = args.eta
 
-    args.agb_model = {
+def main(prefix, filename, eta=1, beta=0.001, lateburst=False,
+         f_agb=0.2, OOB=False, agb_model="C11", A=1.5, 
+         fe_ia_factor=1, traditional_f=False, y_c_cc_0=0.0028,
+         alpha_n=0.5, dt=0.01, n_stars=2):
+
+    print("Loaded")
+    agb_model = {
             "C11": "cristallo11",
             "K10": "karakas10",
             "V13": "ventura13",
             "K16": "karakas16"
-            }[args.agb_model]
+            }[agb_model]
 
-    A = args.lateburst_amplitude
-    lateburst = args.lateburst
-
-    prefix = args.prefix
-
-    print(args)
-
-    name = args.filename
-
-    set_yields(args)
+    set_yields(eta=eta, beta=beta, fe_ia_factor=fe_ia_factor,
+        agb_model=agb_model, oob=OOB, f_agb=f_agb, 
+        y_c_cc_0=y_c_cc_0, alpha_n=alpha_n)
 
     if lateburst:
         spec = "lateburst"
     else:
         spec = "insideout"
 
-    alpha_agb, alpha_cc = calc_alpha(args)
-
     print("configured")
 
-    run_model(name, prefix=prefix, agb_yields=args.agb_model, agb_factor=alpha_agb,
-            eta_factor=eta, spec=spec, burst_size=A)
+    run_model(filename, prefix=prefix,
+              eta_factor=eta, 
+              spec=spec, 
+              burst_size=A, 
+              dt=dt, 
+              n_stars=n_stars,
+              )
     print("complete")
 
 
-def set_yields(args):
-    eta = args.eta
-    vice.yields.ccsne.settings["N"] = y_cc_n
[…]

### 2023-04-06 osc/simulate.sh

@@ -4,6 +4,9 @@ module load miniconda3/4.12.0-py39
 
 # written like this so we can substitute the 
 # name into the file for easier understanding
+
+# first argument is filename
+# second argument is the python call
 echo "Submitting Job"
 rm -f logs/$1.log
 
@@ -24,7 +27,10 @@ cd $SLURM_SUBMIT_DIR
 module load miniconda3/4.12.0-py39
 
 
-python \$SLURM_SUBMIT_DIR/osc/simulate.py \$TMPDIR/ $@
+python -c "
+$2
+" \$TMPDIR/
+
 python \$SLURM_SUBMIT_DIR/osc/json_outputs.py \$TMPDIR/
 
 cp -r -u \$TMPDIR/*.json \$SLURM_SUBMIT_DIR/output

### 2023-04-06 run.sh

@@ -1,0 +1,193 @@
+#!/bin/bash
+
+# Default values
+eta=1
+beta=0.001
+lateburst=false
+agb_fraction=0.2
+out_of_box_agb=false
+agb_model="C11"
+lateburst_amplitude=1.5
+fe_ia_factor="None"
+filename=""
+dt=0.01
+Nstars=2
+alpha_n=0.5
+y_c_cc_0=0.0028
+
+
+function display_help {
+  echo "Usage: $0 [OPTIONS]"
+  echo "Options:"
+  echo "  -e, --eta              the efficiency multiplier of the supernova feedback (default: 1)"
+  echo "  -b, --beta             the power-law index of the star formation law (default: 0.001)"
+  echo "  -l, --lateburst        add a late burst of star formation (default: false)"
+  echo "  -f, --agb_fraction     the mass fraction of AGB stars in the initial mass function (default: 0.2)"
+  echo "  -o, --out_of_box_agb   use an out-of-box AGB model (default: false)"
+  echo "  -m, --agb_model        the name of the AGB model to use (default: C11)"
+  echo "  -n, --filename         the name of the output file (default: auto-generated)"
+  echo "  -A, --lateburst_amplitude   the amplitude of the late burst (default: 1.5)"
+  echo "  -i, --fe_ia_factor     the iron yield factor of type Ia supernovae (default: none)"
+  echo "  -d, --timestep         the size of the time step (default: 0.01)"
+  echo "  -a, --alpha_n          the agb fraction of primary N"
+  echo "  -p, --c_plateau        the amount of plateau carbon"
+  echo "  -h, --help             display this help message"
+}
+
+
+# Function to generate filename
+function generate_filename {
+  # Extract command line arguments
+  local eta="$1"
+  local beta="$2"
+  local lateburst="$3"
+  local agb_fraction="$4"
+  local out_of_box_agb="$5"
+  local agb_model="$6"
+  local lateburst_amplitude="$7"
+  local fe_ia_factor="$8"
+  local dt="$9"
+
+  # Generate filename
+  local filename="${agb_model}_f${agb_fraction}"
+  if [ "$out_of_box_agb" = true ]; then
+    filename="${filename}_OOB"
+  fi
[…]

### 2023-04-06 src/simulation/multizone_sim.py

@@ -8,17 +8,13 @@ import os
 
 from .src.simulations.migration import diskmigration
 from .src.simulations.disks import star_formation_history
-from .. import yields
-from ..yields import amplified_yields
-
-# modify yields
 
 MAX_SF_RADIUS = 15.5 #kpc
 END_TIME = 13.2
 
-def run_model(name, migration_mode="diffusion", spec="insideout", n_stars=2, agb_yields="cristallo11", 
+def run_model(name, migration_mode="diffusion", spec="insideout", n_stars=2, 
               seed=None, multithread=False, dt=0.01, burst_size=1.5, eta_factor=1, 
-              ratio_reduce=False, agb_factor=1, prefix=None):
+              ratio_reduce=False,prefix=None ):
     """
     This function wraps various settings to make running VICE multizone models
     easier for the carbon paper investigation
@@ -45,14 +41,6 @@ def run_model(name, migration_mode="diffusion", spec="insideout", n_stars=2, agb
     n_stars: ``int`` [default: 2]
         The number of stars to create during each timestep of the model.
 
-    agb_yields: ``str`` [default: "cristallo11"]
-        The yield set to use for AGB carbon produciton. Acceptable values are
-        - "cristallo11"
-        - "karakas10"
-        - "ventura13"
-        - "karakas16"
-        Look at VICE for more details
-
     multithread: ``bool`` [default: False]
         If true, runs the multithreaded version of the model.
         The maximum number of threads is currently 8
@@ -68,7 +56,6 @@ def run_model(name, migration_mode="diffusion", spec="insideout", n_stars=2, agb
 
     eta_factor: ``float`` [default: 1]
         A factor by which to reduce the model's outflows. 
-        Does not reduce CCSNe yields
 
     ratio_reduce: ``bool``
         
@@ -89,19 +76,6 @@ def run_model(name, migration_mode="diffusion", spec="insideout", n_stars=2, agb
     Nstars = min(2*MAX_SF_RADIUS/zone_width * END_TIME/dt * n_stars, 3102519)
     print("Nstars = %i" % Nstars)
 
-    # we use the nitrogen yields in each study
-    if type(agb_yields) == str:
-        for elem in ["c", "n", "o", "fe"]:
-            if elem == "fe" and agb_yields == "ventura13":
-                if agb_factor == 1:
-                    vice.yields.agb.settings[elem] = "cristallo11"
-                else:
[…]

### 2023-04-06 src/simulation/old_models/karakas10.py

@@ -1,7 +1,0 @@
-import sys
-sys.path.append("..")
-from multizone_sim import run_model
-
-
-if __name__ == "__main__":
-    run_model("k10", agb_yields="karakas10", n_yields="J22", dt=0.1)

### 2023-04-06 src/simulation/old_models/karakas16.py

@@ -1,7 +1,0 @@
-import sys
-sys.path.append("..")
-from multizone_sim import run_model
-
-
-if __name__ == "__main__":
-    run_model("karakas16", agb_yields="karakas16")

### 2023-04-06 src/simulation/old_models/lateburst.py

@@ -1,6 +1,0 @@
-from multizone_sim import run_model
-
-
-if __name__ == "__main__":
-    #run_model("fiducial", agb_yields="cristallo11", n_stars=8)
-    run_model("lateburst", agb_yields="cristallo11", n_yields="J22", spec="lateburst")

### 2023-04-06 submit_model.sh

@@ -6,7 +6,7 @@ do
   do
     for model in "C11"  #"K10" "V13" "K16"
     do
-      for eta in 0.6 0.3 # 1
+      for eta in 1
       do
         bash osc/run.sh -f $f_agb -b $beta -m $model -e $eta
       done

### 2023-04-06 thesis/tex/main.tex

@@
         \vfill
-       {Daniel Alexandra Boyea}\\
+       {Danielle Alexandra Boyea}\\
        \vfill
@@
     \includegraphics{subgiants_mgfe.pdf}
-    \caption[APOGEE Subgiants]{The [C/Mg] ratio against [Mg/H] (left) and [Mg/Fe] (right) for the sample of subgiants as in \cite{jack_subgiant}.
-The left panel uses blue and orange to represent high and low $\alpha$ sequences respectively.
-On the right, we plot more metal rich ([Mh/H]) stars with darker colors.}
+    \caption[APOGEE Subgiants]{The [C/Mg] ratio against [Mg/H] (top) and [Mg/Fe] (bottom) for our sample of APOGEE subgiants.
+On the top, we plot the high and low $\alpha$ sequences using Eq.
+\ref{eq:high_alpha} in blue and orange.
+On the bottom, we show more metal rich ([Mg/H]) stars with lighter colors.}
     \label{fig:subgiants}
@@
 
-\section{Asymptotic giant branch carbon}
+\section{Asymptotic giant branch carbon}\label{sec:agb}
 
@@
 
-        \caption[AGB carbon yields]{The net fraction carbon yield ($M_\text{C}$, the amount of carbon produced by the star divided by $M$) plotted as a function of mass, $M$.
+        \caption[AGB carbon yields]{The net fraction AGB carbon yield ($\tilde{y}$) plotted as a function of initial stellar mass $M$.
 Lighter colors represent higher values of metalicity ([M/H]).
-Each panel represents a different AGB model.
-K10 reports stars at MoverH -3, -2, etc.
-I can reproduce C11 and K10 but not other V13 and KL16 :(((}
-
+Each panel represents yields from one of our 4 AGB models: C11 \citep{cristallo+11, cristallo+15}, K10 \citep{karakas10}, V13 \citep{ventura+13,ventura+14,ventura+18}, and K16 \citep{KL16, karakas+18}.
+            %C11 reports values at metallicities $Z=$ 0.0001, 0.0003, 0.001, 0.002, 0.003, 0.006, 0.008, 0.01, 0.014, 0.02; K10 at $Z=$0.0001, 0.004, 0.008, 0.02; V13 at $Z=$0.0003, 0.001, 0.002, 0.004, 0.008, 0.014, 0.04; and K16 at $Z=$0.0028, 0.007, 0.014, 0.03.
+        }
             \label{fig:y_agb}
@@
 
-    \caption[AGB yields delayed-time-distribution]{
-    The Delay Time Distribution for AGB STars}
+    \caption[AGB yields delay time distribution]{
+        The normalized delay time distribution (DTD) of AGB carbon, plotted as the net carbon enrichment $M(t)$ normalized to the total carbon enrichment mass $M_{\rm tot}$.
+Left: Each solid curve corresponds to an AGB yield model at solar metallicity (C11, K10, V13, or K16), and the dashed black line represents the delay time distribution of type Ia supernovae ($\propto t^{-1.1}$).
+Each model has similar DTD, and most AGB enrichment occurs befor 1 Gyr.
+Right: each curve represents the C11 AGB model at a different metallicities.
+Higher metallicities cause carbon enrichment to occur earlier and for the DTD to become non-monotonic.
+    }
 
@@
 
-    \caption[AGB yield metallicity dependence]{On the left, we plot the IMF weighted net fractional carbon yields of each AGB model as a function of metalicity.The right panel plots the normalized net carbon AGB yield as a function of time for a population of stars born at the same time at solar metallicity.
-We note that for the right panel, the minimum of the DTD for V13 is }
+    \caption[AGB yield metallicity dependence]{The net fractional IMF-weighted AGB carbon yield $\Ycagb$ as a function of metallicity for each of our AGB yield models.
+    }
 
@@
     \includegraphics{y_c_cc.pdf}
-    \caption[CCSNe carbon yields]{The fist plot shows IMF-weighted net fractional CCSNe yield of
-        carbon, $y_C^{cc}$ against metalicity, [M/H], for different studies.
-        The right plot instead shows [C/O]$^\text{CC}$, the logarithm of the
-        abundance ratio of carbon to oxygen if CCSNe were the only carbon
-        source, also as a function of metallicity for the same set of studies.
-        The black line represents the carbon yield of the fiducial model,
-        $y_C^{CC} = 0.004? (Z/Z_{\sun})^{0.3}$, and becomes dashed over regions
-        where we have not tested our model.\citep{NKT13}, \citep{LC18},
-        \citep{sukhbold+16}, \citep{WW95}
- }
+    \caption[CCSNe carbon yields]{Top: The net fractional IMF-weighted CCSNe yield of
+        carbon, $\Ycc$ against metalicity,$\log Z/Z_\odot$, for different studies.
+        The right plot instead shows the CCSNe carbon to magnisium abundance ratio, defined in Eq. \ref{eq:c_mg_cc}. The black line represents the carbon yield of the fiducial model,
+    $\Ycc = 0.0029 + 0.001 (Z/Z_{\odot})$.
+The pink line represents the C11 AGB model.
+We plot yields from \citet{WW95} as red triangles; \citep{sukhbold+16} as orange diamonds, with larger points representing models with higher explodability; \citet{NKT13} as green stars; and \citep{LC18} as blue circles.
+\citet{LC18} is the only model including rotation.
+\citet{NKT13} and \citet{WW95} also report Population III yields, plotted with arrows at the very left.}
     \label{fig:y_cc}
@@
 We summarise many of the predictions of stellar models in Fig. \ref{fig:y_cc}. 
-\begin{equation}
+\begin{equation}\label{eq:c_mg_cc}
     {\rm [C/O]^{CC}} = \log_{10}\left( \frac{y_{\rm C}^{\rm CC}}{y_{\rm O}^{\rm CC}}\right) - \log_{10} \left( \frac{Z_{C, \sun }}{Z_{O, \sun }} \right)
@@
 While our galaxy is likely not in perfect equilibrium or described by a single, homogenous chemical region, we can still use an equilibrium approximation to understand total yields.
-\cite{WAF17}. \cite{james_dwarf}, \cite{james+22}
 
-Here, we assume a simple one-zone chemical evolution model.
+\cite{james_dwarf}, \cite{james+22}
+
+Following \citet{WAF17}, we assume a simple one-zone chemical evolution model.
 A one zone model is essentially zero-dimensional---the gas and stars are considered to be homogenously mixed, so we can represent all quantaties as scalars.
-We use $M_{X}$ to represent the mass of element X
+
+We define $M_{X}$ to be the mass of element X in the gas phase, $\dot{M}_\star$ to be the star fomation rate (in M$_\odot$ yr$^{-1}$).
 
@@
     \includegraphics[]{analytic.pdf}
-    \caption[Reverse fit yields]{Our reverse fitting method to determine total CCSNe contribution}
+    \caption[Reverse fit yields]{Inferred $\Ycc$ against [Mg/H], assuming equilibrium and 3$\times$C11 AGB yields.
+Blue points are meadians of each metallicity bin with errorbars as the median standard deviation.
+The orange curve is our best fit model.}
 \end{figure}
@@
 
-\begin{equation}
+\begin{equation}\label{eq:high_alpha}
 \begin{cases}
@@
 
-\begin{figure*}
-\label{fig:c_evo}
+\begin{figure}
+\centering
 \includegraphics{evo_tracks.pdf}
 \includegraphics{evo_slices.pdf}
-\caption[Carbon chemical evolution tracks]{The top set of panes show the time evolution of the gas phase of our
-    fiducial model, plotted as tracks through \caah and \caafe where each colored line corresponds to the evolution at that galactic radius. 
-The bottom set instead shows the galaxies gas-phase \caah and \caafe trend at 5 different time slices. 
+\caption[Carbon chemical evolution tracks]{Top: the time evolution of the gas phase of our
+    fiducial model, plotted as tracks through \caah~and \caafe~where each colored line corresponds to the evolution at that galactic radius. 
+    Bottom: snapshots of the gas-phase \caah~and \caafe~trend, each line a different time.
 }
-\end{figure*}
+\label{fig:c_evo}
+\end{figure}
 
@@
 \includegraphics{oob_agb.pdf}
-
-\caption[AGB GCE Models]{Left: the \caah~ \textbf{median} present-day stellar tracks for four different
-AGB models (\cristallo, \karakas, \kl, and \ventura ). The median bin [C/Mg] values from \citet{jack_subgiant} are
-plotted as black points with 1-std errors marked by horizontal grey dashes.
-Right: same as left but for \caafe. While each AGB yield model may
-differ in detail, there is minimal effect on the overall [C/Mg] trends.
-
-While we show the entire dataset in Fig. \ref{fig:subgiants}, we chose to compare the
-binned data to our models as black points with dashes representing the 1-sigma
-spread, as in e.g. Fig. \ref{fig:agb_sims}. \label{fig:agb_sims}
+\caption[AGB GCE Models]{Left: the \caah~median present-day stellar tracks for four different AGB models (C11, K10, V13, K16) with a metallicity-independent $\Ycc$.
+Right: same except [C/Mg] against [Mg/Fe] for the bin $-0.15<\text{[Mg/H]}<-0.05$.
+The median bin [C/Mg] values from \citet{jack_subgiant} are plotted as black points with standard median deviations plotted as grey dashes.
+ While each AGB yield model may differ in detail, there is minimal effect on the overall [C/Mg] trends.
 }
+\label{fig:agb_sims}
 \end{figure}
@@
 
-\caption[Adjusted yield models]{Similar to \ref{fig:agb_sims} except the top plot shows the fiducial model with lower and higher values of $\beta$, the C-CCSNe metallicity dependence.
-The bottom plot is the same except shows varying AGB fractions.}
+\caption[Adjusted yield models]{Similar to \ref{fig:agb_sims} except the top plot shows the fiducial model with lower and higher values of $\zeta$, the C-CCSNe metallicity dependence.
+The bottom plot is the same except shows models with $f_{\rm AGB}=$0.1, 0.2, and 0.4.
+Both the $f_{\rm AGB}$ and $\zeta$ influence \caah, but only $f_{\rm AGB}$ has a significant impact on \caafe.}
 \end{figure}
@@
 \centering
-\includegraphics[]{lateburst_eta.pdf}
+\includegraphics{lateburst_eta.pdf}
+\includegraphics{eta.pdf}
 
-\caption[Lateburst and reduced-outflow models]{Same as Fig.
-\ref{fig:agb_sims} but comparing the fiducial model to the reduced outlow model and a lateburst model.
-(okay, need to totally change approach...)}
+\caption[Lateburst and reduced-outflow models]{Same as Fig. \ref{fig:agb_sims} but comparing the fiducial model to two lateburst models (top), and two reduced outflow models (bottom).}
 \end{figure}
@@
     \includegraphics[scale=0.9]{cooh_scatter.pdf}
-    \caption[Scatter agreement]{The simulated stars of our model at present day plotted on \caah~and colored such that lighter colors represent stars born at greater galactric radii.}
+    \caption[Scatter agreement]{The simulated stars of our model at present day plotted on \caah~and colored such that lighter colors represent stars born at greater galactric radii.
+Our model is able to explain the scatter and shape, relying on a combination of artificial measurment errors and radial migration.}
 \end{figure*}
@@
 
+\begin{figure}
+    \includegraphics{nitrogen.pdf}
+    \includegraphics{c_n.pdf}
+    \caption{Nitrogen almost works?}
+\end{figure}
+
 \begin{figure*}
@@
 \includegraphics[]{summary.pdf}
-\caption[Gas phase abundances]{Present-day gas phase tracks of the fiducial model in \caah~space. M101 is valid comparison to MW ...(van Dokkum et al. 2014)}
+\caption[Gas phase abundances]{Present-day gas phase tracks of the fiducial model in \caah~space. M101 is valid comparison to MW ...(van Dokkum et al. 2014)
+
+    \citep{cooke+17}, \citet{nissen+14}, \citet{fabbian+09}, \citet{berg+19}, \citet{esteban+02}, \citet{esteban+09}, \citet{esteban+14}, \citet{esteban+19},
+}
 \label{fig:gas_phase}
@@
 
+\begin{figure}
+    \centering
+    \includegraphics{logg_jack.pdf}
+\end{figure}
+
 This cut isolates a clean sample of subgiants.
@@
 \begin{figure}[htp]
-    \includegraphics{coofe_agb_extra.pdf}
-    \includegraphics{coofe_agb_extra_0.2.pdf}
+    \centering
+    \includegraphics{agb2.pdf}
 

### 2023-04-07 thesis/tex/main.tex
new captions

@@
 \usepackage{setspace}
+\usepackage{array}
+\setlength\extrarowheight{5pt}
 
@@
 \counterwithout{table}{chapter}
+\counterwithout{equation}{chapter}
 
@@
 \defcitealias{karakas+18}{K18}
-
+\defcitealias{james+21}{J21}
+
+\newcommand{\JJ}{\citetalias{james+21}}
 \newcommand{\cristallo}{\citetalias{cristallo+11}+\citetalias{cristallo+15}}
@@
 \newcommand{\zoo}{\ensuremath{Z/Z_{\sun }}}
-\newcommand{\Ycc}{\ensuremath{y_{\rm C}^{\rm cc}}}
+\newcommand{\Ycc}{\ensuremath{y_{\rm C}^{\rm CC}}}
 \newcommand{\Yct}{\ensuremath{y_{\rm C, 0}^{\rm tot}}}
-\newcommand{\Yoc}{\ensuremath{y_{\rm O}^{\rm cc}}}
-\newcommand{\Ycagb}{\ensuremath{y_{\rm C}^{\rm agb}}}
+\newcommand{\Yoc}{\ensuremath{y_{\rm Mg}^{\rm CC}}}
+\newcommand{\Ycagb}{\ensuremath{y_{\rm C}^{\rm AGB}}}
 \newcommand{\sun}{\ensuremath{\odot}}
+
+\newcommand\T{\rule{0pt}{2.6ex}}       % Top strut
+\newcommand\B{\rule[-1.2ex]{0pt}{0pt}} % Bottom strut
+\newcommand{\possesivecite}[1]{\citeauthor{#1}'s \citeyearpar{#1}}
+
+\setcitestyle{aysep={}} 
+\setcitestyle{notesep={; }}
 
@@
        \textbf{The Galactic Chemical Evolution of Carbon} \\
-        Implications for nucleosynthesis
+       [3\baselineskip]
+        Undergraduate Research Thesis\\
+       [3\baselineskip]
+    Presented in partial fulfillment of the requirements for graduation \textit{with research distinction in Astronomy and Astrophysics} in the College of Arts and Sciences of The Ohio State University \\
+       [3\baselineskip]
+        by \\
+       {Daniel Alexander Boyea}\\
+       [3\baselineskip]
+       The Ohio State University\\
+       April 2023\\
+       [3\baselineskip]
+       Project Advisor: David Weinberg, Department of Astronomy
+       % Rolando Vald\'es Aguilar\\
        \vfill
-        Research Thesis
-        \vfill
-        Presented in partial fulfillment of the requirements for graduation \textit{with research distinction} in Astronomy and Astrophysics in the College of Arts and Sciences of The Ohio State University.
-        \vfill
-        by 
-        \vfill
-       {Danielle Alexandra Boyea}\\
-       \vfill
-       Department of Astronomy\\
-       The Ohio State University\\
-       \vfill
-       April 2023
-       \vfill
-       Thesis Committee:\\
-       David Weinberg, Advisor \\
-       Jennifer Johnson \\
-       Rolando Vald\'es Aguilar\\
-       \vfill
-
    \end{center}
@@
 Stellar evolution models provide highly uncertain predictions for elemental yields due to our limited understanding of stellar physics.
-In this paper, we aim to estimate the nucleosynthetic yields of carbon using galactic chemical evolution models.
-
-We find that the AGB stars make up a fraction $0.20_{-20}^{+80}$ of total carbon production at late times.
+In this paper, I aim to estimate the nucleosynthetic yields of carbon using galactic chemical evolution models.
+
+I find that the AGB stars make up a fraction $0.20_{-20}^{+80}$ of total carbon production at late times.
 
@@
 
-Astronomy is unique among sciences in that we can determine the history of chemical elements.
-While stable on earth, the churning gasses and firery stars can dramatically transform elements into new materials.
-However, we still have much to learn about how each chemical element is made.
-In this work, we will hope to clarify how the chemical element carbon, the basis of life, is made in the universe.
-
-As the universe just began to cool following the big bang, the only elements around were hydrogen, helium, and trace amounts of lithium and berylium.
-All other elements were formed afterwords with the help of stars.
-Stars of different masses, ages, and metalicities have substantially different interior stuctures.
-Different stars produce vastly different amounts of different chemical elements depending on their properties.
-
-Stellar evolution, at the basis of galactical chemical evolution, predict the elemental production of different stellar processes. 
-However, these models are rife with uncertainties, limited by our understanding of critical physical processes such as nuclear reaction rates, convection, opacity, and mass loss (CITE, e.g.
-stellar physics reviews).
-
-Carbon and nitrogen are well studied elements as they are easy to observe (Citations...).
-Additionally, carbon and nitrogen are used as age indicators for giant branch stars (citations, e.g.
-\cite{fiorenzo+21}), and are the only light elements known to be produced significantly in Asymptotic Giant Branch Stars (AGB) (cite).
-
-However, our theoretical understanding of the producion sources of carbon are still uncertain.
-
-While easily visible in many stars, determining birth abundances of carbon and nitrogen are
-
-One challenge of measuring abundances of carbon in star is that when a star becomes a RGB star, material from the CNO-processed core.
+Galactic chemical evolution (GCE) aims to understand the chemical and star formation history of galaxies.
+At the core of GCE models are stellar yields---the amount of each chemical element stars produce (or destroy).
+Different chemical elements are produced in different sites, so stars leave traces of the Galaxy's chemical history.
+Through \textit{Galactic Archeology}, I can reconstruct the history of our galaxy by investigating the clues left in the remains---stars from the early universe \citep{Weinberg+22, emily+19}.
+
+I aim to understand the GCE of carbon, where the element is produced and how the abundances of this element evolve over time.
+Why stuy carbon?
+Carbon is unique nucleosynthetically, one of few light elements (along with nitrogen) which are produced in Asymptotic Giant Branch (AGB) stars \citep[for example,][]{jennifer19, KL14}.
+Carbon and nitrogen are well studied elements as they are easy to observe in stellar spectra, even at the lowest metallicities \citep{FN15} SOMETHING ELSE?.
+Additionally, carbon and nitrogen are used as age indicators in red giant branch stars \citep[e.g.][]{martig16, MG15, fiorenzo+21}.
+While we know carbon is produced in AGB stars and core collapse supernovae (CCSNe), we still have limited understanding of the importaince and metallicity-dependence of each process.
+
+We also know that there is evidence for non-monatonic carbon yield patterns. 
+pattern where carbon is more readily produced by both high metallicity and very low metallicity stars (CEMPS, early GCE results), but our picture. \citep{FN15,cooke+17,berg+19}.
+
+Stellar evolution models predict stellary yields, playing a crucial role in GCE.
+However, these models are rife with uncertainties, limited by our understanding of critical physical processes such as nuclear reaction rates, convection, rotational mixing, opacity, and mass loss CITATIONS.
+Changes in opacity, rotation, reaction rates, and explodability can substantially affect carbon yields \citep{KL14,V13, LC18, emily+21}.
+
+GCE models typically use unmodified nucleosythetic predictions and attempt to create models matching observaions by varying star formation history and other parameters.
+I instead use the observations as a constraint, determining which yield assuptions are consistant with galactic abundance trends.
+
+While there are many stellar measurments of carbon, accurately determining the birth abundance is more challenging.
+For example, when a star becomes a RGB star, material from the CNO-processed core \citep{fiorenzo+21,KL14}.
 Since this core-processed material is now carbon depleted and nitrogen enhanced, measurments of this star's atmosphere will no longer reflect the birth abundances of the star.
-Additionaly, carbon is extremelt challenging to measure gas-phase abundances for because the strongest visible line is ...., e.g. carbon unreliable in GALAH, low detections.
+Additionaly, carbon is faint in HII regions and determining gas-phase abundances is challenging \citet{skillman+20}.
+Other surveys, such as GALAH, have unreliable carbon measurments with low detection rates \citep{emily+19}.
 
@@
 
-We also know that there is evidence for non-monatonic carbon yield patterns. 
-pattern where carbon is more readily produced by both high metallicity and very low metallicity stars (CEMPS, early GCE results), but our picture.
-
-Additionally, stellar models are computationally expensive, even in one dimension, so while there are grids of predictions, these are not always fine enough to make accurate chemical evolution models.
-
 In Fig.
-\ref{fig:subgiants} we present a sample of APOGEE subgiants.
-These subgiants were chosen based on their location in the HR diagram based on criteria in \citet{jack_subgiant} replicated in Appendix \ref{sec:jack}.
+\ref{fig:subgiants}, I present a sample of APOGEE subgiants.
+These subgiants were chosen based on their location in the HR diagram based on the criteria in \citet{jack_subgiant} also replicated in Appendix \ref{sec:jack}.
 Because subgiants have not undergone FDU, their surface abundances are an accurate reflection of the birth abundances (CITATION).
@@
     \caption[APOGEE Subgiants]{The [C/Mg] ratio against [Mg/H] (top) and [Mg/Fe] (bottom) for our sample of APOGEE subgiants.
-On the top, we plot the high and low $\alpha$ sequences using Eq.
-\ref{eq:high_alpha} in blue and orange.
-On the bottom, we show more metal rich ([Mg/H]) stars with lighter colors.}
+On the top, I plot high-$\alpha$ stars in blue and low-$\alpha$ stars in orange using the seperation defined in Equation \ref{eq:high_alpha}.
+On the bottom, I colorcode stars according to their [Mg/H] abundance.}
     \label{fig:subgiants}
@@
 
-Nucleosynthetic predictions 
-Modern theoretical nucleosynthesis provides our starting point for our models.
-We focus on three primary nucleosynthetic pathways: AGB stars, CCSne, and SNeIa.
-Each process has unique timescales and element production which we can trace through the tools of GCE.
+Modern theoretical nucleosynthesis provides the starting point for our models.
+I focus on three primary nucleosynthetic pathways: AGB stars, CCSne, and SNeIa.
+Each process has unique timescales and element production which I can trace through the tools of GCE.
 While carbon is only known to be produced in AGB stars and CCSNe, comparing carbon to iron production (from SNeIa) adds a valuable constraint to our models and insight into the delay-time production of carbon.
@@
 
-We focus on O and Mg as $\alpha$ elements only formed in CCSNe, and use Fe to
+I focus on O and Mg as $\alpha$ elements only formed in CCSNe, and use Fe to
 trace delayed enrichment from SNeIa. C and N are both formed in AGB and CCSNe.
 
-There are two $\alpha$-elements we care about: Mg and O. Stellar observations
+There are two $\alpha$-elements I care about: Mg and O. Stellar observations
 of magnesium are more reliable but oxygen abundances are easier to measure in
-HII regions. We assume that both Mg and O are produced entirely in CCSNe with
+HII regions. I assume that both Mg and O are produced entirely in CCSNe with
 constant, metallicity-independent yields. Thus $\text{[Mg/H]} = \text{[O/H]} =
@@
 
-As we focus on the yields of carbon, we keep yields for other elements fixed in
-most models. Taken from \citet{james+21, james+22}, we let
-\begin{itemize}
-    \item $y_\text{Mg}^\text{CC} = 0.00185$
-    \item $y_\text{Mg}^\text{Ia} = 0$
-    \item $y_\text{Fe}^\text{Ia} = 0.00214$
-    \item $y_\text{Fe}^\text{CC} = 0.0012$
-    \item $y_\text{N}^\text{CC} = 0.00036$
-    \item $\tilde{y}_\text{N}^\text{AGB}(M, Z) = 9\times 10^{-4} M \left(\frac{Z}{Z_\odot}\right)$
-\end{itemize}
-
-Also following \citet{james+21, james+22}, we take the SNeIa Delay Time distribution to be a
+To calculate the net initial mass function (IMF)-weighted yields, I use the \citet{james+21} model (hereafter \JJ) with the Versatile Integrator for Chemical Evolution code (\VICE).
+As stellar evolution models predict per-star yields for stars of each mass, we need to integrate over the IMF to determine the total yields in terms of star formation.
+
+As the focus of this work is on carbon yields, I keep all other yields fixed. The yields I use are based on \citet{james+21, james+22}.
+
+Also following \citet{james+21, james+22}, I take the SNeIa Delay Time distribution to be a
 $t^{-1.1}$ law suggested by the observations of \citet{maoz+12}.
 
-\section{Asymptotic giant branch carbon}\label{sec:agb}
-
-\begin{figure*}
-    \centering
- 	    \includegraphics[scale=1]{agb_yields.pdf}\\
-
-        \caption[AGB carbon yields]{The net fraction AGB carbon yield ($\tilde{y}$) plotted as a function of initial stellar mass $M$.
-Lighter colors represent higher values of metalicity ([M/H]).
-Each panel represents yields from one of our 4 AGB models: C11 \citep{cristallo+11, cristallo+15}, K10 \citep{karakas10}, V13 \citep{ventura+13,ventura+14,ventura+18}, and K16 \citep{KL16, karakas+18}.
-            %C11 reports values at metallicities $Z=$ 0.0001, 0.0003, 0.001, 0.002, 0.003, 0.006, 0.008, 0.01, 0.014, 0.02; K10 at $Z=$0.0001, 0.004, 0.008, 0.02; V13 at $Z=$0.0003, 0.001, 0.002, 0.004, 0.008, 0.014, 0.04; and K16 at $Z=$0.0028, 0.007, 0.014, 0.03.
-        }
-            \label{fig:y_agb}
-\end{figure*}
-
-\begin{figure}
-    \includegraphics[scale=1]{y_agb_t2.pdf}
-
-    \caption[AGB yields delay time distribution]{
-        The normalized delay time distribution (DTD) of AGB carbon, plotted as the net carbon enrichment $M(t)$ normalized to the total carbon enrichment mass $M_{\rm tot}$.
-Left: Each solid curve corresponds to an AGB yield model at solar metallicity (C11, K10, V13, or K16), and the dashed black line represents the delay time distribution of type Ia supernovae ($\propto t^{-1.1}$).
-Each model has similar DTD, and most AGB enrichment occurs befor 1 Gyr.
-Right: each curve represents the C11 AGB model at a different metallicities.
-Higher metallicities cause carbon enrichment to occur earlier and for the DTD to become non-monotonic.
-    }
-
-\end{figure}
-
-\begin{figure*}
-    \centering
-
-    \includegraphics[scale=1]{y_agb_vs_z.pdf}
-
-    \caption[AGB yield metallicity dependence]{The net fractional IMF-weighted AGB carbon yield $\Ycagb$ as a function of metallicity for each of our AGB yield models.
-    }
-
-\end{figure*}
+\begin{table}
+	\centering
+    \caption[Fiducial Model]{Yields for the fiducial model}
+	\label{tab:fiducial_mod}
+	\begin{tabular}{l l l l}
+		\hline
+        Element & $\Ycc$ & $\tilde{y}^{\rm AGB}$ & $y^{\rm SNe Ia}$ \\
+		\hline
+        C & $0.0028 + 0.001(Z/Z_\odot)$ & $2.9\times{\rm C11}$ &  0 \\
+        Mg & 0.00185 & 0 & 0 \\
+        Fe & 0.0012 & 0 & 0.00214 \\
+        N & 0.00072 & $9\times10^{-4}(Z/Z_\odot)M$ & 0\\
+		\hline
+	\end{tabular}
+\end{table}
+
+\section{Asymptotic giant branch stars}\label{sec:agb}
 
@@
 
-In this work, we explore four different sets of AGB star yields representative of the variety of options which also provide reasonably well sampled grids in metallicity and mass necessary for chemical evolution studies.
+In this work, I explore four different sets of AGB star yields representative of the variety of options which also provide reasonably well sampled grids in metallicity and mass necessary for chemical evolution studies.
 \begin{itemize}
@@
 \end{itemize}
-Unless otherwise noted, C11 is the model we choose as our fiducial AGB yield.
-
-We use IMF-Integrated yields calculated with \VICE~throughout this paper (see
+Unless otherwise noted, C11 is the model I choose as our fiducial AGB yield.
+
+I use IMF-Integrated yields calculated with \VICE~throughout this paper (see
 section \ref{sec:vice}, \citet{james+21, james+22}). For an element X and star
@@
 \end{equation}
-where we let $M_{\rm ejected}$ and $M_{\rm X, ejected}$ be the total ejected
+where I let $M_{\rm ejected}$ and $M_{\rm X, ejected}$ be the total ejected
 stellar mass (through winds and supernovae ejecta) and the ejected mass of X,
@@
 
-More useful for GCE are Initial Mass Function (IMF) yields, where we sum up the
+More useful for GCE are Initial Mass Function (IMF) yields, where I sum up the
 contributions of all stars which produce an element.
-We define the IMF-integrated yield of X with: 
+I define the IMF-integrated yield of X with: 
 \begin{equation}
@@
 \end{equation}
-Where $\Phi(M) = \frac{dN}{dM}/ \int_{M_{\rm min}}^{M_{\rm max}} \frac{dN}{dM}\ dM$ is the normalized IMF, $M_{\rm min}$ and $M_{\rm max}$ are the minimum and maximum mass of stars, which we take to be $0.08 M_{\sun}$ and $100 M_{\sun}$ respectively; and $\frac{dN}{dM}$ is the initial mass function, the frequency of stars born between $M$ and $M+dM$.
+Where $\Phi(M) = \frac{dN}{dM}/ \int_{M_{\rm min}}^{M_{\rm max}} \frac{dN}{dM}\ dM$ is the normalized IMF, $M_{\rm min}$ and $M_{\rm max}$ are the minimum and maximum mass of stars, which I take to be $0.08 M_{\sun}$ and $100 M_{\sun}$ respectively; and $\frac{dN}{dM}$ is the initial mass function, the frequency of stars born between $M$ and $M+dM$.
 
 Fig.
-\ref{fig:y_agb} compares the net fractional AGB carbon yield, $m_\text{C}^\text{AGB}(M, Z)$ for each AGB model we consider.
+\ref{fig:y_agb} compares the net fractional AGB carbon yield, $m_\text{C}^\text{AGB}(M, Z)$ for each AGB model I consider.
 Note that the yields may be negative when the birth abundance is higher than the carbon abundance of the material ejected back to the ISM.
@@
 
-\section{CCSNe carbon}
-
-\begin{figure}[htp]
-    \centering
-    \includegraphics{y_c_cc.pdf}
-    \caption[CCSNe carbon yields]{Top: The net fractional IMF-weighted CCSNe yield of
-        carbon, $\Ycc$ against metalicity,$\log Z/Z_\odot$, for different studies.
-        The right plot instead shows the CCSNe carbon to magnisium abundance ratio, defined in Eq. \ref{eq:c_mg_cc}. The black line represents the carbon yield of the fiducial model,
-    $\Ycc = 0.0029 + 0.001 (Z/Z_{\odot})$.
-The pink line represents the C11 AGB model.
-We plot yields from \citet{WW95} as red triangles; \citep{sukhbold+16} as orange diamonds, with larger points representing models with higher explodability; \citet{NKT13} as green stars; and \citep{LC18} as blue circles.
-\citet{LC18} is the only model including rotation.
-\citet{NKT13} and \citet{WW95} also report Population III yields, plotted with arrows at the very left.}
-    \label{fig:y_cc}
-\end{figure}
+\begin{figure*}
+    \centering
+ 	    \includegraphics[scale=1]{agb_yields.pdf}\\
+
+        \caption[AGB carbon yields]{The net fractional AGB carbon yield ($\tilde{y}$) plotted as a function of initial stellar mass $M$.
+Metallicity is colorcoded according to the colorbar.
+I plot $\tilde{y}=0$ for reference.
+Each panel represents yields from one of four AGB models: C11 \citep{cristallo+11, cristallo+15}, K10 \citep{karakas10}, V13 \citep{ventura+13,ventura+14,ventura+18}, and K16 \citep{KL16, karakas+18}.
+            %C11 reports values at metallicities $Z=$ 0.0001, 0.0003, 0.001, 0.002, 0.003, 0.006, 0.008, 0.01, 0.014, 0.02; K10 at $Z=$0.0001, 0.004, 0.008, 0.02; V13 at $Z=$0.0003, 0.001, 0.002, 0.004, 0.008, 0.014, 0.04; and K16 at $Z=$0.0028, 0.007, 0.014, 0.03.
+        }
+            \label{fig:y_agb}
+\end{figure*}
+
+\begin{figure}
+    \includegraphics[scale=1]{y_agb_t2.pdf}
+
+    \caption[AGB yields delay time distribution]{
+        Carbon production by AGB stars as a function of SSP age, normalized to the total mass $M_{\rm tot}$ produced at $t=10$ Gyr.
+Left: The four AGB yield models from liturature  at solar metallicity (C11, K10, V13, or K16).
+The delay time distribution of type Ia supernovae ($\propto t^{-1.1}$) is plotted as a dashed black line for comparison.
+Each model has a similarly shaped DTD, and most AGB enrichment occurs before 1 Gyr.
+Right: The C11 AGB model at different metallicities.
+With increasing metallicity, carbon enrichment occurs earlier, and the DTD eventually becomes non-monotonic.
+    }
+
+\end{figure}
+
+\begin{figure*}
+    \centering
+
+    \includegraphics[scale=1]{y_agb_vs_z.pdf}
+
+    \caption[AGB yield metallicity dependence]{The net fractional IMF-weighted AGB carbon yield $\Ycagb$ as a function of metallicity for each of our AGB yield models.
+    }
+
+\end{figure*}
+
+\section{Core collapse supernovae}
 
@@
 
-We summarise many of the predictions of stellar models in Fig. \ref{fig:y_cc}. 
+I summarise many of the predictions of stellar models in Fig. \ref{fig:y_cc}. 
 \begin{equation}\label{eq:c_mg_cc}
@@
         \item Wide range in predictions, exacerbated to 1 dex range when including variance in oxygen predictions
-        \item (explain) most models have a near-metallicity independent oxygen yield, so we choose the fiducial value of 0.015 despite varience in $y_O^{cc}$
-        \item The fiducial value, where we choose the carbon yield from Sukhbold+16, may be above most predictions of carbon yields but is within the range of yield ratios
+        \item (explain) most models have a near-metallicity independent oxygen yield, so I choose the fiducial value of 0.015 despite varience in $y_O^{cc}$
+        \item The fiducial value, where I choose the carbon yield from Sukhbold+16, may be above most predictions of carbon yields but is within the range of yield ratios
         \item the fiducial value would reach an equilibrium carbon yield of -0.1 without AGB stars
@@
 
+\begin{figure}[htp]
+    \centering
+    \includegraphics{y_c_cc.pdf}
+    \caption[CCSNe carbon yields]{
+        Carbon yields from massive stars.
+        Top: The net fractional IMF-weighted CCSNe yield of carbon (computed using \VICE's \texttt{vice.yields.ccsne.fractional} function) as a function of metallicity.
+        Bottom: The CCSNe carbon to magnisium abundance ratio, defined in Equasion \ref{eq:c_mg_cc}. The black line represents the carbon yield of the fiducial model,
+    $\Ycc = 0.0028 + 0.001 (Z/Z_{\odot})$. 
+    \citet[red triangles]{WW95}, \citet[orange squares and diamonds]{sukhbold+16}, 
+    \citet[green stars]{NKT13}, and \citet[blue circles]{LC18}.
+\citet{sukhbold+16} report yields for different black hole landscales, while \citet{LC18} provide yields at different roational velocities.
+The pink line represents the C11 AGB model.
+}
+    \label{fig:y_cc}
+\end{figure}
+
 \chapter{The Equilibrium Approximation}\label{sec:equilibrium}
@@
 The new elements synthesized in stars balance against elements lost to galactic winds and locked in stellar reminants.
-While our galaxy is likely not in perfect equilibrium or described by a single, homogenous chemical region, we can still use an equilibrium approximation to understand total yields.
-
-\cite{james_dwarf}, \cite{james+22}
-
-Following \citet{WAF17}, we assume a simple one-zone chemical evolution model.
-A one zone model is essentially zero-dimensional---the gas and stars are considered to be homogenously mixed, so we can represent all quantaties as scalars.
-
-We define $M_{X}$ to be the mass of element X in the gas phase, $\dot{M}_\star$ to be the star fomation rate (in M$_\odot$ yr$^{-1}$).
-
-If we assume that the median track is an equilibrium phenomenon, we can calculate the total carbon to oxygen yield ratio.
-Additionally, assuming an AGB yield set enables us to predict the CCSNe carbon yield.
-We begin with the model, which underlies the multizone simulations, that the change in mass of an element is a sum of production, outflows, recycling, and mass left in reminants. We write this as
-\begin{equation}
-M_\text{C} = y_\text{C} \dot{M}_\star - (1 + \eta - r) Z_\text{C} \dot{M}_\star
-\end{equation}
-
-In the case that carbon
-\begin{equation}
-Z_c^{eq}(R) = \frac{y_c^{cc} + \langle y_c^{agb} \rangle }{1 + \eta(R) - r - \tau_\star / \tau_{sfh}}
-\end{equation}Where
-\begin{equation}
-\langle y_c^{agb} \rangle = \frac{\int_0^T y_c^{agb}(M, Z) \dot{M}_\star(T - t) \frac{dN}{dM} \frac{dM}{dt} dt  }{ \dot{M}_\star \int_0^T \frac{dN}{dM} \frac{dM}{dt} dt}
-\end{equation}
-
-Likewise for oxygen:
-\begin{equation}
-Z_O^{eq}(R) = \frac{y_O^{cc}}{1 + \eta(R) - r - \tau_\star / \tau_{sfh}}
-\end{equation}
-
-However, for the yield ratio, the denominator cancles with that of oxygen, so the ratio is fixed.
-\begin{equation}
-\frac{Z_c^{eq}}{Z_o^{eq}} = \frac{y_c^{cc} + \langle y_c^{agb} \rangle }{y_o^{cc}}
-\end{equation}
-
-For this analysis, we let $y_c^{agb}$ represent the default AGB yields from a given yield set, but add a process factor $\alpha_{agb}$ which multaplicatively increases the AGB fraction.
-See Table \ref{tab:alpha_agb}.
-
-\begin{equation}
-    \Ycagb \rightarrow \alpha_{agb}  \Ycagb
-\end{equation}
-
-With these definitions, we can calculate the core collapse yields of carbon as a function of metallicity:
-\begin{equation}
-    y_\text{C}^\text{CC} =  y_\text{O}^\text{CC} \frac{Z_\text{C,eq}}{Z_\text{O,eq}} - \alpha_{agb} \langle y_c^{agb} \rangle
+While our galaxy is likely not in perfect equilibrium or described by a single, homogenous chemical region, I can still use an equilibrium approximation to understand total yields \citep[e.g.][]{james_dwarf,james+22,WAF17}.
+
+Following the formalism of \citet{WAF17}, I assume a simple one-zone chemical evolution model.
+The gas and stars are considered to be homogenously and instantaneusly mixed, so I can represent all quantaties as scalars.
+I define $M_{X}$ to be the mass of element X in the gas phase, $\dot{M}_\star$ to be the star fomation rate (in M$_\odot$ yr$^{-1}$).
+$\eta$ is the mass loading factor, $\eta=\dot{M}_{\rm outflow}/\dot{M}_\star$, representing the strength of outflows.
+$r$ is the recycling fraction, i.e.
+the net fraction of new star formation which will be returned to the ISM.
+
+Given the total IMF-weighted yield of magnesium, $y_{\rm Mg}$, I can write the change in the ISM mass of magnesium, $\dot{M}_{\rm Mg}$ as the sum of newly produced elements, elements lost inside stellar remanents, and elements lost to galactic outflows.
+\begin{equation}
+    \frac{d{M}_{\rm Mg}}{dt} = \dot{M}_{\rm Mg,~new} - \dot{M}_{\rm Mg~reminants} - \dot{M}_{\rm Mg,~outflows}
+\end{equation}
+The newly produced mass can be written in terms of the yield, $\dot{M}_{X,\rm~new}=y_X\dot{M}_\star$.
+In terms of the return mass fraction of stars $r$, the mass lost to reminants is $Z_X (1-r)\dot{M}_\star$.
+And, the outflows deplete a mass $Z_X \eta\dot{M}_\star$.
+Substituting,
+\begin{equation}
+    \frac{d{M}_{X}}{dt} = y_{X} \dot{M}_\star - (1 + \eta - r) Z_{X} \dot{M}_\star
+\end{equation}
+\citep{WAF17}.
+Assuming an exponentially declining star formation history, $\dot{M}_\star \propto e^{-t/\tau_{\rm sfh}}$, this equation can be solved analytically. 
+To find equilibrium, set $\dot{M}_X=0$, and now
+\begin{equation}\label{eq:z_eq}
+    Z_{\rm Mg}^{\rm eq}(R) = \frac{y_{\rm Mg}}{1 + \eta(R) - r - \tau_\star / \tau_{sfh}}
+\end{equation}
+For constant star formation, $\tau_\star/\tau_{\rm sfh} \rightarrow 0$
+
+While Equation \ref{eq:z_eq} can be applied to CCSNe carbon, the delayed time contribution of AGB carbon can complicate the result.
+Instead, using an effective or DTD-integrated yield, $\langle \Ycagb \rangle$
+\begin{equation}
+    \langle \Ycagb\rangle = \frac{\int_0^T \tilde{y}_{\rm C}^{\rm agb}(M, Z) \dot{M}_\star(T - t) \frac{dN}{dM} \frac{dM}{dt} dt  }{ \dot{M}_\star \int_0^T \frac{dN}{dM} \frac{dM}{dt} dt}
+\end{equation}
+So, for carbon, Equation \ref{eq:z_eq} becomes
+\begin{equation}
+    Z_{\rm C}^{\rm eq}(R) = \frac{\Ycc + \langle\Ycagb\rangle}{1 + \eta(R) - r - \tau_\star / \tau_{sfh}}
+\end{equation}
+Taking the ratio of $Z_{\rm C}$ and $Z_{\rm Mg}$, 
+\begin{equation}\label{eq:z_co}
+    \frac{Z_{\rm C}^{\rm eq}}{Z_{\rm Mg}^{\rm eq}} = \frac{\Ycc + \langle \Ycagb \rangle }{\Yoc}
+\end{equation}
+
+With these definitions, I can calculate the core collapse yields of carbon as a function of metallicity:
+\begin{equation}
+    y_\text{C}^\text{CC} =  y_\text{Mg}^\text{CC} \frac{Z_\text{C,~eq}}{Z_\text{Mg,~eq}} - \langle y_c^{agb} \rangle
 \end{equation}
@@
 Rewriting in terms of the observed abundance ratio and dividing by
-$y_\text{O}^\text{CC}$. So, given the outflows or CCSNe oxygen yields, the
-carbon AGB yield, and the \caah mean abundance track, we can estimate the CCSNe carbon yield. Written as a relative yield:
-\begin{equation}
-    \frac{y_\text{C}^\text{CC}}{y_\text{O}^\text{CC}} = \frac{Z_{C, \sun}}{Z_{O, \sun}} 10^{[C/O]} - \frac{\alpha_{agb} \langle y_c^{agb} \rangle}{ y_\text{O}^\text{CC}}
-\end{equation}
-
-This equation corroberates what we have explored earlier in the paper, and provides our analytic estimates of the CCSNe carbon yields.
-Since the AGB term is subtracted, a negative AGB Z-dependence will correspond to a positive CC Z-dependence.
-And as we reduce outflows, the AGB factor increases, steepening the required slope of the carbon yields.
-So, while the AGB yields may agree with eachother, the uncertainties in the oxygen CC yields and outflows leads to a substantial uncertainty in the AGB fraction.
+$y_\text{Mg}^\text{CC}$. So, given the outflows or CCSNe oxygen yields, the
+carbon AGB yield, and the \caah mean abundance track, I can estimate the CCSNe carbon yield. Written as a relative yield:
+\begin{equation}
+    \frac{\Ycc}{\Yoc} = \frac{Z_{\text{C},~\sun}}{Z_{\text{Mg},~\sun}} 10^{[C/Mg]} - \frac{\langle \Ycagb \rangle}{\Yoc}
+\end{equation}
+
+Fitting this relationship to data (figure \ref{fig:analytic}).
 
@@
     \includegraphics[]{analytic.pdf}
-    \caption[Reverse fit yields]{Inferred $\Ycc$ against [Mg/H], assuming equilibrium and 3$\times$C11 AGB yields.
-Blue points are meadians of each metallicity bin with errorbars as the median standard deviation.
-The orange curve is our best fit model.}
-\end{figure}
-
-% y_c^cc = (0.0148 +- 0.00016) Z^{0.154 +- 0.0053}
-\begin{equation}
-    \Ycc = y_{\rm C,~0}^{\rm CC} + \zeta \left(\frac{Z}{Z_\odot}\right)
-\end{equation}
-where we estimate $y_{\rm C,~0}^{\rm CC} = 0.0029\pm 0.0005$ and $\zeta = 0.001\pm0.0004$.
-
-With uncertainties
-
-\section{Model Stellar Yields}
-We define a parameterization of a CC~yield
-  Because of the large uncertainties in CCSNe carbon yields, we choose to explore an analytic expression of the yield enabling us to easily explore how variations of CCSNe carbon yields affect abundance tracks.
-We find that a powerlaw yield with a metallicity-dependent constant minimum is able to match the observations well while remaining a simple parameterization (see below).
-Our expression is:
-  \begin{equation}\label{eq:y_yields}
-   Y_\text{C}^\text{CC}(Z) =  \alpha\ Z^\beta Y_\text{O}^\text{CC} + Y_\text{C, 0}^\text{CC}
-    \end{equation}
-   	Where we estimate $\alpha = 0.02$ and $\beta = 0.25$ (See Section \ref{sec:equilibrium} ).
-Our second model uses $\alpha = 0.44$ and $\beta = 0.63$ with K16 yields and reduced $\eta \rightarrow 1/2 \eta$
-
-    As an overall scaling of yields does not significantly affect our models, we choose to fix the total equilibrium value of the total carbon yield at solar at $Y_{\text{C},\ \sun} = 0.005$, and then scale the yields relative to this value.
-
-\section{Uncertainties}
-
-We only perform this analysis on the C11yields because the range of metallicities of the data (about [M/H] = -0.4, 0.4) only represents about 2 AGB models, relying heavily on our choice of extrapolation.
-C11 have a finer model grid, allowing us to have 5 theoretical predicted points within this metallicity range, allowing us to be more certain of our conclusion.
-
-We do note that this analysis fails to take into account selection effects and biases in APOGEE, and a more robust determination of the carbon yield.
-
-This formulation is degenerate in $\varpi$ until we estimate a better AGB fraction.
-As the seperation between the low and high alpha sequences can be used to estimate the delayed time contribution to carbon, using the model to estimate this value relies heavaly on the details of the SFH in addition to the
-We do give an estimate of the CCSNe yields, however this is dependent on our choice of $\eta$.
-Other choices of $\eta$ vary the value significantly in both magnitude and slope (as AGB contributions increase, we need less CCSNe carbon, however the CCSNe carbon must have a higher metallicity dependence to replicate the V21 data).
-
-\chapter{The Multizone Model}\label{sec:vice}
-
-Unfortunantly, a simple and tidy one-zone model is a poor approximation for our galaxy.
-The galaxy evolves ``inside out''---where star formation is higher towards the center and in the early universe \citep{bird+13}.
-Additionally, stars can migrate several kpc over their lifetimes, mixing together different chemical environments across the galaxy \citep{bird+12,sellwood+binney02}.
-For the rest of this paper, we focus on multizone models, which divide the galaxy into seperate zones and account for stellar migration.
-Our models are created with the Versitile Integrator for Chemical Evolution (\VICE\footnote{\VICE~is available at \url{https://github.com/giganano/VICE}}).
-\VICE~is published and extensively described in \citet{james+21}.
-\citet{james+22} include an additional summary.
-We briefly describe the importaint characteristics of \VICE~here.
-
-As a multi-zone model, the galaxy is divided into 200 rings of 0.1kpc, each with separate gas supplies with outflow and inflow rates.
-Star formation truncates after 15.5kpc.
-We initially assume an ``inside-out'' Star Formation History (SFH), where the star formation rate (SFR) $\Sigma_\star$ is given by
-\begin{equation}
-    \dot{\Sigma}_\star \propto \left(1-e^{-t/\tau_{\rm rise}}\right) e^{-t/\tau_{\rm sfh}}.
-\end{equation}
-The SFR reaches a maximum around $\tau_\text{rise}=2$ Gyr, and $\tau{\rm sfh}$ describes the decay timescale of star formation as a function of radius $R$.
-\VICE~derives $\tau_{\rm sfh}(R)$ from data of MaNGA galaxies in \cite{sanches20}.
-
-We also explore a "lateburst" model which is parameterized with a normal distribution multiplying our fiducial "inside-out" SFH as
-\begin{equation}\label{eq:lateburst}
-    \dot{\Sigma}_{\rm lateburst} \propto \dot{\Sigma}_{\rm insideout} \left(1 + A e^{-(t-\tau_{\rm burst})^2/2\sigma^2_{\rm burst}} \right)
-\end{equation}
-
-$A=1.5$ represents the amplitude of the birth, $\tau_\text{burst}=10.8$Gyr is the time where the burst is strongest, and $\sigma_\text{burst}=1$Gyr is the width of the burst.
-We do explore the effects of variations of this parameterization in section ****.
-
-The gas inflow is calculated based on an extension of a Kennicutt-Schmidt law (e.g. \cite{kennicutt98}), motivated by 
-\begin{equation}
-\dot{\Sigma}_{\star} \propto \\
-\begin{cases}
-    {\Sigma}_{\rm gas} & 2\times 10^7 \leq \Sigma_{\rm gas} \\ 
-    {(\Sigma}_{\rm gas})^{3.6} & 5\times 10^6 \leq \Sigma_{\rm gas} < 2\times10^7 \\ 
-    {(\Sigma}_{\rm gas})^{1.7} & \Sigma_{\rm gas} < 5\times10^6 \\ 
-\end{cases}
-\end{equation}
-
-Help? allowing $\tau_\star = \Sigma_{\rm gas}/\dot{\Sigma}_{\star}$, the depletion timescale, to vary as a function of radius and time??
-
-VICE normalizes the total mass of star formation against observations from \cite{LM15}, and uses a double exponential disk profile for the distribution of star formation.
-We use a Kroupa IMF \cite{kroupa01}.
-
-\VICE\ accounts for radial migration by using the results of the \texttt{h277} hydrodynamical simulation.
-Each VICE SSP is matched to a random nearby star particle \textit{analogue} in \texttt{H277}.
-VICE approximates the migration of this particle by using a $\sqrt{\text{time}}$-diffusion approximation where the change in galactic radius of a star, $\Delta R$, is $\Delta R \propto \sqrt{\text{t}}$.
-VICE does not account for radial gas flows. 
-Using the results of a hydrodynamical simulation without modification limits the free parameters in \VICE; however we do not explore different dynamic histories.
-It is still unknown what role dynamic structure and history plays in chemical evolution.
-
-As the strength of outflows controls the resulting $\alpha$ abundances, \VICE~creates a metallicity gradienty by defining
-\begin{equation}
-\eta(R) = \frac{y_{\alpha}^{\rm CC}}{Z_{\alpha, \odot}} 10^{(-0.08\text{ kpc}^{-1})(R-4\text{ kpc})+0.3} + r - 1.
-\end{equation}
-We do explore uniformly scaling yields and outflows in Section REF.
-While we can constrain relative yields, the absolute scaling of yields and outflows is unknown and chemical evolution models are insensitive to this overal scalling (e.g.
-\cite{james_dwarf}).
-
-\chapter{Multizone model results}
-\section{Data Selection}
-
-We use data from APOGEE DR17 \citep{apogee17} processed with APOSCAP.
-Since subgiant stars have yet to experience FDU, their atmospheric carbon and nitrogen abundances are still reflective of their birth abundances and do not need mixing corrections.
-
-To select for subgiants, we use the following cut in $\log g$ and $T_{\rm eff}$
-which selects stars at the base of the red giant turnoff (FIGURE and
-\cite{jack_subgiant}). We describe our selection criteria along with a 
-comparison to \citet{fiorenzo+21} in Appendix \ref{sec:jack}.
-
-Because the star formation history is left in a simple inside-out form, this multizone model does not reproduce the high-$\alpha$ sequence, therefore we make the following cut to the V21 data to remove the high alpha sequence.
-
-\begin{equation}\label{eq:high_alpha}
-\begin{cases}
-\text{[Mg/Fe]} >0.12-0.13\text{[Fe/H]}, & \text{[Fe/H]}<0\\
-\text{[Mg/Fe]} >0.12, & \text{[Fe/H]}>0\\
-\end{cases}
-\end{equation}
-
-\section{The Evolution of carbon across the galaxy and through time}
-
-\begin{figure}
-\centering
-\includegraphics{evo_tracks.pdf}
-\includegraphics{evo_slices.pdf}
-\caption[Carbon chemical evolution tracks]{Top: the time evolution of the gas phase of our
-    fiducial model, plotted as tracks through \caah~and \caafe~where each colored line corresponds to the evolution at that galactic radius. 
-    Bottom: snapshots of the gas-phase \caah~and \caafe~trend, each line a different time.
-}
-\label{fig:c_evo}
-\end{figure}
-
-Here, we present our fiducial model which we will later show aggrees well with APOGEE. We will later investigate the effects of alterations to this model.
-
-In this model, we use the following yields:
-
-The GCE of carbon is complicated by metallicity dependencies and delayed contributions.
-
-We note the following features of our model:
-
-\begin{enumerate}
-    \item Carbon comes predominantly ($\sim80\%$) from CCSNe but the rest is from AGB stars
-    \item The CCSNe carbon production is more efficient at higher metallicities
-    \item AGB stars produce less carbon at higher metallicities.
-\end{enumerate}
-
-The combination of these features leads to an evolution that proceeds as follows
-\begin{enumerate}
-    \item Initially, CCSNe dominate production before AGB stars can contribute their enrichment, but because CCSNe is highly metalliticy dependent, the C/$\alpha$ ratio increases with time.
-    \item AGB stars begin contributing their carbon, increasing the $C/\alpha$ ratio more steeply as the gas begins to reach its equilibrium metallicity
-    \item When $Z$ reaches equilibrium, the $C/\alpha$ ratio stops increasing or may even decline, as AGB stars formed at higher metallicities reduce the net carbon yields.
-\end{enumerate}
-
-We plot time evolution tracks in Fig.
-\ref{fig:c_evo} for \caah and \caafe for our fiducial model.
-Comparing [C/$\alpha$] against [Fe/H] enables us to see late time evolution of carbon more clearly.
-Because [Fe/H] takes longer to reach equilibrium as half of iron production comes from type-Ia supernovae, the late time evolution is not clustered as tightly horizontally as for [$\alpha$/H].
-This is even more evident in the lower part of Fig.
-\ref{fig:c_evo}.
-While the \caah trend reaches almost equilibrium at 5Gyr, the \caafe trend continues to evolve even until the present day, exposing the effect of the delayed contribution from AGB stars on the evolutionary history.
-
-\begin{itemize}
-    \item Describe definition of $f$ /etc.
-    \item How we match the figures, DTD vs $\zeta$
-
-\end{itemize}
-
-\begin{figure}
-\centering
-\includegraphics{oob_agb.pdf}
-\caption[AGB GCE Models]{Left: the \caah~median present-day stellar tracks for four different AGB models (C11, K10, V13, K16) with a metallicity-independent $\Ycc$.
-Right: same except [C/Mg] against [Mg/Fe] for the bin $-0.15<\text{[Mg/H]}<-0.05$.
-The median bin [C/Mg] values from \citet{jack_subgiant} are plotted as black points with standard median deviations plotted as grey dashes.
- While each AGB yield model may differ in detail, there is minimal effect on the overall [C/Mg] trends.
-}
-\label{fig:agb_sims}
-\end{figure}
-
-\section{Alternate Models}
-
-What happens as we change our choice of AGB stellar yields? We consider four models
-using the published yields in \cristallo, \karakas, \kl, and \ventura~in Fig.
-\ref{fig:agb_sims}.
-
-As we chose to leave $Y_{\rm C}^{\rm CC}$ in a functional form, we chose to
-leave the total IMF-averaged carbon yield to be constant. The magnitude of
-$Y_{\rm C}^{\rm CC}$
-\begin{equation}
-    Y_{\rm C}^{0}  = 0.005  =  Y_{\rm C}^{\rm cc} + Y_{\rm C}^{\rm agb}
-\Big \rvert_{Z=Z_\odot}
-\end{equation}
-where we are choosing to evaluate the total IMF CC and AGB yields at solar
-metallicity. We show our calculations of $Y_{\rm C}^{\rm agb}(Z=Z_{\sun })$  in
-Table \ref{tab:alpha_agb}.
-
-This choice of total carbon yield with our fixed choice of oxygen gives an
-equilibrium value of $Z_{\rm C}/Z_{\rm O} = Y_{\rm C}/Y_{\rm O} = 0.333$ which
+    \caption[Reverse fit yields]{Inferred massive star carbon yields as a function of metallicity.
+I assume equilibrium and $3\times {\rm C11}$ AGB yields (orange curve, see discussion in Section \ref{sec:equilibrium}).
+The binned medians and median absolute devation (divided by $\sqrt{N}$) are blue points.
+    }
+\end{figure}
+
+\section{Yield Models}
+
+Outflow yield degeneracy.
+One challenge of chemical evolution models is that outflows and yields are degenerate.
+To avoid this degeneracy, I instead constrain relative yields.
+As Equation \ref{eq:z_co} shows, the yield ratios are independent of $\eta$, and independent of the SFH (ignoring the DTD term).
+As such, I set the total carbon yields to 
+\begin{equation}
+    \Yct = \Ycc + \Ycagb = 0.005 \frac{\Yoc}{0.00185}
+\end{equation}
+
 is reasonably consistant with the value in \citet{asplund+09} of $Z_{\rm
@@
 
-As the highest AGB yield at solar is from our \karakas~model at $Y_{\rm C}^{\rm
-agb} = 0.000585$ is only 11.7 percent of our required total carbon production,
-each of these models is dominated by CC production of carbon. As a result,
-while the metallicity dependence of the \caah may vary, the
-\caafe diagnostic shows how this small AGB fraction makes the details of
-the AGB model and delay-time-distribution unchange the galaxy production of
-carbon.
-
-Appendix \ref{sec:alt_agb} describes the effects of increasing the AGB model on
-resulting abundance trends. However, we use the \cristallo AGB yields for the
-rest of the main discussion.
-
-Our next exploration is to adjust the relative fraction of AGB star yields. To do this, we hold the total carbon yield at solar metallicity fixed, so for a desired AGB fraction (assuming equilibrium),
+Additionally, each AGB yield set (C11, K10, V13, K16), fails to produce enough AGB carbon for our fiducial model (see REF).
+So, I introduce a process factor, $\alpha_{\rm AGB}$, which represents the multiplicative increase in $\Ycagb$ from the published yields.
+\begin{equation}
+    \Ycagb \rightarrow \alpha_{\rm agb}  \Ycagb.
+\end{equation}
+
+\begin{equation}
+    \alpha_{\rm agb} = f_{\rm agb} \frac{\Yct}{\Ycagb}
+\end{equation}
+\begin{equation}
+    \alpha_{\rm CC} = (1 - f_{\rm agb}) \frac{\Yct}{\Ycc}
+\end{equation}
+
+I have investigated uniform increases in carbon yields and have found these changes make little effect on the resulting trends.
+Fixing the total carbon yield at solar reduces the number of free parameters and keeps the model reasonably consistant with observations, and enables us to more consistantly explore differen AGB models.
 
@@
 		AGB Model & $y_{\rm C, 0}^{\rm AGB}$ & $\alpha_{\rm AGB, 20}$\\
+        \hline
         \hline
@@
 
-\begin{equation}
-    \alpha_{\rm agb} = f_{\rm agb} \frac{\Yct}{\Ycagb}
-\end{equation}
-\begin{equation}
-    \alpha_{\rm CC} = (1 - f_{\rm agb}) \frac{\Yct}{\Ycc}
-\end{equation}
+\section{Uncertainties}
+
+I only perform this analysis on the C11 yields because the range of metallicities of the data (about [M/H] = -0.4, 0.4) only represents about 2 AGB models, relying heavily on our choice of extrapolation.
+C11 have a finer model grid, allowing us to have 5 theoretical predicted points within this metallicity range, allowing us to be more certain of our conclusion.
+
+I do note that this analysis fails to take into account selection effects and biases in APOGEE, and a more robust determination of the carbon yield.
+
+This formulation is degenerate in $\varpi$ until I estimate a better AGB fraction.
+As the seperation between the low and high alpha sequences can be used to estimate the delayed time contribution to carbon, using the model to estimate this value relies heavaly on the details of the SFH in addition to the
+I do give an estimate of the CCSNe yields, however this is dependent on our choice of $\eta$.
+Other choices of $\eta$ vary the value significantly in both magnitude and slope (as AGB contributions increase, I need less CCSNe carbon, however the CCSNe carbon must have a higher metallicity dependence to replicate the V21 data).
+
+\chapter{The Multizone Model}\label{sec:vice}
+
+Classical, ``one-zone'' models of chemical evolution assume instantanius mixing of metals in the star forming ISM \citep[e.g.][]{matteucci21}.
+This simple framework is a poor approximation for the Milky Way.
+The Galaxy evolves ``inside out''---where star formation is higher towards the center and in the early universe \citep{bird+13}.
+Additionally, stars can migrate several kpc over their lifetimes, mixing together different chemical environments across the galaxy \citep{bird+12,sellwood+binney02}.
+For the rest of this paper, I focus on multizone models, which discretize the Galaxy into concentric annuli and allow stare to move between rings.
+Specifically, I make use of the \citet{james+21} (hereaafter \JJ) model for the Milky Way, which runs using the publicaly available Versatile Integrator for Chemical Evolution (\VICE\footnote{\VICE~is available at \url{https://github.com/giganano/VICE}}).
+This model is described extensively in \JJ~and consicely summarized  in \citet{james+22}.
+Here, I provide a prief overiview of the relevant model components.
+
+In the model, the Galaxy is divided into 200 rings, each 100 pc wide.
+Each ring has a seperate stellar population and gas supply.
+Star formation ends beyond a radius $R=15.5$ kpc.
+I initially assume an ``inside-out'' Star Formation History (SFH), where the star formation surface density $\Sigma_\star$ is given by
+\begin{equation}
+    \dot{\Sigma}_\star \propto \left(1-e^{-t/\tau_{\rm rise}}\right) e^{-t/\tau_{\rm sfh}}.
+\end{equation}
+$\tau_\text{rise}=2$ Gyr describes when the star formation rate reaches a maximum, and $\tau_{\rm sfh}$ describes the decay timescale of star formation as a function of radius $R$.
+\JJ~derives $\tau_{\rm sfh}(R)$ through analysis of four integral field spectroscopy surveys in \cite{sanches20}.
+The gas inflow is calculated to maintain our chosen SFR for each radius and time. The gas-SFR law is based on an extension of a Kennicutt-Schmidt law \citep{kennicutt98}, motivated by 
+\begin{equation}
+\dot{\Sigma}_{\star} \propto \\
+\begin{cases}
+    {\Sigma}_{\rm gas} & 2\times 10^7 \leq \Sigma_{\rm gas} \\ 
+    {(\Sigma}_{\rm gas})^{3.6} & 5\times 10^6 \leq \Sigma_{\rm gas} < 2\times10^7 \\ 
+    {(\Sigma}_{\rm gas})^{1.7} & \Sigma_{\rm gas} < 5\times10^6 \\ 
+\end{cases}
+\end{equation}
+The star formation history is normalized such that the total stellar mass reaches $M_\star=5.17\times10^{10} {\rm M}_\odot$ \citep{LM15} and at each $R$ to match the stellar surface density gradient \citep{BHG16}.
+$\tau_\star$ also varies with time due to the redshift dependence of $\tau_\star$ in molecular gas observed by \citet{tacconi18}.
+I assume a Kroupa IMF \cite{kroupa01}.
+
+\JJ\ accounts for radial migration by using the results of the \texttt{h277} hydrodynamical simulation \citep{christensen12, zolotov12, loebman12, BZ14}, with simulation parameters described in \citet{bird+21}.
+Each VICE single stellar population (SSP) is matched to an \textit{analogue} in \texttt{H277}, chosen to form at a similar time and radius $R$.
+By taking the change in radius $\Delta R$ of the analogues, the SSP move to their final radii with a $\sqrt{\text{time}}$ dependence.
+This relationship between displacement and time arises when migration proceeds as a consequence of the diffusion of angular momentum \citep{frankel18, frankel20}.
+I do not account for radial gas flows.
+Using the results of a hydrodynamical simulation without modification limits the free parameters in the model; however, I are limitied to one dynamical history.
+The impact of the details of a galaxy's dynamical history on its chemical evolution is unknown, and I do not explore this question here.
+
+As the strength of outflows controls the resulting $\alpha$ abundances, \JJ~create a metallicity gradienty by defining
+\begin{equation}
+\eta(R) = \frac{y_{\alpha}^{\rm CC}}{Z_{\alpha, \odot}} 10^{(-0.08\text{ kpc}^{-1})(R-4\text{ kpc})+0.3} + r - 1.
+\end{equation}
+This choice of $\eta(R)$ results in a [$\alpha$/H] gradient consistant with Milky Way observations \citep{james+21}.
+
+I could chose to vary the value of $\alpha$; however, the overall scaling of
+yields is unknown so our constraint is really that $Y_{\rm C}/Y_{\rm O} =
+0.dfsjkhld$, based on binning from our data. As discussed in the previous
+section, I chose to leave the total value of the IMF integrated yield fixed,
+and then assert the AGB fraction (next section) and scale the AGB yields from
+literature appropriety. As such,
+
+I explore uniformly scaling yields and outflows in Section REF.
+While I can constrain relative yields, the absolute scaling of yields and outflows is unknown and chemical evolution models are insensitive to this overal scalling \citep[e.g.][]{james_dwarf}.
+
+\chapter{Multizone model results}
+\section{Data Selection}
+
+I use data from APOGEE DR17 \citep{apogee17} processed with APOSCAP.
+Since subgiant stars have yet to experience FDU, their atmospheric carbon and nitrogen abundances are still reflective of their birth abundances and do not need mixing corrections.
+
+To select for subgiants, I use the following cut in $\log g$ and $T_{\rm eff}$
+which selects stars at the base of the red giant turnoff (FIGURE and
+\cite{jack_subgiant}). I describe our selection criteria along with a 
+comparison to \citet{fiorenzo+21} in Appendix \ref{sec:jack}.
+
+The inside-out star formation model fails
+Because the star formation history is left in a simple inside-out form, this multizone model does not reproduce the high-$\alpha$ sequence, therefore I make the following cut to the V21 data to remove the high alpha sequence.
+
+\begin{equation}\label{eq:high_alpha}
+\begin{cases}
+\text{[Mg/Fe]} >0.12-0.13\text{[Fe/H]}, & \text{[Fe/H]}<0\\
+\text{[Mg/Fe]} >0.12, & \text{[Fe/H]}>0\\
+\end{cases}
+\end{equation}
+
+\section{The Evolution of carbon across the galaxy and through time}
+
+Here, I present the time evolution of our fiducial model.
+In the next sections, I will discuss the choice of parameters and agreement with observations.
+Our fiducial model uses the C11 AGB yield set (see section \ref{sec:agb}).
+I amplify the C11 yields by a factor of 2.9, so that $\Ycagb = 0.2y_{\rm C}$, agb
+
+In this model, I use the following yields:
+
+The GCE of carbon is complicated by metallicity dependencies and delayed contributions.
+
+Note the following features of our model:
+
+\begin{enumerate}
+    \item Carbon comes predominantly ($\sim80\%$) from CCSNe but the rest is from AGB stars
+    \item The CCSNe carbon production is more efficient at higher metallicities
+    \item AGB stars produce less carbon at higher metallicities.
+\end{enumerate}
+
+The combination of these features leads to an evolution that proceeds as follows
+\begin{enumerate}
+    \item Initially, CCSNe dominate production before AGB stars can contribute their enrichment, but because CCSNe is highly metalliticy dependent, the C/$\alpha$ ratio increases with time.
+    \item AGB stars begin contributing their carbon, increasing the $C/\alpha$ ratio more steeply as the gas begins to reach its equilibrium metallicity
+    \item When $Z$ reaches equilibrium, the $C/\alpha$ ratio stops increasing or may even decline, as AGB stars formed at higher metallicities reduce the net carbon yields.
+\end{enumerate}
+
+I plot time evolution tracks in Fig.
+\ref{fig:c_evo} for \caah and \caafe for our fiducial model.
+Comparing [C/$\alpha$] against [Fe/H] enables us to see late time evolution of carbon more clearly.
+Because [Fe/H] takes longer to reach equilibrium as half of iron production comes from type-Ia supernovae, the late time evolution is not clustered as tightly horizontally as for [$\alpha$/H].
+This is even more evident in the lower part of Fig.
+\ref{fig:c_evo}.
+While the \caah trend reaches almost equilibrium at 5Gyr, the \caafe trend continues to evolve even until the present day, exposing the effect of the delayed contribution from AGB stars on the evolutionary history.
+
+\begin{itemize}
+    \item Describe definition of $f$ /etc.
+    \item How I match the figures, DTD vs $\zeta$
+
+\end{itemize}
+
+\begin{figure}
+\centering
+\includegraphics{evo_tracks.pdf}
+\includegraphics{evo_slices.pdf}
+\caption[Carbon chemical evolution tracks]{
+    Time evolution of gas phase carbon abundances in our fiducial model.
+
+    Top: Evolutionary tracks parameterized by time at fixed Galactocentric radius in the \caah and \caafe planes.
+
+    Bottom: snapshots of the gas-phase \caah~and \caafe~trend, parameterized by radius at fixed time.
+}
+\label{fig:c_evo}
+\end{figure}
+
+\section{Alternate Models}
+
+What happens as I change our choice of AGB stellar yields? I consider four models
+using the published yields in \cristallo, \karakas, \kl, and \ventura~in Fig.
+\ref{fig:agb_sims}.
+
+As the highest AGB yield at solar is from our \karakas~model at $Y_{\rm C}^{\rm
+agb} = 0.000585$ is only 11.7 percent of our required total carbon production,
+each of these models is dominated by CC production of carbon. As a result,
+while the metallicity dependence of the \caah may vary, the
+\caafe diagnostic shows how this small AGB fraction makes the details of
+the AGB model and delay-time-distribution unchange the galaxy production of
+carbon.
+
+Appendix \ref{sec:alt_agb} describes the effects of increasing the AGB model on
+resulting abundance trends. However, I use the \cristallo AGB yields for the
+rest of the main discussion.
+
+Our next exploration is to adjust the relative fraction of AGB star yields. To do this, I hold the total carbon yield at solar metallicity fixed, so for a desired AGB fraction (assuming equilibrium),
+
+\begin{figure}
+\centering
+\includegraphics{oob_agb.pdf}
+\caption[AGB GCE Models]{
+    Stellar abundance trends in our model, assuming metallicity independent $\Ycc$.
+Colored lines quantify the median [C/Mg] in bins of [Mg/H] for our four AGB yield models from the literature (see \ref{sec:agb}).
+Black points and grey dashes represent the median and standard deviations in the \citet{jack_subgiant} sample.
+In the right panel, I show the trends only for stars where $-0.15\leq {\rm [Mg/H]}\leq -0.05$.
+}
+\label{fig:agb_sims}
+\end{figure}
 
@@
 
-\caption[Adjusted yield models]{Similar to \ref{fig:agb_sims} except the top plot shows the fiducial model with lower and higher values of $\zeta$, the C-CCSNe metallicity dependence.
-The bottom plot is the same except shows models with $f_{\rm AGB}=$0.1, 0.2, and 0.4.
+\caption[Adjusted yield models]{Similar to Figure \ref{fig:agb_sims} except the top plot shows the fiducial model with lower and higher values of $\zeta$, the C-CCSNe metallicity dependence.
+The bottom plot shows models with $f_{\rm AGB}=$0.1, 0.2, and 0.4.
 Both the $f_{\rm AGB}$ and $\zeta$ influence \caah, but only $f_{\rm AGB}$ has a significant impact on \caafe.}
@@
 The next question is how does changing the CCSNe carbon yield affect the model?
-We now consider variations of our fiducial model:
-\begin{itemize}
-    \item $f_{\rm agb} = 0.2$
-    \item AGB model: \cristallo
-    \item $Z_{\rm C}^{\rm cc} = 0.004 (Z/Z_{\sun })^{0.4}$ ($\beta = 4$)
-\end{itemize}
-
-We could chose to vary the value of $\alpha$; however, the overall scaling of
-yields is unknown so our constraint is really that $Y_{\rm C}/Y_{\rm O} =
-0.dfsjkhld$, based on binning from our data. As discussed in the previous
-section, we chose to leave the total value of the IMF integrated yield fixed,
-and then assert the AGB fraction (next section) and scale the AGB yields from
-literature appropriety. As such,
-
-As we display in Fig. \ref{fig:beta_f}, we observe that changes in $\beta$ are
+I now consider variations of our fiducial mode/
+
+As I display in Fig. \ref{fig:beta_f}, I observe that changes in $\beta$ are
 approprietly reflected in the resulting \caah~trend. As the metallicity
@@
 
-Wow! Equilibrium!! See section \ref{sec:equilibrium}
-
-Importantly, the \caafe trend is mostly unaffected by choosing a different
+Carbon as an equilibrium phenominon. See section \ref{sec:equilibrium} Importantly, the \caafe trend is mostly unaffected by choosing a different
 CCSNe yield. As all CCSNe enrichment happens at the same, rapid timescale, by
@@
 These models are indistinguishable in the \caah~plane from our adjusted CCSNe model, so future work investigating the SFH and carbon isotopic ratios in more depth may be able to provide more insight.
-In the next section, we develop the analytic tools to explore this problem in more depth.
+In the next section, I develop the analytic tools to explore this problem in more depth.
+
+\section{Star Formation History} \label{sec:sfh}
 
@@
 \includegraphics{lateburst_eta.pdf}
-\includegraphics{eta.pdf}
-
-\caption[Lateburst and reduced-outflow models]{Same as Fig. \ref{fig:agb_sims} but comparing the fiducial model to two lateburst models (top), and two reduced outflow models (bottom).}
-\end{figure}
-
-We consider a simple modification of our SFH described by our lateburst model
-(see Equation \ref{eq:lateburst})
-
-equation of lateburst
-
-However, we find that the star formation history has a negligable effect on the shape of the mean track.
-More drastic changes in SFH could explain the high alpha/low alpha seperation but we leave further exploration of SFH to future work.
-
-\section{Outflows}
-
-In GCE there are models requiring significant mass loading, but other approaches neglect outlows altogether. (Minchev, Chiappini and Martig (13, 14), Spitoni ++ 19,20,21).
-
-We can modify our model to account for this by $\eta=0$.
+
+\caption[Lateburst models]{Same as Figure \ref{fig:agb_sims} but comparing the fiducial model to alternate star formation histories (see \S \ref{sec:sfh}).}
+\label{fig:sfh_models}
+
+\end{figure}
+
+Here, I consider a "lateburst" model, created by multiplying our fiducial "inside-out" SFH with a gaussian.
+\begin{equation}\label{eq:lateburst}
+    \dot{\Sigma}_{\rm lateburst} \propto \dot{\Sigma}_{\rm insideout} \left(1 + A e^{-(t-\tau_{\rm burst})^2/2\sigma^2_{\rm burst}} \right)
+\end{equation}
+
+$A=1.5$ represents the amplitude of the birth, $\tau_\text{burst}=10.8$Gyr is the time where the burst is strongest, and $\sigma_\text{burst}=1$Gyr is the width of the burst.
+
+I also consider a 2-infall model as a slight variation of the lateburst, where the burst is instead exponential and placed at $t_1=5$ Gyr.
+This approximantly corresponsed to the Gaia-Encelidus merger, inducing higher star formation in the Milky Way \citep{bonaca20, helmi18}.
+\begin{equation}\label{eq:twoinfall}
+    \dot{\Sigma}_{\rm 2-infall} \propto \dot{\Sigma}_{\rm insideout} + 
+\begin{cases}
+    Ae^{-(t-t_1)/\tau_{\rm burst}} & t_1 < t \\
+      0 & t<t_1
+\end{cases}
+\end{equation}
+where I take the burst duration, $\tau_{\rm burst}=1$ Gyr in this case. 
+This more drastic burst is able to more successfuly populate the high-$\alpha$ sequence. I leave more detailed exploration of the effects of star formation histories to future work.
+
+I show these variations on the star formation history in figure \ref{fig:sfh_models}.
+
+\section{Outflows} \label{sec:outflows}
 
@@
 An increase in stellar yields has a near-identical effect as a decrease in outflows.
-However, reducing the outflows reduces the evolution timescale of the system.
+For example, the equilibrium abundance ratios are entirely independent of $\eta$ (see section \ref{sec:equilibrium}).
+My model is able to determine yield ratios well, but is unable to differentiate differences in the overall scaling of outflows and yields.
+
+While my model requires high yields and significant mass loading, other approaches neglect outflows altogether \citep{MCM13, MCM14, spitoni19, spitoni20, spitoni21}.
+By modifying our model such that $\eta=0$, I can create outflow-less models.
 
 The theoretical motivation for decreasing outflows is due to the uncertainty in the explodability landscape---if less massive stars explode, then both the yields and outflows will be reduced by some factor.
-So, when we explore reduced outflow models, we consider models where both the outflows and yields are reduced by approximately the same factor, to leave the equilibrium abundances of a pure CCSNe unchanged.
+So, when I explore reduced outflow models, I consider models where both the outflows and yields are reduced by approximately the same factor, to leave the equilibrium abundances of a pure CCSNe unchanged.
 
@@
 
-We have found that the \caah~relationship may provide insight into this issue.
+I find that the \caah~relationship may provide insight into this issue.
 [O/Fe] is a tracer of the relative contributions of CCSNe and delayed-time sources in chemical evolution.
@@
 
-We find that we can adjust both the outflows and scale down the yields if we change our model for $y_\text{C}^\text{CC}/y_\text{O}^\text{CC}$.
+I find that I can adjust both the outflows and scale down the yields if I change our model for $y_\text{C}^\text{CC}/y_\text{O}^\text{CC}$.
 For example, reducing outflows and CCSNe yields by a factor of two requires the modified parameters
 $\alpha = 0.033$ and $\beta = 0.625$, which results in a slightly lower value at solar but nearly a doubling of the metallicity dependence.
-
-\section{Understanding Scatter}
-
-\begin{figure*}
-    \centering
-    \includegraphics[scale=0.9]{cooh_scatter.pdf}
-    \caption[Scatter agreement]{The simulated stars of our model at present day plotted on \caah~and colored such that lighter colors represent stars born at greater galactric radii.
-Our model is able to explain the scatter and shape, relying on a combination of artificial measurment errors and radial migration.}
-\end{figure*}
-
-Beyond simply comparing median trends, we can compare the distribution 
+\begin{figure}
+
+\includegraphics{eta.pdf}
+
+\caption[Reduced-outflow models]{Same as Figure \ref{fig:agb_sims} but comparing the fiducial model to reduced outflow models (see \S \ref{sec:outflows}).}
+\end{figure}
+
+\section{Comparison to Observations}
+
+Beyond simply comparing median trends, I can compare the distribution 
 shape of our distribution to observations.
 
-\section{Comparison to Observations}
-
-\begin{figure}
-    \includegraphics{nitrogen.pdf}
-    \includegraphics{c_n.pdf}
-    \caption{Nitrogen almost works?}
-\end{figure}
-
-\begin{figure*}
-\centering
-\includegraphics[]{summary.pdf}
-\caption[Gas phase abundances]{Present-day gas phase tracks of the fiducial model in \caah~space. M101 is valid comparison to MW ...(van Dokkum et al. 2014)
-
-    \citep{cooke+17}, \citet{nissen+14}, \citet{fabbian+09}, \citet{berg+19}, \citet{esteban+02}, \citet{esteban+09}, \citet{esteban+14}, \citet{esteban+19},
-}
-\label{fig:gas_phase}
-\end{figure*}
-
 Carbon measurments in stars are difficult. There are measurments which can however be used to test.
 
-We don't predict low metallicity but we are in agreement, substantial error bars.
+I don't predict low metallicity but I are in agreement, substantial error bars.
 
@@
 
-In Fig. \ref{fig:gas_phase}, we plot our fiducial model's gas phase abundances
+In Fig. \ref{fig:gas_phase}, I plot our fiducial model's gas phase abundances
 at present day and 2Gyr compared to C/O
@@
 
-As any constraints in this regieme are poor, we choose to only qualitatively
+As any constraints in this regieme are poor, I choose to only qualitatively
 conclude that CCSNe carbon production increases at extremely low metallicity
@@
 
-Can we use our yield estimations and apply them to extragalactic sources successfully?
+Can I use our yield estimations and apply them to extragalactic sources successfully?
 
@@
 
+\begin{figure}
+    \centering
+    \includegraphics[scale=0.9]{cooh_scatter.pdf}
+    \caption[Scatter agreement]{The stars in the fiducial model in the \caah~plane perturbed by the median [Mg/H] and [C/Mg] measurment errors in the \citet{jack_subgiant} sample.
+Stars are color-coded such that lighter colors represent population sborn at greater galactocentric radii
+    }
+\end{figure}
+
+\begin{figure}
+    %\includegraphics{nitrogen.pdf}
+    \includegraphics{c_n.pdf}
+    \caption{Similar to as Figure \ref{fig:agb_sims}, except I only show the fiducial model and I plot the [C/N] abundance ratio on the y-axis.
+    }
+\end{figure}
+
+\begin{figure*}
+\centering
+\includegraphics[]{summary.pdf}
+\caption[Gas phase abundances]{Gas-phase carbon abundances. We plot our model at $t=2$Gyr and present day as thick solid lines. Points represent measurments in 
+    HII regions    \citep[pink circles;][]{skillman+20, esteban+02, esteban+09, esteban+14, esteban+19}
+    Damped Lynman-$\alpha$ (DLA) systems \citep[blue triangles;][]{cooke+17} 
+    Milky Way halo and thick disk stars \citep[green stars;][]{nissen+14, fabbian+09}. 
+    dwarf galaxies \citep[red diamonds;]{berg+19},
+    and Milky Way high-$\alpha$ stars \citet[yellow points;][]{jack_subgiant}.
+}
+\label{fig:gas_phase}
+\end{figure*}
+
 \chapter{Conclusions}
 
-\begin{itemize}
-    \item James ++23 Nitrogen,
-    \item J++ found yield ratios, APOGEE -> yield assumptions
-    \item SFH and eta don't matter too much.
-
-        \item
-        \item Variations in f and beta
-        \item Evolutionary history
-        \item Gas phase and Pop III
-        \item Implications in Stellar evolution
-        \item Continuing to work on neutron-capture e.t.c., 
-        \item MWM and value of this work
-\end{itemize}
-
-Directions-->SneIa/AGB trends as a constraint on DTD.
+In this work, I investigate the role of carbon yields on the predictions of multizone GCE models.
+\citet{james+22} performed a similar analysis, except focusing on nitrogen.
+\citet{james+22} found, to match APOGEE/\citet{fiorenzo+21}'s observations, nitrogen yields ratios relative to oxygen needed to be about triple what AGB models suggested.
+
+Here, I perform a similar analysis on carbon.
+I summarize the current theoretical nucleosynthetic predictions of carbon.
+Because CCSNe carbon yields are poorly understood, I adopt an equilibrium approximation and determine that a functional form of $\Ycc/\Yoc=1.51 + 0.54 (Z/Z_\odot)$ approximately matches trends in APOGEE subgiants.
+Variations of the metallicity dependence of this CCSNe yield affect trends in \caah but do not affect trends in \caafe when taking a slice in [Mg/H].
+As all theoretical AGB carbon yields decrease with increasing metallicity, increasing the AGB fraction causes the \caah trend to flatten.
+However, the \caafe trend is sensitive to the AGB fraction.
+I estimate that $f_{\rm AGB} = 0.2$ using the C11 yield model. This requires about 3x more AGB carbon production than most nucleosynthetic models predict.
+
+Evolutionary history
+
+Finally, I compare my model against gas phase and metal-poor stellar measurments.
+While my model was built on data near solar metallicity, by including heightened carbon production from population III stars, I can create a self consistant picture of carbon evolution.
+
 Observations of Carbon in metal poor stars, extragalactic (call out any
+
+Implications in Stellar evolution
+
+These carbon yield constraints provide a test for stellar evolution models.
+Carbon yields are sensitive to mass loss treatment, explodability, nuclear cross sections, convection, and stellar structure.
+
+Future surveys such as the Milky Way Mapper will enable further refinement of galactic trends, placing yet more stringent constrants on stellar evolution models.
+MWM and value of this work
+
 existing surveys in e.g. APOGEE/DESI?)
 Abundance ratios (e.g.C12/C13) as additional constraints
-
-The Acknowledgements section is not numbered. Here you can thank helpful
-colleagues, acknowledge funding agencies, telescopes and facilities used etc.
-Try to keep it short.
-
-Numpy, pandas, scipy, VICE, matplotlib
-\cite{numpy, matplotlib}
-
-\cite{OhioSupercomputerCenter1987}
 
@@
 \renewcommand{\thesection}{A.\arabic{section}}
-\renewcommand\thefigure{A.\arabic{figure}}    
+\renewcommand\thefigure{A\arabic{figure}}    
+\renewcommand\theequation{A\arabic{equation}}    
 \setcounter{figure}{0}
+\setcounter{equation}{0}
 
@@
 
-We use the criteria outlined in \cite{jack_subgiant} to create a sample of subgiants from APOGEE DR17 \cite{apogee17} as our primary observational constraint. 
+I use the criteria outlined in \cite{jack_subgiant} to create a sample of subgiants from APOGEE DR17 \cite{apogee17} as our primary observational constraint. 
 \cite{jack_subgiant} selects a region of stars in $\log g$-$T_\text{eff}$ space described by the following polyhedron
 \begin{equation}
-\begin{cases}
-\log g \geq 3.5 \\
-\log g \leq 0.004\ T_\text{eff} - 15.7 \\
-\log g \leq 0.00070588\ T_\text{eff} + 0.358836 \\
-\log g \leq -0.0015\ T_\text{eff} + 12.05 \\
-\log g \geq 0.0012\ T_\text{eff} - 2.8 \\
+    \begin{cases} \label{eq:subgiant_selection}
+        \log \text{g} \geq 3.5 \\
+        \log \text{g} \leq 0.004T_{\rm eff} - 15.7 \\
+        \log \text{g} \leq 0.000706T_{\rm eff} + 0.36 \\
+        \log \text{g} \leq -0.0015T_{\rm eff} + 12.05 \\
+        \log \text{g} \geq 0.0012T_{\rm eff} - 2.8 \\
     \end{cases}
@@
     \includegraphics{logg_jack.pdf}
+    \caption[Subgiant selection]{
+        A Kiel diagram of APOGEE stars.
+Following \citet{jack_subgiant}, we select subgiants in the orange polygon (see Equation \ref{eq:subgiant_selection}).
+These stars have not yet experienced first dredge-up, so their photospheric carbon and nitrogen abundances should reflect their birth mixture.
+    }
 \end{figure}
@@
 
-Additionally, we exclued stars in APOGEE marked by the following flags.
+Additionally, I exclued stars in APOGEE marked by the following flags.
 \begin{itemize}
-\item \texttt{ancillary young embedded cluster}
-\item \texttt{ancillary emission line star}
-\item \texttt{MIR-deected candidate cluster member}
-\item \texttt{selected as part of the EB program}
-\item \texttt{selected as part of the young cluster study (in-SYNC)}
-\item \texttt{W3/4/5 star forming complex}
+\item \verb|APOGEE_MIRCLUSTER_STAR|
+\item \verb|APOGEE_EMISSION_STAR|
+\item \verb|APOGEE_EMBEDDEDCLUSTER_STAR|
+\item \verb|young cluster (IN-SYNC)|
+\item \verb|APOGEE2_W345|
+\item \verb|EB planet|
 \end{itemize}
@@
 A second approach in determining birth abundances in stars is to correct the surface abundance effects of FDU, as in \cite{fiorenzo+21}.
-We do note that there is a slight difference in the yields found through \cite{fiorenzo+21} and \cite{jack_subgiant}.
+I note that there is a slight difference in the yields found through \cite{fiorenzo+21} and \cite{jack_subgiant}.
 As o
 
-We choose to use \cite{jack_subgiant}'s sample as this does not rely on additional layers of modeling, providing a more direct constraint to our model and limiting our systematic uncertainties.
+I choose to use \cite{jack_subgiant}'s sample as this does not rely on additional layers of modeling, providing a more direct constraint to our model and limiting our systematic uncertainties.
 
@@
 
-While we focus the main discussion of the paper on the C11 model, other AGB models can have notable effects on abundance trends at ***
-
-Because the predictions of the AGB yield models we consider are dwarfed by the
+While I focus the main discussion of the paper on the C11 model, other AGB models can have notable effects on abundance trends at ***
+
+Because the predictions of the AGB yield models I consider are dwarfed by the
 required CCSNe carbon production to match observations (see Fig.
-***), we briefly explore here the effects of variations in AGB models affect abundance trend predictions when these models are amplified to match observational [C/MG]-[Mg/Fe] trends.
+***), I briefly explore here the effects of variations in AGB models affect abundance trend predictions when these models are amplified to match observational [C/MG]-[Mg/Fe] trends.
 
 While most models are well represented by our AGB-fraction formalism, V13 presents a challenge as the predicted solar yield is much lower than the lower metallicity predictions, requiring the solar value to be a certain fraction forces us to amplify the yields by an unreasonable about (of order 10-30times) to reach the same $f_{\rm AGB}$ as other models.
-Thus, we instead calculate $f_{\rm AGB}$ at a metallicity of ...
+Thus, I instead calculate $f_{\rm AGB}$ at a metallicity of ...
 for this model.
@@
 
-    \caption[Alternate AGB models]{Comparisons of our 4 different AGB models except with $f_{\rm agb} = 0.2$, and a metallicity dependent CCSNe yield.
-Both panels plot [C/Mg]-[Mg/Fe], except the left has a bin centered at 0, and the right at [Mg/H]$=0.2$.
-The higher metallicity bin exposes how many of the AGB models predict downturns near solar metallicity which are not present in our data.}
+    \caption[Alternate AGB models]{Same as Figure \ref{fig:agb_sims} except where $f_{\rm agb}=0.2$. When yields are amplified, chaos ensues.}
 \end{figure}
@@
 \begin{figure}
+    \centering
     \includegraphics{y_mg.pdf}
+    \caption[Magnesium CCSNe yields]{Same as the top panel of Figure \ref{fig:y_cc}, but for magnesium. Our magnesium yield choice is shown as a dashed line at the top
+    }
 \end{figure}
@@
 \begin{figure}
+    \centering
     \includegraphics{fe_ia.pdf}
+    \caption[Adjusting type Ia iron]{Similar to Figure \ref{fig:agb_sims} except with variations of the SNeIa iron fraction}
 \end{figure}
@@
 \label{lastpage}
+
+\section{Software}
+Software has played an importaint role in this work. 
+\begin{itemize}
+    \item \citep{OhioSupercomputerCenter1987}
+    \item VICE \citet{JW20} \citet{james+21}
+    \item \cite{matplotlib}
+    \item \citet{numpy}
+    \item \citet{pandas}
+    \item Astropy \citep{astropy:2013, astropy:2018, astropy:2022}
+    \item IPython \citep{ipy}
+    \item \citep{scipy}
+\end{itemize}
+
 \end{document}

### 2023-04-07 osc/yields.py
new models

@@ -7,7 +7,7 @@ from vice.yields import ccsne, sneia, agb
 Z_Sun = 0.014
 y_c_0 = 0.005
 y_c_cc_0=0.0028
-y_n_flat = 7.1e-4
+y_n_flat = 7.2e-4
 
 YC_AGB0 = {
         "cristallo11": 3.47e-4,
@@ -47,7 +47,7 @@ def set_defaults():
 
     ccsne.settings["fe"] = 0.0012
     sneia.settings["fe"] = 0.0017
-    sneia.settings["fe"] *= 10**0.1 # correction for mdf, used in
+    # sneia.settings["fe"] *= 10**0.1 # correction for mdf, used in
 
     ccsne.settings["sr"] = 3.5e-8
     sneia.settings["sr"] = 0
@@ -55,6 +55,7 @@ def set_defaults():
     ccsne.settings["n"] = 3.6e-4
 
     sneia.settings["c"] = 0
+    sneia.settings["n"] = 0
 
     ccsne.settings["mg"] = 0.00185
     sneia.settings["mg"] = 0
@@ -73,7 +74,7 @@ def set_agb_elem(elem, study, factor):
         agb.settings[elem] = amplified_yields(elem, study, factor)
 
 def set_agb(study="cristallo11", factor=1):
-    for elem in ["c", "sr", "o", "mg"]:
+    for elem in ["c", "o", "mg"]:
         set_agb_elem(elem, study, factor)
 
 
@@ -135,6 +136,7 @@ def calc_alpha(agb_model="cristallo11" , eta=1, oob=False, f_agb=0.2):
 
     if oob:
         alpha_agb = 1
+        f_agb = YC_AGB0[agb_model]/y_c_0
     else:
         alpha_agb = f_agb*y_c/y_agb
 

### 2023-04-07 run.sh

@@ -50,9 +50,12 @@ function generate_filename {
   local dt="$9"
 
   # Generate filename
-  local filename="${agb_model}_f${agb_fraction}"
+  local filename="${agb_model}"
+
   if [ "$out_of_box_agb" = true ]; then
     filename="${filename}_OOB"
+  else 
+    filename="${filename}_f${agb_fraction}"
   fi
   filename="${filename}_eta${eta}_beta${beta}"
   if [ "$spec" != "insideout" ]; then

### 2023-04-07 src/simulation/multizone_sim.py

@@ -36,6 +36,8 @@ def run_model(name, prefix=None, migration_mode="diffusion", spec="insideout", n
         - "constant"
         - "lateburst"
         - "outerburst"
+        - "twoexp"
+        - "threeexp"
         see vice.migration.src.simulation.disks.star_formation_history
 
     n_stars: ``int`` [default: 2]
@@ -104,7 +106,11 @@ def run_model(name, prefix=None, migration_mode="diffusion", spec="insideout", n
                 burst_size = burst_size)
     elif spec == "twoexp":
         model.evolution = star_formation_history(spec = spec,
-                zone_width = zone_width, tau=1, amplitude=burst_size, t1=5)
+                zone_width = zone_width, timescale2=1, amplitude=burst_size, t1=5)
+    elif spec == "threeexp":
+        model.evolution = star_formation_history(spec = spec,
+                zone_width = zone_width, timescale2=1, amplitude=burst_size, 
+                t1=5, amplitude3=0.2, t2=12)
     else:
         model.evolution = star_formation_history(spec = spec,
                 zone_width = zone_width)

### 2023-04-07 src/simulation/src/simulations/disks.py

@@ -45,6 +45,7 @@ class diskmodel(vice.milkyway):
 		- "lateburst"
 		- "outerburst"
         - "twoexp"
+        - "threeexp"
 
 	verbose : ``bool`` [default : True]
 		Whether or not the run the models with verbose output.
@@ -158,7 +159,8 @@ class star_formation_history:
 					"insideout":	models.insideout,
 					"lateburst":	models.lateburst,
 					"outerburst":	models.outerburst,
-					"twoexp":	models.twoexp
+					"twoexp":	models.twoexp,
+					"threeexp":	models.threeexp,
 				}[spec.lower()]((i + 0.5) * zone_width, **kwargs))
 			i += 1
 

### 2023-04-07 src/simulation/src/simulations/models/__init__.py

@@ -5,3 +5,4 @@ from .lateburst import lateburst
 from .outerburst import outerburst
 from .static import static
 from .twoexp import twoexp
+from .threeexp import threeexp

### 2023-04-07 src/simulation/src/simulations/models/threeexp.py

@@ -3,7 +3,7 @@ This file declares the time-dependence of the star formation history at a
 given radius in the fiducial inside-out model from Johnson et al. (2021).
 """
 
-from .utils import modified_exponential, get_bin_number, interpolate, double_exponential
+from .utils import modified_exponential, get_bin_number, interpolate, triple_exponential
 from .normalize import normalize
 from .gradient import gradient
 import math as m
@@ -12,7 +12,7 @@ from .insideout import insideout
 
 
 
-class twoexp(double_exponential):
+class threeexp(triple_exponential):
 
 	r"""
 	The inside-out SFH model from Johnson et al. (2021).
@@ -38,7 +38,8 @@ class twoexp(double_exponential):
 			amplitude=1, timescale2=1, t1=5,
 			amplitude3=0.3, timescale3=1, t2=10):
 		super().__init__(timescale = insideout.timescale(radius),
-                	amplitude=amplitude, timescale2=timescale2, t1=t1, rise=2)
+                	amplitude=amplitude, timescale2=timescale2, t1=t1, rise=2,
+			amplitude3=amplitude3, timescale3=timescale3, t2=t2)
 		self.norm *= normalize(self, gradient, radius, dt = dt, dr = dr)
 
 	@staticmethod

### 2023-04-07 src/simulation/src/simulations/models/utils.py

@@ -299,6 +299,54 @@ class double_exponential(modified_exponential):
 	def __call__(self, time):
 		return  super().__call__(time) + (time>self.t1)*self.amplitude * m.exp(-(time-self.t1)/self.timescale2)
 
+class triple_exponential(modified_exponential):
+
+	r"""
+	The modified exponential evolution employed by the fiducial inside-out
+	models in Johnson et al. (2021), defined in the following manner:
+
+	.. math:: f(t) \sim (1 - e^{-t/\tau_\text{rise}})e^{-t/\tau}
+
+	Inherits from ``exponential``.
+
+	Parameters
+	----------
+	**kwargs : real numbers
+		All attributes can be assigned via keyword arguments on initialization.
+
+	Attributes
+	----------
+	rise : real number [default : 1]
+		The rise time :math:`\tau_\text{rise}` of the modified exponential.
+
+	Other attributes are inherited from the ``exponential`` object.
+
+	Calling
+	-------
+	This object can be called with only the time coordinate in the same units
+	as the attribute ``timescale``. The result will be in the units of the
+	attribute ``norm``.
+	"""
+
+	def __init__(self, norm=1, timescale=2, timescale2=1, amplitude=1,
+			timescale3=1, amplitude3=0.5, t1=5, t2=10, rise=1):
+		super().__init__(norm = norm, timescale = timescale, rise=rise)
+		self.timescale2 = timescale2
+		self.amplitude = amplitude
+		self.t1 = t1
+		self.timescale3 = timescale3
+		self.t2 = t2
+		self.amplitude3 = amplitude3
+
+
+	def __call__(self, time):
+		return  (super().__call__(time)
+			+ (time>self.t1) * self.amplitude 
+			* m.exp(-(time-self.t1)/self.timescale2)  
+			+ (time>self.t2) * self.amplitude3 
+			* m.exp(-(time-self.t2)/self.timescale3) 
+			)
+
 class gaussian:
 
 	r"""

### 2023-04-08 thesis/tex/main.tex
thesis ?

@@
 
-\titleformat{\chapter}{\normalfont\normalsize\centering}{Chapter \thechapter:}{1em}{}
+\titleformat{\chapter}{\normalfont\normalsize\centering}{\thechapter.}{1em}{}
 \titleformat{\section}{\normalfont\normalsize\centering}{\thesection}{1em}{}
@@
 \usepackage{graphicx}	% Including figure files
-\graphicspath{{../figures/}} \usepackage{natbib}
+\graphicspath{{../figures/}} 
+\usepackage{natbib}
 \usepackage[nottoc,numbib]{tocbibind}
@@
    \begin{center}
-       \vfill
+       \vspace*{5\baselineskip}
        \textbf{The Galactic Chemical Evolution of Carbon} \\
-       [3\baselineskip]
+       \vspace*{3\baselineskip}
         Undergraduate Research Thesis\\
-       [3\baselineskip]
+       \vspace*{3\baselineskip}
     Presented in partial fulfillment of the requirements for graduation \textit{with research distinction in Astronomy and Astrophysics} in the College of Arts and Sciences of The Ohio State University \\
-       [3\baselineskip]
+       \vspace*{3\baselineskip}
         by \\
+       \vspace*{3\baselineskip}
        {Daniel Alexander Boyea}\\
-       [3\baselineskip]
+       \vspace*{3\baselineskip}
        The Ohio State University\\
        April 2023\\
-       [3\baselineskip]
+       \vspace*{3\baselineskip}
        Project Advisor: David Weinberg, Department of Astronomy
@@
 Different chemical elements are produced in different sites, so stars leave traces of the Galaxy's chemical history.
-Through \textit{Galactic Archeology}, I can reconstruct the history of our galaxy by investigating the clues left in the remains---stars from the early universe \citep{Weinberg+22, emily+19}.
+Through \textit{Galactic Archeology}, we can reconstruct the history of our galaxy by investigating the clues left in the remains---stars from the early universe \citep{Weinberg+22, emily+19}.
 

### 2023-04-09 thesis/tex/main.tex
thesis corrections, to equilibrium

@@
 \usepackage{setspace}
-\usepackage{array}
-\setlength\extrarowheight{5pt}
+\usepackage{booktabs}
 
@@
 \makeatother
+\usepackage[tableposition=above]{caption}
 
@@
 \usepackage[nottoc,numbib]{tocbibind}
+
+\usepackage{isotope}
 % \usepackage[titles]{tocloft} % fig titles
@@
 \newcommand{\possesivecite}[1]{\citeauthor{#1}'s \citeyearpar{#1}}
+\newcommand{\alp}{$\alpha$}
 
@@
 Stellar evolution models provide highly uncertain predictions for elemental yields due to our limited understanding of stellar physics.
-In this paper, I aim to estimate the nucleosynthetic yields of carbon using galactic chemical evolution models.
-
-I find that the AGB stars make up a fraction $0.20_{-20}^{+80}$ of total carbon production at late times.
+In this paper, I aim to estimate the nucleosynthetic yields of C using galactic chemical evolution models.
+
+I find that the AGB stars make up a fraction $0.20_{-20}^{+80}$ of total C production at late times.
 
@@
 
-Galactic chemical evolution (GCE) aims to understand the chemical and star formation history of galaxies.
+Galactic chemical evolution (GCE) aims to understand the chemical and star formation histories of galaxies.
 At the core of GCE models are stellar yields---the amount of each chemical element stars produce (or destroy).
-Different chemical elements are produced in different sites, so stars leave traces of the Galaxy's chemical history.
-Through \textit{Galactic Archeology}, we can reconstruct the history of our galaxy by investigating the clues left in the remains---stars from the early universe \citep{Weinberg+22, emily+19}.
-
-I aim to understand the GCE of carbon, where the element is produced and how the abundances of this element evolve over time.
-Why stuy carbon?
-Carbon is unique nucleosynthetically, one of few light elements (along with nitrogen) which are produced in Asymptotic Giant Branch (AGB) stars \citep[for example,][]{jennifer19, KL14}.
-Carbon and nitrogen are well studied elements as they are easy to observe in stellar spectra, even at the lowest metallicities \citep{FN15} SOMETHING ELSE?.
-Additionally, carbon and nitrogen are used as age indicators in red giant branch stars \citep[e.g.][]{martig16, MG15, fiorenzo+21}.
-While we know carbon is produced in AGB stars and core collapse supernovae (CCSNe), we still have limited understanding of the importaince and metallicity-dependence of each process.
-
-We also know that there is evidence for non-monatonic carbon yield patterns. 
-pattern where carbon is more readily produced by both high metallicity and very low metallicity stars (CEMPS, early GCE results), but our picture. \citep{FN15,cooke+17,berg+19}.
+The chemical elements are produced in different amounts by different stars, leaving Galaxy's evolutionary history.
+Through \textit{Galactic Archeology}, we can reconstruct the history of our galaxy by investigating the clues left in reminants from the past \citep{Weinberg+22, emily+19}.
+
+Here, I aim to understand C enrichment---where it is produced and how its abundances evolve over time.
+Why study C?
+C is unique nucleosynthetically, one of few light elements (along with N) produced in Asymptotic Giant Branch (AGB) stars \citep[e.g.][]{jennifer19, KL14}.
+C and N are well studied elements as they are easy to observe in stellar spectra, even at the lowest metallicities \citep{FN15} SOMETHING ELSE?.
+Additionally, C and N are used as age indicators in red giant branch stars \citep[e.g.][]{martig16, MG15, fiorenzo+21}.
+While we know C is produced in AGB stars and core collapse supernovae (CCSNe), we still have limited understanding of the importaince and metallicity-dependence of each process.
+
+Empirically, gas-phase [C/O] ratios decrease with increasing [O/H] at the lowest metallicitis---in high redshift damped Lyman-alpha systems (DLAs)---and then [C/O] increases above $\rm [O/H] \approx 1$ (\citealt{berg+19,cooke+17}; see discussion in SECTION).
+
+\cite{james+22} examend GCE models of N, an elements whose production is closely related to C.
+\cite{james+22} found trends in N and O abundances can be explained by the metallicity dependence of relatice N and O yields.
+Here, I extend their models to C and show that similar constraints on C and O relative yields can be obtained from observed abundance ratios.
+
+We also know that there is evidence for non-monatonic C yield patterns. 
+pattern where C is more readily produced by both high metallicity and very low metallicity stars (CEMPS, early GCE results), but our picture. \citep{FN15,cooke+17,berg+19}.
+
+Despite their centrol role in GCE models, nucleosynthetic yields predicted by stellar evolution models are rife with uncertainties.
+Poorly understood processes, including mass loss, opacity, nuclear reaction rates, rotational mixing, and convection/convective boundaries each shape the production rates of atomic nuclei in stellar interios \citep{KL14,V13, LC18, emily+21}.
+Additionally, changes in massive star's explodabinitily can introduce a factor of \~2 change in population averaged-yields \citep{emily+21}.
 
@@
 However, these models are rife with uncertainties, limited by our understanding of critical physical processes such as nuclear reaction rates, convection, rotational mixing, opacity, and mass loss CITATIONS.
-Changes in opacity, rotation, reaction rates, and explodability can substantially affect carbon yields \citep{KL14,V13, LC18, emily+21}.
+Changes in opacity, rotation, reaction rates, and explodability can substantially affect C yields
 
@@
 
-While there are many stellar measurments of carbon, accurately determining the birth abundance is more challenging.
-For example, when a star becomes a RGB star, material from the CNO-processed core \citep{fiorenzo+21,KL14}.
-Since this core-processed material is now carbon depleted and nitrogen enhanced, measurments of this star's atmosphere will no longer reflect the birth abundances of the star.
-Additionaly, carbon is faint in HII regions and determining gas-phase abundances is challenging \citet{skillman+20}.
-Other surveys, such as GALAH, have unreliable carbon measurments with low detection rates \citep{emily+19}.
+While there are many stellar measurments of C, accurately determining the birth abundance is more challenging.
+For example, when a star becomes a RGB star, material from the CNO-processed core is mixed with the envelope in First Dredge Up (FDU) \citep{fiorenzo+21,KL14}.
+Since this core-processed material is now C depleted and N enhanced, measurments of this star's atmosphere will no longer reflect the birth abundances of the star.
+Additionaly, C is faint in HII regions and determining gas-phase abundances is challenging \citet{skillman+20}.
+Other surveys, such as GALAH, have unreliable C measurments with low detection rates \citep{emily+19}.
 
@@
 
+To this end, I use a sample of subgiant stars from APOGEE \citep{apogee17}.
+According to stellar evolution models (CITES), these stars have not yet experienced dredge-up.
+Their photospheric abundances should thus represent their birth composition.
 In Fig.
-\ref{fig:subgiants}, I present a sample of APOGEE subgiants.
-These subgiants were chosen based on their location in the HR diagram based on the criteria in \citet{jack_subgiant} also replicated in Appendix \ref{sec:jack}.
-Because subgiants have not undergone FDU, their surface abundances are an accurate reflection of the birth abundances (CITATION).
+\ref{fig:subgiants}, I plot this sample, selected by criteria in \citet[see Appendix \ref{sec:jack}]{jack_subgiant}.
+These emperical resolults contain information on the relative C and O yields, which I use later in this work.
 
@@
     \includegraphics{subgiants_mgfe.pdf}
-    \caption[APOGEE Subgiants]{The [C/Mg] ratio against [Mg/H] (top) and [Mg/Fe] (bottom) for our sample of APOGEE subgiants.
+    \caption[APOGEE Subgiants]{The [C/Mg] ratio against [Mg/H] (top) and [Mg/Fe] (bottom) for the \citet{jack_subgiant} sample of APOGEE subgiants.
 On the top, I plot high-$\alpha$ stars in blue and low-$\alpha$ stars in orange using the seperation defined in Equation \ref{eq:high_alpha}.
@@
 
-Modern theoretical nucleosynthesis provides the starting point for our models.
-I focus on three primary nucleosynthetic pathways: AGB stars, CCSne, and SNeIa.
-Each process has unique timescales and element production which I can trace through the tools of GCE.
-While carbon is only known to be produced in AGB stars and CCSNe, comparing carbon to iron production (from SNeIa) adds a valuable constraint to our models and insight into the delay-time production of carbon.
-
-After a group of stars are formed, CCSNe from massive stars are the first enrichment, providing light elements such as C, O, and Mg and heavier elements such as Fe and beyond.
-Importaintly, $\alpha$ elements like O and Mg are only formed in CCSNe (in significant quantities).
+Theoretical models of stellar nucleosynthesis provide the starting point of this investigation.
+I focus on three primary nucleosynthetic pathways: Asymptotic Giant Branch (AGB) stars, Core Collapse Supernovae (CCSNe), and Type Ia Supernovae (SNe Ia).
+Each process has unique timescales and yields, tracable through the tools of GCE.
+While C is only produced in AGB stars and CCSNe, comparing C to Fe, which is produced in SNe Ia, adds a valuable constraint on the delay-time distribution (DTD) of C enrichment.
+
+When a Single Stellar Population (SSP) forms, CCSNe are the first enrichment events.
+CCSNe provide light elements such as C, O, and Mg and heavier elements such as Fe and beyond.
+Metallicity-independent yields from CCSNe are the only statisticly significant source of O and Mg ($\alpha$ elements).
 Next, low mass stars begin to reach the end of their lives.
-The dying breaths of AGB stars are known to be importaint sources of C, N, and a smattering of heavier elements.
-Finally, the white dwarfs, including formation and time to collide/over-eat, explode, releasing much of Fe and nearby elements.
-
-I focus on O and Mg as $\alpha$ elements only formed in CCSNe, and use Fe to
-trace delayed enrichment from SNeIa. C and N are both formed in AGB and CCSNe.
-
-There are two $\alpha$-elements I care about: Mg and O. Stellar observations
-of magnesium are more reliable but oxygen abundances are easier to measure in
-HII regions. I assume that both Mg and O are produced entirely in CCSNe with
-constant, metallicity-independent yields. Thus $\text{[Mg/H]} = \text{[O/H]} =
-[\alpha/\text{H}]$ in our models. (Observational validation?)
-
-For carbon, the dominant producer is from massive stars which eject carbon fused in their cores during CCSNe.
-
-To calculate the net initial mass function (IMF)-weighted yields, I use the \citet{james+21} model (hereafter \JJ) with the Versatile Integrator for Chemical Evolution code (\VICE).
-As stellar evolution models predict per-star yields for stars of each mass, we need to integrate over the IMF to determine the total yields in terms of star formation.
-
-As the focus of this work is on carbon yields, I keep all other yields fixed. The yields I use are based on \citet{james+21, james+22}.
-
+The dying breaths of AGB stars are known to be importaint sources of C, N, and neutron capture elements.
+Finally, white dwarfs explode, releasing Fe and other iron-peak elements.
+
+Stellar measurments of Mg are more reliable, but O abundances are easier to measure in HII regions. 
+I therefore use Mg abundances from the \citet{jack_subgiant} subgiant sample as my primary emperical constraint.
+However, I use O abundances for gas-sphase measurments and low-metallicity stars (\S \ref{sec:gas}).
+I model both Mg and O as metallicity-independent population-averaged yields dominated by massive stars.
+${\rm [O/Mg]}\approx 0$ across a wide range of metallicities in APOGEE \citep{Weinberg+19, Weinberg+22}.
+I adopt O and Mg relative yields given by the solar mixture of \cite{asplund+09} <MATH>.
+
+To calculate the IMF-weighted\footnote{IMF: Initial Mass Function} net yields of C, I use the Versatile Integrator for Chemical Evolution code (\VICE\footnote{\VICE~is available at \url{https://github.com/giganano/VICE}}).
+As stellar evolution models predict per-star yields of a given mass, I need to integrate over the IMF to determine the total yields in terms of star formation.
+
+In the interest of focusing on carbon yields, I hold yields of other elements fixed. 
+I adopt yields from \citet{james+21, james+22}.
+In Table \ref{tab:fiducial_mod}, I tabulate yield values, in units of a stellar population's birth mass.
 Also following \citet{james+21, james+22}, I take the SNeIa Delay Time distribution to be a
@@
 	\label{tab:fiducial_mod}
+
 	\begin{tabular}{l l l l}
-		\hline
+		\toprule
         Element & $\Ycc$ & $\tilde{y}^{\rm AGB}$ & $y^{\rm SNe Ia}$ \\
-		\hline
+		\midrule
         C & $0.0028 + 0.001(Z/Z_\odot)$ & $2.9\times{\rm C11}$ &  0 \\
@@
         N & 0.00072 & $9\times10^{-4}(Z/Z_\odot)M$ & 0\\
-		\hline
+		\bottomrule
 	\end{tabular}
@@
 
-An AGB star is a low mass ($\lesssim 8 M_{\sun}$) star during the final phases of evolution.  In an AGB star, two competing processes determine the outcome of carbon production.
-Third Dredge Up (TDU) is needed to eject carbon from the star, enriching the surface with helium-burning-processed material from the core.
-But Hot Bottom Burning (HBB) at the base of the convection layer changes carbon into nitrogen.
-TDU occurs during thermal pulsations, where the convective layer of the star passes into the inner layers with He-burning products which mixes in C and O into the envelope.
-In contrast, HBB may happen if the base of the convective envelope reaches about 50MK, initiating the CNO cycle, converting most C12 into N14.
-
-Carbon abundances are strongly affected by CNO cycle processing in stars.
-The CNO cycle is one of two series of nuclear reactions( $^{12}$C(p, $\gamma$)$^{13}$N($\beta^+ \nu_e$)$^{14}$N(p, $\gamma$)$^{15}$O($\beta^+\nu_e$)$^{15}$N(p,$\alpha$)$^{12}$C
-
-Because the $^{14}$N(p, $\alpha$) proton capture is the slowest component of the CNO cycle ****, the CNO cycle, to first order, converts all $^{12}$C into $^{14}N$.
-
-The differences in yields between AGB models depend on the mass loss rate, treatment of convection, and nuclear reaction rates.
-
-In this work, I explore four different sets of AGB star yields representative of the variety of options which also provide reasonably well sampled grids in metallicity and mass necessary for chemical evolution studies.
+An AGB star is a low mass ($\lesssim 8 M_{\sun}$) star during its final phase of evolution.
+In an AGB star, two competing processes determine the outcome of C production: Third Drege Up (TDU) and Hot Bottom Burning (HBB).
+DU accompianies thermal puslations in AGB stars.
+Durring a TDU event, material from the CO core is mixed with material exposed to partial He-shell burning, increasing C and O abundances in the envelope \citep{KL14}.
+HBB is the activation of proton capture reactions, and the CNO cycle%
+\footnote{The CNO (I) cycle is
+\isotope[12]{C}(p, $\gamma$)
+\isotope[13]{N}($\beta^+ \nu_e$)
+\isotope[13]{C}(p, $\gamma$)
+\isotope[14]{N}(p, $\gamma$)
+\isotope[15]{O}($\beta^{+}\nu_e$)
+\isotope[15]{N}(p, \alp)
+\isotope[12]{C}.
+ Other minor branches of the CNO cycle are not relevant here.
+ \citep{solar-fusion}.
+}
+at the base of the convective envelope.
+Because the $^{14}$N(p, $\alpha$) proton capture is the slowest component of the CNO cycle \citep{solar-fusion}, the CNO cycle converts nearly all \isotope[12]{C} into \isotope[14]{N}.
+As a result, when both TDU and HBB occur, \isotope[12]{C} yields are lowered (see discussion in \citealt{james+22} and \citealt{ventura+13}).
+
+In this work, I explore four different sets of AGB star yield tables from literature, providing well sampled grids in metallicity and mass for use in chemical evolution models. 
 \begin{itemize}
@@
 \end{itemize}
-Unless otherwise noted, C11 is the model I choose as our fiducial AGB yield.
-
-I use IMF-Integrated yields calculated with \VICE~throughout this paper (see
-section \ref{sec:vice}, \citet{james+21, james+22}). For an element X and star
-with mass $M$, the stellar yield $y$ is defined as the net production of X relative 
-to $M$, or
-\begin{equation}
-    y_{\rm X} = \frac{M_{\rm X,\ ejected} - Z_{0, X} M_{\rm ejected}}{M}   
-\end{equation}
-where I let $M_{\rm ejected}$ and $M_{\rm X, ejected}$ be the total ejected
-stellar mass (through winds and supernovae ejecta) and the ejected mass of X,
-and $Z_{0, X}$ was the birth mass fraction of element X.
-
+I use C11 as the fiducial AGB yield.
+For an element X and star with mass $M$, the stellar yield $\tilde{y}$ is defined as the net production of X relative to $M$, or
+\begin{equation}
+    \tilde{y}_{\rm X} = \frac{M_{\rm X,\ ejected} - Z_{0, X} M_{\rm ejected}}{M}   
+\end{equation}
+where $M_{\rm ejected}$ and $M_{\rm X, ejected}$  are the total ejected mass of the envelope and the element X, respectively.
+
+Fig. \ref{fig:y_agb} compares the AGB C yield $\tilde{y}_\text{C}^\text{AGB}(M, Z)$ for each model I consider. 
+The yields may be negative when the birth abundance is higher than the C abundance of the material ejected back to the ISM. 
+Most models agree on the qualitative shape of the net fractional AGB C yield---% 
+stars with mass $\sim 2--4 M_\odot$ have highest fractional C yields, with the mass of the peak increasing and overal yields decreasing with increasing $Z$.
+High mass, high $Z$ stars destroy \isotope[12]{C} due to HBB.
+
+In Fig. \ref{fig:agb-ssp}, we plot the total production of C by AGB stars as a function of SSP age.
+Effectively, this is equivalent to integrating Eq. \ref{eq:imf-yield} down to $M_{to}$, the turnoff mass for time $t$. 
+\footnote{In our model, the mass-lifetime relation is
+$\log \tau_M = 1.02 - 3.57\log M + 0.90 \left(\log M\right)^2$,
+where $\tau_M$ is in Gyr,
+from \citet{larson74}.}
+As the mass range $2\lesssim M \lesssim 4$ is most important for C production, the characteristic delay time is $\sim 1$Gyr.
+In contrast, Fe from SNeIa (plotted as the dashed black line in Fig \ref{fig:agb-ssp}) has a longer characteristic delay time.
+
+K10 and K16 weight C production more heavily towards massive stars resulting in a faster enrichment delay time, whereas the C11 and V13 models predict a slightly longer timescale with order 1Gyr, but little to no C is produced more than 2Gyr after a star formation event.
+This is in contrast to iron which is still produced by SNeIa up to 10Gyr after a star formation event.
+As shown in the right panel of Fig. \ref{fig:agb-ssp}, with increasing $Z$, C enrichment occurs earlier, and C destruction in low mass stars leads to a declining C abundance at late times.
+
+\begin{figure}
+    \centering
+ 	    \includegraphics[scale=1]{agb_yields.pdf}
+        \caption[AGB C yields]{The net fractional AGB C yield ($\tilde{y}$) plotted as a function of initial stellar mass $M$.
+Metallicity is colorcoded according to the colorbar.
+I plot $\tilde{y}=0$ for reference.
+Each panel represents yields from one of four AGB models: C11 \citep{cristallo+11, cristallo+15}, K10 \citep{karakas10}, V13 \citep{ventura+13,ventura+14,ventura+18}, and K16 \citep{KL16, karakas+18}.
+        }
+        \label{fig:y_agb}
+\end{figure}
+\begin{figure}
+    \includegraphics[scale=1]{y_agb_t2.pdf}
+
+    \caption[AGB yields delay time distribution]{
+        C production by AGB stars as a function of SSP age, normalized to the total mass $M_{\rm tot}$ produced at $t=10$ Gyr.
+Left: The four AGB yield models from literature at solar metallicity (C11, K10, V13, or K16).
+The delay time distribution of type Ia supernovae ($\propto t^{-1.1}$) is plotted as a dashed black line for comparison.
+Right: The C11 AGB model at different metallicities.
+}
+    \label{fig:agb-ssp}
+\end{figure}
+
+Though per-star yieldds are necessary to compute AGB star enrichment rates in GCE models, IMF-averaged yields are useful in interpreting their predictions.
+For a yield $y$ from a star of mass M and initial metallicity $Z$, the IMF-averaged yield is given by
 More useful for GCE are Initial Mass Function (IMF) yields, where I sum up the
@@
 I define the IMF-integrated yield of X with:
-\begin{equation}
-Y_{\rm X}^{\rm proc}(Z) = \int_{M_{\rm min}}^{M_{\rm max}} y_{\rm X}^{\rm proc}(M, Z)\ \Phi(M)  \ dM
-\end{equation}
-Where $\Phi(M) = \frac{dN}{dM}/ \int_{M_{\rm min}}^{M_{\rm max}} \frac{dN}{dM}\ dM$ is the normalized IMF, $M_{\rm min}$ and $M_{\rm max}$ are the minimum and maximum mass of stars, which I take to be $0.08 M_{\sun}$ and $100 M_{\sun}$ respectively; and $\frac{dN}{dM}$ is the initial mass function, the frequency of stars born between $M$ and $M+dM$.
-
-Fig.
-\ref{fig:y_agb} compares the net fractional AGB carbon yield, $m_\text{C}^\text{AGB}(M, Z)$ for each AGB model I consider.
-Note that the yields may be negative when the birth abundance is higher than the carbon abundance of the material ejected back to the ISM.
-
-Most models agree on the qualitative shape of the net fractional AGB carbon yield.
-The stars with the highest fractional carbon yields are between 2 to 4 solar masses, depending on the metallicity and model.
-Both lower and higher mass stars produce less carbon, and high mass stars may even destroy carbon at high metallicity due to highly efficient HBB.
-And all models agree that the carbon yield generally decreases with metallicity.
-
-Metallicity dependence:
-V13 is the only model that stands out, showing a non-monotonic metallicity dependence, however this effect is only for models with [M/H]$\leq -1$.
-Otherwise the major differences between the models are the precise amount of carbon and the slope of the metallicity dependence.
+
+\begin{equation} \label{eq:imf-yield}
+    y_{\rm X}^{\rm proc}(Z) = 
+    \int_{M_{\rm min}}^{M_{\rm max}} 
+    \tilde{y}_{\rm X}^{\rm proc}(M, Z)
+    \frac{dN}{dM}  \ dM
+\end{equation}
+
+where $\frac{dN}{dM}$ is the normalized IMF, $M_{\rm min}$ and $M_{\rm max}$ are the minimum and maximum mass of stars, which I take to be $0.08 M_{\sun}$ and $100 M_{\sun}$ respectively.
+For AGB stars, the yields are truncated above 8 $M_{\odot}$.
+
+In Fig. \ref{fig:yagb-z}, I plot the IMF-averaged C yields for each AGB model as a function of metallicity $Z$.
+V13 differs that it shows a non-monotonic metallicity dependence. However, this effect is only form models with $\log Z/Z_\odot \lesssim -1$.
+Otherwise, models only differ in the yield normalization and strength of metallicity dependence. All models predict yields within a factor of $\sim 2$.
 For example, the three models C11, K10, and K16 predict $y_\text{C}^\text{AGB}$ to be between 0.006 and 0.008 at solar metallicity, but C11 has a much shallower metallicity dependence than the K10 and K16 models.
-And at solar, V13 predicts a value at around 0.004 so the models are all within about a factor of 2.
-
-Another difference is the speed at which equilibrium is reached.
-K10 and K16 weight carbon production more heavily towards massive stars resulting in a faster time to equilibrium, whereas the C11 and V13 models predict a slightly longer timescale with order 1Gyr, but little to no carbon is produced more than 2Gyr after a star formation event.
-This is in contrast to iron which is still produced by SNeIa up to 10Gyr after a star formation event.
-
-\begin{figure*}
-    \centering
- 	    \includegraphics[scale=1]{agb_yields.pdf}\\
-
-        \caption[AGB carbon yields]{The net fractional AGB carbon yield ($\tilde{y}$) plotted as a function of initial stellar mass $M$.
-Metallicity is colorcoded according to the colorbar.
-I plot $\tilde{y}=0$ for reference.
-Each panel represents yields from one of four AGB models: C11 \citep{cristallo+11, cristallo+15}, K10 \citep{karakas10}, V13 \citep{ventura+13,ventura+14,ventura+18}, and K16 \citep{KL16, karakas+18}.
-            %C11 reports values at metallicities $Z=$ 0.0001, 0.0003, 0.001, 0.002, 0.003, 0.006, 0.008, 0.01, 0.014, 0.02; K10 at $Z=$0.0001, 0.004, 0.008, 0.02; V13 at $Z=$0.0003, 0.001, 0.002, 0.004, 0.008, 0.014, 0.04; and K16 at $Z=$0.0028, 0.007, 0.014, 0.03.
-        }
-            \label{fig:y_agb}
-\end{figure*}
-
-\begin{figure}
-    \includegraphics[scale=1]{y_agb_t2.pdf}
-
-    \caption[AGB yields delay time distribution]{
-        Carbon production by AGB stars as a function of SSP age, normalized to the total mass $M_{\rm tot}$ produced at $t=10$ Gyr.
-Left: The four AGB yield models from liturature  at solar metallicity (C11, K10, V13, or K16).
-The delay time distribution of type Ia supernovae ($\propto t^{-1.1}$) is plotted as a dashed black line for comparison.
-Each model has a similarly shaped DTD, and most AGB enrichment occurs before 1 Gyr.
-Right: The C11 AGB model at different metallicities.
-With increasing metallicity, carbon enrichment occurs earlier, and the DTD eventually becomes non-monotonic.
-    }
-
-\end{figure}
-
-\begin{figure*}
-    \centering
-
+V13 instead predicts a yield $\sim 0.004$.
+
+\begin{figure}
+    \centering
     \includegraphics[scale=1]{y_agb_vs_z.pdf}
 
-    \caption[AGB yield metallicity dependence]{The net fractional IMF-weighted AGB carbon yield $\Ycagb$ as a function of metallicity for each of our AGB yield models.
-    }
-
-\end{figure*}
+    \caption[AGB yield metallicity dependence]{The net fractional IMF-weighted AGB C yield $\Ycagb$ as a function of metallicity for each of our AGB yield models.
+    }
+    \label{fig:yagb-z}
+\end{figure}
 
@@
 
-Massive stars form $^{12}$C through the triple--$\alpha$ process. However, the carbon has to get out of the star to be useful. 
+Massive stars form $^{12}$C in their cores through the triple--$\alpha$ process. However, only C ejected through supernovae and stellar winds contributes to the yield. 
 While there are many stellar models providing predictions of CCSNe yields, the results of these models are highly uncertain due to the many stellar modeling uncertainties.
 
-I summarise many of the predictions of stellar models in Fig. \ref{fig:y_cc}. 
+In Fig.
+\ref{fig:y_cc}, I plot calculations of the IMF-integrated yields, using Eq.
+\ref{eq:imf-yield} (computed using \VICE's \texttt{vice.yields.ccsne.fractional} function).
+On the right, I also show the CCSNe-[C/Mg] ratio, defined by
 \begin{equation}\label{eq:c_mg_cc}
-    {\rm [C/O]^{CC}} = \log_{10}\left( \frac{y_{\rm C}^{\rm CC}}{y_{\rm O}^{\rm CC}}\right) - \log_{10} \left( \frac{Z_{C, \sun }}{Z_{O, \sun }} \right)
-\end{equation}
-Notice how even these ratios
+    {\rm [C/Mg]^{CC}} = \log_{10}\left( \frac{\Ycc}{\Yoc}\right) - \log_{10} \left( \frac{Z_{{\rm C},\ \sun }}{Z_{{\rm Mg},\ \sun }} \right).
+\end{equation}
+In other words, ${\rm [C/Mg]^{CC}}$ describes what [C/Mg] would be if CCSNe were the only process producing C.
+Notice that even at $Z=Z_\odot$, there is a wide range ($\sim 1$ dex) in predicted $\Ycc$.
 
     \begin{itemize}
-        \item Wide range in predictions, exacerbated to 1 dex range when including variance in oxygen predictions
-        \item (explain) most models have a near-metallicity independent oxygen yield, so I choose the fiducial value of 0.015 despite varience in $y_O^{cc}$
-        \item The fiducial value, where I choose the carbon yield from Sukhbold+16, may be above most predictions of carbon yields but is within the range of yield ratios
-        \item the fiducial value would reach an equilibrium carbon yield of -0.1 without AGB stars
-        \item Rotation in LC18 appears to increase metallicity dependence of carbon production (read this paper more carefully)
-        \item NKT and LC agree in positive metallicity depenent yields
+        \item Massive stars should dominate C yields, GCE models indicate similar results \citep[e.g.][]{prantzos+18,rybizki+17}.  
+        \item Rotation in LC18 appears to increase metallicity dependence of C production (read this paper more carefully)
+        \item NKT and LC (with rotation)agree in positive metallicity depenent yields
+        \item [C/Mg]
+        \item The fiducial value, where I choose the C yield from Sukhbold+16, may be above most predictions of C yields but is within the range of yield ratios
+        \item the fiducial value would reach an equilibrium C yield of -0.1 without AGB stars
     \end{itemize}
@@
     \includegraphics{y_c_cc.pdf}
-    \caption[CCSNe carbon yields]{
-        Carbon yields from massive stars.
-        Top: The net fractional IMF-weighted CCSNe yield of carbon (computed using \VICE's \texttt{vice.yields.ccsne.fractional} function) as a function of metallicity.
-        Bottom: The CCSNe carbon to magnisium abundance ratio, defined in Equasion \ref{eq:c_mg_cc}. The black line represents the carbon yield of the fiducial model,
+    \caption[CCSNe C yields]{
+        C yields from massive stars.
+        Top: The IMF-weighted CCSNe yield of C a function of metallicity.
+        Bottom: The CCSNe [C/Mg] abundance ratio, defined in Eq. \ref{eq:c_mg_cc}. The black line represents the C yield of the fiducial model,
     $\Ycc = 0.0028 + 0.001 (Z/Z_{\odot})$. 
@@
 
-Chemical abundances reach an equilibrium.
-At least with simple enough assumptions.
-The new elements synthesized in stars balance against elements lost to galactic winds and locked in stellar reminants.
-While our galaxy is likely not in perfect equilibrium or described by a single, homogenous chemical region, I can still use an equilibrium approximation to understand total yields \citep[e.g.][]{james_dwarf,james+22,WAF17}.
-
-Following the formalism of \citet{WAF17}, I assume a simple one-zone chemical evolution model.
-The gas and stars are considered to be homogenously and instantaneusly mixed, so I can represent all quantaties as scalars.
-I define $M_{X}$ to be the mass of element X in the gas phase, $\dot{M}_\star$ to be the star fomation rate (in M$_\odot$ yr$^{-1}$).
-$\eta$ is the mass loading factor, $\eta=\dot{M}_{\rm outflow}/\dot{M}_\star$, representing the strength of outflows.
-$r$ is the recycling fraction, i.e.
-the net fraction of new star formation which will be returned to the ISM.
-
-Given the total IMF-weighted yield of magnesium, $y_{\rm Mg}$, I can write the change in the ISM mass of magnesium, $\dot{M}_{\rm Mg}$ as the sum of newly produced elements, elements lost inside stellar remanents, and elements lost to galactic outflows.
-\begin{equation}
-    \frac{d{M}_{\rm Mg}}{dt} = \dot{M}_{\rm Mg,~new} - \dot{M}_{\rm Mg~reminants} - \dot{M}_{\rm Mg,~outflows}
-\end{equation}
-The newly produced mass can be written in terms of the yield, $\dot{M}_{X,\rm~new}=y_X\dot{M}_\star$.
-In terms of the return mass fraction of stars $r$, the mass lost to reminants is $Z_X (1-r)\dot{M}_\star$.
-And, the outflows deplete a mass $Z_X \eta\dot{M}_\star$.
-Substituting,
-\begin{equation}
-    \frac{d{M}_{X}}{dt} = y_{X} \dot{M}_\star - (1 + \eta - r) Z_{X} \dot{M}_\star
-\end{equation}
-\citep{WAF17}.
+In the presence of metal-poor gas accretion and feedback-driven outflows, galaxies reach an equilibrium abundance in which production of new metals is balanced by losses to new stars and outflows \citep{larson72, dalcanton07, FD08, PS11, lilly13}.
+While our galaxy is likely not in perfect equilibrium or described by a single, homogenous chemical region, the equilibrium approximation is nevertheless useful in understanding yields and metallicity dependence \citep[e.g.][]{james_dwarf,james+22,WAF17}.
+
+I assume a simple ``one-zone'' chemical evolution model \cite[e.g.][]{tinsley80, pagel09, matteucci21}.
+The gas and stars are homogenously and instantaneusly mixed, so spacial dependence is neglected.
+
+I define $M_{X}$ to be the mass of element X in the gas phase, $\dot{M}_\star$ to be the star fomation rate (in M$_\odot$ yr$^{-1}$), and $\eta$ to be the mass loading factor $\eta\equiv\dot{M}_{\rm outflow}/\dot{M}_\star$ representing the strength of outflows.
+SSPs return a fraction $r$ of their birth mass back to the ISM, due to ejected stellar envelopes. $r\approx0.4$ for a \citet{kroupa01} IMF.
+Given the IMF-weighted yield of Mg $y_{\rm Mg}$, the rate of change in the ISM mass of Mg $\dot{M}_{\rm Mg}$ is a simple sum of sources and sinks,
+\begin{equation}
+    \dot{M}_{\rm Mg} = \dot{M}_{\rm Mg,~new} - \dot{M}_{\rm Mg~remnants} - \dot{M}_{\rm Mg,~outflows},
+\end{equation}
+where the first term on the right-hand side describes CCSNe enrichment. 
+In terms of the return mass fraction of stars $r$, the mass lost to remnants is $Z_X (1-r)\dot{M}_\star$.  And, the outflows deplete a mass $Z_X \eta\dot{M}_\star$. Substituting, 
+\begin{equation}
+    \dot{M}_{\rm Mg}= y_{X} \dot{M}_\star - (1 + \eta - r) Z_{X} \dot{M}_\star.
+\end{equation}
 Assuming an exponentially declining star formation history, $\dot{M}_\star \propto e^{-t/\tau_{\rm sfh}}$, this equation can be solved analytically. 
@@
 
-While Equation \ref{eq:z_eq} can be applied to CCSNe carbon, the delayed time contribution of AGB carbon can complicate the result.
-Instead, using an effective or DTD-integrated yield, $\langle \Ycagb \rangle$
+While Equation \ref{eq:z_eq} can be applied to CCSNe C, the delayed time contribution of AGB C can complicate the result. Instead, using an effective or DTD-integrated yield, $\langle \Ycagb \rangle$
 \begin{equation}
@@
 \end{equation}
-So, for carbon, Equation \ref{eq:z_eq} becomes
+So, for C, Equation \ref{eq:z_eq} becomes
 \begin{equation}
@@
 
-With these definitions, I can calculate the core collapse yields of carbon as a function of metallicity:
+With these definitions, I can calculate the core collapse yields of C as a function of metallicity:
 \begin{equation}
@@
 Rewriting in terms of the observed abundance ratio and dividing by
-$y_\text{Mg}^\text{CC}$. So, given the outflows or CCSNe oxygen yields, the
-carbon AGB yield, and the \caah mean abundance track, I can estimate the CCSNe carbon yield. Written as a relative yield:
+$y_\text{Mg}^\text{CC}$. So, given the outflows or CCSNe O yields, the
+C AGB yield, and the \caah mean abundance track, I can estimate the CCSNe C yield. Written as a relative yield:
 \begin{equation}
@@
     \includegraphics[]{analytic.pdf}
-    \caption[Reverse fit yields]{Inferred massive star carbon yields as a function of metallicity.
+    \caption[Reverse fit yields]{Inferred massive star C yields as a function of metallicity.
 I assume equilibrium and $3\times {\rm C11}$ AGB yields (orange curve, see discussion in Section \ref{sec:equilibrium}).
@@
 As Equation \ref{eq:z_co} shows, the yield ratios are independent of $\eta$, and independent of the SFH (ignoring the DTD term).
-As such, I set the total carbon yields to 
+As such, I set the total C yields to 
 \begin{equation}
@@
 
-Additionally, each AGB yield set (C11, K10, V13, K16), fails to produce enough AGB carbon for our fiducial model (see REF).
+Additionally, each AGB yield set (C11, K10, V13, K16), fails to produce enough AGB C for our fiducial model (see REF).
 So, I introduce a process factor, $\alpha_{\rm AGB}$, which represents the multiplicative increase in $\Ycagb$ from the published yields.
@@
 
-I have investigated uniform increases in carbon yields and have found these changes make little effect on the resulting trends.
-Fixing the total carbon yield at solar reduces the number of free parameters and keeps the model reasonably consistant with observations, and enables us to more consistantly explore differen AGB models.
+I have investigated uniform increases in C yields and have found these changes make little effect on the resulting trends.
+Fixing the total C yield at solar reduces the number of free parameters and keeps the model reasonably consistant with observations, and enables us to more consistantly explore differen AGB models.
 
@@
 	\centering
-    \caption[AGB net solar IMF yields]{For each AGB yield set, our calculation of the effective SFH- and IMF-weighted carbon AGB yield, along with the multiplicative factor to reach an AGB contribution of 20.}
+    \caption[AGB net solar IMF yields]{For each AGB yield set, our calculation of the effective SFH- and IMF-weighted C AGB yield, along with the multiplicative factor to reach an AGB contribution of 20.}
 	\label{tab:alpha_agb}
 	\begin{tabular}{lcr} % four columns, alignment for each
-		\hline 
+		\toprule 
 		AGB Model & $y_{\rm C, 0}^{\rm AGB}$ & $\alpha_{\rm AGB, 20}$\\
-        \hline
-        \hline
+        \midrule
 		C11 & 0.000347 & 2.9\\
@@
 		K16 & 0.000421 & 2.4\\
-		\hline
+		\bottomrule
 	\end{tabular}
@@
 
-I do note that this analysis fails to take into account selection effects and biases in APOGEE, and a more robust determination of the carbon yield.
+I do note that this analysis fails to take into account selection effects and biases in APOGEE, and a more robust determination of the C yield.
 
 This formulation is degenerate in $\varpi$ until I estimate a better AGB fraction.
-As the seperation between the low and high alpha sequences can be used to estimate the delayed time contribution to carbon, using the model to estimate this value relies heavaly on the details of the SFH in addition to the
+As the seperation between the low and high alpha sequences can be used to estimate the delayed time contribution to C, using the model to estimate this value relies heavaly on the details of the SFH in addition to the
 I do give an estimate of the CCSNe yields, however this is dependent on our choice of $\eta$.
-Other choices of $\eta$ vary the value significantly in both magnitude and slope (as AGB contributions increase, I need less CCSNe carbon, however the CCSNe carbon must have a higher metallicity dependence to replicate the V21 data).
+Other choices of $\eta$ vary the value significantly in both magnitude and slope (as AGB contributions increase, I need less CCSNe C, however the CCSNe C must have a higher metallicity dependence to replicate the V21 data).
 
@@
 For the rest of this paper, I focus on multizone models, which discretize the Galaxy into concentric annuli and allow stare to move between rings.
-Specifically, I make use of the \citet{james+21} (hereaafter \JJ) model for the Milky Way, which runs using the publicaly available Versatile Integrator for Chemical Evolution (\VICE\footnote{\VICE~is available at \url{https://github.com/giganano/VICE}}).
+Specifically, I make use of the \citet{james+21} (hereaafter \JJ) model for the Milky Way, which runs using the publicaly available Versatile Integrator for Chemical Evolution (\VICE).
 This model is described extensively in \JJ~and consicely summarized  in \citet{james+22}.
@@
 I use data from APOGEE DR17 \citep{apogee17} processed with APOSCAP.
-Since subgiant stars have yet to experience FDU, their atmospheric carbon and nitrogen abundances are still reflective of their birth abundances and do not need mixing corrections.
+Since subgiant stars have yet to experience FDU, their atmospheric C and N abundances are still reflective of their birth abundances and do not need mixing corrections.
 
@@
 
-\section{The Evolution of carbon across the galaxy and through time}
+\section{The Evolution of C across the galaxy and through time}
 
@@
 
-The GCE of carbon is complicated by metallicity dependencies and delayed contributions.
+The GCE of C is complicated by metallicity dependencies and delayed contributions.
 
@@
 \begin{enumerate}
-    \item Carbon comes predominantly ($\sim80\%$) from CCSNe but the rest is from AGB stars
-    \item The CCSNe carbon production is more efficient at higher metallicities
-    \item AGB stars produce less carbon at higher metallicities.
+    \item C comes predominantly ($\sim80\%$) from CCSNe but the rest is from AGB stars
+    \item The CCSNe C production is more efficient at higher metallicities
+    \item AGB stars produce less C at higher metallicities.
 \end{enumerate}
@@
     \item Initially, CCSNe dominate production before AGB stars can contribute their enrichment, but because CCSNe is highly metalliticy dependent, the C/$\alpha$ ratio increases with time.
-    \item AGB stars begin contributing their carbon, increasing the $C/\alpha$ ratio more steeply as the gas begins to reach its equilibrium metallicity
-    \item When $Z$ reaches equilibrium, the $C/\alpha$ ratio stops increasing or may even decline, as AGB stars formed at higher metallicities reduce the net carbon yields.
+    \item AGB stars begin contributing their C, increasing the $C/\alpha$ ratio more steeply as the gas begins to reach its equilibrium metallicity
+    \item When $Z$ reaches equilibrium, the $C/\alpha$ ratio stops increasing or may even decline, as AGB stars formed at higher metallicities reduce the net C yields.
 \end{enumerate}
@@
 \ref{fig:c_evo} for \caah and \caafe for our fiducial model.
-Comparing [C/$\alpha$] against [Fe/H] enables us to see late time evolution of carbon more clearly.
+Comparing [C/$\alpha$] against [Fe/H] enables us to see late time evolution of C more clearly.
 Because [Fe/H] takes longer to reach equilibrium as half of iron production comes from type-Ia supernovae, the late time evolution is not clustered as tightly horizontally as for [$\alpha$/H].
@@
 \includegraphics{evo_slices.pdf}
-\caption[Carbon chemical evolution tracks]{
-    Time evolution of gas phase carbon abundances in our fiducial model.
+\caption[C chemical evolution tracks]{
+    Time evolution of gas phase C abundances in our fiducial model.
 
@@
 As the highest AGB yield at solar is from our \karakas~model at $Y_{\rm C}^{\rm
-agb} = 0.000585$ is only 11.7 percent of our required total carbon production,
-each of these models is dominated by CC production of carbon. As a result,
+agb} = 0.000585$ is only 11.7 percent of our required total C production,
+each of these models is dominated by CC production of C. As a result,
 while the metallicity dependence of the \caah may vary, the
@@
 the AGB model and delay-time-distribution unchange the galaxy production of
-carbon.
+C.
 
@@
 
-Our next exploration is to adjust the relative fraction of AGB star yields. To do this, I hold the total carbon yield at solar metallicity fixed, so for a desired AGB fraction (assuming equilibrium),
+Our next exploration is to adjust the relative fraction of AGB star yields. To do this, I hold the total C yield at solar metallicity fixed, so for a desired AGB fraction (assuming equilibrium),
 
@@
 
-The next question is how does changing the CCSNe carbon yield affect the model?
+The next question is how does changing the CCSNe C yield affect the model?
 I now consider variations of our fiducial mode/
@@
 
-Carbon as an equilibrium phenominon. See section \ref{sec:equilibrium} Importantly, the \caafe trend is mostly unaffected by choosing a different
+C as an equilibrium phenominon. See section \ref{sec:equilibrium} Importantly, the \caafe trend is mostly unaffected by choosing a different
 CCSNe yield. As all CCSNe enrichment happens at the same, rapid timescale, by
@@
 
-So, the scaling of the trend and metallicity dependence of carbon (as seen in
-the \caah~trend) gives information on the total carbon yield and the behavior
-of CCSNe (as the dominating producer of carbon);
-the \caafe trend exposes the delayed effect of carbon from AGB contribution.
+So, the scaling of the trend and metallicity dependence of C (as seen in
+the \caah~trend) gives information on the total C yield and the behavior
+of CCSNe (as the dominating producer of C);
+the \caafe trend exposes the delayed effect of C from AGB contribution.
 
@@
 
-Increasing the relative AGB production lowers the magnitude of  $y_\text{C}^\text{CC}/y_\text{O}^\text{CC}$, but the metallicity dependence of the ratio must increase to compensate for the inverse metallicity dependence of AGB carbon yields.
-
-These models are indistinguishable in the \caah~plane from our adjusted CCSNe model, so future work investigating the SFH and carbon isotopic ratios in more depth may be able to provide more insight.
+Increasing the relative AGB production lowers the magnitude of  $y_\text{C}^\text{CC}/y_\text{O}^\text{CC}$, but the metallicity dependence of the ratio must increase to compensate for the inverse metallicity dependence of AGB C yields.
+
+These models are indistinguishable in the \caah~plane from our adjusted CCSNe model, so future work investigating the SFH and C isotopic ratios in more depth may be able to provide more insight.
 In the next section, I develop the analytic tools to explore this problem in more depth.
@@
 
-The effect of reducing outflows is then increasing the relative contributions of non-CCSNe processes. For carbon, this increases the AGB fraction.
+The effect of reducing outflows is then increasing the relative contributions of non-CCSNe processes. For C, this increases the AGB fraction.
 
@@
 [O/Fe] is a tracer of the relative contributions of CCSNe and delayed-time sources in chemical evolution.
-So, the appearance of a slope in [O/Fe] implies that there is a substantial delay-time process in carbon evolution.
-The metallicity-dependence of carbon yields complicates this picture because
+So, the appearance of a slope in [O/Fe] implies that there is a substantial delay-time process in C evolution.
+The metallicity-dependence of C yields complicates this picture because
 younger stars have higher [O/Fe] as the SNeIa contributions take up to 10Gyr,
 so metal-poor young stars will naturally have lower [C/O], agreeing with the
-slope observed in\caafe. However, a pure CCSNe carbon model cannot reproduce the slope accurately as
+slope observed in\caafe. However, a pure CCSNe C model cannot reproduce the slope accurately as
 
@@
 
-\section{Comparison to Observations}
+\section{Comparison to Observations}\label{sec:gas}
 
@@
 
-Carbon measurments in stars are difficult. There are measurments which can however be used to test.
+C measurments in stars are difficult. There are measurments which can however be used to test.
 
@@
 
-Beyond Milky Way stars, astronomers have observed carbon to oxygen ratios in
+Beyond Milky Way stars, astronomers have observed C to O ratios in
 HII-regions through either Recombination Lines or (OTHER TEchnique0), enabling
-us to probe gas-phase abundances of carbon in our galaxy and other types of
+us to probe gas-phase abundances of C in our galaxy and other types of
 galaxies from dwarf to elliptical.
@@
 
-Measuring carbon in the gas phase is challenging. Carbon emission lines are
+Measuring C in the gas phase is challenging. C emission lines are
 very weak compared to other common lines, (visible/etc.).
@@
 evolution is extremely limited. (despite a pure H/He born star appearing
-simpler lolol). A variety of explanation for the increasing relative carbon
+simpler lolol). A variety of explanation for the increasing relative C
 enrichments for metal-poor stars have been proposed (e.g. ...). The likely case
-that Population III star supernovae produced high abundances of carbon seems
-most plausable, especially given our uncertainty in the carbon yields and the
+that Population III star supernovae produced high abundances of C seems
+most plausable, especially given our uncertainty in the C yields and the
 short timescales required to create this enhancement (e.g. $z\sim 2$ DLA,
@@
 As any constraints in this regieme are poor, I choose to only qualitatively
-conclude that CCSNe carbon production increases at extremely low metallicity
+conclude that CCSNe C production increases at extremely low metallicity
 but the details of this remains an open question.
@@
 \includegraphics[]{summary.pdf}
-\caption[Gas phase abundances]{Gas-phase carbon abundances. We plot our model at $t=2$Gyr and present day as thick solid lines. Points represent measurments in 
+\caption[Gas phase abundances]{Gas-phase C abundances. We plot our model at $t=2$Gyr and present day as thick solid lines. Points represent measurments in 
     HII regions    \citep[pink circles;][]{skillman+20, esteban+02, esteban+09, esteban+14, esteban+19}
@@
 
-In this work, I investigate the role of carbon yields on the predictions of multizone GCE models.
-\citet{james+22} performed a similar analysis, except focusing on nitrogen.
-\citet{james+22} found, to match APOGEE/\citet{fiorenzo+21}'s observations, nitrogen yields ratios relative to oxygen needed to be about triple what AGB models suggested.
-
-Here, I perform a similar analysis on carbon.
-I summarize the current theoretical nucleosynthetic predictions of carbon.
-Because CCSNe carbon yields are poorly understood, I adopt an equilibrium approximation and determine that a functional form of $\Ycc/\Yoc=1.51 + 0.54 (Z/Z_\odot)$ approximately matches trends in APOGEE subgiants.
+In this work, I investigate the role of C yields on the predictions of multizone GCE models.
+\citet{james+22} performed a similar analysis, except focusing on N.
+\citet{james+22} found, to match APOGEE/\citet{fiorenzo+21}'s observations, N yields ratios relative to O needed to be about triple what AGB models suggested.
+
+Here, I perform a similar analysis on C.
+I summarize the current theoretical nucleosynthetic predictions of C.
+Because CCSNe C yields are poorly understood, I adopt an equilibrium approximation and determine that a functional form of $\Ycc/\Yoc=1.51 + 0.54 (Z/Z_\odot)$ approximately matches trends in APOGEE subgiants.
 Variations of the metallicity dependence of this CCSNe yield affect trends in \caah but do not affect trends in \caafe when taking a slice in [Mg/H].
-As all theoretical AGB carbon yields decrease with increasing metallicity, increasing the AGB fraction causes the \caah trend to flatten.
+As all theoretical AGB C yields decrease with increasing metallicity, increasing the AGB fraction causes the \caah trend to flatten.
 However, the \caafe trend is sensitive to the AGB fraction.
-I estimate that $f_{\rm AGB} = 0.2$ using the C11 yield model. This requires about 3x more AGB carbon production than most nucleosynthetic models predict.
+I estimate that $f_{\rm AGB} = 0.2$ using the C11 yield model. This requires about 3x more AGB C production than most nucleosynthetic models predict.
 
@@
 Finally, I compare my model against gas phase and metal-poor stellar measurments.
-While my model was built on data near solar metallicity, by including heightened carbon production from population III stars, I can create a self consistant picture of carbon evolution.
-
-Observations of Carbon in metal poor stars, extragalactic (call out any
+While my model was built on data near solar metallicity, by including heightened C production from population III stars, I can create a self consistant picture of C evolution.
+
+Observations of C in metal poor stars, extragalactic (call out any
 
@@
 
-These carbon yield constraints provide a test for stellar evolution models.
-Carbon yields are sensitive to mass loss treatment, explodability, nuclear cross sections, convection, and stellar structure.
+These C yield constraints provide a test for stellar evolution models. C yields are sensitive to mass loss treatment, explodability, nuclear cross sections, convection, and stellar structure.
 
@@
 Following \citet{jack_subgiant}, we select subgiants in the orange polygon (see Equation \ref{eq:subgiant_selection}).
-These stars have not yet experienced first dredge-up, so their photospheric carbon and nitrogen abundances should reflect their birth mixture.
+These stars have not yet experienced first dredge-up, so their photospheric C and N abundances should reflect their birth mixture.
     }
@@
 This cut isolates a clean sample of subgiants.
-As First Dredge Up, which affects carbon and nitrogen abundances, only occurs during the ascent onto the red giant branch, subgiant stars are unaffected by this enrichment.
+As First Dredge Up, which affects C and N abundances, only occurs during the ascent onto the red giant branch, subgiant stars are unaffected by this enrichment.
 
@@
 Because the predictions of the AGB yield models I consider are dwarfed by the
-required CCSNe carbon production to match observations (see Fig.
+required CCSNe C production to match observations (see Fig.
 ***), I briefly explore here the effects of variations in AGB models affect abundance trend predictions when these models are amplified to match observational [C/MG]-[Mg/Fe] trends.
@@
 This causes a reversal of the [C/Mg]-[Mg/Fe] trend at high [Mg/H] slices (figure ...).
-As our set of observations do not appear to reverse, this indicates that carbon yields likely stay positive even at slightly super-solar, so models like V13 are a poor match to observations.
+As our set of observations do not appear to reverse, this indicates that C yields likely stay positive even at slightly super-solar, so models like V13 are a poor match to observations.
 Plot of age metallicity relationship?
@@
     \includegraphics{y_mg.pdf}
-    \caption[Magnesium CCSNe yields]{Same as the top panel of Figure \ref{fig:y_cc}, but for magnesium. Our magnesium yield choice is shown as a dashed line at the top
+    \caption[Magnesium CCSNe yields]{Same as the top panel of Figure \ref{fig:y_cc}, but for Mg. Our Mg yield choice is shown as a dashed line at the top
     }

### 2023-04-10 thesis/tex/main.tex
more thesis edits

@@
        \textbf{The Galactic Chemical Evolution of Carbon} \\
+       Implications for Stellar Nucleosynthesis\\
        \vspace*{3\baselineskip}
@@
 Why study C?
-C is unique nucleosynthetically, one of few light elements (along with N) produced in Asymptotic Giant Branch (AGB) stars \citep[e.g.][]{jennifer19, KL14}.
-C and N are well studied elements as they are easy to observe in stellar spectra, even at the lowest metallicities \citep{FN15} SOMETHING ELSE?.
+C is unique nucleosynthetically, one of few light elements (along with N) produced in asymptotic giant branch (AGB) stars \citep[e.g.][]{jennifer19, KL14}.
+C and N are well studied elements as they are easy to observe in stellar spectra, even at the lowest metallicities \citep{FN15}(?).
 Additionally, C and N are used as age indicators in red giant branch stars \citep[e.g.][]{martig16, MG15, fiorenzo+21}.
-While we know C is produced in AGB stars and core collapse supernovae (CCSNe), we still have limited understanding of the importaince and metallicity-dependence of each process.
-
-Empirically, gas-phase [C/O] ratios decrease with increasing [O/H] at the lowest metallicitis---in high redshift damped Lyman-alpha systems (DLAs)---and then [C/O] increases above $\rm [O/H] \approx 1$ (\citealt{berg+19,cooke+17}; see discussion in SECTION).
-
-\cite{james+22} examend GCE models of N, an elements whose production is closely related to C.
-\cite{james+22} found trends in N and O abundances can be explained by the metallicity dependence of relatice N and O yields.
+
+Gas-phase [C/O] ratios---observed in very low metallicity, high redshift damped Lyman-alpha systems (DLAs)---decrease with increasing [O/H] \citep{cooke+17}.
+Then, [C/O] increases above $\rm [O/H] \approx 1$ (\citealt{berg+19,nissen+14,fabbian+09}; see discussion in \S\ref{sec:gas}).
+While we know C is produced in AGB stars and core collapse supernovae (CCSNe), we still have limited understanding of the magnitude and metallicity-dependence of each process.
+
+Despite their central role in GCE models, nucleosynthetic yields predicted by stellar evolution models are rife with uncertainties.
+Poorly understood processes, including mass loss, opacity, nuclear reaction rates, rotational mixing, and convection/convective boundaries each shape the production rates of atomic nuclei in stellar interios \citep{KL14,ventura+13, LC18}.
+Additionally, changes in massive star's explodability can introduce a factor of $\sim2$ change in population averaged-yields \citep{emily+21}.
+
+GCE models typically use unmodified nucleosythetic predictions and attempt to create models matching observations by varying the star formation history (SFH) and other evolutionary parameters.
+I choose to introduce C yields as a free parameter, determining which yield prescriptions reproduce Galactic abundance trends.
+\cite{james+22} examined similar GCE models of N, an elements whose production is closely related to C.
+\cite{james+22} found trends in N and O abundances can be explained by the metallicity dependence of relative N and O yields.
 Here, I extend their models to C and show that similar constraints on C and O relative yields can be obtained from observed abundance ratios.
-
-We also know that there is evidence for non-monatonic C yield patterns. 
-pattern where C is more readily produced by both high metallicity and very low metallicity stars (CEMPS, early GCE results), but our picture. \citep{FN15,cooke+17,berg+19}.
-
-Despite their centrol role in GCE models, nucleosynthetic yields predicted by stellar evolution models are rife with uncertainties.
-Poorly understood processes, including mass loss, opacity, nuclear reaction rates, rotational mixing, and convection/convective boundaries each shape the production rates of atomic nuclei in stellar interios \citep{KL14,V13, LC18, emily+21}.
-Additionally, changes in massive star's explodabinitily can introduce a factor of \~2 change in population averaged-yields \citep{emily+21}.
-
-Stellar evolution models predict stellary yields, playing a crucial role in GCE.
-However, these models are rife with uncertainties, limited by our understanding of critical physical processes such as nuclear reaction rates, convection, rotational mixing, opacity, and mass loss CITATIONS.
-Changes in opacity, rotation, reaction rates, and explodability can substantially affect C yields
-
-GCE models typically use unmodified nucleosythetic predictions and attempt to create models matching observaions by varying star formation history and other parameters.
-I instead use the observations as a constraint, determining which yield assuptions are consistant with galactic abundance trends.
-
-While there are many stellar measurments of C, accurately determining the birth abundance is more challenging.
-For example, when a star becomes a RGB star, material from the CNO-processed core is mixed with the envelope in First Dredge Up (FDU) \citep{fiorenzo+21,KL14}.
-Since this core-processed material is now C depleted and N enhanced, measurments of this star's atmosphere will no longer reflect the birth abundances of the star.
-Additionaly, C is faint in HII regions and determining gas-phase abundances is challenging \citet{skillman+20}.
-Other surveys, such as GALAH, have unreliable C measurments with low detection rates \citep{emily+19}.
-
-AGB stars are known to be importaint (cite) from stellar model predictions, previous GCE, and evidence from abundance patterns. (are there detections in PN?)
-
-CCSne are also important (.... SN reminant measurments)
+Additionally, I assess which yield prescriptions reproduce Galactic abundance trends, while assessing the impact of SFH and GCE model assumptions.
+
+Accurate determination of stellar birth abundances for C and N is challenging.
+When a star enters the red giant branch (RGB), material from the CNO-processed core is mixed with the envelope in first dredge up (FDU), enhancing N and depleting C \citep{fiorenzo+21,KL14}.
+Measurements of these evolved stars'  atmospheres will no longer reflect birth abundances.
+Additionally, C is faint in HII regions and determining gas-phase abundances is challenging \citep{skillman+20}.
 
 To this end, I use a sample of subgiant stars from APOGEE \citep{apogee17}.
-According to stellar evolution models (CITES), these stars have not yet experienced dredge-up.
-Their photospheric abundances should thus represent their birth composition.
+According to stellar evolution models (CITES), these stars have not yet experienced FDU.
+Their phosphoric abundances should thus represent their birth composition.
 In Fig.
 \ref{fig:subgiants}, I plot this sample, selected by criteria in \citet[see Appendix \ref{sec:jack}]{jack_subgiant}.
-These emperical resolults contain information on the relative C and O yields, which I use later in this work.
+These emperical resolults contain information on the relative C and Mg yields, which I use later in this work.
 
@@
 Theoretical models of stellar nucleosynthesis provide the starting point of this investigation.
-I focus on three primary nucleosynthetic pathways: Asymptotic Giant Branch (AGB) stars, Core Collapse Supernovae (CCSNe), and Type Ia Supernovae (SNe Ia).
-Each process has unique timescales and yields, tracable through the tools of GCE.
+I focus on three primary nucleosynthetic pathways: Asymptotic giant branch (AGB) stars, core collapse supernovae (CCSNe), and type Ia supernovae (SNe Ia).
+Each process has unique timescales and yields, traceable through the tools of GCE.
 While C is only produced in AGB stars and CCSNe, comparing C to Fe, which is produced in SNe Ia, adds a valuable constraint on the delay-time distribution (DTD) of C enrichment.
 
-When a Single Stellar Population (SSP) forms, CCSNe are the first enrichment events.
+When a single stellar population (SSP) forms, CCSNe are the first enrichment events.
 CCSNe provide light elements such as C, O, and Mg and heavier elements such as Fe and beyond.
-Metallicity-independent yields from CCSNe are the only statisticly significant source of O and Mg ($\alpha$ elements).
+Metallicity-independent yields from CCSNe are the only statistically significant source of O and Mg ($\alpha$ elements).
 Next, low mass stars begin to reach the end of their lives.
-The dying breaths of AGB stars are known to be importaint sources of C, N, and neutron capture elements.
+The dying breaths of AGB stars are known to be important sources of C, N, and neutron capture elements.
 Finally, white dwarfs explode, releasing Fe and other iron-peak elements.
 
-Stellar measurments of Mg are more reliable, but O abundances are easier to measure in HII regions. 
-I therefore use Mg abundances from the \citet{jack_subgiant} subgiant sample as my primary emperical constraint.
-However, I use O abundances for gas-sphase measurments and low-metallicity stars (\S \ref{sec:gas}).
-I model both Mg and O as metallicity-independent population-averaged yields dominated by massive stars.
-${\rm [O/Mg]}\approx 0$ across a wide range of metallicities in APOGEE \citep{Weinberg+19, Weinberg+22}.
-I adopt O and Mg relative yields given by the solar mixture of \cite{asplund+09} <MATH>.
-
-To calculate the IMF-weighted\footnote{IMF: Initial Mass Function} net yields of C, I use the Versatile Integrator for Chemical Evolution code (\VICE\footnote{\VICE~is available at \url{https://github.com/giganano/VICE}}).
-As stellar evolution models predict per-star yields of a given mass, I need to integrate over the IMF to determine the total yields in terms of star formation.
+For an element X and star with mass $M$, the stellar yield $\tilde{y}$ is defined as the net production of X relative to $M$, or
+\begin{equation}
+    \tilde{y}_{\rm X} = \frac{M_{\rm X,\ ejected} - Z_{0, X} M_{\rm ejected}}{M}   
+\end{equation}
+where $M_{\rm ejected}$ and $M_{\rm X, ejected}$  are the total ejected mass of the envelope and the element X, respectively.
+
+Though per-star yields are necessary to compute AGB star enrichment rates in GCE models, IMF-averaged\footnote{IMF: Initial Mass Function} yields are useful in interpreting their predictions.
+For a yield $y$ from a star of mass M and initial metallicity $Z$, the IMF-averaged yield is given by
+\begin{equation} \label{eq:imf-yield}
+    y_{\rm X}^{\rm proc}(Z) = 
+    \int_{M_{\rm min}}^{M_{\rm max}} 
+    \tilde{y}_{\rm X}^{\rm proc}(M, Z)
+    \frac{dN}{dM}  \ dM
+\end{equation}
+where ${dN}/{dM}$ is the normalized IMF, $M_{\rm min}$ and $M_{\rm max}$ are the minimum and maximum mass of stars, which I take to be $0.08 M_{\sun}$ and $100 M_{\sun}$ respectively.
+For AGB stars, the yields are truncated above 8 $M_{\odot}$.
+To calculate the IMF-weighted net yields of C, I use the Versatile Integrator for Chemical Evolution code (\VICE\footnote{\VICE~is available at \url{https://github.com/giganano/VICE}}).
 
@@
 In Table \ref{tab:fiducial_mod}, I tabulate yield values, in units of a stellar population's birth mass.
-Also following \citet{james+21, james+22}, I take the SNeIa Delay Time distribution to be a
+Also following \citet{james+21, james+22}, I take the SNeIa delay time distribution to be a
 $t^{-1.1}$ law suggested by the observations of \citet{maoz+12}.
@@
 An AGB star is a low mass ($\lesssim 8 M_{\sun}$) star during its final phase of evolution.
-In an AGB star, two competing processes determine the outcome of C production: Third Drege Up (TDU) and Hot Bottom Burning (HBB).
-DU accompianies thermal puslations in AGB stars.
-Durring a TDU event, material from the CO core is mixed with material exposed to partial He-shell burning, increasing C and O abundances in the envelope \citep{KL14}.
+In an AGB star, two competing processes determine the outcome of C production: third dredge up (TDU) and hot bottom burning (HBB).
+TDU accompanies thermal pulsations in AGB stars.
+During a TDU event, material from the CO core is mixed with material exposed to partial He-shell burning, increasing C and O abundances in the envelope \citep{KL14}.
 HBB is the activation of proton capture reactions, and the CNO cycle%
@@
 \begin{itemize}
-    \item C11: \citet{cristallo+11} and \citet{cristallo+15}
+    \item C11: \citet{cristallo+11, cristallo+15}
     \item K10: \citet{karakas10}
-    \item V13: \citet{ventura+13}
+    \item V13: \citet{ventura+13,ventura+14,ventura+18}
     \item K16: \citet{KL16} \citet{karakas+18}
@@
 I use C11 as the fiducial AGB yield.
-For an element X and star with mass $M$, the stellar yield $\tilde{y}$ is defined as the net production of X relative to $M$, or
-\begin{equation}
-    \tilde{y}_{\rm X} = \frac{M_{\rm X,\ ejected} - Z_{0, X} M_{\rm ejected}}{M}   
-\end{equation}
-where $M_{\rm ejected}$ and $M_{\rm X, ejected}$  are the total ejected mass of the envelope and the element X, respectively.
 
 Fig. \ref{fig:y_agb} compares the AGB C yield $\tilde{y}_\text{C}^\text{AGB}(M, Z)$ for each model I consider. 
-The yields may be negative when the birth abundance is higher than the C abundance of the material ejected back to the ISM. 
+The yields may be negative when the birth abundance is higher than the C abundance of the material ejected back to the interstellar medium (ISM). 
 Most models agree on the qualitative shape of the net fractional AGB C yield---% 
@@
 In Fig. \ref{fig:agb-ssp}, we plot the total production of C by AGB stars as a function of SSP age.
-Effectively, this is equivalent to integrating Eq. \ref{eq:imf-yield} down to $M_{to}$, the turnoff mass for time $t$. 
+Effectively, this is equivalent to integrating Eq. \ref{eq:imf-yield} down to $M_{to}$, the turnoff mass for time $t$%
 \footnote{In our model, the mass-lifetime relation is
@@
 where $\tau_M$ is in Gyr,
-from \citet{larson74}.}
+from \citet{larson74}.}.
 As the mass range $2\lesssim M \lesssim 4$ is most important for C production, the characteristic delay time is $\sim 1$Gyr.
@@
 
-K10 and K16 weight C production more heavily towards massive stars resulting in a faster enrichment delay time, whereas the C11 and V13 models predict a slightly longer timescale with order 1Gyr, but little to no C is produced more than 2Gyr after a star formation event.
-This is in contrast to iron which is still produced by SNeIa up to 10Gyr after a star formation event.
+K10 and K16 weight C production more heavily towards massive stars resulting in a faster enrichment delay time, whereas the C11 and V13 models predict a slightly longer timescale with order 1 Gyr, but little to no C is produced more than 2 Gyr after a star formation event.
+This is in contrast to iron which is still produced by SNeIa up to 10 Gyr after a star formation event.
 As shown in the right panel of Fig. \ref{fig:agb-ssp}, with increasing $Z$, C enrichment occurs earlier, and C destruction in low mass stars leads to a declining C abundance at late times.
@@
 I plot $\tilde{y}=0$ for reference.
-Each panel represents yields from one of four AGB models: C11 \citep{cristallo+11, cristallo+15}, K10 \citep{karakas10}, V13 \citep{ventura+13,ventura+14,ventura+18}, and K16 \citep{KL16, karakas+18}.
+Each panel represents yields from one of four AGB models: C11, K10, V13, K16 (see \S \ref{sec:agb}).
 }
@@
 
-Though per-star yieldds are necessary to compute AGB star enrichment rates in GCE models, IMF-averaged yields are useful in interpreting their predictions.
-For a yield $y$ from a star of mass M and initial metallicity $Z$, the IMF-averaged yield is given by
-More useful for GCE are Initial Mass Function (IMF) yields, where I sum up the
-contributions of all stars which produce an element.
-I define the IMF-integrated yield of X with:
-
-\begin{equation} \label{eq:imf-yield}
-    y_{\rm X}^{\rm proc}(Z) = 
-    \int_{M_{\rm min}}^{M_{\rm max}} 
-    \tilde{y}_{\rm X}^{\rm proc}(M, Z)
-    \frac{dN}{dM}  \ dM
-\end{equation}
-
-where $\frac{dN}{dM}$ is the normalized IMF, $M_{\rm min}$ and $M_{\rm max}$ are the minimum and maximum mass of stars, which I take to be $0.08 M_{\sun}$ and $100 M_{\sun}$ respectively.
-For AGB stars, the yields are truncated above 8 $M_{\odot}$.
-
 In Fig. \ref{fig:yagb-z}, I plot the IMF-averaged C yields for each AGB model as a function of metallicity $Z$.
@@
 
-In Fig.
-\ref{fig:y_cc}, I plot calculations of the IMF-integrated yields, using Eq.
-\ref{eq:imf-yield} (computed using \VICE's \texttt{vice.yields.ccsne.fractional} function).
-On the right, I also show the CCSNe-[C/Mg] ratio, defined by
+In Fig. \ref{fig:y_cc}, I plot calculations of the IMF-integrated yields, using Eq. \ref{eq:imf-yield} (computed using \VICE's \texttt{vice.yields.ccsne.fractional} function). 
+CCSNe models predict a wide range of C yields, spanning almost 1 dex. 
+Both the \citet{NKT13} and \cite{LC18} models show positive metallicity dependence. 
+The \cite{LC18} models also include rotation, showing that variations in the rotational velocity of the star can dramatically increase C production and the metallicity dependence of $\Ycc$.
+Rotation induces more mixing allowing the CO core to grow larger.
+Our fiducial model's steep metallicity dependence near $Z\approx Z_\odot$ could be explained by rotation.
+
+I show the C11 model for comparison in Fig.
+\ref{fig:y_cc}.
+Especially at $Z\approx Z_\odot$, most CCSNe models would dominate C production.
+I will later show that empirically, CCSNe also dominate C production.
+
+On the bottom of Fig. \ref{fig:y_cc}, I also show the CCSNe-[C/Mg] ratio, defined by
 \begin{equation}\label{eq:c_mg_cc}
@@
 In other words, ${\rm [C/Mg]^{CC}}$ describes what [C/Mg] would be if CCSNe were the only process producing C.
-Notice that even at $Z=Z_\odot$, there is a wide range ($\sim 1$ dex) in predicted $\Ycc$.
-
-    \begin{itemize}
-        \item Massive stars should dominate C yields, GCE models indicate similar results \citep[e.g.][]{prantzos+18,rybizki+17}.  
-        \item Rotation in LC18 appears to increase metallicity dependence of C production (read this paper more carefully)
-        \item NKT and LC (with rotation)agree in positive metallicity depenent yields
-        \item [C/Mg]
-        \item The fiducial value, where I choose the C yield from Sukhbold+16, may be above most predictions of C yields but is within the range of yield ratios
-        \item the fiducial value would reach an equilibrium C yield of -0.1 without AGB stars
-    \end{itemize}
+Once again, different CCSNe models span a large range in [C/Mg]. 
+I chose to instead parameterize $\Ycc$ to enable agreement with observations, as most CCSNe models fail to achieve near-solar [C/Mg].
+
+Assumptions about the explodability landscape affect C and Mg production.
+Increasing the fraction of stars which explode increases $\Ycc$, as stars which directly collapse do not contribute to explosive yields \citep{emily+21}.
+However, C is relatively unaffected by the black-hole landscape, as very massive stars contribute carbon through enriched winds.
+Since Mg is formed deeper in the core of massive stars, the Mg yield drops much more steeply, so models where few stars explode (S16/W18) result in much higher [C/Mg].
+
+CCSNe models also struggle to reach solar [O/Mg], either due to overproduction of O or underproduction of Mg \citep{emily+21}.
+Here, I assume ${\rm [O/Mg]} = 1$, which is not compatible with CCSNe models but is consistent with observations \cite{Weinberg+19, Weinberg+22}.
 
@@
 where the first term on the right-hand side describes CCSNe enrichment. 
-In terms of the return mass fraction of stars $r$, the mass lost to remnants is $Z_X (1-r)\dot{M}_\star$.  And, the outflows deplete a mass $Z_X \eta\dot{M}_\star$. Substituting, 
+In terms of the return mass fraction of stars $r$, the mass lost to remnants is $Z_X (1-r)\dot{M}_\star$.
+And, the outflows deplete a mass $Z_X \eta\dot{M}_\star$.
+Substituting om fpr $\eta$ and $r$,
 \begin{equation}
@@
 \end{equation}
-Assuming an exponentially declining star formation history, $\dot{M}_\star \propto e^{-t/\tau_{\rm sfh}}$, this equation can be solved analytically. 
-To find equilibrium, set $\dot{M}_X=0$, and now
+Assuming an exponentially declining star formation history $\dot{M}_\star \propto e^{-t/\tau_{\rm sfh}}$, the equilivrium abundance is derived analytically by setting $\dot{Z}_{Mg}=0$.
 \begin{equation}\label{eq:z_eq}
@@
 \end{equation}
-For constant star formation, $\tau_\star/\tau_{\rm sfh} \rightarrow 0$
-
-While Equation \ref{eq:z_eq} can be applied to CCSNe C, the delayed time contribution of AGB C can complicate the result. Instead, using an effective or DTD-integrated yield, $\langle \Ycagb \rangle$
+In the special case of constant star formation, $\tau_{\rm sfh}\to\infty$, simplifying the denominator to $1+\eta-r$.
+
+While Equation \ref{eq:z_eq} can be applied to CCSNe C, the delayed nature of AGB C can complicates thes expression. Instead, using a DTD-integrated yield, $\langle \Ycagb \rangle$ enrichment is
 \begin{equation}
@@
 \end{equation}
-So, for C, Equation \ref{eq:z_eq} becomes
+Eq. \ref{eq:z_eq} becomes
 \begin{equation}
@@
 \begin{equation}\label{eq:z_co}
-    \frac{Z_{\rm C}^{\rm eq}}{Z_{\rm Mg}^{\rm eq}} = \frac{\Ycc + \langle \Ycagb \rangle }{\Yoc}
-\end{equation}
-
-With these definitions, I can calculate the core collapse yields of C as a function of metallicity:
+    \frac{Z_{\rm C}^{\rm eq}}{Z_{\rm Mg}^{\rm eq}} = \frac{\Ycc + \langle \Ycagb \rangle }{\Yoc}.
+\end{equation}
+
+Analogous to \cite{james+22} arguments about N, the trends in abundance ratios are set by yield ratios in these GCE models.
+The effect of other GCE parameters (most importaintly $\eta$) cancels.
+As a consequence, yield ratios should establish abundance ratio trends in models which assume a different normalization of element yields and mass-loading (see discussion below).
+This argument can also be inverted to infer  yields from abundance ratio trends.
+To the extent that observed C and Mg trends reflect the equilibrium abundances in different Galatic regions, we can infer the CCSNe (is this plural><?) yield given an assumed AGB star yield (or vice versa).
+Inffering $\Ycc$ from $\Ycagb$,
 \begin{equation}
@@
 \end{equation}
-
-Rewriting in terms of the observed abundance ratio and dividing by
-$y_\text{Mg}^\text{CC}$. So, given the outflows or CCSNe O yields, the
-C AGB yield, and the \caah mean abundance track, I can estimate the CCSNe C yield. Written as a relative yield:
-\begin{equation}
-    \frac{\Ycc}{\Yoc} = \frac{Z_{\text{C},~\sun}}{Z_{\text{Mg},~\sun}} 10^{[C/Mg]} - \frac{\langle \Ycagb \rangle}{\Yoc}
-\end{equation}
-
-Fitting this relationship to data (figure \ref{fig:analytic}).
-
-\begin{figure}
-    \centering
-    \includegraphics[]{analytic.pdf}
-    \caption[Reverse fit yields]{Inferred massive star C yields as a function of metallicity.
-I assume equilibrium and $3\times {\rm C11}$ AGB yields (orange curve, see discussion in Section \ref{sec:equilibrium}).
-The binned medians and median absolute devation (divided by $\sqrt{N}$) are blue points.
-    }
-\end{figure}
+Rewriting this expression as a relative yield of C and Mg,
+\begin{equation}
+    \frac{\Ycc}{\Yoc} = \frac{Z_{\text{C},~\odot}}{Z_{\text{Mg},~\odot}} 10^{\rm [C/Mg]} - \frac{\langle \Ycagb \rangle}{\Yoc}.
+\end{equation}
 
 \section{Yield Models}
+
+If $\Ycc$ gets us to ${\rm [C/Mg] } \approx -1$, then $\Yct = 0.005$, but if 0, $y\approx0.006$. 
+Section 2.2, additional AGB yield 1part per thousand?, Motivate AGB yield ...
 
@@
 So, I introduce a process factor, $\alpha_{\rm AGB}$, which represents the multiplicative increase in $\Ycagb$ from the published yields.
-\begin{equation}
-    \Ycagb \rightarrow \alpha_{\rm agb}  \Ycagb.
-\end{equation}
-
-\begin{equation}
-    \alpha_{\rm agb} = f_{\rm agb} \frac{\Yct}{\Ycagb}
-\end{equation}
-\begin{equation}
-    \alpha_{\rm CC} = (1 - f_{\rm agb}) \frac{\Yct}{\Ycc}
-\end{equation}
+\begin{subequations}
+    \begin{align}
+        \Ycagb \rightarrow &\alpha_{\rm agb}  \Ycagb \\
+        \alpha_{\rm agb} &= &f_{\rm agb} \frac{\Yct}{\Ycagb} \\
+        \alpha_{\rm CC} = &(1 - f_{\rm agb}) \frac{\Yct}{\Ycc}.
+    \end{align}
+\end{subequations}
 
@@
 Fixing the total C yield at solar reduces the number of free parameters and keeps the model reasonably consistant with observations, and enables us to more consistantly explore differen AGB models.
+
+Fitting this relationship to data (figure \ref{fig:analytic}).
+I find that a linear dependence on metallicity,
+
+\begin{equation}
+    \frac{\Ycc}{\Yoc} = y_{\rm}
+\end{equation}
+
+\begin{figure}
+    \centering
+    \includegraphics[]{analytic.pdf}
+    \caption[Reverse fit yields]{Inferred massive star C yields as a function of metallicity.
+I assume equilibrium and $3\times {\rm C11}$ AGB yields (orange curve, see discussion in Section \ref{sec:equilibrium}).
+The binned medians and median absolute devation (divided by $\sqrt{N}$) are blue points.
+    }
+    \label{fig:analytic}
+\end{figure}
 
@@
 
-This formulation is degenerate in $\varpi$ until I estimate a better AGB fraction.
+This formulation is degenerate in $\alpha_{\rm CC}$ until I estimate a better AGB fraction.
 As the seperation between the low and high alpha sequences can be used to estimate the delayed time contribution to C, using the model to estimate this value relies heavaly on the details of the SFH in addition to the
@@
 \JJ~derives $\tau_{\rm sfh}(R)$ through analysis of four integral field spectroscopy surveys in \cite{sanches20}.
+The star formation history is normalized such that the total stellar mass reaches $M_\star=5.17\times10^{10} {\rm M}_\odot$ \citep{LM15} and at each $R$ to match the stellar surface density gradient \citep{BHG16}.
 The gas inflow is calculated to maintain our chosen SFR for each radius and time. The gas-SFR law is based on an extension of a Kennicutt-Schmidt law \citep{kennicutt98}, motivated by 
@@
 \end{equation}
-The star formation history is normalized such that the total stellar mass reaches $M_\star=5.17\times10^{10} {\rm M}_\odot$ \citep{LM15} and at each $R$ to match the stellar surface density gradient \citep{BHG16}.
-$\tau_\star$ also varies with time due to the redshift dependence of $\tau_\star$ in molecular gas observed by \citet{tacconi18}.
-I assume a Kroupa IMF \cite{kroupa01}.
+The scaling of this relationship varies with time due to the redshift dependence of $\tau_\star$ in molecular gas observed by \citet{tacconi18}. I assume a Kroupa IMF \cite{kroupa01}.
 
@@
 This choice of $\eta(R)$ results in a [$\alpha$/H] gradient consistant with Milky Way observations \citep{james+21}.
-
-I could chose to vary the value of $\alpha$; however, the overall scaling of
-yields is unknown so our constraint is really that $Y_{\rm C}/Y_{\rm O} =
-0.dfsjkhld$, based on binning from our data. As discussed in the previous
-section, I chose to leave the total value of the IMF integrated yield fixed,
-and then assert the AGB fraction (next section) and scale the AGB yields from
-literature appropriety. As such,
-
-I explore uniformly scaling yields and outflows in Section REF.
-While I can constrain relative yields, the absolute scaling of yields and outflows is unknown and chemical evolution models are insensitive to this overal scalling \citep[e.g.][]{james_dwarf}.
+I explore models with reduced outflows in \S\ref{sec:outflows}; however, the overall scaling of yields is unknown and this model is insensitive to this normalization.
 
@@
 
-I use data from APOGEE DR17 \citep{apogee17} processed with APOSCAP.
-Since subgiant stars have yet to experience FDU, their atmospheric C and N abundances are still reflective of their birth abundances and do not need mixing corrections.
-
-To select for subgiants, I use the following cut in $\log g$ and $T_{\rm eff}$
-which selects stars at the base of the red giant turnoff (FIGURE and
-\cite{jack_subgiant}). I describe our selection criteria along with a 
-comparison to \citet{fiorenzo+21} in Appendix \ref{sec:jack}.
-
-The inside-out star formation model fails
-Because the star formation history is left in a simple inside-out form, this multizone model does not reproduce the high-$\alpha$ sequence, therefore I make the following cut to the V21 data to remove the high alpha sequence.
-
-\begin{equation}\label{eq:high_alpha}
-\begin{cases}
-\text{[Mg/Fe]} >0.12-0.13\text{[Fe/H]}, & \text{[Fe/H]}<0\\
-\text{[Mg/Fe]} >0.12, & \text{[Fe/H]}>0\\
-\end{cases}
-\end{equation}
+\citet{james+22} compare their model against the \cite{fiorenzo+21} sample of APOGEE \citet{apogee17} red giants whose C and N abundance have been corrected for mixing process using MESA stellar evolution models.
+I instead use the \citet{jack_subgiant} sample of APOGEE subgiants.
+Subgiant stars have not undergone FDU, so their atmospheric C and N abundances are still reflective of their birth abundances and do not need mixing corrections.
+I additionally only compare the models to the low-$\alpha$ sequence.
+The selection criteria and differences between the samples are described in Appendix \ref{sec:jack}
 
@@
 In the next sections, I will discuss the choice of parameters and agreement with observations.
-Our fiducial model uses the C11 AGB yield set (see section \ref{sec:agb}).
-I amplify the C11 yields by a factor of 2.9, so that $\Ycagb = 0.2y_{\rm C}$, agb
-
-In this model, I use the following yields:
-
-The GCE of C is complicated by metallicity dependencies and delayed contributions.
-
-Note the following features of our model:
-
-\begin{enumerate}
-    \item C comes predominantly ($\sim80\%$) from CCSNe but the rest is from AGB stars
-    \item The CCSNe C production is more efficient at higher metallicities
-    \item AGB stars produce less C at higher metallicities.
-\end{enumerate}
-
-The combination of these features leads to an evolution that proceeds as follows
-\begin{enumerate}
-    \item Initially, CCSNe dominate production before AGB stars can contribute their enrichment, but because CCSNe is highly metalliticy dependent, the C/$\alpha$ ratio increases with time.
-    \item AGB stars begin contributing their C, increasing the $C/\alpha$ ratio more steeply as the gas begins to reach its equilibrium metallicity
-    \item When $Z$ reaches equilibrium, the $C/\alpha$ ratio stops increasing or may even decline, as AGB stars formed at higher metallicities reduce the net C yields.
-\end{enumerate}
-
-I plot time evolution tracks in Fig.
-\ref{fig:c_evo} for \caah and \caafe for our fiducial model.
-Comparing [C/$\alpha$] against [Fe/H] enables us to see late time evolution of C more clearly.
-Because [Fe/H] takes longer to reach equilibrium as half of iron production comes from type-Ia supernovae, the late time evolution is not clustered as tightly horizontally as for [$\alpha$/H].
-This is even more evident in the lower part of Fig.
+Our fiducial model uses the C11 AGB yield tables (see section \ref{sec:agb}), and I amplify the C11 yields by a factor of 2.9 so that $f_{\rm AGB} = 0.2$
+
+The fiducial model has the following qualitative characteristics of its C yields: (a) C is predominantly produced in CCSNe, (b) CCSNe produce more C at higher metallicities, (c) AGB stars produce less carbon at higher metallicities.
+
+The evolution proceeds as follows.
+
+Initially, CCSNe dominate production.
+As $\Ycc$ has strong metallicity dependence, [C/Mg] increases with time.
+Shortly thereafter, AGB stars contribute delayed C, increasing [C/Mg] even more steeply.
+As Mg begins to reach equilibrium, the [C/Mg] ratio plateaus as C approaches equilibrium.
+Finally, as $\Ycagb$ decreases or even becomes negative with higher metallicity, the [C/Mg] abundance may decline slightly.
+
+I show the time evolution tracks of the fiducial model in Fig.
+\ref{fig:c_evo} for \caah~ and \caafe~.
+Comparing [C/$\alpha$] against [Mg/Fe] enables us to see late time evolution of C more clearly.
+Because of the extended DTD of SNeIa enrichment, [Fe/H] takes longer to reach equilibrium as half of iron production comes from type-Ia supernovae, the late time evolution is not as clustered as [$\alpha$/H].
+
+This is even more evident in the lower panel of Fig.
 \ref{fig:c_evo}.
-While the \caah trend reaches almost equilibrium at 5Gyr, the \caafe trend continues to evolve even until the present day, exposing the effect of the delayed contribution from AGB stars on the evolutionary history.
-
-\begin{itemize}
-    \item Describe definition of $f$ /etc.
-    \item How I match the figures, DTD vs $\zeta$
-
-\end{itemize}
+While the \caah~trend reaches equilibrium at $\sim5$ Gyr, the \caafe~trend continues to evolve even until the present day, exposing the effect of the relative delay times of AGB stars and SNeIa.
 
@@
 
-What happens as I change our choice of AGB stellar yields? I consider four models
-using the published yields in \cristallo, \karakas, \kl, and \ventura~in Fig.
-\ref{fig:agb_sims}.
-
-As the highest AGB yield at solar is from our \karakas~model at $Y_{\rm C}^{\rm
-agb} = 0.000585$ is only 11.7 percent of our required total C production,
-each of these models is dominated by CC production of C. As a result,
-while the metallicity dependence of the \caah may vary, the
-\caafe diagnostic shows how this small AGB fraction makes the details of
-the AGB model and delay-time-distribution unchange the galaxy production of
-C.
-
-Appendix \ref{sec:alt_agb} describes the effects of increasing the AGB model on
-resulting abundance trends. However, I use the \cristallo AGB yields for the
-rest of the main discussion.
-
-Our next exploration is to adjust the relative fraction of AGB star yields. To do this, I hold the total C yield at solar metallicity fixed, so for a desired AGB fraction (assuming equilibrium),
+In Fig.
+\ref{fig:agb_sims}, I compare the K10, K16, C11, and V13 yield models.
+Each model uses the published, unscaled yield tables.
+As the highest AGB yield at solar, K10, is only $\Ycagb=0.000585$, $f_{\rm AGB} \leq 0.12$ for all models.
+Massive stars dominate C production with unscaled yields.
+
+While it is easy to modify the AGB yields in my model, their small contribution reduces the effect.
+I leave a more detailed discussion of the effects of AGB models for Appendix \ref{sec:alt_agb} and use C11 yields hereafter.
 
@@
 
-\begin{figure}\label{fig:beta_f}
-\centering
-\includegraphics{beta.pdf}
-\includegraphics{f_agb.pdf}
-
-\caption[Adjusted yield models]{Similar to Figure \ref{fig:agb_sims} except the top plot shows the fiducial model with lower and higher values of $\zeta$, the C-CCSNe metallicity dependence.
-The bottom plot shows models with $f_{\rm AGB}=$0.1, 0.2, and 0.4.
-Both the $f_{\rm AGB}$ and $\zeta$ influence \caah, but only $f_{\rm AGB}$ has a significant impact on \caafe.}
-\end{figure}
+Next, I investigate adjustments to $f_{\rm AGB}$ and the CCSNe metallicity dependence $\zeta$ in Fig. \ref{fig:beta_f}.
 
@@
 
-Even changing the AGB model does not affect the conclusion significantly.
-
 An alternate solution is to reduce the outflows and core collapse yields similarly, consistent with a model where more large stars collapse directly into black holes.
@@
 In the next section, I develop the analytic tools to explore this problem in more depth.
+
+\begin{figure}
+\centering
+\includegraphics{beta.pdf}
+\includegraphics{f_agb.pdf}
+
+\caption[Adjusted yield models]{Similar to Figure \ref{fig:agb_sims} except the top plot shows the fiducial model with lower and higher values of $\zeta$, the C-CCSNe metallicity dependence.
+The bottom plot shows models with $f_{\rm AGB}=$0.1, 0.2, and 0.4.
+Both the $f_{\rm AGB}$ and $\zeta$ influence \caah, but only $f_{\rm AGB}$ has a significant impact on \caafe.}
+\label{fig:beta_f}
+\end{figure}
 
@@
 
-\section{Comparison to Observations}\label{sec:gas}
+\section{Gas-phase C abundances}\label{sec:gas}
+
+Stellar measurements of Mg are more reliable, but O abundances are easier to measure in HII regions. 
+I therefore use Mg abundances from the \citet{jack_subgiant} subgiant sample as my primary empirical constraint.
+However, I use O abundances for gas-sphase measurements and low-metallicity stars (\S \ref{sec:gas}).
+I model both Mg and O as metallicity-independent population-averaged yields dominated by massive stars.
+${\rm [O/Mg]}\approx 0$ across a wide range of metallicities in APOGEE \citep{Weinberg+19, Weinberg+22}.
+I adopt O and Mg relative yields given by the solar mixture of \cite{asplund+09} <MATH>.
 
@@
 This cut isolates a clean sample of subgiants.
-As First Dredge Up, which affects C and N abundances, only occurs during the ascent onto the red giant branch, subgiant stars are unaffected by this enrichment.
+As first dredge up, which affects C and N abundances, only occurs during the ascent onto the red giant branch, subgiant stars are unaffected by this enrichment.
 
@@
 As o
+
+\begin{equation}\label{eq:high_alpha}
+\begin{cases}
+\text{[Mg/Fe]} >0.12-0.13\text{[Fe/H]}, & \text{[Fe/H]}<0\\
+\text{[Mg/Fe]} >0.12, & \text{[Fe/H]}>0\\
+\end{cases}
+\end{equation}
 

### 2023-04-10 thesis/tex/main.tex
citatatations

@@
 \newcommand{\alp}{$\alpha$}
+
+\newcommand{\citetjack}{JRoberts et. al (2023, in preperation)}
+\newcommand{\citepjack}{(Roberts et. al 2023, in preperation)}
+\newcommand{\citealtjack}{Robert et. al 2023, in preperation}
 
@@
 At the core of GCE models are stellar yields---the amount of each chemical element stars produce (or destroy).
-The chemical elements are produced in different amounts by different stars, leaving Galaxy's evolutionary history.
-Through \textit{Galactic Archeology}, we can reconstruct the history of our galaxy by investigating the clues left in reminants from the past \citep{Weinberg+22, emily+19}.
+The chemical elements are produced in different amounts by different stars, leaving traces of Galaxy's evolutionary history.
+Through \textit{Galactic Archeology}, we can reconstruct the history of our galaxy by investigating the clues left in reminants of the past \citep{Weinberg+22, emily+19}.
 
@@
 C is unique nucleosynthetically, one of few light elements (along with N) produced in asymptotic giant branch (AGB) stars \citep[e.g.][]{jennifer19, KL14}.
-C and N are well studied elements as they are easy to observe in stellar spectra, even at the lowest metallicities \citep{FN15}(?).
-Additionally, C and N are used as age indicators in red giant branch stars \citep[e.g.][]{martig16, MG15, fiorenzo+21}.
-
-Gas-phase [C/O] ratios---observed in very low metallicity, high redshift damped Lyman-alpha systems (DLAs)---decrease with increasing [O/H] \citep{cooke+17}.
-Then, [C/O] increases above $\rm [O/H] \approx 1$ (\citealt{berg+19,nissen+14,fabbian+09}; see discussion in \S\ref{sec:gas}).
+C and N are well studied elements since they are easy to observe in stellar spectra, even at the lowest metallicities \cite[e.g.][]{fabbian+09, nissen+14, lambert81, laird85, lambert86}.
+Additionally, C and N are used as age indicators in red giant branch stars \citep{martig16, MG15, hasselquist19, fiorenzo+21}.
+
+Gas-phase [C/O] ratios---observed in very low metallicity, high redshift damped Lyman-alpha systems (DLAs)---decrease with increasing [O/H] \citep{FN15, cooke+17}.
+Then, [C/O] increases above $\rm [O/H] \approx 1$ (\citealt{berg+19}; see discussion in \S\ref{sec:gas}).
 While we know C is produced in AGB stars and core collapse supernovae (CCSNe), we still have limited understanding of the magnitude and metallicity-dependence of each process.
@@
 Despite their central role in GCE models, nucleosynthetic yields predicted by stellar evolution models are rife with uncertainties.
-Poorly understood processes, including mass loss, opacity, nuclear reaction rates, rotational mixing, and convection/convective boundaries each shape the production rates of atomic nuclei in stellar interios \citep{KL14,ventura+13, LC18}.
-Additionally, changes in massive star's explodability can introduce a factor of $\sim2$ change in population averaged-yields \citep{emily+21}.
+The production rates of elements in stars are shaped by poorly understood processes, including mass loss, opacity, nuclear reaction rates, rotational mixing, and convection\citep{KL14,ventura+13, LC18}.
+Additionally, changes in massive stars' explodability introduce further variation in population averaged-yields \citep{emily+21}.
 
@@
 I choose to introduce C yields as a free parameter, determining which yield prescriptions reproduce Galactic abundance trends.
-\cite{james+22} examined similar GCE models of N, an elements whose production is closely related to C.
+\cite{james+22} examined similar GCE models of N, an element whose production is closely related to C.
 \cite{james+22} found trends in N and O abundances can be explained by the metallicity dependence of relative N and O yields.
@@
 Accurate determination of stellar birth abundances for C and N is challenging.
-When a star enters the red giant branch (RGB), material from the CNO-processed core is mixed with the envelope in first dredge up (FDU), enhancing N and depleting C \citep{fiorenzo+21,KL14}.
+When a star enters the red giant branch (RGB), material from the CNO-processed core is mixed with the envelope in first dredge up (FDU), enhancing N and depleting C \citep{iben67, fiorenzo+21,KL14}.
 Measurements of these evolved stars'  atmospheres will no longer reflect birth abundances.
-Additionally, C is faint in HII regions and determining gas-phase abundances is challenging \citep{skillman+20}.
+Additionally, gas-phase measurments of C are extremely limited as C lacks strong lines in HII regions \citep{skillman+20}.
 
@@
 In Fig.
-\ref{fig:subgiants}, I plot this sample, selected by criteria in \citet[see Appendix \ref{sec:jack}]{jack_subgiant}.
+\ref{fig:subgiants}, I plot this sample, selected by criteria in (see Appendix \ref{sec:jack}; \citealtjack).
 These emperical resolults contain information on the relative C and Mg yields, which I use later in this work.
@@
     \includegraphics{subgiants_mgfe.pdf}
-    \caption[APOGEE Subgiants]{The [C/Mg] ratio against [Mg/H] (top) and [Mg/Fe] (bottom) for the \citet{jack_subgiant} sample of APOGEE subgiants.
+    \caption[APOGEE Subgiants]{The [C/Mg] ratio against [Mg/H] (top) and [Mg/Fe] (bottom) for the \citetjack~sample of APOGEE subgiants.
 On the top, I plot high-$\alpha$ stars in blue and low-$\alpha$ stars in orange using the seperation defined in Equation \ref{eq:high_alpha}.
@@
 This argument can also be inverted to infer  yields from abundance ratio trends.
-To the extent that observed C and Mg trends reflect the equilibrium abundances in different Galatic regions, we can infer the CCSNe (is this plural><?) yield given an assumed AGB star yield (or vice versa).
+To the extent that observed C and Mg trends reflect the equilibrium abundances in different Galatic regions, we can infer the CCSNe yield given an assumed AGB star yield (or vice versa).
 Inffering $\Ycc$ from $\Ycagb$,
@@
     \begin{align}
-        \Ycagb \rightarrow &\alpha_{\rm agb}  \Ycagb \\
-        \alpha_{\rm agb} &= &f_{\rm agb} \frac{\Yct}{\Ycagb} \\
-        \alpha_{\rm CC} = &(1 - f_{\rm agb}) \frac{\Yct}{\Ycc}.
+        \Ycagb &\rightarrow \alpha_{\rm agb}  \Ycagb \\
+        \alpha_{\rm agb} &= f_{\rm agb} \frac{\Yct}{\Ycagb} \\
+        \alpha_{\rm CC} &= (1 - f_{\rm agb}) \frac{\Yct}{\Ycc}.
     \end{align}
@@
 \begin{equation}
-    \frac{\Ycc}{\Yoc} = y_{\rm}
+    \frac{\Ycc}{\Yoc} = b + \zeta \frac{Z}{Z_\odot}
 \end{equation}
@@
 \JJ\ accounts for radial migration by using the results of the \texttt{h277} hydrodynamical simulation \citep{christensen12, zolotov12, loebman12, BZ14}, with simulation parameters described in \citet{bird+21}.
-Each VICE single stellar population (SSP) is matched to an \textit{analogue} in \texttt{H277}, chosen to form at a similar time and radius $R$.
+Each \VICE single stellar population (SSP) is matched to an \textit{analogue} in \texttt{H277}, chosen to form at a similar time and radius $R$.
 By taking the change in radius $\Delta R$ of the analogues, the SSP move to their final radii with a $\sqrt{\text{time}}$ dependence.
@@
 \citet{james+22} compare their model against the \cite{fiorenzo+21} sample of APOGEE \citet{apogee17} red giants whose C and N abundance have been corrected for mixing process using MESA stellar evolution models.
-I instead use the \citet{jack_subgiant} sample of APOGEE subgiants.
+I instead use the \citetjack~sample of APOGEE subgiants.
 Subgiant stars have not undergone FDU, so their atmospheric C and N abundances are still reflective of their birth abundances and do not need mixing corrections.
@@
 In the next sections, I will discuss the choice of parameters and agreement with observations.
-Our fiducial model uses the C11 AGB yield tables (see section \ref{sec:agb}), and I amplify the C11 yields by a factor of 2.9 so that $f_{\rm AGB} = 0.2$
+Our fiducial model uses the C11 AGB yield tables (see \S\ref{sec:agb}, and Table \ref{tab:fiducial_mod}), and I amplify the C11 yields by a factor of 2.9 so that $f_{\rm AGB} = 0.2$.
 
@@
 The evolution proceeds as follows.
-
 Initially, CCSNe dominate production.
@@
 Massive stars dominate C production with unscaled yields.
-
 While it is easy to modify the AGB yields in my model, their small contribution reduces the effect.
@@
 Colored lines quantify the median [C/Mg] in bins of [Mg/H] for our four AGB yield models from the literature (see \ref{sec:agb}).
-Black points and grey dashes represent the median and standard deviations in the \citet{jack_subgiant} sample.
+Black points and grey dashes represent the median and standard deviations in the \citetjack~sample.
 In the right panel, I show the trends only for stars where $-0.15\leq {\rm [Mg/H]}\leq -0.05$.
@@
 Next, I investigate adjustments to $f_{\rm AGB}$ and the CCSNe metallicity dependence $\zeta$ in Fig. \ref{fig:beta_f}.
-
-The next question is how does changing the CCSNe C yield affect the model?
-I now consider variations of our fiducial mode/
 
@@
 
+As disscused in \S\ref{sec:equilibrium}, the \caah~trend in these models arises as a consequence o fthe relative yield $y_{\rm C}/y_{\rm Mg}$ and its metallicity dependence.
+This is determined by both the AGB fraction $f_{\rm AGB}$ and the metallicity dependence of CCSNe yields $\zeta$.
+As a result, there is a degeneracy between the two.
+I can increase $f_{\rm AGB}$ and $\zeta$ correspondingly, and \caah~would remain unaffected.
+
+This degeneracy is broken by the \caafe~relation.
+The relationship is set by $f_{\rm AGB}$, because a specific amount of C must be released at a delayed time in order to match the SNeIa production of Fe and increase [C/Mg] as [Mg/Fe] decreases to reproduce the data.
+One source of theoretical uncertanty in this result is that the SNeIa yield and DTD have their own uncertainties.
+I discuss variations in $y_{\rm Fe}^{\rm Ia}$ in Appendix \ref{sec:alt_agb}, and find that the quanlitative conclusions are largely unaffected.
+I therefore focus on the choices of $y_{\rm Fe}^{\rm Ia} = $FILLIN choices from the fiducial model here.
+
+Due to instantaneous CCSNe enrichment, the \caafe~relation is approximantly independent of $\zeta$.
+I can therefore choose $f_{\rm AGB}$ such that the \caafe~relation is reproduced, and then choose $\zeta$~to simulatneously reproduce \caah.
+Indeed, the positive slope of the \caah~relationship compared to our GCE models is a clear indication that metallicity dependent yields from massive stars must dominate AGB star production of C.
+Otherwise,  the inverse dependence of $\Ycagb$ on $Z$ makes it extremelly difficult to reproduce a positive slope in \caah.
+If this relationship indeed arises as a consequence of chemical equilibrium and yield ratios, then a positively sloped \caah~relation with high $f_{\rm AGB}$ should only arise if the Galaxy is significantly far from equilibrium.
+
 C as an equilibrium phenominon. See section \ref{sec:equilibrium} Importantly, the \caafe trend is mostly unaffected by choosing a different
@@
 
-One caveat is that the slope of this trend is also determined by the ratio of delayed iron to CCSNe iron production as well.
-If the SNeIa iron fraction is increased, then more iron enters later reducing the slope of the trend as AGB becomes a more rapid mechanism than Fe comparatively.
-The difference however is that changing the Fe franction mostly affects the tail of the distribution as this controls the speed of descent off the high $\alpha$ sequence, but the AGB fraction even changes the behavior for the low $\alpha$ sequence.
-
-One potential tension with data is our models predict a low value for the AGB fraction of stars.
-
-Our model with Z-dependent CCSNe yields has $f_\text{agb} = 0.05$ which implies that CCSNe overwhelms AGB production and there should not be a seperation between low and high alpha sequences.
-However, V21 observes a significant seperation implying a more substantial delayed-time source.
-
-An alternate solution is to reduce the outflows and core collapse yields similarly, consistent with a model where more large stars collapse directly into black holes.
-This leaves the $y_\text{C}^\text{CC}/y_\text{O}^\text{CC}$ ratio unchanged, but because $y_\text{C}^\text{CC}$ is unchanged, the relative size of the AGB contribution is larger.
-
-Increasing the relative AGB production lowers the magnitude of  $y_\text{C}^\text{CC}/y_\text{O}^\text{CC}$, but the metallicity dependence of the ratio must increase to compensate for the inverse metallicity dependence of AGB C yields.
-
-These models are indistinguishable in the \caah~plane from our adjusted CCSNe model, so future work investigating the SFH and C isotopic ratios in more depth may be able to provide more insight.
-In the next section, I develop the analytic tools to explore this problem in more depth.
+V21 observes a significant seperation implying a more substantial delayed-time source.
 
@@
 
-I also consider a 2-infall model as a slight variation of the lateburst, where the burst is instead exponential and placed at $t_1=5$ Gyr.
+I also consider an earlyburst model as a slight variation of the lateburst, where the burst is instead exponential and placed at $t_1=5$ Gyr.
 This approximantly corresponsed to the Gaia-Encelidus merger, inducing higher star formation in the Milky Way \citep{bonaca20, helmi18}.
 \begin{equation}\label{eq:twoinfall}
-    \dot{\Sigma}_{\rm 2-infall} \propto \dot{\Sigma}_{\rm insideout} + 
+    \dot{\Sigma}_{\rm early-burst} \propto \dot{\Sigma}_{\rm insideout} + 
 \begin{cases}
@@
 
-A common degeneracy in chemical evolution models is the yield-outflow degeneracy.
-An increase in stellar yields has a near-identical effect as a decrease in outflows.
-For example, the equilibrium abundance ratios are entirely independent of $\eta$ (see section \ref{sec:equilibrium}).
-My model is able to determine yield ratios well, but is unable to differentiate differences in the overall scaling of outflows and yields.
-
-While my model requires high yields and significant mass loading, other approaches neglect outflows altogether \citep{MCM13, MCM14, spitoni19, spitoni20, spitoni21}.
-By modifying our model such that $\eta=0$, I can create outflow-less models.
-
-The theoretical motivation for decreasing outflows is due to the uncertainty in the explodability landscape---if less massive stars explode, then both the yields and outflows will be reduced by some factor.
-So, when I explore reduced outflow models, I consider models where both the outflows and yields are reduced by approximately the same factor, to leave the equilibrium abundances of a pure CCSNe unchanged.
-
-The effect of reducing outflows is then increasing the relative contributions of non-CCSNe processes. For C, this increases the AGB fraction.
-
-I find that the \caah~relationship may provide insight into this issue.
-[O/Fe] is a tracer of the relative contributions of CCSNe and delayed-time sources in chemical evolution.
-So, the appearance of a slope in [O/Fe] implies that there is a substantial delay-time process in C evolution.
-The metallicity-dependence of C yields complicates this picture because
-younger stars have higher [O/Fe] as the SNeIa contributions take up to 10Gyr,
-so metal-poor young stars will naturally have lower [C/O], agreeing with the
-slope observed in\caafe. However, a pure CCSNe C model cannot reproduce the slope accurately as
-
-I find that I can adjust both the outflows and scale down the yields if I change our model for $y_\text{C}^\text{CC}/y_\text{O}^\text{CC}$.
-For example, reducing outflows and CCSNe yields by a factor of two requires the modified parameters
-$\alpha = 0.033$ and $\beta = 0.625$, which results in a slightly lower value at solar but nearly a doubling of the metallicity dependence.
+GCE models of the Milky Way fall into two classes---those which incorperate significant mass-loading (e.g., as in this work) and those which neglet mass-loading but lower effective yield to match observed abundances \citep{MCM13, MCM14, spitoni19, spitoni20, spitoni21}.
+An increase in stellar yields has a nearly identical effect as a decreease in the mass-loading factor $\eta$ (see Appendix B of \cite{james_dwarf}).
+The equilibrium arguments discussed in \S\ref{sec:equilibrium} suggest howerver that abundance ratios are independent of the choice of normalization and the value of $\eta$.
+We therefore expect our results regarding the relative yield $y_{\rm C}/y_{\rm Mg}$ and its metallicity dependence to extend to the other class of models omitting mass loading.
+I demonstrate this further here.
+
+The theoretical motivation for decreasing yields is the uncertainty in stellar explodability.
+If fewer massive stars explode, then the yields will be reduced by some factor.
+Additionally, some fraction of SN ejecta may be lost directly to an outflow, lowering effective yields.
+To explore reduced outflow models, I lower both $\eta$ and all yields by the same factor to leave the equilibrium abundances unchanged.
+
 \begin{figure}
@@
 
+\section{Scatter}
+
+Beyond simply comparing median trends, I can compare the distribution
+
+\begin{figure}
+    \centering
+    \includegraphics[scale=0.9]{cooh_scatter.pdf}
+    \caption[Scatter agreement]{The stars in the fiducial model in the \caah~plane perturbed by the median [Mg/H] and [C/Mg] measurment errors in the \citetjack~sample.
+Stars are color-coded such that lighter colors represent population sborn at greater galactocentric radii
+    }
+\end{figure}
+
 \section{Gas-phase C abundances}\label{sec:gas}
 
+As an additional test of the model, I next compare the gas-phase predictions against gas-phase C data.
+
+Beyond Milky Way stars, C to O ratios in
+HII-regions through either Recombination Lines or (OTHER TEchnique0), enabling
+us to probe gas-phase abundances of C in our galaxy and other types of
+galaxies from dwarf to elliptical. 
+However, C measurments of HII regions are challenging. C lacks strong collisional excitation lines, and recombination
+Additionally, recombination and collisionally excitation measurments disagree by a factor of $\sim 2$ \cite{GR07}.
+
+In Fig. \ref{fig:gas_phase}, I plot our fiducial model's gas phase abundances
+at present day and 2 Gyr compared to C/O
+abundances measured in both stars, our subgiant sample, halo stars, galaxies,
+and Damped Lynman Alpha (DLA) systems.
+
+I don't predict low metallicity but I are in agreement, substantial error bars.
+With MW and MW-like galaxies.
+
 Stellar measurements of Mg are more reliable, but O abundances are easier to measure in HII regions.
-I therefore use Mg abundances from the \citet{jack_subgiant} subgiant sample as my primary empirical constraint.
+I therefore use Mg abundances from the \citetjack~subgiant sample as my primary empirical constraint.
 However, I use O abundances for gas-sphase measurements and low-metallicity stars (\S \ref{sec:gas}).
@@
 
-Beyond simply comparing median trends, I can compare the distribution 
-shape of our distribution to observations.
-
-C measurments in stars are difficult. There are measurments which can however be used to test.
-
-I don't predict low metallicity but I are in agreement, substantial error bars.
-
-Pop III stars from Cooke++.
-
-Beyond Milky Way stars, astronomers have observed C to O ratios in
-HII-regions through either Recombination Lines or (OTHER TEchnique0), enabling
-us to probe gas-phase abundances of C in our galaxy and other types of
-galaxies from dwarf to elliptical.
-
-In Fig. \ref{fig:gas_phase}, I plot our fiducial model's gas phase abundances
-at present day and 2Gyr compared to C/O
-abundances measured in both stars, our subgiant sample, halo stars, galaxies,
-and even Damped Lynman Alpha (DLA) systems.
-
-Our model appears to be broadly consistant with the gas phase data, however these imply if anything that the slope should be increased.
-
 Are HII regions a good approximation?
+Can I use our yield estimations and apply them to extragalactic sources successfully?
+
+Bursty SFH may not be needed to explain scatter as the C/O slope + differet evolutionary timescales is capable alone of reproducing this scatter.
+While the extragalactic trend appears to be more steeply sloped than our models, this is because of ***e.g. mass-dependent outflow rates/differening SFH between galaxies.
 
@@
 Temperature/modelining limitations. Lack of strong HII calibration. 
-
 Short discussion of measurment challenges in extragalactic galaxies, how other galaxies and dwarf SFH may come into play, why this relation is notecably steeper.
+
+Our model does not consider very-low metallicity stars. Population III stellar yields, with a top-heavy IMF, may predict strongly enhanced carbon yields \cite[e.g.]{hirschi07}.
 
@@
 of stellar evolution is limited, our knowledge of extremely metal poor stellar
-evolution is extremely limited. (despite a pure H/He born star appearing
-simpler lolol). A variety of explanation for the increasing relative C
+evolution is proportionally limited.
+
+A variety of explanation for the increasing relative C
 enrichments for metal-poor stars have been proposed (e.g. ...). The likely case
@@
 
-As any constraints in this regieme are poor, I choose to only qualitatively
-conclude that CCSNe C production increases at extremely low metallicity
-but the details of this remains an open question.
-
-Can I use our yield estimations and apply them to extragalactic sources successfully?
-
-Explain Berg+19,
-
-Bursty SFH may not be needed to explain scatter as the C/O slope + differet evolutionary timescales is capable alone of reproducing this scatter.
-
-While the extragalactic trend appears to be more steeply sloped than our models, this is because of ***e.g. mass-dependent outflow rates/differening SFH between galaxies.
-
-\begin{figure}
-    \centering
-    \includegraphics[scale=0.9]{cooh_scatter.pdf}
-    \caption[Scatter agreement]{The stars in the fiducial model in the \caah~plane perturbed by the median [Mg/H] and [C/Mg] measurment errors in the \citet{jack_subgiant} sample.
-Stars are color-coded such that lighter colors represent population sborn at greater galactocentric radii
-    }
-\end{figure}
+e.g. \cite{cooke+17} suggest Population III stars as a solution to CEMPS \cite{FN15}.
 
@@
     dwarf galaxies \citep[red diamonds;]{berg+19},
-    and Milky Way high-$\alpha$ stars \citet[yellow points;][]{jack_subgiant}.
+    and Milky Way high-$\alpha$ stars (yellow points; \citealtjack)
 }
@@
 \citet{james+22} performed a similar analysis, except focusing on N.
-\citet{james+22} found, to match APOGEE/\citet{fiorenzo+21}'s observations, N yields ratios relative to O needed to be about triple what AGB models suggested.
+\citet{james+22} found, to match APOGEE/\citet{fiorenzo+21}'s observations, $y_{\rm N}^{\rm AGB} \sim M Z$.
 
@@
 
-I use the criteria outlined in \cite{jack_subgiant} to create a sample of subgiants from APOGEE DR17 \cite{apogee17} as our primary observational constraint. 
-\cite{jack_subgiant} selects a region of stars in $\log g$-$T_\text{eff}$ space described by the following polyhedron
+I use the criteria outlined in \citetjack~to create a sample of subgiants from APOGEE DR17 \cite{apogee17} as our primary observational constraint.
+Subgiants are reflective of birth abundances for CNO \citep{souto19}.
+with chemical abundance determinations from ASPCAP \citep{aspcap}.
+SDSS 17 \cite{sdss17}.
+\citetjack~selects a region of stars in $\log g$-$T_\text{eff}$ space described by the following polyhedron
 \begin{equation}
@@
         A Kiel diagram of APOGEE stars.
-Following \citet{jack_subgiant}, we select subgiants in the orange polygon (see Equation \ref{eq:subgiant_selection}).
+Following \citetjack, we select subgiants in the orange polygon (see Equation \ref{eq:subgiant_selection}).
 These stars have not yet experienced first dredge-up, so their photospheric C and N abundances should reflect their birth mixture.
@@
 A second approach in determining birth abundances in stars is to correct the surface abundance effects of FDU, as in \cite{fiorenzo+21}.
-I note that there is a slight difference in the yields found through \cite{fiorenzo+21} and \cite{jack_subgiant}.
+I note that there is a slight difference in the yields found through \cite{fiorenzo+21} and \citetjack.
 As o
@@
 
-I choose to use \cite{jack_subgiant}'s sample as this does not rely on additional layers of modeling, providing a more direct constraint to our model and limiting our systematic uncertainties.
+I choose to use \citetjack's sample as this does not rely on additional layers of modeling, providing a more direct constraint to our model and limiting our systematic uncertainties.
 
@@
 
+\newpage
+
+\section{Software}
+
+Software which has contributed to this work:
+
+\begin{itemize}
+    \item \citet{OhioSupercomputerCenter1987}
+    \item \VICE~\citep{JW20, james+21}
+    \item \texttt{matplotlib} \citep{matplotlib}
+    \item \texttt{scipy} \citep{scipy}
+    \item \texttt{IPython} \citep{ipy}
+    \item \texttt{pandas} \citep{pandas}
+    \item \texttt{numpy} \citep{numpy}
+    \item \texttt{astropy} \citep{astropy:2013, astropy:2018, astropy:2022}
+    \item \texttt{seaborn}
+\end{itemize}
+
 \label{lastpage}
-
-\section{Software}
-Software has played an importaint role in this work. 
-\begin{itemize}
-    \item \citep{OhioSupercomputerCenter1987}
-    \item VICE \citet{JW20} \citet{james+21}
-    \item \cite{matplotlib}
-    \item \citet{numpy}
-    \item \citet{pandas}
-    \item Astropy \citep{astropy:2013, astropy:2018, astropy:2022}
-    \item IPython \citep{ipy}
-    \item \citep{scipy}
-\end{itemize}
-
 \end{document}

### 2023-04-10 thesis/tex/main.tex
more cites, more corrects

@@
 \newcommand{\Ycc}{\ensuremath{y_{\rm C}^{\rm CC}}}
-\newcommand{\Yct}{\ensuremath{y_{\rm C, 0}^{\rm tot}}}
+\newcommand{\Yct}{\ensuremath{y_{\rm C}}}
 \newcommand{\Yoc}{\ensuremath{y_{\rm Mg}^{\rm CC}}}
@@
 
-\newcommand{\citetjack}{JRoberts et. al (2023, in preperation)}
-\newcommand{\citepjack}{(Roberts et. al 2023, in preperation)}
-\newcommand{\citealtjack}{Robert et. al 2023, in preperation}
+\newcommand{\citetjack}{Roberts et.\ al (2023, in preperation)}
+\newcommand{\citepjack}{(Roberts et.\ al 2023, in preperation)}
+\newcommand{\citealtjack}{Robert et.\ al 2023, in preperation}
 
@@
        \vspace*{5\baselineskip}
-       \textbf{The Galactic Chemical Evolution of Carbon} \\
+       \textbf{The Galactic Chemical Evolution of Carbon}\\
        Implications for Stellar Nucleosynthesis\\
@@
        \vspace*{3\baselineskip}
-    Presented in partial fulfillment of the requirements for graduation \textit{with research distinction in Astronomy and Astrophysics} in the College of Arts and Sciences of The Ohio State University \\
+    Presented in partial fulfillment of the requirements for graduation \textit{with research distinction in Astronomy and Astrophysics} in the College of Arts and Sciences of The Ohio State University\\
        \vspace*{3\baselineskip}
-        by \\
+        by\\
        \vspace*{3\baselineskip}
@@
        \vspace*{3\baselineskip}
-       Project Advisor: David Weinberg, Department of Astronomy
+       Project Advisor: Professor David H. Weinberg, Department of Astronomy
        % Rolando Vald\'es Aguilar\\
@@
 \addcontentsline{toc}{chapter}{Abstract}
-Stellar evolution models provide highly uncertain predictions for elemental yields due to our limited understanding of stellar physics.
-In this paper, I aim to estimate the nucleosynthetic yields of C using galactic chemical evolution models.
-
-I find that the AGB stars make up a fraction $0.20_{-20}^{+80}$ of total C production at late times.
+% context
+Stellar evolution models provide uncertain predictions for elemental yields due to our limited understanding of stellar physics. 
+% aims
+Here, I constrain the nucleosynthetic yields of C using multizone Galactic chemical evolution models.
+% background
+Massive star evolutionary models predict a direct relationship beteen population-averaged C yields and stellar metallicity, but AGB star models predict an inverse relationship.
+% results
+Consequently, matching the slopes of the \caah\ and \caafe\ relationships in a sample of APOGEE subgiant stars requires an $\sim 80\%$--$20\%$ balacen between massive stars and AGB stars, respectively.
+% 
+To also match the normailzation of the triends, I estimate the CCSNe C/Mg yield ratio $\Ycc/\Yoc = 1.57 + 0.59 \left(Z/Z_\odot\right)$, which explains the \caah~when including the AGB C contribution.
+%
+Variations in the star formation history impact the low [Mg/Fe] tail of the [C/Mg]-[Mg/Fe] relation, but are only small pertubations compared to the observed scatter.
+Most of the scatter in \caah\ can be attributed to measurment errors and radial migration.
+% 
+Due to the degeneracy between the normaliztion of elemental yields and the strength of mass-loading in Galactic outflows, I constrain only the {\it relative} yield of C and Mg from a simple stellar population and the metallicity dependence thereof.
+While measurments of gas-phase C abundances are difficult, my model is broadly consistant with the [C/O]-[O/H] trend observed in compiled literature measurments.
 
@@
 
-James Johnson, for guiding me through this project and through my last year of undergraduate.
-Wayne Schlingman, for everything you do for everyone. You are the glue holding together our department.
+James Johnson, for guiding me through this project and through my last year of undergraduate. Your feedback at every step of the process has been invaluable.
+Wayne Schlingman, for everything you do for everyone.
+You are the glue holding together our department.
 David Weinberg and Jennifer Johnson, for listening to my earlier drafts of this work and providing excellent suggestions.
@@
 I love so many people in our department who have just been friends and positive support: Kaia, Maria, Autumn, Simon, Mary, Aaliyah, Sanskruti, Alyssa, Harrison, Denis, and so many others. 
-My Family (and Arya, our lovely doodle).
+Finally, I thank my family for supporting me through a challenging year, and Arya for being such a loveable doodle.
 
@@
 Here, I aim to understand C enrichment---where it is produced and how its abundances evolve over time.
-Why study C?
+Why study carbon?
 C is unique nucleosynthetically, one of few light elements (along with N) produced in asymptotic giant branch (AGB) stars \citep[e.g.][]{jennifer19, KL14}.
 C and N are well studied elements since they are easy to observe in stellar spectra, even at the lowest metallicities \cite[e.g.][]{fabbian+09, nissen+14, lambert81, laird85, lambert86}.
-Additionally, C and N are used as age indicators in red giant branch stars \citep{martig16, MG15, hasselquist19, fiorenzo+21}.
+Additionally, C and N are used as age indicators in red giant branch stars \citep{martig16, MG15, hasselquist19, vincenzo+21}.
 
@@
 I choose to introduce C yields as a free parameter, determining which yield prescriptions reproduce Galactic abundance trends.
-\cite{james+22} examined similar GCE models of N, an element whose production is closely related to C.
-\cite{james+22} found trends in N and O abundances can be explained by the metallicity dependence of relative N and O yields.
+\cite{james+23} examined similar GCE models of N, an element whose production is closely related to C.
+\cite{james+23} found trends in N and O abundances can be explained by the metallicity dependence of relative N and O yields.
 Here, I extend their models to C and show that similar constraints on C and O relative yields can be obtained from observed abundance ratios.
@@
 Accurate determination of stellar birth abundances for C and N is challenging.
-When a star enters the red giant branch (RGB), material from the CNO-processed core is mixed with the envelope in first dredge up (FDU), enhancing N and depleting C \citep{iben67, fiorenzo+21,KL14}.
+When a star enters the red giant branch (RGB), material from the CNO-processed core is mixed with the envelope in first dredge up (FDU), enhancing N and depleting C \citep{iben67, vincenzo+21,KL14}.
 Measurements of these evolved stars'  atmospheres will no longer reflect birth abundances.
@@
 In the interest of focusing on carbon yields, I hold yields of other elements fixed. 
-I adopt yields from \citet{james+21, james+22}.
+I adopt yields from \citet{james+21, james+23}.
 In Table \ref{tab:fiducial_mod}, I tabulate yield values, in units of a stellar population's birth mass.
-Also following \citet{james+21, james+22}, I take the SNeIa delay time distribution to be a
+Also following \citet{james+21, james+23}, I take the SNeIa delay time distribution to be a
 $t^{-1.1}$ law suggested by the observations of \citet{maoz+12}.
@@
 
-\section{Asymptotic giant branch stars}\label{sec:agb}
+\section{Asymptotic Giant Branch Stars}\label{sec:agb}
 
@@
 \isotope[12]{C}.
- Other minor branches of the CNO cycle are not relevant here.
+ Other minor branches of the CNO cycle are of minor importance to C yields
  \citep{solar-fusion}.
@@
 Because the $^{14}$N(p, $\alpha$) proton capture is the slowest component of the CNO cycle \citep{solar-fusion}, the CNO cycle converts nearly all \isotope[12]{C} into \isotope[14]{N}.
-As a result, when both TDU and HBB occur, \isotope[12]{C} yields are lowered (see discussion in \citealt{james+22} and \citealt{ventura+13}).
+As a result, when both TDU and HBB occur, \isotope[12]{C} yields are lowered (see discussion in \citealt{james+23} and \citealt{ventura+13}).
 
@@
 Most models agree on the qualitative shape of the net fractional AGB C yield---% 
-stars with mass $\sim 2--4 M_\odot$ have highest fractional C yields, with the mass of the peak increasing and overal yields decreasing with increasing $Z$.
+stars with mass $\sim 2--4 M_\odot$ have highest fractional C yields, with the mass of the peak increasing and overall yields decreasing with increasing $Z$.
 High mass, high $Z$ stars destroy \isotope[12]{C} due to HBB.
@@
 
-\section{Core collapse supernovae}
+\section{Core Collapse Supernovae}
 
@@
 In the presence of metal-poor gas accretion and feedback-driven outflows, galaxies reach an equilibrium abundance in which production of new metals is balanced by losses to new stars and outflows \citep{larson72, dalcanton07, FD08, PS11, lilly13}.
-While our galaxy is likely not in perfect equilibrium or described by a single, homogenous chemical region, the equilibrium approximation is nevertheless useful in understanding yields and metallicity dependence \citep[e.g.][]{james_dwarf,james+22,WAF17}.
+While our galaxy is likely not in perfect equilibrium or described by a single, homogenous chemical region, the equilibrium approximation is nevertheless useful in understanding yields and metallicity dependence \citep[e.g.][]{james_dwarf,james+23,WAF17}.
 
@@
 
-Analogous to \cite{james+22} arguments about N, the trends in abundance ratios are set by yield ratios in these GCE models.
+Analogous to \cite{james+23} arguments about N, the trends in abundance ratios are set by yield ratios in these GCE models.
 The effect of other GCE parameters (most importaintly $\eta$) cancels.
@@
 Rewriting this expression as a relative yield of C and Mg,
-\begin{equation}
+\begin{equation}\label{eq:y_c_eq}
     \frac{\Ycc}{\Yoc} = \frac{Z_{\text{C},~\odot}}{Z_{\text{Mg},~\odot}} 10^{\rm [C/Mg]} - \frac{\langle \Ycagb \rangle}{\Yoc}.
@@
 
-If $\Ycc$ gets us to ${\rm [C/Mg] } \approx -1$, then $\Yct = 0.005$, but if 0, $y\approx0.006$. 
-Section 2.2, additional AGB yield 1part per thousand?, Motivate AGB yield ...
-
-Outflow yield degeneracy.
-One challenge of chemical evolution models is that outflows and yields are degenerate.
-To avoid this degeneracy, I instead constrain relative yields.
-As Equation \ref{eq:z_co} shows, the yield ratios are independent of $\eta$, and independent of the SFH (ignoring the DTD term).
-As such, I set the total C yields to 
-\begin{equation}
-    \Yct = \Ycc + \Ycagb = 0.005 \frac{\Yoc}{0.00185}
-\end{equation}
-
-is reasonably consistant with the value in \citet{asplund+09} of $Z_{\rm
-C}/Z_{\rm O}=0.413$ and was chosen as to match the median value of our sample
-at $Z=Z_{\sun }$.
-
-Additionally, each AGB yield set (C11, K10, V13, K16), fails to produce enough AGB C for our fiducial model (see REF).
-So, I introduce a process factor, $\alpha_{\rm AGB}$, which represents the multiplicative increase in $\Ycagb$ from the published yields.
+As I will discuss in \S\ref{sec:outflows}, the normalization of yields and $\eta$ is degenerate.
+This can be observed in Eq.~\ref{eq:z_co}, where changes in $\eta$ or the scaling of $y_{\rm C}/y_{\rm Mg}$ would not affect equilibrium trends.
+Furthermore, in Eq.~\ref{eq:z_eq}, an increase in both $y_{\rm Mg}$ and $\eta$ would leave $Z_{\rm Mg}^{\rm eq}$ unchanged.
+My models here are unable to distinguish the overall scaling of yields and outflow mass loding, and choosing to keep $y_{\rm C}$ fixed reduces unnecessary free parameters.
+%
+As a result, I choose to leave the total carbon yield fixed at solar $Z$,
 \begin{subequations}
     \begin{align}
-        \Ycagb &\rightarrow \alpha_{\rm agb}  \Ycagb \\
-        \alpha_{\rm agb} &= f_{\rm agb} \frac{\Yct}{\Ycagb} \\
-        \alpha_{\rm CC} &= (1 - f_{\rm agb}) \frac{\Yct}{\Ycc}.
+        \Yct~\big\vert_{Z=Z_\odot} &= \Ycc + \Ycagb = 0.005 \\
+        \Yct/\Yoc~\big\vert_{Z=Z_\odot} &= 2.7.
     \end{align}
 \end{subequations}
-
-I have investigated uniform increases in C yields and have found these changes make little effect on the resulting trends.
-Fixing the total C yield at solar reduces the number of free parameters and keeps the model reasonably consistant with observations, and enables us to more consistantly explore differen AGB models.
-
-Fitting this relationship to data (figure \ref{fig:analytic}).
-I find that a linear dependence on metallicity,
-
-\begin{equation}
-    \frac{\Ycc}{\Yoc} = b + \zeta \frac{Z}{Z_\odot}
-\end{equation}
+This ratio results in an equilibrium abundance ${\rm [C/Mg]} = -0.09$, which is consistant with the \citetjack subgiant sample and is within $\sim 20\%$ of the solar C/Mg mixture from \citet{asplund+09}.
+
+In \S\ref{sec:f-z-models}, I will show that none of the four AGB yield sets (C11, K10, V13, K16) produce enough C relative to this $\Ycc$ value.
+So, I choose to introduce process factors, $\alpha_{\rm AGB}$, and $\alpha_{\rm CC}$ which denote a multiplicitave scaling of $\Ycc$ and $\Ycagb$ respectively.
+\begin{subequations} \label{eq:alpha}
+    \begin{align}
+        \Ycagb &\rightarrow \alpha_{\rm AGB} \left(\Ycagb\right) \\
+        \Ycc &\rightarrow \alpha_{\rm CC} \left(\Ycc\right)\\
+        \alpha_{\rm CC} &= \frac{\Yct - \alpha_{\rm AGB} \left(\Ycagb\right)}{\Ycc}
+    \end{align}
+\end{subequations}
+Above, $\alpha_{\rm CC}$ is dependent on the choice of $\alpha_{\rm AGB}$ to keep the total carbon yield constant.
+
+In \S\ref{sec:f-z-models}, I find that $\alpha_{\rm AGB}\approx 2.9$ for the C11 yield model.
+Using this AGB yield, I can now use Eq.~\ref{eq:y_c_eq} to find an estimate of $\Ycc$ as a function of metallicity.
+I show the values of $\Ycc$ I obtain from the subgiant sample in Fig.~\ref{fig:analytic}.
+From a regression analysis, I suggest here that
+\begin{equation}
+    \Ycc = 0.0028 + \zeta\left(\frac{Z}{Z_\odot}\right),
+\end{equation}
+where $\zeta$, describing the metallicity dependence, is $\zeta\approx0.001$.
 
@@
 I do note that this analysis fails to take into account selection effects and biases in APOGEE, and a more robust determination of the C yield.
+Not all C measurments of stars agree (see \S \ref{sec:jack})
 
@@
 Specifically, I make use of the \citet{james+21} (hereaafter \JJ) model for the Milky Way, which runs using the publicaly available Versatile Integrator for Chemical Evolution (\VICE).
-This model is described extensively in \JJ~and consicely summarized  in \citet{james+22}.
+This model is described extensively in \JJ~and consicely summarized  in \citet{james+23}.
 Here, I provide a prief overiview of the relevant model components.
@@
 
-\chapter{Multizone model results}
+\chapter{Multizone Model Results}
 \section{Data Selection}
 
-\citet{james+22} compare their model against the \cite{fiorenzo+21} sample of APOGEE \citet{apogee17} red giants whose C and N abundance have been corrected for mixing process using MESA stellar evolution models.
+\citet{james+23} compare their model against the \cite{vincenzo+21} sample of APOGEE \citet{apogee17} red giants whose C and N abundance have been corrected for mixing process using MESA stellar evolution models.
 I instead use the \citetjack~sample of APOGEE subgiants.
@@
 
-\section{The Evolution of C across the galaxy and through time}
+\section{The Evolution of C Across the Galaxy and Through Time}
 
@@
 
-\section{Alternate Models}
+\section{Alternate Models}\label{sec:f-z-models}
+
+To make comparison easier, I define the C AGB production fraction as,
+\begin{equation}
+    f_{\rm AGB} = \frac{\Ycagb}{\Yct}\Bigg\vert_{Z=Z_\odot},
+\end{equation}
+where  $\Ycagb$ includes the multiplicitive factor $\alpha_{\rm AGB}$ as defined in Eq.~\ref{eq:alpha}.
 
@@
 
-\section{Gas-phase C abundances}\label{sec:gas}
+\section{Gas-Phase C Abundances}\label{sec:gas}
 
@@
 
-Are HII regions a good approximation?
-Can I use our yield estimations and apply them to extragalactic sources successfully?
-
 Bursty SFH may not be needed to explain scatter as the C/O slope + differet evolutionary timescales is capable alone of reproducing this scatter.
@@
     \includegraphics{c_n.pdf}
-    \caption{Similar to as Figure \ref{fig:agb_sims}, except I only show the fiducial model and I plot the [C/N] abundance ratio on the y-axis.
+    \caption[C/N abundance agreement]{Similar to as Figure \ref{fig:agb_sims}, except I only show the fiducial model and I plot the [C/N] abundance ratio on the y-axis.
     }
@@
 In this work, I investigate the role of C yields on the predictions of multizone GCE models.
-\citet{james+22} performed a similar analysis, except focusing on N.
-\citet{james+22} found, to match APOGEE/\citet{fiorenzo+21}'s observations, $y_{\rm N}^{\rm AGB} \sim M Z$.
+\citet{james+23} performed a similar analysis, except focusing on N.
+\citet{james+23} found, to match APOGEE/\citet{vincenzo+21}'s observations, $y_{\rm N}^{\rm AGB} \sim  Z$.
 
@@
 
-existing surveys in e.g. APOGEE/DESI?)
+Future surves, including SDSS-V/MWM and the DESI Milky Way survey will each measure spectra of $>6$ million milkyway stars.
+\citep{desi, desi:mw}
+
+Combined with kinematic information and distances from GAIA \citep{gaia}
+
+\citep{sdssv}
 Abundance ratios (e.g.C12/C13) as additional constraints
@@
 SDSS 17 \cite{sdss17}.
-\citetjack~selects a region of stars in $\log g$-$T_\text{eff}$ space described by the following polyhedron
+\citetjack~select a region of stars in $\log g$-$T_\text{eff}$ space described by the following polyhedron
 \begin{equation}
@@
 
-A second approach in determining birth abundances in stars is to correct the surface abundance effects of FDU, as in \cite{fiorenzo+21}.
-I note that there is a slight difference in the yields found through \cite{fiorenzo+21} and \citetjack.
+A second approach in determining birth abundances in stars is to correct the surface abundance effects of FDU, as in \cite{vincenzo+21}.
+I note that there is a slight difference in the yields found through \cite{vincenzo+21} and \citetjack.
 As o
@@
 
+, discussion of GALAH C in \citealt{emily+19}).
+
 I choose to use \citetjack's sample as this does not rely on additional layers of modeling, providing a more direct constraint to our model and limiting our systematic uncertainties.
@@
 
-While I focus the main discussion of the paper on the C11 model, other AGB models can have notable effects on abundance trends at ***
-
-Because the predictions of the AGB yield models I consider are dwarfed by the
-required CCSNe C production to match observations (see Fig.
-***), I briefly explore here the effects of variations in AGB models affect abundance trend predictions when these models are amplified to match observational [C/MG]-[Mg/Fe] trends.
-
-While most models are well represented by our AGB-fraction formalism, V13 presents a challenge as the predicted solar yield is much lower than the lower metallicity predictions, requiring the solar value to be a certain fraction forces us to amplify the yields by an unreasonable about (of order 10-30times) to reach the same $f_{\rm AGB}$ as other models.
-Thus, I instead calculate $f_{\rm AGB}$ at a metallicity of ...
-for this model.
+As I focus on constraining relative yields, I neglect O and Mg yield variations in the main text.
+There is substantial variation in Mg predictions (see Fig.
+\ref{fig:y_mg}).
+Most models predict relatively flat Mg trends with metallicity (even with rotating models from \citealt{LC18}).
+Hoever, the variation is significant and my adopted $\Yoc$ yield is much higher than most models.
+This is a known problem (see \citet{emily+21}).
+CCSNe models overpredict O or underpredict Mg, and the resolution is still unknown.
+My results are, however, independent of whether the CCSNe element is O or Mg.
+
+While I focus the main discussion of the paper on the C11 model, other AGB models can impact abundance trends when $f_{\rm AGB}$ becomes larger.
+Here, I briefly explore here the effects of variations in AGB models affect abundance trend predictions when these models are amplified to match observational [C/MG]-[Mg/Fe] trends. 
+See Fig \ref{fig:fagb2}.
 
@@
 As our set of observations do not appear to reverse, this indicates that C yields likely stay positive even at slightly super-solar, so models like V13 are a poor match to observations.
-Plot of age metallicity relationship?
+
+In Fig. \ref{fig:fe_ia}.
+
+I leave exploration of the age-metallicity relation for C to future work.
 
@@
     \caption[Alternate AGB models]{Same as Figure \ref{fig:agb_sims} except where $f_{\rm agb}=0.2$. When yields are amplified, chaos ensues.}
+    \label{fig:fagb2}
 \end{figure}
@@
     }
+    \label{fig:y_mg}
 \end{figure}
@@
     \caption[Adjusting type Ia iron]{Similar to Figure \ref{fig:agb_sims} except with variations of the SNeIa iron fraction}
+    \label{fig:fe_ia}
 \end{figure}
@@
 
-\label{lastpage}
 \end{document}

### 2023-04-13 thesis/tex/main.tex
next edits

@@
 
-% \usepackage{fancyhdr}
-% \pagestyle{fancy}
-% \fancyhead{}
-% \fancyhead[RO,RE]{Carbon Galactic Nucleosynthesis}
 \pagestyle{plain}
@@
 
-\newcommand{\citetjack}{Roberts et.\ al (2023, in preperation)}
-\newcommand{\citepjack}{(Roberts et.\ al 2023, in preperation)}
-\newcommand{\citealtjack}{Robert et.\ al 2023, in preperation}
+\newcommand{\citetjack}{Roberts et.\ al (2023, in prep.)}
+\newcommand{\citepjack}{(Roberts et.\ al 2023, in prep.)}
+\newcommand{\citealtjack}{Robert et.\ al 2023, in prep.}
+
+\newcommand{\about}[1]{${\sim} #1$}
 
@@
        Project Advisor: Professor David H. Weinberg, Department of Astronomy
-       % Rolando Vald\'es Aguilar\\
        \vfill
@@
 % context
-Stellar evolution models provide uncertain predictions for elemental yields due to our limited understanding of stellar physics. 
+Stellar evolution models provide uncertain predictions for elemental yields due to uncertainties in stellar physics.
 % aims
 Here, I constrain the nucleosynthetic yields of C using multizone Galactic chemical evolution models.
-% background
-Massive star evolutionary models predict a direct relationship beteen population-averaged C yields and stellar metallicity, but AGB star models predict an inverse relationship.
 % results
-Consequently, matching the slopes of the \caah\ and \caafe\ relationships in a sample of APOGEE subgiant stars requires an $\sim 80\%$--$20\%$ balacen between massive stars and AGB stars, respectively.
+By matching the slopes of the \caah\ and \caafe\ relationships in a sample of APOGEE subgiant stars, I find that CCSNe and AGB stars contribute \about{80\%} and \about{20\%} of total C production respectively.
 % 
-To also match the normailzation of the triends, I estimate the CCSNe C/Mg yield ratio $\Ycc/\Yoc = 1.57 + 0.59 \left(Z/Z_\odot\right)$, which explains the \caah~when including the AGB C contribution.
+To also match the normalization of the trends, I estimate the CCSNe C/Mg yield ratio $\Ycc/\Yoc = 1.57 + 0.59 \left(Z/Z_\odot\right)$, which explains the \caah\ trend when including the AGB C contribution.
 %
-Variations in the star formation history impact the low [Mg/Fe] tail of the [C/Mg]-[Mg/Fe] relation, but are only small pertubations compared to the observed scatter.
-Most of the scatter in \caah\ can be attributed to measurment errors and radial migration.
+Variations in the star formation history only slightly impact the low [Mg/Fe] tail of the [C/Mg]-[Mg/Fe] relation.
+However, most of the scatter in the \caah\ distribution can be attributed to measurement errors and radial migration.
 % 
-Due to the degeneracy between the normaliztion of elemental yields and the strength of mass-loading in Galactic outflows, I constrain only the {\it relative} yield of C and Mg from a simple stellar population and the metallicity dependence thereof.
-While measurments of gas-phase C abundances are difficult, my model is broadly consistant with the [C/O]-[O/H] trend observed in compiled literature measurments.
+Due to the degeneracy between the normalization of elemental yields and the strength of mass-loading in Galactic outflows, I constrain only the {\it relative} yield of C and Mg from a simple stellar population and the metallicity dependence thereof.
+While measurements of gas-phase C abundances are challenging, my model is broadly consistent with the [C/O]-[O/H] trend observed in compiled literature measurements.
 
@@
 
-I also would not have made it here without all the additional support from my friends and family.
+I also would not have made it here without all the support of my friends and family.
 Eric, even across the country, you have always been a point of support and stability, and I am always happy to be around you.
 Anya, you are a wonderful friend and I cannot thank you enough for your support this year.
-I love so many people in our department who have just been friends and positive support: Kaia, Maria, Autumn, Simon, Mary, Aaliyah, Sanskruti, Alyssa, Harrison, Denis, and so many others. 
+I love so many people in our department who have just been friends and have positive support: Kaia, Maria, Autumn, Simon, Mary, Aaliyah, Sanskruti, Alyssa, Harrison, Denis, and so many others. 
 Finally, I thank my family for supporting me through a challenging year, and Arya for being such a loveable doodle.
@@
 At the core of GCE models are stellar yields---the amount of each chemical element stars produce (or destroy).
-The chemical elements are produced in different amounts by different stars, leaving traces of Galaxy's evolutionary history.
-Through \textit{Galactic Archeology}, we can reconstruct the history of our galaxy by investigating the clues left in reminants of the past \citep{Weinberg+22, emily+19}.
+Each elements is produced in different amounts by different stars, leaving traces of the Galaxy's evolutionary history.
+Through \textit{Galactic Archeology}, we can reconstruct the history of our galaxy by investigating clues left behind in stars.
 
 Here, I aim to understand C enrichment---where it is produced and how its abundances evolve over time.
-Why study carbon?
 C is unique nucleosynthetically, one of few light elements (along with N) produced in asymptotic giant branch (AGB) stars \citep[e.g.][]{jennifer19, KL14}.
-C and N are well studied elements since they are easy to observe in stellar spectra, even at the lowest metallicities \cite[e.g.][]{fabbian+09, nissen+14, lambert81, laird85, lambert86}.
+C and N are well-studied elements since they are easy to observe in stellar spectra, even at the lowest metallicities \cite[e.g.][]{fabbian+09, nissen+14, lambert81, laird85, lambert86}.
 Additionally, C and N are used as age indicators in red giant branch stars \citep{martig16, MG15, hasselquist19, vincenzo+21}.
@@
 Gas-phase [C/O] ratios---observed in very low metallicity, high redshift damped Lyman-alpha systems (DLAs)---decrease with increasing [O/H] \citep{FN15, cooke+17}.
-Then, [C/O] increases above $\rm [O/H] \approx 1$ (\citealt{berg+19}; see discussion in \S\ref{sec:gas}).
-While we know C is produced in AGB stars and core collapse supernovae (CCSNe), we still have limited understanding of the magnitude and metallicity-dependence of each process.
+Then, [C/O] increases above $\rm [O/H] \approx -1$ (\citealt{berg+19}; see discussion in \S\ref{sec:gas}).
+While we know C is produced in AGB stars and core-collapse supernovae (CCSNe), we still have a limited understanding of the magnitude and metallicity-dependence of each process.
 
 Despite their central role in GCE models, nucleosynthetic yields predicted by stellar evolution models are rife with uncertainties.
-The production rates of elements in stars are shaped by poorly understood processes, including mass loss, opacity, nuclear reaction rates, rotational mixing, and convection\citep{KL14,ventura+13, LC18}.
-Additionally, changes in massive stars' explodability introduce further variation in population averaged-yields \citep{emily+21}.
-
-GCE models typically use unmodified nucleosythetic predictions and attempt to create models matching observations by varying the star formation history (SFH) and other evolutionary parameters.
-I choose to introduce C yields as a free parameter, determining which yield prescriptions reproduce Galactic abundance trends.
+The production rates of elements in stars are shaped by poorly understood processes, including mass loss, opacity, nuclear reaction rates, rotational mixing, and convection \citep{KL14,ventura+13, LC18}.
+Changes in massive stars' explodability also introduce further variation and uncertainty in population-averaged yields \citep{emily+21}.
+
+GCE models typically use unmodified nucleosynthetic predictions and attempt to create models matching observations by varying the star formation history (SFH) and other evolutionary parameters.
+Here, I introduce C yields as an additional free parameter, determining which yield prescriptions reproduce Galactic abundance trends.
 \cite{james+23} examined similar GCE models of N, an element whose production is closely related to C.
-\cite{james+23} found trends in N and O abundances can be explained by the metallicity dependence of relative N and O yields.
+\cite{james+23} found that trends in N and O abundances can be explained by the metallicity dependence of relative N and O yields.
 Here, I extend their models to C and show that similar constraints on C and O relative yields can be obtained from observed abundance ratios.
-Additionally, I assess which yield prescriptions reproduce Galactic abundance trends, while assessing the impact of SFH and GCE model assumptions.
+Additionally, I assess which yield prescriptions reproduce Galactic abundance trends while assessing the impact of GCE model assumptions, such as SFH and outflow mass loading.
 
@@
 When a star enters the red giant branch (RGB), material from the CNO-processed core is mixed with the envelope in first dredge up (FDU), enhancing N and depleting C \citep{iben67, vincenzo+21,KL14}.
-Measurements of these evolved stars'  atmospheres will no longer reflect birth abundances.
-Additionally, gas-phase measurments of C are extremely limited as C lacks strong lines in HII regions \citep{skillman+20}.
+Measurements of these evolved stars'  atmospheres will no longer reflect their birth abundances.
+Additionally, gas-phase measurements of C are extremely limited as C lacks strong lines in HII regions \citep{skillman+20}.
 
@@
 Their phosphoric abundances should thus represent their birth composition.
-In Fig.
-\ref{fig:subgiants}, I plot this sample, selected by criteria in (see Appendix \ref{sec:jack}; \citealtjack).
-These emperical resolults contain information on the relative C and Mg yields, which I use later in this work.
+In Fig.~\ref{fig:subgiants}, I plot this sample, selected by the criteria in Roberts et al.
+(2023, in prep; see Appendix \ref{sec:jack}).
+These empirical results contain information on the relative C and Mg yields, which I use later in this work.
 
@@
     \caption[APOGEE Subgiants]{The [C/Mg] ratio against [Mg/H] (top) and [Mg/Fe] (bottom) for the \citetjack~sample of APOGEE subgiants.
-On the top, I plot high-$\alpha$ stars in blue and low-$\alpha$ stars in orange using the seperation defined in Equation \ref{eq:high_alpha}.
-On the bottom, I colorcode stars according to their [Mg/H] abundance.}
+On the top, I plot high and low-$\alpha$ stars in blue and orange, using the separation defined in Equation \ref{eq:high_alpha}.
+On the bottom, I color-code stars according to their [Mg/H] abundance.}
     \label{fig:subgiants}
 \end{figure}
+
 \chapter{Nucleosynthesis}
@@
 Theoretical models of stellar nucleosynthesis provide the starting point of this investigation.
-I focus on three primary nucleosynthetic pathways: Asymptotic giant branch (AGB) stars, core collapse supernovae (CCSNe), and type Ia supernovae (SNe Ia).
+I focus on three primary nucleosynthetic pathways: asymptotic giant branch (AGB) stars, core-collapse supernovae (CCSNe), and type Ia supernovae (SNe Ia).
 Each process has unique timescales and yields, traceable through the tools of GCE.
-While C is only produced in AGB stars and CCSNe, comparing C to Fe, which is produced in SNe Ia, adds a valuable constraint on the delay-time distribution (DTD) of C enrichment.
-
-When a single stellar population (SSP) forms, CCSNe are the first enrichment events.
-CCSNe provide light elements such as C, O, and Mg and heavier elements such as Fe and beyond.
+I compare C, produced in CCSNe and AGB stars, to Mg and Fe as tracers of CCSNe and SNe Ia respectively.
+
+When a single stellar population (SSP) forms, CCSNe are the first enrichment event.
+CCSNe  explode within $\lesssim 40$ Myr, providing light elements (C, O, and Mg) and heavier elements (Fe and beyond).
 Metallicity-independent yields from CCSNe are the only statistically significant source of O and Mg ($\alpha$ elements).
-Next, low mass stars begin to reach the end of their lives.
-The dying breaths of AGB stars are known to be important sources of C, N, and neutron capture elements.
+Next, low-mass stars begin to reach the end of their lives.
+By shedding their outer layers, AGB stars are important sources of C, N, and neutron capture elements.
 Finally, white dwarfs explode, releasing Fe and other iron-peak elements.
@@
 where $M_{\rm ejected}$ and $M_{\rm X, ejected}$  are the total ejected mass of the envelope and the element X, respectively.
-
-Though per-star yields are necessary to compute AGB star enrichment rates in GCE models, IMF-averaged\footnote{IMF: Initial Mass Function} yields are useful in interpreting their predictions.
+For example, if a 1 $M_\odot$ star has $\tilde{y}_{\rm C} = 10^{-3}$, then the star will add $10^{-3}\ M_\odot$ of C to the interstellar medium (ISM).
+Although per-star yields are necessary to compute AGB star enrichment rates in GCE models, IMF-averaged\footnote{IMF: Initial Mass Function} yields are useful in interpreting their predictions.
 For a yield $y$ from a star of mass M and initial metallicity $Z$, the IMF-averaged yield is given by
 \begin{equation} \label{eq:imf-yield}
-    y_{\rm X}^{\rm proc}(Z) = 
+    y_{\rm X}(Z) = 
     \int_{M_{\rm min}}^{M_{\rm max}} 
-    \tilde{y}_{\rm X}^{\rm proc}(M, Z)
+    \tilde{y}_{\rm X}(M, Z)
     \frac{dN}{dM}  \ dM
 \end{equation}
-where ${dN}/{dM}$ is the normalized IMF, $M_{\rm min}$ and $M_{\rm max}$ are the minimum and maximum mass of stars, which I take to be $0.08 M_{\sun}$ and $100 M_{\sun}$ respectively.
+where ${dN}/{dM}$ is the normalized IMF, and $M_{\rm min}$ and $M_{\rm max}$ are the minimum and maximum mass of stars, which I take to be $0.08 M_{\sun}$ and $100 M_{\sun}$ respectively.
 For AGB stars, the yields are truncated above 8 $M_{\odot}$.
-To calculate the IMF-weighted net yields of C, I use the Versatile Integrator for Chemical Evolution code (\VICE\footnote{\VICE~is available at \url{https://github.com/giganano/VICE}}).
-
-In the interest of focusing on carbon yields, I hold yields of other elements fixed. 
-I adopt yields from \citet{james+21, james+23}.
-In Table \ref{tab:fiducial_mod}, I tabulate yield values, in units of a stellar population's birth mass.
+To calculate the IMF-weighted net yields, I use the Versatile Integrator for Chemical Evolution code (\VICE\footnote{\VICE~is available at \url{https://github.com/giganano/VICE}}).
+
+To focus on C yields, I adapt the yield choices of other elements from \citet{james+21, james+23}.
+Table \ref{tab:fiducial_mod} contains my fiducial yields, in units of a SSP's birth mass.
 Also following \citet{james+21, james+23}, I take the SNeIa delay time distribution to be a
-$t^{-1.1}$ law suggested by the observations of \citet{maoz+12}.
+$t^{-1.1}$ power-law suggested by the observations of \citet{maoz+12}.
 
@@
 	\centering
-    \caption[Fiducial Model]{Yields for the fiducial model}
+    \caption[Fiducial Model]{Yields for the fiducial model in units of SSP birh mass. See \S\ref{sec:agb} for the definition of C11.}
 	\label{tab:fiducial_mod}
@@
 In an AGB star, two competing processes determine the outcome of C production: third dredge up (TDU) and hot bottom burning (HBB).
-TDU accompanies thermal pulsations in AGB stars.
+TDU accompanies thermal pulses in AGB stars.
 During a TDU event, material from the CO core is mixed with material exposed to partial He-shell burning, increasing C and O abundances in the envelope \citep{KL14}.
+If this envelope is lost during the AGB phase, then C yields are enhanced.
 HBB is the activation of proton capture reactions, and the CNO cycle%
@@
 at the base of the convective envelope.
-Because the $^{14}$N(p, $\alpha$) proton capture is the slowest component of the CNO cycle \citep{solar-fusion}, the CNO cycle converts nearly all \isotope[12]{C} into \isotope[14]{N}.
+Because the $^{14}$N(p, $\gamma$) proton capture is the slowest component of the CNO cycle \citep{solar-fusion}, the CNO cycle converts nearly all \isotope[12]{C} into \isotope[14]{N}.
 As a result, when both TDU and HBB occur, \isotope[12]{C} yields are lowered (see discussion in \citealt{james+23} and \citealt{ventura+13}).
 
-In this work, I explore four different sets of AGB star yield tables from literature, providing well sampled grids in metallicity and mass for use in chemical evolution models. 
+In this work, I explore four different sets of AGB star yield tables from literature, providing well-sampled grids in metallicity and mass for use in chemical evolution models. 
 \begin{itemize}
@@
     \item K10: \citet{karakas10}
-    \item V13: \citet{ventura+13,ventura+14,ventura+18}
+    \item V13: \citet{ventura+13,ventura+14,ventura+18, ventura+20}
     \item K16: \citet{KL16} \citet{karakas+18}
 \end{itemize}
-I use C11 as the fiducial AGB yield.
-
-Fig. \ref{fig:y_agb} compares the AGB C yield $\tilde{y}_\text{C}^\text{AGB}(M, Z)$ for each model I consider. 
-The yields may be negative when the birth abundance is higher than the C abundance of the material ejected back to the interstellar medium (ISM). 
+I use C11 table, amplified by a factor of 2.9, as the fiducial AGB yield.
+
+Fig.~\ref{fig:y_agb} compares the AGB C yield $\tilde{y}_\text{C}^\text{AGB}(M, Z)$ for each model I consider. 
+The yields may be negative if a star returns material to the ISM with a lower C abundance than the material the star was formed from.
 Most models agree on the qualitative shape of the net fractional AGB C yield---% 
-stars with mass $\sim 2--4 M_\odot$ have highest fractional C yields, with the mass of the peak increasing and overall yields decreasing with increasing $Z$.
-High mass, high $Z$ stars destroy \isotope[12]{C} due to HBB.
-
-In Fig. \ref{fig:agb-ssp}, we plot the total production of C by AGB stars as a function of SSP age.
-Effectively, this is equivalent to integrating Eq. \ref{eq:imf-yield} down to $M_{to}$, the turnoff mass for time $t$%
-\footnote{In our model, the mass-lifetime relation is
+stars with masses between \about{2~M_\odot} and \about{4~M_\odot} have the highest fractional C yields, with the mass of the peak increasing and overall yields decreasing with increasing $Z$.
+High mass, high $Z$ stars destroy \isotope[12]{C} because they experience both TDU and HBB, but HBB is much more efficient.
+
+In Fig.~\ref{fig:agb-ssp}, I plot the total production of C by AGB stars in a SSP at an age $t$. 
+Effectively, this is equivalent to integrating Eq.~\ref{eq:imf-yield} down to $M_{to}$, the turnoff mass for time $t$.
+({In our model, the mass-lifetime relation is
 $\log \tau_M = 1.02 - 3.57\log M + 0.90 \left(\log M\right)^2$,
 where $\tau_M$ is in Gyr,
-from \citet{larson74}.}.
-As the mass range $2\lesssim M \lesssim 4$ is most important for C production, the characteristic delay time is $\sim 1$Gyr.
-In contrast, Fe from SNeIa (plotted as the dashed black line in Fig \ref{fig:agb-ssp}) has a longer characteristic delay time.
-
-K10 and K16 weight C production more heavily towards massive stars resulting in a faster enrichment delay time, whereas the C11 and V13 models predict a slightly longer timescale with order 1 Gyr, but little to no C is produced more than 2 Gyr after a star formation event.
-This is in contrast to iron which is still produced by SNeIa up to 10 Gyr after a star formation event.
-As shown in the right panel of Fig. \ref{fig:agb-ssp}, with increasing $Z$, C enrichment occurs earlier, and C destruction in low mass stars leads to a declining C abundance at late times.
+from \citealt{larson74}.})
+As the mass range $2\lesssim M \lesssim 4$ is most important for C production, about half of C production occurs before \about{1} Gyr, similar to SNe Ia Fe. 
+K10 and K16 weight C production more heavily towards massive stars resulting in a faster enrichment delay time, whereas the C11 and V13 models predict a slightly longer timescale of \about{1} Gyr, but little to no C is produced more than 2 Gyr after a star formation event.
+This is in contrast to Fe whos production lasts up to 10 Gyr after a star formation event.
+As shown in the right panel of Fig.~\ref{fig:agb-ssp}, with increasing $Z$, C enrichment occurs earlier, and C destruction in low-mass stars leads to a declining C abundance at late times.
 
@@
  	    \includegraphics[scale=1]{agb_yields.pdf}
-        \caption[AGB C yields]{The net fractional AGB C yield ($\tilde{y}$) plotted as a function of initial stellar mass $M$.
-Metallicity is colorcoded according to the colorbar.
-I plot $\tilde{y}=0$ for reference.
+        \caption[AGB C yields]{The net fractional AGB C yield  plotted as a function of initial stellar mass $M$ and color-coded according to metallicity.
+The black dashed line shows $\tilde{y}=0$ for reference.
 Each panel represents yields from one of four AGB models: C11, K10, V13, K16 (see \S \ref{sec:agb}).
@@
 
-In Fig. \ref{fig:yagb-z}, I plot the IMF-averaged C yields for each AGB model as a function of metallicity $Z$.
-V13 differs that it shows a non-monotonic metallicity dependence. However, this effect is only form models with $\log Z/Z_\odot \lesssim -1$.
-Otherwise, models only differ in the yield normalization and strength of metallicity dependence. All models predict yields within a factor of $\sim 2$.
+Fig.~\ref{fig:yagb-z} shows IMF-averaged C yields for each AGB model as a function of metallicity $Z$.
+V13 differs in that it shows a non-monotonic metallicity dependence. However, this effect is only for models with $\log Z/Z_\odot \lesssim -1$.
+Otherwise, models differ only in their yield normalization and metallicity dependence. All models predict yields within a factor of \about{2} for fixed metallicity.
 For example, the three models C11, K10, and K16 predict $y_\text{C}^\text{AGB}$ to be between 0.006 and 0.008 at solar metallicity, but C11 has a much shallower metallicity dependence than the K10 and K16 models.
-V13 instead predicts a yield $\sim 0.004$.
+V13 instead predicts a yield \about{0.004}.
 
@@
 
-In Fig. \ref{fig:y_cc}, I plot calculations of the IMF-integrated yields, using Eq. \ref{eq:imf-yield} (computed using \VICE's \texttt{vice.yields.ccsne.fractional} function). 
+In Fig.~\ref{fig:y_cc}, I plot calculations of the IMF-integrated yields, defined with Eq.~\ref{eq:imf-yield} (computed using \VICE's \texttt{vice.yields.ccsne.fractional} function). 
 CCSNe models predict a wide range of C yields, spanning almost 1 dex. 
@@
 Our fiducial model's steep metallicity dependence near $Z\approx Z_\odot$ could be explained by rotation.
-
-I show the C11 model for comparison in Fig.
-\ref{fig:y_cc}.
-Especially at $Z\approx Z_\odot$, most CCSNe models would dominate C production.
-I will later show that empirically, CCSNe also dominate C production.
-
-On the bottom of Fig. \ref{fig:y_cc}, I also show the CCSNe-[C/Mg] ratio, defined by
+Fig.~\ref{fig:ycc} shows the C11 model for comparison on the top.
+Especially at $Z\approx Z_\odot$, most CCSNe models dominate AGB C production.
+I will later also show empirically that CCSNe should dominate C production.
+
+On the bottom of Fig.~\ref{fig:y_cc}, I also show the CCSNe-[C/Mg] ratio, defined by
 \begin{equation}\label{eq:c_mg_cc}
@@
 \end{equation}
-In other words, ${\rm [C/Mg]^{CC}}$ describes what [C/Mg] would be if CCSNe were the only process producing C.
+${\rm [C/Mg]^{CC}}$ describes what [C/Mg] would be if CCSNe were the only process producing C.
 Once again, different CCSNe models span a large range in [C/Mg]. 
 I chose to instead parameterize $\Ycc$ to enable agreement with observations, as most CCSNe models fail to achieve near-solar [C/Mg].
-
 Assumptions about the explodability landscape affect C and Mg production.
-Increasing the fraction of stars which explode increases $\Ycc$, as stars which directly collapse do not contribute to explosive yields \citep{emily+21}.
+Increasing the fraction of stars that explode increases $\Ycc$, as stars that directly collapse do not contribute to explosive yields \citep{emily+21}.
 However, C is relatively unaffected by the black-hole landscape, as very massive stars contribute carbon through enriched winds.
-Since Mg is formed deeper in the core of massive stars, the Mg yield drops much more steeply, so models where few stars explode (S16/W18) result in much higher [C/Mg].
-
-CCSNe models also struggle to reach solar [O/Mg], either due to overproduction of O or underproduction of Mg \citep{emily+21}.
-Here, I assume ${\rm [O/Mg]} = 1$, which is not compatible with CCSNe models but is consistent with observations \cite{Weinberg+19, Weinberg+22}.
+Since Mg is formed deeper in the core of massive stars, the Mg yield drops much more steeply, so models, where few stars explode (S16/W18), result in much higher [C/Mg].
+
+CCSNe models also do not reach [O/Mg] due to overproduction of O, or underproduction of Mg, or both \citep{emily+21}.
+Here, I assume ${\rm [O/Mg]} = 0$, which is not compatible with CCSNe models but is consistent with APOGEE observations \citep{Weinberg+19, Weinberg+22}.
 
@@
         C yields from massive stars.
-        Top: The IMF-weighted CCSNe yield of C a function of metallicity.
-        Bottom: The CCSNe [C/Mg] abundance ratio, defined in Eq. \ref{eq:c_mg_cc}. The black line represents the C yield of the fiducial model,
-    $\Ycc = 0.0028 + 0.001 (Z/Z_{\odot})$. 
+        \textbf{Top:} The IMF-weighted CCSNe yield of C as a function of metallicity.
+        \textbf{Bottom:} The CCSNe [C/Mg] abundance ratio, defined in Eq.~\ref{eq:c_mg_cc}. The black line represents the C yield of the fiducial model,
+    $\Ycc = 0.0028 + 0.001 (Z/Z_{\odot})$. Yields are shown for tables from 
     \citet[red triangles]{WW95}, \citet[orange squares and diamonds]{sukhbold+16}, 
     \citet[green stars]{NKT13}, and \citet[blue circles]{LC18}.
-\citet{sukhbold+16} report yields for different black hole landscales, while \citet{LC18} provide yields at different roational velocities.
-The pink line represents the C11 AGB model.
+\citet{sukhbold+16} report yields for different black hole landscapes, while \citet{LC18} provide yields at different rotational velocities.
+In the top panel, the pink line denotes $\Ycagb$ from C11 for comparison.
 }
@@
 In the presence of metal-poor gas accretion and feedback-driven outflows, galaxies reach an equilibrium abundance in which production of new metals is balanced by losses to new stars and outflows \citep{larson72, dalcanton07, FD08, PS11, lilly13}.
-While our galaxy is likely not in perfect equilibrium or described by a single, homogenous chemical region, the equilibrium approximation is nevertheless useful in understanding yields and metallicity dependence \citep[e.g.][]{james_dwarf,james+23,WAF17}.
+While our galaxy is likely not in perfect equilibrium or described by a single, homogeneous chemical region, the equilibrium approximation is nevertheless useful in understanding yields and metallicity dependence \citep[e.g.][]{james_dwarf,james+23,WAF17}.
 
 I assume a simple ``one-zone'' chemical evolution model \cite[e.g.][]{tinsley80, pagel09, matteucci21}.
-The gas and stars are homogenously and instantaneusly mixed, so spacial dependence is neglected.
-
-I define $M_{X}$ to be the mass of element X in the gas phase, $\dot{M}_\star$ to be the star fomation rate (in M$_\odot$ yr$^{-1}$), and $\eta$ to be the mass loading factor $\eta\equiv\dot{M}_{\rm outflow}/\dot{M}_\star$ representing the strength of outflows.
-SSPs return a fraction $r$ of their birth mass back to the ISM, due to ejected stellar envelopes. $r\approx0.4$ for a \citet{kroupa01} IMF.
-Given the IMF-weighted yield of Mg $y_{\rm Mg}$, the rate of change in the ISM mass of Mg $\dot{M}_{\rm Mg}$ is a simple sum of sources and sinks,
-\begin{equation}
-    \dot{M}_{\rm Mg} = \dot{M}_{\rm Mg,~new} - \dot{M}_{\rm Mg~remnants} - \dot{M}_{\rm Mg,~outflows},
+Newly produced metals are homogeneously and instantaneously mixed, so spatial dependence is neglected.
+I define $M_{X}$ to be the mass of element X in the gas phase, $\dot{M}_\star$ to be the star formation rate (in M$_\odot$ yr$^{-1}$), and $\eta$ to be the mass loading factor $\eta\equiv\dot{M}_{\rm outflow}/\dot{M}_\star$ (representing the strength of outflows).
+SSPs return a fraction $r$ of their birth mass back to the ISM, due to ejected stellar envelopes. ($r\approx0.4$ for a \citealt{kroupa01} IMF.)
+Given the IMF-averaged yield of Mg $y_{\rm Mg}$, the rate of change in the ISM mass of Mg $\dot{M}_{\rm Mg}$ is a simple sum of sources and sinks,
+\begin{equation}
+    \dot{M}_{\rm Mg} =  y_{X}\dot{M}_\star - \dot{M}_{\rm Mg~remnants} - \dot{M}_{\rm Mg,~outflows},
 \end{equation}
@@
 In terms of the return mass fraction of stars $r$, the mass lost to remnants is $Z_X (1-r)\dot{M}_\star$.
-And, the outflows deplete a mass $Z_X \eta\dot{M}_\star$.
-Substituting om fpr $\eta$ and $r$,
+And, the outflows deplete mass at a rate $Z_X \eta\dot{M}_\star$.
+( I assume the composition of outflows is the same as the ISM.) Substituting for $\eta$ and $r$,
 \begin{equation}
@@
 \end{equation}
-Assuming an exponentially declining star formation history $\dot{M}_\star \propto e^{-t/\tau_{\rm sfh}}$, the equilivrium abundance is derived analytically by setting $\dot{Z}_{Mg}=0$.
+Assuming an exponentially declining star formation history $\dot{M}_\star \propto e^{-t/\tau_{\rm sfh}}$, the equilibrium abundance is derived analytically by setting $\dot{Z}_{Mg}=0$.
 \begin{equation}\label{eq:z_eq}
-    Z_{\rm Mg}^{\rm eq}(R) = \frac{y_{\rm Mg}}{1 + \eta(R) - r - \tau_\star / \tau_{sfh}}
-\end{equation}
-In the special case of constant star formation, $\tau_{\rm sfh}\to\infty$, simplifying the denominator to $1+\eta-r$.
-
-While Equation \ref{eq:z_eq} can be applied to CCSNe C, the delayed nature of AGB C can complicates thes expression. Instead, using a DTD-integrated yield, $\langle \Ycagb \rangle$ enrichment is
-\begin{equation}
-    \langle \Ycagb\rangle = \frac{\int_0^T \tilde{y}_{\rm C}^{\rm agb}(M, Z) \dot{M}_\star(T - t) \frac{dN}{dM} \frac{dM}{dt} dt  }{ \dot{M}_\star \int_0^T \frac{dN}{dM} \frac{dM}{dt} dt}
-\end{equation}
-Eq. \ref{eq:z_eq} becomes
+    Z_{\rm Mg}^{\rm eq}(R) = \frac{y_{\rm Mg}}{1 + \eta(R) - r - \tau_\star / \tau_{sfh}},
+\end{equation}
+where $\tau_{\star}$ is the star formation rate.
+In the special case of constant star formation, $\tau_{\rm sfh}\to\infty$, the denominator simplifies to $1+\eta-r$.
+
+While Equation \ref{eq:z_eq} can be applied to CCSNe C, the delayed nature of AGB C can complicate the expression.
+Instead, I use an effective yield, which can be expressed as an integral over the DTD,
+\begin{equation}
+    \langle \Ycagb\rangle = \frac{\int_0^T \tilde{y}_{\rm C}^{\rm agb}(M, Z) \dot{M}_\star(T - t) \frac{dN}{dM} \frac{dM}{dt} dt  }{ \dot{M}_\star \int_0^T \frac{dN}{dM} \frac{dM}{dt} dt}.
+\end{equation}
+Eq.~\ref{eq:z_eq} then becomes
 \begin{equation}
@@
 \end{equation}
-Taking the ratio of $Z_{\rm C}$ and $Z_{\rm Mg}$, 
+And the equilibrium C/Mg abundance ratio is
 \begin{equation}\label{eq:z_co}
@@
 \end{equation}
-
 Analogous to \cite{james+23} arguments about N, the trends in abundance ratios are set by yield ratios in these GCE models.
-The effect of other GCE parameters (most importaintly $\eta$) cancels.
+The effect of other GCE parameters (most importantly $\eta$) cancels.
 As a consequence, yield ratios should establish abundance ratio trends in models which assume a different normalization of element yields and mass-loading (see discussion below).
 This argument can also be inverted to infer  yields from abundance ratio trends.
-To the extent that observed C and Mg trends reflect the equilibrium abundances in different Galatic regions, we can infer the CCSNe yield given an assumed AGB star yield (or vice versa).
-Inffering $\Ycc$ from $\Ycagb$,
+To the extent that observed C and Mg trends reflect the equilibrium abundances in different Galactic regions, we can infer the CCSNe yield given an assumed AGB star yield (or vice versa).
+Inferring $\Ycc$ from $\Ycagb$,
 \begin{equation}
@@
 Furthermore, in Eq.~\ref{eq:z_eq}, an increase in both $y_{\rm Mg}$ and $\eta$ would leave $Z_{\rm Mg}^{\rm eq}$ unchanged.
-My models here are unable to distinguish the overall scaling of yields and outflow mass loding, and choosing to keep $y_{\rm C}$ fixed reduces unnecessary free parameters.
+My models here are unable to distinguish the overall scaling of yields and outflow mass loading, and choosing to keep $y_{\rm C}$ fixed reduces unnecessary free parameters.
 %
@@
 \end{subequations}
-This ratio results in an equilibrium abundance ${\rm [C/Mg]} = -0.09$, which is consistant with the \citetjack subgiant sample and is within $\sim 20\%$ of the solar C/Mg mixture from \citet{asplund+09}.
+This ratio results in an equilibrium abundance ${\rm [C/Mg]} = -0.09$, which is consistent with the \citetjack~subgiant sample and is within \about{20\%} of the solar C/Mg mixture from \citet{asplund+09}.
 
 In \S\ref{sec:f-z-models}, I will show that none of the four AGB yield sets (C11, K10, V13, K16) produce enough C relative to this $\Ycc$ value.
-So, I choose to introduce process factors, $\alpha_{\rm AGB}$, and $\alpha_{\rm CC}$ which denote a multiplicitave scaling of $\Ycc$ and $\Ycagb$ respectively.
+So, I introduce normalization factors, $\alpha_{\rm AGB}$, and $\alpha_{\rm CC}$ which denote a multiplicitave scaling of $\Ycc$ and $\Ycagb$ respectively.
 \begin{subequations} \label{eq:alpha}
@@
 I show the values of $\Ycc$ I obtain from the subgiant sample in Fig.~\ref{fig:analytic}.
-From a regression analysis, I suggest here that
+From regression analysis, I suggest here that
 \begin{equation}
@@
 I assume equilibrium and $3\times {\rm C11}$ AGB yields (orange curve, see discussion in Section \ref{sec:equilibrium}).
-The binned medians and median absolute devation (divided by $\sqrt{N}$) are blue points.
+The binned medians and median absolute deviation (divided by $\sqrt{N}$) are blue points.
     }
@@
 
+\section{Uncertainties}
+
+I only perform this analysis on the C11 yields because C11 has yields tables more finely sampled in metallicity than the other three AGB yield tables.
+As the metallicity range of the data is small ($-0.4\lesssim {\rm [Mg/H]} \lesssim 0.4$), other models are more challenging to interpret in this range.
+Furthermore, the APOGEE observations may have systematics, and other measurements of C abundances \citep[e.g.][]{vincenzo+21} have slight disagreements in the overall shape of the trend (see \S\ref{sec:jack}).
+So, this expression of $\Ycc/\Yoc$ depends on the chosen AGB yield table, the AGB fraction, and the dataset. 
+Additionally, these yields will be systematically biased if the galaxy is out of equilibrium, for example due to a recent starburst (Isern et al.
+19; Mar et al.
+19).
+Further exploration could investigate the magnitude of these uncertainties, but I find that the qualitative conclusions are similar despite substantial variations in the assumptions here.
+
+\chapter{The Multizone Model}\label{sec:vice}
+
+Classical, ``one-zone'' models of chemical evolution assume instantaneous mixing of metals in the star-forming ISM \citep[e.g.][]{matteucci21}.
+This simple framework is a poor approximation for the Milky Way.
+The Galaxy evolves ``inside out''---where star formation is higher towards the center and in the early universe \citep{bird+13}.
+Additionally, stars can migrate several kpc over their lifetimes, mixing together different chemical environments across the galaxy \citep{bird+12,sellwood+binney02}.
+For the rest of this paper, I focus on multizone models, which discretize the Galaxy into concentric annuli and allow stars to move between rings.
+Specifically, I make use of the \citet{james+21} (hereafter \JJ) model for the Milky Way, which runs using the publicly available Versatile Integrator for Chemical Evolution (\VICE).
+This model is described extensively in \JJ~and concisely summarized  in \citet{james+23}.
+Here, I provide a brief overview of the relevant model components.
+
+In the model, the Galaxy is divided into 200 rings, each 100 pc wide.
+Each ring has a separate stellar population and gas supply.
+Star formation ends beyond a radius $R=15.5$ kpc.
+I initially assume an ``inside-out'' Star Formation History (SFH), where the star formation surface density $\Sigma_\star$ is given by
+\begin{equation}
+    \dot{\Sigma}_\star \propto \left(1-e^{-t/\tau_{\rm rise}}\right) e^{-t/\tau_{\rm sfh}}.
+\end{equation}
+$\tau_\text{rise}=2$ Gyr describes when the star formation rate reaches a maximum, and $\tau_{\rm sfh}$ describes the decay timescale of star formation as a function of radius $R$.
+\JJ~derives $\tau_{\rm sfh}(R)$ through analysis of four integral field spectroscopy surveys in \cite{sanches20}.
+The star formation history is normalized such that the total stellar mass reaches $M_\star=5.17\times10^{10} {\rm M}_\odot$ \citep{LM15} and at each $R$ to match the stellar surface density gradient \citep{BHG16}.
+The gas inflow is calculated to maintain our chosen SFR for each radius and time. The gas-SFR law is based on an extension of a Kennicutt-Schmidt law \citep{kennicutt98}, motivated by 
+\begin{equation}
+\dot{\Sigma}_{\star} \propto \\
+\begin{cases}
+    {\Sigma}_{\rm gas} & 2\times 10^7 \leq \Sigma_{\rm gas} \\ 
+    {(\Sigma}_{\rm gas})^{3.6} & 5\times 10^6 \leq \Sigma_{\rm gas} < 2\times10^7 \\ 
+    {(\Sigma}_{\rm gas})^{1.7} & \Sigma_{\rm gas} < 5\times10^6 \\ 
+\end{cases}
+\end{equation}
+The scaling of this relationship varies with time due to the redshift dependence of $\tau_\star$ in molecular gas observed by \citet{tacconi18}. I assume a Kroupa IMF \cite{kroupa01}.
+
+\JJ\ accounts for radial migration by using the results of the \texttt{h277} hydrodynamical simulation \citep{christensen12, zolotov12, loebman12, BZ14}, with simulation parameters described in \citet{bird+21}.
+Each \VICE single stellar population (SSP) is matched to an \textit{analog} in \texttt{H277}, chosen to form at a similar time and radius $R$.
+By taking the change in radius $\Delta R$ of the analogs, the SSP move to their final radii with a $\sqrt{\text{time}}$ dependence.
+This relationship between displacement and time arises when migration proceeds as a consequence of the diffusion of angular momentum \citep{frankel18, frankel20}.
+I do not account for radial gas flows.
+Using the results of a hydrodynamical simulation without modification limits the free parameters in the model; however, I am limited to one dynamical history.
+The impact of the details of a galaxy's dynamical history on its chemical evolution is unknown, and I do not explore this question here.
+
+As the strength of outflows controls the resulting $\alpha$ abundances, \JJ~create a metallicity gradient by defining
+\begin{equation}
+\eta(R) = \frac{y_{\alpha}^{\rm CC}}{Z_{\alpha, \odot}} 10^{(-0.08\text{ kpc}^{-1})(R-4\text{ kpc})+0.3} + r - 1.
+\end{equation}
+This choice of $\eta(R)$ results in a [$\alpha$/H] gradient consistent with Milky Way observations \citep{james+21}.
+I explore models with reduced outflows in \S\ref{sec:outflows}; however, the overall scaling of yields is unknown and this model is insensitive to this normalization.
+
+\chapter{Multizone Model Results}
+\section{Data Selection}
+
+\citet{james+23} compare their model against the \cite{vincenzo+21} sample of APOGEE \citet{apogee17} red giants whose C and N abundance have been corrected for mixing process using MESA stellar evolution models.
+I instead use the \citetjack~sample of APOGEE subgiants.
+Subgiant stars have not undergone FDU, so their atmospheric C and N abundances are still reflective of their birth abundances and do not need mixing corrections.
+I additionally only compare the models to the low-$\alpha$ sequence.
+The selection criteria and differences between the samples are described in Appendix \ref{sec:jack}
+
+\section{The Evolution of C Across the Galaxy and Through Time}
+
+Here, I present the time evolution of our fiducial model.
+In the next sections, I will discuss the choice of parameters and agreement with observations.
+Our fiducial model uses the C11 AGB yield tables (see \S\ref{sec:agb}, and Table \ref{tab:fiducial_mod}), and I amplify the C11 yields by a factor of 2.9 so that $f_{\rm AGB} = 0.2$.
+
+The fiducial model has the following qualitative characteristics of its C yields: (a) C is predominantly produced in CCSNe, (b) CCSNe produce more C at higher metallicities, and (c) AGB stars produce less carbon at higher metallicities.
+
+The evolution proceeds as follows.
+Initially, CCSNe dominate production.
+As $\Ycc$ has strong metallicity dependence, [C/Mg] increases with time.
+Shortly thereafter, AGB stars contribute delayed C, increasing [C/Mg] even more steeply.
+As Mg begins to reach equilibrium, the [C/Mg] ratio plateaus as C approaches equilibrium.
+Finally, as $\Ycagb$ decreases or even becomes negative with higher metallicity, the [C/Mg] abundance may decline slightly.
+
+I show the time evolution tracks of the fiducial model in Fig.~\ref{fig:c_evo} for \caah~ and \caafe~.
+Comparing [C/$\alpha$] against [Mg/Fe] enables us to see the late-time evolution of C more clearly.
+Because of the extended DTD of SNeIa enrichment, [Fe/H] takes longer to reach equilibrium as half of Fe production comes from type-Ia supernovae, and the late time evolution is not as clustered as [$\alpha$/H].
+
+This is even more evident in the lower panel of Fig.~\ref{fig:c_evo}.
+While the \caah~trend reaches equilibrium at \about{5} Gyr, the \caafe~trend continues to evolve even until the present day, exposing the effect of the relative delay times of AGB stars and SNeIa.
+
+\begin{figure}
+\centering
+\includegraphics{evo_tracks.pdf}
+\includegraphics{evo_slices.pdf}
+\caption[C chemical evolution tracks]{
+    Time evolution of gas phase C abundances in our fiducial model.
+
+    Top: Evolutionary tracks parameterized by time at fixed Galactocentric radius in the \caah and \caafe planes.
+
+    Bottom: snapshots of the gas-phase \caah~and \caafe~trend, parameterized by radius at a fixed time.
+}
+\label{fig:c_evo}
+\end{figure}
+
+\section{Alternate Models}\label{sec:f-z-models}
+
+In Fig.~\ref{fig:agb_sims}, I compare the K10, K16, C11, and V13 yield models.
+Each model uses the published, unscaled yield tables.
+As the highest AGB yield at solar, K10 is only $\Ycagb=0.000585$, $f_{\rm AGB} \leq 0.12$ for all models.
+Massive stars dominate C production with unscaled yields.
+While it is easy to modify the AGB yields in my model, their small contribution reduces the effect.
+I leave a more detailed discussion of the effects of AGB models for Appendix \ref{sec:alt_agb} and use C11 yields hereafter.
+
+\begin{figure}
+\centering
+\includegraphics{oob_agb.pdf}
+\caption[AGB GCE Models]{
+    Stellar abundance trends in our model, assuming metallicity independent $\Ycc$.
+Colored lines quantify the median [C/Mg] in bins of [Mg/H] for our four AGB yield models from the literature (see \ref{sec:agb}).
+Black points and grey dashes represent the median and standard deviations in the \citetjack~sample.
+In the right panel, I show the trends only for stars where $-0.15\leq {\rm [Mg/H]}\leq -0.05$.
+}
+\label{fig:agb_sims}
+\end{figure}
+
+Next, I investigate adjustments to the AGB yield fraction $f_{\rm AGB}$ and the CCSNe metallicity dependence $\zeta$ in Fig.~\ref{fig:beta_f}.
+On the top panel of Fig.~\ref{fig:beta_f}, I plot models with varying $\Ycc$ metallicity dependence.
+As discussed in \S\ref{sec:equilibrium}, the \caah~trend is approximated by equilibrium, so the trends of these have steeper \caah~corresponding to steeper metallicity dependence.
+However, \caafe~is minimally affected by these changes since CCSNe are instantaneous in this model.
+
+Now, I vary the proportion of AGB contribution.  The AGB C production fraction is defined as
+\begin{equation}
+    f_{\rm AGB} \equiv \frac{\Ycagb}{\Yct}\Bigg\vert_{Z=Z_\odot},
+\end{equation}
+where  $\Ycagb$ includes the multiplicative factor $\alpha_{\rm AGB}$ as defined in Eq.~\ref{eq:alpha}.
+In the bottom panel of Fig.~\ref{fig:beta_f}, I plot three models with different AGB fractions while using C11 yields.
+The \caafe~relationship is set by $f_{\rm AGB}$ because a specific amount of C must be released at a delayed time in order to match the SNeIa production of Fe and increase [C/Mg] as [Mg/Fe] decreases to reproduce the data.
+Increased $f_{\rm AGB}$ results in a decreased slope in \caah, owing to the negative metallicity dependence of $\Ycagb$.
+So while \caah~alone cannot differentiate models which vary $f_{\rm AGB}$ and $\zeta$ correspondingly, \caafe~provides information on $f_{\rm AGB}$.
+So, I can use \caafe~to estimate $f_{\rm AGB}\approx 0.2$, and then choose $\zeta$ in order to match \caah.
+
+One source of theoretical uncertainty in this result is that the SNeIa yield and DTD have their own uncertainties.
+I discuss variations in $y_{\rm Fe}^{\rm Ia}$ in Appendix \ref{sec:alt_agb}, and find that the qualitative conclusions are largely unaffected.
+I therefore focus on the choices of $y_{\rm Fe}^{\rm Ia} = 0.00214$ choices from the fiducial model here.
+
+So, the scaling of the trend and metallicity dependence of C (as seen in
+the \caah~trend) gives information on the total C yield and the behavior of CCSNe (as the dominating producer of C); the \caafe trend exposes the delayed effect of C from AGB contribution.
+
 \begin{table}
 	\centering
-    \caption[AGB net solar IMF yields]{For each AGB yield set, our calculation of the effective SFH- and IMF-weighted C AGB yield, along with the multiplicative factor to reach an AGB contribution of 20.}
+    \caption[AGB net solar IMF yields]{For each AGB yield set, our calculation of the effective SFH- and IMF-weighted C AGB yield, along with the multiplicative factor reaches an AGB contribution of 20\%.}
 	\label{tab:alpha_agb}
@@
 
-\section{Uncertainties}
-
-I only perform this analysis on the C11 yields because the range of metallicities of the data (about [M/H] = -0.4, 0.4) only represents about 2 AGB models, relying heavily on our choice of extrapolation.
-C11 have a finer model grid, allowing us to have 5 theoretical predicted points within this metallicity range, allowing us to be more certain of our conclusion.
-
-I do note that this analysis fails to take into account selection effects and biases in APOGEE, and a more robust determination of the C yield.
-Not all C measurments of stars agree (see \S \ref{sec:jack})
-
-This formulation is degenerate in $\alpha_{\rm CC}$ until I estimate a better AGB fraction.
-As the seperation between the low and high alpha sequences can be used to estimate the delayed time contribution to C, using the model to estimate this value relies heavaly on the details of the SFH in addition to the
-I do give an estimate of the CCSNe yields, however this is dependent on our choice of $\eta$.
-Other choices of $\eta$ vary the value significantly in both magnitude and slope (as AGB contributions increase, I need less CCSNe C, however the CCSNe C must have a higher metallicity dependence to replicate the V21 data).
-
-\chapter{The Multizone Model}\label{sec:vice}
-
-Classical, ``one-zone'' models of chemical evolution assume instantanius mixing of metals in the star forming ISM \citep[e.g.][]{matteucci21}.
-This simple framework is a poor approximation for the Milky Way.
-The Galaxy evolves ``inside out''---where star formation is higher towards the center and in the early universe \citep{bird+13}.
-Additionally, stars can migrate several kpc over their lifetimes, mixing together different chemical environments across the galaxy \citep{bird+12,sellwood+binney02}.
-For the rest of this paper, I focus on multizone models, which discretize the Galaxy into concentric annuli and allow stare to move between rings.
-Specifically, I make use of the \citet{james+21} (hereaafter \JJ) model for the Milky Way, which runs using the publicaly available Versatile Integrator for Chemical Evolution (\VICE).
-This model is described extensively in \JJ~and consicely summarized  in \citet{james+23}.
-Here, I provide a prief overiview of the relevant model components.
-
-In the model, the Galaxy is divided into 200 rings, each 100 pc wide.
-Each ring has a seperate stellar population and gas supply.
-Star formation ends beyond a radius $R=15.5$ kpc.
-I initially assume an ``inside-out'' Star Formation History (SFH), where the star formation surface density $\Sigma_\star$ is given by
-\begin{equation}
-    \dot{\Sigma}_\star \propto \left(1-e^{-t/\tau_{\rm rise}}\right) e^{-t/\tau_{\rm sfh}}.
-\end{equation}
-$\tau_\text{rise}=2$ Gyr describes when the star formation rate reaches a maximum, and $\tau_{\rm sfh}$ describes the decay timescale of star formation as a function of radius $R$.
-\JJ~derives $\tau_{\rm sfh}(R)$ through analysis of four integral field spectroscopy surveys in \cite{sanches20}.
-The star formation history is normalized such that the total stellar mass reaches $M_\star=5.17\times10^{10} {\rm M}_\odot$ \citep{LM15} and at each $R$ to match the stellar surface density gradient \citep{BHG16}.
-The gas inflow is calculated to maintain our chosen SFR for each radius and time. The gas-SFR law is based on an extension of a Kennicutt-Schmidt law \citep{kennicutt98}, motivated by 
-\begin{equation}
-\dot{\Sigma}_{\star} \propto \\
-\begin{cases}
-    {\Sigma}_{\rm gas} & 2\times 10^7 \leq \Sigma_{\rm gas} \\ 
-    {(\Sigma}_{\rm gas})^{3.6} & 5\times 10^6 \leq \Sigma_{\rm gas} < 2\times10^7 \\ 
-    {(\Sigma}_{\rm gas})^{1.7} & \Sigma_{\rm gas} < 5\times10^6 \\ 
-\end{cases}
-\end{equation}
-The scaling of this relationship varies with time due to the redshift dependence of $\tau_\star$ in molecular gas observed by \citet{tacconi18}. I assume a Kroupa IMF \cite{kroupa01}.
-
-\JJ\ accounts for radial migration by using the results of the \texttt{h277} hydrodynamical simulation \citep{christensen12, zolotov12, loebman12, BZ14}, with simulation parameters described in \citet{bird+21}.
-Each \VICE single stellar population (SSP) is matched to an \textit{analogue} in \texttt{H277}, chosen to form at a similar time and radius $R$.
-By taking the change in radius $\Delta R$ of the analogues, the SSP move to their final radii with a $\sqrt{\text{time}}$ dependence.
-This relationship between displacement and time arises when migration proceeds as a consequence of the diffusion of angular momentum \citep{frankel18, frankel20}.
-I do not account for radial gas flows.
-Using the results of a hydrodynamical simulation without modification limits the free parameters in the model; however, I are limitied to one dynamical history.
-The impact of the details of a galaxy's dynamical history on its chemical evolution is unknown, and I do not explore this question here.
-
-As the strength of outflows controls the resulting $\alpha$ abundances, \JJ~create a metallicity gradienty by defining
-\begin{equation}
-\eta(R) = \frac{y_{\alpha}^{\rm CC}}{Z_{\alpha, \odot}} 10^{(-0.08\text{ kpc}^{-1})(R-4\text{ kpc})+0.3} + r - 1.
-\end{equation}
-This choice of $\eta(R)$ results in a [$\alpha$/H] gradient consistant with Milky Way observations \citep{james+21}.
-I explore models with reduced outflows in \S\ref{sec:outflows}; however, the overall scaling of yields is unknown and this model is insensitive to this normalization.
-
-\chapter{Multizone Model Results}
-\section{Data Selection}
-
-\citet{james+23} compare their model against the \cite{vincenzo+21} sample of APOGEE \citet{apogee17} red giants whose C and N abundance have been corrected for mixing process using MESA stellar evolution models.
-I instead use the \citetjack~sample of APOGEE subgiants.
-Subgiant stars have not undergone FDU, so their atmospheric C and N abundances are still reflective of their birth abundances and do not need mixing corrections.
-I additionally only compare the models to the low-$\alpha$ sequence.
-The selection criteria and differences between the samples are described in Appendix \ref{sec:jack}
-
-\section{The Evolution of C Across the Galaxy and Through Time}
-
-Here, I present the time evolution of our fiducial model.
-In the next sections, I will discuss the choice of parameters and agreement with observations.
-Our fiducial model uses the C11 AGB yield tables (see \S\ref{sec:agb}, and Table \ref{tab:fiducial_mod}), and I amplify the C11 yields by a factor of 2.9 so that $f_{\rm AGB} = 0.2$.
-
-The fiducial model has the following qualitative characteristics of its C yields: (a) C is predominantly produced in CCSNe, (b) CCSNe produce more C at higher metallicities, (c) AGB stars produce less carbon at higher metallicities.
-
-The evolution proceeds as follows.
-Initially, CCSNe dominate production.
-As $\Ycc$ has strong metallicity dependence, [C/Mg] increases with time.
-Shortly thereafter, AGB stars contribute delayed C, increasing [C/Mg] even more steeply.
-As Mg begins to reach equilibrium, the [C/Mg] ratio plateaus as C approaches equilibrium.
-Finally, as $\Ycagb$ decreases or even becomes negative with higher metallicity, the [C/Mg] abundance may decline slightly.
-
-I show the time evolution tracks of the fiducial model in Fig.
-\ref{fig:c_evo} for \caah~ and \caafe~.
-Comparing [C/$\alpha$] against [Mg/Fe] enables us to see late time evolution of C more clearly.
-Because of the extended DTD of SNeIa enrichment, [Fe/H] takes longer to reach equilibrium as half of iron production comes from type-Ia supernovae, the late time evolution is not as clustered as [$\alpha$/H].
-
-This is even more evident in the lower panel of Fig.
-\ref{fig:c_evo}.
-While the \caah~trend reaches equilibrium at $\sim5$ Gyr, the \caafe~trend continues to evolve even until the present day, exposing the effect of the relative delay times of AGB stars and SNeIa.
-
-\begin{figure}
-\centering
-\includegraphics{evo_tracks.pdf}
-\includegraphics{evo_slices.pdf}
-\caption[C chemical evolution tracks]{
-    Time evolution of gas phase C abundances in our fiducial model.
-
-    Top: Evolutionary tracks parameterized by time at fixed Galactocentric radius in the \caah and \caafe planes.
-
-    Bottom: snapshots of the gas-phase \caah~and \caafe~trend, parameterized by radius at fixed time.
-}
-\label{fig:c_evo}
-\end{figure}
-
-\section{Alternate Models}\label{sec:f-z-models}
-
-To make comparison easier, I define the C AGB production fraction as,
-\begin{equation}
-    f_{\rm AGB} = \frac{\Ycagb}{\Yct}\Bigg\vert_{Z=Z_\odot},
-\end{equation}
-where  $\Ycagb$ includes the multiplicitive factor $\alpha_{\rm AGB}$ as defined in Eq.~\ref{eq:alpha}.
-
-In Fig.
-\ref{fig:agb_sims}, I compare the K10, K16, C11, and V13 yield models.
-Each model uses the published, unscaled yield tables.
-As the highest AGB yield at solar, K10, is only $\Ycagb=0.000585$, $f_{\rm AGB} \leq 0.12$ for all models.
-Massive stars dominate C production with unscaled yields.
-While it is easy to modify the AGB yields in my model, their small contribution reduces the effect.
-I leave a more detailed discussion of the effects of AGB models for Appendix \ref{sec:alt_agb} and use C11 yields hereafter.
-
-\begin{figure}
-\centering
-\includegraphics{oob_agb.pdf}
-\caption[AGB GCE Models]{
-    Stellar abundance trends in our model, assuming metallicity independent $\Ycc$.
-Colored lines quantify the median [C/Mg] in bins of [Mg/H] for our four AGB yield models from the literature (see \ref{sec:agb}).
-Black points and grey dashes represent the median and standard deviations in the \citetjack~sample.
-In the right panel, I show the trends only for stars where $-0.15\leq {\rm [Mg/H]}\leq -0.05$.
-}
-\label{fig:agb_sims}
-\end{figure}
-
-Next, I investigate adjustments to $f_{\rm AGB}$ and the CCSNe metallicity dependence $\zeta$ in Fig. \ref{fig:beta_f}.
-
-As I display in Fig. \ref{fig:beta_f}, I observe that changes in $\beta$ are
-approprietly reflected in the resulting \caah~trend. As the metallicity
-dependence steepens with higher $\beta$, the [C/Mg] ratio becomes
-correspondingly more dependent on [Mg/H].
-
-As disscused in \S\ref{sec:equilibrium}, the \caah~trend in these models arises as a consequence o fthe relative yield $y_{\rm C}/y_{\rm Mg}$ and its metallicity dependence.
-This is determined by both the AGB fraction $f_{\rm AGB}$ and the metallicity dependence of CCSNe yields $\zeta$.
-As a result, there is a degeneracy between the two.
-I can increase $f_{\rm AGB}$ and $\zeta$ correspondingly, and \caah~would remain unaffected.
-
-This degeneracy is broken by the \caafe~relation.
-The relationship is set by $f_{\rm AGB}$, because a specific amount of C must be released at a delayed time in order to match the SNeIa production of Fe and increase [C/Mg] as [Mg/Fe] decreases to reproduce the data.
-One source of theoretical uncertanty in this result is that the SNeIa yield and DTD have their own uncertainties.
-I discuss variations in $y_{\rm Fe}^{\rm Ia}$ in Appendix \ref{sec:alt_agb}, and find that the quanlitative conclusions are largely unaffected.
-I therefore focus on the choices of $y_{\rm Fe}^{\rm Ia} = $FILLIN choices from the fiducial model here.
-
-Due to instantaneous CCSNe enrichment, the \caafe~relation is approximantly independent of $\zeta$.
-I can therefore choose $f_{\rm AGB}$ such that the \caafe~relation is reproduced, and then choose $\zeta$~to simulatneously reproduce \caah.
-Indeed, the positive slope of the \caah~relationship compared to our GCE models is a clear indication that metallicity dependent yields from massive stars must dominate AGB star production of C.
-Otherwise,  the inverse dependence of $\Ycagb$ on $Z$ makes it extremelly difficult to reproduce a positive slope in \caah.
-If this relationship indeed arises as a consequence of chemical equilibrium and yield ratios, then a positively sloped \caah~relation with high $f_{\rm AGB}$ should only arise if the Galaxy is significantly far from equilibrium.
-
-C as an equilibrium phenominon. See section \ref{sec:equilibrium} Importantly, the \caafe trend is mostly unaffected by choosing a different
-CCSNe yield. As all CCSNe enrichment happens at the same, rapid timescale, by
-taking a slice in [Mg/H], this metallicity dependence is effectively ignored as
-the only effect can be a vertical offset if the slice is narrow enough.
-
-So, the scaling of the trend and metallicity dependence of C (as seen in
-the \caah~trend) gives information on the total C yield and the behavior
-of CCSNe (as the dominating producer of C);
-the \caafe trend exposes the delayed effect of C from AGB contribution.
-
-V21 observes a significant seperation implying a more substantial delayed-time source.
-
 \begin{figure}
@@
 
-\caption[Adjusted yield models]{Similar to Figure \ref{fig:agb_sims} except the top plot shows the fiducial model with lower and higher values of $\zeta$, the C-CCSNe metallicity dependence.
+\caption[Adjusted yield models]{Similar to Fig.~\ref{fig:agb_sims} except the top plot shows the fiducial model with lower and higher values of $\zeta$, the C-CCSNe metallicity dependence.
 The bottom plot shows models with $f_{\rm AGB}=$0.1, 0.2, and 0.4.
@@
 
-\caption[Lateburst models]{Same as Figure \ref{fig:agb_sims} but comparing the fiducial model to alternate star formation histories (see \S \ref{sec:sfh}).}
+\caption[Lateburst models]{Same as Fig.~\ref{fig:agb_sims} but comparing the fiducial model to alternate star formation histories (see \S \ref{sec:sfh}).}
 \label{fig:sfh_models}
@@
 
-Here, I consider a "lateburst" model, created by multiplying our fiducial "inside-out" SFH with a gaussian.
+Here, I consider a "late burst" model, created by multiplying our fiducial "inside-out" SFH with a Gaussian.
 \begin{equation}\label{eq:lateburst}
@@
 
-I also consider an earlyburst model as a slight variation of the lateburst, where the burst is instead exponential and placed at $t_1=5$ Gyr.
-This approximantly corresponsed to the Gaia-Encelidus merger, inducing higher star formation in the Milky Way \citep{bonaca20, helmi18}.
+I also consider an early burst model as a slight variation of the late burst, where the burst is instead exponential and placed at $t_1=5$ Gyr.
+This approximately corresponds to the Gaia-Encelidus merger, inducing higher star formation in the Milky Way \citep{spitoni21, bonaca20, helmi18}.
 \begin{equation}\label{eq:twoinfall}
@@
 where I take the burst duration, $\tau_{\rm burst}=1$ Gyr in this case.
-This more drastic burst is able to more successfuly populate the high-$\alpha$ sequence. I leave more detailed exploration of the effects of star formation histories to future work.
-
-I show these variations on the star formation history in figure \ref{fig:sfh_models}.
+
+I show three models with these alternate SFH in Fig.~\ref{fig:sfh_models}.
+The changes to SFH leave \caah\ unchanged, but they do introduce slight variation in \caafe.
+Models with higher AGB fractions are more sensitive to variations in SFH.
+The late burst models result in [C/Mg] continuing to increase at low [Mg/Fe], but also introduce a break not present in the data.
+Additionally, the early burst
+is able to reproduce the slight break between the low and high $\alpha$ sequences, but overshoots equilibrium more severely than the fiducial model. 
+The choice of SFH does not change the large-scale slope of \caafe~significantly, so variations of SFH only have minimal effect on my conclusions.
 
@@
 
-GCE models of the Milky Way fall into two classes---those which incorperate significant mass-loading (e.g., as in this work) and those which neglet mass-loading but lower effective yield to match observed abundances \citep{MCM13, MCM14, spitoni19, spitoni20, spitoni21}.
-An increase in stellar yields has a nearly identical effect as a decreease in the mass-loading factor $\eta$ (see Appendix B of \cite{james_dwarf}).
-The equilibrium arguments discussed in \S\ref{sec:equilibrium} suggest howerver that abundance ratios are independent of the choice of normalization and the value of $\eta$.
-We therefore expect our results regarding the relative yield $y_{\rm C}/y_{\rm Mg}$ and its metallicity dependence to extend to the other class of models omitting mass loading.
+GCE models of the Milky Way fall into two classes---those which incorporate significant mass-loading (e.g., as in this work) and those which neglect mass-loading but lower effective yield to match observed abundances \citep{MCM13, MCM14, spitoni19, spitoni20, spitoni21}.
+An increase in stellar yields has a nearly identical effect as a decrease in the mass-loading factor $\eta$ (see Appendix B of \cite{james_dwarf}).
+The equilibrium arguments discussed in \S\ref{sec:equilibrium} suggest however that abundance ratios are independent of the choice of normalization and the value of $\eta$.
+I therefore expect my results regarding the relative yield $y_{\rm C}/y_{\rm Mg}$ and its metallicity dependence to extend to the other class of models omitting mass loading.
 I demonstrate this further here.
@@
 
-\caption[Reduced-outflow models]{Same as Figure \ref{fig:agb_sims} but comparing the fiducial model to reduced outflow models (see \S \ref{sec:outflows}).}
+\caption[Reduced-outflow models]{Same as Fig.~\ref{fig:agb_sims} but comparing the fiducial model to reduced outflow models (see \S \ref{sec:outflows}).}
 \end{figure}
@@
 
-Beyond simply comparing median trends, I can compare the distribution
+Median trends have limitations as they do not consider the actual distribution of \caah~abundances.
+So, I show in Fig.~\ref{fig:scatter} a comparison of the predicted distribution of the model to the contours of the subgiant sample.
+Our model reproduces this 2-dimension distribution well when including scatter based on the median APOGEE abundance errors for each metallicity bin.
+Some of the scatter is due to radial migration, but observational errors are dominant.
+Precision abundance measurements will allow tighter constraints on chemical yields.
 
@@
     \caption[Scatter agreement]{The stars in the fiducial model in the \caah~plane perturbed by the median [Mg/H] and [C/Mg] measurment errors in the \citetjack~sample.
-Stars are color-coded such that lighter colors represent population sborn at greater galactocentric radii
-    }
+Stars are color-coded such that lighter colors represent populations born at greater galactocentric radii
+    }
+    \label{fig:scatter}
 \end{figure}
@@
 As an additional test of the model, I next compare the gas-phase predictions against gas-phase C data.
-
-Beyond Milky Way stars, C to O ratios in
-HII-regions through either Recombination Lines or (OTHER TEchnique0), enabling
-us to probe gas-phase abundances of C in our galaxy and other types of
-galaxies from dwarf to elliptical. 
-However, C measurments of HII regions are challenging. C lacks strong collisional excitation lines, and recombination
-Additionally, recombination and collisionally excitation measurments disagree by a factor of $\sim 2$ \cite{GR07}.
-
-In Fig. \ref{fig:gas_phase}, I plot our fiducial model's gas phase abundances
-at present day and 2 Gyr compared to C/O
-abundances measured in both stars, our subgiant sample, halo stars, galaxies,
-and Damped Lynman Alpha (DLA) systems.
-
-I don't predict low metallicity but I are in agreement, substantial error bars.
-With MW and MW-like galaxies.
+In Fig.~\ref{fig:gas_phase}, I plot our fiducial model's gas phase predictions compared to observations of MW and extragalactic HII regions, halo stars, and Damped Lyman Alpha (DLA) systems.
+The model is broadly consistent with observations, where the model at $t=2$ Gyr approximates the slope of dwarf galaxies and halo stars.
+The increase of C/O at late times is also consistent with the high C/O abundances measured in extragalactic HII regions.
+My model does not extend to very low metallicity, where the trend reverses, but broadly explains observations above $\rm [O/H] \sim -1$.
 
@@
 I therefore use Mg abundances from the \citetjack~subgiant sample as my primary empirical constraint.
-However, I use O abundances for gas-sphase measurements and low-metallicity stars (\S \ref{sec:gas}).
+However, I use O abundances for gas-phase measurements and low-metallicity stars (\S \ref{sec:gas}).
 I model both Mg and O as metallicity-independent population-averaged yields dominated by massive stars.
 ${\rm [O/Mg]}\approx 0$ across a wide range of metallicities in APOGEE \citep{Weinberg+19, Weinberg+22}.
-I adopt O and Mg relative yields given by the solar mixture of \cite{asplund+09} <MATH>.
-
-Bursty SFH may not be needed to explain scatter as the C/O slope + differet evolutionary timescales is capable alone of reproducing this scatter.
-While the extragalactic trend appears to be more steeply sloped than our models, this is because of ***e.g. mass-dependent outflow rates/differening SFH between galaxies.
-
-Measuring C in the gas phase is challenging. C emission lines are
-very weak compared to other common lines, (visible/etc.).
-Temperature/modelining limitations. Lack of strong HII calibration. 
-Short discussion of measurment challenges in extragalactic galaxies, how other galaxies and dwarf SFH may come into play, why this relation is notecably steeper.
-
-Our model does not consider very-low metallicity stars. Population III stellar yields, with a top-heavy IMF, may predict strongly enhanced carbon yields \cite[e.g.]{hirschi07}.
-
-Our model fails to capture the trend past [$\alpha$/H]$=-1$. As our knowledge
-of stellar evolution is limited, our knowledge of extremely metal poor stellar
-evolution is proportionally limited.
-
-A variety of explanation for the increasing relative C
-enrichments for metal-poor stars have been proposed (e.g. ...). The likely case
-that Population III star supernovae produced high abundances of C seems
-most plausable, especially given our uncertainty in the C yields and the
-short timescales required to create this enhancement (e.g. $z\sim 2$ DLA,
-dwarfs, etc.) make it unlikely that AGB stars could be the culprit.
-
-e.g. \cite{cooke+17} suggest Population III stars as a solution to CEMPS \cite{FN15}.
+I adopt O and Mg relative yields given by the solar mixture of \cite{asplund+09}.
+
+C/O gas-phase measurements are hard.
+In HII-regions, C/O abundance ratios are measured with either recombination lines or collisionally excitation lines.
+However C lacks strong collisional excitation lines, and recombination lines fall in the ultraviolet without nearby reference H lines \citep{skillman+20}.
+Additionally, recombination and collisionally excitation measurements disagree by a factor of \about{2} \cite{GR07}.
+Additional to measurement errors, variations in SFH may explain the scatter, as C contains delayed enrichment, and bursts cause variations in C/O.
+
+The decreasing [C/O] abundance at very-low metallicities is likely due to population III stellar yields \citep[e.g.][]{hirschi07}, as suggested by \citep{cooke+17, FN15}.
+As AGB stars do have a significant delay, these stars cannot explain the increase in C yields at low metallicity as the timescales to reach $\rm [O/H]\sim -1$ is faster than this enrichment can occur.
+So, enhanced carbon due to (rotating) massive population III stars at low metallicities explains this trend.
 
@@
     \includegraphics{c_n.pdf}
-    \caption[C/N abundance agreement]{Similar to as Figure \ref{fig:agb_sims}, except I only show the fiducial model and I plot the [C/N] abundance ratio on the y-axis.
+    \caption[C/N abundance agreement]{Similar to Fig.~\ref{fig:agb_sims}, except comparing [C/N] from the fiducial model only.
     }
@@
 \includegraphics[]{summary.pdf}
-\caption[Gas phase abundances]{Gas-phase C abundances. We plot our model at $t=2$Gyr and present day as thick solid lines. Points represent measurments in 
+\caption[Gas phase abundances]{Gas-phase C abundances. We plot our model at $t=2$Gyr and present day as thick solid lines. Points represent measurements in 
     HII regions    \citep[pink circles;][]{skillman+20, esteban+02, esteban+09, esteban+14, esteban+19}
@@
 In this work, I investigate the role of C yields on the predictions of multizone GCE models.
-\citet{james+23} performed a similar analysis, except focusing on N.
-\citet{james+23} found, to match APOGEE/\citet{vincenzo+21}'s observations, $y_{\rm N}^{\rm AGB} \sim  Z$.
-
+\citet{james+23} performed a similar analysis focusing on N.
+They found that matching the observed relationship between N and O abundances (REFS) requires relative N and O yields from simple stellar populations with a roughly linear dependence on metallicity (i.e.
+$y_{\rm N}/y_{\rm O} \propto Z$).
 Here, I perform a similar analysis on C.
-I summarize the current theoretical nucleosynthetic predictions of C.
-Because CCSNe C yields are poorly understood, I adopt an equilibrium approximation and determine that a functional form of $\Ycc/\Yoc=1.51 + 0.54 (Z/Z_\odot)$ approximately matches trends in APOGEE subgiants.
-Variations of the metallicity dependence of this CCSNe yield affect trends in \caah but do not affect trends in \caafe when taking a slice in [Mg/H].
-As all theoretical AGB C yields decrease with increasing metallicity, increasing the AGB fraction causes the \caah trend to flatten.
-However, the \caafe trend is sensitive to the AGB fraction.
-I estimate that $f_{\rm AGB} = 0.2$ using the C11 yield model. This requires about 3x more AGB C production than most nucleosynthetic models predict.
-
-Evolutionary history
-
-Finally, I compare my model against gas phase and metal-poor stellar measurments.
-While my model was built on data near solar metallicity, by including heightened C production from population III stars, I can create a self consistant picture of C evolution.
-
-Observations of C in metal poor stars, extragalactic (call out any
-
-Implications in Stellar evolution
-
-These C yield constraints provide a test for stellar evolution models. C yields are sensitive to mass loss treatment, explodability, nuclear cross sections, convection, and stellar structure.
-
-Future surveys such as the Milky Way Mapper will enable further refinement of galactic trends, placing yet more stringent constrants on stellar evolution models.
-MWM and value of this work
-
-Future surves, including SDSS-V/MWM and the DESI Milky Way survey will each measure spectra of $>6$ million milkyway stars.
-\citep{desi, desi:mw}
-
-Combined with kinematic information and distances from GAIA \citep{gaia}
-
-\citep{sdssv}
-Abundance ratios (e.g.C12/C13) as additional constraints
+
+Though CCSNe C yields are poorly understood, I adopt an equilibrium approximation and determine a functional form that approximately matches trends in APOGEE subgiants and is consistant with massive star nucleosynthesis models.
+Variations of the metallicity dependence of this CCSNe yield affect trends in \caah~but do not affect trends in \caafe\ when taking a slice in [Mg/H].
+As all theoretical AGB C yields decrease with metallicity, increasing the AGB fraction causes the \caah\ trend to flatten.
+However, the \caafe\ trend is sensitive to the AGB fraction.
+From this, I estimate that AGB stars contribute \about{20\%} of total C abundance at solar metallicity.
+The remaining \about{80\%} of C comes from massive stars with a metallicity dependent yield of $\Ycc/\Yoc=1.51 + 0.54 (Z/Z_\odot)$.
+This metallicity dependence is consistent with the rotating stellar models of \citet{LC18}.
+
+I additionally explore variations of the assumed SFH and outflow mass-loading factor $\eta$.
+I find that alternate SFHs can slightly affect \caafe, but \caah~is mostly unaffected.
+Decreasing both outflows and yields by the same factor leaves the \caah~and \caafe~trends unaffected.
+These constraints on the relative yields of C, O, and Mg are robust against variations in $\eta$.
+
+Finally, I compare my model against gas phase measurements and metal-poor stars.
+While my model was built on data near solar metallicity, observations of very low metallicity, high redshift damped Lyman-$\alpha$ systems indicate higher C/O ratios \citep{cooke+17}, consistent with yields from population III stars \citep[e.g.][]{hirschi07}.
+Our combined results self-consistently explain C abundances.
+
+These C yield constraints provide a useful benchmark for stellar evolution models.
+C yields are sensitive to poorly understood processes, including mass loss prescriptions, explodability, nuclear cross sections, convection, and stellar structure.
+Future spectroscopic surveys combined with Gaia kinematics \citep{gaia} will continue to enhance our understanding of chemical evolution.
+Both SDSS-V/MWM \citep{sdssv} and the DESI Milky Way survey \citep{desi, desi:mw} will each measure spectra of $>6$ million Milky Way stars.
+These larger samples will enable similar work to tighten constraints on stellar models and our understanding of galaxy structure and evolution.
 
 %%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%
-
-% The best way to enter references is to use BibTeX:
 
@@
 \addcontentsline{toc}{chapter}{Bibliography}
-\bibliography{main} % if your bibtex file is called example.bib
-
-% Alternatively you could enter them by hand, like this:
-% This method is tedious and prone to error if you have lots of references
-%\begin{thebibliography}{99}
-%\bibitem[\protect\citeauthoryear{Author}{2012}]{Author2012}
-%Author A.~N., 2013, Journal of Improbable Astronomy, 1, 1
-%\bibitem[\protect\citeauthoryear{Others}{2013}]{Others2013}
-%Others S., 2012, Journal of Interesting Stuff, 17, 198
-%\end{thebibliography}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\bibliography{main}
 
@@
 
-This cut isolates a clean sample of subgiants.
+This cut isolates a clean sample of \about{12,000} subgiants.
 As first dredge up, which affects C and N abundances, only occurs during the ascent onto the red giant branch, subgiant stars are unaffected by this enrichment.
 
-Additionally, I exclued stars in APOGEE marked by the following flags.
+Additionally, I included stars in APOGEE marked by the following flags.
 \begin{itemize}
@@
 As I focus on constraining relative yields, I neglect O and Mg yield variations in the main text.
-There is substantial variation in Mg predictions (see Fig.
-\ref{fig:y_mg}).
+There is substantial variation in Mg predictions (see Fig.~\ref{fig:y_mg}).
 Most models predict relatively flat Mg trends with metallicity (even with rotating models from \citealt{LC18}).
-Hoever, the variation is significant and my adopted $\Yoc$ yield is much higher than most models.
+However, the variation is significant and my adopted $\Yoc$ yield is much higher than most models.
 This is a known problem (see \citet{emily+21}).
@@
 While I focus the main discussion of the paper on the C11 model, other AGB models can impact abundance trends when $f_{\rm AGB}$ becomes larger.
-Here, I briefly explore here the effects of variations in AGB models affect abundance trend predictions when these models are amplified to match observational [C/MG]-[Mg/Fe] trends. 
+Here, I briefly explore the effects of variations in AGB models that affect abundance trend predictions when these models are amplified to match observational [C/MG]-[Mg/Fe] trends. 
 See Fig \ref{fig:fagb2}.
@@
 This causes a reversal of the [C/Mg]-[Mg/Fe] trend at high [Mg/H] slices (figure ...).
-As our set of observations do not appear to reverse, this indicates that C yields likely stay positive even at slightly super-solar, so models like V13 are a poor match to observations.
-
-In Fig. \ref{fig:fe_ia}.
-
-I leave exploration of the age-metallicity relation for C to future work.
+As our set of observations does not appear to reverse, this indicates that C yields are likely to stay positive even at slightly super-solar, so models like V13 are a poor match to observations.
+
+In Fig.~\ref{fig:fe_ia}.
+
+I leave the exploration of the age-metallicity relation for C to future work.
 
@@
 
-    \caption[Alternate AGB models]{Same as Figure \ref{fig:agb_sims} except where $f_{\rm agb}=0.2$. When yields are amplified, chaos ensues.}
+    \caption[Alternate AGB models]{Same as Fig.~\ref{fig:agb_sims} except where $f_{\rm agb}=0.2$. When yields are amplified, chaos ensues.}
     \label{fig:fagb2}
@@
     \includegraphics{y_mg.pdf}
-    \caption[Magnesium CCSNe yields]{Same as the top panel of Figure \ref{fig:y_cc}, but for Mg. Our Mg yield choice is shown as a dashed line at the top
+    \caption[Magnesium CCSNe yields]{Same as the top panel of Fig.~\ref{fig:y_cc}, but for Mg. Our Mg yield choice is shown as a dashed line at the top
     }
@@
     \includegraphics{fe_ia.pdf}
-    \caption[Adjusting type Ia iron]{Similar to Figure \ref{fig:agb_sims} except with variations of the SNeIa iron fraction}
+    \caption[Adjusting type Ia iron]{Similar to Fig.~\ref{fig:agb_sims} except with variations of the SNeIa iron fraction}
     \label{fig:fe_ia}
@@
 
-Software which has contributed to this work:
+Software that has contributed to this work:
 

### 2023-04-28 thesis/tex/main.tex
bibliography updates; isolated v21 code

@@
 
-\newcommand{\citetjack}{Roberts et.\ al (2023, in prep.)}
-\newcommand{\citepjack}{(Roberts et.\ al 2023, in prep.)}
-\newcommand{\citealtjack}{Robert et.\ al 2023, in prep.}
+\newcommand{\citetjack}{Roberts et al.~(2023, in prep.)}
+\newcommand{\citepjack}{(Roberts et al.~2023, in prep.)}
+\newcommand{\citealtjack}{Robert et al.~2023, in prep.}
 
@@
        \vspace*{3\baselineskip}
-       Project Advisor: Professor David H. Weinberg, Department of Astronomy
+       Project Advisor: Professor David H. Weinberg, Department of Astronomy \\
+       James W. Johnson 
        \vfill
@@
 At the core of GCE models are stellar yields---the amount of each chemical element stars produce (or destroy).
-Each elements is produced in different amounts by different stars, leaving traces of the Galaxy's evolutionary history.
+Each element is produced in different amounts by different stars, leaving traces of the Galaxy's evolutionary history.
 Through \textit{Galactic Archeology}, we can reconstruct the history of our galaxy by investigating clues left behind in stars.
@@
 To this end, I use a sample of subgiant stars from APOGEE \citep{apogee17}.
-According to stellar evolution models (CITES), these stars have not yet experienced FDU.
-Their phosphoric abundances should thus represent their birth composition.
+According to stellar evolution theory and observations \citep{gilroy89, korn+07, lind+08, souto+18, souto19}, these stars have not yet experienced FDU but have well-mixed photospheres.
+Their photosphoric abundances should thus represent their birth composition.
 In Fig.~\ref{fig:subgiants}, I plot this sample, selected by the criteria in Roberts et al.
@@
 Our fiducial model's steep metallicity dependence near $Z\approx Z_\odot$ could be explained by rotation.
-Fig.~\ref{fig:ycc} shows the C11 model for comparison on the top.
+Fig.~\ref{fig:y_cc} shows the C11 model for comparison on the top.
 Especially at $Z\approx Z_\odot$, most CCSNe models dominate AGB C production.
@@
 CCSNe models also do not reach [O/Mg] due to overproduction of O, or underproduction of Mg, or both \citep{emily+21}.
-Here, I assume ${\rm [O/Mg]} = 0$, which is not compatible with CCSNe models but is consistent with APOGEE observations \citep{Weinberg+19, Weinberg+22}.
+Here, I assume ${\rm [O/Mg]} = 0$, which is not compatible with CCSNe models but is consistent with APOGEE observations \citep{weinberg+19, weinberg+22}.
 
@@
 \end{equation}
-This choice of $\eta(R)$ results in a [$\alpha$/H] gradient consistent with Milky Way observations \citep{james+21}.
-I explore models with reduced outflows in \S\ref{sec:outflows}; however, the overall scaling of yields is unknown and this model is insensitive to this normalization.
+This choice of $\eta(R)$ results in a [$\alpha$/H] gradient consistent with Milky Way observations \citep[e.g.][]{hayden+14, weinberg+19, frinchaboy+13}.
 
@@
 
-\citet{james+23} compare their model against the \cite{vincenzo+21} sample of APOGEE \citet{apogee17} red giants whose C and N abundance have been corrected for mixing process using MESA stellar evolution models.
+\citet{james+23} compare their model against the \cite{vincenzo+21} sample of APOGEE \citep{apogee17} red giants whose C and N abundance have been corrected for mixing process using MESA stellar evolution models.
 I instead use the \citetjack~sample of APOGEE subgiants.
@@
 I additionally only compare the models to the low-$\alpha$ sequence.
-The selection criteria and differences between the samples are described in Appendix \ref{sec:jack}
+The selection criteria and differences between the samples are described in more detail in Appendix \ref{sec:jack}.
 
-\section{The Evolution of C Across the Galaxy and Through Time}
+\section{The Evolution of C Abundances in the Galaxy}
 
-Here, I present the time evolution of our fiducial model.
-In the next sections, I will discuss the choice of parameters and agreement with observations.
-Our fiducial model uses the C11 AGB yield tables (see \S\ref{sec:agb}, and Table \ref{tab:fiducial_mod}), and I amplify the C11 yields by a factor of 2.9 so that $f_{\rm AGB} = 0.2$.
+Here, I present the time evolution of our fiducial model. In the next sections, I will discuss the choice of parameters and agreement with observations. 
+The fiducial model has the following qualitative characteristics of its C yields: (a) C is predominantly produced in CCSNe, (b) CCSNe produce more C at higher metallicities, and (c) AGB stars produce less carbon at higher metallicities.
+Our fiducial model uses the C11 AGB yield tables (see \S\ref{sec:agb}, and Table \ref{tab:fiducial_mod}), and I amplify the C11 yields by a factor of 2.9 such that AGB stars account for 20\% of carbon at $Z=Z_\odot$.
 
-The fiducial model has the following qualitative characteristics of its C yields: (a) C is predominantly produced in CCSNe, (b) CCSNe produce more C at higher metallicities, and (c) AGB stars produce less carbon at higher metallicities.
-
+I show the time evolution tracks of the fiducial model in Fig.~\ref{fig:c_evo} for \caah~ and \caafe~.
+Comparing [C/$\alpha$] against [Mg/Fe] enables us to see the late-time evolution of C more clearly.
+Because of the extended DTD of SNeIa enrichment, [Fe/H] takes longer to reach equilibrium as half of Fe production comes from type-Ia supernovae, and the late time evolution is not as clustered as [$\alpha$/H].
 The evolution proceeds as follows.
@@
 Finally, as $\Ycagb$ decreases or even becomes negative with higher metallicity, the [C/Mg] abundance may decline slightly.
-
-I show the time evolution tracks of the fiducial model in Fig.~\ref{fig:c_evo} for \caah~ and \caafe~.
-Comparing [C/$\alpha$] against [Mg/Fe] enables us to see the late-time evolution of C more clearly.
-Because of the extended DTD of SNeIa enrichment, [Fe/H] takes longer to reach equilibrium as half of Fe production comes from type-Ia supernovae, and the late time evolution is not as clustered as [$\alpha$/H].
 
@@
 I model both Mg and O as metallicity-independent population-averaged yields dominated by massive stars.
-${\rm [O/Mg]}\approx 0$ across a wide range of metallicities in APOGEE \citep{Weinberg+19, Weinberg+22}.
+${\rm [O/Mg]}\approx 0$ across a wide range of metallicities in APOGEE \citep{weinberg+19, weinberg+22}.
 I adopt O and Mg relative yields given by the solar mixture of \cite{asplund+09}.

### 2023-04-28 src/analysis/vincenzo.py

@@ -1,0 +1,256 @@
+import numpy as np
+import pickle
+import matplotlib.pyplot as plt
+import vice
+import pandas as pd
+import os
+
+
+def bracket(df, ele, ele2="H"):
+    """
+    Helper function for subgiants()
+    creates the abundance ratio [A/B]
+    from the  APOGEE dataframe
+    """
+    if ele2 == "H":
+        if ele == "FE":
+            return df["FE_H"]
+        else:
+            return df["%s_FE" % ele] + df["FE_H"]
+    else:
+        if ele2 == "FE":
+            return df["%s_FE" % ele]
+        else:
+            return df["%s_FE" % ele] - df["%s_FE" % ele2]
+
+def vincenzo2021_raw():
+    """
+    Reads in the CNOdredgeup.obj file 
+    from the data in V+21 and returns the file
+    as a pandas dataframe with original column
+    names
+    
+    Note: this does not read in the calabration values for C, N, O abundance:
+
+    For solar:
+    Log C/H = -3.61
+    Log N/H = -4.22
+    Log O/H = -3.34
+
+    Also, corrections for O/H are small (<0.02), so
+    using magnesium may still be okay.
+    """
+    script_dir = os.path.dirname(__file__)
+    rel_path = "./CNOdredgeup.obj"
+    abs_path = os.path.join(script_dir, rel_path)
+    f = open(abs_path, "rb")
+    raw = pickle.load(f, encoding = "bytes")
+    f.close()
+    data = raw[1:13]
+    columns = raw[0].split(", ")[1:13]
+
+    df = {columns[i]: data[i] for i in range(12)}
+    return pd.DataFrame(df, dtype=float)
+
+def mg_fe_cutoff(fe_h):
+    """
+    The cutoff between the high and low alpha seqeunces
+
+    Parameters
+    ----------
+    fe_h: float or np.array
+        The [Fe/H] values to evaluate the boandry at
+
+    Returns
+    -------
+    mg_fe: float or np.array
+        The [Mg/Fe] above which the high alpha sequence is defined
+    """
+    return 0.12 - (fe_h < 0) * 0.13 * fe_h
+
+
+def vincenzo2021():
+    """
[…]

### 2023-04-29 thesis/tex/main.tex
fine adjustments

@@
-\documentclass[12pt,oneside]{report}
-
-% \AddToHook{cmd/section/before}{\clearpage}
+%\DocumentMetadata{testphase=phase-III,testphase=math}
+\documentclass[12pt,oneside,letterpaper]{report}
 
@@
 \usepackage{aas_macros}
-\usepackage[letterpaper, top=1in]{geometry}
+%\usepackage[letterpaper, top=1in]{geometry}
 \usepackage{titlesec}
+\usepackage{microtype}
 
@@
 \usepackage{isotope}
-% \usepackage[titles]{tocloft} % fig titles
-% \renewcommand{\cftfigpresnum}{\figurename\enspace}
-% \setlength{\cftfignumwidth}{5em}
-% \renewcommand{\cfttabpresnum}{\tablename\enspace}
-% \setlength{\cfttabnumwidth}{5em}
+
+\usepackage{accsupp}
+\usepackage[accsupp]{axessibility}
+\pdfcompresslevel=0
+
+% accessibility
+% \usepackage{tagpdf}
+% \usepackage[tagpdf]{axessibility}
+
+\usepackage[]{acro}
+\usepackage{array}
+
+\acsetup{
+    make-links = true,
+    list/template = tabular,
+    templates/colspec = {p{0.2\linewidth} p{0.8\linewidth} },
+    pages/display = none,
+    format/short = {\sc}, 
+}
+
+\DeclareAcronym{cc}{
+    short = ccsn,
+    long = core collapse supernova,
+    short-plural = e,
+    long-plural = e,
+    extra = {massive star explosions}
+}
+\DeclareAcronym{ia}{
+    short = sne ia,
+    long = supernovae type Ia,
+    extra = {exploding white dwarfs}
+}
+
+\DeclareAcronym{agb}{
+    short = agb,
+    long = asymptotic giant branch,
+    short-plural = s,
+    long-plural = \ stars,
+}
+\DeclareAcronym{gce}{
+    short = gce,
+    long = galactic chemical evolution
+}
+
+\DeclareAcronym{dla}{
+    short = {dla},
+    long = {damped Lyman-alpha},
+    short-plural = s,
+    long-plural = \ systems,
+}
+
+\DeclareAcronym{apogee}{
+    short = {apogee},
+    long = {Apache Point Observatory Galactic Evolution Experiment},
+    extra = {a large optical spectroscopic survey of Milky Way stars}
+}
+
+\DeclareAcronym{sfh}{
+    short = sfh,
+    long = star formation history,
+}
+\DeclareAcronym{ssp}{
+    short = ssp,
+    long = single stellar population,
+}
+\DeclareAcronym{imf}{
+    short = imf,
+    long = initial mass function,
+}
+
+\newcommand{\cc}{\ac{cc}}
+\newcommand{\agb}{\ac{agb}}
+\newcommand{\ia}{\ac{ia}}
+
+\newcommand{\sfh}{\ac{sfh}}
+\newcommand{\ssp}{\ac{ssp}}
+\newcommand{\imf}{\ac{imf}}
+\newcommand{\gce}{\ac{gce}}
+\newcommand{\apogee}{\ac{apogee}}
 
@@
 \begin{document}
-
 %\doublespacing
@@
 % results
-By matching the slopes of the \caah\ and \caafe\ relationships in a sample of APOGEE subgiant stars, I find that CCSNe and AGB stars contribute \about{80\%} and \about{20\%} of total C production respectively.
+By matching the slopes of the \caah\ and \caafe\ relationships in a sample of APOGEE subgiant stars, I find that massive stars and low mass stars contribute \about{80\%} and \about{20\%} of total C production respectively.
 % 
-To also match the normalization of the trends, I estimate the CCSNe C/Mg yield ratio $\Ycc/\Yoc = 1.57 + 0.59 \left(Z/Z_\odot\right)$, which explains the \caah\ trend when including the AGB C contribution.
+To also match the normalization of the trends, I estimate the massive star C/Mg yield ratio $\Ycc/\Yoc = 1.57 + 0.59 \left(Z/Z_\odot\right)$, which explains the \caah\ trend when including the low mass C contribution.
 %
@@
 
-Galactic chemical evolution (GCE) aims to understand the chemical and star formation histories of galaxies.
-At the core of GCE models are stellar yields---the amount of each chemical element stars produce (or destroy).
+\Ac{gce} aims to understand the chemical and star formation histories of galaxies.
+At the core of \ac{gce} models are stellar yields---the amount of each chemical element stars produce (or destroy).
 Each element is produced in different amounts by different stars, leaving traces of the Galaxy's evolutionary history.
@@
 Here, I aim to understand C enrichment---where it is produced and how its abundances evolve over time.
-C is unique nucleosynthetically, one of few light elements (along with N) produced in asymptotic giant branch (AGB) stars \citep[e.g.][]{jennifer19, KL14}.
+C is unique nucleosynthetically, one of few light elements (along with N) produced in \ac{agb} stars \citep[e.g.][]{jennifer19, KL14}.
 C and N are well-studied elements since they are easy to observe in stellar spectra, even at the lowest metallicities \cite[e.g.][]{fabbian+09, nissen+14, lambert81, laird85, lambert86}.
@@
 
-Gas-phase [C/O] ratios---observed in very low metallicity, high redshift damped Lyman-alpha systems (DLAs)---decrease with increasing [O/H] \citep{FN15, cooke+17}.
+Gas-phase [C/O] ratios---observed in very low metallicity, high redshift \acp{dla}---decrease with increasing [O/H] \citep{FN15, cooke+17}.
 Then, [C/O] increases above $\rm [O/H] \approx -1$ (\citealt{berg+19}; see discussion in \S\ref{sec:gas}).
-While we know C is produced in AGB stars and core-collapse supernovae (CCSNe), we still have a limited understanding of the magnitude and metallicity-dependence of each process.
-
-Despite their central role in GCE models, nucleosynthetic yields predicted by stellar evolution models are rife with uncertainties.
+While we know C is produced in \ac{agb} stars and \acp{cc}, we still have a limited understanding of the magnitude and metallicity-dependence of each process.
+
+Despite their central role in \gce{} models, nucleosynthetic yields predicted by stellar evolution models are rife with uncertainties.
 The production rates of elements in stars are shaped by poorly understood processes, including mass loss, opacity, nuclear reaction rates, rotational mixing, and convection \citep{KL14,ventura+13, LC18}.
@@
 
-GCE models typically use unmodified nucleosynthetic predictions and attempt to create models matching observations by varying the star formation history (SFH) and other evolutionary parameters.
+\gce{} models typically use unmodified nucleosynthetic predictions and attempt to create models matching observations by varying the \sfh{} and other evolutionary parameters.
 Here, I introduce C yields as an additional free parameter, determining which yield prescriptions reproduce Galactic abundance trends.
-\cite{james+23} examined similar GCE models of N, an element whose production is closely related to C.
+\cite{james+23} examined similar \gce{} models of N, an element whose production is closely related to C.
 \cite{james+23} found that trends in N and O abundances can be explained by the metallicity dependence of relative N and O yields.
 Here, I extend their models to C and show that similar constraints on C and O relative yields can be obtained from observed abundance ratios.
-Additionally, I assess which yield prescriptions reproduce Galactic abundance trends while assessing the impact of GCE model assumptions, such as SFH and outflow mass loading.
+Additionally, I assess which yield prescriptions reproduce Galactic abundance trends while assessing the impact of \gce{} model assumptions, such as \sfh{} and outflow mass loading.
 
 Accurate determination of stellar birth abundances for C and N is challenging.
-When a star enters the red giant branch (RGB), material from the CNO-processed core is mixed with the envelope in first dredge up (FDU), enhancing N and depleting C \citep{iben67, vincenzo+21,KL14}.
+When a star enters the red giant branch, material from the CNO-processed core is mixed with the envelope in first dredge up, enhancing N and depleting C \citep{iben67, vincenzo+21,KL14}.
 Measurements of these evolved stars'  atmospheres will no longer reflect their birth abundances.
@@
 
-To this end, I use a sample of subgiant stars from APOGEE \citep{apogee17}.
-According to stellar evolution theory and observations \citep{gilroy89, korn+07, lind+08, souto+18, souto19}, these stars have not yet experienced FDU but have well-mixed photospheres.
+To this end, I use a sample of subgiant stars from the \apogee{} \citep{apogee17}.
+According to stellar evolution theory and observations \citep{gilroy89, korn+07, lind+08, souto+18, souto19}, these stars have not yet experienced first dredge up but have well-mixed photospheres.
 Their photosphoric abundances should thus represent their birth composition.
@@
     \includegraphics{subgiants_mgfe.pdf}
-    \caption[APOGEE Subgiants]{The [C/Mg] ratio against [Mg/H] (top) and [Mg/Fe] (bottom) for the \citetjack~sample of APOGEE subgiants.
+    \caption[APOGEE Subgiants]{The [C/Mg] ratio against [Mg/H] (top) and [Mg/Fe] (bottom) for the \citetjack~sample of \apogee{} subgiants.
 On the top, I plot high and low-$\alpha$ stars in blue and orange, using the separation defined in Equation \ref{eq:high_alpha}.
@@
 Theoretical models of stellar nucleosynthesis provide the starting point of this investigation.
-I focus on three primary nucleosynthetic pathways: asymptotic giant branch (AGB) stars, core-collapse supernovae (CCSNe), and type Ia supernovae (SNe Ia).
-Each process has unique timescales and yields, traceable through the tools of GCE.
-I compare C, produced in CCSNe and AGB stars, to Mg and Fe as tracers of CCSNe and SNe Ia respectively.
-
-When a single stellar population (SSP) forms, CCSNe are the first enrichment event.
-CCSNe  explode within $\lesssim 40$ Myr, providing light elements (C, O, and Mg) and heavier elements (Fe and beyond).
-Metallicity-independent yields from CCSNe are the only statistically significant source of O and Mg ($\alpha$ elements).
+I focus on three primary nucleosynthetic pathways: \acf{agb} stars, \acf{cc}, and type Ia supernovae \acf{ia}.
+Each process has unique timescales and yields, traceable through the tools of \gce.
+I compare C, produced in \cc{} and \ac{agb} stars, to Mg and Fe as tracers of \cc{} and \acf{ia} espectively.
+
+When a \ssp~forms, \cc{} are the first enrichment event.
+\cc{}  explode within $\lesssim 40$ Myr, providing light elements (C, O, and Mg) and heavier elements (Fe and beyond).
+Metallicity-independent yields from \cc{} are the only statistically significant source of O and Mg ($\alpha$ elements).
 Next, low-mass stars begin to reach the end of their lives.
-By shedding their outer layers, AGB stars are important sources of C, N, and neutron capture elements.
+By shedding their outer layers, \ac{agb} stars are important sources of C, N, and neutron capture elements.
 Finally, white dwarfs explode, releasing Fe and other iron-peak elements.
@@
 where $M_{\rm ejected}$ and $M_{\rm X, ejected}$  are the total ejected mass of the envelope and the element X, respectively.
-For example, if a 1 $M_\odot$ star has $\tilde{y}_{\rm C} = 10^{-3}$, then the star will add $10^{-3}\ M_\odot$ of C to the interstellar medium (ISM).
-Although per-star yields are necessary to compute AGB star enrichment rates in GCE models, IMF-averaged\footnote{IMF: Initial Mass Function} yields are useful in interpreting their predictions.
-For a yield $y$ from a star of mass M and initial metallicity $Z$, the IMF-averaged yield is given by
+For example, if a 1 $M_\odot$ star has $\tilde{y}_{\rm C} = 10^{-3}$, then the star will add $10^{-3}\ M_\odot$ of C to the interstellar medium.
+Although per-star yields are necessary to compute \ac{agb} star enrichment rates in \gce{}  models, \imf-averaged\footnote{IMF: Initial Mass Function} yields are useful in interpreting their predictions.
+For a yield $y$ from a star of mass M and initial metallicity $Z$, the \imf-averaged yield is given by
 \begin{equation} \label{eq:imf-yield}
@@
 \end{equation}
-where ${dN}/{dM}$ is the normalized IMF, and $M_{\rm min}$ and $M_{\rm max}$ are the minimum and maximum mass of stars, which I take to be $0.08 M_{\sun}$ and $100 M_{\sun}$ respectively.
-For AGB stars, the yields are truncated above 8 $M_{\odot}$.
-To calculate the IMF-weighted net yields, I use the Versatile Integrator for Chemical Evolution code (\VICE\footnote{\VICE~is available at \url{https://github.com/giganano/VICE}}).
+where ${dN}/{dM}$ is the normalized \imf, and $M_{\rm min}$ and $M_{\rm max}$ are the minimum and maximum mass of stars, which I take to be $0.08 M_{\sun}$ and $100 M_{\sun}$ respectively.
+For \ac{agb} stars, the yields are truncated above 8 $M_{\odot}$.
+To calculate the \imf-weighted net yields, I use the Versatile Integrator for Chemical Evolution code (\VICE\footnote{\VICE~is available at \url{https://github.com/giganano/VICE}}).
 
 To focus on C yields, I adapt the yield choices of other elements from \citet{james+21, james+23}.
-Table \ref{tab:fiducial_mod} contains my fiducial yields, in units of a SSP's birth mass.
-Also following \citet{james+21, james+23}, I take the SNeIa delay time distribution to be a
+Table \ref{tab:fiducial_mod} contains my fiducial yields, in units of a \ssp's birth mass.
+Also following \citet{james+21, james+23}, I take the \ac{ia} delay time distribution to be a
 $t^{-1.1}$ power-law suggested by the observations of \citet{maoz+12}.
@@
 	\centering
-    \caption[Fiducial Model]{Yields for the fiducial model in units of SSP birh mass. See \S\ref{sec:agb} for the definition of C11.}
+    \caption[Fiducial Model]{Yields for the fiducial model in units of \ssp~birth mass. See \S\ref{sec:agb} for the definition of C11.}
 	\label{tab:fiducial_mod}
@@
 
-An AGB star is a low mass ($\lesssim 8 M_{\sun}$) star during its final phase of evolution.
-In an AGB star, two competing processes determine the outcome of C production: third dredge up (TDU) and hot bottom burning (HBB).
-TDU accompanies thermal pulses in AGB stars.
-During a TDU event, material from the CO core is mixed with material exposed to partial He-shell burning, increasing C and O abundances in the envelope \citep{KL14}.
-If this envelope is lost during the AGB phase, then C yields are enhanced.
-HBB is the activation of proton capture reactions, and the CNO cycle%
+An \ac{agb} star is a low mass ($\lesssim 8 M_{\sun}$) star during its final phase of evolution.
+In an \ac{agb} star, two competing processes determine the outcome of C production: third dredge up and hot bottom burning.
+Third dredge up accompanies thermal pulses in \ac{agb} stars.
+During a third dredge up event, material from the CO core is mixed with material exposed to partial He-shell burning, increasing C and O abundances in the envelope \citep{KL14}.
+If this envelope is lost during the \ac{agb} phase, then C yields are enhanced.
+Hot bottom burning is the activation of proton capture reactions, and the CNO cycle%
 \footnote{The CNO (I) cycle is
@@
 Because the $^{14}$N(p, $\gamma$) proton capture is the slowest component of the CNO cycle \citep{solar-fusion}, the CNO cycle converts nearly all \isotope[12]{C} into \isotope[14]{N}.
-As a result, when both TDU and HBB occur, \isotope[12]{C} yields are lowered (see discussion in \citealt{james+23} and \citealt{ventura+13}).
-
-In this work, I explore four different sets of AGB star yield tables from literature, providing well-sampled grids in metallicity and mass for use in chemical evolution models. 
+As a result, when both third dredge up and Hot bottom burning occur, \isotope[12]{C} yields are lowered (see discussion in \citealt{james+23} and \citealt{ventura+13}).
+
+In this work, I explore four different sets of \ac{agb} star yield tables from literature, providing well-sampled grids in metallicity and mass for use in chemical evolution models. 
 \begin{itemize}
@@
 \end{itemize}
-I use C11 table, amplified by a factor of 2.9, as the fiducial AGB yield.
-
-Fig.~\ref{fig:y_agb} compares the AGB C yield $\tilde{y}_\text{C}^\text{AGB}(M, Z)$ for each model I consider. 
-The yields may be negative if a star returns material to the ISM with a lower C abundance than the material the star was formed from.
-Most models agree on the qualitative shape of the net fractional AGB C yield---% 
+I use C11 table, amplified by a factor of 2.9, as the fiducial \ac{agb} yield.
+
+Fig.~\ref{fig:y_agb} compares the \ac{agb} C yield $\tilde{y}_\text{C}^\text{AGB}(M, Z)$ for each model I consider. 
+The yields may be negative if a star ejects material with a lower average C abundance than the material the star was formed from.
+Most models agree on the qualitative shape of the net fractional \ac{agb} C yield---% 
 stars with masses between \about{2~M_\odot} and \about{4~M_\odot} have the highest fractional C yields, with the mass of the peak increasing and overall yields decreasing with increasing $Z$.
-High mass, high $Z$ stars destroy \isotope[12]{C} because they experience both TDU and HBB, but HBB is much more efficient.
-
-In Fig.~\ref{fig:agb-ssp}, I plot the total production of C by AGB stars in a SSP at an age $t$. 
+High mass, high $Z$ stars destroy \isotope[12]{C} because they experience both third dredge up and hot bottom burning, but the latter is much more efficient.
+
+In Fig.~\ref{fig:agb-ssp}, I plot the total production of C by \ac{agb} stars in a \ssp{} at an age $t$. 
 Effectively, this is equivalent to integrating Eq.~\ref{eq:imf-yield} down to $M_{to}$, the turnoff mass for time $t$.
@@
 from \citealt{larson74}.})
-As the mass range $2\lesssim M \lesssim 4$ is most important for C production, about half of C production occurs before \about{1} Gyr, similar to SNe Ia Fe. 
+As the mass range $2\lesssim M \lesssim 4$ is most important for C production, about half of C production occurs before \about{1} Gyr, similar to \ac{ia} Fe. 
 K10 and K16 weight C production more heavily towards massive stars resulting in a faster enrichment delay time, whereas the C11 and V13 models predict a slightly longer timescale of \about{1} Gyr, but little to no C is produced more than 2 Gyr after a star formation event.
@@
  	    \includegraphics[scale=1]{agb_yields.pdf}
-        \caption[AGB C yields]{The net fractional AGB C yield  plotted as a function of initial stellar mass $M$ and color-coded according to metallicity.
+        \caption[Low mass C yields]{The net fractional \ac{agb} C yield  plotted as a function of initial stellar mass $M$ and color-coded according to metallicity.
 The black dashed line shows $\tilde{y}=0$ for reference.
-Each panel represents yields from one of four AGB models: C11, K10, V13, K16 (see \S \ref{sec:agb}).
+Each panel represents yields from one of four \ac{agb} models: C11, K10, V13, K16 (see \S \ref{sec:agb}).
 }
@@
 
-    \caption[AGB yields delay time distribution]{
-        C production by AGB stars as a function of SSP age, normalized to the total mass $M_{\rm tot}$ produced at $t=10$ Gyr.
-Left: The four AGB yield models from literature at solar metallicity (C11, K10, V13, or K16).
+    \caption[C yields delay time distribution]{
+    C production by \ac{agb} stars as a function of \ssp{} age, normalized to the total mass $M_{\rm tot}$ produced at $t=10$ Gyr.
+Left: The four \ac{agb} yield models from literature at solar metallicity (C11, K10, V13, or K16).
 The delay time distribution of type Ia supernovae ($\propto t^{-1.1}$) is plotted as a dashed black line for comparison.
-Right: The C11 AGB model at different metallicities.
+Right: The C11 \ac{agb} model at different metallicities.
 }
@@
 
-Fig.~\ref{fig:yagb-z} shows IMF-averaged C yields for each AGB model as a function of metallicity $Z$.
+Fig.~\ref{fig:yagb-z} shows \imf-averaged C yields for each \ac{agb} model as a function of metallicity $Z$.
 V13 differs in that it shows a non-monotonic metallicity dependence. However, this effect is only for models with $\log Z/Z_\odot \lesssim -1$.
@@
 
-    \caption[AGB yield metallicity dependence]{The net fractional IMF-weighted AGB C yield $\Ycagb$ as a function of metallicity for each of our AGB yield models.
+    \caption[Low mass yield metallicity dependence]{The net fractional \imf-weighted \ac{agb} C yield $\Ycagb$ as a function of metallicity for each of our \ac{agb} yield models.
     }
@@
 Massive stars form $^{12}$C in their cores through the triple--$\alpha$ process. However, only C ejected through supernovae and stellar winds contributes to the yield. 
-While there are many stellar models providing predictions of CCSNe yields, the results of these models are highly uncertain due to the many stellar modeling uncertainties.
-
-In Fig.~\ref{fig:y_cc}, I plot calculations of the IMF-integrated yields, defined with Eq.~\ref{eq:imf-yield} (computed using \VICE's \texttt{vice.yields.ccsne.fractional} function). 
-CCSNe models predict a wide range of C yields, spanning almost 1 dex. 
+While there are many stellar models providing predictions of \cc{} yields, the results of these models are highly uncertain due to the many stellar modeling uncertainties.
+
+In Fig.~\ref{fig:y_cc}, I plot calculations of the \imf-integrated yields, defined with Eq.~\ref{eq:imf-yield} (computed using \VICE's \texttt{vice.yields.ccsne.fractional} function). 
+\cc{} models predict a wide range of C yields, spanning almost 1 dex. 
 Both the \citet{NKT13} and \cite{LC18} models show positive metallicity dependence. 
@@
 Fig.~\ref{fig:y_cc} shows the C11 model for comparison on the top.
-Especially at $Z\approx Z_\odot$, most CCSNe models dominate AGB C production.
-I will later also show empirically that CCSNe should dominate C production.
-
-On the bottom of Fig.~\ref{fig:y_cc}, I also show the CCSNe-[C/Mg] ratio, defined by
+Especially at $Z\approx Z_\odot$, most \cc{} models dominate \ac{agb} C production.
+I will later also show empirically that \cc{} should dominate C production.
+
+On the bottom of Fig.~\ref{fig:y_cc}, I also show the \cc{}-[C/Mg] ratio, defined by
 \begin{equation}\label{eq:c_mg_cc}
@@
 \end{equation}
-${\rm [C/Mg]^{CC}}$ describes what [C/Mg] would be if CCSNe were the only process producing C.
-Once again, different CCSNe models span a large range in [C/Mg]. 
-I chose to instead parameterize $\Ycc$ to enable agreement with observations, as most CCSNe models fail to achieve near-solar [C/Mg].
+${\rm [C/Mg]^{CC}}$ describes what [C/Mg] would be if \cc{} were the only process producing C.
+Once again, different \acp{cc} models span a large range in [C/Mg]. 
+I chose to instead parameterize $\Ycc$ to enable agreement with observations, as most \acp{cc} models fail to achieve near-solar [C/Mg].
 Assumptions about the explodability landscape affect C and Mg production.
@@
 
-CCSNe models also do not reach [O/Mg] due to overproduction of O, or underproduction of Mg, or both \citep{emily+21}.
-Here, I assume ${\rm [O/Mg]} = 0$, which is not compatible with CCSNe models but is consistent with APOGEE observations \citep{weinberg+19, weinberg+22}.
+\acp{cc} models also do not reach [O/Mg] due to overproduction of O, or underproduction of Mg, or both \citep{emily+21}.
+Here, I assume ${\rm [O/Mg]} = 0$, which is not compatible with \acp{cc} models but is consistent with \apogee{} observations \citep{weinberg+19, weinberg+22}.
 
@@
     \includegraphics{y_c_cc.pdf}
-    \caption[CCSNe C yields]{
+    \caption[Massive star C yields]{
         C yields from massive stars.
-        \textbf{Top:} The IMF-weighted CCSNe yield of C as a function of metallicity.
-        \textbf{Bottom:} The CCSNe [C/Mg] abundance ratio, defined in Eq.~\ref{eq:c_mg_cc}. The black line represents the C yield of the fiducial model,
+        \textbf{Top:} The \imf-weighted \acp{cc} yield of C as a function of metallicity.
+        \textbf{Bottom:} The \acp{cc} [C/Mg] abundance ratio, defined in Eq.~\ref{eq:c_mg_cc}. The black line represents the C yield of the fiducial model,
     $\Ycc = 0.0028 + 0.001 (Z/Z_{\odot})$. Yields are shown for tables from 
@@
 I define $M_{X}$ to be the mass of element X in the gas phase, $\dot{M}_\star$ to be the star formation rate (in M$_\odot$ yr$^{-1}$), and $\eta$ to be the mass loading factor $\eta\equiv\dot{M}_{\rm outflow}/\dot{M}_\star$ (representing the strength of outflows).
-SSPs return a fraction $r$ of their birth mass back to the ISM, due to ejected stellar envelopes. ($r\approx0.4$ for a \citealt{kroupa01} IMF.)
-Given the IMF-averaged yield of Mg $y_{\rm Mg}$, the rate of change in the ISM mass of Mg $\dot{M}_{\rm Mg}$ is a simple sum of sources and sinks,
+\ssp's return a fraction $r$ of their birth mass back to the interstellar medium, due to ejected stellar envelopes.
+($r\approx0.4$ for a \citealt{kroupa01} \imf.)
+Given the \imf-averaged yield of Mg $y_{\rm Mg}$, the rate of change in the gas-phase mass of Mg $\dot{M}_{\rm Mg}$ is a simple sum of sources and sinks,
 \begin{equation}
@@
 \end{equation}
-where the first term on the right-hand side describes CCSNe enrichment. 
+where the first term on the right-hand side describes \acp{cc} enrichment. 
 In terms of the return mass fraction of stars $r$, the mass lost to remnants is $Z_X (1-r)\dot{M}_\star$.
 And, the outflows deplete mass at a rate $Z_X \eta\dot{M}_\star$.
-( I assume the composition of outflows is the same as the ISM.) Substituting for $\eta$ and $r$,
+( I assume the composition of outflows is the same as the interstellar medium.) Substituting for $\eta$ and $r$,
 \begin{equation}
@@
 
-While Equation \ref{eq:z_eq} can be applied to CCSNe C, the delayed nature of AGB C can complicate the expression.
+While Equation \ref{eq:z_eq} can be applied to \acp{cc} C, the delayed nature of \ac{agb} C can complicate the expression.
 Instead, I use an effective yield, which can be expressed as an integral over the DTD,
@@
 \end{equation}
-Analogous to \cite{james+23} arguments about N, the trends in abundance ratios are set by yield ratios in these GCE models.
-The effect of other GCE parameters (most importantly $\eta$) cancels.
+Analogous to \cite{james+23} arguments about N, the trends in abundance ratios are set by yield ratios in these \gce{} models.
+The effect of other \gce{} parameters (most importantly $\eta$) cancels.
 As a consequence, yield ratios should establish abundance ratio trends in models which assume a different normalization of element yields and mass-loading (see discussion below).
 This argument can also be inverted to infer  yields from abundance ratio trends.
-To the extent that observed C and Mg trends reflect the equilibrium abundances in different Galactic regions, we can infer the CCSNe yield given an assumed AGB star yield (or vice versa).
+To the extent that observed C and Mg trends reflect the equilibrium abundances in different Galactic regions, we can infer the \acp{cc} yield given an assumed \ac{agb} star yield (or vice versa).
 Inferring $\Ycc$ from $\Ycagb$,
@@
 
-In \S\ref{sec:f-z-models}, I will show that none of the four AGB yield sets (C11, K10, V13, K16) produce enough C relative to this $\Ycc$ value.
+In \S\ref{sec:f-z-models}, I will show that none of the four \ac{agb} yield sets (C11, K10, V13, K16) produce enough C relative to this $\Ycc$ value.
 So, I introduce normalization factors, $\alpha_{\rm AGB}$, and $\alpha_{\rm CC}$ which denote a multiplicitave scaling of $\Ycc$ and $\Ycagb$ respectively.
@@
 In \S\ref{sec:f-z-models}, I find that $\alpha_{\rm AGB}\approx 2.9$ for the C11 yield model.
-Using this AGB yield, I can now use Eq.~\ref{eq:y_c_eq} to find an estimate of $\Ycc$ as a function of metallicity.
+Using this \ac{agb} yield, I can now use Eq.~\ref{eq:y_c_eq} to find an estimate of $\Ycc$ as a function of metallicity.
 I show the values of $\Ycc$ I obtain from the subgiant sample in Fig.~\ref{fig:analytic}.
@@
     \caption[Reverse fit yields]{Inferred massive star C yields as a function of metallicity.
-I assume equilibrium and $3\times {\rm C11}$ AGB yields (orange curve, see discussion in Section \ref{sec:equilibrium}).
+I assume equilibrium and $3\times {\rm C11}$ \ac{agb} yields (orange curve, see discussion in Section \ref{sec:equilibrium}).
 The binned medians and median absolute deviation (divided by $\sqrt{N}$) are blue points.
@@
 
-I only perform this analysis on the C11 yields because C11 has yields tables more finely sampled in metallicity than the other three AGB yield tables.
+I only perform this analysis on the C11 yields because C11 has yields tables more finely sampled in metallicity than the other three \ac{agb} yield tables.
 As the metallicity range of the data is small ($-0.4\lesssim {\rm [Mg/H]} \lesssim 0.4$), other models are more challenging to interpret in this range.
-Furthermore, the APOGEE observations may have systematics, and other measurements of C abundances \citep[e.g.][]{vincenzo+21} have slight disagreements in the overall shape of the trend (see \S\ref{sec:jack}).
-So, this expression of $\Ycc/\Yoc$ depends on the chosen AGB yield table, the AGB fraction, and the dataset. 
+Furthermore, the \apogee{} observations may have systematics, and other measurements of C abundances \citep[e.g.][]{vincenzo+21} have slight disagreements in the overall shape of the trend (see \S\ref{sec:jack}).
+So, this expression of $\Ycc/\Yoc$ depends on the chosen \ac{agb} yield table, the \ac{agb} fraction, and the dataset. 
 Additionally, these yields will be systematically biased if the galaxy is out of equilibrium, for example due to a recent starburst (Isern et al.
@@
 
-Classical, ``one-zone'' models of chemical evolution assume instantaneous mixing of metals in the star-forming ISM \citep[e.g.][]{matteucci21}.
+Classical, ``one-zone'' models of chemical evolution assume instantaneous mixing of metals in the star-forming interstellar medium \citep[e.g.][]{matteucci21}.
 This simple framework is a poor approximation for the Milky Way.
@@
 Star formation ends beyond a radius $R=15.5$ kpc.
-I initially assume an ``inside-out'' Star Formation History (SFH), where the star formation surface density $\Sigma_\star$ is given by
+I initially assume an ``inside-out'' \sfh{}, where the star formation surface density $\Sigma_\star$ is given by
 \begin{equation}
@@
 The star formation history is normalized such that the total stellar mass reaches $M_\star=5.17\times10^{10} {\rm M}_\odot$ \citep{LM15} and at each $R$ to match the stellar surface density gradient \citep{BHG16}.
-The gas inflow is calculated to maintain our chosen SFR for each radius and time. The gas-SFR law is based on an extension of a Kennicutt-Schmidt law \citep{kennicutt98}, motivated by 
-\begin{equation}
-\dot{\Sigma}_{\star} \propto \\
+The gas inflow is calculated to maintain our chosen \sfh{} for each radius and time. The gas-SFR law is based on an extension of a Kennicutt-Schmidt law \citep{kennicutt98}, motivated by 
+\begin{equation}
+\dot{\Sigma}_{\star} \propto 
 \begin{cases}
@@
 \end{equation}
-The scaling of this relationship varies with time due to the redshift dependence of $\tau_\star$ in molecular gas observed by \citet{tacconi18}. I assume a Kroupa IMF \cite{kroupa01}.
+The scaling of this relationship varies with time due to the redshift dependence of $\tau_\star$ in molecular gas observed by \citet{tacconi18}. I assume a Kroupa \imf \cite{kroupa01}.
 
 \JJ\ accounts for radial migration by using the results of the \texttt{h277} hydrodynamical simulation \citep{christensen12, zolotov12, loebman12, BZ14}, with simulation parameters described in \citet{bird+21}.
-Each \VICE single stellar population (SSP) is matched to an \textit{analog} in \texttt{H277}, chosen to form at a similar time and radius $R$.
-By taking the change in radius $\Delta R$ of the analogs, the SSP move to their final radii with a $\sqrt{\text{time}}$ dependence.
+Each \VICE\ single stellar population (SSP) is matched to an \textit{analog} in \texttt{H277}, chosen to form at a similar time and radius $R$.
+By taking the change in radius $\Delta R$ of the analogs, the \ssp move to their final radii with a $\sqrt{\text{time}}$ dependence.
 This relationship between displacement and time arises when migration proceeds as a consequence of the diffusion of angular momentum \citep{frankel18, frankel20}.
@@
 
-\citet{james+23} compare their model against the \cite{vincenzo+21} sample of APOGEE \citep{apogee17} red giants whose C and N abundance have been corrected for mixing process using MESA stellar evolution models.
-I instead use the \citetjack~sample of APOGEE subgiants.
-Subgiant stars have not undergone FDU, so their atmospheric C and N abundances are still reflective of their birth abundances and do not need mixing corrections.
+\citet{james+23} compare their model against the \cite{vincenzo+21} sample of \apogee{} \citep{apogee17} red giants whose C and N abundance have been corrected for mixing process using MESA stellar evolution models.
+I instead use the \citetjack~sample of \apogee{} subgiants.
+Subgiant stars have not undergone first dredge up but have well mixed atmospheres, so their atmospheric C and N abundances are still reflective of their birth abundances and do not need mixing corrections.
 I additionally only compare the models to the low-$\alpha$ sequence.
@@
 Here, I present the time evolution of our fiducial model. In the next sections, I will discuss the choice of parameters and agreement with observations. 
-The fiducial model has the following qualitative characteristics of its C yields: (a) C is predominantly produced in CCSNe, (b) CCSNe produce more C at higher metallicities, and (c) AGB stars produce less carbon at higher metallicities.
-Our fiducial model uses the C11 AGB yield tables (see \S\ref{sec:agb}, and Table \ref{tab:fiducial_mod}), and I amplify the C11 yields by a factor of 2.9 such that AGB stars account for 20\% of carbon at $Z=Z_\odot$.
+The fiducial model has the following qualitative characteristics of its C yields: (a) C is predominantly produced in \acp{cc}, (b) \acp{cc} produce more C at higher metallicities, and (c) \ac{agb} stars produce less carbon at higher metallicities.
+Our fiducial model uses the C11 \ac{agb} yield tables (see \S\ref{sec:agb}, and Table \ref{tab:fiducial_mod}), and I amplify the C11 yields by a factor of 2.9 such that \ac{agb} stars account for 20\% of carbon at $Z=Z_\odot$.
 
 I show the time evolution tracks of the fiducial model in Fig.~\ref{fig:c_evo} for \caah~ and \caafe~.
-Comparing [C/$\alpha$] against [Mg/Fe] enables us to see the late-time evolution of C more clearly.
-Because of the extended DTD of SNeIa enrichment, [Fe/H] takes longer to reach equilibrium as half of Fe production comes from type-Ia supernovae, and the late time evolution is not as clustered as [$\alpha$/H].
+Comparing [C/Mg] against [Mg/Fe] enables us to see the late-time evolution of C more clearly.
+Because of the extended DTD of \ac{ia} enrichment, [Fe/H] takes longer to reach equilibrium as half of Fe production comes from type-Ia supernovae, and the late time evolution is not as clustered as [Mg/H].
 The evolution proceeds as follows.
-Initially, CCSNe dominate production.
+Initially, \acp{cc} dominate production.
 As $\Ycc$ has strong metallicity dependence, [C/Mg] increases with time.
-Shortly thereafter, AGB stars contribute delayed C, increasing [C/Mg] even more steeply.
+Shortly thereafter, \ac{agb} stars contribute delayed C, increasing [C/Mg] even more steeply.
 As Mg begins to reach equilibrium, the [C/Mg] ratio plateaus as C approaches equilibrium.
 Finally, as $\Ycagb$ decreases or even becomes negative with higher metallicity, the [C/Mg] abundance may decline slightly.
-
 This is even more evident in the lower panel of Fig.~\ref{fig:c_evo}.
-While the \caah~trend reaches equilibrium at \about{5} Gyr, the \caafe~trend continues to evolve even until the present day, exposing the effect of the relative delay times of AGB stars and SNeIa.
+While the \caah~trend reaches equilibrium at \about{5} Gyr, the \caafe~trend continues to evolve even until the present day, exposing the effect of the relative delay times of \ac{agb} stars and \ac{ia}.
 
@@
     Time evolution of gas phase C abundances in our fiducial model.
-
-    Top: Evolutionary tracks parameterized by time at fixed Galactocentric radius in the \caah and \caafe planes.
-
-    Bottom: snapshots of the gas-phase \caah~and \caafe~trend, parameterized by radius at a fixed time.
+    {\bf Top:} Evolutionary tracks parameterized by time at fixed Galactocentric radius in the \caah\ and \caafe\ planes. 
+    {\bf Bottom:} snapshots of the gas-phase \caah\ and \caafe\ trend, parameterized by radius at a fixed time.
 }
@@
 
-In Fig.~\ref{fig:agb_sims}, I compare the K10, K16, C11, and V13 yield models.
-Each model uses the published, unscaled yield tables.
-As the highest AGB yield at solar, K10 is only $\Ycagb=0.000585$, $f_{\rm AGB} \leq 0.12$ for all models.
+Fig.~\ref{fig:agb_sims} compares the K10, K16, C11, and V13 yield models.
+Here, I use the published, unscaled yield tables.
+As the highest \ac{agb} yield at solar, K10 is only $\Ycagb=0.000585$, $f_{\rm AGB} \leq 0.12$ for all models.
 Massive stars dominate C production with unscaled yields.
-While it is easy to modify the AGB yields in my model, their small contribution reduces the effect.
-I leave a more detailed discussion of the effects of AGB models for Appendix \ref{sec:alt_agb} and use C11 yields hereafter.
+While it is easy to modify the \ac{agb} yields in my model, their small contribution reduces the effect.
+I leave a more detailed discussion of the effects of \ac{agb} models for Appendix \ref{sec:alt_agb} and use C11 yields hereafter.
 
@@
     Stellar abundance trends in our model, assuming metallicity independent $\Ycc$.
-Colored lines quantify the median [C/Mg] in bins of [Mg/H] for our four AGB yield models from the literature (see \ref{sec:agb}).
+Colored lines quantify the median [C/Mg] in bins of [Mg/H] for our four \ac{agb} yield models from the literature (see \ref{sec:agb}).
 Black points and grey dashes represent the median and standard deviations in the \citetjack~sample.
@@
 
-Next, I investigate adjustments to the AGB yield fraction $f_{\rm AGB}$ and the CCSNe metallicity dependence $\zeta$ in Fig.~\ref{fig:beta_f}.
+Next, I investigate adjustments to the \ac{agb} yield fraction $f_{\rm AGB}$ and the \acp{cc} metallicity dependence $\zeta$ in Fig.~\ref{fig:beta_f}.
 On the top panel of Fig.~\ref{fig:beta_f}, I plot models with varying $\Ycc$ metallicity dependence.
 As discussed in \S\ref{sec:equilibrium}, the \caah~trend is approximated by equilibrium, so the trends of these have steeper \caah~corresponding to steeper metallicity dependence.
-However, \caafe~is minimally affected by these changes since CCSNe are instantaneous in this model.
-
-Now, I vary the proportion of AGB contribution.  The AGB C production fraction is defined as
+However, \caafe~is minimally affected by these changes since \acp{cc} occure on much shorter timescales than \ac{ia} and \ac{agb} enrichment.
+
+Now, I vary the proportion of \ac{agb} contribution.  The \ac{agb} C production fraction is defined as
 \begin{equation}
@@
 where  $\Ycagb$ includes the multiplicative factor $\alpha_{\rm AGB}$ as defined in Eq.~\ref{eq:alpha}.
-In the bottom panel of Fig.~\ref{fig:beta_f}, I plot three models with different AGB fractions while using C11 yields.
-The \caafe~relationship is set by $f_{\rm AGB}$ because a specific amount of C must be released at a delayed time in order to match the SNeIa production of Fe and increase [C/Mg] as [Mg/Fe] decreases to reproduce the data.
+In the bottom panel of Fig.~\ref{fig:beta_f}, I plot three models with different \ac{agb} fractions while using C11 yields.
+The \caafe~relationship is set by $f_{\rm AGB}$ because a specific amount of C must be released at a delayed time in order to match the \ac{ia} production of Fe and increase [C/Mg] as [Mg/Fe] decreases to reproduce the data.
 Increased $f_{\rm AGB}$ results in a decreased slope in \caah, owing to the negative metallicity dependence of $\Ycagb$.
@@
 
-One source of theoretical uncertainty in this result is that the SNeIa yield and DTD have their own uncertainties.
+One source of theoretical uncertainty in this result is that the \ac{ia} yield and DTD have their own uncertainties.
 I discuss variations in $y_{\rm Fe}^{\rm Ia}$ in Appendix \ref{sec:alt_agb}, and find that the qualitative conclusions are largely unaffected.
-I therefore focus on the choices of $y_{\rm Fe}^{\rm Ia} = 0.00214$ choices from the fiducial model here.
-
-So, the scaling of the trend and metallicity dependence of C (as seen in
-the \caah~trend) gives information on the total C yield and the behavior of CCSNe (as the dominating producer of C); the \caafe trend exposes the delayed effect of C from AGB contribution.
+I therefore focus on the choices of $y_{\rm Fe}^{\rm Ia} = 0.00214$ and a $\propto t^{-1.1}$ DTD choices from the fiducial model here.
+In short, the scaling of the trend and metallicity dependence of C (as seen in
+the \caah\ trend) gives information on the total C yield and the behavior of \acp{cc} (as the dominating producer of C), the \caafe\ trend exposes the delayed effect of C from \ac{agb} contribution.
 
@@
 	\centering
-    \caption[AGB net solar IMF yields]{For each AGB yield set, our calculation of the effective SFH- and IMF-weighted C AGB yield, along with the multiplicative factor reaches an AGB contribution of 20\%.}
+    \caption[Low mass star solar C yields]{For each \ac{agb} yield set, the \imf-weighted C \ac{agb} yield at solar metallicity, along with the multiplicative factor reaches an \ac{agb} contribution of 20\%.}
 	\label{tab:alpha_agb}
@@
 
-\caption[Adjusted yield models]{Similar to Fig.~\ref{fig:agb_sims} except the top plot shows the fiducial model with lower and higher values of $\zeta$, the C-CCSNe metallicity dependence.
+\caption[Adjusted yield models]{Similar to Fig.~\ref{fig:agb_sims} except the top plot shows the fiducial model with lower and higher values of $\zeta$, the meatllicity dependence of $\Ycc$.
 The bottom plot shows models with $f_{\rm AGB}=$0.1, 0.2, and 0.4.
@@
 
-\caption[Lateburst models]{Same as Fig.~\ref{fig:agb_sims} but comparing the fiducial model to alternate star formation histories (see \S \ref{sec:sfh}).}
+\caption[Lateburst models]{Same as Fig.~\ref{fig:agb_sims} but comparing the fiducial model to alternate \sfh{}s (see \S \ref{sec:sfh}).}
 \label{fig:sfh_models}
@@
 
-Here, I consider a "late burst" model, created by multiplying our fiducial "inside-out" SFH with a Gaussian.
+Here, I consider a "lateburst" model, created by multiplying our fiducial "inside-out" \sfh{} with a Gaussian.
 \begin{equation}\label{eq:lateburst}
@@
 
-I also consider an early burst model as a slight variation of the late burst, where the burst is instead exponential and placed at $t_1=5$ Gyr.
-This approximately corresponds to the Gaia-Encelidus merger, inducing higher star formation in the Milky Way \citep{spitoni21, bonaca20, helmi18}.
+I also consider an earlyburst model as a slight variation of the lateburst, where the burst is instead exponential and placed at $t_1=5$ Gyr. 
 \begin{equation}\label{eq:twoinfall}
@@
 where I take the burst duration, $\tau_{\rm burst}=1$ Gyr in this case. 
-
-I show three models with these alternate SFH in Fig.~\ref{fig:sfh_models}.
-The changes to SFH leave \caah\ unchanged, but they do introduce slight variation in \caafe.
-Models with higher AGB fractions are more sensitive to variations in SFH.
+This approximately corresponds to the Gaia-Encelidus merger, inducing higher star formation in the Milky Way \citep{spitoni21, bonaca20, helmi18}.
+
+Fig.~\ref{fig:sfh_models} shows three models with these alternate \sfh{}.
+Changes to the \sfh{} leave \caah\ unchanged, but they do introduce slight variation in \caafe.
+Models with higher \agb{} fractions are more sensitive to variations in \sfh{}.
 The late burst models result in [C/Mg] continuing to increase at low [Mg/Fe], but also introduce a break not present in the data.
@@
 is able to reproduce the slight break between the low and high $\alpha$ sequences, but overshoots equilibrium more severely than the fiducial model. 
-The choice of SFH does not change the large-scale slope of \caafe~significantly, so variations of SFH only have minimal effect on my conclusions.
+The choice of \sfh{} does not change the large-scale slope of \caafe~significantly, so variations of \sfh{} only have minimal effect on my conclusions.
 
@@
 
-GCE models of the Milky Way fall into two classes---those which incorporate significant mass-loading (e.g., as in this work) and those which neglect mass-loading but lower effective yield to match observed abundances \citep{MCM13, MCM14, spitoni19, spitoni20, spitoni21}.
+\gce{} models of the Milky Way fall into two classes---those which incorporate significant mass-loading (e.g., as in this work) and those which neglect mass-loading but lower effective yield to match observed abundances \citep{MCM13, MCM14, spitoni19, spitoni20, spitoni21}.
 An increase in stellar yields has a nearly identical effect as a decrease in the mass-loading factor $\eta$ (see Appendix B of \cite{james_dwarf}).
@@
 So, I show in Fig.~\ref{fig:scatter} a comparison of the predicted distribution of the model to the contours of the subgiant sample.
-Our model reproduces this 2-dimension distribution well when including scatter based on the median APOGEE abundance errors for each metallicity bin.
+Our model reproduces this 2-dimension distribution well when including scatter based on the median \apogee{} abundance errors for each metallicity bin.
 Some of the scatter is due to radial migration, but observational errors are dominant.
@@
 As an additional test of the model, I next compare the gas-phase predictions against gas-phase C data.
-In Fig.~\ref{fig:gas_phase}, I plot our fiducial model's gas phase predictions compared to observations of MW and extragalactic HII regions, halo stars, and Damped Lyman Alpha (DLA) systems.
+In Fig.~\ref{fig:gas_phase}, I plot our fiducial model's gas phase predictions compared to observations of MW and extragalactic HII regions, halo stars, and \acf{dla} systems.
 The model is broadly consistent with observations, where the model at $t=2$ Gyr approximates the slope of dwarf galaxies and halo stars.
@@
 I model both Mg and O as metallicity-independent population-averaged yields dominated by massive stars.
-${\rm [O/Mg]}\approx 0$ across a wide range of metallicities in APOGEE \citep{weinberg+19, weinberg+22}.
+${\rm [O/Mg]}\approx 0$ across a wide range of metallicities in \apogee{} \citep{weinberg+19, weinberg+22}.
 I adopt O and Mg relative yields given by the solar mixture of \cite{asplund+09}.
@@
 Additionally, recombination and collisionally excitation measurements disagree by a factor of \about{2} \cite{GR07}.
-Additional to measurement errors, variations in SFH may explain the scatter, as C contains delayed enrichment, and bursts cause variations in C/O.
+Additional to measurement errors, variations in \sfh{} may explain the scatter, as C contains delayed enrichment, and bursts cause variations in C/O.
 
 The decreasing [C/O] abundance at very-low metallicities is likely due to population III stellar yields \citep[e.g.][]{hirschi07}, as suggested by \citep{cooke+17, FN15}.
-As AGB stars do have a significant delay, these stars cannot explain the increase in C yields at low metallicity as the timescales to reach $\rm [O/H]\sim -1$ is faster than this enrichment can occur.
+As \ac{agb} stars do have a significant delay, these stars cannot explain the increase in C yields at low metallicity as the timescales to reach $\rm [O/H]\sim -1$ is faster than this enrichment can occur.
 So, enhanced carbon due to (rotating) massive population III stars at low metallicities explains this trend.
@@
     HII regions    \citep[pink circles;][]{skillman+20, esteban+02, esteban+09, esteban+14, esteban+19}
-    Damped Lynman-$\alpha$ (DLA) systems \citep[blue triangles;][]{cooke+17} 
+    \acf{dla} systems \citep[blue triangles;][]{cooke+17} 
     Milky Way halo and thick disk stars \citep[green stars;][]{nissen+14, fabbian+09}. 
@@
 
-In this work, I investigate the role of C yields on the predictions of multizone GCE models.
+In this work, I investigate the role of C yields on the predictions of multizone \gce{} models.
 \citet{james+23} performed a similar analysis focusing on N.
-They found that matching the observed relationship between N and O abundances (REFS) requires relative N and O yields from simple stellar populations with a roughly linear dependence on metallicity (i.e.
+They found that matching the observed relationship between N and O abundances \citep{HEK00,PVT10,berg+12, berg+20, skillman+20, izotov+12, james2+15, dopita+16} requires relative N and O yields from simple stellar populations with a roughly linear dependence on metallicity (i.e.
 $y_{\rm N}/y_{\rm O} \propto Z$).
@@
 
-Though CCSNe C yields are poorly understood, I adopt an equilibrium approximation and determine a functional form that approximately matches trends in APOGEE subgiants and is consistant with massive star nucleosynthesis models.
-Variations of the metallicity dependence of this CCSNe yield affect trends in \caah~but do not affect trends in \caafe\ when taking a slice in [Mg/H].
-As all theoretical AGB C yields decrease with metallicity, increasing the AGB fraction causes the \caah\ trend to flatten.
-However, the \caafe\ trend is sensitive to the AGB fraction.
-From this, I estimate that AGB stars contribute \about{20\%} of total C abundance at solar metallicity.
+Though \acp{cc} C yields are poorly understood, I adopt an equilibrium approximation and determine a functional form that approximately matches trends in \apogee{} subgiants and is consistant with massive star nucleosynthesis models.
+Variations of the metallicity dependence of this \acp{cc} yield affect trends in \caah~but do not affect trends in \caafe\ when taking a slice in [Mg/H].
+As all theoretical \ac{agb} C yields decrease with metallicity, increasing the \ac{agb} fraction causes the \caah\ trend to flatten.
+However, the \caafe\ trend is sensitive to the \ac{agb} fraction.
+From this, I estimate that \ac{agb} stars contribute \about{20\%} of total C abundance at solar metallicity.
 The remaining \about{80\%} of C comes from massive stars with a metallicity dependent yield of $\Ycc/\Yoc=1.51 + 0.54 (Z/Z_\odot)$.
@@
 
-I additionally explore variations of the assumed SFH and outflow mass-loading factor $\eta$.
-I find that alternate SFHs can slightly affect \caafe, but \caah~is mostly unaffected.
+I additionally explore variations of the assumed \sfh{} and outflow mass-loading factor $\eta$.
+I find that alternate \sfh{}s can slightly affect \caafe, but \caah~is mostly unaffected.
 Decreasing both outflows and yields by the same factor leaves the \caah~and \caafe~trends unaffected.
@@
 Future spectroscopic surveys combined with Gaia kinematics \citep{gaia} will continue to enhance our understanding of chemical evolution.
-Both SDSS-V/MWM \citep{sdssv} and the DESI Milky Way survey \citep{desi, desi:mw} will each measure spectra of $>6$ million Milky Way stars.
+Both the Sloan Digital Sky Survey V's Milky Way Mapper program (SDSS-V/MWM) \citep{sdssv} and the Dark Energy Spectroscopic Instrument (DESI) Milky Way survey \citep{desi, desi:mw} will each measure spectra of $>6$ million Milky Way stars.
 These larger samples will enable similar work to tighten constraints on stellar models and our understanding of galaxy structure and evolution.
@@
 \bibliography{main}
+
+\newpage
+
+\printacronyms
+\addcontentsline{toc}{chapter}{Acronyms}
 
@@
 
-I use the criteria outlined in \citetjack~to create a sample of subgiants from APOGEE DR17 \cite{apogee17} as our primary observational constraint.
+I use the criteria outlined in \citetjack~to create a sample of subgiants from \apogee{} DR17 \cite{apogee17} as our primary observational constraint.
 Subgiants are reflective of birth abundances for CNO \citep{souto19}.
@@
     \caption[Subgiant selection]{
-        A Kiel diagram of APOGEE stars.
+        A Kiel diagram of \apogee{} stars.
 Following \citetjack, we select subgiants in the orange polygon (see Equation \ref{eq:subgiant_selection}).
@@
 
-Additionally, I included stars in APOGEE marked by the following flags.
+Additionally, I included stars in \apogee{} marked by the following flags.
 \begin{itemize}
@@
 
-A second approach in determining birth abundances in stars is to correct the surface abundance effects of FDU, as in \cite{vincenzo+21}.
+A second approach in determining birth abundances in stars is to correct the surface abundance effects of first dredge up, as in \cite{vincenzo+21}.
 I note that there is a slight difference in the yields found through \cite{vincenzo+21} and \citetjack.
@@
 This is a known problem (see \citet{emily+21}).
-CCSNe models overpredict O or underpredict Mg, and the resolution is still unknown.
-My results are, however, independent of whether the CCSNe element is O or Mg.
-
-While I focus the main discussion of the paper on the C11 model, other AGB models can impact abundance trends when $f_{\rm AGB}$ becomes larger.
-Here, I briefly explore the effects of variations in AGB models that affect abundance trend predictions when these models are amplified to match observational [C/MG]-[Mg/Fe] trends. 
+\acsp{cc} models overpredict O or underpredict Mg, and the resolution is still unknown.
+My results are, however, independent of whether the \acs{cc} element is O or Mg.
+
+While I focus the main discussion of the paper on the C11 model, other \ac{agb} models can impact abundance trends when $f_{\rm AGB}$ becomes larger.
+Here, I briefly explore the effects of variations in \ac{agb} models that affect abundance trend predictions when these models are amplified to match observational [C/MG]-[Mg/Fe] trends. 
 See Fig \ref{fig:fagb2}.
@@
 
-    \caption[Alternate AGB models]{Same as Fig.~\ref{fig:agb_sims} except where $f_{\rm agb}=0.2$. When yields are amplified, chaos ensues.}
+    \caption[Alternate low mass star yield models]{Same as Fig.~\ref{fig:agb_sims} except where $f_{\rm agb}=0.2$. When yields are amplified, chaos ensues.}
     \label{fig:fagb2}
@@
     \includegraphics{y_mg.pdf}
-    \caption[Magnesium CCSNe yields]{Same as the top panel of Fig.~\ref{fig:y_cc}, but for Mg. Our Mg yield choice is shown as a dashed line at the top
+    \caption[Magnesium yields]{Same as the top panel of Fig.~\ref{fig:y_cc}, but for Mg. Our Mg yield choice is shown as a dashed line at the top
     }
@@
     \includegraphics{fe_ia.pdf}
-    \caption[Adjusting type Ia iron]{Similar to Fig.~\ref{fig:agb_sims} except with variations of the SNeIa iron fraction}
+    \caption[Adjusting type Ia iron]{Similar to Fig.~\ref{fig:agb_sims} except with variations of the \ac{ia} iron fraction}
     \label{fig:fe_ia}

### 2023-04-29 thesis/tex/main.tex
glossarieees

@@
-%\DocumentMetadata{testphase=phase-III,testphase=math}
+%! tex program = lualatex
+\DocumentMetadata{testphase=phase-II,
+testphase=math,
+lang=en-US
+}
+
 \documentclass[12pt,oneside,letterpaper]{report}
 
+\tagpdfsetup
+{
+    activate-all,
+}
+
+\usepackage{amsmath}	% Advanced maths commands
+
 \usepackage[T1]{fontenc}
+\usepackage{txfonts}
+% \input{glyphtounicode}
+
+\usepackage{hyperref}
+\hypersetup{
+    colorlinks=true,
+    linkcolor=black,
+    filecolor=black,
+    urlcolor=black,
+    citecolor=black,
+    pdftitle={The Galactic Chemical Evolution of Carbon},
+}
+
+\urlstyle{same}
+
+\usepackage{graphicx}	% Including figure files
+\usepackage{booktabs}
+\graphicspath{{../figures/}} 
+\usepackage{isotope}
+\usepackage[tableposition=above]{caption}
 
 \usepackage{aas_macros}
-%\usepackage[letterpaper, top=1in]{geometry}
+\usepackage{natbib}
+\usepackage[nottoc,numbib]{tocbibind}
+
+%%%%%%%%%%%%%%% Formatting %%%%%%%%%%%%%%%%%%
 \usepackage{titlesec}
-\usepackage{microtype}
-
-\titleformat{\chapter}{\normalfont\normalsize\centering}{\thechapter.}{1em}{}
+
+\titleformat{\chapter}{\normalfont\normalsize\centering\bf}{\thechapter.}{1em}{}
 \titleformat{\section}{\normalfont\normalsize\centering}{\thesection}{1em}{}
@@
 
-\usepackage{setspace}
-\usepackage{booktabs}
-
 \usepackage{etoolbox}% http://ctan.org/pkg/etoolbox
@@
 \makeatother
-\usepackage[tableposition=above]{caption}
-
-\usepackage{amsmath}	% Advanced maths commands
-\usepackage{txfonts}
-\usepackage{hyperref}
-\hypersetup{
-    colorlinks=true,
-    linkcolor=black,
-    filecolor=black,
-    urlcolor=black,
-    citecolor=black,
-    pdftitle={Thesis},
-    pdfpagemode=FullScreen,
-}
-\urlstyle{same}
-% \usepackage{amssymb}	% Extra maths symbols
-
-\usepackage{graphicx}	% Including figure files
-\graphicspath{{../figures/}} 
-\usepackage{natbib}
-\usepackage[nottoc,numbib]{tocbibind}
-
-\usepackage{isotope}
-
-\usepackage{accsupp}
-\usepackage[accsupp]{axessibility}
-\pdfcompresslevel=0
-
-% accessibility
-% \usepackage{tagpdf}
-% \usepackage[tagpdf]{axessibility}
-
-\usepackage[]{acro}
-\usepackage{array}
-
-\acsetup{
-    make-links = true,
-    list/template = tabular,
-    templates/colspec = {p{0.2\linewidth} p{0.8\linewidth} },
-    pages/display = none,
-    format/short = {\sc}, 
-}
-
-\DeclareAcronym{cc}{
-    short = ccsn,
-    long = core collapse supernova,
-    short-plural = e,
-    long-plural = e,
-    extra = {massive star explosions}
-}
-\DeclareAcronym{ia}{
-    short = sne ia,
-    long = supernovae type Ia,
-    extra = {exploding white dwarfs}
-}
-
-\DeclareAcronym{agb}{
-    short = agb,
-    long = asymptotic giant branch,
-    short-plural = s,
-    long-plural = \ stars,
-}
-\DeclareAcronym{gce}{
-    short = gce,
-    long = galactic chemical evolution
-}
-
-\DeclareAcronym{dla}{
-    short = {dla},
-    long = {damped Lyman-alpha},
-    short-plural = s,
-    long-plural = \ systems,
-}
-
-\DeclareAcronym{apogee}{
-    short = {apogee},
-    long = {Apache Point Observatory Galactic Evolution Experiment},
-    extra = {a large optical spectroscopic survey of Milky Way stars}
-}
-
-\DeclareAcronym{sfh}{
-    short = sfh,
-    long = star formation history,
-}
-\DeclareAcronym{ssp}{
-    short = ssp,
-    long = single stellar population,
-}
-\DeclareAcronym{imf}{
-    short = imf,
-    long = initial mass function,
-}
-
-\newcommand{\cc}{\ac{cc}}
-\newcommand{\agb}{\ac{agb}}
-\newcommand{\ia}{\ac{ia}}
-
-\newcommand{\sfh}{\ac{sfh}}
-\newcommand{\ssp}{\ac{ssp}}
-\newcommand{\imf}{\ac{imf}}
-\newcommand{\gce}{\ac{gce}}
-\newcommand{\apogee}{\ac{apogee}}
 
@@
 
+% these don't work with lualatex/phase-iii
+%\usepackage{accsupp}
+%\usepackage[accsupp]{axessibility}
+% \pdfcompresslevel=0
+
+% accessibility
+% \usepackage{tagpdf}
+% \usepackage[tagpdf]{axessibility}
+
+%%%%%%%%%%%%%%% Acronyms %%%%%%%%%%%%%%%%%%
+\usepackage[automake,symbols,nogroupskip,counter=section]{glossaries-extra}
+\makeglossaries
+\MakeAcronymsAbbreviations
+
+\setabbreviationstyle{long-short-sc-desc}
+\newabbreviation
+[description={massive star explosions}]
+{cc}{ccsne}{core collapse supernovae}
+
+\newabbreviation
+[description={Exploding white dwarfs, produces Fe-peak elements}]
+{ia}{sne ia}{supernovae type Ia}
+
+\newabbreviation
+[description={Dying low-mass stars. Produces C, N, and heavy s-process elements.}]
+{agb}{agb}{asymptotic giant branch}
+
+\newabbreviation
+[description={}]
+{gce}{gce}{galactic chemical evolution}
+
+\newabbreviation
+[description={}]
+{sfh}{sfh}{star formation history}
+
+\newabbreviation
+[description={}]
+{ssp}{ssp}{single stellar population}
+
+\newabbreviation
+[description={}]
+{imf}{imf}{initial mass function}
+
+\newabbreviation
+[description={}]
+{apogee}{apogee}{Apache Point Observatory Galactic Evolution Experiment}
+
+\newabbreviation
+[description={}]
+{dla}{dla}{damped Lyman-alpha systems}
+
+\newcommand{\cc}{\gls{cc}}
+\newcommand{\Cc}{\Gls{cc}}
+\newcommand{\agb}{\gls{agb}}
+\newcommand{\ia}{\gls{ia}}
+\newcommand{\sfh}{\gls{sfh}}
+\newcommand{\dla}{\gls{dla}}
+\newcommand{\ssp}{\gls{ssp}}
+\newcommand{\imf}{\gls{imf}}
+\newcommand{\gce}{\gls{gce}}
+\newcommand{\Gce}{\Gls{gce}}
+\newcommand{\apogee}{\gls{apogee}}
+
+\glsxtrnewsymbol
+[description = {The net fraction initial-mass-function weighted massive star yield of carbon}]
+{ycc}{\ensuremath{y_{\rm C}^{\rm CC}}}
+
+\glsxtrnewsymbol
+[description = {The net fraction initial-mass-function weighted low-mass star yield of carbon}]
+{ycagb}{\ensuremath{y_{\rm C}^{\rm AGB}}}
+
+\glsxtrnewsymbol
+[description = {The net fraction initial-mass-function weighted massive star yield of magnesium}]
+{ymg}{\ensuremath{y_{\rm Mg}^{\rm CC}}}
+
+\glsxtrnewsymbol
+[description = {The symbol for the sun}]
+{sun}{\ensuremath{\odot}}
+
+\glsxtrnewsymbol
+[description = {The metal fraction (by weight), i.e. the fraction of material that is not hydrogen or helium}]
+{Z}{\ensuremath{Z}}
+
+\newglossaryentry{mtly}{name={metallicity},
+    description={the (mass) fraction of a star or gass which is not made of either hydrogen or helium. For the sun, the metallicity is $\Zo = 0.014$}
+}
+
+\newcommand{\zoo}{\ensuremath{Z/Z_{\sun }}}
+\newcommand{\Ycc}{\gls{ycc}}
+\newcommand{\Yct}{\ensuremath{y_{\rm C}}}
+\newcommand{\Yoc}{\gls{ymg}}
+\newcommand{\Ycagb}{\gls{ycagb}}
+\newcommand{\sun}{\gls{sun}}
+\newcommand{\Z}{\gls{Z}}
+\newcommand{\Zo}{\gls{Z}_\gls{sun}}
+\newcommand{\abund}[2]{\ensuremath{\[{\rm #1}/{\rm #2}\]}}
+
+%%%%%%%%%%%%%%%%%%% Citation commands %%%%%%%%%%%%%%%%%
 \defcitealias{cristallo+11}{C11}
@@
 
-\newcommand{\zoo}{\ensuremath{Z/Z_{\sun }}}
-\newcommand{\Ycc}{\ensuremath{y_{\rm C}^{\rm CC}}}
-\newcommand{\Yct}{\ensuremath{y_{\rm C}}}
-\newcommand{\Yoc}{\ensuremath{y_{\rm Mg}^{\rm CC}}}
-\newcommand{\Ycagb}{\ensuremath{y_{\rm C}^{\rm AGB}}}
-\newcommand{\sun}{\ensuremath{\odot}}
-
 \newcommand\T{\rule{0pt}{2.6ex}}       % Top strut
@@
 \title{Carbon Nucleosynthesis}
-% The list of authors, and the short list which is used in the headers.
-% If you need two or more lines of authors, add an extra line using \newauthor
 \author{Daniel A. Boyea}
@@
 
+\begin{document}
+
 \pagenumbering{roman}
-
-\begin{document}
-%\doublespacing
 
@@
    \begin{center}
-       \vspace*{5\baselineskip}
        \textbf{The Galactic Chemical Evolution of Carbon}\\
@@
        \vspace*{3\baselineskip}
-       Project Advisor: Professor David H. Weinberg, Department of Astronomy \\
-       James W. Johnson 
+       Project Advisors\\
+       Professor David H. Weinberg, Department of Astronomy \\
+       James W. Johnson, Department of Astronomy
        \vfill
@@
 
-\Ac{gce} aims to understand the chemical and star formation histories of galaxies.
-At the core of \ac{gce} models are stellar yields---the amount of each chemical element stars produce (or destroy).
+\Gce{} aims to understand the chemical and star formation histories of galaxies.
+At the core of \gce{} models are stellar yields---the amount of each chemical element stars produce (or destroy).
 Each element is produced in different amounts by different stars, leaving traces of the Galaxy's evolutionary history.
@@
 Here, I aim to understand C enrichment---where it is produced and how its abundances evolve over time.
-C is unique nucleosynthetically, one of few light elements (along with N) produced in \ac{agb} stars \citep[e.g.][]{jennifer19, KL14}.
+C is unique nucleosynthetically, one of few light elements (along with N) produced in \agb{} stars \citep[e.g.][]{jennifer19, KL14}.
 C and N are well-studied elements since they are easy to observe in stellar spectra, even at the lowest metallicities \cite[e.g.][]{fabbian+09, nissen+14, lambert81, laird85, lambert86}.
@@
 
-Gas-phase [C/O] ratios---observed in very low metallicity, high redshift \acp{dla}---decrease with increasing [O/H] \citep{FN15, cooke+17}.
+Gas-phase [C/O] ratios%
+%
+\footnote{In this paper, I use the standard notation for chemical abundances.
+$[A/B] = \log_{10}\left(A/B\right) - \log_{10}\left(A_{\sun}/B_{\sun}\right)$, i.e.
+$[A/B]$ is the logarithm of the ratio between A and B, scales such that $[A/B]=0$ for the sun.
+Solar abundances are as measured in \citet{asplund+09}}%
+%
+---observed in very low \gls{mtly}, high redshift \dla---decrease with increasing [O/H] \citep{FN15, cooke+17}.
 Then, [C/O] increases above $\rm [O/H] \approx -1$ (\citealt{berg+19}; see discussion in \S\ref{sec:gas}).
-While we know C is produced in \ac{agb} stars and \acp{cc}, we still have a limited understanding of the magnitude and metallicity-dependence of each process.
+While we know C is produced in \agb{} stars and \cc{}, we still have a limited understanding of the magnitude and metallicity-dependence of each process.
 
@@
 
-\gce{} models typically use unmodified nucleosynthetic predictions and attempt to create models matching observations by varying the \sfh{} and other evolutionary parameters.
+\Gce{} models typically use unmodified nucleosynthetic predictions and attempt to create models matching observations by varying the \sfh{} and other evolutionary parameters.
 Here, I introduce C yields as an additional free parameter, determining which yield prescriptions reproduce Galactic abundance trends.
@@
 \begin{figure}[htp]
-    \includegraphics{subgiants_mgh.pdf}
-    \includegraphics{subgiants_mgfe.pdf}
+    \includegraphics[width=\textwidth]{subgiants_mgh.pdf}
+    \includegraphics[width=\textwidth]{subgiants_mgfe.pdf}
     \caption[APOGEE Subgiants]{The [C/Mg] ratio against [Mg/H] (top) and [Mg/Fe] (bottom) for the \citetjack~sample of \apogee{} subgiants.
@@
 Theoretical models of stellar nucleosynthesis provide the starting point of this investigation.
-I focus on three primary nucleosynthetic pathways: \acf{agb} stars, \acf{cc}, and type Ia supernovae \acf{ia}.
+I focus on three primary nucleosynthetic pathways: \agb{} stars, \cc{}, and \ia.
 Each process has unique timescales and yields, traceable through the tools of \gce.
-I compare C, produced in \cc{} and \ac{agb} stars, to Mg and Fe as tracers of \cc{} and \acf{ia} espectively.
+I compare C, produced in \cc{} and \agb\ stars, to Mg and Fe as tracers of \cc{} and \ia{} espectively.
 
@@
 Next, low-mass stars begin to reach the end of their lives.
-By shedding their outer layers, \ac{agb} stars are important sources of C, N, and neutron capture elements.
+By shedding their outer layers, \agb{} stars are important sources of C, N, and neutron capture elements.
 Finally, white dwarfs explode, releasing Fe and other iron-peak elements.
@@
 For example, if a 1 $M_\odot$ star has $\tilde{y}_{\rm C} = 10^{-3}$, then the star will add $10^{-3}\ M_\odot$ of C to the interstellar medium.
-Although per-star yields are necessary to compute \ac{agb} star enrichment rates in \gce{}  models, \imf-averaged\footnote{IMF: Initial Mass Function} yields are useful in interpreting their predictions.
+Although per-star yields are necessary to compute \agb{} star enrichment rates in \gce{}  models, \imf-averaged\footnote{IMF: Initial Mass Function} yields are useful in interpreting their predictions.
 For a yield $y$ from a star of mass M and initial metallicity $Z$, the \imf-averaged yield is given by
@@
 where ${dN}/{dM}$ is the normalized \imf, and $M_{\rm min}$ and $M_{\rm max}$ are the minimum and maximum mass of stars, which I take to be $0.08 M_{\sun}$ and $100 M_{\sun}$ respectively.
-For \ac{agb} stars, the yields are truncated above 8 $M_{\odot}$.
+For \agb{} stars, the yields are truncated above 8 $M_{\odot}$.
 To calculate the \imf-weighted net yields, I use the Versatile Integrator for Chemical Evolution code (\VICE\footnote{\VICE~is available at \url{https://github.com/giganano/VICE}}).
@@
 Table \ref{tab:fiducial_mod} contains my fiducial yields, in units of a \ssp's birth mass.
-Also following \citet{james+21, james+23}, I take the \ac{ia} delay time distribution to be a
+Also following \citet{james+21, james+23}, I take the \ia{} delay time distribution to be a
 $t^{-1.1}$ power-law suggested by the observations of \citet{maoz+12}.
@@
 
-An \ac{agb} star is a low mass ($\lesssim 8 M_{\sun}$) star during its final phase of evolution.
-In an \ac{agb} star, two competing processes determine the outcome of C production: third dredge up and hot bottom burning.
-Third dredge up accompanies thermal pulses in \ac{agb} stars.
+An \agb\ star is a low mass ($\lesssim 8 M_{\sun}$) star during its final phase of evolution.
+In an \agb\ star, two competing processes determine the outcome of C production: third dredge up and hot bottom burning.
+Third dredge up accompanies thermal pulses in \agb\ stars.
 During a third dredge up event, material from the CO core is mixed with material exposed to partial He-shell burning, increasing C and O abundances in the envelope \citep{KL14}.
-If this envelope is lost during the \ac{agb} phase, then C yields are enhanced.
+If this envelope is lost during the \agb\ phase, then C yields are enhanced.
 Hot bottom burning is the activation of proton capture reactions, and the CNO cycle%
@@
 
-In this work, I explore four different sets of \ac{agb} star yield tables from literature, providing well-sampled grids in metallicity and mass for use in chemical evolution models. 
+In this work, I explore four different sets of \agb\ star yield tables from literature, providing well-sampled grids in metallicity and mass for use in chemical evolution models. 
 \begin{itemize}
@@
 \end{itemize}
-I use C11 table, amplified by a factor of 2.9, as the fiducial \ac{agb} yield.
-
-Fig.~\ref{fig:y_agb} compares the \ac{agb} C yield $\tilde{y}_\text{C}^\text{AGB}(M, Z)$ for each model I consider. 
+I use C11 table, amplified by a factor of 2.9, as the fiducial \agb\ yield.
+
+Fig.~\ref{fig:y_agb} compares the \agb\ C yield $\tilde{y}_\text{C}^\text{AGB}(M, Z)$ for each model I consider. 
 The yields may be negative if a star ejects material with a lower average C abundance than the material the star was formed from.
-Most models agree on the qualitative shape of the net fractional \ac{agb} C yield---% 
+Most models agree on the qualitative shape of the net fractional \agb\ C yield---% 
 stars with masses between \about{2~M_\odot} and \about{4~M_\odot} have the highest fractional C yields, with the mass of the peak increasing and overall yields decreasing with increasing $Z$.
@@
 
-In Fig.~\ref{fig:agb-ssp}, I plot the total production of C by \ac{agb} stars in a \ssp{} at an age $t$. 
+In Fig.~\ref{fig:agb-ssp}, I plot the total production of C by \agb\ stars in a \ssp{} at an age $t$. 
 Effectively, this is equivalent to integrating Eq.~\ref{eq:imf-yield} down to $M_{to}$, the turnoff mass for time $t$.
@@
 from \citealt{larson74}.})
-As the mass range $2\lesssim M \lesssim 4$ is most important for C production, about half of C production occurs before \about{1} Gyr, similar to \ac{ia} Fe. 
+As the mass range $2\lesssim M \lesssim 4$ is most important for C production, about half of C production occurs before \about{1} Gyr, similar to \ia\ Fe. 
 K10 and K16 weight C production more heavily towards massive stars resulting in a faster enrichment delay time, whereas the C11 and V13 models predict a slightly longer timescale of \about{1} Gyr, but little to no C is produced more than 2 Gyr after a star formation event.
@@
  	    \includegraphics[scale=1]{agb_yields.pdf}
-        \caption[Low mass C yields]{The net fractional \ac{agb} C yield  plotted as a function of initial stellar mass $M$ and color-coded according to metallicity.
+        \caption[Low mass C yields]{The net fractional \agb\ C yield  plotted as a function of initial stellar mass $M$ and color-coded according to metallicity.
 The black dashed line shows $\tilde{y}=0$ for reference.
-Each panel represents yields from one of four \ac{agb} models: C11, K10, V13, K16 (see \S \ref{sec:agb}).
+Each panel represents yields from one of four \agb\ models: C11, K10, V13, K16 (see \S \ref{sec:agb}).
 }
@@
     \caption[C yields delay time distribution]{
-    C production by \ac{agb} stars as a function of \ssp{} age, normalized to the total mass $M_{\rm tot}$ produced at $t=10$ Gyr.
-Left: The four \ac{agb} yield models from literature at solar metallicity (C11, K10, V13, or K16).
+    C production by \agb\ stars as a function of \ssp{} age, normalized to the total mass $M_{\rm tot}$ produced at $t=10$ Gyr.
+Left: The four \agb\ yield models from literature at solar metallicity (C11, K10, V13, or K16).
 The delay time distribution of type Ia supernovae ($\propto t^{-1.1}$) is plotted as a dashed black line for comparison.
-Right: The C11 \ac{agb} model at different metallicities.
+Right: The C11 \agb\ model at different metallicities.
 }
@@
 
-Fig.~\ref{fig:yagb-z} shows \imf-averaged C yields for each \ac{agb} model as a function of metallicity $Z$.
+Fig.~\ref{fig:yagb-z} shows \imf-averaged C yields for each \agb\ model as a function of metallicity $Z$.
 V13 differs in that it shows a non-monotonic metallicity dependence. However, this effect is only for models with $\log Z/Z_\odot \lesssim -1$.
@@
 
-    \caption[Low mass yield metallicity dependence]{The net fractional \imf-weighted \ac{agb} C yield $\Ycagb$ as a function of metallicity for each of our \ac{agb} yield models.
+    \caption[Low mass yield metallicity dependence]{The net fractional \imf-weighted \agb\ C yield $\Ycagb$ as a function of metallicity for each of our \agb\ yield models.
     }
@@
 Fig.~\ref{fig:y_cc} shows the C11 model for comparison on the top.
-Especially at $Z\approx Z_\odot$, most \cc{} models dominate \ac{agb} C production.
+Especially at $Z\approx Z_\odot$, most \cc{} models dominate \agb\ C production.
 I will later also show empirically that \cc{} should dominate C production.
@@
 ${\rm [C/Mg]^{CC}}$ describes what [C/Mg] would be if \cc{} were the only process producing C.
-Once again, different \acp{cc} models span a large range in [C/Mg]. 
-I chose to instead parameterize $\Ycc$ to enable agreement with observations, as most \acp{cc} models fail to achieve near-solar [C/Mg].
+Once again, different \cc\ models span a large range in [C/Mg]. 
+I chose to instead parameterize $\Ycc$ to enable agreement with observations, as most \cc\ models fail to achieve near-solar [C/Mg].
 Assumptions about the explodability landscape affect C and Mg production.
 Increasing the fraction of stars that explode increases $\Ycc$, as stars that directly collapse do not contribute to explosive yields \citep{emily+21}.
-However, C is relatively unaffected by the black-hole landscape, as very massive stars contribute carbon through enriched winds.
+However, C is relatively unaffected by the black-hole landscape, as very massive stars contribute C through enriched winds.
 Since Mg is formed deeper in the core of massive stars, the Mg yield drops much more steeply, so models, where few stars explode (S16/W18), result in much higher [C/Mg].
 
-\acp{cc} models also do not reach [O/Mg] due to overproduction of O, or underproduction of Mg, or both \citep{emily+21}.
-Here, I assume ${\rm [O/Mg]} = 0$, which is not compatible with \acp{cc} models but is consistent with \apogee{} observations \citep{weinberg+19, weinberg+22}.
+\Cc\ models also do not reach [O/Mg] due to overproduction of O, or underproduction of Mg, or both \citep{emily+21}.
+Here, I assume ${\rm [O/Mg]} = 0$, which is not compatible with \cc\ models but is consistent with \apogee{} observations \citep{weinberg+19, weinberg+22}.
 
@@
         C yields from massive stars.
-        \textbf{Top:} The \imf-weighted \acp{cc} yield of C as a function of metallicity.
-        \textbf{Bottom:} The \acp{cc} [C/Mg] abundance ratio, defined in Eq.~\ref{eq:c_mg_cc}. The black line represents the C yield of the fiducial model,
+        \textbf{Top:} The \imf-weighted \cc\ yield of C as a function of metallicity.
+        \textbf{Bottom:} The \cc\ [C/Mg] abundance ratio, defined in Eq.~\ref{eq:c_mg_cc}. The black line represents the C yield of the fiducial model,
     $\Ycc = 0.0028 + 0.001 (Z/Z_{\odot})$. Yields are shown for tables from 
@@
 \end{equation}
-where the first term on the right-hand side describes \acp{cc} enrichment. 
+where the first term on the right-hand side describes \cc\ enrichment. 
 In terms of the return mass fraction of stars $r$, the mass lost to remnants is $Z_X (1-r)\dot{M}_\star$.
@@
 
-While Equation \ref{eq:z_eq} can be applied to \acp{cc} C, the delayed nature of \ac{agb} C can complicate the expression.
-Instead, I use an effective yield, which can be expressed as an integral over the DTD,
+While Equation \ref{eq:z_eq} can be applied to \cc\ C, the delayed nature of \agb\ C can complicate the expression.
+Instead, I use an effective yield, which can be expressed as an integral over the delay time distribution,
 \begin{equation}
@@
 This argument can also be inverted to infer  yields from abundance ratio trends.
-To the extent that observed C and Mg trends reflect the equilibrium abundances in different Galactic regions, we can infer the \acp{cc} yield given an assumed \ac{agb} star yield (or vice versa).
+To the extent that observed C and Mg trends reflect the equilibrium abundances in different Galactic regions, we can infer the \cc\ yield given an assumed \agb\ star yield (or vice versa).
 Inferring $\Ycc$ from $\Ycagb$,
@@
 %
-As a result, I choose to leave the total carbon yield fixed at solar $Z$,
+As a result, I choose to leave the total C yield fixed at solar $Z$,
 \begin{subequations}
@@
 
-In \S\ref{sec:f-z-models}, I will show that none of the four \ac{agb} yield sets (C11, K10, V13, K16) produce enough C relative to this $\Ycc$ value.
+In \S\ref{sec:f-z-models}, I will show that none of the four \agb\ yield sets (C11, K10, V13, K16) produce enough C relative to this $\Ycc$ value.
 So, I introduce normalization factors, $\alpha_{\rm AGB}$, and $\alpha_{\rm CC}$ which denote a multiplicitave scaling of $\Ycc$ and $\Ycagb$ respectively.
@@
 \end{subequations}
-Above, $\alpha_{\rm CC}$ is dependent on the choice of $\alpha_{\rm AGB}$ to keep the total carbon yield constant.
+Above, $\alpha_{\rm CC}$ is dependent on the choice of $\alpha_{\rm AGB}$ to keep the total C yield constant.
 
 In \S\ref{sec:f-z-models}, I find that $\alpha_{\rm AGB}\approx 2.9$ for the C11 yield model.
-Using this \ac{agb} yield, I can now use Eq.~\ref{eq:y_c_eq} to find an estimate of $\Ycc$ as a function of metallicity.
+Using this \agb\ yield, I can now use Eq.~\ref{eq:y_c_eq} to find an estimate of $\Ycc$ as a function of metallicity.
 I show the values of $\Ycc$ I obtain from the subgiant sample in Fig.~\ref{fig:analytic}.
@@
     \caption[Reverse fit yields]{Inferred massive star C yields as a function of metallicity.
-I assume equilibrium and $3\times {\rm C11}$ \ac{agb} yields (orange curve, see discussion in Section \ref{sec:equilibrium}).
+I assume equilibrium and $3\times {\rm C11}$ \agb\ yields (orange curve, see discussion in Section \ref{sec:equilibrium}).
 The binned medians and median absolute deviation (divided by $\sqrt{N}$) are blue points.
@@
 
-I only perform this analysis on the C11 yields because C11 has yields tables more finely sampled in metallicity than the other three \ac{agb} yield tables.
+I only perform this analysis on the C11 yields because C11 has yields tables more finely sampled in metallicity than the other three \agb\ yield tables.
 As the metallicity range of the data is small ($-0.4\lesssim {\rm [Mg/H]} \lesssim 0.4$), other models are more challenging to interpret in this range.
 Furthermore, the \apogee{} observations may have systematics, and other measurements of C abundances \citep[e.g.][]{vincenzo+21} have slight disagreements in the overall shape of the trend (see \S\ref{sec:jack}).
-So, this expression of $\Ycc/\Yoc$ depends on the chosen \ac{agb} yield table, the \ac{agb} fraction, and the dataset. 
+So, this expression of $\Ycc/\Yoc$ depends on the chosen \agb\ yield table, the \agb\ fraction, and the dataset. 
 Additionally, these yields will be systematically biased if the galaxy is out of equilibrium, for example due to a recent starburst (Isern et al.
@@
 Here, I present the time evolution of our fiducial model. In the next sections, I will discuss the choice of parameters and agreement with observations. 
-The fiducial model has the following qualitative characteristics of its C yields: (a) C is predominantly produced in \acp{cc}, (b) \acp{cc} produce more C at higher metallicities, and (c) \ac{agb} stars produce less carbon at higher metallicities.
-Our fiducial model uses the C11 \ac{agb} yield tables (see \S\ref{sec:agb}, and Table \ref{tab:fiducial_mod}), and I amplify the C11 yields by a factor of 2.9 such that \ac{agb} stars account for 20\% of carbon at $Z=Z_\odot$.
+The fiducial model has the following qualitative characteristics of its C yields: (a) C is predominantly produced in \cc, (b) \cc\ produce more C at higher metallicities, and (c) \agb\ stars produce less C at higher metallicities.
+Our fiducial model uses the C11 \agb\ yield tables (see \S\ref{sec:agb}, and Table \ref{tab:fiducial_mod}), and I amplify the C11 yields by a factor of 2.9 such that \agb\ stars account for 20\% of C at $Z=Z_\odot$.
 
@@
 Comparing [C/Mg] against [Mg/Fe] enables us to see the late-time evolution of C more clearly.
-Because of the extended DTD of \ac{ia} enrichment, [Fe/H] takes longer to reach equilibrium as half of Fe production comes from type-Ia supernovae, and the late time evolution is not as clustered as [Mg/H].
+Because of the extended delay time distribution of \ia\ enrichment, [Fe/H] takes longer to reach equilibrium as half of Fe production comes from type-Ia supernovae, and the late time evolution is not as clustered as [Mg/H].
 The evolution proceeds as follows.
-Initially, \acp{cc} dominate production.
+Initially, \cc\ dominate production.
 As $\Ycc$ has strong metallicity dependence, [C/Mg] increases with time.
-Shortly thereafter, \ac{agb} stars contribute delayed C, increasing [C/Mg] even more steeply.
+Shortly thereafter, \agb\ stars contribute delayed C, increasing [C/Mg] even more steeply.
 As Mg begins to reach equilibrium, the [C/Mg] ratio plateaus as C approaches equilibrium.
@@
 This is even more evident in the lower panel of Fig.~\ref{fig:c_evo}.
-While the \caah~trend reaches equilibrium at \about{5} Gyr, the \caafe~trend continues to evolve even until the present day, exposing the effect of the relative delay times of \ac{agb} stars and \ac{ia}.
+While the \caah~trend reaches equilibrium at \about{5} Gyr, the \caafe~trend continues to evolve even until the present day, exposing the effect of the relative delay times of \agb\ stars and \ia.
 
@@
 Here, I use the published, unscaled yield tables.
-As the highest \ac{agb} yield at solar, K10 is only $\Ycagb=0.000585$, $f_{\rm AGB} \leq 0.12$ for all models.
+As the highest \agb\ yield at solar, K10 is only $\Ycagb=0.000585$, $f_{\rm AGB} \leq 0.12$ for all models.
 Massive stars dominate C production with unscaled yields.
-While it is easy to modify the \ac{agb} yields in my model, their small contribution reduces the effect.
-I leave a more detailed discussion of the effects of \ac{agb} models for Appendix \ref{sec:alt_agb} and use C11 yields hereafter.
+While it is easy to modify the \agb\ yields in my model, their small contribution reduces the effect.
+I leave a more detailed discussion of the effects of \agb\ models for Appendix \ref{sec:alt_agb} and use C11 yields hereafter.
 
@@
 \includegraphics{oob_agb.pdf}
-\caption[AGB GCE Models]{
+\caption[Mean stellar abundance trends]{
     Stellar abundance trends in our model, assuming metallicity independent $\Ycc$.
-Colored lines quantify the median [C/Mg] in bins of [Mg/H] for our four \ac{agb} yield models from the literature (see \ref{sec:agb}).
+Colored lines quantify the median [C/Mg] in bins of [Mg/H] for our four \agb\ yield models from the literature (see \ref{sec:agb}).
 Black points and grey dashes represent the median and standard deviations in the \citetjack~sample.
@@
 
-Next, I investigate adjustments to the \ac{agb} yield fraction $f_{\rm AGB}$ and the \acp{cc} metallicity dependence $\zeta$ in Fig.~\ref{fig:beta_f}.
+Next, I investigate adjustments to the \agb\ yield fraction $f_{\rm AGB}$ and the \cc\ metallicity dependence $\zeta$ in Fig.~\ref{fig:beta_f}.
 On the top panel of Fig.~\ref{fig:beta_f}, I plot models with varying $\Ycc$ metallicity dependence.
 As discussed in \S\ref{sec:equilibrium}, the \caah~trend is approximated by equilibrium, so the trends of these have steeper \caah~corresponding to steeper metallicity dependence.
-However, \caafe~is minimally affected by these changes since \acp{cc} occure on much shorter timescales than \ac{ia} and \ac{agb} enrichment.
-
-Now, I vary the proportion of \ac{agb} contribution.  The \ac{agb} C production fraction is defined as
+However, \caafe~is minimally affected by these changes since \cc\ occure on much shorter timescales than \ia\ and \agb\ enrichment.
+
+Now, I vary the proportion of \agb\ contribution.  The \agb\ C production fraction is defined as
 \begin{equation}
@@
 where  $\Ycagb$ includes the multiplicative factor $\alpha_{\rm AGB}$ as defined in Eq.~\ref{eq:alpha}.
-In the bottom panel of Fig.~\ref{fig:beta_f}, I plot three models with different \ac{agb} fractions while using C11 yields.
-The \caafe~relationship is set by $f_{\rm AGB}$ because a specific amount of C must be released at a delayed time in order to match the \ac{ia} production of Fe and increase [C/Mg] as [Mg/Fe] decreases to reproduce the data.
+In the bottom panel of Fig.~\ref{fig:beta_f}, I plot three models with different \agb\ fractions while using C11 yields.
+The \caafe~relationship is set by $f_{\rm AGB}$ because a specific amount of C must be released at a delayed time in order to match the \ia\ production of Fe and increase [C/Mg] as [Mg/Fe] decreases to reproduce the data.
 Increased $f_{\rm AGB}$ results in a decreased slope in \caah, owing to the negative metallicity dependence of $\Ycagb$.
@@
 
-One source of theoretical uncertainty in this result is that the \ac{ia} yield and DTD have their own uncertainties.
+One source of theoretical uncertainty in this result is that the \ia\ yield and delay time distributions have their own uncertainties.
 I discuss variations in $y_{\rm Fe}^{\rm Ia}$ in Appendix \ref{sec:alt_agb}, and find that the qualitative conclusions are largely unaffected.
-I therefore focus on the choices of $y_{\rm Fe}^{\rm Ia} = 0.00214$ and a $\propto t^{-1.1}$ DTD choices from the fiducial model here.
+I therefore focus on the choices of $y_{\rm Fe}^{\rm Ia} = 0.00214$ and a $\propto t^{-1.1}$ delay time distribution choices from the fiducial model here.
 In short, the scaling of the trend and metallicity dependence of C (as seen in
-the \caah\ trend) gives information on the total C yield and the behavior of \acp{cc} (as the dominating producer of C), the \caafe\ trend exposes the delayed effect of C from \ac{agb} contribution.
+the \caah\ trend) gives information on the total C yield and the behavior of \cc\ (as the dominating producer of C), the \caafe\ trend exposes the delayed effect of C from \agb\ contribution.
 
@@
 	\centering
-    \caption[Low mass star solar C yields]{For each \ac{agb} yield set, the \imf-weighted C \ac{agb} yield at solar metallicity, along with the multiplicative factor reaches an \ac{agb} contribution of 20\%.}
+    \caption[Low mass star solar C yields]{For each \agb\ yield set, the \imf-weighted C \agb\ yield at solar metallicity, along with the multiplicative factor reaches an \agb\ contribution of 20\%.}
 	\label{tab:alpha_agb}
@@
 As an additional test of the model, I next compare the gas-phase predictions against gas-phase C data.
-In Fig.~\ref{fig:gas_phase}, I plot our fiducial model's gas phase predictions compared to observations of MW and extragalactic HII regions, halo stars, and \acf{dla} systems.
+In Fig.~\ref{fig:gas_phase}, I plot our fiducial model's gas phase predictions compared to observations of MW and extragalactic HII regions, halo stars, and \dla\ systems.
 The model is broadly consistent with observations, where the model at $t=2$ Gyr approximates the slope of dwarf galaxies and halo stars.
@@
 The decreasing [C/O] abundance at very-low metallicities is likely due to population III stellar yields \citep[e.g.][]{hirschi07}, as suggested by \citep{cooke+17, FN15}.
-As \ac{agb} stars do have a significant delay, these stars cannot explain the increase in C yields at low metallicity as the timescales to reach $\rm [O/H]\sim -1$ is faster than this enrichment can occur.
-So, enhanced carbon due to (rotating) massive population III stars at low metallicities explains this trend.
+As \agb\ stars do have a significant delay, these stars cannot explain the increase in C yields at low metallicity as the timescales to reach $\rm [O/H]\sim -1$ is faster than this enrichment can occur.
+So, enhanced C due to (rotating) massive population III stars at low metallicities explains this trend.
 
@@
     HII regions    \citep[pink circles;][]{skillman+20, esteban+02, esteban+09, esteban+14, esteban+19}
-    \acf{dla} systems \citep[blue triangles;][]{cooke+17} 
+    \dla\ systems \citep[blue triangles;][]{cooke+17} 
     Milky Way halo and thick disk stars \citep[green stars;][]{nissen+14, fabbian+09}. 
@@
 
-Though \acp{cc} C yields are poorly understood, I adopt an equilibrium approximation and determine a functional form that approximately matches trends in \apogee{} subgiants and is consistant with massive star nucleosynthesis models.
-Variations of the metallicity dependence of this \acp{cc} yield affect trends in \caah~but do not affect trends in \caafe\ when taking a slice in [Mg/H].
-As all theoretical \ac{agb} C yields decrease with metallicity, increasing the \ac{agb} fraction causes the \caah\ trend to flatten.
-However, the \caafe\ trend is sensitive to the \ac{agb} fraction.
-From this, I estimate that \ac{agb} stars contribute \about{20\%} of total C abundance at solar metallicity.
+Though \cc\ C yields are poorly understood, I adopt an equilibrium approximation and determine a functional form that approximately matches trends in \apogee{} subgiants and is consistant with massive star nucleosynthesis models.
+Variations of the metallicity dependence of this \cc\ yield affect trends in \caah~but do not affect trends in \caafe\ when taking a slice in [Mg/H].
+As all theoretical \agb\ C yields decrease with metallicity, increasing the \agb\ fraction causes the \caah\ trend to flatten.
+However, the \caafe\ trend is sensitive to the \agb\ fraction.
+From this, I estimate that \agb\ stars contribute \about{20\%} of total C abundance at solar metallicity.
 The remaining \about{80\%} of C comes from massive stars with a metallicity dependent yield of $\Ycc/\Yoc=1.51 + 0.54 (Z/Z_\odot)$.
@@
 \bibliography{main}
-
-\newpage
-
-\printacronyms
-\addcontentsline{toc}{chapter}{Acronyms}
 
@@
 I use the criteria outlined in \citetjack~to create a sample of subgiants from \apogee{} DR17 \cite{apogee17} as our primary observational constraint.
+\apogee\ is part of the Sloan Digital Sky Survey 17 and measures high resolution spectra of thousands of stars \cite{sdss17}.
 Subgiants are reflective of birth abundances for CNO \citep{souto19}.
-with chemical abundance determinations from ASPCAP \citep{aspcap}.
-SDSS 17 \cite{sdss17}.
+with chemical abundance determinations from the \apogee Stellar Parameter and Chemical Abundance Pipeline \citep{aspcap}.
 \citetjack~select a region of stars in $\log g$-$T_\text{eff}$ space described by the following polyhedron
@@
 This is a known problem (see \citet{emily+21}).
-\acsp{cc} models overpredict O or underpredict Mg, and the resolution is still unknown.
-My results are, however, independent of whether the \acs{cc} element is O or Mg.
-
-While I focus the main discussion of the paper on the C11 model, other \ac{agb} models can impact abundance trends when $f_{\rm AGB}$ becomes larger.
-Here, I briefly explore the effects of variations in \ac{agb} models that affect abundance trend predictions when these models are amplified to match observational [C/MG]-[Mg/Fe] trends. 
+\cc\ models overpredict O or underpredict Mg, and the resolution is still unknown.
+My results are, however, independent of whether the \cc\ element is O or Mg.
+
+While I focus the main discussion of the paper on the C11 model, other \agb\ models can impact abundance trends when $f_{\rm AGB}$ becomes larger.
+Here, I briefly explore the effects of variations in \agb\ models that affect abundance trend predictions when these models are amplified to match observational [C/MG]-[Mg/Fe] trends. 
 See Fig \ref{fig:fagb2}.
@@
     \includegraphics{fe_ia.pdf}
-    \caption[Adjusting type Ia iron]{Similar to Fig.~\ref{fig:agb_sims} except with variations of the \ac{ia} iron fraction}
+    \caption[Adjusting type Ia iron]{Similar to Fig.~\ref{fig:agb_sims} except with variations of the \ia\ iron fraction}
     \label{fig:fe_ia}
@@
 
+\glsaddall
+
+\printglossary[type=symbols,nonumberlist]
+
+\printglossary
+
 \end{document}

### 2023-04-29 thesis/tex/main.tex
symbols list

@@
 %! tex program = lualatex
-\DocumentMetadata{testphase=phase-II,
-testphase=math,
-lang=en-US
-}
+\DocumentMetadata{testphase=phase-III, lang=en-US}
 
@@
 \usepackage{txfonts}
-% \input{glyphtounicode}
 
@@
     colorlinks=true,
-    linkcolor=black,
+    linkcolor=magenta,
     filecolor=black,
-    urlcolor=black,
-    citecolor=black,
+    urlcolor=blue,
+    citecolor=blue,
     pdftitle={The Galactic Chemical Evolution of Carbon},
@@
 % \usepackage{tagpdf}
+
 % \usepackage[tagpdf]{axessibility}
@@
 %%%%%%%%%%%%%%% Acronyms %%%%%%%%%%%%%%%%%%
-\usepackage[automake,symbols,nogroupskip,counter=section]{glossaries-extra}
+\usepackage[acronym,automake,symbols,nogroupskip,counter=section]{glossaries-extra}
+\newglossary*{models}{Stellar Yield Models}
 \makeglossaries
-\MakeAcronymsAbbreviations
-
-\setabbreviationstyle{long-short-sc-desc}
-\newabbreviation
-[description={massive star explosions}]
+
+\setabbreviationstyle[acronym]{long-short-sc}
+
+% \newabbreviation
+% [description={massive star explosions}]
+% {cc}{ccsne}{core collapse supernovae}
+
+\newacronym
+[ description={heelloo}, seealso={ccg} ]
 {cc}{ccsne}{core collapse supernovae}
 
-\newabbreviation
+\newacronym
+[description={Dying low-mass stars. Produces C, N, and heavy s-process elements.}]
+{agb}{agb}{asymptotic giant branch}
+
+\newacronym
 [description={Exploding white dwarfs, produces Fe-peak elements}]
@@
 
-\newabbreviation
-[description={Dying low-mass stars. Produces C, N, and heavy s-process elements.}]
-{agb}{agb}{asymptotic giant branch}
-
-\newabbreviation
-[description={}]
+\newacronym
 {gce}{gce}{galactic chemical evolution}
 
-\newabbreviation
-[description={}]
+\newacronym
 {sfh}{sfh}{star formation history}
 
-\newabbreviation
-[description={}]
+\newacronym
 {ssp}{ssp}{single stellar population}
 
-\newabbreviation
-[description={}]
+\newacronym
 {imf}{imf}{initial mass function}
 
-\newabbreviation
-[description={}]
+\newacronym
 {apogee}{apogee}{Apache Point Observatory Galactic Evolution Experiment}
 
-\newabbreviation
-[description={}]
+\newacronym
 {dla}{dla}{damped Lyman-alpha systems}
@@
 \glsxtrnewsymbol
-[description = {The metal fraction (by weight), i.e. the fraction of material that is not hydrogen or helium}]
+[description = {The metallicity fraction}]
 {Z}{\ensuremath{Z}}
 
-\newglossaryentry{mtly}{name={metallicity},
+\glsxtrnewsymbol
+[description = {The massive star carbon yield metallicity dependence}]
+{zeta}{\ensuremath{\zeta}}
+
+\glsxtrnewsymbol
+[description = {The mass outflow loading factor}]
+{eta}{\ensuremath{\eta}}
+
+\glsxtrnewsymbol
+[description = {The rate of star formation}]
+{sfr}{\ensuremath{\dot{M}_\star}}
+
+\newcommand{\et}{\gls{eta}}
+\newcommand{\zet}{\gls{zeta}}
+\newcommand{\sfr}{\gls{sfr}}
+
+\newglossaryentry{metallicity}{name={metallicity},
     description={the (mass) fraction of a star or gass which is not made of either hydrogen or helium. For the sun, the metallicity is $\Zo = 0.014$}
@@
 
-\newcommand{\zoo}{\ensuremath{Z/Z_{\sun }}}
+\newglossaryentry{alpha}{name={$\alpha$-elements},
+    description={Elements which are made up of $\alpha$-particles (two protons, two neutronns). Essentially light, even-numbered elements like O, Mg, and Na.}
+}
+
+\newglossaryentry{fepeak}{name={Fe-peak elements},
+    description={Fe and nearby elements, produced in \cc\ and \sneia.}
+}
+
+\newglossaryentry{sproc}{name={s-process elements},
+    description={Elements produced through slow neutron captures, typically in \agb\ stars.}
+}
+
+\newglossaryentry{rproc}{name={r-process elements},
+    description={Elements produced through rapid neutron capture process, though to occur in the collision of two neutron stars.}
+}
+
+\newglossaryentry{ccg}
+{
+    name={core collapse supernovae},
+    description ={massive star explosions. core collapse supernovae (\textcs{ccsne}) produce many elements including $\alpha$-elements, Fe-peak elements, and r and s-process elements.}
+}
+
+\newglossaryentry{c11}
+{
+    name={C11},
+    type={models},
+    description={the yield set from \citet{cristallo+11,cristallo+15}.
+The models were run at $m= (1.3, 1.5, 2.0, 2.5, 3.0, 4.0, 5.0, 6.0)$ and $Z=(0.0001, 0.0003, 0.001, 0.002, 0.003, 0.006, 0.008, 0.01, 0.014, 0.02)$.
+},
+}
+\newglossaryentry{k10}
+{
+    name={K10},
+    type={models},
+    description={the yield set from \citet{karakas10}. Includes models run at 
+    $M=(1.0, 1.25, 1.5, 1.75, 1.9, 2.25, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)$ and $Z=(0.0001, 0.004, 0.008, 0.02)$},
+}
+\newglossaryentry{v13}
+{
+    name={V13},
+    type={models},
+    description={the \agb\ yield set from \citet{ventura+13,ventura+14,ventura+18,ventura+20}.
+Includes models with masses $m=(1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 6.0, 6.5, 7.0)$ and with metallicities $Z=(0.0003, 0.001, 0.002, 0.004, 0.008, 0.014, 0.04)$},
+}
+\newglossaryentry{k16}
+{
+    name={K16},
+    type={models},
+    description={The yield set from \citet{KL16, karakas+18}. The model is sampled at 
+        $M=(0.0003, 0.001, 0.002, 0.004, 0.008, 0.014, 0.04)$
+        and $Z=(0.0003, 0.001, 0.002, 0.004, 0.008, 0.014, 0.04)$
+    },
+}
+
+\newcommand{\cxi}{\gls{c11}}
+\newcommand{\kx}{\gls{k10}}
+\newcommand{\kxvi}{\gls{k16}}
+\newcommand{\vviii}{\gls{v13}}
+
 \newcommand{\Ycc}{\gls{ycc}}
-\newcommand{\Yct}{\ensuremath{y_{\rm C}}}
 \newcommand{\Yoc}{\gls{ymg}}
@@
 \newcommand{\Z}{\gls{Z}}
-\newcommand{\Zo}{\gls{Z}_\gls{sun}}
+\newcommand{\Zo}{\gls{Z}_{\gls{sun}}}
+
 \newcommand{\abund}[2]{\ensuremath{\[{\rm #1}/{\rm #2}\]}}
+
+\newcommand{\zoo}{\ensuremath{Z/Z_{\sun }}}
+\newcommand{\Yct}{\ensuremath{y_{\rm C}}}
 
@@
 \begin{document}
+
+\linespread{1.25}
 
@@
        \vspace*{3\baselineskip}
-       {Daniel Alexander Boyea}\\
+       {Daniel Alexander Boyea\\
        \vspace*{3\baselineskip}
@@
 
-James Johnson, for guiding me through this project and through my last year of undergraduate. Your feedback at every step of the process has been invaluable.
-Wayne Schlingman, for everything you do for everyone.
-You are the glue holding together our department.
-David Weinberg and Jennifer Johnson, for listening to my earlier drafts of this work and providing excellent suggestions.
-
-I also would not have made it here without all the support of my friends and family.
+I know I am guilty of skimming the acknowledgements of many works, but I dearly hope that the people who helped me complete this project will appriciate how much they have helped me.
+This year has been an incredibly challenging journey---and perhaps I am not open enough about what it has been like.
+I genuinly would have not made it to this day without everyones help, one way or another.
+
+James Johnson---your mentorship and guidance throughout this project was critical. 
+You helped me learn an incredible amount about being an astronomer, and I am forever greatful for how you have guided this project, through late nights and last minute comments.
+Wayne, for everything you do for everyone---you are the glue holding together our department and nobody can say thank you enough.
+David and Jennifer for helping this project move forward, by providing guidance at critical junctions and being part of my committee.
+Rolando, for being the non-astronomer thrown into this work, and pointing out the flaw of incomprehensability in this work.
+
+Even though you may have not been able to help me with the science, dear friends and family, you have been no less importaint in the completion of this work. 
 Eric, even across the country, you have always been a point of support and stability, and I am always happy to be around you.
-Anya, you are a wonderful friend and I cannot thank you enough for your support this year.
-I love so many people in our department who have just been friends and have positive support: Kaia, Maria, Autumn, Simon, Mary, Aaliyah, Sanskruti, Alyssa, Harrison, Denis, and so many others. 
-Finally, I thank my family for supporting me through a challenging year, and Arya for being such a loveable doodle.
+Anya, you are a wonderful friend and I cannot thank you enough for your unconditional support this year,
+All my friends who are just wonderful, inspiring, and incredible people---Kaia, Maria, Autumn, Simon, Bary, Aaliyah, Sanskruti, Alyssa, Harrison, Denis, Keith, and so many others. 
+And my family (including Arya, my most lovable doodle)---I can not eveen being to thank you enough for simply helping me recover my health and make it to graduation.
 
@@
 %
----observed in very low \gls{mtly}, high redshift \dla---decrease with increasing [O/H] \citep{FN15, cooke+17}.
+---observed in very low \gls{metallicity}, high redshift \dla---decrease with increasing [O/H] \citep{FN15, cooke+17}.
 Then, [C/O] increases above $\rm [O/H] \approx -1$ (\citealt{berg+19}; see discussion in \S\ref{sec:gas}).
@@
 For example, if a 1 $M_\odot$ star has $\tilde{y}_{\rm C} = 10^{-3}$, then the star will add $10^{-3}\ M_\odot$ of C to the interstellar medium.
-Although per-star yields are necessary to compute \agb{} star enrichment rates in \gce{}  models, \imf-averaged\footnote{IMF: Initial Mass Function} yields are useful in interpreting their predictions.
+Although per-star yields are necessary to compute \agb{} star enrichment rates in \gce{}  models, \imf-averaged yields are useful in interpreting their predictions.
 For a yield $y$ from a star of mass M and initial metallicity $Z$, the \imf-averaged yield is given by
@@
 	\centering
-    \caption[Fiducial Model]{Yields for the fiducial model in units of \ssp~birth mass. See \S\ref{sec:agb} for the definition of C11.}
+    \caption[Fiducial Model]{Yields for the fiducial model in units of \ssp~birth mass. See \S\ref{sec:agb} for the definition of \cxi.}
 	\label{tab:fiducial_mod}
@@
 \begin{itemize}
-    \item C11: \citet{cristallo+11, cristallo+15}
+    \item \cxi \citet{cristallo+11, cristallo+15}
     \item K10: \citet{karakas10}
@@
 \end{itemize}
-I use C11 table, amplified by a factor of 2.9, as the fiducial \agb\ yield.
+I use \cxi table, amplified by a factor of 2.9, as the fiducial \agb\ yield.
 
@@
 As the mass range $2\lesssim M \lesssim 4$ is most important for C production, about half of C production occurs before \about{1} Gyr, similar to \ia\ Fe. 
-K10 and K16 weight C production more heavily towards massive stars resulting in a faster enrichment delay time, whereas the C11 and V13 models predict a slightly longer timescale of \about{1} Gyr, but little to no C is produced more than 2 Gyr after a star formation event.
+K10 and K16 weight C production more heavily towards massive stars resulting in a faster enrichment delay time, whereas the \cxi\ and V13 models predict a slightly longer timescale of \about{1} Gyr, but little to no C is produced more than 2 Gyr after a star formation event.
 This is in contrast to Fe whos production lasts up to 10 Gyr after a star formation event.
@@
 The black dashed line shows $\tilde{y}=0$ for reference.
-Each panel represents yields from one of four \agb\ models: C11, K10, V13, K16 (see \S \ref{sec:agb}).
+Each panel represents yields from one of four \agb\ models: \cxi, K10, V13, K16 (see \S \ref{sec:agb}).
 }
@@
 
+\printglossary[type=\acronymtype,nonumberlist]
 \printglossary[type=symbols,nonumberlist]
+\printglossary[type=models]
 

### 2023-05-01 thesis/main.tex
new figs

--- 2023-04-29 thesis/tex/main.tex
@@
 %! tex program = lualatex
-\DocumentMetadata{testphase=phase-III, lang=en-US}
+\DocumentMetadata{lang=en-US}
 
@@
 
-\tagpdfsetup
-{
-    activate-all,
-}
+% \tagpdfsetup
+% {
+%     activate-all,
+% }
 
@@
 
-% \usepackage[tagpdf]{axessibility}
+%\usepackage{axessibility}
 
@@
 
-\newcommand{\et}{\gls{eta}}
-\newcommand{\zet}{\gls{zeta}}
-\newcommand{\sfr}{\gls{sfr}}
+\renewcommand{\eta}{\gls{eta}}
+\renewcommand{\zeta}{\gls{zeta}}
 
@@
     type={models},
-    description={the yield set from \citet{cristallo+11,cristallo+15}.
-The models were run at $m= (1.3, 1.5, 2.0, 2.5, 3.0, 4.0, 5.0, 6.0)$ and $Z=(0.0001, 0.0003, 0.001, 0.002, 0.003, 0.006, 0.008, 0.01, 0.014, 0.02)$.
-},
+    description={the yield set from \citet{cristallo+11,cristallo+15}},
 }
@@
     type={models},
-    description={the yield set from \citet{karakas10}. Includes models run at 
-    $M=(1.0, 1.25, 1.5, 1.75, 1.9, 2.25, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)$ and $Z=(0.0001, 0.004, 0.008, 0.02)$},
+    description={the yield set from \citet{karakas10}},
 }
@@
     type={models},
-    description={the \agb\ yield set from \citet{ventura+13,ventura+14,ventura+18,ventura+20}.
-Includes models with masses $m=(1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 6.0, 6.5, 7.0)$ and with metallicities $Z=(0.0003, 0.001, 0.002, 0.004, 0.008, 0.014, 0.04)$},
+    description={the \agb\ yield set from \citet{ventura+13,ventura+14,ventura+18,ventura+20}},
 }
@@
     type={models},
-    description={The yield set from \citet{KL16, karakas+18}. The model is sampled at 
-        $M=(0.0003, 0.001, 0.002, 0.004, 0.008, 0.014, 0.04)$
-        and $Z=(0.0003, 0.001, 0.002, 0.004, 0.008, 0.014, 0.04)$
-    },
+    description={the yield set from \citet{KL16, karakas+18}},
 }
@@
 For example, if a 1 $M_\odot$ star has $\tilde{y}_{\rm C} = 10^{-3}$, then the star will add $10^{-3}\ M_\odot$ of C to the interstellar medium.
-Although per-star yields are necessary to compute \agb{} star enrichment rates in \gce{}  models, \imf-averaged yields are useful in interpreting their predictions.
+Although per-star yields are necessary to compute \agb{} star enrichment rates in \gce{}  models, \imf-averaged\footnote{IMF: Initial Mass Function} yields are useful in interpreting their predictions.
 For a yield $y$ from a star of mass M and initial metallicity $Z$, the \imf-averaged yield is given by

### 2023-05-01 thesis/tex/main.tex
incramentally more cites and glossaries

@@
-%! tex program = lualatex
-\DocumentMetadata{testphase=phase-III, lang=en-US}
+\DocumentMetadata{lang=en-US}
 
@@
 
-\tagpdfsetup
-{
-    activate-all,
-}
-
-\usepackage{amsmath}	% Advanced maths commands
+\usepackage{amsmath}
+\usepackage{siunitx}
 
@@
 \usepackage{txfonts}
+\usepackage{microtype}
 
@@
     colorlinks=true,
-    linkcolor=magenta,
+    linkcolor=black,
     filecolor=black,
-    urlcolor=blue,
-    citecolor=blue,
+    urlcolor=black,
+    citecolor=black,
     pdftitle={The Galactic Chemical Evolution of Carbon},
+    pdfauthor={Daniel A Boyea},
+    pdfcreator={Themself},
+    pdfkeywords={astronomy,supernovae, stellar yields, chemical evolution, galaxies, carbon},
 }
@@
 \usepackage[nottoc,numbib]{tocbibind}
+\setcitestyle{aysep={}} 
+\setcitestyle{notesep={; }}
 
@@
 
-% these don't work with lualatex/phase-iii
-%\usepackage{accsupp}
-%\usepackage[accsupp]{axessibility}
-% \pdfcompresslevel=0
-
-% accessibility
-% \usepackage{tagpdf}
-
-% \usepackage[tagpdf]{axessibility}
+\newcommand\T{\rule{0pt}{2.6ex}}       % Top strut
+\newcommand\B{\rule[-1.2ex]{0pt}{0pt}} % Bottom strut
+
+\usepackage{accsupp}
+\usepackage[accsupp]{axessibility}
 
 %%%%%%%%%%%%%%% Acronyms %%%%%%%%%%%%%%%%%%
-\usepackage[acronym,automake,symbols,nogroupskip,counter=section]{glossaries-extra}
+\usepackage[acronym,automake,symbols,
+nogroupskip,
+accsupp,
+counter=section,
+postpunc={.},
+]{glossaries-extra}
+
 \newglossary*{models}{Stellar Yield Models}
@@
 \setabbreviationstyle[acronym]{long-short-sc}
-
-% \newabbreviation
-% [description={massive star explosions}]
-% {cc}{ccsne}{core collapse supernovae}
+\renewcommand*{\glsentrycounterlabel}{\theglossaryentry:\space}
 
 \newacronym
-[ description={heelloo}, seealso={ccg} ]
+[ description ={Core collapse supernovae. Massive star explosions. {\sc ccsne} produce many elements including $\alpha$-elements, Fe-peak elements, and r and s-process elements.}
+]
 {cc}{ccsne}{core collapse supernovae}
@@
 \newacronym
+[
+description={Damped Lyman-alpha system. {\sc dla}s are clouds of gas from the 
+early universe which are observed through their absorption of quasar spectra. The name 
+comes from the strong Lyman-alpha lines ($\qty{1216}{\angstrom}$) due to H absorption.}
+]
 {dla}{dla}{damped Lyman-alpha systems}
@@
 
+%%%%%%%%%%%%%%%%%%% Symbols %%%%%%%%%%%%%%%%%%%%%%%%
+\glsxtrnewsymbol
+[description = {The abundance ratio between elements $A$ and $B$. See }]
+{abundratio}{\ensuremath{[A/B]}}
+
+\glsxtrnewsymbol
+[description = {The mass outflow loading factor}]
+{aagb}{\ensuremath{\alpha_{\rm CC}}}
+
+\glsxtrnewsymbol
+[description = {The mass outflow loading factor}]
+{acc}{\ensuremath{\alpha_{\rm CC}}}
+
+\glsxtrnewsymbol
+[description = {The mass outflow loading factor}]
+{eta}{\ensuremath{\eta}}
+
+\glsxtrnewsymbol
+[description = {The massive star carbon yield metallicity dependence}]
+{zeta}{\ensuremath{\zeta}}
+
+\glsxtrnewsymbol
+[description = {The massive star carbon yield metallicity dependence}]
+{sfd}{\ensuremath{\dot{\Sigma}}}
+
+\glsxtrnewsymbol
+[description = {The mass of the sun. $M_\odot = \qty{1.989e33}{g}$}]
+{msun}{\ensuremath{M_\odot}}
+
+\glsxtrnewsymbol
+[description = {The rate of star formation}]
+{sfr}{\ensuremath{\dot{M}_\star}}
+
+\glsxtrnewsymbol
+[description = {The fractional contribution of AGB stars to the total \gls{imfave} carbon yield at solar metallicity.}]
+{fagb}{\ensuremath{f_{\rm AGB}}}
+
+\glsxtrnewsymbol
+[description = {The net fraction initial-mass-function weighted low-mass star yield of carbon}]
+{ytcagb}{\ensuremath{\tilde{y}_{\rm C}^{\rm AGB}}}
+
+\glsxtrnewsymbol
+[description = {The net fraction initial-mass-function weighted low-mass star yield of carbon}]
+{ycagb}{\ensuremath{y_{\rm C}^{\rm AGB}}}
+
 \glsxtrnewsymbol
@@
 \glsxtrnewsymbol
-[description = {The net fraction initial-mass-function weighted low-mass star yield of carbon}]
-{ycagb}{\ensuremath{y_{\rm C}^{\rm AGB}}}
-
-\glsxtrnewsymbol
 [description = {The net fraction initial-mass-function weighted massive star yield of magnesium}]
@@
 \glsxtrnewsymbol
-[description = {The symbol for the sun}]
-{sun}{\ensuremath{\odot}}
+[description = {The metallicity for the sun}]
+{zsun}{\ensuremath{Z_\odot}}
 
@@
 
-\glsxtrnewsymbol
-[description = {The massive star carbon yield metallicity dependence}]
-{zeta}{\ensuremath{\zeta}}
-
-\glsxtrnewsymbol
-[description = {The mass outflow loading factor}]
-{eta}{\ensuremath{\eta}}
-
-\glsxtrnewsymbol
-[description = {The rate of star formation}]
-{sfr}{\ensuremath{\dot{M}_\star}}
-
-\newcommand{\et}{\gls{eta}}
-\newcommand{\zet}{\gls{zeta}}
-\newcommand{\sfr}{\gls{sfr}}
-
+%%%%%%%%%%%%%%%%%%%%%% terms %%%%%%%%%%%%%%%
 \newglossaryentry{metallicity}{name={metallicity},
@@
 
+\newglossaryentry{nucleosynthesis}{name={nucleosynthesis},
+    description={the synthesis of new elements inside stars}
+}
+
+\newglossaryentry{yield}{name={yield},
+    description={the synthesis of new elements inside stars}
+}
+
+\newglossaryentry{multizone}{name={multi-zone},
+    description={the synthesis of new elements inside stars}
+}
+
+\newglossaryentry{onezone}{name={one-zone},
+    description={the synthesis of new elements inside stars}
+}
+
 \newglossaryentry{alpha}{name={$\alpha$-elements},
@@
 
-\newglossaryentry{ccg}
-{
-    name={core collapse supernovae},
-    description ={massive star explosions. core collapse supernovae (\textcs{ccsne}) produce many elements including $\alpha$-elements, Fe-peak elements, and r and s-process elements.}
-}
-
+\newglossaryentry{rgb}{name={red giant branch},
+    description={Red giant branch stars are stars which have completed hydrogen core burning and have expanded in size.}
+}
+
+\newglossaryentry{tdu}{name={third dredge up},
+    description={Third dredge up occurs when ....}
+}
+
+\newglossaryentry{fdu}{name={first dredge up},
+    description={Third dredge up occurs when ....}
+}
+
+\newglossaryentry{hbb}{name={hot bottom burning},
+    description={Third dredge up occurs when ....}
+}
+
+\newglossaryentry{subgiant}{name={subgiant},
+    description={A subgiant is...}
+}
+
+\newglossaryentry{imfave}{name={\gls{imf}-averaged},
+    description={Initial-mass function ....}
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%% Models %%%%%%%%%%%%%%%%%%%%%%%
 \newglossaryentry{c11}
@@
     description={the yield set from \citet{cristallo+11,cristallo+15}.
-The models were run at $m= (1.3, 1.5, 2.0, 2.5, 3.0, 4.0, 5.0, 6.0)$ and $Z=(0.0001, 0.0003, 0.001, 0.002, 0.003, 0.006, 0.008, 0.01, 0.014, 0.02)$.
+The models were run at $M = $ 1.3, 1.5, 2.0, 2.5, 3.0, 4.0, 5.0, 6.0 and $Z= $ 0.0001, 0.0003, 0.001, 0.002, 0.003, 0.006, 0.008, 0.01, 0.014, 0.02.
 },
@@
     description={the yield set from \citet{karakas10}. Includes models run at 
-    $M=(1.0, 1.25, 1.5, 1.75, 1.9, 2.25, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)$ and $Z=(0.0001, 0.004, 0.008, 0.02)$},
+    $M= $ 1.0, 1.25, 1.5, 1.75, 1.9, 2.25, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0 and $Z=$ 0.0001, 0.004, 0.008, 0.02},
 }
@@
 
-\newcommand{\cxi}{\gls{c11}}
-\newcommand{\kx}{\gls{k10}}
-\newcommand{\kxvi}{\gls{k16}}
-\newcommand{\vviii}{\gls{v13}}
+\newcommand{\cxi}{\texttt{\gls{c11}}}
+\newcommand{\kx}{\texttt{\gls{k10}}}
+\newcommand{\kxvi}{\texttt{\gls{k16}}}
+\newcommand{\vxiii}{\texttt{\gls{v13}}}
 
@@
 \newcommand{\Ycagb}{\gls{ycagb}}
-\newcommand{\sun}{\gls{sun}}
-\newcommand{\Z}{\gls{Z}}
-\newcommand{\Zo}{\gls{Z}_{\gls{sun}}}
+\newcommand{\sun}{\odot}
+\newcommand{\Z}{Z}
+\newcommand{\Zo}{Z_{\sun}}
 
@@
 
-%%%%%%%%%%%%%%%%%%% Citation commands %%%%%%%%%%%%%%%%%
-\defcitealias{cristallo+11}{C11}
-\defcitealias{cristallo+15}{C15}
-\defcitealias{ventura+13}{V13}
-\defcitealias{karakas10}{K10}
-\defcitealias{KL16}{KL16}
-\defcitealias{karakas+18}{K18}
 \defcitealias{james+21}{J21}
@@
 \newcommand{\JJ}{\citetalias{james+21}}
-\newcommand{\cristallo}{\citetalias{cristallo+11}+\citetalias{cristallo+15}}
-\newcommand{\karakas}{\citetalias{karakas10}}
-\newcommand{\kl}{\citetalias{KL16}+\citetalias{karakas+18}}
-\newcommand{\ventura}{\citetalias{ventura+13}}
-
 \newcommand{\VICE}{\texttt{VICE}}
@@
 
-\newcommand\T{\rule{0pt}{2.6ex}}       % Top strut
-\newcommand\B{\rule[-1.2ex]{0pt}{0pt}} % Bottom strut
-\newcommand{\possesivecite}[1]{\citeauthor{#1}'s \citeyearpar{#1}}
 \newcommand{\alp}{$\alpha$}
@@
 
-\setcitestyle{aysep={}} 
-\setcitestyle{notesep={; }}
-
-\title{Carbon Nucleosynthesis}
+\title{The Galactic Chemical Evolution of Carbon}
 \author{Daniel A. Boyea}
@@
 \begin{document}
-
-\linespread{1.25}
+% \linespread{1.25}
 
@@
        \vspace*{3\baselineskip}
-       {Daniel Alexander Boyea\\
+       {Daniel Alexander Boyea}\\
        \vspace*{3\baselineskip}
@@
 Anya, you are a wonderful friend and I cannot thank you enough for your unconditional support this year,
-All my friends who are just wonderful, inspiring, and incredible people---Kaia, Maria, Autumn, Simon, Bary, Aaliyah, Sanskruti, Alyssa, Harrison, Denis, Keith, and so many others. 
+All my friends who are just wonderful, inspiring, and incredible people---Kaia, Maria, Autumn, Simon, Bailee, Aaliyah, Sanskruti, Alyssa, Harrison, Denis, Keith, and so many others. 
 And my family (including Arya, my most lovable doodle)---I can not eveen being to thank you enough for simply helping me recover my health and make it to graduation.
@@
 \Gce{} aims to understand the chemical and star formation histories of galaxies.
-At the core of \gce{} models are stellar yields---the amount of each chemical element stars produce (or destroy).
+At the core of \gce{} models are stellar \gls{yield}s---the amount of each chemical element stars produce (or destroy).
 Each element is produced in different amounts by different stars, leaving traces of the Galaxy's evolutionary history.
@@
 C and N are well-studied elements since they are easy to observe in stellar spectra, even at the lowest metallicities \cite[e.g.][]{fabbian+09, nissen+14, lambert81, laird85, lambert86}.
-Additionally, C and N are used as age indicators in red giant branch stars \citep{martig16, MG15, hasselquist19, vincenzo+21}.
+Additionally, C and N are used as age indicators in \gls{rgb} stars \citep{martig16, MG15, hasselquist19, vincenzo+21}.
 
@@
 %
----observed in very low \gls{metallicity}, high redshift \dla---decrease with increasing [O/H] \citep{FN15, cooke+17}.
-Then, [C/O] increases above $\rm [O/H] \approx -1$ (\citealt{berg+19}; see discussion in \S\ref{sec:gas}).
+---observed in very low \gls{metallicity}, high redshift \dla{}---decrease with increasing [O/H] \citep{FN15, cooke+17}.
+Then, [C/O] increases above $\rm [O/H] \approx -1$ (\citealt{berg+19}; see discussion in section \ref{sec:gas}).
 While we know C is produced in \agb{} stars and \cc{}, we still have a limited understanding of the magnitude and metallicity-dependence of each process.
@@
 Accurate determination of stellar birth abundances for C and N is challenging.
-When a star enters the red giant branch, material from the CNO-processed core is mixed with the envelope in first dredge up, enhancing N and depleting C \citep{iben67, vincenzo+21,KL14}.
+When a star enters the \gls{rgb}, material from the CNO-processed core is mixed with the envelope in first dredge up, enhancing N and depleting C \citep{iben67, vincenzo+21,KL14}.
 Measurements of these evolved stars'  atmospheres will no longer reflect their birth abundances.
@@
 
-To this end, I use a sample of subgiant stars from the \apogee{} \citep{apogee17}.
+To this end, I use a sample of \gls{subgiant} stars from the \apogee{} \citep{apogee17}.
 According to stellar evolution theory and observations \citep{gilroy89, korn+07, lind+08, souto+18, souto19}, these stars have not yet experienced first dredge up but have well-mixed photospheres.
@@
 \begin{figure}[htp]
-    \includegraphics[width=\textwidth]{subgiants_mgh.pdf}
-    \includegraphics[width=\textwidth]{subgiants_mgfe.pdf}
-    \caption[APOGEE Subgiants]{The [C/Mg] ratio against [Mg/H] (top) and [Mg/Fe] (bottom) for the \citetjack~sample of \apogee{} subgiants.
+    \centering
+    \includegraphics{subgiants_mgh.pdf}
+    \quad\includegraphics{subgiants_mgfe.pdf}
+    \caption[APOGEE Subgiants]{The [C/Mg] ratio against [Mg/H] (top) and [Mg/Fe] (bottom) for the \citetjack~sample of \apogee{} \gls{subgiant}s.
 On the top, I plot high and low-$\alpha$ stars in blue and orange, using the separation defined in Equation \ref{eq:high_alpha}.
@@
 
-Theoretical models of stellar nucleosynthesis provide the starting point of this investigation.
+Theoretical models of stellar \gls{nucleosynthesis} provide the starting point of this investigation.
 I focus on three primary nucleosynthetic pathways: \agb{} stars, \cc{}, and \ia.
-Each process has unique timescales and yields, traceable through the tools of \gce.
+Each process has unique timescales and \gls{yield}s, traceable through the tools of \gce.
 I compare C, produced in \cc{} and \agb\ stars, to Mg and Fe as tracers of \cc{} and \ia{} espectively.
@@
 For example, if a 1 $M_\odot$ star has $\tilde{y}_{\rm C} = 10^{-3}$, then the star will add $10^{-3}\ M_\odot$ of C to the interstellar medium.
-Although per-star yields are necessary to compute \agb{} star enrichment rates in \gce{}  models, \imf-averaged yields are useful in interpreting their predictions.
-For a yield $y$ from a star of mass M and initial metallicity $Z$, the \imf-averaged yield is given by
+Although per-star yields are necessary to compute \agb{} star enrichment rates in \gce{}  models, \gls{imfave} yields are useful in interpreting their predictions.
+For a yield $y$ from a star of mass M and initial metallicity $Z$, the \gls{imfave} yield is given by
 \begin{equation} \label{eq:imf-yield}
@@
 	\centering
-    \caption[Fiducial Model]{Yields for the fiducial model in units of \ssp~birth mass. See \S\ref{sec:agb} for the definition of \cxi.}
+    \caption[Fiducial Model]{Yields for the fiducial model in units of \ssp~birth mass. See section \ref{sec:agb} for the definition of \cxi.}
 	\label{tab:fiducial_mod}
@@
 
+\begin{figure}[htp]
+    \includegraphics[width=\textwidth]{periodic_table.png}
+    \caption{The periodic table of elements. Taken from \cite{jennifer19}.}
+\end{figure}
+
 \section{Asymptotic Giant Branch Stars}\label{sec:agb}
@@
 An \agb\ star is a low mass ($\lesssim 8 M_{\sun}$) star during its final phase of evolution.
-In an \agb\ star, two competing processes determine the outcome of C production: third dredge up and hot bottom burning.
+In an \agb\ star, two competing processes determine the outcome of C production: \gls{tdu} and \gls{hbb}.
 Third dredge up accompanies thermal pulses in \agb\ stars.
-During a third dredge up event, material from the CO core is mixed with material exposed to partial He-shell burning, increasing C and O abundances in the envelope \citep{KL14}.
+During a \gls{tdu} event, material from the CO core is mixed with material exposed to partial He-shell burning, increasing C and O abundances in the envelope \citep{KL14}.
 If this envelope is lost during the \agb\ phase, then C yields are enhanced.
-Hot bottom burning is the activation of proton capture reactions, and the CNO cycle%
+\gls{hbb} is the activation of proton capture reactions, and the CNO cycle%
 \footnote{The CNO (I) cycle is
@@
 Because the $^{14}$N(p, $\gamma$) proton capture is the slowest component of the CNO cycle \citep{solar-fusion}, the CNO cycle converts nearly all \isotope[12]{C} into \isotope[14]{N}.
-As a result, when both third dredge up and Hot bottom burning occur, \isotope[12]{C} yields are lowered (see discussion in \citealt{james+23} and \citealt{ventura+13}).
-
-In this work, I explore four different sets of \agb\ star yield tables from literature, providing well-sampled grids in metallicity and mass for use in chemical evolution models. 
+As a result, when both \gls{tdu} and \gls{hbb}, \isotope[12]{C} yields are lowered (see discussion in \citealt{james+23} and \citealt{ventura+13}).
+
+    In this work, I explore four different sets of \agb\ star yield tables from literature, providing well-sampled grids in \gls{metallicity} and mass for use in chemical evolution models. 
 \begin{itemize}
-    \item \cxi \citet{cristallo+11, cristallo+15}
-    \item K10: \citet{karakas10}
-    \item V13: \citet{ventura+13,ventura+14,ventura+18, ventura+20}
-    \item K16: \citet{KL16} \citet{karakas+18}
+    \item \cxi: \citet{cristallo+11, cristallo+15}
+    \item \kx: \citet{karakas10}
+    \item \vxiii: \citet{ventura+13,ventura+14,ventura+18, ventura+20}
+    \item \kxvi: \citet{KL16} \citet{karakas+18}
 \end{itemize}
@@
 stars with masses between \about{2~M_\odot} and \about{4~M_\odot} have the highest fractional C yields, with the mass of the peak increasing and overall yields decreasing with increasing $Z$.
-High mass, high $Z$ stars destroy \isotope[12]{C} because they experience both third dredge up and hot bottom burning, but the latter is much more efficient.
+High mass, high $Z$ stars destroy \isotope[12]{C} because they experience both \gls{tdu} and \gls{hbb}, but the latter is much more efficient.
 
@@
 As the mass range $2\lesssim M \lesssim 4$ is most important for C production, about half of C production occurs before \about{1} Gyr, similar to \ia\ Fe. 
-K10 and K16 weight C production more heavily towards massive stars resulting in a faster enrichment delay time, whereas the \cxi\ and V13 models predict a slightly longer timescale of \about{1} Gyr, but little to no C is produced more than 2 Gyr after a star formation event.
+\kx{} and \kxvi{} weight C production more heavily towards massive stars resulting in a faster enrichment delay time, whereas the \cxi\ and \vxiii\ models predict a slightly longer timescale of \about{1} Gyr, but little to no C is produced more than 2 Gyr after a star formation event.
 This is in contrast to Fe whos production lasts up to 10 Gyr after a star formation event.
@@
 
-\begin{figure}
+\begin{figure}[htp]
     \centering
@@
 The black dashed line shows $\tilde{y}=0$ for reference.
-Each panel represents yields from one of four \agb\ models: \cxi, K10, V13, K16 (see \S \ref{sec:agb}).
+Each panel represents yields from one of four \agb\ models: \cxi, \kx{}, \vxiii{}, \kxvi{} (see section \ref{sec:agb}).
 }
@@
 \end{figure}
-\begin{figure}
+\begin{figure}[htp]
+    \centering
     \includegraphics[scale=1]{y_agb_t2.pdf}
@@
     C production by \agb\ stars as a function of \ssp{} age, normalized to the total mass $M_{\rm tot}$ produced at $t=10$ Gyr.
-Left: The four \agb\ yield models from literature at solar metallicity (C11, K10, V13, or K16).
+Left: The four \agb\ yield models from literature at solar metallicity (\cxi, \kx{}, \vxiii{}, or \kxvi{}).
 The delay time distribution of type Ia supernovae ($\propto t^{-1.1}$) is plotted as a dashed black line for comparison.
-Right: The C11 \agb\ model at different metallicities.
+Right: The \cxi\ \agb\ model at different metallicities.
 }
@@
 
-Fig.~\ref{fig:yagb-z} shows \imf-averaged C yields for each \agb\ model as a function of metallicity $Z$.
-V13 differs in that it shows a non-monotonic metallicity dependence. However, this effect is only for models with $\log Z/Z_\odot \lesssim -1$.
+Fig.~\ref{fig:yagb-z} shows \gls{imfave} C yields for each \agb\ model as a function of metallicity $Z$.
+\vxiii{} differs in that it shows a non-monotonic metallicity dependence. However, this effect is only for models with $\log Z/Z_\odot \lesssim -1$.
 Otherwise, models differ only in their yield normalization and metallicity dependence. All models predict yields within a factor of \about{2} for fixed metallicity.
-For example, the three models C11, K10, and K16 predict $y_\text{C}^\text{AGB}$ to be between 0.006 and 0.008 at solar metallicity, but C11 has a much shallower metallicity dependence than the K10 and K16 models.
-V13 instead predicts a yield \about{0.004}.
-
-\begin{figure}
+For example, the three models \cxi, \kx{}, and \kxvi{} predict $y_\text{C}^\text{AGB}$ to be between 0.006 and 0.008 at solar metallicity, but \cxi\ has a much shallower metallicity dependence than the \kx{} and \kxvi{} models.
+\vxiii{} instead predicts a yield \about{0.004}.
+
+\begin{figure}[htp]
     \centering
@@
 Our fiducial model's steep metallicity dependence near $Z\approx Z_\odot$ could be explained by rotation.
-Fig.~\ref{fig:y_cc} shows the C11 model for comparison on the top.
+Fig.~\ref{fig:y_cc} shows the \cxi{} model for comparison on the top.
 Especially at $Z\approx Z_\odot$, most \cc{} models dominate \agb\ C production.
@@
 \citet{sukhbold+16} report yields for different black hole landscapes, while \citet{LC18} provide yields at different rotational velocities.
-In the top panel, the pink line denotes $\Ycagb$ from C11 for comparison.
+    In the top panel, the pink line denotes $\Ycagb$ from \cxi{} for comparison.
 }
@@
 
-I assume a simple ``one-zone'' chemical evolution model \cite[e.g.][]{tinsley80, pagel09, matteucci21}.
+I assume a simple \textit{\gls{onezone}} chemical evolution model \cite[e.g.][]{tinsley80, pagel09, matteucci21}.
 Newly produced metals are homogeneously and instantaneously mixed, so spatial dependence is neglected.
@@
 ($r\approx0.4$ for a \citealt{kroupa01} \imf.)
-Given the \imf-averaged yield of Mg $y_{\rm Mg}$, the rate of change in the gas-phase mass of Mg $\dot{M}_{\rm Mg}$ is a simple sum of sources and sinks,
+Given the \gls{imfave} yield of Mg $y_{\rm Mg}$, the rate of change in the gas-phase mass of Mg $\dot{M}_{\rm Mg}$ is a simple sum of sources and sinks,
 \begin{equation}
@@
 
-As I will discuss in \S\ref{sec:outflows}, the normalization of yields and $\eta$ is degenerate.
+As I will discuss in section \ref{sec:outflows}, the normalization of yields and $\eta$ is degenerate.
 This can be observed in Eq.~\ref{eq:z_co}, where changes in $\eta$ or the scaling of $y_{\rm C}/y_{\rm Mg}$ would not affect equilibrium trends.
@@
 \end{subequations}
-This ratio results in an equilibrium abundance ${\rm [C/Mg]} = -0.09$, which is consistent with the \citetjack~subgiant sample and is within \about{20\%} of the solar C/Mg mixture from \citet{asplund+09}.
-
-In \S\ref{sec:f-z-models}, I will show that none of the four \agb\ yield sets (C11, K10, V13, K16) produce enough C relative to this $\Ycc$ value.
+This ratio results in an equilibrium abundance ${\rm [C/Mg]} = -0.09$, which is consistent with the \citetjack~\gls{subgiant} sample and is within \about{20\%} of the solar C/Mg mixture from \citet{asplund+09}.
+
+In section \ref{sec:f-z-models}, I will show that none of the four \agb\ yield sets (\cxi{}, \kx{}, \vxiii{}, \kxvi{}) produce enough C relative to this $\Ycc$ value.
 So, I introduce normalization factors, $\alpha_{\rm AGB}$, and $\alpha_{\rm CC}$ which denote a multiplicitave scaling of $\Ycc$ and $\Ycagb$ respectively.
@@
 
-In \S\ref{sec:f-z-models}, I find that $\alpha_{\rm AGB}\approx 2.9$ for the C11 yield model.
+In section \ref{sec:f-z-models}, I find that $\alpha_{\rm AGB}\approx 2.9$ for the \cxi{} yield model.
 Using this \agb\ yield, I can now use Eq.~\ref{eq:y_c_eq} to find an estimate of $\Ycc$ as a function of metallicity.
-I show the values of $\Ycc$ I obtain from the subgiant sample in Fig.~\ref{fig:analytic}.
+I show the values of $\Ycc$ I obtain from the \gls{subgiant} sample in Fig.~\ref{fig:analytic}.
 From regression analysis, I suggest here that
@@
 
-I only perform this analysis on the C11 yields because C11 has yields tables more finely sampled in metallicity than the other three \agb\ yield tables.
+I only perform this analysis on the \cxi{} yields because \cxi{} has yields tables more finely sampled in metallicity than the other three \agb\ yield tables.
 As the metallicity range of the data is small ($-0.4\lesssim {\rm [Mg/H]} \lesssim 0.4$), other models are more challenging to interpret in this range.
-Furthermore, the \apogee{} observations may have systematics, and other measurements of C abundances \citep[e.g.][]{vincenzo+21} have slight disagreements in the overall shape of the trend (see \S\ref{sec:jack}).
+Furthermore, the \apogee{} observations may have systematics, and other measurements of C abundances \citep[e.g.][]{vincenzo+21} have slight disagreements in the overall shape of the trend (see section \ref{sec:jack}).
 So, this expression of $\Ycc/\Yoc$ depends on the chosen \agb\ yield table, the \agb\ fraction, and the dataset. 
@@
 
-Classical, ``one-zone'' models of chemical evolution assume instantaneous mixing of metals in the star-forming interstellar medium \citep[e.g.][]{matteucci21}.
+Classical, \textit{\gls{onezone}} models of chemical evolution assume instantaneous mixing of metals in the star-forming interstellar medium \citep[e.g.][]{matteucci21}.
 This simple framework is a poor approximation for the Milky Way.
@@
 Additionally, stars can migrate several kpc over their lifetimes, mixing together different chemical environments across the galaxy \citep{bird+12,sellwood+binney02}.
-For the rest of this paper, I focus on multizone models, which discretize the Galaxy into concentric annuli and allow stars to move between rings.
+For the rest of this paper, I focus on \gls{multizone} models, which discretize the Galaxy into concentric annuli and allow stars to move between rings.
 Specifically, I make use of the \citet{james+21} (hereafter \JJ) model for the Milky Way, which runs using the publicly available Versatile Integrator for Chemical Evolution (\VICE).
@@
 
-\citet{james+23} compare their model against the \cite{vincenzo+21} sample of \apogee{} \citep{apogee17} red giants whose C and N abundance have been corrected for mixing process using MESA stellar evolution models.
-I instead use the \citetjack~sample of \apogee{} subgiants.
+\citet{james+23} compare their model against the \cite{vincenzo+21} sample of \apogee{} \citep{apogee17} \gls{rgb} C and N abundance have been corrected for mixing process using MESA stellar evolution models.
+I instead use the \citetjack~sample of \apogee{} \gls{subgiant}s.
 Subgiant stars have not undergone first dredge up but have well mixed atmospheres, so their atmospheric C and N abundances are still reflective of their birth abundances and do not need mixing corrections.
@@
 The fiducial model has the following qualitative characteristics of its C yields: (a) C is predominantly produced in \cc, (b) \cc\ produce more C at higher metallicities, and (c) \agb\ stars produce less C at higher metallicities.
-Our fiducial model uses the C11 \agb\ yield tables (see \S\ref{sec:agb}, and Table \ref{tab:fiducial_mod}), and I amplify the C11 yields by a factor of 2.9 such that \agb\ stars account for 20\% of C at $Z=Z_\odot$.
-
-I show the time evolution tracks of the fiducial model in Fig.~\ref{fig:c_evo} for \caah~ and \caafe~.
+Our fiducial model uses the \cxi{} \agb\ yield tables (see section \ref{sec:agb}, and Table \ref{tab:fiducial_mod}), and I amplify the \cxi{} yields by a factor of 2.9 such that \agb\ stars account for 20\% of C at $Z=Z_\odot$.
+
+I show the time evolution tracks of the fiducial model in Fig.~\ref{fig:c_evo} for \caah~ and \caafe.
 Comparing [C/Mg] against [Mg/Fe] enables us to see the late-time evolution of C more clearly.
@@
 This is even more evident in the lower panel of Fig.~\ref{fig:c_evo}.
-While the \caah~trend reaches equilibrium at \about{5} Gyr, the \caafe~trend continues to evolve even until the present day, exposing the effect of the relative delay times of \agb\ stars and \ia.
-
-\begin{figure}
+While the \caah\ trend reaches equilibrium at \about{5} Gyr, the \caafe\ trend continues to evolve even until the present day, exposing the effect of the relative delay times of \agb\ stars and \ia.
+
+\begin{figure}[htp]
 \centering
@@
 
-Fig.~\ref{fig:agb_sims} compares the K10, K16, C11, and V13 yield models.
+Fig.~\ref{fig:agb_sims} compares the \kx{}, \kxvi{}, \cxi{}, and \vxiii{} yield models.
 Here, I use the published, unscaled yield tables.
-As the highest \agb\ yield at solar, K10 is only $\Ycagb=0.000585$, $f_{\rm AGB} \leq 0.12$ for all models.
+As the highest \agb\ yield at solar, \kx{} is only $\Ycagb=0.000585$, $f_{\rm AGB} \leq 0.12$ for all models.
 Massive stars dominate C production with unscaled yields.
 While it is easy to modify the \agb\ yields in my model, their small contribution reduces the effect.
-I leave a more detailed discussion of the effects of \agb\ models for Appendix \ref{sec:alt_agb} and use C11 yields hereafter.
-
-\begin{figure}
-\centering
-\includegraphics{oob_agb.pdf}
+I leave a more detailed discussion of the effects of \agb\ models for Appendix \ref{sec:alt_agb} and use \cxi{} yields hereafter.
+
+\begin{figure}[htp]
+\centering
+\includegraphics{agb_oob.pdf}
 \caption[Mean stellar abundance trends]{
@@
 On the top panel of Fig.~\ref{fig:beta_f}, I plot models with varying $\Ycc$ metallicity dependence.
-As discussed in \S\ref{sec:equilibrium}, the \caah~trend is approximated by equilibrium, so the trends of these have steeper \caah~corresponding to steeper metallicity dependence.
+As discussed in section \ref{sec:equilibrium}, the \caah~trend is approximated by equilibrium, so the trends of these have steeper \caah~corresponding to steeper metallicity dependence.
 However, \caafe~is minimally affected by these changes since \cc\ occure on much shorter timescales than \ia\ and \agb\ enrichment.
@@
 where  $\Ycagb$ includes the multiplicative factor $\alpha_{\rm AGB}$ as defined in Eq.~\ref{eq:alpha}.
-In the bottom panel of Fig.~\ref{fig:beta_f}, I plot three models with different \agb\ fractions while using C11 yields.
+In the bottom panel of Fig.~\ref{fig:beta_f}, I plot three models with different \agb\ fractions while using \cxi{} yields.
 The \caafe~relationship is set by $f_{\rm AGB}$ because a specific amount of C must be released at a delayed time in order to match the \ia\ production of Fe and increase [C/Mg] as [Mg/Fe] decreases to reproduce the data.
@@
 
-\begin{figure}
+\begin{figure}[htp]
 \centering
@@
 
-\caption[Lateburst models]{Same as Fig.~\ref{fig:agb_sims} but comparing the fiducial model to alternate \sfh{}s (see \S \ref{sec:sfh}).}
+\caption[Lateburst models]{Same as Fig.~\ref{fig:agb_sims} but comparing the fiducial model to alternate \sfh{}s (see section  \ref{sec:sfh}).}
 \label{fig:sfh_models}
@@
 An increase in stellar yields has a nearly identical effect as a decrease in the mass-loading factor $\eta$ (see Appendix B of \cite{james_dwarf}).
-The equilibrium arguments discussed in \S\ref{sec:equilibrium} suggest however that abundance ratios are independent of the choice of normalization and the value of $\eta$.
+The equilibrium arguments discussed in section \ref{sec:equilibrium} suggest however that abundance ratios are independent of the choice of normalization and the value of $\eta$.
 I therefore expect my results regarding the relative yield $y_{\rm C}/y_{\rm Mg}$ and its metallicity dependence to extend to the other class of models omitting mass loading.
@@
 
-\begin{figure}
-
+\begin{figure}[htp]
+    \centering
 \includegraphics{eta.pdf}
 
-\caption[Reduced-outflow models]{Same as Fig.~\ref{fig:agb_sims} but comparing the fiducial model to reduced outflow models (see \S \ref{sec:outflows}).}
+\caption[Reduced-outflow models]{Same as Fig.~\ref{fig:agb_sims} but comparing the fiducial model to reduced outflow models (see section  \ref{sec:outflows}).}
 \end{figure}
@@
 Median trends have limitations as they do not consider the actual distribution of \caah~abundances.
-So, I show in Fig.~\ref{fig:scatter} a comparison of the predicted distribution of the model to the contours of the subgiant sample.
+So, I show in Fig.~\ref{fig:scatter} a comparison of the predicted distribution of the model to the contours of the \gls{subgiant} sample.
 Our model reproduces this 2-dimension distribution well when including scatter based on the median \apogee{} abundance errors for each metallicity bin.
@@
 Stellar measurements of Mg are more reliable, but O abundances are easier to measure in HII regions.
-I therefore use Mg abundances from the \citetjack~subgiant sample as my primary empirical constraint.
-However, I use O abundances for gas-phase measurements and low-metallicity stars (\S \ref{sec:gas}).
+I therefore use Mg abundances from the \citetjack~\gls{subgiant} sample as my primary empirical constraint.
+However, I use O abundances for gas-phase measurements and low-metallicity stars (section  \ref{sec:gas}).
 I model both Mg and O as metallicity-independent population-averaged yields dominated by massive stars.
@@
 
-\begin{figure}
+\begin{figure}[htp]
     %\includegraphics{nitrogen.pdf}
@@
 
-\begin{figure*}
+\begin{figure}[htp]
 \centering
@@
     HII regions    \citep[pink circles;][]{skillman+20, esteban+02, esteban+09, esteban+14, esteban+19}
-    \dla\ systems \citep[blue triangles;][]{cooke+17} 
+    \dla\ systems \citep[blue triangles;][]{ellison+10, srianand+10, dutta+14, DZ+03, pettini+08, morrison+16,cooke+17}  % a1: Cooke et al.
+(2015); 2: Dutta et al.
+(2014); 3: Cooke et al.
+(2014); 4: Ellison et al.
+(2010); 5: Cooke et al.
+(2011b); 6: This work; 7: Pettini et al.
+(2008); 8: Morrison et al.
+(2016); 9: Srianand et al.
+(2010); 10: Cooke et al.
+(2012); 11: Dessauges-Zavadsky et al.
+(2003)
     Milky Way halo and thick disk stars \citep[green stars;][]{nissen+14, fabbian+09}. 
@@
 \label{fig:gas_phase}
-\end{figure*}
+\end{figure}
 
@@
 
-In this work, I investigate the role of C yields on the predictions of multizone \gce{} models.
+In this work, I investigate the role of C yields on the predictions of \gls{multizone} \gce{} models.
 \citet{james+23} performed a similar analysis focusing on N.
@@
 
-Though \cc\ C yields are poorly understood, I adopt an equilibrium approximation and determine a functional form that approximately matches trends in \apogee{} subgiants and is consistant with massive star nucleosynthesis models.
+Though \cc\ C yields are poorly understood, I adopt an equilibrium approximation and determine a functional form that approximately matches trends in \apogee{} \gls{subgiant} and is consistant with massive star \gls{nucleosynthesis} models.
 Variations of the metallicity dependence of this \cc\ yield affect trends in \caah~but do not affect trends in \caafe\ when taking a slice in [Mg/H].
@@
 Future spectroscopic surveys combined with Gaia kinematics \citep{gaia} will continue to enhance our understanding of chemical evolution.
-Both the Sloan Digital Sky Survey V's Milky Way Mapper program (SDSS-V/MWM) \citep{sdssv} and the Dark Energy Spectroscopic Instrument (DESI) Milky Way survey \citep{desi, desi:mw} will each measure spectra of $>6$ million Milky Way stars.
+Both the Sloan Digital Sky Survey V's Milky Way Mapper program ({\sc SDSS-V/MWM}) \citep{sdssv} and the Dark Energy Spectroscopic Instrument ({\sc DESI}) Milky Way survey \citep{desi, desi:mw} will each measure spectra of $>6$ million Milky Way stars.
 These larger samples will enable similar work to tighten constraints on stellar models and our understanding of galaxy structure and evolution.
@@
 
-I use the criteria outlined in \citetjack~to create a sample of subgiants from \apogee{} DR17 \cite{apogee17} as our primary observational constraint.
+I use the criteria outlined in \citetjack~to create a sample of \gls{subgiant}s from \apogee{} DR17 \cite{apogee17} as our primary observational constraint.
 \apogee\ is part of the Sloan Digital Sky Survey 17 and measures high resolution spectra of thousands of stars \cite{sdss17}.
 Subgiants are reflective of birth abundances for CNO \citep{souto19}.
-with chemical abundance determinations from the \apogee Stellar Parameter and Chemical Abundance Pipeline \citep{aspcap}.
+with chemical abundance determinations from the \apogee\ Stellar Parameter and Chemical Abundance Pipeline ({\sc aspcap}) \citep{aspcap}.
 \citetjack~select a region of stars in $\log g$-$T_\text{eff}$ space described by the following polyhedron
@@
         A Kiel diagram of \apogee{} stars.
-Following \citetjack, we select subgiants in the orange polygon (see Equation \ref{eq:subgiant_selection}).
+Following \citetjack, we select \gls{subgiant}s in the orange polygon (see Equation \ref{eq:subgiant_selection}).
 These stars have not yet experienced first dredge-up, so their photospheric C and N abundances should reflect their birth mixture.
@@
 
-This cut isolates a clean sample of \about{12,000} subgiants.
-As first dredge up, which affects C and N abundances, only occurs during the ascent onto the red giant branch, subgiant stars are unaffected by this enrichment.
+This cut isolates a clean sample of \about{12,000} \gls{subgiant}s.
+As first dredge up, which affects C and N abundances, only occurs during the ascent onto the \gls{rgb}, \gls{subgiant} stars are unaffected by this enrichment.
 
@@
 
-While I focus the main discussion of the paper on the C11 model, other \agb\ models can impact abundance trends when $f_{\rm AGB}$ becomes larger.
+While I focus the main discussion of the paper on the \cxi{} model, other \agb\ models can impact abundance trends when $f_{\rm AGB}$ becomes larger.
 Here, I briefly explore the effects of variations in \agb\ models that affect abundance trend predictions when these models are amplified to match observational [C/MG]-[Mg/Fe] trends. 
@@
 
-V13 is also interesting as at high metallicity, the yields quickly become strongly negative.
+\vxiii{} is also interesting as at high metallicity, the yields quickly become strongly negative.
 This causes a reversal of the [C/Mg]-[Mg/Fe] trend at high [Mg/H] slices (figure ...).
-As our set of observations does not appear to reverse, this indicates that C yields are likely to stay positive even at slightly super-solar, so models like V13 are a poor match to observations.
+As our set of observations does not appear to reverse, this indicates that C yields are likely to stay positive even at slightly super-solar, so models like \vxiii{} are a poor match to observations.
 
@@
 
-\glsaddall
+\renewcommand*{\arraystretch}{1.25}
+
+\glsaddall[types={symbols}]
+
+\printunsrtglossary[type=symbols,nonumberlist,style=long]
+
+\renewcommand*{\arraystretch}{1}
+\printglossary[type=models,nonumberlist]
 
 \printglossary[type=\acronymtype,nonumberlist]
-\printglossary[type=symbols,nonumberlist]
-\printglossary[type=models]
-
 \printglossary

### 2023-05-01 thesis/tex/main.tex
results section edits

@@
 \usepackage{amsmath}
-\usepackage{siunitx}
 
@@
 \usepackage{microtype}
+
+\usepackage{graphicx}	% Including figure files
+\usepackage{booktabs}
+\graphicspath{{../figures/}} 
+\usepackage{isotope}
+\usepackage[tableposition=above]{caption}
+
+\usepackage{aas_macros}
+\usepackage{natbib}
+\usepackage[nottoc,numbib]{tocbibind}
+\setcitestyle{aysep={}} 
+\setcitestyle{notesep={; }}
 
@@
 
-\usepackage{graphicx}	% Including figure files
-\usepackage{booktabs}
-\graphicspath{{../figures/}} 
-\usepackage{isotope}
-\usepackage[tableposition=above]{caption}
-
-\usepackage{aas_macros}
-\usepackage{natbib}
-\usepackage[nottoc,numbib]{tocbibind}
-\setcitestyle{aysep={}} 
-\setcitestyle{notesep={; }}
-
 %%%%%%%%%%%%%%% Formatting %%%%%%%%%%%%%%%%%%
@@
 postpunc={.},
+stylemods={longextra}
 ]{glossaries-extra}
@@
 \setabbreviationstyle[acronym]{long-short-sc}
-\renewcommand*{\glsentrycounterlabel}{\theglossaryentry:\space}
+\GlsXtrEnablePreLocationTag{Section: }{Sections: }
+
+\newglossarystyle{2colsymbol}{%
+    \setglossarystyle{long}% base this style on the list style
+    \renewenvironment{theglossary}{% Change the table type --> 3 columns
+        \glsdescwidth=\dimexpr\linewidth-\dimen0-2\tabcolsep\relax
+        \begin{longtable}{@{}l p{\glsdescwidth}@{}}}%
+        {\end{longtable}}%
+    \renewcommand*{\glossentry}[2]{%  Change the displayed items
+        \glstarget{##1}{\glossentryname{##1}} %
+        \glssymbol{##1}
+        &  \glossentrydesc{##1}  \tabularnewline
+    }
+}
 
 \newacronym
-[ description ={Core collapse supernovae. Massive star explosions. {\sc ccsne} produce many elements including $\alpha$-elements, Fe-peak elements, and r and s-process elements.}
+[ description ={Core collapse supernovae. Massive star explosions. {\sc ccsne} produce many elements including \gls{alpha}, Fe-peak elements, and r and s-process elements.}
 ]
@@
 \newacronym
-[description={Exploding white dwarfs, produces Fe-peak elements}]
+[description={Type Ia Supernovae. Exploding white dwarfs, produces \gls{fepeak} elements and with a long delay time.}]
 {ia}{sne ia}{supernovae type Ia}
@@
 \newacronym
+[description={Single Stellar Population. A group of stars formed all at the same time.}]
 {ssp}{ssp}{single stellar population}
@@
 \newacronym
+[description={A function describing the mass distribution of newly formed stars. I use a \citet{kroupa01} {\sc imf}, which is described as a piecewise powerlaw function of $M$.}]
 {imf}{imf}{initial mass function}
@@
 \newacronym
+[description={A large near-infrared spectroscopic survey of stars in the Milky Way.}]
 {apogee}{apogee}{Apache Point Observatory Galactic Evolution Experiment}
@@
 early universe which are observed through their absorption of quasar spectra. The name 
-comes from the strong Lyman-alpha lines ($\qty{1216}{\angstrom}$) due to H absorption.}
+comes from the strong Lyman-alpha lines ($1216\AA$) due to H absorption.}
 ]
@@
 \glsxtrnewsymbol
-[description = {The mass outflow loading factor}]
-{aagb}{\ensuremath{\alpha_{\rm CC}}}
-
-\glsxtrnewsymbol
-[description = {The mass outflow loading factor}]
+[description = {The multiplicative increase in \agb\ C production. See Eq.~\ref{eq:alpha}}]
+{aagb}{\ensuremath{\alpha_{\rm AGB}}}
+
+\glsxtrnewsymbol
+[description = {The multiplicative increase in \cc\ C production. See Eq.~\ref{eq:alpha}}]
 {acc}{\ensuremath{\alpha_{\rm CC}}}
@@
 \glsxtrnewsymbol
-[description = {The mass outflow loading factor}]
+[description = {The mass outflow loading factor. $\eta$ is the ratio between ejected gas from the galaxy and star formation, i.e. $\eta = \dot{M}_{\rm outflow}/\dot{M}_\star$. }]
 {eta}{\ensuremath{\eta}}
@@
 \glsxtrnewsymbol
-[description = {The massive star carbon yield metallicity dependence}]
+[description = {The massive star carbon yield metallicity dependence. See Eq.~\ref{eq:zeta}}]
 {zeta}{\ensuremath{\zeta}}
@@
 \glsxtrnewsymbol
-[description = {The massive star carbon yield metallicity dependence}]
+[description = {The surface density of star formation by mass.}]
 {sfd}{\ensuremath{\dot{\Sigma}}}
@@
 \glsxtrnewsymbol
-[description = {The mass of the sun. $M_\odot = \qty{1.989e33}{g}$}]
+[description = {The mass of the sun. $M_\odot = 1.989\times10^{33}$\,g}]
 {msun}{\ensuremath{M_\odot}}
@@
 \glsxtrnewsymbol
-[description = {The rate of star formation}]
+[description = {The rate of star formation.}]
 {sfr}{\ensuremath{\dot{M}_\star}}
@@
 {Z}{\ensuremath{Z}}
+
+\glsxtrnewsymbol
+[description = {A nuclear reaction.
+The initial element is $X$, and (optionally) some particle $a$ collides with $X$, and particles $b$ are then released.
+The next isotope symbol is the result of the reaction.}]
+{nuclrxn}{\ensuremath{X(a,b)}}
 
@@
 
-\newglossaryentry{alpha}{name={$\alpha$-elements},
-    description={Elements which are made up of $\alpha$-particles (two protons, two neutronns). Essentially light, even-numbered elements like O, Mg, and Na.}
+\newglossaryentry{alpha}{name={$\alpha$-element},
+    description={Elements which are made up of $\alpha$-particles (He nuclei) throuch the triple-$\alpha$ process (see Eq.
+\ref{eq:triple_alpha}).
+Essentially light, even-numbered elements like O, Mg, and Na.}
 }
@@
 \newglossaryentry{fepeak}{name={Fe-peak elements},
-    description={Fe and nearby elements, produced in \cc\ and \sneia.}
+    description={Fe and nearby elements, produced in \gls{cc} and \gls{ia}.}
 }
@@
 
-\newglossaryentry{rproc}{name={r-process elements},
-    description={Elements produced through rapid neutron capture process, though to occur in the collision of two neutron stars.}
-}
-
 \newglossaryentry{rgb}{name={red giant branch},
@@
 \newglossaryentry{tdu}{name={third dredge up},
-    description={Third dredge up occurs when ....}
+    description={Third dredge up occurs inside \gls{agb} stars.
+During each thermal pulse, material is {\it dredged up} from the core, changing the chemical abundances of the stellar atmosphere.
+(While nominally called {\it third dredge up}, there are typically several third dredge ups.) }
 }
@@
 
+\newglossaryentry{dtd}{name={delay-time distribution},
+    description={The distribution in time of when an element is produced 
+    after a star formation event.}
+}
+
+\newglossaryentry{massloading}{name={mass loading},
+    description={The stength of outflows.}
+}
+
+\newglossaryentry{lowalpha}{name={low-$\alpha$},
+    description={The low-$\alpha$ sequence, as described by Eq.~\ref{eq:high_alpha}. }
+}
+
+\newglossaryentry{highalpha}{name={high-$\alpha$},
+    description={The high-$\alpha$ sequence, as described by Eq.~\ref{eq:high_alpha}. }
+}
+
+\newglossaryentry{cno}{name={CNO cycle},
+    description = { A proton-fusion cycle which occurs in \gls{rgb} stars 
+        consisting of a chain of proton captures releasing a helium nucleus ($\alpha$-particle) and energy. See Eq.~\ref{eq:cno_cycle}.
+}
+}
 %%%%%%%%%%%%%%%%%%%%%%%%%% Models %%%%%%%%%%%%%%%%%%%%%%%
@@
 \newcommand{\abund}[2]{\ensuremath{\[{\rm #1}/{\rm #2}\]}}
+\newcommand{\proton}{\isotope[1][1]{p}}
 
@@
     \caption[APOGEE Subgiants]{The [C/Mg] ratio against [Mg/H] (top) and [Mg/Fe] (bottom) for the \citetjack~sample of \apogee{} \gls{subgiant}s.
-On the top, I plot high and low-$\alpha$ stars in blue and orange, using the separation defined in Equation \ref{eq:high_alpha}.
+On the top, I plot high and \gls{lowalpha} stars in blue and orange, using the separation defined in Equation \ref{eq:high_alpha}.
 On the bottom, I color-code stars according to their [Mg/H] abundance.}
@@
 Table \ref{tab:fiducial_mod} contains my fiducial yields, in units of a \ssp's birth mass.
-Also following \citet{james+21, james+23}, I take the \ia{} delay time distribution to be a
+Also following \citet{james+21, james+23}, I take the \ia{} \gls{dtd} to be a
 $t^{-1.1}$ power-law suggested by the observations of \citet{maoz+12}.
@@
 \gls{hbb} is the activation of proton capture reactions, and the CNO cycle%
-\footnote{The CNO (I) cycle is
-\isotope[12]{C}(p, $\gamma$)
-\isotope[13]{N}($\beta^+ \nu_e$)
-\isotope[13]{C}(p, $\gamma$)
-\isotope[14]{N}(p, $\gamma$)
-\isotope[15]{O}($\beta^{+}\nu_e$)
-\isotope[15]{N}(p, \alp)
-\isotope[12]{C}.
- Other minor branches of the CNO cycle are of minor importance to C yields
+Other minor branches of the \gls{cno} are of minor importance to C yields
  \citep{solar-fusion}.
-}
+
 at the base of the convective envelope.
@@
 from \citealt{larson74}.})
-As the mass range $2\lesssim M \lesssim 4$ is most important for C production, about half of C production occurs before \about{1} Gyr, similar to \ia\ Fe. 
-\kx{} and \kxvi{} weight C production more heavily towards massive stars resulting in a faster enrichment delay time, whereas the \cxi\ and \vxiii\ models predict a slightly longer timescale of \about{1} Gyr, but little to no C is produced more than 2 Gyr after a star formation event.
-This is in contrast to Fe whos production lasts up to 10 Gyr after a star formation event.
+As the mass range $2\lesssim M \lesssim 4$ is most important for C production, about half of C production occurs before \about{1}\,Gyr, similar to \ia\ Fe. 
+\kx{} and \kxvi{} weight C production more heavily towards massive stars resulting in a faster enrichment delay time, whereas the \cxi\ and \vxiii\ models predict a slightly longer timescale of \about{1}\,Gyr, but little to no C is produced more than 2\,Gyr after a star formation event.
+This is in contrast to Fe whos production lasts up to 10\,Gyr after a star formation event.
 As shown in the right panel of Fig.~\ref{fig:agb-ssp}, with increasing $Z$, C enrichment occurs earlier, and C destruction in low-mass stars leads to a declining C abundance at late times.
@@
     \caption[C yields delay time distribution]{
-    C production by \agb\ stars as a function of \ssp{} age, normalized to the total mass $M_{\rm tot}$ produced at $t=10$ Gyr.
+    C production by \agb\ stars as a function of \ssp{} age, normalized to the total mass $M_{\rm tot}$ produced at $t=10$\,Gyr.
 Left: The four \agb\ yield models from literature at solar metallicity (\cxi, \kx{}, \vxiii{}, or \kxvi{}).
-The delay time distribution of type Ia supernovae ($\propto t^{-1.1}$) is plotted as a dashed black line for comparison.
+The \gls{dtd} of type Ia supernovae ($\propto t^{-1.1}$) is plotted as a dashed black line for comparison.
 Right: The \cxi\ \agb\ model at different metallicities.
@@
 While Equation \ref{eq:z_eq} can be applied to \cc\ C, the delayed nature of \agb\ C can complicate the expression.
-Instead, I use an effective yield, which can be expressed as an integral over the delay time distribution,
+Instead, I use an effective yield, which can be expressed as an integral over the \gls{dtd},
 \begin{equation}
@@
 From regression analysis, I suggest here that
-\begin{equation}
+\begin{equation}\label{eq:zeta}
     \Ycc = 0.0028 + \zeta\left(\frac{Z}{Z_\odot}\right),
@@
 \end{equation}
-$\tau_\text{rise}=2$ Gyr describes when the star formation rate reaches a maximum, and $\tau_{\rm sfh}$ describes the decay timescale of star formation as a function of radius $R$.
+$\tau_\text{rise}=2$\,Gyr describes when the star formation rate reaches a maximum, and $\tau_{\rm sfh}$ describes the decay timescale of star formation as a function of radius $R$.
 \JJ~derives $\tau_{\rm sfh}(R)$ through analysis of four integral field spectroscopy surveys in \cite{sanches20}.
@@
 
-\citet{james+23} compare their model against the \cite{vincenzo+21} sample of \apogee{} \citep{apogee17} \gls{rgb} C and N abundance have been corrected for mixing process using MESA stellar evolution models.
+\citet{james+23} compare their model against the \cite{vincenzo+21} sample of \apogee{} \citep{apogee17} \gls{rgb} C and N abundance have been corrected for mixing process using \textsc{mesa} stellar evolution models \citep{mesa}.
 I instead use the \citetjack~sample of \apogee{} \gls{subgiant}s.
 Subgiant stars have not undergone first dredge up but have well mixed atmospheres, so their atmospheric C and N abundances are still reflective of their birth abundances and do not need mixing corrections.
-I additionally only compare the models to the low-$\alpha$ sequence.
+I additionally only compare the models to the \gls{lowalpha} sequence.
 The selection criteria and differences between the samples are described in more detail in Appendix \ref{sec:jack}.
@@
 Comparing [C/Mg] against [Mg/Fe] enables us to see the late-time evolution of C more clearly.
-Because of the extended delay time distribution of \ia\ enrichment, [Fe/H] takes longer to reach equilibrium as half of Fe production comes from type-Ia supernovae, and the late time evolution is not as clustered as [Mg/H].
+Because of the extended \gls{dtd} of \ia\ enrichment, [Fe/H] takes longer to reach equilibrium as half of Fe production comes from type-Ia supernovae, and the late time evolution is not as clustered as [Mg/H].
 The evolution proceeds as follows.
@@
 This is even more evident in the lower panel of Fig.~\ref{fig:c_evo}.
-While the \caah\ trend reaches equilibrium at \about{5} Gyr, the \caafe\ trend continues to evolve even until the present day, exposing the effect of the relative delay times of \agb\ stars and \ia.
+While the \caah\ trend reaches equilibrium at \about{5}\,Gyr, the \caafe\ trend continues to evolve even until the present day, exposing the effect of the relative delay times of \agb\ stars and \ia.
 
@@
 
-One source of theoretical uncertainty in this result is that the \ia\ yield and delay time distributions have their own uncertainties.
+One source of theoretical uncertainty in this result is that the \ia\ yield and \gls{dtd}s have their own uncertainties.
 I discuss variations in $y_{\rm Fe}^{\rm Ia}$ in Appendix \ref{sec:alt_agb}, and find that the qualitative conclusions are largely unaffected.
-I therefore focus on the choices of $y_{\rm Fe}^{\rm Ia} = 0.00214$ and a $\propto t^{-1.1}$ delay time distribution choices from the fiducial model here.
+I therefore focus on the choices of $y_{\rm Fe}^{\rm Ia} = 0.00214$ and a $\propto t^{-1.1}$ \gls{dtd} choices from the fiducial model here.
 In short, the scaling of the trend and metallicity dependence of C (as seen in
@@
 	\label{tab:alpha_agb}
-	\begin{tabular}{lcr} % four columns, alignment for each
+	\begin{tabular}{ccr} % four columns, alignment for each
 		\toprule 
@@
         \midrule
-		C11 & 0.000347 & 2.9\\
-		K10 & 0.000585 & 1.7\\
-		V13 & 0.000060 & 16.5\\
-		K16 & 0.000421 & 2.4\\
+        \cxi & 0.000347 & 2.9\\
+        \kx & 0.000585 & 1.7\\
+        \vxiii & 0.000060 & 16.5\\
+        \kxvi & 0.000421 & 2.4\\
 		\bottomrule
@@
 
-Here, I consider a "lateburst" model, created by multiplying our fiducial "inside-out" \sfh{} with a Gaussian.
+Here, I consider a "late-burst" model, created by multiplying our fiducial "inside-out" \sfh{} with a Gaussian.
 \begin{equation}\label{eq:lateburst}
-    \dot{\Sigma}_{\rm lateburst} \propto \dot{\Sigma}_{\rm insideout} \left(1 + A e^{-(t-\tau_{\rm burst})^2/2\sigma^2_{\rm burst}} \right)
-\end{equation}
-
-$A=1.5$ represents the amplitude of the birth, $\tau_\text{burst}=10.8$Gyr is the time where the burst is strongest, and $\sigma_\text{burst}=1$Gyr is the width of the burst.
-
-I also consider an earlyburst model as a slight variation of the lateburst, where the burst is instead exponential and placed at $t_1=5$ Gyr. 
+    \dot{\Sigma}_{\rm late-burst} \propto \dot{\Sigma}_{\rm insideout} \left(1 + A\,e^{-(t-\tau_{\rm burst})^2/2\sigma^2_{\rm burst}} \right)
+\end{equation}
+
+$A=1.5$ represents the amplitude of the birth, $\tau_\text{burst}=10.8$\,Gyr is the time where the burst is strongest, and $\sigma_\text{burst}=1$\,Gyr is the width of the burst.
+I also consider an earlyburst model as a slight variation of the late-burst, where the burst is instead exponential and placed at $t_1=5$\,Gyr. 
 \begin{equation}\label{eq:twoinfall}
@@
 \begin{cases}
-    Ae^{-(t-t_1)/\tau_{\rm burst}} & t_1 < t \\
+    A\,e^{-(t-t_1)/\tau_{\rm burst}} & t_1 < t \\
       0 & t<t_1
@@
 \end{equation}
-where I take the burst duration, $\tau_{\rm burst}=1$ Gyr in this case. 
+where I take the burst duration, $\tau_{\rm burst}=1$\,Gyr in this case. 
 This approximately corresponds to the Gaia-Encelidus merger, inducing higher star formation in the Milky Way \citep{spitoni21, bonaca20, helmi18}.
@@
 Changes to the \sfh{} leave \caah\ unchanged, but they do introduce slight variation in \caafe.
-Models with higher \agb{} fractions are more sensitive to variations in \sfh{}.
-The late burst models result in [C/Mg] continuing to increase at low [Mg/Fe], but also introduce a break not present in the data.
+Models with higher \agb{} fractions are more sensitive to variations in the \sfh{}.
+The late burst models result in [C/Mg] continuing to increase at low [Mg/Fe], but also introduce a dip not present in the data.
 Additionally, the early burst
 is able to reproduce the slight break between the low and high $\alpha$ sequences, but overshoots equilibrium more severely than the fiducial model. 
-The choice of \sfh{} does not change the large-scale slope of \caafe~significantly, so variations of \sfh{} only have minimal effect on my conclusions.
+In general, any of these \sfh{}s are consistant with this model.
 
@@
 
-\gce{} models of the Milky Way fall into two classes---those which incorporate significant mass-loading (e.g., as in this work) and those which neglect mass-loading but lower effective yield to match observed abundances \citep{MCM13, MCM14, spitoni19, spitoni20, spitoni21}.
-An increase in stellar yields has a nearly identical effect as a decrease in the mass-loading factor $\eta$ (see Appendix B of \cite{james_dwarf}).
+\gce{} models of the Milky Way fall into two classes---those which incorporate significant mass-loading (e.g., as in this work) and those which neglect mass-loading but lower effective yield to match observed abundances \citep[e.g.][]{MCM13, MCM14, spitoni19, spitoni20, spitoni21}.
+An increase in stellar yields has a nearly identical effect as a decrease in the mass-loading factor $\eta$ (see Appendix B of \citealt{james_dwarf}).
 The equilibrium arguments discussed in section \ref{sec:equilibrium} suggest however that abundance ratios are independent of the choice of normalization and the value of $\eta$.
@@
 
+Fig.~\ref{fig:eta} shows models with variations of the mass loading stength.
+While changing the value of $\eta$ affects the metallicity distribution of stars, all of the models in Fig.~\ref{fig:eta} still evolve along the same path.
+Our model is unable to tell apart a uniform decrease in both outflows and yields.
+
 \begin{figure}[htp]
@@
     \includegraphics{eta.pdf}
-
-\caption[Reduced-outflow models]{Same as Fig.~\ref{fig:agb_sims} but comparing the fiducial model to reduced outflow models (see section  \ref{sec:outflows}).}
+    \caption[Reduced-outflow models]{Same as Fig.~\ref{fig:agb_sims} but comparing the fiducial model to reduced mass loading models (see section  \ref{sec:outflows}).}
+    \label{fig:eta}
 \end{figure}
@@
 Some of the scatter is due to radial migration, but observational errors are dominant.
-Precision abundance measurements will allow tighter constraints on chemical yields.
+Precision abundance measurements will allow tighter constraints on relative yields.
 
@@
     \caption[Scatter agreement]{The stars in the fiducial model in the \caah~plane perturbed by the median [Mg/H] and [C/Mg] measurment errors in the \citetjack~sample.
-Stars are color-coded such that lighter colors represent populations born at greater galactocentric radii
+Stars are color-coded such that lighter colors represent populations born at greater galactocentric radii.
     }
@@
 
-As an additional test of the model, I next compare the gas-phase predictions against gas-phase C data.
-In Fig.~\ref{fig:gas_phase}, I plot our fiducial model's gas phase predictions compared to observations of MW and extragalactic HII regions, halo stars, and \dla\ systems.
-The model is broadly consistent with observations, where the model at $t=2$ Gyr approximates the slope of dwarf galaxies and halo stars.
+As an additional test of the model, I next compare the model predictions against gas-phase measurments.
+Fig.~\ref{fig:gas_phase} shows the fiducial model's gas phase predictions compared to observations of MW and extragalactic HII regions, halo stars, and \dla\ systems.
+The model is broadly consistent with observations, where the model at $t=2$\,Gyr approximates the slope of dwarf galaxies and halo stars.
 The increase of C/O at late times is also consistent with the high C/O abundances measured in extragalactic HII regions.
-My model does not extend to very low metallicity, where the trend reverses, but broadly explains observations above $\rm [O/H] \sim -1$.
+My model does not extend to very low metallicity, where the slope of the trend inverts, but broadly explains observations above $\rm [O/H] \gtrsim -1$.
 
@@
 However, I use O abundances for gas-phase measurements and low-metallicity stars (section  \ref{sec:gas}).
-I model both Mg and O as metallicity-independent population-averaged yields dominated by massive stars.
-${\rm [O/Mg]}\approx 0$ across a wide range of metallicities in \apogee{} \citep{weinberg+19, weinberg+22}.
-I adopt O and Mg relative yields given by the solar mixture of \cite{asplund+09}.
-
-C/O gas-phase measurements are hard.
+While I use Mg as the representativve \gls{alpha} for stellar abundances, I instead us O when comparing gas-phase abundances.
+
+Measurments of C abundances in the gas-phase are challenging.
 In HII-regions, C/O abundance ratios are measured with either recombination lines or collisionally excitation lines.
 However C lacks strong collisional excitation lines, and recombination lines fall in the ultraviolet without nearby reference H lines \citep{skillman+20}.
-Additionally, recombination and collisionally excitation measurements disagree by a factor of \about{2} \cite{GR07}.
-Additional to measurement errors, variations in \sfh{} may explain the scatter, as C contains delayed enrichment, and bursts cause variations in C/O.
-
-The decreasing [C/O] abundance at very-low metallicities is likely due to population III stellar yields \citep[e.g.][]{hirschi07}, as suggested by \citep{cooke+17, FN15}.
-As \agb\ stars do have a significant delay, these stars cannot explain the increase in C yields at low metallicity as the timescales to reach $\rm [O/H]\sim -1$ is faster than this enrichment can occur.
-So, enhanced C due to (rotating) massive population III stars at low metallicities explains this trend.
-
-\begin{figure}[htp]
-    %\includegraphics{nitrogen.pdf}
+Additionally, recombination and collisionally excitation measurements disagree by a factor of \about{2} \citep{GR07}.
+Additionally, variations in the \sfh{}s may be a source of scatter, as C contains delayed enrichment, and bursts cause variations in C/O.
+
+The decreasing [C/O] abundance at very-low metallicities is likely due to population III stellar yields \citep[e.g.][]{hirschi07}, as suggested by \citet{cooke+17} and \citet{FN15}.
+\agb\ stars cannot explain the increase in C yields at low metallicity in the \dla{} sample as the evolutionary timescales of \dla{}s are shorter than the typical delay time distribution of \agb\ stars.
+
+\begin{figure}[htp]
+    \centering
     \includegraphics{c_n.pdf}
@@
 \includegraphics[]{summary.pdf}
-\caption[Gas phase abundances]{Gas-phase C abundances. We plot our model at $t=2$Gyr and present day as thick solid lines. Points represent measurements in 
+\caption[Gas phase abundances]{Gas-phase C abundances. We plot our model at $t=2$\,Gyr and present day as thick solid lines. Points represent measurements in 
     HII regions    \citep[pink circles;][]{skillman+20, esteban+02, esteban+09, esteban+14, esteban+19}
-    \dla\ systems \citep[blue triangles;][]{ellison+10, srianand+10, dutta+14, DZ+03, pettini+08, morrison+16,cooke+17}  % a1: Cooke et al.
+    \dla\ systems \citep[blue triangles;][]{ellison+10, srianand+10, dutta+14, DZ+03, pettini+08, morrison+16,cooke+17},  % a1: Cooke et al.
 (2015); 2: Dutta et al.
@@
 (2003)
-    Milky Way halo and thick disk stars \citep[green stars;][]{nissen+14, fabbian+09}. 
-    dwarf galaxies \citep[red diamonds;]{berg+19},
-    and Milky Way high-$\alpha$ stars (yellow points; \citealtjack)
+    dwarf galaxies \citep[red diamonds;][]{berg+19},
+    Milky Way halo and thick disk stars \citep[green stars;][]{nissen+14, fabbian+09},
+    and Milky Way \gls{highalpha} stars (yellow points; \citealtjack).
 }
@@
 \renewcommand{\thesection}{A.\arabic{section}}
-\renewcommand\thefigure{A\arabic{figure}}    
-\renewcommand\theequation{A\arabic{equation}}    
+\renewcommand\thefigure{A.\arabic{figure}}    
+\renewcommand\theequation{A.\arabic{equation}}    
 \setcounter{figure}{0}
@@
 
+\renewcommand*{\theHsection}{A.\arabic{section}}%
+\renewcommand*{\theHsubsection}{A.\arabic{subsection}}%
+\renewcommand*{\theHfigure}{A.\arabic{figure}}%
+\renewcommand*{\theHequation}{A.\arabic{equation}}%
+
 \section{The APOGEE Subgiant Sample}\label{sec:jack}
 
-I use the criteria outlined in \citetjack~to create a sample of \gls{subgiant}s from \apogee{} DR17 \cite{apogee17} as our primary observational constraint.
+As the primary observational constraint, I use the criteria outlined in \citetjack~to create a sample of \gls{subgiant}s from \apogee{} DR17 \citep{apogee17}.
 \apogee\ is part of the Sloan Digital Sky Survey 17 and measures high resolution spectra of thousands of stars \cite{sdss17}.
-Subgiants are reflective of birth abundances for CNO \citep{souto19}.
-with chemical abundance determinations from the \apogee\ Stellar Parameter and Chemical Abundance Pipeline ({\sc aspcap}) \citep{aspcap}.
-\citetjack~select a region of stars in $\log g$-$T_\text{eff}$ space described by the following polyhedron
+Chemical abundance are determined from the \apogee\ Stellar Parameter and Chemical Abundance Pipeline ({\sc aspcap}) \citep{aspcap}.
+
+Photospheric C and N abundances in \gls{subgiant}s are reflective of their birth abundances \citep{gilroy89, korn+07, lind+08, souto+18, souto19} As \gls{fdu}, which affects C and N abundances, only occurs during the ascent onto the \gls{rgb}, \gls{subgiant} stars are unaffected by this enrichment.
+
+An alternate approach for this analysis would be to estimate the birth abundances of \gls{rgb}s by correcting surafe abundance effects from \gls{fdu} as in \cite{vincenzo+21}.
+Subgiants are the more attractive option since these observations do not rely on model-dependent corrections.
+However, \gls{rgb}s are more luminous, potentially allowing better coverage of the Galactic disk, which may make this a better approach depending on the application.
+
+I choose to use \citetjack's sample as this does not rely on additional layers of modeling, providing a more direct constraint to our model and limiting our systematic uncertainties.
+
+Fig.~\ref{fig:subgiant_selection} shows a plot of all \apogee\ stars and the \citetjack polygon selection criterial. 
+ \citetjack~select a region of stars in $\log g$-$T_\text{eff}$ space described by the following criteria
  \begin{equation}
@@
         \log \text{g} \geq 3.5 \\
-        \log \text{g} \leq 0.004T_{\rm eff} - 15.7 \\
-        \log \text{g} \leq 0.000706T_{\rm eff} + 0.36 \\
-        \log \text{g} \leq -0.0015T_{\rm eff} + 12.05 \\
-        \log \text{g} \geq 0.0012T_{\rm eff} - 2.8 \\
+        \log \text{g} \leq 0.004\,T_{\rm eff} - 15.7 \\
+        \log \text{g} \leq 0.000706\,T_{\rm eff} + 0.36 \\
+        \log \text{g} \leq -0.0015\,T_{\rm eff} + 12.05 \\
+        \log \text{g} \geq 0.0012\,T_{\rm eff} - 2.8. \\
     \end{cases}
 \end{equation}
-
-\begin{figure}
-    \centering
-    \includegraphics{logg_jack.pdf}
-    \caption[Subgiant selection]{
-        A Kiel diagram of \apogee{} stars.
-Following \citetjack, we select \gls{subgiant}s in the orange polygon (see Equation \ref{eq:subgiant_selection}).
-These stars have not yet experienced first dredge-up, so their photospheric C and N abundances should reflect their birth mixture.
-    }
-\end{figure}
-
-This cut isolates a clean sample of \about{12,000} \gls{subgiant}s.
-As first dredge up, which affects C and N abundances, only occurs during the ascent onto the \gls{rgb}, \gls{subgiant} stars are unaffected by this enrichment.
-
 Additionally, I included stars in \apogee{} marked by the following flags.
@@
 \end{itemize}
-
-A second approach in determining birth abundances in stars is to correct the surface abundance effects of first dredge up, as in \cite{vincenzo+21}.
-I note that there is a slight difference in the yields found through \cite{vincenzo+21} and \citetjack.
-As o
-
+This cut isolates a clean sample of \about{12,000} \gls{subgiant}s.
+I furthermore isolate the low and \gls{highalpha} sequences with the cut
 \begin{equation}\label{eq:high_alpha}
 \begin{cases}
-\text{[Mg/Fe]} >0.12-0.13\text{[Fe/H]}, & \text{[Fe/H]}<0\\
-\text{[Mg/Fe]} >0.12, & \text{[Fe/H]}>0\\
+\text{[Mg/Fe]} >0.12-0.13\,\text{[Fe/H]}, & \text{[Fe/H]}<0\\
+\text{[Mg/Fe]} >0.12, & \text{[Fe/H]}>0. \\
 \end{cases}
 \end{equation}
-
-, discussion of GALAH C in \citealt{emily+19}).
-
-I choose to use \citetjack's sample as this does not rely on additional layers of modeling, providing a more direct constraint to our model and limiting our systematic uncertainties.
+The \gls{lowalpha} sequence is better reproduced by this model, so I use this cut of the subgiants to compare the models against.
+
+\begin{figure}
+    \centering
+    \includegraphics{logg_jack.pdf}
+    \caption[Subgiant selection]{
+        A Kiel diagram of \apogee{} stars.
+Following \citetjack, we select \gls{subgiant}s in the orange polygon (see Equation \ref{eq:subgiant_selection}).
+These stars have not yet experienced first dredge-up, so their photospheric C and N abundances should reflect their birth mixture.
+    }
+    \label{fig:subgiant_selection}
+\end{figure}
 
 \newpage
-\section{Additional Considerations of Yields}\label{sec:alt_agb}
-
-As I focus on constraining relative yields, I neglect O and Mg yield variations in the main text.
-There is substantial variation in Mg predictions (see Fig.~\ref{fig:y_mg}).
-Most models predict relatively flat Mg trends with metallicity (even with rotating models from \citealt{LC18}).
+\section{Stellar Evolution and C Production}
+While neglected in the main body of the paper, for reference, I include here a brief summary of the physics behind carbon production in low and high mass stars.
+
+Low mass stars ($\lesssim 8 M_\odot$, like our sun), are born when they are fusing H into He ($\isotope[1]{H}(p,\beta^{-}\gamma)\isotope[2]{H}$)
+
+\begin{subequations}\label{eq:cno_cycle}
+\begin{align}
+    \proton + \isotope[12]{C} &\longrightarrow \isotope[13]{N} + \gamma \\
+    \isotope[13]{N} &\longrightarrow  \isotope[13]{C} + \beta^+ + \nu_e  \\
+    \proton + \isotope[13]{C}  &\longrightarrow \isotope[14]{N} + \gamma\\
+    \proton + \isotope[14]{N}  &\longrightarrow \isotope[15]{O} + \gamma\\
+    \isotope[15]{O} &\longrightarrow  \isotope[15]{N} + \beta^{+} + \nu_e \\
+    \proton + \isotope[15]{N} &\longrightarrow \isotope[12]{C} + \alpha
+\end{align}
+\end{subequations}
+
+\begin{subequations} \label{eq:triple_alpha}
+\begin{align}
+    \alpha + \alpha &\longrightarrow \isotope[8][4]{Be} \\ 
+    \alpha + \isotope[8][4]{Be} &\longrightarrow \isotope[12][6]{C} + 2\gamma \\ 
+\end{align}
+
+Additionally, some \isotope[12][6]{C} may furthermore fuse into O, $\alpha + \isotope[12][8]{C} &\longrightarrow \isotope[16][8]{O} + \gamma$.
+
+\end{subequations}
+
+\newpage
+\section{Additional Notes about Yields}\label{sec:alt_agb}
+
+As I focus on constraining relative yields, I neglect O and Mg yield variations in the main text (excluding the uniform scaling of yields and \gls{massloading} in section~\ref{sec:outflows}).
+There is substantial variation in predicted Mg yields (see Fig.~\ref{fig:y_mg}).
+Most models predict relatively flat trends metallicity (even with rotation as in \citealt{LC18}).
 However, the variation is significant and my adopted $\Yoc$ yield is much higher than most models.
-This is a known problem (see \citet{emily+21}).
-\cc\ models overpredict O or underpredict Mg, and the resolution is still unknown.
-My results are, however, independent of whether the \cc\ element is O or Mg.
+This is a known problem (see \citealt{emily+21}).
+\cc\ models updrepredict $[{\rm Mg}/{\rm O}]$, and the reason why is unknown.
+My results are independent of the choice of \cc\ element as I assume $[{\rm Mg}/{\rm O}]=0$.
 
@@
     \item \texttt{astropy} \citep{astropy:2013, astropy:2018, astropy:2022}
-    \item \texttt{seaborn}
+    \item \texttt{seaborn} \citep{seaborn}
 \end{itemize}
@@
 \renewcommand*{\arraystretch}{1.25}
-
 \glsaddall[types={symbols}]
-
-\printunsrtglossary[type=symbols,nonumberlist,style=long]
+\renewcommand{\glslongextraSymDescTabularHeader}{}
+\renewcommand{\glslongextraSymDescTabularFooter}{}
+
+\printunsrtglossary[type=symbols,nonumberlist,style=long-sym-desc]
 
@@
 \printglossary[type=\acronymtype,nonumberlist]
+
 \printglossary

### 2023-05-01 thesis/tex/main.tex
david edits

@@
 counter=section,
-postpunc={.},
 stylemods={longextra}
@@
 \setabbreviationstyle[acronym]{long-short-sc}
-\GlsXtrEnablePreLocationTag{Section: }{Sections: }
+\GlsXtrEnablePreLocationTag{\S }{\S }
 
@@
 \newacronym
-[ description ={Core collapse supernovae. Massive star explosions. {\sc ccsne} produce many elements including \gls{alpha}, Fe-peak elements, and r and s-process elements.}
+[ description ={Core collapse supernovae. Massive star explosions. {\sc ccsne} produce many elements including \gls{alpha}, \gls{fepeak}, and r and \gls{sproc}.}
 ]
@@
 \newacronym
-[description={Dying low-mass stars. Produces C, N, and heavy s-process elements.}]
+[description={Asymptotic giant branch stars. {\sc agb}s are the last phase of \glspl{lowmass}, before stars become white dwarfs. Produces C, N, and heavy s-process elements. See \ref{sec:stel_evo}.}]
 {agb}{agb}{asymptotic giant branch}
@@
 \newacronym
+[description={Galactic chemical evolution.}]
 {gce}{gce}{galactic chemical evolution}
@@
 \newacronym
+[description={Star formation history.}]
 {sfh}{sfh}{star formation history}
@@
 \newacronym
-[description={Single Stellar Population. A group of stars formed all at the same time.}]
+[description={Single stellar population. A group of stars formed all at the same time.}]
 {ssp}{ssp}{single stellar population}
@@
 \newacronym
-[description={A function describing the mass distribution of newly formed stars. I use a \citet{kroupa01} {\sc imf}, which is described as a piecewise powerlaw function of $M$.}]
+[description={Initial mass function.
+A function describing the mass distribution of newly formed stars.
+I use a \citet{kroupa01} {\sc imf}, which is described as a piecewise powerlaw function of $M$.}]
 {imf}{imf}{initial mass function}
@@
 \newacronym
-[description={A large near-infrared spectroscopic survey of stars in the Milky Way.}]
+[description={
+Apache Point Observatory Galactic Evolution Experiment. 
+A large near-infrared spectroscopic survey of stars in the Milky Way. \citep{apogee17}}]
 {apogee}{apogee}{Apache Point Observatory Galactic Evolution Experiment}
@@
 \glsxtrnewsymbol
-[description = {The abundance ratio between elements $A$ and $B$. See }]
+[description = {
+    The abundance ratio between elements $A$ and $B$. $[A/B] =
+    \log_{10}\left(A/B\right) - \log_{10}\left(A_{\sun}/B_{\sun}\right)$, i.e.
+    $[A/B]$ is the logarithm of the ratio between A and B, scales such that
+    $[A/B]=0$ for the sun. Solar abundances are as measured in
+    \citet{asplund+09}.
+}]
 {abundratio}{\ensuremath{[A/B]}}
@@
 \glsxtrnewsymbol
-[description = {The massive star carbon yield metallicity dependence. See Eq.~\ref{eq:zeta}}]
+[description = {The high-mass star carbon yield metallicity dependence. See Eq.~\ref{eq:zeta}}]
 {zeta}{\ensuremath{\zeta}}
@@
 \glsxtrnewsymbol
-[description = {The rate of star formation.}]
+[description = {The rate of star formation (mass of new stars per time interval).}]
 {sfr}{\ensuremath{\dot{M}_\star}}
@@
 \glsxtrnewsymbol
-[description = {The fractional contribution of AGB stars to the total \gls{imfave} carbon yield at solar metallicity.}]
+[description = {The rate of change of the mass of element $X$.}]
+{mdotx}{\ensuremath{\dot{M}_{\rm X}}}
+
+\glsxtrnewsymbol
+[description = {The fractional contribution of AGB stars to the total \gls{imfave} carbon yield at solar metallicity. See Eq.~\ref{eq:f_agb}}]
 {fagb}{\ensuremath{f_{\rm AGB}}}
@@
 \glsxtrnewsymbol
-[description = {The net fraction initial-mass-function weighted low-mass star yield of carbon}]
+[description = {The galactocentric radius---distance from the galactic center in kpc.}]
+{Rgal}{\ensuremath{R}}
+
+\glsxtrnewsymbol
+[description = {The per-star yield of C from \glspl{lowmass} of a given mass. In otherwords, the amount of new C an \agb\ star ejects divided by the initial mass of the star.}]
 {ytcagb}{\ensuremath{\tilde{y}_{\rm C}^{\rm AGB}}}
@@
 \glsxtrnewsymbol
-[description = {The net fraction initial-mass-function weighted low-mass star yield of carbon}]
+[description = {The \gls{imfave} yield of C from \glspl{lowmass}.}]
 {ycagb}{\ensuremath{y_{\rm C}^{\rm AGB}}}
@@
 \glsxtrnewsymbol
-[description = {The net fraction initial-mass-function weighted massive star yield of carbon}]
+[description = {The \gls{imfave} yield of C from \glspl{highmass}.}]
 {ycc}{\ensuremath{y_{\rm C}^{\rm CC}}}
@@
 \glsxtrnewsymbol
-[description = {The net fraction initial-mass-function weighted massive star yield of magnesium}]
+[description = {The \gls{imfave} yield of Mg.}]
 {ymg}{\ensuremath{y_{\rm Mg}^{\rm CC}}}
@@
 \glsxtrnewsymbol
-[description = {The metallicity for the sun}]
+[description = {The metallicity for the sun. $Z_\odot=0.014$. }]
 {zsun}{\ensuremath{Z_\odot}}
@@
 \glsxtrnewsymbol
-[description = {The metallicity fraction}]
+[description = {The metallicity fraction, i.e. the mass fraction of all elements which are not H or He. }]
 {Z}{\ensuremath{Z}}
@@
 \glsxtrnewsymbol
-[description = {A nuclear reaction.
-The initial element is $X$, and (optionally) some particle $a$ collides with $X$, and particles $b$ are then released.
-The next isotope symbol is the result of the reaction.}]
-{nuclrxn}{\ensuremath{X(a,b)}}
+[description = {The mass fraction of element $X$.}]
+{Zx}{\ensuremath{Z_X}}
 
@@
 \newglossaryentry{metallicity}{name={metallicity},
-    description={the (mass) fraction of a star or gass which is not made of either hydrogen or helium. For the sun, the metallicity is $\Zo = 0.014$}
+    description={the (mass) fraction of a star or gass which is not made of either H or He. For the sun, the metallicity is $\Zo = 0.014$}
 }
@@
 \newglossaryentry{nucleosynthesis}{name={nucleosynthesis},
-    description={the synthesis of new elements inside stars}
-}
-
-\newglossaryentry{yield}{name={yield},
-    description={the synthesis of new elements inside stars}
+    description={The synthesis of new elements through fusion inside stars. See section \ref{sec:stel_evo}.}
 }
@@
 \newglossaryentry{rgb}{name={red giant branch},
-    description={Red giant branch stars are stars which have completed hydrogen core burning and have expanded in size.}
+    description={Red giant branch stars are stars which have completed hydrogen core burning and have expanded in size. See appendix \ref{sec:stel_evo}.}
 }
@@
 During each thermal pulse, material is {\it dredged up} from the core, changing the chemical abundances of the stellar atmosphere.
-(While nominally called {\it third dredge up}, there are typically several third dredge ups.) }
+(While nominally called {\it third dredge up}, there are typically several third dredge ups.).
+See appendix \ref{sec:stel_evo}.}
 }
@@
 \newglossaryentry{fdu}{name={first dredge up},
-    description={Third dredge up occurs when ....}
+    description={First dredge up occurs when a \gls{lowmass} enters the \gls{rgb} phase.
+Material from the core is brought to the surface, increasing N and decreasing C abundances.
+See appendix \ref{sec:stel_evo}.}
 }
@@
 \newglossaryentry{hbb}{name={hot bottom burning},
-    description={Third dredge up occurs when ....}
+    description={Hot bottom burning occurs inside \agb\ stars. The base of the convective envelope becomes hot enough for CNO burning to initiate.}
 }
@@
 \newglossaryentry{subgiant}{name={subgiant},
-    description={A subgiant is...}
+    description={A subgiant is a star which is starting to become a \gls{rgb} star.}
 }
@@
 \newglossaryentry{imfave}{name={\gls{imf}-averaged},
-    description={Initial-mass function ....}
+    description={Averaged over the initial-mass function ({\sc imf}).
+The {\imf}-weighted yield is the mass of the newly produced element divided by the mass of star formation for a single stellar population (see \ssp).}
 }
@@
 \newglossaryentry{massloading}{name={mass loading},
-    description={The stength of outflows.}
+    description={The stength of outflows. See also $\gls{eta}$. }
 }
@@
 
+\newglossaryentry{lowmass}{name={low-mass star},
+    description={Low-mass stars are stars with masses $\lesssim 8\,M_\odot$ which end life as a white dwarf. }
+}
+
+\newglossaryentry{highmass}{name={migh-mass star},
+    description={Stars with masses $\lesssim 8\,M_\odot$, which end as a neutron star, black hole, or supernovae.}
+}
+
 \newglossaryentry{cno}{name={CNO cycle},
     description = { A proton-fusion cycle which occurs in \gls{rgb} stars 
-        consisting of a chain of proton captures releasing a helium nucleus ($\alpha$-particle) and energy. See Eq.~\ref{eq:cno_cycle}.
+        consisting of a chain of proton captures releasing a He nucleus ($\alpha$-particle) and energy. See Eq.~\ref{eq:cno_cycle}.
 }
@@
 % results
-By matching the slopes of the \caah\ and \caafe\ relationships in a sample of APOGEE subgiant stars, I find that massive stars and low mass stars contribute \about{80\%} and \about{20\%} of total C production respectively.
+By matching the slopes of the \caah\ and \caafe\ relationships in a sample of APOGEE subgiant stars, I find that high-mass and low-mass stars contribute \about{80\%} and \about{20\%} of total C production respectively.
 % 
@@
 
-I know I am guilty of skimming the acknowledgements of many works, but I dearly hope that the people who helped me complete this project will appriciate how much they have helped me.
+I dearly hope that the people who helped me complete this project will appreciate how much they have helped me.
 This year has been an incredibly challenging journey---and perhaps I am not open enough about what it has been like.
-I genuinly would have not made it to this day without everyones help, one way or another.
+I undoubtedly would not have reached this day without everyone's help.
 
 James Johnson---your mentorship and guidance throughout this project was critical. 
-You helped me learn an incredible amount about being an astronomer, and I am forever greatful for how you have guided this project, through late nights and last minute comments.
+You helped me learn an incredible amount about being an astronomer, and I am forever grateful for how you have guided this project, through late nights and last minute comments.
 Wayne, for everything you do for everyone---you are the glue holding together our department and nobody can say thank you enough.
 David and Jennifer for helping this project move forward, by providing guidance at critical junctions and being part of my committee.
-Rolando, for being the non-astronomer thrown into this work, and pointing out the flaw of incomprehensability in this work.
-
-Even though you may have not been able to help me with the science, dear friends and family, you have been no less importaint in the completion of this work. 
+Rolando, for being the non-astronomer thrown into this work, and pointing out the flaw of incomprehensibility in this work.
+
+Even though you may have not been able to help me with the science, dear friends and family, you have been no less important in the completion of this work. 
 Eric, even across the country, you have always been a point of support and stability, and I am always happy to be around you.
@@
 All my friends who are just wonderful, inspiring, and incredible people---Kaia, Maria, Autumn, Simon, Bailee, Aaliyah, Sanskruti, Alyssa, Harrison, Denis, Keith, and so many others. 
-And my family (including Arya, my most lovable doodle)---I can not eveen being to thank you enough for simply helping me recover my health and make it to graduation.
+And my family (including Arya, my most lovable doodle)---I can not even being to thank you enough for simply helping me recover my health and make it to graduation.
 
@@
 \Gce{} aims to understand the chemical and star formation histories of galaxies.
-At the core of \gce{} models are stellar \gls{yield}s---the amount of each chemical element stars produce (or destroy).
+At the core of \gce{} models are stellar yields---the amount of each chemical element stars produce (or destroy).
 Each element is produced in different amounts by different stars, leaving traces of the Galaxy's evolutionary history.
@@
 The production rates of elements in stars are shaped by poorly understood processes, including mass loss, opacity, nuclear reaction rates, rotational mixing, and convection \citep{KL14,ventura+13, LC18}.
-Changes in massive stars' explodability also introduce further variation and uncertainty in population-averaged yields \citep{emily+21}.
+Changes in \gls{highmass}' explodability also introduce further variation and uncertainty in population-averaged yields \citep{emily+21}.
 
@@
 I focus on three primary nucleosynthetic pathways: \agb{} stars, \cc{}, and \ia.
-Each process has unique timescales and \gls{yield}s, traceable through the tools of \gce.
-I compare C, produced in \cc{} and \agb\ stars, to Mg and Fe as tracers of \cc{} and \ia{} espectively.
+Each process has unique timescales and yields, traceable through the tools of \gce.
+I compare C, produced in \cc{} and \agb\ stars, to Mg and Fe as tracers of \cc{} and \ia{} respectively.
 
 When a \ssp~forms, \cc{} are the first enrichment event.
-\cc{}  explode within $\lesssim 40$ Myr, providing light elements (C, O, and Mg) and heavier elements (Fe and beyond).
+\cc{}  explode within $\lesssim 40$\,Myr, providing light elements (C, O, and Mg) and heavier elements (Fe and beyond).
 Metallicity-independent yields from \cc{} are the only statistically significant source of O and Mg ($\alpha$ elements).
@@
 
-For an element X and star with mass $M$, the stellar yield $\tilde{y}$ is defined as the net production of X relative to $M$, or
+For an element X and star with mass $M$, the net-fractional-stellar yield $\tilde{y}$ is defined as the net production of X relative to $M$, or
 \begin{equation}
@@
 where $M_{\rm ejected}$ and $M_{\rm X, ejected}$  are the total ejected mass of the envelope and the element X, respectively.
-For example, if a 1 $M_\odot$ star has $\tilde{y}_{\rm C} = 10^{-3}$, then the star will add $10^{-3}\ M_\odot$ of C to the interstellar medium.
+For example, if a 1 $M_\odot$ star has $\tilde{y}_{\rm C} = 10^{-3}$, then the star will add $10^{-3}\ M_\odot$ of new C to the interstellar medium.
 Although per-star yields are necessary to compute \agb{} star enrichment rates in \gce{}  models, \gls{imfave} yields are useful in interpreting their predictions.
@@
 \begin{equation} \label{eq:imf-yield}
-    y_{\rm X}(Z) = 
-    \int_{M_{\rm min}}^{M_{\rm max}} 
+    y_{\rm X}(Z,t) = 
+    \int_{M_{\rm min}(t)}^{M_{\rm max}} 
     \tilde{y}_{\rm X}(M, Z)
@@
 \end{equation}
-where ${dN}/{dM}$ is the normalized \imf, and $M_{\rm min}$ and $M_{\rm max}$ are the minimum and maximum mass of stars, which I take to be $0.08 M_{\sun}$ and $100 M_{\sun}$ respectively.
+where ${dN}/{dM}$ is the normalized \imf, $M_{\rm max}=100\,M_\odot$ is the maximum stellar mass, and $M_{\rm min}(t)$ is the minimum mass of stars which die before time $t$.
 For \agb{} stars, the yields are truncated above 8 $M_{\odot}$.
-To calculate the \imf-weighted net yields, I use the Versatile Integrator for Chemical Evolution code (\VICE\footnote{\VICE~is available at \url{https://github.com/giganano/VICE}}).
+To calculate the \gls{imfave} net yields, I use the Versatile Integrator for Chemical Evolution code (\VICE\footnote{\VICE~is available at \url{https://github.com/giganano/VICE}}).
 
@@
 
-\begin{figure}[htp]
-    \includegraphics[width=\textwidth]{periodic_table.png}
-    \caption{The periodic table of elements. Taken from \cite{jennifer19}.}
-\end{figure}
-
 \section{Asymptotic Giant Branch Stars}\label{sec:agb}
 
-An \agb\ star is a low mass ($\lesssim 8 M_{\sun}$) star during its final phase of evolution.
+An \agb\ star is a \gls{lowmass} ($\lesssim 8 M_{\sun}$) during its final phase of evolution (see appendix \ref{sec:stel_evo}).
 In an \agb\ star, two competing processes determine the outcome of C production: \gls{tdu} and \gls{hbb}.
@@
     \item \vxiii: \citet{ventura+13,ventura+14,ventura+18, ventura+20}
-    \item \kxvi: \citet{KL16} \citet{karakas+18}
+    \item \kxvi: \citet{KL16, karakas+18}
 \end{itemize}
-I use \cxi table, amplified by a factor of 2.9, as the fiducial \agb\ yield.
+For my models to match observations, I find I need to uniformly amplify these yield tables (see Eq.~\ref{eq:alpha}). I use \cxi\ table, amplified by a factor of 2.9, as the fiducial \agb\ yield.
 
@@
 As the mass range $2\lesssim M \lesssim 4$ is most important for C production, about half of C production occurs before \about{1}\,Gyr, similar to \ia\ Fe. 
-\kx{} and \kxvi{} weight C production more heavily towards massive stars resulting in a faster enrichment delay time, whereas the \cxi\ and \vxiii\ models predict a slightly longer timescale of \about{1}\,Gyr, but little to no C is produced more than 2\,Gyr after a star formation event.
+\kx{} and \kxvi{} weight C production more heavily towards \gls{highmass}s resulting in a faster enrichment delay time, whereas the \cxi\ and \vxiii\ models predict a slightly longer timescale of \about{1}\,Gyr, but little to no C is produced more than 2\,Gyr after a star formation event.
 This is in contrast to Fe whos production lasts up to 10\,Gyr after a star formation event.
@@
 The black dashed line shows $\tilde{y}=0$ for reference.
-Each panel represents yields from one of four \agb\ models: \cxi, \kx{}, \vxiii{}, \kxvi{} (see section \ref{sec:agb}).
+Each panel represents yields from one of four \agb\ models: \cxi, \kx{}, \vxiii{}, \kxvi{} (see section \ref{sec:agb}) and \ref{sec:oob_models}.
 }
@@
     \caption[Low mass yield metallicity dependence]{The net fractional \imf-weighted \agb\ C yield $\Ycagb$ as a function of metallicity for each of our \agb\ yield models.
+$\Ycagb$ is the net mass of C produced by \agb\ stars per unit mass of star formation, after 10\,Gyr and assuming a \citet{kroupa01} \imf.
     }
@@
 Rotation induces more mixing allowing the CO core to grow larger.
-Our fiducial model's steep metallicity dependence near $Z\approx Z_\odot$ could be explained by rotation.
+As I will later show, \cc\ C production needs to be strongly metallicity-dependent at $Z/Z_\odot \approx 1$, which is consistant with the \cite{LC18} rapidly rotating models.
+
 Fig.~\ref{fig:y_cc} shows the \cxi{} model for comparison on the top.
@@
 I will later also show empirically that \cc{} should dominate C production.
-
 On the bottom of Fig.~\ref{fig:y_cc}, I also show the \cc{}-[C/Mg] ratio, defined by
@@
 However, C is relatively unaffected by the black-hole landscape, as very massive stars contribute C through enriched winds.
-Since Mg is formed deeper in the core of massive stars, the Mg yield drops much more steeply, so models, where few stars explode (S16/W18), result in much higher [C/Mg].
+Since Mg is formed deeper in the core of \gls{highmass}s, the Mg yield drops much more steeply, so models, where few stars explode (S16/W18), result in much higher [C/Mg].
 
@@
     \caption[Massive star C yields]{
-        C yields from massive stars.
+        C yields from high-mass stars.
         \textbf{Top:} The \imf-weighted \cc\ yield of C as a function of metallicity.
-        \textbf{Bottom:} The \cc\ [C/Mg] abundance ratio, defined in Eq.~\ref{eq:c_mg_cc}. The black line represents the C yield of the fiducial model,
+        \textbf{Bottom:} The \cc\ [C/Mg] abundance ratio, defined in Eq.~\ref{eq:c_mg_cc}. The black line is the derived C yield from section \ref{sec:equilibrium},
     $\Ycc = 0.0028 + 0.001 (Z/Z_{\odot})$. Yields are shown for tables from 
@@
 \citet{sukhbold+16} report yields for different black hole landscapes, while \citet{LC18} provide yields at different rotational velocities.
-    In the top panel, the pink line denotes $\Ycagb$ from \cxi{} for comparison.
+    In the top panel, the pink line denotes $\Ycagb$ from \cxi{} for comparison. All models include wind yields.
 }
@@
 \end{equation}
-where $\tau_{\star}$ is the star formation rate.
+where $\tau_{\star}$ is the star formation rate. $\eta$ depends on $R$, as 
 In the special case of constant star formation, $\tau_{\rm sfh}\to\infty$, the denominator simplifies to $1+\eta-r$.
 
-While Equation \ref{eq:z_eq} can be applied to \cc\ C, the delayed nature of \agb\ C can complicate the expression.
-Instead, I use an effective yield, which can be expressed as an integral over the \gls{dtd},
-\begin{equation}
-    \langle \Ycagb\rangle = \frac{\int_0^T \tilde{y}_{\rm C}^{\rm agb}(M, Z) \dot{M}_\star(T - t) \frac{dN}{dM} \frac{dM}{dt} dt  }{ \dot{M}_\star \int_0^T \frac{dN}{dM} \frac{dM}{dt} dt}.
-\end{equation}
+For \agb\ stars, the above equation is more complex in detail, as the \agb\ contribution depends on the \sfh.
+However, for an exponential decay, this effect is minimal, so I simply use $\Ycagb$ for the current \agb\ contribution.
 Eq.~\ref{eq:z_eq} then becomes
 \begin{equation}
-    Z_{\rm C}^{\rm eq}(R) = \frac{\Ycc + \langle\Ycagb\rangle}{1 + \eta(R) - r - \tau_\star / \tau_{sfh}}
+    Z_{\rm C}^{\rm eq}(R) = \frac{\Ycc + \Ycagb}{1 + \eta(R) - r - \tau_\star / \tau_{sfh}}
 \end{equation}
@@
 \begin{equation}\label{eq:z_co}
-    \frac{Z_{\rm C}^{\rm eq}}{Z_{\rm Mg}^{\rm eq}} = \frac{\Ycc + \langle \Ycagb \rangle }{\Yoc}.
+    \frac{Z_{\rm C}^{\rm eq}}{Z_{\rm Mg}^{\rm eq}} = \frac{\Ycc + \Ycagb }{\Yoc}.
 \end{equation}
@@
 \begin{equation}\label{eq:y_c_eq}
-    \frac{\Ycc}{\Yoc} = \frac{Z_{\text{C},~\odot}}{Z_{\text{Mg},~\odot}} 10^{\rm [C/Mg]} - \frac{\langle \Ycagb \rangle}{\Yoc}.
+    \frac{\Ycc}{\Yoc} = \frac{Z_{\text{C},~\odot}}{Z_{\text{Mg},~\odot}} 10^{\rm [C/Mg]} - \frac{\Ycagb}{\Yoc}.
 \end{equation}
@@
 In section \ref{sec:f-z-models}, I will show that none of the four \agb\ yield sets (\cxi{}, \kx{}, \vxiii{}, \kxvi{}) produce enough C relative to this $\Ycc$ value.
-So, I introduce normalization factors, $\alpha_{\rm AGB}$, and $\alpha_{\rm CC}$ which denote a multiplicitave scaling of $\Ycc$ and $\Ycagb$ respectively.
+So, I introduce normalization factors, $\alpha_{\rm AGB}$, and $\alpha_{\rm CC}$ which denote a multiplicative scaling of $\Ycc$ and $\Ycagb$ respectively.
 \begin{subequations} \label{eq:alpha}
@@
     \includegraphics[]{analytic.pdf}
-    \caption[Reverse fit yields]{Inferred massive star C yields as a function of metallicity.
+    \caption[Reverse fit yields]{Inferred high-mass star C yields as a function of metallicity.
 I assume equilibrium and $3\times {\rm C11}$ \agb\ yields (orange curve, see discussion in Section \ref{sec:equilibrium}).
-The binned medians and median absolute deviation (divided by $\sqrt{N}$) are blue points.
+Blue points are the median value of $\Ycc$ for each bin in [Mg/H] with uncertainties based on the median absolute deviation.
     }
@@
 Subgiant stars have not undergone first dredge up but have well mixed atmospheres, so their atmospheric C and N abundances are still reflective of their birth abundances and do not need mixing corrections.
-I additionally only compare the models to the \gls{lowalpha} sequence.
+I only compare the models to the \gls{lowalpha} sequence unless otherwise specified.
 The selection criteria and differences between the samples are described in more detail in Appendix \ref{sec:jack}.
@@
 The fiducial model has the following qualitative characteristics of its C yields: (a) C is predominantly produced in \cc, (b) \cc\ produce more C at higher metallicities, and (c) \agb\ stars produce less C at higher metallicities.
-Our fiducial model uses the \cxi{} \agb\ yield tables (see section \ref{sec:agb}, and Table \ref{tab:fiducial_mod}), and I amplify the \cxi{} yields by a factor of 2.9 such that \agb\ stars account for 20\% of C at $Z=Z_\odot$.
+The fiducial model uses the \cxi{} \agb\ yield tables (see section \ref{sec:agb}, and Table \ref{tab:fiducial_mod}), and I amplify the \cxi{} yields by a factor of 2.9 such that \agb\ stars account for 20\% of C at $Z=Z_\odot$.
 
@@
 
+To parameterize the \agb\ contribution to C production, I define 
+\begin{equation}\label{eq:f_agb}
+    f_{\rm AGB} \equiv \frac{\Ycagb}{\Yct}\Bigg\vert_{Z=Z_\odot},
+\end{equation}
+where  $\Ycagb$ includes the multiplicative factor $\alpha_{\rm AGB}$ as defined in Eq.~\ref{eq:alpha}.
 Fig.~\ref{fig:agb_sims} compares the \kx{}, \kxvi{}, \cxi{}, and \vxiii{} yield models.
-Here, I use the published, unscaled yield tables.
+Here, I use the published, unscaled yield tables ($\alpha_{\rm AGB}=1$).
 As the highest \agb\ yield at solar, \kx{} is only $\Ycagb=0.000585$, $f_{\rm AGB} \leq 0.12$ for all models.
@@
 As discussed in section \ref{sec:equilibrium}, the \caah~trend is approximated by equilibrium, so the trends of these have steeper \caah~corresponding to steeper metallicity dependence.
-However, \caafe~is minimally affected by these changes since \cc\ occure on much shorter timescales than \ia\ and \agb\ enrichment.
-
-Now, I vary the proportion of \agb\ contribution.  The \agb\ C production fraction is defined as
-\begin{equation}
-    f_{\rm AGB} \equiv \frac{\Ycagb}{\Yct}\Bigg\vert_{Z=Z_\odot},
-\end{equation}
-where  $\Ycagb$ includes the multiplicative factor $\alpha_{\rm AGB}$ as defined in Eq.~\ref{eq:alpha}.
+However, \caafe~is minimally affected by these changes since \cc\ occurs on much shorter timescales than \ia\ and \agb\ enrichment.
+
 In the bottom panel of Fig.~\ref{fig:beta_f}, I plot three models with different \agb\ fractions while using \cxi{} yields.
@@
 is able to reproduce the slight break between the low and high $\alpha$ sequences, but overshoots equilibrium more severely than the fiducial model. 
-In general, any of these \sfh{}s are consistant with this model.
+In general, any of these \sfh{}s are consistent with this model.
 
@@
 The theoretical motivation for decreasing yields is the uncertainty in stellar explodability.
-If fewer massive stars explode, then the yields will be reduced by some factor.
+If fewer \gls{highmass}s explode, then the yields will be reduced by some factor.
 Additionally, some fraction of SN ejecta may be lost directly to an outflow, lowering effective yields.
@@
 
-Fig.~\ref{fig:eta} shows models with variations of the mass loading stength.
+Fig.~\ref{fig:eta} shows models with variations of the mass loading strength.
 While changing the value of $\eta$ affects the metallicity distribution of stars, all of the models in Fig.~\ref{fig:eta} still evolve along the same path.
-Our model is unable to tell apart a uniform decrease in both outflows and yields.
+My model is unable to tell apart a uniform decrease in both outflows and yields.
 
@@
     \includegraphics{eta.pdf}
-    \caption[Reduced-outflow models]{Same as Fig.~\ref{fig:agb_sims} but comparing the fiducial model to reduced mass loading models (see section  \ref{sec:outflows}).}
+    \caption[Reduced-outflow models]{Same as Fig.~\ref{fig:agb_sims} but comparing the fiducial model to reduced mass loading models (see section  \ref{sec:outflows}).
+Both yields and mass-loading are adjusted correspondingly such that the equilibrium abundances are unchanged.
+}
     \label{fig:eta}
@@
 So, I show in Fig.~\ref{fig:scatter} a comparison of the predicted distribution of the model to the contours of the \gls{subgiant} sample.
-Our model reproduces this 2-dimension distribution well when including scatter based on the median \apogee{} abundance errors for each metallicity bin.
+The model reproduces this 2-dimension distribution well when including scatter based on the median \apogee{} abundance errors for each metallicity bin.
 Some of the scatter is due to radial migration, but observational errors are dominant.
@@
     \includegraphics[scale=0.9]{cooh_scatter.pdf}
-    \caption[Scatter agreement]{The stars in the fiducial model in the \caah~plane perturbed by the median [Mg/H] and [C/Mg] measurment errors in the \citetjack~sample.
+    \caption[Scatter agreement]{The stars in the fiducial model in the \caah~plane perturbed by the median [Mg/H] and [C/Mg] measurement errors in the \citetjack~sample.
 Stars are color-coded such that lighter colors represent populations born at greater galactocentric radii.
+The plot only includes \gls{lowalpha} stars.
     }
@@
 
-As an additional test of the model, I next compare the model predictions against gas-phase measurments.
+As an additional test of the model, I next compare the model predictions against gas-phase measurements.
 Fig.~\ref{fig:gas_phase} shows the fiducial model's gas phase predictions compared to observations of MW and extragalactic HII regions, halo stars, and \dla\ systems.
 The model is broadly consistent with observations, where the model at $t=2$\,Gyr approximates the slope of dwarf galaxies and halo stars.
-The increase of C/O at late times is also consistent with the high C/O abundances measured in extragalactic HII regions.
+The increase of C/O at higher metallicities is also consistent with the high C/O abundances measured in extragalactic HII regions.
 My model does not extend to very low metallicity, where the slope of the trend inverts, but broadly explains observations above $\rm [O/H] \gtrsim -1$.
@@
 However, I use O abundances for gas-phase measurements and low-metallicity stars (section  \ref{sec:gas}).
-While I use Mg as the representativve \gls{alpha} for stellar abundances, I instead us O when comparing gas-phase abundances.
+While I use Mg as the representative \gls{alpha} for stellar abundances, I instead us O when comparing gas-phase abundances.
 
@@
     \caption[C/N abundance agreement]{Similar to Fig.~\ref{fig:agb_sims}, except comparing [C/N] from the fiducial model only.
+N yields are adapted from \cite{james+23}.
+(See also Table \ref{tab:fiducial_mod}.)
     }
@@
 
-Though \cc\ C yields are poorly understood, I adopt an equilibrium approximation and determine a functional form that approximately matches trends in \apogee{} \gls{subgiant} and is consistant with massive star \gls{nucleosynthesis} models.
+Though \cc\ C yields are poorly understood, I adopt an equilibrium approximation and determine a functional form that approximately matches trends in \apogee{} \gls{subgiant} and is consistent with \gls{highmass} \gls{nucleosynthesis} models.
 Variations of the metallicity dependence of this \cc\ yield affect trends in \caah~but do not affect trends in \caafe\ when taking a slice in [Mg/H].
@@
 From this, I estimate that \agb\ stars contribute \about{20\%} of total C abundance at solar metallicity.
-The remaining \about{80\%} of C comes from massive stars with a metallicity dependent yield of $\Ycc/\Yoc=1.51 + 0.54 (Z/Z_\odot)$.
+The remaining \about{80\%} of C comes from \gls{highmass} with a metallicity dependent yield of $\Ycc/\Yoc=1.51 + 0.54 (Z/Z_\odot)$.
 This metallicity dependence is consistent with the rotating stellar models of \citet{LC18}.
@@
 
-An alternate approach for this analysis would be to estimate the birth abundances of \gls{rgb}s by correcting surafe abundance effects from \gls{fdu} as in \cite{vincenzo+21}.
+An alternate approach for this analysis would be to estimate the birth abundances of \gls{rgb}s by correcting surface abundance effects from \gls{fdu} as in \cite{vincenzo+21}.
 Subgiants are the more attractive option since these observations do not rely on model-dependent corrections.
@@
 
-Fig.~\ref{fig:subgiant_selection} shows a plot of all \apogee\ stars and the \citetjack polygon selection criterial. 
+Fig.~\ref{fig:subgiant_selection} shows a plot of all \apogee\ stars and the \citetjack polygon selection criteria. 
  \citetjack~select a region of stars in $\log g$-$T_\text{eff}$ space described by the following criteria
@@
 \newpage
-\section{Stellar Evolution and C Production}
-While neglected in the main body of the paper, for reference, I include here a brief summary of the physics behind carbon production in low and high mass stars.
-
-Low mass stars ($\lesssim 8 M_\odot$, like our sun), are born when they are fusing H into He ($\isotope[1]{H}(p,\beta^{-}\gamma)\isotope[2]{H}$)
-
+\section{Low-mass stellar evolution}\label{sec:stel_evo}
+For reference, I include here a brief summary of the physics behind carbon production in \glspl{lowmass}.
+\Glspl{lowmass} ($\lesssim 8 M_\odot$, like our sun), are born when they are fusing H into He.
+Typically, the dominant process is through the aptly named \textit{pp chain}, which takes four protons $\proton$ and releases a He nucleus $\alpha$, positrons $\beta^{+}$, photons $\gamma$, and electron neutrinos $\nu_{\rm e}$.
+\begin{subequations}
+    \begin{align}
+        \proton + \proton &\longrightarrow \isotope[2][1]{H} + \beta^+ + \nu_{\rm e} \\
+        \proton + \isotope[2][1]{H} &\longrightarrow \isotope[3][2]{He} + \gamma\\
+        \proton + \isotope[3][2]{He} &\longrightarrow \isotope[4][2]{He} + \beta^+ + \nu_{\rm e}.
+    \end{align}
+\end{subequations}
+However, when the core temperature becomes high enough, the \gls{cno} begins to activate.
+Starting with \isotope[12]{C}, the \gls{cno} is a series of proton captures which result in the creation of a new He nucleus.
 \begin{subequations}\label{eq:cno_cycle}
@@
     \proton + \isotope[12]{C} &\longrightarrow \isotope[13]{N} + \gamma \\
-    \isotope[13]{N} &\longrightarrow  \isotope[13]{C} + \beta^+ + \nu_e  \\
+    \isotope[13]{N} &\longrightarrow  \isotope[13]{C} + \beta^+ + \nu_{\rm e}  \\
     \proton + \isotope[13]{C}  &\longrightarrow \isotope[14]{N} + \gamma\\
-    \proton + \isotope[14]{N}  &\longrightarrow \isotope[15]{O} + \gamma\\
-    \isotope[15]{O} &\longrightarrow  \isotope[15]{N} + \beta^{+} + \nu_e \\
+    \proton + \isotope[14]{N}  &\longrightarrow \isotope[15]{O} + \gamma \label{eq:n14}\\
+    \isotope[15]{O} &\longrightarrow  \isotope[15]{N} + \beta^{+} + \nu_{\rm e} \\
     \proton + \isotope[15]{N} &\longrightarrow \isotope[12]{C} + \alpha
@@
 \end{subequations}
-
+The \gls{cno} is more intense at high metallicities, as the abundance of \isotope[12]{C} is higher.
+Since the slowest reaction in the \gls{cno} is the \isotope[14]{N} proton capture (Eq.~\ref{eq:n14}; also see \citealt{solar-fusion}), the net effect is to convert \isotope[12]{C} into \isotope[14]{N}.
+
+After the end of the main sequence (core H burning), a star begins to ascend the \gls{rgb}.
+The star first becomes a \gls{subgiant}, slightly more luminous and redder than the main sequence.
+Then, \gls{fdu} occurs, when the contracting core drives convection currents through, bring processed material from the core to the surface.
+Because of the \gls{cno}, the surface abundances of C will be lowered and N enhanced.
+
+Stars with masses $\gtrsim 0.6M_\odot$ build up a large He core during the \gls{rgb}.
+Eventually, conditions are dense and hot enough for He to being to fuse, and the star now enters the He-burning phase.
+(Second dredge up occurs during this transition.) As the next (accessible) stable nuclei after He is C, the primary process to fuse He is through the triple-$\alpha$ process, where 3 He are combined to form \isotope[12]{C}.
 \begin{subequations} \label{eq:triple_alpha}
@@
 \end{align}
-
-Additionally, some \isotope[12][6]{C} may furthermore fuse into O, $\alpha + \isotope[12][8]{C} &\longrightarrow \isotope[16][8]{O} + \gamma$.
+Additionally, some \isotope[12][6]{C} may furthermore fuse into O, $\alpha + \isotope[12][8]{C} \longrightarrow \isotope[16][8]{O} + \gamma$.
+
+When the star's core becomes full of C and O, the star finally enters the asymptotic giant branch phase (\agb).
+(Only the most massive low-mass stars burn further than O, creating some Mg, but these stars are a small fraction of low-mass stars.) An \agb\ star has a more complex structure, with an inert core, a He-burning shell, and an outer H-burning shell.
+The double shell structure causes instabilities towards the end of the \agb\ phase.
+In this thermally pupating phase, a He-flash happens (where the He-shell becomes much more luminous).
+This flash causes the star to expand, driving convective currents which dredge up material from the CO core (\gls{tdu}), and fusion stops temporarily.
+The star settles again, and stays stable for several Myr until the cycle repeats again.
+During each He-flash, some material from the stellar surface is lost.
+This mass-loss is the source of \agb\ enrichment.
+Finally, the star losses enough mass such that the thermal pulses stop and the star becomes a white dwarf, no longer fusing anything.
 
@@
 \newpage
-\section{Additional Notes about Yields}\label{sec:alt_agb}
+\section{O vs Mg}\label{sec:alt_agb}
 
@@
 This is a known problem (see \citealt{emily+21}).
-\cc\ models updrepredict $[{\rm Mg}/{\rm O}]$, and the reason why is unknown.
+\cc\ models underpredict $[{\rm Mg}/{\rm O}]$, and the reason why is unknown.
 My results are independent of the choice of \cc\ element as I assume $[{\rm Mg}/{\rm O}]=0$.
 
-While I focus the main discussion of the paper on the \cxi{} model, other \agb\ models can impact abundance trends when $f_{\rm AGB}$ becomes larger.
-Here, I briefly explore the effects of variations in \agb\ models that affect abundance trend predictions when these models are amplified to match observational [C/MG]-[Mg/Fe] trends. 
-See Fig \ref{fig:fagb2}.
-
-\vxiii{} is also interesting as at high metallicity, the yields quickly become strongly negative.
-This causes a reversal of the [C/Mg]-[Mg/Fe] trend at high [Mg/H] slices (figure ...).
-As our set of observations does not appear to reverse, this indicates that C yields are likely to stay positive even at slightly super-solar, so models like \vxiii{} are a poor match to observations.
-
-In Fig.~\ref{fig:fe_ia}.
-
-I leave the exploration of the age-metallicity relation for C to future work.
-
-\begin{figure}[htp]
-    \centering
-    \includegraphics{agb2.pdf}
-
-    \caption[Alternate low mass star yield models]{Same as Fig.~\ref{fig:agb_sims} except where $f_{\rm agb}=0.2$. When yields are amplified, chaos ensues.}
-    \label{fig:fagb2}
-\end{figure}
-
-\begin{figure}[htp]
-    \centering
-    \includegraphics{y_mg.pdf}
-    \caption[Magnesium yields]{Same as the top panel of Fig.~\ref{fig:y_cc}, but for Mg. Our Mg yield choice is shown as a dashed line at the top
+\begin{figure}[htp]
+    \centering
+    \includegraphics{y_o_mg.pdf}
+    \caption[Magnesium yields]{Same as the top panel of Fig.~\ref{fig:y_cc}, but for Mg.
     }
     \label{fig:y_mg}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics{fe_ia.pdf}
-    \caption[Adjusting type Ia iron]{Similar to Fig.~\ref{fig:agb_sims} except with variations of the \ia\ iron fraction}
-    \label{fig:fe_ia}
 \end{figure}
@@
 
-\renewcommand*{\arraystretch}{1.25}
+\renewcommand*{\arraystretch}{1.8}
 \glsaddall[types={symbols}]
@@
 \printglossary[type=models,nonumberlist]
+\label{sec:oob_models}
 

### 2023-05-02 thesis/tex/main.tex
grammar edits

@@
 \usepackage{booktabs}
+\usepackage{longtable}
 \graphicspath{{../figures/}} 
@@
     pdfcreator={Themself},
-    pdfkeywords={astronomy,supernovae, stellar yields, chemical evolution, galaxies, carbon},
+    pdfkeywords={astronomy, supernovae, modeling, stellar yields, chemical evolution, galaxies, carbon},
 }
@@
 ]{glossaries-extra}
-
-\newglossary*{models}{Stellar Yield Models}
 \makeglossaries
@@
 
-\newglossarystyle{2colsymbol}{%
-    \setglossarystyle{long}% base this style on the list style
-    \renewenvironment{theglossary}{% Change the table type --> 3 columns
-        \glsdescwidth=\dimexpr\linewidth-\dimen0-2\tabcolsep\relax
-        \begin{longtable}{@{}l p{\glsdescwidth}@{}}}%
-        {\end{longtable}}%
-    \renewcommand*{\glossentry}[2]{%  Change the displayed items
-        \glstarget{##1}{\glossentryname{##1}} %
-        \glssymbol{##1}
-        &  \glossentrydesc{##1}  \tabularnewline
-    }
-}
-
 \newacronym
-[ description ={Core collapse supernovae. Massive star explosions. {\sc ccsne} produce many elements including \gls{alpha}, \gls{fepeak}, and r and \gls{sproc}.}
+[ description ={Core collapse supernovae. Massive star explosions. {\sc Ccsne} produce many elements including \gls{alpha}, \gls{fepeak}, and r and \gls{sproc}.}
 ]
@@
 \newacronym
-[description={Asymptotic giant branch stars. {\sc agb}s are the last phase of \glspl{lowmass}, before stars become white dwarfs. Produces C, N, and heavy s-process elements. See \ref{sec:stel_evo}.}]
+[description={Asymptotic giant branch stars.
+The {\sc agb} phase is the last phase of \glspl{lowmass}, before stars become white dwarfs.
+Produces C, N, and heavy \gls{sproc} elements.
+See \ref{sec:stel_evo}.}.]
 {agb}{agb}{asymptotic giant branch}
@@
 \newacronym
-[description={Type Ia Supernovae. Exploding white dwarfs, produces \gls{fepeak} elements and with a long delay time.}]
+[description={Type Ia Supernovae. Exploding white dwarfs. Produces \gls{fepeak} and has a long delay time.}]
 {ia}{sne ia}{supernovae type Ia}
@@
 A function describing the mass distribution of newly formed stars.
-I use a \citet{kroupa01} {\sc imf}, which is described as a piecewise powerlaw function of $M$.}]
+I use a \citet{kroupa01} {\sc imf}, which is described as a piecewise power-law function of $M$.}]
 {imf}{imf}{initial mass function}
@@
 Apache Point Observatory Galactic Evolution Experiment. 
-A large near-infrared spectroscopic survey of stars in the Milky Way. \citep{apogee17}}]
+A large near-infrared spectroscopic survey of stars in the Milky Way. \citep{apogee17}.}]
 {apogee}{apogee}{Apache Point Observatory Galactic Evolution Experiment}
@@
 
-%%%%%%%%%%%%%%%%%%% Symbols %%%%%%%%%%%%%%%%%%%%%%%%
-\glsxtrnewsymbol
-[description = {
-    The abundance ratio between elements $A$ and $B$. $[A/B] =
-    \log_{10}\left(A/B\right) - \log_{10}\left(A_{\sun}/B_{\sun}\right)$, i.e.
-    $[A/B]$ is the logarithm of the ratio between A and B, scales such that
-    $[A/B]=0$ for the sun. Solar abundances are as measured in
-    \citet{asplund+09}.
-}]
-{abundratio}{\ensuremath{[A/B]}}
-
-\glsxtrnewsymbol
-[description = {The multiplicative increase in \agb\ C production. See Eq.~\ref{eq:alpha}}]
-{aagb}{\ensuremath{\alpha_{\rm AGB}}}
-
-\glsxtrnewsymbol
-[description = {The multiplicative increase in \cc\ C production. See Eq.~\ref{eq:alpha}}]
-{acc}{\ensuremath{\alpha_{\rm CC}}}
-
-\glsxtrnewsymbol
-[description = {The mass outflow loading factor. $\eta$ is the ratio between ejected gas from the galaxy and star formation, i.e. $\eta = \dot{M}_{\rm outflow}/\dot{M}_\star$. }]
-{eta}{\ensuremath{\eta}}
-
-\glsxtrnewsymbol
-[description = {The high-mass star carbon yield metallicity dependence. See Eq.~\ref{eq:zeta}}]
-{zeta}{\ensuremath{\zeta}}
-
-\glsxtrnewsymbol
-[description = {The surface density of star formation by mass.}]
-{sfd}{\ensuremath{\dot{\Sigma}}}
-
-\glsxtrnewsymbol
-[description = {The mass of the sun. $M_\odot = 1.989\times10^{33}$\,g}]
-{msun}{\ensuremath{M_\odot}}
-
-\glsxtrnewsymbol
-[description = {The rate of star formation (mass of new stars per time interval).}]
-{sfr}{\ensuremath{\dot{M}_\star}}
-
-\glsxtrnewsymbol
-[description = {The rate of change of the mass of element $X$.}]
-{mdotx}{\ensuremath{\dot{M}_{\rm X}}}
-
-\glsxtrnewsymbol
-[description = {The fractional contribution of AGB stars to the total \gls{imfave} carbon yield at solar metallicity. See Eq.~\ref{eq:f_agb}}]
-{fagb}{\ensuremath{f_{\rm AGB}}}
-
-\glsxtrnewsymbol
-[description = {The galactocentric radius---distance from the galactic center in kpc.}]
-{Rgal}{\ensuremath{R}}
-
-\glsxtrnewsymbol
-[description = {The per-star yield of C from \glspl{lowmass} of a given mass. In otherwords, the amount of new C an \agb\ star ejects divided by the initial mass of the star.}]
-{ytcagb}{\ensuremath{\tilde{y}_{\rm C}^{\rm AGB}}}
-
-\glsxtrnewsymbol
-[description = {The \gls{imfave} yield of C from \glspl{lowmass}.}]
-{ycagb}{\ensuremath{y_{\rm C}^{\rm AGB}}}
-
-\glsxtrnewsymbol
-[description = {The \gls{imfave} yield of C from \glspl{highmass}.}]
-{ycc}{\ensuremath{y_{\rm C}^{\rm CC}}}
-
-\glsxtrnewsymbol
-[description = {The \gls{imfave} yield of Mg.}]
-{ymg}{\ensuremath{y_{\rm Mg}^{\rm CC}}}
-
-\glsxtrnewsymbol
-[description = {The metallicity for the sun. $Z_\odot=0.014$. }]
-{zsun}{\ensuremath{Z_\odot}}
-
-\glsxtrnewsymbol
-[description = {The metallicity fraction, i.e. the mass fraction of all elements which are not H or He. }]
-{Z}{\ensuremath{Z}}
-
-\glsxtrnewsymbol
-[description = {The mass fraction of element $X$.}]
-{Zx}{\ensuremath{Z_X}}
-
 %%%%%%%%%%%%%%%%%%%%%% terms %%%%%%%%%%%%%%%
 \newglossaryentry{metallicity}{name={metallicity},
-    description={the (mass) fraction of a star or gass which is not made of either H or He. For the sun, the metallicity is $\Zo = 0.014$}
+    description={the (mass) fraction of a star or gas which is not made of either H or He. For the sun, the metallicity is $\Zo = 0.014$}
+}
+
+\newglossaryentry{yield}{name={yield},
+    description={The net production of a new element during a star's lifecycle divided by the star's mass (including winds and supernovae ejecta). }
 }
@@
 \newglossaryentry{multizone}{name={multi-zone},
-    description={the synthesis of new elements inside stars}
+    description={A chemical evolution model where a galaxy is divided into several zones, each with different stars, gas, and properties. }
 }
@@
 \newglossaryentry{onezone}{name={one-zone},
-    description={the synthesis of new elements inside stars}
+    description={A chemical evolution model where the gas is all the same composition, i.e. neglecting spatial variations.}
 }
@@
 \newglossaryentry{alpha}{name={$\alpha$-element},
-    description={Elements which are made up of $\alpha$-particles (He nuclei) throuch the triple-$\alpha$ process (see Eq.
-\ref{eq:triple_alpha}).
+    description={Elements which are made up of $\alpha$-particles (He nuclei) throuch the triple-$\alpha$ process (see Eq.~\ref{eq:triple_alpha}).
 Essentially light, even-numbered elements like O, Mg, and Na.}
@@
 \newglossaryentry{rgb}{name={red giant branch},
-    description={Red giant branch stars are stars which have completed hydrogen core burning and have expanded in size. See appendix \ref{sec:stel_evo}.}
+    description={Red giant branch stars are stars that have completed hydrogen core burning and have expanded in size. See Appendix \ref{sec:stel_evo}.}
 }
@@
 (While nominally called {\it third dredge up}, there are typically several third dredge ups.).
-See appendix \ref{sec:stel_evo}.}
+See Appendix \ref{sec:stel_evo}.}
 }
@@
 Material from the core is brought to the surface, increasing N and decreasing C abundances.
-See appendix \ref{sec:stel_evo}.}
+See Appendix \ref{sec:stel_evo}.}
 }
@@
 \newglossaryentry{subgiant}{name={subgiant},
-    description={A subgiant is a star which is starting to become a \gls{rgb} star.}
+    description={A star in the process of leaving the main sequence and becoming a \gls{rgb}.}
 }
@@
 
-\newglossaryentry{dtd}{name={delay-time distribution},
+\newglossaryentry{dtd}{name={delay time distribution},
     description={The distribution in time of when an element is produced 
@@
 \newglossaryentry{massloading}{name={mass loading},
-    description={The stength of outflows. See also $\gls{eta}$. }
+    description={The strength of outflows relative to star formation. See also $\eta$. }
 }
@@
 \newglossaryentry{lowmass}{name={low-mass star},
-    description={Low-mass stars are stars with masses $\lesssim 8\,M_\odot$ which end life as a white dwarf. }
-}
-
-\newglossaryentry{highmass}{name={migh-mass star},
+    description={Stars with masses $\lesssim 8\,M_\odot$ which end life as a white dwarf. }
+}
+
+\newglossaryentry{highmass}{name={high-mass star},
     description={Stars with masses $\lesssim 8\,M_\odot$, which end as a neutron star, black hole, or supernovae.}
+}
+
+\newglossaryentry{insideout}{name={{\it insideout}},
+    description={Our fiducial star formation history. The rate of star formation is highest towards the center of the galaxy and at earlier times. See Eq.~\ref{eq:inside_out}.}
 }
@@
 }
-%%%%%%%%%%%%%%%%%%%%%%%%%% Models %%%%%%%%%%%%%%%%%%%%%%%
-\newglossaryentry{c11}
-{
-    name={C11},
-    type={models},
-    description={the yield set from \citet{cristallo+11,cristallo+15}.
-The models were run at $M = $ 1.3, 1.5, 2.0, 2.5, 3.0, 4.0, 5.0, 6.0 and $Z= $ 0.0001, 0.0003, 0.001, 0.002, 0.003, 0.006, 0.008, 0.01, 0.014, 0.02.
-},
-}
-\newglossaryentry{k10}
-{
-    name={K10},
-    type={models},
-    description={the yield set from \citet{karakas10}. Includes models run at 
-    $M= $ 1.0, 1.25, 1.5, 1.75, 1.9, 2.25, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0 and $Z=$ 0.0001, 0.004, 0.008, 0.02},
-}
-\newglossaryentry{v13}
-{
-    name={V13},
-    type={models},
-    description={the \agb\ yield set from \citet{ventura+13,ventura+14,ventura+18,ventura+20}.
-Includes models with masses $m=(1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 6.0, 6.5, 7.0)$ and with metallicities $Z=(0.0003, 0.001, 0.002, 0.004, 0.008, 0.014, 0.04)$},
-}
-\newglossaryentry{k16}
-{
-    name={K16},
-    type={models},
-    description={The yield set from \citet{KL16, karakas+18}. The model is sampled at 
-        $M=(0.0003, 0.001, 0.002, 0.004, 0.008, 0.014, 0.04)$
-        and $Z=(0.0003, 0.001, 0.002, 0.004, 0.008, 0.014, 0.04)$
-    },
-}
-
-\newcommand{\cxi}{\texttt{\gls{c11}}}
-\newcommand{\kx}{\texttt{\gls{k10}}}
-\newcommand{\kxvi}{\texttt{\gls{k16}}}
-\newcommand{\vxiii}{\texttt{\gls{v13}}}
-
-\newcommand{\Ycc}{\gls{ycc}}
-\newcommand{\Yoc}{\gls{ymg}}
-\newcommand{\Ycagb}{\gls{ycagb}}
-\newcommand{\sun}{\odot}
-\newcommand{\Z}{Z}
-\newcommand{\Zo}{Z_{\sun}}
-
-\newcommand{\abund}[2]{\ensuremath{\[{\rm #1}/{\rm #2}\]}}
-\newcommand{\proton}{\isotope[1][1]{p}}
-
-\newcommand{\zoo}{\ensuremath{Z/Z_{\sun }}}
-\newcommand{\Yct}{\ensuremath{y_{\rm C}}}
 
 \defcitealias{james+21}{J21}
+\newcommand{\citetjack}{Roberts et al.~(2023, in prep.)}
+\newcommand{\citepjack}{(Roberts et al.~2023, in prep.)}
+\newcommand{\citealtjack}{Robert et al.~2023, in prep.}
+
+\newcommand{\cxi}{\texttt{\hyperlink{C11}{C11}}}
+\newcommand{\kx}{\texttt{\hyperlink{K10}{K10}}}
+\newcommand{\kxvi}{\texttt{\hyperlink{K16}{K16}}}
+\newcommand{\vxiii}{\texttt{\hyperlink{V13}{V13}}}
 
@@
 
-\newcommand{\citetjack}{Roberts et al.~(2023, in prep.)}
-\newcommand{\citepjack}{(Roberts et al.~2023, in prep.)}
-\newcommand{\citealtjack}{Robert et al.~2023, in prep.}
+\newcommand{\Ycc}{\ensuremath{y_{\rm C}^{\rm CC}}}
+\newcommand{\Yoc}{\ensuremath{y_{\rm Mg}^{\rm CC}}}
+\newcommand{\Ycagb}{\ensuremath{y_{\rm C}^{\rm AGB}}}
+\newcommand{\sun}{\odot}
+\newcommand{\Z}{Z}
+\newcommand{\Zo}{Z_{\sun}}
+
+\newcommand{\proton}{\isotope[1][1]{p}}
+
+\newcommand{\zoo}{\ensuremath{Z/Z_{\sun }}}
+\newcommand{\Yct}{\ensuremath{y_{\rm C}}}
 
@@
 
-% These dates will be filled out by the publisher
 \date{\today}
@@
        Project Advisors\\
-       Professor David H. Weinberg, Department of Astronomy \\
-       James W. Johnson, Department of Astronomy
+       James W. Johnson, Department of Astronomy \\
+       Professor David H. Weinberg, Department of Astronomy 
        \vfill
@@
 % context
-Stellar evolution models provide uncertain predictions for elemental yields due to uncertainties in stellar physics.
+Limited knowledge of stellar physics leads to uncertainties in elemental yield predictions.
 % aims
-Here, I constrain the nucleosynthetic yields of C using multizone Galactic chemical evolution models.
+As an independent approach, I constrain the nucleosynthetic yields of C using multizone Galactic chemical evolution models.
 % results
-By matching the slopes of the \caah\ and \caafe\ relationships in a sample of APOGEE subgiant stars, I find that high-mass and low-mass stars contribute \about{80\%} and \about{20\%} of total C production respectively.
+By matching the median trends of \caah\ and \caafe\ in  {\sc APOGEE} subgiant stars, I find that high-mass and low-mass stars contribute \about{80\%} and \about{20\%} of total C production respectively.
 % 
-To also match the normalization of the trends, I estimate the massive star C/Mg yield ratio $\Ycc/\Yoc = 1.57 + 0.59 \left(Z/Z_\odot\right)$, which explains the \caah\ trend when including the low mass C contribution.
+To match the normalization of the trends, I estimate the massive star C/Mg yield ratio $\Ycc/\Yoc = 1.57 + 0.59 \left(Z/Z_\odot\right)$,  explaining the \caah\ trend when including the low mass C contribution.
 %
@@
 % 
-Due to the degeneracy between the normalization of elemental yields and the strength of mass-loading in Galactic outflows, I constrain only the {\it relative} yield of C and Mg from a simple stellar population and the metallicity dependence thereof.
+Due to the degeneracy between the normalization of elemental yields and the strength of mass-loading in Galactic outflows, I am only able to constrain the relative yields of C/Mg and its metallicity dependence.
 While measurements of gas-phase C abundances are challenging, my model is broadly consistent with the [C/O]-[O/H] trend observed in compiled literature measurements.
@@
 
-I dearly hope that the people who helped me complete this project will appreciate how much they have helped me.
+I hope that the people who helped me complete this project will appreciate how much they have helped me.
 This year has been an incredibly challenging journey---and perhaps I am not open enough about what it has been like.
@@
 James Johnson---your mentorship and guidance throughout this project was critical. 
-You helped me learn an incredible amount about being an astronomer, and I am forever grateful for how you have guided this project, through late nights and last minute comments.
+You helped me learn an incredible amount about being an astronomer, and I am forever grateful for how you have guided this project, through late nights and last-minute comments.
 Wayne, for everything you do for everyone---you are the glue holding together our department and nobody can say thank you enough.
@@
 
-\Gce{} aims to understand the chemical and star formation histories of galaxies.
-At the core of \gce{} models are stellar yields---the amount of each chemical element stars produce (or destroy).
+\Gce{} aims to understand the chemical enrichment and star formation histories of galaxies.
+At the core of \gce{} models are stellar \gls{yield}---the amount of each chemical element stars produce (or destroy).
 Each element is produced in different amounts by different stars, leaving traces of the Galaxy's evolutionary history.
@@
 
-Here, I aim to understand C enrichment---where it is produced and how its abundances evolve over time.
+Here, I aim to understand C enrichment---where it is produced and how its abundances evolve.
 C is unique nucleosynthetically, one of few light elements (along with N) produced in \agb{} stars \citep[e.g.][]{jennifer19, KL14}.
@@
 $[A/B] = \log_{10}\left(A/B\right) - \log_{10}\left(A_{\sun}/B_{\sun}\right)$, i.e.
-$[A/B]$ is the logarithm of the ratio between A and B, scales such that $[A/B]=0$ for the sun.
-Solar abundances are as measured in \citet{asplund+09}}%
+$[A/B]$ is the logarithm of the ratio between A and B, scaled such that $[A/B]=0$ for the sun.
+Solar abundances are as measured in \citet{asplund+09}.}%
 %
----observed in very low \gls{metallicity}, high redshift \dla{}---decrease with increasing [O/H] \citep{FN15, cooke+17}.
-Then, [C/O] increases above $\rm [O/H] \approx -1$ (\citealt{berg+19}; see discussion in section \ref{sec:gas}).
+---observed in very low \gls{metallicity}
+\footnote{Astronomers are not chemists. By metallicity, I mean the (mass) fraction of any element which is not H or He, denoted by $Z$. For the sun, $Z_\odot=0.014$. }
+, high redshift
+\footnote{i.e. observed in the early universe.}
+\dla{}---decrease with increasing [O/H] \citep{FN15, cooke+17}. Then, [C/O] increases above $\rm [O/H] \approx -1$ (\citealt{berg+19}; see discussion in section \ref{sec:gas}).
 While we know C is produced in \agb{} stars and \cc{}, we still have a limited understanding of the magnitude and metallicity-dependence of each process.
 
-Despite their central role in \gce{} models, nucleosynthetic yields predicted by stellar evolution models are rife with uncertainties.
-The production rates of elements in stars are shaped by poorly understood processes, including mass loss, opacity, nuclear reaction rates, rotational mixing, and convection \citep{KL14,ventura+13, LC18}.
-Changes in \gls{highmass}' explodability also introduce further variation and uncertainty in population-averaged yields \citep{emily+21}.
+Nucleosynthetic yields predicted by stellar evolution models are rife with uncertainties, despite their central role in \gce{} models, nucleosynthetic yields predicted by stellar evolution models are rife with uncertainties.
+The production rates of elements in stars are shaped by poorly understood processes, including mass loss, opacity, nuclear reaction rates, rotational mixing, convection, and explodability \citep{KL14,ventura+13, LC18, emily+21}.
 
@@
 \cite{james+23} examined similar \gce{} models of N, an element whose production is closely related to C.
-\cite{james+23} found that trends in N and O abundances can be explained by the metallicity dependence of relative N and O yields.
-Here, I extend their models to C and show that similar constraints on C and O relative yields can be obtained from observed abundance ratios.
-Additionally, I assess which yield prescriptions reproduce Galactic abundance trends while assessing the impact of \gce{} model assumptions, such as \sfh{} and outflow mass loading.
-
-Accurate determination of stellar birth abundances for C and N is challenging.
+They  found that trends in N and O abundances can be explained by the \gls{metallicity} dependence of relative N and O yields.
+Here, I extend their models to C, deriving similar constraints on C/Mg yields.
+I assess which yield prescriptions reproduce Galactic abundance trends while investigating the impact of \gce{} model assumptions, such as \sfh{} and outflow mass loading.
+
+C abundances are challenging to measure.
 When a star enters the \gls{rgb}, material from the CNO-processed core is mixed with the envelope in first dredge up, enhancing N and depleting C \citep{iben67, vincenzo+21,KL14}.
@@
 
-To this end, I use a sample of \gls{subgiant} stars from the \apogee{} \citep{apogee17}.
-According to stellar evolution theory and observations \citep{gilroy89, korn+07, lind+08, souto+18, souto19}, these stars have not yet experienced first dredge up but have well-mixed photospheres.
-Their photosphoric abundances should thus represent their birth composition.
+As my observational constraint, I use a sample of \gls{subgiant} stars from the \apogee{} \citep{apogee17}.
+According to stellar evolution theory and observations \citep{gilroy89, korn+07, lind+08, souto+18, souto19}, these stars have not yet experienced \gls{fdu} but have well-mixed envelopes.
+So, their surface abundances should thus represent their birth composition.
 In Fig.~\ref{fig:subgiants}, I plot this sample, selected by the criteria in Roberts et al.
 (2023, in prep; see Appendix \ref{sec:jack}).
-These empirical results contain information on the relative C and Mg yields, which I use later in this work.
+In this sample, [C/Mg] increases with \gls{metallicity}, and [C/Mg] decreases with [Mg/Fe] at fixed [Mg/H].
+Using these trends, I will develop a model of the enrichment sources and evolution of C.
 
@@
     \quad\includegraphics{subgiants_mgfe.pdf}
-    \caption[APOGEE Subgiants]{The [C/Mg] ratio against [Mg/H] (top) and [Mg/Fe] (bottom) for the \citetjack~sample of \apogee{} \gls{subgiant}s.
-On the top, I plot high and \gls{lowalpha} stars in blue and orange, using the separation defined in Equation \ref{eq:high_alpha}.
+    \caption[Subgiant Abundances]{The [C/Mg] ratio against [Mg/H] (top) and [Mg/Fe] (bottom) for the \citetjack~sample of \apogee{} \gls{subgiant}s.
+On the top, I plot high and \gls{lowalpha} stars in blue and orange, using the separation defined in Equation \ref{eq:high_alpha} (the high and low-$\alpha$ stars are named for their high or low \gls{alpha} to Fe ratios, or in this case, Mg/Fe).
 On the bottom, I color-code stars according to their [Mg/H] abundance.}
@@
 I focus on three primary nucleosynthetic pathways: \agb{} stars, \cc{}, and \ia.
-Each process has unique timescales and yields, traceable through the tools of \gce.
-I compare C, produced in \cc{} and \agb\ stars, to Mg and Fe as tracers of \cc{} and \ia{} respectively.
+Each process has unique timescales and \glspl{yield}, traceable through the tools of \gce.
+C is produced in both \cc\ and \agb\ stars.
+I also compare C to Mg and Fe, which trace \cc{} and \ia{} respectively.
 
 When a \ssp~forms, \cc{} are the first enrichment event.
-\cc{}  explode within $\lesssim 40$\,Myr, providing light elements (C, O, and Mg) and heavier elements (Fe and beyond).
-Metallicity-independent yields from \cc{} are the only statistically significant source of O and Mg ($\alpha$ elements).
-Next, low-mass stars begin to reach the end of their lives.
+\Gls{cc}  explode within $\lesssim 40$\,Myr, providing light elements (C, O, and Mg) and heavier elements (Fe and beyond).
+O and Mg are produced almost entirely from \cc\ with metallicity-independent yields.
+Next, \glspl{lowmass} stars begin to reach the end of their lives.
 By shedding their outer layers, \agb{} stars are important sources of C, N, and neutron capture elements.
@@
 
-For an element X and star with mass $M$, the net-fractional-stellar yield $\tilde{y}$ is defined as the net production of X relative to $M$, or
+For an element $X$ and star with mass $M$, the net-fractional stellar \gls{yield} $\tilde{y}$ is defined as the net production of new $X$ relative to $M$, or
 \begin{equation}
-    \tilde{y}_{\rm X} = \frac{M_{\rm X,\ ejected} - Z_{0, X} M_{\rm ejected}}{M}   
-\end{equation}
-where $M_{\rm ejected}$ and $M_{\rm X, ejected}$  are the total ejected mass of the envelope and the element X, respectively.
+    \tilde{y}_{X} = \frac{M_{X,\ \rm ejected} - Z_{0, X}\,M_{\rm ejected}}{M}   
+\end{equation}
+where $M_{\rm ejected}$ and $M_{X, \rm ejected}$  are the total ejected mass of the envelope and the element X, respectively.
 For example, if a 1 $M_\odot$ star has $\tilde{y}_{\rm C} = 10^{-3}$, then the star will add $10^{-3}\ M_\odot$ of new C to the interstellar medium.
@@
 \end{equation}
-where ${dN}/{dM}$ is the normalized \imf, $M_{\rm max}=100\,M_\odot$ is the maximum stellar mass, and $M_{\rm min}(t)$ is the minimum mass of stars which die before time $t$.
-For \agb{} stars, the yields are truncated above 8 $M_{\odot}$.
+where ${dN}/{dM}$ is the normalized \imf, $M_{\rm max}=100\,M_\odot$ is the maximum stellar mass, and $M_{\rm min}(t)$ is the mass of stars with lifetime $t$. 
+\footnote{In my model, the mass-lifetime relation is
+$\log \tau_M = 1.02 - 3.57\log M + 0.90 \left(\log M\right)^2$,
+where $\tau_M$ is in Gyr,
+from \citealt{larson74}.  For \agb{} stars, the stellar yields are truncated above 8 $M_{\odot}$. }
+I use $t=10\,$Gyr for total yields when $t$ is not used.
 To calculate the \gls{imfave} net yields, I use the Versatile Integrator for Chemical Evolution code (\VICE\footnote{\VICE~is available at \url{https://github.com/giganano/VICE}}).
@@
 To focus on C yields, I adapt the yield choices of other elements from \citet{james+21, james+23}.
-Table \ref{tab:fiducial_mod} contains my fiducial yields, in units of a \ssp's birth mass.
+Table \ref{tab:fiducial_mod} contains my fiducial \glspl{yield}, in units of a \ssp's birth mass.
 Also following \citet{james+21, james+23}, I take the \ia{} \gls{dtd} to be a
@@
 	\centering
-    \caption[Fiducial Model]{Yields for the fiducial model in units of \ssp~birth mass. See section \ref{sec:agb} for the definition of \cxi.}
+    \caption[Fiducial Model Yields]{Yields for the fiducial model (in units of \ssp~birth mass). See Section \ref{sec:agb} for the definition of \cxi.}
 	\label{tab:fiducial_mod}
@@
 
-An \agb\ star is a \gls{lowmass} ($\lesssim 8 M_{\sun}$) during its final phase of evolution (see appendix \ref{sec:stel_evo}).
+An \agb\ star is a \gls{lowmass} ($\lesssim 8 M_{\sun}$) during its final phase of evolution (see Appendix \ref{sec:stel_evo}).
 In an \agb\ star, two competing processes determine the outcome of C production: \gls{tdu} and \gls{hbb}.
-Third dredge up accompanies thermal pulses in \agb\ stars.
-During a \gls{tdu} event, material from the CO core is mixed with material exposed to partial He-shell burning, increasing C and O abundances in the envelope \citep{KL14}.
+Third dredge up accompanies thermal pulses in \agb\ stars, where material from the CO core is mixed with the envelope, increasing surface C abundances \citep{KL14}.
 If this envelope is lost during the \agb\ phase, then C yields are enhanced.
-\gls{hbb} is the activation of proton capture reactions, and the CNO cycle%
-Other minor branches of the \gls{cno} are of minor importance to C yields
- \citep{solar-fusion}.
-
+\gls{hbb} is the activation of proton capture reactions and the CNO cycle%
 at the base of the convective envelope.
-Because the $^{14}$N(p, $\gamma$) proton capture is the slowest component of the CNO cycle \citep{solar-fusion}, the CNO cycle converts nearly all \isotope[12]{C} into \isotope[14]{N}.
-As a result, when both \gls{tdu} and \gls{hbb}, \isotope[12]{C} yields are lowered (see discussion in \citealt{james+23} and \citealt{ventura+13}).
+Because the $^{14}$N proton capture is the slowest component of the CNO cycle \citep{solar-fusion}, the CNO cycle converts nearly all \isotope[12]{C} into \isotope[14]{N}.
+As a result, when both \gls{tdu} and \gls{hbb} occur, \isotope[12]{C} yields are lowered (see discussion in \citealt{james+23} and \citealt{ventura+13}).
 
@@
 \end{itemize}
-For my models to match observations, I find I need to uniformly amplify these yield tables (see Eq.~\ref{eq:alpha}). I use \cxi\ table, amplified by a factor of 2.9, as the fiducial \agb\ yield.
-
-Fig.~\ref{fig:y_agb} compares the \agb\ C yield $\tilde{y}_\text{C}^\text{AGB}(M, Z)$ for each model I consider. 
+For my models to match observations, I find that need to uniformly amplify these yield tables (see Eq.~\ref{eq:alpha}). I use \cxi\ table, amplified by a factor of 2.9, as the fiducial \agb\ yield.
+
+Fig.~\ref{fig:y_agb} compares the stellar \agb\ C yield $\tilde{y}_\text{C}^\text{AGB}(M, Z)$ for these four models.
 The yields may be negative if a star ejects material with a lower average C abundance than the material the star was formed from.
@@
 
-In Fig.~\ref{fig:agb-ssp}, I plot the total production of C by \agb\ stars in a \ssp{} at an age $t$. 
-Effectively, this is equivalent to integrating Eq.~\ref{eq:imf-yield} down to $M_{to}$, the turnoff mass for time $t$.
-({In our model, the mass-lifetime relation is
-$\log \tau_M = 1.02 - 3.57\log M + 0.90 \left(\log M\right)^2$,
-where $\tau_M$ is in Gyr,
-from \citealt{larson74}.})
-As the mass range $2\lesssim M \lesssim 4$ is most important for C production, about half of C production occurs before \about{1}\,Gyr, similar to \ia\ Fe. 
-\kx{} and \kxvi{} weight C production more heavily towards \gls{highmass}s resulting in a faster enrichment delay time, whereas the \cxi\ and \vxiii\ models predict a slightly longer timescale of \about{1}\,Gyr, but little to no C is produced more than 2\,Gyr after a star formation event.
-This is in contrast to Fe whos production lasts up to 10\,Gyr after a star formation event.
+Fig.~\ref{fig:agb-ssp} shows the total production of C by \agb\ stars in a \ssp{} at an age $t$, i.e. $\tilde{y}_{\rm C}(Z_\odot, t)$. 
+As the mass range $2M_\odot\lesssim M \lesssim 4M_\odot$ is most important for C production, about half of C production occurs before \about{1}\,Gyr, similar to \ia\ Fe. 
+\kx{} and \kxvi{} weight C production more heavily towards \glspl{highmass} resulting in a faster enrichment delay time, whereas the \cxi\ and \vxiii\ models predict a slightly longer timescale of \about{1}\,Gyr, but little to no C is produced more than 2\,Gyr after a star formation event.
+This is in contrast to Fe whose production lasts up to 10\,Gyr after a star formation event.
 As shown in the right panel of Fig.~\ref{fig:agb-ssp}, with increasing $Z$, C enrichment occurs earlier, and C destruction in low-mass stars leads to a declining C abundance at late times.
@@
  	    \includegraphics[scale=1]{agb_yields.pdf}
-        \caption[Low mass C yields]{The net fractional \agb\ C yield  plotted as a function of initial stellar mass $M$ and color-coded according to metallicity.
+        \caption[Low-Mass Stellar Carbon Yields]{The net fractional \agb\ C yield  plotted as a function of initial stellar mass $M$ and color-coded according to metallicity.
 The black dashed line shows $\tilde{y}=0$ for reference.
-Each panel represents yields from one of four \agb\ models: \cxi, \kx{}, \vxiii{}, \kxvi{} (see section \ref{sec:agb}) and \ref{sec:oob_models}.
+Each panel represents yields from one of four \agb\ models: \cxi, \kx{}, \vxiii{}, \kxvi{} (see Section \ref{sec:agb} and \ref{sec:oob_models}).
 }
@@
 
-    \caption[C yields delay time distribution]{
+    \caption[Carbon Delay Time Distribution]{
     C production by \agb\ stars as a function of \ssp{} age, normalized to the total mass $M_{\rm tot}$ produced at $t=10$\,Gyr.
-Left: The four \agb\ yield models from literature at solar metallicity (\cxi, \kx{}, \vxiii{}, or \kxvi{}).
+\textbf{Left:} The four \agb\ yield models from literature at solar metallicity (\cxi, \kx{}, \vxiii{}, or \kxvi{}).
 The \gls{dtd} of type Ia supernovae ($\propto t^{-1.1}$) is plotted as a dashed black line for comparison.
-Right: The \cxi\ \agb\ model at different metallicities.
+\textbf{Right:} The \cxi\ \agb\ model at different metallicities.
 }
@@
 
-    \caption[Low mass yield metallicity dependence]{The net fractional \imf-weighted \agb\ C yield $\Ycagb$ as a function of metallicity for each of our \agb\ yield models.
-$\Ycagb$ is the net mass of C produced by \agb\ stars per unit mass of star formation, after 10\,Gyr and assuming a \citet{kroupa01} \imf.
+    \caption[Low-Mass-Star Yield Metallicity Dependence]{The net fractional \imf-weighted \agb\ C yield $\Ycagb$ as a function of metallicity for each of our \agb\ yield models.
+($\Ycagb$ is the net mass of C produced by \agb\ stars per unit mass of star formation, after 10\,Gyr and assuming a \citet{kroupa01} \imf.)
     }
@@
 
-Massive stars form $^{12}$C in their cores through the triple--$\alpha$ process. However, only C ejected through supernovae and stellar winds contributes to the yield. 
+Massive stars form $^{12}$C in their cores through the triple--$\alpha$ process (see Appendix \ref{sec:stel_evo}).
+However, only C ejected through supernovae and stellar winds contributes to the yield.
 While there are many stellar models providing predictions of \cc{} yields, the results of these models are highly uncertain due to the many stellar modeling uncertainties.
 
-In Fig.~\ref{fig:y_cc}, I plot calculations of the \imf-integrated yields, defined with Eq.~\ref{eq:imf-yield} (computed using \VICE's \texttt{vice.yields.ccsne.fractional} function). 
-\cc{} models predict a wide range of C yields, spanning almost 1 dex. 
+Fig.~\ref{fig:y_cc} plots calculations of the \imf-integrated yields, defined with Eq.~\ref{eq:imf-yield} (computed using \VICE's \texttt{vice.yields.ccsne.fractional} function). 
+\Gls{cc} models predict a wide range of C yields, spanning almost 1 dex. 
 Both the \citet{NKT13} and \cite{LC18} models show positive metallicity dependence. 
-The \cite{LC18} models also include rotation, showing that variations in the rotational velocity of the star can dramatically increase C production and the metallicity dependence of $\Ycc$.
+The \cite{LC18} models also include rotation, showing that variations in the rotational velocity of the star can dramatically increase the magnitude and metallicity dependence of $\Ycc$.
 Rotation induces more mixing allowing the CO core to grow larger.
-As I will later show, \cc\ C production needs to be strongly metallicity-dependent at $Z/Z_\odot \approx 1$, which is consistant with the \cite{LC18} rapidly rotating models.
-
-Fig.~\ref{fig:y_cc} shows the \cxi{} model for comparison on the top.
+As I will later show, \cc\ C production needs to be strongly metallicity-dependent at $Z/Z_\odot \approx 1$, which is consistent with the \cite{LC18} rapidly rotating models.
+
+Fig.~\ref{fig:y_cc} shows the \cxi{} \agb\ model for comparison on the top.
 Especially at $Z\approx Z_\odot$, most \cc{} models dominate \agb\ C production.
-I will later also show empirically that \cc{} should dominate C production.
+Later, I will also show empirically this is the case.
 On the bottom of Fig.~\ref{fig:y_cc}, I also show the \cc{}-[C/Mg] ratio, defined by
@@
 However, C is relatively unaffected by the black-hole landscape, as very massive stars contribute C through enriched winds.
-Since Mg is formed deeper in the core of \gls{highmass}s, the Mg yield drops much more steeply, so models, where few stars explode (S16/W18), result in much higher [C/Mg].
-
-\Cc\ models also do not reach [O/Mg] due to overproduction of O, or underproduction of Mg, or both \citep{emily+21}.
+Since Mg is formed deeper in the core of \glspl{highmass}, the Mg yield drops much more steeply, so models where few stars explode (S16/W18) have higher [C/Mg].
+
+\Cc\ models also do not reach [O/Mg] due to overproduction of O or underproduction of Mg, or both \citep{emily+21}.
 Here, I assume ${\rm [O/Mg]} = 0$, which is not compatible with \cc\ models but is consistent with \apogee{} observations \citep{weinberg+19, weinberg+22}.
@@
     \includegraphics{y_c_cc.pdf}
-    \caption[Massive star C yields]{
+    \caption[High-Mass Star Carbon Yields]{
         C yields from high-mass stars.
         \textbf{Top:} The \imf-weighted \cc\ yield of C as a function of metallicity.
-        \textbf{Bottom:} The \cc\ [C/Mg] abundance ratio, defined in Eq.~\ref{eq:c_mg_cc}. The black line is the derived C yield from section \ref{sec:equilibrium},
+        \textbf{Bottom:} The \cc\ [C/Mg] abundance ratio, defined in Eq.~\ref{eq:c_mg_cc}. The black line is the derived C yield from Section \ref{sec:equilibrium},
     $\Ycc = 0.0028 + 0.001 (Z/Z_{\odot})$. Yields are shown for tables from 
@@
 Newly produced metals are homogeneously and instantaneously mixed, so spatial dependence is neglected.
-I define $M_{X}$ to be the mass of element X in the gas phase, $\dot{M}_\star$ to be the star formation rate (in M$_\odot$ yr$^{-1}$), and $\eta$ to be the mass loading factor $\eta\equiv\dot{M}_{\rm outflow}/\dot{M}_\star$ (representing the strength of outflows).
-\ssp's return a fraction $r$ of their birth mass back to the interstellar medium, due to ejected stellar envelopes.
-($r\approx0.4$ for a \citealt{kroupa01} \imf.)
-Given the \gls{imfave} yield of Mg $y_{\rm Mg}$, the rate of change in the gas-phase mass of Mg $\dot{M}_{\rm Mg}$ is a simple sum of sources and sinks,
+I define $M_{X}$ to be the mass of element $X$ in the gas phase, $\dot{M}_\star$ to be the star formation rate (in M$_\odot$ yr$^{-1}$), and $\eta$ to be the mass loading factor $\eta\equiv\dot{M}_{\rm outflow}/\dot{M}_\star$ (representing the strength of outflows).
+A \ssp\ returns a fraction $r$ of their birth mass to the interstellar medium, due to ejected stellar envelopes.
+\footnote{$r\approx0.4$ for a \citealt{kroupa01} \imf.}
+Given the \gls{imfave} yield of Mg $y_{\rm Mg}$, the rate of change in the gas-phase mass of Mg is a simple sum of sources and sinks,
 \begin{equation}
-    \dot{M}_{\rm Mg} =  y_{X}\dot{M}_\star - \dot{M}_{\rm Mg~remnants} - \dot{M}_{\rm Mg,~outflows},
+    \dot{M}_{\rm Mg} =  y_{X}\,\dot{M}_\star - \dot{M}_{\rm Mg~remnants} - \dot{M}_{\rm Mg,~outflows},
 \end{equation}
 where the first term on the right-hand side describes \cc\ enrichment. 
-In terms of the return mass fraction of stars $r$, the mass lost to remnants is $Z_X (1-r)\dot{M}_\star$.
-And, the outflows deplete mass at a rate $Z_X \eta\dot{M}_\star$.
-( I assume the composition of outflows is the same as the interstellar medium.) Substituting for $\eta$ and $r$,
+In terms of the return mass fraction of stars $r$, the mass lost to remnants is $Z_X\,\dot{M}_\star\,(1-r)$.
+And, the outflows deplete mass at a rate $Z_X \,\dot{M}_\star\,\eta$.
+(I assume the composition of outflows is the same as the interstellar medium.) Substituting for $\eta$ and $r$,
 \begin{equation}
@@
 \end{equation}
-where $\tau_{\star}$ is the star formation rate. $\eta$ depends on $R$, as 
+where $\tau_{\star}$ is the star formation rate. ($\eta$ depends on $R$ to create a metallicity gradient. See also Section \ref{sec:vice} and Eq.~\ref{eq:eta_r}.)
 In the special case of constant star formation, $\tau_{\rm sfh}\to\infty$, the denominator simplifies to $1+\eta-r$.
 
-For \agb\ stars, the above equation is more complex in detail, as the \agb\ contribution depends on the \sfh.
-However, for an exponential decay, this effect is minimal, so I simply use $\Ycagb$ for the current \agb\ contribution.
+Likewise, for \agb\ stars,
+\footnote{In detail, the \agb\ contribution requires integration over the \sfh\ to account for the finite lifetimes of stars.
+However, for this exponential \sfh, this effect is minimal, so I simply use $\Ycagb$ for the current \agb\ contribution.}
 Eq.~\ref{eq:z_eq} then becomes
@@
 
-As I will discuss in section \ref{sec:outflows}, the normalization of yields and $\eta$ is degenerate.
+As I will discuss in Section \ref{sec:outflows}, the normalization of yields and $\eta$ is degenerate.
 This can be observed in Eq.~\ref{eq:z_co}, where changes in $\eta$ or the scaling of $y_{\rm C}/y_{\rm Mg}$ would not affect equilibrium trends.
 Furthermore, in Eq.~\ref{eq:z_eq}, an increase in both $y_{\rm Mg}$ and $\eta$ would leave $Z_{\rm Mg}^{\rm eq}$ unchanged.
-My models here are unable to distinguish the overall scaling of yields and outflow mass loading, and choosing to keep $y_{\rm C}$ fixed reduces unnecessary free parameters.
-%
-As a result, I choose to leave the total C yield fixed at solar $Z$,
+My models here are unable to distinguish the overall scaling of yields and outflow mass loading.
+So, choosing to keep $y_{\rm C}$ fixed reduces unnecessary free parameters.
+So, at solar metallicity, I set
 \begin{subequations}
@@
 
-In section \ref{sec:f-z-models}, I will show that none of the four \agb\ yield sets (\cxi{}, \kx{}, \vxiii{}, \kxvi{}) produce enough C relative to this $\Ycc$ value.
+In Section \ref{sec:f-z-models}, I will show that none of the four \agb\ yield sets (\cxi{}, \kx{}, \vxiii{}, \kxvi{}) produce enough C relative to this $\Ycc$ value.
 So, I introduce normalization factors, $\alpha_{\rm AGB}$, and $\alpha_{\rm CC}$ which denote a multiplicative scaling of $\Ycc$ and $\Ycagb$ respectively.
@@
     \begin{align}
-        \Ycagb &\rightarrow \alpha_{\rm AGB} \left(\Ycagb\right) \\
-        \Ycc &\rightarrow \alpha_{\rm CC} \left(\Ycc\right)\\
-        \alpha_{\rm CC} &= \frac{\Yct - \alpha_{\rm AGB} \left(\Ycagb\right)}{\Ycc}
+        \Ycagb &\rightarrow \alpha_{\rm AGB}\ \Ycagb \\
+        \Ycc &\rightarrow \alpha_{\rm CC}\ \Ycc\\
+        \alpha_{\rm CC} &= \frac{\Yct - \alpha_{\rm AGB}\ \Ycagb}{\Ycc}
     \end{align}
@@
 
-In section \ref{sec:f-z-models}, I find that $\alpha_{\rm AGB}\approx 2.9$ for the \cxi{} yield model.
+In Section \ref{sec:f-z-models}, I find that $\alpha_{\rm AGB}\approx 2.9$ for the \cxi{} yield model.
 Using this \agb\ yield, I can now use Eq.~\ref{eq:y_c_eq} to find an estimate of $\Ycc$ as a function of metallicity.
 I show the values of $\Ycc$ I obtain from the \gls{subgiant} sample in Fig.~\ref{fig:analytic}.
-From regression analysis, I suggest here that
+From a regression analysis, I suggest here that
 \begin{equation}\label{eq:zeta}
@@
 \end{equation}
-where $\zeta$, describing the metallicity dependence, is $\zeta\approx0.001$.
+where $\zeta\approx.001$ describes the metallicity dependence.
 
@@
     \includegraphics[]{analytic.pdf}
-    \caption[Reverse fit yields]{Inferred high-mass star C yields as a function of metallicity.
+    \caption[Reverse-Fit Yields]{Inferred high-mass star C yields as a function of metallicity.
 I assume equilibrium and $3\times {\rm C11}$ \agb\ yields (orange curve, see discussion in Section \ref{sec:equilibrium}).
@@
 As the metallicity range of the data is small ($-0.4\lesssim {\rm [Mg/H]} \lesssim 0.4$), other models are more challenging to interpret in this range.
-Furthermore, the \apogee{} observations may have systematics, and other measurements of C abundances \citep[e.g.][]{vincenzo+21} have slight disagreements in the overall shape of the trend (see section \ref{sec:jack}).
+Furthermore, the \apogee{} observations may have systematics, and other measurements of C abundances \citep[e.g.][]{vincenzo+21} have slight disagreements in the overall shape of the trend (see Section \ref{sec:jack}).
 So, this expression of $\Ycc/\Yoc$ depends on the chosen \agb\ yield table, the \agb\ fraction, and the dataset. 
-Additionally, these yields will be systematically biased if the galaxy is out of equilibrium, for example due to a recent starburst (Isern et al.
+Additionally, these yields will be systematically biased if the galaxy is out of equilibrium, for example, due to a recent starburst (Isern et al.
 19; Mar et al.
@@
 Classical, \textit{\gls{onezone}} models of chemical evolution assume instantaneous mixing of metals in the star-forming interstellar medium \citep[e.g.][]{matteucci21}.
-This simple framework is a poor approximation for the Milky Way.
-The Galaxy evolves ``inside out''---where star formation is higher towards the center and in the early universe \citep{bird+13}.
-Additionally, stars can migrate several kpc over their lifetimes, mixing together different chemical environments across the galaxy \citep{bird+12,sellwood+binney02}.
-For the rest of this paper, I focus on \gls{multizone} models, which discretize the Galaxy into concentric annuli and allow stars to move between rings.
+This simple framework is a poor approximation of the Milky Way.
+The Galaxy evolves \gls{insideout}---where star formation is higher towards the center and in the early universe \citep{bird+13}.
+Additionally, stars can migrate several kpcs over their lifetimes, mixing different chemical environments across the galaxy \citep{bird+12,sellwood+binney02}.
+For the rest of this paper, I focus on \gls{multizone} models, which discretize the Galaxy into concentric rings in which stars move between.
 Specifically, I make use of the \citet{james+21} (hereafter \JJ) model for the Milky Way, which runs using the publicly available Versatile Integrator for Chemical Evolution (\VICE).
@@
 Star formation ends beyond a radius $R=15.5$ kpc.
-I initially assume an ``inside-out'' \sfh{}, where the star formation surface density $\Sigma_\star$ is given by
-\begin{equation}
+I initially assume an \gls{insideout} \sfh{}, where the star formation surface density $\Sigma_\star$ is given by
+\begin{equation}\label{eq:inside_out}
     \dot{\Sigma}_\star \propto \left(1-e^{-t/\tau_{\rm rise}}\right) e^{-t/\tau_{\rm sfh}}.
@@
 \JJ~derives $\tau_{\rm sfh}(R)$ through analysis of four integral field spectroscopy surveys in \cite{sanches20}.
-The star formation history is normalized such that the total stellar mass reaches $M_\star=5.17\times10^{10} {\rm M}_\odot$ \citep{LM15} and at each $R$ to match the stellar surface density gradient \citep{BHG16}.
-The gas inflow is calculated to maintain our chosen \sfh{} for each radius and time. The gas-SFR law is based on an extension of a Kennicutt-Schmidt law \citep{kennicutt98}, motivated by 
+The star formation history is normalized such that the total stellar mass reaches $5.17\times10^{10} {\rm M}_\odot$ \citep{LM15} and at each $R$ to match the stellar surface density gradient \citep{BHG16}.
+The gas inflow is calculated to maintain our chosen \sfh{} for each radius and time. The gas-star-formation law is based on an extension of a Kennicutt-Schmidt law \citep{kennicutt98}
 \begin{equation}
@@
 \end{equation}
-The scaling of this relationship varies with time due to the redshift dependence of $\tau_\star$ in molecular gas observed by \citet{tacconi18}. I assume a Kroupa \imf \cite{kroupa01}.
+The scaling of this relationship varies with time due to the redshift dependence of $\tau_\star$ in molecular gas observed by \citet{tacconi18}. I assume a \citet{kroupa01} \imf.
 
@@
 Using the results of a hydrodynamical simulation without modification limits the free parameters in the model; however, I am limited to one dynamical history.
-The impact of the details of a galaxy's dynamical history on its chemical evolution is unknown, and I do not explore this question here.
+The impact of the details of a galaxy's dynamical history on its chemical evolution is unknown.
 
 As the strength of outflows controls the resulting $\alpha$ abundances, \JJ~create a metallicity gradient by defining
-\begin{equation}
+\begin{equation}\label{eq:eta_r}
 \eta(R) = \frac{y_{\alpha}^{\rm CC}}{Z_{\alpha, \odot}} 10^{(-0.08\text{ kpc}^{-1})(R-4\text{ kpc})+0.3} + r - 1.
@@
 
-\citet{james+23} compare their model against the \cite{vincenzo+21} sample of \apogee{} \citep{apogee17} \gls{rgb} C and N abundance have been corrected for mixing process using \textsc{mesa} stellar evolution models \citep{mesa}.
+\citet{james+23} compare their model against the \cite{vincenzo+21} sample of \apogee{} \citep{apogee17} \gls{rgb} stars.
+\citet{vincenzo+21} use \textsc{mesa} stellar evolution models \citep{mesa} to correct for the effects of \gls{fdu}.
 I instead use the \citetjack~sample of \apogee{} \gls{subgiant}s.
-Subgiant stars have not undergone first dredge up but have well mixed atmospheres, so their atmospheric C and N abundances are still reflective of their birth abundances and do not need mixing corrections.
+Subgiant stars have not undergone \gls{fdu} but have well-mixed atmospheres, so their atmospheric C and N abundances are still reflective of their birth abundances and do not need mixing corrections.
 I only compare the models to the \gls{lowalpha} sequence unless otherwise specified.
@@
 
-Here, I present the time evolution of our fiducial model. In the next sections, I will discuss the choice of parameters and agreement with observations. 
+Here, I present the time evolution of our fiducial model. In the next Sections, I will discuss the choice of parameters and agreement with observations. 
 The fiducial model has the following qualitative characteristics of its C yields: (a) C is predominantly produced in \cc, (b) \cc\ produce more C at higher metallicities, and (c) \agb\ stars produce less C at higher metallicities.
-The fiducial model uses the \cxi{} \agb\ yield tables (see section \ref{sec:agb}, and Table \ref{tab:fiducial_mod}), and I amplify the \cxi{} yields by a factor of 2.9 such that \agb\ stars account for 20\% of C at $Z=Z_\odot$.
+The fiducial model uses the \cxi{} \agb\ yield tables (see Section \ref{sec:agb}, and Table \ref{tab:fiducial_mod}), and I amplify the \cxi{} yields by a factor of 2.9 such that \agb\ stars account for 20\% of C at $Z=Z_\odot$.
 
@@
 Comparing [C/Mg] against [Mg/Fe] enables us to see the late-time evolution of C more clearly.
-Because of the extended \gls{dtd} of \ia\ enrichment, [Fe/H] takes longer to reach equilibrium as half of Fe production comes from type-Ia supernovae, and the late time evolution is not as clustered as [Mg/H].
+Because of the extended \gls{dtd} of \ia\ enrichment, [Fe/H] takes longer to reach equilibrium, and the late-time evolution is not as clustered as [Mg/H].
 The evolution proceeds as follows.
@@
 \includegraphics{evo_slices.pdf}
-\caption[C chemical evolution tracks]{
+\caption[Carbon Chemical Evolution Tracks]{
     Time evolution of gas phase C abundances in our fiducial model.
@@
 
-\section{Alternate Models}\label{sec:f-z-models}
+\section{Low and High-Mass Stellar Yields}\label{sec:f-z-models}
 
@@
 Fig.~\ref{fig:agb_sims} compares the \kx{}, \kxvi{}, \cxi{}, and \vxiii{} yield models.
-Here, I use the published, unscaled yield tables ($\alpha_{\rm AGB}=1$).
+I use the published, unscaled yield tables ($\alpha_{\rm AGB}=1$) for Fig.~\ref{fig:agb_sims}.
 As the highest \agb\ yield at solar, \kx{} is only $\Ycagb=0.000585$, $f_{\rm AGB} \leq 0.12$ for all models.
@@
 \includegraphics{agb_oob.pdf}
-\caption[Mean stellar abundance trends]{
+\caption[Median Stellar Abundance Trends]{
     Stellar abundance trends in our model, assuming metallicity independent $\Ycc$.
 Colored lines quantify the median [C/Mg] in bins of [Mg/H] for our four \agb\ yield models from the literature (see \ref{sec:agb}).
-Black points and grey dashes represent the median and standard deviations in the \citetjack~sample.
+Black points and grey dashes represent the median and standard deviations of [C/Mg] for each [Mg/H] bin in the \citetjack~sample.
 In the right panel, I show the trends only for stars where $-0.15\leq {\rm [Mg/H]}\leq -0.05$.
@@
 On the top panel of Fig.~\ref{fig:beta_f}, I plot models with varying $\Ycc$ metallicity dependence.
-As discussed in section \ref{sec:equilibrium}, the \caah~trend is approximated by equilibrium, so the trends of these have steeper \caah~corresponding to steeper metallicity dependence.
+As discussed in Section \ref{sec:equilibrium}, the \caah~trend is approximated by equilibrium, so the trends of these have steeper \caah~corresponding to steeper metallicity dependence.
 However, \caafe~is minimally affected by these changes since \cc\ occurs on much shorter timescales than \ia\ and \agb\ enrichment.
@@
 In the bottom panel of Fig.~\ref{fig:beta_f}, I plot three models with different \agb\ fractions while using \cxi{} yields.
-The \caafe~relationship is set by $f_{\rm AGB}$ because a specific amount of C must be released at a delayed time in order to match the \ia\ production of Fe and increase [C/Mg] as [Mg/Fe] decreases to reproduce the data.
+The \caafe~relationship is set by $f_{\rm AGB}$ because a specific amount of C must be released at a delayed time to match the \ia\ production of Fe and increase [C/Mg] as [Mg/Fe] decreases to reproduce the data.
 Increased $f_{\rm AGB}$ results in a decreased slope in \caah, owing to the negative metallicity dependence of $\Ycagb$.
 So while \caah~alone cannot differentiate models which vary $f_{\rm AGB}$ and $\zeta$ correspondingly, \caafe~provides information on $f_{\rm AGB}$.
-So, I can use \caafe~to estimate $f_{\rm AGB}\approx 0.2$, and then choose $\zeta$ in order to match \caah.
+So, I can use \caafe~to estimate $f_{\rm AGB}\approx 0.2$, and then choose $\zeta$ to match \caah.
 
@@
 I discuss variations in $y_{\rm Fe}^{\rm Ia}$ in Appendix \ref{sec:alt_agb}, and find that the qualitative conclusions are largely unaffected.
-I therefore focus on the choices of $y_{\rm Fe}^{\rm Ia} = 0.00214$ and a $\propto t^{-1.1}$ \gls{dtd} choices from the fiducial model here.
+I, therefore, focus on the choices of $y_{\rm Fe}^{\rm Ia} = 0.00214$ and a $t^{-1.1}$ \gls{dtd} choices from the fiducial model here.
 In short, the scaling of the trend and metallicity dependence of C (as seen in
@@
 	\centering
-    \caption[Low mass star solar C yields]{For each \agb\ yield set, the \imf-weighted C \agb\ yield at solar metallicity, along with the multiplicative factor reaches an \agb\ contribution of 20\%.}
+    \caption[Low-Mass Stellar Carbon Yields at Solar Metallicity]{For each \agb\ yield set, the \gls{imfave} \agb\ C yield at solar metallicity $y_{\rm C, 0}^{\rm AGB}$ and the multiplicative factor reaches an \agb\ contribution of 20\% $\alpha_{\rm AGB, 20}$.}
 	\label{tab:alpha_agb}
@@
 
-\caption[Adjusted yield models]{Similar to Fig.~\ref{fig:agb_sims} except the top plot shows the fiducial model with lower and higher values of $\zeta$, the meatllicity dependence of $\Ycc$.
+\caption[Adjusted Yield Models]{Similar to Fig.~\ref{fig:agb_sims} except the top plot shows the fiducial model with lower and higher values of $\zeta$, the metallicity dependence of $\Ycc$.
 The bottom plot shows models with $f_{\rm AGB}=$0.1, 0.2, and 0.4.
@@
 
-\caption[Lateburst models]{Same as Fig.~\ref{fig:agb_sims} but comparing the fiducial model to alternate \sfh{}s (see section  \ref{sec:sfh}).}
+\caption[Alternate Star-Formation-History Models]{Similar to Fig.~\ref{fig:agb_sims} but comparing the fiducial model to alternate \glspl{sfh} (see Section  \ref{sec:sfh}).}
 \label{fig:sfh_models}
@@
 
-Here, I consider a "late-burst" model, created by multiplying our fiducial "inside-out" \sfh{} with a Gaussian.
+Here, I consider a \textit{lateburst} model, created by multiplying our fiducial \gls{insideout} \sfh{} with a Gaussian.
 \begin{equation}\label{eq:lateburst}
-    \dot{\Sigma}_{\rm late-burst} \propto \dot{\Sigma}_{\rm insideout} \left(1 + A\,e^{-(t-\tau_{\rm burst})^2/2\sigma^2_{\rm burst}} \right)
+    \dot{\Sigma}_{\rm lateburst} \propto \dot{\Sigma}_{\rm insideout} \left(1 + A\,e^{-(t-\tau_{\rm burst})^2/2\sigma^2_{\rm burst}} \right)
 \end{equation}
@@
 $A=1.5$ represents the amplitude of the birth, $\tau_\text{burst}=10.8$\,Gyr is the time where the burst is strongest, and $\sigma_\text{burst}=1$\,Gyr is the width of the burst.
-I also consider an earlyburst model as a slight variation of the late-burst, where the burst is instead exponential and placed at $t_1=5$\,Gyr. 
+I also consider an \textit{earlyburst} model as a slight variation of the lateburst, where the burst is instead exponential and placed at $t_1=5$\,Gyr. 
 \begin{equation}\label{eq:twoinfall}
-    \dot{\Sigma}_{\rm early-burst} \propto \dot{\Sigma}_{\rm insideout} + 
+    \dot{\Sigma}_{\rm earlyburst} \propto \dot{\Sigma}_{\rm insideout} + 
 \begin{cases}
@@
 Additionally, the early burst
-is able to reproduce the slight break between the low and high $\alpha$ sequences, but overshoots equilibrium more severely than the fiducial model. 
+reproduces the slight break between the low and high $\alpha$ sequences, but overshoots equilibrium more severely than the fiducial model. 
 In general, any of these \sfh{}s are consistent with this model.
@@
 
-\gce{} models of the Milky Way fall into two classes---those which incorporate significant mass-loading (e.g., as in this work) and those which neglect mass-loading but lower effective yield to match observed abundances \citep[e.g.][]{MCM13, MCM14, spitoni19, spitoni20, spitoni21}.
+\Gce{} models of the Milky Way fall into two classes---those which incorporate significant mass-loading (e.g., as in this work) and those which neglect mass-loading but lower effective yield to match observed abundances \citep[e.g.][]{MCM13, MCM14, spitoni19, spitoni20, spitoni21}.
 An increase in stellar yields has a nearly identical effect as a decrease in the mass-loading factor $\eta$ (see Appendix B of \citealt{james_dwarf}).
-The equilibrium arguments discussed in section \ref{sec:equilibrium} suggest however that abundance ratios are independent of the choice of normalization and the value of $\eta$.
-I therefore expect my results regarding the relative yield $y_{\rm C}/y_{\rm Mg}$ and its metallicity dependence to extend to the other class of models omitting mass loading.
+The equilibrium arguments discussed in Section \ref{sec:equilibrium} suggest however that abundance ratios are independent of the choice of normalization and the value of $\eta$.
+I, therefore, expect my results regarding the relative yield $y_{\rm C}/y_{\rm Mg}$ and its metallicity dependence to extend to the other class of models omitting mass loading.
 I demonstrate this further here.
@@
 The theoretical motivation for decreasing yields is the uncertainty in stellar explodability.
-If fewer \gls{highmass}s explode, then the yields will be reduced by some factor.
+If fewer \glspl{highmass} explode, then the yields will be reduced by some factor.
 Additionally, some fraction of SN ejecta may be lost directly to an outflow, lowering effective yields.
@@
 While changing the value of $\eta$ affects the metallicity distribution of stars, all of the models in Fig.~\ref{fig:eta} still evolve along the same path.
-My model is unable to tell apart a uniform decrease in both outflows and yields.
+My model is unable to differentiate a uniform decrease in both outflows and yields.
 
@@
     \includegraphics{eta.pdf}
-    \caption[Reduced-outflow models]{Same as Fig.~\ref{fig:agb_sims} but comparing the fiducial model to reduced mass loading models (see section  \ref{sec:outflows}).
+    \caption[Reduced-Outflow Models]{Similar to Fig.~\ref{fig:agb_sims} but comparing the fiducial model to reduced mass loading models (see Section  \ref{sec:outflows}).
 Both yields and mass-loading are adjusted correspondingly such that the equilibrium abundances are unchanged.
@@
 The model reproduces this 2-dimension distribution well when including scatter based on the median \apogee{} abundance errors for each metallicity bin.
-Some of the scatter is due to radial migration, but observational errors are dominant.
+Some scatter is due to radial migration, but observational errors are dominant.
 Precision abundance measurements will allow tighter constraints on relative yields.
@@
     \includegraphics[scale=0.9]{cooh_scatter.pdf}
-    \caption[Scatter agreement]{The stars in the fiducial model in the \caah~plane perturbed by the median [Mg/H] and [C/Mg] measurement errors in the \citetjack~sample.
+    \caption[Scatter Agreement]{The stars in the fiducial model in the \caah~plane compared to contours of the \gls{subgiant} sample.
+I added random noise to the scatter points equal to the median uncertainties in the \gls{subgiant} sample.
 Stars are color-coded such that lighter colors represent populations born at greater galactocentric radii.
@@
 
-\section{Gas-Phase C Abundances}\label{sec:gas}
+\section{Gas-Phase Abundances}\label{sec:gas}
 
 As an additional test of the model, I next compare the model predictions against gas-phase measurements.
-Fig.~\ref{fig:gas_phase} shows the fiducial model's gas phase predictions compared to observations of MW and extragalactic HII regions, halo stars, and \dla\ systems.
+Fig.~\ref{fig:gas_phase} shows the fiducial model's gas phase predictions compared to observations of the Milky Way and extragalactic HII regions, halo stars, and \dla\ systems.
 The model is broadly consistent with observations, where the model at $t=2$\,Gyr approximates the slope of dwarf galaxies and halo stars.
@@
 
-Stellar measurements of Mg are more reliable, but O abundances are easier to measure in HII regions.
-I therefore use Mg abundances from the \citetjack~\gls{subgiant} sample as my primary empirical constraint.
-However, I use O abundances for gas-phase measurements and low-metallicity stars (section  \ref{sec:gas}).
-While I use Mg as the representative \gls{alpha} for stellar abundances, I instead us O when comparing gas-phase abundances.
-
-Measurments of C abundances in the gas-phase are challenging.
-In HII-regions, C/O abundance ratios are measured with either recombination lines or collisionally excitation lines.
+Mg measurements are more reliable, but O abundances are easier to measure in HII regions.
+So while I use Mg as the representative \gls{alpha} for stellar abundances, I instead use O when comparing gas-phase abundances.
+As I assume ${\rm[Mg/O]}=0$, my model is independent of the choice of the \gls{alpha}
+
+Measurements of C abundances in the gas-phase are challenging.
+In HII regions, C/O abundance ratios are measured with either recombination lines or collisional excitation lines.
 However C lacks strong collisional excitation lines, and recombination lines fall in the ultraviolet without nearby reference H lines \citep{skillman+20}.
-Additionally, recombination and collisionally excitation measurements disagree by a factor of \about{2} \citep{GR07}.
-Additionally, variations in the \sfh{}s may be a source of scatter, as C contains delayed enrichment, and bursts cause variations in C/O.
+Additionally, recombination and collisional excitation measurements disagree by a factor of \about{2} \citep{GR07}.
+Variations in the \sfh{}s may furthermore increase scatter, as \agb\ are a delayed source of C.
 
 The decreasing [C/O] abundance at very-low metallicities is likely due to population III stellar yields \citep[e.g.][]{hirschi07}, as suggested by \citet{cooke+17} and \citet{FN15}.
-\agb\ stars cannot explain the increase in C yields at low metallicity in the \dla{} sample as the evolutionary timescales of \dla{}s are shorter than the typical delay time distribution of \agb\ stars.
+\Gls{agb} stars cannot explain the increase in C yields at low metallicity in the \dla{} sample as the evolutionary timescales of \dla{}s are shorter than the typical delay time distribution of \agb\ stars.
 
@@
     \includegraphics{c_n.pdf}
-    \caption[C/N abundance agreement]{Similar to Fig.~\ref{fig:agb_sims}, except comparing [C/N] from the fiducial model only.
+    \caption[C/N Abundance Agreement]{Similar to Fig.~\ref{fig:agb_sims}, except comparing [C/N] from the fiducial model only.
 N yields are adapted from \cite{james+23}.
@@
 \includegraphics[]{summary.pdf}
-\caption[Gas phase abundances]{Gas-phase C abundances. We plot our model at $t=2$\,Gyr and present day as thick solid lines. Points represent measurements in 
+\caption[Gas-Phase Abundances]{Gas-phase C abundances. We plot our model at $t=2$\,Gyr and present day as thick solid lines. Points represent measurements in 
     HII regions    \citep[pink circles;][]{skillman+20, esteban+02, esteban+09, esteban+14, esteban+19}
@@
 Though \cc\ C yields are poorly understood, I adopt an equilibrium approximation and determine a functional form that approximately matches trends in \apogee{} \gls{subgiant} and is consistent with \gls{highmass} \gls{nucleosynthesis} models.
-Variations of the metallicity dependence of this \cc\ yield affect trends in \caah~but do not affect trends in \caafe\ when taking a slice in [Mg/H].
+Variations of the metallicity dependence of this \cc\ yield affect trends in \caah~but do not affect trends in \caafe\ (when taking a slice in [Mg/H]).
 As all theoretical \agb\ C yields decrease with metallicity, increasing the \agb\ fraction causes the \caah\ trend to flatten.
@@
 The remaining \about{80\%} of C comes from \gls{highmass} with a metallicity dependent yield of $\Ycc/\Yoc=1.51 + 0.54 (Z/Z_\odot)$.
-This metallicity dependence is consistent with the rotating stellar models of \citet{LC18}.
+This metallicity dependence is roughly consistent with rotating stellar yields.
 
@@
 While my model was built on data near solar metallicity, observations of very low metallicity, high redshift damped Lyman-$\alpha$ systems indicate higher C/O ratios \citep{cooke+17}, consistent with yields from population III stars \citep[e.g.][]{hirschi07}.
-Our combined results self-consistently explain C abundances.
+Population III stars, \cc\, and \agb stars altogether explain the observed evolutionary history of C.
 
 These C yield constraints provide a useful benchmark for stellar evolution models.
-C yields are sensitive to poorly understood processes, including mass loss prescriptions, explodability, nuclear cross sections, convection, and stellar structure.
+C yields are sensitive to poorly understood processes, including mass loss prescriptions, explodability, nuclear cross Sections, convection, and stellar structure.
 Future spectroscopic surveys combined with Gaia kinematics \citep{gaia} will continue to enhance our understanding of chemical evolution.
-Both the Sloan Digital Sky Survey V's Milky Way Mapper program ({\sc SDSS-V/MWM}) \citep{sdssv} and the Dark Energy Spectroscopic Instrument ({\sc DESI}) Milky Way survey \citep{desi, desi:mw} will each measure spectra of $>6$ million Milky Way stars.
+Both the Sloan Digital Sky Survey V's Milky Way Mapper program ({\sc SDSS-V/MWM}) \citep{sdssv} and the Dark Energy Spectroscopic Instrument ({\sc DESI}) Milky Way survey \citep{desi, desi:mw} will each measure spectra of upwards 6,000,000 Milky Way stars.
 These larger samples will enable similar work to tighten constraints on stellar models and our understanding of galaxy structure and evolution.
@@
 \appendix
-\chapter*{Appendix}
-\addcontentsline{toc}{chapter}{Appendix}
-\renewcommand{\thesection}{A.\arabic{section}}
-\renewcommand\thefigure{A.\arabic{figure}}    
-\renewcommand\theequation{A.\arabic{equation}}    
-\setcounter{figure}{0}
-\setcounter{equation}{0}
-
-\renewcommand*{\theHsection}{A.\arabic{section}}%
-\renewcommand*{\theHsubsection}{A.\arabic{subsection}}%
-\renewcommand*{\theHfigure}{A.\arabic{figure}}%
-\renewcommand*{\theHequation}{A.\arabic{equation}}%
-
-\section{The APOGEE Subgiant Sample}\label{sec:jack}
-
-As the primary observational constraint, I use the criteria outlined in \citetjack~to create a sample of \gls{subgiant}s from \apogee{} DR17 \citep{apogee17}.
-\apogee\ is part of the Sloan Digital Sky Survey 17 and measures high resolution spectra of thousands of stars \cite{sdss17}.
-Chemical abundance are determined from the \apogee\ Stellar Parameter and Chemical Abundance Pipeline ({\sc aspcap}) \citep{aspcap}.
-
-Photospheric C and N abundances in \gls{subgiant}s are reflective of their birth abundances \citep{gilroy89, korn+07, lind+08, souto+18, souto19} As \gls{fdu}, which affects C and N abundances, only occurs during the ascent onto the \gls{rgb}, \gls{subgiant} stars are unaffected by this enrichment.
-
-An alternate approach for this analysis would be to estimate the birth abundances of \gls{rgb}s by correcting surface abundance effects from \gls{fdu} as in \cite{vincenzo+21}.
+% \chapter*{Appendix}
+% \addcontentsline{toc}{chapter}{Appendix}
+% \renewcommand{\thesection}{A.\arabic{section}}
+% \renewcommand\thefigure{A.\arabic{figure}}    
+% \renewcommand\theequation{A.\arabic{equation}}    
+% \setcounter{figure}{0}
+% \setcounter{equation}{0}
+% 
+% \renewcommand*{\theHsection}{A.\arabic{section}}%
+% \renewcommand*{\theHsubsection}{A.\arabic{subsection}}%
+% \renewcommand*{\theHfigure}{A.\arabic{figure}}%
+% \renewcommand*{\theHequation}{A.\arabic{equation}}%
+
+\chapter{The Subgiant Sample}\label{sec:jack}
+
+As the primary observational constraint, I use the criteria outlined in \citetjack~to create a sample of \glspl{subgiant} from \apogee{} DR17 \citep{apogee17}.
+\Gls{apogee} is part of the Sloan Digital Sky Survey and measures high-resolution spectra of thousands of stars \cite{sdss17}.
+Chemical abundances are determined from the \apogee\ Stellar Parameter and Chemical Abundance Pipeline ({\sc aspcap}) \citep{aspcap}.
+
+Photospheric C and N abundances in \glspl{subgiant} are reflective of their birth abundances \citep{gilroy89, korn+07, lind+08, souto+18, souto19} As \gls{fdu}, which affects C and N abundances, only occurs during the ascent onto the \gls{rgb}, \gls{subgiant} stars are unaffected by this enrichment.
+
+An alternate approach for this analysis would be to estimate the birth abundances of \gls{rgb} stars by correcting surface abundance effects from \gls{fdu} as in \cite{vincenzo+21}.
 Subgiants are the more attractive option since these observations do not rely on model-dependent corrections.
-However, \gls{rgb}s are more luminous, potentially allowing better coverage of the Galactic disk, which may make this a better approach depending on the application.
-
-I choose to use \citetjack's sample as this does not rely on additional layers of modeling, providing a more direct constraint to our model and limiting our systematic uncertainties.
+However, \gls{rgb} stars are more luminous, potentially allowing better coverage of the Galactic disk.
+
+I choose to use \citetjack\ sample as this does not rely on additional layers of modeling, providing a more direct constraint to our model and limiting our systematic uncertainties.
 
 Fig.~\ref{fig:subgiant_selection} shows a plot of all \apogee\ stars and the \citetjack polygon selection criteria. 
- \citetjack~select a region of stars in $\log g$-$T_\text{eff}$ space described by the following criteria
+ \citetjack~select a region of stars based on surface gravity $\log g$, and effective surface temperature, $T_\text{eff}$.
  \begin{equation}
@@
 \end{equation}
-The \gls{lowalpha} sequence is better reproduced by this model, so I use this cut of the subgiants to compare the models against.
+The \gls{lowalpha} sequence is better reproduced by this model, so I use this cut of the subgiants to compare the models against except for comparing \caafe.
 
@@
     \includegraphics{logg_jack.pdf}
-    \caption[Subgiant selection]{
+    \caption[Subgiant Selection]{
         A Kiel diagram of \apogee{} stars.
-Following \citetjack, we select \gls{subgiant}s in the orange polygon (see Equation \ref{eq:subgiant_selection}).
+Following \citetjack, I select \gls{subgiant}s in the orange polygon (see Equation \ref{eq:subgiant_selection}).
 These stars have not yet experienced first dredge-up, so their photospheric C and N abundances should reflect their birth mixture.
@@
 \newpage
-\section{Low-mass stellar evolution}\label{sec:stel_evo}
+\chapter{Low-Mass Stellar Evolution}\label{sec:stel_evo}
 For reference, I include here a brief summary of the physics behind carbon production in \glspl{lowmass}.
@@
 However, when the core temperature becomes high enough, the \gls{cno} begins to activate.
-Starting with \isotope[12]{C}, the \gls{cno} is a series of proton captures which result in the creation of a new He nucleus.
+Starting with \isotope[12]{C}, the \gls{cno} is a series of proton captures that result in the creation of a new He nucleus.
 \begin{subequations}\label{eq:cno_cycle}
@@
 \end{subequations}
+(There are other less important minor branches of the \gls{cno} cycle
+ \citep{solar-fusion}.)
 The \gls{cno} is more intense at high metallicities, as the abundance of \isotope[12]{C} is higher.
@@
 The star first becomes a \gls{subgiant}, slightly more luminous and redder than the main sequence.
-Then, \gls{fdu} occurs, when the contracting core drives convection currents through, bring processed material from the core to the surface.
+Then, \gls{fdu} occurs when the contracting core drives convection currents through, bringing processed material from the core to the surface.
 Because of the \gls{cno}, the surface abundances of C will be lowered and N enhanced.
@@
 Eventually, conditions are dense and hot enough for He to being to fuse, and the star now enters the He-burning phase.
-(Second dredge up occurs during this transition.) As the next (accessible) stable nuclei after He is C, the primary process to fuse He is through the triple-$\alpha$ process, where 3 He are combined to form \isotope[12]{C}.
+(Second dredge-up occurs during this transition.) As the next (accessible) stable isotope after He is C, the primary process to fuse He is through the triple-$\alpha$ process, where three He nuclei are combined to form \isotope[12]{C}.
 \begin{subequations} \label{eq:triple_alpha}
@@
 \end{align}
-Additionally, some \isotope[12][6]{C} may furthermore fuse into O, $\alpha + \isotope[12][8]{C} \longrightarrow \isotope[16][8]{O} + \gamma$.
+Additionally, some \isotope[12][6]{C} may furthermore fuse into O, $\alpha + \isotope[12][6]{C} \longrightarrow \isotope[16][8]{O} + \gamma$.
 
@@
 The double shell structure causes instabilities towards the end of the \agb\ phase.
-In this thermally pupating phase, a He-flash happens (where the He-shell becomes much more luminous).
-This flash causes the star to expand, driving convective currents which dredge up material from the CO core (\gls{tdu}), and fusion stops temporarily.
-The star settles again, and stays stable for several Myr until the cycle repeats again.
+In this thermally pupating phase, each pulse begins with a He-flash (where the He-shell becomes much more luminous).
+This flash causes the star to expand, driving convective currents that dredge up material from the CO core (\gls{tdu}), and fusion stops temporarily.
+The star settles again and stays stable for several Myr until the cycle repeats.
 During each He-flash, some material from the stellar surface is lost.
 This mass-loss is the source of \agb\ enrichment.
-Finally, the star losses enough mass such that the thermal pulses stop and the star becomes a white dwarf, no longer fusing anything.
+Finally, the star losses enough mass such that the thermal pulses stop.
+The star becomes a white dwarf, left to cool for eternity.
 
@@
 \newpage
-\section{O vs Mg}\label{sec:alt_agb}
-
-As I focus on constraining relative yields, I neglect O and Mg yield variations in the main text (excluding the uniform scaling of yields and \gls{massloading} in section~\ref{sec:outflows}).
+\chapter{Oxygen and Magnesium}\label{sec:alt_agb}
+
+As I focus on constraining relative yields, I neglect O and Mg yield variations in the main text (excluding the uniform scaling of yields and \gls{massloading} in Section~\ref{sec:outflows}).
 There is substantial variation in predicted Mg yields (see Fig.~\ref{fig:y_mg}).
@@
 This is a known problem (see \citealt{emily+21}).
-\cc\ models underpredict $[{\rm Mg}/{\rm O}]$, and the reason why is unknown.
+\Gls{cc} models underpredict $[{\rm Mg}/{\rm O}]$, and the reason why is unknown.
 My results are independent of the choice of \cc\ element as I assume $[{\rm Mg}/{\rm O}]=0$.
@@
     \includegraphics{y_o_mg.pdf}
-    \caption[Magnesium yields]{Same as the top panel of Fig.~\ref{fig:y_cc}, but for Mg.
+    \caption[O/Mg Yields]{Similar to the top panel of Fig.~\ref{fig:y_cc}, but for Mg.
     }
@@
 
-\newpage
-
-\section{Software}
-
+\chapter{Software}
 Software that has contributed to this work:
@@
 
+\chapter{Low-Mass Stellar Yield Models} \label{sec:oob_models}
+    \cxi\ is from \citet{cristallo+11,cristallo+15}, \vxiii{} from \cite{ventura+13,ventura+14,ventura+18,vincenzo+21}, \kx{} from \citet{karakas10}, and \kxvi{} from \cite{KL16,karakas+18}
 \renewcommand*{\arraystretch}{1.8}
-\glsaddall[types={symbols}]
-\renewcommand{\glslongextraSymDescTabularHeader}{}
-\renewcommand{\glslongextraSymDescTabularFooter}{}
-
-\printunsrtglossary[type=symbols,nonumberlist,style=long-sym-desc]
-
+\begin{table}[h]
+    \centering
+    \begin{tabular}{l p{2.2in} p{2.2in}}
+    \toprule
+    model & Masses/$M_\odot$ & $Z$ \\
+    \midrule
+    \hypertarget{C11}{\texttt{C11}} &
+    1.3, 1.5, 2.0, 2.5, 3.0, 4.0, 5.0, 6.0
+    & 0.0001, 0.0003, 0.001, 0.002, 0.003, 0.006, 0.008, 0.01, 0.014, 0.02 \\
+
+    \hypertarget{K10}{\texttt{K10}} &
+    1.0, 1.25, 1.5, 1.75, 1.9, 2.25, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0 
+    &  0.0001, 0.004, 0.008, 0.02. \\
+
+    \hypertarget{V13}{\texttt{V13}} 
+    & 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 6.0, 6.5, 7.0
+    & 0.0003, 0.001, 0.002, 0.004, 0.008, 0.014, 0.04 \\
+
+    \hypertarget{K16}{\texttt{K16}} 
+     & 1.0, 1.25, 1.5, 1.75, 2.25, 2.5, 2.75, 3.0, 3.25, 3.5, 3.75, 4.0, 4.5, 5.0, 5.5, 6.0, 7.0
+     & 0.0003, 0.001, 0.002, 0.004, 0.008, 0.014, 0.04 \\
+         \bottomrule
+    \end{tabular}
+\end{table}
+
+\chapter{Symbols}
+
+\setlength{\tabcolsep}{0pt}
+\begin{longtable}{p{0.2\textwidth} p{0.8\textwidth}}
+    $[A/B]$ & 
+    The abundance ratio between elements $A$ and $B$. $[A/B] =
+    \log_{10}\left(A/B\right) - \log_{10}\left(A_{\sun}/B_{\sun}\right)$, i.e.
+    $[A/B]$ is the logarithm of the ratio between A and B, scales such that
+    $[A/B]=0$ for the sun. Solar abundances are as measured in
+    \citet{asplund+09}. \\
+
+$\alpha_{\rm AGB}$ & 
+The multiplicative increase in \agb\ C production. See Eq.~\ref{eq:alpha}. \\
+
+$\alpha_{\rm CC}$ &
+The multiplicative increase in \cc\ C production. See Eq.~\ref{eq:alpha}. \\
+
+$\eta$ & 
+The mass outflow loading factor. $\eta$ is the ratio between ejected gas from the galaxy and star formation, i.e. $\eta = \dot{M}_{\rm outflow}/\dot{M}_\star$. \\
+
+$\zeta$ & 
+{The high-mass star carbon yield metallicity dependence. See Eq.~\ref{eq:zeta}}. \\
+
+$\ensuremath{\dot{\Sigma}}$ & 
+The surface mass density of star formation. \\
+
+$M$ &
+The mass of a star, in units of $M_\odot$ \\
+
+$\ensuremath{M_\odot}$ &
+The mass of the sun. $M_\odot = 1.989\times10^{33}$\,g.  \\
+
+$\dot{M}_\star$ & 
+The rate of star formation (mass of new stars per time interval). \\
+
+$\dot{M}_{\rm X}$ &
+The rate of change of the mass of element $X$. \\
+
+$f_{\rm AGB}$ &
+The fractional contribution of \agb\ stars to the total \gls{imfave} carbon yield at solar metallicity. See Eq.~\ref{eq:f_agb} \\
+
+$R$ &
+The galactocentric radius (distance from the galactic center) in kpc. \\
+
+$\tilde{y}_{\rm C}^{\rm AGB}$ &
+The per-star yield of C from \glspl{lowmass} of a given mass. In other words, the amount of new C an \agb\ star ejects divided by the initial mass of the star. \\
+
+$y_{\rm C}^{\rm AGB}$ &
+The \gls{imfave} yield of C from \glspl{lowmass}. \\
+
+$y_{\rm C}^{\rm CC}$ &
+The \gls{imfave} yield of C from \glspl{highmass}. \\
+
+$y_{\rm Mg}^{\rm CC}$ &
+The \gls{imfave} yield of Mg. \\
+
+$Z_\odot$ &
+The metallicity for the sun. $Z_\odot=0.014$.  \\
+
+$Z$ &
+The metallicity fraction, i.e. the mass fraction of all elements which are not H or He.  \\
+
+$Z_X$ &
+The mass fraction of element $X$. \\
+
+\end{longtable}
+
+\setlength{\tabcolsep}{6pt}
 \renewcommand*{\arraystretch}{1}
-\printglossary[type=models,nonumberlist]
-\label{sec:oob_models}
 

### 2023-05-19 out/paper_old/tex/main.tex
multithread options back and reorginization

--- 2023-03-21 carbon_paper/tex/main.tex
@@
 \newcommand{\zoo}{\ensuremath{Z/Z_{\sun }}}
-\newcommand{\Ycc}{\ensuremath{Y_{\rm C}^{\rm cc}}}
-\newcommand{\Yct}{\ensuremath{Y_{\rm C, 0}^{\rm tot}}}
-\newcommand{\Yoc}{\ensuremath{Y_{\rm O}^{\rm cc}}}
-\newcommand{\Ycagb}{\ensuremath{Y_{\rm C}^{\rm agb}}}
+\newcommand{\Ycc}{\ensuremath{y_{\rm C}^{\rm cc}}}
+\newcommand{\Yct}{\ensuremath{y_{\rm C, 0}^{\rm tot}}}
+\newcommand{\Yoc}{\ensuremath{y_{\rm O}^{\rm cc}}}
+\newcommand{\Ycagb}{\ensuremath{y_{\rm C}^{\rm agb}}}
 
@@
     \includegraphics[]{subgiants_mgfe.pdf}
-    \caption{Chemical abundance relationships of our sample of APOGEE subgiants (see Jack et al. 2023). Left panel shows }
+    \caption{The [C/Mg] ratio against [Mg/H] (left) and [Mg/Fe] (right).
+The left panel uses blue and orange to represent high and low $\alpha$ sequences respectively.
+On the right, we plot more metal rich ([Mh/H]) stars with darker colors.}
     \label{fig:subgiants}
@@
 \begin{figure*}
-\includegraphics[scale=0.6]{oob_agb-1.pdf}
+\includegraphics[]{oob_agb.pdf}
 
@@
 \begin{figure*}\label{fig:beta_f}
-\includegraphics[scale=0.6]{beta-1.pdf}
-\includegraphics[scale=0.6]{f_agb-1.pdf}
+\includegraphics{beta.pdf}
+\includegraphics{f_agb.pdf}
 
@@
 
+One caveat is that the slope of this trend is also determined by the ratio of delayed iron to CCSNe iron production as well.
+If the SNeIa iron fraction is increased, then more iron enters later reducing the slope of the trend as AGB becomes a more rapid mechanism than Fe comparatively.
+The difference however is that changing the Fe franction mostly affects the tail of the distribution as this controls the speed of descent off the high $\alpha$ sequence, but the AGB fraction even changes the behavior for the low $\alpha$ sequence.
+
 \subsection{The AGB Fraction }
@@
 \begin{figure*}
-\includegraphics[scale=0.6]{lateburst_eta-1.pdf}
+\includegraphics[]{lateburst_eta.pdf}
 
@@
 
-\begin{figure}
-    \includegraphics[scale=0.6]{cooh_scatter.pdf}
+\begin{figure*}
+    \includegraphics[scale=0.9]{cooh_scatter.pdf}
+    \includegraphics[scale=0.9]{cnoh_scatter.pdf}
     \caption{The simulated stars of our model at present day plotted on \caah~and colored such that lighter colors represent stars born at greater galactric radii.}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[scale=0.6]{cnoh.pdf}
-    \caption{Caption}
-    \label{fig:cnofe}
-\end{figure}
+\end{figure*}
 
@@
 
-In the first panel, both V13 and the subgiant sample predict similar trends in [C/Mg]-[Mg/H] but there appears to be a systematic offset of about 0.2dex.
-Reproducing the trend is promising as V21's mixing corrections were metallicity-dependent so the uncorrected sample of APOGEE giants does not match the subgiant trend.
-
-The systematic offset could be explained by overpredicting the effects of FDU or other *** in V21's stellar evolution models??? or other subgiant physics???
-
-In the second panel, agreement appears to be better. Both the MDF and the slope are nearly identical,
-There is a slight deviation in slope between the models, and this could again be a systematic such as underestimation of **8some stellar effect**** at higher metallicities.
-
-We compare both of **** in Fig. \ref{fig:fiorenzo_jack}.
-
-\begin{figure*}
-    \centering
-    \includegraphics[scale=0.5]{fiorenzo_vs_jack_c-1.pdf}
-    \includegraphics[scale=0.5]{fiorenzo_vs_jack_n-1.pdf}
-    \caption{A comparison of estimated stellar birth abundance trends from the subgiant sample and
-        \citet{fiorenzo+21}
-    }
-    \label{fig:fiorenzo_jack}
-\end{figure*}
-
 \section{Effects of Alternate AGB Models}\label{sec:alt_agb}

### 2023-05-19 out/thesis/tex/main.tex
multithread options back and reorginization

--- 2023-05-02 thesis/tex/main.tex
@@
 Produces C, N, and heavy \gls{sproc} elements.
-See \ref{sec:stel_evo}.}.]
+See Appendix \ref{sec:stel_evo}.}.]
 {agb}{agb}{asymptotic giant branch}
@@
 [description={Type Ia Supernovae. Exploding white dwarfs. Produces \gls{fepeak} and has a long delay time.}]
-{ia}{sne ia}{supernovae type Ia}
+{ia}{sne ia}{type Ia supernovae}
 
@@
 \newglossaryentry{nucleosynthesis}{name={nucleosynthesis},
-    description={The synthesis of new elements through fusion inside stars. See section \ref{sec:stel_evo}.}
+    description={The synthesis of new elements through fusion inside stars. See Appendix \ref{sec:stel_evo}.}
 }
@@
 % results
-By matching the median trends of \caah\ and \caafe\ in  {\sc APOGEE} subgiant stars, I find that high-mass and low-mass stars contribute \about{80\%} and \about{20\%} of total C production respectively.
+By matching the median trends of \caah\ and \caafe\ in  {\sc apogee} subgiant stars, I find that high-mass and low-mass stars contribute \about{80\%} and \about{20\%} of total C production respectively.
 % 
@@
 David and Jennifer for helping this project move forward, by providing guidance at critical junctions and being part of my committee.
-Rolando, for being the non-astronomer thrown into this work, and pointing out the flaw of incomprehensibility in this work.
+RVA, for being the non-astronomer forced to listen to my thesis and providing valuable feedback about the understandability of this work.
 
@@
 Anya, you are a wonderful friend and I cannot thank you enough for your unconditional support this year,
-All my friends who are just wonderful, inspiring, and incredible people---Kaia, Maria, Autumn, Simon, Bailee, Aaliyah, Sanskruti, Alyssa, Harrison, Denis, Keith, and so many others. 
+All my friends who are just wonderful, inspiring, and incredible people---Kaia, Maria, Mary, Autumn, Simon, Bailee, Aaliyah, Sanskruti, Alyssa, Harrison, Denis, Natalia, Keith, and so many others. 
 And my family (including Arya, my most lovable doodle)---I can not even being to thank you enough for simply helping me recover my health and make it to graduation.
@@
 \Gce{} aims to understand the chemical enrichment and star formation histories of galaxies.
-At the core of \gce{} models are stellar \gls{yield}---the amount of each chemical element stars produce (or destroy).
+At the core of \gce{} models are stellar \glspl{yield}---the amount of each chemical element stars synthesize.
 Each element is produced in different amounts by different stars, leaving traces of the Galaxy's evolutionary history.
@@
 %
----observed in very low \gls{metallicity}
+---observed in very low \gls{metallicity},%
 \footnote{Astronomers are not chemists. By metallicity, I mean the (mass) fraction of any element which is not H or He, denoted by $Z$. For the sun, $Z_\odot=0.014$. }
-, high redshift
+ high redshift%
 \footnote{i.e. observed in the early universe.}
@@
 
-Nucleosynthetic yields predicted by stellar evolution models are rife with uncertainties, despite their central role in \gce{} models, nucleosynthetic yields predicted by stellar evolution models are rife with uncertainties.
-The production rates of elements in stars are shaped by poorly understood processes, including mass loss, opacity, nuclear reaction rates, rotational mixing, convection, and explodability \citep{KL14,ventura+13, LC18, emily+21}.
-
-\Gce{} models typically use unmodified nucleosynthetic predictions and attempt to create models matching observations by varying the \sfh{} and other evolutionary parameters.
+Nucleosynthetic yields predicted by stellar evolution models are rife with uncertainties, despite their central role in \gce{} models.
+The production rates of elements in stars are shaped by poorly understood processes, including mass loss, nuclear reaction rates, rotational mixing, convection, and explodability \citep{KL14,ventura+13, LC18, emily+21}.
+
+\Gce{} models typically use unmodified nucleosynthetic predictions and attempt to match observations by varying the \sfh{} and other evolutionary parameters.
 Here, I introduce C yields as an additional free parameter, determining which yield prescriptions reproduce Galactic abundance trends.
@@
 \end{equation}
-where ${dN}/{dM}$ is the normalized \imf, $M_{\rm max}=100\,M_\odot$ is the maximum stellar mass, and $M_{\rm min}(t)$ is the mass of stars with lifetime $t$. 
+where ${dN}/{dM}$ is the normalized \imf, $M_{\rm max}=100\,M_\odot$ is the maximum stellar mass, and $M_{\rm min}(t)$ is the mass of stars with lifetime $t$.%
 \footnote{In my model, the mass-lifetime relation is
@@
 		\midrule
-        C & $0.0028 + 0.001(Z/Z_\odot)$ & $2.9\times{\rm C11}$ &  0 \\
+        C & $0.0028 + 0.001\,(Z/Z_\odot)$ & $2.9\times{\rm C11}$ &  0 \\
         Mg & 0.00185 & 0 & 0 \\
         Fe & 0.0012 & 0 & 0.00214 \\
-        N & 0.00072 & $9\times10^{-4}(Z/Z_\odot)M$ & 0\\
+        N & 0.00072 & $9\times10^{-4}\,(Z/Z_\odot)\,M$ & 0\\
 		\bottomrule
@@
 If this envelope is lost during the \agb\ phase, then C yields are enhanced.
-\gls{hbb} is the activation of proton capture reactions and the CNO cycle%
+\Gls{hbb} is the activation of proton capture reactions and the CNO cycle 
 at the base of the convective envelope.
@@
 Most models agree on the qualitative shape of the net fractional \agb\ C yield---% 
-stars with masses between \about{2~M_\odot} and \about{4~M_\odot} have the highest fractional C yields, with the mass of the peak increasing and overall yields decreasing with increasing $Z$.
+stars with masses between \about{2\,M_\odot} and \about{4\,M_\odot} have the highest fractional C yields, with the mass of the peak increasing and overall yields decreasing with increasing $Z$.
 High mass, high $Z$ stars destroy \isotope[12]{C} because they experience both \gls{tdu} and \gls{hbb}, but the latter is much more efficient.
@@
 Fig.~\ref{fig:agb-ssp} shows the total production of C by \agb\ stars in a \ssp{} at an age $t$, i.e. $\tilde{y}_{\rm C}(Z_\odot, t)$. 
-As the mass range $2M_\odot\lesssim M \lesssim 4M_\odot$ is most important for C production, about half of C production occurs before \about{1}\,Gyr, similar to \ia\ Fe. 
-\kx{} and \kxvi{} weight C production more heavily towards \glspl{highmass} resulting in a faster enrichment delay time, whereas the \cxi\ and \vxiii\ models predict a slightly longer timescale of \about{1}\,Gyr, but little to no C is produced more than 2\,Gyr after a star formation event.
+As the mass range $2\,M_\odot\lesssim M \lesssim 4\,M_\odot$ is most important for C production, about half of C production occurs before \about{1}\,Gyr, similar to \ia\ Fe. 
+\kx{} and \kxvi{} weight C production more heavily towards \glspl{highmass} resulting in a faster enrichment delay time, whereas the \cxi\ and \vxiii\ models predict a slightly longer timescale of \about{1}\,Gyr.
+In any case, little to no C is produced more than 2\,Gyr after a star formation event.
 This is in contrast to Fe whose production lasts up to 10\,Gyr after a star formation event.
@@
 The black dashed line shows $\tilde{y}=0$ for reference.
-Each panel represents yields from one of four \agb\ models: \cxi, \kx{}, \vxiii{}, \kxvi{} (see Section \ref{sec:agb} and \ref{sec:oob_models}).
+Each panel represents yields from one of four \agb\ models: \cxi, \kx{}, \vxiii{}, \kxvi{} (see Section \ref{sec:agb} and  Appendix \ref{sec:oob_models}).
 }
@@
     \caption[Low-Mass-Star Yield Metallicity Dependence]{The net fractional \imf-weighted \agb\ C yield $\Ycagb$ as a function of metallicity for each of our \agb\ yield models.
-($\Ycagb$ is the net mass of C produced by \agb\ stars per unit mass of star formation, after 10\,Gyr and assuming a \citet{kroupa01} \imf.)
+($\Ycagb$ is the net mass of C produced by \agb\ stars per unit mass of star formation, after 10\,Gyr and assuming a \citealt{kroupa01} \imf.)
     }
@@
 Fig.~\ref{fig:y_cc} plots calculations of the \imf-integrated yields, defined with Eq.~\ref{eq:imf-yield} (computed using \VICE's \texttt{vice.yields.ccsne.fractional} function). 
-\Gls{cc} models predict a wide range of C yields, spanning almost 1 dex. 
+\Gls{cc} models predict a wide range of C yields, spanning almost a factor of ten. 
 Both the \citet{NKT13} and \cite{LC18} models show positive metallicity dependence. 
@@
 Later, I will also show empirically this is the case.
-On the bottom of Fig.~\ref{fig:y_cc}, I also show the \cc{}-[C/Mg] ratio, defined by
+On the bottom of Fig.~\ref{fig:y_cc}, I also show the \cc{} [C/Mg] ratio, defined by
 \begin{equation}\label{eq:c_mg_cc}
@@
 Newly produced metals are homogeneously and instantaneously mixed, so spatial dependence is neglected.
-I define $M_{X}$ to be the mass of element $X$ in the gas phase, $\dot{M}_\star$ to be the star formation rate (in M$_\odot$ yr$^{-1}$), and $\eta$ to be the mass loading factor $\eta\equiv\dot{M}_{\rm outflow}/\dot{M}_\star$ (representing the strength of outflows).
-A \ssp\ returns a fraction $r$ of their birth mass to the interstellar medium, due to ejected stellar envelopes.
+I define $M_{X}$ to be the mass of element $X$ in the gas-phase, $\dot{M}_\star$ to be the star formation rate (in $M_\odot\,$yr$^{-1}$), and $\eta$ to be the mass loading factor $\eta\equiv\dot{M}_{\rm outflow}/\dot{M}_\star$ (representing the strength of outflows).
+A \ssp\ returns a fraction $r$ of their birth mass to the interstellar medium, due to ejected stellar envelopes.%
 \footnote{$r\approx0.4$ for a \citealt{kroupa01} \imf.}
@@
 \begin{equation}
-    \dot{M}_{\rm Mg}= y_{X} \dot{M}_\star - (1 + \eta - r) Z_{X} \dot{M}_\star.
+    \dot{M}_{\rm Mg}= y_{X}\,\dot{M}_\star - (1 + \eta - r)\,Z_{X}\,\dot{M}_\star.
 \end{equation}
@@
 
-Likewise, for \agb\ stars,
+Likewise, for \agb\ stars,%
 \footnote{In detail, the \agb\ contribution requires integration over the \sfh\ to account for the finite lifetimes of stars.
@@
 \begin{equation}
-    Z_{\rm C}^{\rm eq}(R) = \frac{\Ycc + \Ycagb}{1 + \eta(R) - r - \tau_\star / \tau_{sfh}}
+    Z_{\rm C}^{\rm eq}(R) = \frac{\Ycc + \Ycagb}{1 + \eta(R) - r - \tau_\star / \tau_{\rm sfh}}
 \end{equation}
@@
 My models here are unable to distinguish the overall scaling of yields and outflow mass loading.
-So, choosing to keep $y_{\rm C}$ fixed reduces unnecessary free parameters.
+Choosing to keep $y_{\rm C}$ fixed reduces unnecessary free parameters.
 So, at solar metallicity, I set
@@
 \end{subequations}
-This ratio results in an equilibrium abundance ${\rm [C/Mg]} = -0.09$, which is consistent with the \citetjack~\gls{subgiant} sample and is within \about{20\%} of the solar C/Mg mixture from \citet{asplund+09}.
+This ratio results in an equilibrium abundance ${\rm [C/Mg]} = -0.09$, which is consistent with the \gls{subgiant} sample and is within \about{20\%} of the solar C/Mg mixture from \citet{asplund+09}.
 
@@
 \end{equation}
-where $\zeta\approx.001$ describes the metallicity dependence.
+where $\zeta\approx0.001$ describes the metallicity dependence.
 
@@
 As the metallicity range of the data is small ($-0.4\lesssim {\rm [Mg/H]} \lesssim 0.4$), other models are more challenging to interpret in this range.
-Furthermore, the \apogee{} observations may have systematics, and other measurements of C abundances \citep[e.g.][]{vincenzo+21} have slight disagreements in the overall shape of the trend (see Section \ref{sec:jack}).
+Furthermore, the \apogee{} observations may have systematics.
+Other measurements of C abundances \citep[e.g.][]{vincenzo+21} have slight disagreements in the overall shape of the trend (see Section \ref{sec:jack}).
 So, this expression of $\Ycc/\Yoc$ depends on the chosen \agb\ yield table, the \agb\ fraction, and the dataset. 
-Additionally, these yields will be systematically biased if the galaxy is out of equilibrium, for example, due to a recent starburst (Isern et al.
-19; Mar et al.
-19).
+Additionally, these yields will be systematically biased if the galaxy is out of equilibrium, for example, due to a recent starburst \citep{mor+19,isern19}.
 Further exploration could investigate the magnitude of these uncertainties, but I find that the qualitative conclusions are similar despite substantial variations in the assumptions here.
@@
 
-In the model, the Galaxy is divided into 200 rings, each 100 pc wide.
+In the model, the Galaxy is divided into 200 rings, each 100\,pc wide.
 Each ring has a separate stellar population and gas supply.
-Star formation ends beyond a radius $R=15.5$ kpc.
+Star formation ends beyond a radius $R=15.5\,$kpc.
 I initially assume an \gls{insideout} \sfh{}, where the star formation surface density $\Sigma_\star$ is given by
@@
 \JJ~derives $\tau_{\rm sfh}(R)$ through analysis of four integral field spectroscopy surveys in \cite{sanches20}.
-The star formation history is normalized such that the total stellar mass reaches $5.17\times10^{10} {\rm M}_\odot$ \citep{LM15} and at each $R$ to match the stellar surface density gradient \citep{BHG16}.
-The gas inflow is calculated to maintain our chosen \sfh{} for each radius and time. The gas-star-formation law is based on an extension of a Kennicutt-Schmidt law \citep{kennicutt98}
+The star formation history is normalized such that the total stellar mass reaches $5.17\times10^{10}\,M_\odot$ \citep{LM15} and at each $R$ to match the stellar surface density gradient \citep{BHG16}.
+The gas inflow is calculated to maintain our chosen \sfh{} for each radius and time, using an extension of a Kennicutt-Schmidt law \citep{kennicutt98},
 \begin{equation}
@@
 \JJ\ accounts for radial migration by using the results of the \texttt{h277} hydrodynamical simulation \citep{christensen12, zolotov12, loebman12, BZ14}, with simulation parameters described in \citet{bird+21}.
-Each \VICE\ single stellar population (SSP) is matched to an \textit{analog} in \texttt{H277}, chosen to form at a similar time and radius $R$.
+Each \VICE\ single stellar population (\ssp) is matched to an \textit{analog} in \texttt{H277}, chosen to form at a similar time and radius $R$.
 By taking the change in radius $\Delta R$ of the analogs, the \ssp move to their final radii with a $\sqrt{\text{time}}$ dependence.
@@
 Using the results of a hydrodynamical simulation without modification limits the free parameters in the model; however, I am limited to one dynamical history.
-The impact of the details of a galaxy's dynamical history on its chemical evolution is unknown.
+The impact of the details of a galaxy's dynamical history on its chemical evolution is still unknown.
 
@@
 \begin{equation}\label{eq:eta_r}
-\eta(R) = \frac{y_{\alpha}^{\rm CC}}{Z_{\alpha, \odot}} 10^{(-0.08\text{ kpc}^{-1})(R-4\text{ kpc})+0.3} + r - 1.
+\eta(R) = \frac{y_{\alpha}^{\rm CC}}{Z_{\alpha, \odot}} 10^{(-0.08\,\text{kpc}^{-1})(R-4\,\text{kpc})+0.3} + r - 1.
 \end{equation}
@@
 
-\section{The Evolution of C Abundances in the Galaxy}
+\section{The Evolution of Carbon Abundances in the Galaxy}
 
@@
 Finally, as $\Ycagb$ decreases or even becomes negative with higher metallicity, the [C/Mg] abundance may decline slightly.
-This is even more evident in the lower panel of Fig.~\ref{fig:c_evo}.
-While the \caah\ trend reaches equilibrium at \about{5}\,Gyr, the \caafe\ trend continues to evolve even until the present day, exposing the effect of the relative delay times of \agb\ stars and \ia.
+This is more evident in the lower panel of Fig.~\ref{fig:c_evo}---while the \caah\ trend reaches equilibrium at \about{5}\,Gyr, the \caafe\ trend continues to evolve even until the present day, exposing the effect of the relative delay times of \agb\ stars and \ia.
 
@@
 \caption[Carbon Chemical Evolution Tracks]{
-    Time evolution of gas phase C abundances in our fiducial model.
+    Time evolution of gas-phase C abundances in our fiducial model.
     {\bf Top:} Evolutionary tracks parameterized by time at fixed Galactocentric radius in the \caah\ and \caafe\ planes. 
-    {\bf Bottom:} snapshots of the gas-phase \caah\ and \caafe\ trend, parameterized by radius at a fixed time.
+    {\bf Bottom:} Snapshots of the gas-phase \caah\ and \caafe\ trend, parameterized by radius at a fixed time.
 }
@@
     Stellar abundance trends in our model, assuming metallicity independent $\Ycc$.
-Colored lines quantify the median [C/Mg] in bins of [Mg/H] for our four \agb\ yield models from the literature (see \ref{sec:agb}).
+Colored lines quantify the median [C/Mg] in bins of [Mg/H] for our four \agb\ yield models from the literature (see Section \ref{sec:agb}).
 Black points and grey dashes represent the median and standard deviations of [C/Mg] for each [Mg/H] bin in the \citetjack~sample.
@@
 
-\Gce{} models of the Milky Way fall into two classes---those which incorporate significant mass-loading (e.g., as in this work) and those which neglect mass-loading but lower effective yield to match observed abundances \citep[e.g.][]{MCM13, MCM14, spitoni19, spitoni20, spitoni21}.
+\Gce{} models of the Milky Way fall into two classes---those which incorporate significant mass-loading (e.g., this work) and those which neglect mass-loading but lower effective yield to match observed abundances \citep[e.g.][]{MCM13, MCM14, spitoni19, spitoni20, spitoni21}.
 An increase in stellar yields has a nearly identical effect as a decrease in the mass-loading factor $\eta$ (see Appendix B of \citealt{james_dwarf}).
@@
 If fewer \glspl{highmass} explode, then the yields will be reduced by some factor.
-Additionally, some fraction of SN ejecta may be lost directly to an outflow, lowering effective yields.
+Additionally, some fraction of supernovae ejecta may be lost directly to an outflow, lowering effective yields.
 To explore reduced outflow models, I lower both $\eta$ and all yields by the same factor to leave the equilibrium abundances unchanged.
@@
 Median trends have limitations as they do not consider the actual distribution of \caah~abundances.
-So, I show in Fig.~\ref{fig:scatter} a comparison of the predicted distribution of the model to the contours of the \gls{subgiant} sample.
+So, Fig.~\ref{fig:scatter} compares the predicted distribution of the model to contours of the \gls{subgiant} sample.
 The model reproduces this 2-dimension distribution well when including scatter based on the median \apogee{} abundance errors for each metallicity bin.
@@
     \caption[Scatter Agreement]{The stars in the fiducial model in the \caah~plane compared to contours of the \gls{subgiant} sample.
-I added random noise to the scatter points equal to the median uncertainties in the \gls{subgiant} sample.
+I add random noise to the scatter points equal to the median uncertainties in the \gls{subgiant} sample.
 Stars are color-coded such that lighter colors represent populations born at greater galactocentric radii.
@@
 As an additional test of the model, I next compare the model predictions against gas-phase measurements.
-Fig.~\ref{fig:gas_phase} shows the fiducial model's gas phase predictions compared to observations of the Milky Way and extragalactic HII regions, halo stars, and \dla\ systems.
+Fig.~\ref{fig:gas_phase} shows the fiducial model's gas-phase predictions compared to observations of the Milky Way and extragalactic HII regions, halo stars, and \dla\ systems.
 The model is broadly consistent with observations, where the model at $t=2$\,Gyr approximates the slope of dwarf galaxies and halo stars.
@@
 \citet{james+23} performed a similar analysis focusing on N.
-They found that matching the observed relationship between N and O abundances \citep{HEK00,PVT10,berg+12, berg+20, skillman+20, izotov+12, james2+15, dopita+16} requires relative N and O yields from simple stellar populations with a roughly linear dependence on metallicity (i.e.
+They found that matching the observed relationship between N and O abundances%
+\footnote{e.g.
+\citet{HEK00,PVT10,berg+12, berg+20, skillman+20, izotov+12, james2+15, dopita+16}.} requires relative N and O yields from simple stellar populations with a roughly linear dependence on metallicity (i.e.
 $y_{\rm N}/y_{\rm O} \propto Z$).
@@
 
-Finally, I compare my model against gas phase measurements and metal-poor stars.
+Finally, I compare my model against gas-phase measurements and metal-poor stars.
 While my model was built on data near solar metallicity, observations of very low metallicity, high redshift damped Lyman-$\alpha$ systems indicate higher C/O ratios \citep{cooke+17}, consistent with yields from population III stars \citep[e.g.][]{hirschi07}.
@@
 These C yield constraints provide a useful benchmark for stellar evolution models.
-C yields are sensitive to poorly understood processes, including mass loss prescriptions, explodability, nuclear cross Sections, convection, and stellar structure.
+C yields are sensitive to poorly understood processes, including mass-loss prescriptions, explodability, nuclear cross sections, convection, and stellar structure.
 Future spectroscopic surveys combined with Gaia kinematics \citep{gaia} will continue to enhance our understanding of chemical evolution.
@@
 % 
-% \renewcommand*{\theHsection}{A.\arabic{section}}%
 % \renewcommand*{\theHsubsection}{A.\arabic{subsection}}%
@@
 \end{align}
-Additionally, some \isotope[12][6]{C} may furthermore fuse into O, $\alpha + \isotope[12][6]{C} \longrightarrow \isotope[16][8]{O} + \gamma$.
+Additionally, some \isotope[12][6]{C} may furthermore fuse into O through $\alpha + \isotope[12][6]{C} \longrightarrow \isotope[16][8]{O} + \gamma$.
 
@@
 The double shell structure causes instabilities towards the end of the \agb\ phase.
-In this thermally pupating phase, each pulse begins with a He-flash (where the He-shell becomes much more luminous).
+In this thermally pulsating phase, each pulse begins with a He-flash (where the He-shell becomes much more luminous).
 This flash causes the star to expand, driving convective currents that dredge up material from the CO core (\gls{tdu}), and fusion stops temporarily.
-The star settles again and stays stable for several Myr until the cycle repeats.
+The star settles again and stays stable for several Myrs until the cycle repeats.
 During each He-flash, some material from the stellar surface is lost.

### 2023-05-19 out/paper_old/agb_yields.py

@@ -1,0 +1,63 @@
+import matplotlib.pyplot as plt
+import vice
+import numpy as np
+import matplotlib as mpl
+
+import plot_style
+
+
+
+cmap = mpl.cm.viridis
+Z_max = 0.02
+Z_min = 0.0001
+AGB_MODELS = ["cristallo11", "karakas10", "ventura13", "karakas16"]
+AGB_LABELS = ["C11+C15", "K10", "V13", "KL16+K18"]
+
+# plt.rc('xtick.minor', visible=False)
+
+def plot_c_table(study = "cristallo11", ax=None, fig=None, **kwargs):
+    if ax is None:
+        fig, ax = plt.subplots()
+
+    y1, m1, z1 = vice.yields.agb.grid('c', study=study)
+    N = len(z1)
+
+    for i in range(N):
+        y = np.array(y1)[:,i]
+        z = z1[i]
+        c = (np.log(z) - np.log(Z_min))/np.log(Z_max/Z_min)
+        f = ax.plot(m1, y, "o", label=f"Z = {z}", c=cmap(c), **kwargs)
+        f = ax.plot(m1, y, label=f"Z = {z}", c=cmap(c), **kwargs)
+        # ax.set_xticks(np.arange(1, 8))
+    
+    ax.axhline(0, color="k", ls="--", zorder=-1)
+
+    return f
+
+
+fig, axs = plt.subplots(2, 2, figsize=((np.sqrt(5) + 1)*plot_style.WIDTH, 2*plot_style.WIDTH), sharex=True, sharey=True)
+plt.subplots_adjust(hspace=0, wspace=0)
+# plt.minorticks_off()
+
+for i in range(4):
+    study = AGB_MODELS[i]
+    label = AGB_LABELS[i]
+    ax = axs[i//2][i%2]
+    f = plot_c_table(study, ax=ax, fig=fig)
+    ax.text(0.9, 0.9, label, horizontalalignment='right',
+            verticalalignment='top', transform=ax.transAxes)
+    #plt.legend()
+    # ax.tick_params(
+    #         length=5
+    #         )
+
+
+
+norm = mpl.colors.Normalize(vmin=np.log10(Z_min/0.014), vmax=np.log10(Z_max/0.014))
+mappable = mpl.cm.ScalarMappable(cmap=cmap, norm=norm)
[…]

### 2023-05-19 out/paper_old/evo_slices.py

@@ -1,0 +1,61 @@
+import matplotlib.pyplot as plt
+import numpy as np
+from dataclasses import dataclass
+
+import vice
+
+import sys
+sys.path.append("../")
+
+from src.analysis.vice_model import vice_model
+import src.analysis.apogee_analysis as aah
+import src.analysis.plotting_utils as pluto
+
+import plot_style
+
+@dataclass
+class model_id():
+    agb: str = None
+    eta: str = None
+    f_agb: str = None
+    beta: str = None
+    name: str = None
+    version: str = ""
+
+
+def find_model(id):
+    """
+    Finds the pickled model with either the given name or the parameters 
+    and returns the vice_model object
+    """
+    if id.name is None:
+        name = id.agb + "_f" + id.f_agb + "_Z" + id.beta + "_eta" + id.eta + id.version
+    else:
+        name = id.name
+    file_name = "../output/" + name + ".json"
+    return vice_model(file_name)
+
+
+fiducial = find_model(model_id(agb="cristallo11", f_agb="0.2", eta="1.0",
+    beta="0.4", version="_v0.1.3"))
+
+fig = plt.figure(figsize=(6.3, 3.15))
+gs = fig.add_gridspec(1, 2, wspace=0)
+axs = gs.subplots(sharey=True)
+
+plt.sca(axs[0])
+fiducial.plot_t_slices("[o/h]", "[c/o]", ax=axs[0])
+axs[0].set(
+           ylim=(-0.7, 0.3),
+           xlabel=r"[$\alpha$/H]",
+           ylabel=r"[C/$\alpha$]"
+          )
+
+
+fiducial.plot_t_slices("[o/fe]", "[c/o]", ax=axs[1], legend=False)
+axs[1].set(
+           ylabel="",
+           xlabel=r"[$\alpha$/Fe]"
+          )
+
+plot_style.save()

### 2023-05-19 out/paper_old/make_plots.sh

@@ -1,0 +1,13 @@
+#/bin/bash
+
+python agb_yields.py
+
+python y_agb_vs_t.py
+python y_agb_vs_z.py
+
+python y_c_cc.py
+python y_co_cc.py
+
+python evo_slices.py
+python evo_tracks.py
+

### 2023-05-19 out/paper_old/y_agb_vs_t.py

@@ -1,0 +1,35 @@
+import matplotlib.pyplot as plt
+import vice
+import sys
+import numpy as np
+
+import plot_style
+
+
+AGB_MODELS = ["cristallo11", "karakas10", "ventura13", "karakas16"]
+AGB_LABELS = ["C11+C15", "K10", "V13", "KL16+K18"]
+vice.yields.ccsne.settings["c"] = 0
+vice.yields.sneia.settings["c"] = 0
+vice.yields.ccsne.settings["fe"] = 0
+
+for i in range(4):
+    model = AGB_MODELS[i]
+    vice.yields.agb.settings["c"] = model
+    m_c, times = vice.single_stellar_population("c", Z=0.014 * 10**0)
+    m_c = [c for c in m_c]
+    plt.plot(times, np.array(m_c)/m_c[-1])
+
+m_fe, times = vice.single_stellar_population("fe", Z=0.014)
+m_fe = [fe for fe in m_fe]
+plt.plot(times, np.array(m_fe)/m_fe[-1], label="SN Ia Fe",
+         linestyle="--", color="k")
+
+
+plt.xlabel("t/Gyr")
+plt.ylabel(r"$M(t)/M_{\rm tot}$")
+plt.xscale("log")
+plt.legend()
+plt.ylim(-0.3, 1.1)
+plt.xlim(0.03, 13.2)
+
+plot_style.save()

### 2023-05-19 out/paper_old/y_c_cc.py

@@ -1,0 +1,118 @@
+import matplotlib.pyplot as plt
+import vice
+import numpy as np
+import matplotlib as mpl
+
+import plot_style
+
+
+colors = plot_style.COLORS
+
+# some studies have -inf values, which are ignored
+allowed_MoverH = {
+    "LC18": [-3, -2, -1, 0],
+    "S16/N20": [0],
+    #"CL13": [0],
+    "NKT13": [-1.15, -0.54, -0.24, 0.15, 0.55],
+    #"CL04": [-np.inf, -4, -2, -1, -0.37, 0.15],
+    "WW95": [-4, -2, -1, 0]
+    }
+
+allowed_rotations = {
+    "LC18": [0, 150, 300],
+    "S16/N20": [0],
+    "CL13": [0, 300],
+    "NKT13": [0],
+    "CL04": [0],
+    "WW95": [0]
+}
+
+M_max = {
+    "LC18": 120,
+    "S16/N20": 120,
+    "NKT13": 40,
+    "WW95": 40,
+    "CL04": 35,
+    "CL13": 120,
+}
+
+ccsne_studies = ["LC18", "S16/N20", "WW95","NKT13"]
+
+N = len(ccsne_studies)
+
+
+for i in range(N):
+    study=ccsne_studies[i]
+    metalicities = allowed_MoverH[study]
+    rotations = allowed_rotations[study]
+    m_upper = M_max[study]
+    
+    for j in range(len(rotations)):
+        rotation = rotations[j]
+        y = [vice.yields.ccsne.fractional('c', study=study, MoverH=metalicity, 
+            rotation=rotation, m_upper=m_upper)[0]
+             for metalicity in metalicities]
+        
+        Z = list(map(lambda x: 10**x, metalicities))
+        if rotation == 0:
+            marker = ["v", "o", "*", "s"][i]
+        elif rotation == 150:
+            marker=">"
+        elif rotation == 300:
+            marker="^"
+        plt.scatter(np.log10(Z), y, color=colors[i], label=f"{study}, v={rotation}", marker=marker)
+
+
+plt.ylim(0, 0.0055)
+
+#plt.legend(bbox_to_anchor=(1,1), loc="upper left")
+
+def y_c_cc(Z):
[…]

### 2023-05-19 out/paper_old/y_co_cc.py

@@ -1,0 +1,83 @@
+import matplotlib.pyplot as plt
+import vice
+import numpy as np
+import matplotlib as mpl
+
+import plot_style
+
+colors = plot_style.COLORS
+
+allowed_MoverH = {
+    "LC18": [-3, -2, -1, 0],
+    "S16/N20": [0],
+    #"CL13": [0],
+    "NKT13": [-1.15, -0.54, -0.24, 0.15, 0.55],
+    #"CL04": [-np.inf, -4, -2, -1, -0.37, 0.15],
+    "WW95": [-4, -2, -1, 0]
+    }
+allowed_rotations = {
+    "LC18": [0, 150, 300],
+    "S16/N20": [0],
+    "CL13": [0, 300],
+    "NKT13": [0],
+    "CL04": [0],
+    "WW95": [0]
+}
+
+M_max = {
+    "LC18": 120,
+    "S16/N20": 120,
+    "NKT13": 40,
+    "WW95": 40,
+    "CL04": 35,
+    "CL13": 120,
+}
+
+ccsne_studies = ["LC18", "S16/N20", "WW95","NKT13"]
+
+for i in range(len(ccsne_studies)):
+    study=ccsne_studies[i]
+    metalicities = allowed_MoverH[study]
+    rotations = allowed_rotations[study]
+    m_upper = M_max[study]
+    
+    for j in range(len(rotations)):
+        rotation = rotations[j]
+        yc = [vice.yields.ccsne.fractional('c', study=study, MoverH=metalicity, 
+            rotation=rotation, m_upper=m_upper)[0]
+             for metalicity in metalicities]
+        yo = [vice.yields.ccsne.fractional('o', study=study, MoverH=metalicity, 
+            rotation=rotation, m_upper=m_upper)[0]
+              for metalicity in metalicities]
+        y = np.log10(np.array(yc)/yo) - np.log10(vice.solar_z("c")/vice.solar_z("o"))
+        
+        Z = list(map(lambda x: 10**x, metalicities))
+        if rotation == 0:
+            marker = ["v", "o", "*", "s"][i]
+        elif rotation == 150:
+            marker=">"
+        elif rotation == 300:
+            marker="^"
[…]

### 2023-05-19 run.py

@@ -20,9 +20,9 @@ def main():
     print(pycall)
 
     if args.test_run:
-        subprocess.call(["bash", "local_run.sh", filename, pycall])
+        subprocess.call(["bash", "local_run.sh", filename, pycall, args.threads])
     else:
-        subprocess.call(["bash", "submit.sh", filename, pycall])
+        subprocess.call(["bash", "submit.sh", filename, pycall, args.threads])
 
 
 
@@ -57,6 +57,8 @@ def parse_args():
                         help="the agb fraction of primary N (0.0)")
     parser.add_argument("-t", "--test_run", action="store_true", 
                         help="only run a test")
+    parser.add_argument("-T", "--threads", default=1,
+                        help="number of threads to run. default=1")
     return parser.parse_args()
 
 
@@ -87,6 +89,9 @@ def generate_filename(args):
     if args.n_stars != 2:
         filename += "_nstars" + str(args.n_stars)
 
+    if args.threads != 1:
+        filename += "_nthreads" + str(args.threads)
+
     return filename
 
 
@@ -111,6 +116,7 @@ run_model(
      n_stars={args.n_stars},
      alpha_n={args.alpha_n},
      migration_mode='{args.migration_mode}',
+     n_threads={args.threads}
     )
 """
     return pycall

### 2023-05-19 submit.sh

@@ -1,6 +1,6 @@
 #!/bin/bash
 
-module load miniconda3/4.12.0-py39
+# module load miniconda3/4.12.0-py39
 
 # written like this so we can substitute the 
 # name into the file for easier understanding
@@ -12,8 +12,8 @@ rm -f logs/$1.log
 
 sbatch <<EOT
 #!/bin/bash
-#SBATCH --time=2:00:00
-#SBATCH --ntasks=1
+#SBATCH --time=8:00:00
+#SBATCH --ntasks=$3
 #SBATCH --mem=32gb
 #SBATCH --job-name=$1
 #SBATCH --mail-type=BEGIN,END,FAIL
@@ -22,6 +22,7 @@ sbatch <<EOT
 
 
 set -x
+exoprt OMP_NUM_THREADS=1
 
 cd $SLURM_SUBMIT_DIR
 # # miniconda is specificed in bashrc
@@ -30,14 +31,16 @@ cd $SLURM_SUBMIT_DIR
 python --version
 
 
+exoprt OMP_NUM_THREADS=$3
 python -c "
 $2
 " \$TMPDIR/
 
-python \$SLURM_SUBMIT_DIR/src/json_outputs.py \$TMPDIR/
+exoprt OMP_NUM_THREADS=1
+python \$SLURM_SUBMIT_DIR/surp/simulation/json_outputs.py \$TMPDIR/
 
 cp -r -u \$TMPDIR/*.vice \$SLURM_SUBMIT_DIR/out
-# cp -r -u \$TMPDIR/*.json \$SLURM_SUBMIT_DIR/out
+cp -r -u \$TMPDIR/*.json \$SLURM_SUBMIT_DIR/out
 # cp -r -u \$TMPDIR/*.csv \$SLURM_SUBMIT_DIR/results
 
 scontrol show job=\$SLURM_JOB_ID

### 2023-05-19 surp/analysis/vice_model.py

@@ -7,6 +7,8 @@ import matplotlib.pyplot as plt
 import os.path
 from os.path import exists
 import json
+import seaborn as sns
+
 
 from . import apogee_analysis as aah
 from . import gas_phase_data
@@ -57,9 +59,8 @@ class vice_model():
         with open(filename, "r") as f:
             d = json.load(f)
 
-        self.stars = d["stars"]
-        for name, val in self.stars.items():
-            self.stars[name] = pd.DataFrame(val)
+        self.stars = pd.DataFrame(d["stars"])
+        self.stars_unsampled = pd.DataFrame(d["stars_unsampled"])
 
         self.history = pd.DataFrame(d["history"])
 
@@ -77,6 +78,7 @@ class vice_model():
 
         if xlim is not None:
             plt.xlim(xlim)
+
 
     def plot_mean_stars(self, x, y, plot_data=True, xlim=None,
             star_group="solar", ax=None, s=1, **kwargs):

### 2023-05-19 surp/simulation/multizone_sim.py

@@ -30,7 +30,8 @@ def run_model(filename, prefix=None,
               alpha_n=0,
               test=False, # these are not used yet...
               seed=None, 
-              ratio_reduce=False):
+              ratio_reduce=False,
+              n_threads=1):
     """
     This function wraps various settings to make running VICE multizone models
     easier for the carbon paper investigation
@@ -98,7 +99,8 @@ def run_model(filename, prefix=None,
                          n_stars=n_stars, timestep=timestep,
                          ratio_reduce=ratio_reduce, eta=eta,
                          migration_mode=migration_mode, 
-                         lateburst_amplitude=lateburst_amplitude, spec=spec)
+                         lateburst_amplitude=lateburst_amplitude, spec=spec,
+                         n_threads=n_threads)
     print(model)
     model.run(np.arange(0, END_TIME, timestep), overwrite=True, pickle=True)
 
@@ -108,7 +110,8 @@ def run_model(filename, prefix=None,
 
 def create_model(prefix, filename, n_stars, 
                  timestep, spec, ratio_reduce,
-                 eta, migration_mode, lateburst_amplitude):
+                 eta, migration_mode, lateburst_amplitude,
+                 n_threads):
 
     simple = migration_mode == "post-process"
     if simple:
@@ -133,6 +136,8 @@ def create_model(prefix, filename, n_stars,
     model.mode = "sfr"
     model.dt = timestep
     model.bins = np.arange(-3, 3, 0.01)
+    model.setup_nthreads = n_threads
+    model.nthreads = min(len(model.elements), n_threads)
             
     model.evolution = create_evolution(spec=spec, burst_size=lateburst_amplitude)
 

### 2023-05-19 surp/simulation/vice_to_json.py

@@ -18,7 +18,7 @@ from surp import yields
 
 def json_output(file_name, isotopic=False, overwrite=False):
     """
-    Creates a vice_model object from the given vice_file and then pickles this object
+    Creates a json object from the given vice_file and then pickles this object
     to store model information in a single file
 
     TODO: Implement isotopic handling
@@ -83,35 +83,6 @@ def reduce_history(multioutput):
 
 
 
-def filt_stars(multioutput):
-    """
-    Helper function which both
-    converts stars from vice.multioutput to 
-    a pandas dataframe and samples the stars
-    to weight by mass correctly"""
-
-    n_stars = 10_000
-    unsampled_stars = pd.DataFrame(multioutput.stars.todict())
-
-    # filter out numerical artifacts
-    s = unsampled_stars[unsampled_stars["zone_origin"] < max_zone]
-    stars = {}
-    stars["all"]= sample_stars(s, n_stars)
-
-    solar_filter = s["r_final"] > 7
-    solar_filter &= s["r_final"] < 9
-    solar_filter &= s["abs_z"] > 0
-    solar_filter &= s["abs_z"] < 0.5
-    stars["solar"] = sample_stars(s[solar_filter], n_stars)
-
-    apogee_filter = s["r_final"] > 7
-    apogee_filter &= s["r_final"] < 9
-    apogee_filter &= s["abs_z"] > 0
-    apogee_filter &= s["abs_z"] < 1
-    stars["apogee"] = sample_stars(s[apogee_filter], n_stars)
-    
-    return unsampled_stars, stars
-
 
 def create_star_sample(stars, num=12000):
     cdf = load_cdf()
@@ -121,7 +92,6 @@ def create_star_sample(stars, num=12000):
         sample = pd.concat((sample, rand_star(stars, cdf)), ignore_index=True)
 
     return sample
-
 
 
 
@@ -139,10 +109,10 @@ def rand_star(stars, cdf):
 def rand_star_in_zone(stars, zone):
     df = stars.loc[stars.zone_final == zone]
 
-    size = len(stars)
-    index = random.choices(np.arange(size), weights=stars["mass"], k=1)
+    size = len(df)
+    index = random.choices(np.arange(size), weights=df["mass"], k=1)
 
-    return stars.iloc[index]
+    return df.iloc[index]
 
 
 

### 2023-05-19 surp/simulation/vice_utils.py

@@ -83,10 +83,6 @@ def sample_stars(stars, num=1000):
     return vice.dataframe(result)
 
 
-def sample_apogee_style(stars, num=1000):
-    pass
-
-
 
 def filter_stars(stars, R_min, R_max, z_min=0, z_max=2):
     return stars.filter("zone_final", ">", R_to_zone(R_min)).filter(

### 2023-07-02 carbon_paper/tex/main.tex
more developed intro

--- 2023-03-13 carbon_paper/tex/main.tex
@@
 % Write the name in the bibliography as "\VAN{Noord}{Van}{van} Noord, Thomas"
-\DeclareRobustCommand{\VAN}[3]{#2}
-\let\VANthebibliography\thebibliography
-\def\thebibliography{\DeclareRobustCommand{\VAN}[3]{##3}\VANthebibliography}
 
@@
 % \usepackage{amssymb}	% Extra maths symbols
+
+\usepackage{isotope}
+
+\usepackage{hyperref}
+
 \graphicspath{{../figures/}}
@@
 %%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%
-\defcitealias{cristallo+11}{C11}
-\defcitealias{cristallo+15}{C15}
-\defcitealias{ventura+13}{V13}
-
-\newcommand{\cristallo}{\citetalias{cristallo+11}+\citetalias{cristallo+15}}
 
@@
 % overwriting existing commands. Example:
-% \newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared
+%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared
+
+\newcommand{\cc}{CCSNe}
+\newcommand{\agb}{AGB}
+\newcommand{\ia}{SNe Ia}
+\newcommand{\sfh}{SFH}
+\newcommand{\dla}{DLA}
+\newcommand{\ssp}{SSP}
+\newcommand{\imf}{IMF}
+\newcommand{\gce}{GCE}
+\newcommand{\apogee}{APOGEE}
+
+\newcommand{\lims}{lower-intermediate mass stars}
+\newcommand{\hms}{high-mass stars}
+
+\defcitealias{james+21}{J21}
+\newcommand{\citetjack}{Roberts et al.~(2023, in prep.)}
+\newcommand{\citepjack}{(Roberts et al.~2023, in prep.)}
+\newcommand{\citealtjack}{Robert et al.~2023, in prep.}
+
+\newcommand{\cxi}{\texttt{\hyperlink{C11}{C11}}}
+\newcommand{\kx}{\texttt{\hyperlink{K10}{K10}}}
+\newcommand{\kxvi}{\texttt{\hyperlink{K16}{K16}}}
+\newcommand{\vxiii}{\texttt{\hyperlink{V13}{V13}}}
+
+\newcommand{\JJ}{\citetalias{james+21}}
 \newcommand{\VICE}{\texttt{VICE}}
+\newcommand{\caah}{[C/Mg]-[Mg/H]}
+\newcommand{\caafe}{[C/Mg]-[Mg/Fe]}
+
+\newcommand{\alp}{$\alpha$}
+\newcommand{\Ycc}{\ensuremath{y_{\rm C}^{\rm cc}}}
+\newcommand{\Yoc}{\ensuremath{y_{\rm Mg}^{\rm cc}}}
+\newcommand{\Ycagb}{\ensuremath{y_{\rm C}^{\rm agb}}}
+\newcommand{\Z}{Z}
+\newcommand{\Zo}{%
+    \ifmmode Z_{\sun}%
+    \else $Z_{\sun}$%
+    \fi}
+\newcommand{\Mo}{%
+    \ifmmode {\rm M}_{\sun}%
+    \else M$_{\sun}$
+    \fi}
+\newcommand{\about}[1]{${\sim} #1$}
+
+\newcommand{\proton}{\isotope[1][1]{p}}
+\newcommand{\zoo}{\ensuremath{Z/Z_{\sun }}}
+\newcommand{\Yct}{\ensuremath{y_{\rm C}}}
 
@@
 % Keep the title short and informative.
-\title[Constraining carbon yields]{The galactic chemical evolution of carbon: Constraining stellar nucleosynthesis}
+\title[Origin and Galactic Evolution of C]{The Galactic Chemical Evolution of Carbon: Implications for Stellar Nucleosynthesis }
 
@@
 % If you need two or more lines of authors, add an extra line using \newauthor
-\author[D. A. Boyea et al.]{
-Daniel A. Boyea,$^{1}$\
-et al.
-% James W. Johnson,$^{1}$
-% David Weinberg
-% Jack Roberts
-% Jennifer Johnson
-% ?
+\author[D. A. Boyea et. al.]{
+Daniel A. Boyea,$^{1}$\thanks{E-mail: boyea.2@osu.edu}
+A. N. Other,$^{2}$
+Third Author$^{2,3}$
+and Fourth Author$^{3}$
 \\
 % List of institutions
-$^{1}$Department of Astronomy, The Ohio State University\\
-$^{2}$Department, Institution, Street Address, City Postal Code, Country\\
-$^{3}$Another Department, Different Institution, Street Address, City Postal Code, Country
+$^{1}$Department of Astronomy, the Ohio State University, 191 W. Woodruff, Columbus, OH 43210, USA
 }
@@
 \begin{abstract}
-Stellar evolution models provide highly uncertain predictions for elemental yields due to our limited understanding of stellar physics.
-In this paper, we aim to estimate the nucleosynthetic yields of carbon using galactic chemical evolution models.
+% context
+Limited knowledge of stellar physics leads to uncertainties in elemental yield predictions.
+% aims
+As an independent approach, we constrain the nucleosynthetic yields of C using multi-zone Galactic chemical evolution models.
+% results
+By matching the median trends of \caah\ and \caafe\ in  {\sc apogee} subgiant stars, we find that high-mass and low-mass stars contribute \about{80\%} and \about{20\%} of total C production respectively.
+% 
+To match the normalization of the trends, we estimate the massive star C/Mg yield ratio $\Ycc/\Yoc = 1.57 + 0.59 \left(Z/Z_\odot\right)$,  explaining the \caah\ trend when including the low mass C contribution.
+%
+Variations in the star formation history only slightly impact the low [Mg/Fe] tail of the [C/Mg]-[Mg/Fe] relation.
+However, most of the scatter in the \caah\ distribution can be attributed to measurement errors and radial migration.
+% 
+Due to the degeneracy between the normalization of elemental yields and the strength of mass-loading in Galactic outflows, we am only able to constrain the relative yields of C/Mg and its metallicity dependence.
+While measurements of gas-phase C abundances are challenging, our model is broadly consistent with the [C/O]-[O/H] trend observed in compiled literature measurements.
 
-We find that the AGB stars make up a fraction $0.20_{-20}^{+80}$ of total carbon production at late times. 
 \end{abstract}
-
-% Select between one and six entries from the list of approved keywords.
-% Don't make up new ones.
-\begin{keywords}
-Need to find some...
-\end{keywords}
 
@@
 
-A fundamental question of Galactic Chemical Evolution (GCE) is understanding the physical processes which make each element.
-Stellar evolution models can be used to predict how much of each element stars with a variety of physical properties produce.
-However, these models are rife with uncertainties, limited by our understanding of critical physical processes such as nuclear reaction rates, convection, opacity, and mass loss (CITE, e.g.
-stellar physics reviews).
+Carbon is a distinctive and well-studied element in astronomy. 
+Formed in the cores of stars during He fusion, C is the lightest directly synthesized element after He, one of the only light elements formed in low-mass stars, and one the most abundant metals\footnotemark{}.
+% \citep[e.g.][]{jennifer19, KL14}
+C structurally changes the environments it pollutes, modifying stellar evolution, facilitating the formation of stars and planets, and forming the basis of earthly life.
+% C/N as age indicator?
+As such, understanding the origin of C has wide ranging implications. 
+While we know both lower-intermediate-mass and high-mass stars produce C, the relative importance of each process is still unknown.
 
-Carbon and nitrogen are the only lighter elements produced significantly by low mass stars, so*****, reasons WHY this study.
+\footnotetext{Astronomers are not chemists. By metallicity, we mean the (mass) fraction of any element which is not H or He, denoted by $Z$. For the sun, $Z_\odot=0.014$. }
 
-Asymptotic Giant Branch (AGB) stars are known to be importaint (cite) from stellar model predictions, previous GCE, and evidence from abundance patterns. (are there detections in PN?)
+Galactic chemical evolution is a powerful tool in understanding the origin of elements. 
+Each enrichment process has distinct chemical signatures and timescales, enabling us to reconstruct chemical histories.
+Many previous works have used GCE in attemt to understand C abundances, whether through using theoretical stellar models \citep{DTS78, prantzos+18, chiappini+03} 
+or understanding  observation \citep{tinsley79, HEK00, BF06, rybizki+17, berg+19, KKL20}.
+(See also review in \citealt{romano22}.)
+%
+Every study agrees that C is produced by a combination of high-mass and \lims{}, different studies disagree on which process is dominant. 
+For example CITES conclude \hms{} dominate wherease CITES conclude \lims{} contribute the majority of C.
+C is also generally understood to have strong metalliicity dependent CCSNe enrichment.
 
-CCSNe are also important (.... SN reminant measurments)
+One of the primary uncertainties of GCE models are nucleosynthetic yields. Yield predictions -- the amounts of each chemical element stars produce --
+are shaped by poorly understood processes, including mass loss, nuclear reaction rates, rotational mixing, convection, and explodability \citep{romano+10,KL14,ventura+13, LC18, emily+21}.
+To better understand where carbon comes from and how it evolves, our aim is to use a combination of recent high-resolution observations from APOGEE and multi-zone models to develop estimates of the required C yields to reproduce galactic trends.
+\cite{james+23} examined similar \gce{} models of N (which is closely related to C), finding that trends in N and O are explained by the metallicity dependence of N/O yields.
+Here, we extend their models to C, deriving similar constraints on C/Mg yields.
+We assess which yield prescriptions reproduce Galactic abundance trends while investigating the impact of \gce{} model assumptions, such as \sfh{} and outflow mass loading.
 
-We also know that there is evidence for non-monatonic carbon yield patterns. 
-pattern where carbon is more readily produced by both high metallicity and very low metallicity stars (CEMPS, early GCE results), but our picture.
+We know, from observations of MW stars and extragalactic gas measurments, that C/O traces a banana shape in O/H (see \ref{fig:gas_phase}). 
+% \cite[e.g.][]{fabbian+09, nissen+14, lambert81, laird85, lambert86}. 
+At very low metallicities, C/O decreases with increasing metallicity, from observations of halo stars and damped Lyman-alpha systems\footnotemark{} \citep{nissen+14, cooke+17, fabbian+09}. 
+\footnotetext{DLAs; high redshift clouds of gas observed as absorption lines in yet higher redshift quasars}
+%
+However, the trend reverses around $[{\rm O/H}]\approx-1$\footnotemark{}. 
+C/O instead increases with increasing metallicity in observations of HII regions and Milky Way stars (\citealt{berg+19}; see discussion in section \ref{sec:gas}).
 
-Additionally, stellar models are computationally expensive, even in one dimension, so while there are grids of predictions, these are not always fine enough to make accurate chemical evolution models.
+\footnotetext{In this paper, we use the standard notation for chemical abundances.
+$[A/B] = \log_{10}\left(A/B\right) - \log_{10}\left(A_{\sun}/B_{\sun}\right)$, i.e.
+$[A/B]$ is the logarithm of the ratio between A and B, scaled such that $[A/B]=0$ for the sun.
+Solar abundances are as measured in \citet{asplund+09}.}
 
-Previous models (CIte). We use \VICE (CITE) to create multi-zone models of GCE enabling us to account for the effects of migration on our predicted yields.
+However, observations of C are not without challenges. 
+As stars ascend the red giant branch (RGB) at the end of H core burning, C abundances are changed by \textit{first dredge up}\footnotemark{}.
+This has the benefit of allowing C/N to be used as an age indicator in RGB stars \citep{MG15, martig16, hasselquist19, vincenzo+21}, but evolved stars are no longer as useful for determining birth abundances.
+Works such as \citet{vincenzo+21} attempt to correct for these changes but this requires MESA stellar modeling.
+In optical spectroscopy, C lines are relatively faint, and surveys such as GALAH struggle against low detection rates, potentially biasing sample measurments.
+While APOGEE includes more reliable C$_2$ lines, there is an additional risk of systematics because .....
+In the gas phase, HII regions are our best window into C abundances in our galaxy and extragalactic regions including dwarf. 
+Unfortunantly, C lacks strong optical emission lines.
+Approaches use either recombination lines or ...
+in the ultraviolet, but these methods disagree, making gas-phase abundances a limited metric for GCE models of C.
 
-\citet{prantzos+18}
-\citep{WAF17}
-\citep{james+21}
-\citep{fiorenzo+21}
+    As our primary observational constraint, we use a sample of subgiant stars from the \apogee{} \citep{apogee17}.
+selected by the criteria in Roberts et al.
+(2023, in prep; see Appendix \ref{sec:jack}).
+According to stellar evolution theory and observations \citep{gilroy89, korn+07, lind+08, souto+18, souto19}, these stars have not yet experienced first dredge up (FDU) but have well-mixed envelopes.
+So, subgiant surface abundances should represent their birth composition.
+Fig.~\ref{fig:subgiants} shows the subgiant sample plotted in \caah\ and \caafe{}. [C/Mg] increases with metallicity, and [C/Mg] decreases with [Mg/Fe] at fixed [Mg/H]. 
+Using these trends, we will develop a model of the enrichment sources and evolution of C.
 
-\citep[e.g.][]{james+22}
-
-Carbon abundances are strongly affected by CNO cycle processing in stars.
-The CNO cycle is one of two series of nuclear reactions( $^{12}$C(p, $\gamma$)$^{13}$N($\beta^+ \nu_e$)$^{14}$N(p, $\gamma$)$^{15}$O($\beta^+\nu_e$)$^{15}$N(p,$\alpha$)$^{12}$C
-
-Because the $^{14}$N(p, $\alpha$) proton capture is the slowest component of the CNO cycle ****, the CNO cycle, to first order, converts all $^{12}$C into $^{14}N$.
-
-One challenge of measuring abundances of carbon in star is that when a star becomes a RGB star, material from the CNO-processed core.
-Since this core-processed material is now carbon depleted and nitrogen enhanced, measurments of this star's atmosphere will no longer reflect the birth abundances of the star.
-
-In Figure \ref{fig:sum} we present a sample of APOGEE subgiants.
-These subgiants were chosen based on their location in the HR diagram based on criteria in \citet{jack_subgiant} replicated in Appendix \ref{sec:jack}.
-Because subgiants have not undergone FDU, their surface abundances are an accurate reflection of the birth abundances (CITATION).
+\footnotetext{First dredge up (FDU) is when material from CNO processed core is mixed with the (convective) stellar envelop during the ascent onto the RGB.
+As a result, C is decreased and N is increased depending on the strength of this process and the envelop mass.}
 
@@
     \centering
-    \includegraphics[]{subgiants_mgh.pdf}
-    \includegraphics[]{subgiants_mgfe.pdf}
-    \caption{Chemical abundance relationships of our sample of APOGEE subgiants (see Jack et al. 2023). Left panel shows }
-    \label{fig:sum}
+    \includegraphics{subgiants.pdf}
+    \caption[Subgiant Abundances]{The [C/Mg] ratio against [Mg/H] (top) and [Mg/Fe] (bottom) for the \citetjack~sample of \apogee{} subgiants.
+On the top, we plot high and low-$\alpha$ stars in blue and orange, using the separation defined in Equation \ref{eq:high_alpha} (the high and low-$\alpha$ stars are named for their high or low $\alpha$-element to Fe ratios, or in this case, Mg/Fe).
+On the bottom, we colour-code stars according to their [Mg/H] abundance.} \label{fig:subgiants}
 \end{figure*}
+
 \section{Nucleosynthesis}
 
-Galactic chemical evolution are fundamentally intertwined with our understanding of stellar nucleosynthesis.
-In this paper, we are concerned with three major nucleosynthetic pathways: AGB stars, CCSNe, and Supernovae type Ia.
-While only AGB stars and CCSNe are producers of carbon, SNeIa Fe can be used to compare with the AGB delayed carbon component.
+Yields -- the amounts of each chemical element stars synthesise -- are central to studies of galactic chemical evolution (GCE). 
+In this section, we discuss the yield choices of our model and literature models for C yields. 
+We focus on three nucleosynthetic pathways: asymptotic giant branch (\agb{}) stars, core collapse supernovae (\cc{}), and type Ia supernovae (\ia{}).
+C is produced in both \agb{} and \cc{} stars.
+We also use Mg and Fe as tracers of \cc{} and \ia{} enrichment respectively. 
+O and Mg are produced almost entirely from \cc\ with metallicity-independent yields, making each element. In contrast Fe is produced in similar amounts by \cc\ and \ia.
 
-\VICE allows us to explore the nucleosynthesis of various models, as it includes AGB tables for C11, et.c
+After a single stellar population (SSP)\footnotemark{} forms, \cc{} are the first chemical enrichers.
+\cc{} explode within $\lesssim 40$\,Myr, providing light elements (C, O, and Mg) and heavier elements (Fe and beyond).
+Next, low-mass stars begin to reach the end of their lives.
+By shedding their outer layers, \agb{} stars are important sources of C, N, and neutron capture elements.
+Finally, white dwarfs explode in \ia{}, releasing Fe and other iron-peak elements.
 
-We discuss carbon nucleosythesis in more detail in the next two sections.
-We assume that the only dominant sources of carbon are from AGB stars and CCSNe/massive star winds.
-***JUSTIFY***.
-Below  is a brief overview of our  nucleosythetic assumptions of other elements.
+\footnotetext{SSP: Single stellar population. Technical name for a group of stars born in the same conditions at the same time, i.e. an open cluster.}
 
-Let $y_{\rm X}^{\rm proc}(M, Z)$ be the fractional yield of element X by a process proc for stars of a mass $M$ (in solar masses) and at metallicity $Z$ defined as: 
+To quantify yields, we define the stellar yield to be the fraction of a stars initial mass which is newly synthesized and released as a given element. 
+For an element $X$ and star with mass $M$, the net-fractional stellar yield $\tilde{y}$ is 
 \begin{equation}
-    y_{\rm X} = \frac{M_{\rm X,\ ej} - M_{\rm X,\ birth}}{M}   
+\tilde{y}_{X} = \frac{M_{\rm ejected}}{M_{\rm birth}} (Z_{f, X} -  Z_{0, X})
 \end{equation}
+where $M_{\rm ejected}$ and $M_{\rm birth}$  are the total ejected mass and the birth mass of the star, and $Z_{f, X}$ and $Z_{0, X}$ are the initial birth abundance and final abundance of the ejected envelop respectably.
+For example, if a 1\,\Mo\ star has $\tilde{y}_{\rm C} = 10^{-3}$, then the star will add $10^{-3}\,\Mo$ of new C to the interstellar medium.
+Although per-star yields are necessary to compute \agb{} star enrichment rates in \gce{}  models, \imf-averaged yields are useful in interpreting their predictions.
+For a yield $y$ from a star of mass M and initial metallicity $Z$, the \imf-averaged yield is given by
+\begin{equation} \label{eq:imf-yield}
+    y_{\rm X}(Z,t) = 
+    \int_{M_{\rm min}(t)}^{M_{\rm max}} 
+    \tilde{y}_{\rm X}(M, Z)
+    \frac{dN}{dM}  \ dM
+\end{equation}
+where ${dN}/{dM}$ is the normalized \imf, $M_{\rm max}=100\,\Mo$ is the maximum stellar mass, and $M_{\rm min}(t)$ is the mass of stars with lifetime $t$.\footnotemark{}
+We use $t=10\,$Gyr for total yields when $t$ is not used.
+To calculate the \imf-averaged net yields, we use the Versatile Integrator for Chemical Evolution code (\VICE\footnotemark{}).
 
-Where $M_{\rm X,\ ej}$ and $M_{\rm X,\ birth}$ are the mass of element X ejected and initially present in the star. 
-We define the IMF-integrated yield of X with: 
-\begin{equation}
-Y_{\rm X}^{\rm proc}(Z) = \int_{M_{\rm min}}^{M_{\rm max}} y_{\rm X}^{\rm proc}(M, Z)\ \Phi(M)  \ dM
-\end{equation}
-Where $\Phi(M) = \frac{dN}{dM}/ \int_{M_{\rm min}}^{M_{\rm max}} \frac{dN}{dM}\ dM$ is the normalized IMF, $M_{\rm min}$ and $M_{\rm max}$ are the minimum and maximum mass of stars, which we take to be $0.08 M_{\sun}$ and $100 M_{\sun}$ respectively; and $\frac{dN}{dM}$ is the initial mass function, the frequency of stars born between $M$ and $M+dM$.
+We adapt the yield choices of elements besides C from \citet{james+21, james+23}.
+Table \ref{tab:fiducial_mod} contains our fiducial yields. 
+Following \citet{james+21, james+23}, we also take the \ia{} delay time distribution to be a $t^{-1.1}$ power-law, as suggested by the observations of \citet{maoz+12}.
 
-There are two $\alpha$-elements we care about: Mg and O.
-Stellar observations of magnesium are more reliable but oxygen abundances are easier to measure in HII regions.
-We assume that both Mg and O are produced entirely in CCSNe with constant, metallicity-independent yields.
-Thus $\text{[Mg/H]} = \text{[O/H]} = [\alpha/\text{H}]$ in our models
+\addtocounter{footnote}{-2}
+    \stepcounter{footnote}\footnotetext{In our model, the mass-lifetime relation is
+$\log \tau_M = 1.02 - 3.57\log M + 0.90 \left(\log M\right)^2$,
+where $\tau_M$ is in Gyr, from \citealt{larson74}}
 
+\stepcounter{footnote}\footnotetext{\VICE~is available at \url{https://github.com/giganano/VICE}}
+
+\begin{table}
+	\centering
+    \caption[Fiducial Model Yields]{Yields for the fiducial model (in units of \ssp~birth mass). See Section \ref{sec:agb} for the definition of \cxi.}
+	\label{tab:fiducial_mod}
+
+	\begin{tabular}{l l l l}
+		\hline
+        Element & $\Ycc$ & $\tilde{y}^{\rm AGB}$ & $y^{\rm SNe Ia}$ \\
+		\hline
+        C & $0.0028 + 0.001\,(Z/Z_\odot)$ & $2.9\times{\rm C11}$ &  0 \\
+        Mg & 0.00185 & 0 & 0 \\
+        Fe & 0.0012 & 0 & 0.00214 \\
+        N & 0.00072 & $9\times10^{-4}\,(Z/Z_\odot)\,M$ & 0\\
+		\hline
+	\end{tabular}
+\end{table}
+
+\subsection{Asymptotic Giant Branch Stars}\label{sec:agb}
+
+An \agb\ star is a low-mass star ($\lesssim 8 M_{\sun}$) during its final phase of evolution.  
+In an \agb\ star, two competing processes determine the outcome of C production: \textit{third dredge up} and \textit{hot bottom burning}.  
+Third dredge up accompanies thermal pulses in \agb\ stars, where material from the CO core is mixed with the envelope, increasing surface C abundances \citep{KL14}.
+The C yields of the star are increased as this C-enhanced envelope is released to the interstellar medium.
+Hot bottom burning is the activation of the CNO cycle\footnotemark{}
+at the bottom of the convective envelope when $T\gtrsim 50\,{\rm MK}$.
+Because the $^{14}$N proton capture is the slowest component of the CNO cycle, the CNO cycle converts nearly all \isotope[12]{C} into \isotope[14]{N} \citep{solar-fusion}.
+
+Hot bottom burning and third dredge-up result in mass-dependent C yields. 
+Stars less than about??2\,\Mo do not experience third dredge-up.
+As a result, these stars C abundances are only affected by first dredge-up, resulting in little change to C yields or slight destruction of C.
+In 2?? to 4?? \Mo stars, third dredge up becomes important, enriching the outer layers with C, making these stars the most important producers of C. 
+In massive, high-metallicity \agb\ stars, both hot bottom burning and third dredge up occur; however, third dredge up is much more efficient, resulting in significant \isotope[12]{C} destruction.
+
+\footnotetext{
+    The CNO cycle and the details of AGB evolution are described in appendix \ref{sec:stel_evo}.
+}
+
+    In this work, we explore four different sets of \agb\ star yield tables from literature,
+    providing necessary well-sampled grids in mass and metallicity. We refer to the yields from the following studies as the following.
 \begin{itemize}
-    \item observational validation
+    \item \cxi: \citet{cristallo+11, cristallo+15}
+    \item \kx: \citet{karakas10}
+    \item \vxiii: \citet{ventura+13,ventura+14,ventura+18, ventura+20}
+    \item \kxvi: \citet{KL16, karakas+18}
 \end{itemize}
-For carbon, the dominant producer is from massive stars which eject carbon fused in their cores during CCSNe.
+For our models to match observations, we find that need to uniformly amplify these yield tables. We use \cxi\ table, amplified by a factor of 2.9, as the fiducial \agb\ yield.
 
-Taken from J21 and J22, we make the following yield assumptions:
-\begin{itemize}
-    \item $Y_\text{O}^\text{CC} = 0.015$
-    \item $Y_\text{O}^\text{Ia} = 0$
-    \item $Y_\text{Fe}^\text{Ia} = 0.00214?$
-    \item $Y_\text{Fe}^\text{CC} = 0.0012$
-    \item $Y_\text{N}^\text{CC} = 0.00036$
-    \item $y_\text{N}^\text{AGB}(M, Z) = 9\times 10^{-4} M \left(\frac{Z}{Z_\odot}\right)$
-\end{itemize}
-Also following J21/J22, we take the SNeIa Delay Time distribution to be a $t^{-1.1}$ law based on
-the observations by \citet{maoz+12}.
+Fig.~\ref{fig:y_agb} compares the stellar \agb\ C yield for these four models.
+Note that the net yields may be negative if a star ejects material with a lower average C abundance than the material the star was formed from.
+Most models agree on the qualitative shape of the net fractional \agb\ C yield---% 
+stars with masses between about 2--4\,\Mo have the highest fractional C yields. As metallicity increases, the total AGB C yield decreases and the mass of the peak increases.
 
-We leave consistent throughout the paper.
-While different CCSNe models predict different absolute values for $y_\text{O}^\text{CC}$, they also predict that the yield is metallicity-independent within the uncertainties of the model.
+Fig.~\ref{fig:agb-ssp}, on the left, shows the total production of C by \agb\ stars in a \ssp{} at an age $t$, i.e. $\tilde{y}_{\rm C}(Z_\odot, t)$. 
+As the mass range $2\,\Mo\lesssim M \lesssim 4\,\Mo$ is most important for C production, about half of C production occurs before \about{1}\,Gyr, similar to \ia\ Fe. 
+\kx{} and \kxvi{} weight C production more heavily towards high-mass AGB stars resulting in a faster enrichment delay time, whereas the \cxi\ and \vxiii\ models predict a slightly longer timescale of \about{1}\,Gyr.
+In any case, little to no C is produced more than 2\,Gyr after a star formation event.
+In contrast, Fe production continues steadily for 10\,Gyr.
 
-\subsection{Asymptotic giant branch carbon}
-
-An AGB star is a low mass ($\lesssim 8 M_{\sun}$) star during the final phases of evolution.
-The star has already completed Hydrogen core burning, Hydrogen shell burning during the red giant branch phase, and Helium core burning.
-So, the structure consists of an inert core of carbon and oxygen surrounded by a Helium burning shell and a Hydrogen burning shell.
-The double shell burning leads to thermal instabilities which drive off the outer layers of the star in a series of violent pulsations, ejecting the envelope and leaving behind a C/O white dwarf.
-
-In an AGB star, TDU and HBB are two major processes involved in carbon production and destruction.
-TDU occurs during thermal pulsations, where the convective layer of the star passes into the inner layers with He-burning products which mixes in C and O into the envelope.
-In contrast, HBB may happen if the base of the convective envelope reaches about 50MK, initiating the CNO cycle, converting most C12 into N14.
-
-The differences in yields between AGB models depend on the mass loss rate, treatment of convection, and nuclear reaction rates.
-
-In this work, we explore four different sets of AGB star yields representative of the variety of options which also provide reasonably well sampled grids in metallicity and mass necessary for chemical evolution studies.
-\begin{itemize}
-    \item \citetalias{cristallo+11}
-    \item \cristallo
-    \item \cite[C11][Hi]{cristallo+11}: \citet{cristallo+11}
-    \item K10: \citet{karakas10}
-    \item V13: \citet{ventura+13}
-    \item K16: \citet{KL16}
-\end{itemize}
-Unless otherwise noted, C11 is the model we choose as our fiducial AGB yield.
-
-Figure \ref{fig:y_agb} compares the net fractional AGB carbon yield, $m_\text{C}^\text{AGB}(M, Z)$ for each AGB model we consider.
-Note that the yields may be negative when the birth abundance is higher than the carbon abundance of the material ejected back to the ISM.
-
-Most models agree on the qualitative shape of the net fractional AGB carbon yield.
-The stars with the highest fractional carbon yields are between 2 to 4 solar masses, depending on the metallicity and model.
-Both lower and higher mass stars produce less carbon, and high mass stars may even destroy carbon at high metallicity due to highly efficient HBB.
-And all models agree that the carbon yield generally decreases with metallicity.
-
-Metallicity dependence:
-V13 is the only model that stands out, showing a non-monotonic metallicity dependence, however this effect is only for models with [M/H]$\leq -1$.
-Otherwise the major differences between the models are the precise amount of carbon and the slope of the metallicity dependence.
-For example, the three models C11, K10, and K16 predict $y_\text{C}^\text{AGB}$ to be between 0.006 and 0.008 at solar metallicity, but C11 has a much shallower metallicity dependence than the K10 and K16 models.
-And at solar, V13 predicts a value at around 0.004 so the models are all within about a factor of 2.
-
-Another difference is the speed at which equilibrium is reached.
-K10 and K16 weight carbon production more heavily towards massive stars resulting in a faster time to equilibrium, whereas the C11 and V13 models predict a slightly longer timescale with order 1Gyr, but little to no carbon is produced more than 2Gyr after a star formation event.
-This is in contrast to iron which is still produced by SNeIa up to 10Gyr after a star formation event.
+The right panel of Fig.~\ref{fig:agb-ssp} shows \imf-averaged C yields for each \agb\ model as a function of metallicity $Z$.
+\vxiii{} differs in that it shows a non-monotonic metallicity dependence. However, this effect is only for models with $\log Z/Z_\odot \lesssim -1$.
+Otherwise, models differ only in their yield normalization and metallicity dependence. All models predict yields within a factor of \about{2} for fixed metallicity.
+For example, the three models \cxi, \kx{}, and \kxvi{} predict $y_\text{C}^\text{AGB}$ to be between 0.006 and 0.008 at solar metallicity, but \cxi\ has a much shallower metallicity dependence than the \kx{} and \kxvi{} models.
+\vxiii{} instead predicts a yield \about{0.004}.
+    As shown in the right panel of Fig.~\ref{fig:agb-ssp}, with increasing $Z$, C enrichment occurs earlier, and C destruction in low-mass stars leads to a declining C abundance at late times.
 
@@
     \centering
- 	    \includegraphics[scale=1]{agb_yields.pdf}\\
-
-    \caption{The net fraction carbon yield ($M_\text{C}$, the amount of carbon produced by the star divided by $M$) plotted as a function of mass, $M$.
-Lighter colors represent higher values of metalicity ([M/H]).
-Each panel represents a different AGB model.
-K10 reports stars at MoverH -3, -2, etc.
-I can reproduce C11 and K10 but not other V13 and KL16 :(((}
-
+ 	    \includegraphics[scale=1]{agb_yields.pdf}
+        \caption[]{The net fractional \agb\ C yield  plotted as a function of initial stellar mass $M$ and colour-coded according to metallicity.
+The black dashed line shows $\tilde{y}=0$ for reference.
+Each panel represents yields from one of four \agb\ models: \cxi, \kx{}, \vxiii{}, \kxvi{} (see Section \ref{sec:agb} and  Appendix \ref{sec:oob_models}).
+}
         \label{fig:y_agb}
@@
     \centering
+    \includegraphics{y_agb_vs_t.pdf}
+    \includegraphics{y_agb_vs_z.pdf}
 
-    \includegraphics[scale=1]{y_agb_vs_z-1.pdf}
-    \includegraphics[scale=1]{y_agb_vs_t-1.pdf}
+    \caption[]{ C production by \agb\ stars as a function of \ssp{} age, normalized to the total mass $M_{\rm tot}$ produced at $t=10$\,Gyr.
+\textbf{Left:} The four \agb\ yield models from literature at solar metallicity (\cxi, \kx{}, \vxiii{}, or \kxvi{}).
+The dashed black line shows the delay time distribution of type Ia supernovae ($\propto t^{-1.1}$) for comparison.
+\textbf{Right:} The (\imf-weighted) \agb\ C yield $\Ycagb$ as a function of metallicity for each of the \agb\ yield models.
+($\Ycagb$ is the net mass of C produced by \agb\ stars per unit mass of star formation, after 10\,Gyr and assuming a \citealt{kroupa01} \imf.) }
 
-    \caption{On the left, we plot the IMF weighted net fractional carbon yields of each AGB model as a function of metalicity.The right panel plots the normalized net carbon AGB yield as a function of time for a population of stars born at the same time at solar metallicity.
-We note that for the right panel, the minimum of the DTD for V13 is }
+    \label{fig:agb-ssp}
 
@@
 
-\subsection{CCSNe carbon}
+\subsection{Core Collapse Supernovae}
 
-While there are many stellar models providing predictions of CCSNe yields, the results of these models are highly uncertain due to the many stellar modeling uncertainties.
+Massive stars form $^{12}$C in their cores through the triple--$\alpha$ process (see Appendix \ref{sec:stel_evo}).
+However, only C ejected through supernovae and stellar winds contributes to the yield.
+While there are many stellar models providing predictions of \cc{} yields, the results of these models are highly uncertain due to the many stellar modeling uncertainties.
 
-We summarise many of the predictions of stellar models in Figure \ref{fig:y_cc}. Pink squares
-represent \citep{NKT13}, etc. etc.
-\citep{LC18}
-\citep{sukhbold+16}
-\citep{WW95}
+Fig.~\ref{fig:y_cc} plots calculations of the \imf-integrated yields, defined with Eq.~\ref{eq:imf-yield} (computed using \VICE's \texttt{vice.yields.ccsne.fractional} function). 
+\cc{} models predict a wide range of C yields, spanning almost a factor of ten. 
+Both the \citet{NKT13} and \cite{LC18} models show positive metallicity dependence. 
+The \cite{LC18} models also include rotation, showing that variations in the rotational velocity of the star can dramatically increase the magnitude and metallicity dependence of $\Ycc$.
+Rotation induces more mixing allowing the CO core to grow larger.
+As we will later show, \cc\ C production needs to be strongly metallicity-dependent at $Z/Z_\odot \approx 1$, which is consistent with the \cite{LC18} rapidly rotating models.
 
-On the right, we plot the expected CCSNe abundance ratio of each model as a function of metallicity, defining
-\begin{equation}
-    {\rm [C/O]^{CC}} = \log_{10}\left( \frac{y_{\rm C}^{\rm CC}}{y_{\rm O}^{\rm CC}}\right) - \log_{10} \left( \frac{Z_{C, \sun }}{Z_{O, \sun }} \right)
+Fig.~\ref{fig:y_cc} shows the \cxi{} \agb\ model for comparison on the left.
+Especially at $Z\approx Z_\odot$, most \cc{} models dominate \agb\ C production.
+Later, we will also show empirically this is the case.
+On the right of Fig.~\ref{fig:y_cc}, we also show the \cc{} [C/Mg] ratio, defined by
+\begin{equation}\label{eq:c_mg_cc}
+    {\rm [C/Mg]^{CC}} = \log_{10}\left( \frac{\Ycc}{\Yoc}\right) - \log_{10} \left( \frac{Z_{{\rm C},\ \sun }}{Z_{{\rm Mg},\ \sun }} \right).
 \end{equation}
-Notice how even these ratios 
+If only \cc{} produced C, then ${\rm [C/Mg]^{CC}}$ describes the equilibrium abundance of [C/Mg].
+Once again, different \cc\ models span a large range in [C/Mg]. 
+we chose to instead parameterize $\Ycc$ to enable agreement with observations, as most \cc\ models fail to achieve near-solar [C/Mg].
+Assumptions about the explodability landscape affect C and Mg production.
+Increasing the fraction of stars that explode increases $\Ycc$, as stars that directly collapse do not contribute to explosive yields \citep{emily+21}.
+However, C is relatively unaffected by the black-hole landscape, as very massive stars contribute C through enriched winds.
+Since Mg is formed deeper in the core of \hms, the Mg yield drops much more steeply, so models where few stars explode (S16/W18) have higher [C/Mg].
+
+\cc\ models do not reach [O/Mg] due to overproduction of O or underproduction of Mg, or both \citep{emily+21}.
+Here, we assume ${\rm [O/Mg]} = 0$, which is not compatible with \cc\ models but is consistent with \apogee{} observations \citep{weinberg+19, weinberg+22}.
+Out model predictions of [C/Mg] and [C/H] are identical. There is a slight slope in [O/Mg] with metallicity, so this could add a systematic to our model.
+
 \begin{figure*}
-    \includegraphics[scale=0.9]{y_c_cc-2.pdf}
-    \includegraphics[scale=0.9]{y_co_cc.pdf}
-    \caption{The fist plot shows IMF-weighted net fractional CCSNe yield of carbon, $y_C^{cc}$ against metalicity, [M/H], for different studies.
-The right plot instead shows [C/O]$^\text{CC}$, the logarithm of the abundance ratio of carbon to oxygen if CCSNe were the only carbon source, also as a function of metallicity for the same set of studies.
-The black line represents the carbon yield of the fiducial model, $y_C^{CC} = 0.004?
-(Z/Z_{\sun})^{0.3}$, and becomes dashed over regions where we have not tested our model.
+    \centering
+    \includegraphics{cc_yields.pdf}
+    \caption[High-Mass Star Carbon Yields]{
+        C yields from high-mass stars.
+        \textbf{Left} The \imf-weighted \cc\ yield of C as a function of metallicity.
+        \textbf{Right} The \cc\ [C/Mg] abundance ratio, defined in Eq.~\ref{eq:c_mg_cc}. The black line is the derived C yield from Section \ref{sec:equilibrium},
+    $\Ycc = 0.0028 + 0.001 (Z/Z_{\odot})$. Yields are shown for tables from 
+    \citet[red triangles]{WW95}, \citet[orange squares and diamonds]{sukhbold+16}, 
+    \citet[green stars]{NKT13}, and \citet[blue circles]{LC18}.
+\citet{sukhbold+16} report yields for different black hole landscapes, while \citet{LC18} provide yields at different rotational velocities.
+    In the top panel, the pink line denotes $\Ycagb$ from \cxi{} for comparison. All models include wind yields.
 }
@@
 
-    \begin{itemize}
-        \item Wide range in predictions, exacerbated to 1 dex range when including variance in oxygen predictions
-        \item (explain) most models have a near-metallicity independent oxygen yield, so we choose the fiducial value of 0.015 despite varience in $y_O^{cc}$
-        \item The fiducial value, where we choose the carbon yield from Sukhbold+16, may be above most predictions of carbon yields but is within the range of yield ratios
-        \item the fiducial value would reach an equilibrium carbon yield of -0.1 without AGB stars
-        \item Rotation in LC18 appears to increase metallicity dependence of carbon production (read this paper more carefully)
-        \item NKT and LC agree in positive metallicity depenent yields
-    \end{itemize}
+\section{The Equilibrium Approximation}\label{sec:equilibrium}
 
-\section{The Multizone Model}
+In the presence of metal-poor gas accretion and feedback-driven outflows, galaxies reach an equilibrium abundance in which production of new metals is balanced by losses to new stars and outflows \citep{larson72, dalcanton07, FD08, PS11, lilly13}.
+While our galaxy is likely not in perfect equilibrium or described by a single, homogeneous chemical
+envirnoment, the equilibrium approximation is nevertheless useful in understanding yields and
+metallicity dependence of solar neighborhood stars \citep[e.g.][]{james_dwarf,james+23,WAF17}.
 
-To simulate the chemical evolution of a Milky way like galaxy, we use the Versitile Integrator for
-Chemical Evolution (\VICE\footnote{\VICE~is available at \url{https://github.com/giganano/VICE}}) published in \citet{james+21} and also briefly described in
-\citet{james+22}. 
-As a multi-zone model, the galaxy is divided into 200 rings of 0.1kpc, each with separate gas supplies with outflow and inflow rates.
+We assume a simple \textit{one-zone} chemical evolution model \cite[e.g.][]{tinsley80, pagel09, matteucci21}.
+Newly produced metals are homogeneously and instantaneously mixed, so spatial dependence is neglected.
+We define $M_{X}$ to be the mass of element $X$ in the gas-phase, $\dot{M}_\star$ to be the star formation rate (in $\Mo\,{\rm yr}^{-1}$), and $\eta$ to be the mass loading factor $\eta\equiv\dot{M}_{\rm outflow}/\dot{M}_\star$ (representing the strength of outflows).
+A \ssp\ returns a fraction $r$ of their birth mass to the interstellar medium, due to ejected stellar envelopes.\footnotemark{}
+Given the \imf-averaged yield of Mg $y_{\rm Mg}$, the rate of change in the gas-phase mass of Mg is a simple sum of sources and sinks,
+\begin{equation}
+    \dot{M}_{\rm Mg} =  y_{\rm Mg}\,\dot{M}_\star - \dot{M}_{\rm Mg,remnants} - \dot{M}_{\rm Mg,outflows},
+\end{equation}
+where $y_{\rm Mg} \dot{M}_{\star}$ describes \cc\ enrichment. 
+In terms of the return mass fraction of stars $r$, the mass lost to remnants is $Z_{\rm Mg}\,\dot{M}_\star\,(1-r)$.
+And, the outflows deplete mass at a rate $Z_{\rm Mg} \,\dot{M}_\star\,\eta$.
+(We assume the composition of outflows is the same as the interstellar medium.) Substituting for $\eta$ and $r$,
+\begin{equation}
+    \dot{M}_{\rm Mg}= y_{Mg}\,\dot{M}_\star - (1 + \eta - r)\,Z_{Mg}\,\dot{M}_\star.
+\end{equation}
+Assuming an exponentially declining star formation history $\dot{M}_\star \propto e^{-t/\tau_{\rm sfh}}$, the equilibrium abundance is derived analytically by setting $\dot{Z}_{Mg}=0$.
+\begin{equation}\label{eq:z_eq}
+    Z_{\rm Mg}^{\rm eq}(R) = \frac{y_{\rm Mg}}{1 + \eta(R) - r - \tau_\star / \tau_{sfh}},
+\end{equation}
+where $\tau_{\star}$ is the star formation rate. ($\eta$ depends on $R$ to create a metallicity gradient. See also Section \ref{sec:vice} and Eq.~\ref{eq:eta_r}.)
+In the special case of constant star formation, $\tau_{\rm sfh}\to\infty$, the denominator simplifies to $1+\eta-r$.
 
-\VICE\ accounts for radial migration by using the results of the \texttt{h277} hydrodynamical simulation.
-Each VICE SSP is matched to a random nearby star particle \textit{analogue} in \texttt{H277}.
-VICE approximates the migration of this particle by using a $\sqrt{\text{time}}$-diffusion approximation where the change in galactic radius of a star, $\Delta R$, is $\Delta R \propto \sqrt{\text{t}}$.
-VICE does not account for radial gas flows.
-
-Other approaches have used dynamical arguments to implement their stellar mirgrations.
-We note that our approach does not introduce more free parameters which may bias conclusions.
-However, we only consider one dynamic history, and it is still unknown how variations in the dynamic history of a galaxy impact its chemical evolution.
-
-We initially assume an "inside-out" SFH where the star formation rate peaks in the early evolution of the galaxy and is higher closer to the galactic center.
-The star formation rate, $\Sigma_\star$, for our fiducial model is parameterized by
+Likewise, for \agb\ stars,%
+\footnote{In detail, the \agb\ contribution requires integration over the \sfh\ to account for the finite lifetimes of stars.
+However, for this exponential \sfh, this effect is minimal, so we simply use $\Ycagb$ for the current \agb\ contribution.}
+Eq.~\ref{eq:z_eq} then becomes
 \begin{equation}
-    \dot{\Sigma}_\star \propto \left(1-e^{-t/\tau_{\rm rise}}\right) e^{-t/\tau_{\rm sfh}}
+    Z_{\rm C}^{\rm eq}(R) = \frac{\Ycc + \Ycagb}{1 + \eta(R) - r - \tau_\star / \tau_{\rm sfh}}
 \end{equation}
-where $\tau_\text{rise}=2$Gyr is the
-and $\tau_{sfh}$ is the rate of decline of the star formation rate, which is based on *****.
-
-We also explore a "lateburst" model which is parameterized with a normal distribution multiplying our fiducial "inside-out" SFH as
+And the equilibrium C/Mg abundance ratio is
+\begin{equation}\label{eq:z_co}
+    \frac{Z_{\rm C}^{\rm eq}}{Z_{\rm Mg}^{\rm eq}} = \frac{\Ycc + \Ycagb }{\Yoc}.
+\end{equation}
+Analogous to \cite{james+23} arguments about N, the trends in abundance ratios are set by yield ratios in these \gce{} models.
+The effect of other \gce{} parameters (most importantly $\eta$) cancels.
+As a consequence, yield ratios should establish abundance ratio trends in models which assume a different normalization of element yields and mass-loading (see discussion below).
+This argument can also be inverted to infer  yields from abundance ratio trends.
+To the extent that observed C and Mg trends reflect the equilibrium abundances in different Galactic regions, we can infer the \cc\ yield given an assumed \agb\ star yield (or vice versa).
+Inferring $\Ycc$ from $\Ycagb$,
 \begin{equation}
-    \dot{\Sigma}_{\rm lateburst} \propto \dot{\Sigma}_{\rm insideout} \left(1 + A e^{-(t-\tau_{\rm burst})^2/2\sigma^2_{\rm burst}} \right)
+    y_\text{C}^\text{CC} =  y_\text{Mg}^\text{CC} \frac{Z_\text{C,~eq}}{Z_\text{Mg,~eq}} - \langle y_c^{agb} \rangle
+\end{equation}
+Rewriting this expression as a relative yield of C and Mg,
+\begin{equation}\label{eq:y_c_eq}
+    \frac{\Ycc}{\Yoc} = \frac{Z_{\text{C},~\odot}}{Z_{\text{Mg},~\odot}} 10^{\rm [C/Mg]} - \frac{\Ycagb}{\Yoc}.
 \end{equation}
 
-$A=1.5$ represents the amplitude of the birth, $\tau_\text{burst}=10.8$Gyr is the time where the burst is strongest, and $\sigma_\text{burst}=1$Gyr is the width of the burst.
-We do explore the effects of variations of this parameterization in section ****.
+\footnotetext{$r\approx0.4$ for a \citealt{kroupa01} \imf.}
 
-VICE normalizes the total mass of star formation against observations from ******.
-The gas inflow is calculated based on our star formation parameterization by using a schmit law 
+\subsection{Yield Models}
+
+As we will discuss in Section \ref{sec:outflows}, the normalization of yields and $\eta$ is degenerate.
+This can be observed in Eq.~\ref{eq:z_co}, where changes in $\eta$ or the scaling of $y_{\rm C}/y_{\rm Mg}$ would not affect equilibrium trends.
+Furthermore, in Eq.~\ref{eq:z_eq}, an increase in both $y_{\rm Mg}$ and $\eta$ would leave $Z_{\rm Mg}^{\rm eq}$ unchanged.
+Our models here are unable to distinguish the overall scaling of yields and outflow mass loading.
+Choosing to keep $y_{\rm C}$ fixed reduces unnecessary free parameters.
+So, at solar metallicity, we set
+\begin{subequations}
+    \begin{align}
+        \Yct~\big\vert_{Z=Z_\odot} &= \Ycc + \Ycagb = 0.005 \\
+        \Yct/\Yoc~\big\vert_{Z=Z_\odot} &= 2.7.
+    \end{align}
+\end{subequations}
+This ratio results in an equilibrium abundance ${\rm [C/Mg]} = -0.09$, which is consistent with the subgiant sample and is within \about{20\%} of the solar C/Mg mixture from \citet{asplund+09}.
+
+In Section \ref{sec:f-z-models}, we will show that none of the four \agb\ yield sets (\cxi{}, \kx{}, \vxiii{}, \kxvi{}) produce enough C relative to this $\Ycc$ value.
+So, we introduce normalization factors, $\alpha_{\rm AGB}$, and $\alpha_{\rm CC}$ which denote a multiplicative scaling of $\Ycc$ and $\Ycagb$ respectively.
+\begin{subequations} \label{eq:alpha}
+    \begin{align}
+        \Ycagb &\rightarrow \alpha_{\rm AGB}\ \Ycagb \\
+        \Ycc &\rightarrow \alpha_{\rm CC}\ \Ycc\\
+        \alpha_{\rm CC} &= \frac{\Yct - \alpha_{\rm AGB}\ \Ycagb}{\Ycc}
+    \end{align}
+\end{subequations}
+Above, $\alpha_{\rm CC}$ is dependent on the choice of $\alpha_{\rm AGB}$ to keep the total C yield constant.
+
+In Section \ref{sec:f-z-models}, we find that $\alpha_{\rm AGB}\approx 2.9$ for the \cxi{} yield model.
+Using this \agb\ yield, we can now use Eq.~\ref{eq:y_c_eq} to find an estimate of $\Ycc$ as a function of metallicity.
+We show the values of $\Ycc$ we obtain from the subgiant sample in Fig.~\ref{fig:analytic}.
+From a regression analysis, we suggest here that
+\begin{equation}\label{eq:zeta}
+    \Ycc = 0.0028 + \zeta\left(\frac{Z}{Z_\odot}\right),
+\end{equation}
+where $\zeta\approx0.001$ describes the metallicity dependence.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{analytic.pdf}
+    \caption[Reverse-Fit Yields]{Inferred high-mass star C yields as a function of metallicity.
+We assume equilibrium and $3\times {\rm C11}$ \agb\ yields (orange curve, see discussion in Section \ref{sec:equilibrium}).
+Blue points are the median value of $\Ycc$ for each bin in [Mg/H] with uncertainties based on the median absolute deviation.
+    }
+    \label{fig:analytic}
+\end{figure}
+
+\subsection{Uncertainties}
+
+We only perform this analysis on the \cxi{} yields because \cxi{} has yields tables more finely sampled in metallicity than the other three \agb\ yield tables.
+As the metallicity range of the data is small ($-0.4\lesssim {\rm [Mg/H]} \lesssim 0.4$), other models are more challenging to interpret in this range.
+Furthermore, the \apogee{} observations may have systematics.
+Other measurements of C abundances \citep[e.g.][]{vincenzo+21} have slight disagreements in the overall shape of the trend (see Section \ref{sec:jack}).
+So, this expression of $\Ycc/\Yoc$ depends on the chosen \agb\ yield table, the \agb\ fraction, and the dataset. 
+Additionally, these yields will be systematically biased if the galaxy is out of equilibrium, for example, due to a recent starburst \citep{mor+19,isern19}.
+Further exploration could investigate the magnitude of these uncertainties, but we find that the qualitative conclusions are similar despite substantial variations in the assumptions here.
+
+\section{The Multi-zone Model}\label{sec:vice}
+
+Classical, \textit{one-zone} models of chemical evolution assume instantaneous mixing of metals in the star-forming interstellar medium \citep[e.g.][]{matteucci21}.
+This simple framework is a poor approximation of the Milky Way.
+The Galaxy evolves insideout---where star formation is higher towards the center and in the early universe \citep{bird+13}.
+Additionally, stars can migrate several kpcs over their lifetimes, mixing different chemical environments across the galaxy \citep{bird+12,sellwood+binney02}.
+For the rest of this paper, we focus on multi-zone models, which discretize the Galaxy into concentric rings in which stars move between.
+Our models extends the \citet{james+21} (hereafter \JJ) Milky Way model, run with the publicly available Versatile Integrator for Chemical Evolution (\VICE). 
+This model is described extensively in \JJ~and concisely summarized  in \citet{james+23}. Here, we provide a brief overview of the relevant model components.
+
+In the model, the Galaxy is divided into 200 rings, each 100\,pc wide.
+Each ring has a separate stellar population and gas supply.
+Star formation ends beyond a radius $R=15.5\,$kpc.
+We initially assume an insideout \sfh{}, where the star formation surface density $\Sigma_\star$ is given by
+\begin{equation}\label{eq:inside_out}
+    \dot{\Sigma}_\star \propto \left(1-e^{-t/\tau_{\rm rise}}\right) e^{-t/\tau_{\rm sfh}}.
+\end{equation}
+$\tau_\text{rise}=2$\,Gyr describes when the star formation rate reaches a maximum, and $\tau_{\rm sfh}$ describes the decay timescale of star formation as a function of radius $R$.
+\JJ~derives $\tau_{\rm sfh}(R)$ through analysis of four integral field spectroscopy surveys in \cite{sanches20}.
+The star formation history is normalized such that the total stellar mass reaches $5.17\times10^{10}\,\Mo$ \citep{LM15} and at each $R$ to match the stellar surface density gradient \citep{BHG16}.
+The gas inflow is calculated to maintain our chosen \sfh{} for each radius and time, using an extension of a Kennicutt-Schmidt law \citep{kennicutt98},
 \begin{equation}
-    dM_g \propto \dot{\Sigma}^{1/n}
+\dot{\Sigma}_{\star} \propto 
+\begin{cases}
+    {\Sigma}_{\rm gas} & 2\times 10^7 \leq \Sigma_{\rm gas} \\ 
+    {(\Sigma}_{\rm gas})^{3.6} & 5\times 10^6 \leq \Sigma_{\rm gas} < 2\times10^7 \\ 
+    {(\Sigma}_{\rm gas})^{1.7} & \Sigma_{\rm gas} < 5\times10^6 \\ 
+\end{cases}
+\end{equation} UNITS.
+The scaling of this relationship varies with time due to the redshift dependence of $\tau_\star$ in molecular gas observed by \citet{tacconi18}. We assume a \citet{kroupa01} \imf.
+
+\JJ\ accounts for radial migration by using the results of the \texttt{h277} hydrodynamical
+simulation \citep{christensen12, zolotov12, loebman12, BZ14}, with simulation parameters described
+in \citet{bird+21}. Each \VICE\ single stellar population (SSP) is matched to an \textit{analog} in
+\texttt{H277}, chosen to form at a similar time and radius $R$. By taking the change in radius
+$\Delta R$ of the analogs, the SSPs move to their final radii with a $\sqrt{\text{time}}$ dependence.
+This relationship between displacement and time arises when migration proceeds as a consequence of the diffusion of angular momentum \citep{frankel18, frankel20}.
+We do not account for radial gas flows.
+Using the results of a hydrodynamical simulation without modification limits the free parameters in the model; however, we am limited to one dynamical history.
+The impact of the details of a galaxy's dynamical history on its chemical evolution is still unknown.
+
+As the strength of outflows controls the resulting $\alpha$ abundances, \JJ~create a metallicity gradient by defining
+\begin{equation}\label{eq:eta_r}
+\eta(R) = \frac{y_{\alpha}^{\rm CC}}{Z_{\alpha, \odot}} 10^{(-0.08\,\text{kpc}^{-1})(R-4\,\text{kpc})+0.3} + r - 1.
 \end{equation}
-where we take $n$ to be ****
+This choice of $\eta(R)$ results in a [$\alpha$/H] gradient consistent with Milky Way observations \citep[e.g.][]{hayden+14, weinberg+19, frinchaboy+13}.
 
-Salpeter IMF.
-
-\subsection{Yield Parameterization}
-  Because of the large uncertainties in CCSNe carbon yields, we choose to explore an analytic expression of the yield enabling us to easily explore how variations of CCSNe carbon yields affect abundance tracks.
-We find that a powerlaw yield with a metallicity-dependent constant minimum is able to match the observations well while remaining a simple parameterization (see below).
-Our expression is:
-    \begin{equation}
-   y_\text{C}^\text{CC}(Z) =  \alpha\ Z^\beta y_\text{O}^\text{CC} + y_\text{C, 0}^\text{CC}
-    \end{equation}
-   	Where we estimate $\alpha = 0.02$ and $\beta = 0.25$ (See Section \ref{equilibrium} ).
-Our second model uses $\alpha = 0.44$ and $\beta = 0.63$ with K16 yields and reduced $\eta \rightarrow 1/2 \eta$
-
-    As an overall scaling of yields does not significantly affect our models, we choose to fix the total equilibrium value of the total carbon yield at solar at $Y_{\text{C},\ \sun} = 0.005$, and then scale the yields relative to this value.
-
-\section{Multizone model results}
-
+\section{Results}
 \subsection{Data Selection}
 
-We use data from APOGEE DR17 processed with APOSCAP.
-Since subgiant stars have yet to experience FDU, their atmospheric carbon and nitrogen abundances are still reflective of their birth abundances and do not need mixing corrections.
+\citet{james+23} compare their model against the \cite{vincenzo+21} sample of \apogee{} \citep{apogee17} RGB stars.
+\citet{vincenzo+21} use \textsc{mesa} stellar evolution models \citep{mesa} to correct for the effects of First Dredge Up (FDU).
+We instead use the \citetjack~sample of \apogee{} subgiants.
+Subgiant stars have not undergone FDU but have well-mixed atmospheres, so their atmospheric C and N abundances are still reflective of their birth abundances and do not need mixing corrections.
+We only compare the models to the low-$\alpha$ sequence unless otherwise specified.
+The selection criteria and differences between the samples are described in more detail in Appendix \ref{sec:jack}.
 
-To select for subgiants, we use the following cut in $\log g$ and $T_{\rm eff}$ which selects stars at the base of the red giant turnoff (FIGURE and \cite{jack_subgiant})
+\subsection{The Evolution of Carbon Abundances in the Galaxy}
 
-Because the star formation history is left in a simple inside-out form, this multizone model does not reproduce the high-$\alpha$ sequence, therefore we make the following cut to the V21 data to remove the high alpha sequence.
+Here, we present the time evolution of our fiducial model. In the next Sections, we will discuss the choice of parameters and agreement with observations. 
+The fiducial model has the following qualitative characteristics of its C yields: (a) C is predominantly produced in \cc, (b) \cc\ produce more C at higher metallicities, and (c) \agb\ stars produce less C at higher metallicities.
+The fiducial model uses the \cxi{} \agb\ yield tables (see Section \ref{sec:agb}, and Table \ref{tab:fiducial_mod}), and we amplify the \cxi{} yields by a factor of 2.9 such that \agb\ stars account for 20\% of C at $Z=Z_\odot$.
 
-\begin{equation}
+We show the time evolution tracks of the fiducial model in Fig.~\ref{fig:c_evo} for \caah~ and \caafe.
+Comparing [C/Mg] against [Mg/Fe] enables us to see the late-time evolution of C more clearly.
+Because of the extended delay time distribution of \ia\ enrichment, [Fe/H] takes longer to reach equilibrium, and the late-time evolution is not as clustered as [Mg/H].
+The evolution proceeds as follows.
+Initially, \cc\ dominate production.
+As $\Ycc$ has strong metallicity dependence, [C/Mg] increases with time.
+Shortly thereafter, \agb\ stars contribute delayed C, increasing [C/Mg] even more steeply.
+As Mg begins to reach equilibrium, the [C/Mg] ratio plateaus as C approaches equilibrium.
+Finally, as $\Ycagb$ decreases or even becomes negative with higher metallicity, the [C/Mg] abundance may decline slightly.
+This is more evident in the lower panel of Fig.~\ref{fig:c_evo}---while the \caah\ trend reaches equilibrium at \about{5}\,Gyr, the \caafe\ trend continues to evolve even until the present day, exposing the effect of the relative delay times of \agb\ stars and \ia.
+
+\begin{figure*}
+\centering
+\includegraphics{all_the_tracks.pdf}
+\includegraphics{coofe_tracks.pdf}
+\caption[Carbon Chemical Evolution Tracks]{
+    Time evolution of gas-phase C abundances in our fiducial model.
+    {\bf Top:} Evolutionary tracks parameterized by time at fixed Galactocentric radius in the \caah\ and \caafe\ planes. 
+    {\bf Bottom:} Snapshots of the gas-phase \caah\ and \caafe\ trend, parameterized by radius at a fixed time.
+}
+\label{fig:c_evo}
+\end{figure*}
+
+\subsection{Low mass stellar yields}\label{sec:f-z-models}
+
+Discussion of negative yields.
+
+Negative AGB yields cause a morphological change in the abundance trends.
+If the yields of low mass stars are negative, then at late times in a SSP, C abundances will decrease.
+This will appear as a downturn in the \caafe{} abundance trends as [Mg/Fe] approaches solar values.
+As we do not observe this in the data, this is either obscured by star formation history (Seee eeee) or observational scatter.
+
+Instead, if lower-intermediate mass AGB stars produce negative carbon yields, it is possible to observe this as a dip in the early parts of the \caafe{} trend...
+
+To parameterize the \agb\ contribution to C production, we define 
+\begin{equation}\label{eq:f_agb}
+    f_{\rm AGB} \equiv \frac{\Ycagb}{\Yct}\Bigg\vert_{Z=Z_\odot},
+\end{equation}
+where  $\Ycagb$ includes the multiplicative factor $\alpha_{\rm AGB}$ as defined in Eq.~\ref{eq:alpha}.
+Fig.~\ref{fig:agb_sims} compares the \kx{}, \kxvi{}, \cxi{}, and \vxiii{} yield models.
+We use the published, unscaled yield tables ($\alpha_{\rm AGB}=1$) for Fig.~\ref{fig:agb_sims}.
+As the highest \agb\ yield at solar, \kx{} is only $\Ycagb=0.000585$, $f_{\rm AGB} \leq 0.12$ for all models.
+Massive stars dominate C production with unscaled yields.
+While it is easy to modify the \agb\ yields in our model, their small contribution reduces the effect.
+We leave a more detailed discussion of the effects of \agb\ models for Appendix \ref{sec:f-z-models} and use \cxi{} yields hereafter.
+
+\begin{figure*}
+\centering
+\includegraphics{agb_oob.pdf}
+\caption[Median Stellar Abundance Trends]{
+    Stellar abundance trends in our model, assuming metallicity independent $\Ycc$.
+Colored lines quantify the median [C/Mg] in bins of [Mg/H] for our four \agb\ yield models from the literature (see Section \ref{sec:agb}).
+Black points and grey dashes represent the median and standard deviations of [C/Mg] for each [Mg/H] bin in the \citetjack~sample.
+In the right panel, we show the trends only for stars where $-0.15\leq {\rm [Mg/H]}\leq -0.05$.
+}
+\label{fig:agb_sims}
+\end{figure*}
+
+Next, we investigate adjustments to the \agb\ yield fraction $f_{\rm AGB}$ and the \cc\ metallicity dependence $\zeta$ in Fig.~\ref{fig:beta_f}.
+On the top panel of Fig.~\ref{fig:beta_f}, we plot models with varying $\Ycc$ metallicity dependence.
+As discussed in Section \ref{sec:equilibrium}, the \caah~trend is approximated by equilibrium, so the trends of these have steeper \caah~corresponding to steeper metallicity dependence.
+However, \caafe~is minimally affected by these changes since \cc\ occurs on much shorter timescales than \ia\ and \agb\ enrichment.
+
+In the bottom panel of Fig.~\ref{fig:beta_f}, we plot three models with different \agb\ fractions while using \cxi{} yields.
+The \caafe~relationship is set by $f_{\rm AGB}$ because a specific amount of C must be released at a delayed time to match the \ia\ production of Fe and increase [C/Mg] as [Mg/Fe] decreases to reproduce the data.
+Increased $f_{\rm AGB}$ results in a decreased slope in \caah, owing to the negative metallicity dependence of $\Ycagb$.
+So while \caah~alone cannot differentiate models which vary $f_{\rm AGB}$ and $\zeta$ correspondingly, \caafe~provides information on $f_{\rm AGB}$.
+So, we can use \caafe~to estimate $f_{\rm AGB}\approx 0.2$, and then choose $\zeta$ to match \caah.
+
+One source of theoretical uncertainty in this result is that the \ia\ yield and delay time distributions have their own uncertainties.
+We discuss variations in $y_{\rm Fe}^{\rm Ia}$ in Appendix \ref{sec:f-z-models}, and find that the qualitative conclusions are largely unaffected.
+I, therefore, focus on the choices of $y_{\rm Fe}^{\rm Ia} = 0.00214$ and a $t^{-1.1}$ delay time distribution choices from the fiducial model here.
+In short, the scaling of the trend and metallicity dependence of C (as seen in
+the \caah\ trend) gives information on the total C yield and the behavior of \cc\ (as the dominating producer of C), the \caafe\ trend exposes the delayed effect of C from \agb\ contribution.
+
+\begin{table}
+	\centering
+    \caption[Low-Mass Stellar Carbon Yields at Solar Metallicity]{For each \agb\ yield set, the \imf-averaged \agb\ C yield at solar metallicity $y_{\rm C, 0}^{\rm AGB}$ and the multiplicative factor reaches an \agb\ contribution of 20\% $\alpha_{\rm AGB, 20}$.}
+	\label{tab:alpha_agb}
+	\begin{tabular}{ccr} % four columns, alignment for each
+		\hline 
+		AGB Model & $y_{\rm C, 0}^{\rm AGB}$ & $\alpha_{\rm AGB, 20}$\\
+        \hline
+        \cxi & 0.000347 & 2.9\\
+        \kx & 0.000585 & 1.7\\
+        \vxiii & 0.000060 & 16.5\\
+        \kxvi & 0.000421 & 2.4\\
+		\hline
+	\end{tabular}
+\end{table}
+
+\begin{figure*}
+\centering
+\includegraphics{beta.pdf}
+\includegraphics{f_agb.pdf}
+
+\caption[Adjusted Yield Models]{Similar to Fig.~\ref{fig:agb_sims} except the top plot shows the fiducial model with lower and higher values of $\zeta$, the metallicity dependence of $\Ycc$.
+The bottom plot shows models with $f_{\rm AGB}=$0.1, 0.2, and 0.4.
+Both the $f_{\rm AGB}$ and $\zeta$ influence \caah, but only $f_{\rm AGB}$ has a significant impact on \caafe.}
+\label{fig:beta_f}
+\end{figure*}
+
+\subsection{Star Formation History} \label{sec:sfh}
+
+Here, we consider a \textit{lateburst} model, created by multiplying our fiducial insideout \sfh{} with a Gaussian.
+\begin{equation}\label{eq:lateburst}
+    \dot{\Sigma}_{\rm lateburst} \propto \dot{\Sigma}_{\rm insideout} \left(1 + A\,e^{-(t-\tau_{\rm burst})^2/2\sigma^2_{\rm burst}} \right)
+\end{equation}
+
+$A=1.5$ represents the amplitude of the birth, $\tau_\text{burst}=10.8$\,Gyr is the time where the burst is strongest, and $\sigma_\text{burst}=1$\,Gyr is the width of the burst.
+We also consider an \textit{earlyburst} model as a slight variation of the lateburst, where the burst is instead exponential and placed at $t_1=5$\,Gyr. 
+\begin{equation}\label{eq:twoinfall}
+    \dot{\Sigma}_{\rm earlyburst} \propto \dot{\Sigma}_{\rm insideout} + 
 \begin{cases}
-\text{[Mg/Fe]} >0.12-0.13\text{[Fe/H]}, & \text{[Fe/H]}<0\\
-\text{[Mg/Fe]} >0.12, & \text{[Fe/H]}>0\\
+    A\,e^{-(t-t_1)/\tau_{\rm burst}} & t_1 < t \\
+      0 & t<t_1
 \end{cases}
 \end{equation}
+where we take the burst duration, $\tau_{\rm burst}=1$\,Gyr in this case. 
+This approximately corresponds to the Gaia-Encelidus merger, inducing higher star formation in the Milky Way \citep{spitoni21, bonaca20, helmi18}.
 
-See Appendix \ref{sec:jack} for further discussion of our sample and comparison to FIORENZO.
-
-\subsection{The Evolution of carbon across the galaxy and through time}
-
-The GCE of carbon is complicated by metallicity dependencies and delayed contributions.
-
-We note the following features of our model:
-
-\begin{enumerate}
-    \item Carbon comes predominantly ($\sim80\%$) from CCSNe but the rest is from AGB stars
-    \item The CCSNe carbon production is more efficient at higher metallicities
-    \item AGB stars produce less carbon at higher metallicities.
-\end{enumerate}
-
-The combination of these features leads to an evolution that proceeds as follows
-\begin{enumerate}
-    \item Initially, CCSNe dominate production before AGB stars can contribute their enrichment, but because CCSNe is highly metalliticy dependent, the C/$\alpha$ ratio increases with time.
-    \item AGB stars begin contributing their carbon, increasing the $C/\alpha$ ratio more steeply as the gas begins to reach its equilibrium metallicity
-    \item When $Z$ reaches equilibrium, the $C/\alpha$ ratio stops increasing or may even decline, as AGB stars formed at higher metallicities reduce the net carbon yields.
-\end{enumerate}
-
-We plot time evolution tracks in Figure \ref{fig:c_evo} for $[C/\alpha]-[\alpha/H]$ and $[C/\alpha]-[Fe/H]$ for our fiducial model.
-Each colored track corresponds to a different galactic radius and 1Gyr time steps are marked with crosses on the lines.
-
-Comparing [C/$\alpha$] against [Fe/H] enables us to see late time evolution of carbon more clearly.
-Because [Fe/H] takes longer to reach equilibrium as half of iron production comes from type-Ia supernovae, the late time evolution is not clustered as tightly horizontally as for [$\alpha$/H].
-
-This is even more evident in the lower part of Figure \ref{fig:c_evo}, where we instead plot snapshots of the galactic radial trend at different times for our model.
-While the [C/$\alpha$]-[$\alpha$/H] trend reaches almost equilibrium at 5Gyr, the [C/$\alpha$]-[$\alpha$/Fe] trend continues to evolve even until the present day, exposing the effect of the delayed contribution from AGB stars on the evolutionary history.
+Fig.~\ref{fig:sfh_models} shows three models with these alternate \sfh{}.
+Changes to the \sfh{} leave \caah\ unchanged, but they do introduce slight variation in \caafe.
+Models with higher \agb{} fractions are more sensitive to variations in the \sfh{}.
+The late burst models result in [C/Mg] continuing to increase at low [Mg/Fe], but also introduce a dip not present in the data.
+Additionally, the early burst
+reproduces the slight break between the low and high $\alpha$ sequences, but overshoots equilibrium more severely than the fiducial model. 
+In general, any of these \sfh{}s are consistent with this model.
 
 \begin{figure*}
-\label{fig:c_evo}
-\includegraphics{evo_tracks-9.pdf}
-\includegraphics{evo_slices-2.pdf}
-\caption{The top set of panes show the time evolution of the gas phase of our fiducial model, plotted as tracks through [C/O]-[O/H] and [C/O]-[O/Fe] where each colored line corresponds to the evolution at that galactic radius.
-The bottom set instead shows the galaxies gas-phase [C/O]-[O/H] and [C/O]-[O/Fe] trend at 5 different time slices. 
+\centering
+\includegraphics{lateburst_eta.pdf}
+
+\caption{Similar to Fig.~\ref{fig:agb_sims} but comparing the fiducial model to alternate star formation histories (see Section  \ref{sec:sfh}).}
+
+\label{fig:sfh_models}
+\end{figure*}
+
+\subsection{Degeneracies} \label{sec:outflows}
+
+Radial migration doesn't matter...
+
+\gce{} models of the Milky Way fall into two classes---those which incorporate significant mass-loading (e.g., this work) and those which neglect mass-loading but lower effective yield to match observed abundances \citep[e.g.][]{MCM13, MCM14, spitoni19, spitoni20, spitoni21}.
+An increase in stellar yields has a nearly identical effect as a decrease in the mass-loading factor $\eta$ (see Appendix B of \citealt{james_dwarf}).
+The equilibrium arguments discussed in Section \ref{sec:equilibrium} suggest however that abundance ratios are independent of the choice of normalization and the value of $\eta$.
+I, therefore, expect our results regarding the relative yield $y_{\rm C}/y_{\rm Mg}$ and its metallicity dependence to extend to the other class of models omitting mass loading.
+We demonstrate this further here.
+
+The theoretical motivation for decreasing yields is the uncertainty in stellar explodability.
+If fewer \hms\ explode, then the yields will be reduced by some factor.
+Additionally, some fraction of supernovae ejecta may be lost directly to an outflow, lowering effective yields.
+To explore reduced outflow models, we lower both $\eta$ and all yields by the same factor to leave the equilibrium abundances unchanged.
+
+Fig.~\ref{fig:eta} shows models with variations of the mass loading strength.
+While changing the value of $\eta$ affects the metallicity distribution of stars, all of the models in Fig.~\ref{fig:eta} still evolve along the same path.
+Our model is unable to differentiate a uniform decrease in both outflows and yields.
+
+\begin{figure*}
+    \centering
+    \includegraphics{eta.pdf}
+    \caption[Reduced-Outflow Models]{Similar to Fig.~\ref{fig:agb_sims} but comparing the fiducial model to reduced mass loading models (see Section  \ref{sec:outflows}).
+Both yields and mass-loading are adjusted correspondingly such that the equilibrium abundances are unchanged.
+}
+    \label{fig:eta}
+\end{figure*}
+
+\subsection{Gas-Phase Abundances}\label{sec:gas}
+
+C abundances are challenging to measure.
+When a star enters the Red Giant Branch (RGB), material from the CNO-processed core is mixed with the envelope in first dredge up, enhancing N and depleting C \citep{iben67, vincenzo+21,KL14}.
+Measurements of these evolved stars'  atmospheres will no longer reflect their birth abundances.
+Additionally, gas-phase measurements of C are extremely limited as C lacks strong lines in HII regions \citep{skillman+20}.
+
+As an additional test of the model, we next compare the model predictions against gas-phase measurements.
+Fig.~\ref{fig:gas_phase} shows the fiducial model's gas-phase predictions compared to observations of the Milky Way and extragalactic HII regions, halo stars, and \dla\ systems.
+The model is broadly consistent with observations, where the model at $t=2$\,Gyr approximates the slope of dwarf galaxies and halo stars.
+The increase of C/O at higher metallicities is also consistent with the high C/O abundances measured in extragalactic HII regions.
+Our model does not extend to very low metallicity, where the slope of the trend inverts, but broadly explains observations above $\rm [O/H] \gtrsim -1$.
+
+Mg measurements are more reliable, but O abundances are easier to measure in HII regions.
+So while we use Mg as the representative alpha for stellar abundances, we instead use O when comparing gas-phase abundances.
+As we assume ${\rm[Mg/O]}=0$, our model is independent of the choice of the alpha
+
+Measurements of C abundances in the gas-phase are challenging.
+In HII regions, C/O abundance ratios are measured with either recombination lines or collisional excitation lines.
+However C lacks strong collisional excitation lines, and recombination lines fall in the ultraviolet without nearby reference H lines \citep{skillman+20}.
+Additionally, recombination and collisional excitation measurements disagree by a factor of \about{2} \citep{GR07}.
+Variations in the \sfh{}s may furthermore increase scatter, as \agb\ are a delayed source of C.
+
+The decreasing [C/O] abundance at very-low metallicities is likely due to population III stellar yields \citep[e.g.][]{hirschi07}, as suggested by \citet{cooke+17} and \citet{FN15}.
+agb stars cannot explain the increase in C yields at low metallicity in the \dla{} sample as the evolutionary timescales of \dla{}s are shorter than the typical delay time distribution of \agb\ stars.
+
+\begin{figure*}
+    \centering
+    \includegraphics{nitrogen.pdf}
+    \caption[C/N Abundance Agreement]{Similar to Fig.~\ref{fig:agb_sims}, except comparing [C/N] from the fiducial model only.
+N yields are adapted from \cite{james+23}.
+(See also Table \ref{tab:fiducial_mod}.)
     }
@@
 
-\subsection{Effects of AGB Yields}
-\begin{figure*}
-\includegraphics[scale=0.6]{oob_agb-1.pdf}
-
-\caption{Abundance tracks for 4 different choices of AGB models.
-Each panel has different abundance ratios on the axis but is otherwise the same.
-The black points are Jack Roberts selection of APOGEE subgiants.
-Each model is plotted as a line representing the mean stellar abundance in each bin on x.}
-\label{fig:stars_abundances}
-\end{figure*}
-
-How much does the choice of AGB model affect chemical evolution? 
-Short description of effects of AGB model choices, and how we can rule out models like V21.  Maybe point to appendex B?
-
-Our next exploration is to adjust the relative fraction of AGB star yields. To do this, we hold the total carbon yield at solar metallicity fixed, so for a desired AGB fraction (assuming equilibrium),
-
-\begin{equation}
-    \alpha_{AGB} = f_{agb} \frac{y_{desired}}{y_0^{agb}}
-\end{equation}
-\begin{equation}
-    \alpha_{CC} = (1 - f_{agb}) \frac{y_{desired}}{y_0^{cc}}
-\end{equation}
-
-\subsection{Star Formation History}
-
-We do run models with an alternate "lateburst" stars formation history.
-
-equation of lateburst
-
-However, we find that the star formation history has a negligable effect on the shape of the mean track.
-More drastic changes in SFH could explain the high alpha/low alpha seperation but we leave further exploration of SFH to future work.
-
-% \begin{figure*}
-% \includegraphics[width=1.5\columnwidth]{cooh_lateburst.pdf}
-% \caption{Same as Fig. \ref{fig:stars_abundances} but with different model choices.}
-% \end{figure*}
-
-\begin{figure*}
-\includegraphics[scale=0.6]{beta-1.pdf}
-\includegraphics[scale=0.6]{f_agb-1.pdf}
-
-\caption{Similar to \ref{fig:stars_abundances} except the top plot shows the fiducial model with lower and higher values of $\beta$, the C-CCSNe metallicity dependence.
-The bottom plot is the same except shows varying AGB fractions.}
-\end{figure*}
-
-\begin{figure*}
-\includegraphics[scale=0.6]{lateburst_eta-1.pdf}
-
-\caption{Same as Figure \ref{fig:stars_abundances} but comparing the fiducial model to the reduced outlow model and a lateburst model. (okay, need to totally change approach...)}
-\end{figure*}
-
-\subsection{Adjusted CCSNe Yields}
-
-\begin{figure}
-    \includegraphics[scale=0.6]{cooh_scatter.pdf}
-    \caption{The simulated stars of our model at present day plotted on [C/O]-[O/H] and colored such that lighter colors represent stars born at greater galactric radii.}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[scale=0.6]{cnoh.pdf}
-    \caption{Caption}
-    \label{fig:cnofe}
-\end{figure}
-
 \begin{figure*}
 \centering
-\includegraphics[]{summary-2.pdf}
-\caption{Present-day gas phase tracks of the fiducial model in [C/O]-[O/H] space. M101 is valid comparison to MW ...(van Dokkum et al. 2014)}
+\includegraphics[]{summary.pdf}
+\caption[Gas-Phase Abundances]{Gas-phase C abundances. We plot our model at $t=2$\,Gyr and present day as thick solid lines. Points represent measurements in 
+    HII regions    \citep[pink circles;][]{skillman+20, esteban+02, esteban+09, esteban+14, esteban+19}
+    \dla\ systems \citep[blue triangles;][]{ellison+10, srianand+10, dutta+14, DZ+03, pettini+08, morrison+16,cooke+17},  % a1: Cooke et al.
+(2015); 2: Dutta et al.
+(2014); 3: Cooke et al.
+(2014); 4: Ellison et al.
+(2010); 5: Cooke et al.
+(2011b); 6: This work; 7: Pettini et al.
+(2008); 8: Morrison et al.
+(2016); 9: Srianand et al.
+(2010); 10: Cooke et al.
+(2012); 11: Dessauges-Zavadsky et al.
+(2003)
+    dwarf galaxies \citep[red diamonds;][]{berg+19},
+    Milky Way halo and thick disk stars \citep[green stars;][]{nissen+14, fabbian+09},
+    and Milky Way high-$\alpha$ stars (yellow points; \citealtjack).
+}
 \label{fig:gas_phase}
 \end{figure*}
-\subsection{The AGB Fraction }
-One potential tension with data is our models predict a low value for the AGB fraction of stars.
-
-Our model with Z-dependent CCSNe yields has $f_\text{agb} = 0.05$ which implies that CCSNe overwhelms AGB production and there should not be a seperation between low and high alpha sequences.
-However, V21 observes a significant seperation implying a more substantial delayed-time source.
-
-Even changing the AGB model does not affect the conclusion significantly.
-
-An alternate solution is to reduce the outflows and core collapse yields similarly, consistent with a model where more large stars collapse directly into black holes.
-This leaves the $y_\text{C}^\text{CC}/y_\text{O}^\text{CC}$ ratio unchanged, but because $y_\text{C}^\text{CC}$ is unchanged, the relative size of the AGB contribution is larger.
-
-Increasing the relative AGB production lowers the magnitude of  $y_\text{C}^\text{CC}/y_\text{O}^\text{CC}$, but the metallicity dependence of the ratio must increase to compensate for the inverse metallicity dependence of AGB carbon yields.
-
-We find that we can adjust both the outflows and scale down the yields if we change our model for $y_\text{C}^\text{CC}/y_\text{O}^\text{CC}$.
-For example, reducing outflows and CCSNe yields by a factor of two requires the modified parameters
-$\alpha = 0.033$ and $\beta = 0.625$, which results in a slightly lower value at solar but nearly a doubling of the metallicity dependence.
-
-These models are indistinguishable in the [C/O]-[O/H] plane from our adjusted CCSNe model, so future work investigating the SFH and carbon isotopic ratios in more depth may be able to provide more insight.
-In the next section, we develop the analytic tools to explore this problem in more depth.
-
-\subsection{Outflows}
-A common degeneracy in chemical evolution models is the yield-outflow degeneracy.
-An increase in stellar yields has a near-identical effect as a decrease in outflows.
-However, reducing the outflows reduces the evolution timescale of the system.
-
-The theoretical motivation for decreasing outflows is due to the uncertainty in the explodability landscape---if less massive stars explode, then both the yields and outflows will be reduced by some factor.
-So, when we explore reduced outflow models, we consider models where both the outflows and yields are reduced by approximately the same factor, to leave the equilibrium abundances of a pure CCSNe unchanged.
-
-The effect of reducing outflows is then increasing the relative contributions of non-CCSNe processes. For carbon, this increases the AGB fraction.
-
-We have found that the [C/O]-[O/Fe] relationship may provide insight into this issue.
-[O/Fe] is a tracer of the relative contributions of CCSNe and delayed-time sources in chemical evolution.
-So, the appearance of a slope in [O/Fe] implies that there is a substantial delay-time process in carbon evolution.
-The metallicity-dependence of carbon yields complicates this picture because younger stars have higher [O/Fe] as the SNeIa contributions take up to 10Gyr, so metal-poor young stars will naturally have lower [C/O], agreeing with the slope observed in [C/O]-[O/Fe].
-However, a pure CCSNe carbon model cannot reproduce the slope accurately as
-
-\subsection{Comparison to HII Region Observations}
-In Figure \ref{fig:gas_phase}, we plot our two favorite models against HII-region measured carbon abundances from **********
-
-Our model appears to be broadly consistant with the gas phase data, however these imply if anything that the slope should be increased.
-
-Are HII regions a good approximation?
-
-Short discussion of measurment challenges in extragalactic galaxies, how other galaxies and dwarf SFH may come into play, why this relation is notecably steeper.
-
-\section{The Equilibrium Approximation}\label{equilibrium}
-If we assume that the median track is an equilibrium phenomenon, we can calculate the total carbon to oxygen yield ratio.
-Additionally, assuming an AGB yield set enables us to predict the CCSNe carbon yield.
-We begin with the model, which underlies the multizone simulations, that the change in mass of an element is a sum of production, outflows, recycling, and mass left in reminants. We write this as
-\begin{equation}
-M_\text{C} = y_\text{C} \dot{M}_\star - (1 + \eta - r) Z_\text{C} \dot{M}_\star
-\end{equation}
-
-In the case that carbon
-\begin{equation}
-Z_c^{eq}(R) = \frac{y_c^{cc} + \langle y_c^{agb} \rangle }{1 + \eta(R) - r - \tau_\star / \tau_{sfh}}
-\end{equation}Where
-\begin{equation}
-\langle y_c^{agb} \rangle = \frac{\int_0^T y_c^{agb}(M, Z) \dot{M}_\star(T - t) \frac{dN}{dM} \frac{dM}{dt} dt  }{ \dot{M}_\star \int_0^T \frac{dN}{dM} \frac{dM}{dt} dt}
-\end{equation}
-
-Likewise for oxygen:
-\begin{equation}
-Z_O^{eq}(R) = \frac{y_O^{cc}}{1 + \eta(R) - r - \tau_\star / \tau_{sfh}}
-\end{equation}
-
-However, for the yield ratio, the denominator cancles with that of oxygen, so the ratio is fixed.
-\begin{equation}
-\frac{Z_c^{eq}}{Z_o^{eq}} = \frac{y_c^{cc} + \langle y_c^{agb} \rangle }{y_o^{cc}}
-\end{equation}
-
-For this analysis, we let $y_c^{agb}$ represent the default AGB yields from a given yield set, but add a process factor $\alpha_{agb}$ which multaplicatively increases the AGB fraction.
-See Table \ref{tab:alpha_agb}.
-
-\begin{equation}
-    y_{\rm C}^{\rm CC} \rightarrow \alpha_{agb}  y_{\rm C}^{\rm CC}
-\end{equation}
-
-With these definitions, we can calculate the core collapse yields of carbon as a function of metallicity:
-\begin{equation}
-    y_\text{C}^\text{CC} =  y_\text{O}^\text{CC} \frac{Z_\text{C,eq}}{Z_\text{O,eq}} - \alpha_{agb} \langle y_c^{agb} \rangle
-\end{equation}
-
-Rewriting in terms of the observed abundance ratio and dividing by $y_\text{O}^\text{CC}$.
-So, given the outflows or CCSNe oxygen yields, the carbon AGB yield, and the [C/O]-[O/H] mean abundance track, we can estimate the CCSNe carbon yield.
-Written as a relative yield:
-\begin{equation}
-    \frac{y_\text{C}^\text{CC}}{y_\text{O}^\text{CC}} = \frac{Z_{C, \sun}}{Z_{O, \sun}} 10^{[C/O]} - \frac{\alpha_{agb} \langle y_c^{agb} \rangle}{ y_\text{O}^\text{CC}}
-\end{equation}
-
-This equation corroberates what we have explored earlier in the paper, and provides our analytic estimates of the CCSNe carbon yields.
-Since the AGB term is subtracted, a negative AGB Z-dependence will correspond to a positive CC Z-dependence.
-And as we reduce outflows, the AGB factor increases, steepening the required slope of the carbon yields.
-So, while the AGB yields may agree with eachother, the uncertainties in the oxygen CC yields and outflows leads to a substantial uncertainty in the AGB fraction.
-
-\begin{figure}
-    \centering
-    \includegraphics[scale=0.3]{analytic_y-4.pdf}
-    \caption{Our reverse fitting method to determine total CCSNe contribution}
-\end{figure}
-
-% y_c^cc = (0.0148 +- 0.00016) Z^{0.154 +- 0.0053}
-\begin{equation}
-    y_C = (0.004 \pm 0.00002) + (0.008 \pm 0.0001) \text{[M/H]} 
-\end{equation}
-
-\subsection{Uncertainties}
-
-We only perform this analysis on the C11/15 yields because the range of metallicities of the data (about [M/H] = -0.4, 0.4) only represents about 2 AGB models, relying heavily on our choice of extrapolation.
-C11/C15 have a finer model grid, allowing us to have 5 theoretical predicted points within this metallicity range, allowing us to be more certain of our conclusion.
-
-We do note that this analysis fails to take into account selection effects and biases in APOGEE, and a more robust determination of the carbon yield.
-
-This formulation is degenerate in $\varpi$ until we estimate a better AGB fraction.
-As the seperation between the low and high alpha sequences can be used to estimate the delayed time contribution to carbon, using the model to estimate this value relies heavaly on the details of the SFH in addition to the
-We do give an estimate of the CCSNe yields, however this is dependent on our choice of $\eta$.
-Other choices of $\eta$ vary the value significantly in both magnitude and slope (as AGB contributions increase, we need less CCSNe carbon, however the CCSNe carbon must have a higher metallicity dependence to replicate the V21 data).
-
-\section{Modeling extragalactic carbon trends}
-Can we use our yield estimations and apply them to extragalactic sources successfully?
-
-Explain Berg+19,
-
-Bursty SFH may not be needed to explain scatter as the C/O slope + differet evolutionary timescales is capable alone of reproducing this scatter.
-
-While the extragalactic trend appears to be more steeply sloped than our models, this is because of ***e.g. mass-dependent outflow rates/differening SFH between galaxies.
 
@@
 
-The last numbered section should briefly summarise what has been done, and describe
-the final conclusions which the authors draw from their work.
+In this work, we investigate the role of C yields on the predictions of multi-zone \gce{} models.
+\citet{james+23} performed a similar analysis focusing on N.
+They found that matching the observed relationship between N and O abundances%
+\footnote{e.g.
+\citet{HEK00,PVT10,berg+12, berg+20, skillman+20, izotov+12, james2+15, dopita+16}.} requires relative N and O yields from simple stellar populations with a roughly linear dependence on metallicity (i.e.
+$y_{\rm N}/y_{\rm O} \propto Z$).
+Here, we perform a similar analysis on C.
 
+Though \cc\ C yields are poorly understood, we adopt an equilibrium approximation and determine a functional form that approximately matches trends in \apogee{} subgiant and is consistent with high-mass nucleosynthesis models.
+Variations of the metallicity dependence of this \cc\ yield affect trends in \caah~but do not affect trends in \caafe\ (when taking a slice in [Mg/H]).
+As all theoretical \agb\ C yields decrease with metallicity, increasing the \agb\ fraction causes the \caah\ trend to flatten.
+However, the \caafe\ trend is sensitive to the \agb\ fraction.
+From this, we estimate that \agb\ stars contribute \about{20\%} of total C abundance at solar metallicity.
+The remaining \about{80\%} of C comes from high-mass stars with a metallicity dependent yield of $\Ycc/\Yoc=1.51 + 0.54 (Z/Z_\odot)$.
+This metallicity dependence is roughly consistent with rotating stellar yields.
+
+We additionally explore variations of the assumed \sfh{} and outflow mass-loading factor $\eta$.
+We find that alternate \sfh{}s can slightly affect \caafe, but \caah~is mostly unaffected.
+Decreasing both outflows and yields by the same factor leaves the \caah~and \caafe~trends unaffected.
+These constraints on the relative yields of C, O, and Mg are robust against variations in $\eta$.
+
+Finally, we compare our model against gas-phase measurements and metal-poor stars.
+While our model was built on data near solar metallicity, observations of very low metallicity, high redshift damped Lyman-$\alpha$ systems indicate higher C/O ratios \citep{cooke+17}, consistent with yields from population III stars \citep[e.g.][]{hirschi07}.
+Population III stars, \cc\, and \agb stars altogether explain the observed evolutionary history of C.
+
+These C yield constraints provide a useful benchmark for stellar evolution models.
+C yields are sensitive to poorly understood processes, including mass-loss prescriptions, explodability, nuclear cross sections, convection, and stellar structure.
+Future spectroscopic surveys combined with Gaia kinematics \citep{gaia} will continue to enhance our understanding of chemical evolution.
+Both the Sloan Digital Sky Survey V's Milky Way Mapper program ({\sc SDSS-V/MWM}) \citep{sdssv} and the Dark Energy Spectroscopic Instrument ({\sc DESI}) Milky Way survey \citep{desi, desi:mw} will each measure spectra of upwards 6,000,000 Milky Way stars.
+These larger samples will enable similar work to tighten constraints on stellar models and our understanding of galaxy structure and evolution.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%Log in with your OSC username and password.
+
+%%%%%
 \section*{Acknowledgements}
 
-The Acknowledgements section is not numbered. Here you can thank helpful
+ Here you can thank helpful
 colleagues, acknowledge funding agencies, telescopes and facilities used etc.
@@
 
-Numpy, pandas, scipy, VICE, matplotlib
-\cite{numpy, matplotlib}
-
-\cite{OhioSupercomputerCenter1987}
+Software that has contributed to this work included  
+\VICE~\citep{JW20, james+21},
+\texttt{matplotlib} \citep{matplotlib},
+\texttt{scipy} \citep{scipy},
+\texttt{IPython} \citep{ipy},
+\texttt{pandas} \citep{pandas},
+\texttt{numpy} \citep{numpy},
+\texttt{astropy} \citep{astropy:2013, astropy:2018, astropy:2022},
+and 
+\texttt{seaborn} \citep{seaborn}
+.
+Additionally, we thank \citet{OhioSupercomputerCenter1987} for the use of its facilities for the simulations.
 
@@
 %%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%
-
-% The best way to enter references is to use BibTeX:
-
 \bibliographystyle{mnras}
-\bibliography{main} % if your bibtex file is called example.bib
-
-% Alternatively you could enter them by hand, like this:
-% This method is tedious and prone to error if you have lots of references
-%\begin{thebibliography}{99}
-%\bibitem[\protect\citeauthoryear{Author}{2012}]{Author2012}
-%Author A.~N., 2013, Journal of Improbable Astronomy, 1, 1
-%\bibitem[\protect\citeauthoryear{Others}{2013}]{Others2013}
-%Others S., 2012, Journal of Interesting Stuff, 17, 198
-%\end{thebibliography}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\bibliography{main}
 
@@
 
-\section{Validating the APOGEE Subgiant Sample}\label{sec:jack}
-Our APOGEE subgiant sample excludes stars marked with the following flags:
+\section{The Subgiant Sample}\label{sec:jack}
+
+As the primary observational constraint, we use the criteria outlined in \citetjack~to create a sample of subgiant from \apogee{} DR17 \citep{apogee17}.
+apogee is part of the Sloan Digital Sky Survey and measures high-resolution spectra of thousands of stars \cite{sdss17}.
+Chemical abundances are determined from the \apogee\ Stellar Parameter and Chemical Abundance Pipeline ({\sc aspcap}) \citep{aspcap}.
+
+Photospheric C and N abundances in subgiant are reflective of their birth abundances \citep{gilroy89, korn+07, lind+08, souto+18, souto19} As FDU, which affects C and N abundances, only occurs during the ascent onto the RGB, subgiant stars are unaffected by this enrichment.
+
+An alternate approach for this analysis would be to estimate the birth abundances of RGB stars by correcting surface abundance effects from FDU as in \cite{vincenzo+21}.
+Subgiants are the more attractive option since these observations do not rely on model-dependent corrections.
+However, RGB stars are more luminous, potentially allowing better coverage of the Galactic disk.
+
+We choose to use \citetjack\ sample as this does not rely on additional layers of modeling, providing a more direct constraint to our model and limiting our systematic uncertainties.
+
+Fig.~\ref{fig:subgiant_selection} shows a plot of all \apogee\ stars and the \citetjack polygon selection criteria. 
+ \citetjack~select a region of stars based on surface gravity $\log g$, and effective surface temperature, $T_\text{eff}$.
+ \begin{equation}
+    \begin{cases} \label{eq:subgiant_selection}
+        \log \text{g} \geq 3.5 \\
+        \log \text{g} \leq 0.004\,T_{\rm eff} - 15.7 \\
+        \log \text{g} \leq 0.000706\,T_{\rm eff} + 0.36 \\
+        \log \text{g} \leq -0.0015\,T_{\rm eff} + 12.05 \\
+        \log \text{g} \geq 0.0012\,T_{\rm eff} - 2.8. \\
+    \end{cases}
+\end{equation}
+Additionally, we included stars in \apogee{} marked by the following flags.
 \begin{itemize}
-\item \texttt{ancillary young embedded cluster}
-\item \texttt{ancillary emission line star}
-\item \texttt{MIR-deected candidate cluster member}
-\item \texttt{selected as part of the EB program}
-\item \texttt{selected as part of the young cluster study (in-SYNC)}
-\item \texttt{W3/4/5 star forming complex}
+\item \verb|APOGEE_MIRCLUSTER_STAR|
+\item \verb|APOGEE_EMISSION_STAR|
+\item \verb|APOGEE_EMBEDDEDCLUSTER_STAR|
+\item \verb|young cluster (IN-SYNC)|
+\item \verb|APOGEE2_W345|
+\item \verb|EB planet|
+\end{itemize}
+This cut isolates a clean sample of \about{12,000} subgiants.
+We furthermore isolate the low- and high-$\alpha$ sequences with the cut
+\begin{equation}\label{eq:high_alpha}
+\begin{cases}
+\text{[Mg/Fe]} >0.12-0.13\,\text{[Fe/H]}, & \text{[Fe/H]}<0\\
+\text{[Mg/Fe]} >0.12, & \text{[Fe/H]}>0. \\
+\end{cases}
+\end{equation}
+The low-$\alpha$ sequence is better reproduced by this model, so we use this cut of the subgiants to compare the models against except for comparing \caafe.
+
+\begin{figure}
+    \centering
+    \includegraphics{logg_jack.pdf}
+    \caption[Subgiant Selection]{
+        A Kiel diagram of \apogee{} stars.
+Following \citetjack, we select subgiants in the orange polygon (see Equation \ref{eq:subgiant_selection}).
+These stars have not yet experienced first dredge-up, so their photospheric C and N abundances should reflect their birth mixture.
+    }
+    \label{fig:subgiant_selection}
+\end{figure}
+
+\newpage
+\section{Low-Mass Stellar Evolution}\label{sec:stel_evo}
+For reference, we include here a brief summary of the physics behind carbon production in lowmass.
+lowmass ($\lesssim 8 \Mo$, like our sun), are born when they are fusing H into He.
+Typically, the dominant process is through the aptly named \textit{pp chain}, which takes four protons $\proton$ and releases a He nucleus $\alpha$, positrons $\beta^{+}$, photons $\gamma$, and electron neutrinos $\nu_{\rm e}$.
+\begin{subequations}
+    \begin{align}
+        \proton + \proton &\longrightarrow \isotope[2][1]{H} + \beta^+ + \nu_{\rm e} \\
+        \proton + \isotope[2][1]{H} &\longrightarrow \isotope[3][2]{He} + \gamma\\
+        \proton + \isotope[3][2]{He} &\longrightarrow \isotope[4][2]{He} + \beta^+ + \nu_{\rm e}.
+    \end{align}
+\end{subequations}
+However, when the core temperature becomes high enough, the cno begins to activate.
+Starting with \isotope[12]{C}, the cno is a series of proton captures that result in the creation of a new He nucleus.
+\begin{subequations}\label{eq:cno_cycle}
+\begin{align}
+    \proton + \isotope[12]{C} &\longrightarrow \isotope[13]{N} + \gamma \\
+    \isotope[13]{N} &\longrightarrow  \isotope[13]{C} + \beta^+ + \nu_{\rm e}  \\
+    \proton + \isotope[13]{C}  &\longrightarrow \isotope[14]{N} + \gamma\\
+    \proton + \isotope[14]{N}  &\longrightarrow \isotope[15]{O} + \gamma \label{eq:n14}\\
+    \isotope[15]{O} &\longrightarrow  \isotope[15]{N} + \beta^{+} + \nu_{\rm e} \\
+    \proton + \isotope[15]{N} &\longrightarrow \isotope[12]{C} + \alpha
+\end{align}
+\end{subequations}
+(There are other less important minor branches of the cno cycle
+ \citep{solar-fusion}.)
+The cno is more intense at high metallicities, as the abundance of \isotope[12]{C} is higher.
+Since the slowest reaction in the cno is the \isotope[14]{N} proton capture (Eq.~\ref{eq:n14}; also see \citealt{solar-fusion}), the net effect is to convert \isotope[12]{C} into \isotope[14]{N}.
+
+After the end of the main sequence (core H burning), a star begins to ascend the RGB.
+The star first becomes a subgiant, slightly more luminous and redder than the main sequence.
+Then, FDU occurs when the contracting core drives convection currents through, bringing processed material from the core to the surface.
+Because of the cno, the surface abundances of C will be lowered and N enhanced.
+
+Stars with masses $\gtrsim 0.6\,\Mo$ build up a large He core during the RGB.
+Eventually, conditions are dense and hot enough for He to being to fuse, and the star now enters the He-burning phase.
+(Second dredge-up occurs during this transition.) As the next (accessible) stable isotope after He is C, the primary process to fuse He is through the triple-$\alpha$ process, where three He nuclei are combined to form \isotope[12]{C}.
+\begin{subequations} \label{eq:triple_alpha}
+\begin{align}
+    \alpha + \alpha &\longrightarrow \isotope[8][4]{Be} \\ 
+    \alpha + \isotope[8][4]{Be} &\longrightarrow \isotope[12][6]{C} + 2\gamma \\ 
+\end{align}
+Additionally, some \isotope[12][6]{C} may furthermore fuse into O through $\alpha + \isotope[12][6]{C} \longrightarrow \isotope[16][8]{O} + \gamma$.
+
+When the star's core becomes full of C and O, the star finally enters the asymptotic giant branch phase (\agb).
+(Only the most massive low-mass stars burn further than O, creating some Mg, but these stars are a small fraction of low-mass stars.) An \agb\ star has a more complex structure, with an inert core, a He-burning shell, and an outer H-burning shell.
+The double shell structure causes instabilities towards the end of the \agb\ phase.
+In this thermally pulsating phase, each pulse begins with a He-flash (where the He-shell becomes much more luminous).
+This flash causes the star to expand, driving convective currents that dredge up material from the CO core (third dredge up), and fusion stops temporarily.
+The star settles again and stays stable for several Myrs until the cycle repeats.
+During each He-flash, some material from the stellar surface is lost.
+This mass-loss is the source of \agb\ enrichment.
+Finally, the star losses enough mass such that the thermal pulses stop.
+The star becomes a white dwarf, left to cool for eternity.
+
+\end{subequations}
+
+\section{Other Observational and Theoretical Challenges}
+
+Oxygen Magnesium problem.
+As we focus on constraining relative yields, we neglect O and Mg yield variations in the main text (excluding the uniform scaling of yields and massloading in Section~\ref{sec:outflows}).
+There is substantial variation in predicted Mg yields.
+Most models predict relatively flat trends metallicity (even with rotation as in \citealt{LC18}).
+However, the variation is significant and our adopted $\Yoc$ yield is much higher than most models.
+This is a known problem (see \citealt{emily+21}).
+cc models underpredict $[{\rm Mg}/{\rm O}]$, and the reason why is unknown.
+Our results are independent of the choice of \cc\ element as we assume $[{\rm Mg}/{\rm O}]=0$.
+
+Carbonn abundance measurments. E.g.
+
+\section{Low-Mass Stellar Yield Models} \label{sec:oob_models}
+
+\hypertarget{C11}{\texttt{C11}}. Yields from \citet{cristallo+11,cristallo+15}. 
+\begin{itemize}
+    \item 
+        masses 1.3, 1.5, 2.0, 2.5, 3.0, 4.0, 5.0, and 6.0 M$_{\odot}$ 
+    \item metallicities $Z = $ 0.0001, 0.0003, 0.001, 0.002, 0.003, 0.006, 0.008, 0.01, 0.014, 0.02. 
 \end{itemize}
 
-To select stars only in the subgiant branch, we select stars in a polygon in $\log g$-$T_\text{eff}$ space described by the following cuts:
-\begin{equation}
-\begin{cases}
-\log g \geq 3.5 \\
-\log g \leq 0.004\ T_\text{eff} - 15.7 \\
-\log g \leq 0.00070588\ T_\text{eff} + 0.358836 \\
-\log g \leq -0.0015\ T_\text{eff} + 12.05 \\
-\log g \geq 0.0012\ T_\text{eff} - 2.8 \\
-\end{cases}
-\end{equation}
+\hypertarget{K10}{\texttt{K10}} ,
+     \kx{} from \citet{karakas10}, and 
+1.0, 1.25, 1.5, 1.75, 1.9, 2.25, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0 
+,  0.0001, 0.004, 0.008, 0.02.
 
-Instead of excluding stars which have experienced FDU and thus modified carbon abundances as JACK's subgiant sample does, another approach to predict the birth abundances of carbon and nitrogen in stars is to model the predicted abundance effects of dredge up and then correct the measured abundances, as is done in V21.
+\hypertarget{V13}{\texttt{V13}} 
+     \vxiii{} from \cite{ventura+13,ventura+14,ventura+18,vincenzo+21}, 
+, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 6.0, 6.5, 7.0
+, 0.0003, 0.001, 0.002, 0.004, 0.008, 0.014, 0.04
 
-In the first panel, both V13 and the subgiant sample predict similar trends in [C/Mg]-[Mg/H] but there appears to be a systematic offset of about 0.2dex.
-Reproducing the trend is promising as V21's mixing corrections were metallicity-dependent so the uncorrected sample of APOGEE giants does not match the subgiant trend.
+\hypertarget{K16}{\texttt{K16}} 
+ , 1.0, 1.25, 1.5, 1.75, 2.25, 2.5, 2.75, 3.0, 3.25, 3.5, 3.75, 4.0, 4.5, 5.0, 5.5, 6.0, 7.0
+ , 0.0003, 0.001, 0.002, 0.004, 0.008, 0.014, 0.04 
+    \kxvi{} from \cite{KL16,karakas+18}
 
-The systematic offset could be explained by overpredicting the effects of FDU or other *** in V21's stellar evolution models??? or other subgiant physics???
+\section{Symbols}
 
-In the second panel, agreement appears to be better. Both the MDF and the slope are nearly identical,
-There is a slight deviation in slope between the models, and this could again be a systematic such as underestimation of **8some stellar effect**** at higher metallicities.
+\setlength{\tabcolsep}{0pt}
+\begin{tabular}{p{0.2\columnwidth} p{0.6\columnwidth}}
+    $[A/B]$ & 
+    The abundance ratio between elements $A$ and $B$. $[A/B] =
+    \log_{10}\left(A/B\right) - \log_{10}\left(A_{\sun}/B_{\sun}\right)$, i.e.
+    $[A/B]$ is the logarithm of the ratio between A and B, scales such that
+    $[A/B]=0$ for the sun. Solar abundances are as measured in
+    \citet{asplund+09}. \\
 
-We compare both of **** in Figure \ref{fig:fiorenzo_jack}.
+$\alpha_{\rm AGB}$ & 
+The multiplicative increase in \agb\ C production. See Eq.~\ref{eq:alpha}. \\
 
-\begin{figure*}
-    \centering
-    \includegraphics[scale=0.5]{fiorenzo_vs_jack_c-1.pdf}
-    \includegraphics[scale=0.5]{fiorenzo_vs_jack_n-1.pdf}
-    \caption{A comparison of estimated stellar birth abundance trends from the subgiant sample and
-        \citet{fiorenzo+21}
-    }
-    \label{fig:fiorenzo_jack}
-\end{figure*}
+$\alpha_{\rm CC}$ &
+The multiplicative increase in \cc\ C production. See Eq.~\ref{eq:alpha}. \\
 
-\section{Effects of Alternate AGB Models}\label{sec:alt_agb}
+$\eta$ & 
+The mass outflow loading factor. $\eta$ is the ratio between ejected gas from the galaxy and star formation, i.e. $\eta = \dot{M}_{\rm outflow}/\dot{M}_\star$. \\
 
-\begin{table}
-	\centering
-	\caption{For each AGB yield set, our calculation of the effective SFH- and IMF-weighted carbon AGB yield, along with the multiplicative factor to reach an AGB contribution of 20.}
-	\label{tab:alpha_agb}
-	\begin{tabular}{lcr} % four columns, alignment for each
-		\hline
-		Study & $y_{\rm C, 0}^{\rm agb}$ & $\alpha_{\rm agb, 20}$\\
-		\hline
-		C11 & 0.000347 & 2.9\\
-		K10 & 0.000585 & 1.7\\
-		V13 & 0.000060 & 16.5\\
-		K16 & 0.000421 & 2.4\\
-		\hline
+$\zeta$ & 
+{The high-mass star carbon yield metallicity dependence. See Eq.~\ref{eq:zeta}}. \\
+
+$\ensuremath{\dot{\Sigma}}$ & 
+The surface mass density of star formation. \\
+
+$M$ &
+The mass of a star, in units of \Mo \\
+
+$\dot{M}_\star$ & 
+The rate of star formation (mass of new stars per time interval). \\
+
+$\dot{M}_{\rm X}$ &
+The rate of change of the mass of element $X$. \\
+
+$f_{\rm AGB}$ &
+The fractional contribution of \agb\ stars to the total \imf-averaged carbon yield at solar metallicity. See Eq.~\ref{eq:f_agb} \\
+
+$R$ &
+The galactocentric radius (distance from the galactic center) in kpc. \\
+
+$\tilde{y}_{\rm C}^{\rm AGB}$ &
+The per-star yield of C from lowmass of a given mass. In other words, the amount of new C an \agb\ star ejects divided by the initial mass of the star. \\
+
+$y_{\rm C}^{\rm AGB}$ &
+The \imf-averaged yield of C from low-mass stars. \\
+
+$y_{\rm C}^{\rm CC}$ &
+The \imf-averaged yield of C from high-mass stars. \\
+
+$y_{\rm Mg}^{\rm CC}$ &
+The \imf-averaged yield of Mg. \\
+
+$Z_\odot$ &
+The metallicity for the sun. $Z_\odot=0.014$.  \\
+
+$Z$ &
+The metallicity fraction, i.e. the mass fraction of all elements which are not H or He.  \\
+
+$Z_X$ &
+The mass fraction of element $X$. \\
+
 \end{tabular}
-\end{table}
 
-While we focus the main discussion of the paper on the C11 model, other AGB models can have notable effects on abundance trends at ***
+\setlength{\tabcolsep}{6pt}
+\renewcommand*{\arraystretch}{1}
 
-Because the predictions of the AGB yield models we consider are dwarfed by the required CCSNe carbon production to match observations (see Figure ***), we briefly explore here the effects of variations in AGB models affect abundance trend predictions when these models are amplified to match observational [C/MG]-[Mg/Fe] trends.
-
-While most models are well represented by our AGB-fraction formalism, V13 presents a challenge as the predicted solar yield is much lower than the lower metallicity predictions, requiring the solar value to be a certain fraction forces us to amplify the yields by an unreasonable about (of order 10-30times) to reach the same $f_{\rm AGB}$ as other models.
-Thus, we instead calculate $f_{\rm AGB}$ at a metallicity of ...
-for this model.
-
-V13 is also interesting as at high metallicity, the yields quickly become strongly negative.
-This causes a reversal of the [C/Mg]-[Mg/Fe] trend at high [Mg/H] slices (figure ...).
-As our set of observations do not appear to reverse, this indicates that carbon yields likely stay positive even at slightly super-solar, so models like V13 are a poor match to observations.
-Plot of age metallicity relationship?
-
-\begin{figure*}
-\includegraphics[scale=0.45]{agb_adj-2.pdf}
-\includegraphics[scale=0.45]{abg_adj_z-1.pdf}
-
-\caption{Same as \ref{fig:stars_abundances} but comparing our fiducial model to our recommended z-dependent $y_\text{C}^\text{CC}$ model.
-A plot of the stars of our favored CCSNe model colored by radius.
-The contours represent the density of V+21 data.
-The model is given Gaussian scatter equivalent to the mean error in the abundances reported by APOGEE.
-}
-\end{figure*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% Don't change these lines
 \bsp	% typesetting comment
@@
 \end{document}
-
-% End of mnras_template.tex

### 2023-07-02 surp/analysis/apogee_analysis.py

@@ -115,6 +115,7 @@ def find_subgiants():
     # add high/low alpha column
     df["high_alpha"] = df["MG_FE"] > mg_fe_cutoff(df["FE_H"])
     
+    # df.drop(columns=["X_M_SPEC", "X_H_SPEC"], inplace=True)
     return df
 
 
@@ -132,7 +133,7 @@ def read_subgiants():
         subgiants = find_subgiants()
         subgiants.to_csv(abs_path)
     else:
-        subgiants = pd.read_csv(abs_path)
+        subgiants = pd.read_csv(abs_path, index_col=0, dtype={"MEMBER": str})
 
     return subgiants
 

### 2023-07-03 carbon_paper/tex/main.tex
removed uneccessary apendicies

@@
 
+% citations
+\defcitealias{james+21}{J21}
+\newcommand{\JJ}{\citetalias{james+21}}
+\newcommand{\VICE}{\textsc{vice}}
+\newcommand{\citetjack}{Roberts et al.~(2023, in prep.)}
+\newcommand{\citepjack}{(Roberts et al.~2023, in prep.)}
+\newcommand{\citealtjack}{Robert et al.~2023, in prep.}
+\newcommand{\cxi}{\texttt{\hyperlink{C11}{C11}}}
+\newcommand{\kx}{\texttt{\hyperlink{K10}{K10}}}
+\newcommand{\kxvi}{\texttt{\hyperlink{K16}{K16}}}
+\newcommand{\vxiii}{\texttt{\hyperlink{V13}{V13}}}
+
+% Acronyms
 \newcommand{\cc}{CCSNe}
@@
 
+% internal abbreviations
 \newcommand{\lims}{lower-intermediate mass stars}
 \newcommand{\hms}{high-mass stars}
-
-\defcitealias{james+21}{J21}
-\newcommand{\citetjack}{Roberts et al.~(2023, in prep.)}
-\newcommand{\citepjack}{(Roberts et al.~2023, in prep.)}
-\newcommand{\citealtjack}{Robert et al.~2023, in prep.}
-
-\newcommand{\cxi}{\texttt{\hyperlink{C11}{C11}}}
-\newcommand{\kx}{\texttt{\hyperlink{K10}{K10}}}
-\newcommand{\kxvi}{\texttt{\hyperlink{K16}{K16}}}
-\newcommand{\vxiii}{\texttt{\hyperlink{V13}{V13}}}
-
-\newcommand{\JJ}{\citetalias{james+21}}
-\newcommand{\VICE}{\texttt{VICE}}
 \newcommand{\caah}{[C/Mg]-[Mg/H]}
@@
 
-\newcommand{\alp}{$\alpha$}
+% other
+\makeatletter
+\newcommand{\C}[1][\@nil]{
+    \def\tmp{#1}%
+    \ifx\tmp\@nnil%
+        \ensuremath{\rm C}%
+    \else%
+        \ifmmode ^{#1}{\rm C}%
+        \else $^{#1}$C%
+        \fi%
+\fi }
+\makeatother
+
+\newcommand{\proton}{\isotope[1][1]{p}}
+\newcommand{\Yct}{\ensuremath{y_{\rm C}}}
 \newcommand{\Ycc}{\ensuremath{y_{\rm C}^{\rm cc}}}
@@
 \newcommand{\Ycagb}{\ensuremath{y_{\rm C}^{\rm agb}}}
-\newcommand{\Z}{Z}
+
+    \newcommand{\y}{\ensuremath{\rotatebox[origin=B,y=0.5ex]{180}{y}}}
+\newcommand{\Mo}{%
+    \ifmmode {\rm M}_{\sun}%
+    \else M$_{\sun}$
+    \fi}
 \newcommand{\Zo}{%
@@
     \fi}
-\newcommand{\Mo}{%
-    \ifmmode {\rm M}_{\sun}%
-    \else M$_{\sun}$
-    \fi}
+
 \newcommand{\about}[1]{${\sim} #1$}
-
-\newcommand{\proton}{\isotope[1][1]{p}}
-\newcommand{\zoo}{\ensuremath{Z/Z_{\sun }}}
-\newcommand{\Yct}{\ensuremath{y_{\rm C}}}
 
@@
 
+\citet{james+23} compare their model against the \cite{vincenzo+21} sample of \apogee{} \citep{apogee17} RGB stars.
+\citet{vincenzo+21} use \textsc{mesa} stellar evolution models \citep{mesa} to correct for the effects of First Dredge Up (FDU).
+We instead use the \citetjack~sample of \apogee{} subgiants.
+Subgiant stars have not undergone FDU but have well-mixed atmospheres, so their atmospheric C and N abundances are still reflective of their birth abundances and do not need mixing corrections.
+We only compare the models to the low-$\alpha$ sequence unless otherwise specified.
+The selection criteria and differences between the samples are described in more detail in Appendix \ref{sec:jack}.
+
 \footnotetext{First dredge up (FDU) is when material from CNO processed core is mixed with the (convective) stellar envelop during the ascent onto the RGB.
@@
 To quantify yields, we define the stellar yield to be the fraction of a stars initial mass which is newly synthesized and released as a given element. 
-For an element $X$ and star with mass $M$, the net-fractional stellar yield $\tilde{y}$ is 
+For an element $X$ and star with mass $M$, the net-fractional stellar yield $\y$ is 
 \begin{equation}
-\tilde{y}_{X} = \frac{M_{\rm ejected}}{M_{\rm birth}} (Z_{f, X} -  Z_{0, X})
-\end{equation}
-where $M_{\rm ejected}$ and $M_{\rm birth}$  are the total ejected mass and the birth mass of the star, and $Z_{f, X}$ and $Z_{0, X}$ are the initial birth abundance and final abundance of the ejected envelop respectably.
-For example, if a 1\,\Mo\ star has $\tilde{y}_{\rm C} = 10^{-3}$, then the star will add $10^{-3}\,\Mo$ of new C to the interstellar medium.
+\y_{X} = \frac{M_{\rm ejected}}{M_{\rm birth}} \Delta Z_X
+\end{equation}
+where $M_{\rm ejected}$ and $M_{\rm birth}$  are the total ejected mass and the birth mass of the star, and $\Delta Z_X$ is the change in mass fraction of abundance X from birth to ejected.
+For example, if a 1\,\Mo\ star has $\y_{\C} = 10^{-3}$, then the star will add $10^{-3}\,\Mo$ of new C to the interstellar medium.
 Although per-star yields are necessary to compute \agb{} star enrichment rates in \gce{}  models, \imf-averaged yields are useful in interpreting their predictions. 
-For a yield $y$ from a star of mass M and initial metallicity $Z$, the \imf-averaged yield is given by
+Given the fractional yield $\y(M, Z)$ as a function of initial stellar mass $M$ and metallicity $Z$, the \imf-averaged yield is given by 
 \begin{equation} \label{eq:imf-yield}
     y_{\rm X}(Z,t) = 
+    \frac{
     \int_{M_{\rm min}(t)}^{M_{\rm max}} 
-    \tilde{y}_{\rm X}(M, Z)
-    \frac{dN}{dM}  \ dM
-\end{equation}
-where ${dN}/{dM}$ is the normalized \imf, $M_{\rm max}=100\,\Mo$ is the maximum stellar mass, and $M_{\rm min}(t)$ is the mass of stars with lifetime $t$.\footnotemark{}
+    \y_{\rm X}(M, Z)
+    \frac{dN}{dM}\ M\ dM
+}
+{
+    \int \frac{dN}{dM}\ M\ dM
+}
+\end{equation}
+where ${dN}/{dM}$ is the \imf, $M_{\rm max}=100\,\Mo$ is the maximum stellar mass, and $M_{\rm min}(t)$ is the mass of stars with lifetime $t$.\footnotemark{}
 We use $t=10\,$Gyr for total yields when $t$ is not used.
@@
 		\hline
-        Element & $\Ycc$ & $\tilde{y}^{\rm AGB}$ & $y^{\rm SNe Ia}$ \\
+        Element & $\Ycc$ & $\y^{\rm AGB}$ & $y^{\rm SNe Ia}$ \\
 		\hline
@@
 at the bottom of the convective envelope when $T\gtrsim 50\,{\rm MK}$.
-Because the $^{14}$N proton capture is the slowest component of the CNO cycle, the CNO cycle converts nearly all \isotope[12]{C} into \isotope[14]{N} \citep{solar-fusion}.
+Because the $^{14}$N proton capture is the slowest component of the CNO cycle, the CNO cycle converts nearly all \C[12] into $^{14}$N \citep{solar-fusion}.
+
+\footnotetext{
+    The CNO cycle is a series of proton-capture reactions with CNO elements resulting in energy generation and the creation of an $\alpha$ particle. $\C[12]({\rm p}, \gamma)
+    ^{13}{\rm N}(\beta^+, \nu_{\rm e})
+    ^{13}{\rm C}({\rm p}, \gamma)\allowbreak
+    ^{14}{\rm N}({\rm p}, \gamma)\allowbreak
+    ^{15}{\rm O}(\beta^+, \nu_{\rm e})\allowbreak
+    ^{15}{\rm N}({\rm p}, \alpha)
+    \C[12]$. 
+There are other less important minor branches of the CNO cycle
+ \citep{solar-fusion}.
+}
 
@@
 In 2?? to 4?? \Mo stars, third dredge up becomes important, enriching the outer layers with C, making these stars the most important producers of C. 
-In massive, high-metallicity \agb\ stars, both hot bottom burning and third dredge up occur; however, third dredge up is much more efficient, resulting in significant \isotope[12]{C} destruction.
-
-\footnotetext{
-    The CNO cycle and the details of AGB evolution are described in appendix \ref{sec:stel_evo}.
-}
+In massive, high-metallicity \agb\ stars, both hot bottom burning and third dredge up occur; however, third dredge up is much more efficient, resulting in significant \C[12] destruction.
 
@@
 \end{itemize}
+In Appendix~\ref{sec:oob_models}, the masses, metallicites, and notable differences between each yield set are briefly described. 
 For our models to match observations, we find that need to uniformly amplify these yield tables. We use \cxi\ table, amplified by a factor of 2.9, as the fiducial \agb\ yield.
@@
 
-Fig.~\ref{fig:agb-ssp}, on the left, shows the total production of C by \agb\ stars in a \ssp{} at an age $t$, i.e. $\tilde{y}_{\rm C}(Z_\odot, t)$. 
+Fig.~\ref{fig:agb-ssp}, on the left, shows the total production of C by \agb\ stars in a \ssp{} at an age $t$, i.e. $\y_{\rm C}(Z_\odot, t)$. 
 As the mass range $2\,\Mo\lesssim M \lesssim 4\,\Mo$ is most important for C production, about half of C production occurs before \about{1}\,Gyr, similar to \ia\ Fe. 
@@
         \caption[]{The net fractional \agb\ C yield  plotted as a function of initial stellar mass $M$ and colour-coded according to metallicity.
-The black dashed line shows $\tilde{y}=0$ for reference.
+The black dashed line shows $\y=0$ for reference.
 Each panel represents yields from one of four \agb\ models: \cxi, \kx{}, \vxiii{}, \kxvi{} (see Section \ref{sec:agb} and  Appendix \ref{sec:oob_models}).
@@
 
-Massive stars form $^{12}$C in their cores through the triple--$\alpha$ process (see Appendix \ref{sec:stel_evo}).
-However, only C ejected through supernovae and stellar winds contributes to the yield.
+Massive stars form $^{12}$C in their cores through the triple--$\alpha$ process. However, only C ejected through supernovae and stellar winds contributes to the yield. 
 While there are many stellar models providing predictions of \cc{} yields, the results of these models are highly uncertain due to the many stellar modeling uncertainties.
@@
 Here, we assume ${\rm [O/Mg]} = 0$, which is not compatible with \cc\ models but is consistent with \apogee{} observations \citep{weinberg+19, weinberg+22}.
+
 Out model predictions of [C/Mg] and [C/H] are identical. There is a slight slope in [O/Mg] with metallicity, so this could add a systematic to our model.
+
+As we focus on constraining relative yields, we neglect O and Mg yield variations in the main text (excluding the uniform scaling of yields and massloading in Section~\ref{sec:outflows}).
+There is substantial variation in predicted Mg yields.
+Most models predict relatively flat trends metallicity (even with rotation as in \citealt{LC18}).
+However, the variation is significant and our adopted $\Yoc$ yield is much higher than most models.
+This is a known problem (see \citealt{emily+21}).
+\cc\ models underpredict $[{\rm Mg}/{\rm O}]$, and the reason why is unknown.
 
@@
 A \ssp\ returns a fraction $r$ of their birth mass to the interstellar medium, due to ejected stellar envelopes.\footnotemark{}
-Given the \imf-averaged yield of Mg $y_{\rm Mg}$, the rate of change in the gas-phase mass of Mg is a simple sum of sources and sinks,
+Here, we will use $\alpha$ as a representative $\alpha$-element, such as O or Mg. 
+Given the \imf-averaged yield $y_\alpha$, the rate of change in the gas-phase mass of $\alpha$ is a simple sum of sources and sinks,
 \begin{equation}
-    \dot{M}_{\rm Mg} =  y_{\rm Mg}\,\dot{M}_\star - \dot{M}_{\rm Mg,remnants} - \dot{M}_{\rm Mg,outflows},
-\end{equation}
-where $y_{\rm Mg} \dot{M}_{\star}$ describes \cc\ enrichment. 
-In terms of the return mass fraction of stars $r$, the mass lost to remnants is $Z_{\rm Mg}\,\dot{M}_\star\,(1-r)$.
-And, the outflows deplete mass at a rate $Z_{\rm Mg} \,\dot{M}_\star\,\eta$.
+    \dot{M}_\alpha =  y_\alpha\,\dot{M}_\star - \dot{M}_{\alpha,\,\text{remnants}} - \dot{M}_{\alpha,\,\text{outflows}}
+\end{equation}
+where $y_\alpha\,\dot{M}_{\star}$ describes \cc\ enrichment. 
+In terms of the return mass fraction of stars $r$, the mass lost to remnants is $Z_\alpha\,\dot{M}_\star\,(1-r)$.
+And, the outflows deplete mass at a rate $Z_\alpha \,\dot{M}_\star\,\eta$.
 (We assume the composition of outflows is the same as the interstellar medium.) Substituting for $\eta$ and $r$,
 \begin{equation}
-    \dot{M}_{\rm Mg}= y_{Mg}\,\dot{M}_\star - (1 + \eta - r)\,Z_{Mg}\,\dot{M}_\star.
-\end{equation}
-Assuming an exponentially declining star formation history $\dot{M}_\star \propto e^{-t/\tau_{\rm sfh}}$, the equilibrium abundance is derived analytically by setting $\dot{Z}_{Mg}=0$.
+    \dot{M}_\alpha= y_\alpha\,\dot{M}_\star - (1 + \eta - r)\,Z_\alpha\,\dot{M}_\star.
+\end{equation}
+Assuming an exponentially declining star formation history $\dot{M}_\star \propto e^{-t/\tau_{\rm sfh}}$, the equilibrium abundance is derived analytically by setting $\dot{Z}_\alpha=0$.
 \begin{equation}\label{eq:z_eq}
-    Z_{\rm Mg}^{\rm eq}(R) = \frac{y_{\rm Mg}}{1 + \eta(R) - r - \tau_\star / \tau_{sfh}},
+    Z_\alpha^{\rm eq}(R) = \frac{y_\alpha}{1 + \eta(R) - r - \tau_\star / \tau_{\rm sfh}},
 \end{equation}
@@
 \end{equation}
-And the equilibrium C/Mg abundance ratio is
+And the equilibrium C/$\alpha$ abundance ratio is
 \begin{equation}\label{eq:z_co}
-    \frac{Z_{\rm C}^{\rm eq}}{Z_{\rm Mg}^{\rm eq}} = \frac{\Ycc + \Ycagb }{\Yoc}.
+    \frac{Z_{\rm C}^{\rm eq}}{Z_\alpha^{\rm eq}} = \frac{\Ycc + \Ycagb }{y_\alpha}.
 \end{equation}
@@
 This argument can also be inverted to infer  yields from abundance ratio trends.
-To the extent that observed C and Mg trends reflect the equilibrium abundances in different Galactic regions, we can infer the \cc\ yield given an assumed \agb\ star yield (or vice versa).
+To the extent that observed C and $\alpha$ trends reflect the equilibrium abundances in different Galactic regions, we can infer the \cc\ yield given an assumed \agb\ star yield (or vice versa).
 Inferring $\Ycc$ from $\Ycagb$,
 \begin{equation}
-    y_\text{C}^\text{CC} =  y_\text{Mg}^\text{CC} \frac{Z_\text{C,~eq}}{Z_\text{Mg,~eq}} - \langle y_c^{agb} \rangle
+    y_\text{C}^\alpha =  y_\alpha^\text{CC} \frac{Z_\text{C,\,eq}}{Z_{\alpha,\,{\rm eq}}} - \Ycagb
 \end{equation}
@@
 \begin{equation}\label{eq:y_c_eq}
-    \frac{\Ycc}{\Yoc} = \frac{Z_{\text{C},~\odot}}{Z_{\text{Mg},~\odot}} 10^{\rm [C/Mg]} - \frac{\Ycagb}{\Yoc}.
+    \frac{\Ycc}{y_\alpha} = \left(\frac{Z_{\text{C}}}{Z_{\alpha}}\right)_\odot 10^{[{\rm C}/\alpha]} - \frac{\Ycagb}{y_\alpha}.
 \end{equation}
@@
     \begin{align}
-        \Yct~\big\vert_{Z=Z_\odot} &= \Ycc + \Ycagb = 0.005 \\
-        \Yct/\Yoc~\big\vert_{Z=Z_\odot} &= 2.7.
+        \Yct(\Zo) &= \Ycc + \Ycagb = 0.005 \\
+        \left(\frac{\Yct}{\Yoc}\right)_{\Zo} &= 2.7.
     \end{align}
@@
     \begin{align}
-        \Ycagb &\rightarrow \alpha_{\rm AGB}\ \Ycagb \\
-        \Ycc &\rightarrow \alpha_{\rm CC}\ \Ycc\\
-        \alpha_{\rm CC} &= \frac{\Yct - \alpha_{\rm AGB}\ \Ycagb}{\Ycc}
+        \Ycagb &\rightarrow \alpha_{\rm agb}\ \Ycagb \\
+        \Ycc &\rightarrow \alpha_{\rm cc}\ \Ycc\\
+        \alpha_{\rm CC} &= \frac{\Yct - \alpha_{\rm agb}\ \Ycagb}{\Ycc}
     \end{align}
 \end{subequations}
-Above, $\alpha_{\rm CC}$ is dependent on the choice of $\alpha_{\rm AGB}$ to keep the total C yield constant.
-
-In Section \ref{sec:f-z-models}, we find that $\alpha_{\rm AGB}\approx 2.9$ for the \cxi{} yield model.
+Above, $\alpha_{\rm cc}$ is dependent on the choice of $\alpha_{\rm agb}$ to keep the total C yield constant.
+
+In Section \ref{sec:f-z-models}, we find that $\alpha_{\rm agb}\approx 2.9$ for the \cxi{} yield model.
 Using this \agb\ yield, we can now use Eq.~\ref{eq:y_c_eq} to find an estimate of $\Ycc$ as a function of metallicity.
@@
 This simple framework is a poor approximation of the Milky Way.
-The Galaxy evolves insideout---where star formation is higher towards the center and in the early universe \citep{bird+13}.
-Additionally, stars can migrate several kpcs over their lifetimes, mixing different chemical environments across the galaxy \citep{bird+12,sellwood+binney02}.
+The Galaxy evolves \textit{inside-out}---where star formation is higher towards the center and in the early universe \citep{bird+13}.
+Additionally, stars can migrate several kpc over their lifetimes, mixing different chemical environments across the galaxy \citep{bird+12,sellwood+binney02}.
 For the rest of this paper, we focus on multi-zone models, which discretize the Galaxy into concentric rings in which stars move between.
-Our models extends the \citet{james+21} (hereafter \JJ) Milky Way model, run with the publicly available Versatile Integrator for Chemical Evolution (\VICE). 
+Our models extends the \citet[hereafter \JJ]{james+21} Milky Way model, run with the publicly available Versatile Integrator for Chemical Evolution (\VICE). 
 This model is described extensively in \JJ~and concisely summarized  in \citet{james+23}. Here, we provide a brief overview of the relevant model components.
 
-In the model, the Galaxy is divided into 200 rings, each 100\,pc wide.
+Our model is as follows.
+The Galaxy is divided into 200 rings, each 100\,pc wide.
 Each ring has a separate stellar population and gas supply.
-Star formation ends beyond a radius $R=15.5\,$kpc.
-We initially assume an insideout \sfh{}, where the star formation surface density $\Sigma_\star$ is given by
+We initially assume an inside-out \sfh{}, where the star formation surface density $\Sigma_\star$ is given by
 \begin{equation}\label{eq:inside_out}
@@
 \JJ~derives $\tau_{\rm sfh}(R)$ through analysis of four integral field spectroscopy surveys in \cite{sanches20}.
-The star formation history is normalized such that the total stellar mass reaches $5.17\times10^{10}\,\Mo$ \citep{LM15} and at each $R$ to match the stellar surface density gradient \citep{BHG16}.
+At each $R$, the star formation history is normalized to match the stellar surface density gradient \citep{BHG16} and the total stellar mass reaches $5.17\times10^{10}\,\Mo$ \citep{LM15}.
+Star formation ends beyond a radius $R=15.5\,$kpc.
 The gas inflow is calculated to maintain our chosen \sfh{} for each radius and time, using an extension of a Kennicutt-Schmidt law \citep{kennicutt98},
@@
 \end{cases}
-\end{equation} UNITS.
+\end{equation} 
+where $\Sigma_{\rm gas}$ is measured in \Mo\,kpc$^{-2}$. 
 The scaling of this relationship varies with time due to the redshift dependence of $\tau_\star$ in molecular gas observed by \citet{tacconi18}. We assume a \citet{kroupa01} \imf.
 
-\JJ\ accounts for radial migration by using the results of the \texttt{h277} hydrodynamical
-simulation \citep{christensen12, zolotov12, loebman12, BZ14}, with simulation parameters described
-in \citet{bird+21}. Each \VICE\ single stellar population (SSP) is matched to an \textit{analog} in
-\texttt{H277}, chosen to form at a similar time and radius $R$. By taking the change in radius
-$\Delta R$ of the analogs, the SSPs move to their final radii with a $\sqrt{\text{time}}$ dependence.
-This relationship between displacement and time arises when migration proceeds as a consequence of the diffusion of angular momentum \citep{frankel18, frankel20}.
+To account for radial migration, \JJ\ used the \texttt{h277} hydrodynamical
+simulation results \citep{christensen12, zolotov12, loebman12, BZ14}. Simulation parameters are described in \citet{bird+21}. 
+Each \VICE\ single stellar population (SSP) is matched to an \textit{analog} in \texttt{H277}, chosen to form at a similar time and radius $R$.
+By taking the change in radius $\Delta R$ of the analogs, the SSPs move to their final radii with a $\sqrt{\text{time}}$ dependence.
+The $\Delta R \propto \sqrt{\rm time}$ dependence arises when migration proceeds as a consequence of the diffusion of angular momentum \citep{frankel18, frankel20}.
 We do not account for radial gas flows.
 Using the results of a hydrodynamical simulation without modification limits the free parameters in the model; however, we am limited to one dynamical history. 
-The impact of the details of a galaxy's dynamical history on its chemical evolution is still unknown.
-
-As the strength of outflows controls the resulting $\alpha$ abundances, \JJ~create a metallicity gradient by defining
+We do explore a normal-distribution random walk migration based on \citet{frankel18}, without noticeable impacts on our results.
+All models shown here use the \texttt{h277}-based migration.
+The full impact of the details of a galaxy's dynamical history on its chemical evolution is still unknown.
+
+As the strength of outflows controls the resulting $\alpha$-element abundances, \JJ~create a metallicity gradient by defining
 \begin{equation}\label{eq:eta_r}
-\eta(R) = \frac{y_{\alpha}^{\rm CC}}{Z_{\alpha, \odot}} 10^{(-0.08\,\text{kpc}^{-1})(R-4\,\text{kpc})+0.3} + r - 1.
+\eta(R) = r - 1 + \frac{y_{\alpha}^{\rm CC}}{Z_{\alpha, \odot}} 10^{(-0.08\,\text{kpc}^{-1})(R-4\,\text{kpc})+0.3}.
 \end{equation}
@@
 
-\citet{james+23} compare their model against the \cite{vincenzo+21} sample of \apogee{} \citep{apogee17} RGB stars.
-\citet{vincenzo+21} use \textsc{mesa} stellar evolution models \citep{mesa} to correct for the effects of First Dredge Up (FDU).
-We instead use the \citetjack~sample of \apogee{} subgiants.
+We use the \citetjack~sample of \apogee{} subgiants.
 Subgiant stars have not undergone FDU but have well-mixed atmospheres, so their atmospheric C and N abundances are still reflective of their birth abundances and do not need mixing corrections.
@@
 
-\subsection{The Evolution of Carbon Abundances in the Galaxy}
+\subsection{Evolution of Carbon Abundances}
 
@@
 
-Here, we consider a \textit{lateburst} model, created by multiplying our fiducial insideout \sfh{} with a Gaussian.
+Here, we consider a \textit{lateburst} model, created by multiplying our fiducial inside-out \sfh{} with a Gaussian.
 \begin{equation}\label{eq:lateburst}
-    \dot{\Sigma}_{\rm lateburst} \propto \dot{\Sigma}_{\rm insideout} \left(1 + A\,e^{-(t-\tau_{\rm burst})^2/2\sigma^2_{\rm burst}} \right)
+    \dot{\Sigma}_{\rm lateburst} \propto \dot{\Sigma}_{\rm inside-out} \left(1 + A\,e^{-(t-\tau_{\rm burst})^2/2\sigma^2_{\rm burst}} \right)
 \end{equation}
@@
 \begin{equation}\label{eq:twoinfall}
-    \dot{\Sigma}_{\rm earlyburst} \propto \dot{\Sigma}_{\rm insideout} + 
+    \dot{\Sigma}_{\rm earlyburst} \propto \dot{\Sigma}_{\rm inside-out} + 
 \begin{cases}
@@
 
-\newpage
-\section{Low-Mass Stellar Evolution}\label{sec:stel_evo}
-For reference, we include here a brief summary of the physics behind carbon production in lowmass.
-lowmass ($\lesssim 8 \Mo$, like our sun), are born when they are fusing H into He.
-Typically, the dominant process is through the aptly named \textit{pp chain}, which takes four protons $\proton$ and releases a He nucleus $\alpha$, positrons $\beta^{+}$, photons $\gamma$, and electron neutrinos $\nu_{\rm e}$.
-\begin{subequations}
-    \begin{align}
-        \proton + \proton &\longrightarrow \isotope[2][1]{H} + \beta^+ + \nu_{\rm e} \\
-        \proton + \isotope[2][1]{H} &\longrightarrow \isotope[3][2]{He} + \gamma\\
-        \proton + \isotope[3][2]{He} &\longrightarrow \isotope[4][2]{He} + \beta^+ + \nu_{\rm e}.
-    \end{align}
-\end{subequations}
-However, when the core temperature becomes high enough, the cno begins to activate.
-Starting with \isotope[12]{C}, the cno is a series of proton captures that result in the creation of a new He nucleus.
-\begin{subequations}\label{eq:cno_cycle}
-\begin{align}
-    \proton + \isotope[12]{C} &\longrightarrow \isotope[13]{N} + \gamma \\
-    \isotope[13]{N} &\longrightarrow  \isotope[13]{C} + \beta^+ + \nu_{\rm e}  \\
-    \proton + \isotope[13]{C}  &\longrightarrow \isotope[14]{N} + \gamma\\
-    \proton + \isotope[14]{N}  &\longrightarrow \isotope[15]{O} + \gamma \label{eq:n14}\\
-    \isotope[15]{O} &\longrightarrow  \isotope[15]{N} + \beta^{+} + \nu_{\rm e} \\
-    \proton + \isotope[15]{N} &\longrightarrow \isotope[12]{C} + \alpha
-\end{align}
-\end{subequations}
-(There are other less important minor branches of the cno cycle
- \citep{solar-fusion}.)
-The cno is more intense at high metallicities, as the abundance of \isotope[12]{C} is higher.
-Since the slowest reaction in the cno is the \isotope[14]{N} proton capture (Eq.~\ref{eq:n14}; also see \citealt{solar-fusion}), the net effect is to convert \isotope[12]{C} into \isotope[14]{N}.
-
-After the end of the main sequence (core H burning), a star begins to ascend the RGB.
-The star first becomes a subgiant, slightly more luminous and redder than the main sequence.
-Then, FDU occurs when the contracting core drives convection currents through, bringing processed material from the core to the surface.
-Because of the cno, the surface abundances of C will be lowered and N enhanced.
-
-Stars with masses $\gtrsim 0.6\,\Mo$ build up a large He core during the RGB.
-Eventually, conditions are dense and hot enough for He to being to fuse, and the star now enters the He-burning phase.
-(Second dredge-up occurs during this transition.) As the next (accessible) stable isotope after He is C, the primary process to fuse He is through the triple-$\alpha$ process, where three He nuclei are combined to form \isotope[12]{C}.
-\begin{subequations} \label{eq:triple_alpha}
-\begin{align}
-    \alpha + \alpha &\longrightarrow \isotope[8][4]{Be} \\ 
-    \alpha + \isotope[8][4]{Be} &\longrightarrow \isotope[12][6]{C} + 2\gamma \\ 
-\end{align}
-Additionally, some \isotope[12][6]{C} may furthermore fuse into O through $\alpha + \isotope[12][6]{C} \longrightarrow \isotope[16][8]{O} + \gamma$.
-
-When the star's core becomes full of C and O, the star finally enters the asymptotic giant branch phase (\agb).
-(Only the most massive low-mass stars burn further than O, creating some Mg, but these stars are a small fraction of low-mass stars.) An \agb\ star has a more complex structure, with an inert core, a He-burning shell, and an outer H-burning shell.
-The double shell structure causes instabilities towards the end of the \agb\ phase.
-In this thermally pulsating phase, each pulse begins with a He-flash (where the He-shell becomes much more luminous).
-This flash causes the star to expand, driving convective currents that dredge up material from the CO core (third dredge up), and fusion stops temporarily.
-The star settles again and stays stable for several Myrs until the cycle repeats.
-During each He-flash, some material from the stellar surface is lost.
-This mass-loss is the source of \agb\ enrichment.
-Finally, the star losses enough mass such that the thermal pulses stop.
-The star becomes a white dwarf, left to cool for eternity.
-
-\end{subequations}
-
-\section{Other Observational and Theoretical Challenges}
-
-Oxygen Magnesium problem.
-As we focus on constraining relative yields, we neglect O and Mg yield variations in the main text (excluding the uniform scaling of yields and massloading in Section~\ref{sec:outflows}).
-There is substantial variation in predicted Mg yields.
-Most models predict relatively flat trends metallicity (even with rotation as in \citealt{LC18}).
-However, the variation is significant and our adopted $\Yoc$ yield is much higher than most models.
-This is a known problem (see \citealt{emily+21}).
-cc models underpredict $[{\rm Mg}/{\rm O}]$, and the reason why is unknown.
-Our results are independent of the choice of \cc\ element as we assume $[{\rm Mg}/{\rm O}]=0$.
-
-Carbonn abundance measurments. E.g.
-
-\section{Low-Mass Stellar Yield Models} \label{sec:oob_models}
-
-\hypertarget{C11}{\texttt{C11}}. Yields from \citet{cristallo+11,cristallo+15}. 
-\begin{itemize}
-    \item 
-        masses 1.3, 1.5, 2.0, 2.5, 3.0, 4.0, 5.0, and 6.0 M$_{\odot}$ 
-    \item metallicities $Z = $ 0.0001, 0.0003, 0.001, 0.002, 0.003, 0.006, 0.008, 0.01, 0.014, 0.02. 
-\end{itemize}
-
-\hypertarget{K10}{\texttt{K10}} ,
-     \kx{} from \citet{karakas10}, and 
-1.0, 1.25, 1.5, 1.75, 1.9, 2.25, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0 
-,  0.0001, 0.004, 0.008, 0.02.
+\section{\agb\ Yield Models} \label{sec:oob_models}
+A brief summary of the four \agb\ models we consider, the masses and metallicites of each yield set, and differences between the models.
+
+\hypertarget{C11}{\texttt{C11}}. 
+Yields from \citet{cristallo+11,cristallo+15}. 
+Models include masses 1.3, 1.5, 2.0, 2.5, 3.0, 4.0, 5.0, and 6.0 \Mo; and 
+metallicities $Z = $ 0.0001, 0.0003, 0.001, 0.002, 0.003, 0.006, 0.008, 0.01, 0.014, 0.02.
+
+\hypertarget{K10}{\texttt{K10}}.
+Yields are published in \citet{karakas10}. 
+Models include masses  1.0, 1.25, 1.5, 1.75, 1.9, 2.25, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0 \Mo;
+and metallicities $Z=$ 0.0001, 0.004, 0.008, 0.02.
 
 \hypertarget{V13}{\texttt{V13}} 
-     \vxiii{} from \cite{ventura+13,ventura+14,ventura+18,vincenzo+21}, 
-, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 6.0, 6.5, 7.0
-, 0.0003, 0.001, 0.002, 0.004, 0.008, 0.014, 0.04
+Yields are published in \citet{ventura+13,ventura+14,ventura+18,vincenzo+21}, 
+Models include masses 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 6.0, 6.5, 7.0 \Mo; 
+and metallicities $Z=$ 0.0003, 0.001, 0.002, 0.004, 0.008, 0.014, 0.04.
+\vxiii is evololved with DHFJKSLDF,
+\vxiii is unusual in that hot bottom burning is much stronger than other models, resulting in much lower stellar yields and negative yields above solar metallicities.
 
 \hypertarget{K16}{\texttt{K16}} 
- , 1.0, 1.25, 1.5, 1.75, 2.25, 2.5, 2.75, 3.0, 3.25, 3.5, 3.75, 4.0, 4.5, 5.0, 5.5, 6.0, 7.0
- , 0.0003, 0.001, 0.002, 0.004, 0.008, 0.014, 0.04 
-    \kxvi{} from \cite{KL16,karakas+18}
-
-\section{Symbols}
-
-\setlength{\tabcolsep}{0pt}
-\begin{tabular}{p{0.2\columnwidth} p{0.6\columnwidth}}
-    $[A/B]$ & 
-    The abundance ratio between elements $A$ and $B$. $[A/B] =
-    \log_{10}\left(A/B\right) - \log_{10}\left(A_{\sun}/B_{\sun}\right)$, i.e.
-    $[A/B]$ is the logarithm of the ratio between A and B, scales such that
-    $[A/B]=0$ for the sun. Solar abundances are as measured in
-    \citet{asplund+09}. \\
-
-$\alpha_{\rm AGB}$ & 
-The multiplicative increase in \agb\ C production. See Eq.~\ref{eq:alpha}. \\
-
-$\alpha_{\rm CC}$ &
-The multiplicative increase in \cc\ C production. See Eq.~\ref{eq:alpha}. \\
-
-$\eta$ & 
-The mass outflow loading factor. $\eta$ is the ratio between ejected gas from the galaxy and star formation, i.e. $\eta = \dot{M}_{\rm outflow}/\dot{M}_\star$. \\
-
-$\zeta$ & 
-{The high-mass star carbon yield metallicity dependence. See Eq.~\ref{eq:zeta}}. \\
-
-$\ensuremath{\dot{\Sigma}}$ & 
-The surface mass density of star formation. \\
-
-$M$ &
-The mass of a star, in units of \Mo \\
-
-$\dot{M}_\star$ & 
-The rate of star formation (mass of new stars per time interval). \\
-
-$\dot{M}_{\rm X}$ &
-The rate of change of the mass of element $X$. \\
-
-$f_{\rm AGB}$ &
-The fractional contribution of \agb\ stars to the total \imf-averaged carbon yield at solar metallicity. See Eq.~\ref{eq:f_agb} \\
-
-$R$ &
-The galactocentric radius (distance from the galactic center) in kpc. \\
-
-$\tilde{y}_{\rm C}^{\rm AGB}$ &
-The per-star yield of C from lowmass of a given mass. In other words, the amount of new C an \agb\ star ejects divided by the initial mass of the star. \\
-
-$y_{\rm C}^{\rm AGB}$ &
-The \imf-averaged yield of C from low-mass stars. \\
-
-$y_{\rm C}^{\rm CC}$ &
-The \imf-averaged yield of C from high-mass stars. \\
-
-$y_{\rm Mg}^{\rm CC}$ &
-The \imf-averaged yield of Mg. \\
-
-$Z_\odot$ &
-The metallicity for the sun. $Z_\odot=0.014$.  \\
-
-$Z$ &
-The metallicity fraction, i.e. the mass fraction of all elements which are not H or He.  \\
-
-$Z_X$ &
-The mass fraction of element $X$. \\
-
-\end{tabular}
-
-\setlength{\tabcolsep}{6pt}
-\renewcommand*{\arraystretch}{1}
+Yields are published in \citet{KL16,karakas+18}
+Models include masses 1.0, 1.25, 1.5, 1.75, 2.25, 2.5, 2.75, 3.0, 3.25, 3.5, 3.75, 4.0, 4.5, 5.0, 5.5, 6.0, 7.0 \Mo; 
+and metallicities $Z=$ 0.0003, 0.001, 0.002, 0.004, 0.008, 0.014, 0.04.
+This yield set was extended up to metallicities of 0.1 in DFJSD; however, we do not consider this range here.
 

### 2023-07-04 carbon_paper/tex/main.tex
new cc yield model

@@
         Fe & 0.0012 & 0 & 0.00214 \\
-        N & 0.00072 & $9\times10^{-4}\,(Z/Z_\odot)\,M$ & 0\\
+        N & 0.00072 & 0.0009$(Z/Z_\odot)\,M$ & 0\\
 		\hline
@@
     providing necessary well-sampled grids in mass and metallicity. We refer to the yields from the following studies as the following.
-\begin{itemize}
+\begin{enumerate}
     \item \cxi: \citet{cristallo+11, cristallo+15}
@@
     \item \kxvi: \citet{KL16, karakas+18}
-\end{itemize}
+\end{enumerate}
 In Appendix~\ref{sec:oob_models}, the masses, metallicites, and notable differences between each yield set are briefly described. 
@@
 
-The right panel of Fig.~\ref{fig:agb-ssp} shows \imf-averaged C yields for each \agb\ model as a function of metallicity $Z$.
+The right panel of Fig.~\ref{fig:agb-ssp} shows \imf-averaged C yields for each \agb\ model as a function of metallicity.
 \vxiii{} differs in that it shows a non-monotonic metallicity dependence. However, this effect is only for models with $\log Z/Z_\odot \lesssim -1$.
@@
     As shown in the right panel of Fig.~\ref{fig:agb-ssp}, with increasing $Z$, C enrichment occurs earlier, and C destruction in low-mass stars leads to a declining C abundance at late times.
+
+We also briefly explore an analytic AGB model, defined as a cubic piecewise in mass and linear in metallicity.
+The piecewise is defined to have a maximum at $m_1$ and minimums at
+the end points $m-\delta m_-$ and $m+\delta m_+$. The function becomes constant
+outside of this range with (optionally) negative yields.
+And the resulting equation (excepting a prefactor)
+
+\begin{equation}
+y(m) = 
+\begin{cases}
+y_0 & m \leq m_0 - \delta m_- \\
+y_1 + (y_0 - y_1) \left(3 (\frac{m_0 - m}{\delta m_-})^2 - 
+2 (\frac{m_0 - m}{\delta m_-})^3\right) 
+    & m_0 - \delta m_- < m \leq m_0 \\
+y_1 + (y_2 - y_1) \left(3 (\frac{m - m_0}{\delta m_+})^2 - 
+2 (\frac{m-m_0}{\delta m_+})^3\right) 
+    & m_0 < m \leq m_0 + \delta m_+ \\
+y_2 & m_0 + \delta m_+ \leq m
+\end{cases}
+\end{equation}
 
@@
 
-Here, we present the time evolution of our fiducial model. In the next Sections, we will discuss the choice of parameters and agreement with observations. 
-The fiducial model has the following qualitative characteristics of its C yields: (a) C is predominantly produced in \cc, (b) \cc\ produce more C at higher metallicities, and (c) \agb\ stars produce less C at higher metallicities.
-The fiducial model uses the \cxi{} \agb\ yield tables (see Section \ref{sec:agb}, and Table \ref{tab:fiducial_mod}), and we amplify the \cxi{} yields by a factor of 2.9 such that \agb\ stars account for 20\% of C at $Z=Z_\odot$.
-
-We show the time evolution tracks of the fiducial model in Fig.~\ref{fig:c_evo} for \caah~ and \caafe.
+Here, we present the time evolution of our fiducial model. In the next sections, we will discuss the choice of parameters and agreement with observations. 
+The fiducial model has the following qualitative characteristics of its C yields.
+\begin{itemize}
+    \item C is predominantly produced in \cc
+    \item \cc\ produce more C at higher metallicities
+    \item \agb\ stars produce less C at higher metallicities 
+\end{itemize} 
+The fiducial model uses the \cxi{} \agb\ yield tables (see Section \ref{sec:agb}, and Table \ref{tab:fiducial_mod}).
+We also amplify the \cxi{} yields by a factor of 2.9 such that \agb\ stars account for 20\% of C at $Z=Z_\odot$.
+
+Fig.~\ref{fig:c_evo} shows time evolution tracks of the fiducial model for \caah~ and \caafe.
 Comparing [C/Mg] against [Mg/Fe] enables us to see the late-time evolution of C more clearly.
@@
     Time evolution of gas-phase C abundances in our fiducial model.
-    {\bf Top:} Evolutionary tracks parameterized by time at fixed Galactocentric radius in the \caah\ and \caafe\ planes. 
-    {\bf Bottom:} Snapshots of the gas-phase \caah\ and \caafe\ trend, parameterized by radius at a fixed time.
+    Each line represents a zone at a different galactic radii.
+The lines are coloured-coded by time.
+The top shows \caah\ and the bottom \caafe.
+We artificially restrict the axis range in each case to better see solar-annulus and present-day evolution.
 }
@@
 \subsection{Low mass stellar yields}\label{sec:f-z-models}
-
-Discussion of negative yields.
-
-Negative AGB yields cause a morphological change in the abundance trends.
-If the yields of low mass stars are negative, then at late times in a SSP, C abundances will decrease.
-This will appear as a downturn in the \caafe{} abundance trends as [Mg/Fe] approaches solar values.
-As we do not observe this in the data, this is either obscured by star formation history (Seee eeee) or observational scatter.
-
-Instead, if lower-intermediate mass AGB stars produce negative carbon yields, it is possible to observe this as a dip in the early parts of the \caafe{} trend...
 
@@
 the \caah\ trend) gives information on the total C yield and the behavior of \cc\ (as the dominating producer of C), the \caafe\ trend exposes the delayed effect of C from \agb\ contribution.
+
+Negative AGB yields cause a morphological change in the abundance trends.
+If the yields of low mass stars are negative, then at late times in a SSP, C abundances will decrease.
+This will appear as a downturn in the \caafe{} abundance trends as [Mg/Fe] approaches solar values.
+As we do not observe this in the data, this is either obscured by star formation history (Seee eeee) or observational scatter.
+Instead, if lower-intermediate mass AGB stars produce negative carbon yields, it is possible to observe this as a dip in the early parts of the \caafe{} trend...
 

### 2023-07-04 surp/yields.py

@@ -7,7 +7,7 @@ from vice.yields import ccsne, sneia, agb
 
 Z_Sun = 0.014
 y_c_0 = 0.005
-y_c_cc_0=0.0028
+y_c_cc_0=0.004
 y_n_flat = 7.2e-4
 
 
@@ -23,7 +23,7 @@ YC_AGB0 = {
 # default settings
 
 
-def set_yields(eta=1, beta=0.001, fe_ia_factor=None,
+def set_yields(eta=1, beta=0.7, fe_ia_factor=None,
                agb_model="cristallo11", oob=False, f_agb=0.2,
                alpha_n=0, 
                mass_factor=1,
@@ -37,7 +37,7 @@ def set_yields(eta=1, beta=0.001, fe_ia_factor=None,
 
     set_n(eta, alpha_n)
     
-    prefactor = y_c_0 * alpha_cc / (y_c_cc_0 + beta)
+    prefactor = y_c_0 * alpha_cc / y_c_cc_0
     vice.yields.ccsne.settings["c"] = LinCC(zeta=beta*prefactor, y0=prefactor*y_c_cc_0)
 
     set_eta(eta)
@@ -72,15 +72,24 @@ class LinAGB:
 
 
 class LinCC:
-    def __init__(self, zeta, y0):
-        self.zeta = zeta
+    def __init__(self, zeta, y0, pop_iii=0.2, Z_iii=10**(-5.5)):
+        # defaults
+        # zeta = 0.70
+        # y0 = 0.004
+        # Z_iii = 10**-5.5
+        # pop_iii = 0.005
         self.y0 = y0
+        self.zeta = zeta
+        self.pop_iii = pop_iii
+        self.Z_iii = Z_iii
 
     def __call__(self, Z):
-        return self.y0 + self.zeta*(Z/Z_Sun) 
+        return self.y0*(1 - self.zeta 
+                        + self.zeta * Z*2/(Z + Z_Sun) 
+                        + self.pop_iii*2/(1 + Z/self.Z_iii))
 
     def __str__(self):
-        return f"{self.y0:0.2e} + {self.zeta:0.2e} Z/Z0"
+        return f"{self.y0:0.2e} + {self.zeta:0.2e} Z/Z0 + {self.pop_iii} 1/(1+Z/Z1)"
 
 
 def set_defaults():

### 2023-07-04 run.py
singlezone model

@@ -33,8 +33,8 @@ def parse_args():
 
     parser.add_argument("-e", "--eta", type=float, default=1,
                         help="the efficiency multiplier of the supernova feedback")
-    parser.add_argument("-b", "--beta", type=float, default=0.001, 
-                        help="the power-law index of the star formation law, default=0.001")
+    parser.add_argument("-z", "--zeta", type=float, default=0.7, 
+                        help="the solar fraction of CCSNe secondary C, default=0.7")
     parser.add_argument("-s", "--spec", default="insideout", 
                         help="""star formation specification. Options include
                         [insideout, constant, lateburst, outerburst, 
@@ -106,7 +106,7 @@ def generate_filename(args):
     if args.eta != 1:
         filename += "_eta" + str(args.eta) 
         
-    filename += "_beta" + str(args.beta)
+    filename += "_zeta" + str(args.zeta)
 
     if args.spec != "insideout":
         filename += "_" + args.spec + str(args.lateburst_amplitude)
@@ -147,7 +147,7 @@ from surp.simulation.multizone_sim import run_model
 yield_kwargs = {{
      'oob': {args.out_of_box_agb},
      'f_agb': {args.agb_fraction},
-     'beta': {args.beta}, 
+     'beta': {args.zeta}, 
      'fe_ia_factor': {args.fe_ia_factor},
      'm_low': {args.m_low},
      'm_mid': {args.m_mid},

### 2023-07-04 carbon_paper/tex/main.tex
singlezone model
new f_agb plot

@@
 % Keep the title short and informative.
-\title[Origin and Galactic Evolution of C]{The Galactic Chemical Evolution of Carbon: Implications for Stellar Nucleosynthesis }
+\title[The Origin and Galactic Evolution of Carbon]{The Galactic Chemical Evolution of Carbon: Implications for Stellar Nucleosynthesis }
 
@@
 Daniel A. Boyea,$^{1}$\thanks{E-mail: boyea.2@osu.edu}
-A. N. Other,$^{2}$
+James W. Johnson,$^{1}$
 Third Author$^{2,3}$
@@
 are shaped by poorly understood processes, including mass loss, nuclear reaction rates, rotational mixing, convection, and explodability \citep{romano+10,KL14,ventura+13, LC18, emily+21}.
-To better understand where carbon comes from and how it evolves, our aim is to use a combination of recent high-resolution observations from APOGEE and multi-zone models to develop estimates of the required C yields to reproduce galactic trends.
-\cite{james+23} examined similar \gce{} models of N (which is closely related to C), finding that trends in N and O are explained by the metallicity dependence of N/O yields.
+To better understand where C comes from and how it evolves, our aim is to use a combination of APOGEE observations and multi-zone models to develop estimates of the required C yields to reproduce galactic trends.
+\cite{james+23} examined similar \gce{} models of N (which is closely related to C), finding that trends in N and O\footnotemark{} are explained by the metallicity dependence of N/O yields.
+\citet{james+23} determine that \agb\ N abundances roughly dependence on metallicity (i.e.
+$y_{\rm N}/y_{\rm O} \propto Z$).
 Here, we extend their models to C, deriving similar constraints on C/Mg yields.
@@
 
+\footnotetext{e.g. \citet{HEK00,PVT10,berg+12, berg+20, skillman+20, izotov+12, james2+15, dopita+16}.} 
 We know, from observations of MW stars and extragalactic gas measurments, that C/O traces a banana shape in O/H (see \ref{fig:gas_phase}). 
@@
 \citet{james+23} compare their model against the \cite{vincenzo+21} sample of \apogee{} \citep{apogee17} RGB stars.
-\citet{vincenzo+21} use \textsc{mesa} stellar evolution models \citep{mesa} to correct for the effects of First Dredge Up (FDU).
+\citet{vincenzo+21} use \textsc{mesa} stellar evolution models \citep{mesa} to correct for the effects of first dredge up.
 We instead use the \citetjack~sample of \apogee{} subgiants.
-Subgiant stars have not undergone FDU but have well-mixed atmospheres, so their atmospheric C and N abundances are still reflective of their birth abundances and do not need mixing corrections.
+Subgiant stars have not undergone first dredge up but have well-mixed atmospheres, so their atmospheric C and N abundances are still reflective of their birth abundances and do not need mixing corrections.
 We only compare the models to the low-$\alpha$ sequence unless otherwise specified.
@@
 \begin{equation}
-\y_{X} = \frac{M_{\rm ejected}}{M_{\rm birth}} \Delta Z_X
+\y_{X} =  \Delta Z_X \frac{M_{\rm ejected}}{M_{\rm birth}}
 \end{equation}
@@
 		\hline
-        Element & $\Ycc$ & $\y^{\rm AGB}$ & $y^{\rm SNe Ia}$ \\
+        Element & $y^{\rm cc}$ & $\y^{\rm agb}$ & $y^{\rm ia}$ \\
 		\hline
-        C & $0.0028 + 0.001\,(Z/Z_\odot)$ & $2.9\times{\rm C11}$ &  0 \\
+        C & Eq.~\ref{eq:zeta} & $2.9\times{\rm C11}$ &  0 \\
         Mg & 0.00185 & 0 & 0 \\
         Fe & 0.0012 & 0 & 0.00214 \\
-        N & 0.00072 & 0.0009$(Z/Z_\odot)\,M$ & 0\\
+        N & 0.00072 & 0.0009$M\left(\frac{Z}{Z_\odot}\right)$ & 0\\
 		\hline
@@
 Most models agree on the qualitative shape of the net fractional \agb\ C yield---% 
-stars with masses between about 2--4\,\Mo have the highest fractional C yields. As metallicity increases, the total AGB C yield decreases and the mass of the peak increases.
+stars with masses between about 2--4\,\Mo have the highest fractional C yields. As metallicity increases, the total \agb\ C yield decreases and the mass of the peak increases.
 
@@
 As the mass range $2\,\Mo\lesssim M \lesssim 4\,\Mo$ is most important for C production, about half of C production occurs before \about{1}\,Gyr, similar to \ia\ Fe. 
-\kx{} and \kxvi{} weight C production more heavily towards high-mass AGB stars resulting in a faster enrichment delay time, whereas the \cxi\ and \vxiii\ models predict a slightly longer timescale of \about{1}\,Gyr.
+\kx{} and \kxvi{} weight C production more heavily towards high-mass \agb\ stars resulting in a faster enrichment delay time, whereas the \cxi\ and \vxiii\ models predict a slightly longer timescale of \about{1}\,Gyr.
 In any case, little to no C is produced more than 2\,Gyr after a star formation event.
@@
 Otherwise, models differ only in their yield normalization and metallicity dependence. All models predict yields within a factor of \about{2} for fixed metallicity.
-For example, the three models \cxi, \kx{}, and \kxvi{} predict $y_\text{C}^\text{AGB}$ to be between 0.006 and 0.008 at solar metallicity, but \cxi\ has a much shallower metallicity dependence than the \kx{} and \kxvi{} models.
+For example, the three models \cxi, \kx{}, and \kxvi{} predict $y_\text{C}^\text{agb}$ to be between 0.006 and 0.008 at solar metallicity, but \cxi\ has a much shallower metallicity dependence than the \kx{} and \kxvi{} models.
 \vxiii{} instead predicts a yield \about{0.004}.
     As shown in the right panel of Fig.~\ref{fig:agb-ssp}, with increasing $Z$, C enrichment occurs earlier, and C destruction in low-mass stars leads to a declining C abundance at late times.
-
-We also briefly explore an analytic AGB model, defined as a cubic piecewise in mass and linear in metallicity.
-The piecewise is defined to have a maximum at $m_1$ and minimums at
-the end points $m-\delta m_-$ and $m+\delta m_+$. The function becomes constant
-outside of this range with (optionally) negative yields.
-And the resulting equation (excepting a prefactor)
-
-\begin{equation}
-y(m) = 
-\begin{cases}
-y_0 & m \leq m_0 - \delta m_- \\
-y_1 + (y_0 - y_1) \left(3 (\frac{m_0 - m}{\delta m_-})^2 - 
-2 (\frac{m_0 - m}{\delta m_-})^3\right) 
-    & m_0 - \delta m_- < m \leq m_0 \\
-y_1 + (y_2 - y_1) \left(3 (\frac{m - m_0}{\delta m_+})^2 - 
-2 (\frac{m-m_0}{\delta m_+})^3\right) 
-    & m_0 < m \leq m_0 + \delta m_+ \\
-y_2 & m_0 + \delta m_+ \leq m
-\end{cases}
-\end{equation}
 
@@
 
-\subsection{Yield Models}
+\subsection{Analytic Yield Models}
 
@@
 
-In Section \ref{sec:f-z-models}, we will show that none of the four \agb\ yield sets (\cxi{}, \kx{}, \vxiii{}, \kxvi{}) produce enough C relative to this $\Ycc$ value.
-So, we introduce normalization factors, $\alpha_{\rm AGB}$, and $\alpha_{\rm CC}$ which denote a multiplicative scaling of $\Ycc$ and $\Ycagb$ respectively.
+In Section \ref{sec:agb_results}, we will show that none of the four \agb\ yield sets (\cxi{}, \kx{}, \vxiii{}, \kxvi{}) produce enough C relative to this $\Ycc$ value.
+So, we introduce normalization factors, $\alpha_{\rm agb}$, and $\alpha_{\rm CC}$ which denote a multiplicative scaling of $\Ycc$ and $\Ycagb$ respectively.
 \begin{subequations} \label{eq:alpha}
@@
 
-In Section \ref{sec:f-z-models}, we find that $\alpha_{\rm agb}\approx 2.9$ for the \cxi{} yield model.
+In Section \ref{sec:agb_results}, we find that $\alpha_{\rm agb}\approx 2.9$ for the \cxi{} yield model.
 Using this \agb\ yield, we can now use Eq.~\ref{eq:y_c_eq} to find an estimate of $\Ycc$ as a function of metallicity.
@@
 \begin{equation}\label{eq:zeta}
-    \Ycc = 0.0028 + \zeta\left(\frac{Z}{Z_\odot}\right),
+    \Ycc = 0.004 \left(1 - \zeta + \zeta\,\frac{2Z}{Z + Z_\odot} + \frac{2\xi}{1 + Z/Z_{\rm III}}\right),
 \end{equation}
@@
 \end{figure}
+
+We also briefly explore an analytic \agb\ model, defined as a cubic piecewise in mass and linear in metallicity.
+The piecewise is defined to have a maximum at $m_1$ and minimums at
+the end points $m-\delta m_-$ and $m+\delta m_+$. The function becomes constant
+outside of this range with (optionally) negative yields.
+And the resulting equation (excepting a prefactor)
+
+\begin{equation}
+\y(m) = 
+\begin{cases}
+\y_0 & m \leq m_0 - \delta m_- \\
+\y_1 + (\y_0 - \y_1)\; f\!\left(\frac{m_0 - m}{\delta m_-}\right) 
+    & m_0 - \delta m_- < m \leq m_0 \\
+    \y_1 + (\y_2 - \y_1)\; f\!\left(\frac{m - m_0}{\delta m_+}\right)
+    & m_0 < m \leq m_0 + \delta m_+ \\
+\y_2 & m_0 + \delta m_+ \leq m
+\end{cases}
+\end{equation}
+
+where 
+\begin{equation}
+    f(x) = 3x^2 - 2x^3
+\end{equation}
+
+For the full equation, we take the above functional form multiplied by a
+metallicity dependent term, so
+
+\begin{equation}
+    \y_{\rm C}^{\rm agb}(m, Z) = \frac{\y(m) \left[\y_1 + \zeta \log_{10}(Z/Z_\odot) \right]}{\int_1^8 m\,\y(m)\,{\rm IMF}(m)\;dm}
+\end{equation}
+
+\subsection{Delayed C}
+To parameterize the \agb\ contribution to C production, we define $f_{\rm agb}$ to be the fraction of C which comes from \agb\ stars. 
+\begin{equation}\label{eq:f_agb}
+    f_{\rm agb} \equiv \frac{\Ycagb(Z=\Zo)}{\Yct(Z=\Zo)},
+\end{equation}
+($\Ycagb$ includes the multiplicative factor $\alpha_{\rm agb}$ as defined in Eq.~\ref{eq:alpha}).
+
+We can use the \caafe{} diagram of APOGEE stars to estimate the delayed portion of C.
+When binned in metallicity, median [C/Mg] changes by about 0.25 dex across the range of [Mg/Fe].
+As high-$\alpha$ stars have little to no delayed \ia\ Fe, these stars would also have little to no delayed \agb\ C.
+This means that AGB C stars make up about at most a fraction $f_{\rm agb} \approx 1 - 10^{-0.25} \approx 0.6$ of C production.
 
@@
 
-We use the \citetjack~sample of \apogee{} subgiants.
-Subgiant stars have not undergone FDU but have well-mixed atmospheres, so their atmospheric C and N abundances are still reflective of their birth abundances and do not need mixing corrections.
-We only compare the models to the low-$\alpha$ sequence unless otherwise specified.
-The selection criteria and differences between the samples are described in more detail in Appendix \ref{sec:jack}.
+Subgiants provide the ideal observational constraint to our model.
+Since first dredge up changes C surface abundances in evolved stars, these stars require model-dependent corrections to recover surface abundances \citep[e.g.][]{vincenzo+21}.
+On the other hand, gravitational settling can affect main sequence stellar abundances \citep[e.g.][]{souto19}.
+Subgiants have well-mixed envelopes, so gravitational settling is not as significant, and subgiants have not yet experienced first dredge up.
+We use a sample of APOGEE DR17 stars \citep{apogee17} as selected in \citetjack.
+We only compare the models to the low-$\alpha$ sequence (representing the thin disk) unless otherwise specified.
+The selection criteria and differences between the samples are described in more detail in Appendix~\ref{sec:jack}.
 
@@
 The fiducial model has the following qualitative characteristics of its C yields.
-\begin{itemize}
-    \item C is predominantly produced in \cc
+\begin{enumerate}
+    \item C is mostly (\about{80\%}) produced in \cc
     \item \cc\ produce more C at higher metallicities
     \item \agb\ stars produce less C at higher metallicities 
-\end{itemize} 
-The fiducial model uses the \cxi{} \agb\ yield tables (see Section \ref{sec:agb}, and Table \ref{tab:fiducial_mod}).
-We also amplify the \cxi{} yields by a factor of 2.9 such that \agb\ stars account for 20\% of C at $Z=Z_\odot$.
-
-Fig.~\ref{fig:c_evo} shows time evolution tracks of the fiducial model for \caah~ and \caafe.
-Comparing [C/Mg] against [Mg/Fe] enables us to see the late-time evolution of C more clearly.
-Because of the extended delay time distribution of \ia\ enrichment, [Fe/H] takes longer to reach equilibrium, and the late-time evolution is not as clustered as [Mg/H].
-The evolution proceeds as follows.
-Initially, \cc\ dominate production.
-As $\Ycc$ has strong metallicity dependence, [C/Mg] increases with time.
-Shortly thereafter, \agb\ stars contribute delayed C, increasing [C/Mg] even more steeply.
-As Mg begins to reach equilibrium, the [C/Mg] ratio plateaus as C approaches equilibrium.
-Finally, as $\Ycagb$ decreases or even becomes negative with higher metallicity, the [C/Mg] abundance may decline slightly.
-This is more evident in the lower panel of Fig.~\ref{fig:c_evo}---while the \caah\ trend reaches equilibrium at \about{5}\,Gyr, the \caafe\ trend continues to evolve even until the present day, exposing the effect of the relative delay times of \agb\ stars and \ia.
+\end{enumerate} 
+The fiducial model uses the \cxi{} \agb\ yield tables uniformly scaled by a factor of 2.9 (see Section \ref{sec:agb}, and Table \ref{tab:fiducial_mod}).
+
+Fig.~\ref{fig:c_evo} shows time evolution tracks of the fiducial model for \caah\ and \caafe. 
+As discussed in Section~\ref{sec:equilibrium}, \caah\ is set by the total C/Mg yields. 
+\caafe\ is instead useful in understanding delayed C production. 
+As both Fe and C are delayed elements, [Mg/Fe] steadily decreases after a star formation event, unlike [Mg/H] which quickly reaches equilibrium.
+All plots showing \caafe\ going forward are selected in metallicity such that $-0.15 \leq {\rm [Mg/H]} \leq -0.05$, so metallicity-dependent yields do not affect this plot.
+The \caafe{}-diagram is, in essance, an emperical delay-time-distribution for a single stellar population of C, especially as we assume a $\propto t^{-1.1}$ delay-time-distribution for Fe. 
+Comparing the top and bottom panels of Fig.~\ref{fig:c_evo} highlights the differences between \caah\ and \caafe.
+While \caah\ quickly reaches its final equilibrium distribution (within \about{5}\,Gyr), \caafe\ continues to evolve in both [Mg/Fe] and [C/Mg] until the simulation ends.
+
+C evolution proceeds as follows, (for a single zone)
+\begin{enumerate}
+    \item \cc\ initially dominate production. As $\Ycc$ has strong metallicity dependence, [C/Mg] increases with time. 
+    \item \agb stars contribute delayed C, causing [C/Mg] to increase even faster with [Mg/H]. 
+    \item[(iii)] [C/Mg] plateaus as C also approaches equilibrium. 
+    \item[(iv)] [C/Mg] may decrease due to declining SFH or slightly negative yields from \about{1}\,\Mo stars.
+
+\end{enumerate}
 
@@
 
-\subsection{Low mass stellar yields}\label{sec:f-z-models}
-
-To parameterize the \agb\ contribution to C production, we define 
-\begin{equation}\label{eq:f_agb}
-    f_{\rm AGB} \equiv \frac{\Ycagb}{\Yct}\Bigg\vert_{Z=Z_\odot},
-\end{equation}
-where  $\Ycagb$ includes the multiplicative factor $\alpha_{\rm AGB}$ as defined in Eq.~\ref{eq:alpha}.
-Fig.~\ref{fig:agb_sims} compares the \kx{}, \kxvi{}, \cxi{}, and \vxiii{} yield models.
-We use the published, unscaled yield tables ($\alpha_{\rm AGB}=1$) for Fig.~\ref{fig:agb_sims}.
-As the highest \agb\ yield at solar, \kx{} is only $\Ycagb=0.000585$, $f_{\rm AGB} \leq 0.12$ for all models.
-Massive stars dominate C production with unscaled yields.
-While it is easy to modify the \agb\ yields in our model, their small contribution reduces the effect.
-We leave a more detailed discussion of the effects of \agb\ models for Appendix \ref{sec:f-z-models} and use \cxi{} yields hereafter.
-
-\begin{figure*}
-\centering
-\includegraphics{agb_oob.pdf}
+Fig.~\ref{fig:f_agb_evo} shows $f_{\rm agb}$ calculated from the fiducial model of current effective C yields in the gas phase (using the SFH as a proxy for $\Ycc$. 
+At early times, \cc\ dominate.
+As the galaxy evolves, \agb\ have time to add C, increasing $f_{\rm agb}$.
+However, the metal-rich inner regions lower \agb\ C yields, so these regions never reach as high of a $f_{\rm agb}$ as the outer regions do.
+
+\begin{figure}
+    \centering
+    \includegraphics{f_agb_rt.pdf}
+    \caption[]{The evolution of $f_{\rm agb}$ across the Galaxy and with time.}
+    \label{fig:f_agb_evo}
+\end{figure}
+
+\subsection{High-mass stellar yields}\label{sec:results_highmass}
+\cc, which likely make up the majority of C, set the overal C abundances. 
+ and the \cc\ metallicity dependence $\zeta$ in Fig.~\ref{fig:first_models}.
+Fig.~\ref{fig:first_models} shows models with varying $\Ycc$ metallicity dependence.
+As the \caah~trend is approximated by the equilibrium C/Mg abundance with metallicity, the models with stronger metallicity dependence have a stronger slope in \caah.
+However, \caafe~is minimally affected by these changes since \cc\ occurs on much shorter timescales than \ia\ and \agb\ enrichment, and we only consider stars in a small metallicity range for \caafe.
+
+ Fig.~\ref{fig:first_models}
+
+\begin{figure*}
+\includegraphics[height=2in, width=6in]{beta.pdf}
+
 \caption[Median Stellar Abundance Trends]{
@@
 }
+\label{fig:first_models}
+\end{figure*}
+
+\subsection{Low mass stellar yields}\label{sec:agb_results}
+
+Fig.~\ref{fig:agb_sims} compares the \kx{}, \kxvi{}, \cxi{}, and \vxiii{} yield models.
+As the highest \agb\ yield at solar, \kx{} is only $\Ycagb=0.000585$, so $f_{\rm agb} \leq 0.12$ for all models.
+Massive stars dominate C production with unscaled yields.  
+With the exception of \vxiii, the different \agb\ models only affect the overall metallicity dependence (in \caah).
+We leave a more detailed discussion of the effects of \agb\ models for Appendix~\ref{sec:oob_models} and use \cxi{} (OR ANALYTIC?) yields hereafter.
+
+\begin{figure*}
+\centering
+\includegraphics[height=2in, width=6in]{agb_oob.pdf}
+
+\caption[]{Similar to Fig.~\ref{fig:first_models}, except where each line corresponds to one of our four \agb\ yield sets (\cxi, \kx, \vxiii, \kxvi).}
 \label{fig:agb_sims}
@@
 
-Next, we investigate adjustments to the \agb\ yield fraction $f_{\rm AGB}$ and the \cc\ metallicity dependence $\zeta$ in Fig.~\ref{fig:beta_f}.
-On the top panel of Fig.~\ref{fig:beta_f}, we plot models with varying $\Ycc$ metallicity dependence.
-As discussed in Section \ref{sec:equilibrium}, the \caah~trend is approximated by equilibrium, so the trends of these have steeper \caah~corresponding to steeper metallicity dependence.
-However, \caafe~is minimally affected by these changes since \cc\ occurs on much shorter timescales than \ia\ and \agb\ enrichment.
-
-In the bottom panel of Fig.~\ref{fig:beta_f}, we plot three models with different \agb\ fractions while using \cxi{} yields.
-The \caafe~relationship is set by $f_{\rm AGB}$ because a specific amount of C must be released at a delayed time to match the \ia\ production of Fe and increase [C/Mg] as [Mg/Fe] decreases to reproduce the data.
-Increased $f_{\rm AGB}$ results in a decreased slope in \caah, owing to the negative metallicity dependence of $\Ycagb$.
-So while \caah~alone cannot differentiate models which vary $f_{\rm AGB}$ and $\zeta$ correspondingly, \caafe~provides information on $f_{\rm AGB}$.
-So, we can use \caafe~to estimate $f_{\rm AGB}\approx 0.2$, and then choose $\zeta$ to match \caah.
-
-One source of theoretical uncertainty in this result is that the \ia\ yield and delay time distributions have their own uncertainties.
-We discuss variations in $y_{\rm Fe}^{\rm Ia}$ in Appendix \ref{sec:f-z-models}, and find that the qualitative conclusions are largely unaffected.
-I, therefore, focus on the choices of $y_{\rm Fe}^{\rm Ia} = 0.00214$ and a $t^{-1.1}$ delay time distribution choices from the fiducial model here.
-In short, the scaling of the trend and metallicity dependence of C (as seen in
-the \caah\ trend) gives information on the total C yield and the behavior of \cc\ (as the dominating producer of C), the \caafe\ trend exposes the delayed effect of C from \agb\ contribution.
-
-Negative AGB yields cause a morphological change in the abundance trends.
+Here, we investigate adjustments to the \agb\ yield fraction $f_{\rm agb}$
+Fig.~\ref{fig:f_agb} shows three models with different \agb\ fractions while using \cxi{} yields.
+The \caafe~relationship is set by $f_{\rm agb}$ because a specific amount of C must be released at a delayed time to match the \ia\ production of Fe and increase [C/Mg] as [Mg/Fe] decreases to reproduce the data.
+Increased $f_{\rm agb}$ results in a decreased slope in \caah, owing to the negative metallicity dependence of $\Ycagb$.
+So while \caah~alone cannot differentiate models which vary $f_{\rm agb}$ and $\zeta$ correspondingly, \caafe~provides information on $f_{\rm agb}$.
+So, we can use \caafe~to estimate $f_{\rm agb}\approx 0.2$, and then choose $\zeta$ to match \caah.
+
+Negative \agb\ yields cause a morphological change in the abundance trends.
 If the yields of low mass stars are negative, then at late times in a SSP, C abundances will decrease.
@@
 As we do not observe this in the data, this is either obscured by star formation history (Seee eeee) or observational scatter.
-Instead, if lower-intermediate mass AGB stars produce negative carbon yields, it is possible to observe this as a dip in the early parts of the \caafe{} trend...
+Instead, if lower-intermediate mass \agb\ stars produce negative carbon yields, it is possible to observe this as a dip in the early parts of the \caafe{} trend...
 
@@
 	\centering
-    \caption[Low-Mass Stellar Carbon Yields at Solar Metallicity]{For each \agb\ yield set, the \imf-averaged \agb\ C yield at solar metallicity $y_{\rm C, 0}^{\rm AGB}$ and the multiplicative factor reaches an \agb\ contribution of 20\% $\alpha_{\rm AGB, 20}$.}
+    \caption[Low-Mass Stellar Carbon Yields at Solar Metallicity]{For each \agb\ yield set, the \imf-averaged \agb\ C yield at solar metallicity $y_{\rm C, 0}^{\rm agb}$ and the multiplicative factor reaches an \agb\ contribution of 20\% $\alpha_{\rm agb, 20}$.}
 	\label{tab:alpha_agb}
@@
 		\hline 
-		AGB Model & $y_{\rm C, 0}^{\rm AGB}$ & $\alpha_{\rm AGB, 20}$\\
+		\agb\ Model & $y_{\rm C, 0}^{\rm agb}$ & $\alpha_{\rm agb, 20}$\\
         \hline
@@
 \centering
-\includegraphics{beta.pdf}
-\includegraphics{f_agb.pdf}
-
-\caption[Adjusted Yield Models]{Similar to Fig.~\ref{fig:agb_sims} except the top plot shows the fiducial model with lower and higher values of $\zeta$, the metallicity dependence of $\Ycc$.
-The bottom plot shows models with $f_{\rm AGB}=$0.1, 0.2, and 0.4.
-Both the $f_{\rm AGB}$ and $\zeta$ influence \caah, but only $f_{\rm AGB}$ has a significant impact on \caafe.}
-\label{fig:beta_f}
+\includegraphics[height=2in, width=6in]{f_agb.pdf}
+
+\caption[Adjusted Yield Models]{Similar to Fig.~\ref{fig:first_models}, except where the \agb\ C contribution is varied from the fiducial ($f_{\rm agb}=0.2$) to 0.1 and 0.3 (see Eq.~\ref{eq:f_agb} and Section.~\ref{sec:agb_results}.}
+\label{fig:f_agb}
 \end{figure*}
@@
 \centering
-\includegraphics{lateburst_eta.pdf}
-
-\caption{Similar to Fig.~\ref{fig:agb_sims} but comparing the fiducial model to alternate star formation histories (see Section  \ref{sec:sfh}).}
+\includegraphics[height=2in, width=6in]{lateburst_eta.pdf}
+
+\caption{Similar to Fig.~\ref{fig:first_models} but comparing the fiducial model to alternate star formation histories (see Section  \ref{sec:sfh}).}
 
@@
 The equilibrium arguments discussed in Section \ref{sec:equilibrium} suggest however that abundance ratios are independent of the choice of normalization and the value of $\eta$.
-I, therefore, expect our results regarding the relative yield $y_{\rm C}/y_{\rm Mg}$ and its metallicity dependence to extend to the other class of models omitting mass loading.
+We, therefore, expect our results regarding the relative yield $y_{\rm C}/y_{\rm Mg}$ and its metallicity dependence to extend to the other class of models omitting mass loading.
 We demonstrate this further here.
@@
 
-\begin{figure*}
-    \centering
-    \includegraphics{eta.pdf}
-    \caption[Reduced-Outflow Models]{Similar to Fig.~\ref{fig:agb_sims} but comparing the fiducial model to reduced mass loading models (see Section  \ref{sec:outflows}).
+An addition source of theoretical uncertainty in this result is that the \ia\ yield and delay time distributions have their own uncertainties.
+We discuss variations in $y_{\rm Fe}^{\rm Ia}$ in NOWHERE, and find that the qualitative conclusions are largely unaffected.
+We, therefore, focus on the choices of $y_{\rm Fe}^{\rm Ia} = 0.00214$ and a $t^{-1.1}$ delay time distribution choices from the fiducial model here.
+In short, the scaling of the trend and metallicity dependence of C (as seen in
+the \caah\ trend) gives information on the total C yield and the behavior of \cc\ (as the dominating producer of C), the \caafe\ trend exposes the delayed effect of C from \agb\ contribution.
+
+\begin{figure*}
+    \centering
+    \includegraphics[height=2in, width=6in]{eta.pdf}
+    \caption[Reduced-Outflow Models]{Similar to Fig.~\ref{fig:first_models} but comparing the fiducial model to reduced mass loading models (see Section  \ref{sec:outflows}).
 Both yields and mass-loading are adjusted correspondingly such that the equilibrium abundances are unchanged.
@@
     \centering
-    \includegraphics{nitrogen.pdf}
-    \caption[C/N Abundance Agreement]{Similar to Fig.~\ref{fig:agb_sims}, except comparing [C/N] from the fiducial model only.
+    \includegraphics[height=2in, width=6in]{nitrogen.pdf}
+    \caption[C/N Abundance Agreement]{Similar to Fig.~\ref{fig:first_models}, except comparing [C/N] from the fiducial model only.
 N yields are adapted from \cite{james+23}.
@@
 In this work, we investigate the role of C yields on the predictions of multi-zone \gce{} models.
-\citet{james+23} performed a similar analysis focusing on N.
-They found that matching the observed relationship between N and O abundances%
-\footnote{e.g.
-\citet{HEK00,PVT10,berg+12, berg+20, skillman+20, izotov+12, james2+15, dopita+16}.} requires relative N and O yields from simple stellar populations with a roughly linear dependence on metallicity (i.e.
-$y_{\rm N}/y_{\rm O} \propto Z$).
-Here, we perform a similar analysis on C.
-
-Though \cc\ C yields are poorly understood, we adopt an equilibrium approximation and determine a functional form that approximately matches trends in \apogee{} subgiant and is consistent with high-mass nucleosynthesis models.
+
+As \cc\ C yields are poorly understood, we adopt an equilibrium approximation and determine a functional form that approximately matches trends in \apogee{} subgiant and is consistent with high-mass nucleosynthesis models.
 Variations of the metallicity dependence of this \cc\ yield affect trends in \caah~but do not affect trends in \caafe\ (when taking a slice in [Mg/H]).
@@
 \VICE~\citep{JW20, james+21},
-\texttt{matplotlib} \citep{matplotlib},
-\texttt{scipy} \citep{scipy},
-\texttt{IPython} \citep{ipy},
-\texttt{pandas} \citep{pandas},
-\texttt{numpy} \citep{numpy},
-\texttt{astropy} \citep{astropy:2013, astropy:2018, astropy:2022},
+\textsc{matplotlib} \citep{matplotlib},
+\textsc{scipy} \citep{scipy},
+\textsc{IPython} \citep{ipy},
+\textsc{pandas} \citep{pandas},
+\textsc{numpy} \citep{numpy},
+\textsc{astropy} \citep{astropy:2013, astropy:2018, astropy:2022},
 and 
-\texttt{seaborn} \citep{seaborn}
+\textsc{seaborn} \citep{seaborn}
 .
@@
 
-Photospheric C and N abundances in subgiant are reflective of their birth abundances \citep{gilroy89, korn+07, lind+08, souto+18, souto19} As FDU, which affects C and N abundances, only occurs during the ascent onto the RGB, subgiant stars are unaffected by this enrichment.
-
-An alternate approach for this analysis would be to estimate the birth abundances of RGB stars by correcting surface abundance effects from FDU as in \cite{vincenzo+21}.
+Photospheric C and N abundances in subgiant are reflective of their birth abundances \citep{gilroy89, korn+07, lind+08, souto+18, souto19} As first dredge up, which affects C and N abundances, only occurs during the ascent onto the RGB, subgiant stars are unaffected by this enrichment.
+
+An alternate approach for this analysis would be to estimate the birth abundances of RGB stars by correcting surface abundance effects from first dredge up as in \cite{vincenzo+21}.
 Subgiants are the more attractive option since these observations do not rely on model-dependent corrections.

### 2023-07-07 carbon_paper/tex/main.tex
thesis edits

@@
 % Acronyms
+\newcommand{\agb}{AGB}
+\newcommand{\apogee}{APOGEE}
 \newcommand{\cc}{CCSNe}
-\newcommand{\agb}{AGB}
+\newcommand{\gce}{GCE}
 \newcommand{\ia}{SNe Ia}
+\newcommand{\imf}{IMF}
 \newcommand{\sfh}{SFH}
-\newcommand{\dla}{DLA}
 \newcommand{\ssp}{SSP}
-\newcommand{\imf}{IMF}
-\newcommand{\gce}{GCE}
-\newcommand{\apogee}{APOGEE}
 
@@
 
-\newcommand{\proton}{\isotope[1][1]{p}}
 \newcommand{\Yct}{\ensuremath{y_{\rm C}}}
@@
 % context
-Limited knowledge of stellar physics leads to uncertainties in elemental yield predictions.
-% aims
-As an independent approach, we constrain the nucleosynthetic yields of C using multi-zone Galactic chemical evolution models.
+C is an important element across astronomy. However, its origin remains poorly understood. 
+% 
+As stellar yields are highly uncertain, we aim to constrain the stellar yields of C through multi-zone Galactic chemical evolution models. 
 % results
-By matching the median trends of \caah\ and \caafe\ in  {\sc apogee} subgiant stars, we find that high-mass and low-mass stars contribute \about{80\%} and \about{20\%} of total C production respectively.
+We use \apogee\ subgiants to constrain the model. 
 % 
-To match the normalization of the trends, we estimate the massive star C/Mg yield ratio $\Ycc/\Yoc = 1.57 + 0.59 \left(Z/Z_\odot\right)$,  explaining the \caah\ trend when including the low mass C contribution.
-%
-Variations in the star formation history only slightly impact the low [Mg/Fe] tail of the [C/Mg]-[Mg/Fe] relation.
-However, most of the scatter in the \caah\ distribution can be attributed to measurement errors and radial migration.
-% 
-Due to the degeneracy between the normalization of elemental yields and the strength of mass-loading in Galactic outflows, we am only able to constrain the relative yields of C/Mg and its metallicity dependence.
-While measurements of gas-phase C abundances are challenging, our model is broadly consistent with the [C/O]-[O/H] trend observed in compiled literature measurements.
+We find that \caafe\ is an emirical estimate of the delayed C sources, enabling us to estimate that \agb\ stars and \cc\ produce about 20\% and 80\% of C, respectively.  
+The \caah\ trend instead represents the equilibrium abundances of C and Mg. 
+We use the \caah\ trend to estimate the CCSNe C/Mg yield, determining that  $\Ycc/\Yoc = EQUATION$ when including \agb\ C. 
+% misc
+Our models are relatively independent of uniform scaling of yields and outflows, alternate \sfh{}s. 
+However, the stars which contribute to \agb\ C production and the \ia\ delay time distribution of Fe contribute uncertainties to our conclusions. 
+% gas phase
+While reliable gas-phase and low-metallicity measurments of C are challenging, we find that our model and a singlezone model with our recommended yields replicate the broad trends of \caah across different environments and metallicities.
 
@@
 are shaped by poorly understood processes, including mass loss, nuclear reaction rates, rotational mixing, convection, and explodability \citep{romano+10,KL14,ventura+13, LC18, emily+21}.
-To better understand where C comes from and how it evolves, our aim is to use a combination of APOGEE observations and multi-zone models to develop estimates of the required C yields to reproduce galactic trends.
+To better understand where C comes from and how it evolves, our aim is to use a combination of \apogee\ observations and multi-zone models to develop estimates of the required C yields to reproduce galactic trends.
 \cite{james+23} examined similar \gce{} models of N (which is closely related to C), finding that trends in N and O\footnotemark{} are explained by the metallicity dependence of N/O yields.
@@
 In optical spectroscopy, C lines are relatively faint, and surveys such as GALAH struggle against low detection rates, potentially biasing sample measurments.
-While APOGEE includes more reliable C$_2$ lines, there is an additional risk of systematics because .....
+While \apogee\ includes more reliable C$_2$ lines, there is an additional risk of systematics because .....
 In the gas phase, HII regions are our best window into C abundances in our galaxy and extragalactic regions including dwarf. 
@@
 We also use Mg and Fe as tracers of \cc{} and \ia{} enrichment respectively. 
-O and Mg are produced almost entirely from \cc\ with metallicity-independent yields, making each element. In contrast Fe is produced in similar amounts by \cc\ and \ia.
+O and Mg are produced almost entirely from \cc\ with metallicity-independent yields. In contrast Fe is produced in similar amounts by \cc\ and \ia.
 
@@
 \end{equation}
-Assuming an exponentially declining star formation history $\dot{M}_\star \propto e^{-t/\tau_{\rm sfh}}$, the equilibrium abundance is derived analytically by setting $\dot{Z}_\alpha=0$.
+Assuming an exponentially declining \sfh{} $\dot{M}_\star \propto e^{-t/\tau_{\rm sfh}}$, the equilibrium abundance is derived analytically by setting $\dot{Z}_\alpha=0$.
 \begin{equation}\label{eq:z_eq}
@@
 
-We can use the \caafe{} diagram of APOGEE stars to estimate the delayed portion of C.
+We can use the \caafe{} diagram of \apogee\ stars to estimate the delayed portion of C.
 When binned in metallicity, median [C/Mg] changes by about 0.25 dex across the range of [Mg/Fe].
@@
 \JJ~derives $\tau_{\rm sfh}(R)$ through analysis of four integral field spectroscopy surveys in \cite{sanches20}.
-At each $R$, the star formation history is normalized to match the stellar surface density gradient \citep{BHG16} and the total stellar mass reaches $5.17\times10^{10}\,\Mo$ \citep{LM15}.
+At each $R$, the \sfh{} is normalized to match the stellar surface density gradient \citep{BHG16} and the total stellar mass reaches $5.17\times10^{10}\,\Mo$ \citep{LM15}.
 Star formation ends beyond a radius $R=15.5\,$kpc.
@@
 Subgiants have well-mixed envelopes, so gravitational settling is not as significant, and subgiants have not yet experienced first dredge up.
-We use a sample of APOGEE DR17 stars \citep{apogee17} as selected in \citetjack.
+We use a sample of \apogee\ DR17 stars \citep{apogee17} as selected in \citetjack.
 We only compare the models to the low-$\alpha$ sequence (representing the thin disk) unless otherwise specified.
@@
 
- Fig.~\ref{fig:first_models}
-
 \begin{figure*}
@@
 This will appear as a downturn in the \caafe{} abundance trends as [Mg/Fe] approaches solar values.
-As we do not observe this in the data, this is either obscured by star formation history (Seee eeee) or observational scatter.
+As we do not observe this in the data, this is either obscured by \sfh\ (Seee eeee) or observational scatter.
 Instead, if lower-intermediate mass \agb\ stars produce negative carbon yields, it is possible to observe this as a dip in the early parts of the \caafe{} trend...
+
+FIGUREEE
 
@@
 	\label{tab:alpha_agb}
-	\begin{tabular}{ccr} % four columns, alignment for each
+	\begin{tabular}{cccr} % four columns, alignment for each
 		\hline 
-		\agb\ Model & $y_{\rm C, 0}^{\rm agb}$ & $\alpha_{\rm agb, 20}$\\
+        \agb\ Model & $y_{\rm C}^{\rm agb}(\Zo)$ & $d \Ycagb(\Zo)/dZ$ 
+                    & $\alpha_{\rm agb, 20}$\\
         \hline
-        \cxi & 0.000347 & 2.9\\
-        \kx & 0.000585 & 1.7\\
-        \vxiii & 0.000060 & 16.5\\
-        \kxvi & 0.000421 & 2.4\\
+        \cxi & 0.000418 & -0.022 & 2.9\\
+        \kx & 0.00065 & -0.063 & 1.7\\
+        \vxiii & 0.00049 & -0.032 & 16.5\\
+        \kxvi & 0.00056 & -0.034 & 2.4\\
 		\hline
@@
 
-Here, we consider a \textit{lateburst} model, created by multiplying our fiducial inside-out \sfh{} with a Gaussian.
-\begin{equation}\label{eq:lateburst}
-    \dot{\Sigma}_{\rm lateburst} \propto \dot{\Sigma}_{\rm inside-out} \left(1 + A\,e^{-(t-\tau_{\rm burst})^2/2\sigma^2_{\rm burst}} \right)
-\end{equation}
-
-$A=1.5$ represents the amplitude of the birth, $\tau_\text{burst}=10.8$\,Gyr is the time where the burst is strongest, and $\sigma_\text{burst}=1$\,Gyr is the width of the burst.
-We also consider an \textit{earlyburst} model as a slight variation of the lateburst, where the burst is instead exponential and placed at $t_1=5$\,Gyr. 
+In this section, we consider two modifications of our fiducial \sfh{}: \textit{lateburst} and \textit{earlyburst}.
+Our lateburst model adds a Gaussian factor to the inside-out \sfh{},
+\begin{equation}\label{eq:late-burst}
+    \dot{\Sigma}_\text{lateburst} \propto \dot{\Sigma}_\text{inside-out} \left(1 + A\,e^{-(t-\tau_{\rm burst})^2/2\sigma^2_{\rm burst}} \right)
+\end{equation}
+where $A=1.5$ represents the amplitude of the birth, $\tau_\text{burst}=10.8$\,Gyr is the time where the burst is strongest, and $\sigma_\text{burst}=1$\,Gyr is the width of the burst.
+Our earlyburst model is similar, but the burst is exponential and placed at $t_1=5$\,Gyr. 
 \begin{equation}\label{eq:twoinfall}
@@
 \end{equation}
-where we take the burst duration, $\tau_{\rm burst}=1$\,Gyr in this case. 
+where we take the burst duration, $\tau_{\rm burst}=1$\,Gyr.
 This approximately corresponds to the Gaia-Encelidus merger, inducing higher star formation in the Milky Way \citep{spitoni21, bonaca20, helmi18}.
@@
 
-\caption{Similar to Fig.~\ref{fig:first_models} but comparing the fiducial model to alternate star formation histories (see Section  \ref{sec:sfh}).}
+\caption{Similar to Fig.~\ref{fig:first_models} but comparing the fiducial model to alternate \sfh{}s (see Section  \ref{sec:sfh}).}
 
@@
 \subsection{Degeneracies} \label{sec:outflows}
-
-Radial migration doesn't matter...
 
@@
 
+Measurements of C abundances are challenging.
+In HII regions, C/O abundance ratios are measured with either recombination lines or collisional excitation lines.
+However C lacks strong collisional excitation lines, and recombination lines fall in the ultraviolet without nearby reference H lines \citep{skillman+20}.
+Additionally, recombination and collisional excitation measurements disagree by a factor of \about{2} \citep{GR07}.
+Variations in the \sfh{}s may furthermore increase scatter, as \agb\ are a delayed source of C.
 C abundances are challenging to measure.
@@
 As an additional test of the model, we next compare the model predictions against gas-phase measurements.
-Fig.~\ref{fig:gas_phase} shows the fiducial model's gas-phase predictions compared to observations of the Milky Way and extragalactic HII regions, halo stars, and \dla\ systems.
+Fig.~\ref{fig:gas_phase} shows the fiducial model's gas-phase predictions compared to observations of the Milky Way and extragalactic HII regions, halo stars, and damped Lyman-alpha systems.
 The model is broadly consistent with observations, where the model at $t=2$\,Gyr approximates the slope of dwarf galaxies and halo stars.
@@
 So while we use Mg as the representative alpha for stellar abundances, we instead use O when comparing gas-phase abundances.
-As we assume ${\rm[Mg/O]}=0$, our model is independent of the choice of the alpha
-
-Measurements of C abundances in the gas-phase are challenging.
-In HII regions, C/O abundance ratios are measured with either recombination lines or collisional excitation lines.
-However C lacks strong collisional excitation lines, and recombination lines fall in the ultraviolet without nearby reference H lines \citep{skillman+20}.
-Additionally, recombination and collisional excitation measurements disagree by a factor of \about{2} \citep{GR07}.
-Variations in the \sfh{}s may furthermore increase scatter, as \agb\ are a delayed source of C.
-
-The decreasing [C/O] abundance at very-low metallicities is likely due to population III stellar yields \citep[e.g.][]{hirschi07}, as suggested by \citet{cooke+17} and \citet{FN15}.
-agb stars cannot explain the increase in C yields at low metallicity in the \dla{} sample as the evolutionary timescales of \dla{}s are shorter than the typical delay time distribution of \agb\ stars.
+As we assume ${\rm[Mg/O]}=0$, our model is independent of the choice of the $\alpha$-element.
+
+The elevated [C/O] abundance at very-low metallicities is likely due to population III stellar yields \citep[e.g.][]{hirschi07}, as suggested by \citet{cooke+17} and \citet{FN15}.
+\agb\ stars cannot explain the increase in C yields at low metallicity in the damped Lyman-alphas sample as the evolutionary timescales of damped Lyman-alpha systems are shorter than the typical delay time distribution of \agb\ stars.
+
+DISCUSSION ABOUT SINGLE ZONE
 
@@
     HII regions    \citep[pink circles;][]{skillman+20, esteban+02, esteban+09, esteban+14, esteban+19}
-    \dla\ systems \citep[blue triangles;][]{ellison+10, srianand+10, dutta+14, DZ+03, pettini+08, morrison+16,cooke+17},  % a1: Cooke et al.
+    damped Lyman-alpha (DLA) systems \citep[blue triangles;][]{ellison+10, srianand+10, dutta+14, DZ+03, pettini+08, morrison+16,cooke+17},  % a1: Cooke et al.
 (2015); 2: Dutta et al.
@@
 While our model was built on data near solar metallicity, observations of very low metallicity, high redshift damped Lyman-$\alpha$ systems indicate higher C/O ratios \citep{cooke+17}, consistent with yields from population III stars \citep[e.g.][]{hirschi07}.
-Population III stars, \cc\, and \agb stars altogether explain the observed evolutionary history of C.
+Population III stars, \cc\, and \agb\ stars altogether explain the observed evolutionary history of C.
 
@@
 These larger samples will enable similar work to tighten constraints on stellar models and our understanding of galaxy structure and evolution.
+MAYBE MENTION METAL-POOR OR OTHER PROJECTS?
 

### 2023-07-09 carbon_paper/tex/main.tex
thesis edits

@@
 
-\graphicspath{{../figures/}}
+\graphicspath{{figures/}}
 
@@
 \newcommand{\Ycagb}{\ensuremath{y_{\rm C}^{\rm agb}}}
-
 \newcommand{\y}{\ensuremath{\rotatebox[origin=B,y=0.5ex]{180}{y}}}
+
 \newcommand{\Mo}{%
@@
 After a single stellar population (SSP)\footnotemark{} forms, \cc{} are the first chemical enrichers.
-\cc{} explode within $\lesssim 40$\,Myr, providing light elements (C, O, and Mg) and heavier elements (Fe and beyond).
-Next, low-mass stars begin to reach the end of their lives.
+\cc{} explode within $\lesssim 40$\,Myr, providing light elements (e.g.
+C, O, and Mg) and heavier elements (Fe and beyond).
+Next, low-mass stars begin to reach the end of their lives, entering the \agb{} phase.
 By shedding their outer layers, \agb{} stars are important sources of C, N, and neutron capture elements.
@@
 \end{equation}
-where $M_{\rm ejected}$ and $M_{\rm birth}$  are the total ejected mass and the birth mass of the star, and $\Delta Z_X$ is the change in mass fraction of abundance X from birth to ejected.
-For example, if a 1\,\Mo\ star has $\y_{\C} = 10^{-3}$, then the star will add $10^{-3}\,\Mo$ of new C to the interstellar medium.
+where $M_{\rm ejected}$ and $M_{\rm birth}$  are the total ejected mass and the birth mass of the star, and $\Delta Z_X$ is the change in $Z_X$ from the birth material to the ejected material of the star.%
+\footnote{$Z_{X}$ represents the mass fraction of element $X$.}
+%
+For example, a 1\,\Mo\ star with $\y_{\C} = 10^{-3}$ will add $10^{-3}\,\Mo$ of new C to the interstellar medium. 
+Also, note that yields may be negative if the material returned to the interstellar medium has a lower abundance $Z_X$ than the material the star was formed from.
 Although per-star yields are necessary to compute \agb{} star enrichment rates in \gce{}  models, \imf-averaged yields are useful in interpreting their predictions. 
@@
 We use $t=10\,$Gyr for total yields when $t$ is not used.
-To calculate the \imf-averaged net yields, we use the Versatile Integrator for Chemical Evolution code (\VICE\footnotemark{}).
+To calculate the \imf-averaged net yields, we use the Versatile Integrator for Chemical Evolution code (\VICE).\footnotemark{}
 
@@
         C & Eq.~\ref{eq:zeta} & $2.9\times{\rm C11}$ &  0 \\
+        O & 0.015 & 0 & 0 \\
         Mg & 0.00185 & 0 & 0 \\
@@
 Hot bottom burning and third dredge-up result in mass-dependent C yields. 
-Stars less than about??2\,\Mo do not experience third dredge-up.
+Stars less than \about{2}\,\Mo do not experience third dredge-up.
 As a result, these stars C abundances are only affected by first dredge-up, resulting in little change to C yields or slight destruction of C.
-In 2?? to 4?? \Mo stars, third dredge up becomes important, enriching the outer layers with C, making these stars the most important producers of C. 
-In massive, high-metallicity \agb\ stars, both hot bottom burning and third dredge up occur; however, third dredge up is much more efficient, resulting in significant \C[12] destruction.
+Between \about{2} and \about{5} \Mo, third dredge up becomes important, enriching the outer layers with C, making these stars the most important producers of C. 
+In \agb\ stars more massive than \about{5}\,\Mo, both hot bottom burning and third dredge up occur; however, third dredge up is much more efficient, resulting in significant \C[12] destruction.
 
     In this work, we explore four different sets of \agb\ star yield tables from literature,
-    providing necessary well-sampled grids in mass and metallicity. We refer to the yields from the following studies as the following.
-\begin{enumerate}
+    providing necessary well-sampled grids in mass and metallicity. We refer to the yields from the following studies as the following,
+\begin{description}
     \item \cxi: \citet{cristallo+11, cristallo+15}
@@
     \item \kxvi: \citet{KL16, karakas+18}
-\end{enumerate}
+\end{description}
 In Appendix~\ref{sec:oob_models}, the masses, metallicites, and notable differences between each yield set are briefly described. 
@@
 Fig.~\ref{fig:y_agb} compares the stellar \agb\ C yield for these four models.
-Note that the net yields may be negative if a star ejects material with a lower average C abundance than the material the star was formed from.
-Most models agree on the qualitative shape of the net fractional \agb\ C yield---% 
-stars with masses between about 2--4\,\Mo have the highest fractional C yields. As metallicity increases, the total \agb\ C yield decreases and the mass of the peak increases.
+Most models agree on the qualitative shape of the net fractional \agb\ C yield.
+Stellar yields peak between masses of about 2--4 \Mo and decline as stars become more or less massive.
+As metallicity increases, the total \agb\ C yield decreases.
+The mass of peak C yields also increases slightly with metallicity.
+More metal-rich stars lose mass more quickly due to higher opacities, so these stars behave more like low-mass AGB stars.
+MORE PHYSICS
 
@@
 \vxiii{} differs in that it shows a non-monotonic metallicity dependence. However, this effect is only for models with $\log Z/Z_\odot \lesssim -1$.
-Otherwise, models differ only in their yield normalization and metallicity dependence. All models predict yields within a factor of \about{2} for fixed metallicity.
+Otherwise, models differ only in their yield normalization and metallicity dependence. 
+All yield models span a range of \about{2} for a given metallicity.
 For example, the three models \cxi, \kx{}, and \kxvi{} predict $y_\text{C}^\text{agb}$ to be between 0.006 and 0.008 at solar metallicity, but \cxi\ has a much shallower metallicity dependence than the \kx{} and \kxvi{} models.
 \vxiii{} instead predicts a yield \about{0.004}.
-    As shown in the right panel of Fig.~\ref{fig:agb-ssp}, with increasing $Z$, C enrichment occurs earlier, and C destruction in low-mass stars leads to a declining C abundance at late times.
 
@@
 Massive stars form $^{12}$C in their cores through the triple--$\alpha$ process. However, only C ejected through supernovae and stellar winds contributes to the yield. 
-While there are many stellar models providing predictions of \cc{} yields, the results of these models are highly uncertain due to the many stellar modeling uncertainties.
+While there are many stellar models providing predictions of \cc{} yields, the results of these models are highly uncertain due to the complexity of stellar modeling.
 
@@
 Both the \citet{NKT13} and \cite{LC18} models show positive metallicity dependence. 
-The \cite{LC18} models also include rotation, showing that variations in the rotational velocity of the star can dramatically increase the magnitude and metallicity dependence of $\Ycc$.
-Rotation induces more mixing allowing the CO core to grow larger.
-As we will later show, \cc\ C production needs to be strongly metallicity-dependent at $Z/Z_\odot \approx 1$, which is consistent with the \cite{LC18} rapidly rotating models.
-
+As metallicity increases, stars lose more of their mass to winds.
+In particular, C enriched envelop material is lost through winds before synthesized into heavier elements, so C yields can be strongly metallicity dependent (VERIFY).
 Fig.~\ref{fig:y_cc} shows the \cxi{} \agb\ model for comparison on the left.
@@
 Later, we will also show empirically this is the case.
-On the right of Fig.~\ref{fig:y_cc}, we also show the \cc{} [C/Mg] ratio, defined by
+The right of Fig.~\ref{fig:y_cc} shows the \cc{} [C/Mg] ratio for the different models, defined by
 \begin{equation}\label{eq:c_mg_cc}
@@
 If only \cc{} produced C, then ${\rm [C/Mg]^{CC}}$ describes the equilibrium abundance of [C/Mg].
-Once again, different \cc\ models span a large range in [C/Mg]. 
-we chose to instead parameterize $\Ycc$ to enable agreement with observations, as most \cc\ models fail to achieve near-solar [C/Mg].
+Different \cc\ models also span a large range in [C/Mg]. 
+We chose to instead parameterize $\Ycc$ to simplify model inputs, as most \cc\ models fail to achieve near-solar [C/Mg].
+
+Both rotation and explodability introduce substantial variations.
+The \cite{LC18} models include rotation, showing that variations in the rotational velocity of the star can dramatically increase the magnitude and metallicity dependence of $\Ycc$.
+Rotation induces more mixing allowing the CO core to grow larger and contributes to wind losses.
+As we will later show, \cc\ C production needs to be strongly metallicity-dependent at $Z/Z_\odot \approx 1$, which is consistent with the \cite{LC18} rapidly rotating models.
 Assumptions about the explodability landscape affect C and Mg production.
@@
 
-\cc\ models do not reach [O/Mg] due to overproduction of O or underproduction of Mg, or both \citep{emily+21}.
-Here, we assume ${\rm [O/Mg]} = 0$, which is not compatible with \cc\ models but is consistent with \apogee{} observations \citep{weinberg+19, weinberg+22}.
-
-Out model predictions of [C/Mg] and [C/H] are identical. There is a slight slope in [O/Mg] with metallicity, so this could add a systematic to our model.
-
+O and Mg are both $\alpha$-elements, light elements produced in \cc{} through He-nuclei fusion. 
 As we focus on constraining relative yields, we neglect O and Mg yield variations in the main text (excluding the uniform scaling of yields and massloading in Section~\ref{sec:outflows}).
@@
 Most models predict relatively flat trends metallicity (even with rotation as in \citealt{LC18}). 
-However, the variation is significant and our adopted $\Yoc$ yield is much higher than most models.
-This is a known problem (see \citealt{emily+21}).
-\cc\ models underpredict $[{\rm Mg}/{\rm O}]$, and the reason why is unknown.
+However, the variation is significant and our adopted $\Yoc$ yield is much higher than most models, but O and Mg yields of \cc\ models do not fully match observations.
+\cc\ models underpredict $[{\rm Mg}/{\rm O}]$, and the reason why is unknown (see e.g.
+\citealt{emily+21}).
+Here, we assume ${\rm [O/Mg]} = 0$, which is not compatible with \cc\ models but is consistent with \apogee{} observations \citep{weinberg+19, weinberg+22}.
+Because O and Mg are not perfectly identical in \apogee{}, the specific choice of $\alpha$-element may be a possible systematic.
 
@@
     In the top panel, the pink line denotes $\Ycagb$ from \cxi{} for comparison. All models include wind yields. 
+    (OUT OF DATE)
 }
@@
 
-\section{The Equilibrium Approximation}\label{sec:equilibrium}
-
-In the presence of metal-poor gas accretion and feedback-driven outflows, galaxies reach an equilibrium abundance in which production of new metals is balanced by losses to new stars and outflows \citep{larson72, dalcanton07, FD08, PS11, lilly13}.
+\section{Analytic Approximations}
+In this section, we describe approximations of galactic abundance trends and C yield models.
+While these are insufficient to describe the galaxy in full detail, we can use these simplified models to inform our investigation.
+
+\subsection{Equilibrium Abundances}\label{sec:equilibrium}
+
+Galaxies, when moderated by metal-poor gas accretion and feedback-driven outflows, reach a chemical equilibrium.
+The production of new metals is balanced by losses to new stars and outflows \citep{larson72, dalcanton07, FD08, PS11, lilly13}.
 While our galaxy is likely not in perfect equilibrium or described by a single, homogeneous chemical
@@
 
-We assume a simple \textit{one-zone} chemical evolution model \cite[e.g.][]{tinsley80, pagel09, matteucci21}.
-Newly produced metals are homogeneously and instantaneously mixed, so spatial dependence is neglected.
+Here, we assume a simple \textit{one-zone} chemical evolution model \cite[e.g.][]{tinsley80, pagel09, matteucci21}.
+Newly produced metals are homogeneously and instantaneously mixed, so this model evolves as a single, spatially-uniform chemical zone.
 We define $M_{X}$ to be the mass of element $X$ in the gas-phase, $\dot{M}_\star$ to be the star formation rate (in $\Mo\,{\rm yr}^{-1}$), and $\eta$ to be the mass loading factor $\eta\equiv\dot{M}_{\rm outflow}/\dot{M}_\star$ (representing the strength of outflows).
-A \ssp\ returns a fraction $r$ of their birth mass to the interstellar medium, due to ejected stellar envelopes.\footnotemark{}
+A \ssp\ returns a fraction $r$ of their birth mass to the interstellar medium, due to ejected stellar envelopes.%
+\footnote{$r\approx0.4$ for a \citealt{kroupa01} \imf.}
 Here, we will use $\alpha$ as a representative $\alpha$-element, such as O or Mg. 
 Given the \imf-averaged yield $y_\alpha$, the rate of change in the gas-phase mass of $\alpha$ is a simple sum of sources and sinks,
-\begin{equation}
+\begin{equation} \label{eq:mdot_1}
     \dot{M}_\alpha =  y_\alpha\,\dot{M}_\star - \dot{M}_{\alpha,\,\text{remnants}} - \dot{M}_{\alpha,\,\text{outflows}}
@@
 And, the outflows deplete mass at a rate $Z_\alpha \,\dot{M}_\star\,\eta$.
-(We assume the composition of outflows is the same as the interstellar medium.) Substituting for $\eta$ and $r$,
+(We assume the composition of outflows is the same as the interstellar medium.) With these definitions, Eq.~\ref{eq:mdot_1} is
 \begin{equation}
@@
 
-Likewise, for \agb\ stars,%
+Likewise, for C production, where both \agb\ stars and \cc\ play a role,%
 \footnote{In detail, the \agb\ contribution requires integration over the \sfh\ to account for the finite lifetimes of stars.
@@
 \end{equation}
-And the equilibrium C/$\alpha$ abundance ratio is
+The equilibrium C/$\alpha$ abundance ratio is then
 \begin{equation}\label{eq:z_co}
@@
 This argument can also be inverted to infer  yields from abundance ratio trends.
-To the extent that observed C and $\alpha$ trends reflect the equilibrium abundances in different Galactic regions, we can infer the \cc\ yield given an assumed \agb\ star yield (or vice versa).
-Inferring $\Ycc$ from $\Ycagb$,
-\begin{equation}
-    y_\text{C}^\alpha =  y_\alpha^\text{CC} \frac{Z_\text{C,\,eq}}{Z_{\alpha,\,{\rm eq}}} - \Ycagb
-\end{equation}
-Rewriting this expression as a relative yield of C and Mg,
+To the extent that observed C and $\alpha$ trends reflect the equilibrium abundances in different Galactic regions, we can infer the total C yield.
 \begin{equation}\label{eq:y_c_eq}
-    \frac{\Ycc}{y_\alpha} = \left(\frac{Z_{\text{C}}}{Z_{\alpha}}\right)_\odot 10^{[{\rm C}/\alpha]} - \frac{\Ycagb}{y_\alpha}.
-\end{equation}
-
-\footnotetext{$r\approx0.4$ for a \citealt{kroupa01} \imf.}
-
-\subsection{Analytic Yield Models}
-
-As we will discuss in Section \ref{sec:outflows}, the normalization of yields and $\eta$ is degenerate.
-This can be observed in Eq.~\ref{eq:z_co}, where changes in $\eta$ or the scaling of $y_{\rm C}/y_{\rm Mg}$ would not affect equilibrium trends.
-Furthermore, in Eq.~\ref{eq:z_eq}, an increase in both $y_{\rm Mg}$ and $\eta$ would leave $Z_{\rm Mg}^{\rm eq}$ unchanged.
-Our models here are unable to distinguish the overall scaling of yields and outflow mass loading.
-Choosing to keep $y_{\rm C}$ fixed reduces unnecessary free parameters.
-So, at solar metallicity, we set
-\begin{subequations}
+    \Ycc + \Ycagb =  y_\alpha \left(\frac{Z_{\rm C}}{Z_{\alpha}}\right)_\odot 10^{[{\rm C}/\alpha]}.
+\end{equation}
+As we know [C/$\alpha$] as a function of metallicity, Eq.~\ref{eq:y_c_eq} enables us to estimate both the magnitude and metallicity-dependence of $\Yct/y_\alpha$.
+In Fig.~\ref{fig:analytic}, we show the inferred total C yields, based on this equation, and our best fitting linear model. From a linear regression, we suggest that
+\begin{subequations}\label{eq:yc_inferred}
     \begin{align}
-        \Yct(\Zo) &= \Ycc + \Ycagb = 0.005 \\
-        \left(\frac{\Yct}{\Yoc}\right)_{\Zo} &= 2.7.
+        \frac{\Yct(Z)}{y_{\rm O}} &\approx \frac{1}{3} + 4 \left(Z-\Zo\right) \\
+        \frac{\Yct(Z)}{y_{\rm Mg}} &\approx 2.7 + 32 \left(Z-\Zo\right).
     \end{align}
 \end{subequations}
-This ratio results in an equilibrium abundance ${\rm [C/Mg]} = -0.09$, which is consistent with the subgiant sample and is within \about{20\%} of the solar C/Mg mixture from \citet{asplund+09}.
+These yield ratios results in an equilibrium abundance $[{\rm C}/\alpha] = -0.09$, which is consistent with the subgiant sample and is within \about{20\%} of the solar C/Mg mixture from \citet{asplund+09}.
+
+\subsection{Analytic AGB}
 
 In Section \ref{sec:agb_results}, we will show that none of the four \agb\ yield sets (\cxi{}, \kx{}, \vxiii{}, \kxvi{}) produce enough C relative to this $\Ycc$ value.
-So, we introduce normalization factors, $\alpha_{\rm agb}$, and $\alpha_{\rm CC}$ which denote a multiplicative scaling of $\Ycc$ and $\Ycagb$ respectively.
-\begin{subequations} \label{eq:alpha}
-    \begin{align}
-        \Ycagb &\rightarrow \alpha_{\rm agb}\ \Ycagb \\
-        \Ycc &\rightarrow \alpha_{\rm cc}\ \Ycc\\
-        \alpha_{\rm CC} &= \frac{\Yct - \alpha_{\rm agb}\ \Ycagb}{\Ycc}
-    \end{align}
-\end{subequations}
-Above, $\alpha_{\rm cc}$ is dependent on the choice of $\alpha_{\rm agb}$ to keep the total C yield constant.
-
-In Section \ref{sec:agb_results}, we find that $\alpha_{\rm agb}\approx 2.9$ for the \cxi{} yield model.
-Using this \agb\ yield, we can now use Eq.~\ref{eq:y_c_eq} to find an estimate of $\Ycc$ as a function of metallicity.
-We show the values of $\Ycc$ we obtain from the subgiant sample in Fig.~\ref{fig:analytic}.
-From a regression analysis, we suggest here that
-\begin{equation}\label{eq:zeta}
-    \Ycc = 0.004 \left(1 - \zeta + \zeta\,\frac{2Z}{Z + Z_\odot} + \frac{2\xi}{1 + Z/Z_{\rm III}}\right),
-\end{equation}
-where $\zeta\approx0.001$ describes the metallicity dependence.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\columnwidth]{analytic.pdf}
-    \caption[Reverse-Fit Yields]{Inferred high-mass star C yields as a function of metallicity.
-We assume equilibrium and $3\times {\rm C11}$ \agb\ yields (orange curve, see discussion in Section \ref{sec:equilibrium}).
-Blue points are the median value of $\Ycc$ for each bin in [Mg/H] with uncertainties based on the median absolute deviation.
-    }
-    \label{fig:analytic}
-\end{figure}
+So, we introduce a normalization factor $\alpha_{\rm agb}$, which denotes a multiplicative scaling of $\Ycagb$
+\begin{equation} \label{eq:alpha}
+        \Ycagb \rightarrow \alpha_{\rm agb}\ \Ycagb.
+\end{equation}
+To parameterize the \agb\ contribution to C production, we define $f_{\rm agb}$ to be the fraction of C which comes from \agb\ stars. 
+\begin{equation}\label{eq:f_agb}
+    f_{\rm agb} \equiv \frac{\Ycagb(Z=\Zo)}{\Yct(Z=\Zo)},
+\end{equation}
+($f_{\rm agb}$ accounts for the multiplicative factor $\alpha_{\rm agb}$ as defined in Eq.~\ref{eq:alpha}).
+
+We can use the \caafe{} diagram of \apogee\ stars to estimate the delayed portion of C.
+When binned in metallicity, median [C/Mg] changes by about 0.25 dex across the range of [Mg/Fe].
+As high-$\alpha$ stars have little to no delayed \ia\ Fe, these stars would also have little to no delayed \agb\ C.
+This means that AGB C stars make up about at most a fraction $f_{\rm agb} \approx 1 - 10^{-0.25} \approx 0.6$ of C production.
 
@@
 \begin{equation}
-    \y_{\rm C}^{\rm agb}(m, Z) = \frac{\y(m) \left[\y_1 + \zeta \log_{10}(Z/Z_\odot) \right]}{\int_1^8 m\,\y(m)\,{\rm IMF}(m)\;dm}
-\end{equation}
-
-\subsection{Delayed C}
-To parameterize the \agb\ contribution to C production, we define $f_{\rm agb}$ to be the fraction of C which comes from \agb\ stars. 
-\begin{equation}\label{eq:f_agb}
-    f_{\rm agb} \equiv \frac{\Ycagb(Z=\Zo)}{\Yct(Z=\Zo)},
-\end{equation}
-($\Ycagb$ includes the multiplicative factor $\alpha_{\rm agb}$ as defined in Eq.~\ref{eq:alpha}).
-
-We can use the \caafe{} diagram of \apogee\ stars to estimate the delayed portion of C.
-When binned in metallicity, median [C/Mg] changes by about 0.25 dex across the range of [Mg/Fe].
-As high-$\alpha$ stars have little to no delayed \ia\ Fe, these stars would also have little to no delayed \agb\ C.
-This means that AGB C stars make up about at most a fraction $f_{\rm agb} \approx 1 - 10^{-0.25} \approx 0.6$ of C production.
+    \y_{\rm C}^{\rm agb}(m, Z) = \frac{\y(m)}{\int_1^8 m\,\y(m)\,{\rm IMF}(m)\;dm} 
+    \left(\y_1 + \zeta \left(Z-\Zo\right) \right)
+\end{equation}
+
+\subsection{CCSNe Carbon Yields}
+With the total C yield of Eq.~\ref{eq:yc_inferred} and given an \agb\ C yield, we can derive an observationally-consistant \cc\ C yield.
+\begin{subequations}
+    \begin{gather}
+        \Ycc(\Zo) = \Yct(\Zo) - \Ycagb(\Zo)\\
+        \zeta^{\rm cc} \equiv \frac{d\Ycc(\Zo)}{dZ} = \frac{d\Yct(\Zo)}{dZ} - \frac{d\Ycagb(\Zo)}{dZ}
+    \end{gather}
+\end{subequations}
+
+Furthermore, we can assert that the slope, $d \Yct / dZ$ at solar metallicity is consistant. We find from Fig.~\ref{fig:analytic} that
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{analytic.pdf}
+    \caption[Reverse-Fit Yields]{Inferred high-mass star C yields as a function of metallicity.
+We assume equilibrium and $3\times {\rm C11}$ \agb\ yields (orange curve, see discussion in Section \ref{sec:equilibrium}).
+Blue points are the median value of $\Ycc$ for each bin in [Mg/H] with uncertainties based on the 16-84 percentile range.
+    }
+    \label{fig:analytic}
+\end{figure}
+
+\begin{equation}\label{eq:zeta}
+    \Ycc = y_0 + \zeta\,(Z-\Zo) + \frac{2\,y_{\rm III}}{1 + Z/Z_{\rm III}},
+\end{equation}
+where $\zeta\approx0.001$ describes the metallicity dependence.
+
+\begin{table}
+	\centering
+    \caption[]{For each \agb\ yield set, the \imf-averaged \agb\ C yield at solar metallicity $y_{\rm C, 0}^{\rm agb}$ and the multiplicative factor reaches an \agb\ contribution of 20\% $\alpha_{\rm agb, 20}$.
+<UPDATE>}
+	\label{tab:alpha_agb}
+	\begin{tabular}{cccr} % four columns, alignment for each
+		\hline 
+    \agb\ Model & $y_{\rm C}^{\rm agb}(\Zo)$ & $\zeta^{\rm agb}(\Zo)$ 
+                & $\alpha_{20}^{\rm agb}$\\
+        \hline
+        \cxi & 4.2E-4 & -0.022 & 2.9\\
+        \kx & 6.5E-4 & -0.063 & 1.7\\
+        \vxiii & 4.9E-4 & -0.032 & 16.5\\
+        \kxvi & 5.6E-4 & -0.034 & 2.4\\
+		\hline
+	\end{tabular}
+\end{table}
 
@@
 Further exploration could investigate the magnitude of these uncertainties, but we find that the qualitative conclusions are similar despite substantial variations in the assumptions here.
+
+As we will discuss in Section \ref{sec:outflows}, the normalization of yields and $\eta$ is degenerate.
+This can be observed in Eq.~\ref{eq:z_co}, where changes in $\eta$ or the scaling of $y_{\rm C}/y_{\rm Mg}$ would not affect equilibrium trends.
+Furthermore, in Eq.~\ref{eq:z_eq}, an increase in both $y_{\rm Mg}$ and $\eta$ would leave $Z_{\rm Mg}^{\rm eq}$ unchanged.
+Our models here are unable to distinguish the overall scaling of yields and outflow mass loading.
+Choosing to keep $y_{\rm C}$ fixed reduces unnecessary free parameters.
+So, at solar metallicity, we set
 
@@
 The fiducial model has the following qualitative characteristics of its C yields.
-\begin{enumerate}
+\begin{description}
     \item C is mostly (\about{80\%}) produced in \cc
@@
     \item \agb\ stars produce less C at higher metallicities 
-\end{enumerate} 
+\end{description} 
 The fiducial model uses the \cxi{} \agb\ yield tables uniformly scaled by a factor of 2.9 (see Section \ref{sec:agb}, and Table \ref{tab:fiducial_mod}).
@@
 \includegraphics{all_the_tracks.pdf}
-\includegraphics{coofe_tracks.pdf}
 \caption[Carbon Chemical Evolution Tracks]{
@@
 \begin{figure*}
-\includegraphics[height=2in, width=6in]{beta.pdf}
+\includegraphics{zeta.pdf}
 
@@
 \centering
-\includegraphics[height=2in, width=6in]{agb_oob.pdf}
+\includegraphics{caah_agbs.pdf}
+\includegraphics{caah_indifferent.pdf}
 
@@
 
-\begin{table}
-	\centering
-    \caption[Low-Mass Stellar Carbon Yields at Solar Metallicity]{For each \agb\ yield set, the \imf-averaged \agb\ C yield at solar metallicity $y_{\rm C, 0}^{\rm agb}$ and the multiplicative factor reaches an \agb\ contribution of 20\% $\alpha_{\rm agb, 20}$.}
-	\label{tab:alpha_agb}
-	\begin{tabular}{cccr} % four columns, alignment for each
-		\hline 
-        \agb\ Model & $y_{\rm C}^{\rm agb}(\Zo)$ & $d \Ycagb(\Zo)/dZ$ 
-                    & $\alpha_{\rm agb, 20}$\\
-        \hline
-        \cxi & 0.000418 & -0.022 & 2.9\\
-        \kx & 0.00065 & -0.063 & 1.7\\
-        \vxiii & 0.00049 & -0.032 & 16.5\\
-        \kxvi & 0.00056 & -0.034 & 2.4\\
-		\hline
-	\end{tabular}
-\end{table}
-
-\begin{figure*}
-\centering
-\includegraphics[height=2in, width=6in]{f_agb.pdf}
-
-\caption[Adjusted Yield Models]{Similar to Fig.~\ref{fig:first_models}, except where the \agb\ C contribution is varied from the fiducial ($f_{\rm agb}=0.2$) to 0.1 and 0.3 (see Eq.~\ref{eq:f_agb} and Section.~\ref{sec:agb_results}.}
+\begin{figure}
+\centering
+\includegraphics{caafe_agbs.pdf}
+
+\caption[]{Similar to Fig.~\ref{fig:first_models}, except where the \agb\ C contribution is varied from the fiducial ($f_{\rm agb}=0.2$) to 0.1 and 0.3 (see Eq.~\ref{eq:f_agb} and Section.~\ref{sec:agb_results}.}
+\label{fig:caafe_agbs}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{caafe_fagb.pdf}
+
+\caption[]{Similar to Fig.~\ref{fig:first_models}, except where the \agb\ C contribution is varied from the fiducial ($f_{\rm agb}=0.2$) to 0.1 and 0.3 (see Eq.~\ref{eq:f_agb} and Section.~\ref{sec:agb_results}.}
 \label{fig:f_agb}
-\end{figure*}
+\end{figure}
 
@@
 
-\begin{figure*}
-\centering
-\includegraphics[height=2in, width=6in]{lateburst_eta.pdf}
+\begin{figure}
+\centering
+\includegraphics{caafe_sfh.pdf}
 
@@
 \label{fig:sfh_models}
-\end{figure*}
+\end{figure}
 
@@
 
-\begin{figure*}
-    \centering
-    \includegraphics[height=2in, width=6in]{eta.pdf}
+\begin{figure}
+    \centering
+    \includegraphics{caafe_eta.pdf}
     \caption[Reduced-Outflow Models]{Similar to Fig.~\ref{fig:first_models} but comparing the fiducial model to reduced mass loading models (see Section  \ref{sec:outflows}).
@@
     \label{fig:eta}
-\end{figure*}
+\end{figure}
 
@@
 DISCUSSION ABOUT SINGLE ZONE
+$\eta=6$, $\tau_{\star}=9\,{\rm Gyr}$, ${\rm SFH} = e^{-t/2{\rm\,Gyr}}$.
 
@@
     \centering
-    \includegraphics[height=2in, width=6in]{nitrogen.pdf}
+    \includegraphics{nitrogen.pdf}
     \caption[C/N Abundance Agreement]{Similar to Fig.~\ref{fig:first_models}, except comparing [C/N] from the fiducial model only.
@@
     and Milky Way high-$\alpha$ stars (yellow points; \citealtjack).
+    (OUT OF DATE)
 }

### 2023-07-11 carbon_paper/tex/main.tex
new draft

@@
 \usepackage{newtxtext,newtxmath}
+\usepackage{anyfontsize}
 % Depending on your LaTeX fonts installation, you might get better results with one of these:
@@
 \newcommand{\imf}{IMF}
-\newcommand{\sfh}{SFH}
+\newcommand{\sfh}{SFH} % check where first defined
 \newcommand{\ssp}{SSP}
@@
 Third Author$^{2,3}$
-and Fourth Author$^{3}$
+and Others$^{1,3}$
 \\
@@
 % misc
-Our models are relatively independent of uniform scaling of yields and outflows, alternate \sfh{}s. 
+Our models are relatively independent of uniform scaling of yields and outflows, and alternate star formation histories. 
 However, the stars which contribute to \agb\ C production and the \ia\ delay time distribution of Fe contribute uncertainties to our conclusions. 
@@
 Here, we extend their models to C, deriving similar constraints on C/Mg yields.
-We assess which yield prescriptions reproduce Galactic abundance trends while investigating the impact of \gce{} model assumptions, such as \sfh{} and outflow mass loading.
+We assess which yield prescriptions reproduce Galactic abundance trends while investigating the impact of \gce{} model assumptions, such as the star formation history (\sfh{}) and outflow mass loading.
 
@@
     \includegraphics{subgiants.pdf}
-    \caption[Subgiant Abundances]{The [C/Mg] ratio against [Mg/H] (top) and [Mg/Fe] (bottom) for the \citetjack~sample of \apogee{} subgiants.
+    \caption{The [C/Mg] ratio against [Mg/H] (top) and [Mg/Fe] (bottom) for the \citetjack~sample of \apogee{} subgiants.
 On the top, we plot high and low-$\alpha$ stars in blue and orange, using the separation defined in Equation \ref{eq:high_alpha} (the high and low-$\alpha$ stars are named for their high or low $\alpha$-element to Fe ratios, or in this case, Mg/Fe).
@@
 	\centering
-    \caption[Fiducial Model Yields]{Yields for the fiducial model (in units of \ssp~birth mass). See Section \ref{sec:agb} for the definition of \cxi.}
+    \caption[]{Yields for the fiducial model (in units of \ssp~birth mass). See Section \ref{sec:agb} for the definition of \cxi.}
 	\label{tab:fiducial_mod}
@@
 \end{equation}
-Assuming an exponentially declining \sfh{} $\dot{M}_\star \propto e^{-t/\tau_{\rm sfh}}$, the equilibrium abundance is derived analytically by setting $\dot{Z}_\alpha=0$.
+Assuming an exponentially declining star formation history (\sfh{}) $\dot{M}_\star \propto e^{-t/\tau_{\rm sfh}}$, the equilibrium abundance is derived analytically by setting $\dot{Z}_\alpha=0$.
 \begin{equation}\label{eq:z_eq}
@@
 
+\begin{figure}
+    \centering
+    \includegraphics{analytic.pdf}
+    \caption[]{Inferred high-mass star C yields as a function of metallicity.
+We assume equilibrium and $3\times {\rm C11}$ \agb\ yields (orange curve, see discussion in Section \ref{sec:equilibrium}).
+Blue points are the median value of $\Ycc$ for each bin in [Mg/H] with uncertainties based on the 16-84 percentile range.
+    }
+    \label{fig:analytic}
+\end{figure}
+
 \subsection{Analytic AGB}
 
-In Section \ref{sec:agb_results}, we will show that none of the four \agb\ yield sets (\cxi{}, \kx{}, \vxiii{}, \kxvi{}) produce enough C relative to this $\Ycc$ value.
+To parameterize the \agb\ contribution to C production, we define $f_{\rm agb}$ to be the fraction of C which comes from \agb\ stars. 
+\begin{equation}\label{eq:f_agb}
+    f_{\rm agb} \equiv \frac{\Ycagb(Z=\Zo)}{\Yct(Z=\Zo)},
+\end{equation}
+In Section \ref{sec:agb_results}, we will show that $f_{\rm agb} \approx 0.2$. 
+None of the \agb\ yield sets (\cxi{}, \kx{}, \vxiii{}, \kxvi{}) produce enough C relative to our total $\Ycc$ values.
 So, we introduce a normalization factor $\alpha_{\rm agb}$, which denotes a multiplicative scaling of $\Ycagb$
@@
 \end{equation}
-To parameterize the \agb\ contribution to C production, we define $f_{\rm agb}$ to be the fraction of C which comes from \agb\ stars. 
-\begin{equation}\label{eq:f_agb}
-    f_{\rm agb} \equiv \frac{\Ycagb(Z=\Zo)}{\Yct(Z=\Zo)},
-\end{equation}
-($f_{\rm agb}$ accounts for the multiplicative factor $\alpha_{\rm agb}$ as defined in Eq.~\ref{eq:alpha}).
+Table~\ref{tab:alpha_agb} contains the required values of $\alpha_{\rm agb}$ to reach $f_{\rm agb}=0.2$, the yields at solar metallicity, and the metallicity for each \agb\ yield set.
 
@@
 \end{subequations}
-
-Furthermore, we can assert that the slope, $d \Yct / dZ$ at solar metallicity is consistant. We find from Fig.~\ref{fig:analytic} that
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\columnwidth]{analytic.pdf}
-    \caption[Reverse-Fit Yields]{Inferred high-mass star C yields as a function of metallicity.
-We assume equilibrium and $3\times {\rm C11}$ \agb\ yields (orange curve, see discussion in Section \ref{sec:equilibrium}).
-Blue points are the median value of $\Ycc$ for each bin in [Mg/H] with uncertainties based on the 16-84 percentile range.
-    }
-    \label{fig:analytic}
-\end{figure}
-
+This method reduces the number of free parameters of the model and enables all models to match \caah\ trends in \apogee{} subgiants when considering \agb\ yields with different metallicity dependences and normalizations.
+Table~\ref{tab:alpha_agb} contains our adaptive (regression-derived) values of $\zeta^{\rm agb}$ and $\Ycagb(\Zo)$.
+Table~\ref{tab:alpha_agb} also shows $\alpha^{\rm agb}_{20}$, the value of $\alpha^{\rm agb}$ required with our adopted total yields (Eq.~\ref{eq:yc_inferred}) to reach 20\% \agb\ C.
+
+Our full \cc\ C yield model adds a low-metallicity enhancement term, which is insignificant at solar metallicities (e.g.
+thin disk stars) but enables models in Section~\ref{sec:gas} to match low-metallicity environments.
+All-together, 
 \begin{equation}\label{eq:zeta}
-    \Ycc = y_0 + \zeta\,(Z-\Zo) + \frac{2\,y_{\rm III}}{1 + Z/Z_{\rm III}},
-\end{equation}
-where $\zeta\approx0.001$ describes the metallicity dependence.
+    \Ycc = y_{\rm C, 0}^{\rm cc} + \zeta^{\rm cc}\,(Z-\Zo) + \frac{2\,y_{\rm III}}{1 + Z/Z_{\rm III}}.
+\end{equation}
 
@@
 
-Our model is as follows.
+Star formation is treaded as follows.
 The Galaxy is divided into 200 rings, each 100\,pc wide.
@@
 Star formation ends beyond a radius $R=15.5\,$kpc.
-The gas inflow is calculated to maintain our chosen \sfh{} for each radius and time, using an extension of a Kennicutt-Schmidt law \citep{kennicutt98},
+The gas inflow is calculated to maintain the \sfh{} for each radius and time, using an extension of a Kennicutt-Schmidt law \citep{kennicutt98},
 \begin{equation}
@@
 Subgiants provide the ideal observational constraint to our model. 
-Since first dredge up changes C surface abundances in evolved stars, these stars require model-dependent corrections to recover surface abundances \citep[e.g.][]{vincenzo+21}.
+When a star enters the Red Giant Branch (RGB), material from the CNO-processed core is mixed with the envelope in first dredge up, enhancing N and depleting C \citep{iben67, vincenzo+21,KL14}.
+RGB stars thus require model-dependent corrections to recover surface abundances \citep[e.g.][]{vincenzo+21}.
 On the other hand, gravitational settling can affect main sequence stellar abundances \citep[e.g.][]{souto19}.
@@
     \item \cc\ initially dominate production. As $\Ycc$ has strong metallicity dependence, [C/Mg] increases with time. 
-    \item \agb stars contribute delayed C, causing [C/Mg] to increase even faster with [Mg/H]. 
-    \item[(iii)] [C/Mg] plateaus as C also approaches equilibrium. 
-    \item[(iv)] [C/Mg] may decrease due to declining SFH or slightly negative yields from \about{1}\,\Mo stars.
+    \item \agb\ stars contribute delayed C, causing [C/Mg] to increase even faster with [Mg/H]. 
+    \item{} [C/Mg] plateaus as C also approaches equilibrium. 
+    \item{} [C/Mg] may decrease due to declining SFH or slightly negative yields from \about{1}\,\Mo stars.
 
@@
 \includegraphics{all_the_tracks.pdf}
-\caption[Carbon Chemical Evolution Tracks]{
+\caption[]{
     Time evolution of gas-phase C abundances in our fiducial model.
@@
 The lines are coloured-coded by time.
-The top shows \caah\ and the bottom \caafe.
+The left shows \caah\ and the right \caafe.
 We artificially restrict the axis range in each case to better see solar-annulus and present-day evolution.
+    <UPDATE, CHECK LEFT?RIGHT USAGE>
 }
@@
 
-\subsection{High-mass stellar yields}\label{sec:results_highmass}
-\cc, which likely make up the majority of C, set the overal C abundances. 
- and the \cc\ metallicity dependence $\zeta$ in Fig.~\ref{fig:first_models}.
+\subsection{High-Mass Stellar Yields}\label{sec:results_highmass}
+
+\cc, which likely make up the majority of C, set the overall C abundance trends.
  Fig.~\ref{fig:first_models} shows models with varying $\Ycc$ metallicity dependence.
-As the \caah~trend is approximated by the equilibrium C/Mg abundance with metallicity, the models with stronger metallicity dependence have a stronger slope in \caah.
-However, \caafe~is minimally affected by these changes since \cc\ occurs on much shorter timescales than \ia\ and \agb\ enrichment, and we only consider stars in a small metallicity range for \caafe.
+As the \caah~trend is approximated by equilibrium trends, the models with stronger metallicity dependence have a stronger slope in \caah.
+ However, \caafe~is minimally affected by these changes since \cc\ occurs on much shorter timescales than \ia\ and \agb\ enrichment.
+The only effects on \caafe, when considering the narrow metallicity slice, are because of either the slight change in equilibrium abundances, the imperfect evolution of the galaxy, or that the interstellar medium abundances are set by stars which were born at poorer metallicities.
+ Hence, \caah\ tells us about the total C yield with metallicity, which \caafe\ is independent of.
+If we know the \agb\ C yields, then with observed \caafe\ abundance trends, we can infer the \cc\ C yields with metallicity.
 
 \begin{figure*}
-\includegraphics{zeta.pdf}
-
-\caption[Median Stellar Abundance Trends]{
+\includegraphics{all_p1.pdf}
+
+\caption[]{
     Stellar abundance trends in our model, assuming metallicity independent $\Ycc$.
@@
 
-\subsection{Low mass stellar yields}\label{sec:agb_results}
-
-Fig.~\ref{fig:agb_sims} compares the \kx{}, \kxvi{}, \cxi{}, and \vxiii{} yield models.
-As the highest \agb\ yield at solar, \kx{} is only $\Ycagb=0.000585$, so $f_{\rm agb} \leq 0.12$ for all models.
-Massive stars dominate C production with unscaled yields.  
-With the exception of \vxiii, the different \agb\ models only affect the overall metallicity dependence (in \caah).
-We leave a more detailed discussion of the effects of \agb\ models for Appendix~\ref{sec:oob_models} and use \cxi{} (OR ANALYTIC?) yields hereafter.
-
-\begin{figure*}
-\centering
-\includegraphics{caah_agbs.pdf}
-\includegraphics{caah_indifferent.pdf}
-
-\caption[]{Similar to Fig.~\ref{fig:first_models}, except where each line corresponds to one of our four \agb\ yield sets (\cxi, \kx, \vxiii, \kxvi).}
-\label{fig:agb_sims}
-\end{figure*}
+\subsection{Low-Mass Stellar Yields}\label{sec:agb_results}
+
+\caafe\ is sensitive to the assumptions about delayed C from \agb\ stars.
+If no C comes from low-mass stars, then [C/Mg] would be independent of [Mg/Fe], only [Mg/H].
+Instead, C shows strong trends  in \caafe\, independent of metallicity.
+
+In Fig.
+<REF>, we first show the four C yield models (\kx, \kxvi, \cxi, \vxiii).
+For the most part, the \agb\ yield sets result in qualitatively similar predictions.
+\vxiii, however, does not reproduce solar trends as the model predicts strong C production at slightly above solar metallicities, resulting in a decreasing [C/Mg] with [Fe/Mg].
+As all \agb\ models predict some low-mass C destruction, each model does predict a downturn in [C/Mg] as [Fe/Mg] increases.
+A recent burst in star formation may hide this downturn (see NEXT SECTION), but the C destruction is not supported directly by observations.
 
@@
 
-FIGUREEE
-
-\begin{figure}
-\centering
-\includegraphics{caafe_agbs.pdf}
+\begin{figure*}
+\centering
+\includegraphics{all_p2.pdf}
 
@@
 \label{fig:caafe_agbs}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{caafe_fagb.pdf}
-
-\caption[]{Similar to Fig.~\ref{fig:first_models}, except where the \agb\ C contribution is varied from the fiducial ($f_{\rm agb}=0.2$) to 0.1 and 0.3 (see Eq.~\ref{eq:f_agb} and Section.~\ref{sec:agb_results}.}
-\label{fig:f_agb}
-\end{figure}
+\end{figure*}
 
@@
 Our lateburst model adds a Gaussian factor to the inside-out \sfh{},
-\begin{equation}\label{eq:late-burst}
+\begin{equation}\label{eq:lateburst}
     \dot{\Sigma}_\text{lateburst} \propto \dot{\Sigma}_\text{inside-out} \left(1 + A\,e^{-(t-\tau_{\rm burst})^2/2\sigma^2_{\rm burst}} \right)
@@
 where $A=1.5$ represents the amplitude of the birth, $\tau_\text{burst}=10.8$\,Gyr is the time where the burst is strongest, and $\sigma_\text{burst}=1$\,Gyr is the width of the burst.
-Our earlyburst model is similar, but the burst is exponential and placed at $t_1=5$\,Gyr. 
+Our earlyburst model instead >>>>>?????  at $t_1=5$\,Gyr. 
 \begin{equation}\label{eq:twoinfall}
-    \dot{\Sigma}_{\rm earlyburst} \propto \dot{\Sigma}_{\rm inside-out} + 
+    \dot{\Sigma}_{\rm earlyburst} \propto A\,e^{-(t-t_1)/\tau_{\rm burst}} + 
 \begin{cases}
-    A\,e^{-(t-t_1)/\tau_{\rm burst}} & t_1 < t \\
+    \left(1-e^{-t/\tau_\text{rise}}\right)e^{-t/\tau_\text{rise}} & t_1 < t \\
       0 & t<t_1
@@
 The late burst models result in [C/Mg] continuing to increase at low [Mg/Fe], but also introduce a dip not present in the data.
-Additionally, the early burst
+Additionally, the early-burst
 reproduces the slight break between the low and high $\alpha$ sequences, but overshoots equilibrium more severely than the fiducial model. 
 In general, any of these \sfh{}s are consistent with this model.
-
-\begin{figure}
-\centering
-\includegraphics{caafe_sfh.pdf}
-
-\caption{Similar to Fig.~\ref{fig:first_models} but comparing the fiducial model to alternate \sfh{}s (see Section  \ref{sec:sfh}).}
-
-\label{fig:sfh_models}
-\end{figure}
 
@@
 
-\begin{figure}
-    \centering
-    \includegraphics{caafe_eta.pdf}
-    \caption[Reduced-Outflow Models]{Similar to Fig.~\ref{fig:first_models} but comparing the fiducial model to reduced mass loading models (see Section  \ref{sec:outflows}).
-Both yields and mass-loading are adjusted correspondingly such that the equilibrium abundances are unchanged.
-}
-    \label{fig:eta}
-\end{figure}
-
 \subsection{Gas-Phase Abundances}\label{sec:gas}
+
+As a final test of the model, we compare the model predictions against gas-phase measurements.
+Fig.~\ref{fig:gas_phase} shows the fiducial model's gas-phase predictions compared to observations of the Milky Way and extragalactic HII regions, halo stars, and damped Lyman-alpha systems.
+While obervations in HII regions and Milky Way stars agree that C/O generally increases at near-solar metallicities, damped Lyman-alpha systems and metal poor stars imply that C/O may also increase again at very low metallicities.
 
@@
 Additionally, recombination and collisional excitation measurements disagree by a factor of \about{2} \citep{GR07}.
-Variations in the \sfh{}s may furthermore increase scatter, as \agb\ are a delayed source of C.
-C abundances are challenging to measure.
-When a star enters the Red Giant Branch (RGB), material from the CNO-processed core is mixed with the envelope in first dredge up, enhancing N and depleting C \citep{iben67, vincenzo+21,KL14}.
-Measurements of these evolved stars'  atmospheres will no longer reflect their birth abundances.
-Additionally, gas-phase measurements of C are extremely limited as C lacks strong lines in HII regions \citep{skillman+20}.
-
-As an additional test of the model, we next compare the model predictions against gas-phase measurements.
-Fig.~\ref{fig:gas_phase} shows the fiducial model's gas-phase predictions compared to observations of the Milky Way and extragalactic HII regions, halo stars, and damped Lyman-alpha systems.
-The model is broadly consistent with observations, where the model at $t=2$\,Gyr approximates the slope of dwarf galaxies and halo stars.
-The increase of C/O at higher metallicities is also consistent with the high C/O abundances measured in extragalactic HII regions.
-Our model does not extend to very low metallicity, where the slope of the trend inverts, but broadly explains observations above $\rm [O/H] \gtrsim -1$.
-
-Mg measurements are more reliable, but O abundances are easier to measure in HII regions.
-So while we use Mg as the representative alpha for stellar abundances, we instead use O when comparing gas-phase abundances.
-As we assume ${\rm[Mg/O]}=0$, our model is independent of the choice of the $\alpha$-element.
-
-The elevated [C/O] abundance at very-low metallicities is likely due to population III stellar yields \citep[e.g.][]{hirschi07}, as suggested by \citet{cooke+17} and \citet{FN15}.
-\agb\ stars cannot explain the increase in C yields at low metallicity in the damped Lyman-alphas sample as the evolutionary timescales of damped Lyman-alpha systems are shorter than the typical delay time distribution of \agb\ stars.
-
-DISCUSSION ABOUT SINGLE ZONE
-$\eta=6$, $\tau_{\star}=9\,{\rm Gyr}$, ${\rm SFH} = e^{-t/2{\rm\,Gyr}}$.
+While broad consistancy of our model with gas-phase measurments is nice, the large measurment errors limit the evaluative power of HII regions.
+We additionally include Milky Way thick disk (high-$\alpha$) and halo stars, which span a larger range of metallicities than thin disk stars.
+However, metal-poor abundance measurments require consideration of 3D-NLTE effects (e.g.
+CITE).
+Finally, dwarf galaxies, damped Lyman-alpha systems, and extragalactic regions may represent different \sfh{}s than the Milky Way.
+As \agb\ C production is sensitive to variations in the \sfh, these environments may not exactly match our subgiant sample, limiting the usefulness of these abundance measurments in evaluating our model.
+
+Fig.~\ref{fig:gas_phase} shows the single-zone model and time-slices of the fiducial multi-zone model at present day and $t=2$\,Gyr. 
+Here, we consider a single-zone model with parameters consistant with the Gaia-Encelidus sausage\footnotemark{}.
+We chose the model to have outflows $\eta=6$, star formation efficiency $\tau_{\star}=9\,{\rm Gyr}$, and a star formation history $\propto e^{-t/2{\rm\,Gyr}}$, evolved for 6\,Gyr.
+The single-zone model is better able to replicate the slope of the abundances in dwarf galaxies, HII-regions, and halo stars.
+The single-zone model is an evolutionary track, whereas the multi-zone models moreso show equilibrium tracks.
+As the single-zone model also evolves slower, the late contribution of AGB stars causes the steeper slope at near-solar metallicities.
+By including an increase of C yields at low-metallicity, the single-zone model is also able to reproduce the increasing [C/O] abundances with decreasing metallicity past ${\rm [O/H]} < -1.5$.
+In any case, there is large scatter in the measurments, which both models fall within.
+
+\footnotetext{See e.g.
+CITATION.
+Th Gaia-Encelidus sausage (GSE) is a kinematically and chemically distinct group of halo stars consistant with the merger of a dwarf galaxy early in the Milky Way's formation.}
 
@@
 \centering
-    \includegraphics{nitrogen.pdf}
-    \caption[C/N Abundance Agreement]{Similar to Fig.~\ref{fig:first_models}, except comparing [C/N] from the fiducial model only.
-N yields are adapted from \cite{james+23}.
-(See also Table \ref{tab:fiducial_mod}.)
-    }
-\end{figure*}
-
-\begin{figure*}
-\centering
 \includegraphics[]{summary.pdf}
-\caption[Gas-Phase Abundances]{Gas-phase C abundances. We plot our model at $t=2$\,Gyr and present day as thick solid lines. Points represent measurements in 
+\caption[]{Gas-phase C abundances. We plot our model at $t=2$\,Gyr and present day as thick solid lines. Points represent measurements in 
     HII regions    \citep[pink circles;][]{skillman+20, esteban+02, esteban+09, esteban+14, esteban+19}
@@
 
-In this work, we investigate the role of C yields on the predictions of multi-zone \gce{} models.
-
-As \cc\ C yields are poorly understood, we adopt an equilibrium approximation and determine a functional form that approximately matches trends in \apogee{} subgiant and is consistent with high-mass nucleosynthesis models.
-Variations of the metallicity dependence of this \cc\ yield affect trends in \caah~but do not affect trends in \caafe\ (when taking a slice in [Mg/H]).
-As all theoretical \agb\ C yields decrease with metallicity, increasing the \agb\ fraction causes the \caah\ trend to flatten.
-However, the \caafe\ trend is sensitive to the \agb\ fraction.
-From this, we estimate that \agb\ stars contribute \about{20\%} of total C abundance at solar metallicity.
-The remaining \about{80\%} of C comes from high-mass stars with a metallicity dependent yield of $\Ycc/\Yoc=1.51 + 0.54 (Z/Z_\odot)$.
-This metallicity dependence is roughly consistent with rotating stellar yields.
+In this work, we investigated the role of C yields on the predictions of multi-zone \gce{} models. 
+We began by adopting an equilibrium approximation to estimate the total C yields with metallicity from \apogee{} subgiant \caah{} trends.
+We find that <EQUATION>.
+We show that \caah{} is a diagnostic for total C yields with metallicity, but \caafe{} provides information about delayed C production.
+From the \caafe{} trends, we estimate that \agb\ stars contribute \about{20\%} of total C abundances, with 1--3\,\Mo the most importaint.
+In this model, the remaining \about{80\%} of C comes from high-mass stars with a metallicity dependent yield of $\Ycc/\Yoc=<\text{EQUATION}>$, broadly consistant with rotating \cc\ models.
 
@@
 We find that alternate \sfh{}s can slightly affect \caafe, but \caah~is mostly unaffected.
-Decreasing both outflows and yields by the same factor leaves the \caah~and \caafe~trends unaffected.
+Decreasing both outflows and yields by the same factor leaves the \caah~and \caafe~trends unaffected, ingoring effect to the metalliticy distribution of starrs.
 These constraints on the relative yields of C, O, and Mg are robust against variations in $\eta$.
 
-Finally, we compare our model against gas-phase measurements and metal-poor stars.
-While our model was built on data near solar metallicity, observations of very low metallicity, high redshift damped Lyman-$\alpha$ systems indicate higher C/O ratios \citep{cooke+17}, consistent with yields from population III stars \citep[e.g.][]{hirschi07}.
-Population III stars, \cc\, and \agb\ stars altogether explain the observed evolutionary history of C.
+Finally, we compare our model against gas-phase measurements and Milky Way halo stars.
+By including yields which are enhanced at low metallicities, \cc\ and \agb\ stars together are able to explain the general trends of C from metallicities of -3 to 0.5.
 
@@
 These larger samples will enable similar work to tighten constraints on stellar models and our understanding of galaxy structure and evolution.
-MAYBE MENTION METAL-POOR OR OTHER PROJECTS?
 
@@
     \includegraphics{logg_jack.pdf}
-    \caption[Subgiant Selection]{
+    \caption[]{
         A Kiel diagram of \apogee{} stars.
@@
 
+\begin{figure}
+    \centering
+    \includegraphics{apogee_caafe_binned}
+    \caption{hello}
+    \label{fig:caafe_binned}
+\end{figure}
+
 \bsp	% typesetting comment

### 2023-07-21 run.py
fixed some minor yield things

@@ -52,7 +52,7 @@ def parse_args():
                         help="use the conroy ++ 2022 sfe law")
     parser.add_argument("-m", "--agb_model", default="C11", 
                         help="the name of the AGB model to use ")
-    parser.add_argument("-M", "--migration_mode", default="diffusion", 
+    parser.add_argument("-M", "--migration_mode", default="rand_walk", 
                         help="""The migration mode. Default is diffusion.
                         Acceptable options include post-process, linear, 
                         sudden, and rand_walk""")

### 2023-07-21 submit.sh

@@ -12,7 +12,7 @@ rm -f logs/$1.log
 
 sbatch <<EOT
 #!/bin/bash
-#SBATCH --time=32:00:00
+#SBATCH --time=8:00:00
 #SBATCH --ntasks=$3
 #SBATCH --mem=32gb
 #SBATCH --job-name=$1

### 2023-07-21 surp/simulation/filter_warnings.py

@@ -1,7 +1,8 @@
 from warnings import filterwarnings
 
 filterwarnings('ignore', message='Using un-released version of VICE', module='vice', append=True)
-filterwarnings('ignore', message='Using a pre-release', module='vice', append=True)
+filterwarnings('ignore', message='Using a pre-release of VICE', module='vice', append=True)
+filterwarnings('ignore', lineno=150, module='vice', append=True)
 filterwarnings('ignore', message='Functions of stellar mass and metallicity', module='vice', append=True)
 filterwarnings('ignore', message='Functions of stellar mass and metallicity', module='vice', append=True)
 filterwarnings('ignore', lineno=131, module='vice', append=True)

### 2023-07-21 surp/simulation/multizone_sim.py

@@ -81,8 +81,6 @@ def run_model(filename, save_dir=None,
     eta_factor: ``float`` [default: 1]
         A factor by which to reduce the model's outflows. 
 
-    ratio_reduce: ``bool``
-        
     """
     print("initialized")
 
@@ -118,7 +116,6 @@ def run_model(filename, save_dir=None,
 def create_model(save_dir, filename, timestep,
         n_stars=2, 
         spec="insideout",
-        ratio_reduce=False,
         eta=1, 
         migration_mode="diffusion", 
         lateburst_amplitude=1,
@@ -169,8 +166,7 @@ def create_model(save_dir, filename, timestep,
                 name=model.name, 
                 sigma_R=sigma_R)
 
-    model.mass_loading = create_mass_loading(eta_factor=eta, 
-                                             ratio_reduce=ratio_reduce)
+    model.mass_loading = mass_loading(factor=eta)
 
     return model
 
@@ -222,31 +218,16 @@ def conroy_sf_law(area=None):
         if t < 2.5:
             tau_st = 50
         elif 2.5 <= t < 3.7:
-            tau_st = 50/(1+3*(t-2.5))^2
+            tau_st = 50/(1+3*(t-2.5))**2
         else:
             tau_st = 2.36
 
-        return vice.toolkit.J21_sf_law(area, t, present_day_molecular=tau_st)(t, m)
+        return vice.toolkit.J21_sf_law(area, tau_st)(t, m)
 
     return inner
 
     
 
-def create_mass_loading(eta_factor, ratio_reduce=False):
-    # for changing value of eta
-    if ratio_reduce:
-        def eta_f(R):
-            ml = mass_loading()
-            eta_0 = ml(R)
-            r = 0.4 # this is an approximation
-            eta =  (1 - r) * (eta_factor - 1) + eta_factor * eta_0
-            if eta < 0:
-                eta = 0
-            return eta
-    else:
-        eta_f = mass_loading(eta_factor)
-
-    return eta_f
 
 
 class mass_loading:
@@ -255,9 +236,9 @@ class mass_loading:
         pass
 
     def __call__(self, R_gal):
-        return self._factor*(
+        return np.maximum(0,
                 -0.6 
-                + 0.015 / 0.00572 
+                + self._factor * 0.015 / 0.00572 
                 * 10**(0.08*(R_gal - 4) - 0.3)
                )
 

### 2023-07-21 surp/yields.py

@@ -66,6 +66,8 @@ def set_yields(eta=1, zeta=None, fe_ia_factor=None,
     
     vice.yields.ccsne.settings["c"] = C_CC_model(zeta=zeta, y0=y_cc)
 
+    set_defaults()
+
     set_eta(eta)
 
     set_isotopic()
@@ -118,27 +120,42 @@ class C_CC_model:
         return f"{self.y0:0.2e} + {self.zeta:0.2e} (Z - Z0)"
 
 
+class ZeroAGB:
+    def __init__(self):
+        pass
+
+    def __call__(self, *args, **kwargs):
+        return 0
+
+    def __str__(self):
+        return "0"
+
+    def __repr__(self):
+        return "0"
 
 def set_defaults():
+    sneia.settings["c"] = 0
+
     ccsne.settings["o"] = 0.015
     sneia.settings["o"] = 0
+    agb.settings["o"] = ZeroAGB()
 
     ccsne.settings["fe"] = 0.0012
     sneia.settings["fe"] = 0.0017
+    agb.settings["fe"] = ZeroAGB()
     # sneia.settings["fe"] *= 10**0.1 # correction for mdf, used in
 
     ccsne.settings["sr"] = 3.5e-8
     sneia.settings["sr"] = 0
 
     ccsne.settings["n"] = 3.6e-4
-
-    sneia.settings["c"] = 0
     sneia.settings["n"] = 0
+
 
     ccsne.settings["mg"] = 0.00185
     sneia.settings["mg"] = 0
+    agb.settings["mg"] = ZeroAGB()
 
-set_defaults()
 
 
 

### 2023-07-21 carbon_paper/tex/main.tex

@@
 % context
-C is an important element across astronomy. However, its origin remains poorly understood. 
+C is an important element across astronomy; however, its origin remains poorly understood. 
 % 
-As stellar yields are highly uncertain, we aim to constrain the stellar yields of C through multi-zone Galactic chemical evolution models. 
-% results
-We use \apogee\ subgiants to constrain the model. 
+We aim to constrain the stellar yields of C through multi-zone Galactic chemical evolution models by comparing predictions with \apogee\ subgiants abundances.
 % 
@@
 Carbon is a distinctive and well-studied element in astronomy. 
-Formed in the cores of stars during He fusion, C is the lightest directly synthesized element after He, one of the only light elements formed in low-mass stars, and one the most abundant metals\footnotemark{}.
-% \citep[e.g.][]{jennifer19, KL14}
-C structurally changes the environments it pollutes, modifying stellar evolution, facilitating the formation of stars and planets, and forming the basis of earthly life.
+Formed in the cores of stars during He fusion, C is the lightest directly synthesized element after He, one of the only light elements formed in low-mass stars, and one the most abundant metals \citep[e.g.][]{jennifer19, KL14}.\footnotemark{}
+C structurally changes the environments it pollutes---regulating stellar evolution, facilitating the formation of stars and planets, and forming the basis of earthly life.
 % C/N as age indicator?
@@
 
-\footnotetext{Astronomers are not chemists. By metallicity, we mean the (mass) fraction of any element which is not H or He, denoted by $Z$. For the sun, $Z_\odot=0.014$. }
-
-Galactic chemical evolution is a powerful tool in understanding the origin of elements. 
-Each enrichment process has distinct chemical signatures and timescales, enabling us to reconstruct chemical histories.
+\footnotetext{By metallicity, we mean the (mass) fraction of any element which is not H or He, denoted by $Z$. For the sun, we take $Z_\odot=0.014$. }
+
+Galactic chemical evolution (\gce) is a powerful tool, capable of uncovering the origins of the elements. 
+Each enrichment process has characteristic chemical signatures and timescales, enabling us to reconstruct chemical histories.
 Many previous works have used GCE in attemt to understand C abundances, whether through using theoretical stellar models \citep{DTS78, prantzos+18, chiappini+03} 
@@
 For example CITES conclude \hms{} dominate wherease CITES conclude \lims{} contribute the majority of C.
-C is also generally understood to have strong metalliicity dependent CCSNe enrichment.
+C is also generally understood to have strong metallicity dependent CCSNe enrichment.
 
@@
 are shaped by poorly understood processes, including mass loss, nuclear reaction rates, rotational mixing, convection, and explodability \citep{romano+10,KL14,ventura+13, LC18, emily+21}.
-To better understand where C comes from and how it evolves, our aim is to use a combination of \apogee\ observations and multi-zone models to develop estimates of the required C yields to reproduce galactic trends.
-\cite{james+23} examined similar \gce{} models of N (which is closely related to C), finding that trends in N and O\footnotemark{} are explained by the metallicity dependence of N/O yields.
+To better understand where C comes from and how it evolves, our aim is to combine \apogee\ observations and multi-zone models to develop observationally-consistant yields.
+\cite{james+23} examined similar \gce{} models of N (which is closely related to C), finding that trends in N and O are explained by the metallicity dependence of N/O yields.
 \citet{james+23} determine that \agb\ N abundances roughly dependence on metallicity (i.e.
@@
 
-\footnotetext{e.g. \citet{HEK00,PVT10,berg+12, berg+20, skillman+20, izotov+12, james2+15, dopita+16}.} 
-We know, from observations of MW stars and extragalactic gas measurments, that C/O traces a banana shape in O/H (see \ref{fig:gas_phase}). 
-% \cite[e.g.][]{fabbian+09, nissen+14, lambert81, laird85, lambert86}. 
-At very low metallicities, C/O decreases with increasing metallicity, from observations of halo stars and damped Lyman-alpha systems\footnotemark{} \citep{nissen+14, cooke+17, fabbian+09}. 
-\footnotetext{DLAs; high redshift clouds of gas observed as absorption lines in yet higher redshift quasars}
-%
-However, the trend reverses around $[{\rm O/H}]\approx-1$\footnotemark{}. 
-C/O instead increases with increasing metallicity in observations of HII regions and Milky Way stars (\citealt{berg+19}; see discussion in section \ref{sec:gas}).
+% \footnotetext{e.g. \citet{HEK00,PVT10,berg+12, berg+20, skillman+20, izotov+12, james2+15, dopita+16}.} 
+We know, from observations of MW stars and extragalactic gas measurments, that C/O traces a banana shape in O/H (see Fig.~\ref{fig:gas_phase} and section~\ref{sec:gas}). 
+C (and O) have been observed in local and extragalactic HII regions (CITES), dwarf galaxies \citep[e.g.]{berg+19}, halo and thick disc Milky Way stars \cite[e.g.][]{fabbian+09, nissen+14, lambert81, laird85, lambert86}, and damped Lyman-alpha systems.
+\footnote{DLAs; high redshift clouds of gas observed as absorption lines in yet higher redshift quasars}
+The many observations of C and O paint a broadly consistant picture of a global trend.
+At the very lowest metallicities, where $[{\rm O/H}]\lesssim-2$,\footnotemark{} observations suggest that C/O declines with metallicity.
+From $-2 \lesssim {\rm [O/H]}\lesssim -1$, C/O is roughtly constant with metallicities. 
+And, at higher metallicities $-1 \lesssim {\rm [O/H]}$, C/O increases with increasing metallicity.
 
@@
 However, observations of C are not without challenges. 
-As stars ascend the red giant branch (RGB) at the end of H core burning, C abundances are changed by \textit{first dredge up}\footnotemark{}.
-This has the benefit of allowing C/N to be used as an age indicator in RGB stars \citep{MG15, martig16, hasselquist19, vincenzo+21}, but evolved stars are no longer as useful for determining birth abundances.
-Works such as \citet{vincenzo+21} attempt to correct for these changes but this requires MESA stellar modeling.
-In optical spectroscopy, C lines are relatively faint, and surveys such as GALAH struggle against low detection rates, potentially biasing sample measurments.
-While \apogee\ includes more reliable C$_2$ lines, there is an additional risk of systematics because .....
-In the gas phase, HII regions are our best window into C abundances in our galaxy and extragalactic regions including dwarf. 
-Unfortunantly, C lacks strong optical emission lines.
-Approaches use either recombination lines or ...
-in the ultraviolet, but these methods disagree, making gas-phase abundances a limited metric for GCE models of C.
-
-    As our primary observational constraint, we use a sample of subgiant stars from the \apogee{} \citep{apogee17}.
-selected by the criteria in Roberts et al.
+As stars ascend the red giant branch (RGB) at the end of H core burning, C abundances are modified through \textit{first dredge up}\footnotemark{}.
+Because the effects of first dredge up are mass-dependent, C and N abundances are frequently used as age indicators for RGB stars \citep{MG15, martig16, hasselquist19, vincenzo+21}.
+Evolved RGB stars thus require modelling-dependent corrections to recover birth C and N abundances \citep[e.g.][]{vincenzo+21}.
+C is also challenging to determine in optical spectroscopy. 
+C lines are relatively faint, and surveys such as GALAH struggle against low detection rates, potentially biasing sample measurments. 
+(e.g. gaia-eso AS WELL \citealt{franchini+20}).
+In the gas phase, HII regions are our best window into C abundances.
+Unfortunantly, C lacks strong collisional excitation lines, and recombination lines fall in the ultraviolet without nearby reference H lines \citep{skillman+20}.
+Recombination-line and collisional-excitation-line measurements furthermore disagree by a factor of \about{2} \citep{GR07}.
+
+\footnotetext{First dredge up is when material from CNO processed core is mixed with the (convective) stellar envelop during the ascent onto the RGB.
+As a result, C is decreased and N is increased depending on the strength of this process and the envelop mass.}
+
+    As our primary observational constraint, we use a sample of subgiant stars from the \apogee{} \citep{apogee17} selected by the criteria in Roberts et al.
 (2023, in prep; see Appendix \ref{sec:jack}).
-According to stellar evolution theory and observations \citep{gilroy89, korn+07, lind+08, souto+18, souto19}, these stars have not yet experienced first dredge up (FDU) but have well-mixed envelopes.
-So, subgiant surface abundances should represent their birth composition.
+According to stellar evolution theory and observations \citep{gilroy89, korn+07, lind+08, souto+18, souto19}, these stars have not yet experienced first dredge up yet have well-mixed envelopes.
+So, subgiant surface abundances most accurately represent their birth composition.
+INTRO TO \apogee\ takes high-resolution near-infrared spectroscopic measurments of stars, allowing accurate determination of chemical abundances and stellar parameters.
+In particular, near-infrared C abundances are more reliable than in optical spectroscopy (CITE??).
 Fig.~\ref{fig:subgiants} shows the subgiant sample plotted in \caah\ and \caafe{}. [C/Mg] increases with metallicity, and [C/Mg] decreases with [Mg/Fe] at fixed [Mg/H]. 
-Using these trends, we will develop a model of the enrichment sources and evolution of C.
-
-\citet{james+23} compare their model against the \cite{vincenzo+21} sample of \apogee{} \citep{apogee17} RGB stars.
-\citet{vincenzo+21} use \textsc{mesa} stellar evolution models \citep{mesa} to correct for the effects of first dredge up.
-We instead use the \citetjack~sample of \apogee{} subgiants.
-Subgiant stars have not undergone first dredge up but have well-mixed atmospheres, so their atmospheric C and N abundances are still reflective of their birth abundances and do not need mixing corrections.
-We only compare the models to the low-$\alpha$ sequence unless otherwise specified.
-The selection criteria and differences between the samples are described in more detail in Appendix \ref{sec:jack}.
-
-\footnotetext{First dredge up (FDU) is when material from CNO processed core is mixed with the (convective) stellar envelop during the ascent onto the RGB.
-As a result, C is decreased and N is increased depending on the strength of this process and the envelop mass.}
+Using the subgiant abundance trends, we will develop a model of the enrichment sources and evolution of C.
 
@@
 Yields -- the amounts of each chemical element stars synthesise -- are central to studies of galactic chemical evolution (GCE). 
-In this section, we discuss the yield choices of our model and literature models for C yields. 
+In this section, we compare literature yield predictions and discuss our fiducial yield choices. 
 We focus on three nucleosynthetic pathways: asymptotic giant branch (\agb{}) stars, core collapse supernovae (\cc{}), and type Ia supernovae (\ia{}).
@@
 We also use Mg and Fe as tracers of \cc{} and \ia{} enrichment respectively. 
-O and Mg are produced almost entirely from \cc\ with metallicity-independent yields. In contrast Fe is produced in similar amounts by \cc\ and \ia.
+O and Mg are produced almost entirely from \cc\ with metallicity-independent yields. In contrast, Fe is produced in similar amounts by \cc\ and \ia.
 
@@
 Also, note that yields may be negative if the material returned to the interstellar medium has a lower abundance $Z_X$ than the material the star was formed from.
-Although per-star yields are necessary to compute \agb{} star enrichment rates in \gce{}  models, \imf-averaged yields are useful in interpreting their predictions. 
+Although per-star yields are necessary to compute \agb{} star enrichment rates in \gce{}  models, initial-mass-function (\imf) averaged yields are useful in interpreting their predictions.
+An IMF-averaged yield adds together the yields of stars of each mass, weighted by the fraction of stars of each mass (the \imf).
 Given the fractional yield $\y(M, Z)$ as a function of initial stellar mass $M$ and metallicity $Z$, the \imf-averaged yield is given by 
@@
 where ${dN}/{dM}$ is the \imf, $M_{\rm max}=100\,\Mo$ is the maximum stellar mass, and $M_{\rm min}(t)$ is the mass of stars with lifetime $t$.\footnotemark{}
-We use $t=10\,$Gyr for total yields when $t$ is not used.
 To calculate the \imf-averaged net yields, we use the Versatile Integrator for Chemical Evolution code (\VICE).\footnotemark{}
@@
 Table \ref{tab:fiducial_mod} contains our fiducial yields. 
-Following \citet{james+21, james+23}, we also take the \ia{} delay time distribution to be a $t^{-1.1}$ power-law, as suggested by the observations of \citet{maoz+12}.
+Following \citet{james+21, james+23}, we also take the \ia{} delay time distribution to be a $t^{-1.1}$ power-law with a minimum delay time of 140\,Myr, as suggested by the observations of \citet{maoz+12}.
 
@@
 $\log \tau_M = 1.02 - 3.57\log M + 0.90 \left(\log M\right)^2$,
-where $\tau_M$ is in Gyr, from \citealt{larson74}}
+where $\tau_M$ is in Gyr, from \citealt{larson74}.
+We use $t_{\rm end}=10\,$Gyr for total yields when $t$ is not used.}
 
@@
 
-An \agb\ star is a low-mass star ($\lesssim 8 M_{\sun}$) during its final phase of evolution.  
+An \agb\ star is a low-mass ($\lesssim 8 M_{\sun}$) star during its final phase of evolution.
+Inside an \agb\ star, an inert CO core is surrounded by thermally-unstable He and H-burning shells below a convective envelope.
 In an \agb\ star, two competing processes determine the outcome of C production: \textit{third dredge up} and \textit{hot bottom burning}.  
@@
 Between \about{2} and \about{5} \Mo, third dredge up becomes important, enriching the outer layers with C, making these stars the most important producers of C. 
-In \agb\ stars more massive than \about{5}\,\Mo, both hot bottom burning and third dredge up occur; however, third dredge up is much more efficient, resulting in significant \C[12] destruction.
+In \agb\ stars more massive than \about{5}\,\Mo, both hot bottom burning and third dredge up occur; however, hot bottom burning is much more efficient, resulting in significant \C[12] destruction.
 
@@
 
-Fig.~\ref{fig:y_agb} compares the stellar \agb\ C yield for these four models.
+Fig.~\ref{fig:y_agb} compares the stellar \agb\ C yields for these four models.
 Most models agree on the qualitative shape of the net fractional \agb\ C yield.
@@
 The mass of peak C yields also increases slightly with metallicity.
-More metal-rich stars lose mass more quickly due to higher opacities, so these stars behave more like low-mass AGB stars.
-MORE PHYSICS
+Metal poor stars dredge up more material due to the decreased power of the CNO cycle, resulting in increasing carbon yields with decreasing metalicity \citep{ventura+13}.
 
@@
 In any case, little to no C is produced more than 2\,Gyr after a star formation event.
-In contrast, Fe production continues steadily for 10\,Gyr.
+Fe production, in contrast, continues steadily for 10\,Gyr.
 
@@
 All yield models span a range of \about{2} for a given metallicity.
-For example, the three models \cxi, \kx{}, and \kxvi{} predict $y_\text{C}^\text{agb}$ to be between 0.006 and 0.008 at solar metallicity, but \cxi\ has a much shallower metallicity dependence than the \kx{} and \kxvi{} models.
-\vxiii{} instead predicts a yield \about{0.004}.
+For example, all four models predict $y_\text{C}^\text{agb}(\Zo)$ to be between 0.004 and 0.008 at solar metallicity.
+The models also differ slightly in the strength of metallicity dependence, with about a factor of 3 discrepency (see Table~\ref{tab:alpha_agb}).
 
@@
 
-Massive stars form $^{12}$C in their cores through the triple--$\alpha$ process. However, only C ejected through supernovae and stellar winds contributes to the yield. 
+Massive stars form $^{12}$C in their cores through the triple--$\alpha$ process.\footnote{The 3-$\alpha$ process fuses 3 He nuclei into O.} 
+However, only C ejected through supernovae and stellar winds contributes to the yield. 
 While there are many stellar models providing predictions of \cc{} yields, the results of these models are highly uncertain due to the complexity of stellar modeling.
@@
 Assumptions about the explodability landscape affect C and Mg production.
-Increasing the fraction of stars that explode increases $\Ycc$, as stars that directly collapse do not contribute to explosive yields \citep{emily+21}.
-However, C is relatively unaffected by the black-hole landscape, as very massive stars contribute C through enriched winds.
-Since Mg is formed deeper in the core of \hms, the Mg yield drops much more steeply, so models where few stars explode (S16/W18) have higher [C/Mg].
+As fewer high-mass stars explode, both C and Mg yields decrease, but Mg yields decrease more as more C is lost to winds, so [C/Mg] increases with decreasing explodability.
 
@@
 \citealt{emily+21}).
-Here, we assume ${\rm [O/Mg]} = 0$, which is not compatible with \cc\ models but is consistent with \apogee{} observations \citep{weinberg+19, weinberg+22}.
-Because O and Mg are not perfectly identical in \apogee{}, the specific choice of $\alpha$-element may be a possible systematic.
+Here, we assume ${\rm [O/Mg]} = 0$, which nevertheless consistent with \apogee{} observations \citep{weinberg+19, weinberg+22}.
 
@@
 Newly produced metals are homogeneously and instantaneously mixed, so this model evolves as a single, spatially-uniform chemical zone.
-We define $M_{X}$ to be the mass of element $X$ in the gas-phase, $\dot{M}_\star$ to be the star formation rate (in $\Mo\,{\rm yr}^{-1}$), and $\eta$ to be the mass loading factor $\eta\equiv\dot{M}_{\rm outflow}/\dot{M}_\star$ (representing the strength of outflows).
+We define $M_{X}$ to be the gas mass of element $X$, $\dot{M}_\star$ to be the star formation rate (in $\Mo\,{\rm yr}^{-1}$), and $\eta$ to be the mass loading factor $\eta\equiv\dot{M}_{\rm outflow}/\dot{M}_\star$ (representing the strength of outflows).
 A \ssp\ returns a fraction $r$ of their birth mass to the interstellar medium, due to ejected stellar envelopes.%
@@
 Here, we will use $\alpha$ as a representative $\alpha$-element, such as O or Mg. 
-Given the \imf-averaged yield $y_\alpha$, the rate of change in the gas-phase mass of $\alpha$ is a simple sum of sources and sinks,
+Given the \imf-averaged yield $y_\alpha$, the rate of change in the gas-phase mass of $\alpha$ is a sum of sources and sinks,
 \begin{equation} \label{eq:mdot_1}
@@
 And, the outflows deplete mass at a rate $Z_\alpha \,\dot{M}_\star\,\eta$.
-(We assume the composition of outflows is the same as the interstellar medium.) With these definitions, Eq.~\ref{eq:mdot_1} is
+(We assume the composition of outflows is the same as the interstellar medium.) With these definitions, Eq.~\ref{eq:mdot_1} becomes
 \begin{equation}
@@
 where $\tau_{\star}$ is the star formation rate. ($\eta$ depends on $R$ to create a metallicity gradient. See also Section \ref{sec:vice} and Eq.~\ref{eq:eta_r}.)
-In the special case of constant star formation, $\tau_{\rm sfh}\to\infty$, the denominator simplifies to $1+\eta-r$.
+In the special case of constant star formation, $\tau_{\rm sfh}\to\infty$ and the denominator simplifies to $1+\eta-r$.
 
@@
 
+Both observational and theoretical uncertainties limit the accuracy of our relative yield predictions.
+As the metallicity range of our data is small ($-0.4\lesssim {\rm [Mg/H]} \lesssim 0.4$),
+our model does not extend beyond near-solar metallicities.
+Additionally, the derived yields will be systematically biased if the galaxy is out of equilibrium, for example, due to a recent starburst \citep{mor+19,isern19}. 
+As we will discuss in Section \ref{sec:outflows}, the normalization of yields and $\eta$ is degenerate.
+If we increase yields and $\eta$ by a similar factor, equilibrium abundances from Eq.~\ref{eq:z_eq} would be unchanged, so our model cannot distinguish changes in both yields and outflows.
+
 \begin{figure}
@@
 We can use the \caafe{} diagram of \apogee\ stars to estimate the delayed portion of C.
-When binned in metallicity, median [C/Mg] changes by about 0.25 dex across the range of [Mg/Fe].
+When binned in metallicity, median [C/Mg] changes by about 0.2 dex across the range of [Mg/Fe] at solar metallicities (see Fig.~\ref{fig:caafe_binned}).
 As high-$\alpha$ stars have little to no delayed \ia\ Fe, these stars would also have little to no delayed \agb\ C.
-This means that AGB C stars make up about at most a fraction $f_{\rm agb} \approx 1 - 10^{-0.25} \approx 0.6$ of C production.
+This means that AGB C stars make up about at most a fraction $f_{\rm agb} \approx 1 - 10^{-0.2} \approx 0.4$ of C production.
 
@@
 outside of this range with (optionally) negative yields.
-And the resulting equation (excepting a prefactor)
-
-\begin{equation}
+The mass dependence is
+\begin{equation} \label{eq:yca_m}
 \y(m) = 
@@
 \end{equation}
-
-where 
+where $\y_1$ approximantly represents the total \imf-integrated yield, $\y_0$ and $\y_1$ represent the yields for low-mass and high-mass \agb\ stars respectively, and 
 \begin{equation}
-    f(x) = 3x^2 - 2x^3
-\end{equation}
-
+    f(x) = 3x^2 - 2x^3.
+\end{equation}
 For the full equation, we take the above functional form multiplied by a
 metallicity dependent term, so 
-
-\begin{equation}
+\begin{equation} \label{eq:yca_z}
     \y_{\rm C}^{\rm agb}(m, Z) = \frac{\y(m)}{\int_1^8 m\,\y(m)\,{\rm IMF}(m)\;dm} 
@@
 Table~\ref{tab:alpha_agb} contains our adaptive (regression-derived) values of $\zeta^{\rm agb}$ and $\Ycagb(\Zo)$. 
-Table~\ref{tab:alpha_agb} also shows $\alpha^{\rm agb}_{20}$, the value of $\alpha^{\rm agb}$ required with our adopted total yields (Eq.~\ref{eq:yc_inferred}) to reach 20\% \agb\ C.
-
+For example, in our fiducial model, $\Ycc = 0.004 + 0.102 (Z-\Zo)$.
 Our full \cc\ C yield model adds a low-metallicity enhancement term, which is insignificant at solar metallicities (e.g.
 thin disk stars) but enables models in Section~\ref{sec:gas} to match low-metallicity environments.
+We parameterize low-metallicity enrichment with $y_l$ and $Z_l$, the yield and transition metallicity for enhanced low-metallicity yields.
 All-together, 
 \begin{equation}\label{eq:zeta}
-    \Ycc = y_{\rm C, 0}^{\rm cc} + \zeta^{\rm cc}\,(Z-\Zo) + \frac{2\,y_{\rm III}}{1 + Z/Z_{\rm III}}.
+    \Ycc = y_{\rm C, 0}^{\rm cc} + \zeta^{\rm cc}\,(Z-\Zo) + \frac{2\,y_l}{1 + Z/Z_l}.
 \end{equation}
@@
 	\centering
-    \caption[]{For each \agb\ yield set, the \imf-averaged \agb\ C yield at solar metallicity $y_{\rm C, 0}^{\rm agb}$ and the multiplicative factor reaches an \agb\ contribution of 20\% $\alpha_{\rm agb, 20}$.
-<UPDATE>}
+    \caption[]{For each \agb\ yield set, the \imf-averaged \agb\ C yield at solar metallicity $y_{\rm C, 0}^{\rm agb}$ and the multiplicative factor reaches an \agb\ contribution of 20\% $\alpha_{\rm agb, 20}$.}
 	\label{tab:alpha_agb}
@@
         \hline
-        \cxi & 4.2E-4 & -0.022 & 2.9\\
-        \kx & 6.5E-4 & -0.063 & 1.7\\
-        \vxiii & 4.9E-4 & -0.032 & 16.5\\
-        \kxvi & 5.6E-4 & -0.034 & 2.4\\
+        \cxi & 4.2E-4 & -0.0175 & 2.4\\
+        \kx & 6.4E-4 & -0.059 & 1.6\\
+        \vxiii & 2.2E-4 & -0.021 & 4.5\\
+        \kxvi & 5E-4 & -0.029 & 2.0\\
 		\hline
@@
 \end{table}
-
-\subsection{Uncertainties}
-
-We only perform this analysis on the \cxi{} yields because \cxi{} has yields tables more finely sampled in metallicity than the other three \agb\ yield tables.
-As the metallicity range of the data is small ($-0.4\lesssim {\rm [Mg/H]} \lesssim 0.4$), other models are more challenging to interpret in this range.
-Furthermore, the \apogee{} observations may have systematics.
-Other measurements of C abundances \citep[e.g.][]{vincenzo+21} have slight disagreements in the overall shape of the trend (see Section \ref{sec:jack}).
-So, this expression of $\Ycc/\Yoc$ depends on the chosen \agb\ yield table, the \agb\ fraction, and the dataset. 
-Additionally, these yields will be systematically biased if the galaxy is out of equilibrium, for example, due to a recent starburst \citep{mor+19,isern19}.
-Further exploration could investigate the magnitude of these uncertainties, but we find that the qualitative conclusions are similar despite substantial variations in the assumptions here.
-
-As we will discuss in Section \ref{sec:outflows}, the normalization of yields and $\eta$ is degenerate.
-This can be observed in Eq.~\ref{eq:z_co}, where changes in $\eta$ or the scaling of $y_{\rm C}/y_{\rm Mg}$ would not affect equilibrium trends.
-Furthermore, in Eq.~\ref{eq:z_eq}, an increase in both $y_{\rm Mg}$ and $\eta$ would leave $Z_{\rm Mg}^{\rm eq}$ unchanged.
-Our models here are unable to distinguish the overall scaling of yields and outflow mass loading.
-Choosing to keep $y_{\rm C}$ fixed reduces unnecessary free parameters.
-So, at solar metallicity, we set
 
@@
 
-Star formation is treaded as follows.
-The Galaxy is divided into 200 rings, each 100\,pc wide.
-Each ring has a separate stellar population and gas supply.
+Star formation is set seperately for each zone.
+The Galaxy is divided into 200 rings, each 100\,pc wide representing a single zone.
+Each ring (or zone) has a separate stellar population and gas supply.
 We initially assume an inside-out \sfh{}, where the star formation surface density $\Sigma_\star$ is given by
@@
 
-To account for radial migration, \JJ\ used the \texttt{h277} hydrodynamical
-simulation results \citep{christensen12, zolotov12, loebman12, BZ14}. Simulation parameters are described in \citet{bird+21}. 
+To account for radial migration, we use the \texttt{h277} hydrodynamical
+simulation results (with simulation parameters as in \citealt{bird+21}; see also \citealt{christensen12, zolotov12, loebman12, BZ14}).  
 Each \VICE\ single stellar population (SSP) is matched to an \textit{analog} in \texttt{H277}, chosen to form at a similar time and radius $R$.
@@
 We do not account for radial gas flows.
-Using the results of a hydrodynamical simulation without modification limits the free parameters in the model; however, we am limited to one dynamical history. 
-We do explore a normal-distribution random walk migration based on \citet{frankel18}, without noticeable impacts on our results.
+Using the results of a hydrodynamical simulation without modification limits the free parameters in the model; however, we are limited to one dynamical history. 
+We also explore a normal-distribution random walk migration based on \citet{frankel18}, without noticeable impacts on our results.
 All models shown here use the \texttt{h277}-based migration.
@@
 \section{Results}
-\subsection{Data Selection}
-
-Subgiants provide the ideal observational constraint to our model. 
-When a star enters the Red Giant Branch (RGB), material from the CNO-processed core is mixed with the envelope in first dredge up, enhancing N and depleting C \citep{iben67, vincenzo+21,KL14}.
-RGB stars thus require model-dependent corrections to recover surface abundances \citep[e.g.][]{vincenzo+21}.
-On the other hand, gravitational settling can affect main sequence stellar abundances \citep[e.g.][]{souto19}.
-Subgiants have well-mixed envelopes, so gravitational settling is not as significant, and subgiants have not yet experienced first dredge up.
-We use a sample of \apogee\ DR17 stars \citep{apogee17} as selected in \citetjack.
-We only compare the models to the low-$\alpha$ sequence (representing the thin disk) unless otherwise specified.
-The selection criteria and differences between the samples are described in more detail in Appendix~\ref{sec:jack}.
 
@@
 
+\subsection{Data and Sample Selection}
+
+Subgiants provide the ideal observational constraint to our model. 
+When a star enters the Red Giant Branch (RGB), material from the CNO-processed core is mixed with the envelope in first dredge up, enhancing N and depleting C \citep{iben67, vincenzo+21,KL14}.
+RGB stars thus require model-dependent corrections to recover surface abundances \citep[e.g.][]{vincenzo+21}.
+On the other hand, gravitational settling can affect main sequence stellar abundances \citep[e.g.][]{souto19}.
+Subgiants have well-mixed envelopes, so gravitational settling is not as significant, and subgiants have not yet experienced first dredge up.
+We use a sample of \apogee\ DR17 stars \citep{apogee17} as selected in \citetjack.
+The selection criteria and differences between the samples are described in more detail in Appendix~\ref{sec:jack}.
+
+When plotting the data and models, we bin by groups of 500 (or 150) stars in [Mg/H] ([Mg/Fe]).
+When plotting \caah, we select only the low-$\alpha$ sequence.
+For \caafe, we instead select stars with $-0.15 \leq {\rm [Mg/H]} \leq -0.05$.
+To create a sample with similar characteristics of the subgiant observations, we sample 12,000 stars from the simulations such that the cumulative distribution function of stars in $R_{\rm gal}$ is the same for the subgiants and our comparison sample.
+
 \subsection{High-Mass Stellar Yields}\label{sec:results_highmass}
 
-\cc, which likely make up the majority of C, set the overall C abundance trends.
- Fig.~\ref{fig:first_models} shows models with varying $\Ycc$ metallicity dependence.
-As the \caah~trend is approximated by equilibrium trends, the models with stronger metallicity dependence have a stronger slope in \caah.
- However, \caafe~is minimally affected by these changes since \cc\ occurs on much shorter timescales than \ia\ and \agb\ enrichment.
+\cc, which we assume make up the majority of C, set the overall C abundance trends.
+The top of Fig.~\ref{fig:first_models} shows models with varying $\Ycc$ metallicity dependence, $\zeta^{\rm cc}$.
+As the \caah~trend is approximated by equilibrium trends, the models with higher $\zeta^{\rm cc}$ also have a steeper slope in \caah.
+However, \caafe~is minimally affected by changes to $\zeta^{\rm cc}$ since \cc\ occurs on much shorter timescales than \ia\ and \agb\ enrichment.
 The only effects on \caafe, when considering the narrow metallicity slice, are because of either the slight change in equilibrium abundances, the imperfect evolution of the galaxy, or that the interstellar medium abundances are set by stars which were born at poorer metallicities.
@@
 
-In Fig.
-<REF>, we first show the four C yield models (\kx, \kxvi, \cxi, \vxiii).
+In the middle row of Fig.~\ref{fig:first_models}, we first show the four C yield models (\kx, \kxvi, \cxi, \vxiii).
 For the most part, the \agb\ yield sets result in qualitatively similar predictions.
@@
 As all \agb\ models predict some low-mass C destruction, each model does predict a downturn in [C/Mg] as [Fe/Mg] increases.
-A recent burst in star formation may hide this downturn (see NEXT SECTION), but the C destruction is not supported directly by observations.
-
-Here, we investigate adjustments to the \agb\ yield fraction $f_{\rm agb}$
-Fig.~\ref{fig:f_agb} shows three models with different \agb\ fractions while using \cxi{} yields.
+A recent burst in star formation may hide this downturn (see section~\ref{sec:sfh}), but the C destruction is not supported directly by observations.
+
+We also investigate adjustments to the \agb\ yield fraction $f_{\rm agb}$
+The bottom of Fig.~\ref{fig:first_models} shows three models with different \agb\ fractions while using \cxi{} yields.
 The \caafe~relationship is set by $f_{\rm agb}$ because a specific amount of C must be released at a delayed time to match the \ia\ production of Fe and increase [C/Mg] as [Mg/Fe] decreases to reproduce the data.
@@
 
-Negative \agb\ yields cause a morphological change in the abundance trends.
-If the yields of low mass stars are negative, then at late times in a SSP, C abundances will decrease.
-This will appear as a downturn in the \caafe{} abundance trends as [Mg/Fe] approaches solar values.
-As we do not observe this in the data, this is either obscured by \sfh\ (Seee eeee) or observational scatter.
-Instead, if lower-intermediate mass \agb\ stars produce negative carbon yields, it is possible to observe this as a dip in the early parts of the \caafe{} trend...
+Finally, in the top row of Fig.~\ref{fig:second_models}, we plot variations of the analytic \agb\ models (Eqns.~\ref{eq:yca_m} and \ref{eq:yca_z})  where C production occurs in different mass ranges.
+If all C comes from stars with masses $>4\Mo$, then [C/Mg] is almost independent of [Fe/Mg].
+On the other hand, if all C comes from stars with masses between 1 and 2 \Mo, then [C/Mg] increases across almost the whole range of [Fe/Mg].
+As the observed trend in \caafe\ is almost linear, then the delay-time-distribution of C is similar to Fe, so C is likely produced in a mix of stars between 1 and 4\Mo.
+We cannot constrain upper-intermediate \agb\ C production as this behaves similar to \cc\ C.
 
@@
 \caption[]{Similar to Fig.~\ref{fig:first_models}, except where the \agb\ C contribution is varied from the fiducial ($f_{\rm agb}=0.2$) to 0.1 and 0.3 (see Eq.~\ref{eq:f_agb} and Section.~\ref{sec:agb_results}.}
-\label{fig:caafe_agbs}
+\label{fig:second_models}
 \end{figure*}
 
-\subsection{Star Formation History} \label{sec:sfh}
+\subsection{Star Formation History and Outflows} \label{sec:sfh}
 
@@
 where $A=1.5$ represents the amplitude of the birth, $\tau_\text{burst}=10.8$\,Gyr is the time where the burst is strongest, and $\sigma_\text{burst}=1$\,Gyr is the width of the burst.
-Our earlyburst model instead >>>>>?????  at $t_1=5$\,Gyr. 
+Our earlyburst model is instead a double exponential, with the second exponential begining at $t_1=5\,$Gyr.
 \begin{equation}\label{eq:twoinfall}
-    \dot{\Sigma}_{\rm earlyburst} \propto A\,e^{-(t-t_1)/\tau_{\rm burst}} + 
+    \dot{\Sigma}_{\rm earlyburst} \propto A\,e^{-t/\tau_{\rm burst}} + 
 \begin{cases}
-    \left(1-e^{-t/\tau_\text{rise}}\right)e^{-t/\tau_\text{rise}} & t_1 < t \\
+    e^{-(t-t_1)/\tau_\text{sfh}} & t_1 < t \\
       0 & t<t_1
@@
 \end{equation}
-where we take the burst duration, $\tau_{\rm burst}=1$\,Gyr.
+where we take the burst duration, $\tau_{\rm burst}=2$\,Gyr.
 This approximately corresponds to the Gaia-Encelidus merger, inducing higher star formation in the Milky Way \citep{spitoni21, bonaca20, helmi18}.
 
-Fig.~\ref{fig:sfh_models} shows three models with these alternate \sfh{}.
+The middle row of Fig.~\ref{fig:second_models} shows three models with our alternate \sfh{}.
 Changes to the \sfh{} leave \caah\ unchanged, but they do introduce slight variation in \caafe.
@@
 
+The middle row of Fig.~\ref{fig:second_models} also shows a model where $\eta$ and yields are decreased by a factor 0.3.
+While changing the value of $\eta$ affects the metallicity distribution of stars, the model still evolves along the same paths.
+Our model is unable to differentiate a uniform decrease in both outflows and yields.
+
 \subsection{Degeneracies} \label{sec:outflows}
@@
 
-Fig.~\ref{fig:eta} shows models with variations of the mass loading strength.
-While changing the value of $\eta$ affects the metallicity distribution of stars, all of the models in Fig.~\ref{fig:eta} still evolve along the same path.
-Our model is unable to differentiate a uniform decrease in both outflows and yields.
-
 An addition source of theoretical uncertainty in this result is that the \ia\ yield and delay time distributions have their own uncertainties.
-We discuss variations in $y_{\rm Fe}^{\rm Ia}$ in NOWHERE, and find that the qualitative conclusions are largely unaffected.
-We, therefore, focus on the choices of $y_{\rm Fe}^{\rm Ia} = 0.00214$ and a $t^{-1.1}$ delay time distribution choices from the fiducial model here.
-In short, the scaling of the trend and metallicity dependence of C (as seen in
-the \caah\ trend) gives information on the total C yield and the behavior of \cc\ (as the dominating producer of C), the \caafe\ trend exposes the delayed effect of C from \agb\ contribution.
+We do compute models (not shown here) where $y_{\rm Fe}^{\rm Ia}$ is varied.
+Increasing $y_{\rm Fe}^{\rm Ia}$ has a similar affect as decreasing $f^{\rm agb}$.
+Here, we only show models with $y_{\rm Fe}^{\rm Ia} = 0.00214$ and a $t^{-1.1}$ delay-time-distribution choices from the fiducial model here.
 
@@
 In HII regions, C/O abundance ratios are measured with either recombination lines or collisional excitation lines.
-However C lacks strong collisional excitation lines, and recombination lines fall in the ultraviolet without nearby reference H lines \citep{skillman+20}.
-Additionally, recombination and collisional excitation measurements disagree by a factor of \about{2} \citep{GR07}.
-While broad consistancy of our model with gas-phase measurments is nice, the large measurment errors limit the evaluative power of HII regions.
+While broad consistancy of our model with gas-phase measurments is promising, the large measurment errors limit the evaluative power of HII regions.
 We additionally include Milky Way thick disk (high-$\alpha$) and halo stars, which span a larger range of metallicities than thin disk stars.
-However, metal-poor abundance measurments require consideration of 3D-NLTE effects (e.g.
+However, metal-poor abundance measurments require consideration of 3D-NLTE effects, which can be an \about{0.2} dex effect  (e.g.
 CITE).
@@
 Here, we consider a single-zone model with parameters consistant with the Gaia-Encelidus sausage\footnotemark{}.
-We chose the model to have outflows $\eta=6$, star formation efficiency $\tau_{\star}=9\,{\rm Gyr}$, and a star formation history $\propto e^{-t/2{\rm\,Gyr}}$, evolved for 6\,Gyr.
+We chose the model to have mass loading $\eta=6$, star formation efficiency $\tau_{\star}=9\,{\rm Gyr}$, and a star formation history $\propto e^{-t/2{\rm\,Gyr}}$, evolved for 6\,Gyr.
 The single-zone model is better able to replicate the slope of the abundances in dwarf galaxies, HII-regions, and halo stars.
-The single-zone model is an evolutionary track, whereas the multi-zone models moreso show equilibrium tracks.
+The single-zone model does not produce an equilibrium track, unlike the multi-zone models.
 As the single-zone model also evolves slower, the late contribution of AGB stars causes the steeper slope at near-solar metallicities.
@@
 We began by adopting an equilibrium approximation to estimate the total C yields with metallicity from \apogee{} subgiant \caah{} trends.
-We find that <EQUATION>.
+We find that $\Yct/y_{\rm O} = 1/3 + 4(Z-\Zo)$ and $\Yct/y_{\rm Mg} = 2.7 + 32 (Z-\Zo)$, where we assume ${\rm [Mg/O]} = 0$.
 We show that \caah{} is a diagnostic for total C yields with metallicity, but \caafe{} provides information about delayed C production.
-From the \caafe{} trends, we estimate that \agb\ stars contribute \about{20\%} of total C abundances, with 1--3\,\Mo the most importaint.
-In this model, the remaining \about{80\%} of C comes from high-mass stars with a metallicity dependent yield of $\Ycc/\Yoc=<\text{EQUATION}>$, broadly consistant with rotating \cc\ models.
+From the \caafe{} trends, we estimate that \agb\ stars with masses between about 1 and 3 \Mo contribute \about{20\%} of total C abundances.
+In this model, the remaining \about{80\%} of C comes from high-mass stars with a metallicity dependent yield of $\Ycc/y_{\rm Mg} = 2.2 + 55 (Z/\Zo)$, broadly consistant with rotating \cc\ models.
 
 We additionally explore variations of the assumed \sfh{} and outflow mass-loading factor $\eta$.
-We find that alternate \sfh{}s can slightly affect \caafe, but \caah~is mostly unaffected.
+We find that alternate \sfh{}s can perturb \caafe and \caah\ abundances slightly.
 Decreasing both outflows and yields by the same factor leaves the \caah~and \caafe~trends unaffected, ingoring effect to the metalliticy distribution of starrs.
@@
 Finally, we compare our model against gas-phase measurements and Milky Way halo stars.
-By including yields which are enhanced at low metallicities, \cc\ and \agb\ stars together are able to explain the general trends of C from metallicities of -3 to 0.5.
-
-These C yield constraints provide a useful benchmark for stellar evolution models.
+By including yields which are enhanced at low metallicities, \cc\ and \agb\ stars together are able to explain the general trends of C from metallicities of ${\rm [O/H]} = -3$ to 0.5.
+
+Our C yield constraints provide a useful benchmark for stellar evolution models.
 C yields are sensitive to poorly understood processes, including mass-loss prescriptions, explodability, nuclear cross sections, convection, and stellar structure.
@@
 metallicities $Z = $ 0.0001, 0.0003, 0.001, 0.002, 0.003, 0.006, 0.008, 0.01, 0.014, 0.02. 
+C11 uses a higher triple-$\alpha$ reaction rate than others and has weaker hot bottom burning, so
 
@@
 and metallicities $Z=$ 0.0001, 0.004, 0.008, 0.02.
+K10 use an ad-hoc mass-loss prescription which likely is not physical as opacities are poorly understood.
+K10 also has a lower temperature at the base of the convective envelope so hot bottom burning is not as strong as other models, likely explaining why low-metallicity C yields are higher.
 
@@
 \vxiii is evololved with DHFJKSLDF,
-\vxiii is unusual in that hot bottom burning is much stronger than other models, resulting in much lower stellar yields and negative yields above solar metallicities.
+\vxiii is unusual in that hot bottom burning is much stronger than other models due to more efficient convection and higher temperatures at the base of the convective envelope, resulting in much lower stellar yields and negative yields above solar metallicities.
 
@@
 This yield set was extended up to metallicities of 0.1 in DFJSD; however, we do not consider this range here.
+K16 has stronger dredge up than C11, but lower 3-alpha reaction rates.
+However, K16 has more rapid puses and stays higher mass for longer.
+HBB is stronger at high mass than C11.
 

### 2023-07-25 carbon_paper/tex/main.tex
more consise draft

@@
 % Basic setup. Most papers should leave these options alone.
-\documentclass[fleqn,usenatbib]{mnras}
+\documentclass[fleqn,
+%referee,
+usenatbib]{mnras}
 
@@
 \newcommand{\vxiii}{\texttt{\hyperlink{V13}{V13}}}
+\newcommand{\cfactor}{2.3}
 
@@
 % other
+\newcommand{\ycmg}{\ensuremath{2.7 + 32\left(Z-\Zo\right)}}
+\newcommand{\ycccmg}{1}
+\newcommand{\yco}{1}
+\newcommand{\fmeas}{20\%}
+
 \makeatletter
@@
 \newcommand{\Ycagb}{\ensuremath{y_{\rm C}^{\rm agb}}}
-\newcommand{\y}{\ensuremath{\rotatebox[origin=B,y=0.5ex]{180}{y}}}
+% \newcommand{\y}{\ensuremath{\rotatebox[origin=B,y=0.5ex]{180}{y}}}
+\newcommand{\y}{Y}
 
@@
     \ifmmode {\rm M}_{\sun}%
-    \else M$_{\sun}$
+    \else {M$_{\sun}$}%
     \fi}
@@
 % gas phase
-While reliable gas-phase and low-metallicity measurments of C are challenging, we find that our model and a singlezone model with our recommended yields replicate the broad trends of \caah across different environments and metallicities.
+While reliable gas-phase and low-metallicity measurments of C are challenging, we find that our model and a singlezone model with our recommended yields replicate the broad trends of \caah{} across different environments and metallicities.
 
@@
 Formed in the cores of stars during He fusion, C is the lightest directly synthesized element after He, one of the only light elements formed in low-mass stars, and one the most abundant metals \citep[e.g.][]{jennifer19, KL14}.\footnotemark{}
-C structurally changes the environments it pollutes---regulating stellar evolution, facilitating the formation of stars and planets, and forming the basis of earthly life.
-% C/N as age indicator?
+C structurally changes the environments it pollutes -- regulating stellar evolution, facilitating the formation of stars and planets, and forming the basis of earthly life.
+% Because the effects of first dredge up are mass-dependent, C and N abundances are frequently used as age indicators for RGB stars \citep{MG15, martig16, hasselquist19, vincenzo+21}. 
 As such, understanding the origin of C has wide ranging implications. 
@@
 
-Galactic chemical evolution (\gce) is a powerful tool, capable of uncovering the origins of the elements. 
-Each enrichment process has characteristic chemical signatures and timescales, enabling us to reconstruct chemical histories.
-Many previous works have used GCE in attemt to understand C abundances, whether through using theoretical stellar models \citep{DTS78, prantzos+18, chiappini+03} 
-or understanding  observation \citep{tinsley79, HEK00, BF06, rybizki+17, berg+19, KKL20}.
-(See also review in \citealt{romano22}.)
-%
-Every study agrees that C is produced by a combination of high-mass and \lims{}, different studies disagree on which process is dominant. 
-For example CITES conclude \hms{} dominate wherease CITES conclude \lims{} contribute the majority of C.
-C is also generally understood to have strong metallicity dependent CCSNe enrichment.
-
-One of the primary uncertainties of GCE models are nucleosynthetic yields. Yield predictions -- the amounts of each chemical element stars produce --
-are shaped by poorly understood processes, including mass loss, nuclear reaction rates, rotational mixing, convection, and explodability \citep{romano+10,KL14,ventura+13, LC18, emily+21}.
-To better understand where C comes from and how it evolves, our aim is to combine \apogee\ observations and multi-zone models to develop observationally-consistant yields.
-\cite{james+23} examined similar \gce{} models of N (which is closely related to C), finding that trends in N and O are explained by the metallicity dependence of N/O yields.
-\citet{james+23} determine that \agb\ N abundances roughly dependence on metallicity (i.e.
-$y_{\rm N}/y_{\rm O} \propto Z$).
-Here, we extend their models to C, deriving similar constraints on C/Mg yields.
-We assess which yield prescriptions reproduce Galactic abundance trends while investigating the impact of \gce{} model assumptions, such as the star formation history (\sfh{}) and outflow mass loading.
-
-% \footnotetext{e.g. \citet{HEK00,PVT10,berg+12, berg+20, skillman+20, izotov+12, james2+15, dopita+16}.} 
-We know, from observations of MW stars and extragalactic gas measurments, that C/O traces a banana shape in O/H (see Fig.~\ref{fig:gas_phase} and section~\ref{sec:gas}). 
-C (and O) have been observed in local and extragalactic HII regions (CITES), dwarf galaxies \citep[e.g.]{berg+19}, halo and thick disc Milky Way stars \cite[e.g.][]{fabbian+09, nissen+14, lambert81, laird85, lambert86}, and damped Lyman-alpha systems.
-\footnote{DLAs; high redshift clouds of gas observed as absorption lines in yet higher redshift quasars}
-The many observations of C and O paint a broadly consistant picture of a global trend.
-At the very lowest metallicities, where $[{\rm O/H}]\lesssim-2$,\footnotemark{} observations suggest that C/O declines with metallicity.
-From $-2 \lesssim {\rm [O/H]}\lesssim -1$, C/O is roughtly constant with metallicities. 
-And, at higher metallicities $-1 \lesssim {\rm [O/H]}$, C/O increases with increasing metallicity.
-
-\footnotetext{In this paper, we use the standard notation for chemical abundances.
+We know, from observations of MW stars and (extragalactic) gas, that C/O traces a banana shape in O/H (see Fig.~\ref{fig:gas_phase} and section~\ref{sec:gas}). 
+At the very lowest metallicities, where $[{\rm O/H}]\lesssim-2$,%
+\footnote{In this paper, we use the standard notation for chemical abundances.
 $[A/B] = \log_{10}\left(A/B\right) - \log_{10}\left(A_{\sun}/B_{\sun}\right)$, i.e.
@@
 Solar abundances are as measured in \citet{asplund+09}.}
-
-However, observations of C are not without challenges. 
-As stars ascend the red giant branch (RGB) at the end of H core burning, C abundances are modified through \textit{first dredge up}\footnotemark{}.
-Because the effects of first dredge up are mass-dependent, C and N abundances are frequently used as age indicators for RGB stars \citep{MG15, martig16, hasselquist19, vincenzo+21}.
-Evolved RGB stars thus require modelling-dependent corrections to recover birth C and N abundances \citep[e.g.][]{vincenzo+21}.
-C is also challenging to determine in optical spectroscopy. 
-C lines are relatively faint, and surveys such as GALAH struggle against low detection rates, potentially biasing sample measurments. 
-(e.g. gaia-eso AS WELL \citealt{franchini+20}).
-In the gas phase, HII regions are our best window into C abundances.
-Unfortunantly, C lacks strong collisional excitation lines, and recombination lines fall in the ultraviolet without nearby reference H lines \citep{skillman+20}.
-Recombination-line and collisional-excitation-line measurements furthermore disagree by a factor of \about{2} \citep{GR07}.
-
-\footnotetext{First dredge up is when material from CNO processed core is mixed with the (convective) stellar envelop during the ascent onto the RGB.
+%
+observations suggest that C/O declines with metallicity.
+From $-2 \lesssim {\rm [O/H]}\lesssim -1$, C/O is roughtly constant with metallicities. 
+And, at higher metallicities $-1 \lesssim {\rm [O/H]}$, C/O increases with increasing metallicity.
+    As our primary observational constraint, we use a sample of subgiant stars from the \apogee{} \citep{apogee17} selected by the criteria in Roberts et al. (2023, in prep).
+    According to stellar evolution theory and observations \citep{gilroy89, korn+07, lind+08, souto+18, souto19}, these stars have not yet experienced \textit{first dredge up}%
+\footnote{First dredge up is when material from CNO processed core is mixed with the (convective) stellar envelop during the ascent onto the RGB.
 As a result, C is decreased and N is increased depending on the strength of this process and the envelop mass.}
-
-    As our primary observational constraint, we use a sample of subgiant stars from the \apogee{} \citep{apogee17} selected by the criteria in Roberts et al.
-(2023, in prep; see Appendix \ref{sec:jack}).
-According to stellar evolution theory and observations \citep{gilroy89, korn+07, lind+08, souto+18, souto19}, these stars have not yet experienced first dredge up yet have well-mixed envelopes.
-So, subgiant surface abundances most accurately represent their birth composition.
-INTRO TO \apogee\ takes high-resolution near-infrared spectroscopic measurments of stars, allowing accurate determination of chemical abundances and stellar parameters.
-In particular, near-infrared C abundances are more reliable than in optical spectroscopy (CITE??).
+yet have well-mixed envelopes. So, subgiant surface abundances most accurately represent their birth composition. 
+In contrast, evolved RGB stars require modelling-dependent corrections to recover birth C abundances \citep[e.g.][]{vincenzo+21}. 
 Fig.~\ref{fig:subgiants} shows the subgiant sample plotted in \caah\ and \caafe{}. [C/Mg] increases with metallicity, and [C/Mg] decreases with [Mg/Fe] at fixed [Mg/H]. 
@@
 
+Galactic chemical evolution (\gce) is a powerful tool, capable of uncovering the origins of the elements. 
+Each enrichment process has characteristic chemical signatures and timescales, enabling us to reconstruct chemical histories.
+Many previous works have used GCE in attemt to understand C abundances, whether through using theoretical stellar models \citep{DTS78, prantzos+18, chiappini+03} 
+or understanding  observation (\citealt{tinsley79, HEK00, BF06, rybizki+17, berg+19, KKL20};
+See also review in \citealt{romano22}).
+%
+Every study agrees that C is produced by a combination of high-mass and \lims{}, different studies disagree on which process is dominant. 
+For example CITES conclude \hms{} dominate wherease CITES conclude \lims{} contribute the majority of C.
+C is also generally understood to have strong metallicity dependent CCSNe enrichment.
+
+One of the primary uncertainties of GCE models are nucleosynthetic yields. Yield predictions -- the amounts of each chemical element stars produce --
+are shaped by poorly understood processes, including mass loss, nuclear reaction rates, rotational mixing, convection, and explodability \citep{romano+10,KL14,ventura+13, LC18, emily+21}.
+To better understand where C comes from and how it evolves, our aim is to combine \apogee\ observations and multi-zone models to develop observationally-consistant yields.
+\cite{james+23} examined similar \gce{} models of N (which is closely related to C), finding that trends in N and O are explained by the metallicity dependence of N/O yields.
+\citet{james+23} determine that \agb\ N abundances roughly depend linearly on metallicity (i.e.
+$y_{\rm N}/y_{\rm O} \propto Z$).
+Here, we extend their models to C, deriving similar constraints on C/Mg yields.
+We assess which yield prescriptions reproduce Galactic abundance trends while investigating the impact of \gce{} model assumptions, such as the star formation history (\sfh{}) and outflow mass loading.
+
 \section{Nucleosynthesis}
+We adapt the yield choices of elements besides C from \citet{james+21, james+23}.
+Table \ref{tab:fiducial_mod} contains our fiducial yields. 
+Following \citet{james+21, james+23}, we also take the \ia{} delay time distribution to be a $t^{-1.1}$ power-law with a minimum delay time of 140\,Myr, as suggested by the observations of \citet{maoz+12}.
 
@@
 
-We adapt the yield choices of elements besides C from \citet{james+21, james+23}.
-Table \ref{tab:fiducial_mod} contains our fiducial yields. 
-Following \citet{james+21, james+23}, we also take the \ia{} delay time distribution to be a $t^{-1.1}$ power-law with a minimum delay time of 140\,Myr, as suggested by the observations of \citet{maoz+12}.
-
 \addtocounter{footnote}{-2}
@@
 		\hline
-        C & Eq.~\ref{eq:zeta} & $2.9\times{\rm C11}$ &  0 \\
+        C & Eq.~\ref{eq:zeta} & $2.3\times$\cxi &  0 \\
         O & 0.015 & 0 & 0 \\
@@
 
-An \agb\ star is a low-mass ($\lesssim 8 M_{\sun}$) star during its final phase of evolution.
+An \agb\ star is a low-mass ($\lesssim 8\,\Mo$) star during its final phase of evolution.
 Inside an \agb\ star, an inert CO core is surrounded by thermally-unstable He and H-burning shells below a convective envelope.
@@
 As a result, these stars C abundances are only affected by first dredge-up, resulting in little change to C yields or slight destruction of C.
-Between \about{2} and \about{5} \Mo, third dredge up becomes important, enriching the outer layers with C, making these stars the most important producers of C. 
+Above \about{2}\,\Mo{}, third dredge up becomes important, enriching the outer layers with C.
+\agb\ stars between 2 and 5 \Mo are the most abundant producers of C.
 In \agb\ stars more massive than \about{5}\,\Mo, both hot bottom burning and third dredge up occur; however, hot bottom burning is much more efficient, resulting in significant \C[12] destruction.
@@
     providing necessary well-sampled grids in mass and metallicity. We refer to the yields from the following studies as the following,
+For our models to match observations, we find that need to uniformly amplify these yield tables. We use \cxi\ table, amplified by a factor of 2.9, as the fiducial \agb\ yield.
+Variations in models are due to different treatments of reaction rates, convection, and mass-loss.
 \begin{description}
-    \item \cxi: \citet{cristallo+11, cristallo+15}
-    \item \kx: \citet{karakas10}
-    \item \vxiii: \citet{ventura+13,ventura+14,ventura+18, ventura+20}
-    \item \kxvi: \citet{KL16, karakas+18}
+    \item \hypertarget{C11}{\texttt{C11}}: \citet{cristallo+11, cristallo+15}
+    \item \hypertarget{K10}{\texttt{K10}}: \citet{karakas10}
+\item \hypertarget{V13}{\texttt{V13}}: \citet{ventura+13,ventura+14,ventura+18, ventura+20}
+    \item \hypertarget{K16}{\texttt{K16}}: \citet{KL16, karakas+18}
 \end{description}
-In Appendix~\ref{sec:oob_models}, the masses, metallicites, and notable differences between each yield set are briefly described. 
-For our models to match observations, we find that need to uniformly amplify these yield tables. We use \cxi\ table, amplified by a factor of 2.9, as the fiducial \agb\ yield.
 
@@
 
+\begin{table*}
+	\centering
+    \caption[]{For each \agb\ yield set, the \imf-averaged \agb\ C yield at solar metallicity $y_{\rm C, 0}^{\rm agb}$ and the multiplicative factor reaches an \agb\ contribution of 20\% $\alpha_{\rm agb, 20}$.}
+
+	\label{tab:alpha_agb}
+    \begin{tabular}{c ccc p{5cm} p{5cm}} % four columns, alignment for each
+		\hline 
+        \agb\ table 
+                & $y_{\rm C}^{\rm agb}(\Zo)$ & $\zeta^{\rm agb}(\Zo)$ & $\alpha_{20}^{\rm agb}$
+                & masses (\Mo) & metallicites 
+                \\
+        \hline
+        \cxi 
+                &  0.00042 & -0.0175 & 2.4
+                & 1.3, 1.5, 2, 2.5, 3, 4, 5, 6
+                & 0.0001, 0.0003, 0.001, 0.002, 0.003, 0.006, 0.008, 0.01, 0.014, 0.02
+                \\
+        \kx 
+                & 0.00064 & -0.059 & 1.6
+                & 1, 1.25, 1.5, 1.75, 1.9, 2.25, 2.5, 3, 3.5, 4, 4.5, 5, 5.5, 6 
+                &  0.0001, 0.004, 0.008, 0.02
+                \\
+        \vxiii 
+                & 0.00022 & -0.021 & 4.5
+                & 1.5, 2, 2.5, 3, 3.5, 4, 4.5, 5, 6, 6.5, 7
+                & 0.0003, 0.001, 0.002, 0.004, 0.008, 0.014, 0.04
+                \\
+        \kxvi 
+                & 0.0005 & -0.029 & 2.0
+                & 1, 1.25, 1.5, 1.75, 2.25, 2.5, 2.75, 3, 3.25, 3.5, 3.75, 4, 4.5, 5, 5.5, 6, 7 
+                & 0.0003, 0.001, 0.002, 0.004, 0.008, 0.014, 0.04
+                \\
+		\hline
+	\end{tabular}
+\end{table*}
+
 \begin{figure*}
@@
 The black dashed line shows $\y=0$ for reference.
-Each panel represents yields from one of four \agb\ models: \cxi, \kx{}, \vxiii{}, \kxvi{} (see Section \ref{sec:agb} and  Appendix \ref{sec:oob_models}).
-}
+Each panel represents yields from one of four \agb\ models: \cxi{}, \kx{}, \vxiii{}, \kxvi{}, and our analytic model (see sections \ref{sec:agb}) }
+
         \label{fig:y_agb}
@@
     \centering
+    \includegraphics{y_agb_vs_z.pdf}
     \includegraphics{y_agb_vs_t.pdf}
-    \includegraphics{y_agb_vs_z.pdf}
-
-    \caption[]{ C production by \agb\ stars as a function of \ssp{} age, normalized to the total mass $M_{\rm tot}$ produced at $t=10$\,Gyr.
-\textbf{Left:} The four \agb\ yield models from literature at solar metallicity (\cxi, \kx{}, \vxiii{}, or \kxvi{}).
-The dashed black line shows the delay time distribution of type Ia supernovae ($\propto t^{-1.1}$) for comparison.
-\textbf{Right:} The (\imf-weighted) \agb\ C yield $\Ycagb$ as a function of metallicity for each of the \agb\ yield models.
-($\Ycagb$ is the net mass of C produced by \agb\ stars per unit mass of star formation, after 10\,Gyr and assuming a \citealt{kroupa01} \imf.) }
+
+    \caption[]{ C yields from \agb\ stars as a function of \ssp{} age, as a fraction of the C yield at $t_{\rm end}=10\,$Gyr. 
+\textbf{Left} The (\imf-weighted) \agb\ C yield $\Ycagb$ as a function of metallicity for each of the \agb\ yield models.
+($\Ycagb$ is the net mass of C produced by \agb\ stars per unit mass of star formation, after 10\,Gyr and assuming a \citealt{kroupa01} \imf.)
+    \textbf{Right} Our four considered \agb\ yield models at solar metallicity (\cxi{}, \kx{}, \vxiii{}, \kxvi{}.
+The dashed red line shows the delay time distribution of type Ia supernovae ($\propto t^{-1.1}$) for comparison, and the minimum of V13 is $y(t)/y(t_{\rm end}=-3.3$.
+}
 
@@
 
-Massive stars form $^{12}$C in their cores through the triple--$\alpha$ process.\footnote{The 3-$\alpha$ process fuses 3 He nuclei into O.} 
+Massive stars form $^{12}$C in their cores through the triple--$\alpha$ process.\footnote{The 3-$\alpha$ process fuses 3 He nuclei into \C[12].} 
 However, only C ejected through supernovae and stellar winds contributes to the yield. 
@@
     \includegraphics{cc_yields.pdf}
-    \caption[High-Mass Star Carbon Yields]{
+    \caption[]{
         C yields from high-mass stars.
         \textbf{Left} The \imf-weighted \cc\ yield of C as a function of metallicity.
-        \textbf{Right} The \cc\ [C/Mg] abundance ratio, defined in Eq.~\ref{eq:c_mg_cc}. The black line is the derived C yield from Section \ref{sec:equilibrium},
-    $\Ycc = 0.0028 + 0.001 (Z/Z_{\odot})$. Yields are shown for tables from 
+        \textbf{Right} The \cc\ [C/Mg] abundance ratio, defined in Eq.~\ref{eq:c_mg_cc}.
+The black line is the derived C yield from Section \ref{sec:equilibrium} and Eq.~\ref{eq:zeta}.
+Yields are shown for tables from
     \citet[red triangles]{WW95}, \citet[orange squares and diamonds]{sukhbold+16}, 
@@
     In the top panel, the pink line denotes $\Ycagb$ from \cxi{} for comparison. All models include wind yields. 
-    (OUT OF DATE)
 }
@@
 
-\section{Analytic Approximations}
-In this section, we describe approximations of galactic abundance trends and C yield models.
-While these are insufficient to describe the galaxy in full detail, we can use these simplified models to inform our investigation.
-
 \subsection{Equilibrium Abundances}\label{sec:equilibrium}
 
+Here, we assume a simple \textit{one-zone} chemical evolution model \cite[e.g.][]{tinsley80, pagel09, matteucci21}.
 Galaxies, when moderated by metal-poor gas accretion and feedback-driven outflows, reach a chemical equilibrium.
@@
 
-Here, we assume a simple \textit{one-zone} chemical evolution model \cite[e.g.][]{tinsley80, pagel09, matteucci21}.
-Newly produced metals are homogeneously and instantaneously mixed, so this model evolves as a single, spatially-uniform chemical zone.
-We define $M_{X}$ to be the gas mass of element $X$, $\dot{M}_\star$ to be the star formation rate (in $\Mo\,{\rm yr}^{-1}$), and $\eta$ to be the mass loading factor $\eta\equiv\dot{M}_{\rm outflow}/\dot{M}_\star$ (representing the strength of outflows).
-A \ssp\ returns a fraction $r$ of their birth mass to the interstellar medium, due to ejected stellar envelopes.%
-\footnote{$r\approx0.4$ for a \citealt{kroupa01} \imf.}
-Here, we will use $\alpha$ as a representative $\alpha$-element, such as O or Mg. 
-Given the \imf-averaged yield $y_\alpha$, the rate of change in the gas-phase mass of $\alpha$ is a sum of sources and sinks,
-\begin{equation} \label{eq:mdot_1}
-    \dot{M}_\alpha =  y_\alpha\,\dot{M}_\star - \dot{M}_{\alpha,\,\text{remnants}} - \dot{M}_{\alpha,\,\text{outflows}}
-\end{equation}
-where $y_\alpha\,\dot{M}_{\star}$ describes \cc\ enrichment. 
-In terms of the return mass fraction of stars $r$, the mass lost to remnants is $Z_\alpha\,\dot{M}_\star\,(1-r)$.
-And, the outflows deplete mass at a rate $Z_\alpha \,\dot{M}_\star\,\eta$.
-(We assume the composition of outflows is the same as the interstellar medium.) With these definitions, Eq.~\ref{eq:mdot_1} becomes
-\begin{equation}
-    \dot{M}_\alpha= y_\alpha\,\dot{M}_\star - (1 + \eta - r)\,Z_\alpha\,\dot{M}_\star.
-\end{equation}
-Assuming an exponentially declining star formation history (\sfh{}) $\dot{M}_\star \propto e^{-t/\tau_{\rm sfh}}$, the equilibrium abundance is derived analytically by setting $\dot{Z}_\alpha=0$.
-\begin{equation}\label{eq:z_eq}
-    Z_\alpha^{\rm eq}(R) = \frac{y_\alpha}{1 + \eta(R) - r - \tau_\star / \tau_{\rm sfh}},
-\end{equation}
-where $\tau_{\star}$ is the star formation rate. ($\eta$ depends on $R$ to create a metallicity gradient. See also Section \ref{sec:vice} and Eq.~\ref{eq:eta_r}.)
-In the special case of constant star formation, $\tau_{\rm sfh}\to\infty$ and the denominator simplifies to $1+\eta-r$.
-
-Likewise, for C production, where both \agb\ stars and \cc\ play a role,%
-\footnote{In detail, the \agb\ contribution requires integration over the \sfh\ to account for the finite lifetimes of stars.
-However, for this exponential \sfh, this effect is minimal, so we simply use $\Ycagb$ for the current \agb\ contribution.}
-Eq.~\ref{eq:z_eq} then becomes
-\begin{equation}
-    Z_{\rm C}^{\rm eq}(R) = \frac{\Ycc + \Ycagb}{1 + \eta(R) - r - \tau_\star / \tau_{\rm sfh}}
-\end{equation}
-The equilibrium C/$\alpha$ abundance ratio is then
-\begin{equation}\label{eq:z_co}
-    \frac{Z_{\rm C}^{\rm eq}}{Z_\alpha^{\rm eq}} = \frac{\Ycc + \Ycagb }{y_\alpha}.
-\end{equation}
-Analogous to \cite{james+23} arguments about N, the trends in abundance ratios are set by yield ratios in these \gce{} models.
-The effect of other \gce{} parameters (most importantly $\eta$) cancels.
-As a consequence, yield ratios should establish abundance ratio trends in models which assume a different normalization of element yields and mass-loading (see discussion below).
-This argument can also be inverted to infer  yields from abundance ratio trends.
-To the extent that observed C and $\alpha$ trends reflect the equilibrium abundances in different Galactic regions, we can infer the total C yield.
-\begin{equation}\label{eq:y_c_eq}
-    \Ycc + \Ycagb =  y_\alpha \left(\frac{Z_{\rm C}}{Z_{\alpha}}\right)_\odot 10^{[{\rm C}/\alpha]}.
-\end{equation}
-As we know [C/$\alpha$] as a function of metallicity, Eq.~\ref{eq:y_c_eq} enables us to estimate both the magnitude and metallicity-dependence of $\Yct/y_\alpha$.
+\cite{james+23} show that trends in N and O abundance ratios are set by the yield ratio and their metallicity dependences. 
+Here, we find a similar conclusion for C and Mg, where equilibrium C/Mg is given by
+\begin{equation}\label{eq:equilibrium_yields}
+    \frac{Z_{\rm C}^{\rm eq}}{Z_{\rm Mg}^{\rm eq}} = \frac{\Ycc + \Ycagb }{y_{\rm Mg}}.
+\end{equation}
+
 In Fig.~\ref{fig:analytic}, we show the inferred total C yields, based on this equation, and our best fitting linear model. From a linear regression, we suggest that
@@
 As we will discuss in Section \ref{sec:outflows}, the normalization of yields and $\eta$ is degenerate.
-If we increase yields and $\eta$ by a similar factor, equilibrium abundances from Eq.~\ref{eq:z_eq} would be unchanged, so our model cannot distinguish changes in both yields and outflows.
-
-\begin{figure}
-    \centering
-    \includegraphics{analytic.pdf}
-    \caption[]{Inferred high-mass star C yields as a function of metallicity.
-We assume equilibrium and $3\times {\rm C11}$ \agb\ yields (orange curve, see discussion in Section \ref{sec:equilibrium}).
-Blue points are the median value of $\Ycc$ for each bin in [Mg/H] with uncertainties based on the 16-84 percentile range.
-    }
-    \label{fig:analytic}
-\end{figure}
-
-\subsection{Analytic AGB}
-
-To parameterize the \agb\ contribution to C production, we define $f_{\rm agb}$ to be the fraction of C which comes from \agb\ stars. 
-\begin{equation}\label{eq:f_agb}
-    f_{\rm agb} \equiv \frac{\Ycagb(Z=\Zo)}{\Yct(Z=\Zo)},
-\end{equation}
-In Section \ref{sec:agb_results}, we will show that $f_{\rm agb} \approx 0.2$. 
-None of the \agb\ yield sets (\cxi{}, \kx{}, \vxiii{}, \kxvi{}) produce enough C relative to our total $\Ycc$ values.
-So, we introduce a normalization factor $\alpha_{\rm agb}$, which denotes a multiplicative scaling of $\Ycagb$
-\begin{equation} \label{eq:alpha}
-        \Ycagb \rightarrow \alpha_{\rm agb}\ \Ycagb.
-\end{equation}
-Table~\ref{tab:alpha_agb} contains the required values of $\alpha_{\rm agb}$ to reach $f_{\rm agb}=0.2$, the yields at solar metallicity, and the metallicity for each \agb\ yield set.
-
-We can use the \caafe{} diagram of \apogee\ stars to estimate the delayed portion of C.
-When binned in metallicity, median [C/Mg] changes by about 0.2 dex across the range of [Mg/Fe] at solar metallicities (see Fig.~\ref{fig:caafe_binned}).
-As high-$\alpha$ stars have little to no delayed \ia\ Fe, these stars would also have little to no delayed \agb\ C.
-This means that AGB C stars make up about at most a fraction $f_{\rm agb} \approx 1 - 10^{-0.2} \approx 0.4$ of C production.
-
-We also briefly explore an analytic \agb\ model, defined as a cubic piecewise in mass and linear in metallicity.
-The piecewise is defined to have a maximum at $m_1$ and minimums at
-the end points $m-\delta m_-$ and $m+\delta m_+$. The function becomes constant
-outside of this range with (optionally) negative yields.
-The mass dependence is
-\begin{equation} \label{eq:yca_m}
-\y(m) = 
-\begin{cases}
-\y_0 & m \leq m_0 - \delta m_- \\
-\y_1 + (\y_0 - \y_1)\; f\!\left(\frac{m_0 - m}{\delta m_-}\right) 
-    & m_0 - \delta m_- < m \leq m_0 \\
-    \y_1 + (\y_2 - \y_1)\; f\!\left(\frac{m - m_0}{\delta m_+}\right)
-    & m_0 < m \leq m_0 + \delta m_+ \\
-\y_2 & m_0 + \delta m_+ \leq m
-\end{cases}
-\end{equation}
-where $\y_1$ approximantly represents the total \imf-integrated yield, $\y_0$ and $\y_1$ represent the yields for low-mass and high-mass \agb\ stars respectively, and 
-\begin{equation}
-    f(x) = 3x^2 - 2x^3.
-\end{equation}
-For the full equation, we take the above functional form multiplied by a
-metallicity dependent term, so 
-\begin{equation} \label{eq:yca_z}
-    \y_{\rm C}^{\rm agb}(m, Z) = \frac{\y(m)}{\int_1^8 m\,\y(m)\,{\rm IMF}(m)\;dm} 
-    \left(\y_1 + \zeta \left(Z-\Zo\right) \right)
-\end{equation}
-
-\subsection{CCSNe Carbon Yields}
+If we increase yields and $\eta$ by a similar factor, equilibrium abundances from Eq.~\ref{eq:equilibrium_yields} would be unchanged, so our model cannot distinguish changes in both yields and outflows.
+
 With the total C yield of Eq.~\ref{eq:yc_inferred} and given an \agb\ C yield, we can derive an observationally-consistant \cc\ C yield.
@@
 
-\begin{table}
-	\centering
-    \caption[]{For each \agb\ yield set, the \imf-averaged \agb\ C yield at solar metallicity $y_{\rm C, 0}^{\rm agb}$ and the multiplicative factor reaches an \agb\ contribution of 20\% $\alpha_{\rm agb, 20}$.}
-	\label{tab:alpha_agb}
-	\begin{tabular}{cccr} % four columns, alignment for each
-		\hline 
-    \agb\ Model & $y_{\rm C}^{\rm agb}(\Zo)$ & $\zeta^{\rm agb}(\Zo)$ 
-                & $\alpha_{20}^{\rm agb}$\\
-        \hline
-        \cxi & 4.2E-4 & -0.0175 & 2.4\\
-        \kx & 6.4E-4 & -0.059 & 1.6\\
-        \vxiii & 2.2E-4 & -0.021 & 4.5\\
-        \kxvi & 5E-4 & -0.029 & 2.0\\
-		\hline
-	\end{tabular}
-\end{table}
+\begin{figure}
+    \centering
+    \includegraphics{analytic.pdf}
+    \caption[]{Inferred total C yields as a function of metallicity.
+We assume chemical equilibrium (orange curve, see discussion in Section \ref{sec:equilibrium}).
+Blue points are the median value of $\Ycc$ for each (number) bin in [Mg/H] with uncertainties based on the 16--84 percentile range.
+    }
+    \label{fig:analytic}
+\end{figure}
 
@@
 
+Our models extends the \citet[hereafter \JJ]{james+21} Milky Way model, run with the publicly available Versatile Integrator for Chemical Evolution (\VICE). 
+This model is described extensively in \JJ~and concisely summarized  in \citet{james+23}. Here, we provide a brief overview of the relevant model components.
 Classical, \textit{one-zone} models of chemical evolution assume instantaneous mixing of metals in the star-forming interstellar medium \citep[e.g.][]{matteucci21}.
 This simple framework is a poor approximation of the Milky Way.
-The Galaxy evolves \textit{inside-out}---where star formation is higher towards the center and in the early universe \citep{bird+13}.
+The Galaxy evolves \textit{inside-out} -- where star formation is higher towards the center and in the early universe \citep{bird+13}.
 Additionally, stars can migrate several kpc over their lifetimes, mixing different chemical environments across the galaxy \citep{bird+12,sellwood+binney02}.
 For the rest of this paper, we focus on multi-zone models, which discretize the Galaxy into concentric rings in which stars move between.
-Our models extends the \citet[hereafter \JJ]{james+21} Milky Way model, run with the publicly available Versatile Integrator for Chemical Evolution (\VICE). 
-This model is described extensively in \JJ~and concisely summarized  in \citet{james+23}. Here, we provide a brief overview of the relevant model components.
 
@@
 
+\section{Data Selection}
+
+Subgiants provide the ideal observational constraint to our model. 
+When a star enters the Red Giant Branch (RGB), material from the CNO-processed core is mixed with the envelope in first dredge up, enhancing N and depleting C \citep{iben67, vincenzo+21,KL14}.
+RGB stars thus require model-dependent corrections to recover surface abundances \citep[e.g.][]{vincenzo+21}.
+On the other hand, gravitational settling can affect main sequence stellar abundances \citep[e.g.][]{souto19}.
+Subgiants have well-mixed envelopes, so gravitational settling is not as significant, and subgiants have not yet experienced first dredge up.
+We use a sample of \apogee\ DR17 stars \citep{apogee17} as selected in \citetjack.
+
+When plotting the data and models, we bin by groups of 500 (or 150) stars in [Mg/H] ([Mg/Fe]).
+When plotting \caah, we select only the low-$\alpha$ sequence.
+For \caafe, we instead select stars with $-0.15 \leq {\rm [Mg/H]} \leq -0.05$.
+To create a sample with similar characteristics of the subgiant observations, we sample 12,000 stars from the simulations such that the cumulative distribution function of stars in $R_{\rm gal}$ is the same for the subgiants and our comparison sample.
+
+As the primary observational constraint, we use the criteria outlined in \citetjack~to create a sample of subgiant from \apogee{} DR17 \citep{apogee17}.
+apogee is part of the Sloan Digital Sky Survey and measures high-resolution spectra of thousands of stars \cite{sdss17}.
+Chemical abundances are determined from the \apogee\ Stellar Parameter and Chemical Abundance Pipeline ({\sc aspcap}) \citep{aspcap}.
+
+Photospheric C and N abundances in subgiant are reflective of their birth abundances \citep{gilroy89, korn+07, lind+08, souto+18, souto19} As first dredge up, which affects C and N abundances, only occurs during the ascent onto the RGB, subgiant stars are unaffected by this enrichment.
+
+An alternate approach for this analysis would be to estimate the birth abundances of RGB stars by correcting surface abundance effects from first dredge up as in \cite{vincenzo+21}.
+Subgiants are the more attractive option since these observations do not rely on model-dependent corrections.
+However, RGB stars are more luminous, potentially allowing better coverage of the Galactic disk.
+
+We choose to use \citetjack\ sample as this does not rely on additional layers of modeling, providing a more direct constraint to our model and limiting our systematic uncertainties.
+
+Fig.~\ref{fig:subgiant_selection} shows a plot of all \apogee\ stars and the \citetjack polygon selection criteria. 
+ \citetjack~select a region of stars based on surface gravity $\log g$, and effective surface temperature, $T_\text{eff}$.
+ \begin{equation}
+    \begin{cases} \label{eq:subgiant_selection}
+        \log \text{g} \geq 3.5 \\
+        \log \text{g} \leq 0.004\,T_{\rm eff} - 15.7 \\
+        \log \text{g} \leq 0.000706\,T_{\rm eff} + 0.36 \\
+        \log \text{g} \leq -0.0015\,T_{\rm eff} + 12.05 \\
+        \log \text{g} \geq 0.0012\,T_{\rm eff} - 2.8. \\
+    \end{cases}
+\end{equation}
+Additionally, we included stars in \apogee{} marked by the following flags.
+\begin{description}
+\item \verb|APOGEE_MIRCLUSTER_STAR|
+\item \verb|APOGEE_EMISSION_STAR|
+\item \verb|APOGEE_EMBEDDEDCLUSTER_STAR|
+\item \verb|young cluster (IN-SYNC)|
+\item \verb|APOGEE2_W345|
+\item \verb|EB planet|
+\end{description}
+This cut isolates a clean sample of \about{12,000} subgiants.
+We furthermore isolate the low- and high-$\alpha$ sequences with the cut
+\begin{equation}\label{eq:high_alpha}
+\begin{cases}
+\text{[Mg/Fe]} >0.12-0.13\,\text{[Fe/H]}, & \text{[Fe/H]}<0\\
+\text{[Mg/Fe]} >0.12, & \text{[Fe/H]}>0. \\
+\end{cases}
+\end{equation}
+The low-$\alpha$ sequence is better reproduced by this model, so we use this cut of the subgiants to compare the models against except for comparing \caafe.
+
+\begin{figure}
+    \centering
+    \includegraphics{logg_jack.pdf}
+    \caption[]{
+        A Kiel diagram of \apogee{} stars.
+Following \citetjack, we select subgiants in the black pentagon (see Equation \ref{eq:subgiant_selection}).
+These stars have not yet experienced first dredge-up, so their photospheric C and N abundances should reflect their birth mixture.
+    }
+    \label{fig:subgiant_selection}
+\end{figure}
+
 \section{Results}
@@
 The \caafe{}-diagram is, in essance, an emperical delay-time-distribution for a single stellar population of C, especially as we assume a $\propto t^{-1.1}$ delay-time-distribution for Fe. 
-Comparing the top and bottom panels of Fig.~\ref{fig:c_evo} highlights the differences between \caah\ and \caafe.
+Comparing the left and right panels of Fig.~\ref{fig:c_evo} highlights the differences between \caah\ and \caafe.
 While \caah\ quickly reaches its final equilibrium distribution (within \about{5}\,Gyr), \caafe\ continues to evolve in both [Mg/Fe] and [C/Mg] until the simulation ends.
@@
     Time evolution of gas-phase C abundances in our fiducial model.
-    Each line represents a zone at a different galactic radii.
-The lines are coloured-coded by time.
-The left shows \caah\ and the right \caafe.
-We artificially restrict the axis range in each case to better see solar-annulus and present-day evolution.
-    <UPDATE, CHECK LEFT?RIGHT USAGE>
+    Each line represents a zone at a different galactic radii. The lines are coloured-coded by time. The left shows \caah\ and the right \caafe. 
 }
@@
 \end{figure*}
-
-Fig.~\ref{fig:f_agb_evo} shows $f_{\rm agb}$ calculated from the fiducial model of current effective C yields in the gas phase (using the SFH as a proxy for $\Ycc$. 
-At early times, \cc\ dominate.
-As the galaxy evolves, \agb\ have time to add C, increasing $f_{\rm agb}$.
-However, the metal-rich inner regions lower \agb\ C yields, so these regions never reach as high of a $f_{\rm agb}$ as the outer regions do.
-
-\begin{figure}
-    \centering
-    \includegraphics{f_agb_rt.pdf}
-    \caption[]{The evolution of $f_{\rm agb}$ across the Galaxy and with time.}
-    \label{fig:f_agb_evo}
-\end{figure}
-
-\subsection{Data and Sample Selection}
-
-Subgiants provide the ideal observational constraint to our model. 
-When a star enters the Red Giant Branch (RGB), material from the CNO-processed core is mixed with the envelope in first dredge up, enhancing N and depleting C \citep{iben67, vincenzo+21,KL14}.
-RGB stars thus require model-dependent corrections to recover surface abundances \citep[e.g.][]{vincenzo+21}.
-On the other hand, gravitational settling can affect main sequence stellar abundances \citep[e.g.][]{souto19}.
-Subgiants have well-mixed envelopes, so gravitational settling is not as significant, and subgiants have not yet experienced first dredge up.
-We use a sample of \apogee\ DR17 stars \citep{apogee17} as selected in \citetjack.
-The selection criteria and differences between the samples are described in more detail in Appendix~\ref{sec:jack}.
-
-When plotting the data and models, we bin by groups of 500 (or 150) stars in [Mg/H] ([Mg/Fe]).
-When plotting \caah, we select only the low-$\alpha$ sequence.
-For \caafe, we instead select stars with $-0.15 \leq {\rm [Mg/H]} \leq -0.05$.
-To create a sample with similar characteristics of the subgiant observations, we sample 12,000 stars from the simulations such that the cumulative distribution function of stars in $R_{\rm gal}$ is the same for the subgiants and our comparison sample.
 
@@
     Stellar abundance trends in our model, assuming metallicity independent $\Ycc$.
-Colored lines quantify the median [C/Mg] in bins of [Mg/H] for our four \agb\ yield models from the literature (see Section \ref{sec:agb}).
+Coloured lines represent the median [C/Mg] in bins of [Mg/H] (left) or [Mg/Fe] (right) for each model.
 Black points and grey dashes represent the median and standard deviations of [C/Mg] for each [Mg/H] bin in the \citetjack~sample.
-In the right panel, we show the trends only for stars where $-0.15\leq {\rm [Mg/H]}\leq -0.05$.
+In the right panels, we show the trends only for stars where $-0.15\leq {\rm [Mg/H]}\leq -0.05$.
+    \textbf{Top}: Models with different metallicity dependences for  \cc\ C yiels.
+    \textbf{Middle}: Our four different \agb\ models.
+    \textbf{Bottom}: Different \agb\ fractinos of C.
 }
@@
 \subsection{Low-Mass Stellar Yields}\label{sec:agb_results}
+
+To parameterize the \agb\ contribution to C production, we define $f_{\rm agb}$ to be the fraction of C which comes from \agb\ stars. 
+\begin{equation}\label{eq:f_agb}
+    f_{\rm agb} \equiv \frac{\Ycagb(Z=\Zo)}{\Yct(Z=\Zo)},
+\end{equation}
+In Section \ref{sec:agb_results}, we will show that $f_{\rm agb} \approx 0.2$. 
+None of the \agb\ yield sets (\cxi{}, \kx{}, \vxiii{}, \kxvi{}) produce enough C relative to our total $\Ycc$ values.
+So, we introduce a normalization factor $\alpha_{\rm agb}$, which denotes a multiplicative scaling of $\Ycagb$
+\begin{equation} \label{eq:alpha}
+        \Ycagb \rightarrow \alpha_{\rm agb}\ \Ycagb.
+\end{equation}
+Table~\ref{tab:alpha_agb} contains the required values of $\alpha_{\rm agb}$ to reach $f_{\rm agb}=0.2$, the yields at solar metallicity, and the metallicity for each \agb\ yield set.
+
+We can use the \caafe{} diagram of \apogee\ stars to estimate the delayed portion of C.
+When binned in metallicity, median [C/Mg] changes by about 0.2 dex across the range of [Mg/Fe] at solar metallicities.
+As high-$\alpha$ stars have little to no delayed \ia\ Fe, these stars would also have little to no delayed \agb\ C.
+This means that AGB C stars make up about at most a fraction $f_{\rm agb} \approx 1 - 10^{-0.2} \approx 0.4$ of C production.
 
@@
 
-Finally, in the top row of Fig.~\ref{fig:second_models}, we plot variations of the analytic \agb\ models (Eqns.~\ref{eq:yca_m} and \ref{eq:yca_z})  where C production occurs in different mass ranges.
+Finally, in the top row of Fig.~\ref{fig:second_models}, we plot FINISH where C production occurs in different mass ranges.
 If all C comes from stars with masses $>4\Mo$, then [C/Mg] is almost independent of [Fe/Mg].
@@
 \centering
-\includegraphics{all_p2.pdf}
-
-\caption[]{Similar to Fig.~\ref{fig:first_models}, except where the \agb\ C contribution is varied from the fiducial ($f_{\rm agb}=0.2$) to 0.1 and 0.3 (see Eq.~\ref{eq:f_agb} and Section.~\ref{sec:agb_results}.}
+\includegraphics{nitrogen.pdf}
+
+\caption[]{Similar to Fig.~\ref{fig:first_models}.
+The top panels show models with different mass-ranges contributing \agb\ C yields.
+The middle panels show different star formation histories (section \ref{sec:sfh}) and yield normalizations.
+The bottom panels show [N/Mg] against [Mg/H] and [Fe/Mg] for the fiducial model.
+}
 \label{fig:second_models}
@@
 where $A=1.5$ represents the amplitude of the birth, $\tau_\text{burst}=10.8$\,Gyr is the time where the burst is strongest, and $\sigma_\text{burst}=1$\,Gyr is the width of the burst.
-Our earlyburst model is instead a double exponential, with the second exponential begining at $t_1=5\,$Gyr.
-\begin{equation}\label{eq:twoinfall}
-    \dot{\Sigma}_{\rm earlyburst} \propto A\,e^{-t/\tau_{\rm burst}} + 
-\begin{cases}
-    e^{-(t-t_1)/\tau_\text{sfh}} & t_1 < t \\
-      0 & t<t_1
-\end{cases}
-\end{equation}
-where we take the burst duration, $\tau_{\rm burst}=2$\,Gyr.
-This approximately corresponds to the Gaia-Encelidus merger, inducing higher star formation in the Milky Way \citep{spitoni21, bonaca20, helmi18}.
+% Our earlyburst model is instead a double exponential, with the second exponential begining at $t_1=5\,$Gyr.
+% \begin{equation}\label{eq:twoinfall}
+%     \dot{\Sigma}_{\rm earlyburst} \propto A\,e^{-t/\tau_{\rm burst}} + 
+% \begin{cases}
+%     e^{-(t-t_1)/\tau_\text{sfh}} & t_1 < t \\
+%       0 & t<t_1
+% \end{cases}
+% \end{equation}
+% where we take the burst duration, $\tau_{\rm burst}=2$\,Gyr.
+% This approximately corresponds to the Gaia-Encelidus merger, inducing higher star formation in the Milky Way \citep{spitoni21, bonaca20, helmi18}.
 
@@
 
-\gce{} models of the Milky Way fall into two classes---those which incorporate significant mass-loading (e.g., this work) and those which neglect mass-loading but lower effective yield to match observed abundances \citep[e.g.][]{MCM13, MCM14, spitoni19, spitoni20, spitoni21}.
+Our conclutions are limited by the many uncertainties in \gce\ modeling.
+
+The overall scaling of yields and outflows is unknown and challenging to constrain.
+\gce{} models of the Milky Way fall into two classes -- those which incorporate significant mass-loading (e.g., this work) and those which neglect mass-loading but lower effective yield to match observed abundances \citep[e.g.][]{MCM13, MCM14, spitoni19, spitoni20, spitoni21}.
 An increase in stellar yields has a nearly identical effect as a decrease in the mass-loading factor $\eta$ (see Appendix B of \citealt{james_dwarf}).
@@
 We demonstrate this further here.
-
 The theoretical motivation for decreasing yields is the uncertainty in stellar explodability.
@@
 
+C lines are relatively faint, and surveys such as GALAH struggle against low detection rates, potentially biasing sample measurments. 
+(e.g. gaia-eso AS WELL \citealt{franchini+20}).
+In the gas phase, HII regions are our best window into C abundances.
+Unfortunantly, C lacks strong collisional excitation lines, and recombination lines fall in the ultraviolet without nearby reference H lines \citep{skillman+20}.
+Recombination-line and collisional-excitation-line measurements furthermore disagree by a factor of \about{2} \citep{GR07}.
+
 Fig.~\ref{fig:gas_phase} shows the single-zone model and time-slices of the fiducial multi-zone model at present day and $t=2$\,Gyr. 
 Here, we consider a single-zone model with parameters consistant with the Gaia-Encelidus sausage\footnotemark{}.
-We chose the model to have mass loading $\eta=6$, star formation efficiency $\tau_{\star}=9\,{\rm Gyr}$, and a star formation history $\propto e^{-t/2{\rm\,Gyr}}$, evolved for 6\,Gyr.
+We chose the model to have mass loading $\eta=20$, star formation efficiency $\tau_{\star}=16\,{\rm Gyr}$, and a star formation history $\propto e^{-t/3{\rm\,Gyr}}$, evolved for 2\,Gyr \citep{james_dwarf}.
 The single-zone model is better able to replicate the slope of the abundances in dwarf galaxies, HII-regions, and halo stars.
@@
 \includegraphics[]{summary.pdf}
-\caption[]{Gas-phase C abundances. We plot our model at $t=2$\,Gyr and present day as thick solid lines. Points represent measurements in 
+\caption[]{Gas-phase C abundances. We plot our model at $t=2$\,Gyr and present day as thick solid lines. Black lines are single-zone models. Points represent measurements in 
     HII regions    \citep[pink circles;][]{skillman+20, esteban+02, esteban+09, esteban+14, esteban+19}
@@
     dwarf galaxies \citep[red diamonds;][]{berg+19},
-    Milky Way halo and thick disk stars \citep[green stars;][]{nissen+14, fabbian+09},
+    Milky Way halo and thick disk stars \citep[green stars;][]{amarsi+19, nissen+14, fabbian+09},
     and Milky Way high-$\alpha$ stars (yellow points; \citealtjack).
-    (OUT OF DATE)
 }
@@
 
-\section{The Subgiant Sample}\label{sec:jack}
-
-As the primary observational constraint, we use the criteria outlined in \citetjack~to create a sample of subgiant from \apogee{} DR17 \citep{apogee17}.
-apogee is part of the Sloan Digital Sky Survey and measures high-resolution spectra of thousands of stars \cite{sdss17}.
-Chemical abundances are determined from the \apogee\ Stellar Parameter and Chemical Abundance Pipeline ({\sc aspcap}) \citep{aspcap}.
-
-Photospheric C and N abundances in subgiant are reflective of their birth abundances \citep{gilroy89, korn+07, lind+08, souto+18, souto19} As first dredge up, which affects C and N abundances, only occurs during the ascent onto the RGB, subgiant stars are unaffected by this enrichment.
-
-An alternate approach for this analysis would be to estimate the birth abundances of RGB stars by correcting surface abundance effects from first dredge up as in \cite{vincenzo+21}.
-Subgiants are the more attractive option since these observations do not rely on model-dependent corrections.
-However, RGB stars are more luminous, potentially allowing better coverage of the Galactic disk.
-
-We choose to use \citetjack\ sample as this does not rely on additional layers of modeling, providing a more direct constraint to our model and limiting our systematic uncertainties.
-
-Fig.~\ref{fig:subgiant_selection} shows a plot of all \apogee\ stars and the \citetjack polygon selection criteria. 
- \citetjack~select a region of stars based on surface gravity $\log g$, and effective surface temperature, $T_\text{eff}$.
- \begin{equation}
-    \begin{cases} \label{eq:subgiant_selection}
-        \log \text{g} \geq 3.5 \\
-        \log \text{g} \leq 0.004\,T_{\rm eff} - 15.7 \\
-        \log \text{g} \leq 0.000706\,T_{\rm eff} + 0.36 \\
-        \log \text{g} \leq -0.0015\,T_{\rm eff} + 12.05 \\
-        \log \text{g} \geq 0.0012\,T_{\rm eff} - 2.8. \\
-    \end{cases}
-\end{equation}
-Additionally, we included stars in \apogee{} marked by the following flags.
-\begin{itemize}
-\item \verb|APOGEE_MIRCLUSTER_STAR|
-\item \verb|APOGEE_EMISSION_STAR|
-\item \verb|APOGEE_EMBEDDEDCLUSTER_STAR|
-\item \verb|young cluster (IN-SYNC)|
-\item \verb|APOGEE2_W345|
-\item \verb|EB planet|
-\end{itemize}
-This cut isolates a clean sample of \about{12,000} subgiants.
-We furthermore isolate the low- and high-$\alpha$ sequences with the cut
-\begin{equation}\label{eq:high_alpha}
-\begin{cases}
-\text{[Mg/Fe]} >0.12-0.13\,\text{[Fe/H]}, & \text{[Fe/H]}<0\\
-\text{[Mg/Fe]} >0.12, & \text{[Fe/H]}>0. \\
-\end{cases}
-\end{equation}
-The low-$\alpha$ sequence is better reproduced by this model, so we use this cut of the subgiants to compare the models against except for comparing \caafe.
-
-\begin{figure}
-    \centering
-    \includegraphics{logg_jack.pdf}
-    \caption[]{
-        A Kiel diagram of \apogee{} stars.
-Following \citetjack, we select subgiants in the orange polygon (see Equation \ref{eq:subgiant_selection}).
-These stars have not yet experienced first dredge-up, so their photospheric C and N abundances should reflect their birth mixture.
-    }
-    \label{fig:subgiant_selection}
-\end{figure}
-
-\section{\agb\ Yield Models} \label{sec:oob_models}
-A brief summary of the four \agb\ models we consider, the masses and metallicites of each yield set, and differences between the models.
-
-\hypertarget{C11}{\texttt{C11}}. 
-Yields from \citet{cristallo+11,cristallo+15}. 
-Models include masses 1.3, 1.5, 2.0, 2.5, 3.0, 4.0, 5.0, and 6.0 \Mo; and 
-metallicities $Z = $ 0.0001, 0.0003, 0.001, 0.002, 0.003, 0.006, 0.008, 0.01, 0.014, 0.02. 
-C11 uses a higher triple-$\alpha$ reaction rate than others and has weaker hot bottom burning, so
-
-\hypertarget{K10}{\texttt{K10}}.
-Yields are published in \citet{karakas10}. 
-Models include masses  1.0, 1.25, 1.5, 1.75, 1.9, 2.25, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0 \Mo;
-and metallicities $Z=$ 0.0001, 0.004, 0.008, 0.02.
-K10 use an ad-hoc mass-loss prescription which likely is not physical as opacities are poorly understood.
-K10 also has a lower temperature at the base of the convective envelope so hot bottom burning is not as strong as other models, likely explaining why low-metallicity C yields are higher.
-
-\hypertarget{V13}{\texttt{V13}} 
-Yields are published in \citet{ventura+13,ventura+14,ventura+18,vincenzo+21}, 
-Models include masses 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 6.0, 6.5, 7.0 \Mo; 
-and metallicities $Z=$ 0.0003, 0.001, 0.002, 0.004, 0.008, 0.014, 0.04.
-\vxiii is evololved with DHFJKSLDF,
-\vxiii is unusual in that hot bottom burning is much stronger than other models due to more efficient convection and higher temperatures at the base of the convective envelope, resulting in much lower stellar yields and negative yields above solar metallicities.
-
-\hypertarget{K16}{\texttt{K16}} 
-Yields are published in \citet{KL16,karakas+18}
-Models include masses 1.0, 1.25, 1.5, 1.75, 2.25, 2.5, 2.75, 3.0, 3.25, 3.5, 3.75, 4.0, 4.5, 5.0, 5.5, 6.0, 7.0 \Mo; 
-and metallicities $Z=$ 0.0003, 0.001, 0.002, 0.004, 0.008, 0.014, 0.04.
-This yield set was extended up to metallicities of 0.1 in DFJSD; however, we do not consider this range here.
-K16 has stronger dredge up than C11, but lower 3-alpha reaction rates.
-However, K16 has more rapid puses and stays higher mass for longer.
-HBB is stronger at high mass than C11.
-
-\begin{figure}
-    \centering
-    \includegraphics{apogee_caafe_binned}
-    \caption{hello}
-    \label{fig:caafe_binned}
-\end{figure}
-
 \bsp	% typesetting comment

### 2023-08-01 run.py
newer models

@@ -4,6 +4,15 @@ import sys
 import os
 
 
+M_LOW_DEFAULT = 1.3
+M_MID_DEFAULT = 2.3
+M_HIGH_DEFAULT = 4
+N_THREADS_DEFAULT = 1
+DT_DEFAULT = 0.02
+SIGMA_R_DEFAULT = 1.27
+ZETA_AGB_DEFAULT = -0.02
+
+
 def main():
     args = parse_args()
     filename = args.filename
@@ -14,7 +23,7 @@ def main():
     if args.test_run and args.threads is None:
         args.threads = 1
     elif args.threads is None:
-        args.threads = 8
+        args.threads = N_THREADS_DEFAULT
 
     if not filename:
         filename = generate_filename(args)
@@ -56,7 +65,7 @@ def parse_args():
                         help="""The migration mode. Default is diffusion.
                         Acceptable options include post-process, linear, 
                         sudden, and rand_walk""")
-    parser.add_argument("-S", "--sigma_R", default=1.27, type=float,
+    parser.add_argument("-S", "--sigma_R", default=SIGMA_R_DEFAULT, type=float,
                         help="migration strength in kpc/Gyr^0.5")
     parser.add_argument("-F", "--filename", default=None,
                         help="the name of the output file ")
@@ -64,9 +73,9 @@ def parse_args():
                         help="the amplitude of the late burst")
     parser.add_argument("-i", "--fe_ia_factor", default="None", 
                         help="the iron yield factor of type Ia supernovae ")
-    parser.add_argument("-d", "--timestep", type=float, default=0.01, 
+    parser.add_argument("-d", "--timestep", type=float, default=DT_DEFAULT, 
                         help="the size of the time step ")
-    parser.add_argument("-n", "--n_stars", type=int, default=2, 
+    parser.add_argument("-n", "--n_stars", type=int, default=1, 
                         help="the number of stars")
     parser.add_argument("-a", "--alpha_n", type=float, default=0, 
                         help="the agb fraction of primary N (0.0)")
@@ -74,13 +83,13 @@ def parse_args():
                         help="only run a test")
     parser.add_argument("-j", "--threads", default=None, type=int,
                         help="number of threads to run. default=1")
-    parser.add_argument("--m_low", default=1.3,
+    parser.add_argument("--m_low", default=M_LOW_DEFAULT,
[…]

### 2023-08-01 surp/yields.py

@@ -47,6 +47,7 @@ def set_yields(eta=1, zeta=None, fe_ia_factor=None,
     eta
     
     """
+    set_defaults()
 
     set_fe(fe_ia_factor)
 
@@ -66,7 +67,6 @@ def set_yields(eta=1, zeta=None, fe_ia_factor=None,
     
     vice.yields.ccsne.settings["c"] = C_CC_model(zeta=zeta, y0=y_cc)
 
-    set_defaults()
 
     set_eta(eta)
 
@@ -237,7 +237,7 @@ def calc_zeta(agb_model, alpha_agb, zeta_agb):
 
 
 def a_agb(m_low=1.3, m_mid=None, m_high=4, yl_agb=0, ym_agb=5e-4, yh_agb=0,
-        zeta_agb=-0.03):
+        zeta_agb=-0.03, mz_agb=0):
     """
     An analytic version of AGB yields.
 
@@ -250,6 +250,7 @@ def a_agb(m_low=1.3, m_mid=None, m_high=4, yl_agb=0, ym_agb=5e-4, yh_agb=0,
     ym_agb: the total yield
     yh_agb: the yield at m_high 
     zeta_agb: the metallicity dependent part of the yield at ym_agb
+    mz_agb: mass-metallicity coupling constant
     """
     if m_mid is None:
         m_mid = (m_low + m_high)/2
@@ -272,7 +273,7 @@ def a_agb(m_low=1.3, m_mid=None, m_high=4, yl_agb=0, ym_agb=5e-4, yh_agb=0,
             m_h = -8
         else:
             print("warning, negative z, z=", z)
-        return A_agb * y_spline(m) * (ym_agb + zeta_agb * (z - Z_Sun) )
+        return A_agb * y_spline(m + mz_agb*m_h) * (ym_agb + zeta_agb * (z - Z_Sun) )
     return inner
 
 

### 2023-08-01 carbon_paper/tex/main.tex
tex updates

@@
 \documentclass[fleqn,
-%referee,
+% referee,
 usenatbib]{mnras}
@@
 \newcommand{\VICE}{\textsc{vice}}
+
 \newcommand{\citetjack}{Roberts et al.~(2023, in prep.)}
@@
 \newcommand{\vxiii}{\texttt{\hyperlink{V13}{V13}}}
-\newcommand{\cfactor}{2.3}
+\newcommand{\cfactor}{2.4}
 
@@
 % gas phase
-While reliable gas-phase and low-metallicity measurments of C are challenging, we find that our model and a singlezone model with our recommended yields replicate the broad trends of \caah{} across different environments and metallicities.
+While reliable gas-phase and low-metallicity measurments of C are challenging, we find that our model and a single-zone model with our recommended yields replicate the broad trends of \caah{} across different environments and metallicities.
 
@@
     As our primary observational constraint, we use a sample of subgiant stars from the \apogee{} \citep{apogee17} selected by the criteria in Roberts et al. (2023, in prep).
-    According to stellar evolution theory and observations \citep{gilroy89, korn+07, lind+08, souto+18, souto19}, these stars have not yet experienced \textit{first dredge up}%
-\footnote{First dredge up is when material from CNO processed core is mixed with the (convective) stellar envelop during the ascent onto the RGB.
-As a result, C is decreased and N is increased depending on the strength of this process and the envelop mass.}
-yet have well-mixed envelopes. So, subgiant surface abundances most accurately represent their birth composition. 
-In contrast, evolved RGB stars require modelling-dependent corrections to recover birth C abundances \citep[e.g.][]{vincenzo+21}. 
+According to stellar evolution theory and observations, subgiants most accurately represent their birth composition \citep{gilroy89, korn+07, lind+08, souto+18, souto19}.
 Fig.~\ref{fig:subgiants} shows the subgiant sample plotted in \caah\ and \caafe{}. [C/Mg] increases with metallicity, and [C/Mg] decreases with [Mg/Fe] at fixed [Mg/H]. 
 Using the subgiant abundance trends, we will develop a model of the enrichment sources and evolution of C.
-
-\begin{figure*}
-    \centering
-    \includegraphics{subgiants.pdf}
-    \caption{The [C/Mg] ratio against [Mg/H] (top) and [Mg/Fe] (bottom) for the \citetjack~sample of \apogee{} subgiants.
-On the top, we plot high and low-$\alpha$ stars in blue and orange, using the separation defined in Equation \ref{eq:high_alpha} (the high and low-$\alpha$ stars are named for their high or low $\alpha$-element to Fe ratios, or in this case, Mg/Fe).
-On the bottom, we colour-code stars according to their [Mg/H] abundance.} \label{fig:subgiants}
-\end{figure*}
 
@@
 
+\section{Data Selection}
+
+\begin{figure*}
+    \centering
+    \includegraphics{subgiants.pdf}
+    \caption{The [C/Mg] ratio against [Mg/H] (top) and [Mg/Fe] (bottom) for the \citetjack~sample of \apogee{} subgiants.
+On the top, we plot high and low-$\alpha$ stars in blue and orange, using the separation defined in Equation \ref{eq:high_alpha} (the high and low-$\alpha$ stars are named for their high or low $\alpha$-element to Fe ratios, or in this case, Mg/Fe).
+On the bottom, we colour-code stars according to their [Mg/H] abundance.} \label{fig:subgiants}
+\end{figure*}
+
+Subgiants provide the ideal observational constraint to our model. 
+When a star enters the Red Giant Branch (RGB), material from the CNO-processed core is mixed with the envelope in first dredge up, enhancing N and depleting C \citep{iben67, vincenzo+21,KL14}.
+RGB stars thus require model-dependent corrections to recover surface abundances \citep[e.g.][]{vincenzo+21}.
+On the other hand, gravitational settling can affect main sequence stellar abundances \citep[e.g.][]{souto19}.
+Subgiants have well-mixed envelopes, so gravitational settling is not as significant, and subgiants have not yet experienced first dredge up.
+We use a sample of \apogee\ DR17 stars \citep{apogee17} as selected in \citetjack.
+Chemical abundances are determined from the \apogee\ Stellar Parameter and Chemical Abundance Pipeline ({\sc aspcap}) \citep{aspcap}.
+
+Fig.~\ref{fig:subgiant_selection} shows a plot of all \apogee\ stars and the \citetjack polygon selection criteria. 
+ \citetjack~select a region of stars based on surface gravity $\log g$, and effective surface temperature, $T_\text{eff}$.
+ \begin{equation}
+    \begin{cases} \label{eq:subgiant_selection}
+        \log \text{g} \geq 3.5 \\
+        \log \text{g} \leq 0.004\,T_{\rm eff} - 15.7 \\
+        \log \text{g} \leq 0.000706\,T_{\rm eff} + 0.36 \\
+        \log \text{g} \leq -0.0015\,T_{\rm eff} + 12.05 \\
+        \log \text{g} \geq 0.0012\,T_{\rm eff} - 2.8. \\
+    \end{cases}
+\end{equation}
+Additionally, we exclude stars in \apogee{} marked by any of the following flags.
+\begin{description}
+\item \verb|APOGEE_MIRCLUSTER_STAR|
+\item \verb|APOGEE_EMISSION_STAR|
+\item \verb|APOGEE_EMBEDDEDCLUSTER_STAR|
+\item \verb|young cluster (IN-SYNC)|
+\item \verb|APOGEE2_W345|
+\item \verb|EB planet|
+\end{description}
+Our final sample contains \about{12,000} subgiants.
+
+When plotting the data and models, we bin by groups of 500 (or 150) stars in [Mg/H] ([Mg/Fe]).
+When plotting \caah, we select only the low-$\alpha$ sequence.
+For \caafe, we instead select stars with $-0.15 \leq {\rm [Mg/H]} \leq -0.05$.
+When plotting \caah, we isolate the low- and high-$\alpha$ sequences with the cut
+\begin{equation}\label{eq:high_alpha}
+\begin{cases}
+\text{[Mg/Fe]} >0.12-0.13\,\text{[Fe/H]}, & \text{[Fe/H]}<0\\
+\text{[Mg/Fe]} >0.12, & \text{[Fe/H]}>0. \\
+\end{cases}
+\end{equation}
+The low-$\alpha$ sequence is better reproduced by this model, so we use this cut of the subgiants to compare the models against except for comparing \caafe.
+
+\begin{figure}
+    \centering
+    \includegraphics{logg_jack.pdf}
+    \caption[]{
+        A Kiel diagram of \apogee{} stars.
+Following \citetjack, we select subgiants in the black pentagon (see Equation \ref{eq:subgiant_selection}).
+These stars have not yet experienced first dredge-up, so their photospheric C and N abundances should reflect their birth mixture.
+    }
+    \label{fig:subgiant_selection}
+\end{figure}
+
 \section{Nucleosynthesis}
-We adapt the yield choices of elements besides C from \citet{james+21, james+23}.
 Table \ref{tab:fiducial_mod} contains our fiducial yields. 
-Following \citet{james+21, james+23}, we also take the \ia{} delay time distribution to be a $t^{-1.1}$ power-law with a minimum delay time of 140\,Myr, as suggested by the observations of \citet{maoz+12}.
-
-Yields -- the amounts of each chemical element stars synthesise -- are central to studies of galactic chemical evolution (GCE). 
-In this section, we compare literature yield predictions and discuss our fiducial yield choices. 
-We focus on three nucleosynthetic pathways: asymptotic giant branch (\agb{}) stars, core collapse supernovae (\cc{}), and type Ia supernovae (\ia{}).
-C is produced in both \agb{} and \cc{} stars.
-We also use Mg and Fe as tracers of \cc{} and \ia{} enrichment respectively. 
-O and Mg are produced almost entirely from \cc\ with metallicity-independent yields. In contrast, Fe is produced in similar amounts by \cc\ and \ia.
-
-After a single stellar population (SSP)\footnotemark{} forms, \cc{} are the first chemical enrichers.
-\cc{} explode within $\lesssim 40$\,Myr, providing light elements (e.g.
-C, O, and Mg) and heavier elements (Fe and beyond).
-Next, low-mass stars begin to reach the end of their lives, entering the \agb{} phase.
-By shedding their outer layers, \agb{} stars are important sources of C, N, and neutron capture elements.
-Finally, white dwarfs explode in \ia{}, releasing Fe and other iron-peak elements.
-
-\footnotetext{SSP: Single stellar population. Technical name for a group of stars born in the same conditions at the same time, i.e. an open cluster.}
-
-To quantify yields, we define the stellar yield to be the fraction of a stars initial mass which is newly synthesized and released as a given element. 
-For an element $X$ and star with mass $M$, the net-fractional stellar yield $\y$ is 
-\begin{equation}
-\y_{X} =  \Delta Z_X \frac{M_{\rm ejected}}{M_{\rm birth}}
-\end{equation}
-where $M_{\rm ejected}$ and $M_{\rm birth}$  are the total ejected mass and the birth mass of the star, and $\Delta Z_X$ is the change in $Z_X$ from the birth material to the ejected material of the star.%
-\footnote{$Z_{X}$ represents the mass fraction of element $X$.}
-%
-For example, a 1\,\Mo\ star with $\y_{\C} = 10^{-3}$ will add $10^{-3}\,\Mo$ of new C to the interstellar medium. 
-Also, note that yields may be negative if the material returned to the interstellar medium has a lower abundance $Z_X$ than the material the star was formed from.
-Although per-star yields are necessary to compute \agb{} star enrichment rates in \gce{}  models, initial-mass-function (\imf) averaged yields are useful in interpreting their predictions.
-An IMF-averaged yield adds together the yields of stars of each mass, weighted by the fraction of stars of each mass (the \imf).
-Given the fractional yield $\y(M, Z)$ as a function of initial stellar mass $M$ and metallicity $Z$, the \imf-averaged yield is given by 
-\begin{equation} \label{eq:imf-yield}
-    y_{\rm X}(Z,t) = 
-    \frac{
-    \int_{M_{\rm min}(t)}^{M_{\rm max}} 
-    \y_{\rm X}(M, Z)
-    \frac{dN}{dM}\ M\ dM
-}
-{
-    \int \frac{dN}{dM}\ M\ dM
-}
-\end{equation}
-where ${dN}/{dM}$ is the \imf, $M_{\rm max}=100\,\Mo$ is the maximum stellar mass, and $M_{\rm min}(t)$ is the mass of stars with lifetime $t$.\footnotemark{}
-To calculate the \imf-averaged net yields, we use the Versatile Integrator for Chemical Evolution code (\VICE).\footnotemark{}
-
-\addtocounter{footnote}{-2}
-    \stepcounter{footnote}\footnotetext{In our model, the mass-lifetime relation is
-$\log \tau_M = 1.02 - 3.57\log M + 0.90 \left(\log M\right)^2$,
-where $\tau_M$ is in Gyr, from \citealt{larson74}.
-We use $t_{\rm end}=10\,$Gyr for total yields when $t$ is not used.}
-
-\stepcounter{footnote}\footnotetext{\VICE~is available at \url{https://github.com/giganano/VICE}}
+For O, N, Mg, and Fe, we adapt the yield choices of \citet{james+21, james+23}.
+Following \citet{james+21, james+23}, we take the \ia{} delay time distribution to be a $t^{-1.1}$ power-law with a minimum delay time of 140\,Myr, as suggested by the observations of \citet{maoz+12}.
 
@@
 	\centering
-    \caption[]{Yields for the fiducial model (in units of \ssp~birth mass). See Section \ref{sec:agb} for the definition of \cxi.}
+    \caption[]{Yields for the fiducial model (in units of \ssp~birth mass). See section \ref{sec:agb} for the definition of \cxi.}
 	\label{tab:fiducial_mod}
@@
 		\hline
-        C & Eq.~\ref{eq:zeta} & $2.3\times$\cxi &  0 \\
+        C & Eq.~\ref{eq:zeta} & $\cfactor\times$\cxi &  0 \\
         O & 0.015 & 0 & 0 \\
@@
 
-An \agb\ star is a low-mass ($\lesssim 8\,\Mo$) star during its final phase of evolution.
-Inside an \agb\ star, an inert CO core is surrounded by thermally-unstable He and H-burning shells below a convective envelope.
+    In this work, we explore four different sets of \agb\ star yield tables from literature,
+    providing necessary well-sampled grids in mass and metallicity. We refer to the yields from the following studies as the following,
+\begin{description}
+    \item \hypertarget{C11}{\texttt{C11}}: \citet{cristallo+11, cristallo+15}
+    \item \hypertarget{K10}{\texttt{K10}}: \citet{karakas10}
+\item \hypertarget{V13}{\texttt{V13}}: \citet{ventura+13,ventura+14,ventura+18, ventura+20}
+    \item \hypertarget{K16}{\texttt{K16}}: \citet{KL16, karakas+18}
+\end{description}
+Table~\ref{tab:agb} contains the masses and metallicities used in each model.
+
+Fig.~\ref{fig:y_agb} compares the stellar \agb\ C yields for these four models.
+We define the stellar \agb\ yield to be the fraction of the stars initial mass $M$ which is newly synthesized into C.
+If $\Delta Z_{\rm C}$ represents the change in the mass fraction of C abundance, then
+\begin{equation}
+    \y_{\rm C}^{\rm agb} =  \Delta Z_{\rm C} \frac{M_{\rm ejected}}{M}.
+\end{equation}
+Note that yields may be negative if the material returned to the interstellar medium has a lower abundance $Z_{\rm C}$ than the material the star was formed from.
+Most models agree on the qualitative shape of the net fractional \agb\ C yield.
+Stellar yields peak between masses of about 2--4 \Mo and decline as stars become more or less massive.
+As metallicity increases, the total \agb\ C yield decreases.
+The mass of peak C yields also increases slightly with metallicity.
+
+The left panel of Fig.~\ref{fig:agb-ssp} shows \imf-averaged C yields for each \agb\ model as a function of metallicity.
+An IMF-averaged yield adds together the yields of stars of each mass, weighted by the fraction of stars of each mass (the \imf). 
+\begin{equation} \label{eq:imf-agb-yield}
+    \Ycagb(Z,t) = 
+    \frac{
+    \int_{M_{\rm to}(t)}^{8\,\Mo} 
+    \y_{\rm X}(M, Z)
+    \frac{dN}{dM}\ M\ dM
+}
+{
+    \int_{0.08\Mo}^{100\Mo} \frac{dN}{dM}\ M\ dM
+}
+\end{equation}
+where ${dN}/{dM}$ is the \imf{} and $M_{\rm to}(t)$ is the mass of stars with lifetime $t$.%
+\footnotetext{In our model, the mass-lifetime relation is
+$\log \tau_M = 1.02 - 3.57\log M + 0.90 \left(\log M\right)^2$,
+where $\tau_M$ is in Gyr, from \citealt{larson74}.
+We use $t_{\rm end}=10\,$Gyr for total yields when $t$ is not used.}
+The \agb\ models mostly differ in their yield normalization and metallicity dependence. 
+All yield models span a range of \about{2} for a given metallicity.
+For example, all four models predict $y_\text{C}^\text{agb}(\Zo)$ to be between 0.004 and 0.008 at solar metallicity.
+The models also differ slightly in the strength of metallicity dependence, with about a factor of 3 discrepency (see Table~\ref{tab:agb}).
+
+Fig.~\ref{fig:agb-ssp}, on the right, shows the total production of C by \agb\ stars in a \ssp{} at an age $t$, i.e. $\y_{\rm C}(Z_\odot, t)$. 
+As the mass range $2\,\Mo\lesssim M \lesssim 4\,\Mo$ is most important for C production, about half of C production occurs before \about{1}\,Gyr, similar to \ia\ Fe. 
+\kx{} and \kxvi{} weight C production more heavily towards high-mass \agb\ stars resulting in a faster enrichment delay time, whereas the \cxi\ and \vxiii\ models predict a slightly longer timescale of \about{1}\,Gyr.
+In any case, little to no C is produced more than 2\,Gyr after a star formation event.
+Fe production, in contrast, continues steadily for 10\,Gyr.
+
 In an \agb\ star, two competing processes determine the outcome of C production: \textit{third dredge up} and \textit{hot bottom burning}.  
@@
 
-Hot bottom burning and third dredge-up result in mass-dependent C yields. 
+Hot bottom burning and third dredge-up result in mass and metallicity dependent C yields. 
 Stars less than \about{2}\,\Mo do not experience third dredge-up.
@@
 In \agb\ stars more massive than \about{5}\,\Mo, both hot bottom burning and third dredge up occur; however, hot bottom burning is much more efficient, resulting in significant \C[12] destruction.
-
-    In this work, we explore four different sets of \agb\ star yield tables from literature,
-    providing necessary well-sampled grids in mass and metallicity. We refer to the yields from the following studies as the following,
-For our models to match observations, we find that need to uniformly amplify these yield tables. We use \cxi\ table, amplified by a factor of 2.9, as the fiducial \agb\ yield.
-Variations in models are due to different treatments of reaction rates, convection, and mass-loss.
-\begin{description}
-    \item \hypertarget{C11}{\texttt{C11}}: \citet{cristallo+11, cristallo+15}
-    \item \hypertarget{K10}{\texttt{K10}}: \citet{karakas10}
-\item \hypertarget{V13}{\texttt{V13}}: \citet{ventura+13,ventura+14,ventura+18, ventura+20}
-    \item \hypertarget{K16}{\texttt{K16}}: \citet{KL16, karakas+18}
-\end{description}
-
-Fig.~\ref{fig:y_agb} compares the stellar \agb\ C yields for these four models.
-Most models agree on the qualitative shape of the net fractional \agb\ C yield.
-Stellar yields peak between masses of about 2--4 \Mo and decline as stars become more or less massive.
-As metallicity increases, the total \agb\ C yield decreases.
-The mass of peak C yields also increases slightly with metallicity.
 Metal poor stars dredge up more material due to the decreased power of the CNO cycle, resulting in increasing carbon yields with decreasing metalicity \citep{ventura+13}.
 
-Fig.~\ref{fig:agb-ssp}, on the left, shows the total production of C by \agb\ stars in a \ssp{} at an age $t$, i.e. $\y_{\rm C}(Z_\odot, t)$. 
-As the mass range $2\,\Mo\lesssim M \lesssim 4\,\Mo$ is most important for C production, about half of C production occurs before \about{1}\,Gyr, similar to \ia\ Fe. 
-\kx{} and \kxvi{} weight C production more heavily towards high-mass \agb\ stars resulting in a faster enrichment delay time, whereas the \cxi\ and \vxiii\ models predict a slightly longer timescale of \about{1}\,Gyr.
-In any case, little to no C is produced more than 2\,Gyr after a star formation event.
-Fe production, in contrast, continues steadily for 10\,Gyr.
-
-The right panel of Fig.~\ref{fig:agb-ssp} shows \imf-averaged C yields for each \agb\ model as a function of metallicity.
-\vxiii{} differs in that it shows a non-monotonic metallicity dependence. However, this effect is only for models with $\log Z/Z_\odot \lesssim -1$.
-Otherwise, models differ only in their yield normalization and metallicity dependence. 
-All yield models span a range of \about{2} for a given metallicity.
-For example, all four models predict $y_\text{C}^\text{agb}(\Zo)$ to be between 0.004 and 0.008 at solar metallicity.
-The models also differ slightly in the strength of metallicity dependence, with about a factor of 3 discrepency (see Table~\ref{tab:alpha_agb}).
+For our models to match observations, we find that need to uniformly amplify these yield tables.
+\begin{equation} \label{eq:alpha}
+        \Ycagb \rightarrow \alpha_{\rm agb}\ \Ycagb.
+\end{equation}
+We use \cxi\ table, with $\alpha_{\rm agb}=\cfactor$, as the fiducial \agb\ yield.
+Variations in models are due to different treatments of reaction rates, convection, and mass-loss.
+Table~\ref{tab:agb} contains the stellar masses and metallicites each yield set contains, the approximate solar C yield $\Ycagb(\Zo)$, the metallicity dependence at solar $\zeta^{\rm agb} = d\Ycagb/dZ$, and the required factor $\alpha$ to reach 20\% \agb\ C production.
 
@@
 
-	\label{tab:alpha_agb}
+	\label{tab:agb}
     \begin{tabular}{c ccc p{5cm} p{5cm}} % four columns, alignment for each
@@
 
-Massive stars form $^{12}$C in their cores through the triple--$\alpha$ process.\footnote{The 3-$\alpha$ process fuses 3 He nuclei into \C[12].} 
+Massive stars form $^{12}$C in their cores through the triple--$\alpha$ process.
 However, only C ejected through supernovae and stellar winds contributes to the yield. 
@@
 
-Fig.~\ref{fig:y_cc} plots calculations of the \imf-integrated yields, defined with Eq.~\ref{eq:imf-yield} (computed using \VICE's \texttt{vice.yields.ccsne.fractional} function). 
+Fig.~\ref{fig:y_cc} plots calculations of the \imf-integrated yields.
+For \cc\, 
+\begin{equation} \label{eq:imf-cc-yield}
+    \Ycc(Z) = 
+    \frac{
+    \int_{8\,\Mo}^{100\,\Mo} 
+    \y_{\rm X}(M, Z)
+    \frac{dN}{dM}\ M\ dM
+}
+{
+    \int_{0.08\Mo}^{100\Mo} \frac{dN}{dM}\ M\ dM
+}
+\end{equation}
+where ${dN}/{dM}$ is the \imf{} and $M_{\rm to}(t)$ is the mass of stars with lifetime $t$.%
 \cc{} models predict a wide range of C yields, spanning almost a factor of ten. 
@@
 Different \cc\ models also span a large range in [C/Mg].
-We chose to instead parameterize $\Ycc$ to simplify model inputs, as most \cc\ models fail to achieve near-solar [C/Mg].
 
-Both rotation and explodability introduce substantial variations.
+Rotation, binarity, and explodability introduce substantial uncertainties in \cc\ predictions.
 The \cite{LC18} models include rotation, showing that variations in the rotational velocity of the star can dramatically increase the magnitude and metallicity dependence of $\Ycc$.
@@
 As fewer high-mass stars explode, both C and Mg yields decrease, but Mg yields decrease more as more C is lost to winds, so [C/Mg] increases with decreasing explodability.
+Finally, stripped binaries produce about twice as much C as single massive stars and other effects of binary evolution are unstudied \citep{farmer+21}.
 
-O and Mg are both $\alpha$-elements, light elements produced in \cc{} through He-nuclei fusion. 
-As we focus on constraining relative yields, we neglect O and Mg yield variations in the main text (excluding the uniform scaling of yields and massloading in Section~\ref{sec:outflows}).
-There is substantial variation in predicted Mg yields.
-Most models predict relatively flat trends metallicity (even with rotation as in \citealt{LC18}). 
+\cc\ do not satisfactorily explain C, O, and Mg abundances.
+Most models here overproduce C relative to Mg. This could be related to overproduction of O relative to Mg, a known problem of \cc\ models.
+There is substantial variation in predicted Mg yields but most models predict flat trends.
 However, the variation is significant and our adopted $\Yoc$ yield is much higher than most models, but O and Mg yields of \cc\ models do not fully match observations.
@@
 Here, we assume ${\rm [O/Mg]} = 0$, which nevertheless consistent with \apogee{} observations \citep{weinberg+19, weinberg+22}.
+ As we focus on constraining relative yields, we neglect O and Mg yield variations in the main text, leaving them constant and metallicity-independent. We also choose to parameterize C yields.
 
@@
         \textbf{Right} The \cc\ [C/Mg] abundance ratio, defined in Eq.~\ref{eq:c_mg_cc}.
-The black line is the derived C yield from Section \ref{sec:equilibrium} and Eq.~\ref{eq:zeta}.
+The black line is the derived C yield from section \ref{sec:equilibrium} and Eq.~\ref{eq:zeta}.
 Yields are shown for tables from
@@
 
-Here, we assume a simple \textit{one-zone} chemical evolution model \cite[e.g.][]{tinsley80, pagel09, matteucci21}.
 Galaxies, when moderated by metal-poor gas accretion and feedback-driven outflows, reach a chemical equilibrium.
 The production of new metals is balanced by losses to new stars and outflows \citep{larson72, dalcanton07, FD08, PS11, lilly13}.
+Here, we assume a simple \textit{one-zone} chemical evolution model \cite[e.g.][]{tinsley80, pagel09, matteucci21}.
 While our galaxy is likely not in perfect equilibrium or described by a single, homogeneous chemical
@@
 \cite{james+23} show that trends in N and O abundance ratios are set by the yield ratio and their metallicity dependences. 
-Here, we find a similar conclusion for C and Mg, where equilibrium C/Mg is given by
+Here, we find a similar conclusion for C and Mg (see section xxx in \citealt{james+21}), where equilibrium C/Mg is given by
 \begin{equation}\label{eq:equilibrium_yields}
@@
 \end{subequations}
-These yield ratios results in an equilibrium abundance $[{\rm C}/\alpha] = -0.09$, which is consistent with the subgiant sample and is within \about{20\%} of the solar C/Mg mixture from \citet{asplund+09}.
+These yield ratios results in an equilibrium abundance $[{\rm C}/\alpha] = -0.09$ at solar metallicity, which is consistent with the subgiant sample and is within \about{20\%} of the solar C/Mg mixture from \citet{asplund+09}.
 
 Both observational and theoretical uncertainties limit the accuracy of our relative yield predictions.
-As the metallicity range of our data is small ($-0.4\lesssim {\rm [Mg/H]} \lesssim 0.4$),
-our model does not extend beyond near-solar metallicities.
 Additionally, the derived yields will be systematically biased if the galaxy is out of equilibrium, for example, due to a recent starburst \citep{mor+19,isern19}.
-As we will discuss in Section \ref{sec:outflows}, the normalization of yields and $\eta$ is degenerate.
-If we increase yields and $\eta$ by a similar factor, equilibrium abundances from Eq.~\ref{eq:equilibrium_yields} would be unchanged, so our model cannot distinguish changes in both yields and outflows.
 
@@
 This method reduces the number of free parameters of the model and enables all models to match \caah\ trends in \apogee{} subgiants when considering \agb\ yields with different metallicity dependences and normalizations.
-Table~\ref{tab:alpha_agb} contains our adaptive (regression-derived) values of $\zeta^{\rm agb}$ and $\Ycagb(\Zo)$. 
+We use values of $\Ycagb$ and $\zeta^{\rm agb}$ as presented in Table~\ref{tab:agb}.
 For example, in our fiducial model, $\Ycc = 0.004 + 0.102 (Z-\Zo)$.
 Our full \cc\ C yield model adds a low-metallicity enhancement term, which is insignificant at solar metallicities (e.g.
-thin disk stars) but enables models in Section~\ref{sec:gas} to match low-metallicity environments.
+thin disk stars) but enables models in section~\ref{sec:gas} to match low-metallicity environments.
 We parameterize low-metallicity enrichment with $y_l$ and $Z_l$, the yield and transition metallicity for enhanced low-metallicity yields.
@@
     \caption[]{Inferred total C yields as a function of metallicity.
-We assume chemical equilibrium (orange curve, see discussion in Section \ref{sec:equilibrium}).
+We assume chemical equilibrium (orange curve, see discussion in section \ref{sec:equilibrium}).
 Blue points are the median value of $\Ycc$ for each (number) bin in [Mg/H] with uncertainties based on the 16--84 percentile range.
@@
 
-Our models extends the \citet[hereafter \JJ]{james+21} Milky Way model, run with the publicly available Versatile Integrator for Chemical Evolution (\VICE). 
+Our models extends the \citet[hereafter \JJ]{james+21} Milky Way model, run with the publicly available Versatile Integrator for Chemical Evolution (\VICE).%
+    \footnote{\VICE~is available at \url{https://github.com/giganano/VICE}}
 This model is described extensively in \JJ~and concisely summarized  in \citet{james+23}. Here, we provide a brief overview of the relevant model components.
@@
 Additionally, stars can migrate several kpc over their lifetimes, mixing different chemical environments across the galaxy \citep{bird+12,sellwood+binney02}.
-For the rest of this paper, we focus on multi-zone models, which discretize the Galaxy into concentric rings in which stars move between.
+Multi-zone models account for stellar migration and changing environments by including multiple zones with different chemical conditions which stars can move between.
 
@@
 
-To account for radial migration, we use the \texttt{h277} hydrodynamical
-simulation results (with simulation parameters as in \citealt{bird+21}; see also \citealt{christensen12, zolotov12, loebman12, BZ14}).  
-Each \VICE\ single stellar population (SSP) is matched to an \textit{analog} in \texttt{H277}, chosen to form at a similar time and radius $R$.
-By taking the change in radius $\Delta R$ of the analogs, the SSPs move to their final radii with a $\sqrt{\text{time}}$ dependence.
+To account for radial migration, we use a Gaussian-based migration scheme.
 The $\Delta R \propto \sqrt{\rm time}$ dependence arises when migration proceeds as a consequence of the diffusion of angular momentum \citep{frankel18, frankel20}.
+As such, at each time step, each star particle moves some change in radius, based on 
+\begin{subequations}
+    \begin{align}
+        \delta R &\sim N(0, \sigma_R)\\
+        \sigma_R &= 1.27\,{\rm kpc} \left(\frac{dt}{1\,{\rm Gyr}}\right)^{0.5}
+    \end{align}
+\end{subequations}
+where $N(\mu, \sigma)$ represents a draw from normal distribution.
 We do not account for radial gas flows.
-Using the results of a hydrodynamical simulation without modification limits the free parameters in the model; however, we are limited to one dynamical history. 
-We also explore a normal-distribution random walk migration based on \citet{frankel18}, without noticeable impacts on our results.
-All models shown here use the \texttt{h277}-based migration.
+Not shown here, we also explore migration based on the \texttt{h277} hydrodynamical
+simulation results (with simulation parameters as in \citealt{bird+21}; see also \citealt{christensen12, zolotov12, loebman12, BZ14}), which leaves our qualitative conclusions unchanged. 
 The full impact of the details of a galaxy's dynamical history on its chemical evolution is still unknown.
@@
 As the strength of outflows controls the resulting $\alpha$-element abundances, \JJ~create a metallicity gradient by defining
-\begin{equation}\label{eq:eta_r}
+\begin{equation}\label{eq:mass_loading}
 \eta(R) = r - 1 + \frac{y_{\alpha}^{\rm CC}}{Z_{\alpha, \odot}} 10^{(-0.08\,\text{kpc}^{-1})(R-4\,\text{kpc})+0.3}.
@@
 This choice of $\eta(R)$ results in a [$\alpha$/H] gradient consistent with Milky Way observations \citep[e.g.][]{hayden+14, weinberg+19, frinchaboy+13}.
+Note that if we change our assumed $y_{\rm Mg}$, the values of $\eta$ will change similarly to maintain the correct chemical trends.
 
-\section{Data Selection}
-
-Subgiants provide the ideal observational constraint to our model. 
-When a star enters the Red Giant Branch (RGB), material from the CNO-processed core is mixed with the envelope in first dredge up, enhancing N and depleting C \citep{iben67, vincenzo+21,KL14}.
-RGB stars thus require model-dependent corrections to recover surface abundances \citep[e.g.][]{vincenzo+21}.
-On the other hand, gravitational settling can affect main sequence stellar abundances \citep[e.g.][]{souto19}.
-Subgiants have well-mixed envelopes, so gravitational settling is not as significant, and subgiants have not yet experienced first dredge up.
-We use a sample of \apogee\ DR17 stars \citep{apogee17} as selected in \citetjack.
-
-When plotting the data and models, we bin by groups of 500 (or 150) stars in [Mg/H] ([Mg/Fe]).
-When plotting \caah, we select only the low-$\alpha$ sequence.
-For \caafe, we instead select stars with $-0.15 \leq {\rm [Mg/H]} \leq -0.05$.
 To create a sample with similar characteristics of the subgiant observations, we sample 12,000 stars from the simulations such that the cumulative distribution function of stars in $R_{\rm gal}$ is the same for the subgiants and our comparison sample.
-
-As the primary observational constraint, we use the criteria outlined in \citetjack~to create a sample of subgiant from \apogee{} DR17 \citep{apogee17}.
-apogee is part of the Sloan Digital Sky Survey and measures high-resolution spectra of thousands of stars \cite{sdss17}.
-Chemical abundances are determined from the \apogee\ Stellar Parameter and Chemical Abundance Pipeline ({\sc aspcap}) \citep{aspcap}.
-
-Photospheric C and N abundances in subgiant are reflective of their birth abundances \citep{gilroy89, korn+07, lind+08, souto+18, souto19} As first dredge up, which affects C and N abundances, only occurs during the ascent onto the RGB, subgiant stars are unaffected by this enrichment.
-
-An alternate approach for this analysis would be to estimate the birth abundances of RGB stars by correcting surface abundance effects from first dredge up as in \cite{vincenzo+21}.
-Subgiants are the more attractive option since these observations do not rely on model-dependent corrections.
-However, RGB stars are more luminous, potentially allowing better coverage of the Galactic disk.
-
-We choose to use \citetjack\ sample as this does not rely on additional layers of modeling, providing a more direct constraint to our model and limiting our systematic uncertainties.
-
-Fig.~\ref{fig:subgiant_selection} shows a plot of all \apogee\ stars and the \citetjack polygon selection criteria. 
- \citetjack~select a region of stars based on surface gravity $\log g$, and effective surface temperature, $T_\text{eff}$.
- \begin{equation}
-    \begin{cases} \label{eq:subgiant_selection}
-        \log \text{g} \geq 3.5 \\
-        \log \text{g} \leq 0.004\,T_{\rm eff} - 15.7 \\
-        \log \text{g} \leq 0.000706\,T_{\rm eff} + 0.36 \\
-        \log \text{g} \leq -0.0015\,T_{\rm eff} + 12.05 \\
-        \log \text{g} \geq 0.0012\,T_{\rm eff} - 2.8. \\
-    \end{cases}
-\end{equation}
-Additionally, we included stars in \apogee{} marked by the following flags.
-\begin{description}
-\item \verb|APOGEE_MIRCLUSTER_STAR|
-\item \verb|APOGEE_EMISSION_STAR|
-\item \verb|APOGEE_EMBEDDEDCLUSTER_STAR|
-\item \verb|young cluster (IN-SYNC)|
-\item \verb|APOGEE2_W345|
-\item \verb|EB planet|
-\end{description}
-This cut isolates a clean sample of \about{12,000} subgiants.
-We furthermore isolate the low- and high-$\alpha$ sequences with the cut
-\begin{equation}\label{eq:high_alpha}
-\begin{cases}
-\text{[Mg/Fe]} >0.12-0.13\,\text{[Fe/H]}, & \text{[Fe/H]}<0\\
-\text{[Mg/Fe]} >0.12, & \text{[Fe/H]}>0. \\
-\end{cases}
-\end{equation}
-The low-$\alpha$ sequence is better reproduced by this model, so we use this cut of the subgiants to compare the models against except for comparing \caafe.
-
-\begin{figure}
-    \centering
-    \includegraphics{logg_jack.pdf}
-    \caption[]{
-        A Kiel diagram of \apogee{} stars.
-Following \citetjack, we select subgiants in the black pentagon (see Equation \ref{eq:subgiant_selection}).
-These stars have not yet experienced first dredge-up, so their photospheric C and N abundances should reflect their birth mixture.
-    }
-    \label{fig:subgiant_selection}
-\end{figure}
 
@@
 \end{description} 
-The fiducial model uses the \cxi{} \agb\ yield tables uniformly scaled by a factor of 2.9 (see Section \ref{sec:agb}, and Table \ref{tab:fiducial_mod}).
+The fiducial model uses the \cxi{} \agb\ yield tables uniformly scaled by a factor of \cfactor{} (see section \ref{sec:agb}, and Table \ref{tab:fiducial_mod}).
 
 Fig.~\ref{fig:c_evo} shows time evolution tracks of the fiducial model for \caah\ and \caafe. 
-As discussed in Section~\ref{sec:equilibrium}, \caah\ is set by the total C/Mg yields. 
+As discussed in section~\ref{sec:equilibrium}, \caah\ is set by the total C/Mg yields. 
 \caafe\ is instead useful in understanding delayed C production. 
@@
 
-C evolution proceeds as follows, (for a single zone)
+C evolution proceeds as follows, 
 \begin{enumerate}
@@
 
-\subsection{High-Mass Stellar Yields}\label{sec:results_highmass}
+\subsection{Yield Variations}\label{sec:results_highmass}
+\label{sec:agb_results}
 
@@
 
-\subsection{Low-Mass Stellar Yields}\label{sec:agb_results}
-
 To parameterize the \agb\ contribution to C production, we define $f_{\rm agb}$ to be the fraction of C which comes from \agb\ stars. 
@@
 \end{equation}
-In Section \ref{sec:agb_results}, we will show that $f_{\rm agb} \approx 0.2$. 
-None of the \agb\ yield sets (\cxi{}, \kx{}, \vxiii{}, \kxvi{}) produce enough C relative to our total $\Ycc$ values.
-So, we introduce a normalization factor $\alpha_{\rm agb}$, which denotes a multiplicative scaling of $\Ycagb$
-\begin{equation} \label{eq:alpha}
-        \Ycagb \rightarrow \alpha_{\rm agb}\ \Ycagb.
-\end{equation}
-Table~\ref{tab:alpha_agb} contains the required values of $\alpha_{\rm agb}$ to reach $f_{\rm agb}=0.2$, the yields at solar metallicity, and the metallicity for each \agb\ yield set.
 
@@
 
-Finally, in the top row of Fig.~\ref{fig:second_models}, we plot FINISH where C production occurs in different mass ranges.
-If all C comes from stars with masses $>4\Mo$, then [C/Mg] is almost independent of [Fe/Mg].
-On the other hand, if all C comes from stars with masses between 1 and 2 \Mo, then [C/Mg] increases across almost the whole range of [Fe/Mg].
-As the observed trend in \caafe\ is almost linear, then the delay-time-distribution of C is similar to Fe, so C is likely produced in a mix of stars between 1 and 4\Mo.
-We cannot constrain upper-intermediate \agb\ C production as this behaves similar to \cc\ C.
-
 \begin{figure*}
@@
 }
-\label{fig:second_models}
+\label{fig:nitrogen}
 \end{figure*}
@@
 
-The middle row of Fig.~\ref{fig:second_models} shows three models with our alternate \sfh{}.
+The middle row of Fig.~\ref{fig:first_models} shows three models with our alternate \sfh{}.
 Changes to the \sfh{} leave \caah\ unchanged, but they do introduce slight variation in \caafe.
@@
 
-The middle row of Fig.~\ref{fig:second_models} also shows a model where $\eta$ and yields are decreased by a factor 0.3.
-While changing the value of $\eta$ affects the metallicity distribution of stars, the model still evolves along the same paths.
-Our model is unable to differentiate a uniform decrease in both outflows and yields.
-
 \subsection{Degeneracies} \label{sec:outflows}
@@
 
-The overall scaling of yields and outflows is unknown and challenging to constrain.
-\gce{} models of the Milky Way fall into two classes -- those which incorporate significant mass-loading (e.g., this work) and those which neglect mass-loading but lower effective yield to match observed abundances \citep[e.g.][]{MCM13, MCM14, spitoni19, spitoni20, spitoni21}.
-An increase in stellar yields has a nearly identical effect as a decrease in the mass-loading factor $\eta$ (see Appendix B of \citealt{james_dwarf}).
-The equilibrium arguments discussed in Section \ref{sec:equilibrium} suggest however that abundance ratios are independent of the choice of normalization and the value of $\eta$.
-We, therefore, expect our results regarding the relative yield $y_{\rm C}/y_{\rm Mg}$ and its metallicity dependence to extend to the other class of models omitting mass loading.
-We demonstrate this further here.
-The theoretical motivation for decreasing yields is the uncertainty in stellar explodability.
-If fewer \hms\ explode, then the yields will be reduced by some factor.
-Additionally, some fraction of supernovae ejecta may be lost directly to an outflow, lowering effective yields.
-To explore reduced outflow models, we lower both $\eta$ and all yields by the same factor to leave the equilibrium abundances unchanged.
+A known uncertainty is the overall scaling of outflows and yields. While Milky Way \gce{} models like ours incorperate significant mass-loading, others
+neglect mass-loading and instead use lower yields \citep[e.g.][]{MCM13, MCM14, spitoni19, spitoni20, spitoni21}.
+Our parameterization of $\eta$ illustrates this (see Equation~\ref{eq:mass_loading}) -- lowering $y_\alpha$ will additionly lower our values of $\eta$. 
+We consider a model where our adapted values of all yields are halved, in the bottom row of Fig.~\ref{fig:first_models}. This change does not affect our results.
 
 An addition source of theoretical uncertainty in this result is that the \ia\ yield and delay time distributions have their own uncertainties.
-We do compute models (not shown here) where $y_{\rm Fe}^{\rm Ia}$ is varied.
-Increasing $y_{\rm Fe}^{\rm Ia}$ has a similar affect as decreasing $f^{\rm agb}$.
-Here, we only show models with $y_{\rm Fe}^{\rm Ia} = 0.00214$ and a $t^{-1.1}$ delay-time-distribution choices from the fiducial model here.
+Increasing both $y_{\rm Fe}^{\rm Ia}$ and $\Ycagb$ correspondingly leaves \caafe\ mostly unchanged.
+We show a model where we increase \ia Fe yields by 20\% and increase $f_{\rm agb}$ to 0.3, leaving median trends unchanged.
+
+Finally, the specific masses of \agb\ stars do affect the delay-time-distribution.
+If \agb\ are produced more by \about{1}\,\Mo stars than upper-intermediate \agb\ stars, then the delay-time-distribution of \agb\ C is more extended.
+In this case, a
+On the other hand, upper-intermediate \agb\ stars with masses greater than 5\,\Mo have lifetimes less than about 100\,Myr, which is only slightly longer than \cc.
+As such, changes to the amount of C from \cc\ and 5--8\Mo \agb\ stars is nearly indestinguashible from median abundance trends alone.
 

### 2024-02-20 carbon_paper/notes/analytic_agb.tex
udpated figs, mcmc singlezone

\hypertarget{the-equation}{%
\section{The equation}\label{the-equation}}

Literature AGB yields generally have the following properties:

\begin{itemize}
\tightlist
\item
  a peak yield at mass between 2 and \(3\,M_\odot\)
\item
  asymmetric peak
\item
  near zero yield at both \(1\,M_\odot\) and \(8\,M_\odot\)
\item
  total yield with decreases with metallicity
\item
  peak mass which increases with metallicity
\item
  negative yields at lowest and highest masses at high metallicity
\end{itemize}

As a simple working model, we use a piecewise cubic spline in mass and
an independent linear relationship in log-metallicity. Our parameters
are

\begin{itemize}
\tightlist
\item
  \(m_0\)
\item
  \(\delta m_+\)
\item
  \(\delta m_-\)
\item
  \(\zeta = dy/dz\)
\item
  \(y_1\), the total yield at solar metallicity
\item
  \(y_0\), the (negative) low-mass yield
\item
  \(y_2\), the (negative) upper-intermediate-mass yield
\end{itemize}

The piecewise is defined to have a maximum at \(m_0\) and minimums at
the end points \(m_-\) and \(m_+\). The function becomes constant
outside of this range with (optionally) negative yields.

And the resulting equation (excepting a prefactor)

\[
y(m) = \begin{cases}
y_0 & m < m_- \\
y_0 + (y_1 - y_0) \left(3 (\frac{m - m_-}{m_0 - m_-})^2 - 
2 (\frac{m-m_-}{m_0 - m_-})^3\right) & m_- < m < m_0 \\
y_1 + (y_2 - y_1) \left(3 (\frac{m - m_0}{m_+ - m_0})^2 - 
2 (\frac{m-m_0}{m_+ - m_0})^3\right) & m_0 < m < m_+ \\
y_2 & m_+ > m
\end{cases}
\]

For the full equation, we take the above functional form multiplied by a
metallicity dependent term, so \[
y_{\rm C}^{\rm AGB}(m, Z) = \frac{y(m) \left[y_1 + \zeta \log_{10}(Z/Z_\odot) \right]}{\int_1^8 m\,y(m)\,{\rm IMF}(m)\;dm}
\]

\hypertarget{comparison-to-existing-models}{%
\subsection{Comparison to existing
models}\label{comparison-to-existing-models}}

\includegraphics{figures/analytic_vs_studies_agb.pdf} A comparison
between the analytic yield model and the literature models. The AGB
IMF-integrated yield is plotted for each model as a function of mass.
Each panel displays the models at a different metallicity. As the AGB
literature models qualitatively agree, the analytic model's asymmetric
piecewise yield with a linear metallicity dependence reproduces the
qualitative behavior of the yields within the range spanned by the
models.

\includegraphics{figures/agb_ana_vs_z.pdf}\\
The metallicity dependence of four literature models and the analytic
AGB yield. The linear approximation is adequate since most models have
approximately linear metallicity dependence at solar \(Z\) and are
monotonic.

\includegraphics{figures/agb_ana_dtd.pdf}\\
The DTD of the same literature models and out analytic model. The
analytic model sits within the DTDs of all of the literature models with
the same qualitative shape. However, without the negative low and high
mass yields, the analytic model does not exhibit the overshoot at the
beginning and ends.

\hypertarget{effects-of-alternate-parameters}{%
\section{Effects of alternate
parameters}\label{effects-of-alternate-parameters}}

\hypertarget{metallicity-dependence}{%
\subsection{Metallicity dependence}\label{metallicity-dependence}}

Interestingly, the metallicity dependence of AGB yields does matter.
Increasing the metallicity dependence ``flattens'' the caafe
relationship. While we do only select one metallicity, because of the
delay time of AGB yields, the higher Mg/Fe stars, which are formed with
a rapidly declining SFH, reach higher metallicities faster. This means
that the AGB progeneters are at lower metallicity than in regions where
Mg/Fe is lower. As AGB yields are predicted to have a negative
metallicity dependence, the resulting trends are flattened.

We also note that the metallicity dependence of AGB yields is directly
degenerate with the metallicity dependence of CCSNe in caah as this is
mostlhy sensitive to the combined metallicity dependence of
IMF-integrated C yields.

\includegraphics{figures/agb_z_dependence.pdf}\\
Each line plots a model with a different metallicity dependence. As the
metallicity dependence is increased (from z0 to z-15), the model is less
steep in caafe.

\hypertarget{mass-distribution}{%
\subsection{Mass distribution}\label{mass-distribution}}

The masses which are important for AGB C production furthermore
complicate results. When only upper intermediate mass stars produce C,
the AGB componet is produced more quickly, resulting in a flatter caafe,
similar to a higher CCSNe C fraction.

One way to conceptualize the caafe diagram is as a comparison between
the Fe and C DTDs. As this diagram is selected in metallicity, the stars
should trace out the shape of a single stellar population born at the
target metallicity -0.1. As Fe and C are produced, the track moves from
bottom right (low Fe and C) to top left (higher Fe and C) with a shape
dependent on the timescales for each process. When AGB C is weighted
heavily towards low mass stars \(\sim 1\,M_\odot\), then the DTD for AGB
is slower than Fe, resulting in a curve which bends up. On the other
hand, if the masses are weighted towards higher mass stars, then the DTD
instead bends down as C is produced quicker initially but slower at
large times than Fe.

As our obervations suggest either a non-monotonic or streight
relationship between Fe and C DTDs, we can conclude that C is produced
with a similar overall DTD as Fe is.

We can furthermore compare the effects of shifting the DTD. For our
example, m0.9 shifts up the mass of the DTD and m1,1 shifts down the
mass. as expected, both of these shifts have similar effects to the
previous investigation. However, bu shifting up the mass, the negative
yields at low masses in C11 results in a sharper down-turn than we would
expect.

\includegraphics{figures/agb_mass.pdf}
\includegraphics{figures/shift_mass.pdf}

\hypertarget{negative-yields}{%
\subsection{Negative yields}\label{negative-yields}}

\includegraphics{figures/negative_yields.pdf} The models with negative
yields. When the low mass end of AGB stars destroy carbon, the end of
the caafe model turns down at low Mg/Fe since these are the longer lived
stars. When the high mass AGB stars destroy carbon, then only the high
Mg/Fe exhibits a dip. In either case, the effect of adding negative
yields results in a non-monotonic caafe diagram. However, we expect the
high-mass yields to be less visible as the system evolves more quickly
than at the end.

\hypertarget{alternate-sfh}{%
\subsection{Alternate SFH}\label{alternate-sfh}}

\includegraphics{figures/twoexp_strength.pdf} These are variations of
the earlyburst model in increasing strength. The effect of these two
strong bursts is to initially drop C/Mg at the beginning of the burst
and then to overhoot C/Mg at later times when Mg/Fe is closer to solar
as star formation slows down.

\hypertarget{degeneracies}{%
\section{Degeneracies}\label{degeneracies}}

\includegraphics{figures/ia_agb_degeneracy.pdf} As the caafe depends on
both the C and Fe DTD, by adjusting both the fraction of SNeIa Fe and
AGB C simultaneously, the effects can be canceld out, so this causes an
uncertainty in the model.

### 2024-02-20 models/make_params.py

@@ -39,6 +39,7 @@ def parse_args():
     parser.add_argument("-z", "--zeta", type=float, default=None, 
                         help="the metallicity dependence of CCSNe C. By default calculated from emperical relationships")
 
+
     parser.add_argument("-e", "--eta", type=float, default=1,
                         help="a uniform factor to scale yields by")
     parser.add_argument("-s", "--spec", default="insideout", 
@@ -57,6 +58,8 @@ def parse_args():
                         help="the multiplicative amplitude of the late burst")
     parser.add_argument("-i", "--fe_ia_factor", default=1, type=float,
                         help="the iron yield factor of type Ia supernovae ")
+    parser.add_argument("-R", "--RIa", default="plaw", 
+                        help="SNe Ia DTD")
 
     parser.add_argument("--alpha_agb", default=None,
                         help="manually set the AGB scaling factor?")
@@ -71,9 +74,9 @@ def parse_args():
     parser.add_argument("--zeta_agb", default=-0.1,
                         help="metallicity dependence of AGB C in the analytic model")
 
-    parser.add_argument("--yl_cc", default=8.67e-4, 
+    parser.add_argument("--yl_cc", default=8.67e-4, type=float,
                         help="the C CC yield at Z=0")
-    parser.add_argument("--zl_cc", default=0, 
+    parser.add_argument("--zl_cc", default=0, type=float,
                         help="Metallicity to switch to low Z CC")
 
     parser.add_argument("-d", "--timestep", type=float, default=0.02, 
@@ -138,6 +141,7 @@ def generate_filename(parser, args):
     filename += arg_to_fname(parser, args, "migration_mode", name="")
     filename += arg_to_fname(parser, args, "sigma_R", depends = (args.migration_mode in ["gaussian", "rand_walk"]))
     filename += arg_to_fname(parser, args, "fe_ia_factor", name="fe_ia")
+    filename += arg_to_fname(parser, args, "RIa")
     filename += arg_to_fname(parser, args, "agb_n_model", name="N")
     filename += arg_to_fname(parser, args, "conroy_sf", flag=True)
     filename += arg_to_fname(parser, args, "timestep", name="dt")
@@ -190,6 +194,7 @@ def generate_params(args):
         conroy_sf = args.conroy_sf,
         yield_kwargs= yield_kwargs,
         zone_width = args.zone_width,
+        RIa = args.RIa,
     )
 
     return kwargs

### 2024-02-20 surp/gce_math.py

@@ -51,7 +51,7 @@ def brak_to_abund(data, ele, ele2="h"):
         return 10**data * vice.solar_z(ele) / vice.solar_z(ele2)
 
 def molar_mass(ele):
-    return molmass.ELEMENTS[ele.upper()].mass
+    return molmass.ELEMENTS[ele.title()].mass
 
 def A_to_Z(A, ele, mixing_correction=0, X=0.71):
     logZ = (A - 12)  + np.log10(X * mmass(ele)) 

### 2024-02-20 surp/simulation/multizone_sim.py

@@ -47,6 +47,7 @@ def create_model(filename, timestep=0.02,
         sigma_R=1.27, 
         verbose=False,
         conroy_sf=False, 
+        RIa="plaw",
         zone_width=0.01):
 
     """"
@@ -139,6 +140,8 @@ def create_model(filename, timestep=0.02,
     model.bins = np.arange(-3, 3, 0.01)
     model.setup_nthreads = n_threads
     model.nthreads = min(len(model.elements), n_threads)
+    model.RIa = RIa
+    print("sneia model: ", RIa)
     print("using setup threads = ", n_threads)
     print("using model threads = ", model.nthreads)
             

### 2024-02-20 surp/vincenzo.py

@@ -66,8 +66,8 @@ def vincenzo2021():
     data["[c/h]"] = raw["CHbirth_stars_bracket"]
     data["[n/h]"] = raw["NHbirth_stars_bracket"]
 
-    data["[n/o]"] = log_to_bracket(raw["NObirth_stars"], "n", "o")
-    data["[c/n]"] = log_to_bracket(raw["CNbirth_stars"], "c", "n")
+    data["[n/o]"] = gcem.log_to_brak(raw["NObirth_stars"], "n", "o")
+    data["[c/n]"] = gcem.log_to_brak(raw["CNbirth_stars"], "c", "n")
 
     data["age"] = raw["age_stars"]
 

### 2024-02-20 surp/yields.py

@@ -25,7 +25,7 @@ ZETA_C_0 = 0.029
 # comments from linear regression of sampled points
 # regression ran on points with M_H > -1 except -1.5 for P16 and -2 for C11
 Y_C_AGB = {
-        "cristallo11": 3.0e-4, # 2.8 pm 0.5
+        "cristallo11": 3.8e-4, # 2.8 pm 0.5
         "ventura13": 2.1e-4, # 3.0 pm 1.3
         "karakas16": 3.6e-4, # 4.3 pm 0.6
         "pignatari16": 6.9e-4, # 7.5 pm 1.5
@@ -33,7 +33,7 @@ Y_C_AGB = {
 }
 
 ZETA_C_AGB = {
-        "cristallo11": -0.015, # -0.032 pm 0.004
+        "cristallo11": -0.01, # -0.032 pm 0.004
         "ventura13": -0.04, #  -0.04 pm 0.01
         "karakas16": -0.04, # -0.04 pm 0.006
         "pignatari16": -0.01, # -0.010 pm 0.16
@@ -115,6 +115,7 @@ def set_c_yields(
     mass_factor: float = 1,
     no_negative: bool = False,
     a_agb_kwargs: dict = {},
+    interp_kind: str = "linear",
     **kwargs
     ):
     """
@@ -153,12 +154,13 @@ def set_c_yields(
         if "zeta_agb" not in a_agb_kwargs.keys():
             raise ValueError("for analytic AGB model, zeta_agb must be specified")
 
-        y0 = alpha_agb * Y_C_AGB["A"]
-        agb.settings["c"] = C_AGB_Model(y0=y0, **a_agb_kwargs)
+        y0 = alpha_agb * y_c_agb
         zeta_agb = a_agb_kwargs["zeta_agb"]
+        a_agb_kwargs["zeta_agb"] *= alpha_agb
+        agb.settings["c"] = C_AGB_Model(y0=y0, **a_agb_kwargs)
     else:
         agb.settings["c"] = interpolator("c", agb_model, prefactor=alpha_agb,
-            mass_factor=mass_factor, no_negative=no_negative)
+            mass_factor=mass_factor, no_negative=no_negative, interp_kind=interp_kind)
         zeta_agb = ZETA_C_AGB[agb_model]
 
 
@@ -234,10 +236,14 @@ def print_yc_tot():
         alpha = yagb.prefactor
         y0_agb = alpha * Y_C_AGB[model]
[…]

### 2024-04-23 carbon_paper/tex/main.tex
updated draft again

@@
 \documentclass[fleqn,
-% referee,
+%referee, % this line changes to double-spaced 1 column
 usenatbib]{mnras}
@@
 % \usepackage{amssymb}	% Extra maths symbols
-
-\usepackage{isotope}
-
 \usepackage{hyperref}
+\usepackage[normalem]{ulem}
+\usepackage[dvipsnames]{xcolor}
+% \usepackage{enumitem}
 
 \graphicspath{{figures/}} 
+% \linespread{1.8}
 
@@
 
-\newcommand{\citetjack}{Roberts et al.~(2023, in prep.)}
-\newcommand{\citepjack}{(Roberts et al.~2023, in prep.)}
-\newcommand{\citealtjack}{Robert et al.~2023, in prep.}
+\newcommand{\citetjack}{\citet{jack}}
+\newcommand{\citepjack}{(Roberts et al.~2024, in prep.)}
+\newcommand{\citealtjack}{Robert et al.~2024, in prep.}
 \newcommand{\cxi}{\texttt{\hyperlink{C11}{C11}}}
-\newcommand{\kx}{\texttt{\hyperlink{K10}{K10}}}
+\newcommand{\pxvi}{\texttt{\hyperlink{P16}{P16}}}
 \newcommand{\kxvi}{\texttt{\hyperlink{K16}{K16}}}
@@
 \newcommand{\cfactor}{2.4}
+\newcommand{\nsubgiants}{16,365}
 
@@
 \newcommand{\apogee}{APOGEE}
-\newcommand{\cc}{CCSNe}
+\newcommand{\aspcap}{\textsc{aspcap}}
+\newcommand{\cc}{CCSN}
 \newcommand{\gce}{GCE}
-\newcommand{\ia}{SNe Ia}
-\newcommand{\imf}{IMF}
-\newcommand{\sfh}{SFH} % check where first defined
-\newcommand{\ssp}{SSP}
+\newcommand{\ia}{SN Ia}
 
 % internal abbreviations
-\newcommand{\lims}{lower-intermediate mass stars}
-\newcommand{\hms}{high-mass stars}
 \newcommand{\caah}{[C/Mg]-[Mg/H]}
@@
 \newcommand{\Yct}{\ensuremath{y_{\rm C}}}
-\newcommand{\Ycc}{\ensuremath{y_{\rm C}^{\rm cc}}}
-\newcommand{\Yoc}{\ensuremath{y_{\rm Mg}^{\rm cc}}}
-\newcommand{\Ycagb}{\ensuremath{y_{\rm C}^{\rm agb}}}
+\newcommand{\Ycc}{\ensuremath{y_{\rm C}^{\rm CC}}}
+\newcommand{\Yoc}{\ensuremath{y_{\rm Mg}^{\rm CC}}}
+\newcommand{\Ycagb}{\ensuremath{y_{\rm C}^{\rm AGB}}}
 % \newcommand{\y}{\ensuremath{\rotatebox[origin=B,y=0.5ex]{180}{y}}}
@@
     \fi}
+
 \newcommand{\Zo}{%
@@
 
+%%% citepos command
+\makeatletter
+\DeclareRobustCommand\citepos
+  {\begingroup
+   \let\NAT@nmfmt\NAT@posfmt% ...except with a different name format
+   \NAT@swafalse\let\NAT@ctype\z@\NAT@partrue
+   \@ifstar{\NAT@fulltrue\NAT@citetp}{\NAT@fullfalse\NAT@citetp}}
+
+\let\NAT@orig@nmfmt\NAT@nmfmt
+\def\NAT@posfmt#1{\NAT@orig@nmfmt{#1's}}
+
+\makeatother
+
+%%%%%%%%%%% JWJ' editing macros %%%%%%%%%%%
+\newcommand{\strike}[1]{{\color{ForestGreen} \sout{#1}}}
+\newcommand{\add}[1]{{\color{ForestGreen} #1}}
+\newcommand{\note}[1]{{\color{ForestGreen} \textit{ \small (JWJ: #1)}}}
+% \LetLtxMacro\origcitep\citep
+% \LetLtxMacro\origcitet\citet
+% \renewcommand{\citep}[2][]{%
+%     \mbox{\origcitep[#1][]{#2}}
+% }
+% \renewcommand{\citet}[2][]{%
+%     \mbox{\origcitet[#1][]{#2}}
+% }
+
+\newcommand{\dbstrike}[1]{{\color{Thistle} \sout{#1}}}
+\newcommand{\dbadd}[1]{{\color{Thistle} #1}}
+\newcommand{\dbnote}[1]{{\color{Thistle} \textit{\small (DB: #1)}}}
+
+% \LetLtxMacro\origcite\cite
+
+% This is my command. I want to strike out, 
+% \newcommand{\strikeit}[1]{%
+%   \ifcorrectingmode
+%   \mbox{\sout{#1}}%
+% %  \makebox[\textwidth][s]{\sout{#1}}%
+%   \fi
+% }
+
+% \renewcommand{\cite}[2][]{%
+%   \ifcorrectingmode
+%   \mbox{\origcite[#1]{#2}}%
+%   \else
+%   \origcite[#1]{#2}%
+%   \fi
+% }
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 % If you need two or more lines of authors, add an extra line using \newauthor
-\author[D. A. Boyea et. al.]{
-Daniel A. Boyea,$^{1}$\thanks{E-mail: boyea.2@osu.edu}
-James W. Johnson,$^{1}$
+\author[D. A. Boyea et. al.]{%
+Daniel A. Boyea,$^{1, 2, 3}$\thanks{%
+Contact e-mail:~\href{mailto:boyea.2@osu.edu}{boyea.2@osu.edu}}
+James W. Johnson,$^{1, 2, 4}$
 Third Author$^{2,3}$
@@
 % List of institutions
-$^{1}$Department of Astronomy, the Ohio State University, 191 W. Woodruff, Columbus, OH 43210, USA
+$^{1}$Department of Astronomy, The Ohio State University, 140 W. 18th Ave., Columbus, OH, 43210, USA
+\\
+$^{2}$Center for Cosmology \& Astroparticle Physics (CCAPP), The Ohio State University, 191 W. Woodruff Ave., Columbus, OH, 43210, USA
+\\
+$^{3}$Department of Physics \& Astronomy, University of Victoria, Victoria, BC V8P 5C2, Canada
+\\
+$^{4}$The Observatories of the Carnegie Institution for Science, 813 Santa Barbara St., Pasadena, CA, 91101, USA
 }
@@
 % Enter the current year, for the copyright statements etc.
-\pubyear{2023}
+\pubyear{2024}
 
@@
 % context
-C is an important element across astronomy; however, its origin remains poorly understood. 
+The origin of C, despite its importance, remains poorly understood. 
 % 
@@
 % 
-We find that \caafe\ is an emirical estimate of the delayed C sources, enabling us to estimate that \agb\ stars and \cc\ produce about 20\% and 80\% of C, respectively.  
+We find that \caafe\ trends, when restricted in metallicity, are an empirical estimate of the delayed C sources, enabling us to estimate that \agb\ stars and \cc\ produce about 20\% and 80\% of C, respectively.
 The \caah\ trend instead represents the equilibrium abundances of C and Mg. 
@@
 % gas phase
-While reliable gas-phase and low-metallicity measurments of C are challenging, we find that our model and a single-zone model with our recommended yields replicate the broad trends of \caah{} across different environments and metallicities.
+While reliable gas-phase and low-metallicity measurements of C are challenging, we find that our model and a single-zone model with our recommended yields replicate the broad trends of \caah{} across different environments and metallicities.
 
@@
 
+\begin{keywords}
+galaxies: abundances -- galaxies: evolution -- galaxies: star formation -- galaxies: stellar content -- methods: numerical
+\end{keywords}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-Carbon is a distinctive and well-studied element in astronomy. 
-Formed in the cores of stars during He fusion, C is the lightest directly synthesized element after He, one of the only light elements formed in low-mass stars, and one the most abundant metals \citep[e.g.][]{jennifer19, KL14}.\footnotemark{}
-C structurally changes the environments it pollutes -- regulating stellar evolution, facilitating the formation of stars and planets, and forming the basis of earthly life.
-% Because the effects of first dredge up are mass-dependent, C and N abundances are frequently used as age indicators for RGB stars \citep{MG15, martig16, hasselquist19, vincenzo+21}. 
-As such, understanding the origin of C has wide ranging implications. 
-While we know both lower-intermediate-mass and high-mass stars produce C, the relative importance of each process is still unknown.
-
-\footnotetext{By metallicity, we mean the (mass) fraction of any element which is not H or He, denoted by $Z$. For the sun, we take $Z_\odot=0.014$. }
-
-We know, from observations of MW stars and (extragalactic) gas, that C/O traces a banana shape in O/H (see Fig.~\ref{fig:gas_phase} and section~\ref{sec:gas}). 
-At the very lowest metallicities, where $[{\rm O/H}]\lesssim-2$,%
-\footnote{In this paper, we use the standard notation for chemical abundances.
+Despite being one of the most abundant metals in the universe~\citep[e.g.][]{asplund+09}, C nucleosynthesis is poorly understood.
+Formed in the cores of stars during He fusion, C is the first \dbadd{primary?
+element} after He.
+Additionally, C is one of the only light elements formed in low-mass stars \citep[e.g.,][]{KL14}.
+\dbnote{I don't like how many e.g.'s there are, and is this the right citation here?}
+\dbadd{
+Because the effects of first dredge up are mass-dependent, C and N abundances are frequently used as age indicators for RGB stars \citep{MG15, martig16, hasselquist19, vincenzo+21}. 
+}
+\dbnote{C abundnces for stellar structure (opacities) and star formation (line cooling)}
+Broadly, it is well understood that both lower-intermediate-mass and high-mass stars produce C.
+However, the relative yields from these two classes of stars and their dependence on  metallicitys unknown \add{(see discussion below)}.
+
+% \footnotetext{\strike{By metallicity, we mean the (mass) fraction of any element which is not H or He, denoted by $Z$. For the sun, we take $Z_\odot=0.016$. CHECK THIS~} }
+
+Like many other metals, C nucleosynthesis \dbstrike{is poorly understood because its predicted yields} \dbadd{predictions from stellar evolution are highly uncertain \citep[see reviews][]{romano+10, KL14}}.
+\strike{Yield predictions} are shaped by poorly understood processes, such as mass loss rates \citep{ventura+13}?, nuclear reaction networks, rotational mixing \citep{frischknecht+16, LC18}, and convection ~\citep{chieffi2001}.
+\dbnote{check citations here...}.
+Binarity (and the metallicity dependence thereof), e.g. MKB2019, farme,
+Small changes in the initial mass ($0.01\Mo$) of massive stars can dramatically change the subsequent evolution \citep{bruenn+2023, emily+21}.
+As such, accurate yield predictions would require a much more densly sampled set of models in mass, metallicity, and rotation rates then are presently available.
+Furthermore, binary evolution is rarely included in massive star models with possibly important implications for yields \citep{farmer+21}, despite the large (metallicity-dependent) fraction of massive stars which live in binary systems \citep{MKB2019}.
+
+\dbnote{added paragraph here}
+In light of these difficulties with accurate theoretical modeling, recent work has instead sought to characterize chemical yields empirically.
+\citet{HLA20} measured the abundance ratios in the ejecta of Cassiopeia A using spatial resolved X-ray spectra.
+\citet{weinberg+19, weinberg+22} analyzed the abundance ratio trends of high- and low-alpha sequence stars in APOGEE~\citep{apogee17} to infer relative yields of prompt and delayed enrichment sources and the metallicity dependence thereof.
+\citet{emily+19, emily+22, emily+23} applied the same methodology to GALAH~\citep{DeSilva2015, Martell2017}.
+\citet{rodriguez+21, rodriguez+23} measured the mean Fe yield of core-collapse supernovae (CCSNe) using the radioactive tails of their lightcurves.
+
+\dbnote{combine this with previous, shorten J23 description and call out other ongoing work e.g. Miquela's He, James's chemical equilibrium, ...}
+Most notably for our purposes,~\citet{james+23} used Galactic chemical evolution (GCE) models to show that the correlation between gas-phase N and O abundances (see their Fig.
+1) can be explained by the metallicity dependence of relative N and O yields.
+Variations in assumptions regarding GCE parameters, such as the detailed star formation history (SFH), did not impact their conclusions and are instead a likely source of scatter in the observed relation.
+Here, we apply similar methodology to constrain C yields, which are closely related to N.
+
+GCE connects a galaxy's evolutionary history to the detailed elemental abundances in its gas and stars.
+Each enrichment process has characteristic chemical signatures and timescales, enabling us to reconstruct \strike{chemical} \add{enrichment} histories.
+\add{As an element that is well-measured in stellar spectra, many} \dbadd{with large samples of stellar C abundancess}, \strike{Many} previous GCE works \add{have} focused on C abundances (\citealt{DTS78, BF06, prantzos+18, berg+19}; see also the recent reviews by \citealt{romano22} and \citealt{RM21}).
+To date there is no consensus on the detailed origin of C; some authors have argued that high-mass stars should dominate~\citep[e.g.][]{prantzos+94, HEK00, romano+20, franchini+20, gustafsson22}, and others have argued that AGB stars should contribute at least half of the C in the universe~\citep[e.g.][]{tinsley79, chiappini+03, mattsson10, KKU11, rybizki+17, KKL20}.
+
+    As our primary observational constraint, we use a sample of subgiant stars from the \apogee{} \citep{apogee17} selected by the criteria in \citetjack.
+According to stellar evolution theory and observations, subgiants most accurately represent their birth composition \citep{gilroy89, korn+07, lind+08, souto+18, souto19}.
+Fig.~\ref{fig:subgiants} shows the subgiant sample plotted in \caah\ and \caafe{}.\footnotemark{} In this sample, [C/Mg] increases with metallicity, and [C/Mg] decreases with [Mg/Fe] at fixed [Mg/H]. 
+From observations of nearby stars and (extragalactic) gas, we know that [C/O] against [O/H] traces a banana shape (see Fig.~\ref{fig:gas_phase} and section~\ref{sec:gas}).
+At the very lowest metallicities\strike{, where} \add{(}$[{\rm O/H}]\lesssim-2$\add{)},%
+%
+observations \strike{suggest} \add{indicate} that [C/Mg] declines with metallicity.
+From $-2 \lesssim {\rm [O/H]}\lesssim -1$, [C/Mg] is roughly constant with metallicity. 
+At higher metallicities ([O/H]~$\gtrsim -1$), [C/Mg] increases with metallicity.
+
+\strike{Using the subgiant abundance trends, we will develop a model of the enrichment sources and evolution of C.}
+\add{We will show in section~\ref{sec:results} below that these correlations in the bulk population abundances alone are quite constraining for the origin of C.}
+
+\footnotetext{In this paper, we use the standard notation for chemical abundances.
 $[A/B] = \log_{10}\left(A/B\right) - \log_{10}\left(A_{\sun}/B_{\sun}\right)$, i.e.
-$[A/B]$ is the logarithm of the ratio between A and B, scaled such that $[A/B]=0$ for the sun.
-Solar abundances are as measured in \citet{asplund+09}.}
-%
-observations suggest that C/O declines with metallicity.
-From $-2 \lesssim {\rm [O/H]}\lesssim -1$, C/O is roughtly constant with metallicities. 
-And, at higher metallicities $-1 \lesssim {\rm [O/H]}$, C/O increases with increasing metallicity.
-    As our primary observational constraint, we use a sample of subgiant stars from the \apogee{} \citep{apogee17} selected by the criteria in Roberts et al. (2023, in prep).
-According to stellar evolution theory and observations, subgiants most accurately represent their birth composition \citep{gilroy89, korn+07, lind+08, souto+18, souto19}.
-Fig.~\ref{fig:subgiants} shows the subgiant sample plotted in \caah\ and \caafe{}. [C/Mg] increases with metallicity, and [C/Mg] decreases with [Mg/Fe] at fixed [Mg/H]. 
-Using the subgiant abundance trends, we will develop a model of the enrichment sources and evolution of C.
-
-Galactic chemical evolution (\gce) is a powerful tool, capable of uncovering the origins of the elements. 
-Each enrichment process has characteristic chemical signatures and timescales, enabling us to reconstruct chemical histories.
-Many previous works have used GCE in attemt to understand C abundances, whether through using theoretical stellar models \citep{DTS78, prantzos+18, chiappini+03} 
-or understanding  observation (\citealt{tinsley79, HEK00, BF06, rybizki+17, berg+19, KKL20};
-See also review in \citealt{romano22}).
-%
-Every study agrees that C is produced by a combination of high-mass and \lims{}, different studies disagree on which process is dominant. 
-For example CITES conclude \hms{} dominate wherease CITES conclude \lims{} contribute the majority of C.
-C is also generally understood to have strong metallicity dependent CCSNe enrichment.
-
-One of the primary uncertainties of GCE models are nucleosynthetic yields. Yield predictions -- the amounts of each chemical element stars produce --
-are shaped by poorly understood processes, including mass loss, nuclear reaction rates, rotational mixing, convection, and explodability \citep{romano+10,KL14,ventura+13, LC18, emily+21}.
-To better understand where C comes from and how it evolves, our aim is to combine \apogee\ observations and multi-zone models to develop observationally-consistant yields.
-\cite{james+23} examined similar \gce{} models of N (which is closely related to C), finding that trends in N and O are explained by the metallicity dependence of N/O yields.
-\citet{james+23} determine that \agb\ N abundances roughly depend linearly on metallicity (i.e.
-$y_{\rm N}/y_{\rm O} \propto Z$).
-Here, we extend their models to C, deriving similar constraints on C/Mg yields.
-We assess which yield prescriptions reproduce Galactic abundance trends while investigating the impact of \gce{} model assumptions, such as the star formation history (\sfh{}) and outflow mass loading.
-
-\section{Data Selection}
+$[A/B]$ is the logarithm of the mass ratio between A and B, scaled such that $[A/B]=0$ for the sun (see Table~\ref{tab:fiducial_mod} for solar scale.)}
+
+In Section~\ref{sec:data_selection} we describe the selection for our subgiant observational sample.
+Section~\ref{sec:nucleosynthesis} discusses theoretical estimates of \agb\ and \cc\ C yields. We parameterize our yield choices and derive a estimate of C/Mg yields observationally.
+Section~\ref{sec:vice} reviews the multizone model and modifications thereof for this work.
+Section~\ref{sec:results} presents our multizone model predictions and GCE parameters which are observationally permissable. 
+Finally Section~\ref{sec:gas} compares our model to literature collected observations of halo stars and extragalactic HII regions.
+
+\section{Data Selection}\label{sec:data_selection}
 
@@
 
-Subgiants provide the ideal observational constraint to our model. 
-When a star enters the Red Giant Branch (RGB), material from the CNO-processed core is mixed with the envelope in first dredge up, enhancing N and depleting C \citep{iben67, vincenzo+21,KL14}.
-RGB stars thus require model-dependent corrections to recover surface abundances \citep[e.g.][]{vincenzo+21}.
-On the other hand, gravitational settling can affect main sequence stellar abundances \citep[e.g.][]{souto19}.
-Subgiants have well-mixed envelopes, so gravitational settling is not as significant, and subgiants have not yet experienced first dredge up.
-We use a sample of \apogee\ DR17 stars \citep{apogee17} as selected in \citetjack.
-Chemical abundances are determined from the \apogee\ Stellar Parameter and Chemical Abundance Pipeline ({\sc aspcap}) \citep{aspcap}.
-
-Fig.~\ref{fig:subgiant_selection} shows a plot of all \apogee\ stars and the \citetjack polygon selection criteria. 
- \citetjack~select a region of stars based on surface gravity $\log g$, and effective surface temperature, $T_\text{eff}$.
+% Subgiants are a useful empirical benchmark because their photospheric abundances should reflect their birth mixture. 
+As an emperical benchmark, we use subgiant stars, whose photospheres accurately represent birth abundances. 
+During main sequence evolution, metals can fall to below the convective envelope (i.e., ``gravitational settling").
+When stars leave the main sequence and become subgiants, these metals are mixed with the convective envelope \citep[]{gratton+00, souto19}. 
+ \textit{First dredge up} during the red giant phase brings CNO processed core material to the surface \citet{iben67, KL14}.
+
+We use the sample of \apogee\ DR17 subgiants from \citetjack, selecting stars within the $\log g$-$T_\text{eff}$ polygon given by
  \begin{equation}
@@
 \end{equation}
-Additionally, we exclude stars in \apogee{} marked by any of the following flags.
-\begin{description}
-\item \verb|APOGEE_MIRCLUSTER_STAR|
-\item \verb|APOGEE_EMISSION_STAR|
-\item \verb|APOGEE_EMBEDDEDCLUSTER_STAR|
-\item \verb|young cluster (IN-SYNC)|
-\item \verb|APOGEE2_W345|
-\item \verb|EB planet|
-\end{description}
-Our final sample contains \about{12,000} subgiants.
-
-When plotting the data and models, we bin by groups of 500 (or 150) stars in [Mg/H] ([Mg/Fe]).
-When plotting \caah, we select only the low-$\alpha$ sequence.
-For \caafe, we instead select stars with $-0.15 \leq {\rm [Mg/H]} \leq -0.05$.
-When plotting \caah, we isolate the low- and high-$\alpha$ sequences with the cut
-\begin{equation}\label{eq:high_alpha}
-\begin{cases}
-\text{[Mg/Fe]} >0.12-0.13\,\text{[Fe/H]}, & \text{[Fe/H]}<0\\
-\text{[Mg/Fe]} >0.12, & \text{[Fe/H]}>0. \\
-\end{cases}
-\end{equation}
-The low-$\alpha$ sequence is better reproduced by this model, so we use this cut of the subgiants to compare the models against except for comparing \caafe.
-
-\begin{figure}
-    \centering
-    \includegraphics{logg_jack.pdf}
-    \caption[]{
-        A Kiel diagram of \apogee{} stars.
-Following \citetjack, we select subgiants in the black pentagon (see Equation \ref{eq:subgiant_selection}).
-These stars have not yet experienced first dredge-up, so their photospheric C and N abundances should reflect their birth mixture.
-    }
-    \label{fig:subgiant_selection}
-\end{figure}
-
-\section{Nucleosynthesis}
-Table \ref{tab:fiducial_mod} contains our fiducial yields. 
-For O, N, Mg, and Fe, we adapt the yield choices of \citet{james+21, james+23}.
-Following \citet{james+21, james+23}, we take the \ia{} delay time distribution to be a $t^{-1.1}$ power-law with a minimum delay time of 140\,Myr, as suggested by the observations of \citet{maoz+12}.
+Also following \citet{jack}, we exclude stars with the flags:
+        \verb|APOGEE_MIRCLUSTER_STAR|,
+        \verb|APOGEE_EMISSION_STAR|,
+        \verb|APOGEE_EMBEDDEDCLUSTER_STAR|,
+        \verb|APOGEE2_YOUNG_CLUSTER|,
+            \verb|APOGEE2_W345|,
+        \verb|APOGEE2_EB|, and
+        \verb|ASPCAP_BAD|.
+We additionally remove stars with no reported C, Mg, or Fe abundances. These cuts yield a sample containing \nsubgiants\ subgiants.
+
+\section{Nucleosynthesis}\label{sec:nucleosynthesis}
+
+Table \ref{tab:fiducial_mod} contains our fiducial yields and abundance scale. 
+For O, Mg, and Fe, we adopt the yields in \citet{david_fe}. We use a scaled variation of the N yield from \citet{james+23}. 
+Following \citet{james+21, james+23}, we take the \ia{} delay time distribution to be a $t^{-1.1}$ power-law with a minimum delay time of 150\,Myr, as suggested by the observations of \citet{maoz+12}.
+We use solar abundances from \citet{magg+22} with a +0.04 gravitational settiling correction as in \citet{david_fe}.
+\dbadd{Magg22 finds Z/X = 0.0225 for the surface?
+what do we use for the solar metallicity?}.
+Assuming He abundance from $Y=0.2725$ from \citet{AAG2021}, resulting in a $Z_\odot=0.01606$
 
@@
 	\centering
-    \caption[]{Yields for the fiducial model (in units of \ssp~birth mass). See section \ref{sec:agb} for the definition of \cxi.}
+    \caption[]{Solar abundance scale and fiducial yields (in units of SSP~birth mass). See section \ref{sec:agb} for the definition of \cxi. The solar abundance scale is \citet{magg+22} + 0.04. }
 	\label{tab:fiducial_mod}
 
-	\begin{tabular}{l l l l}
+	\begin{tabular}{l l l l l}
 		\hline
-        Element & $y^{\rm cc}$ & $\y^{\rm agb}$ & $y^{\rm ia}$ \\
+        Element & $Z_{X,\,\sun}$ & $y_X^{\rm cc}$ & $\y_X^{\rm agb}$ & $y_X^{\rm ia}$  \\
 		\hline
-        C & Eq.~\ref{eq:zeta} & $\cfactor\times$\cxi &  0 \\
-        O & 0.015 & 0 & 0 \\
-        Mg & 0.00185 & 0 & 0 \\
-        Fe & 0.0012 & 0 & 0.00214 \\
-        N & 0.00072 & 0.0009$M\left(\frac{Z}{Z_\odot}\right)$ & 0\\
+        C & 0.00339 & Eq.~\ref{eq:y_cc} & $\cfactor\times$\cxi &  0 \\
+        O & 0.00733 & 7.12e-3 & 0 & 0 \\
+        Mg & 0.000671 & 6.69e-4 & 0 & 0 \\
+        Fe & 0.00137 & 4.72e-4 & 0 & 6.69e-4 \\
+        N &0.00104 & 4.001e-4 & 0.0009$M\left(\frac{Z}{Z_\odot}\right)$ & 0\\
+        % C & 0.00339 & Eq.~\ref{eq:zeta} & $\cfactor\times$\cxi &  0 \\
+        % O & 0.00733 & 0.015 & 0 & 0 \\
+        % Mg & 0.000671 & 0.00185 & 0 & 0 \\
+        % Fe & 0.00137 & 0.0012 & 0 & 0.00214 \\
+        % N &0.00104 & 0.00072 & 0.0009$M\left(\frac{Z}{Z_\odot}\right)$ & 0\\
 		\hline
@@
 
+\dbnote{I like the definition of Y to go here since that is model independent, but IMF-integrated could still be specific to AGB/CC.}
+
 \subsection{Asymptotic Giant Branch Stars}\label{sec:agb}
 
-    In this work, we explore four different sets of \agb\ star yield tables from literature,
-    providing necessary well-sampled grids in mass and metallicity. We refer to the yields from the following studies as the following,
+An Asymptotic Giant Branch (AGB) star is a low mass star during its last nuclear burning phase (He shell burning; see e.g.
+\citealt{PR2023}) which enriches the ISM through mass loss during thermal pulses.
+    In this work, we explore four different stellar AGB yield tables from the literature which provide
+    well-sampled grids in mass and metallicity. We refer to the tables as 
 \begin{description}
     \item \hypertarget{C11}{\texttt{C11}}: \citet{cristallo+11, cristallo+15}
-    \item \hypertarget{K10}{\texttt{K10}}: \citet{karakas10}
     \item \hypertarget{V13}{\texttt{V13}}: \citet{ventura+13,ventura+14,ventura+18, ventura+20}
     \item \hypertarget{K16}{\texttt{K16}}: \citet{KL16, karakas+18}
+    \item \hypertarget{P16}{\texttt{P16}}: \citet{pignatari+16, ritter+18, battino+19, battino+21}
 \end{description}
-Table~\ref{tab:agb} contains the masses and metallicities used in each model.
-
-Fig.~\ref{fig:y_agb} compares the stellar \agb\ C yields for these four models.
-We define the stellar \agb\ yield to be the fraction of the stars initial mass $M$ which is newly synthesized into C.
+Table~\ref{tab:agb} notes the masses and metallicities for each grid of yields.
+We use the same tables as \citet{james+23}, except that we have swapped \citet{karakas10} for \citet{ritter+18}.
+
+We define a yield to be the fraction of a star's initial mass $M_{\rm birth}$ which is converted into freshly synthesized C.
 If $\Delta Z_{\rm C}$ represents the change in the mass fraction of C abundance, then
 \begin{equation}
-    \y_{\rm C}^{\rm agb} =  \Delta Z_{\rm C} \frac{M_{\rm ejected}}{M}.
-\end{equation}
-Note that yields may be negative if the material returned to the interstellar medium has a lower abundance $Z_{\rm C}$ than the material the star was formed from.
-Most models agree on the qualitative shape of the net fractional \agb\ C yield.
-Stellar yields peak between masses of about 2--4 \Mo and decline as stars become more or less massive.
-As metallicity increases, the total \agb\ C yield decreases.
-The mass of peak C yields also increases slightly with metallicity.
-
-The left panel of Fig.~\ref{fig:agb-ssp} shows \imf-averaged C yields for each \agb\ model as a function of metallicity.
-An IMF-averaged yield adds together the yields of stars of each mass, weighted by the fraction of stars of each mass (the \imf). 
+    \y_{\rm C}^{\rm AGB} =  \Delta Z_{\rm C} \frac{M_{\rm ejected}}{M_{\rm birth}}.
+\end{equation}
+The yields may be negative if the material returned to the ISM has a lower $Z_{\rm C}$ than the material the star was formed from.
+
+Fig.~\ref{fig:y_agb} compares the stellar \agb\ C yields for these four models.
+Most models agree on general yield trends in mass and metallicity.
+C production peak between masses of $\sim$ 2--4 \Mo\ and declines as stars become more or less massive.
+As metallicity increases, the net yield decreases and the mass of peak C production increases slightly.
+
+The left panel of Fig.~\ref{fig:agb-ssp} shows IMF-averaged C yields for each \agb\ model as a function of metallicity.
+An IMF-averaged yield adds together the yields of stars of each mass, weighted by the fraction of stars of each mass (the IMF). 
 \begin{equation} \label{eq:imf-agb-yield}
-    \Ycagb(Z,t) = 
+    \Ycagb(Z,\tau) = 
     \frac{
-    \int_{M_{\rm to}(t)}^{8\,\Mo} 
-    \y_{\rm X}(M, Z)
-    \frac{dN}{dM}\ M\ dM
+    \int_{M_{\rm to}(\tau)}^{8\,\Mo} 
+    \y_{\rm X}(M, Z) M\ 
+    \frac{dN}{dM}\ dM
 }
 {
-    \int_{0.08\Mo}^{100\Mo} \frac{dN}{dM}\ M\ dM
-}
-\end{equation}
-where ${dN}/{dM}$ is the \imf{} and $M_{\rm to}(t)$ is the mass of stars with lifetime $t$.%
-\footnotetext{In our model, the mass-lifetime relation is
-$\log \tau_M = 1.02 - 3.57\log M + 0.90 \left(\log M\right)^2$,
-where $\tau_M$ is in Gyr, from \citealt{larson74}.
-We use $t_{\rm end}=10\,$Gyr for total yields when $t$ is not used.}
+    \int_{0.08\Mo}^{100\Mo}\ M\ \frac{dN}{dM}\ dM
+}
+\end{equation}
+where ${dN}/{dM}$ is the IMF and $M_{\rm to}(\tau)$ is the mass of stars with lifetime $\tau$.%
+\footnote{In this paper, we take the metallicity-independent parabola in $\log \tau$-$\log m$ space from \citet{larson74} as our mass-lifetime relation.} \dbnote{are the numbers in the integral bounds okay here or should we write this out or put in footnote?
+And should we be using a more recent MLR?}
 The \agb\ models mostly differ in their yield normalization and metallicity dependence. 
-All yield models span a range of \about{2} for a given metallicity.
-For example, all four models predict $y_\text{C}^\text{agb}(\Zo)$ to be between 0.004 and 0.008 at solar metallicity.
-The models also differ slightly in the strength of metallicity dependence, with about a factor of 3 discrepency (see Table~\ref{tab:agb}).
-
-Fig.~\ref{fig:agb-ssp}, on the right, shows the total production of C by \agb\ stars in a \ssp{} at an age $t$, i.e. $\y_{\rm C}(Z_\odot, t)$. 
-As the mass range $2\,\Mo\lesssim M \lesssim 4\,\Mo$ is most important for C production, about half of C production occurs before \about{1}\,Gyr, similar to \ia\ Fe. 
-\kx{} and \kxvi{} weight C production more heavily towards high-mass \agb\ stars resulting in a faster enrichment delay time, whereas the \cxi\ and \vxiii\ models predict a slightly longer timescale of \about{1}\,Gyr.
+The normalizations span a factor of \about{2}.
+For example, at $Z = 0.1\Zo$, each models predicts $Y_{\rm C}^{\rm AGB}$ to be between 0.0008 and
+0.0016.
+The metallicity dependence of the yields span a factor of \about{3} (see $\zeta^{\rm AGB}$ in
+Table~\ref{tab:agb} and discussion in section~\ref{sec:equilibrium} below).
+Variations in \agb\ models are due to different choices of reaction rates, convection treatments, and mass-loss rates.
+
+The right panel of Fig.~\ref{fig:agb-ssp} shows the total production of C by \agb\ stars by a SSP as a function of age at solar metallicity. 
+As the mass range $2\,\Mo\lesssim M \lesssim 4\,\Mo$ is most important for C production, half the yield is produced before \about{1}\,Gyr, similar to Fe production by \ia. 
+\kxvi{} weight C production more heavily towards high-mass \agb\ stars, resulting in shorter delay times, whereas the \cxi\ and \vxiii\ models predict a slightly longer timescale of \about{1}\,Gyr.
 In any case, little to no C is produced more than 2\,Gyr after a star formation event.
@@
 
-In an \agb\ star, two competing processes determine the outcome of C production: \textit{third dredge up} and \textit{hot bottom burning}.  
-Third dredge up accompanies thermal pulses in \agb\ stars, where material from the CO core is mixed with the envelope, increasing surface C abundances \citep{KL14}.
-The C yields of the star are increased as this C-enhanced envelope is released to the interstellar medium.
-Hot bottom burning is the activation of the CNO cycle\footnotemark{}
-at the bottom of the convective envelope when $T\gtrsim 50\,{\rm MK}$.
-Because the $^{14}$N proton capture is the slowest component of the CNO cycle, the CNO cycle converts nearly all \C[12] into $^{14}$N \citep{solar-fusion}.
-
-\footnotetext{
-    The CNO cycle is a series of proton-capture reactions with CNO elements resulting in energy generation and the creation of an $\alpha$ particle. $\C[12]({\rm p}, \gamma)
-    ^{13}{\rm N}(\beta^+, \nu_{\rm e})
-    ^{13}{\rm C}({\rm p}, \gamma)\allowbreak
-    ^{14}{\rm N}({\rm p}, \gamma)\allowbreak
-    ^{15}{\rm O}(\beta^+, \nu_{\rm e})\allowbreak
-    ^{15}{\rm N}({\rm p}, \alpha)
-    \C[12]$. 
-There are other less important minor branches of the CNO cycle
- \citep{solar-fusion}.
-}
-
-Hot bottom burning and third dredge-up result in mass and metallicity dependent C yields. 
-Stars less than \about{2}\,\Mo do not experience third dredge-up.
-As a result, these stars C abundances are only affected by first dredge-up, resulting in little change to C yields or slight destruction of C.
-Above \about{2}\,\Mo{}, third dredge up becomes important, enriching the outer layers with C.
-\agb\ stars between 2 and 5 \Mo are the most abundant producers of C.
-In \agb\ stars more massive than \about{5}\,\Mo, both hot bottom burning and third dredge up occur; however, hot bottom burning is much more efficient, resulting in significant \C[12] destruction.
-Metal poor stars dredge up more material due to the decreased power of the CNO cycle, resulting in increasing carbon yields with decreasing metalicity \citep{ventura+13}.
-
-For our models to match observations, we find that need to uniformly amplify these yield tables.
+In \agb\ stars, two competing processes determine the outcome of C production: {third dredge up} (TDU) and {hot bottom burning} (HBB).  
+TDU accompanies thermal pulses in \agb\ stars, where material from the CO core is mixed with the envelope, increasing surface C abundances \citep{KL14}.
+The C yields of the star are increased as this C-enhanced envelope is released to the ISM.
+HBB\ is the activation of the CNO cycle at the bottom of the convective envelope. 
+TDU increases C yields and HBB converts C into N. When both processes activate, highly efficient N production ensues (see discussion in e.g. \citealt{james+23, ventura+13}). 
+%Because the $^{14}$N proton capture is the slowest component of the CNO cycle, the CNO cycle converts nearly all \C[12] into $^{14}$N \citep{solar-fusion}.
+
+% \footnotetext{
+%     The CNO cycle is a series of proton-capture reactions with CNO elements resulting in energy generation and the creation of an $\alpha$ particle. $\C[12]({\rm p}, \gamma)
+%     ^{13}{\rm N}(\beta^+, \nu_{\rm e})
+%     ^{13}{\rm C}({\rm p}, \gamma)\allowbreak
+%     ^{14}{\rm N}({\rm p}, \gamma)\allowbreak
+%     ^{15}{\rm O}(\beta^+, \nu_{\rm e})\allowbreak
+%     ^{15}{\rm N}({\rm p}, \alpha)
+%     \C[12]$. 
+% There are other less important minor branches of the CNO cycle
+%  \citep{solar-fusion}.
+% }
+
+Both HBB and TDU result in mass and metallicity dependent C yields. 
+Stars less than \about{2}\,\Mo\ do not experience TDU As a result, these stars C abundances are only affected by first dredge-up (CITE), resulting in small net C yields.
+Above \about{2}\,\Mo{}, TDU becomes important, enriching the outer layers with C.
+In \agb\ stars more massive than \about{5}\,\Mo, efficient HBB turns most \C[12] into $^{14}$N.
+Metal poor stars dredge up more material \dbnote{for which physics, compactness, mixing efficiency( Boothroyd \& Sackmann 1988))? etc.}, resulting in elevated C production \citep{ventura+13}.
+
+For our models to better match observations, we uniformly amplify the yield tables according to
 \begin{equation} \label{eq:alpha}
@@
 \end{equation}
-We use \cxi\ table, with $\alpha_{\rm agb}=\cfactor$, as the fiducial \agb\ yield.
-Variations in models are due to different treatments of reaction rates, convection, and mass-loss.
-Table~\ref{tab:agb} contains the stellar masses and metallicites each yield set contains, the approximate solar C yield $\Ycagb(\Zo)$, the metallicity dependence at solar $\zeta^{\rm agb} = d\Ycagb/dZ$, and the required factor $\alpha$ to reach 20\% \agb\ C production.
+We use the \cxi\ table, with $\alpha_{\rm agb}=\cfactor$, as the fiducial \agb\ yield.
 
@@
 	\centering
-    \caption[]{For each \agb\ yield set, the \imf-averaged \agb\ C yield at solar metallicity $y_{\rm C, 0}^{\rm agb}$ and the multiplicative factor reaches an \agb\ contribution of 20\% $\alpha_{\rm agb, 20}$.}
+    \caption[]{For each \agb\ yield set, the IMF-averaged \agb\ C yield at solar metallicity $y_{\rm C, 0}^{\rm agb}$ and the multiplicative factor reaches an \agb\ contribution of 20\% $\alpha_{0.2}^{\rm agb}$.}
 
 	\label{tab:agb}
-    \begin{tabular}{c ccc p{5cm} p{5cm}} % four columns, alignment for each
+    \begin{tabular}{c cc cc  c p{5cm} p{5cm}} % four columns, alignment for each
 		\hline 
         \agb\ table 
-                & $y_{\rm C}^{\rm agb}(\Zo)$ & $\zeta^{\rm agb}(\Zo)$ & $\alpha_{20}^{\rm agb}$
-                & masses (\Mo) & metallicites 
-                \\
+                & $y_{\rm C}^{\rm agb}(\Zo)$ & y & $\zeta^{\rm agb}(\Zo)$ & $\zeta$ &  $\alpha_{0.2}^{\rm agb}$
+                & masses (\Mo) & metallicites ($\log Z/\Zo$)\\
         \hline
         \cxi 
-                &  0.00042 & -0.0175 & 2.4
+                &  $3.5^{+0.3}_{-0.3}$ & 4.0
+                & $-3.5^{+0.3}_{-0.3}$ & -3.5
+                & 1.32
                 & 1.3, 1.5, 2, 2.5, 3, 4, 5, 6
-                & 0.0001, 0.0003, 0.001, 0.002, 0.003, 0.006, 0.008, 0.01, 0.014, 0.02
-                \\
-        \kx 
-                & 0.00064 & -0.059 & 1.6
-                & 1, 1.25, 1.5, 1.75, 1.9, 2.25, 2.5, 3, 3.5, 4, 4.5, 5, 5.5, 6 
-                &  0.0001, 0.004, 0.008, 0.02
+                & -2.15, -1.67, -1.15, -0.85, -0.67, -0.37, -0.24, -0.15, 0.0, 0.15
                 \\
         \vxiii 
-                & 0.00022 & -0.021 & 4.5
+                & $2.7^{+1.3}_{-1.3}$ & 2.6 
+                & $-4.9^{+1.4}_{-1.6}$ & -4.9
+                & 2.5
                 & 1.5, 2, 2.5, 3, 3.5, 4, 4.5, 5, 6, 6.5, 7
-                & 0.0003, 0.001, 0.002, 0.004, 0.008, 0.014, 0.04
+                & -1.67, -1.15, -0.85, -0.54, -0.24, 0.0, 0.46
                 \\
         \kxvi 
-                & 0.0005 & -0.029 & 2.0
+                & $3.0^{+0.4}_{-0.5}$ & 3.5
+                & $-10.1^{+0.9}_{-1.3}$ & -10
+                & 1.11
                 & 1, 1.25, 1.5, 1.75, 2.25, 2.5, 2.75, 3, 3.25, 3.5, 3.75, 4, 4.5, 5, 5.5, 6, 7 
-                & 0.0003, 0.001, 0.002, 0.004, 0.008, 0.014, 0.04
+                & -0.7, -0.3, 0.0, 0.33 
+                \\
+        \pxvi 
+                & $6.2^{+1.1}_{-1.1}$ & 8
+                & $-5.3^{+1.0}_{-0.9}$ & -3.
+                & 1, 1.65, 2, 3, 4, 5, 6, 7
+                &  -2.15 , -1.15 , -0.37 , -0.15 , 0.15
                 \\
@@
 The black dashed line shows $\y=0$ for reference.
-Each panel represents yields from one of four \agb\ models: \cxi{}, \kx{}, \vxiii{}, \kxvi{}, and our analytic model (see sections \ref{sec:agb}) }
+Each panel represents yields from one of four \agb\ models: \cxi{}, \vxiii{}, \kxvi{}, \pxvi{} (see sections \ref{sec:agb}) }
 
@@
 
-    \caption[]{ C yields from \agb\ stars as a function of \ssp{} age, as a fraction of the C yield at $t_{\rm end}=10\,$Gyr. 
-\textbf{Left} The (\imf-weighted) \agb\ C yield $\Ycagb$ as a function of metallicity for each of the \agb\ yield models.
-($\Ycagb$ is the net mass of C produced by \agb\ stars per unit mass of star formation, after 10\,Gyr and assuming a \citealt{kroupa01} \imf.)
-    \textbf{Right} Our four considered \agb\ yield models at solar metallicity (\cxi{}, \kx{}, \vxiii{}, \kxvi{}.
-The dashed red line shows the delay time distribution of type Ia supernovae ($\propto t^{-1.1}$) for comparison, and the minimum of V13 is $y(t)/y(t_{\rm end}=-3.3$.
+    \caption[]{ C yields from \agb\ stars as a function of SSP age, as a fraction of the C yield at $t_{\rm end}=10\,$Gyr. 
+\textbf{Left} The (IMF-weighted) \agb\ C yield $\Ycagb$ as a function of metallicity for each of the \agb\ yield models.
+($\Ycagb$ is the net mass of C produced by \agb\ stars per unit mass of star formation, after 10\,Gyr and assuming a \citealt{kroupa01} IMF.)
+    \textbf{Right} Our four considered \agb\ yield models at solar metallicity (\cxi{}, \vxiii{}, \kxvi{}, \pxvi{}.
+The dashed red line shows the delay time distribution of type Ia supernovae ($\propto t^{-1.1}$) for comparison, and the minimum of V13 is $y(t)/y(t_{\rm end}=-46$.
 }
@@
 
-Massive stars form $^{12}$C in their cores through the triple--$\alpha$ process.
-However, only C ejected through supernovae and stellar winds contributes to the yield. 
+Massive stars form $^{12}$C in their cores through the triple--$\alpha$ reaction.
+Surviving C ejected through supernovae and winds form the massive star yields.
 While there are many stellar models providing predictions of \cc{} yields, the results of these models are highly uncertain due to the complexity of stellar modeling.
 
-Fig.~\ref{fig:y_cc} plots calculations of the \imf-integrated yields.
-For \cc\, 
+Fig.~\ref{fig:y_cc} plots calculations of IMF-averaged yields for a handful of massive star yields from the literature.
+For \cc\, the IMF-averaged yield is
 \begin{equation} \label{eq:imf-cc-yield}
@@
     \int_{8\,\Mo}^{100\,\Mo} 
-    \y_{\rm X}(M, Z)
+    \y_{\rm C}(M, Z)
     \frac{dN}{dM}\ M\ dM
@@
 \end{equation}
-where ${dN}/{dM}$ is the \imf{} and $M_{\rm to}(t)$ is the mass of stars with lifetime $t$.%
-\cc{} models predict a wide range of C yields, spanning almost a factor of ten. 
-Both the \citet{NKT13} and \cite{LC18} models show positive metallicity dependence. 
+where ${dN}/{dM}$ is the IMF and 8\,\Mo is the assumed minimum mass of \cc\ progeneters (see \VICE\ documentation and \citealt{emily+21}). 
+\cc{} models predict a wide range of C yields, spanning nearly a factor of ten. 
+Rotation, binarity, and explodability introduce substantial uncertainties in \cc\ predictions \citep{farmer+21}.
+The \cite{LC18} models, which include rotation, show that the induced mixing (e.g.
+\citealt{frischknecht+16}) can dramatically increase the magnitude and metallicity dependence of $\Ycc$.
+As we will later emperically show, \cc\ C production needs to be strongly metallicity-dependent at $Z \approx \Zo$, which is consistent with \citepos{LC18} rapidly rotating models.
 As metallicity increases, stars lose more of their mass to winds.
-In particular, C enriched envelop material is lost through winds before synthesized into heavier elements, so C yields can be strongly metallicity dependent (VERIFY).
-Fig.~\ref{fig:y_cc} shows the \cxi{} \agb\ model for comparison on the left.
-Especially at $Z\approx Z_\odot$, most \cc{} models dominate \agb\ C production.
-Later, we will also show empirically this is the case.
-The right of Fig.~\ref{fig:y_cc} shows the \cc{} [C/Mg] ratio for the different models, defined by
+In particular, C enriched envelop material is lost through winds before synthesized into heavier elements, resulting in $Z$-dependent C production \citep{LC18}.
+The left panel of Fig.~\ref{fig:y_cc} shows the \cxi{} \agb\ model. Especially at $Z\approx Z_\odot$, most \cc{} models dominate \agb\ C production.
+
+The right panel of Fig.~\ref{fig:y_cc} shows the average [C/Mg] ratio of \cc\ ejecta for the different models, defined by
 \begin{equation}\label{eq:c_mg_cc}
@@
 \end{equation}
-If only \cc{} produced C, then ${\rm [C/Mg]^{CC}}$ describes the equilibrium abundance of [C/Mg].
-Different \cc\ models also span a large range in [C/Mg].
-
-Rotation, binarity, and explodability introduce substantial uncertainties in \cc\ predictions.
-The \cite{LC18} models include rotation, showing that variations in the rotational velocity of the star can dramatically increase the magnitude and metallicity dependence of $\Ycc$.
-Rotation induces more mixing allowing the CO core to grow larger and contributes to wind losses.
-As we will later show, \cc\ C production needs to be strongly metallicity-dependent at $Z/Z_\odot \approx 1$, which is consistent with the \cite{LC18} rapidly rotating models.
-Assumptions about the explodability landscape affect C and Mg production.
-As fewer high-mass stars explode, both C and Mg yields decrease, but Mg yields decrease more as more C is lost to winds, so [C/Mg] increases with decreasing explodability.
-Finally, stripped binaries produce about twice as much C as single massive stars and other effects of binary evolution are unstudied \citep{farmer+21}.
-
-\cc\ do not satisfactorily explain C, O, and Mg abundances.
-Most models here overproduce C relative to Mg. This could be related to overproduction of O relative to Mg, a known problem of \cc\ models.
-There is substantial variation in predicted Mg yields but most models predict flat trends.
-However, the variation is significant and our adopted $\Yoc$ yield is much higher than most models, but O and Mg yields of \cc\ models do not fully match observations.
-\cc\ models underpredict $[{\rm Mg}/{\rm O}]$, and the reason why is unknown (see e.g.
-\citealt{emily+21}).
-Here, we assume ${\rm [O/Mg]} = 0$, which nevertheless consistent with \apogee{} observations \citep{weinberg+19, weinberg+22}.
- As we focus on constraining relative yields, we neglect O and Mg yield variations in the main text, leaving them constant and metallicity-independent. We also choose to parameterize C yields.
+The models we have considered here predict [C/Mg]$^{\rm CC}$ ratios that closely trace the metallicity-dependence of the C yield, a consequence of approximately
+metallicity-independent Mg production \citep[e.g][]{andrews+17}.
+However, [C/Mg]$^{\rm CC}$ is super-solar in all models except
+\citet{NKT13}.
+This result arises due to the so-called ``oxygen-magnesium problem,'' whereby Mg
+is under-produced relative to O (see discussion in \citealt{emily+21}).
+resulting in [C/Mg] ratios higher than observed.
+To avoid this problem in our \gce\ models, we simply assume the O and Mg yields
+from massive stars reflect the solar mixture, consistent with observations from \apogee\ \citep{weinberg+19, weinberg+22} \dbnote{update these citations?}.
+
+To simplify the exploration of C yields from \cc\, we use the parameterazation, 
+\begin{equation}\label{eq:y_cc}
+    \Ycc = y_{\rm C, 0}^{\rm cc} + \zeta^{\rm cc}\,(Z-\Zo) .
+\end{equation}
+While a linear yield model is able to explain APOGEE abundances, we also consider in section~\ref{sec:gas} a bi-linear yield model which could also explain low-metallicity observations of C.
+\begin{equation}\label{eq:y_cc_bilinear}
+    \Ycc = \begin{cases}
+    y_{\rm C, 0}^{\rm CC} + \zeta^{\rm CC}\,(Z-\Zo) & Z > Z_1 \\
+    y + \zeta_1^{\rm CC} & Z < Z_1
+    \end{cases}
+\end{equation}
 
@@
         C yields from high-mass stars.
-        \textbf{Left} The \imf-weighted \cc\ yield of C as a function of metallicity.
+        \textbf{Left} The IMF-weighted \cc\ yield of C as a function of metallicity.
         \textbf{Right} The \cc\ [C/Mg] abundance ratio, defined in Eq.~\ref{eq:c_mg_cc}.
@@
 
-Galaxies, when moderated by metal-poor gas accretion and feedback-driven outflows, reach a chemical equilibrium.
-The production of new metals is balanced by losses to new stars and outflows \citep{larson72, dalcanton07, FD08, PS11, lilly13}.
-Here, we assume a simple \textit{one-zone} chemical evolution model \cite[e.g.][]{tinsley80, pagel09, matteucci21}.
-While our galaxy is likely not in perfect equilibrium or described by a single, homogeneous chemical
-envirnoment, the equilibrium approximation is nevertheless useful in understanding yields and
-metallicity dependence of solar neighborhood stars \citep[e.g.][]{james_dwarf,james+23,WAF17}.
-
-\cite{james+23} show that trends in N and O abundance ratios are set by the yield ratio and their metallicity dependences. 
-Here, we find a similar conclusion for C and Mg (see section xxx in \citealt{james+21}), where equilibrium C/Mg is given by
+Building on \citepos{WAF17} analytic models of chemical equilibrium,
+\citet{james+23} demonstrate that the relationship between N and O can be
+explained by the metallicity dependence of their relative yields (see discussion
+in their section 4.6).
+We find similar results extending these arguments to C and Mg.
+The equilibrium C/Mg abundance ratio is 
 \begin{equation}\label{eq:equilibrium_yields}
-    \frac{Z_{\rm C}^{\rm eq}}{Z_{\rm Mg}^{\rm eq}} = \frac{\Ycc + \Ycagb }{y_{\rm Mg}}.
-\end{equation}
-
-In Fig.~\ref{fig:analytic}, we show the inferred total C yields, based on this equation, and our best fitting linear model. From a linear regression, we suggest that
+    {\rm [C/Mg]_{eq}} = \log \left(\frac{\Ycc + \Ycagb }{y_{\rm Mg}}\right) - \log \left(\frac{Z_{\rm C,\,\odot}}{Z_{\rm Mg,\,\odot}}\right)
+\end{equation}
+
+We isolate the low-$\alpha$ sequence of subgiants to represent the equilibrium abundance trends, defined by [Mg/Fe] - [Fe/H] as in \citet{weinberg+19}.
+Low-$\alpha$ stars are defined as stars with
+\begin{equation}\label{eq:high_alpha}
+\begin{cases}
+\text{[Mg/Fe]} <0.12-0.13\,\text{[Fe/H]}, & \text{[Fe/H]}<0\\
+\text{[Mg/Fe]} <0.12, & \text{[Fe/H]}>0. \\
+\end{cases}
+\end{equation}
+with high-$\alpha$ stars being otherwise from \citet{weinberg+19, weinberg+22, emily+19, emily+21}.
+
+In Fig.~\ref{fig:analytic}, we show the inferred C/Mg yield ratio against metallicity. 
 \begin{subequations}\label{eq:yc_inferred}
     \begin{align}
-        \frac{\Yct(Z)}{y_{\rm O}} &\approx \frac{1}{3} + 4 \left(Z-\Zo\right) \\
-        \frac{\Yct(Z)}{y_{\rm Mg}} &\approx 2.7 + 32 \left(Z-\Zo\right).
+        \frac{\Yct(Z)}{y_{\rm Mg}} &\approx 4.20 + 1.64 \log (Z/\Zo)\\
+        \frac{\Yct(Z)}{y_{\rm Mg}} &\approx 4.12 + 1.21 \log(Z/\Zo) + 3.07 \log(Z/\Zo)^2
     \end{align}
 \end{subequations}
-These yield ratios results in an equilibrium abundance $[{\rm C}/\alpha] = -0.09$ at solar metallicity, which is consistent with the subgiant sample and is within \about{20\%} of the solar C/Mg mixture from \citet{asplund+09}.
+These yield ratios results in an equilibrium abundance $[{\rm C/Mg}] = -0.09$ at solar metallicity, which is consistent with our subgiant sample and is within \about{20\%} of the solar C/Mg mixture.
+(check this!)
+
+With the total C yield of Eq.~\ref{eq:yc_inferred} and given an \agb\ C yield, we can derive an \cc\ C yield that would predict observationally consistant [C/Mg] ratios.
+\begin{subequations}
+    \begin{align}
+        \Ycc(\Zo) &= \Yct(\Zo) - \Ycagb(\Zo)\\
+        \zeta^{\rm cc} &= \zeta - \zeta^{\rm agb}
+    \end{align}
+\end{subequations}
+where $\zeta$ is the (solar) metallicity dependence of the C yield at $Z=\Zo$
+\begin{equation}
+    \zeta = \frac{d y_{\rm C}}{d Z} \Big \vert_{(Z=\Zo)},
+\end{equation}
+and $\zeta^{\rm cc}$ and $\zeta^{\rm agb}$ correspond to the specific enrichment channels. 
+This method reduces the number of free parameters and enables all yield models to match \caah\ trends in \apogee{} subgiants, even when considering alternative \agb\ yield tables.
+Table~\ref{tab:agb} provides $\zeta^{\rm agb}$ for each \agb\ yield table we consider.
 
 Both observational and theoretical uncertainties limit the accuracy of our relative yield predictions.
-Additionally, the derived yields will be systematically biased if the galaxy is out of equilibrium, for example, due to a recent starburst \citep{mor+19,isern19}.
-
-With the total C yield of Eq.~\ref{eq:yc_inferred} and given an \agb\ C yield, we can derive an observationally-consistant \cc\ C yield.
-\begin{subequations}
-    \begin{gather}
-        \Ycc(\Zo) = \Yct(\Zo) - \Ycagb(\Zo)\\
-        \zeta^{\rm cc} \equiv \frac{d\Ycc(\Zo)}{dZ} = \frac{d\Yct(\Zo)}{dZ} - \frac{d\Ycagb(\Zo)}{dZ}
-    \end{gather}
-\end{subequations}
-This method reduces the number of free parameters of the model and enables all models to match \caah\ trends in \apogee{} subgiants when considering \agb\ yields with different metallicity dependences and normalizations.
-We use values of $\Ycagb$ and $\zeta^{\rm agb}$ as presented in Table~\ref{tab:agb}.
-For example, in our fiducial model, $\Ycc = 0.004 + 0.102 (Z-\Zo)$.
-Our full \cc\ C yield model adds a low-metallicity enhancement term, which is insignificant at solar metallicities (e.g.
-thin disk stars) but enables models in section~\ref{sec:gas} to match low-metallicity environments.
-We parameterize low-metallicity enrichment with $y_l$ and $Z_l$, the yield and transition metallicity for enhanced low-metallicity yields.
-All-together, 
-\begin{equation}\label{eq:zeta}
-    \Ycc = y_{\rm C, 0}^{\rm cc} + \zeta^{\rm cc}\,(Z-\Zo) + \frac{2\,y_l}{1 + Z/Z_l}.
-\end{equation}
+Additionally, the derived yields will be systematically biased if the galaxy is out of equilibrium, e.g. due to a recent starburst \citep{mor+19,isern19}.
 
@@
     \centering
-    \includegraphics{analytic.pdf}
+    \includegraphics{figures/equilibrium_yields.pdf}
     \caption[]{Inferred total C yields as a function of metallicity.
@@
 
+\subsection{Single-zone models and \caafe{}}
+\dbnote{This will be a section I will write after a little more investigation.
+I think this should go by the equilibrium model, but maybe move both sections to after a discussion of the fiducial model: Multizone description $\to$ justify equilibrium and singlezone $\to$ consideration of other parameters.
+Or maybe just a different section?}
+
 \section{The Multi-zone Model}\label{sec:vice}
@@
 This model is described extensively in \JJ~and concisely summarized  in \citet{james+23}. Here, we provide a brief overview of the relevant model components.
-Classical, \textit{one-zone} models of chemical evolution assume instantaneous mixing of metals in the star-forming interstellar medium \citep[e.g.][]{matteucci21}.
+
+Classical, \textit{one-zone} models of chemical evolution assume instantaneous mixing of metals in the star-forming ISM\ \citep[e.g.][]{matteucci21}.
 This simple framework is a poor approximation of the Milky Way.
-The Galaxy evolves \textit{inside-out} -- where star formation is higher towards the center and in the early universe \citep{bird+13}.
-Additionally, stars can migrate several kpc over their lifetimes, mixing different chemical environments across the galaxy \citep{bird+12,sellwood+binney02}.
-Multi-zone models account for stellar migration and changing environments by including multiple zones with different chemical conditions which stars can move between.
-
-Star formation is set seperately for each zone.
-The Galaxy is divided into 200 rings, each 100\,pc wide representing a single zone.
+The Galaxy evolves \textit{inside-out} -- where star formation is higher towards the center and in the early universe \citep{WF91, kauffmann96, bird+13}.
+Stars can also migrate several kpc over their lifetimes, mixing different chemical environments across the galaxy \citep{bird+12,sellwood+binney02}.
+Multi-zone models account for stellar migration and changing environments by stitching together multiple one-zone models and mixing stellar populations.
+
+The Galaxy is divided into 200 rings, each representing a single, 100\,pc zone.
 Each ring (or zone) has a separate stellar population and gas supply.
-We initially assume an inside-out \sfh{}, where the star formation surface density $\Sigma_\star$ is given by
+We initially assume an inside-out SFH from \JJ, where the star formation surface density $\dot{\Sigma}_\star$ is given by
 \begin{equation}\label{eq:inside_out}
@@
 \end{equation}
-$\tau_\text{rise}=2$\,Gyr describes when the star formation rate reaches a maximum, and $\tau_{\rm sfh}$ describes the decay timescale of star formation as a function of radius $R$.
-\JJ~derives $\tau_{\rm sfh}(R)$ through analysis of four integral field spectroscopy surveys in \cite{sanches20}.
-At each $R$, the \sfh{} is normalized to match the stellar surface density gradient \citep{BHG16} and the total stellar mass reaches $5.17\times10^{10}\,\Mo$ \citep{LM15}.
-Star formation ends beyond a radius $R=15.5\,$kpc.
-The gas inflow is calculated to maintain the \sfh{} for each radius and time, using an extension of a Kennicutt-Schmidt law \citep{kennicutt98},
+$\tau_\text{rise}=2$\,Gyr loosely describes when the star formation rate reaches a maximum, and $\tau_{\rm sfh}$ describes the decay timescale of star formation as a function of radius $R$.
+\JJ\ derive $\tau_{\rm sfh}(R)$ through analysis of four integral field spectroscopy surveys in \cite{sanches20}.
+At each $R$, the SFH is normalized to match the stellar surface density gradient \citep{BHG16} assuming a total stellar mass of $5.17\times10^{10}\,\Mo$ \citep{LM15}.
+Star formation ends beyond a radius $R=15.5\,$kpc, but stellar populations are allowed to migrate as far as $R=20\,$kpc.
+The gas inflow is calculated to maintain the SFH for each radius and time, using an extension of the Kennicutt-Schmidt law \citep{kennicutt98} motivated by the combined observations of \citet{bigiel+10} and \citet{leroy+13},
 \begin{equation}
@@
 \begin{cases}
-    {\Sigma}_{\rm gas} & 2\times 10^7 \leq \Sigma_{\rm gas} \\ 
-    {(\Sigma}_{\rm gas})^{3.6} & 5\times 10^6 \leq \Sigma_{\rm gas} < 2\times10^7 \\ 
-    {(\Sigma}_{\rm gas})^{1.7} & \Sigma_{\rm gas} < 5\times10^6 \\ 
+    {\Sigma}_{\rm gas} & 2\times 10^7 \Mo\,{\rm kpc}^{-2} \leq \Sigma_{\rm gas} \\ 
+    {(\Sigma}_{\rm gas})^{3.6} & 5\times 10^6 \Mo\,{\rm kpc}^{-2}\leq \Sigma_{\rm gas} < 2\times10^7 \Mo\,{\rm kpc}^{-2}\\ 
+    {(\Sigma}_{\rm gas})^{1.7} & \Sigma_{\rm gas} < 5\times10^6 \Mo\,{\rm kpc}^{-2}.
 \end{cases}
 \end{equation} 
-where $\Sigma_{\rm gas}$ is measured in \Mo\,kpc$^{-2}$. 
-The scaling of this relationship varies with time due to the redshift dependence of $\tau_\star$ in molecular gas observed by \citet{tacconi18}. We assume a \citet{kroupa01} \imf.
-
-To account for radial migration, we use a Gaussian-based migration scheme.
-The $\Delta R \propto \sqrt{\rm time}$ dependence arises when migration proceeds as a consequence of the diffusion of angular momentum \citep{frankel18, frankel20}.
-As such, at each time step, each star particle moves some change in radius, based on 
+The scaling of this relationship varies with time due to the redshift dependence of $\tau_\star$ in molecular gas observed by \citet{tacconi18}. We assume a \citet{kroupa01} IMF.
+
+To account for radial migration, we use a normally-distributed, $\sqrt{\rm time}$ migration scheme. The final position of each star particle is sampled from
 \begin{subequations}
 \begin{align}
-        \delta R &\sim N(0, \sigma_R)\\
-        \sigma_R &= 1.27\,{\rm kpc} \left(\frac{dt}{1\,{\rm Gyr}}\right)^{0.5}
+        R_{\rm end} &\sim N(R_{\rm birth}, \sigma_R ) \\
+        \sigma_{R} &= 1.27\,{\rm kpc} \sqrt{\frac{t_{\rm end} - t_{\rm birth}}{\rm Gyr}}
 \end{align}
 \end{subequations}
-where $N(\mu, \sigma)$ represents a draw from normal distribution.
+At the boundaries, stars at $R=0$ move to $R=0$ if $R_{\rm end}<0$ and stars will move to $R=20$\,kpc if $R_{\rm end} > 20$\,kpc.
+\dbnote{would be better to change s.t.
+star truncates at 20 but moves there earlier...}
+The star moves from its birth radius to its final radius via
+\begin{equation}
+        R(t) = \Delta R \sqrt{\frac{t - t_{\rm birth}}{t_{\rm end} - t_{\rm birth}}}
+\end{equation}
+The $\Delta R \propto \sqrt{\rm time}$ dependence arises when migration proceeds as a consequence of the diffusion of angular momentum \citep{frankel18, frankel20}.
+At each time step, each star particle travels a radial distance sampled from 
+where $N(\mu, \sigma)$ represents a draw from normal distribution and $dt=20$\,Myr is the simulation timestep.%
+\footnote{Not shown here, we also explored variations of temporal, spatial resolution and migration strength and found these do not affect median trends significantly.}
 We do not account for radial gas flows.
-Not shown here, we also explore migration based on the \texttt{h277} hydrodynamical
+Not shown here, we also explore migration based on random walks and the \texttt{h277} hydrodynamical
 simulation results (with simulation parameters as in \citealt{bird+21}; see also \citealt{christensen12, zolotov12, loebman12, BZ14}), which leaves our qualitative conclusions unchanged. 
@@
 
-As the strength of outflows controls the resulting $\alpha$-element abundances, \JJ~create a metallicity gradient by defining
+As the strength of outflows controls the resulting $\alpha$-element abundances, we extend \JJ and create a metallicity gradient by defining
 \begin{equation}\label{eq:mass_loading}
-\eta(R) = r - 1 + \frac{y_{\alpha}^{\rm CC}}{Z_{\alpha, \odot}} 10^{(-0.08\,\text{kpc}^{-1})(R-4\,\text{kpc})+0.3}.
-\end{equation}
+\eta(R) = \frac{y_{\alpha}^{\rm cc}}{Z_{\alpha}(R)} -1 + r + \tau_{\star} / \tau_{\rm sfh} 
+\end{equation}
+where 
+\begin{equation}
+    \log Z(R) = \log Z_{\alpha,\ \odot} + 
+    0.29 + 
+    \begin{cases}
+        -0.015(R-5) & R < 5 \\
+        -0.09(R-5) & R \geq 5
+    \end{cases}
+\end{equation}
+and we approximate $\tau_\star/\tau_{\rm sfh} \approx 0.3$ 
+adapted from \citet{hayden+14}.
 This choice of $\eta(R)$ results in a [$\alpha$/H] gradient consistent with Milky Way observations \citep[e.g.][]{hayden+14, weinberg+19, frinchaboy+13}.
-Note that if we change our assumed $y_{\rm Mg}$, the values of $\eta$ will change similarly to maintain the correct chemical trends.
-
-To create a sample with similar characteristics of the subgiant observations, we sample 12,000 stars from the simulations such that the cumulative distribution function of stars in $R_{\rm gal}$ is the same for the subgiants and our comparison sample.
-
-\section{Results}
+If we change our assumed $y_{\rm Mg}$, the values of $\eta$ will change similarly to maintain the correct chemical trends.
+
+\section{Results}\label{sec:results}
 
@@
 
-Here, we present the time evolution of our fiducial model. In the next sections, we will discuss the choice of parameters and agreement with observations. 
-The fiducial model has the following qualitative characteristics of its C yields.
-\begin{description}
-    \item C is mostly (\about{80\%}) produced in \cc
-    \item \cc\ produce more C at higher metallicities
-    \item \agb\ stars produce less C at higher metallicities 
-\end{description} 
-The fiducial model uses the \cxi{} \agb\ yield tables uniformly scaled by a factor of \cfactor{} (see section \ref{sec:agb}, and Table \ref{tab:fiducial_mod}).
-
-Fig.~\ref{fig:c_evo} shows time evolution tracks of the fiducial model for \caah\ and \caafe. 
-As discussed in section~\ref{sec:equilibrium}, \caah\ is set by the total C/Mg yields. 
-\caafe\ is instead useful in understanding delayed C production. 
-As both Fe and C are delayed elements, [Mg/Fe] steadily decreases after a star formation event, unlike [Mg/H] which quickly reaches equilibrium.
-All plots showing \caafe\ going forward are selected in metallicity such that $-0.15 \leq {\rm [Mg/H]} \leq -0.05$, so metallicity-dependent yields do not affect this plot.
-The \caafe{}-diagram is, in essance, an emperical delay-time-distribution for a single stellar population of C, especially as we assume a $\propto t^{-1.1}$ delay-time-distribution for Fe. 
-Comparing the left and right panels of Fig.~\ref{fig:c_evo} highlights the differences between \caah\ and \caafe.
-While \caah\ quickly reaches its final equilibrium distribution (within \about{5}\,Gyr), \caafe\ continues to evolve in both [Mg/Fe] and [C/Mg] until the simulation ends.
-
-C evolution proceeds as follows, 
+Fig.~\ref{fig:c_evo} shows evolutionary tracks for every zone of the fiducial model for [C/Mg] against [Mg/H] and [Mg/Fe].
+\caah\ trend quickly reaches our equilibrium state in \about{5}\,Gyr. \caafe\ tracks continue to evolve due to the long tail in the DTD of \ia.
+
+The evolution of abundances in our fiducial model:
 \begin{enumerate}
-    \item \cc\ initially dominate production. As $\Ycc$ has strong metallicity dependence, [C/Mg] increases with time. 
-    \item \agb\ stars contribute delayed C, causing [C/Mg] to increase even faster with [Mg/H]. 
-    \item{} [C/Mg] plateaus as C also approaches equilibrium. 
-    \item{} [C/Mg] may decrease due to declining SFH or slightly negative yields from \about{1}\,\Mo stars.
+    \item[(1)] Star formation begins.
+Initially, \cc\ dominate enrichment.
+[C/Mg] evolves with yields set by $\Ycc/\Yoc$, resulting in increasing values with [Mg/H].
+[Mg/H] quickly approaches its equilibrium value, but Fe remains low in comparison (in agreement with \citealt{WAF17}).
+    \item[(2)]  A few hundred million years later,  delayed sources  enrich the ISM. \agb\ stars release C, raising [C/Mg], and \ia\ expel Fe, lowering Mg/Fe. 
+    \item[(3)] Several billion years later, [C/Mg] plateaus as C also approaches equilibrium. [Mg/H] reaches equilibrium. [Fe/H] continues to incrase due to ongoing \ia\ from old stellar populations.
+    \item[(4)] In the final few billion years, [C/Mg] decreases slightly due to declining \agb\ C yields. \caah\ trends shift only slightly, and [Mg/Fe] slowly and steadily decreases.
 
 \end{enumerate}
+
+This evolution is driven most dominantly by our chosen elemental yields, their
+dependence on metallicity, and their DTDs.
+As we will demonstrate in section 5.2 below, the slope of the [C/Mg]-[Mg/H] trend is
+set by the relative contributions of CCSNe and AGB stars to the overall C abundance.
+The positive metallicity dependence of massive star C yields outweighs the negative
+dependence of AGB star yields, causing [C/Mg] to increase with [Mg/H].
 
@@
 \centering
-\includegraphics{all_the_tracks.pdf}
+\includegraphics{figures/all_the_tracks.pdf}
 \caption[]{
     Time evolution of gas-phase C abundances in our fiducial model.
-    Each line represents a zone at a different galactic radii. The lines are coloured-coded by time. The left shows \caah\ and the right \caafe. 
+    Each line represents a zone at a different galactic radii. The lines are colour-coded by time. The left shows \caah\ and the right \caafe. 
 }
@@
 
+% note about \caafe plane
+% As low-$\alpha$ stars were formed in regions closer to chemical equilibrium, we only plot the medians of the low-$\alpha$ sequences in \caah. 
+% Instead, \caafe\ trends are set by the proportion of \agb\ C contribution.
+The \caafe{}-diagram, when restricted to a narrow range of metallicities, becomes an empirical delay-time-distribution of C.
+% High-$\alpha$ stars were formed in regions further from chemical equilibrium than stars with low [Mg/Fe].
+Immediately after a star formation event, \cc\ elements dominate and only after sufficient time do \ia\ elements like Fe reach their higher-equilibrium abundances.
+% Likewise, high-[Mg/Fe] stars will have a greater portion of \cc\ C, as low-[Mg/Fe] stars will include more \agb\ C. 
+% When binned in metallicity, median [C/Mg] changes by about 0.2 dex across the range of [Mg/Fe] at solar metallicities.
+As high-$\alpha$ stars have little to no delayed \ia\ Fe, these stars would also have little to no delayed \agb\ C.
+This means that AGB C stars make up about at most a fraction $f_{\rm agb} \approx 1 - 10^{-0.2} \approx 0.4$ of C production.
+% 
+% \begin{figure}
+%     \centering
+%     \includegraphics{apogee_caafe_binned.pdf}
+%     \caption{Caption}
+%     \label{fig:caafe_binned}
+% \end{figure}
+
 \subsection{Yield Variations}\label{sec:results_highmass}
@@
 
-\cc, which we assume make up the majority of C, set the overall C abundance trends.
-The top of Fig.~\ref{fig:first_models} shows models with varying $\Ycc$ metallicity dependence, $\zeta^{\rm cc}$.
-As the \caah~trend is approximated by equilibrium trends, the models with higher $\zeta^{\rm cc}$ also have a steeper slope in \caah.
-However, \caafe~is minimally affected by changes to $\zeta^{\rm cc}$ since \cc\ occurs on much shorter timescales than \ia\ and \agb\ enrichment.
-The only effects on \caafe, when considering the narrow metallicity slice, are because of either the slight change in equilibrium abundances, the imperfect evolution of the galaxy, or that the interstellar medium abundances are set by stars which were born at poorer metallicities.
- Hence, \caah\ tells us about the total C yield with metallicity, which \caafe\ is independent of.
-If we know the \agb\ C yields, then with observed \caafe\ abundance trends, we can infer the \cc\ C yields with metallicity.
-
 \begin{figure*}
-\includegraphics{all_p1.pdf}
+\includegraphics{sims_agb.pdf}
 
 \caption[]{
-    Stellar abundance trends in our model, assuming metallicity independent $\Ycc$.
-Coloured lines represent the median [C/Mg] in bins of [Mg/H] (left) or [Mg/Fe] (right) for each model.
-Black points and grey dashes represent the median and standard deviations of [C/Mg] for each [Mg/H] bin in the \citetjack~sample.
-In the right panels, we show the trends only for stars where $-0.15\leq {\rm [Mg/H]}\leq -0.05$.
-    \textbf{Top}: Models with different metallicity dependences for  \cc\ C yiels.
-    \textbf{Middle}: Our four different \agb\ models.
-    \textbf{Bottom}: Different \agb\ fractinos of C.
+    Stellar abundance trend predictions of our models .
+Coloured lines represent the median [C/Mg] in bins of [Mg/H] (left) or [Mg/Fe] (right) for each \agb\ table.
+Black points and grey dashes represent the median and 16th-84th percentiles of [C/Mg] in each bin in the \citetjack~sample.
+    The left panel only shows low-$\alpha$ stars. In the right panels, we show the trends only for stars where $-0.15\leq {\rm [Mg/H]}\leq -0.05$.
+    Stars are binned into 20 (left) or 12 (right) equal number bins. 
 }
@@
 
-To parameterize the \agb\ contribution to C production, we define $f_{\rm agb}$ to be the fraction of C which comes from \agb\ stars. 
+\begin{figure*}
+\includegraphics{sims_zeta_f.pdf}
+
+\caption[]{
+    Similar to Fig.~\ref{fig:first_models}. 
+    \textbf{Top}: Models with different metallicity dependences for  \cc\ C yields. \textbf{Bottom}: Different \agb\ fractinos of C.
+}
+\label{fig:zeta_f}
+\end{figure*}
+
+\begin{figure*}
+\includegraphics{figures/sims_degens.pdf}
+
+\caption[]{
+    Similar to Fig.~\ref{fig:first_models}. 
+    \textbf{Top}: Models with different metallicity dependences for  \cc\ C yields. \textbf{Bottom}: Different \agb\ fractinos of C.
+}
+\label{fig:sims_degens}
+\end{figure*}
+
+We evaluate our models by comparing predicted median stellar trends to our subgiant sample (see section~\ref{sec:data_selection}. 
+We draw 12,000 stars from the simulated stellar populations such that the selection probability is proportional to a stellar population's mass and that the subsample follows the same distribution in Galactocentric radius as the subgiants.
+
+Fig.~\ref{fig:first_models} show the four C yield models (\cxi, \vxiii, \kxvi, \pxvi).
+For the most part, different \agb\ yield tables result in qualitatively similar predictions.
+\vxiii, however, does not reproduce solar trends as the model predicts strong C destruction at slightly super-solar metallicities, resulting in inversions in both \caah\ and \caafe.
+As all \agb\ models predict C yields to decline with metallicity, all models predict an increasingly downward slope in \caafe\ with [Mg/Fe].
+A recent burst in star formation may hide this downturn (see section~\ref{sec:sfh}), but C destruction at the level predicted by \vxiii\ is not supported by our sample.
+Because the effects of alternate \agb\ yield sets are small, we focus on \cxi{} model for the remained of this paper. Alternate yield sets minimally affect our conclusions.
+
+The top of Fig.~\ref{fig:zeta_f} shows models with varying strengths of the $\Ycc$ metallicity dependence, $\zeta^{\rm cc}$.
+With higher $\zeta^{\rm cc}$, the model predicts a steeper \caah trend, owing to the direct relationship between the C/Mg equilibrium abundances and yield ratios.
+However, \caafe~is minimally affected by changes to $\zeta^{\rm cc}$ since \cc\ occurs on much shorter timescales than \ia\ and \agb\ enrichment.%
+\footnote{The only effects on \caafe, when considering the narrow metallicity slice, are because of either the slight change in equilibrium abundances, the imperfect evolution of the galaxy, or that the ISM abundances are set by stars which were born at poorer metallicities.
+}
+%  Hence, \caah\ tells us about the total C yield with metallicity, which \caafe\ is independent of.
+If we know the \agb\ C yields, then with observed \caafe\ abundance trends, we can infer the \cc\ C yields with metallicity.
+
+The bottom of Fig.~\ref{fig:first_models} shows three models with different C \agb\  fractions, defined as 
 \begin{equation}\label{eq:f_agb}
-    f_{\rm agb} \equiv \frac{\Ycagb(Z=\Zo)}{\Yct(Z=\Zo)},
-\end{equation}
-
-We can use the \caafe{} diagram of \apogee\ stars to estimate the delayed portion of C.
-When binned in metallicity, median [C/Mg] changes by about 0.2 dex across the range of [Mg/Fe] at solar metallicities.
-As high-$\alpha$ stars have little to no delayed \ia\ Fe, these stars would also have little to no delayed \agb\ C.
-This means that AGB C stars make up about at most a fraction $f_{\rm agb} \approx 1 - 10^{-0.2} \approx 0.4$ of C production.
-
-\caafe\ is sensitive to the assumptions about delayed C from \agb\ stars.
-If no C comes from low-mass stars, then [C/Mg] would be independent of [Mg/Fe], only [Mg/H].
-Instead, C shows strong trends  in \caafe\, independent of metallicity.
-
-In the middle row of Fig.~\ref{fig:first_models}, we first show the four C yield models (\kx, \kxvi, \cxi, \vxiii).
-For the most part, the \agb\ yield sets result in qualitatively similar predictions.
-\vxiii, however, does not reproduce solar trends as the model predicts strong C production at slightly above solar metallicities, resulting in a decreasing [C/Mg] with [Fe/Mg].
-As all \agb\ models predict some low-mass C destruction, each model does predict a downturn in [C/Mg] as [Fe/Mg] increases.
-A recent burst in star formation may hide this downturn (see section~\ref{sec:sfh}), but the C destruction is not supported directly by observations.
-
-We also investigate adjustments to the \agb\ yield fraction $f_{\rm agb}$
-The bottom of Fig.~\ref{fig:first_models} shows three models with different \agb\ fractions while using \cxi{} yields.
-The \caafe~relationship is set by $f_{\rm agb}$ because a specific amount of C must be released at a delayed time to match the \ia\ production of Fe and increase [C/Mg] as [Mg/Fe] decreases to reproduce the data.
-Increased $f_{\rm agb}$ results in a decreased slope in \caah, owing to the negative metallicity dependence of $\Ycagb$.
-So while \caah~alone cannot differentiate models which vary $f_{\rm agb}$ and $\zeta$ correspondingly, \caafe~provides information on $f_{\rm agb}$.
-So, we can use \caafe~to estimate $f_{\rm agb}\approx 0.2$, and then choose $\zeta$ to match \caah.
-
-\begin{figure*}
-\centering
-\includegraphics{nitrogen.pdf}
-
-\caption[]{Similar to Fig.~\ref{fig:first_models}.
-The top panels show models with different mass-ranges contributing \agb\ C yields.
-The middle panels show different star formation histories (section \ref{sec:sfh}) and yield normalizations.
-The bottom panels show [N/Mg] against [Mg/H] and [Fe/Mg] for the fiducial model.
-}
-\label{fig:nitrogen}
-\end{figure*}
-
-\subsection{Star Formation History and Outflows} \label{sec:sfh}
-
-In this section, we consider two modifications of our fiducial \sfh{}: \textit{lateburst} and \textit{earlyburst}.
-Our lateburst model adds a Gaussian factor to the inside-out \sfh{},
+    f_{\rm agb} \equiv \frac{\Ycagb(\Zo)}{\Yct(\Zo)}.
+\end{equation}
+Modifications of $f_{\rm agb}$ affect \caafe{} trends significantly more than \caah.
+At fixed metallicity, the \caafe\ trend is principally sensitive to how much C and Fe comes from delayed sources.
+Increasing the \agb\ fraction therefore steepens the \caafe\ trend as expected.
+Though each yield model predicts the trend to flatten at ${\rm [Mg/Fe} \lesssim 0.1 $, the median is still within the width of the observed distribution and the overall agreement is good.
+
+\subsection{Variations in Star Formation History} \label{sec:sfh}
+
+In this section, we consider an alternate SFH, namely one which exhibits a late-time elevation in the star formation rate.
+Motivated by the findings of \citet[see discussion in \JJ]{mor+19,isern19}, this \textit{lateburst} model
+adds a Gaussian burst to the fiducial inside-out model, 
 \begin{equation}\label{eq:lateburst}
@@
 
-The middle row of Fig.~\ref{fig:first_models} shows three models with our alternate \sfh{}.
-Changes to the \sfh{} leave \caah\ unchanged, but they do introduce slight variation in \caafe.
-Models with higher \agb{} fractions are more sensitive to variations in the \sfh{}.
-The late burst models result in [C/Mg] continuing to increase at low [Mg/Fe], but also introduce a dip not present in the data.
-Additionally, the early-burst
-reproduces the slight break between the low and high $\alpha$ sequences, but overshoots equilibrium more severely than the fiducial model. 
-In general, any of these \sfh{}s are consistent with this model.
+The bottom of Fig.~\ref{fig:first_models} compares the fiducial and lateburst models.
+The lateburst slightly shifts \caah\ down and only slightly perturbs \caafe.
+These variations are small compared to the width of the observed distribution.
+Building on \citet{james+23}, we therefore conclude that the \caah\ and \caafe\ trends reflect nucleosynthetic yields more than the Galactic SFH.
 
@@
 
-Our conclutions are limited by the many uncertainties in \gce\ modeling.
-
-A known uncertainty is the overall scaling of outflows and yields. While Milky Way \gce{} models like ours incorperate significant mass-loading, others
+While some Milky Way \gce{} models (including ours) incorporate significant mass-loading, others
 neglect mass-loading and instead use lower yields \citep[e.g.][]{MCM13, MCM14, spitoni19, spitoni20, spitoni21}.
-Our parameterization of $\eta$ illustrates this (see Equation~\ref{eq:mass_loading}) -- lowering $y_\alpha$ will additionly lower our values of $\eta$. 
-We consider a model where our adapted values of all yields are halved, in the bottom row of Fig.~\ref{fig:first_models}. This change does not affect our results.
-
-An addition source of theoretical uncertainty in this result is that the \ia\ yield and delay time distributions have their own uncertainties.
-Increasing both $y_{\rm Fe}^{\rm Ia}$ and $\Ycagb$ correspondingly leaves \caafe\ mostly unchanged.
-We show a model where we increase \ia Fe yields by 20\% and increase $f_{\rm agb}$ to 0.3, leaving median trends unchanged.
-
-Finally, the specific masses of \agb\ stars do affect the delay-time-distribution.
-If \agb\ are produced more by \about{1}\,\Mo stars than upper-intermediate \agb\ stars, then the delay-time-distribution of \agb\ C is more extended.
-In this case, a
-On the other hand, upper-intermediate \agb\ stars with masses greater than 5\,\Mo have lifetimes less than about 100\,Myr, which is only slightly longer than \cc.
-As such, changes to the amount of C from \cc\ and 5--8\Mo \agb\ stars is nearly indestinguashible from median abundance trends alone.
-
-\subsection{Gas-Phase Abundances}\label{sec:gas}
-
-As a final test of the model, we compare the model predictions against gas-phase measurements.
-Fig.~\ref{fig:gas_phase} shows the fiducial model's gas-phase predictions compared to observations of the Milky Way and extragalactic HII regions, halo stars, and damped Lyman-alpha systems.
-While obervations in HII regions and Milky Way stars agree that C/O generally increases at near-solar metallicities, damped Lyman-alpha systems and metal poor stars imply that C/O may also increase again at very low metallicities.
-
-Measurements of C abundances are challenging. 
-In HII regions, C/O abundance ratios are measured with either recombination lines or collisional excitation lines.
-While broad consistancy of our model with gas-phase measurments is promising, the large measurment errors limit the evaluative power of HII regions.
-We additionally include Milky Way thick disk (high-$\alpha$) and halo stars, which span a larger range of metallicities than thin disk stars.
-However, metal-poor abundance measurments require consideration of 3D-NLTE effects, which can be an \about{0.2} dex effect  (e.g.
-CITE).
-Finally, dwarf galaxies, damped Lyman-alpha systems, and extragalactic regions may represent different \sfh{}s than the Milky Way.
-As \agb\ C production is sensitive to variations in the \sfh, these environments may not exactly match our subgiant sample, limiting the usefulness of these abundance measurments in evaluating our model.
-
-C lines are relatively faint, and surveys such as GALAH struggle against low detection rates, potentially biasing sample measurments. 
-(e.g. gaia-eso AS WELL \citealt{franchini+20}).
-In the gas phase, HII regions are our best window into C abundances.
-Unfortunantly, C lacks strong collisional excitation lines, and recombination lines fall in the ultraviolet without nearby reference H lines \citep{skillman+20}.
-Recombination-line and collisional-excitation-line measurements furthermore disagree by a factor of \about{2} \citep{GR07}.
-
-Fig.~\ref{fig:gas_phase} shows the single-zone model and time-slices of the fiducial multi-zone model at present day and $t=2$\,Gyr. 
-Here, we consider a single-zone model with parameters consistant with the Gaia-Encelidus sausage\footnotemark{}.
-We chose the model to have mass loading $\eta=20$, star formation efficiency $\tau_{\star}=16\,{\rm Gyr}$, and a star formation history $\propto e^{-t/3{\rm\,Gyr}}$, evolved for 2\,Gyr \citep{james_dwarf}.
-The single-zone model is better able to replicate the slope of the abundances in dwarf galaxies, HII-regions, and halo stars.
-The single-zone model does not produce an equilibrium track, unlike the multi-zone models.
-As the single-zone model also evolves slower, the late contribution of AGB stars causes the steeper slope at near-solar metallicities.
-By including an increase of C yields at low-metallicity, the single-zone model is also able to reproduce the increasing [C/O] abundances with decreasing metallicity past ${\rm [O/H]} < -1.5$.
-In any case, there is large scatter in the measurments, which both models fall within.
+Both classes of models are able to reproduce many details of the disk abundance structure due to the strong degeneracy between the normalizations of elemental yields and mass-loading (see discussion in, e.g.
+\citealt{sandford+22} and appendix B of \citealt{james+23}).
+Our parameterization of $\eta$ illustrates this (see Equation~\ref{eq:mass_loading}) -- choosing a lower value of $y_{\alpha}$ will similarly result in lower values of $\eta$ while maintaining the same metallicity gradient.
+We consider a model where we double all yields, in the top row of Fig.~\ref{fig:sims_degens}. A uniform change in yields and outflows leaves our median trends relatively unchanged.
+
+Additionally, Fe yields and the \ia\  delay-time-distribution have their own uncertainties. Increasing both $y_{\rm Fe}^{\rm Ia}$ and $\Ycagb$ correspondingly leaves \caafe\ mostly unchanged.
+
+Fig.~\ref{fig:sims_degens} demonstrates this point with a model in which we increase the \ia\ Fe yields by 20\% and increase $f_{\rm AGB}$ to 0.3. 
+Fundamentally, the \caafe\ trends demand yield models in which these delayed components of C and Fe enrichment are in a particular proportion.
+
+Finally, the delay-time-distribution of \agb\ stars is determined by the mass dependence of the yield.
+If we shift the yield tables down in mass artificially, then the delay-time-distribution of \agb\ C is more extended.
+A lower $f_{\rm agb}$ is needed to produce a similar trend in \caafe{}.
+The top panel of Fig.~\ref{fig:nitrogen} demonstrates this point with a model.
+Conversely, shifting the yield tables up in mass shortens the DTD and requires a higher \agb\ fraction in order to make up the difference (verify).
+
+Initial mass function (and possible metallicity dependence)? Metallicity dependent Oxygen/Magnesium and Iron yields? Gas phase migration?
+
+\subsection{Nitrogen}
+
+\begin{figure*}
+\centering
+\includegraphics{figures/c_n.pdf}
+
+\caption[]{Similar to Fig.~\ref{fig:first_models}.
+The top panels show models with different mass-ranges contributing \agb\ C yields.
+The middle panels show different star formation histories (section \ref{sec:sfh}) and yield normalizations.
+The bottom panels show [N/Mg] against [Mg/H] and [Mg/Fe] for the fiducial model.
+}
+\label{fig:nitrogen}
+\end{figure*}
+
+N production, also affected by the CNO cycle, is closely tied to C.
+As a test of our model, we use the \agb\ N yield suggested by \citet{james+23}.The bottom row of Fig.~\ref{fig:nitrogen} shows [C/N] versus [Mg/H] and [Mg/Fe] for our fiducial model.
+We are able to closely match the [N/Mg]-[Mg/H] trend.
+The [N/Mg]-[Mg/Fe] is predicted to be more shallow than observed -- a limitation of the model potentially implying a more extended DTD for N production.
+We do not explore this further here since our focus is C.
+
+Though photospheric abundances of both C and N in red giants are affected by FDU, (see discussion in section~\ref{sec:data_selection}), their total abundance is conserved by the CNO cycle [e.g.
+CITE].
+C+N therefoe enables an additional test of the yields emperically calibrated in this paper and by \citet{james+23}.
+Thanks to the higher luminosities of red giants, we can make this comparison across a broader range of Galactocentric radii and, consequently, metallicity.
+
+Fig.~\ref{fig:cn} shows the predicted [C+N/Mg]-[Mg/H] trend in comparison to \citepos{weinberg+22} sample, also taken from \apogee\ DR17 (see their section 3).
+The model predicts a slightly shallower trend than the data, though the differences are within the width of the observed distribution, with differences at the $<0.05$dex level at fixed [Mg/H].
+While the number of stars in our subgiant sample drops off significantly at $\rm [Mg/H] \approx -0.3$, this comparison supports our empirically calibrated C and N yields down to $\rm [Mg/H] \approx-0.5$ (50\% lower in Z).
+
+\section{Gas-Phase Abundances}\label{sec:gas}
+
+\begin{table}
+	\centering
+    \caption[]{Single zone model parameters}
+	\label{tab:singlezone_params}
+
+	\begin{tabular}{l l l l l}
+		\hline
+        Model & $\eta$ & $t_{\rm end}$ & $\tau_\star$ & $\tau_{\rm sfh}$ \\
+		\hline
+        1 & 0 & 13 & 2 & 5\\
+        2 & 1 & 10 & 2 & 10\\
+        3 & 9 & 3 & 5 & 3\\
+        4 & 12 & 2 & 10 & 2\\
+		\hline
+	\end{tabular}
+\end{table}
+
+As a final test of our model, we compare the predictions against C abundances
+in the gas-phase.
+These measurements are challenging since C lacks strong collisional excitation
+lines, and its recombination lines fall in the ultraviolet with no nearby
+H lines to reference~\citep[e.g.,][]{skillman+20}.
+These two classes of spectral lines are also systematically discrepant at the
+factor of~$\sim$2 level~\citep{GR07}.
+As a consequence, the uncertainties associated with any one measurement are
+substantial (see the representative error bars in Fig. 13), but we are able to
+illuminate the underlying mean trends by combining observations from multiple
+sources.
+\par
+Fig. 13 shows our compilation alongside the gas-phase abundances in our model
+at snapshots of~$t = 2$ Gyr and the present day.
+While we used Mg as our representative alpha element in our APOGEE sample, O
+is more readily observed in the gas-phase, so we shift focus to C/O in this
+section.
+The model at the present day is consistent with the mean trend seen in HII
+regions in the MW and similar star forming galaxies at redshift~$z \sim 0$.
+Together with our results in~\S~5, this agreement suggests that our yield model
+is an accurate description of C nucleosynthesis at metallicities typical of
+MW-like galaxies.
+
+Nonetheless, our model does not extend as low in metallicity as dwarf galaxies
+or (especially) damped Lyman-alpha systems.
+To test our model at these abundances, we run a suite of one-zone GCE models
+with a handful of different parameter choices.
+\note{[Describe parameter choices here, beginning with some fiducial set of
+choices] Note: after seeing Fig. 13, I'd say it's worth using different
+linestyles to mark the different parameter choices in Fig. 8 -- I'd stick
+with black as color already differentiates between multi-ring and one-zone
+models.}
+Fig.~\ref{fig:gas_phase} also plots a single-zone model and time-slices of the fiducial multi-zone models gas-phase at present day and $t=2$\,Gyr. 
+Our single-zone model is designed to have parameters broadly consistent with the Gaia-Encelidus sausage.
+We evolve the singlezone model for 2\,Gyr, using mass loading $\eta=20$, star formation efficiency $\tau_{\star}=30\,{\rm Gyr}$, and a star formation history $\propto e^{-t/3{\rm\,Gyr}}$.
+The single-zone model uses a 1.5 mass factor times f=0.25 C11 yields.
+Note that the mass shift results in significant C destruction by high-mass AGB stars at low metallicities, enabling the model to reproduce the low [C/O] abundances at [O/H] = -1.
 
@@
 
+Each of these one-zone models predicts a steeper C/O-O/H trend than our
+fiducial multi-ring model from previous sections.
+This difference arises because the trend in the multi-ring models arises as a
+superposition of end-points (see Fig. 7), qualitatively similar to, e.g.,
+\citepos{schonrich-binney09} argument regarding
+the low-alpha sequence.
+In the one-zone models, the trend instead arises as an evolutionary sequence.
+To demonstrate this point further empirically, Fig. 13 includes measurements
+in halo and thick disk stars.
+This sample indeed shows a C/O-O/H trend that is clearly steeper than our
+fiducial multi-ring model, which is an accurate representation of the APOGEE
+low-alpha sequence (see Fig. 8).
+
+At the lowest metallicities ($\log_{10}(Z / Z_\odot) \lesssim -2$), our suite
+of one-zone models is consistent with the C/O ratios seen in damped Lyman-alpha
+systems.
+For all parameter choices, these ratios simply reflect the relative C and O
+yields of low-metallicity massive stars (see Fig. 5), with the increase in C/O
+at higher metallicities arising due to the onset of AGB star enrichment (see
+Fig. 7).
+As a consequence, our yield model as parameterized predicts that C/O ratios
+should never be significantly below~$\sim$half solar.
+This prediction is challenged by the measurements in both dwarf galaxies and
+halo/thick disk stars in Fig. 13, which suggest ratios~$\sim$$0.2 - 0.3$ dex
+below solar between~$\log$(O/H) = X and Y.
+
+This discrepancy could arise at least in part due to failures of our yield
+prescription and, by extension, could point to shortcomings in stellar
+nucleosynthesis models.
+However, we cannot rule out the possibility of systematic uncertainties in
+abundance determinations playing a role.
+At these metallicities, deviations from local thermal equilibrium (LTE) can
+bias measurements at the~$\sim$0.2 dex level~\citep[e.g.,][]{amarsi+19}.
+Considerations of non-LTE effects are not included in our APOGEE sample, but
+the corrections are smaller near solar metallicity.
+
 \begin{figure*}
 \centering
-\includegraphics[]{summary.pdf}
+\includegraphics[]{figures/summary_plot.pdf}
 \caption[]{Gas-phase C abundances. We plot our model at $t=2$\,Gyr and present day as thick solid lines. Black lines are single-zone models. Points represent measurements in 
@@
     Milky Way halo and thick disk stars \citep[green stars;][]{amarsi+19, nissen+14, fabbian+09},
-    and Milky Way high-$\alpha$ stars (yellow points; \citealtjack).
-}
+    and Milky Way high-$\alpha$ stars (yellow points; \citealtjack), and high redshift galaxy through JWST \citep[yellow hexagon;][]{arellano-cordova+2022}.
+}
+
 \label{fig:gas_phase}
@@
 
-\section{Conclusions}
-
-In this work, we investigated the role of C yields on the predictions of multi-zone \gce{} models. 
-We began by adopting an equilibrium approximation to estimate the total C yields with metallicity from \apogee{} subgiant \caah{} trends.
-We find that $\Yct/y_{\rm O} = 1/3 + 4(Z-\Zo)$ and $\Yct/y_{\rm Mg} = 2.7 + 32 (Z-\Zo)$, where we assume ${\rm [Mg/O]} = 0$.
-We show that \caah{} is a diagnostic for total C yields with metallicity, but \caafe{} provides information about delayed C production.
-From the \caafe{} trends, we estimate that \agb\ stars with masses between about 1 and 3 \Mo contribute \about{20\%} of total C abundances.
-In this model, the remaining \about{80\%} of C comes from high-mass stars with a metallicity dependent yield of $\Ycc/y_{\rm Mg} = 2.2 + 55 (Z/\Zo)$, broadly consistant with rotating \cc\ models.
-
-We additionally explore variations of the assumed \sfh{} and outflow mass-loading factor $\eta$.
-We find that alternate \sfh{}s can perturb \caafe and \caah\ abundances slightly.
-Decreasing both outflows and yields by the same factor leaves the \caah~and \caafe~trends unaffected, ingoring effect to the metalliticy distribution of starrs.
-These constraints on the relative yields of C, O, and Mg are robust against variations in $\eta$.
-
-Finally, we compare our model against gas-phase measurements and Milky Way halo stars.
-By including yields which are enhanced at low metallicities, \cc\ and \agb\ stars together are able to explain the general trends of C from metallicities of ${\rm [O/H]} = -3$ to 0.5.
-
-Our C yield constraints provide a useful benchmark for stellar evolution models.
-C yields are sensitive to poorly understood processes, including mass-loss prescriptions, explodability, nuclear cross sections, convection, and stellar structure.
-Future spectroscopic surveys combined with Gaia kinematics \citep{gaia} will continue to enhance our understanding of chemical evolution.
-Both the Sloan Digital Sky Survey V's Milky Way Mapper program ({\sc SDSS-V/MWM}) \citep{sdssv} and the Dark Energy Spectroscopic Instrument ({\sc DESI}) Milky Way survey \citep{desi, desi:mw} will each measure spectra of upwards 6,000,000 Milky Way stars.
-These larger samples will enable similar work to tighten constraints on stellar models and our understanding of galaxy structure and evolution.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%Log in with your OSC username and password.
-
-%%%%%
+\section{Conclusions}\label{sec:conclusions}
+
+Building on~\citet{james+23}, we quantify the impact of C yield assumptions on Milky Way GCE models.
+We use Roberts et al.'s (2023) sample of APOGEE subgiants as our primary observational benchmark, as subgiant atmospheres most likely reflect their birth C abundances (see discussion in section~\ref{sec:data_selection}).
+In our fiducial model, C initially increases following the slope of the \cc\ C dependence.
+Later, AGB contributions from C cause a sharp rise in \caah, which slows down due to declining AGB C production and the approach towards equilibrium.
+The chemical elemental reach a quasi-equilibrium within \about{5}\,Gyr.
+As a result, the current C/Mg versus metallicity gradient is a superposition of equilibrium states, mixed together from different Galactic positions.
+
+The slope of the predicted \caah\ relation is principally sensitive to the collective metallicity dependence of \cc\ C yields.
+While AGB yields are predicted to decline with metallicity, out models show that \cc\ dominate the trend and make an overall positive metallicity trend. 
+As the strength of the \cc\ metallicity dependence increases, the slope of the \caah\ trend correspondingly increases.
+The small effects of \agb\ C yield on the \caah\ trend can be easily corrected by small adjustments of the \cc\ yield's metallicity dependence.
+Our predicted slope of NUMBER is approximately consistent with the \citet{LC18} rotating stellar models, however no simulation contains sufficient mass resolution or accuracy to reproduce the observed trends accurately.
+
+Because massive star enrichment dominates the C mass budget in our models, the predictions are relatively insensitive to the choice of AGB star yield model.
+Of the \agb\ tables tested here, \cxi, \kxvi, and \pxvi\ all predict similar abundance trends in [C/Mg] with [Mg/H] and [Fe/Mg].
+The strong destruction of C by massive stars at \about{} solar metallicity   in \vxiii\ are instead in tension with the data (See Figs.~\ref{fig:first_models})  and~\ref{fig:agb-ssp})
+As both the \cxi\ and \pxvi\ models predict \about{} linear N yields as well, these combined models best explain combined C and N abundance trends (see Appendix!?).
+
+As in~\citet{james+23}, we have constrained yield ratios as opposed to absolute yields.
+For example, scaling yields and outflows by a corresponding factor leaves abundance ratio trends unchanged (Fig.~\ref{fig:sims_degens}).
+Effects such as black hole formation could create systematic shifts on predicted chemical yields.
+Variations in the SFH instead only induce minor systematic shifts
+
+When combined with~\citeauthor{james+23}'s~\citeyearpar{james+23} empirically calibrated N yields, we find that our fiducial model accurately describes the [C/N]-[Mg/H] relation in our sample.
+The [C/N]-[Mg/Fe] relation, on the other hand, is shallower than the data, indicating that the DTD of C production may be sharper than our AGB yield tables would suggest (or the N DTD more extended, or both).
+
+Finally, we compare our models againsts a compilation of literature gas-phase and halo-star abundances (see Fig.~\ref{fig:gas_phase}).
+Our fiducial model fails to explain the lowest values of [C/O] at metallicities of -1 to -2.
+We briefly consider a modified variation of the CCSNe yield of C which drops to explain these values, which maintains trends consistant with APOGEE.
+
+Our results demonstrate the power of empirically calibrated stellar yields.
+In our GCE models, trends in abundance ratios with metallicity are largely determined by trends in yield ratios with metallicity.
+As a result, the metallicity dependence of the total, population-averaged C yield is tightly constrained by the [C/Mg]-[Mg/H] relation, but the metallicity dependencies of the individual contributions from CCSNe and AGB stars are less precisely determined.
+Due to the sensitivity of elemental yields to poorly understood processes, such as mass-loss rates and convection, our results provide a useful benchmark for stellar evolution models~\citep[see the discussion in e.g.][]{gil-pons2022}.
+With abundance measurements for several million stars provided by upcoming spectroscopic surveys, particularly SDSS-V's Milky Way Mapper program~\citep{sdssv}, constraints on both stellar nucleosynthesis and the assembly history of our Galaxy will become increasingly more powerful.
+
+More C observations across different galactic environments will continue to refine a complete understanding of C production, including the yields of the first stars,  evolution in the bulge, and so on.
+
 \section*{Acknowledgements}
@@
 
+\apogee\ is part of SDSS-IV \citep{sloan_telescope, apogee_instrumentation, sdss_iv_overview, sdss17, apogee17, aspcap}.
+
+Funding for the Sloan Digital Sky 
+Survey IV has been provided by the 
+Alfred P. Sloan Foundation, the U.S. 
+Department of Energy Office of 
+Science, and the Participating 
+Institutions.
+
+SDSS-IV acknowledges support and 
+resources from the Center for High 
+Performance Computing  at the 
+University of Utah. The SDSS 
+website is www.sdss4.org.
+
+SDSS-IV is managed by the 
+Astrophysical Research Consortium 
+for the Participating Institutions 
+of the SDSS Collaboration including 
+the Brazilian Participation Group, 
+the Carnegie Institution for Science, 
+Carnegie Mellon University, Center for 
+Astrophysics | Harvard \& 
+Smithsonian, the Chilean Participation 
+Group, the French Participation Group, 
+Instituto de Astrof\'isica de 
+Canarias, The Johns Hopkins 
+University, Kavli Institute for the 
+Physics and Mathematics of the 
+Universe (IPMU) / University of 
+Tokyo, the Korean Participation Group, 
+Lawrence Berkeley National Laboratory, 
+Leibniz Institut f\"ur Astrophysik 
+Potsdam (AIP),  Max-Planck-Institut 
+f\"ur Astronomie (MPIA Heidelberg), 
+Max-Planck-Institut f\"ur 
+Astrophysik (MPA Garching), 
+Max-Planck-Institut f\"ur 
+Extraterrestrische Physik (MPE), 
+National Astronomical Observatories of 
+China, New Mexico State University, 
+New York University, University of 
+Notre Dame, Observat\'ario 
+Nacional / MCTI, The Ohio State 
+University, Pennsylvania State 
+University, Shanghai 
+Astronomical Observatory, United 
+Kingdom Participation Group, 
+Universidad Nacional Aut\'onoma 
+de M\'exico, University of Arizona, 
+University of Colorado Boulder, 
+University of Oxford, University of 
+Portsmouth, University of Utah, 
+University of Virginia, University 
+of Washington, University of 
+Wisconsin, Vanderbilt University, 
+and Yale University.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+\section{Comparison with other samples}
+
+Discuss
+\begin{description}
+    \item \citet{vincenzo+21}
+    \item Gaia-ESO survey
+    \item \citet{bensby+21}
+    \item \citet{weinberg+22}
+    \item GALAH: Low completion, one line (6588Å), likely observational effects of lower detection rates for metal poor stars, but also strong systematic from APOGEE.
+    \end{description}
+
+    There are large spectroscopic surveys (RAVE, LAMOST)  but they do not have C abundances.
+
+\begin{figure}
+    \centering
+    \includegraphics{c+n.pdf}
+    \caption{[C+N/Mg]}
+    \label{fig:cn}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics{figures/cmg_mgh_allstar.pdf}
+    \includegraphics{figures/cmg_mgfe_allstar.pdf}
+    \caption{Caption}
+    \label{fig:enter-label}
+\end{figure}
+
 \bsp	% typesetting comment

### 2024-08-29 carbon_paper/tex/main.tex
updated text (created 3panel degeneracy figure)

@@
 
+\usepackage{tikz}
+
 \graphicspath{{figures/}} 
@@
 
-\newcommand{\citetjack}{\citet{jack}}
-\newcommand{\citepjack}{(Roberts et al.~2024, in prep.)}
-\newcommand{\citealtjack}{Robert et al.~2024, in prep.}
-\newcommand{\cxi}{\texttt{\hyperlink{C11}{C11}}}
-\newcommand{\pxvi}{\texttt{\hyperlink{P16}{P16}}}
-\newcommand{\kxvi}{\texttt{\hyperlink{K16}{K16}}}
-\newcommand{\vxiii}{\texttt{\hyperlink{V13}{V13}}}
-\newcommand{\cfactor}{2.4}
-\newcommand{\nsubgiants}{16,365}
+\newcommand{\fruity}{\texttt{\hyperlink{fruity}{Fruity}}}
+\newcommand{\nugrid}{\texttt{\hyperlink{nugrid}{NuGrid}}}
+\newcommand{\monash}{\texttt{\hyperlink{monash}{Monash}}}
+\newcommand{\aton}{\texttt{\hyperlink{aton}{ATON}}}
+\newcommand{\cfactor}{1.44}
+\newcommand{\nsubgiants}{14,069}
 
@@
 \newcommand{\ycmg}{\ensuremath{2.7 + 32\left(Z-\Zo\right)}}
-\newcommand{\ycccmg}{1}
-\newcommand{\yco}{1}
 \newcommand{\fmeas}{20\%}
@@
 
-\newcommand{\Yct}{\ensuremath{y_{\rm C}}}
-\newcommand{\Ycc}{\ensuremath{y_{\rm C}^{\rm CC}}}
-\newcommand{\Yoc}{\ensuremath{y_{\rm Mg}^{\rm CC}}}
-\newcommand{\Ycagb}{\ensuremath{y_{\rm C}^{\rm AGB}}}
-% \newcommand{\y}{\ensuremath{\rotatebox[origin=B,y=0.5ex]{180}{y}}}
+\newcommand{\Yct}{{y_{\rm C}}}
+\newcommand{\Ycc}{{y_{\rm C}^{\rm CC}}}
+\newcommand{\Yoc}{{y_{\rm Mg}^{\rm CC}}}
+\newcommand{\Ycagb}{{y_{\rm C}^{\rm AGB}}}
+\newcommand{\aagb}{\alpha_{\rm C}^{\rm AGB}}
+\newcommand{\zagb}{\zeta_{\rm C}^{\rm AGB}}
+\newcommand{\zcc}{\zeta_{\rm C}^{\rm CC}}
+ \newcommand{\yb}{\ensuremath{\rotatebox[origin=B,y=0.5ex]{180}{y}}}
 \newcommand{\y}{Y}
-
-\newcommand{\Mo}{%
-    \ifmmode {\rm M}_{\sun}%
-    \else {M$_{\sun}$}%
-    \fi}
-
-\newcommand{\Zo}{%
-    \ifmmode Z_{\sun}%
-    \else $Z_{\sun}$%
-    \fi}
+\newcommand{\fagb}{f_{\rm C}^{\rm AGB}}
+
+\newcommand{\Mo}{ {\rm M}_{\sun}}
+
+\newcommand{\Zo}{ Z_{\sun}}
 
@@
 \makeatother
+
+% Caption macros
+\newcommand{\captionline}[2][very
+thick]{\tikz[baseline={([yshift=-.5ex]current bounding box.base)}]{
+\draw[#2,#1, line cap=round] (0,0) -- (0.3,0); }}
 
@@
 \newcommand{\dbadd}[1]{{\color{Thistle} #1}}
-\newcommand{\dbnote}[1]{{\color{Thistle} \textit{\small (DB: #1)}}}
+\newcommand{\dbnote}[1]{ {\color{Thistle} \textit{\small (DB: #1)}} }
 
@@
 
-Despite being one of the most abundant metals in the universe~\citep[e.g.][]{asplund+09}, C nucleosynthesis is poorly understood.
-Formed in the cores of stars during He fusion, C is the first \dbadd{primary?
+\begin{figure*}
+    \centering
+    \includegraphics{subgiants.pdf}
+    \caption{The [C/Mg] ratio against [Mg/H] (left) and [Mg/Fe] (right) for the \citet{jack}~sample of \apogee{} subgiants.
+On the left, we plot high and low-$\alpha$ stars in blue and orange, using the separation defined in Equation \ref{eq:high_alpha} \dbstrike{(the high and low-$\alpha$ stars are named for their high or low $\alpha$-element (Mg) to Fe ratios)}.
+On the right, we colour-code stars according to their [Mg/H] abundance.} \label{fig:subgiants}
+\end{figure*}
+
+Despite being the most abundant metal in the Universe~\citep[e.g.][]{magg+22}, the nucleosynthetic origin of C is inadequately understood. \dbnote{need synonyms for poorly understood}
+Broadly, studies agree that both high mass and asymptotic giant branch (AGB) stars produce C, but their relative yields are disputed.
+From a Galactic chemical evolution (GCE) perspective, some authors have argued that high-mass stars should dominate~\citep[e.g.][]{prantzos+94, HEK00, romano+20, franchini+20, gustafsson22}, and others have argued that AGB stars should contribute at least half of the C in the universe~\citep[e.g.][]{tinsley79, chiappini+03, mattsson10, KKU11, rybizki+17, KKL20}.
+\dbadd{We aim to empirically characterize the yields of C and the ratio of AGB and CCSNe production.}
+
+% Formed in the cores of stars during He fusion, C is the first \dbadd{primary?
 element} after He.
@@
 \dbnote{I don't like how many e.g.'s there are, and is this the right citation here?}
-\dbadd{
-Because the effects of first dredge up are mass-dependent, C and N abundances are frequently used as age indicators for RGB stars \citep{MG15, martig16, hasselquist19, vincenzo+21}. 
-}
-\dbnote{C abundnces for stellar structure (opacities) and star formation (line cooling)}
-Broadly, it is well understood that both lower-intermediate-mass and high-mass stars produce C.
-However, the relative yields from these two classes of stars and their dependence on  metallicitys unknown \add{(see discussion below)}.
-
-% \footnotetext{\strike{By metallicity, we mean the (mass) fraction of any element which is not H or He, denoted by $Z$. For the sun, we take $Z_\odot=0.016$. CHECK THIS~} }
-
-Like many other metals, C nucleosynthesis \dbstrike{is poorly understood because its predicted yields} \dbadd{predictions from stellar evolution are highly uncertain \citep[see reviews][]{romano+10, KL14}}.
-\strike{Yield predictions} are shaped by poorly understood processes, such as mass loss rates \citep{ventura+13}?, nuclear reaction networks, rotational mixing \citep{frischknecht+16, LC18}, and convection ~\citep{chieffi2001}.
-\dbnote{check citations here...}.
-Binarity (and the metallicity dependence thereof), e.g. MKB2019, farme,
-Small changes in the initial mass ($0.01\Mo$) of massive stars can dramatically change the subsequent evolution \citep{bruenn+2023, emily+21}.
-As such, accurate yield predictions would require a much more densly sampled set of models in mass, metallicity, and rotation rates then are presently available.
-Furthermore, binary evolution is rarely included in massive star models with possibly important implications for yields \citep{farmer+21}, despite the large (metallicity-dependent) fraction of massive stars which live in binary systems \citep{MKB2019}.
-
-\dbnote{added paragraph here}
-In light of these difficulties with accurate theoretical modeling, recent work has instead sought to characterize chemical yields empirically.
+%\dbadd{
+% Because the effects of first dredge up are mass-dependent, C and N abundances are frequently used as age indicators for RGB stars \citep{MG15, martig16, hasselquist19, vincenzo+21}. 
+% }
+% \dbnote{C abundnces for stellar structure (opacities) and star formation (line cooling)}
+
+Predictions of C yields from stellar evolution and supernova (SN) models are riddled with uncertainties (see, e.g., the reviews/summaries by \citealt{romano+10, KL14}).
+Stellar yields are shaped by many poorly understood processes, such as mass loss rates \citep{sukhbold+16, beasor+2020}, rotational mixing \citep{frischknecht+16, LC18}, reaction rates \dbadd{citations}, and convection \citep{chieffi2001, ventura+13}.
+\dbnote{I checked these, is sukhbold the best reference on mass loss?}
+\dbadd{In addition, stellar parameters such as convection and mass loss are calibrated to match observed stars and cannot be predicted from first principles.} \dbnote{need to check if this means SE models are calibrated to match yields or just stellar parameters.}
+Small changes in the initial mass of only $\sim$$0.01 M_\odot$  were recently shown to have dramatic effects on the evolution and explosion outcomes of massive stars \citep{bruenn+2023, vartanyan_burrows2023}.
+Furthermore, many stars are found in binary systems \dbadd{(e.g. \citealt{MKB2019}, others?)}, the effects of which are almost entirely unexplored in stellar nucleosynthesis models \citet{farmer+21}.
+Therefore, accurate yield predictions from stellar theory requires both a much greater understanding of stellar physics and a much more densely sampled grid of models than is currently available.
+
+In light of the challenges of stellar theory, recent work has instead sought to characterize chemical yields empirically.
 \citet{HLA20} measured the abundance ratios in the ejecta of Cassiopeia A using spatial resolved X-ray spectra.
 \citet{weinberg+19, weinberg+22} analyzed the abundance ratio trends of high- and low-alpha sequence stars in APOGEE~\citep{apogee17} to infer relative yields of prompt and delayed enrichment sources and the metallicity dependence thereof.
-\citet{emily+19, emily+22, emily+23} applied the same methodology to GALAH~\citep{DeSilva2015, Martell2017}.
+\citet{emily+19, emily+22, emily+24} applied the same methodology to GALAH~\citep{DeSilva2015, Martell2017}.
 \citet{rodriguez+21, rodriguez+23} measured the mean Fe yield of core-collapse supernovae (CCSNe) using the radioactive tails of their lightcurves.
-
-\dbnote{combine this with previous, shorten J23 description and call out other ongoing work e.g. Miquela's He, James's chemical equilibrium, ...}
-Most notably for our purposes,~\citet{james+23} used Galactic chemical evolution (GCE) models to show that the correlation between gas-phase N and O abundances (see their Fig.
-1) can be explained by the metallicity dependence of relative N and O yields.
-Variations in assumptions regarding GCE parameters, such as the detailed star formation history (SFH), did not impact their conclusions and are instead a likely source of scatter in the observed relation.
-Here, we apply similar methodology to constrain C yields, which are closely related to N.
-
-GCE connects a galaxy's evolutionary history to the detailed elemental abundances in its gas and stars.
-Each enrichment process has characteristic chemical signatures and timescales, enabling us to reconstruct \strike{chemical} \add{enrichment} histories.
-\add{As an element that is well-measured in stellar spectra, many} \dbadd{with large samples of stellar C abundancess}, \strike{Many} previous GCE works \add{have} focused on C abundances (\citealt{DTS78, BF06, prantzos+18, berg+19}; see also the recent reviews by \citealt{romano22} and \citealt{RM21}).
-To date there is no consensus on the detailed origin of C; some authors have argued that high-mass stars should dominate~\citep[e.g.][]{prantzos+94, HEK00, romano+20, franchini+20, gustafsson22}, and others have argued that AGB stars should contribute at least half of the C in the universe~\citep[e.g.][]{tinsley79, chiappini+03, mattsson10, KKU11, rybizki+17, KKL20}.
-
-    As our primary observational constraint, we use a sample of subgiant stars from the \apogee{} \citep{apogee17} selected by the criteria in \citetjack.
-According to stellar evolution theory and observations, subgiants most accurately represent their birth composition \citep{gilroy89, korn+07, lind+08, souto+18, souto19}.
-Fig.~\ref{fig:subgiants} shows the subgiant sample plotted in \caah\ and \caafe{}.\footnotemark{} In this sample, [C/Mg] increases with metallicity, and [C/Mg] decreases with [Mg/Fe] at fixed [Mg/H]. 
-From observations of nearby stars and (extragalactic) gas, we know that [C/O] against [O/H] traces a banana shape (see Fig.~\ref{fig:gas_phase} and section~\ref{sec:gas}).
-At the very lowest metallicities\strike{, where} \add{(}$[{\rm O/H}]\lesssim-2$\add{)},%
-%
-observations \strike{suggest} \add{indicate} that [C/Mg] declines with metallicity.
-From $-2 \lesssim {\rm [O/H]}\lesssim -1$, [C/Mg] is roughly constant with metallicity. 
-At higher metallicities ([O/H]~$\gtrsim -1$), [C/Mg] increases with metallicity.
-
-\strike{Using the subgiant abundance trends, we will develop a model of the enrichment sources and evolution of C.}
-\add{We will show in section~\ref{sec:results} below that these correlations in the bulk population abundances alone are quite constraining for the origin of C.}
-
-\footnotetext{In this paper, we use the standard notation for chemical abundances.
-$[A/B] = \log_{10}\left(A/B\right) - \log_{10}\left(A_{\sun}/B_{\sun}\right)$, i.e.
-$[A/B]$ is the logarithm of the mass ratio between A and B, scaled such that $[A/B]=0$ for the sun (see Table~\ref{tab:fiducial_mod} for solar scale.)}
+\dbnote{even papers as far back as at least https://ui.adsabs.harvard.edu/abs/1997NuPhA.621...27G/abstract do this.
+Include this series as well: https://ui.adsabs.harvard.edu/abs/2023MNRAS.525.1329L/abstract}
+
+% \note{Reading through at least at this moment, I'd say this is a reasonable place for a new paragraph.
+I wouldn't worry about referencing Weller et al.
+(2024) since He chemical evolution is not super relevant here.}
+ Folowing many previous works  (e.g.
+\citealt{DTS78, BF06, prantzos+18, berg+19}; see also the recent reviews by \citealt{romano22} and \citealt{RM21}.) this paper focuses on the evolution of C in GCE models.
+Most notably for our purposes, \citet{james+23} recently showed that the enrichment history of the Galactic disk can be described as an equilibrium phenomenon.
+In equilibrium GCE, trends in abundance ratios with metallicity arise as a consequence of trends in yield ratios (see discussion in their section {\color{red} X.Y}).
+\citet{james+23} had previously shown that the correlation between gas-phase N and O abundances (see their Fig.
+1) could be described as a consequence of the metallicity dependence of the relative N and O yields.
+The equilibrium scenario suggests that this argument should extend to any element whose enrichment by stellar populations does not require long timescales ($\gtrsim$few Gyr).
+We therefore extend \citepos{james+23} arguments to C, which is closely related to N.
+
+We use a sample of subgiant stars from APOGEE \citep{apogee17} as our primary observational constraint.
+\dbadd{APOGEE Subgiants provide a large, homogenous sample of well-measured C abundances unaffected by stellar evolution}.
+Subgiants advantageously have photospheric abundances directly representing birth C abundances \citep{gilroy89, korn+07, lind+08, souto+18, souto19}.
+In other evolutionary phases, the measured abundances are known to be affected by internal processes (see discussion in section 2 below), namely gravitational settling in main sequence stars {\color{red} (reference)} and dredge-up in red giants {\color{red} (reference)},
+Our sample should greatly mitigate these difficulties with inferring birth abundances of C, which have been a significant source of uncertainty for previous investigations of its nucleosynthetic origin.
+
+% \dbnote{not sure the observations below need to be  too detailed here?
+Maybe just state that C/O appears to have a universal shape across environments and direct to that section since our main focus is on APOGEE?
+and disk chemistry?
+}
+% \dbstrike{
+% From observations of nearby stars and (extragalactic) gas, we know that [C/O] against [O/H] traces a banana shape (see Fig.~\ref{fig:gas_phase} and section~\ref{sec:gas}).
+% At the very lowest metallicities ($[{\rm O/H}]\lesssim-2$),%
+% %
+% observations indicate that [C/Mg] declines with metallicity.
+% From $-2 \lesssim {\rm [O/H]}\lesssim -1$, [C/Mg] is roughly constant with metallicity. 
+% At higher metallicities ([O/H]~$\gtrsim -1$), [C/Mg] increases with metallicity.
+% }
+% \dbstrike{We will show in section~\ref{sec:results} below that these correlations in the bulk population abundances alone are quite constraining for the origin of C.}
 
@@
 
-\section{Data Selection}\label{sec:data_selection}
-
-\begin{figure*}
-    \centering
-    \includegraphics{subgiants.pdf}
-    \caption{The [C/Mg] ratio against [Mg/H] (top) and [Mg/Fe] (bottom) for the \citetjack~sample of \apogee{} subgiants.
-On the top, we plot high and low-$\alpha$ stars in blue and orange, using the separation defined in Equation \ref{eq:high_alpha} (the high and low-$\alpha$ stars are named for their high or low $\alpha$-element to Fe ratios, or in this case, Mg/Fe).
-On the bottom, we colour-code stars according to their [Mg/H] abundance.} \label{fig:subgiants}
-\end{figure*}
+\footnotetext{In this paper, we use the standard notation for chemical abundances.
+$[A/B] = \log_{10}\left(A/B\right) - \log_{10}\left(A_{\sun}/B_{\sun}\right)$, i.e.
+$[A/B]$ is the logarithm of the mass ratio between A and B, scaled such that $[A/B]=0$ for the sun (see Table~\ref{tab:fiducial_mod} for solar scale.) }
+
+% \footnotetext{\strike{By metallicity, we mean the (mass) fraction of any element which is not H or He, denoted by $Z$. For the sun, we take $Z_\odot=0.016$.} }
+
+\section{The Subgiant Sample}\label{sec:data_selection}
 
@@
 When stars leave the main sequence and become subgiants, these metals are mixed with the convective envelope \citep[]{gratton+00, souto19}. 
- \textit{First dredge up} during the red giant phase brings CNO processed core material to the surface \citet{iben67, KL14}.
-
-We use the sample of \apogee\ DR17 subgiants from \citetjack, selecting stars within the $\log g$-$T_\text{eff}$ polygon given by
+ \textit{First dredge up} during the red giant phase brings CNO processed core material to the surface \citep{iben67, KL14}.
+
+We use the sample of \apogee\ DR17 subgiants from \citet{jack}, selecting stars from allStar-dr17-synspec\_rev1 within the $\log g$-$T_\text{eff}$ polygon given by
  \begin{equation}
@@
         \log \text{g} \leq 0.004\,T_{\rm eff} - 15.7 \\
-        \log \text{g} \leq 0.000706\,T_{\rm eff} + 0.36 \\
+        \log \text{g} \leq 0.0007\,T_{\rm eff} + 0.36 \\
         \log \text{g} \leq -0.0015\,T_{\rm eff} + 12.05 \\
@@
         \verb|APOGEE2_EB|, and
-        \verb|ASPCAP_BAD|.
-We additionally remove stars with no reported C, Mg, or Fe abundances. These cuts yield a sample containing \nsubgiants\ subgiants.
+        \verb|DUPLICATE|.
+We additionally remove stars with no reported C, Mg, or Fe abundances (in the {\tt X\_FE} columns). These cuts yield a sample containing \nsubgiants\ subgiants.
+
+Fig.~\ref{fig:subgiants} shows the subgiant sample plotted in \caah\ and \caafe{}.\footnotemark{} In this sample, [C/Mg] increases with metallicity, and [C/Mg] decreases with [Mg/Fe] at fixed [Mg/H].
+
+\dbadd{
+Not shown here, we investigate the median trends for different samples and surveys, including APOGEE Giants with mixing corrections \citep{vincenzo+21}, APOGEE dwarfs, Gaia-ESO dwarfs, GALAH subgiants, LAMOST MRS (CITE), and smaller spectroscopic samples of stars.
+The predominant difference between any survey with our sample is a systematic offset in [C/Mg] in both [Mg/Fe] and [Fe/H] of at most 0.2 dex.
+The exception is GALAH, who's C abundances are highly incomplete, based on a single line and thus C measurements are likely unreliable (see e.g.
+Emily).
+If the median trend of [C/Mg] is offset from what we assume, then we can simply scale our C yields by the appropriate factor (e.g.
+-0.15 dex => $10^{-0.15} \approx 0.7$, so $y_{\rm C} \rightarrow  0.7 y_{\rm C}$) without significantly changing our results.
+}
 
@@
 Table \ref{tab:fiducial_mod} contains our fiducial yields and abundance scale.
-For O, Mg, and Fe, we adopt the yields in \citet{david_fe}. We use a scaled variation of the N yield from \citet{james+23}. 
-Following \citet{james+21, james+23}, we take the \ia{} delay time distribution to be a $t^{-1.1}$ power-law with a minimum delay time of 150\,Myr, as suggested by the observations of \citet{maoz+12}.
-We use solar abundances from \citet{magg+22} with a +0.04 gravitational settiling correction as in \citet{david_fe}.
-\dbadd{Magg22 finds Z/X = 0.0225 for the surface?
-what do we use for the solar metallicity?}.
-Assuming He abundance from $Y=0.2725$ from \citet{AAG2021}, resulting in a $Z_\odot=0.01606$
+We use solar abundances from \citet{magg+22} with a +0.04 gravitational settling correction  and assuming $X_\odot= 0.71, \mu_{H} = 1$ as in \citet{david_fe}.
+We thus assume $Z_\odot=0.016$ as apposed to $Z=0.014$ in \citet{asplund+09}.
+% Z = (1-Y) / (1 + X/Z)
 
@@
 	\centering
-    \caption[]{Solar abundance scale and fiducial yields (in units of SSP~birth mass). See section \ref{sec:agb} for the definition of \cxi. The solar abundance scale is \citet{magg+22} + 0.04. }
+    \caption[]{Solar abundance scale and fiducial yields (in units of SSP~birth mass). See section \ref{sec:agb} for the definition of \fruity. The solar abundance scale is \citet{magg+22} + 0.04. }
 	\label{tab:fiducial_mod}
@@
 		\hline
-        C & 0.00339 & Eq.~\ref{eq:y_cc} & $\cfactor\times$\cxi &  0 \\
+        C & 0.00339 & Eq.~\ref{eq:y_cc} & $\cfactor\times$\fruity &  0 \\
         O & 0.00733 & 7.12e-3 & 0 & 0 \\
-        Mg & 0.000671 & 6.69e-4 & 0 & 0 \\
+        Mg & 0.000671 & 6.52-4 & 0 & 0 \\
         Fe & 0.00137 & 4.72e-4 & 0 & 6.69e-4 \\
         N &0.00104 & 4.001e-4 & 0.0009$M\left(\frac{Z}{Z_\odot}\right)$ & 0\\
-        % C & 0.00339 & Eq.~\ref{eq:zeta} & $\cfactor\times$\cxi &  0 \\
+        % C & 0.00339 & Eq.~\ref{eq:zeta} & $\cfactor\times$\fruity &  0 \\
         % O & 0.00733 & 0.015 & 0 & 0 \\
@@
 
-\dbnote{I like the definition of Y to go here since that is model independent, but IMF-integrated could still be specific to AGB/CC.}
+We define a stellar yield as the fraction of a star's initial mass $M$ which is converted into freshly synthesized C.
+If $\Delta Z_{\rm C}$ represents the change in the mass fraction of C abundance, then the stellar yield is
+\begin{equation}
+    \y_{\rm C}^{\rm AGB} =  \Delta Z_{\rm C} \frac{M_{\rm ejected}}{M} = 
+    \frac{W_{\rm C}(M) - Z_{\rm C}\, M_{\rm ejected}}{M}
+\end{equation}
+where $\Delta Z_{\rm C}$ represents the change in mean metallicity of the initial composition the star was born from, $M_{\rm ejected} = M - M_{\rm rem}$ is the total ejected wind mass through the stars lifetime, $W_{\rm C}$ is the total mass of C ejected through winds, and $Z_{\rm C}$ is the initial C mass fraction of the star.
+For CCSNe, 
+\begin{equation} \label{eq:imf-cc-yield}
+   Y_{\rm C}^{\rm CC}(Z) = 
+    \frac{E(M)\,M_{\rm C}(M) + W_{\rm C}(M) - Z_{\rm C}\,M}{M}
+\end{equation}
+\dbnote{Is the - Z M term right or should M be Mzams - Mrem ?}
+where $E(M)$ is the explodability function, $M_{\rm C}(M)$ is the mass ejected in a successful supernovae, and $W_{\rm C}$ and $Z_{\rm C}$ are as above.
+We assume 8\,$\Mo$ is the minimum mass of \cc\ progeneters (see \VICE\ documentation and \citealt{emily+21}). 
+Note that a yield may be negative if a star expels gas with lower $Z_{\rm C}$ than the star was born with.
+
+An IMF-averaged yield adds together the yields of stars of each mass, weighted by the fraction of stars of each mass (the IMF). 
+The IMF-averaged yield $y_X^{\rm proc}$ for element $X$ under the enrichment process ${\rm proc}$ is given by
+\begin{equation} \label{eq:imf-agb-yield}
+    y_{X}^{\rm proc}(Z,\tau) = 
+    \frac{
+    \int_{M_{\rm to}(\tau)}^{M_{\rm max}} 
+    \y_{\rm X}^{\rm proc}(M, Z) M\ 
+    \frac{dN}{dM}\ dM
+}
+{
+    \int_{M_{\rm min}}^{M_{\rm max}}\ M\ \frac{dN}{dM}\ dM
+}
+\end{equation}
+where ${dN}/{dM}$ is the IMF and $M_{\rm to}(\tau)$ is the mass of stars with lifetime $\tau$, and $M_{\rm min}=0.08$ and $M_{\rm max} = 100$ are the assumed maximum and minimum values of the IMF.
+$y$ thus represents the amount of freshly synthesized material returned to the ISM per unit of star formation. 
+Note that in detail, the core collapse enrichment occurs on such short timescales that $M_{\rm to} = M_{\rm min, cc} = 8\,\Mo$
 
@@
 
-An Asymptotic Giant Branch (AGB) star is a low mass star during its last nuclear burning phase (He shell burning; see e.g.
-\citealt{PR2023}) which enriches the ISM through mass loss during thermal pulses.
-    In this work, we explore four different stellar AGB yield tables from the literature which provide
-    well-sampled grids in mass and metallicity. We refer to the tables as 
+\begin{figure*}
+    \centering
+ 	    \includegraphics[scale=1]{agb_yields.pdf}
+        \caption[]{\dbnote{replace y label with stellar C yield}.
+The net fractional \agb\ C yield  plotted as a function of initial stellar mass $M$ and colour-coded according to metallicity.
+The black dashed line shows $\y=0$ for reference.
+Each panel represents yields from one of four \agb\ models: \fruity{}, \aton{}, \monash{}, \nugrid{} (see sections \ref{sec:agb}) }
+
+        \label{fig:y_agb}
+\end{figure*}
+
+\begin{figure*}
+    \centering
+    \includegraphics{y_agb_vs_z.pdf}
+    \includegraphics{y_agb_vs_t.pdf}
+
+    \caption[]{\textbf{Left} \dbnote{ylabel: integrated carbon AGB yield} The (IMF-weighted) \agb\ C yield $\Ycagb$ as a function of metallicity for each of the \agb\ yield models.
+($\Ycagb$ is the net mass of C produced by \agb\ stars per unit mass of star formation, after 10\,Gyr and assuming a \citealt{kroupa01} IMF.)
+    \textbf{Right} cumulative C return as a function of age for a solar metallicity single stellar population.
+The dashed black line shows the delay time distribution of type Ia supernovae ($\propto t^{-1.1}$) for comparison.
+The minimum of \aton{} is $y(t)/y(t_{\rm end})=-46$.
+\dbnote{I think this changed with the new integration scheme...}
+}
+
+    \label{fig:agb-ssp}
+
+\end{figure*}
+
+An Asymptotic Giant Branch (AGB) star is a low mass star during its last nuclear (He shell) burning phase which enriches the interstellar medium (ISM) through mass loss during thermal pulses.(see e.g.
+\citealt{PR2023} \dbnote{or more introductory textbook like Ryden intro to astro?}) .
+In this work, we explore four different stellar AGB yield tables from the literature which provide well-sampled grids in mass and metallicity. We refer to the tables as 
 \begin{description}
-    \item \hypertarget{C11}{\texttt{C11}}: \citet{cristallo+11, cristallo+15}
-    \item \hypertarget{V13}{\texttt{V13}}: \citet{ventura+13,ventura+14,ventura+18, ventura+20}
-    \item \hypertarget{K16}{\texttt{K16}}: \citet{KL16, karakas+18}
-    \item \hypertarget{P16}{\texttt{P16}}: \citet{pignatari+16, ritter+18, battino+19, battino+21}
+    \item \hypertarget{fruity}{\texttt{FRUITY}}: \citet{cristallo+11, cristallo+15}
+    \item \hypertarget{aton}{\texttt{ATON}}: \citet{ventura+13,ventura+14,ventura+18, ventura+20}
+    \item \hypertarget{monash}{\texttt{Monash}}: \citet{KL16, karakas+18}
+    \item \hypertarget{nugrid}{\texttt{NuGrid}}: \citet{pignatari+16, ritter+18, battino+19, battino+21}
 \end{description}
 Table~\ref{tab:agb} notes the masses and metallicities for each grid of yields.
-We use the same tables as \citet{james+23}, except that we have swapped \citet{karakas10} for \citet{ritter+18}.
-
-We define a yield to be the fraction of a star's initial mass $M_{\rm birth}$ which is converted into freshly synthesized C.
-If $\Delta Z_{\rm C}$ represents the change in the mass fraction of C abundance, then
-\begin{equation}
-    \y_{\rm C}^{\rm AGB} =  \Delta Z_{\rm C} \frac{M_{\rm ejected}}{M_{\rm birth}}.
-\end{equation}
-The yields may be negative if the material returned to the ISM has a lower $Z_{\rm C}$ than the material the star was formed from.
+We use the same tables as \citet{james+23}, except that we have swapped \citet{karakas10} for \citet{pignatari+16}.
 
@@
 Most models agree on general yield trends in mass and metallicity.
-C production peak between masses of $\sim$ 2--4 \Mo\ and declines as stars become more or less massive.
+C production peak between masses of $\sim$ 2--4 $\Mo$ and declines as stars become more or less massive.
 As metallicity increases, the net yield decreases and the mass of peak C production increases slightly.
 
+In order to integrate yields across the metallicity and mass range of interest, we interpolate yield tables linearly in both $Z$ and mass.
+Below the last sampled mass, $Y_{\rm C}^{\rm AGB}$ is linearly interpolated to 0 at $0.5\Mo$.
+The choice of yields for stars of masses $\Mo \lesssim 1.5$ produces about a 20\% uncertainty in the late DTD (past 3\,Gyr) of \agb\ C production from these models.
+More complete grids in mass and metallicity would be needed to more accurately compare GCE predictions between AGB evolution models.
+Furthermore, note the non-monotonic IMF-averaged yields in \nugrid\ and \aton\ particularly at low metallicities.
+
 The left panel of Fig.~\ref{fig:agb-ssp} shows IMF-averaged C yields for each \agb\ model as a function of metallicity.
-An IMF-averaged yield adds together the yields of stars of each mass, weighted by the fraction of stars of each mass (the IMF). 
-\begin{equation} \label{eq:imf-agb-yield}
-    \Ycagb(Z,\tau) = 
-    \frac{
-    \int_{M_{\rm to}(\tau)}^{8\,\Mo} 
-    \y_{\rm X}(M, Z) M\ 
-    \frac{dN}{dM}\ dM
-}
-{
-    \int_{0.08\Mo}^{100\Mo}\ M\ \frac{dN}{dM}\ dM
-}
-\end{equation}
-where ${dN}/{dM}$ is the IMF and $M_{\rm to}(\tau)$ is the mass of stars with lifetime $\tau$.%
-\footnote{In this paper, we take the metallicity-independent parabola in $\log \tau$-$\log m$ space from \citet{larson74} as our mass-lifetime relation.} \dbnote{are the numbers in the integral bounds okay here or should we write this out or put in footnote?
-And should we be using a more recent MLR?}
 The \agb\ models mostly differ in their yield normalization and metallicity dependence.  
@@
 0.0016.
-The metallicity dependence of the yields span a factor of \about{3} (see $\zeta^{\rm AGB}$ in
-Table~\ref{tab:agb} and discussion in section~\ref{sec:equilibrium} below).
-Variations in \agb\ models are due to different choices of reaction rates, convection treatments, and mass-loss rates.
+To characterize the metallicity dependence of each table, we fit the yield to a linear model in $\log Z$
+\begin{equation}\label{eq:agb_z_approx}
+    y_{\rm C}^{\rm AGB}(Z) = y_0 + \zagb \log(Z / \Zo).
+\end{equation}
+Table \ref{tab:agb} contains the fit parameters $y_0$ and $\zagb$ for each AGB table\footnote{we perform a MCMC fit using standard RMS error to estimate best parameters and uncertanties.}
+The metallicity dependence of the yields span a factor of \about{3}.
+Variations in \agb\ model yields are due to different choices of reaction rates, convection treatments, and mass-loss rates \citet{ventura+15} \dbnote{better ref here, is there a good review on AGB physics uncertanties?}.
 
@@
 As the mass range $2\,\Mo\lesssim M \lesssim 4\,\Mo$ is most important for C production, half the yield is produced before \about{1}\,Gyr, similar to Fe production by \ia. 
-\kxvi{} weight C production more heavily towards high-mass \agb\ stars, resulting in shorter delay times, whereas the \cxi\ and \vxiii\ models predict a slightly longer timescale of \about{1}\,Gyr.
+\monash{} weight C production more heavily towards high-mass \agb\ stars, resulting in shorter delay times, whereas the \fruity\ and \aton\ models predict a slightly longer timescale of \about{1}\,Gyr.
 In any case, little to no C is produced more than 2\,Gyr after a star formation event.
@@
 Both HBB and TDU result in mass and metallicity dependent C yields. 
-Stars less than \about{2}\,\Mo\ do not experience TDU As a result, these stars C abundances are only affected by first dredge-up (CITE), resulting in small net C yields.
-Above \about{2}\,\Mo{}, TDU becomes important, enriching the outer layers with C.
-In \agb\ stars more massive than \about{5}\,\Mo, efficient HBB turns most \C[12] into $^{14}$N.
-Metal poor stars dredge up more material \dbnote{for which physics, compactness, mixing efficiency( Boothroyd \& Sackmann 1988))? etc.}, resulting in elevated C production \citep{ventura+13}.
+Stars less than \about{2}\,$\Mo$ do not experience TDU As a result, these stars C abundances are only affected by first dredge-up (CITE), resulting in small net C yields.
+Above \about{2}\,$\Mo$, TDU becomes important, enriching the outer layers with C.
+In \agb\ stars more massive than \about{5}\,$\Mo$, efficient HBB turns most \C[12] into $^{14}$N.
+Metal poor stars dredge up more material \dbnote{for which physics, compactness, mixing efficiency( Boothroyd \& Sackmann 1988))? etc.}, resulting in elevated C production \citep[e.g.][]{ventura+13}.
+This is due to  the more compact and higher core masses in low-mass stars, causing a stronger thin-shell instability leading to stronger pulse-driven convections and dredging up more C.
+Note that HBB also increases with lower metallicity, but the effects of stronger TDU outweighs this.
+Additionally, as stars evolve through the TPAGB, they dredge up more material for the same reasons.
+The number of pulses is driven by the chosen mass loss formulation.
+
+The major uncertanties in AGB evolution are convective treatment, reaction rates, and mass loss prescriptions.
+In particular, the N14pgamma reaction rate uncertainty causes a factor of 2 difference in predicted C yields \citep{herwig+austin2004, HAL2006} \dbnote{look at present-day reaction rates here}.
+Another example is the convective prescription.
+A series of papers has compared \aton{} and \monash{}, concluding that the different convection methods (full spectrum of turbulance versus mixing length theory) and the mass loss formulation (V, Blocker) are responsable for the significant differences in C yields between the models.
+\aton{} predicts strong HBB which occurs a solar mass sooner than in \monash{}, causing much lower C yields.
+Note that most of the physics included in stellar modeling is empirically calibrated: we cannot determine mass-loss rates, mixing and extra mixing from first principles---our understanding of the essential ingredients to stellar evolution is through empirical inference.
 
@@
 \end{equation}
-We use the \cxi\ table, with $\alpha_{\rm agb}=\cfactor$, as the fiducial \agb\ yield.
+We use the \fruity\ table, with $\alpha_{\rm agb}=\cfactor$, as the fiducial \agb\ yield.
 
@@
 	\centering
-    \caption[]{For each \agb\ yield set, the IMF-averaged \agb\ C yield at solar metallicity $y_{\rm C, 0}^{\rm agb}$ and the multiplicative factor reaches an \agb\ contribution of 20\% $\alpha_{0.2}^{\rm agb}$.}
+    \caption[]{For each \agb\ yield set, the IMF-averaged \agb\ C yield at solar metallicity $y_{\rm C, 0}^{\rm agb}$ and fraction of solar C produced in the model $f_\odot^{\rm AGB}$.
+We also include the masses and metallicities each grid is sampled on.
+    }
 
 	\label{tab:agb}
-    \begin{tabular}{c cc cc  c p{5cm} p{5cm}} % four columns, alignment for each
+    \begin{tabular}{c  cc  c p{5cm} p{5cm}} % four columns, alignment for each
 		\hline 
         \agb\ table 
-                & $y_{\rm C}^{\rm agb}(\Zo)$ & y & $\zeta^{\rm agb}(\Zo)$ & $\zeta$ &  $\alpha_{0.2}^{\rm agb}$
-                & masses (\Mo) & metallicites ($\log Z/\Zo$)\\
+                & $y_{\rm C}^{\rm agb}(\Zo)$ %& y
+                & $\zagb(\Zo)$ %& $\zeta$ 
+                &  $f_\odot^{\rm agb}$
+                & masses ($\Mo$) & metallicites ($Z$)\\
         \hline
-        \cxi 
-                &  $3.5^{+0.3}_{-0.3}$ & 4.0
-                & $-3.5^{+0.3}_{-0.3}$ & -3.5
-                & 1.32
+        \fruity 
+                &  $3.82^{+0.3}_{-0.3}$ %& 4.0
+                & $-3.5^{+0.3}_{-0.3}$ %& -3.5
+                & 0.138
                 & 1.3, 1.5, 2, 2.5, 3, 4, 5, 6
-                & -2.15, -1.67, -1.15, -0.85, -0.67, -0.37, -0.24, -0.15, 0.0, 0.15
+                & 0.0001, 0.0003, 0.001, 0.002, 0.003, 0.006, 0.008, 0.01, 0.014, 0.02
                 \\
-        \vxiii 
-                & $2.7^{+1.3}_{-1.3}$ & 2.6 
-                & $-4.9^{+1.4}_{-1.6}$ & -4.9
-                & 2.5
+        \aton 
+                & $1.85^{+1.0}_{-1.1}$ %& 2.6 
+                & $-9.4^{+1.5}_{-1.7}$ %& -4.9
+                & 0.067
                 & 1.5, 2, 2.5, 3, 3.5, 4, 4.5, 5, 6, 6.5, 7
-                & -1.67, -1.15, -0.85, -0.54, -0.24, 0.0, 0.46
+                & 0.0003, 0.001, 0.002, 0.004, 0.008, 0.014, 0.04
                 \\
-        \kxvi 
-                & $3.0^{+0.4}_{-0.5}$ & 3.5
-                & $-10.1^{+0.9}_{-1.3}$ & -10
-                & 1.11
+        \monash 
+                & $2.8^{+0.4}_{-0.5}$ %& 3.5
+                & $-10.1^{+0.8}_{-0.9}$% & -10
+                & 0.102
                 & 1, 1.25, 1.5, 1.75, 2.25, 2.5, 2.75, 3, 3.25, 3.5, 3.75, 4, 4.5, 5, 5.5, 6, 7 
-                & -0.7, -0.3, 0.0, 0.33 
+                & 0.0028, 0.007, 0.014, 0.03
                 \\
-        \pxvi 
-                & $6.2^{+1.1}_{-1.1}$ & 8
-                & $-5.3^{+1.0}_{-0.9}$ & -3.
+        \nugrid 
+                & $5.9^{+1.2}_{-1.1}$ %& 8
+                & $-5.7^{+1.0}_{-1.0}$ %& -3.
+                & 0.214
                 & 1, 1.65, 2, 3, 4, 5, 6, 7
-                &  -2.15 , -1.15 , -0.37 , -0.15 , 0.15
+                &  0.0001, 0.001, 0.006, 0.01, 0.02
                 \\
@@
 
-\begin{figure*}
-    \centering
- 	    \includegraphics[scale=1]{agb_yields.pdf}
-        \caption[]{The net fractional \agb\ C yield  plotted as a function of initial stellar mass $M$ and colour-coded according to metallicity.
-The black dashed line shows $\y=0$ for reference.
-Each panel represents yields from one of four \agb\ models: \cxi{}, \vxiii{}, \kxvi{}, \pxvi{} (see sections \ref{sec:agb}) }
-
-        \label{fig:y_agb}
-\end{figure*}
-
-\begin{figure*}
-    \centering
-    \includegraphics{y_agb_vs_z.pdf}
-    \includegraphics{y_agb_vs_t.pdf}
-
-    \caption[]{ C yields from \agb\ stars as a function of SSP age, as a fraction of the C yield at $t_{\rm end}=10\,$Gyr. 
-\textbf{Left} The (IMF-weighted) \agb\ C yield $\Ycagb$ as a function of metallicity for each of the \agb\ yield models.
-($\Ycagb$ is the net mass of C produced by \agb\ stars per unit mass of star formation, after 10\,Gyr and assuming a \citealt{kroupa01} IMF.)
-    \textbf{Right} Our four considered \agb\ yield models at solar metallicity (\cxi{}, \vxiii{}, \kxvi{}, \pxvi{}.
-The dashed red line shows the delay time distribution of type Ia supernovae ($\propto t^{-1.1}$) for comparison, and the minimum of V13 is $y(t)/y(t_{\rm end}=-46$.
-}
-
-    \label{fig:agb-ssp}
-
-\end{figure*}
-
 \subsection{Core Collapse Supernovae}
 
-Massive stars form $^{12}$C in their cores through the triple--$\alpha$ reaction.
-Surviving C ejected through supernovae and winds form the massive star yields.
+Massive stars form $^{12}$C in their cores through the triple--$\alpha$ reaction \dbnote{any more introduction needed here?}.
+Later, C not transformed into other elements is released to the ISM through winds or a supernovae.
 While there are many stellar models providing predictions of \cc{} yields, the results of these models are highly uncertain due to the complexity of stellar modeling.
+\dbnote{maybe (re)move this sentence?
+not sure...}
 
 Fig.~\ref{fig:y_cc} plots calculations of IMF-averaged yields for a handful of massive star yields from the literature.
-For \cc\, the IMF-averaged yield is
-\begin{equation} \label{eq:imf-cc-yield}
-    \Ycc(Z) = 
-    \frac{
-    \int_{8\,\Mo}^{100\,\Mo} 
-    \y_{\rm C}(M, Z)
-    \frac{dN}{dM}\ M\ dM
-}
-{
-    \int_{0.08\Mo}^{100\Mo} \frac{dN}{dM}\ M\ dM
-}
-\end{equation}
-where ${dN}/{dM}$ is the IMF and 8\,\Mo is the assumed minimum mass of \cc\ progeneters (see \VICE\ documentation and \citealt{emily+21}). 
 \cc{} models predict a wide range of C yields, spanning nearly a factor of ten. 
@@
 \citealt{frischknecht+16}) can dramatically increase the magnitude and metallicity dependence of $\Ycc$.
-As we will later emperically show, \cc\ C production needs to be strongly metallicity-dependent at $Z \approx \Zo$, which is consistent with \citepos{LC18} rapidly rotating models.
+As we will later emperically show, \cc\ C production needs to be strongly metallicity-dependent at $Z \approx \Zo$, which is consistent with \citepos{LC18} rapidly rotating models and to a lesser extent \citet{NKT13}.
 As metallicity increases, stars lose more of their mass to winds.
 In particular, C enriched envelop material is lost through winds before synthesized into heavier elements, resulting in $Z$-dependent C production \citep{LC18}.
-The left panel of Fig.~\ref{fig:y_cc} shows the \cxi{} \agb\ model. Especially at $Z\approx Z_\odot$, most \cc{} models dominate \agb\ C production.
+The left panel of Fig.~\ref{fig:y_cc} shows the \fruity{} \agb\ model. Especially at $Z\approx Z_\odot$, most \cc models dominate \agb\ C production.
 
@@
 \begin{equation}\label{eq:y_cc}
-    \Ycc = y_{\rm C, 0}^{\rm cc} + \zeta^{\rm cc}\,(Z-\Zo) .
-\end{equation}
-While a linear yield model is able to explain APOGEE abundances, we also consider in section~\ref{sec:gas} a bi-linear yield model which could also explain low-metallicity observations of C.
-\begin{equation}\label{eq:y_cc_bilinear}
     \Ycc = \begin{cases}
-    y_{\rm C, 0}^{\rm CC} + \zeta^{\rm CC}\,(Z-\Zo) & Z > Z_1 \\
-    y + \zeta_1^{\rm CC} & Z < Z_1
+    y_{\rm C, 0}^{\rm cc} + \zcc\,\log(Z/\Zo) + A \log(Z/\Zo)^2 & Z \geq Z_{\rm low}
+    \\
+    y_{\rm C, low}^{\rm cc} & Z < Z_{\rm low}
     \end{cases}
@@
 
+where $Z_{\rm low}$ is the transition between low-metallicity constant yields and the linear(quadratic) yields near solar.
+We take $A=0$ in the fiducial model, representing a linear model, and $y_{\rm C,low}^{\rm CC} = 0.XXX$ with $Z_{\rm low} = XXX$.
+This results in a continuous yield where
+In our Quadratic model, we take $Z_{\rm low}$ to be the vertex of the parabola, such that the yield is monotonic and $y_{\rm low}$ is the value of the vertex.
+\dbnote{Fill in description here. Could also try a BiLinear model with vertex near Fe/H=0}
 \begin{figure*}
@@
     \caption[]{
+    \dbnote{y label: integrated CCSNe carbon yield}
         C yields from high-mass stars.
@@
         \textbf{Right} The \cc\ [C/Mg] abundance ratio, defined in Eq.~\ref{eq:c_mg_cc}.
-The black line is the derived C yield from section \ref{sec:equilibrium} and Eq.~\ref{eq:zeta}.
+The black line is the derived C yield from section \ref{sec:equilibrium} and Eq.~\ref{eq:y_cc}.
 Yields are shown for tables from
-    \citet[red triangles]{WW95}, \citet[orange squares and diamonds]{sukhbold+16}, 
+    \citet[red triangles]{WW95}, \citet[orange square and diamond]{sukhbold+16}, 
     \citet[green stars]{NKT13}, and \citet[blue circles]{LC18}.
 \citet{sukhbold+16} report yields for different black hole landscapes, while \citet{LC18} provide yields at different rotational velocities.
-    In the top panel, the pink line denotes $\Ycagb$ from \cxi{} for comparison. All models include wind yields. 
+    In the left panel, the pink line denotes $\Ycagb$ from \fruity{} for comparison. All models include wind yields. 
 }
@@
 
-We isolate the low-$\alpha$ sequence of subgiants to represent the equilibrium abundance trends, defined by [Mg/Fe] - [Fe/H] as in \citet{weinberg+19}.
+We isolate the low-$\alpha$ sequence of subgiants to represent the equilibrium abundance trends, defined by [Mg/Fe] - [Fe/H] as in \citet{jack} (a +0.02 correction from \citet{weinberg+19}).
 Low-$\alpha$ stars are defined as stars with
@@
 \begin{cases}
-\text{[Mg/Fe]} <0.12-0.13\,\text{[Fe/H]}, & \text{[Fe/H]}<0\\
-\text{[Mg/Fe]} <0.12, & \text{[Fe/H]}>0. \\
+\text{[Mg/Fe]} <0.16-0.13\,\text{[Fe/H]}, & \text{[Fe/H]}<0\\
+\text{[Mg/Fe]} <0.16, & \text{[Fe/H]}>0. \\
 \end{cases}
 \end{equation}
-with high-$\alpha$ stars being otherwise from \citet{weinberg+19, weinberg+22, emily+19, emily+21}.
-
-In Fig.~\ref{fig:analytic}, we show the inferred C/Mg yield ratio against metallicity. 
+with high-$\alpha$ stars being otherwise from \citet{weinberg+19, weinberg+22, emily+19, emily+21}. \dbnote{I want to move this paragraph to \S 2.}
+
+We propose the following functional form for total C yields near solar metallicities:
 \begin{subequations}\label{eq:yc_inferred}
@@
         \frac{\Yct(Z)}{y_{\rm Mg}} &\approx 4.20 + 1.64 \log (Z/\Zo)\\
-        \frac{\Yct(Z)}{y_{\rm Mg}} &\approx 4.12 + 1.21 \log(Z/\Zo) + 3.07 \log(Z/\Zo)^2
+        \frac{\Yct(Z)}{y_{\rm Mg}} &\approx 4.22 + 2.178 \log(Z/\Zo) + 5.53 \log(Z/\Zo)^2
     \end{align}
 \end{subequations}
-These yield ratios results in an equilibrium abundance $[{\rm C/Mg}] = -0.09$ at solar metallicity, which is consistent with our subgiant sample and is within \about{20\%} of the solar C/Mg mixture.
-(check this!)
-
+At solar metallicity, these yield ratios results in an equilibrium abundance $[{\rm C/Mg}] = -0.08$ which is consistent with our subgiant sample and is within \about{20\%} of the solar C/Mg mixture. 
+For the quadratic form, we hold the yields constant past the vertex (at {\color{red} [M/H] = ?}) to avoid a premature upturn in \caah.
+We discuss the choice of these functional forms more in appenix~\dbadd{X}.
+In Fig.~\ref{fig:analytic}, we show the inferred C/Mg yield ratio against metallicity.
+
+\dbnote{check zetas}
 With the total C yield of Eq.~\ref{eq:yc_inferred} and given an \agb\ C yield, we can derive an \cc\ C yield that would predict observationally consistant [C/Mg] ratios.
+(by subtracting the assumed AGB contribution from the total yield fit above.)
 \begin{subequations}
@@
         \Ycc(\Zo) &= \Yct(\Zo) - \Ycagb(\Zo)\\
-        \zeta^{\rm cc} &= \zeta - \zeta^{\rm agb}
+        \zeta &= \zcc + \zagb
     \end{align}
 \end{subequations}
+% \dbnote{I think I can get rid of the below equation.}
+% \note{I'd suggest keeping it -- since you use $\zeta$ to distinguish between models, and it shows up in figure legends, the visibility of its exact definition will improve readability.}
 where $\zeta$ is the (solar) metallicity dependence of the C yield at $Z=\Zo$
 \begin{equation}
-    \zeta = \frac{d y_{\rm C}}{d Z} \Big \vert_{(Z=\Zo)},
-\end{equation}
-and $\zeta^{\rm cc}$ and $\zeta^{\rm agb}$ correspond to the specific enrichment channels. 
-This method reduces the number of free parameters and enables all yield models to match \caah\ trends in \apogee{} subgiants, even when considering alternative \agb\ yield tables.
-Table~\ref{tab:agb} provides $\zeta^{\rm agb}$ for each \agb\ yield table we consider.
+    \zeta = \frac{d y_{\rm C}}{d \log Z} \Big \vert_{(Z=\Zo)},
+\end{equation}
+and $\zcc$ and $\zagb$ correspond to the specific enrichment channels.
 
 Both observational and theoretical uncertainties limit the accuracy of our relative yield predictions.
-Additionally, the derived yields will be systematically biased if the galaxy is out of equilibrium, e.g. due to a recent starburst \citep{mor+19,isern19}.
-
-\begin{figure}
-    \centering
-    \includegraphics{figures/equilibrium_yields.pdf}
-    \caption[]{Inferred total C yields as a function of metallicity.
-We assume chemical equilibrium (orange curve, see discussion in section \ref{sec:equilibrium}).
-Blue points are the median value of $\Ycc$ for each (number) bin in [Mg/H] with uncertainties based on the 16--84 percentile range.
-    }
-    \label{fig:analytic}
-\end{figure}
-
-\subsection{Single-zone models and \caafe{}}
-\dbnote{This will be a section I will write after a little more investigation.
-I think this should go by the equilibrium model, but maybe move both sections to after a discussion of the fiducial model: Multizone description $\to$ justify equilibrium and singlezone $\to$ consideration of other parameters.
-Or maybe just a different section?}
+Additionally, the derived yields will be systematically biased if the galaxy is out of equilibrium, e.g.
+due to a recent starburst \citep{mor+19,isern19}.
 
@@
 The Galaxy evolves \textit{inside-out} -- where star formation is higher towards the center and in the early universe \citep{WF91, kauffmann96, bird+13}.
-Stars can also migrate several kpc over their lifetimes, mixing different chemical environments across the galaxy \citep{bird+12,sellwood+binney02}.
+Stars can also migrate several kpc over their life/times, mixing different chemical environments across the galaxy \citep{bird+12,sellwood+binney02}.
 Multi-zone models account for stellar migration and changing environments by stitching together multiple one-zone models and mixing stellar populations.
+\dbnote{does this belong in intro or here?.
+Thinking here now because feels more like methodology justification, but not sure still.}
+
+For our O, Mg, and Fe yields, we adopt the yields in \citet{david_fe}. We use a scaled variation of the AGB N yield from \citet{james+23} with a metallicity-independent CCSNe N yield. 
+Following \citet{james+21, james+23}, we take the \ia{} delay time distribution to be a $t^{-1.1}$ power-law with a minimum delay time of 150\,Myr, as suggested by the observations of \citet{maoz+12}.
+\dbnote{discuss SNe Ia (maximum 4\% of C but likely much less) and SAGB (also minimal). Also: can novae produce any C?}
 
@@
         R_{\rm end} &\sim N(R_{\rm birth}, \sigma_R ) \\
-        \sigma_{R} &= 1.27\,{\rm kpc} \sqrt{\frac{t_{\rm end} - t_{\rm birth}}{\rm Gyr}}
+        \sigma_{R} &= 1.27\,{\rm kpc} \sqrt{\frac{t_{\rm end} - t_{\rm birth}}{1 \rm Gyr}}
 \end{align}
@@
 At the boundaries, stars at $R=0$ move to $R=0$ if $R_{\rm end}<0$ and stars will move to $R=20$\,kpc if $R_{\rm end} > 20$\,kpc. 
-\dbnote{would be better to change s.t.
-star truncates at 20 but moves there earlier...}
 The star moves from its birth radius to its final radius via
@@
 where $N(\mu, \sigma)$ represents a draw from normal distribution and $dt=20$\,Myr is the simulation timestep.%
-\footnote{Not shown here, we also explored variations of temporal, spatial resolution and migration strength and found these do not affect median trends significantly.}
+\footnote{Not shown here, we also explored variations of temporal, spatial resolution, migration strength, and the mass lifetimre relation. We found these do not affect median trends significantly.}
 We do not account for radial gas flows.
 Not shown here, we also explore migration based on random walks and the \texttt{h277} hydrodynamical
-simulation results (with simulation parameters as in \citealt{bird+21}; see also \citealt{christensen12, zolotov12, loebman12, BZ14}), which leaves our qualitative conclusions unchanged. 
+simulation results\footnote{(with simulation parameters as in \citealt{bird+21}; see also \citealt{christensen12, zolotov12, loebman12, BZ14} \dbnote{is this okay as footnote?} }, which leaves our qualitative conclusions unchanged.
 The full impact of the details of a galaxy's dynamical history on its chemical evolution is still unknown.
@@
 \begin{equation}
-    \log Z(R) = \log Z_{\alpha,\ \odot} + 
+    \log Z_{\alpha}(R) = \log Z_{\alpha,\ \odot} + 
     0.29 + 
@@
 \end{equation}
-and we approximate $\tau_\star/\tau_{\rm sfh} \approx 0.3$ 
-adapted from \citet{hayden+14}.
+is adapted from \citet{hayden+14}.  We approximate $r=0.4$, and $\tau_\star/\tau_{\rm sfh} \approx 0.0$ \dbnote{double check this...}.
 This choice of $\eta(R)$ results in a [$\alpha$/H] gradient consistent with Milky Way observations \citep[e.g.][]{hayden+14, weinberg+19, frinchaboy+13}.
@@
 
+Finally, we tune the carbon yields of CCSNe in slope and normalization to approximately match the median trends in most cases.
+A tabulated description of our model parameters is available in appendix~\dbadd{model parameters}.
+
 \section{Results}\label{sec:results}
@@
 \subsection{Evolution of Carbon Abundances}
+
+\begin{figure*}
+\centering
+\includegraphics{figures/all_the_tracks.pdf}
+\caption[]{
+    Time evolution of gas-phase C abundances in our fiducial model for [C/Mg] versus [Mg/H] (left) and [Mg/Fe] (right).
+    Each line represents a zone at a different galactic radius and is colour-coded by time. While \caah\ settles into the final trend $\sim{8}$\,Gyr ago, \caafe\ continues to evolve for much longer.
+}
+\label{fig:c_evo}
+\end{figure*}
 
@@
 
-\begin{figure*}
-\centering
-\includegraphics{figures/all_the_tracks.pdf}
-\caption[]{
-    Time evolution of gas-phase C abundances in our fiducial model.
-    Each line represents a zone at a different galactic radii. The lines are colour-coded by time. The left shows \caah\ and the right \caafe. 
-}
-\label{fig:c_evo}
-\end{figure*}
+To create representative stellar samples to compare with APOGEE, 
+We draw \nsubgiants\ stars from the simulated stellar populations such that the selection probability is proportional to a stellar population's mass and that the subsample follows the same distribution in Galactocentric radius as the subgiants.
+Fig.~\ref{fig:equilibrium_validity} displays our sample of stars and compares them to analytic representations of the mean trend. 
+The median sequence of the low-$\alpha$ stars closely follows the {\it equilibrium track}, defined by the ratio between total C and Mg yields at each metallicity.
+There is a slight ($\sim{0.02}$ dex) divergence between the median track and equilibrium at higher metallicities, caused by our particular choice of C yields and the finite time it takes to reach equilibrium especially at higher metallicities with an increasing yield.
+However, if the low-$\alpha$ sequence is approximantly matched by our {it total} C yield, then we expect our model to agree with stellar observations.
+On the other hand, in \caafe\ equilibrium is a vertical line.
+As we assume both Mg and Fe yields are metallicity independent, there is only one value of [Mg/Fe] in the equilibrium sequence, corresponding to the low-$\alpha$ population.
+The median trend here instead reveals the delay time distribution of C, revealed by the green single-zone model included.
+
+Galactocentric radii are taken from astroNN {\color{red} citation}. \dbadd{Using Gaia parallaxes does not affect our conclusions ?}
 
@@
 \begin{figure*}
-\includegraphics{sims_agb.pdf}
+    \centering
+    \includegraphics{figures/subgiants_equilibrium_reproduced.pdf}
+    \caption{Similar to Fig.~\ref{fig:subgiants} except for the stars of our fiducial model. 
+    The solid, black lines show the equilibrium abundance track.
+The black scatter points with errorbars are the median bins for the low-$\alpha$ sequence (left) and the \caafe\ trend (right).
+The green solid line on the right shows the singlezone evolution of \caafe\ with properties matching our solar-annulus.
+The median trend of low-$\alpha$ stars is an excellent approximation for the equilibrium abundance of C.
+    \dbnote{we add synthetic scatter found by fitting the metallicity-dependent reported errors with a linear fit in APOGEE and adding gaussian noise.}
+    \dbnote{is there too much going on here?}
+    \label{fig:equilibrium_validity}
+    }
+\end{figure*}
+
+\begin{figure*}
+\includegraphics{sims_zeta_f.pdf}
 
@@
 Coloured lines represent the median [C/Mg] in bins of [Mg/H] (left) or [Mg/Fe] (right) for each \agb\ table.
-Black points and grey dashes represent the median and 16th-84th percentiles of [C/Mg] in each bin in the \citetjack~sample.
+Black points and grey dashes represent the median and 16th-84th percentiles of [C/Mg] in each bin in the \citet{jack}~sample.
     The left panel only shows low-$\alpha$ stars. In the right panels, we show the trends only for stars where $-0.15\leq {\rm [Mg/H]}\leq -0.05$.
     Stars are binned into 20 (left) or 12 (right) equal number bins. 
-}
-\label{fig:first_models}
-\end{figure*}
-
-\begin{figure*}
-\includegraphics{sims_zeta_f.pdf}
-
-\caption[]{
-    Similar to Fig.~\ref{fig:first_models}. 
     \textbf{Top}: Models with different metallicity dependences for  \cc\ C yields. \textbf{Bottom}: Different \agb\ fractinos of C.
@@
 \begin{figure*}
-\includegraphics{figures/sims_degens.pdf}
+\includegraphics{figures/zeta_f_mass_sfh.pdf}
 
 \caption[]{
-    Similar to Fig.~\ref{fig:first_models}. 
-    \textbf{Top}: Models with different metallicity dependences for  \cc\ C yields. \textbf{Bottom}: Different \agb\ fractinos of C.
+    Similar to Fig.~\ref{fig:zeta_f}, except for \caafe\ for a variety of models.
+    {\bf Left} models where both the \agb\ fraction and the CCSNe slope are varied simultaneously.
+    {\bf Middle} models where the \agb\ yields are shifted by some factor in mass.
+    {\bf Right} alternate star formations and a model where yields and outflows are $\sim$ doubled.
+
+    \dbnote{I looked into the halfed yields model.
+Since in this paper, we assume $y_o/Z_o \sim 1$, it is essentially impossible to reach solar Z when halfing the yields.
+I am swapping for all yields are doubled and I think if a referee complains about our choice of $\eta\sim0.4 \ne 0$ at the sun, we can deal with that later}
+
+    \dbnote{middle pannel is reproduced in analytic multizone models. low-priority but possibly interesting is if the analytic DTD or singlezone models reflect this trend as well.}
 }
@@
 
-We evaluate our models by comparing predicted median stellar trends to our subgiant sample (see section~\ref{sec:data_selection}. 
-We draw 12,000 stars from the simulated stellar populations such that the selection probability is proportional to a stellar population's mass and that the subsample follows the same distribution in Galactocentric radius as the subgiants.
-
-Fig.~\ref{fig:first_models} show the four C yield models (\cxi, \vxiii, \kxvi, \pxvi).
-For the most part, different \agb\ yield tables result in qualitatively similar predictions.
-\vxiii, however, does not reproduce solar trends as the model predicts strong C destruction at slightly super-solar metallicities, resulting in inversions in both \caah\ and \caafe.
-As all \agb\ models predict C yields to decline with metallicity, all models predict an increasingly downward slope in \caafe\ with [Mg/Fe].
-A recent burst in star formation may hide this downturn (see section~\ref{sec:sfh}), but C destruction at the level predicted by \vxiii\ is not supported by our sample.
-Because the effects of alternate \agb\ yield sets are small, we focus on \cxi{} model for the remained of this paper. Alternate yield sets minimally affect our conclusions.
-
-The top of Fig.~\ref{fig:zeta_f} shows models with varying strengths of the $\Ycc$ metallicity dependence, $\zeta^{\rm cc}$.
-With higher $\zeta^{\rm cc}$, the model predicts a steeper \caah trend, owing to the direct relationship between the C/Mg equilibrium abundances and yield ratios.
-However, \caafe~is minimally affected by changes to $\zeta^{\rm cc}$ since \cc\ occurs on much shorter timescales than \ia\ and \agb\ enrichment.%
-\footnote{The only effects on \caafe, when considering the narrow metallicity slice, are because of either the slight change in equilibrium abundances, the imperfect evolution of the galaxy, or that the ISM abundances are set by stars which were born at poorer metallicities.
+The top of Fig.~\ref{fig:zeta_f} shows models with varying strengths of the $\Ycc$ metallicity dependence, $\zcc$.
+With higher $\zcc$, the model predicts a steeper \caah\ trend, owing to the direct relationship between the C/Mg equilibrium abundances and yield ratios.
+However, \caafe~is minimally affected by changes to $\zcc$ since \cc\ occurs on much shorter timescales than \ia\ and \agb\ enrichment.%
+\footnote{The only effects on \caafe, when considering the narrow metallicity slice, are because of either the systematic change in equilibrium abundances, the imperfect evolution of the galaxy, or that the ISM abundances are set by stars which were born at poorer metallicities.
 }
@@
 
-The bottom of Fig.~\ref{fig:first_models} shows three models with different C \agb\  fractions, defined as 
+The bottom of Fig.~\ref{fig:zeta_f} shows three models with different C \agb\  fractions, defined as 
 \begin{equation}\label{eq:f_agb}
-    f_{\rm agb} \equiv \frac{\Ycagb(\Zo)}{\Yct(\Zo)}.
-\end{equation}
-Modifications of $f_{\rm agb}$ affect \caafe{} trends significantly more than \caah.
+    \fagb \equiv \frac{\Ycagb(\Zo)}{\Yct(\Zo)}.
+\end{equation}
+Modifications of $\fagb$ affect both \caafe\ and \caah.
 At fixed metallicity, the \caafe\ trend is principally sensitive to how much C and Fe comes from delayed sources.
 Increasing the \agb\ fraction therefore steepens the \caafe\ trend as expected.
-Though each yield model predicts the trend to flatten at ${\rm [Mg/Fe} \lesssim 0.1 $, the median is still within the width of the observed distribution and the overall agreement is good.
+Though each yield model predicts the trend to flatten at ${\rm [Mg/Fe]} \lesssim 0.1 $, the median is still within the width of the observed distribution and the overall agreement is good.
+Additionally, increasing \agb\ contribution to C leads to a declining net slope for the total C yield owing to the negative slope of \agb\ C production with metallicity.
+
+Because both the increase in \cc\ slope $\zcc$ and AGB fraction $\fagb$ have similar impacts to \caah, we can change both parameters simultaneously to retain agreement in \caah.
+We show example models in the left panel of Fig.~\ref{fig:sims_degens} in \caafe, (as models cannot be readily distinguished in \caah).
+The principle effect of increasing $\fagb$ and adjusting $\zcc$ correspondingly is to increase the amplitude of the trend in \caafe.
+Models with little to no AGB C production will produce stars with [C/Mg] independent of [Mg/Fe] in a metallicity slice.
+As the AGB fraction increases to an extreme $f^{\rm AGB}=0.5$, the trend becomes much steeper than the fiducial but remains a mere rescaling of the same shape.
+
+A second factor affecting \caafe\ is the assumed delay time distribution of \agb\ carbon production.
+The middle panel of Fig.~\ref{fig:sims_degens} shows models where the AGB yields have been shifted by some factor in mass.
+When the AGB C production is weighted towards more massive AGB stars, then the delay time distribution becomes more like CCSN.
+As such, the predicted \caafe\ trend resembles the model which only contains CCSN production.
+The \caafe\ trend therefore is much less sensitive to the C production by stars with masses $M \gtrsim 5 \Mo$.
+On the other hand, shifting the C production towards low mass stars changes both the shape and amplitude of the DTD.
+This is evident in a transition point, where the \caafe\ trend changes slope.
+For the most extreme case, where the masses are shifted by a factor of 0.5; the AGB production is more delayed than SNeIa, causing a steepining of \caafe\ towards low [Mg/Fe].
+Intermediate values are more linear in \caafe, matching the observed trend.
+We note that the fiducial model instead transitions from steep to shallow as [Mg/Fe] decreases.
+This is evidence that AGB C likely needs to be weighted more towards low mass stars than is predicted by current AGB stellar models.
+
+Considering the effects of changes in the amplitude and mass of AGB C production, we can now predict and understand the differences between different yield tables.
+Fig.~\ref{fig:agb_predictions} show the four C yield models (\fruity, \aton, \monash, \nugrid, with no scaling).
+For the most part, different \agb\ yield tables result in qualitatively similar predictions.
+While small adjustments in the \cc\ yields results in identical tracks through \caah, each model predicts slightly different tracks in \caafe.
+Differences are due to the total C production from the AGB model, and the delay time distribution of the model.
+For example, V13 predicts that AGB stars produce almost net zero C at solar metallicity, and \monash\ predicts the shortest delay time distribution of all models.
+These models thus are almost consistent with pure \cc\ enrichment of C.
+Additionally, \nugrid\ yields are about double \fruity, resulting in a steeper slope in \caafe.
+%\aton, however, does not reproduce solar trends as the model predicts strong C destruction at slightly super-solar metallicities, resulting in inversions in both \caah\ and \caafe. 
+As all \agb\ models predict C yields to decline with metallicity, all models predict an increasingly downward slope in \caafe\ with [Mg/Fe].
+A recent burst in star formation may hide this downturn (see section~\ref{sec:sfh}), but C destruction at the level predicted by \aton\ is not supported by our sample.
+Because the effects of alternate \agb\ yield sets are small, we focus on \fruity{} model for the remained of this paper. Alternate yield sets minimally affect our conclusions.
+
+\dbadd{the inter-study differences for AGB yields can be explained by the differing mass dependence, and the metallicity dependence.}
 
 \subsection{Variations in Star Formation History} \label{sec:sfh}
-
 In this section, we consider an alternate SFH, namely one which exhibits a late-time elevation in the star formation rate.
@@
 where $A=1.5$ represents the amplitude of the birth, $\tau_\text{burst}=10.8$\,Gyr is the time where the burst is strongest, and $\sigma_\text{burst}=1$\,Gyr is the width of the burst.
-% Our earlyburst model is instead a double exponential, with the second exponential begining at $t_1=5\,$Gyr.
-% \begin{equation}\label{eq:twoinfall}
-%     \dot{\Sigma}_{\rm earlyburst} \propto A\,e^{-t/\tau_{\rm burst}} + 
-% \begin{cases}
-%     e^{-(t-t_1)/\tau_\text{sfh}} & t_1 < t \\
-%       0 & t<t_1
-% \end{cases}
-% \end{equation}
-% where we take the burst duration, $\tau_{\rm burst}=2$\,Gyr.
-% This approximately corresponds to the Gaia-Encelidus merger, inducing higher star formation in the Milky Way \citep{spitoni21, bonaca20, helmi18}.
-
-The bottom of Fig.~\ref{fig:first_models} compares the fiducial and lateburst models.
+
+We additionally consider a two-infall like model as presented in \dbadd{dubay + 24}, which is defined as.
+
+\begin{equation}\label{twoinfall}
+\dot{\Sigma}_{\rm in} \propto exp(-t/\tau_1) + A_{2,1} \theta(t - t_{1}) \exp(-t/\tau_2)
+\end{equation}
+
+where $\tau_1=0.4\,$Gyr, $\tau_2$ is 1/2 of the value from Sanchez, $A_{2,1}=0.5$, $t_1=4.1$, and the star formation also abruptly transitions from $\nu=2$ to $\nu=1$ at $t=t_1$.
+
+The right panel of Fig.~\ref{fig:sims_degens} compares the fiducial, lateburst, and two-infall models.
 The lateburst slightly shifts \caah\ down and only slightly perturbs \caafe.
@@
 
+\dbnote{there has to be a good reason why \caafe\ is not affected or maybe only more extreme pertubations make a difference?}
+
 \subsection{Degeneracies} \label{sec:outflows}
@@
 Both classes of models are able to reproduce many details of the disk abundance structure due to the strong degeneracy between the normalizations of elemental yields and mass-loading (see discussion in, e.g.
-\citealt{sandford+22} and appendix B of \citealt{james+23}).
+\citealt{sandford+24} and appendix B of \citealt{james+23}).
 Our parameterization of $\eta$ illustrates this (see Equation~\ref{eq:mass_loading}) -- choosing a lower value of $y_{\alpha}$ will similarly result in lower values of $\eta$ while maintaining the same metallicity gradient.
-We consider a model where we double all yields, in the top row of Fig.~\ref{fig:sims_degens}. A uniform change in yields and outflows leaves our median trends relatively unchanged.
-
-Additionally, Fe yields and the \ia\  delay-time-distribution have their own uncertainties. Increasing both $y_{\rm Fe}^{\rm Ia}$ and $\Ycagb$ correspondingly leaves \caafe\ mostly unchanged.
-
-Fig.~\ref{fig:sims_degens} demonstrates this point with a model in which we increase the \ia\ Fe yields by 20\% and increase $f_{\rm AGB}$ to 0.3. 
-Fundamentally, the \caafe\ trends demand yield models in which these delayed components of C and Fe enrichment are in a particular proportion.
-
-Finally, the delay-time-distribution of \agb\ stars is determined by the mass dependence of the yield.
-If we shift the yield tables down in mass artificially, then the delay-time-distribution of \agb\ C is more extended.
-A lower $f_{\rm agb}$ is needed to produce a similar trend in \caafe{}.
-The top panel of Fig.~\ref{fig:nitrogen} demonstrates this point with a model.
-Conversely, shifting the yield tables up in mass shortens the DTD and requires a higher \agb\ fraction in order to make up the difference (verify).
-
-Initial mass function (and possible metallicity dependence)? Metallicity dependent Oxygen/Magnesium and Iron yields? Gas phase migration?
+We consider a model where we double all yields, in the right panel of Fig.~\ref{fig:sims_degens}. A uniform change in yields and outflows leaves our median trends relatively unchanged.
+
+\dbnote{paragraph about how fagb and zeta are interdependent, but not fully degenerate in \caafe.}
+
+Additionally, Fe yields and the \ia\  delay-time-distribution have their own uncertainties.
+Increasing both $y_{\rm Fe}^{\rm Ia}$ and $\Ycagb$ correspondingly leaves \caafe\ mostly unchanged.
+Not shown here, if both processes increase by a similar proportion of the total yield, then our predictions in \caafe\ are unchanged.
+Therefore, we cannot know the DTD of C much better than that of Fe in this framework.
+
+\dbnote{Other things to discuss possibly ? :
+ Initial mass function (and possible metallicity dependence)? Metallicity dependent Oxygen/Magnesium and Iron yields? Gas phase migration / ISM cooling?  MLR
+ }
 
 \subsection{Nitrogen}
+
+\begin{figure}
+\centering
+\includegraphics{figures/nitrogen.pdf}
+
+\caption[]{Similar to Fig.~\ref{fig:zeta_f} except for [C/N] against [Mg/H] for the fiducial model.
+Combining our results with the suggested yield from \JJ\ (rescaled to our adopted yields) explains both the thin-disk evolution of C and N.
+}
+\label{fig:nitrogen}
+\end{figure}
+
+N production, also affected by the CNO cycle, is closely tied to C.
+As a test of our model, we use the \agb\ N yield suggested by \citet{james+23}.
+Fig.~\ref{fig:nitrogen} shows [C/N] versus [Mg/H] and for our fiducial model.
+We are able to closely match the [C/N]-[Mg/H] trend.
+
+\section{Gas-Phase Abundances}\label{sec:gas}
 
@@
 \centering
-\includegraphics{figures/c_n.pdf}
-
-\caption[]{Similar to Fig.~\ref{fig:first_models}.
-The top panels show models with different mass-ranges contributing \agb\ C yields.
-The middle panels show different star formation histories (section \ref{sec:sfh}) and yield normalizations.
-The bottom panels show [N/Mg] against [Mg/H] and [Mg/Fe] for the fiducial model.
-}
-\label{fig:nitrogen}
+\includegraphics[]{figures/summary.pdf}
+\caption[]{\dbnote{warning: caption in progress} 
+Gas-phase C abundances. 
+We plot the fiducial model's present-day ISM abundances as a thick blue line (\protect\captionline[line width=1.5pt]{blue}).
+Black lines are single-zone models: a fiducial yields and MW-like model (solid black), and three corrected yield models representing the MW (dotted), GSE (dashed) and Wukong (dash-dots).
+Points represent measurements in 
+    HII regions \citep[orange circles;][]{skillman+20, esteban+02, esteban+09, esteban+14, esteban+19}
+    damped Lyman-alpha (DLA) systems \citep[rust triangles;][]{ellison+10, srianand+10, dutta+14, DZ+03, pettini+08, morrison+16,cooke+17}, ({\color{red} citations})
+    dwarf galaxies \citep[green diamonds;][]{berg+19},
+    Milky Way stars \citep[yellow stars;][]{amarsi+19},
+    and high redshift galaxies \citep[pink squares;][]{arellano-cordova+2022} ({\color{red} citations}).
+
+}
+
+\label{fig:gas_phase}
 \end{figure*}
-
-N production, also affected by the CNO cycle, is closely tied to C.
-As a test of our model, we use the \agb\ N yield suggested by \citet{james+23}.The bottom row of Fig.~\ref{fig:nitrogen} shows [C/N] versus [Mg/H] and [Mg/Fe] for our fiducial model.
-We are able to closely match the [N/Mg]-[Mg/H] trend.
-The [N/Mg]-[Mg/Fe] is predicted to be more shallow than observed -- a limitation of the model potentially implying a more extended DTD for N production.
-We do not explore this further here since our focus is C.
-
-Though photospheric abundances of both C and N in red giants are affected by FDU, (see discussion in section~\ref{sec:data_selection}), their total abundance is conserved by the CNO cycle [e.g.
-CITE].
-C+N therefoe enables an additional test of the yields emperically calibrated in this paper and by \citet{james+23}.
-Thanks to the higher luminosities of red giants, we can make this comparison across a broader range of Galactocentric radii and, consequently, metallicity.
-
-Fig.~\ref{fig:cn} shows the predicted [C+N/Mg]-[Mg/H] trend in comparison to \citepos{weinberg+22} sample, also taken from \apogee\ DR17 (see their section 3).
-The model predicts a slightly shallower trend than the data, though the differences are within the width of the observed distribution, with differences at the $<0.05$dex level at fixed [Mg/H].
-While the number of stars in our subgiant sample drops off significantly at $\rm [Mg/H] \approx -0.3$, this comparison supports our empirically calibrated C and N yields down to $\rm [Mg/H] \approx-0.5$ (50\% lower in Z).
-
-\section{Gas-Phase Abundances}\label{sec:gas}
-
-\begin{table}
-	\centering
-    \caption[]{Single zone model parameters}
-	\label{tab:singlezone_params}
-
-	\begin{tabular}{l l l l l}
-		\hline
-        Model & $\eta$ & $t_{\rm end}$ & $\tau_\star$ & $\tau_{\rm sfh}$ \\
-		\hline
-        1 & 0 & 13 & 2 & 5\\
-        2 & 1 & 10 & 2 & 10\\
-        3 & 9 & 3 & 5 & 3\\
-        4 & 12 & 2 & 10 & 2\\
-		\hline
-	\end{tabular}
-\end{table}
+% \begin{table}
+% 	\centering
+%     \caption[]{Single zone model parameters.
+\dbnote{change dwarf parameters to match Wukong from James' dwarf paper.
+$\eta=47.99\pm 5$, $t_{\rm end} = 3.36\pm 0.5$, $\tau_\star=44.97\pm 7$, $\tau_{\rm sfh} = 3.08\pm 1$}}
+% 	\label{tab:singlezone_params}
+% 
+% 	\begin{tabular}{l l l l l}
+% 		\hline
+%         Model & $\eta$ & $t_{\rm end}$ & $\tau_\star$ & $\tau_{\rm sfh}$ \\
+% 		\hline
+%         1 & 0.5 & 13.2 & 2.5 & 14\\
+%         2 & 1 & 10 & 2 & 10\\
+%         3 & 9 & 3 & 5 & 3\\
+% 	\end{tabular}
+% \end{table}
 
@@
 sources.
-\par
-Fig. 13 shows our compilation alongside the gas-phase abundances in our model
+\dbnote{I believe that dust might warrent a discussion here since this can capture gas-phase metallicity, substantially affecting observations.
+But we also just don't know how to measure gas-phase abundances well at all.
+Reassuring as it means that our focus on stars is very justified.
+There is an additional complication that CEL and RL abundances (especially for O) need to be put on the same scale with +0.2 dex corrections, and there is not a clear understanding which one is better.
+\citet{MM19}
+}
+
+\dbnote{does it make sense to include more high-redshift galaxies? 
+Many of these seem to be through stacked spectra or other challenging measurments, e.g. redshifting the CEL lines in Berg++ dwarfs at $z\sim 2$
+}
+
+DLAs are .......
+Most similar tothose in local group dwarfs (Cooke+2015, berg+2015, cia+2016 from MM2019 review).
+
+Fig.~\ref{fig:gas_phase} shows our compilation alongside the gas-phase abundances in our model
 at snapshots of~$t = 2$ Gyr and the present day.
@@
 or (especially) damped Lyman-alpha systems.
-To test our model at these abundances, we run a suite of one-zone GCE models
-with a handful of different parameter choices.
-\note{[Describe parameter choices here, beginning with some fiducial set of
-choices] Note: after seeing Fig. 13, I'd say it's worth using different
-linestyles to mark the different parameter choices in Fig. 8 -- I'd stick
-with black as color already differentiates between multi-ring and one-zone
-models.}
+To test our model at these abundances, we show 4 different one-zone GCE models.
+\begin{enumerate}
+    \item Fiducial MW: $\eta=0.5$, $t_{\rm end} = 13.2$, $\tau_\star=2$, $\tau_{\rm sfh} = 14$
+    \item Corrected MW-like. 
+    \item Corrected Gaia-Sausage Enceledus like. $\eta=9.56$, $t_{\rm end}=10.73$, $\tau_\star = 26.60$, $\tau_{\rm sfh} = 2.18$, infall mode
+    \item Corrected Wukong-like: $\eta=47.99\pm 5$, $t_{\rm end} = 3.36\pm 0.5$, $\tau_\star=44.97\pm 7$, $\tau_{\rm sfh} = 3.08\pm 1$, infall modej
+\end{enumerate}
+with the exception of the fiducial like model, we use the bi-log-linear CCSNe yield model which plateaus at a [C/Mg] at low metallicity consistant with observations of metal-poor stars and dwarf galaxies.
+\dbnote{check timescales to metallicity = -1 (could sagb affect the trends here?). Also try different yield sets for these just to see if any agree naturally... }
+
 Fig.~\ref{fig:gas_phase} also plots a single-zone model and time-slices of the fiducial multi-zone models gas-phase at present day and $t=2$\,Gyr. 
@@
 
-\footnotetext{See e.g.
-CITATION.
-Th Gaia-Encelidus sausage (GSE) is a kinematically and chemically distinct group of halo stars consistant with the merger of a dwarf galaxy early in the Milky Way's formation.}
-
 Each of these one-zone models predicts a steeper C/O-O/H trend than our
@@
 This difference arises because the trend in the multi-ring models arises as a
-superposition of end-points (see Fig. 7), qualitatively similar to, e.g.,
+superposition of end-points (see Fig.~\ref{fig:c_evo}), qualitatively similar to, e.g.,
 \citepos{schonrich-binney09} argument regarding
@@
 In the one-zone models, the trend instead arises as an evolutionary sequence.
-To demonstrate this point further empirically, Fig. 13 includes measurements
+To demonstrate this point further empirically, Fig.~\ref{fig:gas_phase} includes measurements
 in halo and thick disk stars.
@@
 This prediction is challenged by the measurements in both dwarf galaxies and
-halo/thick disk stars in Fig. 13, which suggest ratios~$\sim$$0.2 - 0.3$ dex
+halo/thick disk stars in Fig.~\ref{fig:gas_phase}, which suggest ratios~$\sim$$0.2 - 0.3$ dex
 below solar between~$\log$(O/H) = X and Y.
@@
 
-\begin{figure*}
-\centering
-\includegraphics[]{figures/summary_plot.pdf}
-\caption[]{Gas-phase C abundances. We plot our model at $t=2$\,Gyr and present day as thick solid lines. Black lines are single-zone models. Points represent measurements in 
-    HII regions    \citep[pink circles;][]{skillman+20, esteban+02, esteban+09, esteban+14, esteban+19}
-    damped Lyman-alpha (DLA) systems \citep[blue triangles;][]{ellison+10, srianand+10, dutta+14, DZ+03, pettini+08, morrison+16,cooke+17},  % a1: Cooke et al.
-(2015); 2: Dutta et al.
-(2014); 3: Cooke et al.
-(2014); 4: Ellison et al.
-(2010); 5: Cooke et al.
-(2011b); 6: This work; 7: Pettini et al.
-(2008); 8: Morrison et al.
-(2016); 9: Srianand et al.
-(2010); 10: Cooke et al.
-(2012); 11: Dessauges-Zavadsky et al.
-(2003)
-    dwarf galaxies \citep[red diamonds;][]{berg+19},
-    Milky Way halo and thick disk stars \citep[green stars;][]{amarsi+19, nissen+14, fabbian+09},
-    and Milky Way high-$\alpha$ stars (yellow points; \citealtjack), and high redshift galaxy through JWST \citep[yellow hexagon;][]{arellano-cordova+2022}.
-}
-
-\label{fig:gas_phase}
-\end{figure*}
+\dbnote{Discussion on a complex landscape of C production: elevation at lowest metallicities but with stochastic mixing, Pop III and many other problems; declining at [O/H] = -1, increasing due to Z-dependent CCSNe and delayed AGB enrichment up to 0, and flat in disks due to chemical equilibrium, but maybe also more flat CCSNe too.}
+
+\dbnote{depending on what everyone thinks, may be worth discussing CEMPs since they have enough literature although not necessarily relavent here.
+Carigi+Peimbert 2011, Molla+2015.
+Lyman limit systems in Lehner+2016.}
+
+\dbnote{other stellar surveys...
+Gustafsson+1999, bensby\&feltzing+2006, Spite+2005, Neiva \& Przybilla+2012, Tautvaisiene+2016.}
 
@@
 Building on~\citet{james+23}, we quantify the impact of C yield assumptions on Milky Way GCE models.
-We use Roberts et al.'s (2023) sample of APOGEE subgiants as our primary observational benchmark, as subgiant atmospheres most likely reflect their birth C abundances (see discussion in section~\ref{sec:data_selection}).
+We use \citepos{jack} sample of APOGEE subgiants as our primary observational benchmark, as subgiant atmospheres most likely reflect their birth C abundances (see discussion in section~\ref{sec:data_selection}).
 In our fiducial model, C initially increases following the slope of the \cc\ C dependence.
@@
 Because massive star enrichment dominates the C mass budget in our models, the predictions are relatively insensitive to the choice of AGB star yield model.
-Of the \agb\ tables tested here, \cxi, \kxvi, and \pxvi\ all predict similar abundance trends in [C/Mg] with [Mg/H] and [Fe/Mg].
-The strong destruction of C by massive stars at \about{} solar metallicity   in \vxiii\ are instead in tension with the data (See Figs.~\ref{fig:first_models})  and~\ref{fig:agb-ssp})
-As both the \cxi\ and \pxvi\ models predict \about{} linear N yields as well, these combined models best explain combined C and N abundance trends (see Appendix!?).
+Of the \agb\ tables tested here, \fruity, \monash, and \nugrid\ all predict similar abundance trends in [C/Mg] with [Mg/H] and [Fe/Mg].
+The strong destruction of C by massive stars at \about{} solar metallicity   in \aton\ are instead in tension with the data (See Figs.~\ref{fig:agb_predictions})  and~\ref{fig:agb-ssp})
+As both the \fruity\ and \nugrid\ models predict \about{} linear N yields as well, these combined models best explain combined C and N abundance trends (see Appendix!?).
 
@@
 As a result, the metallicity dependence of the total, population-averaged C yield is tightly constrained by the [C/Mg]-[Mg/H] relation, but the metallicity dependencies of the individual contributions from CCSNe and AGB stars are less precisely determined.
-Due to the sensitivity of elemental yields to poorly understood processes, such as mass-loss rates and convection, our results provide a useful benchmark for stellar evolution models~\citep[see the discussion in e.g.][]{gil-pons2022}.
+Due to the sensitivity of elemental yields to poorly understood processes, such as mass-loss rates and convection, our results provide a useful benchmark for stellar evolution models~\citep[see the discussion in e.g.][]{gil-pons+2022}.
 With abundance measurements for several million stars provided by upcoming spectroscopic surveys, particularly SDSS-V's Milky Way Mapper program~\citep{sdssv}, constraints on both stellar nucleosynthesis and the assembly history of our Galaxy will become increasingly more powerful.
@@
 \section*{Acknowledgements}
-
- Here you can thank helpful
-colleagues, acknowledge funding agencies, telescopes and facilities used etc.
-Try to keep it short.
 
@@
 
+\dbnote{do I need acknowledgements for appendix spectro-surveys?}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-The inclusion of a Data Availability Statement is a requirement for articles published in MNRAS.
-Data Availability Statements provide a standardised format for readers to understand the availability of data underlying the research results described in the article.
-The statement may refer to original data generated in the course of the study or to third-party data analysed in the article.
-The statement should describe and provide means of access, where possible, by linking to the data or providing the required accession numbers for the relevant databases or DOIs.
+\dbadd{data and codes used in this paper are all publicly available. (do i need links here?). }
 
@@
 
-\section{Comparison with other samples}
-
-Discuss
-\begin{description}
-    \item \citet{vincenzo+21}
-    \item Gaia-ESO survey
-    \item \citet{bensby+21}
-    \item \citet{weinberg+22}
-    \item GALAH: Low completion, one line (6588Å), likely observational effects of lower detection rates for metal poor stars, but also strong systematic from APOGEE.
-    \end{description}
-
-    There are large spectroscopic surveys (RAVE, LAMOST)  but they do not have C abundances.
+\section{Model Parameters}
+
+\begin{table*}
+	\centering
+    \caption[]{Description of the models presented in this paper.}
+	\label{tab:model_parameters}
+
+	\begin{tabular}{l l l l l}
+		\hline
+            name & $Y_{\rm C}^{\rm AGB}$ & $y_{\rm C}^{\rm CC}$ & additional parameters \& notes \\
+            \hline
+            fiducial & 1.45 x fruity & $0.002203 + 0.00196x + Ax^2$ & default model. See Section~X.X \\
+            FRUITY & 1 x fruity & $0.0024 + 0.002x + Ax^2$ \\
+            Monash & 1 x monash & $0.0024 + 0.0025x + Ax^2$ \\
+            ATON & 1 x aton & $0.00255 + 0.0025x + 0.0021 x^2$& \\
+            NuGRID & 1 x nugrid(M, Z) & $0.0024 + 0.00136x + 0.0016x^2$& \\
+            f=0.0 &  \\
+            f=0.5 & 3.623 x fruity & $0.00138 + \zeta x + Ax^2$ & \\
+            steep & 1.45xfruity & $zeta=$ \\
+            shallow & 1.45xfruity & $zeta=0$ \\
+            fz=0 \\
+            fz=0.5 \\
+            m0.5 & 1.44 fruity(m/0.5, Z)  & 0.00225 " & \\
+            m0.8 & 1.44 fruity(m/0.8, Z) & " \\
+            m1.5 & 1.44 fruity(m/1.5, Z) & 0.002194 " \\
+            m2 & 1.44 fruity(m/2, Z) & 0.2587 " \\
+            lateburst & & & SFH$\sim {\rm insideout} (1+N(t, 13.2, 1))$\\
+            twoinfall & & & SFH$\sim$ ... , ... \\
+            2y & & & all yields doubled;  $\eta$ adjusted to Eq.~N \\
+            lowz correction& other equation & --- & --- \\
+		\hline
+	\end{tabular}
+\end{table*}
+
+For our added scatter, we use the polynomial fits to the reported internal APOGEE error with metallicity.
+In detail, these polynomials should also very with logg, teff, however as all of our stars are subgiants, these effects should be smaller.
+We also use $x={\rm [Fe/H]}$ for brevety.
+\begin{subequations}
+\begin{align}
+    \delta {\rm [Mg/H]} &= 0.0652 x^2 + 0.00522 x + 0.0338 \\
+    \delta {\rm [Mg/Fe]} &= 0.00793 x^2 - 0.00802 x + 0.0138 \\
+    \delta {\rm [C/Mg]} &= -0.0378x + 0.03506 
+\end{align}
+\end{subequations}
+
+\begin{figure*}
+\includegraphics{sims_agb.pdf}
+
+\caption[]{
+    Similar to Fig.~\ref{fig:zeta_f}. 
+}
+\label{fig:agb_predictions}
+\end{figure*}
+
+The best fits assuming perfect equilibrium.
+\begin{subequations}
+    \begin{align}
+        \frac{\Yct(Z)}{y_{\rm Mg}} &\approx 4.20 + 1.64 \log (Z/\Zo)\\
+        \frac{\Yct(Z)}{y_{\rm Mg}} &\approx 4.12 + 1.21 \log(Z/\Zo) + 3.07 \log(Z/\Zo)^2
+    \end{align}
+\end{subequations}
 
@@
     \centering
-    \includegraphics{c+n.pdf}
-    \caption{[C+N/Mg]}
-    \label{fig:cn}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics{figures/cmg_mgh_allstar.pdf}
-    \includegraphics{figures/cmg_mgfe_allstar.pdf}
-    \caption{Caption}
-    \label{fig:enter-label}
+    \includegraphics{figures/equilibrium_yields.pdf}
+    \caption[]{Inferred total C yields as a function of metallicity.
+We assume chemical equilibrium (orange curve, see discussion in section \ref{sec:equilibrium}).
+Blue points are the median value of $\Ycc$ for each (number) bin in [Mg/H] with uncertainties based on the 16--84 percentile range.
+    \note{I'd rephrase this caption slightly to be a little more specific about what the lines are representing.
+Something to the effect of "The orange solid and green dashed curves show fits to the blue points under the assumption of a chemical equilibrium trend (see discussion in section \ref{sec:equilibrium}).
+    }
+
+    \dbnote{Considering cutting this figure (requires about 0.1 dex adjustment and compare to Fig.~\ref{fig:equilibrium_validity})}
+    }
+    \label{fig:analytic}
 \end{figure}

### 2024-08-29 carbon_paper/tex/survey_comparison.tex
survey comparison seperated from main text

\documentclass[11pt]{article}

% MNRAS is set in Times font. If you don't have this installed (most LaTeX
% installations will be fine) or prefer the old Computer Modern fonts, comment
% out the following line
\usepackage{newtxtext,newtxmath}
\usepackage{anyfontsize}
\usepackage{aas_macros}
% Depending on your LaTeX fonts installation, you might get better results with one of these:
%\usepackage{mathptmx}
%\usepackage{txfonts}

% Use vector fonts, so it zooms properly in on-screen viewing software
% Don't change these lines unless you know what you are doing
\usepackage[T1]{fontenc}

% Allow "Thomas van Noord" and "Simon de Laguarde" and alike to be sorted by "N" and "L" etc. in the bibliography.
% Write the name in the bibliography as "\VAN{Noord}{Van}{van} Noord, Thomas"

%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%

% Only include extra packages if you really need them. Common packages are:
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
% \usepackage{amssymb}	% Extra maths symbols
\usepackage{hyperref}
\usepackage[normalem]{ulem}
\usepackage[dvipsnames]{xcolor}

\graphicspath{{figures/}}

\usepackage{natbib}

% Acronyms
\newcommand{\agb}{AGB}
\newcommand{\apogee}{APOGEE}
\newcommand{\aspcap}{\textsc{aspcap}}
\newcommand{\cc}{CCSN}
\newcommand{\gce}{GCE}
\newcommand{\ia}{SN Ia}

% internal abbreviations
\newcommand{\caah}{[C/Mg]-[Mg/H]}
\newcommand{\caafe}{[C/Mg]-[Mg/Fe]}

% other
\newcommand{\ycmg}{\ensuremath{2.7 + 32\left(Z-\Zo\right)}}
\newcommand{\ycccmg}{1}
\newcommand{\yco}{1}
\newcommand{\fmeas}{20\%}

\makeatletter
\newcommand{\C}[1][\@nil]{
    \def\tmp{#1}%
    \ifx\tmp\@nnil%
        \ensuremath{\rm C}%
    \else%
        \ifmmode ^{#1}{\rm C}%
        \else $^{#1}$C%
        \fi%
\fi }
\makeatother

\newcommand{\Yct}{{y_{\rm C}}}
\newcommand{\Ycc}{{y_{\rm C}^{\rm CC}}}
\newcommand{\Yoc}{{y_{\rm Mg}^{\rm CC}}}
\newcommand{\Ycagb}{{y_{\rm C}^{\rm AGB}}}
 \newcommand{\yb}{\ensuremath{\rotatebox[origin=B,y=0.5ex]{180}{y}}}
\newcommand{\y}{Y}

\newcommand{\Mo}{ {\rm M}_{\sun}}

\newcommand{\Zo}{ Z_{\sun}}

\newcommand{\about}[1]{${\sim} #1$}

\newcommand{\dbnote}[1]{ {\color{Thistle} \textit{\small (DB: #1)}} }

% MAIN DOCUMENT
\title{Comparison of C inn observations}

\author{daniel}

\begin{document}

\maketitle

This document is a summary of the differences between measurements and surveys as it is related to C. Below, we provide brief descriptions of the relavant characteristics of C determination and survey properties.

Some relevant literature comparing surveys includes \citet{hegedhus+2023}, and \dots.

\section{Stars}

\subsection{Large Spectroscopic Surveys}
In general (see Fig.~\ref{fig:other_surveys}, all surveys (except for GALAH, see below) agree in both the \caah\ and \caafe\ trends, up to a \about{0.2} dex offset. Changing our adopted equilibrium trend to any of these would only affect the yield scale, which is already a known degeneracy in chemical evolution modeling.

We do not renormalize surveys and instead use reported abundances. Each survey sets zero points in slightly different manners, and given the systematic uncertainty in this step, the absolute abundance scale of a survey is less precise than abundance trends.

% \begin{figure}
%     \centering
%     \includegraphics{c+n.pdf}
%     \caption{[C+N/Mg]. This figure is likely getting cut, check if looks good with full sample (reassuring), and maybe look at [Mg/Fe] here too, but if agrees, we do not need it anymore...}
%     \label{fig:cn}
% \end{figure}

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/cmg_other_surveys.pdf}
    \caption{Binned median trends for several surveys.
    With the exception of GALAH (see text), all samples agree up to a normalization for \caah\, and, even more encouragingly, samples approximately trace out the same trend in \caafe.}
    \label{fig:other_surveys}
\end{figure*}

% \begin{figure*}
%     \centering
%     \includegraphics{figures/caah_catalogues.pdf}
%     \caption{Similar to binned trends (REF) but for three other samples of stars with Birth C estimates.
%     With the exception of GALAH (see text), all samples agree upto a normalization for \caah\, and, even more encouragingly, samples approximantly trace out the same trend in \caafe.}
%     \label{fig:other_catalogues}
% \end{figure*}

\subsubsection{APOGEE} 
APOGEE (The Apache Point Observatory Galactic Evolution Experiment) is a large spectroscopic survey carried out on the Sloann 2.5 metre telescope and Irénée du Pont Telescope in Chile.
APOGEE DR17 provides over 600,000 stars observed with medium-high resolution spectroscopy ($R\gtrsim 22,000$) in the near infrared (1.51–1.70 $\mu$m) \citep{apogee17}.

While we focus on APOGEE subgiants, there are several other approaches to using APOGEE data to validate our models:
APOGEE ASPCAP fits molecular C lines (calibrated only to lab data) whereas atomic lines are on the Grevesse 2007 scale. The reported atomic C abundances are broadly consistent with the molecular measurements. 
See Jonsson + 2020 for a description of the data reduction for APOGEE DR16 (no DR17 published yet).

A second approach is to add corrections to the effects of first dredge up, as \citet{vincenzo+21} has done.

The {\bf Gaia-ESO} survey (Gilmore + 2022, Randich+2022) is a large ($10^5$) stellar spectroscopic instrument using FLAMES/VLT with both the GIRAFFE (R $\sim$ 20k) and UVES ($R\sim 50k$) spectrographs. 
Here, we use the catalogue published in  \citep{hourihane+2023} containing 114,816 stars.
GSO uses the Grevesse 2007 solar abundances for the low resolution survey but does not calibrate (?) the high resolution survey, so we apply XXX corrections.
WG10 uses 5380.33, 6587.61 as the C lines (worley+2024).
However, for high resolution observations (WG11), C is derived from the swan bands:
C2 Swan (1, 0) band head at 5135 Å and C2 Swan (0, 1) band head at 5635.5 Å
(Tautvaišiene˙ et al. 2015); discussed as but are not sensitive to non-local thermodynamic equilibrium (NLTE) deviations (cf. Clegg et al. 1981;
Gustafsson et al. 1999)

our flags are
\begin{itemize}
    \item No flags in SNR, SRP, BIN, SSA, IPA, PSC< EML
    \item errors in LOGG < 0.5
    \item errors in Teff < 200
    \item logg >= 3.5
    \item no NaN C, Mg, Fe, and respective errors.
\end{itemize}

With these selections, 263 stars in UVES and 26509 in GIRAFFE. However, only 29 stars in UVES now have C2 measurements, 214 with C I, and 142 with CI in GIRAFFE. No star reports using more than 2 lines to measure C.
We note that we only find very few stars with reliable stellar parameters and C abundance measurements in both surveys. In particular, the Girraffe low-resolution survey only has < 0.4\% completion for our GSO dwarf sample, and only 547 stars pass our cuts in the high resolution survey with less than half containing some carbon abundance measurement.

Note that the GSO-UVES C abundances are re-calculted in \citet{franchini+20}, with much higher completeness
which result in trends very similar to the general survey (except for a \~ 0.2 dex offset).

\textbf{GALAH}: 
The Galactic Archeology XXX with HERMES survey \citep{DeSilva2015, Martell2017}
is a high-resolution ($R\sim 50,000$), large ($10^5?$ stars), optical (lambda in ...) survey predominantly targeting local dwarfs.

GALAH is perhaps the strongest outlier in terms of the infered \caah\ trend: predicting a steep negative slope of > 0.5 (compared to < 0.1 for APOGEE)
However, GALAH may not be the ideal survey for measuring C. Reported C measurments have low completion (50\% or down to 20 \% at lower metallicities) and are based on one weak line (6587.6100Å, in supplemental material of DR3 paper).
So, whlikely observational effects of lower detection rates for metal poor stars, but also strong systematic from APOGEE. Reference Emily's appendix
GALAH is the one survey which could be consistent with a very different abundance trend in the milky way, declining from +0.3 to -0.2 across the sampled range. 
Crossmatches with apogee reveal that completion is not the whole story-and stars with C abundances measured in both surveys exhibit a similar systematic trend with metallicity. 
\dbnote{Note how results would be affected if using Galah instead}
GALAH consideres NLTE for O, Mg, and Fe, (among others) but not C, using the SME code on a small sample, then applied to the whole survey using the Cannon.

We select our sample with
\begin{itemize}
    \item no FLAG\_SP
    \item no FLAG FE\_H
    \item SNR C3 IRAF > 30
    \item no nan in TEFF \& LOGG
    \item error LOGG < 0.5
    \item error TEFF < 200
    \item LOGG >= 3.5
    \item 6500 >= TEFF >= 4500
    \item no flag C, O, or Mg \# should be Fe instead of O
    \item No NaNs in C, Mg, Fe
\end{itemize}
This results in 97,212 stars.

\textbf{LAMOST}: Lamost has low and medium resolution surveys. Here, we use the dataset from ... derived from machine learning on APOGEE and GALAH.

\begin{itemize}
    \item Qual = 0
    \item 3.5 < logg < 5
    \item 7000 > teff > 4000
    \item no flag on FE and MG and C 
\end{itemize}

\textbf{DESI} is an ongoing large spectroscopic survey. The Milky Way survey aims to record spectra for 30,000 stars, with the potential to measure stellar parameters, radial velocities, and chemical abundances (C, Mg, Fe, Si?). the early data-release 1 does contain the information, but it does not appear to be well-calibrated or explained yet. 
COMPLETION NOTE??
Finally, we note a few examples of other, smaller spectroscopic catalogues here. We do not show plots of these as their abundance trends for dwarfs are within the range of large spectroscopic surveys. (Note the downturn at O/H about 0.4??)

There are other large spectroscopic surveys (RAVE, SEGUE, the really old one?)  but they do not have C abundances. (Jofre ARAA)
H3 might have C but not publicly available?

\citet{bensby+21}

Hypatia catalog (Hinkel + 2017).
 Luck et al. 2018.
Harps-GTO: publically available :).

California-Kepler Survey: HIRES (Brewer+2016): also publically available

% SPECIES (Soto & Jenkins) no C
% Hawkins + 2016 (apokasc): only giants...> used by Vincenzo ? 
% SPOCS (Valenti & Fischer 2005): No C
% AMBRE (no C)

\section{Gas-Phase and Extragalactic Abundances}

Table of sources and measurements if time...

\subsection{H II regions}
interestingly, the same techniques can be applied to both Milky Way HII regions and nearby extragalactic ones.

\subsubsection{Damped Lymnan Alpha}
In Figure.~\ref{fig:gas_phase}, we show damped-lynman alpha systems as compiled in \citet{cooke+17}. These are clouds of gas observed by their (strong Lynman alpha) absorption in quasar spectra. As such, a handful of studies have been able to determine the abundances of these systems, which are typically at redshifts $z\sim 3$. 
According to REVIEW, it is still uncertain what astrophysical systems these are (circumgalactic, dwarf galaxies, etc.?), but they are most likely understood as high-redshift analgues of compact blue dwarf galaxies.

\begin{table}
\centering
\caption{
Damped lyman alpha measurements
References are (1) dessauges-zavadsky+03, (2) : pettini+08, 3: \citet{ellison+10}, }
\begin{tabular}{lrlll}
    \hline
    Quasar & $z_{\rm abs}$ & [C/O] & [O/H] & references \\
    \hline
    Q1101-264 & 1.838000 & $0.77 \pm 0.09$ & $-1.66 \pm 0.07$ & (1) \\
    Q2059-360 & 2.507000 & $-0.41 \pm 0.28$ & $-1.38 \pm 0.23$ & (1) \\
    J2155+1358 & 4.212000 & $-0.29 \pm 0.08$ & $-1.82 \pm 0.11$ & (1) \\
    Q0913+072 & 2.618000 & $-0.39 \pm 0.05$ & $-2.42 \pm 0.04$ & (2)\\
    J1016+4040 & 2.816000 & $-0.21 \pm 0.05$ & $-2.48 \pm 0.11$ & (2)\\
    J1558+4053 & 2.553000 & $-0.06 \pm 0.07$ & $-2.47 \pm 0.06$ & (2)\\
    Q2206-199 & 2.076000 & $-0.38 \pm 0.04$ & $-2.09 \pm 0.05$ & (2)\\
    J0140-0839 & 3.696000 & $-0.30 \pm 0.08$ & $-2.77 \pm 0.15$ & (3) \\
    J1337+3152 & 3.167000 & $-0.19 \pm 0.11$ & $-2.59 \pm 0.17$ & srianand+10 \\
    J0311-1722 & 3.734000 & $-0.42 \pm 0.11$ & $-2.31 \pm 0.10$ & cooke+11 \\
    J1001+0343 & 3.078000 & $-0.41 \pm 0.03$ & $-2.67 \pm 0.05$ & cooke+11 \\
    J1358+6522 & 3.067295 & $-0.03 \pm 0.11$ & $-2.24 \pm 0.09$ & cooke+12 \\
    J0035-0918 & 2.340060 & $0.16 \pm 0.24$ & $-2.71 \pm 0.17$ & dutta+14 \\
    J0953-0504 & 4.202870 & $-0.50 \pm 0.03$ & $-2.57 \pm 0.10$ & dutta+14 \\
    J0035-0918 & 2.340000 & $0.08 \pm 0.16$ & $-2.46 \pm 0.07$ & cooke+15 \\
    J1111+1332 & 2.270000 & $-0.18 \pm 0.11$ & $-1.94 \pm 0.08$ & cooke+15 \\
    Q1202+3235 & 4.977000 & $0.20 \pm 0.09$ & $-2.00 \pm 0.12$ & morrison+16 \\
    J0903+2628 & 3.077590 & $-0.38 \pm 0.04$ & $-3.07 \pm 0.05$ & cooke+17 \\
    J0035-0918 & 2.340064 & $-0.12 \pm 0.14$ & $-2.47 \pm 0.06$ & welsh+20 \\
    HS0105+1619 & 2.536000 & $0.11 \pm 0.04$ & $-1.78 \pm 0.02$ & cooke+14 \\
    Q0913+072 & 2.618000 & $-0.36 \pm 0.01$ & $-2.42 \pm 0.01$ & cooke+14 \\
    J1358+6522 & 3.067000 & $-0.27 \pm 0.06$ & $-2.33 \pm 0.02$ & cooke+14 \\
    \hline
\end{tabular}
\end{table}

C abundances are measured in XXXX.

Hello

\newpage

\bibliographystyle{mnras}
\bibliography{main}

\end{document}

### 2025-01-16 models/fiducial/sspw_const/reanalyze.py
near-final model set

@@ -1,0 +1,44 @@
+import surp
+from surp import ViceModel, MWParams
+import sys
+import argparse
+
+# weight function here
+
+def weight_func(mass, metallicity, age):
+    return mass
+
+
+args = argparse.ArgumentParser(description="Run a VICE model with the given parameters and yields")
+
+args.add_argument("-i", "--interactive", action="store_true", help="Run the model in interactive (verbose) mode")
+
+
+args = args.parse_args()
+
+model_out = "model.json"
+stars_out = "stars.csv"
+vice_name = "../run/milkyway.vice"
+
+params_file = "params.toml"
+yields_file = "yield_params.toml"
+
+params = surp.MWParams.from_file(params_file)
+yields = surp.yields.YieldParams.from_file(yields_file)
+
+if args.interactive:
+    params.verbose = True
+
+print(params)
+print(yields)
+
+surp.yields.set_yields(yields)
+
+
+print(f"saving processed stars to {model_out} and {stars_out}")
+processed = ViceModel.from_vice(vice_name, params.zone_width, seed=params.seed, weight_function=weight_func)
+processed.save(model_out, overwrite=True)
+processed.stars.to_csv(stars_out)
+processed.stars_unsampled.to_csv("stars_all.csv")
+
+print("bye bye!")

### 2025-01-16 models/fiducial/sspw_peaked/reanalyze.py

@@ -1,0 +1,47 @@
+import surp
+from surp import ViceModel, MWParams
+import sys
+import argparse
+import numpy as np
+
+# weight function here
+
+def weight_func(mass, metallicity, age):
+    x = age
+    y = np.interp(age, [0, 2, 4, 6, 14], [0, 0, 1, 0.3, 0])
+    return mass * y
+
+
+args = argparse.ArgumentParser(description="Run a VICE model with the given parameters and yields")
+
+args.add_argument("-i", "--interactive", action="store_true", help="Run the model in interactive (verbose) mode")
+
+
+args = args.parse_args()
+
+model_out = "model.json"
+stars_out = "stars.csv"
+vice_name = "../run/milkyway.vice"
+
+params_file = "params.toml"
+yields_file = "yield_params.toml"
+
+params = surp.MWParams.from_file(params_file)
+yields = surp.yields.YieldParams.from_file(yields_file)
+
+if args.interactive:
+    params.verbose = True
+
+print(params)
+print(yields)
+
+surp.yields.set_yields(yields)
+
+
+print(f"saving processed stars to {model_out} and {stars_out}")
+processed = ViceModel.from_vice(vice_name, params.zone_width, seed=params.seed, weight_function=weight_func)
+processed.save(model_out, overwrite=True)
+processed.stars.to_csv(stars_out)
+processed.stars_unsampled.to_csv("stars_all.csv")
+
+print("bye bye!")

### 2025-01-16 models/perturbations/fruity_2/run.py

@@ -1,20 +1,0 @@
-import surp
-import vice
-
-import sys
-sys.path.append("..")
-from ag_run import ag_run 
-
-
-
-agb_model = surp.yield_models.ZeroAGB()
-cc_model = 0.0
-ia_model = 0
-
-
-if __name__ == "__main__":
-    ag_run(
-            agb_model = agb_model,
-            cc_model = cc_model,
-            ia_model = ia_model,
-    )

### 2025-01-16 surp/_globals.py

@@ -15,7 +15,7 @@ X_SUN = 0.71 # 0.709 inferred
 
 ELEMENTS = ["c", "n", "mg", "fe"]
 
-AGB_MODELS = ["cristallo11", "ventura13", "karakas16", "pignatari16"]
+AGB_MODELS = ["cristallo11", "ventura13", "karakas16", "battino19"]
 
 def _find_data_dir():
     """Dynamically determines data directory whe n library is imported"""

### 2025-01-16 surp/vice_utils.py

@@ -110,7 +110,7 @@ def _zone_to_int(zone: str):
 def ssp_weight(mass, metallicity, age):
     """A functional form for the weight of finding a sampled star from an SSP given its age and metallicity"""
 
-    return np.where(age < 2, 0, 1) * mass
+    return mass
 
 
 def reduce_stars(multioutput, *,  weight_function=ssp_weight):

### 2025-01-16 carbon_paper/tex/main.tex
updated draft with mcmc models

@@
 \newcommand{\Ycagb}{{y_{\rm C}^{\rm AGB}}}
+\newcommand{\ycagb}{\y_{\rm C}^{\rm AGB}}
 \newcommand{\aagb}{\alpha_{\rm C}^{\rm AGB}}
@@
 \newcommand{\zcc}{\zeta_{\rm C}^{\rm CC}}
+\newcommand{\noneqagb}{\nu_{\rm C}^{\rm AGB}}
  \newcommand{\yb}{\ensuremath{\rotatebox[origin=B,y=0.5ex]{180}{y}}}
@@
 \newcommand{\fagb}{f_{\rm C}^{\rm AGB}}
+
+\newcommand{\zetao}{\zeta^{(0)}}
+\newcommand{\zetai}{\zeta^{(1)}}
+\newcommand{\zetaii}{\zeta^{(2)}}
 
@@
 
-\newcommand{\dbstrike}[1]{{\color{Thistle} \sout{#1}}}
+\newcommand{\dbstrike}[1]{{\color{Thistle} \sout{#1} }}
 \newcommand{\dbadd}[1]{{\color{Thistle} #1}}
@@
 % context
-The origin of C, despite its importance, remains poorly understood. 
+The astrophysical origin of carbon remains largely uncertain---different studies propose that either asymptotic giant branch (AGB) stars or core collapse supernovae (CCSNe) may be the dominant process.
 % 
@@
 The \caah\ trend instead represents the equilibrium abundances of C and Mg. 
-We use the \caah\ trend to estimate the CCSNe C/Mg yield, determining that  $\Ycc/\Yoc = EQUATION$ when including \agb\ C. 
+We use the \caah\ trend to estimate total C/Mg yield ratio, determining that  $\Ycc/\Yoc = EQUATION$.
 % misc
@@
     \caption{The [C/Mg] ratio against [Mg/H] (left) and [Mg/Fe] (right) for the \citet{jack}~sample of \apogee{} subgiants.
-On the left, we plot high and low-$\alpha$ stars in blue and orange, using the separation defined in Equation \ref{eq:high_alpha} \dbstrike{(the high and low-$\alpha$ stars are named for their high or low $\alpha$-element (Mg) to Fe ratios)}.
+On the left, we plot high and low-$\alpha$ stars in blue and orange, using the separation defined in Eq.~\ref{eq:high_alpha}.
 On the right, we colour-code stars according to their [Mg/H] abundance.} \label{fig:subgiants}
@@
 
-Despite being the most abundant metal in the Universe~\citep[e.g.][]{magg+22}, the nucleosynthetic origin of C is inadequately understood. \dbnote{need synonyms for poorly understood}
-Broadly, studies agree that both high mass and asymptotic giant branch (AGB) stars produce C, but their relative yields are disputed.
+Despite being the most abundant metal in the Universe~\citep[e.g.][]{magg+22}, the nucleosynthetic origin of C is poorly understood. 
+There is broad agreement that both high mass and asymptotic giant branch (AGB) stars produce C \citep{jennifer19}, but their relative yields are disputed.
 From a Galactic chemical evolution (GCE) perspective, some authors have argued that high-mass stars should dominate~\citep[e.g.][]{prantzos+94, HEK00, romano+20, franchini+20, gustafsson22}, and others have argued that AGB stars should contribute at least half of the C in the universe~\citep[e.g.][]{tinsley79, chiappini+03, mattsson10, KKU11, rybizki+17, KKL20}.
-\dbadd{We aim to empirically characterize the yields of C and the ratio of AGB and CCSNe production.}
+In this paper, we aim to constrain C production using subgiant stars and multi-zone GCE models \dbstrike{incorporating stellar radial migration}.
 
@@
 % \dbnote{C abundnces for stellar structure (opacities) and star formation (line cooling)}
-
-Predictions of C yields from stellar evolution and supernova (SN) models are riddled with uncertainties (see, e.g., the reviews/summaries by \citealt{romano+10, KL14}).
-Stellar yields are shaped by many poorly understood processes, such as mass loss rates \citep{sukhbold+16, beasor+2020}, rotational mixing \citep{frischknecht+16, LC18}, reaction rates \dbadd{citations}, and convection \citep{chieffi2001, ventura+13}.
-\dbnote{I checked these, is sukhbold the best reference on mass loss?}
-\dbadd{In addition, stellar parameters such as convection and mass loss are calibrated to match observed stars and cannot be predicted from first principles.} \dbnote{need to check if this means SE models are calibrated to match yields or just stellar parameters.}
-Small changes in the initial mass of only $\sim$$0.01 M_\odot$  were recently shown to have dramatic effects on the evolution and explosion outcomes of massive stars \citep{bruenn+2023, vartanyan_burrows2023}.
-Furthermore, many stars are found in binary systems \dbadd{(e.g. \citealt{MKB2019}, others?)}, the effects of which are almost entirely unexplored in stellar nucleosynthesis models \citet{farmer+21}.
-Therefore, accurate yield predictions from stellar theory requires both a much greater understanding of stellar physics and a much more densely sampled grid of models than is currently available.
-
-In light of the challenges of stellar theory, recent work has instead sought to characterize chemical yields empirically.
-\citet{HLA20} measured the abundance ratios in the ejecta of Cassiopeia A using spatial resolved X-ray spectra.
+% \dbadd{In addition, stellar parameters such as convection and mass loss are calibrated to match observed stars and cannot be predicted from first principles.} \dbnote{need to check if this means SE models are calibrated to match yields or just stellar parameters.}
+
+Predictions of C yields from stellar evolution and supernova (SN) models are riddled with uncertainties (see, e.g., the reviews by \citealt{romano+10, KL14}).
+Some \dbadd{substantial uncertanties} include mass loss rates \citep{sukhbold+16, beasor+2020}, rotational mixing \citep{frischknecht+16, LC18}, nuclear reaction rates \dbadd{CITE}, and convection \citep{chieffi2001, ventura+13}.
+Recent work also suggests that small changes in a stars's initial mass of 
+ $\sim$$0.01 M_\odot$  have significant effects on the evolution and explosion outcomes of massive stars \citep{bruenn+2023, vartanyan_burrows2023}.
+Furthermore, many \add{massive} stars are found in binary systems \dbadd{\url{https://ui.adsabs.harvard.edu/abs/2012Sci...337..444S/abstract} ??}, the effects of which are almost entirely
+unexplored in stellar nucleosynthesis models \citet{farmer+21}.
+Accurate predictions of metal yields from stellar evolution models remain elusive.
+
+Given the challenge of {\it a priori} yield predictions, recent work aims to empirically characterize elemental production \dbnote{does it make sense to frame this as only recent work?
+I just don't know but I feel like there are very early examples which at least use observations as a guide for yields, like maybe even B2FH.
+or garnett1997}
 \citet{weinberg+19, weinberg+22} analyzed the abundance ratio trends of high- and low-alpha sequence stars in APOGEE~\citep{apogee17} to infer relative yields of prompt and delayed enrichment sources and the metallicity dependence thereof.
@@
 \citet{rodriguez+21, rodriguez+23} measured the mean Fe yield of core-collapse supernovae (CCSNe) using the radioactive tails of their lightcurves.
-\dbnote{even papers as far back as at least https://ui.adsabs.harvard.edu/abs/1997NuPhA.621...27G/abstract do this.
-Include this series as well: https://ui.adsabs.harvard.edu/abs/2023MNRAS.525.1329L/abstract}
-
-% \note{Reading through at least at this moment, I'd say this is a reasonable place for a new paragraph.
-I wouldn't worry about referencing Weller et al.
-(2024) since He chemical evolution is not super relevant here.}
- Folowing many previous works  (e.g.
+Their measurements, provide one of few empirical anchors on the absolute scale of yields \citep{david_fe}.
+\dbadd{Additionally the series of papers including \citet{eitner+2020} includes some relevant work.}
+
+ % Folowing many previous works  (e.g.
 \citealt{DTS78, BF06, prantzos+18, berg+19}; see also the recent reviews by \citealt{romano22} and \citealt{RM21}.) this paper focuses on the evolution of C in GCE models.
-Most notably for our purposes, \citet{james+23} recently showed that the enrichment history of the Galactic disk can be described as an equilibrium phenomenon.
-In equilibrium GCE, trends in abundance ratios with metallicity arise as a consequence of trends in yield ratios (see discussion in their section {\color{red} X.Y}).
+\citet{james+24} recently argued that the enrichment history of the Galactic disk can be described as an equilibrium phenomenon.
+In equilibrium GCE, trends in abundance ratios closely trace yield ratios (see their section 5.2.2).
 \citet{james+23} had previously shown that the correlation between gas-phase N and O abundances (see their Fig.
 1) could be described as a consequence of the metallicity dependence of the relative N and O yields.
-The equilibrium scenario suggests that this argument should extend to any element whose enrichment by stellar populations does not require long timescales ($\gtrsim$few Gyr).
-We therefore extend \citepos{james+23} arguments to C, which is closely related to N.
+Under their equilibrium scenario, this argument should extend to any element whose enrichment by stellar populations does not require long timescales ($\gtrsim$few Gyr).
+We show in \add{REF 3.1} that the characteristic delay times of C production should be $\sim$ few hundred Myr, within this limit. 
+\dbnote{This is complicated by the difference between high alpha and low alpha, and 1-2Msun stars do produce carbon...}
 
 We use a sample of subgiant stars from APOGEE \citep{apogee17} as our primary observational constraint.
-\dbadd{APOGEE Subgiants provide a large, homogenous sample of well-measured C abundances unaffected by stellar evolution}.
-Subgiants advantageously have photospheric abundances directly representing birth C abundances \citep{gilroy89, korn+07, lind+08, souto+18, souto19}.
-In other evolutionary phases, the measured abundances are known to be affected by internal processes (see discussion in section 2 below), namely gravitational settling in main sequence stars {\color{red} (reference)} and dredge-up in red giants {\color{red} (reference)},
-Our sample should greatly mitigate these difficulties with inferring birth abundances of C, which have been a significant source of uncertainty for previous investigations of its nucleosynthetic origin.
+APOGEE Subgiants provide a large, homogeneous sample of well-measured C abundances unaffected by stellar evolution.
+\dbadd{Subgiants' photospheric C abundance closely matches their birth composition.}
+\dbstrike{Subgiants have the advantage that their photospheric abundances of C directly reflect their birth C abundances much more closely than other spectral types.} \citep{gilroy89, korn+07, lind+08, souto+18, souto19}.
+In other evolutionary phases, the measured abundances are known to be affected by internal processes (see discussion in section 2 below).
+Our sample should therefore be unaffected by uncertainties with inferring their birth abundances.
 
@@
 In Section~\ref{sec:data_selection} we describe the selection for our subgiant observational sample.
-Section~\ref{sec:nucleosynthesis} discusses theoretical estimates of \agb\ and \cc\ C yields. We parameterize our yield choices and derive a estimate of C/Mg yields observationally.
-Section~\ref{sec:vice} reviews the multizone model and modifications thereof for this work.
-Section~\ref{sec:results} presents our multizone model predictions and GCE parameters which are observationally permissable. 
-Finally Section~\ref{sec:gas} compares our model to literature collected observations of halo stars and extragalactic HII regions.
-
-\footnotetext{In this paper, we use the standard notation for chemical abundances.
-$[A/B] = \log_{10}\left(A/B\right) - \log_{10}\left(A_{\sun}/B_{\sun}\right)$, i.e.
-$[A/B]$ is the logarithm of the mass ratio between A and B, scaled such that $[A/B]=0$ for the sun (see Table~\ref{tab:fiducial_mod} for solar scale.) }
+In Section~\ref{sec:nucleosynthesis}, we discusses theoretical estimates of \agb\ and \cc\ C yields and present the yield prescriptions we use for our models.
+In Section~\ref{sec:vice}, we describe the remaining details of our GCE models.
+In Section~\ref{sec:results}, we present our model predictions and discuss their observationally distinguishable predictions. 
+In Section~\ref{sec:gas}, we compare our model to observations of halo stars and extragalactic HII regions from the literature. 
+We summarize our conclusins in section~\ref{sec:conclusions}.
 
@@
 % Subgiants are a useful empirical benchmark because their photospheric abundances should reflect their birth mixture. 
-As an emperical benchmark, we use subgiant stars, whose photospheres accurately represent birth abundances. 
-During main sequence evolution, metals can fall to below the convective envelope (i.e., ``gravitational settling").
-When stars leave the main sequence and become subgiants, these metals are mixed with the convective envelope \citep[]{gratton+00, souto19}. 
- \textit{First dredge up} during the red giant phase brings CNO processed core material to the surface \citep{iben67, KL14}.
-
-We use the sample of \apogee\ DR17 subgiants from \citet{jack}, selecting stars from allStar-dr17-synspec\_rev1 within the $\log g$-$T_\text{eff}$ polygon given by
+We use subgiant stars as our empirical benchmark.
+Subgiants have the advantage that their photospheric C and N abundances should closely approximate their birth mixture.
+During main sequence evolution, metals can fall below the convective envelope (i.e., ``gravitational settling''; e.g. \dbadd{CITE}).
+When stars evolve off main sequence, these metals are reincorporated into the convective envelope \citep[]{gratton+00, souto19}. 
+When a star becomes a red giant, \textit{first dredge up} pollutes its photosphere with core, CNO-processed material
+\citep{iben67, KL14}.
+
+We use the sample of \apogee\ DR17 subgiants from \citet{jack}. We select stars from the ASPCAP pipeline (revision 1) within the $\log g$-$T_\text{eff}$ polygon given by
  \begin{equation}
@@
 \end{equation}
-Also following \citet{jack}, we exclude stars with the flags:
+Following \citet{jack}, we also exclude stars with the flags:
         \verb|APOGEE_MIRCLUSTER_STAR|,
@@
         \verb|DUPLICATE|.
-We additionally remove stars with no reported C, Mg, or Fe abundances (in the {\tt X\_FE} columns). These cuts yield a sample containing \nsubgiants\ subgiants.
-
-Fig.~\ref{fig:subgiants} shows the subgiant sample plotted in \caah\ and \caafe{}.\footnotemark{} In this sample, [C/Mg] increases with metallicity, and [C/Mg] decreases with [Mg/Fe] at fixed [Mg/H].
-
-\dbadd{
-Not shown here, we investigate the median trends for different samples and surveys, including APOGEE Giants with mixing corrections \citep{vincenzo+21}, APOGEE dwarfs, Gaia-ESO dwarfs, GALAH subgiants, LAMOST MRS (CITE), and smaller spectroscopic samples of stars.
-The predominant difference between any survey with our sample is a systematic offset in [C/Mg] in both [Mg/Fe] and [Fe/H] of at most 0.2 dex.
-The exception is GALAH, who's C abundances are highly incomplete, based on a single line and thus C measurements are likely unreliable (see e.g.
-Emily).
-If the median trend of [C/Mg] is offset from what we assume, then we can simply scale our C yields by the appropriate factor (e.g.
--0.15 dex => $10^{-0.15} \approx 0.7$, so $y_{\rm C} \rightarrow  0.7 y_{\rm C}$) without significantly changing our results.
-}
+We additionally remove stars with no reported (or flagged unreliable), C, Mg, or Fe abundances. These cuts yield a sample containing \nsubgiants\ subgiants.
+
+Fig.~\ref{fig:subgiants} shows out subgiant sample plotted in the \caah\ and \caafe{} planes.\footnotemark{} In this sample, [C/Mg] increases with [Mg/H], and [C/Mg] decreases with [Mg/Fe] at fixed [Mg/H].
+
+\footnotetext{In this paper, we use the standard notation for chemical abundances.
+$[A/B] = \log_{10}\left(A/B\right) - \log_{10}\left(A_{\sun}/B_{\sun}\right)$, i.e.
+$[A/B]$ is the logarithm of the mass ratio between A and B, scaled such that $[A/B]=0$ for the sun (see Table~\ref{tab:fiducial_mod} for solar scale.) }
+
+We have also investigated these thrends in other catlogues (not show) in order to understand the systematic uncertainties of our APOGEE subgiant sample.
+Namely, we we consider subgiants/dwarfs from GALAH DR4, Gaia-ESO DR5.1, and LAMOST with similar selection criteria.
+Additionally, we consider APOGEE Giants with first dredge up mixing corrections from \citep{vincenzo+21}.
+In general, different surveys follow similar trends in \caah\ and \caafe\ but with systematic offsets at the $\sim{0.1}$ dex level in [C/Mg] given [Mg/H] and slight variations in the slope.
+\dbnote{Galah DR4 fixes the issues we were seeing and updates how they process C.}
+These systematic differences are not a major concern for our conclusions since our models are mostly constrained by the slope of \caah\ and \caafe,  not their normalization (see Fig.~7?
+and discussion in section \dbadd{5.2}).
 
@@
 
-Table \ref{tab:fiducial_mod} contains our fiducial yields and abundance scale.
-We use solar abundances from \citet{magg+22} with a +0.04 gravitational settling correction  and assuming $X_\odot= 0.71, \mu_{H} = 1$ as in \citet{david_fe}.
-We thus assume $Z_\odot=0.016$ as apposed to $Z=0.014$ in \citet{asplund+09}.
-% Z = (1-Y) / (1 + X/Z)
+Following \citet{james+23}, we integrate yields and our GCE models using the publicly available Versatile Integrator for Chemical Evolution (\VICE, \citealt{JW20}).
+We retain their prescription for O, Fe, an yields, scaled down to the normalization recommended by \citet{david_fe} based on .....
+Table~\ref{tab:fiducial_mod} summarizes these choices.
+As required by \VICE, these yields quantify the mass of some element that is newly produced (i.e.
+net yields as opposed to gross yields).
+The SN yields are in units of the proginitors initial mass, while the AGB yields are defined relative to the star's zero-age main sequence mass.
+
+\dbadd{paragraph about yields in general}
+A yield quantifies the new production of a chemical species.
+For a given star, we define the {\it net fractional yield} to be the mean change in the chemical abundance from the birth to ejected mass, multiplied by the ejected fraction of a stars mass, i.e.
+\begin{equation} 
+   Y_{\rm C}^{\rm AGB}(Z) = 
+    \delta Z_X \frac{M_{\rm ej}}{M}
+\end{equation}
+Note that yields may become negative if more of the initial chemical abundance of X is transformed into other elements than other elements transformed into X.
+In general, we describe yields by their population-averaged forms, the amount of newly produced X per unit mass of star formation (from supernovae and stellar winds).
+\begin{equation} 
+   y_{X}(Z) = 
+    \frac{M_X - M_{\rm X, ini}}{M_{\rm ssp}}
+\end{equation}
+
+In \VICE, massive star nucleosynthesis is approximated as occurring instantaneously after a star formation event.
+Under this approximation, the yield is simply a constant  of proportionality between the metal production rate and the SFR:
+\begin{equation}
+    \dot{M}_X^{\rm CC} = y_{X}^{\rm cc}\, \dot{M}_\star
+\end{equation}
+The population-averaged yield, $y_{X}^{\rm cc}$ can be expressed as
+\begin{equation}
+y_{X}^{\rm CC} = \frac{
+\int_8^u (E(m) m_X + w_X - Z_X(m - m_{\rm rem}) )\frac{dN}{dM}\ dM
+}{
+\int_l^u m\,\frac{dN}{dM}\ dm
+}
+\end{equation}
+where $m_X$ and $w_X$ are the mass of X ejected in a CCSN explosion and through stellar winds respectively, from a star of initial mass $m$.
+$E((m)$ is a function describing the fraction of stars of mass $m$ that successfully explode (se discussion in \S \dbadd{3.2} below).
+$m_{\rm rem}$ is the mass of the remnant left behind, $dN/dM$ is the IMF, for which we assume \dbadd{cite}.
+$l$ and $u$ are the lower and upper mass limits of star formation.
+$8\,\Mo$ is the minimum mass of a CCSN progenitor.
+In section \S 3.2 below, we compute the values of $\Ycc$ using \VICE's `vice.yields.ccsne.fractional` function and discuss theoretical expectations of C yields based on massive star evolutionary models.
+
+The population averaged SNe Ia yield, $y_{X}^{\rm ia}$, is given by,
+\begin{equation}
+    y_{X}^{\rm Ia} = m_{x}^{\rm Ia} \frac{N_{\rm Ia}}{m_\star}
+\end{equation}
+where $m_{X}^{\rm Ia}$ is the average mass of X produced in a single SN Ia event, and $N_{\rm Ia} / M_\star$ is the number of such events per unit mass of star formation.
+The latter can be expressed as an integral over the SN Ia delay-time-distribution (DTD), which describes the rate at which stellar populations produce X through SN Ia in \VICE.
+Following \citet{james+23}, we use a $t^{-1.1}$ single power-law with a minimum delay-time of 150 Myr based on comparisons of the SN IA rate as a function of redshift and the cosmic SFR (e.g.
+\citealt{maoz+12}).
+
+The net yield from a single AGB star is given by \begin{equation} \label{eq:net-yield}
+   Y_{\rm C}^{\rm AGB}(Z) = 
+    \delta Z_X \frac{M_{\rm ej}}{M}
+\end{equation}
+where $M_{\rm ej}$ is the mass of the ejected envelope, and $\delta Z_X$ is the average change in the abundance of X in the envelope over the lifetime of the star.
+Models of AGB star nucleosynthesis report values of $Y_X^{\rm AGB}$ sampled on a grid of initial masses and metallicities (see discussion in \S \dbadd{3.1}), and \VICE\ accepts these tables directly as input.
+The population-averaged AGB star yield is then given by
+\begin{equation} \label{eq:imf-agb-yield}
+    y_{X}^{\rm agb}(Z,\tau) = 
+    \frac{
+    \int_{l}^{M_{\rm max}^{\rm AGB}} 
+    \y_{\rm X}^{\rm proc}(M, Z) M\ 
+    \frac{dN}{dM}\ dM
+}
+{
+    \int_{l}^{u}\ M\ \frac{dN}{dM}\ dM
+}
+\end{equation}
+where $m_{\rm min}$ is the minimum and maximum initial mass of stars that become AGBs.
+While $m_{\rm min}$ theoretically extends as low as $0.1 \Mo$, we interpolate yields to zero past $0.5 \Mo$ as these stars live longer than the disk and no yield grid extends this low.
+In Section~\ref{sec:agb},  we discuss theoretical expectations for C production in AGB stars and our adopted tables of $\Ycagb$ from the literature.
+\dbadd{specify exactly how we change the yield interpolation for AGB stars}
 
@@
 	\centering
-    \caption[]{Solar abundance scale and fiducial yields (in units of SSP~birth mass). See section \ref{sec:agb} for the definition of \fruity. The solar abundance scale is \citet{magg+22} + 0.04. }
+    \caption[]{Solar abundance scale and fiducial yields (in units of stellar population birth mass).
+See section \ref{sec:agb} for the definition of \fruity.
+The solar abundance scale is \citet{magg+22} + 0.04.
+}
 	\label{tab:fiducial_mod}
@@
 
-We define a stellar yield as the fraction of a star's initial mass $M$ which is converted into freshly synthesized C.
-If $\Delta Z_{\rm C}$ represents the change in the mass fraction of C abundance, then the stellar yield is
-\begin{equation}
-    \y_{\rm C}^{\rm AGB} =  \Delta Z_{\rm C} \frac{M_{\rm ejected}}{M} = 
-    \frac{W_{\rm C}(M) - Z_{\rm C}\, M_{\rm ejected}}{M}
-\end{equation}
-where $\Delta Z_{\rm C}$ represents the change in mean metallicity of the initial composition the star was born from, $M_{\rm ejected} = M - M_{\rm rem}$ is the total ejected wind mass through the stars lifetime, $W_{\rm C}$ is the total mass of C ejected through winds, and $Z_{\rm C}$ is the initial C mass fraction of the star.
-For CCSNe, 
-\begin{equation} \label{eq:imf-cc-yield}
-   Y_{\rm C}^{\rm CC}(Z) = 
-    \frac{E(M)\,M_{\rm C}(M) + W_{\rm C}(M) - Z_{\rm C}\,M}{M}
-\end{equation}
-\dbnote{Is the - Z M term right or should M be Mzams - Mrem ?}
-where $E(M)$ is the explodability function, $M_{\rm C}(M)$ is the mass ejected in a successful supernovae, and $W_{\rm C}$ and $Z_{\rm C}$ are as above.
-We assume 8\,$\Mo$ is the minimum mass of \cc\ progeneters (see \VICE\ documentation and \citealt{emily+21}). 
-Note that a yield may be negative if a star expels gas with lower $Z_{\rm C}$ than the star was born with.
-
-An IMF-averaged yield adds together the yields of stars of each mass, weighted by the fraction of stars of each mass (the IMF). 
-The IMF-averaged yield $y_X^{\rm proc}$ for element $X$ under the enrichment process ${\rm proc}$ is given by
-\begin{equation} \label{eq:imf-agb-yield}
-    y_{X}^{\rm proc}(Z,\tau) = 
-    \frac{
-    \int_{M_{\rm to}(\tau)}^{M_{\rm max}} 
-    \y_{\rm X}^{\rm proc}(M, Z) M\ 
-    \frac{dN}{dM}\ dM
-}
-{
-    \int_{M_{\rm min}}^{M_{\rm max}}\ M\ \frac{dN}{dM}\ dM
-}
-\end{equation}
-where ${dN}/{dM}$ is the IMF and $M_{\rm to}(\tau)$ is the mass of stars with lifetime $\tau$, and $M_{\rm min}=0.08$ and $M_{\rm max} = 100$ are the assumed maximum and minimum values of the IMF.
-$y$ thus represents the amount of freshly synthesized material returned to the ISM per unit of star formation. 
-Note that in detail, the core collapse enrichment occurs on such short timescales that $M_{\rm to} = M_{\rm min, cc} = 8\,\Mo$
-
 \subsection{Asymptotic Giant Branch Stars}\label{sec:agb}
@@
  	    \includegraphics[scale=1]{agb_yields.pdf}
-        \caption[]{\dbnote{replace y label with stellar C yield}.
+        \caption[]{\dbnote{replace y label with stellar C yield, draw actual interpolations...}.
 The net fractional \agb\ C yield  plotted as a function of initial stellar mass $M$ and colour-coded according to metallicity.
@@
 The dashed black line shows the delay time distribution of type Ia supernovae ($\propto t^{-1.1}$) for comparison.
-The minimum of \aton{} is $y(t)/y(t_{\rm end})=-46$.
-\dbnote{I think this changed with the new integration scheme...}
+The minimum of \aton{} is at $y( 0.30\,{\rm Gyr})/y(t_{\rm end})=-7.81$ and is large as the net yield is close to zero.
 }
@@
 An Asymptotic Giant Branch (AGB) star is a low mass star during its last nuclear (He shell) burning phase which enriches the interstellar medium (ISM) through mass loss during thermal pulses.(see e.g.
-\citealt{PR2023} \dbnote{or more introductory textbook like Ryden intro to astro?}) .
+\citealt{PR2023}).
 In this work, we explore four different stellar AGB yield tables from the literature which provide well-sampled grids in mass and metallicity. We refer to the tables as 
@@
 Table~\ref{tab:agb} notes the masses and metallicities for each grid of yields.
-We use the same tables as \citet{james+23}, except that we have swapped \citet{karakas10} for \citet{pignatari+16}.
-
-Fig.~\ref{fig:y_agb} compares the stellar \agb\ C yields for these four models.
-Most models agree on general yield trends in mass and metallicity.
-C production peak between masses of $\sim$ 2--4 $\Mo$ and declines as stars become more or less massive.
-As metallicity increases, the net yield decreases and the mass of peak C production increases slightly.
+We use the same tables as \citet{james+23}, except that we have swapped \citet{karakas10} for \citet{pignatari+16}. \dbadd{the selection of tables is the same as CITE with the exception that ...}
+For our models to better match observations, we uniformly amplify the yield tables according to
+\begin{equation} \label{eq:alpha}
+        \Ycagb \rightarrow \alpha_{\rm agb}\ \Ycagb.
+\end{equation}
+We use the \fruity\ table, with $\alpha_{\rm agb}=\cfactor$, as the fiducial \agb\ yield.
+
+Fig.~\ref{fig:y_agb} compares the C yields for these four AGB models.
+\dbadd{there is good agreement} Most models agree on general yield trends in mass and metallicity.
+C production peak between masses of $\sim$ 2--4 $\Mo$. As metallicity increases, the net yield decreases and the mass of peak C production increases slightly.
 
@@
 Below the last sampled mass, $Y_{\rm C}^{\rm AGB}$ is linearly interpolated to 0 at $0.5\Mo$.
-The choice of yields for stars of masses $\Mo \lesssim 1.5$ produces about a 20\% uncertainty in the late DTD (past 3\,Gyr) of \agb\ C production from these models.
-More complete grids in mass and metallicity would be needed to more accurately compare GCE predictions between AGB evolution models.
-Furthermore, note the non-monotonic IMF-averaged yields in \nugrid\ and \aton\ particularly at low metallicities.
+The choice of yields for stars of masses $\Mo \lesssim 1.5$ produces about a 20\% uncertainty in the slope of the DTD past 3\,Gyr \dbstrike{but these old populations account for a small fraction of the total C}.
+\strike{More complete grids in mass and metallicity would be needed to more accurately compare GCE predictions between AGB evolution models.
+}
 
 The left panel of Fig.~\ref{fig:agb-ssp} shows IMF-averaged C yields for each \agb\ model as a function of metallicity.
-The \agb\ models mostly differ in their yield normalization and metallicity dependence.  
-The normalizations span a factor of \about{2}.
-For example, at $Z = 0.1\Zo$, each models predicts $Y_{\rm C}^{\rm AGB}$ to be between 0.0008 and
-0.0016.
+The IMF-averaged yields differ in normalization and metallicity dependence.  
+The normalizations span a factor of \about{2}. (e.g. between $6\times 10^{-4}$ and $12 \times 10^{-4}$ at $Z=0.33\,\Zo$).
+Both \nugrid{} and \aton{} predict non-monotonic C yields with $Z$, but it is unclear if this prediction is significant given the uncertainties associated with any one model.
 To characterize the metallicity dependence of each table, we fit the yield to a linear model in $\log Z$
@@
 \end{equation}
-Table \ref{tab:agb} contains the fit parameters $y_0$ and $\zagb$ for each AGB table\footnote{we perform a MCMC fit using standard RMS error to estimate best parameters and uncertanties.}
-The metallicity dependence of the yields span a factor of \about{3}.
-Variations in \agb\ model yields are due to different choices of reaction rates, convection treatments, and mass-loss rates \citet{ventura+15} \dbnote{better ref here, is there a good review on AGB physics uncertanties?}.
-
-The right panel of Fig.~\ref{fig:agb-ssp} shows the total production of C by \agb\ stars by a SSP as a function of age at solar metallicity. 
-As the mass range $2\,\Mo\lesssim M \lesssim 4\,\Mo$ is most important for C production, half the yield is produced before \about{1}\,Gyr, similar to Fe production by \ia. 
+Table \ref{tab:agb} contains the fit parameters $y_0$ and $\zagb$ for each AGB table.
+The values of $\zagb$ span a factor of $\sim{3}$ between models.
+These variations are due to different choices of reaction rates, convection treatments, and mass-loss rates \citep{ventura+15} \dbadd{REF}, but can be qualitatively understood by comparing the strength of third dredge up (TDU) and hot bottom burning (HBB) (see discussion below and \JJ).
+
+The right panel of Fig.~\ref{fig:agb-ssp} shows the total production of C by \agb\ stars by a single stellar population (SSP; cluster of stars born at the same time from the same material) as a function of age at solar metallicity.
+As the mass range $2\,\Mo\lesssim M \lesssim 4\,\Mo$ is predicted to be most important for C production, half the yield is produced before \about{1}\,Gyr, similar to Fe production by \ia. 
 \monash{} weight C production more heavily towards high-mass \agb\ stars, resulting in shorter delay times, whereas the \fruity\ and \aton\ models predict a slightly longer timescale of \about{1}\,Gyr.
@@
 
-In \agb\ stars, two competing processes determine the outcome of C production: {third dredge up} (TDU) and {hot bottom burning} (HBB).  
-TDU accompanies thermal pulses in \agb\ stars, where material from the CO core is mixed with the envelope, increasing surface C abundances \citep{KL14}.
-The C yields of the star are increased as this C-enhanced envelope is released to the ISM.
-HBB\ is the activation of the CNO cycle at the bottom of the convective envelope. 
-TDU increases C yields and HBB converts C into N. When both processes activate, highly efficient N production ensues (see discussion in e.g. \citealt{james+23, ventura+13}). 
+In AGB stars, {third dredge up} (TDU) and {hot bottom burning} (HBB) are two processes driving C evolution in \agb\ stars with competing effects.
+TDU accompanies thermal pulses, where material from the CO core is mixed with the envelope, increasing surface C abundances 
+later released to the ISM \citep{KL14}.  
+HBB\ is the activation of the CNO cycle at the bottom of the convective envelope \dbadd{with a net effect of ...}.
+TDU increases C yields and HBB converts C into N. When both processes are active, highly efficient N production ensues (see discussion in e.g. \citealt{james+23, ventura+13}). 
 %Because the $^{14}$N proton capture is the slowest component of the CNO cycle, the CNO cycle converts nearly all \C[12] into $^{14}$N \citep{solar-fusion}.
@@
 
-Both HBB and TDU result in mass and metallicity dependent C yields. 
-Stars less than \about{2}\,$\Mo$ do not experience TDU As a result, these stars C abundances are only affected by first dredge-up (CITE), resulting in small net C yields.
+Both HBB and TDU result in mass- and metallicity-dependent C yields. 
+Stars less than \about{2}\,$\Mo$ do not experience TDU. As a result, C yields from these stars are affected only by first dredge-up \citep[Table 1]{karakas10}, resulting in small net C yields.
 Above \about{2}\,$\Mo$, TDU becomes important, enriching the outer layers with C.
 In \agb\ stars more massive than \about{5}\,$\Mo$, efficient HBB turns most \C[12] into $^{14}$N.
-Metal poor stars dredge up more material \dbnote{for which physics, compactness, mixing efficiency( Boothroyd \& Sackmann 1988))? etc.}, resulting in elevated C production \citep[e.g.][]{ventura+13}.
-This is due to  the more compact and higher core masses in low-mass stars, causing a stronger thin-shell instability leading to stronger pulse-driven convections and dredging up more C.
-Note that HBB also increases with lower metallicity, but the effects of stronger TDU outweighs this.
-Additionally, as stars evolve through the TPAGB, they dredge up more material for the same reasons.
-The number of pulses is driven by the chosen mass loss formulation.
-
-The major uncertanties in AGB evolution are convective treatment, reaction rates, and mass loss prescriptions.
-In particular, the N14pgamma reaction rate uncertainty causes a factor of 2 difference in predicted C yields \citep{herwig+austin2004, HAL2006} \dbnote{look at present-day reaction rates here}.
-Another example is the convective prescription.
-A series of papers has compared \aton{} and \monash{}, concluding that the different convection methods (full spectrum of turbulance versus mixing length theory) and the mass loss formulation (V, Blocker) are responsable for the significant differences in C yields between the models.
-\aton{} predicts strong HBB which occurs a solar mass sooner than in \monash{}, causing much lower C yields.
-Note that most of the physics included in stellar modeling is empirically calibrated: we cannot determine mass-loss rates, mixing and extra mixing from first principles---our understanding of the essential ingredients to stellar evolution is through empirical inference.
-
-For our models to better match observations, we uniformly amplify the yield tables according to
-\begin{equation} \label{eq:alpha}
-        \Ycagb \rightarrow \alpha_{\rm agb}\ \Ycagb.
-\end{equation}
-We use the \fruity\ table, with $\alpha_{\rm agb}=\cfactor$, as the fiducial \agb\ yield.
+TDU is more efficient for more compact, massive cores.
+HBB requires a more massive AGB star to reach sufficient temperatures at the base of the convective envelope to initiate proton captures.
+Both processes are more efficient at low metallicity due to the lower opacities and, more compact internal structures, and hotter temperatures.
+These two processes drive C yields from AGB stars, but their details are ultimantly set by the uncertain choices for stellar evolution models.
+
+% compactness causes stronger thin-shell instability
+% C yields increase because TDU outweights HBB when low Z.
+
+The major uncertanties in AGB stellar evolution are convection, nuclear reaction rates, and mass loss prescriptions.
+In particular, the $^{14}{\rm N}({\rm p},\gamma)$ reaction rate uncertainty causes a factor of 2 difference in predicted C yields \citep{herwig+austin2004, HAL2006} \dbnote{look at present-day reaction rates here}.
+CITES compared the \aton{} and \monash{} models, finding that differences in yields are primarily driven by differences in mass-loss and convection prescriptions.
+\aton{} predicts strong HBB to set in $\sim{1}\,\Mo$ lower than in \monash{}, leading to much lower C yields.
+Most of the physics included in stellar modeling is empirically calibrated. Mass-loss rates, convection, and extra mixing are not sufficiently well understood to be computed from first principles.
 
@@
 	\centering
-    \caption[]{For each \agb\ yield set, the IMF-averaged \agb\ C yield at solar metallicity $y_{\rm C, 0}^{\rm agb}$ and fraction of solar C produced in the model $f_\odot^{\rm AGB}$.
+    \caption[]{For each \agb\ yield set, the IMF-averaged \agb\ C yield at solar metallicity $y_{\rm C, 0}^{\rm agb}$.
+The solar value and slope for a linear fit to the yield (least squares, excluding lowest-metallicity point for \aton).
+The fraction of solar C produced in the model $f_\odot^{\rm AGB}$.
 We also include the masses and metallicities each grid is sampled on.
+    \dbnote{MCMC gives same results as LS here, so we can simplify this discussion.}
     }
@@
 	\label{tab:agb}
-    \begin{tabular}{c  cc  c p{5cm} p{5cm}} % four columns, alignment for each
+    \begin{tabular}{c  ccc  c p{5cm} p{5cm}} % four columns, alignment for each
 		\hline 
         \agb\ table 
-                & $y_{\rm C}^{\rm agb}(\Zo)$ %& y
-                & $\zagb(\Zo)$ %& $\zeta$ 
+                & $y_{\rm C}^{\rm agb}(\Zo)\times10^4$ %& y
+                & $\bar y_{\rm C}^{\rm agb}(\Zo)\times10^4$ %& y
+                & $\zagb(\Zo)\times10^4$ %& $\zeta$ 
                 &  $f_\odot^{\rm agb}$
-                & masses ($\Mo$) & metallicites ($Z$)\\
+                & masses ($\Mo$) & metallicities ($Z$)\\
         \hline
         \fruity 
-                &  $3.82^{+0.3}_{-0.3}$ %& 4.0
-                & $-3.5^{+0.3}_{-0.3}$ %& -3.5
+                & 3.229
+                &  $3.8\pm0.3$
+                & $-3.5\pm0.3$
                 & 0.138
@@
         \aton 
-                & $1.85^{+1.0}_{-1.1}$ %& 2.6 
-                & $-9.4^{+1.5}_{-1.7}$ %& -4.9
+                & 0.2851
+                & $1.4\pm1.8$
+                & $-10. \pm 3$
                 & 0.067
@@
         \monash 
-                & $2.8^{+0.4}_{-0.5}$ %& 3.5
-                & $-10.1^{+0.8}_{-0.9}$% & -10
+                &  3.444
+                & $2.8 \pm 0.5$
+                & $-11.0\pm 1.0$
                 & 0.102
@@
         \nugrid 
-                & $5.9^{+1.2}_{-1.1}$ %& 8
-                & $-5.7^{+1.0}_{-1.0}$ %& -3.
+                & 10.95
+                & $8.3\pm 1.9$
+                & $-4.6\pm1.7$
                 & 0.214
@@
     \dbnote{y label: integrated CCSNe carbon yield}
+    \dbnote{might be interesting to plot every CCSNe yield used in this paper in light grey to show strength of our constraint}
         C yields from high-mass stars.
@@
 
-\subsection{Equilibrium Abundances}\label{sec:equilibrium}
-
-Building on \citepos{WAF17} analytic models of chemical equilibrium,
-\citet{james+23} demonstrate that the relationship between N and O can be
-explained by the metallicity dependence of their relative yields (see discussion
-in their section 4.6).
-We find similar results extending these arguments to C and Mg.
-The equilibrium C/Mg abundance ratio is 
-\begin{equation}\label{eq:equilibrium_yields}
-    {\rm [C/Mg]_{eq}} = \log \left(\frac{\Ycc + \Ycagb }{y_{\rm Mg}}\right) - \log \left(\frac{Z_{\rm C,\,\odot}}{Z_{\rm Mg,\,\odot}}\right)
-\end{equation}
-
-We isolate the low-$\alpha$ sequence of subgiants to represent the equilibrium abundance trends, defined by [Mg/Fe] - [Fe/H] as in \citet{jack} (a +0.02 correction from \citet{weinberg+19}).
-Low-$\alpha$ stars are defined as stars with
-\begin{equation}\label{eq:high_alpha}
-\begin{cases}
-\text{[Mg/Fe]} <0.16-0.13\,\text{[Fe/H]}, & \text{[Fe/H]}<0\\
-\text{[Mg/Fe]} <0.16, & \text{[Fe/H]}>0. \\
-\end{cases}
-\end{equation}
-with high-$\alpha$ stars being otherwise from \citet{weinberg+19, weinberg+22, emily+19, emily+21}. \dbnote{I want to move this paragraph to \S 2.}
-
+\subsection{Adpoted Fiducial Yields}
 We propose the following functional form for total C yields near solar metallicities:
@@
 For the quadratic form, we hold the yields constant past the vertex (at {\color{red} [M/H] = ?}) to avoid a premature upturn in \caah.
-We discuss the choice of these functional forms more in appenix~\dbadd{X}.
-In Fig.~\ref{fig:analytic}, we show the inferred C/Mg yield ratio against metallicity.
+We discuss the choice of these functional forms more in appendix~\dbadd{X}.
 
@@
 \end{subequations}
-At the boundaries, stars at $R=0$ move to $R=0$ if $R_{\rm end}<0$ and stars will move to $R=20$\,kpc if $R_{\rm end} > 20$\,kpc. 
+If a star would cross a boundary, then the star is reflected back.
 The star moves from its birth radius to its final radius via
@@
 
-Galactocentric radii are taken from astroNN {\color{red} citation}. \dbadd{Using Gaia parallaxes does not affect our conclusions ?}
+Galactocentric radii are taken from astroNN {\color{red} citation}. \dbadd{Using Gaia parallaxes does not affect our conclusions.}
 
@@
 
+\subsection{Equilibrium Framework}\label{sec:equilibrium}
+
+Based on the \citepos{WAF17} analytic models of chemical equilibrium for constant star formation, the equilibrium abundance ratio between two elements depends only on the relative yields.
+For C/Mg, we have \dbstrike{ ,
+{james+23} demonstrate that the relationship between N and O can be
+explained by the metallicity dependence of their relative yields (see discussion
+in their section 4.6).
+We find similar results extending these arguments to C and Mg.
+The equilibrium C/Mg abundance ratio is 
+}
+\begin{equation}\label{eq:equilibrium_yields}
+    {\rm [C/Mg]_{eq}} \equiv \log \left(\frac{\Ycc + \Ycagb }{y_{\rm Mg}}\right) - \log \left(\frac{Z_{\rm C,\,\odot}}{Z_{\rm Mg,\,\odot}}\right)
+\end{equation}
+\dbnote{
+where  the correction for a non-constant SFH is 
+\begin{equation}
+    \noneqagb \equiv \frac{\dot{M}_{\rm C}^{\rm AGB}}{\Ycagb\,\dot{M}_{\star}}
+\end{equation}
+}
+
 \subsection{Yield Variations}\label{sec:results_highmass}
@@
     \includegraphics{figures/subgiants_equilibrium_reproduced.pdf}
-    \caption{Similar to Fig.~\ref{fig:subgiants} except for the stars of our fiducial model. 
+    \caption{
+    Similar to Fig.~\ref{fig:subgiants} except for the stars of our fiducial model. 
     The solid, black lines show the equilibrium abundance track.
@@
 The median trend of low-$\alpha$ stars is an excellent approximation for the equilibrium abundance of C.
+    \dbnote{The more I look at this figure, maybe we just add green lines to Fig. 5 and skip this one}
     \dbnote{we add synthetic scatter found by fitting the metallicity-dependent reported errors with a linear fit in APOGEE and adding gaussian noise.}
     \dbnote{is there too much going on here?}
+    \dbnote{would it make sense to maybe place this fig close to Fig.~1 since they are very similar so it is easier to compare? Not sure how to make continuity work then..}
     \label{fig:equilibrium_validity}
@@
 \caption[]{
+\dbnote{out of date}
+    \dbnote{does it make sense to show SEM error bars instead of percentiles since we are focused on the median trend, not the spread?.}
     Stellar abundance trend predictions of our models .
@@
 \begin{figure*}
+\includegraphics{sims_agb.pdf}
+
+\caption[]{
+    Similar to Fig.~\ref{fig:zeta_f} except showing the mean tracks for different (unscaled) AGB yield tables with best-fit CCSNe parameters.
+Variations in the \caafe\ plane are due to the different total AGB C yield and variations in the mass-dependence of each yield table.
+}
+\label{fig:agb_predictions}
+\end{figure*}
+
+\begin{figure*}
 \includegraphics{figures/zeta_f_mass_sfh.pdf}
@@
 
-    \dbnote{I looked into the halfed yields model.
+    \dbnote{the left panel is the +- 3 sigma range of models from the MCMC analysis.
+I suspect the errors are very underestimated and I am not sure how to approach it, but the plot might make more sense if the model has the right curvature (like mass factor 0.7).
+There are 100+ observations per bin so maybe we need to account for apogee systematics as well??}
+
+    \dbnote{I looked into the halved yields model.
 Since in this paper, we assume $y_o/Z_o \sim 1$, it is essentially impossible to reach solar Z when halfing the yields.
@@
 
-    \dbnote{middle pannel is reproduced in analytic multizone models. low-priority but possibly interesting is if the analytic DTD or singlezone models reflect this trend as well.}
+    \dbnote{the mass shifts change the net C production, so I may change the $\alpha$ values for these models so they are easier to compare here}
 }
@@
 
-where $\tau_1=0.4\,$Gyr, $\tau_2$ is 1/2 of the value from Sanchez, $A_{2,1}=0.5$, $t_1=4.1$, and the star formation also abruptly transitions from $\nu=2$ to $\nu=1$ at $t=t_1$.
+where $\tau_1=0.4\,$Gyr, $\tau_2$/G is 1/2 of the value from Sanchez, $A_{2,1}=0.5$, $t_1=4.1$, and the star formation also abruptly transitions from $\nu=2$/Gyr to $\nu=1$/Gyr at $t=t_1$.
 
@@
 Both classes of models are able to reproduce many details of the disk abundance structure due to the strong degeneracy between the normalizations of elemental yields and mass-loading (see discussion in, e.g.
-\citealt{sandford+24} and appendix B of \citealt{james+23}).
+\citealt{sandford+24} and Appendix B of \citealt{james+23}).
 Our parameterization of $\eta$ illustrates this (see Equation~\ref{eq:mass_loading}) -- choosing a lower value of $y_{\alpha}$ will similarly result in lower values of $\eta$ while maintaining the same metallicity gradient.
@@
 \dbnote{Other things to discuss possibly ? :
- Initial mass function (and possible metallicity dependence)? Metallicity dependent Oxygen/Magnesium and Iron yields? Gas phase migration / ISM cooling?  MLR
+ Initial mass function (and possible metallicity dependence)? Metallicity-Dependent Oxygen/Magnesium and Iron yields? Gas phase migration / ISM cooling?  MLR
  }
@@
 \includegraphics[]{figures/summary.pdf}
-\caption[]{\dbnote{warning: caption in progress} 
+\caption[]{
 Gas-phase C abundances. 
@@
 Points represent measurements in 
-    HII regions \citep[orange circles;][]{skillman+20, esteban+02, esteban+09, esteban+14, esteban+19}
-    damped Lyman-alpha (DLA) systems \citep[rust triangles;][]{ellison+10, srianand+10, dutta+14, DZ+03, pettini+08, morrison+16,cooke+17}, ({\color{red} citations})
-    dwarf galaxies \citep[green diamonds;][]{berg+19},
+    MW HII regions \citep[orange circles][]{mendez-delgado+22}
+    extragalactic RL HII regions \citep[green circles;][]{peimbert+05, skillman+20, toribio-san-cipriano+16, toribio-san-cipriano+17, esteban+14, esteban+09}
+    extragalactic CEL HII regions \citep[green diamonds;][]{garnett+95, senchyna+17, izotov+thuan99, garnett+99, berg+16, berg+19, pena-guerrero+17}
+    damped Lyman-alpha (DLA) systems \citep[rust triangles;][]{omera+01, cooke+14, welsh+22, ellison+10, welsh+20, cooke+18, riemer-sorensen+17, DZ+03, cooke+17, cooke+11, dutta+14, morrison+16, srianand+10, pettini+08, kislitsyn+24, cooke+15},
     Milky Way stars \citep[yellow stars;][]{amarsi+19},
-    and high redshift galaxies \citep[pink squares;][]{arellano-cordova+2022} ({\color{red} citations}).
+    and high redshift galaxies \citep[pink squares, CEL lines;][]{steidel+16, stark+14, matthee+21, mainali+20, jones+23, amorin+17, iani+23, james+14, erb+10, bayliss+14, berg+18, christensen+12, arellano-cordova+2022}.
 
@@
 
-\section{Conclusions}\label{sec:conclusions}
+\section{Discussion \& Conclusions}\label{sec:conclusions}
 
@@
 
-\dbnote{do I need acknowledgements for appendix spectro-surveys?}
+\dbnote{do I need acknowledgments for appendix spectro-surveys?}
 
@@
 
+\section{Monte-Carlo Markov Chain inference}
+
+As a way to quickly explore which combinations of yields agree with \caah, and \caafe, we run Monte Carloe Marcov chains using the following approximation framework.
+We intend these results to be more illustrative and first order, as the number of approximations and systematics in the analysis is substantial.
+
+\subsection{Methods}
+
+As a first step, we hold all GCE parameters except for the C yield constant for each MCMC model.
+We additionally assume that the metallicity is that of the fiducial yield set, to avoid second-order effects from metallicity-dependent yields.
+We then seperate each process into four different components
+\begin{enumerate}
+    \item $\alpha$ AGB yield (scale).
+    \item $\zetao$ Constant CCSNe yield
+    \item $\zetai$ Linear CCSNe yield. Held constant past [M/H] = -2
+    \item $\zetaii$ quadratic CCSNe yield. Also held constant ...
+\end{enumerate}
+Since each process is tracked separately, we can then predict the total C abundance at any point in the model by adding together the C abundances from each process
+\begin{equation}
+    Z_{\rm C} = \sum_{i} \alpha_i Z_{\rm C}^{i}. 
+\end{equation}
+Since the models do also have statistical uncertainties, the variance of the mean is given by
+\begin{equation}
+    V(\bar Z_{\rm C}) = \sum_{i} \alpha_i^2 V(\bar Z_{\rm C}^{i})
+\end{equation}
+
+To formulate a likelihood, we assume that model agreement is characterized primarily by the \textit{mean trends} in [C/Mg] with [Mg/Fe] and [Mg/H].
+For each bin, we calculate the mean $Z_{\rm C}$ for each model component.
+Then these means are added together and the resulting $Z_{rm C}$ is compared to the $Z_{\rm C}$ of the subgiants in the bin, using a likelihood
+\begin{equation} \label{eq:mcmc_likelihood}
+    \log {\cal L} \propto \chi^2 = \sum_b \frac{(\bar Z_{b, \rm C,\ model} - \bar Z_{b, \rm C,\ obs})^2} {s_{b, \rm obs}^2 + {\rm Var}(\bar Z_{b, \rm C,\ model})}
+\end{equation}
+
+We adopt the following priors
+\begin{subequations}
+\begin{align}
+    \alpha &\sim N(1, 1) \\
+    \zeta^{(0)} &\sim N(2, 1) \\
+    \zeta^{(1)} &\sim N(0, 1) \\
+    \zeta^{(2)} &\sim N(0, 4) \\
+\end{align}
+\end{subequations}
+
+We then run a Monte-Carlo Markov Chain (MCMC) using Turing.jl with a No-U-turn sampler (acceptance rate of 0.65), combining 8 walkers with 10,000 steps each.
+
+(in progress) To ensure this method is relatively robust, we will perform similar MCMC simulations varying the bin size/method, the MCMC sampler (HMC, ensemble stretch moves from pyemcee, MH, MH random walk), the likelihood (including median \& distribution based), and explore 2D bins.
+In each case, the derived parameters are within their uncertainties (excluding the KS test model).
+Finally, we additionally do run multizone simulations for the fiducial model varying each parameter by 5-sigma (from the distribution) and ensuring that the resulting trend is within the uncertainty of this approximation.
+
+(in progress) We check that removing the likelihood in \caafe{} causes...
+Additionally, we try and fit models without AGB components, without quadratic components, etc., finding that each model fits the data poorer than the above formulation.
+
+\subsection{Results}
+
+Fig.~\ref{fig:mcmc} displays the distribution and correlation of each parameter in the fiducial MCMC model.
+Each parameter is relatively well-constrained.
+The most prominant correlation, between $\zetao$ and $\alpha$, represents that the total solar-yield is well constrained.
+The other main correlation, between $\zetai$ and $\zetaii$, arises from the shape of the \caah\ trend.
+If the quadratic component is decreased, than the slope  (past M/H $\sim 0.1$) increases, so the linear component must decrease in order to maintain agreememnt with the data.
+
+Fig.~\ref{fig:mcmc_caahfe} shows the resulting mean trends in \caah\ and \caafe\ for the median best MCMC parameters for each AGB mode.
+Regardless of the AGB model, there is a reasonable choice of \cc\ yields which can precisely match the \caah\ trend.
+On the other hand, the agreement with the \caafe\ trend tends to be more poor for each AGB model, where they all predict a later decrease in \caafe\ than is observed.
+This is improved by yield models with a higher \agb\ enrichment from low mass stars ($\lesssim 2.5$).
+
+Fig.~\ref{fig:mcmc_ytot} shows the AGB fraction at solar metallicity and the total C yield with metallicity for each MCMC run. 
+In essentially each case, the majority of samples have a AGB fraction between 0.15 and 0.4.
+
+\begin{figure}
+\centering
+\includegraphics{figures/mcmc_corner.pdf}
+\caption[]{
+MCMC samples. Could actually just try plotting the distributions from each model here...
+}
+
+\label{fig:mcmc}
+\end{figure}
+
+\begin{figure*}
+    \centering
+    \includegraphics[]{figures/mcmc_caahfe_predicted.pdf}
+    \caption{Predicted mean tracks for the mean models.
+\dbnote{This figure is almost identical to Figure 8, so may need to think about if we need both....especially since the MCMC now informs the choice of parameters in Fig.
+8.}}
+    \label{fig:mcmc_caahfe}
+\end{figure*}
+
+\begin{figure*}
+    \centering
+    \includegraphics[]{figures/mcmc_fagb.pdf}
+    \includegraphics[]{figures/mcmc_y_tot.pdf}
+    \caption{Caption}
+    \label{fig:mcmc_ytot}
+\end{figure*}
+
 \section{Model Parameters}
+
+\begin{table*}
+    \caption{
+    Best-fit parameters from MCMC analysis for various models discussed.
+    \dbnote{Not sure if we should use analytic, nugrid, shifted fruity or normal fruity yields as fiducial here.}}
+    \begin{tabular}{l l l l l l l l l l} 
+    \hline
+    model            & $\chi2$  & $\log p$ & alpha & zeta0 & zeta1 & zeta2 & fagba & ytota & zeta1a\\
+\hline
+analytic         &      5.0 &     0.94 & $0.38^{+0.02}_{-0.02}$  &  $2.41^{+0.02}_{-0.02}$  &  $1.51^{+0.04}_{-0.04}$  &  $2.24^{+0.13}_{-0.13}$  &  $0.14^{+0.01}_{-0.01}$  &  $4.28^{+0.01}_{-0.01}$  &  $1.73^{+0.07}_{-0.07}$\\
+lateburst        &      8.7 &   -26.31 & $0.48^{+0.03}_{-0.03}$  &  $2.28^{+0.03}_{-0.03}$  &  $1.90^{+0.09}_{-0.09}$  &  $2.95^{+0.22}_{-0.21}$  &  $0.17^{+0.01}_{-0.01}$  &  $4.23^{+0.01}_{-0.01}$  &  $2.18^{+0.13}_{-0.13}$\\
+twoinfall        &      7.2 &    -5.68 & $0.55^{+0.05}_{-0.04}$  &  $2.36^{+0.04}_{-0.04}$  &  $2.12^{+0.11}_{-0.10}$  &  $1.96^{+0.20}_{-0.19}$  &  $0.19^{+0.02}_{-0.01}$  &  $4.48^{+0.02}_{-0.02}$  &  $2.41^{+0.16}_{-0.15}$\\
+eta2             &      6.2 &    -1.85 & $0.55^{+0.03}_{-0.03}$  &  $2.19^{+0.03}_{-0.03}$  &  $1.39^{+0.04}_{-0.04}$  &  $2.81^{+0.15}_{-0.15}$  &  $0.20^{+0.01}_{-0.01}$  &  $4.20^{+0.01}_{-0.01}$  &  $1.29^{+0.05}_{-0.05}$\\
+fruity           &      6.7 &    -8.99 & $2.05^{+0.13}_{-0.13}$  &  $2.00^{+0.05}_{-0.05}$  &  $2.27^{+0.07}_{-0.07}$  &  $2.54^{+0.14}_{-0.14}$  &  $0.28^{+0.02}_{-0.02}$  &  $4.26^{+0.01}_{-0.01}$  &  $2.38^{+0.07}_{-0.07}$\\
+fruitym0.7      &      5.6 &    -0.62 & $0.99^{+0.06}_{-0.06}$  &  $2.42^{+0.02}_{-0.02}$  &  $1.63^{+0.04}_{-0.05}$  &  $2.38^{+0.14}_{-0.14}$  &  $0.15^{+0.01}_{-0.01}$  &  $4.36^{+0.01}_{-0.01}$  &  $2.03^{+0.07}_{-0.07}$\\
+aton             &      9.1 &   -19.66 & $1.78^{+0.12}_{-0.12}$  &  $2.49^{+0.02}_{-0.02}$  &  $3.60^{+0.16}_{-0.15}$  &  $2.03^{+0.14}_{-0.15}$  &  $0.09^{+0.01}_{-0.01}$  &  $4.21^{+0.01}_{-0.01}$  &  $2.78^{+0.08}_{-0.08}$\\
+monash           &     11.1 &   -23.94 & $2.92^{+0.23}_{-0.22}$  &  $1.56^{+0.09}_{-0.10}$  &  $4.74^{+0.26}_{-0.25}$  &  $4.31^{+0.26}_{-0.25}$  &  $0.34^{+0.03}_{-0.03}$  &  $3.65^{+0.05}_{-0.05}$  &  $2.34^{+0.10}_{-0.10}$\\
+nugrid           &     10.3 &   -14.80 & $0.93^{+0.05}_{-0.05}$  &  $1.71^{+0.06}_{-0.06}$  &  $1.26^{+0.04}_{-0.04}$  &  $2.78^{+0.14}_{-0.14}$  &  $0.31^{+0.02}_{-0.02}$  &  $3.80^{+0.03}_{-0.03}$  &  $1.28^{+0.08}_{-0.08}$\\
+v21              &     20.0 &  -205.34 & $0.68^{+0.03}_{-0.03}$  &  $3.45^{+0.03}_{-0.03}$  &  $1.84^{+0.10}_{-0.10}$  &  $1.71^{+0.24}_{-0.25}$  &  $0.16^{+0.01}_{-0.01}$  &  $6.33^{+0.02}_{-0.02}$  &  $1.78^{+0.15}_{-0.16}$\\
+gso              &      3.5 &   -14.96 & $0.95^{+0.51}_{-0.49}$  &  $3.26^{+0.45}_{-0.46}$  &  $-0.66^{+0.90}_{-0.91}$  &  $-1.15^{+2.65}_{-2.70}$  &  $0.23^{+0.12}_{-0.11}$  &  $6.47^{+0.25}_{-0.25}$  &  $-2.46^{+1.67}_{-1.71}$\\
+galah            &     12.3 &   -85.65 & $0.48^{+0.02}_{-0.02}$  &  $2.80^{+0.02}_{-0.02}$  &  $0.90^{+0.05}_{-0.05}$  &  $2.13^{+0.13}_{-0.13}$  &  $0.15^{+0.01}_{-0.01}$  &  $5.03^{+0.01}_{-0.01}$  &  $0.65^{+0.07}_{-0.07}$\\
+
+\hline
+total & &   &  $0.65^{+1.25}_{-0.19}$  &  $2.36^{+0.45}_{-0.43}$  &  $1.63^{+0.75}_{-0.42}$  &  $2.29^{+0.62}_{-0.43}$  &  $0.19^{+0.14}_{-0.05}$  &  $4.26^{+2.07}_{-0.07}$  &  $1.68^{+0.74}_{-1.11}$\\
+\hline
+    \end{tabular}
+
+\end{table*}
 
@@
 
-	\begin{tabular}{l l l l l}
+	\begin{tabular}{l l l l l l l l l l}
 		\hline
-            name & $Y_{\rm C}^{\rm AGB}$ & $y_{\rm C}^{\rm CC}$ & additional parameters \& notes \\
+            name & $\alpha_{\rm C}^{\rm AGB}$ & $Y_{\rm C}^{\rm AGB}$ & $\zeta_0$ & $\zeta_1$ & $\zeta_2$ \\ 
             \hline
-            fiducial & 1.45 x fruity & $0.002203 + 0.00196x + Ax^2$ & default model. See Section~X.X \\
-            FRUITY & 1 x fruity & $0.0024 + 0.002x + Ax^2$ \\
-            Monash & 1 x monash & $0.0024 + 0.0025x + Ax^2$ \\
-            ATON & 1 x aton & $0.00255 + 0.0025x + 0.0021 x^2$& \\
-            NuGRID & 1 x nugrid(M, Z) & $0.0024 + 0.00136x + 0.0016x^2$& \\
+            fiducial & 2.04 & fruity & 2.01 & 2.27 & 2.53 \\
+            FRUITY & 1 & fruity & 2.39 & 1.86 & 2.37 \\
+            Monash & 1 & monash & 2.36 & 2.60 & 2.95 \\
+            ATON & 1 & aton & 2.61 & 2.67 & 2.12 \\
+            NuGRID & 1 & nugrid & 1.78 & 1.62 & 3.01 \\
             f=0.0 &  \\
-            f=0.5 & 3.623 x fruity & $0.00138 + \zeta x + Ax^2$ & \\
-            steep & 1.45xfruity & $zeta=$ \\
-            shallow & 1.45xfruity & $zeta=0$ \\
+            f=0.5 & 3.623 & fruity  \\
+            steep & 2.04 & fruity \\
+            shallow & 2.04 & fruity \\
             fz=0 \\
             fz=0.5 \\
-            m0.5 & 1.44 fruity(m/0.5, Z)  & 0.00225 " & \\
-            m0.8 & 1.44 fruity(m/0.8, Z) & " \\
-            m1.5 & 1.44 fruity(m/1.5, Z) & 0.002194 " \\
-            m2 & 1.44 fruity(m/2, Z) & 0.2587 " \\
-            lateburst & & & SFH$\sim {\rm insideout} (1+N(t, 13.2, 1))$\\
-            twoinfall & & & SFH$\sim$ ... , ... \\
-            2y & & & all yields doubled;  $\eta$ adjusted to Eq.~N \\
-            lowz correction& other equation & --- & --- \\
+            m0.5 & 2.04 & fruity(m/0.5)  & 2.44 & 1.42 & 2.11 \\
+            m0.7 & 2.04 & fruity(m/0.7) & 2.03 & 1.92 & 3.03 \\
+            m1.5 & 2.04 & fruity(m/1.5) & 2.08 & 1.88 & 1.87 \\
 		\hline
@@
 
-\begin{figure*}
-\includegraphics{sims_agb.pdf}
-
-\caption[]{
-    Similar to Fig.~\ref{fig:zeta_f}. 
-}
-\label{fig:agb_predictions}
-\end{figure*}
-
-The best fits assuming perfect equilibrium.
-\begin{subequations}
-    \begin{align}
-        \frac{\Yct(Z)}{y_{\rm Mg}} &\approx 4.20 + 1.64 \log (Z/\Zo)\\
-        \frac{\Yct(Z)}{y_{\rm Mg}} &\approx 4.12 + 1.21 \log(Z/\Zo) + 3.07 \log(Z/\Zo)^2
-    \end{align}
-\end{subequations}
-
-\begin{figure}
-    \centering
-    \includegraphics{figures/equilibrium_yields.pdf}
-    \caption[]{Inferred total C yields as a function of metallicity.
-We assume chemical equilibrium (orange curve, see discussion in section \ref{sec:equilibrium}).
-Blue points are the median value of $\Ycc$ for each (number) bin in [Mg/H] with uncertainties based on the 16--84 percentile range.
-    \note{I'd rephrase this caption slightly to be a little more specific about what the lines are representing.
-Something to the effect of "The orange solid and green dashed curves show fits to the blue points under the assumption of a chemical equilibrium trend (see discussion in section \ref{sec:equilibrium}).
-    }
-
-    \dbnote{Considering cutting this figure (requires about 0.1 dex adjustment and compare to Fig.~\ref{fig:equilibrium_validity})}
-    }
-    \label{fig:analytic}
-\end{figure}
+Low-$\alpha$ stars are defined to have 
+\begin{equation}\label{eq:high_alpha}
+\begin{cases}
+\text{[Mg/Fe]} <0.16-0.13\,\text{[Fe/H]}, & \text{[Fe/H]}<0\\
+\text{[Mg/Fe]} <0.16, & \text{[Fe/H]}>0. \\
+\end{cases}
+\end{equation}
 

### 2025-01-16 carbon_paper/tex/template/mnras_template.tex
updated draft with mcmc models

--- 2023-03-04 carbon_paper/main.tex
@@
 %%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%
-\defcitealias{2011ApJS..197...17C}{C11}
-\defcitealias{2015ApJS..219...40C}{C15}
-
-\newcommand{\cristallo}{\citetalias{2011ApJS..197...17C}+\citetalias{2015ApJS..219...40C}}
 
@@
 % overwriting existing commands. Example:
-% \newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared
-\newcommand{\VICE}{\texttt{VICE}}
+%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared
 
@@
 % Keep the title short and informative.
-\title[Constraining carbon yields]{The galactic chemical evolution of carbon: Constraining stellar nucleosynthesis}
+\title[Short title, max. 45 characters]{MNRAS \LaTeXe\ template -- title goes here}
 
@@
 % If you need two or more lines of authors, add an extra line using \newauthor
-\author[D. A. Boyea et al.]{
-Daniel A. Boyea,$^{1}$\
-et al.
-% James W. Johnson,$^{1}$
-% David Weinberg
-% Jack Roberts
-% Jennifer Johnson
-% ?
+\author[K. T. Smith et al.]{
+Keith T. Smith,$^{1}$\thanks{E-mail: mn@ras.org.uk (KTS)}
+A. N. Other,$^{2}$
+Third Author$^{2,3}$
+and Fourth Author$^{3}$
 \\
 % List of institutions
-$^{1}$Department of Astronomy, The Ohio State University\\
+$^{1}$Royal Astronomical Society, Burlington House, Piccadilly, London W1J 0BQ, UK\\
 $^{2}$Department, Institution, Street Address, City Postal Code, Country\\
@@
 % Enter the current year, for the copyright statements etc.
-\pubyear{2023}
+\pubyear{2015}
 
@@
 \begin{abstract}
-Stellar evolution models provide highly uncertain predictions for elemental yields due to our limited understanding of stellar physics.
-In this paper, we aim to estimate the nucleosynthetic yields of carbon using galactic chemical evolution models.
-
-We find that the AGB stars make up a fraction $0.20_{-20}^{+80}$ of total carbon production at late times. 
+This is a simple template for authors to write new MNRAS papers.
+The abstract should briefly describe the aims, methods, and main results of the paper.
+It should be a single paragraph not more than 250 words (200 words for Letters).
+No references should appear in the abstract.
 \end{abstract}
@@
 \begin{keywords}
-Need to find some...
+keyword1 -- keyword2 -- keyword3
 \end{keywords}
@@
 
-A fundamental question of Galactic Chemical Evolution (GCE) is understanding the physical processes which make each element.
-Stellar evolution models can be used to predict how much of each element stars with a variety of physical properties produce.
-However, these models are rife with uncertainties, limited by our understanding of critical physical processes such as nuclear reaction rates, convection, opacity, and mass loss (CITE, e.g.
-stellar physics reviews).
+This is a simple template for authors to write new MNRAS papers.
+See \texttt{mnras\_sample.tex} for a more complex example, and \texttt{mnras\_guide.tex}
+for a full user guide.
 
-Carbon and nitrogen are the only lighter elements produced significantly by low mass stars, so*****, reasons WHY this study.
+All papers should start with an Introduction section, which sets the work
+in context, cites relevant earlier studies in the field by \citet{Fournier1901},
+and describes the problem the authors aim to solve \citep[e.g.][]{vanDijk1902}.
+Multiple citations can be joined in a simple way like \citet{deLaguarde1903, delaGuarde1904}.
 
-Asymptotic Giant Branch (AGB) stars are known to be importaint (cite) from stellar model predictions, previous GCE, and evidence from abundance patterns. (are there detections in PN?)
+\section{Methods, Observations, Simulations etc.}
 
-CCSNe are also important (.... SN reminant measurments)
+Normally the next section describes the techniques the authors used.
+It is frequently split into subsections, such as Section~\ref{sec:maths} below.
 
-We also know that there is evidence for non-monatonic carbon yield patterns. 
-pattern where carbon is more readily produced by both high metallicity and very low metallicity stars (CEMPS, early GCE results), but our picture.
+\subsection{Maths}
+\label{sec:maths} % used for referring to this section from elsewhere
 
-Additionally, stellar models are computationally expensive, even in one dimension, so while there are grids of predictions, these are not always fine enough to make accurate chemical evolution models.
-
-Previous models (CIte). We use \VICE (CITE) to create multi-zone models of GCE enabling us to account for the effects of migration on our predicted yields.
-
-\citet{2018MNRAS.476.3432P}
-\citep{2017ApJ...837..183W}
-\citep{2021MNRAS.508.4484J}
-\citep{2021arXiv210603912V}
-
-\citep[e.g.][]{2022arXiv220204666J}
-
-Carbon abundances are strongly affected by CNO cycle processing in stars.
-The CNO cycle is one of two series of nuclear reactions( $^{12}$C(p, $\gamma$)$^{13}$N($\beta^+ \nu_e$)$^{14}$N(p, $\gamma$)$^{15}$O($\beta^+\nu_e$)$^{15}$N(p,$\alpha$)$^{12}$C
-
-Because the $^{14}$N(p, $\alpha$) proton capture is the slowest component of the CNO cycle ****, the CNO cycle, to first order, converts all $^{12}$C into $^{14}N$.
-
-One challenge of measuring abundances of carbon in star is that when a star becomes a RGB star, material from the CNO-processed core.
-Since this core-processed material is now carbon depleted and nitrogen enhanced, measurments of this star's atmosphere will no longer reflect the birth abundances of the star.
-
-In Figure \ref{fig:sum} we present a sample of APOGEE subgiants.
-These subgiants were chosen based on their location in the HR diagram based on criteria in \citet{jack_subgiant} replicated in Appendix \ref{sec:jack}.
-Because subgiants have not undergone FDU, their surface abundances are an accurate reflection of the birth abundances (CITATION).
+Simple mathematics can be inserted into the flow of the text e.g. $2\times3=6$
+or $v=220$\,km\,s$^{-1}$, but more complicated expressions should be entered
+as a numbered equation:
 
 \begin{equation}
-\begin{cases}
-\text{[Mg/Fe]} >0.12-0.13\text{[Fe/H]}, & \text{[Fe/H]}<0\\
-\text{[Mg/Fe]} >0.12, & \text{[Fe/H]}>0\\
-\end{cases}
+    x=\frac{-b\pm\sqrt{b^2-4ac}}{2a}.
+	\label{eq:quadratic}
 \end{equation}
 
-\begin{figure*}
-    \centering
-    \includegraphics[]{figures/subgiants_mgh.pdf}
-    \includegraphics[]{figures/subgiants_mgfe.pdf}
-    \caption{Chemical abundance relationships of our sample of APOGEE subgiants (see Jack et al. 2023). Left panel shows }
-    \label{fig:sum}
-\end{figure*}
-\section{Nucleosynthesis}
+Refer back to them as e.g. equation~(\ref{eq:quadratic}).
 
-Galactic chemical evolution are fundamentally intertwined with our understanding of stellar nucleosynthesis.
-In this paper, we are concerned with three major nucleosynthetic pathways: AGB stars, CCSNe, and Supernovae type Ia.
-While only AGB stars and CCSNe are producers of carbon, SNeIa Fe can be used to compare with the AGB delayed carbon component.
+\subsection{Figures and tables}
 
-\VICE allows us to explore the nucleosynthesis of various models, as it includes AGB tables for C11, et.c
+Figures and tables should be placed at logical positions in the text. Don't
+worry about the exact layout, which will be handled by the publishers.
 
-We discuss carbon nucleosythesis in more detail in the next two sections.
-We assume that the only dominant sources of carbon are from AGB stars and CCSNe/massive star winds.
-***JUSTIFY***.
-Below  is a brief overview of our  nucleosythetic assumptions of other elements.
+Figures are referred to as e.g. Fig.~\ref{fig:example_figure}, and tables as
+e.g. Table~\ref{tab:example_table}.
 
-Let $y_{\rm X}^{\rm proc}(M, Z)$ be the fractional yield of element X by a process proc for stars of a mass $M$ (in solar masses) and at metallicity $Z$ defined as: 
-\begin{equation}
-    y_{\rm X} = \frac{M_{\rm X,\ ej} - M_{\rm X,\ birth}}{M}   
-\end{equation}
+% Example figure
+\begin{figure}
+	% To include a figure from a file named example.*
+	% Allowable file formats are eps or ps if compiling using latex
+	% or pdf, png, jpg if compiling using pdflatex
+	\includegraphics[width=\columnwidth]{example}
+    \caption{This is an example figure. Captions appear below each figure.
+	Give enough detail for the reader to understand what they're looking at,
+	but leave detailed discussion to the main body of the text.}
+    \label{fig:example_figure}
+\end{figure}
 
-Where $M_{\rm X,\ ej}$ and $M_{\rm X,\ birth}$ are the mass of element X ejected and initially present in the star. 
-We define the IMF-integrated yield of X with: 
-\begin{equation}
-Y_{\rm X}^{\rm proc}(Z) = \int_{M_{\rm min}}^{M_{\rm max}} y_{\rm X}^{\rm proc}(M, Z)\ \Phi(M)  \ dM
-\end{equation}
-Where $\Phi(M) = \frac{dN}{dM}/ \int_{M_{\rm min}}^{M_{\rm max}} \frac{dN}{dM}\ dM$ is the normalized IMF, $M_{\rm min}$ and $M_{\rm max}$ are the minimum and maximum mass of stars, which we take to be $0.08 M_{\sun}$ and $100 M_{\sun}$ respectively; and $\frac{dN}{dM}$ is the initial mass function, the frequency of stars born between $M$ and $M+dM$.
-
-There are two $\alpha$-elements we care about: Mg and O.
-Stellar observations of magnesium are more reliable but oxygen abundances are easier to measure in HII regions.
-We assume that both Mg and O are produced entirely in CCSNe with constant, metallicity-independent yields.
-Thus $\text{[Mg/H]} = \text{[O/H]} = [\alpha/\text{H}]$ in our models
-
-\begin{itemize}
-    \item observational validation
-\end{itemize}
-For carbon, the dominant producer is from massive stars which eject carbon fused in their cores during CCSNe.
-
-Taken from J21 and J22, we make the following yield assumptions:
-\begin{itemize}
-    \item $Y_\text{O}^\text{CC} = 0.015$
-    \item $Y_\text{O}^\text{Ia} = 0$
-    \item $Y_\text{Fe}^\text{Ia} = 0.00214?$
-    \item $Y_\text{Fe}^\text{CC} = 0.0012$
-    \item $Y_\text{N}^\text{CC} = 0.00036$
-    \item $y_\text{N}^\text{AGB}(M, Z) = 9\times 10^{-4} M \left(\frac{Z}{Z_\odot}\right)$
-\end{itemize}
-Also following J21/J22, we take the SNeIa Delay Time distribution to be a $t^{-1.1}$ law based on the observations by \citet{2012MNRAS.426.3282M}.
-
-We leave consistent throughout the paper.
-While different CCSNe models predict different absolute values for $y_\text{O}^\text{CC}$, they also predict that the yield is metallicity-independent within the uncertainties of the model.
-
-\subsection{Asymptotic giant branch carbon}
-
-An AGB star is a low mass ($\lesssim 8 M_{\sun}$) star during the final phases of evolution.
-The star has already completed Hydrogen core burning, Hydrogen shell burning during the red giant branch phase, and Helium core burning.
-So, the structure consists of an inert core of carbon and oxygen surrounded by a Helium burning shell and a Hydrogen burning shell.
-The double shell burning leads to thermal instabilities which drive off the outer layers of the star in a series of violent pulsations, ejecting the envelope and leaving behind a C/O white dwarf.
-
-In an AGB star, TDU and HBB are two major processes involved in carbon production and destruction.
-TDU occurs during thermal pulsations, where the convective layer of the star passes into the inner layers with He-burning products which mixes in C and O into the envelope.
-In contrast, HBB may happen if the base of the convective envelope reaches about 50MK, initiating the CNO cycle, converting most C12 into N14.
-
-The differences in yields between AGB models depend on the mass loss rate, treatment of convection, and nuclear reaction rates.
-
-In this work, we explore four different sets of AGB star yields representative of the variety of options which also provide reasonably well sampled grids in metallicity and mass necessary for chemical evolution studies.
-\begin{itemize}
-    \item~\VICE~\VICE~\VICE
-    \item \citetalias{2015ApJS..219...40C}
-    \item \cristallo
-    \item \cite[C11][Hi]{2011ApJS..197...17C}: \citet{2011ApJS..197...17C, 2015ApJS..219...40C}
-    \item K10: \citet{2010MNRAS.403.1413K}
-    \item V13: \citet{2013MNRAS.431.3642V}
-    \item K16: \citet{2016ApJ...825...26K}
-\end{itemize}
-Unless otherwise noted, C11 is the model we choose as our fiducial AGB yield.
-
-Figure \ref{fig:y_agb} compares the net fractional AGB carbon yield, $m_\text{C}^\text{AGB}(M, Z)$ for each AGB model we consider.
-Note that the yields may be negative when the birth abundance is higher than the carbon abundance of the material ejected back to the ISM.
-
-Most models agree on the qualitative shape of the net fractional AGB carbon yield.
-The stars with the highest fractional carbon yields are between 2 to 4 solar masses, depending on the metallicity and model.
-Both lower and higher mass stars produce less carbon, and high mass stars may even destroy carbon at high metallicity due to highly efficient HBB.
-And all models agree that the carbon yield generally decreases with metallicity.
-
-Metallicity dependence:
-V13 is the only model that stands out, showing a non-monotonic metallicity dependence, however this effect is only for models with [M/H]$\leq -1$.
-Otherwise the major differences between the models are the precise amount of carbon and the slope of the metallicity dependence.
-For example, the three models C11, K10, and K16 predict $y_\text{C}^\text{AGB}$ to be between 0.006 and 0.008 at solar metallicity, but C11 has a much shallower metallicity dependence than the K10 and K16 models.
-And at solar, V13 predicts a value at around 0.004 so the models are all within about a factor of 2.
-
-Another difference is the speed at which equilibrium is reached.
-K10 and K16 weight carbon production more heavily towards massive stars resulting in a faster time to equilibrium, whereas the C11 and V13 models predict a slightly longer timescale with order 1Gyr, but little to no carbon is produced more than 2Gyr after a star formation event.
-This is in contrast to iron which is still produced by SNeIa up to 10Gyr after a star formation event.
-
-\begin{figure*}
-    \centering
- 	    \includegraphics[scale=1]{figures/agb_yields.pdf}\\
-
-    \caption{The net fraction carbon yield ($M_\text{C}$, the amount of carbon produced by the star divided by $M$) plotted as a function of mass, $M$.
-Lighter colors represent higher values of metalicity ([M/H]).
-Each panel represents a different AGB model.
-K10 reports stars at MoverH -3, -2, etc.
-I can reproduce C11 and K10 but not other V13 and KL16 :(((}
-
-    \label{fig:y_agb}
-\end{figure*}
-
-\begin{figure*}
-    \centering
-
-    \includegraphics[scale=1]{figures/y_agb_vs_z-1.pdf}
-    \includegraphics[scale=1]{figures/y_agb_vs_t-1.pdf}
-
-    \caption{On the left, we plot the IMF weighted net fractional carbon yields of each AGB model as a function of metalicity.The right panel plots the normalized net carbon AGB yield as a function of time for a population of stars born at the same time at solar metallicity.
-We note that for the right panel, the minimum of the DTD for V13 is }
-
-\end{figure*}
-
-\subsection{CCSNe carbon}
-
-While there are many stellar models providing predictions of CCSNe yields, the results of these models are highly uncertain due to the many stellar modeling uncertainties.
-
-We summarise many of the predictions of stellar models in Figure \ref{fig:y_cc}. Pink squares represent \citep{2013ARA&A..51..457N}, etc. etc.
-\citep{2018ApJS..237...13L}
-\citep{2016ApJ...821...38S}
-\citep{1995ApJS..101..181W}
-
-On the right, we plot the expected CCSNe abundance ratio of each model as a function of metallicity, defining
-\begin{equation}
-    {\rm [C/O]^{CC}} = \log_{10}\left( \frac{y_{\rm C}^{\rm CC}}{y_{\rm O}^{\rm CC}}\right) - \log_{10} \left( \frac{Z_{C, \sun }}{Z_{O, \sun }} \right)
-\end{equation}
-Notice how even these ratios 
-\begin{figure*}
-    \includegraphics[scale=0.9]{figures/y_c_cc-2.pdf}
-    \includegraphics[scale=0.9]{figures/y_co_cc.pdf}
-    \caption{The fist plot shows IMF-weighted net fractional CCSNe yield of carbon, $y_C^{cc}$ against metalicity, [M/H], for different studies.
-The right plot instead shows [C/O]$^\text{CC}$, the logarithm of the abundance ratio of carbon to oxygen if CCSNe were the only carbon source, also as a function of metallicity for the same set of studies.
-The black line represents the carbon yield of the fiducial model, $y_C^{CC} = 0.004?
-(Z/Z_{\sun})^{0.3}$, and becomes dashed over regions where we have not tested our model.
-}
-    \label{fig:y_cc}
-\end{figure*}
-
-    \begin{itemize}
-        \item Wide range in predictions, exacerbated to 1 dex range when including variance in oxygen predictions
-        \item (explain) most models have a near-metallicity independent oxygen yield, so we choose the fiducial value of 0.015 despite varience in $y_O^{cc}$
-        \item The fiducial value, where we choose the carbon yield from Sukhbold+16, may be above most predictions of carbon yields but is within the range of yield ratios
-        \item the fiducial value would reach an equilibrium carbon yield of -0.1 without AGB stars
-        \item Rotation in LC18 appears to increase metallicity dependence of carbon production (read this paper more carefully)
-        \item NKT and LC agree in positive metallicity depenent yields
-    \end{itemize}
-
-\section{The Multizone Model}
-
-To simulate the chemical evolution of a Milky way like galaxy, we use the Versitile Integrator for Chemical Evolution (\VICE ) published in \citet{2021MNRAS.508.4484J} and also briefly described in \citet{2022arXiv220204666J}.
-As a multi-zone model, the galaxy is divided into 200 rings of 0.1kpc, each with separate gas supplies with outflow and inflow rates.
-
-\VICE\ accounts for radial migration by using the results of the \texttt{h277} hydrodynamical simulation.
-Each VICE SSP is matched to a random nearby star particle \textit{analogue} in \texttt{H277}.
-VICE approximates the migration of this particle by using a $\sqrt{\text{time}}$-diffusion approximation where the change in galactic radius of a star, $\Delta R$, is $\Delta R \propto \sqrt{\text{t}}$.
-VICE does not account for radial gas flows.
-
-Other approaches have used dynamical arguments to implement their stellar mirgrations.
-We note that our approach does not introduce more free parameters which may bias conclusions.
-However, we only consider one dynamic history, and it is still unknown how variations in the dynamic history of a galaxy impact its chemical evolution.
-
-We initially assume an "inside-out" SFH where the star formation rate peaks in the early evolution of the galaxy and is higher closer to the galactic center.
-The star formation rate, $\Sigma_\star$, for our fiducial model is parameterized by
-\begin{equation}
-    \dot{\Sigma}_\star \propto \left(1-e^{-t/\tau_{\rm rise}}\right) e^{-t/\tau_{\rm sfh}}
-\end{equation}
-where $\tau_\text{rise}=2$Gyr is the
-and $\tau_{sfh}$ is the rate of decline of the star formation rate, which is based on *****.
-
-We also explore a "lateburst" model which is parameterized with a normal distribution multiplying our fiducial "inside-out" SFH as
-\begin{equation}
-    \dot{\Sigma}_{\rm lateburst} \propto \dot{\Sigma}_{\rm insideout} \left(1 + A e^{-(t-\tau_{\rm burst})^2/2\sigma^2_{\rm burst}} \right)
-\end{equation}
-
-$A=1.5$ represents the amplitude of the birth, $\tau_\text{burst}=10.8$Gyr is the time where the burst is strongest, and $\sigma_\text{burst}=1$Gyr is the width of the burst.
-We do explore the effects of variations of this parameterization in section ****.
-
-VICE normalizes the total mass of star formation against observations from ******.
-The gas inflow is calculated based on our star formation parameterization by using a schmit law 
-\begin{equation}
-    dM_g \propto \dot{\Sigma}^{1/n}
-\end{equation}
-where we take $n$ to be ****
-
-Salpeter IMF.
-
-\subsection{Yield Parameterization}
-  Because of the large uncertainties in CCSNe carbon yields, we choose to explore an analytic expression of the yield enabling us to easily explore how variations of CCSNe carbon yields affect abundance tracks.
-We find that a powerlaw yield with a metallicity-dependent constant minimum is able to match the observations well while remaining a simple parameterization (see below).
-Our expression is:
-    \begin{equation}
-   y_\text{C}^\text{CC}(Z) =  \alpha\ Z^\beta y_\text{O}^\text{CC} + y_\text{C, 0}^\text{CC}
-    \end{equation}
-   	Where we estimate $\alpha = 0.02$ and $\beta = 0.25$ (See Section \ref{equilibrium} ).
-Our second model uses $\alpha = 0.44$ and $\beta = 0.63$ with K16 yields and reduced $\eta \rightarrow 1/2 \eta$
-
-    As an overall scaling of yields does not significantly affect our models, we choose to fix the total equilibrium value of the total carbon yield at solar at $Y_{\text{C},\ \sun} = 0.005$, and then scale the yields relative to this value.
-
-\section{Multizone model results}
-
-\subsection{Data Selection}
-
-We use data from APOGEE DR17 processed with APOSCAP.
-Since subgiant stars have yet to experience FDU, their atmospheric carbon and nitrogen abundances are still reflective of their birth abundances and do not need mixing corrections.
-
-To select for subgiants, we use the following cut in $\log g$ and $T_{\rm eff}$ which selects stars at the base of the red giant turnoff (FIGURE and \cite{jack_subgiant})
-
-Because the star formation history is left in a simple inside-out form, this multizone model does not reproduce the high-$\alpha$ sequence, therefore we make the following cut to the V21 data to remove the high alpha sequence.
-(do we?)
-
-See Appendix \ref{sec:jack} for further discussion of our sample and comparison to FIORENZO.
-
-\subsection{The Evolution of carbon across the galaxy and through time}
-
-The GCE of carbon is complicated by metallicity dependencies and delayed contributions.
-
-We note the following features of our model:
-
-\begin{enumerate}
-    \item Carbon comes predominantly ($\sim80\%$) from CCSNe but the rest is from AGB stars
-    \item The CCSNe carbon production is more efficient at higher metallicities
-    \item AGB stars produce less carbon at higher metallicities.
-\end{enumerate}
-
-The combination of these features leads to an evolution that proceeds as follows
-\begin{enumerate}
-    \item Initially, CCSNe dominate production before AGB stars can contribute their enrichment, but because CCSNe is highly metalliticy dependent, the C/$\alpha$ ratio increases with time.
-    \item AGB stars begin contributing their carbon, increasing the $C/\alpha$ ratio more steeply as the gas begins to reach its equilibrium metallicity
-    \item When $Z$ reaches equilibrium, the $C/\alpha$ ratio stops increasing or may even decline, as AGB stars formed at higher metallicities reduce the net carbon yields.
-\end{enumerate}
-
-We plot time evolution tracks in Figure \ref{fig:c_evo} for $[C/\alpha]-[\alpha/H]$ and $[C/\alpha]-[Fe/H]$ for our fiducial model.
-Each colored track corresponds to a different galactic radius and 1Gyr time steps are marked with crosses on the lines.
-
-Comparing [C/$\alpha$] against [Fe/H] enables us to see late time evolution of carbon more clearly.
-Because [Fe/H] takes longer to reach equilibrium as half of iron production comes from type-Ia supernovae, the late time evolution is not clustered as tightly horizontally as for [$\alpha$/H].
-
-This is even more evident in the lower part of Figure \ref{fig:c_evo}, where we instead plot snapshots of the galactic radial trend at different times for our model.
-While the [C/$\alpha$]-[$\alpha$/H] trend reaches almost equilibrium at 5Gyr, the [C/$\alpha$]-[$\alpha$/Fe] trend continues to evolve even until the present day, exposing the effect of the delayed contribution from AGB stars on the evolutionary history.
-
-\begin{figure*}
-\label{fig:c_evo}
-\includegraphics{figures/evo_tracks-9.pdf}
-\includegraphics{figures/evo_slices-2.pdf}
-\caption{The top set of panes show the time evolution of the gas phase of our fiducial model, plotted as tracks through [C/O]-[O/H] and [C/O]-[O/Fe] where each colored line corresponds to the evolution at that galactic radius.
-The bottom set instead shows the galaxies gas-phase [C/O]-[O/H] and [C/O]-[O/Fe] trend at 5 different time slices. 
-}
-\end{figure*}
-
-\subsection{Effects of AGB Yields}
-\begin{figure*}
-\includegraphics[scale=0.6]{figures/oob_agb-1.pdf}
-
-\caption{Abundance tracks for 4 different choices of AGB models.
-Each panel has different abundance ratios on the axis but is otherwise the same.
-The black points are Jack Roberts selection of APOGEE subgiants.
-Each model is plotted as a line representing the mean stellar abundance in each bin on x.}
-\label{fig:stars_abundances}
-\end{figure*}
-
-How much does the choice of AGB model affect chemical evolution? 
-Short description of effects of AGB model choices, and how we can rule out models like V21.  Maybe point to appendex B?
-
-Our next exploration is to adjust the relative fraction of AGB star yields. To do this, we hold the total carbon yield at solar metallicity fixed, so for a desired AGB fraction (assuming equilibrium),
-
-\begin{equation}
-    \alpha_{AGB} = f_{agb} \frac{y_{desired}}{y_0^{agb}}
-\end{equation}
-\begin{equation}
-    \alpha_{CC} = (1 - f_{agb}) \frac{y_{desired}}{y_0^{cc}}
-\end{equation}
-
+% Example table
 \begin{table}
 	\centering
-	\caption{For each AGB yield set, our calculation of the effective SFH- and IMF-weighted carbon AGB yield, along with the multiplicative factor to reach an AGB contribution of 20.}
-	\label{tab:alpha_agb}
-	\begin{tabular}{lcr} % four columns, alignment for each
+	\caption{This is an example table. Captions appear above each table.
+	Remember to define the quantities, symbols and units used.}
+	\label{tab:example_table}
+	\begin{tabular}{lccr} % four columns, alignment for each
 		\hline
-		Study & $y_{\rm C, 0}^{\rm agb}$ & $\alpha_{\rm agb, 20}$\\
+		A & B & C & D\\
 		\hline
-		C11 & 0.000405 & 3.6\\
-		K10 & 0.000643 & 2.3\\
-		V13 & 0.000214 & 6.8\\
-		K16 & 0.000404 & 3.6\\
+		1 & 2 & 3 & 4\\
+		2 & 4 & 6 & 8\\
+		3 & 5 & 7 & 9\\
 		\hline
@@
 \end{table}
-
-\subsection{Star Formation History}
-
-We do run models with an alternate "lateburst" stars formation history.
-
-equation of lateburst
-
-However, we find that the star formation history has a negligable effect on the shape of the mean track.
-More drastic changes in SFH could explain the high alpha/low alpha seperation but we leave further exploration of SFH to future work.
-
-% \begin{figure*}
-% \includegraphics[width=1.5\columnwidth]{figures/cooh_lateburst.pdf}
-% \caption{Same as Fig. \ref{fig:stars_abundances} but with different model choices.}
-% \end{figure*}
-
-\begin{figure*}
-\includegraphics[scale=0.6]{figures/beta-1.pdf}
-\includegraphics[scale=0.6]{figures/f_agb-1.pdf}
-
-\caption{Similar to \ref{fig:stars_abundances} except the top plot shows the fiducial model with lower and higher values of $\beta$, the C-CCSNe metallicity dependence.
-The bottom plot is the same except shows varying AGB fractions.}
-\end{figure*}
-
-\begin{figure*}
-\includegraphics[scale=0.6]{figures/lateburst_eta-1.pdf}
-
-\caption{Same as Figure \ref{fig:stars_abundances} but comparing the fiducial model to the reduced outlow model and a lateburst model. (okay, need to totally change approach...)}
-\end{figure*}
-
-\subsection{Adjusted CCSNe Yields}
-
-\begin{figure}
-    \includegraphics[scale=0.6]{figures/cooh_scatter.pdf}
-    \caption{The simulated stars of our model at present day plotted on [C/O]-[O/H] and colored such that lighter colors represent stars born at greater galactric radii.}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[scale=0.6]{figures/cnoh.pdf}
-    \caption{Caption}
-    \label{fig:cnofe}
-\end{figure}
-
-\begin{figure*}
-\centering
-\includegraphics[]{figures/summary-2.pdf}
-\caption{Present-day gas phase tracks of the fiducial model in [C/O]-[O/H] space. M101 is valid comparison to MW ...(van Dokkum et al. 2014)}
-\label{fig:gas_phase}
-\end{figure*}
-\subsection{The AGB Fraction }
-One potential tension with data is our models predict a low value for the AGB fraction of stars.
-
-Our model with Z-dependent CCSNe yields has $f_\text{agb} = 0.05$ which implies that CCSNe overwhelms AGB production and there should not be a seperation between low and high alpha sequences.
-However, V21 observes a significant seperation implying a more substantial delayed-time source.
-
-Even changing the AGB model does not affect the conclusion significantly.
-
-An alternate solution is to reduce the outflows and core collapse yields similarly, consistent with a model where more large stars collapse directly into black holes.
-This leaves the $y_\text{C}^\text{CC}/y_\text{O}^\text{CC}$ ratio unchanged, but because $y_\text{C}^\text{CC}$ is unchanged, the relative size of the AGB contribution is larger.
-
-Increasing the relative AGB production lowers the magnitude of  $y_\text{C}^\text{CC}/y_\text{O}^\text{CC}$, but the metallicity dependence of the ratio must increase to compensate for the inverse metallicity dependence of AGB carbon yields.
-
-We find that we can adjust both the outflows and scale down the yields if we change our model for $y_\text{C}^\text{CC}/y_\text{O}^\text{CC}$.
-For example, reducing outflows and CCSNe yields by a factor of two requires the modified parameters
-$\alpha = 0.033$ and $\beta = 0.625$, which results in a slightly lower value at solar but nearly a doubling of the metallicity dependence.
-
-These models are indistinguishable in the [C/O]-[O/H] plane from our adjusted CCSNe model, so future work investigating the SFH and carbon isotopic ratios in more depth may be able to provide more insight.
-In the next section, we develop the analytic tools to explore this problem in more depth.
-
-\subsection{Outflows}
-A common degeneracy in chemical evolution models is the yield-outflow degeneracy.
-An increase in stellar yields has a near-identical effect as a decrease in outflows.
-However, reducing the outflows reduces the evolution timescale of the system.
-
-The theoretical motivation for decreasing outflows is due to the uncertainty in the explodability landscape---if less massive stars explode, then both the yields and outflows will be reduced by some factor.
-So, when we explore reduced outflow models, we consider models where both the outflows and yields are reduced by approximately the same factor, to leave the equilibrium abundances of a pure CCSNe unchanged.
-
-The effect of reducing outflows is then increasing the relative contributions of non-CCSNe processes. For carbon, this increases the AGB fraction.
-
-We have found that the [C/O]-[O/Fe] relationship may provide insight into this issue.
-[O/Fe] is a tracer of the relative contributions of CCSNe and delayed-time sources in chemical evolution.
-So, the appearance of a slope in [O/Fe] implies that there is a substantial delay-time process in carbon evolution.
-The metallicity-dependence of carbon yields complicates this picture because younger stars have higher [O/Fe] as the SNeIa contributions take up to 10Gyr, so metal-poor young stars will naturally have lower [C/O], agreeing with the slope observed in [C/O]-[O/Fe].
-However, a pure CCSNe carbon model cannot reproduce the slope accurately as
-
-\subsection{Comparison to HII Region Observations}
-In Figure \ref{fig:gas_phase}, we plot our two favorite models against HII-region measured carbon abundances from **********
-
-Our model appears to be broadly consistant with the gas phase data, however these imply if anything that the slope should be increased.
-
-Are HII regions a good approximation?
-
-Short discussion of measurment challenges in extragalactic galaxies, how other galaxies and dwarf SFH may come into play, why this relation is notecably steeper.
-
-\section{The Equilibrium Approximation}\label{equilibrium}
-If we assume that the median track is an equilibrium phenomenon, we can calculate the total carbon to oxygen yield ratio.
-Additionally, assuming an AGB yield set enables us to predict the CCSNe carbon yield.
-We begin with the model, which underlies the multizone simulations, that the change in mass of an element is a sum of production, outflows, recycling, and mass left in reminants. We write this as
-\begin{equation}
-M_\text{C} = y_\text{C} \dot{M}_\star - (1 + \eta - r) Z_\text{C} \dot{M}_\star
-\end{equation}
-
-In the case that carbon
-\begin{equation}
-Z_c^{eq}(R) = \frac{y_c^{cc} + \langle y_c^{agb} \rangle }{1 + \eta(R) - r - \tau_\star / \tau_{sfh}}
-\end{equation}Where
-\begin{equation}
-\langle y_c^{agb} \rangle = \frac{\int_0^T y_c^{agb}(M, Z) \dot{M}_\star(T - t) \frac{dN}{dM} \frac{dM}{dt} dt  }{ \dot{M}_\star \int_0^T \frac{dN}{dM} \frac{dM}{dt} dt}
-\end{equation}
-
-Likewise for oxygen:
-\begin{equation}
-Z_O^{eq}(R) = \frac{y_O^{cc}}{1 + \eta(R) - r - \tau_\star / \tau_{sfh}}
-\end{equation}
-
-However, for the yield ratio, the denominator cancles with that of oxygen, so the ratio is fixed.
-\begin{equation}
-\frac{Z_c^{eq}}{Z_o^{eq}} = \frac{y_c^{cc} + \langle y_c^{agb} \rangle }{y_o^{cc}}
-\end{equation}
-
-For this analysis, we let $y_c^{agb}$ represent the default AGB yields from a given yield set, but add a process factor $\alpha_{agb}$ which multaplicatively increases the AGB fraction.
-See Table \ref{tab:alpha_agb}.
-
-\begin{equation}
-    y_{\rm C}^{\rm CC} \rightarrow \alpha_{agb}  y_{\rm C}^{\rm CC}
-\end{equation}
-
-With these definitions, we can calculate the core collapse yields of carbon as a function of metallicity:
-\begin{equation}
-    y_\text{C}^\text{CC} =  y_\text{O}^\text{CC} \frac{Z_\text{C,eq}}{Z_\text{O,eq}} - \alpha_{agb} \langle y_c^{agb} \rangle
-\end{equation}
-
-Rewriting in terms of the observed abundance ratio and dividing by $y_\text{O}^\text{CC}$.
-So, given the outflows or CCSNe oxygen yields, the carbon AGB yield, and the [C/O]-[O/H] mean abundance track, we can estimate the CCSNe carbon yield.
-Written as a relative yield:
-\begin{equation}
-    \frac{y_\text{C}^\text{CC}}{y_\text{O}^\text{CC}} = \frac{Z_{C, \sun}}{Z_{O, \sun}} 10^{[C/O]} - \frac{\alpha_{agb} \langle y_c^{agb} \rangle}{ y_\text{O}^\text{CC}}
-\end{equation}
-
-This equation corroberates what we have explored earlier in the paper, and provides our analytic estimates of the CCSNe carbon yields.
-Since the AGB term is subtracted, a negative AGB Z-dependence will correspond to a positive CC Z-dependence.
-And as we reduce outflows, the AGB factor increases, steepening the required slope of the carbon yields.
-So, while the AGB yields may agree with eachother, the uncertainties in the oxygen CC yields and outflows leads to a substantial uncertainty in the AGB fraction.
-
-\begin{figure}
-    \centering
-    \includegraphics[scale=0.3]{figures/analytic_y-4.pdf}
-    \caption{Our reverse fitting method to determine total CCSNe contribution}
-\end{figure}
-
-% y_c^cc = (0.0148 +- 0.00016) Z^{0.154 +- 0.0053}
-\begin{equation}
-    y_C = (0.004 \pm 0.00002) + (0.008 \pm 0.0001) \text{[M/H]} 
-\end{equation}
-
-\subsection{Uncertainties}
-
-We only perform this analysis on the C11/15 yields because the range of metallicities of the data (about [M/H] = -0.4, 0.4) only represents about 2 AGB models, relying heavily on our choice of extrapolation.
-C11/C15 have a finer model grid, allowing us to have 5 theoretical predicted points within this metallicity range, allowing us to be more certain of our conclusion.
-
-We do note that this analysis fails to take into account selection effects and biases in APOGEE, and a more robust determination of the carbon yield.
-
-This formulation is degenerate in $\varpi$ until we estimate a better AGB fraction.
-As the seperation between the low and high alpha sequences can be used to estimate the delayed time contribution to carbon, using the model to estimate this value relies heavaly on the details of the SFH in addition to the
-We do give an estimate of the CCSNe yields, however this is dependent on our choice of $\eta$.
-Other choices of $\eta$ vary the value significantly in both magnitude and slope (as AGB contributions increase, we need less CCSNe carbon, however the CCSNe carbon must have a higher metallicity dependence to replicate the V21 data).
-
-\section{Modeling extragalactic carbon trends}
-Can we use our yield estimations and apply them to extragalactic sources successfully?
-
-Explain Berg+19,
-
-Bursty SFH may not be needed to explain scatter as the C/O slope + differet evolutionary timescales is capable alone of reproducing this scatter.
-
-While the extragalactic trend appears to be more steeply sloped than our models, this is because of ***e.g. mass-dependent outflow rates/differening SFH between galaxies.
 
@@
 Try to keep it short.
-
-Numpy, pandas, scipy, VICE, matplotlib
-\cite{numpy, matplotlib}
-
-\cite{OhioSupercomputerCenter1987}
 
@@
 \bibliographystyle{mnras}
-\bibliography{main} % if your bibtex file is called example.bib
+\bibliography{example} % if your bibtex file is called example.bib
 
@@
 
-\section{Validating the APOGEE Subgiant Sample}\label{sec:jack}
-Our APOGEE subgiant sample excludes stars marked with the following flags:
-\begin{itemize}
-\item \texttt{ancillary young embedded cluster}
-\item \texttt{ancillary emission line star}
-\item \texttt{MIR-deected candidate cluster member}
-\item \texttt{selected as part of the EB program}
-\item \texttt{selected as part of the young cluster study (in-SYNC)}
-\item \texttt{W3/4/5 star forming complex}
-\end{itemize}
+\section{Some extra material}
 
-To select stars only in the subgiant branch, we select stars in a polygon in $\log g$-$T_\text{eff}$ space described by the following cuts:
-\begin{equation}
-\begin{cases}
-\log g \geq 3.5 \\
-\log g \leq 0.004\ T_\text{eff} - 15.7 \\
-\log g \leq 0.00070588\ T_\text{eff} + 0.358836 \\
-\log g \leq -0.0015\ T_\text{eff} + 12.05 \\
-\log g \geq 0.0012\ T_\text{eff} - 2.8 \\
-\end{cases}
-\end{equation}
-
-Instead of excluding stars which have experienced FDU and thus modified carbon abundances as JACK's subgiant sample does, another approach to predict the birth abundances of carbon and nitrogen in stars is to model the predicted abundance effects of dredge up and then correct the measured abundances, as is done in V21.
-
-In the first panel, both V13 and the subgiant sample predict similar trends in [C/Mg]-[Mg/H] but there appears to be a systematic offset of about 0.2dex.
-Reproducing the trend is promising as V21's mixing corrections were metallicity-dependent so the uncorrected sample of APOGEE giants does not match the subgiant trend.
-
-The systematic offset could be explained by overpredicting the effects of FDU or other *** in V21's stellar evolution models??? or other subgiant physics???
-
-In the second panel, agreement appears to be better. Both the MDF and the slope are nearly identical,
-There is a slight deviation in slope between the models, and this could again be a systematic such as underestimation of **8some stellar effect**** at higher metallicities.
-
-We compare both of **** in Figure \ref{fig:fiorenzo_jack}.
-
-\begin{figure*}
-    \centering
-    \includegraphics[scale=0.5]{figures/fiorenzo_vs_jack_c-1.pdf}
-    \includegraphics[scale=0.5]{figures/fiorenzo_vs_jack_n-1.pdf}
-    \caption{A comparison of estimated stellar birth abundance trends from the subgiant sample and \citet{2021arXiv210603912V}
-    }
-    \label{fig:fiorenzo_jack}
-\end{figure*}
-
-\section{Effects of Alternate AGB Models}\label{sec:alt_agb}
-
-While we focus the main discussion of the paper on the C11 model, other AGB models can have notable effects on abundance trends at ***
-
-Because the predictions of the AGB yield models we consider are dwarfed by the required CCSNe carbon production to match observations (see Figure ***), we briefly explore here the effects of variations in AGB models affect abundance trend predictions when these models are amplified to match observational [C/MG]-[Mg/Fe] trends.
-
-While most models are well represented by our AGB-fraction formalism, V13 presents a challenge as the predicted solar yield is much lower than the lower metallicity predictions, requiring the solar value to be a certain fraction forces us to amplify the yields by an unreasonable about (of order 10-30times) to reach the same $f_{\rm AGB}$ as other models.
-Thus, we instead calculate $f_{\rm AGB}$ at a metallicity of ...
-for this model.
-
-V13 is also interesting as at high metallicity, the yields quickly become strongly negative.
-This causes a reversal of the [C/Mg]-[Mg/Fe] trend at high [Mg/H] slices (figure ...).
-As our set of observations do not appear to reverse, this indicates that carbon yields likely stay positive even at slightly super-solar, so models like V13 are a poor match to observations.
-Plot of age metallicity relationship?
-
-\begin{figure*}
-\includegraphics[scale=0.45]{figures/agb_adj-2.pdf}
-\includegraphics[scale=0.45]{figures/abg_adj_z-1.pdf}
-
-\caption{Same as \ref{fig:stars_abundances} but comparing our fiducial model to our recommended z-dependent $y_\text{C}^\text{CC}$ model.
-A plot of the stars of our favored CCSNe model colored by radius.
-The contours represent the density of V+21 data.
-The model is given Gaussian scatter equivalent to the mean error in the abundances reported by APOGEE.
-}
-\end{figure*}
+If you want to present additional material which would interrupt the flow of the main paper,
+it can be placed in an Appendix which appears after the list of references.
 

### 2025-01-16 carbon_paper/tex/survey_comparison.tex
adds carbon equations documentation

@@
 \usepackage{aas_macros}
+\usepackage{longtable}
+\usepackage{booktabs}
 % Depending on your LaTeX fonts installation, you might get better results with one of these:
@@
 
-This document is a summary of the differences between measurements and surveys as it is related to C.
-Below, we provide brief descriptions of the relavant characteristics of C determination and survey properties.
+This document is a work-in-progress summary of the differences between measurements and surveys as it is related to C.
+We provide brief descriptions of the abundance determination methods and survey characteristics.
 
@@
     \caption{Binned median trends for several surveys.
-    With the exception of GALAH (see text), all samples agree up to a normalization for \caah\, and, even more encouragingly, samples approximately trace out the same trend in \caafe.}
+    All samples agree up to a normalization for \caah\, and, even more encouragingly, samples approximately trace out the same trend in \caafe.}
     \label{fig:other_surveys}
@@
 
-GALAH is perhaps the strongest outlier in terms of the infered \caah\ trend: predicting a steep negative slope of > 0.5 (compared to < 0.1 for APOGEE)
-However, GALAH may not be the ideal survey for measuring C.
-Reported C measurments have low completion (50\% or down to 20 \% at lower metallicities) and are based on one weak line (6587.6100Å, in supplemental material of DR3 paper).
+GALAH DR4 substantially improves the C abundances.
+
+DR3 was a strong outlier in terms of \caah.
+DR3 reported C measurments have low completion (50\% or down to 20 \% at lower metallicities) and are based on one weak line (6587.6100Å, in supplemental material of DR3 paper).
 So, whlikely observational effects of lower detection rates for metal poor stars, but also strong systematic from APOGEE. Reference Emily's appendix
@@
 Crossmatches with apogee reveal that completion is not the whole story-and stars with C abundances measured in both surveys exhibit a similar systematic trend with metallicity. 
-\dbnote{Note how results would be affected if using Galah instead}
 GALAH consideres NLTE for O, Mg, and Fe, (among others) but not C, using the SME code on a small sample, then applied to the whole survey using the Cannon.
@@
 \centering
-\caption{
-Damped lyman alpha measurements
-References are (1) dessauges-zavadsky+03, (2) : pettini+08, 3: \citet{ellison+10}, }
 \begin{tabular}{lrlll}
 \hline
-    Quasar & $z_{\rm abs}$ & [C/O] & [O/H] & references \\
+QSO & redshift & C/O & O/H & study \\
 \hline
-    Q1101-264 & 1.838000 & $0.77 \pm 0.09$ & $-1.66 \pm 0.07$ & (1) \\
-    Q2059-360 & 2.507000 & $-0.41 \pm 0.28$ & $-1.38 \pm 0.23$ & (1) \\
-    J2155+1358 & 4.212000 & $-0.29 \pm 0.08$ & $-1.82 \pm 0.11$ & (1) \\
-    Q0913+072 & 2.618000 & $-0.39 \pm 0.05$ & $-2.42 \pm 0.04$ & (2)\\
-    J1016+4040 & 2.816000 & $-0.21 \pm 0.05$ & $-2.48 \pm 0.11$ & (2)\\
-    J1558+4053 & 2.553000 & $-0.06 \pm 0.07$ & $-2.47 \pm 0.06$ & (2)\\
-    Q2206-199 & 2.076000 & $-0.38 \pm 0.04$ & $-2.09 \pm 0.05$ & (2)\\
-    J0140-0839 & 3.696000 & $-0.30 \pm 0.08$ & $-2.77 \pm 0.15$ & (3) \\
-    J1337+3152 & 3.167000 & $-0.19 \pm 0.11$ & $-2.59 \pm 0.17$ & srianand+10 \\
+HS 0105+1619 & 2.535998 & $0.23 \pm 0.07$ & $-1.75 \pm 0.03$ & omera+01 \\
+J1358+6522 & 3.067259 & $-0.27 \pm 0.06$ & $-2.34 \pm 0.06$ & cooke+14 \\
+J0955+4116 & 3.279908 & $-0.46 \pm 0.15$ & $-2.47 \pm 0.06$ & welsh+2022 \\
+J0140-0839 & 3.696000 & $-0.30 \pm 0.08$ & $-2.77 \pm 0.15$ & ellison+10 \\
+J0035-0918 & 2.340064 & $-0.12 \pm 0.14$ & $-2.47 \pm 0.06$ & welsh+20 \\
+Q1243+307 & 2.525640 & $0.24 \pm 0.03$ & $-2.79 \pm 0.03$ & cooke+18 \\
+PKS1937-101 & 3.572400 & $1.56 \pm 0.13$ & $-2.57 \pm 0.13$ & riemer-sorensen+17 \\
+Q1101-264 & 1.838000 & $0.77 \pm 0.09$ & $-1.66 \pm 0.07$ & dessauges-zavadsky+03 \\
+Q2059-360 & 2.507000 & $-0.41 \pm 0.28$ & $-1.38 \pm 0.23$ & dessauges-zavadsky+03 \\
+J2155+1358 & 4.212000 & $-0.29 \pm 0.08$ & $-1.82 \pm 0.11$ & dessauges-zavadsky+03 \\
+J0903+2628 & 3.077590 & $-0.38 \pm 0.04$ & $-3.07 \pm 0.05$ & cooke+17 \\
 J0311-1722 & 3.734000 & $-0.42 \pm 0.11$ & $-2.31 \pm 0.10$ & cooke+11 \\
 J1001+0343 & 3.078000 & $-0.41 \pm 0.03$ & $-2.67 \pm 0.05$ & cooke+11 \\
-    J1358+6522 & 3.067295 & $-0.03 \pm 0.11$ & $-2.24 \pm 0.09$ & cooke+12 \\
-    J0035-0918 & 2.340060 & $0.16 \pm 0.24$ & $-2.71 \pm 0.17$ & dutta+14 \\
 J0953-0504 & 4.202870 & $-0.50 \pm 0.03$ & $-2.57 \pm 0.10$ & dutta+14 \\
-    J0035-0918 & 2.340000 & $0.08 \pm 0.16$ & $-2.46 \pm 0.07$ & cooke+15 \\
+Q1202+3235 & 4.977000 & $0.20 \pm 0.09$ & $-2.00 \pm 0.12$ & morrison+16 \\
+J1337+3152 & 3.167000 & $-0.19 \pm 0.11$ & $-2.69 \pm 0.17$ & srianand+10 \\
+Q0913+072 & 2.618000 & $-0.39 \pm 0.05$ & $-2.42 \pm 0.04$ & pettini+08 \\
+J1016+4040 & 2.816000 & $-0.21 \pm 0.05$ & $-2.48 \pm 0.11$ & pettini+08 \\
+J1558+4053 & 2.553000 & $-0.06 \pm 0.07$ & $-2.47 \pm 0.06$ & pettini+08 \\
+Q2206-199 & 2.076000 & $-0.38 \pm 0.04$ & $-2.09 \pm 0.05$ & pettini+08 \\
+J1332+0052 & 3.421086 & $-0.03 \pm 0.02$ & $-1.72 \pm 0.02$ & kislitsyn+24 \\
 J1111+1332 & 2.270000 & $-0.18 \pm 0.11$ & $-1.94 \pm 0.08$ & cooke+15 \\
-    Q1202+3235 & 4.977000 & $0.20 \pm 0.09$ & $-2.00 \pm 0.12$ & morrison+16 \\
-    J0903+2628 & 3.077590 & $-0.38 \pm 0.04$ & $-3.07 \pm 0.05$ & cooke+17 \\
-    J0035-0918 & 2.340064 & $-0.12 \pm 0.14$ & $-2.47 \pm 0.06$ & welsh+20 \\
-    HS0105+1619 & 2.536000 & $0.11 \pm 0.04$ & $-1.78 \pm 0.02$ & cooke+14 \\
-    Q0913+072 & 2.618000 & $-0.36 \pm 0.01$ & $-2.42 \pm 0.01$ & cooke+14 \\
-    J1358+6522 & 3.067000 & $-0.27 \pm 0.06$ & $-2.33 \pm 0.02$ & cooke+14 \\
 \hline
@@
 \end{table}
-
 C abundances are measured in XXXX.
@@
 
+\begin{longtable}{lllll}
+\hline
+galaxy & region & C/O & O/H & study \\
+\hline
+LMC & 30 Dor & $-0.27 \pm 0.26$ & $-0.51 \pm 0.10$ & garnett+1995 \\
+SMC & SMC N88A & $-0.51 \pm 0.17$ & $-0.72 \pm 0.04$ & garnett+1995 \\
+NGC 2363 & NGC 2363 & $-0.42 \pm 0.15$ & $-0.89 \pm 0.04$ & garnett+1995 \\
+Tol 1214-277 & Tol 1214-277 & $-0.59 \pm 0.28$ & $-1.22 \pm 0.05$ & garnett+1995 \\
+SDSS J094401.87-003832.1 & centre & $-1.15 \pm 0.06$ & $-1.00 \pm 0.07$ & senchyna+17 \\
+SDSS J102429.25+052450.9 & centre & $-0.60 \pm 0.20$ & $-0.89 \pm 0.04$ & senchyna+17 \\
+UGC 5189 & SDSS J094256.74+092816.2, & $-0.53 \pm 0.45$ & $-0.57 \pm 0.06$ & senchyna+17 \\
+Mrk 193 & Mrk 193 & $-0.31 \pm 0.04$ & $-0.90 \pm 0.04$ & senchyna+17 \\
+SDSS J094252.78+354726.0 & centre & $-0.47 \pm 0.30$ & $-0.64 \pm 0.08$ & senchyna+17 \\
+LEDA 41360 & centre & $-0.81 \pm 0.15$ & $-1.00 \pm 0.08$ & senchyna+17 \\
+IC 700 & LEDA 35380 & $-0.80 \pm 0.14$ & $-0.46 \pm 0.07$ & senchyna+17 \\
+LEDA 36857 & centre & $-0.54 \pm 0.09$ & $-0.80 \pm 0.04$ & senchyna+17 \\
+NGC 4204 & Mrk 1315 & $-0.53 \pm 0.09$ & $-0.51 \pm 0.07$ & senchyna+17 \\
+NGC 4301 & SDSS J122225.79+043404.7 & $-0.59 \pm 0.20$ & $-0.33 \pm 0.11$ & senchyna+17 \\
+I Zw 18 & I Zw 18 & $-0.54 \pm 0.07$ & $-1.69 \pm 0.04$ & izotov+thuan1999 \\
+SBS 0335-052 & SBS 0335-052 & $-0.62 \pm 0.08$ & $-1.49 \pm 0.01$ & izotov+thuan1999 \\
+UM 469 & UM 469 & $-0.24 \pm 0.20$ & $-0.84 \pm 0.05$ & izotov+thuan1999 \\
+NGC 4861 & NGC 4861 & $-0.17 \pm 0.16$ & $-0.78 \pm 0.02$ & izotov+thuan1999 \\
+Tol 1345-420 & Tol 1345-420 & $-0.40 \pm 0.16$ & $-0.70 \pm 0.05$ & izotov+thuan1999 \\
+NGC 5253 & NGC 5253 & $-0.35 \pm 0.13$ & $-0.65 \pm 0.05$ & izotov+thuan1999 \\
+M101 & NGC 5455 & $-0.11 \pm 0.15$ & $-0.42 \pm 0.03$ & garnett+1999 \\
+M101 & NGC 5461 & $0.01 \pm 0.21$ & $-0.30 \pm 0.03$ & garnett+1999 \\
+M101 & NGC 5471 & $-0.47 \pm 0.05$ & $-0.75 \pm 0.03$ & garnett+1999 \\
+NGC 2403 & VS 38 & $-0.17 \pm 0.13$ & $-0.23 \pm 0.05$ & garnett+1999 \\
+NGC 2403 & VS 44 & $-0.19 \pm 0.14$ & $-0.31 \pm 0.04$ & garnett+1999 \\
+NGC 2403 & VS 9 & $-0.38 \pm 0.19$ & $-0.65 \pm 0.03$ & garnett+1999 \\
+J082555 & NaN & $-0.08 \pm 0.06$ & $-1.44 \pm 0.01$ & berg+16 \\
+J104457 & NaN & $-0.50 \pm 0.06$ & $-1.36 \pm 0.02$ & berg+16 \\
+J120122 & NaN & $-0.24 \pm 0.11$ & $-1.36 \pm 0.03$ & berg+16 \\
+J124159 & NaN & $-0.61 \pm 0.16$ & $-1.08 \pm 0.04$ & berg+16 \\
+J122622 & NaN & $-0.56 \pm 0.05$ & $-0.91 \pm 0.01$ & berg+16 \\
+J122436 & NaN & $-0.38 \pm 0.07$ & $-0.97 \pm 0.02$ & berg+16 \\
+J124827 & NaN & $-0.42 \pm 0.17$ & $-1.00 \pm 0.03$ & berg+16 \\
+J223831 & NaN & $-0.45 \pm 0.10$ & $-1.23 \pm 0.02$ & berg+19 \\
+J141851 & NaN & $-0.67 \pm 0.07$ & $-1.27 \pm 0.02$ & berg+19 \\
+J120202 & NaN & $-0.59 \pm 0.09$ & $-1.18 \pm 0.02$ & berg+19 \\
+J121402 & NaN & $-0.28 \pm 0.10$ & $-1.15 \pm 0.02$ & berg+19 \\
+J084236 & NaN & $-0.74 \pm 0.11$ & $-1.20 \pm 0.02$ & berg+19 \\
+J171236 & NaN & $-0.56 \pm 0.10$ & $-1.12 \pm 0.02$ & berg+19 \\
+J113116 & NaN & $-0.58 \pm 0.14$ & $-1.17 \pm 0.02$ & berg+19 \\
+J133126 & NaN & $-0.51 \pm 0.07$ & $-1.12 \pm 0.02$ & berg+19 \\
+J132853 & NaN & $-0.83 \pm 0.12$ & $-1.09 \pm 0.02$ & berg+19 \\
+J095430 & NaN & $-0.39 \pm 0.11$ & $-1.11 \pm 0.02$ & berg+19 \\
+J132347 & NaN & $-0.82 \pm 0.08$ & $-1.23 \pm 0.02$ & berg+19 \\
+J094718 & NaN & $-0.17 \pm 0.12$ & $-1.09 \pm 0.02$ & berg+19 \\
+J150934 & NaN & $-0.58 \pm 0.09$ & $-1.11 \pm 0.02$ & berg+19 \\
+J100348 & NaN & $-0.34 \pm 0.13$ & $-1.07 \pm 0.02$ & berg+19 \\
+J025346 & NaN & $-0.40 \pm 0.11$ & $-0.90 \pm 0.02$ & berg+19 \\
+J015809 & NaN & $-0.32 \pm 0.14$ & $-1.06 \pm 0.02$ & berg+19 \\
+J104654 & NaN & $-0.58 \pm 0.10$ & $-0.90 \pm 0.02$ & berg+19 \\
+J093006 & NaN & $-0.68 \pm 0.10$ & $-0.79 \pm 0.02$ & berg+19 \\
+J092055 & NaN & $-0.44 \pm 0.12$ & $-0.95 \pm 0.02$ & berg+19 \\
+Mrk 960 & NaN & $-0.41 \pm 0.39$ & $-0.70 \pm 0.19$ & pena-guerreno+17 \\
+SBS 0218+003 & NaN & $-0.96 \pm 0.25$ & $-0.82 \pm 0.06$ & pena-guerreno+17 \\
+Mrk 1087 & NaN & $0.40 \pm 0.33$ & $-0.40 \pm 0.14$ & pena-guerreno+17 \\
+NGC 1741 & NaN & $-0.21 \pm 0.30$ & $-0.56 \pm 0.10$ & pena-guerreno+17 \\
+Mrk 5 & NaN & $-0.80 \pm 0.29$ & $-0.83 \pm 0.10$ & pena-guerreno+17 \\
+Mrk 1199 & NaN & $0.79 \pm 0.45$ & $-0.48 \pm 0.22$ & pena-guerreno+17 \\
+IRAS 08208+2816 & NaN & $-0.68 \pm 0.26$ & $-0.38 \pm 0.11$ & pena-guerreno+17 \\
+IRAS 08339+6517 & NaN & $0.06 \pm 0.26$ & $-0.39 \pm 0.07$ & pena-guerreno+17 \\
+SBS 0926+606A & NaN & $-0.48 \pm 0.24$ & $-0.83 \pm 0.09$ & pena-guerreno+17 \\
+Arp 252 & NaN & $0.06 \pm 0.34$ & $-0.68 \pm 0.15$ & pena-guerreno+17 \\
+SBS 0948+532 & NaN & $-0.49 \pm 0.24$ & $-0.78 \pm 0.09$ & pena-guerreno+17 \\
+Tol 9 & NaN & $0.17 \pm 0.36$ & $-0.23 \pm 0.15$ & pena-guerreno+17 \\
+SBS 1054+365 & NaN & $-0.42 \pm 0.20$ & $-0.70 \pm 0.09$ & pena-guerreno+17 \\
+POX 4 & NaN & $-0.49 \pm 0.14$ & $-0.75 \pm 0.05$ & pena-guerreno+17 \\
+SBS 1319+579 & NaN & $-0.32 \pm 0.26$ & $-0.62 \pm 0.09$ & pena-guerreno+17 \\
+SBS 1415+437 & NaN & $-1.42 \pm 0.24$ & $-1.25 \pm 0.07$ & pena-guerreno+17 \\
+Tol 1457-262 & NaN & $-1.22 \pm 0.46$ & $-0.98 \pm 0.16$ & pena-guerreno+17 \\
+III Zw 107 & NaN & $-0.51 \pm 0.28$ & $-0.59 \pm 0.10$ & pena-guerreno+17 \\
+\hline
+\end{longtable}
+
+\begin{longtable}{lllll}
+\hline
+galaxy & region & C/O & O/H & study \\
+\hline
+NGC 6822 & region V & $-0.15 \pm 0.21$ & $-0.44 \pm 0.09$ & peimbert+05 \\
+MW & Sh 2-311 & $-0.10 \pm 0.14$ & $-0.24 \pm 0.05$ & mendez-delgado+22 \\
+MW & NGC 2579 & $-0.14 \pm 0.09$ & $-0.26 \pm 0.03$ & mendez-delgado+22 \\
+MW & NGC 3576 & $-0.02 \pm 0.08$ & $-0.08 \pm 0.04$ & mendez-delgado+22 \\
+MW & NGC 3603 & $0.04 \pm 0.12$ & $-0.10 \pm 0.05$ & mendez-delgado+22 \\
+MW & M8 & $0.04 \pm 0.10$ & $-0.11 \pm 0.04$ & mendez-delgado+22 \\
+MW & M16 & $0.03 \pm 0.15$ & $-0.01 \pm 0.05$ & mendez-delgado+22 \\
+MW & M17 & $0.26 \pm 0.06$ & $-0.06 \pm 0.02$ & mendez-delgado+22 \\
+MW & M20 & $0.02 \pm 0.25$ & $-0.10 \pm 0.06$ & mendez-delgado+22 \\
+MW & M42 & $0.03 \pm 0.07$ & $-0.16 \pm 0.02$ & mendez-delgado+22 \\
+M101 & H1013 & $0.17 \pm 0.07$ & $-0.24 \pm 0.02$ & skillman+20 \\
+M101 & H1052 & $0.13 \pm 0.04$ & $-0.24 \pm 0.01$ & skillman+20 \\
+M101 & NGC 5461 & $-0.10 \pm 0.12$ & $-0.33 \pm 0.02$ & skillman+20 \\
+M101 & NGC 5462 & $-0.18 \pm 0.19$ & $-0.36 \pm 0.05$ & skillman+20 \\
+M101 & NGC 5462 & $-0.07 \pm 0.12$ & $-0.38 \pm 0.01$ & skillman+20 \\
+M101 & NGC 5455 & $-0.13 \pm 0.11$ & $-0.42 \pm 0.02$ & skillman+20 \\
+M101 & NGC 5447 & $-0.09 \pm 0.09$ & $-0.39 \pm 0.01$ & skillman+20 \\
+M101 & NGC 5447 & $-0.04 \pm 0.17$ & $-0.46 \pm 0.01$ & skillman+20 \\
+M101 & H1216 & $-0.42 \pm 0.50$ & $-0.55 \pm 0.03$ & skillman+20 \\
+M101 & NGC 5471 & $-0.26 \pm 0.46$ & $-0.67 \pm 0.03$ & skillman+20 \\
+NGC 300 & R20 & $-0.01 \pm 0.22$ & $-0.12 \pm 0.11$ & toribo-san-cipriano+16 \\
+NGC 300 & R23 & $-0.22 \pm 0.23$ & $-0.11 \pm 0.13$ & toribo-san-cipriano+16 \\
+NGC 300 & R14 & $-0.15 \pm 0.21$ & $-0.19 \pm 0.11$ & toribo-san-cipriano+16 \\
+NGC 300 & R2 & $-0.31 \pm 0.22$ & $-0.24 \pm 0.12$ & toribo-san-cipriano+16 \\
+M33 & NGC 588 & $-0.26 \pm 0.19$ & $-0.32 \pm 0.09$ & toribo-san-cipriano+16 \\
+M33 & IC 132 & $-0.12 \pm 0.15$ & $-0.34 \pm 0.12$ & toribo-san-cipriano+16 \\
+LMC & 30 Dor & $-0.29 \pm 0.06$ & $-0.28 \pm 0.04$ & toribo-san-cipriano+17 \\
+LMC & N44C & $-0.22 \pm 0.03$ & $-0.23 \pm 0.02$ & toribo-san-cipriano+17 \\
+LMC & IC 2111 & $-0.21 \pm 0.08$ & $-0.20 \pm 0.07$ & toribo-san-cipriano+17 \\
+LMC & NGC 1714 & $-0.24 \pm 0.07$ & $-0.25 \pm 0.07$ & toribo-san-cipriano+17 \\
+LMC & N11B & $-0.27 \pm 0.04$ & $-0.22 \pm 0.02$ & toribo-san-cipriano+17 \\
+SMC & N66A & $-0.46 \pm 0.06$ & $-0.46 \pm 0.03$ & toribo-san-cipriano+17 \\
+SMC & N81 & $-0.46 \pm 0.04$ & $-0.47 \pm 0.02$ & toribo-san-cipriano+17 \\
+SMC & NGC 456 & $-0.41 \pm 0.19$ & $-0.45 \pm 0.09$ & toribo-san-cipriano+17 \\
+SMC & N88A & $-0.33 \pm 0.03$ & $-0.59 \pm 0.02$ & toribo-san-cipriano+17 \\
+NGC 6822 & centre & $-0.31 \pm 0.15$ & $-0.46 \pm 0.05$ & esteban+14 \\
+NGC 5408 & centre & $-0.41 \pm 0.19$ & $-0.60 \pm 0.04$ & esteban+14 \\
+M31 & K932 & $0.05 \pm 0.16$ & $-0.19 \pm 0.03$ & esteban+09 \\
+M33 & NGC 595 & $0.05 \pm 0.17$ & $-0.12 \pm 0.05$ & esteban+09 \\
+M33 & NGC 604 & $0.01 \pm 0.14$ & $-0.21 \pm 0.03$ & esteban+09 \\
+NGC 2366 & NGC-2363 & $-0.08 \pm 0.14$ & $-0.77 \pm 0.05$ & esteban+09 \\
+NGC 2403 & VS 24 & $0.30 \pm 0.28$ & $-0.44 \pm 0.04$ & esteban+09 \\
+NGC 2403 & VS 38 & $0.42 \pm 0.20$ & $-0.52 \pm 0.05$ & esteban+09 \\
+NGC 2403 & VS 44 & $-0.08 \pm 0.22$ & $-0.20 \pm 0.04$ & esteban+09 \\
+\hline
+\end{longtable}
+
 \newpage
+
+\begin{table}[]
+\centering
+\begin{tabular}{lrlll}
+\toprule
+galaxy & redshift & C/O & O/H & study \\
+\midrule
+MOSFIRE stack & 2.400000 & $-0.39 \pm 0.09$ & $-0.43 \pm 0.10$ & steidel+2016 \\
+876\_330 & NaN & $-0.47 \pm 0.17$ & $-1.07 \pm 0.50$ & stark+2014 \\
+863\_348 & NaN & $-0.53 \pm 0.08$ & $-0.99 \pm 0.50$ & stark+2014 \\
+860\_359 & NaN & $-0.37 \pm 0.08$ & $-1.02 \pm 0.50$ & stark+2014 \\
+MARCS 0451-1.1 & NaN & $-0.50 \pm 0.13$ & $-1.52 \pm 0.50$ & stark+2014 \\
+XLS-z2 stack & 2.000000 & $-0.59 \pm 0.20$ & $-0.98 \pm 0.06$ & mathee+2021 \\
+RXCJ0232-588 & 1.644800 & $-0.47 \pm 0.19$ & $-1.21 \pm 0.24$ & mainali+2020 \\
+GLASS 150008 & 6.228950 & $-0.80 \pm 0.12$ & $-1.42 \pm 0.23$ & jones+2023 \\
+VUDS 510583858 & 2.414100 & $-0.74 \pm 0.10$ & $-1.38 \pm 0.31$ & amorin+2017 \\
+VUDS 510838687 & 2.553900 & $-0.36 \pm 0.06$ & $-1.25 \pm 0.36$ & amorin+2017 \\
+VUDS 511267982 & 2.825600 & $-0.46 \pm 0.08$ & $-1.22 \pm 0.24$ & amorin+2017 \\
+VUDS5100534435 & 2.963500 & $-0.79 \pm 0.09$ & $-1.10 \pm 0.20$ & amorin+2017 \\
+VUDS5100565880 & 3.050500 & $-0.17 \pm 0.10$ & $-1.22 \pm 0.26$ & amorin+2017 \\
+VUDS5100750978 & 2.963000 & $-0.57 \pm 0.04$ & $-1.26 \pm 0.21$ & amorin+2017 \\
+VUDS5100994378 & 2.797000 & $-0.40 \pm 0.06$ & $-1.30 \pm 0.32$ & amorin+2017 \\
+VUDS5100998761 & 2.446000 & $-0.43 \pm 0.06$ & $-1.43 \pm 0.19$ & amorin+2017 \\
+VUDS5101421970 & 2.465000 & $-0.60 \pm 0.11$ & $-1.23 \pm 0.38$ & amorin+2017 \\
+VUDS5101444192 & 3.424000 & $-0.46 \pm 0.08$ & $-1.15 \pm 0.25$ & amorin+2017 \\
+abell2895b & 3.720960 & $-0.78 \pm 0.23$ & $-1.45 \pm 0.02$ & iani+2023 \\
+CASSOWARY 20 & 1.433000 & $-0.85 \pm 0.30$ & $-0.99 \pm 0.21$ & james+2014 \\
+Q2343-BX418 & 2.304800 & $-0.41 \pm 0.10$ & $-1.01 \pm 0.10$ & erb+2010 \\
+SGAS J105039.6+001730 & 3.625300 & $-0.58 \pm 0.06$ & $-0.51 \pm 0.10$ & bayliss+2014 \\
+SL2S J0217-0513 & 1.844350 & $-0.60 \pm 0.09$ & $-1.31 \pm nan$ & berg+2018 \\
+Abell1689 Arc 31.1 & 1.833900 & $-0.82 \pm 0.08$ & $-1.12 \pm 0.13$ & christensen+2014 \\
+SMACS J2031.8-4036 ID 1.1 & 3.506100 & $-0.59 \pm 0.09$ & $-1.05 \pm 0.03$ & christensen+2014 \\
+s04590 & 8.459000 & $-0.62 \pm 0.38$ & $-1.69 \pm 0.12$ & AC2022 \\
+\bottomrule
+\end{tabular}
+\end{table}
 

### 2025-01-16 models/perturbations/mc_analysis/run_binned_mc.jl
adds intrinsic dispersion to mcmc

@@ -10,19 +10,6 @@ struct ConstDist  <: ContinuousUnivariateDistribution
     mean::Float64
 end
 
-function Base.rand(rng::AbstractRNG, d::ConstDist)
-    return d.mean
-end
-
-Distributions.minimum(d::ConstDist) = d.mean
-Distributions.maximum(d::ConstDist) = d.mean
-Distributions.logpdf(d::ConstDist, x) = x == d.mean ? 0.0 : -Inf
-Distributions.cdf(d::ConstDist, x) = x < d.mean ? 0.0 : 1.0
-Distributions.sampler(d::ConstDist) = d
-Distributions.insupport(d::ConstDist, x) = x == d.mean
-Distributions.quantile(d::ConstDist, p) = d.mean
-
-
 function get_args()
     s = ArgParseSettings(
         description = """runs a MCMC model from a binned multi-component multizone model
@@ -139,6 +126,7 @@ end
         
 
     params ~ arraydist(priors[.!is_const])
+    sigma_int ~ LogNormal(-3, 1) # mean of 0.05 dex
 
     const_params = [p.mean for p in priors[is_const]]
     all_params = vcat(const_params, params)
@@ -152,8 +140,8 @@ end
     sigma_ah = models_ah.obs_err ./ sqrt.(models_ah.obs_counts)
     sigma_afe = models_afe.obs_err ./ sqrt.(models_afe.obs_counts)
 
-    sigma2_ah = @. sigma_ah^2 + sem_ah^2 
-    sigma2_afe = @. sigma_afe^2 + sem_afe^2
+    sigma2_ah = @. sigma_ah^2 + sem_ah^2 + sigma_int^2
+    sigma2_afe = @. sigma_afe^2 + sem_afe^2 + sigma_int^2
 
     # Data likelihoods
     models_ah.obs ~ MvNormal(mu_ah, diagm(sigma2_ah))

### 2025-03-06 carbon_paper/tex/main.tex
updated draft

@@
 \documentclass[fleqn,
-%referee, % this line changes to double-spaced 1 column
+% referee, % this line changes to double-spaced 1 column
 usenatbib]{mnras}
@@
 \newcommand{\aton}{\texttt{\hyperlink{aton}{ATON}}}
-\newcommand{\cfactor}{1.44}
+\newcommand{\cfactor}{1.95}
 \newcommand{\nsubgiants}{14,069}
+
+% displays fractions within fractions well
+\newcommand{\ddfrac}[2]{\ensuremath{%
+    \frac{\displaystyle{#1}}{\displaystyle{#2}}
+}}
 
@@
 
+\newcommand{\Var}{\operatorname{Var}}
+
 % other
-\newcommand{\ycmg}{\ensuremath{2.7 + 32\left(Z-\Zo\right)}}
 \newcommand{\fmeas}{20\%}
@@
  \newcommand{\yb}{\ensuremath{\rotatebox[origin=B,y=0.5ex]{180}{y}}}
-\newcommand{\y}{Y}
+\newcommand{\y}{p}
 \newcommand{\fagb}{f_{\rm C}^{\rm AGB}}
 
-\newcommand{\zetao}{\zeta^{(0)}}
-\newcommand{\zetai}{\zeta^{(1)}}
-\newcommand{\zetaii}{\zeta^{(2)}}
+\newcommand{\zetao}{\zeta_0}
+\newcommand{\zetai}{\zeta_{1}}
+\newcommand{\zetaii}{\zeta_{2}}
+\newcommand{\Zl}{x_{\rm low}}
 
@@
 % 
-We find that \caafe\ trends, when restricted in metallicity, are an empirical estimate of the delayed C sources, enabling us to estimate that \agb\ stars and \cc\ produce about 20\% and 80\% of C, respectively.
-The \caah\ trend instead represents the equilibrium abundances of C and Mg. 
-We use the \caah\ trend to estimate total C/Mg yield ratio, determining that  $\Ycc/\Yoc = EQUATION$.
+We show \caah\ trend represents the equilibrium abundances of C and Mg, deriving the total C yield as a function of metallicity. 
+Instead, the \caafe\ trend (at a given metallicity) is an empirical estimate of the delay time distribution of C.
+We infer that AGB stars produce between 10 and 40\% of C. Additionally, we show that all AGB models produce C too quickly, and the low-mass AGB C yield is likely underestimated. 
 % misc
@@
 On the left, we plot high and low-$\alpha$ stars in blue and orange, using the separation defined in Eq.~\ref{eq:high_alpha}.
-On the right, we colour-code stars according to their [Mg/H] abundance.} \label{fig:subgiants}
+On the right, we colour-code stars according to their [Mg/H] abundance.
+The median subgiant trends serve as our emperical benchmark.
+} \label{fig:subgiants}
 \end{figure*}
@@
 
-Given the challenge of {\it a priori} yield predictions, recent work aims to empirically characterize elemental production \dbnote{does it make sense to frame this as only recent work?
+Given the challenge of theoretical yield predictions, recent work aims to empirically characterize elemental production \dbnote{does it make sense to frame this as only recent work?
 I just don't know but I feel like there are very early examples which at least use observations as a guide for yields, like maybe even B2FH.
@@
 Under their equilibrium scenario, this argument should extend to any element whose enrichment by stellar populations does not require long timescales ($\gtrsim$few Gyr).
-We show in \add{REF 3.1} that the characteristic delay times of C production should be $\sim$ few hundred Myr, within this limit. 
+We show in section~\ref{sec:agb} that the characteristic delay times of C production should be $\sim$ 1 Gyr, within this limit. 
 \dbnote{This is complicated by the difference between high alpha and low alpha, and 1-2Msun stars do produce carbon...}
@@
 Subgiants have the advantage that their photospheric C and N abundances should closely approximate their birth mixture.
-During main sequence evolution, metals can fall below the convective envelope (i.e., ``gravitational settling''; e.g. \dbadd{CITE}).
+During main sequence evolution, metals can fall below the convective envelope (\textit{gravitational settling}; e.g. \citealt{turncotte+98}).
 When stars evolve off main sequence, these metals are reincorporated into the convective envelope \citep[]{gratton+00, souto19}. 
@@
 \citep{iben67, KL14}.
+\dbnote{Why exactly do we use subgiants? Consistent stellar parameters, subgiant spectra are easier than white dwarfs? only a $\sim 0.05$ dex correction}
 
@@
 In general, different surveys follow similar trends in \caah\ and \caafe\ but with systematic offsets at the $\sim{0.1}$ dex level in [C/Mg] given [Mg/H] and slight variations in the slope.
-\dbnote{Galah DR4 fixes the issues we were seeing and updates how they process C.}
 These systematic differences are not a major concern for our conclusions since our models are mostly constrained by the slope of \caah\ and \caafe,  not their normalization (see Fig.~7?
@@
 
-Following \citet{james+23}, we integrate yields and our GCE models using the publicly available Versatile Integrator for Chemical Evolution (\VICE, \citealt{JW20}).
-We retain their prescription for O, Fe, an yields, scaled down to the normalization recommended by \citet{david_fe} based on .....
-Table~\ref{tab:fiducial_mod} summarizes these choices.
-As required by \VICE, these yields quantify the mass of some element that is newly produced (i.e.
-net yields as opposed to gross yields).
-The SN yields are in units of the proginitors initial mass, while the AGB yields are defined relative to the star's zero-age main sequence mass.
-
-\dbadd{paragraph about yields in general}
 A yield quantifies the new production of a chemical species.
-For a given star, we define the {\it net fractional yield} to be the mean change in the chemical abundance from the birth to ejected mass, multiplied by the ejected fraction of a stars mass, i.e.
+For a given star, we define the {\it net fractional yield of $X$} as the fraction of a stars initial mass synthesized into new $X$.
+Specifically, the net fractional yield of element $X$ is
 \begin{equation} 
-   Y_{\rm C}^{\rm AGB}(Z) = 
-    \delta Z_X \frac{M_{\rm ej}}{M}
-\end{equation}
-Note that yields may become negative if more of the initial chemical abundance of X is transformed into other elements than other elements transformed into X.
-In general, we describe yields by their population-averaged forms, the amount of newly produced X per unit mass of star formation (from supernovae and stellar winds).
+   \y_{\rm X}(M, Z) = 
+    \frac{m_{X, \rm ej}- Z_{X,\rm  ini}\,m_{\rm ej}}{m}
+\end{equation}
+where $Z_X$ is the initial abundance of $X$, $m_{\rm ej}$ is the ejected mass, $m_{X, \rm ej}$ is the ejected mass of $X$, and $m$ is the initial mass of the star.
+Note that yields may become negative if more X is transformed into other elements than is produced ($Z_{X,\rm ej} < Z_{X,\rm ini}$).
+We also describe yields by their population-averaged quantities, the amount of newly produced X per unit mass of star formation, 
 \begin{equation} 
    y_{X}(Z) = 
-    \frac{M_X - M_{\rm X, ini}}{M_{\rm ssp}}
-\end{equation}
-
-In \VICE, massive star nucleosynthesis is approximated as occurring instantaneously after a star formation event.
-Under this approximation, the yield is simply a constant  of proportionality between the metal production rate and the SFR:
-\begin{equation}
-    \dot{M}_X^{\rm CC} = y_{X}^{\rm cc}\, \dot{M}_\star
-\end{equation}
-The population-averaged yield, $y_{X}^{\rm cc}$ can be expressed as
-\begin{equation}
-y_{X}^{\rm CC} = \frac{
-\int_8^u (E(m) m_X + w_X - Z_X(m - m_{\rm rem}) )\frac{dN}{dM}\ dM
-}{
-\int_l^u m\,\frac{dN}{dM}\ dm
-}
-\end{equation}
-where $m_X$ and $w_X$ are the mass of X ejected in a CCSN explosion and through stellar winds respectively, from a star of initial mass $m$.
-$E((m)$ is a function describing the fraction of stars of mass $m$ that successfully explode (se discussion in \S \dbadd{3.2} below).
-$m_{\rm rem}$ is the mass of the remnant left behind, $dN/dM$ is the IMF, for which we assume \dbadd{cite}.
-$l$ and $u$ are the lower and upper mass limits of star formation.
-$8\,\Mo$ is the minimum mass of a CCSN progenitor.
-In section \S 3.2 below, we compute the values of $\Ycc$ using \VICE's `vice.yields.ccsne.fractional` function and discuss theoretical expectations of C yields based on massive star evolutionary models.
-
-The population averaged SNe Ia yield, $y_{X}^{\rm ia}$, is given by,
-\begin{equation}
-    y_{X}^{\rm Ia} = m_{x}^{\rm Ia} \frac{N_{\rm Ia}}{m_\star}
-\end{equation}
-where $m_{X}^{\rm Ia}$ is the average mass of X produced in a single SN Ia event, and $N_{\rm Ia} / M_\star$ is the number of such events per unit mass of star formation.
-The latter can be expressed as an integral over the SN Ia delay-time-distribution (DTD), which describes the rate at which stellar populations produce X through SN Ia in \VICE.
-Following \citet{james+23}, we use a $t^{-1.1}$ single power-law with a minimum delay-time of 150 Myr based on comparisons of the SN IA rate as a function of redshift and the cosmic SFR (e.g.
-\citealt{maoz+12}).
-
-The net yield from a single AGB star is given by \begin{equation} \label{eq:net-yield}
-   Y_{\rm C}^{\rm AGB}(Z) = 
-    \delta Z_X \frac{M_{\rm ej}}{M}
-\end{equation}
-where $M_{\rm ej}$ is the mass of the ejected envelope, and $\delta Z_X$ is the average change in the abundance of X in the envelope over the lifetime of the star.
-Models of AGB star nucleosynthesis report values of $Y_X^{\rm AGB}$ sampled on a grid of initial masses and metallicities (see discussion in \S \dbadd{3.1}), and \VICE\ accepts these tables directly as input.
-The population-averaged AGB star yield is then given by
-\begin{equation} \label{eq:imf-agb-yield}
-    y_{X}^{\rm agb}(Z,\tau) = 
-    \frac{
-    \int_{l}^{M_{\rm max}^{\rm AGB}} 
-    \y_{\rm X}^{\rm proc}(M, Z) M\ 
-    \frac{dN}{dM}\ dM
-}
-{
-    \int_{l}^{u}\ M\ \frac{dN}{dM}\ dM
-}
-\end{equation}
-where $m_{\rm min}$ is the minimum and maximum initial mass of stars that become AGBs.
-While $m_{\rm min}$ theoretically extends as low as $0.1 \Mo$, we interpolate yields to zero past $0.5 \Mo$ as these stars live longer than the disk and no yield grid extends this low.
-In Section~\ref{sec:agb},  we discuss theoretical expectations for C production in AGB stars and our adopted tables of $\Ycagb$ from the literature.
-\dbadd{specify exactly how we change the yield interpolation for AGB stars}
+    \frac{M_X - r\,Z_{X, \rm ini}\,M_{\rm ssp}}{M_{\rm ssp}},
+\end{equation}
+where $M_X$ is the total expelled mass of element X, $M_{\rm ssp}$ is the birth mass of the single stellar population (SSP\footnote{An SSP is a cluster of stars born at the same time from the same material.}), and $r$ is the return fraction (fraction of the SSP mass returned to the interstellar medium).
+
+Following \citet{james+23}, we integrate yields and our GCE models using the publicly available Versatile Integrator for Chemical Evolution (\VICE, \citealt{JW20}).
+We use the O, Mg, and Fe yields recommended by \citet{david_fe} based on measurements of the mean CCSN Fe yield \citep{rodriguez+23} and APOGEE chemical abundances.
+Our N yield is scaled from \citep{james+23}.
+Table~\ref{tab:fiducial_mod} summarizes these choices. 
+We assume a \citet{kroupa01} initial mass function.
 
@@
 See section \ref{sec:agb} for the definition of \fruity.
-The solar abundance scale is \citet{magg+22} + 0.04.
+The solar abundance scale is \citet{magg+22} + 0.04 dex suggested by \citet{david_fe}.
+    \dbnote{any tips to make this table a little bit smaller?}
     }
@@
 		\hline
-        Element & $Z_{X,\,\sun}$ & $y_X^{\rm cc}$ & $\y_X^{\rm agb}$ & $y_X^{\rm ia}$  \\
+         & $Z_{X,\,\sun}$ & $y_X^{\rm cc}$ & $\y_X^{\rm agb}$ & $y_X^{\rm ia}$  \\
 		\hline
-        C & 0.00339 & Eq.~\ref{eq:y_cc} & $\cfactor\times$\fruity &  0 \\
-        O & 0.00733 & 7.12e-3 & 0 & 0 \\
-        Mg & 0.000671 & 6.52-4 & 0 & 0 \\
-        Fe & 0.00137 & 4.72e-4 & 0 & 6.69e-4 \\
-        N &0.00104 & 4.001e-4 & 0.0009$M\left(\frac{Z}{Z_\odot}\right)$ & 0\\
-        % C & 0.00339 & Eq.~\ref{eq:zeta} & $\cfactor\times$\fruity &  0 \\
-        % O & 0.00733 & 0.015 & 0 & 0 \\
-        % Mg & 0.000671 & 0.00185 & 0 & 0 \\
-        % Fe & 0.00137 & 0.0012 & 0 & 0.00214 \\
-        % N &0.00104 & 0.00072 & 0.0009$M\left(\frac{Z}{Z_\odot}\right)$ & 0\\
+        C & $33.9\times10^{-4}$ & Eq.~\ref{eq:y_cc} & $\cfactor\times$\fruity &  0 \\
+        O & $73.3\times10^{-4}$ & $71.3\times10^{-4}$ & 0 & 0 \\
+        Mg & $6.71\times10^{-4}$ & $6.52\times 10^{-4}$ & 0 & 0 \\
+        Fe & $13.7\times10^{-4}$ & $4.73\times10^{-4}$ & 0 & $7.82\times10^{-4}$ \\
+        N & $10.4\times10^{-4}$ & $5\times10^{-4}$ & $5\times10^{-4}M\left(\frac{Z}{Z_\odot}\right)$ & 0\\
 		\hline
@@
  	    \includegraphics[scale=1]{agb_yields.pdf}
-        \caption[]{\dbnote{replace y label with stellar C yield, draw actual interpolations...}.
-The net fractional \agb\ C yield  plotted as a function of initial stellar mass $M$ and colour-coded according to metallicity.
-The black dashed line shows $\y=0$ for reference.
-Each panel represents yields from one of four \agb\ models: \fruity{}, \aton{}, \monash{}, \nugrid{} (see sections \ref{sec:agb}) }
+        \caption[]{The net fractional \agb\ C yield  plotted as a function of initial stellar mass and colour-coded according to metallicity.
+The black dashed line shows $\Ycagb=0$ for reference.
+Each panel represents yields from one of four \agb\ models: \fruity{}, \aton{}, \monash{}, \nugrid{} (see sections \ref{sec:agb}) }.
 
@@
 
-    \caption[]{\textbf{Left} \dbnote{ylabel: integrated carbon AGB yield} The (IMF-weighted) \agb\ C yield $\Ycagb$ as a function of metallicity for each of the \agb\ yield models.
-($\Ycagb$ is the net mass of C produced by \agb\ stars per unit mass of star formation, after 10\,Gyr and assuming a \citealt{kroupa01} IMF.)
-    \textbf{Right} cumulative C return as a function of age for a solar metallicity single stellar population.
-The dashed black line shows the delay time distribution of type Ia supernovae ($\propto t^{-1.1}$) for comparison.
+    \caption[]{\textbf{Left} The integrated \agb\ C yield $\Ycagb$ as a function of metallicity for each of the \agb\ yield tables.
+    \textbf{Right} cumulative C return fraction as a function of age for a solar metallicity single stellar population.
+The dashed black line shows the cumulative return fraction of type Ia supernovae ($\propto t^{-1.1}$) for comparison.
 The minimum of \aton{} is at $y( 0.30\,{\rm Gyr})/y(t_{\rm end})=-7.81$ and is large as the net yield is close to zero.
@@
 
-An Asymptotic Giant Branch (AGB) star is a low mass star during its last nuclear (He shell) burning phase which enriches the interstellar medium (ISM) through mass loss during thermal pulses.(see e.g.
+An Asymptotic Giant Branch (AGB) star is a low mass star undergoing He shell burning, the last nuclear phase (see e.g.
 \citealt{PR2023}).
+AGB stars enrich the interstellar medium (ISM) through mass expelled during thermal pulses.
 In this work, we explore four different stellar AGB yield tables from the literature which provide well-sampled grids in mass and metallicity. We refer to the tables as 
@@
 \end{description}
-Table~\ref{tab:agb} notes the masses and metallicities for each grid of yields.
-We use the same tables as \citet{james+23}, except that we have swapped \citet{karakas10} for \citet{pignatari+16}. \dbadd{the selection of tables is the same as CITE with the exception that ...}
+Each AGB yield table reports yields for stellar models on a grid of masses and metallicities as reported in Table~\ref{tab:agb}.
+We use the same tables as \citet{james+23}, except that we have swapped \citet{karakas10} for \citet{pignatari+16}. 
 For our models to better match observations, we uniformly amplify the yield tables according to
 \begin{equation} \label{eq:alpha}
-        \Ycagb \rightarrow \alpha_{\rm agb}\ \Ycagb.
+        \ycagb(M, Z) \rightarrow \alpha_{\rm agb}\ \ycagb(M, Z).
 \end{equation}
 We use the \fruity\ table, with $\alpha_{\rm agb}=\cfactor$, as the fiducial \agb\ yield.
-
 Fig.~\ref{fig:y_agb} compares the C yields for these four AGB models.
-\dbadd{there is good agreement} Most models agree on general yield trends in mass and metallicity.
+Most models agree on general yield trends in mass and metallicity.
 C production peak between masses of $\sim$ 2--4 $\Mo$. As metallicity increases, the net yield decreases and the mass of peak C production increases slightly.
 
-In order to integrate yields across the metallicity and mass range of interest, we interpolate yield tables linearly in both $Z$ and mass.
-Below the last sampled mass, $Y_{\rm C}^{\rm AGB}$ is linearly interpolated to 0 at $0.5\Mo$.
-The choice of yields for stars of masses $\Mo \lesssim 1.5$ produces about a 20\% uncertainty in the slope of the DTD past 3\,Gyr \dbstrike{but these old populations account for a small fraction of the total C}.
-\strike{More complete grids in mass and metallicity would be needed to more accurately compare GCE predictions between AGB evolution models.
-}
+In order to integrate AGB yields with \VICE, we linearly interpolate yield tables in both mass and metallicity.
+Below the smallest mass in a table, $\ycagb$ is linearly extrapolated to 0 at $1\Mo$.
+The population-averaged AGB star yield is calculated with
+\begin{equation} \label{eq:imf-agb-yield}
+    y_{X}^{\rm agb}(Z,\tau) = 
+    \frac{1}{A}\int^{u_{\rm AGB}}_{M_\textrm{post-AGB}(\tau)} 
+    \y_{\rm X}(M, Z)\ 
+    \frac{dN}{dM}\ M\ dM
+\end{equation}
+are the minimum and maximum mass of star formation, $u_{\rm AGB}=8\Mo$ is the maximum mass of an AGB star, $M_\textrm{post-AGB}(\tau)$ is the mass of stars which complete AGB evolution at age $\tau$, and $dN/dM$ is the initial mass function.
+$A = \int_l^u M \frac{dN}{dM} dm$ is the IMF normalization coefficient and  $l=0.08\,\Mo$ and $u = 100\,\Mo$.
+We assume a \citet{larson74} mass-lifetime-relationship and assume that the total lifetime of stars is 1.1 times the MS lifetime.
 
@@
 The normalizations span a factor of \about{2}. (e.g. between $6\times 10^{-4}$ and $12 \times 10^{-4}$ at $Z=0.33\,\Zo$).
-Both \nugrid{} and \aton{} predict non-monotonic C yields with $Z$, but it is unclear if this prediction is significant given the uncertainties associated with any one model.
+Both \nugrid{} and \aton{} predict non-monotonic C yields with $Z$, but it is unclear if this prediction is significant given the uncertainties associated with AGB modelling.
 To characterize the metallicity dependence of each table, we fit the yield to a linear model in $\log Z$
 \begin{equation}\label{eq:agb_z_approx}
-    y_{\rm C}^{\rm AGB}(Z) = y_0 + \zagb \log(Z / \Zo).
-\end{equation}
-Table \ref{tab:agb} contains the fit parameters $y_0$ and $\zagb$ for each AGB table.
+    y_{\rm C}^{\rm AGB}(Z) = \zetao + \zetai \log(Z / \Zo).
+\end{equation}
+Table \ref{tab:agb} contains the fit parameters $\bar y_{\rm C, 0}^{\rm AGB}$ and $\zagb$ for each AGB table.
 The values of $\zagb$ span a factor of $\sim{3}$ between models.
-These variations are due to different choices of reaction rates, convection treatments, and mass-loss rates \citep{ventura+15} \dbadd{REF}, but can be qualitatively understood by comparing the strength of third dredge up (TDU) and hot bottom burning (HBB) (see discussion below and \JJ).
-
-The right panel of Fig.~\ref{fig:agb-ssp} shows the total production of C by \agb\ stars by a single stellar population (SSP; cluster of stars born at the same time from the same material) as a function of age at solar metallicity.
+These variations are due to different choices of reaction rates, convection treatments, and mass-loss rates (see discussion below and \JJ).
+
+The right panel of Fig.~\ref{fig:agb-ssp} shows the total relative production of C by \agb\ stars by a solar metallicity SSP as a function of age.
 As the mass range $2\,\Mo\lesssim M \lesssim 4\,\Mo$ is predicted to be most important for C production, half the yield is produced before \about{1}\,Gyr, similar to Fe production by \ia. 
-\monash{} weight C production more heavily towards high-mass \agb\ stars, resulting in shorter delay times, whereas the \fruity\ and \aton\ models predict a slightly longer timescale of \about{1}\,Gyr.
+\monash{} weights C production more heavily towards high-mass \agb\ stars, resulting in shorter delay times, whereas the \fruity\ model predict a slightly longer timescale of \about{1}\,Gyr.
 In any case, little to no C is produced more than 2\,Gyr after a star formation event.
@@
 
-In AGB stars, {third dredge up} (TDU) and {hot bottom burning} (HBB) are two processes driving C evolution in \agb\ stars with competing effects.
+In AGB stars, {third dredge up} (TDU) and {hot bottom burning} (HBB) are two competing processes driving C evolution.
 TDU accompanies thermal pulses, where material from the CO core is mixed with the envelope, increasing surface C abundances 
 later released to the ISM \citep{KL14}.  
-HBB\ is the activation of the CNO cycle at the bottom of the convective envelope \dbadd{with a net effect of ...}.
-TDU increases C yields and HBB converts C into N. When both processes are active, highly efficient N production ensues (see discussion in e.g. \citealt{james+23, ventura+13}). 
+HBB\ is the activation of the CNO cycle at the bottom of the convective envelope.
+TDU increases C yields and HBB converts C into N.
+\dbstrike{When both processes are active, highly efficient N production ensues (see discussion in e.g.
+{james+23, ventura+13}).} \dbnote{move to next paragraph?}.
 %Because the $^{14}$N proton capture is the slowest component of the CNO cycle, the CNO cycle converts nearly all \C[12] into $^{14}$N \citep{solar-fusion}.
@@
 
-Both HBB and TDU result in mass- and metallicity-dependent C yields. 
-Stars less than \about{2}\,$\Mo$ do not experience TDU. As a result, C yields from these stars are affected only by first dredge-up \citep[Table 1]{karakas10}, resulting in small net C yields.
+Both HBB and TDU result in mass and metallicity dependent C yields. 
+Stars less than \about{2}\,$\Mo$ do not experience TDU. As a result, C yields from these stars are affected only by first dredge-up, resulting in small net C yields \citep[Table 1]{karakas10}.
 Above \about{2}\,$\Mo$, TDU becomes important, enriching the outer layers with C.
 In \agb\ stars more massive than \about{5}\,$\Mo$, efficient HBB turns most \C[12] into $^{14}$N.
-TDU is more efficient for more compact, massive cores.
-HBB requires a more massive AGB star to reach sufficient temperatures at the base of the convective envelope to initiate proton captures.
-Both processes are more efficient at low metallicity due to the lower opacities and, more compact internal structures, and hotter temperatures.
-These two processes drive C yields from AGB stars, but their details are ultimantly set by the uncertain choices for stellar evolution models.
+TDU is more efficient for compact, massive cores.
+HBB requires a more massive AGB star to reach sufficient temperatures at the base of the convective envelope to initiate CNO.
+Both processes are more efficient at low metallicity due to the lower opacities, hotter temperatures, and more compact internal structures.
+The details of each process are ultimately set by the uncertain choices for stellar evolution models.
 
@@
 
-The major uncertanties in AGB stellar evolution are convection, nuclear reaction rates, and mass loss prescriptions.
-In particular, the $^{14}{\rm N}({\rm p},\gamma)$ reaction rate uncertainty causes a factor of 2 difference in predicted C yields \citep{herwig+austin2004, HAL2006} \dbnote{look at present-day reaction rates here}.
-CITES compared the \aton{} and \monash{} models, finding that differences in yields are primarily driven by differences in mass-loss and convection prescriptions.
+The primary uncertainties in AGB stellar evolution are convection, nuclear reaction rates, and mass loss prescriptions.
+\citet{ventura+15} compared the \aton{} and \monash{} models, finding that differences in yields are primarily driven by differences in mass-loss and convection prescriptions.
 \aton{} predicts strong HBB to set in $\sim{1}\,\Mo$ lower than in \monash{}, leading to much lower C yields.
-Most of the physics included in stellar modeling is empirically calibrated. Mass-loss rates, convection, and extra mixing are not sufficiently well understood to be computed from first principles.
+Moreover, the $^{14}{\rm N}({\rm p},\gamma)$ reaction rate uncertainty causes a factor of 2 difference in predicted C yields \citep{herwig+austin2004, HAL2006} \dbnote{palmerini+11, reaction rates updated since then}.
+Most of the physics included in stellar modelling is empirically calibrated. Mass-loss rates, convection, and extra mixing are not sufficiently well understood to be computed from first principles.
+
+Super AGB stars are the class of AGB stars with masses $\sim8$ to $\sim10\Mo$ which burn O into Si and Mg.
+While we neglect super-AGB stars in the discussion above, these stars are not predicted to be substantial producers of C, similar to high mass AGB stars.
+From the \citet{doherty+14, doherty+14b} yield table (extending the \monash\ yields), the highest net fractional yield is only -0.002 for super solar metallicity, which would have a negligible impact on the integrated yield).
+Additionally, as discussed in section~\ref{sec:degeneracies} below, the short lifetimes of high mass AGB and super-AGB stars mean they have negligable impacts on our conclusions and can be grouped with CCSNe yields.
 
@@
 	\centering
-    \caption[]{For each \agb\ yield set, the IMF-averaged \agb\ C yield at solar metallicity $y_{\rm C, 0}^{\rm agb}$.
-The solar value and slope for a linear fit to the yield (least squares, excluding lowest-metallicity point for \aton).
-The fraction of solar C produced in the model $f_\odot^{\rm AGB}$.
-We also include the masses and metallicities each grid is sampled on.
-    \dbnote{MCMC gives same results as LS here, so we can simplify this discussion.}
+    \caption[]{For each \agb\ yield set, the IMF-averaged \agb\ C yield at solar metallicity $y_{\rm C, 0}^{\rm AGB}$, the linear fit solar yield $\zetao$ and slope $\zetai$ (see Eq.~\ref{eq:agb_z_approx}), the fraction of solar C produced in the model $f_\odot^{\rm AGB}$, and the masses and metallicities each yield table is sampled on.
+    $f_{\rm odot}^{\rm AGB}$ is calculated based on $\zetao$ assuming a total C yield of $\Yct = 0.00275$.
     }
@@
 	\label{tab:agb}
-    \begin{tabular}{c  ccc  c p{5cm} p{5cm}} % four columns, alignment for each
+    \begin{tabular}{c  ccc  c p{4cm} p{4cm}} % four columns, alignment for each
 		\hline 
         \agb\ table 
-                & $y_{\rm C}^{\rm agb}(\Zo)\times10^4$ %& y
-                & $\bar y_{\rm C}^{\rm agb}(\Zo)\times10^4$ %& y
-                & $\zagb(\Zo)\times10^4$ %& $\zeta$ 
-                &  $f_\odot^{\rm agb}$
+                & $y_{\rm C, \odot}^{\rm AGB}\times10^4$ %& y
+                & $\zetao^{\rm AGB}\times 10^4$ %& y
+                & $\zetai^{\rm AGB}\times 10^4$
+                &  $f_\odot^{\rm AGB}$
                 & masses ($\Mo$) & metallicities ($Z$)\\
@@
                 & $-3.5\pm0.3$
-                & 0.138
+                & 0.14
                 & 1.3, 1.5, 2, 2.5, 3, 4, 5, 6
@@
                 & $-10. \pm 3$
-                & 0.067
+                & 0.05
                 & 1.5, 2, 2.5, 3, 3.5, 4, 4.5, 5, 6, 6.5, 7
@@
                 & $-11.0\pm 1.0$
-                & 0.102
+                & 0.10
                 & 1, 1.25, 1.5, 1.75, 2.25, 2.5, 2.75, 3, 3.25, 3.5, 3.75, 4, 4.5, 5, 5.5, 6, 7 
@@
                 & $-4.6\pm1.7$
-                & 0.214
+                & 0.30
                 & 1, 1.65, 2, 3, 4, 5, 6, 7
@@
 
-Massive stars form $^{12}$C in their cores through the triple--$\alpha$ reaction \dbnote{any more introduction needed here?}.
-Later, C not transformed into other elements is released to the ISM through winds or a supernovae.
-While there are many stellar models providing predictions of \cc{} yields, the results of these models are highly uncertain due to the complexity of stellar modeling.
-\dbnote{maybe (re)move this sentence?
-not sure...}
-
-Fig.~\ref{fig:y_cc} plots calculations of IMF-averaged yields for a handful of massive star yields from the literature.
+Massive stars form $^{12}$C in their cores through the triple-$\alpha$ reaction \dbadd{(He-burning)} which is later released to the ISM through winds and supernovae.
+
+In \VICE, massive star nucleosynthesis is approximated as occurring instantaneously after a star formation event.
+Under this approximation, the yield is simply a constant  of proportionality between the metal production rate and the SFR:
+\begin{equation}
+    \dot{M}_X^{\rm CC} = y_{X}^{\rm CC}\, \dot{M}_\star
+\end{equation}
+The population-averaged yield, $y_{X}^{\rm CC}$ can be expressed as
+\begin{equation}
+%y_{X}^{\rm CC} = \frac{ \int_{l_{\rm CC}}^{u} (E(M) M_{X\rm, SN} + w_X - Z_X\,(M-M_{\rm rem}) )\frac{dN}{dM}\ dM }{ \int_{l}^{u} M\,\frac{dN}{dM}\ dM }
+y_{X}^{\rm CC} = \int_{l_{\rm CC}}^{u} \left[E(m) m_{X\rm, SN} + w_X - Z_X\,(m-m_{\rm rem})\right]\,\frac{1}{A} \frac{dN}{dm}\ dm
+\end{equation}
+where $E(m)$ is the fraction of stars of mass $m$ which explode, $M_{X,\rm SN}$ and $w_X$ are the mass of X ejected in a CCSN explosion and through stellar winds respectively, $Z_X$ is the initial abundance of $X$, $dN/dM$ is the IMF, $l_{\rm CC}=8\Mo$ is the initial minimum mass of a CCSN progenitor, $M_{\rm ej}$ is the total mass ejected from the star in winds?.
+\dbstrike{We integrate yields using \VICE's {\tt vice.yields.ccsne.fractional} function.} \dbnote{is this too detailed?}
+
+Fig.~\ref{fig:y_cc} shows the integrated yields of several massive star yield models from the literature. 
 \cc{} models predict a wide range of C yields, spanning nearly a factor of ten. 
-Rotation, binarity, and explodability introduce substantial uncertainties in \cc\ predictions \citep{farmer+21}.
  The \cite{LC18} models, which include rotation, show that the induced mixing (e.g.
@@
 As we will later emperically show, \cc\ C production needs to be strongly metallicity-dependent at $Z \approx \Zo$, which is consistent with \citepos{LC18} rapidly rotating models and to a lesser extent \citet{NKT13}.
-As metallicity increases, stars lose more of their mass to winds.
-In particular, C enriched envelop material is lost through winds before synthesized into heavier elements, resulting in $Z$-dependent C production \citep{LC18}.
-The left panel of Fig.~\ref{fig:y_cc} shows the \fruity{} \agb\ model. Especially at $Z\approx Z_\odot$, most \cc models dominate \agb\ C production.
-
-The right panel of Fig.~\ref{fig:y_cc} shows the average [C/Mg] ratio of \cc\ ejecta for the different models, defined by
+The left panel of Fig.~\ref{fig:y_cc} also shows the IMF-averaged \agb\ star yields from the \fruity\ model (in Fig.~\ref{fig:agb-ssp}).
+Especially at $Z\approx Z_\odot$, most \cc\ models dominate \agb\ C production.
+
+The right panel of Fig.~\ref{fig:y_cc} shows the average [C/Mg] ratio of \cc\ ejecta for the different models, given by
 \begin{equation}\label{eq:c_mg_cc}
@@
 metallicity-independent Mg production \citep[e.g][]{andrews+17}.
-However, [C/Mg]$^{\rm CC}$ is super-solar in all models except
-\citet{NKT13}.
-This result arises due to the so-called ``oxygen-magnesium problem,'' whereby Mg
-is under-produced relative to O (see discussion in \citealt{emily+21}).
-resulting in [C/Mg] ratios higher than observed.
-To avoid this problem in our \gce\ models, we simply assume the O and Mg yields
-from massive stars reflect the solar mixture, consistent with observations from \apogee\ \citep{weinberg+19, weinberg+22} \dbnote{update these citations?}.
-
-To simplify the exploration of C yields from \cc\, we use the parameterazation, 
+
+As opacity increases with metallicity, high-mass stars experience stronger winds.
+In particular, C enriched envelop material is lost through winds before conversion into heavier elements, resulting in $Z$-dependent C production \citep{LC18}.
+While there are many stellar models providing predictions of \cc{} yields, the results of these models are highly uncertain.
+Furthermore, rotation, binarity, and explodability introduce substantial uncertainties in \cc\ predictions \citep{farmer+21}.
+
+The oxygen-magnesium problem is a know problem where Mg tends to be under-produced in CCSN models relative to 
+ O (see discussion in \citealt{emily+21}).
+Because we update our solar mixture to \citet{magg+22}, the O and Mg abundances of the sun are closer to predictions of CCSN models compared to \citet{asplund+09} solar scale.
+To avoid this problem in our \gce\ models, we simply assume the O and Mg yields from massive stars reflect the solar mixture, consistent with observations from \apogee\ \citep{weinberg+19, weinberg+22, david_fe}.
+We are more focused on relative yields and trends than the scale of yields.
+Surveys also have \about{0.1} dex systematic offfsets for a variety of reasons in [C/Mg].
+
+To simplify the exploration of C yields from \cc\, we use the parameterization, 
 \begin{equation}\label{eq:y_cc}
     \Ycc = \begin{cases}
-    y_{\rm C, 0}^{\rm cc} + \zcc\,\log(Z/\Zo) + A \log(Z/\Zo)^2 & Z \geq Z_{\rm low}
+    \zetao + \zetai\,x + \zetaii x^2 & x \geq \Zl
     \\
-    y_{\rm C, low}^{\rm cc} & Z < Z_{\rm low}
+    \zetao + \zetai\,\Zl + \zetaii \Zl^2 & x < \Zl
     \end{cases}
 \end{equation}
-
-where $Z_{\rm low}$ is the transition between low-metallicity constant yields and the linear(quadratic) yields near solar.
-We take $A=0$ in the fiducial model, representing a linear model, and $y_{\rm C,low}^{\rm CC} = 0.XXX$ with $Z_{\rm low} = XXX$.
-This results in a continuous yield where
-In our Quadratic model, we take $Z_{\rm low}$ to be the vertex of the parabola, such that the yield is monotonic and $y_{\rm low}$ is the value of the vertex.
-\dbnote{Fill in description here. Could also try a BiLinear model with vertex near Fe/H=0}
+where $x=\log Z/\Zo$, $x_{\rm low}$ is the transition between low-metallicity constant yields and the quadratic yields near solar.
+In our fiducial model, we take $x_{\rm low} = -\zetai / 2\zetaii$ to be the vertex of the parabola, such that the yield is monotonic.
+
 \begin{figure*}
@@
         \textbf{Left} The IMF-weighted \cc\ yield of C as a function of metallicity.
-        \textbf{Right} The \cc\ [C/Mg] abundance ratio, defined in Eq.~\ref{eq:c_mg_cc}.
-The black line is the derived C yield from section \ref{sec:equilibrium} and Eq.~\ref{eq:y_cc}.
-Yields are shown for tables from
+        \textbf{Right} The \cc\ [C/Mg] abundance ratio, defined in Eq.~\ref{eq:c_mg_cc}. The black line is the derived C yield from section~\ref{sec:mcmc_results}. Yields are shown for tables from 
     \citet[red triangles]{WW95}, \citet[orange square and diamond]{sukhbold+16}, 
@@
 
-\subsection{Adpoted Fiducial Yields}
-We propose the following functional form for total C yields near solar metallicities:
-\begin{subequations}\label{eq:yc_inferred}
-    \begin{align}
-        \frac{\Yct(Z)}{y_{\rm Mg}} &\approx 4.20 + 1.64 \log (Z/\Zo)\\
-        \frac{\Yct(Z)}{y_{\rm Mg}} &\approx 4.22 + 2.178 \log(Z/\Zo) + 5.53 \log(Z/\Zo)^2
-    \end{align}
-\end{subequations}
-At solar metallicity, these yield ratios results in an equilibrium abundance $[{\rm C/Mg}] = -0.08$ which is consistent with our subgiant sample and is within \about{20\%} of the solar C/Mg mixture. 
-For the quadratic form, we hold the yields constant past the vertex (at {\color{red} [M/H] = ?}) to avoid a premature upturn in \caah.
-We discuss the choice of these functional forms more in appendix~\dbadd{X}.
-
-\dbnote{check zetas}
-With the total C yield of Eq.~\ref{eq:yc_inferred} and given an \agb\ C yield, we can derive an \cc\ C yield that would predict observationally consistant [C/Mg] ratios.
-(by subtracting the assumed AGB contribution from the total yield fit above.)
-\begin{subequations}
-    \begin{align}
-        \Ycc(\Zo) &= \Yct(\Zo) - \Ycagb(\Zo)\\
-        \zeta &= \zcc + \zagb
-    \end{align}
-\end{subequations}
-% \dbnote{I think I can get rid of the below equation.}
-% \note{I'd suggest keeping it -- since you use $\zeta$ to distinguish between models, and it shows up in figure legends, the visibility of its exact definition will improve readability.}
-where $\zeta$ is the (solar) metallicity dependence of the C yield at $Z=\Zo$
+\subsection{Supernova Type Ia}
+The population averaged SN Ia yield, $y_{X}^{\rm ia}$, is given by,
 \begin{equation}
-    \zeta = \frac{d y_{\rm C}}{d \log Z} \Big \vert_{(Z=\Zo)},
-\end{equation}
-and $\zcc$ and $\zagb$ correspond to the specific enrichment channels.
-
-Both observational and theoretical uncertainties limit the accuracy of our relative yield predictions.
-Additionally, the derived yields will be systematically biased if the galaxy is out of equilibrium, e.g.
-due to a recent starburst \citep{mor+19,isern19}.
+    y_{X}^{\rm Ia} = m_{X}^{\rm Ia} \frac{N_{\rm Ia}}{M_\star}
+\end{equation}
+where $m_{X}^{\rm Ia}$ is the average mass of $X$ produced in a single SN Ia event, and $N_{\rm Ia} / M_\star$ is the number of such events per unit mass of star formation.
+\dbstrike{The latter can be expressed as an integral over the SN Ia delay-time-distribution (DTD), which describes the rate at which stellar populations produce X through SN Ia in \VICE.} Following \citet{james+23}, we use a $t^{-1.1}$  delay time distribution (DTD) with a minimum delay-time of 150 Myr, based on comparisons of the SN Ia rate as a function of redshift and the cosmic SFR (e.g.
+\citealt{maoz+12}).
+
+Supernovae type Ia produce negligible C.
+For our adopted yield scale, the highest magnitude CCSNe yield of the models from iwamoto99 is $1.1\times10^{-4}$, corresponding to about 4\% of our total C production, however most models predict a \ia\ C yield of less than $0.4 \times 10^{-4}$.
+We do check that including this contribution negligibly impacts our results, so we neglect SNIa C production for simplicity.
+
+Novae are important contributes of \C[13], but produce far less \C[12] \dbadd{CITE}.
 
@@
 The Galaxy evolves \textit{inside-out} -- where star formation is higher towards the center and in the early universe \citep{WF91, kauffmann96, bird+13}.
-Stars can also migrate several kpc over their life/times, mixing different chemical environments across the galaxy \citep{bird+12,sellwood+binney02}.
-Multi-zone models account for stellar migration and changing environments by stitching together multiple one-zone models and mixing stellar populations.
+Stars can also migrate several kpc over their lifetimes, mixing different chemical environments across the galaxy \citep{bird+12,sellwood+binney02}.
+To account for different environments and stellar migration, multi-zone models stitch together multiple one-zone models and mix stellar populations between zones.
 \dbnote{does this belong in intro or here?.
 Thinking here now because feels more like methodology justification, but not sure still.}
-
-For our O, Mg, and Fe yields, we adopt the yields in \citet{david_fe}. We use a scaled variation of the AGB N yield from \citet{james+23} with a metallicity-independent CCSNe N yield. 
-Following \citet{james+21, james+23}, we take the \ia{} delay time distribution to be a $t^{-1.1}$ power-law with a minimum delay time of 150\,Myr, as suggested by the observations of \citet{maoz+12}.
-\dbnote{discuss SNe Ia (maximum 4\% of C but likely much less) and SAGB (also minimal). Also: can novae produce any C?}
 
@@
 \end{equation} 
-The scaling of this relationship varies with time due to the redshift dependence of $\tau_\star$ in molecular gas observed by \citet{tacconi18}. We assume a \citet{kroupa01} IMF.
+The scaling of this relationship varies with time due to the redshift dependence of $\tau_\star$ in molecular gas observed by \citet{tacconi18}.
 
@@
 The $\Delta R \propto \sqrt{\rm time}$ dependence arises when migration proceeds as a consequence of the diffusion of angular momentum \citep{frankel18, frankel20}.
-At each time step, each star particle travels a radial distance sampled from 
-where $N(\mu, \sigma)$ represents a draw from normal distribution and $dt=20$\,Myr is the simulation timestep.%
 \footnote{Not shown here, we also explored variations of temporal, spatial resolution, migration strength, and the mass lifetimre relation. We found these do not affect median trends significantly.}
@@
 \end{equation}
-is adapted from \citet{hayden+14}.  We approximate $r=0.4$, and $\tau_\star/\tau_{\rm sfh} \approx 0.0$ \dbnote{double check this...}.
+is adapted from \citet{hayden+14}.  We approximate $r=0.4$, and $\tau_\star/\tau_{\rm sfh} = 0.0$ .
 This choice of $\eta(R)$ results in a [$\alpha$/H] gradient consistent with Milky Way observations \citep[e.g.][]{hayden+14, weinberg+19, frinchaboy+13}.
@@
 
-Finally, we tune the carbon yields of CCSNe in slope and normalization to approximately match the median trends in most cases.
-A tabulated description of our model parameters is available in appendix~\dbadd{model parameters}.
+\dbnote{moved this here since next subsection depends on representative sample}
+To create representative stellar samples to compare with APOGEE, 
+we draw \nsubgiants\ stars from the simulated stellar populations.
+First, we draw a random zone (weighted by number of subgiants in zone) and then draw a random particle in the zone weighted by SSP mass.
+Galactocentric radii are taken from astroNN \citep{leung+bovy19, leung+bovy19b}, however Gaia parallaxes yield a similar distribution.
+Alternative distributions of stars (including uniform distributions in 7-9kpc) minimally affect median trends.
+
+\subsection{Monte-Carlo Markov Chain Yield Inference} \label{sec:mcmc_methods}
+
+In GCE, total elemental abundances are (to first order) linear with respect to combinations of yields \citep[e.g.][]{WAF17}.
+\dbnote{might be useful to include a complete set of differential equations for our model somewhere to better illustrate this.}
+Assume that the yields do not depend on the yields (e.g. metallicity dependence is negligable). 
+Given a set of yields $\{y_X^i\}_i$ and resulting abundance evolution $\{Z_{X}^i(R, t) \}$, then if $y_X'$, the yield of X, is a linear combination of $\{y_X^i\}$, $y_X' = \sum_i \alpha_i\, y_X^i$ where $\alpha_i \in \mathbb{R}$, the abundance evolution of element X is
+\begin{equation}\label{eq:lin_combo}
+    Z_X'(R, t) = \sum_i \alpha_i Z_X^i(R, t).
+\end{equation}
+Therefore, we can efficiently explore combinations of yields without the need for full simulations.
+This allows for direct observational inference of the yield combinations which best agree with the data.
+We use Monte Carole Markov Chain (MCMC) inference to generate the posterior distributions of yield coefficients.
+Note that many other GCE parameters are nonlinear with abundance and require full multi-zone simulations, such as star formation history, outflows, and migration prescriptions.
+Also note that metallicity-dependent yields also introduce a second-order effect (metallicity depends on yields which depend on metallicity).
+
+Our first step is to run a multi-zone model tracking the abundances of each process we are interested in. 
+We focus on the binned \textit{mean} abundances of the low-$\alpha$ sequence in \caah, and the $-0.15 \leq {\rm [M/H]} \leq -0.05$ metallicity slice in \caafe\ (with 20 bin edges between -0.4 and 0.3 in [Mg/H] and 12 bin edges between 0.025 and 0.25 in [Mg/Fe]).
+We separate the C yield  into four different components
+\begin{enumerate}
+    \item $\alpha$. Prefactor for an AGB yield table
+    \item $\zetao$ Constant CCSN yield  ($y_0 = \zeta_0$)
+    \item $\zetai$ Linear CCSN yield ($y_1 = \zeta_1 \log Z/\Zo$) \footnotemark{}
+    \item $\zetaii$ Quadratic CCSN yield ($y_2 = \zeta_2 (\log Z/\Zo)^2$)
+\end{enumerate}
+The total C abundances for a linear of these yields is given from Eq.~\ref{eq:lin_combo}.
+Since we are taking means of each bin, there is a statistical uncertainty associated with the mean in a given bin, $\sigma_{i, \rm model}$. The total variance of the combined yield model is 
+\begin{equation}
+    \sigma^2_{\rm model} = \sum_{i} \alpha_i^2 \sigma^2_{i, \rm model}
+\end{equation}
+Similarly, we represent the mean and variance of the observations in each bin with $\bar Z_{b, \rm obs}$ and $\sigma^2_{b, \rm obs}$.  
+\begin{equation} \label{eq:mcmc_likelihood}
+    \log {\cal L} \propto \chi^2 = \sum_b \frac{(\bar Z_{b,\rm\ model} - \bar Z_{b,\rm\ obs})^2} {\sigma_{b, \rm tot}^2}
+\end{equation}
+where the total variance in a bin is 
+\begin{equation}
+    \sigma_{b, \rm tot} = \sigma_{\rm int}^2 + \sigma_{b, \rm obs}^2 + \sigma^2_{b, \rm model}
+\end{equation}
+where we model $\sigma_{\rm int}^2$ as a free parameter in the model.
+\footnotetext{In detail, $y_1$ and $y_2$ are held constant past $\log Z/\Zo < -2$ and the $y_1$ component is modelled with a positive constant offset later subtracted to avoid negative abundances.}
+
+We adopt the following priors
+\begin{subequations}
+\begin{align}
+    \alpha &\sim N(1, 1) \\
+    \zeta^{(0)} &\sim N(2, 1) \\
+    \zeta^{(1)} &\sim N(0, 1) \\
+    \zeta^{(2)} &\sim N(0, 4) \\
+    \ln \sigma _{\rm int}&\sim N(-3, 1) \\
+\end{align}
+\end{subequations}
+We run the MCMC using Turing.jl with a No-U-turn sampler (acceptance rate of 0.65), combining 8 chains with 10,000 steps each. \dbnote{todo: increase at least for fiducial}.
+
+To ensure this method is relatively robust, we will perform similar MCMC simulations varying the bin size and method, the MCMC sampler (Halmotonian, ensemble stretch moves from python-emcee, Metropolis-Hastings, Metropolis-Hastings random walk), the likelihood (including median U test, t-test, and KL-divergence based instead of mean + variance), and explore 2D bin likelihoods.
+In each case, the derived parameters are within their uncertainties (excluding the KS-divergence model).
+We check that removing the likelihood in \caafe{} causes $\alpha$ to become unconstrained, as $\alpha$ is degenerate with the CCSN yields in \caah.
 
@@
     Each line represents a zone at a different galactic radius and is colour-coded by time. While \caah\ settles into the final trend $\sim{8}$\,Gyr ago, \caafe\ continues to evolve for much longer.
+    \dbnote{radii between 2kpc and 15.5 kpc ?}
+    \dbnote{add equilibrium lines (green?)}
 }
@@
 
-Fig.~\ref{fig:c_evo} shows evolutionary tracks for every zone of the fiducial model for [C/Mg] against [Mg/H] and [Mg/Fe].
+% \begin{figure*}
+%     \centering
+%     \includegraphics{figures/subgiants_equilibrium_reproduced.pdf}
+%     \caption{
+%     Similar to Fig.~\ref{fig:subgiants} except for the stars of our fiducial model. 
+%     The solid, black lines show the equilibrium abundance track.
+The black scatter points with errorbars are the median bins for the low-$\alpha$ sequence (left) and the \caafe\ trend (right).
+The green solid line on the right shows the singlezone evolution of \caafe\ with properties matching our solar-annulus.
+The median trend of low-$\alpha$ stars is an excellent approximation for the equilibrium abundance of C.
+%     \dbnote{The more I look at this figure, maybe we just add green lines to Fig. 5 and skip this one}
+%     \dbnote{we add synthetic scatter found by fitting the metallicity-dependent reported errors with a linear fit in APOGEE and adding gaussian noise.}
+%     \dbnote{is there too much going on here?}
+%     \dbnote{would it make sense to maybe place this fig close to Fig.~1 since they are very similar so it is easier to compare? Not sure how to make continuity work then..}
+%     \label{fig:equilibrium_validity}
+%     }
+% \end{figure*}
+
+Fig.~\ref{fig:c_evo} shows evolutionary tracks for every zone of the fiducial model.
 \caah\ trend quickly reaches our equilibrium state in \about{5}\,Gyr. \caafe\ tracks continue to evolve due to the long tail in the DTD of \ia.
 
-The evolution of abundances in our fiducial model:
+The evolution of abundances in our fiducial model is as follows:
 \begin{enumerate}
-    \item[(1)] Star formation begins.
+    \item[(1)] {\it CCSN phase.} Star formation begins.
 Initially, \cc\ dominate enrichment.
@@
 [Mg/H] quickly approaches its equilibrium value, but Fe remains low in comparison (in agreement with \citealt{WAF17}).
-    \item[(2)]  A few hundred million years later,  delayed sources  enrich the ISM. \agb\ stars release C, raising [C/Mg], and \ia\ expel Fe, lowering Mg/Fe. 
-    \item[(3)] Several billion years later, [C/Mg] plateaus as C also approaches equilibrium. [Mg/H] reaches equilibrium. [Fe/H] continues to incrase due to ongoing \ia\ from old stellar populations.
-    \item[(4)] In the final few billion years, [C/Mg] decreases slightly due to declining \agb\ C yields. \caah\ trends shift only slightly, and [Mg/Fe] slowly and steadily decreases.
+    \item[(2)]  {\it AGB/SN Ia phase.} A few hundred million years later, delayed sources enrich the ISM. \agb\ stars release C, raising [C/Mg], and \ia\ expel Fe, lowering Mg/Fe. 
+    \item[(3)] {\it Approach to equilibrium.} Several billion years later, [C/Mg] plateaus as C also approaches equilibrium.
+[Mg/H] reaches equilibrium.
+[Fe/H] continues to increase due to ongoing \ia\ from old stellar populations.
+    \item {\it Present day.} The abundances of C, Mg, and Fe reach their equilibrium values.
 
 \end{enumerate}
-
-This evolution is driven most dominantly by our chosen elemental yields, their
-dependence on metallicity, and their DTDs.
-As we will demonstrate in section 5.2 below, the slope of the [C/Mg]-[Mg/H] trend is
-set by the relative contributions of CCSNe and AGB stars to the overall C abundance.
-The positive metallicity dependence of massive star C yields outweighs the negative
-dependence of AGB star yields, causing [C/Mg] to increase with [Mg/H].
-
-To create representative stellar samples to compare with APOGEE, 
-We draw \nsubgiants\ stars from the simulated stellar populations such that the selection probability is proportional to a stellar population's mass and that the subsample follows the same distribution in Galactocentric radius as the subgiants.
-Fig.~\ref{fig:equilibrium_validity} displays our sample of stars and compares them to analytic representations of the mean trend. 
-The median sequence of the low-$\alpha$ stars closely follows the {\it equilibrium track}, defined by the ratio between total C and Mg yields at each metallicity.
-There is a slight ($\sim{0.02}$ dex) divergence between the median track and equilibrium at higher metallicities, caused by our particular choice of C yields and the finite time it takes to reach equilibrium especially at higher metallicities with an increasing yield.
-However, if the low-$\alpha$ sequence is approximantly matched by our {it total} C yield, then we expect our model to agree with stellar observations.
-On the other hand, in \caafe\ equilibrium is a vertical line.
-As we assume both Mg and Fe yields are metallicity independent, there is only one value of [Mg/Fe] in the equilibrium sequence, corresponding to the low-$\alpha$ population.
-The median trend here instead reveals the delay time distribution of C, revealed by the green single-zone model included.
-
-Galactocentric radii are taken from astroNN {\color{red} citation}. \dbadd{Using Gaia parallaxes does not affect our conclusions.}
-
-% note about \caafe plane
-% As low-$\alpha$ stars were formed in regions closer to chemical equilibrium, we only plot the medians of the low-$\alpha$ sequences in \caah. 
-% Instead, \caafe\ trends are set by the proportion of \agb\ C contribution.
-The \caafe{}-diagram, when restricted to a narrow range of metallicities, becomes an empirical delay-time-distribution of C.
-% High-$\alpha$ stars were formed in regions further from chemical equilibrium than stars with low [Mg/Fe].
-Immediately after a star formation event, \cc\ elements dominate and only after sufficient time do \ia\ elements like Fe reach their higher-equilibrium abundances.
-% Likewise, high-[Mg/Fe] stars will have a greater portion of \cc\ C, as low-[Mg/Fe] stars will include more \agb\ C. 
-% When binned in metallicity, median [C/Mg] changes by about 0.2 dex across the range of [Mg/Fe] at solar metallicities.
-As high-$\alpha$ stars have little to no delayed \ia\ Fe, these stars would also have little to no delayed \agb\ C.
-This means that AGB C stars make up about at most a fraction $f_{\rm agb} \approx 1 - 10^{-0.2} \approx 0.4$ of C production.
-% 
-% \begin{figure}
-%     \centering
-%     \includegraphics{apogee_caafe_binned.pdf}
-%     \caption{Caption}
-%     \label{fig:caafe_binned}
-% \end{figure}
-
-\subsection{Equilibrium Framework}\label{sec:equilibrium}
-
+This evolution is predominantly driven by our chosen elemental yields, their
+metallicity dependence, and their DTDs.
+As we will demonstrate in Section~\ref{sec:agb_results} below, the final slope of \caah\ depends on both the contributions and metallicity dependences of CCSN and AGB C yields.
+Although AGB models predict declining C production with metallicity, the greater contribution and positive metallicity dependence of CCSN C outweigh declining AGB production.
+
+ Fig.~\ref{fig:c_evo} {\color{red} will} show the  equilibrium tracks in \caah\, and \caafe.
 Based on the \citepos{WAF17} analytic models of chemical equilibrium for constant star formation, the equilibrium abundance ratio between two elements depends only on the relative yields.
-For C/Mg, we have \dbstrike{ ,
-{james+23} demonstrate that the relationship between N and O can be
-explained by the metallicity dependence of their relative yields (see discussion
-in their section 4.6).
-We find similar results extending these arguments to C and Mg.
-The equilibrium C/Mg abundance ratio is 
-}
+For C/Mg,
 \begin{equation}\label{eq:equilibrium_yields}
@@
 \end{equation}
-\dbnote{
-where  the correction for a non-constant SFH is 
-\begin{equation}
-    \noneqagb \equiv \frac{\dot{M}_{\rm C}^{\rm AGB}}{\Ycagb\,\dot{M}_{\star}}
-\end{equation}
-}
+As such, the equilibrium abundance represents the steady-state expectation for C abundances.  
+However, in the \caafe\ plane, the equilibrium track is constant in [Mg/Fe] and only appears as a vertical line representing the range of equilibrium [C/Mg] values.
+The trends in \caafe\ are instead representative of the temporal evolution of [C/Mg].
+\caafe\ is well approximated by either a single-stellar-population or a single zone model because of the shallow metallicity gradient of the Milky Way.
+\dbnote{is this right?}
 
@@
 \begin{figure*}
-    \centering
-    \includegraphics{figures/subgiants_equilibrium_reproduced.pdf}
-    \caption{
-    Similar to Fig.~\ref{fig:subgiants} except for the stars of our fiducial model. 
-    The solid, black lines show the equilibrium abundance track.
-The black scatter points with errorbars are the median bins for the low-$\alpha$ sequence (left) and the \caafe\ trend (right).
-The green solid line on the right shows the singlezone evolution of \caafe\ with properties matching our solar-annulus.
-The median trend of low-$\alpha$ stars is an excellent approximation for the equilibrium abundance of C.
-    \dbnote{The more I look at this figure, maybe we just add green lines to Fig. 5 and skip this one}
-    \dbnote{we add synthetic scatter found by fitting the metallicity-dependent reported errors with a linear fit in APOGEE and adding gaussian noise.}
-    \dbnote{is there too much going on here?}
-    \dbnote{would it make sense to maybe place this fig close to Fig.~1 since they are very similar so it is easier to compare? Not sure how to make continuity work then..}
-    \label{fig:equilibrium_validity}
-    }
-\end{figure*}
-
-\begin{figure*}
     \includegraphics{sims_zeta_f.pdf}
@@
     \caption[]{
-\dbnote{out of date}
-    \dbnote{does it make sense to show SEM error bars instead of percentiles since we are focused on the median trend, not the spread?.}
         Stellar abundance trend predictions of our models .
@@
         Stars are binned into 20 (left) or 12 (right) equal number bins. 
-    \textbf{Top}: Models with different metallicity dependences for  \cc\ C yields. \textbf{Bottom}: Different \agb\ fractinos of C.
+        \textbf{Top}: Models with different metallicity dependences for  \cc\ C yields. \textbf{Bottom}: Models with different AGB C fractions $\fagb$ (only changing $\aagb$ and $\zetao$).
     }
@@
 
+The top of Fig.~\ref{fig:zeta_f} shows models with varying strengths of the $\Ycc$ metallicity dependence, $\zcc$.
+With higher $\zcc$, the model predicts a steeper \caah\ trend, owing to the direct relationship between the C/Mg equilibrium abundances and yield ratios.
+However, \caafe~is minimally affected by changes to $\zcc$ for stars at a given [Mg/H].
+CCSN occurs on much shorter timescales than AGB and SN Ia enrichment, so CC carbon reaches equilibrium before delayed C and Fe production modifies trends. 
+\footnote{The only effects on \caafe, when considering the narrow metallicity slice, are because of either the systematic change in equilibrium abundances, the imperfect evolution of the galaxy, or that the ISM abundances are set by stars which were born at poorer metallicities.
+}
+
+The bottom of Fig.~\ref{fig:zeta_f} shows three models with different C \agb\  fractions, defined as 
+\begin{equation}\label{eq:f_agb}
+    \fagb \equiv \frac{\Ycagb(\Zo)}{\Yct(\Zo)}.
+\end{equation}
+Modifications of $\fagb$ affect both \caafe\ and \caah.
+At fixed metallicity, the \caafe\ trend is principally sensitive to how much C and Fe comes from delayed sources.
+Increasing the \agb\ fraction therefore steepens the \caafe\ trend as expected.
+Though each yield model predicts the trend to flatten at ${\rm [Mg/Fe]} \lesssim 0.1 $, the median is still within the width of the observed distribution and the overall agreement is good.
+Additionally, increasing \agb\ contribution to C leads to a declining net slope for the total C yield owing to the negative slope of \agb\ C production with metallicity.
+
+\subsection{Yield Inference Results} \label{sec:mcmc_results}
+
+\begin{figure}
+\centering
+\includegraphics{figures/mcmc_corner.pdf}
+\caption[]{
+A corner plot of the posterior samples from the MCMC simulation for the fiducial + \fruity\ model fit to the binned mean trends.
+$\alpha$ represents the scale factor for the AGB yields, and $\zetao$, $\zetai$ and $\zetaii$ represent the constant, linear, and quadratic components of the CCSN yield.
+See section~\ref{sec:mcmc_methods} for a description of the methods.
+}
+
+\label{fig:mcmc}
+\end{figure}
+
 \begin{figure*}
-\includegraphics{sims_agb.pdf}
+    \centering
+    \includegraphics[]{figures/mcmc_fagb.pdf}
+    \includegraphics[]{figures/mcmc_y_tot.pdf}
 
     \caption[]{
-    Similar to Fig.~\ref{fig:zeta_f} except showing the mean tracks for different (unscaled) AGB yield tables with best-fit CCSNe parameters.
-Variations in the \caafe\ plane are due to the different total AGB C yield and variations in the mass-dependence of each yield table.
-}
-\label{fig:agb_predictions}
+    \textbf{Left:} Posterior distribution of $\fagb$ from MCMC samples for each model we show.
+Regardless of assumptions, the best values of $\fagb$ range from about 0.1 to 0.35 and in all cases is less than 0.5.
+    \textbf{Right:} The final total C yield (CCSN + AGB) for the median parameters from MCMC fits for each model.
+Additionally, we show individual samples from the \fruity{} \ MCMC model as faint blue lines.
+    \dbnote{mark alpha=1.}
+    }
+
+    \label{fig:mcmc_ytot}
 \end{figure*}
+
+Fig.~\ref{fig:mcmc} shows the distribution and correlation of each parameter in the fiducial MCMC model.
+Each parameter is relatively well-constrained.
+The most prominent correlation, between $\zetao$ and $\alpha$ represents the constraint on the equilibrium abundance of C near solar.
+The other main correlation, between $\zetai$ and $\zetaii$, arises from the shape of the \caah\ trend.
+If the quadratic component decreases, then the \caah\  slope (past [Mg/H] $\lesssim 0.1$) increases, so the linear component must decrease in order to maintain agreement with the data.
+
+Table~\ref{tab:mcmc_results} contains the resulting posterior distributions for each parameter for a variety of both AGB models and GCE assumptions. 
+For the fiducial model, the best fit yields are 
+\begin{equation}
+    \frac{\Ycc}{y_{\rm Mg}} = (2.01\pm  0.08) + (2.20 \pm 0.15) x + (2.73 \pm 0.31) x^2
+\end{equation}
+where $x = \log Z/\Zo$.
+Fig.~\ref{fig:mcmc_ytot} shows the AGB fraction at solar metallicity and the total C yield with metallicity for each MCMC run. 
+In essentially each case, the majority of samples have a AGB fraction between 0.15 and 0.4.
+
+\begin{table*}
+
+    \caption{
+    Best-fit parameters (medians and 16-84th percentile errors) from MCMC analysis for various models discussed.
+    The columns are:  modelname \textit{model}, best fit reduced $\chi^2$, best fit log posterior probability $\log p$, AGB scaling $\aagb$, 
+    \dbnote{Not sure if we should use analytic, nugrid, shifted fruity or normal fruity yields as fiducial for this section, e.g. for eta, lateburst, twoinfall, etc...}}
+    \label{tab:mcmc_results}
+{ 
+\renewcommand{\baselinestretch}{1.2}
+    \begin{tabular}{l l l l l l l l l l l} 
+    \hline
+    model            & $\chi2$  & $\log p$ & $\aagb$ & $\zetao$ & $\zetai$ & $\zetaii$ & $\sigma_{\rm int}$ & $\fagb$ & $\Yct$ & $\zeta_{\rm 1, tot}$\\
+\hline
+fruity           &      6.9 &    20.06 & $1.96^{+0.21}_{-0.21}$  &  $2.01^{+0.08}_{-0.08}$  &  $2.20^{+0.15}_{-0.15}$  &  $2.73^{+0.31}_{-0.31}$  &  $0.08^{+0.02}_{-0.01}$  &  $0.27^{+0.03}_{-0.03}$  &  $2.75^{+0.02}_{-0.02}$  &  $1.52^{+0.13}_{-0.13}$\\
+fruity m0.7      &      6.3 &    28.60 & $1.10^{+0.10}_{-0.10}$  &  $2.33^{+0.04}_{-0.04}$  &  $1.71^{+0.11}_{-0.11}$  &  $2.89^{+0.27}_{-0.27}$  &  $0.06^{+0.01}_{-0.01}$  &  $0.17^{+0.01}_{-0.01}$  &  $2.80^{+0.01}_{-0.02}$  &  $1.37^{+0.10}_{-0.10}$\\
+aton             &     10.5 &    10.66 & $1.56^{+0.24}_{-0.24}$  &  $2.50^{+0.04}_{-0.04}$  &  $3.37^{+0.32}_{-0.32}$  &  $2.50^{+0.40}_{-0.39}$  &  $0.11^{+0.02}_{-0.02}$  &  $0.08^{+0.01}_{-0.01}$  &  $2.72^{+0.02}_{-0.02}$  &  $1.81^{+0.17}_{-0.17}$\\
+monash           &     10.8 &     6.86 & $2.06^{+0.37}_{-0.39}$  &  $1.92^{+0.16}_{-0.15}$  &  $3.68^{+0.42}_{-0.45}$  &  $3.52^{+0.47}_{-0.47}$  &  $0.13^{+0.03}_{-0.02}$  &  $0.23^{+0.05}_{-0.05}$  &  $2.49^{+0.05}_{-0.05}$  &  $1.41^{+0.20}_{-0.19}$\\
+nugrid           &      6.1 &    23.68 & $1.00^{+0.10}_{-0.10}$  &  $1.75^{+0.10}_{-0.10}$  &  $1.58^{+0.12}_{-0.12}$  &  $3.19^{+0.31}_{-0.30}$  &  $0.07^{+0.02}_{-0.01}$  &  $0.32^{+0.03}_{-0.03}$  &  $2.58^{+0.02}_{-0.02}$  &  $1.12^{+0.12}_{-0.13}$\\
+analytic         &      5.1 &    29.80 & $0.43^{+0.04}_{-0.04}$  &  $2.33^{+0.04}_{-0.04}$  &  $1.57^{+0.10}_{-0.10}$  &  $2.69^{+0.27}_{-0.26}$  &  $0.06^{+0.01}_{-0.01}$  &  $0.15^{+0.01}_{-0.01}$  &  $2.75^{+0.01}_{-0.01}$  &  $1.15^{+0.10}_{-0.11}$\\
+eta2             &      6.6 &    24.28 & $0.47^{+0.05}_{-0.04}$  &  $2.24^{+0.05}_{-0.05}$  &  $1.45^{+0.09}_{-0.10}$  &  $2.95^{+0.32}_{-0.32}$  &  $0.07^{+0.02}_{-0.01}$  &  $0.17^{+0.02}_{-0.02}$  &  $2.71^{+0.02}_{-0.01}$  &  $0.98^{+0.09}_{-0.09}$\\
+lateburst        &      8.0 &    21.72 & $0.56^{+0.05}_{-0.05}$  &  $2.25^{+0.05}_{-0.05}$  &  $1.75^{+0.18}_{-0.18}$  &  $2.55^{+0.37}_{-0.36}$  &  $0.08^{+0.02}_{-0.01}$  &  $0.20^{+0.02}_{-0.02}$  &  $2.81^{+0.02}_{-0.02}$  &  $1.19^{+0.18}_{-0.18}$\\
+twoinfall        &      6.3 &    17.12 & $0.54^{+0.06}_{-0.06}$  &  $2.31^{+0.07}_{-0.07}$  &  $1.72^{+0.19}_{-0.20}$  &  $1.69^{+0.30}_{-0.30}$  &  $0.09^{+0.02}_{-0.02}$  &  $0.19^{+0.02}_{-0.02}$  &  $2.85^{+0.02}_{-0.03}$  &  $1.18^{+0.20}_{-0.20}$\\
+fruitylin       &    &    & $1.95$  &  $2.10^{+0.02}_{-0.02}$  &  $1.55^{+0.08}_{-0.08}$  &     &  $0.09^{+0.02}_{-0.01}$  &  $0.26^{+0.00}_{-0.00}$  &  $2.84^{+0.02}_{-0.02}$  &  $0.87^{+0.08}_{-0.08}$\\
+analyticlin     &    &    & $0.43$  &  $2.41^{+0.02}_{-0.02}$  &  $0.89^{+0.09}_{-0.09}$  &     &  $0.10^{+0.02}_{-0.01}$  &  $0.15^{+0.00}_{-0.00}$  &  $2.84^{+0.02}_{-0.02}$  &  $0.46^{+0.09}_{-0.09}$\\
+\hline
+total & &   &  -  &  $2.26^{+0.11}_{-0.37}$  &  $1.74^{+1.53}_{-0.24}$  &  $2.79^{+0.49}_{-0.58}$  &  $0.08^{+0.03}_{-0.02}$  &  $0.19^{+0.09}_{-0.04}$  &  $2.74^{+0.07}_{-0.16}$  &  $1.26^{+0.32}_{-0.24}$\\
+\hline
+    \end{tabular}
+
+}
+
+\end{table*}
+
+\subsection{Unknowns and Degeneracies} \label{sec:sfh} \label{sec:outflows}
+\label{sec:degeneracies}
 
@@
         {\bf Right} alternate star formations and a model where yields and outflows are $\sim$ doubled.
-
-    \dbnote{the left panel is the +- 3 sigma range of models from the MCMC analysis.
-I suspect the errors are very underestimated and I am not sure how to approach it, but the plot might make more sense if the model has the right curvature (like mass factor 0.7).
-There are 100+ observations per bin so maybe we need to account for apogee systematics as well??}
-
-    \dbnote{I looked into the halved yields model.
-Since in this paper, we assume $y_o/Z_o \sim 1$, it is essentially impossible to reach solar Z when halfing the yields.
-I am swapping for all yields are doubled and I think if a referee complains about our choice of $\eta\sim0.4 \ne 0$ at the sun, we can deal with that later}
-
-    \dbnote{the mass shifts change the net C production, so I may change the $\alpha$ values for these models so they are easier to compare here}
+    \dbnote{update caption here}
     }
@@
 
-The top of Fig.~\ref{fig:zeta_f} shows models with varying strengths of the $\Ycc$ metallicity dependence, $\zcc$.
-With higher $\zcc$, the model predicts a steeper \caah\ trend, owing to the direct relationship between the C/Mg equilibrium abundances and yield ratios.
-However, \caafe~is minimally affected by changes to $\zcc$ since \cc\ occurs on much shorter timescales than \ia\ and \agb\ enrichment.%
-\footnote{The only effects on \caafe, when considering the narrow metallicity slice, are because of either the systematic change in equilibrium abundances, the imperfect evolution of the galaxy, or that the ISM abundances are set by stars which were born at poorer metallicities.
-}
-%  Hence, \caah\ tells us about the total C yield with metallicity, which \caafe\ is independent of.
-If we know the \agb\ C yields, then with observed \caafe\ abundance trends, we can infer the \cc\ C yields with metallicity.
-
-The bottom of Fig.~\ref{fig:zeta_f} shows three models with different C \agb\  fractions, defined as 
-\begin{equation}\label{eq:f_agb}
-    \fagb \equiv \frac{\Ycagb(\Zo)}{\Yct(\Zo)}.
-\end{equation}
-Modifications of $\fagb$ affect both \caafe\ and \caah.
-At fixed metallicity, the \caafe\ trend is principally sensitive to how much C and Fe comes from delayed sources.
-Increasing the \agb\ fraction therefore steepens the \caafe\ trend as expected.
-Though each yield model predicts the trend to flatten at ${\rm [Mg/Fe]} \lesssim 0.1 $, the median is still within the width of the observed distribution and the overall agreement is good.
-Additionally, increasing \agb\ contribution to C leads to a declining net slope for the total C yield owing to the negative slope of \agb\ C production with metallicity.
+\begin{figure*}
+    \includegraphics[]{figures/mcmc_caahfe_predicted.pdf}
+
+    \caption[]{
+        Similar to Fig.~\ref{fig:zeta_f} except showing the mean tracks for different best-fit AGB yield tables with best-fit CCSNe parameters.
+Variations in the \caafe\ plane are due to the different total AGB C yield and variations in the mass-dependence of each yield table.
+    \dbnote{use actual best fit median trends here instead of inferred yields? Update labels, remove one of analytic / fruity m0.7}.
+    }
+    \label{fig:agb_predictions}
+\end{figure*}
+
+Assumptions about the AGB yields, the star formation history, and outflows negligibly impact \caah\ due to chemical equilibrium.
+However, these degeneracies can inform and affect the interpretation of \caafe.
 
@@
 Models with little to no AGB C production will produce stars with [C/Mg] independent of [Mg/Fe] in a metallicity slice.
-As the AGB fraction increases to an extreme $f^{\rm AGB}=0.5$, the trend becomes much steeper than the fiducial but remains a mere rescaling of the same shape.
+As the AGB fraction increases to an extreme $f^{\rm AGB}=0.5$, the trend becomes steeper than the fiducial but remains a rescaling of the same shape.
 
 A second factor affecting \caafe\ is the assumed delay time distribution of \agb\ carbon production.
-The middle panel of Fig.~\ref{fig:sims_degens} shows models where the AGB yields have been shifted by some factor in mass.
-When the AGB C production is weighted towards more massive AGB stars, then the delay time distribution becomes more like CCSN.
-As such, the predicted \caafe\ trend resembles the model which only contains CCSN production.
-The \caafe\ trend therefore is much less sensitive to the C production by stars with masses $M \gtrsim 5 \Mo$.
-On the other hand, shifting the C production towards low mass stars changes both the shape and amplitude of the DTD.
-This is evident in a transition point, where the \caafe\ trend changes slope.
-For the most extreme case, where the masses are shifted by a factor of 0.5; the AGB production is more delayed than SNeIa, causing a steepining of \caafe\ towards low [Mg/Fe].
-Intermediate values are more linear in \caafe, matching the observed trend.
-We note that the fiducial model instead transitions from steep to shallow as [Mg/Fe] decreases.
-This is evidence that AGB C likely needs to be weighted more towards low mass stars than is predicted by current AGB stellar models.
-
-Considering the effects of changes in the amplitude and mass of AGB C production, we can now predict and understand the differences between different yield tables.
-Fig.~\ref{fig:agb_predictions} show the four C yield models (\fruity, \aton, \monash, \nugrid, with no scaling).
-For the most part, different \agb\ yield tables result in qualitatively similar predictions.
-While small adjustments in the \cc\ yields results in identical tracks through \caah, each model predicts slightly different tracks in \caafe.
-Differences are due to the total C production from the AGB model, and the delay time distribution of the model.
-For example, V13 predicts that AGB stars produce almost net zero C at solar metallicity, and \monash\ predicts the shortest delay time distribution of all models.
-These models thus are almost consistent with pure \cc\ enrichment of C.
-Additionally, \nugrid\ yields are about double \fruity, resulting in a steeper slope in \caafe.
-%\aton, however, does not reproduce solar trends as the model predicts strong C destruction at slightly super-solar metallicities, resulting in inversions in both \caah\ and \caafe. 
-As all \agb\ models predict C yields to decline with metallicity, all models predict an increasingly downward slope in \caafe\ with [Mg/Fe].
-A recent burst in star formation may hide this downturn (see section~\ref{sec:sfh}), but C destruction at the level predicted by \aton\ is not supported by our sample.
-Because the effects of alternate \agb\ yield sets are small, we focus on \fruity{} model for the remained of this paper. Alternate yield sets minimally affect our conclusions.
-
-\dbadd{the inter-study differences for AGB yields can be explained by the differing mass dependence, and the metallicity dependence.}
-
-\subsection{Variations in Star Formation History} \label{sec:sfh}
-In this section, we consider an alternate SFH, namely one which exhibits a late-time elevation in the star formation rate.
-Motivated by the findings of \citet[see discussion in \JJ]{mor+19,isern19}, this \textit{lateburst} model
+The middle panel of Fig.~\ref{fig:sims_degens} shows models where the AGB yields have been shifted by a factor in mass.
+When the AGB C production is weighted towards more massive AGB stars, then the delay time distribution becomes more rapid, causing equilibrium to be reached sooner (at higher [Mg/Fe]).
+The \caafe\ trend therefore is less sensitive to the C production by stars with masses $M \gtrsim 5 \Mo$ \dbnote{calculate timescales here}.
+On the other hand, shifting the C production towards low mass stars extends the DTD towards longer times.
+In Fig.~\ref{fig:sims_degens}, models shifted towards lower masses increase the amplitude of the \caafe\ trend, particularly steepening the high [Mg/Fe] slope.
+For the most extreme case, where the masses are shifted by a factor of 0.5; the AGB production is more delayed than SNeIa, causing an increasing slope of \caafe\ towards low [Mg/Fe].
+An intermediate mass shifts (0.7) is approximant linear in \caafe, qualitatively matching the observed trend.
+
+Fig.~\ref{fig:agb_predictions} shows the resulting median trends in \caah\ and \caafe\ for the median parameters for each AGB model.
+Regardless of the AGB model, there is a reasonable choice of \cc\ yields which can closely match the \caah\ trend.
+All AGB models predict similar \caafe\ trends.
+However, each (unshifted) yield table underpredicts the slope of \caafe\ at low [Mg/Fe].
+As discussed above, the relative flattening in \caafe\ results from a AGB DTD that is more prompt than SNe Ia.
+Also, note that the median parameters (from Table~\ref{tab:mcmc_results}) suggest an amplification of AGB yields of between 1.5 and 2 for all models except \nugrid.
+Without this amplification, the overal trend in \caafe\ would be much flatter than is observed.
+We suggest that most AGB yield models require an increase in the amplitude of C production and a weighting of C production more towards low mass stars in order to better match observations in this GCE framework.
+
+We consider two alternative SFHs. 
+Motivated by the findings of \citet[see discussion in \JJ]{mor+19,isern19}, the \textit{lateburst} model
 adds a Gaussian burst to the fiducial inside-out model, 
@@
 
-We additionally consider a two-infall like model as presented in \dbadd{dubay + 24}, which is defined as.
-
+We also consider a two-infall like model as presented in \dbadd{dubay + 24}, which is defined as.
 \begin{equation}\label{twoinfall}
-\dot{\Sigma}_{\rm in} \propto exp(-t/\tau_1) + A_{2,1} \theta(t - t_{1}) \exp(-t/\tau_2)
-\end{equation}
-
-where $\tau_1=0.4\,$Gyr, $\tau_2$/G is 1/2 of the value from Sanchez, $A_{2,1}=0.5$, $t_1=4.1$, and the star formation also abruptly transitions from $\nu=2$/Gyr to $\nu=1$/Gyr at $t=t_1$.
+\dot{\Sigma}_{\rm in} \propto e^{-t/\tau_1} + A \theta(t - t_{2}) e^{-t/\tau_2}
+\end{equation}
+where $\tau_1=\#\,$Gyr, $\tau_2=4\,$Gyr, $A=\Sigma_{\rm thin} / \Sigma_{\rm thick}$ \dbadd{explanation}, $t_2=4$, and the star formation also abruptly transitions from $\nu=2$/Gyr to $\nu=1$/Gyr at $t=t_1$?
 
 The right panel of Fig.~\ref{fig:sims_degens} compares the fiducial, lateburst, and two-infall models.
-The lateburst slightly shifts \caah\ down and only slightly perturbs \caafe.
-These variations are small compared to the width of the observed distribution.
-Building on \citet{james+23}, we therefore conclude that the \caah\ and \caafe\ trends reflect nucleosynthetic yields more than the Galactic SFH.
-
-\dbnote{there has to be a good reason why \caafe\ is not affected or maybe only more extreme pertubations make a difference?}
-
-\subsection{Degeneracies} \label{sec:outflows}
+The pertubations to \caafe\ are small.
+The largest change is to the distribution of [Mg/Fe], but the \caafe\ trends are identical for the lateburst or is slightly shifted and steeper for the two infall model.
+So, variations due to SFH considered here are most likely smaller than width of the observed distribution.
+Building on \citet{james+23}, we conclude that the \caah\ and \caafe\ trends reflect nucleosynthetic yields more than the Galactic SFH. 
+\dbnote{There has to be a good reason why \caafe\ is not affected or maybe only more extreme pertubations make a difference?}
 
@@
 We consider a model where we double all yields, in the right panel of Fig.~\ref{fig:sims_degens}. A uniform change in yields and outflows leaves our median trends relatively unchanged. 
-
-\dbnote{paragraph about how fagb and zeta are interdependent, but not fully degenerate in \caafe.}
+\dbnote{This paragraph is slightly off, the actual value of eta around the sun is only 0.5 so reducing outflows more does not keep metallicity gradient. Do we need to change framing here?}
 
@@
 Not shown here, if both processes increase by a similar proportion of the total yield, then our predictions in \caafe\ are unchanged.
-Therefore, we cannot know the DTD of C much better than that of Fe in this framework.
+Therefore, we cannot know the DTD of C more accurately than that of Fe in this framework.
 
 \dbnote{Other things to discuss possibly ? :
- Initial mass function (and possible metallicity dependence)? Metallicity-Dependent Oxygen/Magnesium and Iron yields? Gas phase migration / ISM cooling?  MLR
+ Initial mass function (and possible metallicity dependence)?
+ISM stochasticy and inhomogeneities.
+Metallicity-Dependent Oxygen/Magnesium and Iron yields?
+Gas phase migration / ISM cooling?
+mass-lifetime relation.
+Spectroscopic systematics.
  }
@@
 We are able to closely match the [C/N]-[Mg/H] trend.
+\dbnote{sentence about [C/N]-[Mg/Fe]}
 
@@
 \caption[]{
+\dbnote{will probably add each SZ model description to fig caption. Should citations be moved outside of caption for reader's sake?}
+\dbnote{remove connecting lines on MW HII regions. Should I plot outliers at all?}.
 Gas-phase C abundances. 
-We plot the fiducial model's present-day ISM abundances as a thick blue line (\protect\captionline[line width=1.5pt]{blue}).
+We plot the fiducial model's present-day ISM abundances as a thick blue line.
 Black lines are single-zone models: a fiducial yields and MW-like model (solid black), and three corrected yield models representing the MW (dotted), GSE (dashed) and Wukong (dash-dots).
@@
 As a final test of our model, we compare the predictions against C abundances
-in the gas-phase.
-These measurements are challenging since C lacks strong collisional excitation
-lines, and its recombination lines fall in the ultraviolet with no nearby
-H lines to reference~\citep[e.g.,][]{skillman+20}.
-These two classes of spectral lines are also systematically discrepant at the
-factor of~$\sim$2 level~\citep{GR07}.
-As a consequence, the uncertainties associated with any one measurement are
-substantial (see the representative error bars in Fig. 13), but we are able to
-illuminate the underlying mean trends by combining observations from multiple
-sources.
-\dbnote{I believe that dust might warrent a discussion here since this can capture gas-phase metallicity, substantially affecting observations.
-But we also just don't know how to measure gas-phase abundances well at all.
-Reassuring as it means that our focus on stars is very justified.
-There is an additional complication that CEL and RL abundances (especially for O) need to be put on the same scale with +0.2 dex corrections, and there is not a clear understanding which one is better.
-\citet{MM19}
-}
-
-\dbnote{does it make sense to include more high-redshift galaxies? 
-Many of these seem to be through stacked spectra or other challenging measurments, e.g. redshifting the CEL lines in Berg++ dwarfs at $z\sim 2$
-}
-
-DLAs are .......
-Most similar tothose in local group dwarfs (Cooke+2015, berg+2015, cia+2016 from MM2019 review).
-
-Fig.~\ref{fig:gas_phase} shows our compilation alongside the gas-phase abundances in our model
-at snapshots of~$t = 2$ Gyr and the present day.
+in the gas phase.
+Besides stellar observations, C has been observed in extragalactic HII regions, high redshift galaxies (HII regions), metal-poor stars, and Damped-Lynman-$\alpha$ systems (DLAs).\footnote{DLAs are gas clouds observed as absorption spectra in front of background quasars}
 While we used Mg as our representative alpha element in our APOGEE sample, O
@@
 section.
-The model at the present day is consistent with the mean trend seen in HII
-regions in the MW and similar star forming galaxies at redshift~$z \sim 0$.
-Together with our results in~\S~5, this agreement suggests that our yield model
-is an accurate description of C nucleosynthesis at metallicities typical of
-MW-like galaxies.
-
-Nonetheless, our model does not extend as low in metallicity as dwarf galaxies
-or (especially) damped Lyman-alpha systems.
-To test our model at these abundances, we show 4 different one-zone GCE models.
+HII measurements of C are challenging since C lacks strong recombination lines (RL)
+ and its collisional excited lines (CEL) fall in the far ultraviolet without nearby reference H lines \citep[][]{skillman+20}.
+Furthermore, CEL and RL derived abundances are systematically discrepent by \about{0.5}\,dex \citep{GR07}.
+Metals may also be trapped in dust grains or in unobserved ionization states, requiring additional modeling \citep{MM19}.
+As a consequence, the uncertainties of HII abundances are substantial (see representative error bars on Fig.~\ref{fig:gas_phase}).
+\dbnote{
+There is a complication I have not done that CEL and RL abundances (especially for O) need to be put on the same scale with +0.2 dex corrections.
+Probably need to double check derivations of metallicities...
+}.
+DLAs, on the other hand, are relatively precise because these regions are lower-ionization, have a well-defined region (column density) and often have high-quality spectra covering rest-frame UV and optical {\color{red} CITE/verify}.
+
+Fig.~\ref{fig:gas_phase} compiles literature measurements of DLAs, HII regions (MW, extragalactic, dwarfs), high redshift galaxies, and MW halo/thick disk stars.
+Despite the inhomogeneities, uncertainties, and variety of systems, there is still a coherent global trend.
+Near solar metallicities, most observations (from disky galaxies) have near-solar [C/O].
+As metallicity decreases, [C/O] also decreases, reaching a minimum of \about{-0.6} around ${\rm [O/H] \sim -1}$.
+Finally, [C/O] appears to increase again at the lowest metallicities observed (${\rm [M/H] \lesssim -2}$).
+
+Fig.~\ref{fig:gas_phase} also shows the present-day gas phase abundance of our fiducial model and several single-zone models.
+The gas phase predictions of our multizone model agree reasonably with MW (and similar metallicity extragalactic) HII regions.
+Stellar abundance remain, comparatively, a more stringent constraint.
+To better represent the evolution of low-metallicity and dwarf galaxy environments, we create an illustrative suite of single-zone models.
+These models evolve only a single, homogenous gas supply.
+We assume a constant star formation efficiency $\dot M_\star = M_{\rm gas} / \tau_\star$.
+We also use an exponential infall history for dwarf galaxies of the form
+\begin{equation}
+    \dot\Sigma_{\rm in} \sim e^{-t/\tau_{\rm sfh}}.
+\end{equation}
+Yields are set to the best-fit analytic AGB model, but low metallicity evolution is predominantly driven by the choice of CCSNe C yields.
+We introduce an alternate CCSNe model to better agree with these low-$Z$ observations.
+\begin{equation} 
+    \Ycc / 10^{-3} = \begin{cases}
+        0.8 & \log Z / \Zo < -1.81 \\
+        2.41 + 0.89\, \log Z / \Zo & {\rm otherwise }
+    \end{cases}
+\end{equation}
+where the low-metallicity limit was chosen to match the approximate minimum of observed [C/O] values.
+The models shown in Fig.~\ref{fig:gas_phase} have the parameters: 
 \begin{enumerate}
-    \item Fiducial MW: $\eta=0.5$, $t_{\rm end} = 13.2$, $\tau_\star=2$, $\tau_{\rm sfh} = 14$
-    \item Corrected MW-like. 
-    \item Corrected Gaia-Sausage Enceledus like. $\eta=9.56$, $t_{\rm end}=10.73$, $\tau_\star = 26.60$, $\tau_{\rm sfh} = 2.18$, infall mode
-    \item Corrected Wukong-like: $\eta=47.99\pm 5$, $t_{\rm end} = 3.36\pm 0.5$, $\tau_\star=44.97\pm 7$, $\tau_{\rm sfh} = 3.08\pm 1$, infall modej
+    \item Fiducial MW. Solid black line. $\eta=0.5$, $t_{\rm end} = 13.2$, $\tau_\star=2$, $\tau_{\rm sfh} = 14$, insideout SFH.
+    \item Corrected MW-like. Dotted. Same parameters as  fiducial single-zone but with corrected yields.
+    \item Corrected Gaia-Sausage Enceledus like. Dashed. $\eta=5.74$, $t_{\rm end}=10.73$, $\tau_\star = 26.60$, $\tau_{\rm sfh} = 2.18$, infall mode
+    \item Corrected Wukong-like. Dash-doted. $\eta=28.8$, $t_{\rm end} = 3.36$, $\tau_\star=44.97$, $\tau_{\rm sfh} = 3.08$, infall mode
 \end{enumerate}
-with the exception of the fiducial like model, we use the bi-log-linear CCSNe yield model which plateaus at a [C/Mg] at low metallicity consistant with observations of metal-poor stars and dwarf galaxies.
 \dbnote{check timescales to metallicity = -1 (could sagb affect the trends here?). Also try different yield sets for these just to see if any agree naturally... }
 
-Fig.~\ref{fig:gas_phase} also plots a single-zone model and time-slices of the fiducial multi-zone models gas-phase at present day and $t=2$\,Gyr. 
-Our single-zone model is designed to have parameters broadly consistent with the Gaia-Encelidus sausage.
-We evolve the singlezone model for 2\,Gyr, using mass loading $\eta=20$, star formation efficiency $\tau_{\star}=30\,{\rm Gyr}$, and a star formation history $\propto e^{-t/3{\rm\,Gyr}}$.
-The single-zone model uses a 1.5 mass factor times f=0.25 C11 yields.
-Note that the mass shift results in significant C destruction by high-mass AGB stars at low metallicities, enabling the model to reproduce the low [C/O] abundances at [O/H] = -1.
-
-Each of these one-zone models predicts a steeper C/O-O/H trend than our
-fiducial multi-ring model from previous sections.
-This difference arises because the trend in the multi-ring models arises as a
-superposition of end-points (see Fig.~\ref{fig:c_evo}), qualitatively similar to, e.g.,
-\citepos{schonrich-binney09} argument regarding
-the low-alpha sequence.
-In the one-zone models, the trend instead arises as an evolutionary sequence.
-To demonstrate this point further empirically, Fig.~\ref{fig:gas_phase} includes measurements
-in halo and thick disk stars.
-This sample indeed shows a C/O-O/H trend that is clearly steeper than our
-fiducial multi-ring model, which is an accurate representation of the APOGEE
-low-alpha sequence (see Fig. 8).
-
-At the lowest metallicities ($\log_{10}(Z / Z_\odot) \lesssim -2$), our suite
-of one-zone models is consistent with the C/O ratios seen in damped Lyman-alpha
-systems.
-For all parameter choices, these ratios simply reflect the relative C and O
-yields of low-metallicity massive stars (see Fig. 5), with the increase in C/O
-at higher metallicities arising due to the onset of AGB star enrichment (see
-Fig. 7).
-As a consequence, our yield model as parameterized predicts that C/O ratios
-should never be significantly below~$\sim$half solar.
-This prediction is challenged by the measurements in both dwarf galaxies and
-halo/thick disk stars in Fig.~\ref{fig:gas_phase}, which suggest ratios~$\sim$$0.2 - 0.3$ dex
-below solar between~$\log$(O/H) = X and Y.
-
-This discrepancy could arise at least in part due to failures of our yield
-prescription and, by extension, could point to shortcomings in stellar
-nucleosynthesis models.
-However, we cannot rule out the possibility of systematic uncertainties in
-abundance determinations playing a role.
-At these metallicities, deviations from local thermal equilibrium (LTE) can
-bias measurements at the~$\sim$0.2 dex level~\citep[e.g.,][]{amarsi+19}.
-Considerations of non-LTE effects are not included in our APOGEE sample, but
-the corrections are smaller near solar metallicity.
-
-\dbnote{Discussion on a complex landscape of C production: elevation at lowest metallicities but with stochastic mixing, Pop III and many other problems; declining at [O/H] = -1, increasing due to Z-dependent CCSNe and delayed AGB enrichment up to 0, and flat in disks due to chemical equilibrium, but maybe also more flat CCSNe too.}
-
-\dbnote{depending on what everyone thinks, may be worth discussing CEMPs since they have enough literature although not necessarily relavent here.
-Carigi+Peimbert 2011, Molla+2015.
-Lyman limit systems in Lehner+2016.}
-
-\dbnote{other stellar surveys...
-Gustafsson+1999, bensby\&feltzing+2006, Spite+2005, Neiva \& Przybilla+2012, Tautvaisiene+2016.}
+When comparing the MW-like single-zone model to the fiducial final gas-phase abundances, notice that the slope of the singlezone track near solar metallicities is steeper. 
+While the trend in the multi-zone models arises as a
+superposition of end-points, the single-zone trend instead arises as an evolutionary sequence (see Fig.~\ref{fig:c_evo}).
+The increase in [C/O] abundances is a result of both delayed AGB contribution and the metallicity-dependent C CCSNe yields.
+The halo and thick disk stars also support that the past [C/O] abundances were increasing with metallicity, in contrast to the near-constant [C/O] of the low-$\alpha$ sequence.
+The initial [C/O] value of these single-zone mdoel is governed by the respective ratio of C to O yields.
+As a result, the fiducial yield set predicts too high of a minimum [C/O], motivating our corrected yields.
+With the corrected yield set, the single-zone models are able to reproduce the general trend of [C/O] with metallicity.
+An alternative explanation is that more C comes from delayed sources than is predicted by our fiducial model.
+However, reaching the [C/O] minimum of -0.6 requires that \about{75\%} of C comes from AGB stars, which is not reconcilable with the stellar \caafe\ trend.
+
+SFH variations likely explain part of the observed scatter in Fig.~\ref{fig:gas_phase}. 
+In our models, variations in the SFHs change when [C/O] begins to increase with metallicity and the final [C/O] value of the model.
+Similar to [O/Fe] trends with metallicity, the slower and burstier SFH of dwarf galaxies causes delayed sources to affect abundance ratios at a lower metallicity than for MW-like systems.
+
+Our single-zone models do not capture the elevated [C/O] ratio at the lowest metallicities.
+This could be remedied by modifying our CCSNe yield, but low-metallicity C abundances are beyond our scope.
+Additionally, inhomogeneous mixing and individual contributions from supernovae become important in this regime, adding additional scatter and complexity to modelling.
+\dbnote{Are CEMPs worth mentioning here? since they have enough literature although not necessarily relavent here. Carigi+Peimbert 2011, Molla+2015.}
+
+Altogether, our yields (with some adjustments) are able to reproduce the global C trend from dwarf galaxies to solar metallicity MW-like galaxies.
 
@@
 
-\section{Monte-Carlo Markov Chain inference}
-
-As a way to quickly explore which combinations of yields agree with \caah, and \caafe, we run Monte Carloe Marcov chains using the following approximation framework.
-We intend these results to be more illustrative and first order, as the number of approximations and systematics in the analysis is substantial.
-
-\subsection{Methods}
-
-As a first step, we hold all GCE parameters except for the C yield constant for each MCMC model.
-We additionally assume that the metallicity is that of the fiducial yield set, to avoid second-order effects from metallicity-dependent yields.
-We then seperate each process into four different components
-\begin{enumerate}
-    \item $\alpha$ AGB yield (scale).
-    \item $\zetao$ Constant CCSNe yield
-    \item $\zetai$ Linear CCSNe yield. Held constant past [M/H] = -2
-    \item $\zetaii$ quadratic CCSNe yield. Also held constant ...
-\end{enumerate}
-Since each process is tracked separately, we can then predict the total C abundance at any point in the model by adding together the C abundances from each process
-\begin{equation}
-    Z_{\rm C} = \sum_{i} \alpha_i Z_{\rm C}^{i}. 
-\end{equation}
-Since the models do also have statistical uncertainties, the variance of the mean is given by
-\begin{equation}
-    V(\bar Z_{\rm C}) = \sum_{i} \alpha_i^2 V(\bar Z_{\rm C}^{i})
-\end{equation}
-
-To formulate a likelihood, we assume that model agreement is characterized primarily by the \textit{mean trends} in [C/Mg] with [Mg/Fe] and [Mg/H].
-For each bin, we calculate the mean $Z_{\rm C}$ for each model component.
-Then these means are added together and the resulting $Z_{rm C}$ is compared to the $Z_{\rm C}$ of the subgiants in the bin, using a likelihood
-\begin{equation} \label{eq:mcmc_likelihood}
-    \log {\cal L} \propto \chi^2 = \sum_b \frac{(\bar Z_{b, \rm C,\ model} - \bar Z_{b, \rm C,\ obs})^2} {s_{b, \rm obs}^2 + {\rm Var}(\bar Z_{b, \rm C,\ model})}
-\end{equation}
-
-We adopt the following priors
-\begin{subequations}
-\begin{align}
-    \alpha &\sim N(1, 1) \\
-    \zeta^{(0)} &\sim N(2, 1) \\
-    \zeta^{(1)} &\sim N(0, 1) \\
-    \zeta^{(2)} &\sim N(0, 4) \\
-\end{align}
-\end{subequations}
-
-We then run a Monte-Carlo Markov Chain (MCMC) using Turing.jl with a No-U-turn sampler (acceptance rate of 0.65), combining 8 walkers with 10,000 steps each.
-
-(in progress) To ensure this method is relatively robust, we will perform similar MCMC simulations varying the bin size/method, the MCMC sampler (HMC, ensemble stretch moves from pyemcee, MH, MH random walk), the likelihood (including median \& distribution based), and explore 2D bins.
-In each case, the derived parameters are within their uncertainties (excluding the KS test model).
-Finally, we additionally do run multizone simulations for the fiducial model varying each parameter by 5-sigma (from the distribution) and ensuring that the resulting trend is within the uncertainty of this approximation.
-
-(in progress) We check that removing the likelihood in \caafe{} causes...
-Additionally, we try and fit models without AGB components, without quadratic components, etc., finding that each model fits the data poorer than the above formulation.
-
-\subsection{Results}
-
-Fig.~\ref{fig:mcmc} displays the distribution and correlation of each parameter in the fiducial MCMC model.
-Each parameter is relatively well-constrained.
-The most prominant correlation, between $\zetao$ and $\alpha$, represents that the total solar-yield is well constrained.
-The other main correlation, between $\zetai$ and $\zetaii$, arises from the shape of the \caah\ trend.
-If the quadratic component is decreased, than the slope  (past M/H $\sim 0.1$) increases, so the linear component must decrease in order to maintain agreememnt with the data.
-
-Fig.~\ref{fig:mcmc_caahfe} shows the resulting mean trends in \caah\ and \caafe\ for the median best MCMC parameters for each AGB mode.
-Regardless of the AGB model, there is a reasonable choice of \cc\ yields which can precisely match the \caah\ trend.
-On the other hand, the agreement with the \caafe\ trend tends to be more poor for each AGB model, where they all predict a later decrease in \caafe\ than is observed.
-This is improved by yield models with a higher \agb\ enrichment from low mass stars ($\lesssim 2.5$).
-
-Fig.~\ref{fig:mcmc_ytot} shows the AGB fraction at solar metallicity and the total C yield with metallicity for each MCMC run. 
-In essentially each case, the majority of samples have a AGB fraction between 0.15 and 0.4.
-
-\begin{figure}
-\centering
-\includegraphics{figures/mcmc_corner.pdf}
-\caption[]{
-MCMC samples. Could actually just try plotting the distributions from each model here...
-}
-
-\label{fig:mcmc}
-\end{figure}
-
-\begin{figure*}
-    \centering
-    \includegraphics[]{figures/mcmc_caahfe_predicted.pdf}
-    \caption{Predicted mean tracks for the mean models.
-\dbnote{This figure is almost identical to Figure 8, so may need to think about if we need both....especially since the MCMC now informs the choice of parameters in Fig.
-8.}}
-    \label{fig:mcmc_caahfe}
-\end{figure*}
-
-\begin{figure*}
-    \centering
-    \includegraphics[]{figures/mcmc_fagb.pdf}
-    \includegraphics[]{figures/mcmc_y_tot.pdf}
-    \caption{Caption}
-    \label{fig:mcmc_ytot}
-\end{figure*}
-
-\section{Model Parameters}
-
-\begin{table*}
-    \caption{
-    Best-fit parameters from MCMC analysis for various models discussed.
-    \dbnote{Not sure if we should use analytic, nugrid, shifted fruity or normal fruity yields as fiducial here.}}
-    \begin{tabular}{l l l l l l l l l l} 
-    \hline
-    model            & $\chi2$  & $\log p$ & alpha & zeta0 & zeta1 & zeta2 & fagba & ytota & zeta1a\\
-\hline
-analytic         &      5.0 &     0.94 & $0.38^{+0.02}_{-0.02}$  &  $2.41^{+0.02}_{-0.02}$  &  $1.51^{+0.04}_{-0.04}$  &  $2.24^{+0.13}_{-0.13}$  &  $0.14^{+0.01}_{-0.01}$  &  $4.28^{+0.01}_{-0.01}$  &  $1.73^{+0.07}_{-0.07}$\\
-lateburst        &      8.7 &   -26.31 & $0.48^{+0.03}_{-0.03}$  &  $2.28^{+0.03}_{-0.03}$  &  $1.90^{+0.09}_{-0.09}$  &  $2.95^{+0.22}_{-0.21}$  &  $0.17^{+0.01}_{-0.01}$  &  $4.23^{+0.01}_{-0.01}$  &  $2.18^{+0.13}_{-0.13}$\\
-twoinfall        &      7.2 &    -5.68 & $0.55^{+0.05}_{-0.04}$  &  $2.36^{+0.04}_{-0.04}$  &  $2.12^{+0.11}_{-0.10}$  &  $1.96^{+0.20}_{-0.19}$  &  $0.19^{+0.02}_{-0.01}$  &  $4.48^{+0.02}_{-0.02}$  &  $2.41^{+0.16}_{-0.15}$\\
-eta2             &      6.2 &    -1.85 & $0.55^{+0.03}_{-0.03}$  &  $2.19^{+0.03}_{-0.03}$  &  $1.39^{+0.04}_{-0.04}$  &  $2.81^{+0.15}_{-0.15}$  &  $0.20^{+0.01}_{-0.01}$  &  $4.20^{+0.01}_{-0.01}$  &  $1.29^{+0.05}_{-0.05}$\\
-fruity           &      6.7 &    -8.99 & $2.05^{+0.13}_{-0.13}$  &  $2.00^{+0.05}_{-0.05}$  &  $2.27^{+0.07}_{-0.07}$  &  $2.54^{+0.14}_{-0.14}$  &  $0.28^{+0.02}_{-0.02}$  &  $4.26^{+0.01}_{-0.01}$  &  $2.38^{+0.07}_{-0.07}$\\
-fruitym0.7      &      5.6 &    -0.62 & $0.99^{+0.06}_{-0.06}$  &  $2.42^{+0.02}_{-0.02}$  &  $1.63^{+0.04}_{-0.05}$  &  $2.38^{+0.14}_{-0.14}$  &  $0.15^{+0.01}_{-0.01}$  &  $4.36^{+0.01}_{-0.01}$  &  $2.03^{+0.07}_{-0.07}$\\
-aton             &      9.1 &   -19.66 & $1.78^{+0.12}_{-0.12}$  &  $2.49^{+0.02}_{-0.02}$  &  $3.60^{+0.16}_{-0.15}$  &  $2.03^{+0.14}_{-0.15}$  &  $0.09^{+0.01}_{-0.01}$  &  $4.21^{+0.01}_{-0.01}$  &  $2.78^{+0.08}_{-0.08}$\\
-monash           &     11.1 &   -23.94 & $2.92^{+0.23}_{-0.22}$  &  $1.56^{+0.09}_{-0.10}$  &  $4.74^{+0.26}_{-0.25}$  &  $4.31^{+0.26}_{-0.25}$  &  $0.34^{+0.03}_{-0.03}$  &  $3.65^{+0.05}_{-0.05}$  &  $2.34^{+0.10}_{-0.10}$\\
-nugrid           &     10.3 &   -14.80 & $0.93^{+0.05}_{-0.05}$  &  $1.71^{+0.06}_{-0.06}$  &  $1.26^{+0.04}_{-0.04}$  &  $2.78^{+0.14}_{-0.14}$  &  $0.31^{+0.02}_{-0.02}$  &  $3.80^{+0.03}_{-0.03}$  &  $1.28^{+0.08}_{-0.08}$\\
-v21              &     20.0 &  -205.34 & $0.68^{+0.03}_{-0.03}$  &  $3.45^{+0.03}_{-0.03}$  &  $1.84^{+0.10}_{-0.10}$  &  $1.71^{+0.24}_{-0.25}$  &  $0.16^{+0.01}_{-0.01}$  &  $6.33^{+0.02}_{-0.02}$  &  $1.78^{+0.15}_{-0.16}$\\
-gso              &      3.5 &   -14.96 & $0.95^{+0.51}_{-0.49}$  &  $3.26^{+0.45}_{-0.46}$  &  $-0.66^{+0.90}_{-0.91}$  &  $-1.15^{+2.65}_{-2.70}$  &  $0.23^{+0.12}_{-0.11}$  &  $6.47^{+0.25}_{-0.25}$  &  $-2.46^{+1.67}_{-1.71}$\\
-galah            &     12.3 &   -85.65 & $0.48^{+0.02}_{-0.02}$  &  $2.80^{+0.02}_{-0.02}$  &  $0.90^{+0.05}_{-0.05}$  &  $2.13^{+0.13}_{-0.13}$  &  $0.15^{+0.01}_{-0.01}$  &  $5.03^{+0.01}_{-0.01}$  &  $0.65^{+0.07}_{-0.07}$\\
-
-\hline
-total & &   &  $0.65^{+1.25}_{-0.19}$  &  $2.36^{+0.45}_{-0.43}$  &  $1.63^{+0.75}_{-0.42}$  &  $2.29^{+0.62}_{-0.43}$  &  $0.19^{+0.14}_{-0.05}$  &  $4.26^{+2.07}_{-0.07}$  &  $1.68^{+0.74}_{-1.11}$\\
-\hline
-    \end{tabular}
-
-\end{table*}
-
-\begin{table*}
+\section{Model parameters and details}
+
+\begin{table}
 	\centering
@@
             \hline
-            fiducial & 2.04 & fruity & 2.01 & 2.27 & 2.53 \\
-            FRUITY & 1 & fruity & 2.39 & 1.86 & 2.37 \\
-            Monash & 1 & monash & 2.36 & 2.60 & 2.95 \\
-            ATON & 1 & aton & 2.61 & 2.67 & 2.12 \\
-            NuGRID & 1 & nugrid & 1.78 & 1.62 & 3.01 \\
-            f=0.0 &  \\
-            f=0.5 & 3.623 & fruity  \\
-            steep & 2.04 & fruity \\
-            shallow & 2.04 & fruity \\
-            fz=0 \\
-            fz=0.5 \\
-            m0.5 & 2.04 & fruity(m/0.5)  & 2.44 & 1.42 & 2.11 \\
-            m0.7 & 2.04 & fruity(m/0.7) & 2.03 & 1.92 & 3.03 \\
-            m1.5 & 2.04 & fruity(m/1.5) & 2.08 & 1.88 & 1.87 \\
+            fiducial & 1.95 & fruity & 2.01 & 2.19 & 2.72 \\
+            Monash & 2.06 & monash & 1.92 & 3.68 & 3.52 \\
+            ATON & 1.56 & aton & 2.50 & 3.37 & 2.50 \\
+            NuGRID & 1.00 & nugrid & 1.75 & 1.58 & 3.19 \\
+            steep & 1.95 & fruity & 2.01 & 3.0 & 2.72 \\
+            shallow & 1.95 & fruity & 2.01 & 1.0 & 2.72 \\
+            f=0.1 & 0.721 & fruity & 2.47 & 2.19 & 2.72  \\
+            f=0.4 & 2.88 & fruity & 1.64 & 2.19 & 2.72 \\
+            f=0.1, zeta & 0.721 & fruity & 2.47 & 1.75 & 2.72  \\
+            f=0.4, zeta & 2.88 & fruity & 1.64 & 2.51 & 2.72 \\
+            m0.5 & 2.23 & fruity(m/0.5)  & 2.27 & 1.60 & 2.23 \\
+            m0.7 & 1.73 & fruity(m/0.7) & 2.08 & 1.83 & 3.31 \\
+            m1.5 & 2.12 & fruity(m/1.5) & 2.02 & 1.98 & 2.27 \\
 		\hline
 	\end{tabular}
-\end{table*}
+\end{table}
 
@@
 
+\section{NuGrid Yield Tables}
+
 \bsp	% typesetting comment

### 2025-03-07 carbon_paper/tex/main.tex
c paper updates, fixed solar scale

@@
 % Enter the current year, for the copyright statements etc.
-\pubyear{2024}
+\pubyear{2025}
 
@@
 From a Galactic chemical evolution (GCE) perspective, some authors have argued that high-mass stars should dominate~\citep[e.g.][]{prantzos+94, HEK00, romano+20, franchini+20, gustafsson22}, and others have argued that AGB stars should contribute at least half of the C in the universe~\citep[e.g.][]{tinsley79, chiappini+03, mattsson10, KKU11, rybizki+17, KKL20}.
-In this paper, we aim to constrain C production using subgiant stars and multi-zone GCE models \dbstrike{incorporating stellar radial migration}.
+In this paper, we aim to constrain C production using subgiant stars and multi-zone GCE models.% \dbstrike{incorporating stellar radial migration}.
 
@@
 Predictions of C yields from stellar evolution and supernova (SN) models are riddled with uncertainties (see, e.g., the reviews by \citealt{romano+10, KL14}).
-Some \dbadd{substantial uncertanties} include mass loss rates \citep{sukhbold+16, beasor+2020}, rotational mixing \citep{frischknecht+16, LC18}, nuclear reaction rates \dbadd{CITE}, and convection \citep{chieffi2001, ventura+13}.
-Recent work also suggests that small changes in a stars's initial mass of 
+Some salient unknowns include mass loss rates \citep{sukhbold+16, beasor+2020}, rotational mixing \citep{frischknecht+16, LC18}, nuclear reaction rates \citep{herwig+05, herwig+austin2004}, and convection \citep{chieffi2001, ventura+13}.
+Recent work additionally suggests that small changes in a stars's initial mass of 
  $\sim$$0.01 M_\odot$  have significant effects on the evolution and explosion outcomes of massive stars \citep{bruenn+2023, vartanyan_burrows2023}.
-Furthermore, many \add{massive} stars are found in binary systems \dbadd{\url{https://ui.adsabs.harvard.edu/abs/2012Sci...337..444S/abstract} ??}, the effects of which are almost entirely
+ Furthermore, many stars are found in binary systems \citep{sana+12}, the effects of which are almost entirely
 unexplored in stellar nucleosynthesis models \citet{farmer+21}.
@@
 
-Given the challenge of theoretical yield predictions, recent work aims to empirically characterize elemental production \dbnote{does it make sense to frame this as only recent work?
-I just don't know but I feel like there are very early examples which at least use observations as a guide for yields, like maybe even B2FH.
-or garnett1997}
-\citet{weinberg+19, weinberg+22} analyzed the abundance ratio trends of high- and low-alpha sequence stars in APOGEE~\citep{apogee17} to infer relative yields of prompt and delayed enrichment sources and the metallicity dependence thereof.
+Given the challenge of theoretical yield predictions, recent work aims to empirically characterize elemental production.
+\dbnote{are there older relevant references like garnett1997?
+or other relevant work (eitner+20?)}
+\citet{weinberg+19, weinberg+22} analyzed the abundance ratio trends of high- and low-alpha sequence stars in APOGEE~\citep{apogee17} to infer relative yields of prompt and delayed enrichment sources and their metallicity dependence.
 \citet{emily+19, emily+22, emily+24} applied the same methodology to GALAH~\citep{DeSilva2015, Martell2017}.
@@
 Their measurements, provide one of few empirical anchors on the absolute scale of yields \citep{david_fe}.
-\dbadd{Additionally the series of papers including \citet{eitner+2020} includes some relevant work.}
 
@@
 We show in section~\ref{sec:agb} that the characteristic delay times of C production should be $\sim$ 1 Gyr, within this limit. 
-\dbnote{This is complicated by the difference between high alpha and low alpha, and 1-2Msun stars do produce carbon...}
+\dbnote{This is complicated by the difference between high alpha and low alpha, and 1-2Msun stars do produce carbon.... Also, I would like to call out reviews and general works on C at some point.}
 
@@
 \dbstrike{Subgiants have the advantage that their photospheric abundances of C directly reflect their birth C abundances much more closely than other spectral types.} \citep{gilroy89, korn+07, lind+08, souto+18, souto19}.
-In other evolutionary phases, the measured abundances are known to be affected by internal processes (see discussion in section 2 below).
+In other evolutionary phases, the measured abundances are known to be affected by internal processes (see discussion in section~\ref{sec:data_selection} below).
 Our sample should therefore be unaffected by uncertainties with inferring their birth abundances.
 
-% \dbnote{not sure the observations below need to be  too detailed here?
-Maybe just state that C/O appears to have a universal shape across environments and direct to that section since our main focus is on APOGEE?
-and disk chemistry?
-}
-% \dbstrike{
-% From observations of nearby stars and (extragalactic) gas, we know that [C/O] against [O/H] traces a banana shape (see Fig.~\ref{fig:gas_phase} and section~\ref{sec:gas}).
-% At the very lowest metallicities ($[{\rm O/H}]\lesssim-2$),%
-% %
-% observations indicate that [C/Mg] declines with metallicity.
-% From $-2 \lesssim {\rm [O/H]}\lesssim -1$, [C/Mg] is roughly constant with metallicity. 
-% At higher metallicities ([O/H]~$\gtrsim -1$), [C/Mg] increases with metallicity.
-% }
-% \dbstrike{We will show in section~\ref{sec:results} below that these correlations in the bulk population abundances alone are quite constraining for the origin of C.}
-
-In Section~\ref{sec:data_selection} we describe the selection for our subgiant observational sample.
-In Section~\ref{sec:nucleosynthesis}, we discusses theoretical estimates of \agb\ and \cc\ C yields and present the yield prescriptions we use for our models.
-In Section~\ref{sec:vice}, we describe the remaining details of our GCE models.
-In Section~\ref{sec:results}, we present our model predictions and discuss their observationally distinguishable predictions. 
-In Section~\ref{sec:gas}, we compare our model to observations of halo stars and extragalactic HII regions from the literature. 
+In section~\ref{sec:data_selection} we describe the selection for our subgiant observational sample.
+In section~\ref{sec:nucleosynthesis}, we discusses theoretical estimates of \agb\ and \cc\ C yields and present the yield prescriptions we use for our models.
+In section~\ref{sec:vice}, we describe the remaining details of our GCE models.
+In section~\ref{sec:results}, we present our model predictions and discuss their observationally distinguishable predictions. 
+In section~\ref{sec:gas}, we compare our model to observations of halo stars and extragalactic HII regions from the literature. 
 We summarize our conclusins in section~\ref{sec:conclusions}.
 
-% \footnotetext{\strike{By metallicity, we mean the (mass) fraction of any element which is not H or He, denoted by $Z$. For the sun, we take $Z_\odot=0.016$.} }
+% \footnotetext{\strike{By metallicity, we mean the (mass) fraction of any element which is not H or He, denoted by $Z$. For the sun, we take $Z_\odot=0.0176$.} }
 
@@
 During main sequence evolution, metals can fall below the convective envelope (\textit{gravitational settling}; e.g. \citealt{turncotte+98}).
-When stars evolve off main sequence, these metals are reincorporated into the convective envelope \citep[]{gratton+00, souto19}. 
-When a star becomes a red giant, \textit{first dredge up} pollutes its photosphere with core, CNO-processed material
+When stars evolve off main sequence and become subgiants, these metals are reincorporated into the convective envelope \citep[]{gratton+00, souto19}. 
+However, once a star becomes a red giant, \textit{first dredge up} pollutes its photosphere with core, CNO-processed material
 \citep{iben67, KL14}. 
-\dbnote{Why exactly do we use subgiants? Consistent stellar parameters, subgiant spectra are easier than white dwarfs? only a $\sim 0.05$ dex correction}
+\dbnote{Is there other justification for subgiants? Consistent stellar parameters, subgiant spectra are easier than white dwarfs? only a $\sim 0.05$ dex correction}
 
@@
 Fig.~\ref{fig:subgiants} shows out subgiant sample plotted in the \caah\ and \caafe{} planes.\footnotemark{} In this sample, [C/Mg] increases with [Mg/H], and [C/Mg] decreases with [Mg/Fe] at fixed [Mg/H].
+Our aim is to reproduce these trends.
 
@@
 We have also investigated these thrends in other catlogues (not show) in order to understand the systematic uncertainties of our APOGEE subgiant sample.
-Namely, we we consider subgiants/dwarfs from GALAH DR4, Gaia-ESO DR5.1, and LAMOST with similar selection criteria.
+Namely, we we consider subgiants/dwarfs from GALAH DR4 \citep{galah_dr4}, Gaia-ESO DR5.1 \citep{gaiaeso_dr5.1}, and LAMOST \citep{lamost} with similar selection criteria.
 Additionally, we consider APOGEE Giants with first dredge up mixing corrections from \citep{vincenzo+21}.
 In general, different surveys follow similar trends in \caah\ and \caafe\ but with systematic offsets at the $\sim{0.1}$ dex level in [C/Mg] given [Mg/H] and slight variations in the slope.
-These systematic differences are not a major concern for our conclusions since our models are mostly constrained by the slope of \caah\ and \caafe,  not their normalization (see Fig.~7?
-and discussion in section \dbadd{5.2}).
+These systematic differences are not a major concern for our conclusions since our models are mostly constrained by the slope of \caah\ and \caafe,  not their normalization (see Fig.~\ref{fig:zeta_f} and discussion in section \dbadd{5.2}).
 
@@
 A yield quantifies the new production of a chemical species.
-For a given star, we define the {\it net fractional yield of $X$} as the fraction of a stars initial mass synthesized into new $X$.
-Specifically, the net fractional yield of element $X$ is
+For a given star, we define the {\it stellar yield of $X$} as the fraction of a star's initial mass synthesized into a new element, $X$.
+Specifically, the stellar yield of $X$ is
+\begin{equation} \label{eq:stellar_yield_def}
+   \y_{\rm X}(m, Z) := 
+    \frac{m_{X, \rm ej}- Z_{X,\rm  ini}\,m_{\rm ej}}{m}
+\end{equation}
+where $Z_{X,\rm ini}$ is the initial mass abundance of $X$, $m_{\rm ej}$ is the ejected mass, $m_{X, \rm ej}$ is the ejected mass of $X$, and $m$ is the initial mass of the star.
+Note that yields may become negative if more X is transformed into other elements than is produced.
+We also describe yields by their population-averaged quantities, {\it integrated yields}, the amount of newly produced X per unit mass of star formation. 
+The integrated yield of $X$ is
 \begin{equation} 
-   \y_{\rm X}(M, Z) = 
-    \frac{m_{X, \rm ej}- Z_{X,\rm  ini}\,m_{\rm ej}}{m}
-\end{equation}
-where $Z_X$ is the initial abundance of $X$, $m_{\rm ej}$ is the ejected mass, $m_{X, \rm ej}$ is the ejected mass of $X$, and $m$ is the initial mass of the star.
-Note that yields may become negative if more X is transformed into other elements than is produced ($Z_{X,\rm ej} < Z_{X,\rm ini}$).
-We also describe yields by their population-averaged quantities, the amount of newly produced X per unit mass of star formation, 
-\begin{equation} 
-   y_{X}(Z) = 
+   y_{X}(Z) := 
     \frac{M_X - r\,Z_{X, \rm ini}\,M_{\rm ssp}}{M_{\rm ssp}},
 \end{equation}
-where $M_X$ is the total expelled mass of element X, $M_{\rm ssp}$ is the birth mass of the single stellar population (SSP\footnote{An SSP is a cluster of stars born at the same time from the same material.}), and $r$ is the return fraction (fraction of the SSP mass returned to the interstellar medium).
-
+where $M_X$ is the total expelled mass of element X, $M_{\rm ssp}$ is the birth mass of the single stellar population (SSP)\footnote{An SSP is a cluster of stars born at the same time from the same material.}, and $r$ is the return fraction (fraction of the SSP mass returned to the interstellar medium).
+
+Table~\ref{tab:fiducial_mod} summarizes our yield choices. 
 Following \citet{james+23}, we integrate yields and our GCE models using the publicly available Versatile Integrator for Chemical Evolution (\VICE, \citealt{JW20}).
@@
 Our N yield is scaled from \citep{james+23}.
-Table~\ref{tab:fiducial_mod} summarizes these choices. 
-We assume a \citet{kroupa01} initial mass function.
+We assume a \citet{kroupa01} initial mass function (IMF).
 
@@
 
-An Asymptotic Giant Branch (AGB) star is a low mass star undergoing He shell burning, the last nuclear phase (see e.g.
+An asymptotic giant branch (AGB) star is a low mass star undergoing He shell burning, the last nuclear phase (see e.g.
 \citealt{PR2023}).
 AGB stars enrich the interstellar medium (ISM) through mass expelled during thermal pulses.
-In this work, we explore four different stellar AGB yield tables from the literature which provide well-sampled grids in mass and metallicity. We refer to the tables as 
+
+We explore four different stellar AGB yield tables from the literature which provide well-sampled grids in mass and metallicity. We refer to the tables as 
 \begin{description}
@@
 We use the same tables as \citet{james+23}, except that we have swapped \citet{karakas10} for \citet{pignatari+16}.
+(See section~\ref{sec:nugrid_yields} for the implementation and recalculation of these yields.)
 For our models to better match observations, we uniformly amplify the yield tables according to
 \begin{equation} \label{eq:alpha}
-        \ycagb(M, Z) \rightarrow \alpha_{\rm agb}\ \ycagb(M, Z).
+        \ycagb(m, Z) \rightarrow \alpha_{\rm agb}\ \ycagb(m, Z).
 \end{equation}
 We use the \fruity\ table, with $\alpha_{\rm agb}=\cfactor$, as the fiducial \agb\ yield.
+
 Fig.~\ref{fig:y_agb} compares the C yields for these four AGB models.
@@
 \begin{equation} \label{eq:imf-agb-yield}
-    y_{X}^{\rm agb}(Z,\tau) = 
-    \frac{1}{A}\int^{u_{\rm AGB}}_{M_\textrm{post-AGB}(\tau)} 
-    \y_{\rm X}(M, Z)\ 
-    \frac{dN}{dM}\ M\ dM
-\end{equation}
-are the minimum and maximum mass of star formation, $u_{\rm AGB}=8\Mo$ is the maximum mass of an AGB star, $M_\textrm{post-AGB}(\tau)$ is the mass of stars which complete AGB evolution at age $\tau$, and $dN/dM$ is the initial mass function.
-$A = \int_l^u M \frac{dN}{dM} dm$ is the IMF normalization coefficient and  $l=0.08\,\Mo$ and $u = 100\,\Mo$.
-We assume a \citet{larson74} mass-lifetime-relationship and assume that the total lifetime of stars is 1.1 times the MS lifetime.
+    y_{X}^{\rm AGB}(Z,\tau) = 
+    \int^{u_{\rm AGB}}_{m_\textrm{post-AGB}(\tau)} 
+    \y_{\rm X}(m, Z)\ 
+    \frac{1}{A}\frac{dN}{dm}\ m\ dm
+\end{equation}
+are the minimum and maximum mass of star formation, $u_{\rm AGB}=8\Mo$ is the maximum mass of an AGB star, $m_\textrm{post-AGB}(\tau)$ is the mass of stars which complete AGB evolution at age $\tau$, and $dN/dm$ is the initial mass function (IMF).
+The IMF normalization is
+\begin{equation} \label{eq:imf_normalization}
+    A := \int_l^u m \frac{dN}{dm} dm
+\end{equation}
+    where  $l=0.08\,\Mo$ and $u = 100\,\Mo$ are the assummed minimum and maximum mass of star formation.
+We assume a \citet{larson74} mass-lifetime-relationship and assume that the total lifetime (through post-AGB) is $1.1\times$ the main sequence lifetime.
 
@@
 The IMF-averaged yields differ in normalization and metallicity dependence.  
-The normalizations span a factor of \about{2}. (e.g. between $6\times 10^{-4}$ and $12 \times 10^{-4}$ at $Z=0.33\,\Zo$).
-Both \nugrid{} and \aton{} predict non-monotonic C yields with $Z$, but it is unclear if this prediction is significant given the uncertainties associated with AGB modelling.
+The normalizations span a factor of \about{2}. (e.g. between $6\times 10^{-4}$ and $12 \times 10^{-4}$ at $Z=0.33\,\Zo$)
+Both \nugrid{} and \aton{} predict non-monotonic C yields with $Z$, but AGB modeling uncertanties may eclipse this prediction's significance.
 To characterize the metallicity dependence of each table, we fit the yield to a linear model in $\log Z$
 \begin{equation}\label{eq:agb_z_approx}
-    y_{\rm C}^{\rm AGB}(Z) = \zetao + \zetai \log(Z / \Zo).
-\end{equation}
-Table \ref{tab:agb} contains the fit parameters $\bar y_{\rm C, 0}^{\rm AGB}$ and $\zagb$ for each AGB table.
+    y_{\rm C}^{\rm AGB}(Z) = \zetao^{\rm AGB} + \zetai^{\rm AGB} \log(Z / \Zo).
+\end{equation}
+Table \ref{tab:agb} also contains the linear fit parameters for each AGB table.
 The values of $\zagb$ span a factor of $\sim{3}$ between models.
@@
 TDU increases C yields and HBB converts C into N. 
-\dbstrike{When both processes are active, highly efficient N production ensues (see discussion in e.g.
-{james+23, ventura+13}).} \dbnote{move to next paragraph?}.
 %Because the $^{14}$N proton capture is the slowest component of the CNO cycle, the CNO cycle converts nearly all \C[12] into $^{14}$N \citep{solar-fusion}.
@@
 \aton{} predicts strong HBB to set in $\sim{1}\,\Mo$ lower than in \monash{}, leading to much lower C yields.
-Moreover, the $^{14}{\rm N}({\rm p},\gamma)$ reaction rate uncertainty causes a factor of 2 difference in predicted C yields \citep{herwig+austin2004, HAL2006} \dbnote{palmerini+11, reaction rates updated since then}.
+Moreover, the $^{14}{\rm N}({\rm p},\gamma)$ reaction rate uncertainty causes a factor of 2 difference in predicted C yields \citep{herwig+austin2004, HAL2006}.
 Most of the physics included in stellar modelling is empirically calibrated. Mass-loss rates, convection, and extra mixing are not sufficiently well understood to be computed from first principles.
@@
 From the \citet{doherty+14, doherty+14b} yield table (extending the \monash\ yields), the highest net fractional yield is only -0.002 for super solar metallicity, which would have a negligible impact on the integrated yield).
-Additionally, as discussed in section~\ref{sec:degeneracies} below, the short lifetimes of high mass AGB and super-AGB stars mean they have negligable impacts on our conclusions and can be grouped with CCSNe yields.
+Additionally, as discussed in section~\ref{sec:degeneracies} below, the short lifetimes of high mass AGB and super-AGB stars mean they have minimally affect our conclusions and can be grouped with CCSNe yields.
 
@@
 
-Massive stars form $^{12}$C in their cores through the triple-$\alpha$ reaction \dbadd{(He-burning)} which is later released to the ISM through winds and supernovae.
-
-In \VICE, massive star nucleosynthesis is approximated as occurring instantaneously after a star formation event.
+Massive stars form $^{12}$C in their cores through the triple-$\alpha$ reaction (He-burning) which is later released to the ISM through winds and supernovae.
+
+We approximate massive star enrichment as occurring instantaneously after a star formation event.
 Under this approximation, the yield is simply a constant  of proportionality between the metal production rate and the SFR:
@@
 \end{equation}
-The population-averaged yield, $y_{X}^{\rm CC}$ can be expressed as
+The CCSN integrated yield is given by
 \begin{equation}
-%y_{X}^{\rm CC} = \frac{ \int_{l_{\rm CC}}^{u} (E(M) M_{X\rm, SN} + w_X - Z_X\,(M-M_{\rm rem}) )\frac{dN}{dM}\ dM }{ \int_{l}^{u} M\,\frac{dN}{dM}\ dM }
 y_{X}^{\rm CC} = \int_{l_{\rm CC}}^{u} \left[E(m) m_{X\rm, SN} + w_X - Z_X\,(m-m_{\rm rem})\right]\,\frac{1}{A} \frac{dN}{dm}\ dm
 \end{equation}
-where $E(m)$ is the fraction of stars of mass $m$ which explode, $M_{X,\rm SN}$ and $w_X$ are the mass of X ejected in a CCSN explosion and through stellar winds respectively, $Z_X$ is the initial abundance of $X$, $dN/dM$ is the IMF, $l_{\rm CC}=8\Mo$ is the initial minimum mass of a CCSN progenitor, $M_{\rm ej}$ is the total mass ejected from the star in winds?.
-\dbstrike{We integrate yields using \VICE's {\tt vice.yields.ccsne.fractional} function.} \dbnote{is this too detailed?}
+where $E(m)$ is the fraction of stars of mass $m$ which explode, $m_{X,\rm SN}$ and $w_X$ are the mass of $X$ ejected in a CCSN explosion and through stellar winds respectively, $Z_X$ is the initial abundance of $X$, $dN/dm$ is the IMF, $l_{\rm CC}=8\Mo$ is the initial minimum mass of a CCSN progenitor.
+%\dbstrike{We integrate yields using \VICE's {\tt vice.yields.ccsne.fractional} function.} \dbnote{is this too detailed?}
 
@@
     \caption[]{
-    \dbnote{y label: integrated CCSNe carbon yield}
     \dbnote{might be interesting to plot every CCSNe yield used in this paper in light grey to show strength of our constraint}
@@
 
-To account for radial migration, we use a normally-distributed, $\sqrt{\rm time}$ migration scheme. The final position of each star particle is sampled from
-\begin{subequations}
-\begin{align}
-        R_{\rm end} &\sim N(R_{\rm birth}, \sigma_R ) \\
-        \sigma_{R} &= 1.27\,{\rm kpc} \sqrt{\frac{t_{\rm end} - t_{\rm birth}}{1 \rm Gyr}}
-\end{align}
-\end{subequations}
-If a star would cross a boundary, then the star is reflected back.
-The star moves from its birth radius to its final radius via
-\begin{equation}
-        R(t) = \Delta R \sqrt{\frac{t - t_{\rm birth}}{t_{\rm end} - t_{\rm birth}}}
-\end{equation}
-The $\Delta R \propto \sqrt{\rm time}$ dependence arises when migration proceeds as a consequence of the diffusion of angular momentum \citep{frankel18, frankel20}.
-\footnote{Not shown here, we also explored variations of temporal, spatial resolution, migration strength, and the mass lifetimre relation. We found these do not affect median trends significantly.}
+We use the radial migration prescription described in appendix C of \citet{dubay+24}.\footnote{Not shown here, we also explored variations of temporal, spatial resolution, migration strength, and the mass lifetimre relation.
+We found these do not affect median trends significantly.}
 We do not account for radial gas flows.
@@
 
-\dbnote{moved this here since next subsection depends on representative sample}
 To create representative stellar samples to compare with APOGEE, 
@@
 Assume that the yields do not depend on the yields (e.g. metallicity dependence is negligable). 
-Given a set of yields $\{y_X^i\}_i$ and resulting abundance evolution $\{Z_{X}^i(R, t) \}$, then if $y_X'$, the yield of X, is a linear combination of $\{y_X^i\}$, $y_X' = \sum_i \alpha_i\, y_X^i$ where $\alpha_i \in \mathbb{R}$, the abundance evolution of element X is
+Given a set of yields $\{y_X^i\}_i$ and resulting abundance evolution $\{Z_{X}^i(R, t) \}$, let $y_X'$, the yield of X, be a linear combination of $\{y_X^i\}$
+\begin{equation}
+    y_X' = \sum_i \alpha_i\, y_X^i \quad {\rm where\ } \alpha_i \in \mathbb{R}.
+\end{equation}
+Then the abundance evolution of element $X$ is
 \begin{equation}\label{eq:lin_combo}
@@
 We focus on the binned \textit{mean} abundances of the low-$\alpha$ sequence in \caah, and the $-0.15 \leq {\rm [M/H]} \leq -0.05$ metallicity slice in \caafe\ (with 20 bin edges between -0.4 and 0.3 in [Mg/H] and 12 bin edges between 0.025 and 0.25 in [Mg/Fe]).
-We separate the C yield  into four different components
+We separate the C yield  into four different components.
 \begin{enumerate}
-    \item $\alpha$. Prefactor for an AGB yield table
-    \item $\zetao$ Constant CCSN yield  ($y_0 = \zeta_0$)
-    \item $\zetai$ Linear CCSN yield ($y_1 = \zeta_1 \log Z/\Zo$) \footnotemark{}
-    \item $\zetaii$ Quadratic CCSN yield ($y_2 = \zeta_2 (\log Z/\Zo)^2$)
+    \item $\alpha$: Prefactor for an AGB yield table
+    \item $\zetao$: Constant CCSN yield  ($y_0 = \zeta_0$)
+    \item $\zetai$: Linear CCSN yield ($y_1 = \zeta_1 \log Z/\Zo$) \footnotemark{}
+    \item $\zetaii$: Quadratic CCSN yield ($y_2 = \zeta_2 (\log Z/\Zo)^2$)
 \end{enumerate}
@@
 \end{equation}
-Similarly, we represent the mean and variance of the observations in each bin with $\bar Z_{b, \rm obs}$ and $\sigma^2_{b, \rm obs}$.  
+Similarly, we represent the mean and variance of the observations in each bin $b$ with $\bar Z_{b, \rm obs}$ and $\sigma^2_{b, \rm obs}$.  
 \begin{equation} \label{eq:mcmc_likelihood}
@@
 \end{subequations}
-We run the MCMC using Turing.jl with a No-U-turn sampler (acceptance rate of 0.65), combining 8 chains with 10,000 steps each. \dbnote{todo: increase at least for fiducial}.
+We run the MCMC using Turing.jl with a No-U-turn sampler (acceptance rate of 0.65), combining 16 independent chains with 3,000 steps each for a total of 48,000 samples.
 
@@
 metallicity dependence, and their DTDs.
-As we will demonstrate in Section~\ref{sec:agb_results} below, the final slope of \caah\ depends on both the contributions and metallicity dependences of CCSN and AGB C yields.
+As we will demonstrate in section~\ref{sec:agb_results} below, the final slope of \caah\ depends on both the contributions and metallicity dependences of CCSN and AGB C yields.
 Although AGB models predict declining C production with metallicity, the greater contribution and positive metallicity dependence of CCSN C outweigh declining AGB production.
@@
 
-\section{NuGrid Yield Tables}
+\section{NuGrid Yield Tables} \label{sec:nugrid_yields}
+In this section, we present updated calculations of the \citep{battino+19, battino+21} yield tables and describe their incorperation into VICE.
+
+\citep{battino+19, battino+21} update the \citep{ritter+18} yield models with new reaction rates and increased mixing.
+These changes allow for better production of {\it s}--process isotopes in their AGB stars, and are recommended for the masses they update.
+However, between these models, the only updates are for masses M=2,3 at metallicities Z=0.01, 0.02, 0.001, 0.002.
+
+Because the yield tables included in \citep{battino+19, battino+21} are inconsistent with the \citet{ritter+18} definitions of yields, we recalculate these yields from the publically available data on \url{https://astrohub.uvic.ca}.
+
+The total ejected mass of $X$ from an AGB star is given by 
+\begin{equation}
+    M_{X, \rm ej} = \int Z_{X, \rm surf}(t) \dot{m}(t)\ dt 
+\end{equation}
+where $Z_{X, \rm surf}$ is the surface abundance of $X$, $\dot m$ is the mass loss rate, and the integral is taken over the entire evolution. 
+One complication is that MESA stops before the end of the AGB phase due to instabilities during the transition to the planetary nebulae. 
+As a result, the practical calculation is 
+\begin{subequations}
+    \begin{align}
+        M_{X, \rm ej} &= Z_{\rm X, surf, end} (m_{\rm end} - m_{\rm rem}) \\ 
+                      &+ \sum_i \frac{1}{2} (Z_X(t_i) - Z_X(t_{i+1}))\ (m(t_i) - m(t_{i+1}))
+    \end{align}
+\end{subequations}
+where $m_{\rm end}$ and $Z_{X, \rm surf, end}$ are the final mass and surface abundance of $X$ at the end of MESA evolution, $m_{\rm rem}$ is the mass remaining in the star at the end of MESA evolution, and the sum is taken over all timesteps in the MESA output.
+We use the final H-free mass as the reminant mass.
+
+We use the \citet{ritter+18} tables from $M_{X, \rm ej}$, which we can reproduce from the same methods as above.
+Finally, the $p_{X}$ yields are calculated from $M_{\rm X, ej}$ with Eq.~\ref{eq:stellar_yield_def}.
 

### 2025-03-07 surp/_globals.py

@@ -9,9 +9,9 @@ N_SUBGIANTS = 14_066
 # Mag++2022 scale: 
 # Z_X = 0.0225 
 # Y_ini = 0.2734, X_ini = 0.0176
-Z_SUN = 0.016  # 0.0176 in paper
-Y_SUN  = 0.274 # 0.2734 in paper
-X_SUN = 0.71 # 0.709 inferred
+Z_SUN = 0.0176
+Y_SUN  = 0.2734
+X_SUN = 0.709 # 1 - Y - Z
 
 ELEMENTS = ["c", "n", "mg", "fe"]
 

### 2025-03-07 tests/test_gce_math.py

@@ -31,23 +31,23 @@ def test_mol_mass():
 
 
 def test_solar_z():
-    assert gcem.solar_z('H') == approx(0.71)
-    assert gcem.solar_z('he') == approx(0.274)
-    assert gcem.solar_z('M') == approx(0.016)
+    assert gcem.solar_z('H') == approx(0.709)
+    assert gcem.solar_z('he') == approx(0.2734)
+    assert gcem.solar_z('M') == approx(0.0176)
     for ele in surp.ELEMENTS:
         assert gcem.solar_z(ele) == approx(vice.solar_z(ele))
 
 
 
 def test_Z_to_MH_single():
-    assert gcem.Z_to_MH(0.016) == approx(0.0)
-    assert gcem.Z_to_MH(0.0016) == approx(-1.0)
-    assert gcem.Z_to_MH(0.16) == approx(1.0)
+    assert gcem.Z_to_MH(0.0176) == approx(0.0)
+    assert gcem.Z_to_MH(0.00176) == approx(-1.0)
+    assert gcem.Z_to_MH(0.176) == approx(1.0)
     assert gcem.Z_to_MH(0) == -np.inf
 
 
 def test_MH_to_Z_single():
-    assert gcem.MH_to_Z(0.0) == approx(0.016)
+    assert gcem.MH_to_Z(0.0) == approx(0.0176)
     assert gcem.MH_to_Z(-1.0) == approx(0.0016)
     assert gcem.MH_to_Z(1.0) == approx(0.16)
     assert gcem.MH_to_Z(-np.inf) == 0.0
@@ -130,9 +130,9 @@ def test_abundance_scale():
     # use Mag + 22 meanwhie
     surp.yields.set_magg22_scale()
     correction = 0.04
-    acc = 8e-3 # rounding errors. We round to 100s place
+    acc = 8e-3 # rounding errors. We round to 1000s place like reported
     assert surp.Z_SUN + surp.Y_SUN + surp.X_SUN == approx(1.0)
-    assert surp.Z_SUN / surp.X_SUN == approx(0.0225, rel=acc)
+    assert surp.Z_SUN / surp.X_SUN == approx(0.0225 * 10**correction, rel=acc)
 
 
     assert gcem.eps_to_abundance(12, "h") == approx(gcem.X_SUN)

### 2025-03-09 carbon_paper/mc_plot_utils.py
new models for mcmc analse to final figure set

@@ -1,0 +1,248 @@
+import toml
+import matplotlib.pyplot as plt
+import numpy as np
+import pandas as pd
+
+from dataclasses import dataclass
+
+from corner import corner
+
+import arya
+import surp.gce_math as gcem
+
+
+@dataclass
+class MCMCResult:
+    params: dict
+    labels: list
+    all_labels: list
+    samples: pd.DataFrame
+    afe: pd.DataFrame
+    ah: pd.DataFrame
+
+
+    @classmethod
+    def from_file(cls, modelname, y0=None, y_a=None, zeta_a=None, burn=0):
+        modeldir = "../models/perturbations/mc_analysis/" + modelname + "/"
+    
+        with open(modeldir + "params.toml", "r") as f:
+            params = toml.load(f)
+    
+    
+        samples = pd.read_csv(modeldir + "mcmc_samples.csv")
+        filt = samples.iteration >= burn
+        samples = samples[filt]
+
+        all_labels = [k for k, v in params.items() if type(v) == dict]
+        filt_const = [(v["prior"] != "Normal" or v["prior_args"][1] != 0.0) for k, v in params.items() if type(v) == dict]
+        labels = np.array(all_labels)[filt_const]
+        
+        for label in np.array(all_labels)[~np.array(filt_const)]:
+            print("adding ", label)
+            samples[label] = params[label]["prior_args"][0]
+            
+        print("length of samples = ", len(samples))
+
+        
+        if y0 is not None:
+            ya = samples["alpha"] * y0
+            yt = ya + samples["y0_cc"] * 1e-3
+            f = ya / yt
+            samples["f_agb"] = f
+            samples["y_tot"] = yt
+            
+        if y_a is not None:
+            ya = samples["alpha"] * y_a
+            yt = ya + samples["y0_cc"] * 1e-3
+            f = ya / yt
+            samples["f_agb_a"] = f
+            samples["y_tot_a"] = yt
+            samples["zeta1_a"] = samples["zeta_cc"] * 1e-3 + samples["alpha"] * zeta_a
+        
+        afe = pd.read_csv(modeldir + "mg_fe_binned.csv")
+        ah = pd.read_csv(modeldir + "mg_h_binned.csv")
[…]

### 2025-03-09 carbon_paper/mw_model_plots.py

@@ -1,0 +1,160 @@
+import matplotlib.pyplot as plt
+import matplotlib
+import numpy as np
+
+import pandas as pd
+
+import vice
+
+import surp
+from surp import subgiants
+from surp import gce_math as gcem
+
+import arya
+arya.style.set_size((10/3, 10/3))
+from arya import COLORS
+
+def find_model(name):
+    """
+    Finds the pickled model with either the given name or the parameters 
+    and returns the csv summary
+    """
+    
+    file_name = "../models/" + name + "/stars.csv"
+    model =  pd.read_csv(file_name, index_col=0)
+    return model
+
+
+def to_nice_name(apogee_name):
+    name = apogee_name.replace("_", "/").title()
+    name = f"[{name}]"
+    return name
+
+
+data_kwargs = dict(
+    color="k", 
+    stat="median",
+    err_kwargs=dict(facecolor="k", alpha=0.3)
+)
+
+model_kwargs = dict(
+    stat="median", errorbar=None,
+    aes="line"
+)
+
+
+def zooh_models(models, labels,x="MG_H", y="C_MG", use_true=True, sequential=False, filt_ha=True, **kwargs):
+    kwargs = dict(numbins=20, **kwargs)
+    
+    N = len(models)
+    
+    if sequential:
+        hm = arya.HueMap(clim=(0, N))
+    else:
+        hm = lambda i: COLORS[i]
+    # end
+        
+    if use_true:
+        xm=x + "_true"
+        ym=y+ "_true"
+    else:
+        xm = x
+        ym = y
+    for i in range(N):
+        name = labels[i]
+        model = models[i]
+        if filt_ha:
+            df = surp.filter_high_alpha(model)
+        else:
+            df = model
+        color = hm(i)
+            
+        arya.medianplot(df, xm, ym, label=name, color=color, **model_kwargs, **kwargs)
+    # end
+
+    if filt_ha:
+        df = surp.filter_high_alpha(subgiants)
+    else:
+        df = subgiants
+        
+    arya.medianplot(df, x=x, y=y, zorder=-2, **data_kwargs, **kwargs)
+    plt.xlabel(to_nice_name(x))
+    plt.ylabel(to_nice_name(y))
+    
+
+# end
+
+
+    
[…]

### 2025-03-09 models/fiducial/sspw_const/reanalyze.py

@@ -2,11 +2,12 @@ import surp
 from surp import ViceModel, MWParams
 import sys
 import argparse
+import numpy as np
 
 # weight function here
 
 def weight_func(mass, metallicity, age):
-    return mass
+    return np.where(age > 2, mass, 0)
 
 
 args = argparse.ArgumentParser(description="Run a VICE model with the given parameters and yields")

### 2025-03-09 models/perturbations/analytic_eta2/run.py

@@ -5,27 +5,26 @@ import sys
 sys.path.append("..")
 from multi_run import ag_run 
 
-m_h_0 = -2
+m_h_0 = -1
 zeta_0 = 0.001
 
 agb_model = surp.yield_models.C_AGB_Model(y0=0.001, zeta=-0.001, tau_agb=1, t_D=0.15)
 cc_lin = surp.yield_models.BiLogLin_CC(y0=-m_h_0 * zeta_0, zeta=zeta_0, y1=0)
-cc_quad = surp.yield_models.Quadratic_CC(y0=0, zeta=0, A=0.001, Z1=0.00016)
+cc_quad = surp.yield_models.Quadratic_CC(y0=0, zeta=0, A=0.001, Z1=surp.Z_SUN * 10**m_h_0)
 
 
-yield_scale = 2
 yields_dict = {
     "ag" : {
-        "agb": yield_scale * agb_model
+        "agb": agb_model
     },
     "cd" : {
-        "ccsne": yield_scale * 0.001
+        "ccsne": 0.001
         },
     "in" : {
-        "ccsne": yield_scale * cc_lin
+        "ccsne": cc_lin
     },
     "sn" : {
-        "ccsne": yield_scale * cc_quad
+        "ccsne": cc_quad
     },
     }
             

### 2025-03-09 models/perturbations/analytic_lateburst/run.py

@@ -5,12 +5,12 @@ import sys
 sys.path.append("..")
 from multi_run import ag_run 
 
-m_h_0 = -2
+m_h_0 = -1
 zeta_0 = 0.001
 
 agb_model = surp.yield_models.C_AGB_Model(y0=0.001, zeta=-0.001, tau_agb=1, t_D=0.15)
 cc_lin = surp.yield_models.BiLogLin_CC(y0=-m_h_0 * zeta_0, zeta=zeta_0, y1=0)
-cc_quad = surp.yield_models.Quadratic_CC(y0=0, zeta=0, A=0.001, Z1=0.00016)
+cc_quad = surp.yield_models.Quadratic_CC(y0=0, zeta=0, A=0.001, Z1=surp.Z_SUN * 10**m_h_0)
 
 
 yields_dict = {

### 2025-03-09 models/perturbations/analytic_twoinfall/run.py

@@ -1,35 +1,0 @@
-import surp
-import vice
-
-import sys
-sys.path.append("..")
-from multi_run import ag_run 
-
-m_h_0 = -2
-zeta_0 = 0.001
-
-agb_model = surp.yield_models.C_AGB_Model(y0=0.001, zeta=-0.001, tau_agb=1, t_D=0.15)
-cc_lin = surp.yield_models.BiLogLin_CC(y0=-m_h_0 * zeta_0, zeta=zeta_0, y1=0)
-cc_quad = surp.yield_models.Quadratic_CC(y0=0, zeta=0, A=0.001, Z1=0.00016)
-
-
-yields_dict = {
-    "ag" : {
-        "agb": agb_model
-    },
-    "cd" : {
-        "ccsne": 0.001
-        },
-    "in" : {
-        "ccsne": cc_lin
-    },
-    "sn" : {
-        "ccsne": cc_quad
-    },
-    }
-            
-
-if __name__ == "__main__":
-    ag_run(
-            yields_dict = yields_dict,
-    )

### 2025-03-09 models/perturbations/eta2/run.py

@@ -12,19 +12,20 @@ agb_model = surp.agb_interpolator.interpolator("c")
 cc_lin = surp.yield_models.BiLogLin_CC(y0=-m_h_0 * zeta_0, zeta=zeta_0, y1=0)
 cc_quad = surp.yield_models.Quadratic_CC(y0=0, zeta=0, A=0.001, Z1=surp.Z_SUN * 10**m_h_0)
 
+yield_scale = 2
 
 yields_dict = {
     "ag" : {
-        "agb": agb_model
+        "agb": yield_scale*agb_model
     },
     "cd" : {
-        "ccsne": 0.001
+        "ccsne": yield_scale* 0.001
         },
     "in" : {
-        "ccsne": cc_lin
+        "ccsne": yield_scale*cc_lin
     },
     "sn" : {
-        "ccsne": cc_quad
+        "ccsne": yield_scale*cc_quad
     },
 }
             

### 2025-03-09 models/perturbations/template_all/run.py

@@ -8,7 +8,7 @@ from multi_run import ag_run
 m_h_0 = -1
 zeta_0 = 0.001
 
-agb_model = surp.agb_interpolator.interpolator("c", prefactor=zeta_0)
+agb_model = surp.agb_interpolator.interpolator("c")
 cc_lin = surp.yield_models.BiLogLin_CC(y0=-m_h_0 * zeta_0, zeta=zeta_0, y1=0)
 cc_quad = surp.yield_models.Quadratic_CC(y0=0, zeta=0, A=0.001, Z1=surp.Z_SUN * 10**m_h_0)
 

### 2025-03-09 surp/simulation/properties.py

@@ -30,7 +30,6 @@ def create_migration(bins, params):
     - params.n_stars: the number of stars to produce per timestep (gaussian and
         random walk)
     - params.timestep: the timestep of the model
-    - params.sigma_R: the standard deviation of the migration in R 
     - params.verbose: whether to print verbose output (gaussian only)
     - params.seed: the seed for the migration (gaussian only)
     - params.N_star_tot: the total number of stars in the model (hydrodisk only)
@@ -43,7 +42,7 @@ def create_migration(bins, params):
 
     if kind == "rand_walk":
         migration = rand_walk_stars(bins, n_stars=params.n_stars, dt=params.timestep, 
-            name=filename, sigma_R=params.sigma_R
+            name=filename, **params.migration_kwargs
             )
     elif kind == "gaussian":
         final_positions = final_positions_gaussian_py(

### 2025-03-09 carbon_paper/tex/main.tex
draft updates: new set of models with new yield scale

@@
 \newcommand{\aton}{\texttt{\hyperlink{aton}{ATON}}}
-\newcommand{\cfactor}{1.95}
-\newcommand{\nsubgiants}{14,069}
+\newcommand{\cfactor}{2.40}
+\newcommand{\nsubgiants}{14,066}
 
@@
 % other
-\newcommand{\fmeas}{20\%}
 
@@
         \verb|DUPLICATE|.
-We additionally remove stars with no reported (or flagged unreliable), C, Mg, or Fe abundances. These cuts yield a sample containing \nsubgiants\ subgiants.
+We additionally remove stars with no reported (or flagged unreliable), C, N, Mg, or Fe abundances. These cuts yield a sample containing \nsubgiants\ subgiants.
 
@@
 Following \citet{james+23}, we integrate yields and our GCE models using the publicly available Versatile Integrator for Chemical Evolution (\VICE, \citealt{JW20}).
+Our solar abundance scale is from \citet{magg+22} with a 0.04 dex gravitational settling correction.
+Also from \citet{magg+22}, we adopt $\Zo = 0.0176$.
 We use the O, Mg, and Fe yields recommended by \citet{david_fe} based on measurements of the mean CCSN Fe yield \citep{rodriguez+23} and APOGEE chemical abundances.
@@
 The solar abundance scale is \citet{magg+22} + 0.04 dex suggested by \citet{david_fe}.
+        \dbnote{Technically, I believe this abundance scale is off by the hydrogen 1 atomic weight. But this is < the systematic correction so I think this is negligable?}.
     \dbnote{any tips to make this table a little bit smaller?}
@@
     \caption[]{\textbf{Left} The integrated \agb\ C yield $\Ycagb$ as a function of metallicity for each of the \agb\ yield tables.
-    \textbf{Right} cumulative C return fraction as a function of age for a solar metallicity single stellar population.
+        \textbf{Right} cumulative C return fraction as a function of age for a metallicity of ${\rm [M/H]}=-0.1$ single stellar population.
 The dashed black line shows the cumulative return fraction of type Ia supernovae ($\propto t^{-1.1}$) for comparison.
-The minimum of \aton{} is at $y( 0.30\,{\rm Gyr})/y(t_{\rm end})=-7.81$ and is large as the net yield is close to zero.
+The minimum of \aton{} is at $y( 0.30\,{\rm Gyr})/y(t_{\rm end})=-3$ and is large as the net yield is close to zero.
 }
@@
         \fruity 
-                & 3.229
-                &  $3.8\pm0.3$
+                & 3.11
+                &  $3.7\pm0.3$
                 & $-3.5\pm0.3$
-                & 0.14
+                & 0.13
                 & 1.3, 1.5, 2, 2.5, 3, 4, 5, 6
@@
         \aton 
-                & 0.2851
-                & $1.4\pm1.8$
+                & -0.009
+                & $1.0\pm1.8$
                 & $-10. \pm 3$
-                & 0.05
+                & 0.04
                 & 1.5, 2, 2.5, 3, 3.5, 4, 4.5, 5, 6, 6.5, 7
@@
         \monash 
-                &  3.444
-                & $2.8 \pm 0.5$
+                &  2.96
+                & $2.3 \pm 0.5$
                 & $-11.0\pm 1.0$
-                & 0.10
+                & 0.08
                 & 1, 1.25, 1.5, 1.75, 2.25, 2.5, 2.75, 3, 3.25, 3.5, 3.75, 4, 4.5, 5, 5.5, 6, 7 
@@
         \nugrid 
-                & 10.95
-                & $8.3\pm 1.9$
+                & 9.25
+                & $8.1\pm 1.9$
                 & $-4.6\pm1.7$
-                & 0.30
+                & 0.29
                 & 1, 1.65, 2, 3, 4, 5, 6, 7
@@
     \dbnote{might be interesting to plot every CCSNe yield used in this paper in light grey to show strength of our constraint}
+    \dbnote{I may change the piecewise model to be linear in log-log space instead of log-linear space}
         C yields from high-mass stars.
@@
 
-We use the radial migration prescription described in appendix C of \citet{dubay+24}.\footnote{Not shown here, we also explored variations of temporal, spatial resolution, migration strength, and the mass lifetimre relation.
-We found these do not affect median trends significantly.}
+For radial migration of stars, inspired by \citet{frankel18}, we sample the change of radii of stars from a gaussian distribution with standard deviation $\sigma = 3.6\,{\rm kpc} ((t_{\rm end} - t_{\rm birth})/8\,{\rm Gyr})^{0.5}$, where $t_{\rm birth}$ is the birth time of the SSP and $t_{\rm end}=13.2$\,Gyr is the simulation end time.
+Stars migrate to their final position with a $\sqrt{t}$ dependence, consistent with diffusion of angular momentum \citep{frankel18, frankel20}.
+If a star's would move past $R=0$ or $R=20\,$kpc, the star reflects off these boundaries instead with the same velocity.%
+\footnote{Not shown here, we also explored variations of temporal, spatial resolution, migration strength, and the mass lifetime relation. We found these do not affect median trends significantly.}
+\dbnote{ Final set of models will use the radial migration prescription described in appendix C of {dubay+24} instead.
+I have checked that changes to derived parameters for the fiducial model is within the parameter uncertanties, so nothing substantial should change.
+}.
 We do not account for radial gas flows.
@@
 
-As the strength of outflows controls the resulting $\alpha$-element abundances, we extend \JJ and create a metallicity gradient by defining
+As the strength of outflows controls the resulting equilibrium $\alpha$-element abundances, we extend \JJ and create a metallicity gradient by defining
 \begin{equation}\label{eq:mass_loading}
-\eta(R) = \frac{y_{\alpha}^{\rm cc}}{Z_{\alpha}(R)} -1 + r + \tau_{\star} / \tau_{\rm sfh} 
+\eta(R) = \frac{y_{\alpha}^{\rm cc}}{Z_{\alpha}(R)} -1 + r %+ \tau_{\star} / \tau_{\rm sfh} 
 \end{equation}
@@
 \end{equation}
-is adapted from \citet{hayden+14}.  We approximate $r=0.4$, and $\tau_\star/\tau_{\rm sfh} = 0.0$ .
+is adapted from \citet{hayden+14}.  We approximate $r=0.4$. %, and $\tau_\star/\tau_{\rm sfh} = 0.0$ .
 This choice of $\eta(R)$ results in a [$\alpha$/H] gradient consistent with Milky Way observations \citep[e.g.][]{hayden+14, weinberg+19, frinchaboy+13}.
@@
     \zeta^{(2)} &\sim N(0, 4) \\
-    \ln \sigma _{\rm int}&\sim N(-3, 1) \\
+    \ln \sigma _{\rm int}&\sim N(-3, 1)
 \end{align}
@@
 \caption[]{
-A corner plot of the posterior samples from the MCMC simulation for the fiducial + \fruity\ model fit to the binned mean trends.
-$\alpha$ represents the scale factor for the AGB yields, and $\zetao$, $\zetai$ and $\zetaii$ represent the constant, linear, and quadratic components of the CCSN yield.
+A corner plot of the posterior samples from the MCMC simulation for the analytic model fit to the binned mean trends.
+$\alpha$ represents the scale factor for the AGB yields, and $\zetao$, $\zetai$ and $\zetaii$ represent the constant, linear, and quadratic components of the CCSN yield (all scaled by $10^{-3}$).
+$\sigma_{\rm int}$ is the intrensic scatter.
 See section~\ref{sec:mcmc_methods} for a description of the methods.
@@
 Regardless of assumptions, the best values of $\fagb$ range from about 0.1 to 0.35 and in all cases is less than 0.5.
+The black X marks the predicted value of $\fagb$ assuming our fiducial yield scale (as in Table~\ref{tab:agb}).
     \textbf{Right:} The final total C yield (CCSN + AGB) for the median parameters from MCMC fits for each model.
 Additionally, we show individual samples from the \fruity{} \ MCMC model as faint blue lines.
-    \dbnote{mark alpha=1.}
     }
@@
 \begin{table*}
-
     \caption{
         Best-fit parameters (medians and 16-84th percentile errors) from MCMC analysis for various models discussed.
-    The columns are:  modelname \textit{model}, best fit reduced $\chi^2$, best fit log posterior probability $\log p$, AGB scaling $\aagb$, 
-    \dbnote{Not sure if we should use analytic, nugrid, shifted fruity or normal fruity yields as fiducial for this section, e.g. for eta, lateburst, twoinfall, etc...}}
+        The columns are:  modelname \textit{model}, best fit reduced $\chi^2$, best fit log posterior probability $\log p$, AGB scaling $\aagb$, CCSN constant, linear, and quadratic coefficients times $10^3$ $\zetao$, $\zetai$, $\zetaii$, the intrensic scatter $\sigma_{\rm int}$, the AGB fraction $\fagb$, the total C yield at solar metallicity $\Yct$, and the total C yield at solar metallicity $\zeta_{\rm 1, tot}$.
+    }
     \label{tab:mcmc_results}
+
 { 
@@
 \hline
-fruity           &      6.9 &    20.06 & $1.96^{+0.21}_{-0.21}$  &  $2.01^{+0.08}_{-0.08}$  &  $2.20^{+0.15}_{-0.15}$  &  $2.73^{+0.31}_{-0.31}$  &  $0.08^{+0.02}_{-0.01}$  &  $0.27^{+0.03}_{-0.03}$  &  $2.75^{+0.02}_{-0.02}$  &  $1.52^{+0.13}_{-0.13}$\\
-fruity m0.7      &      6.3 &    28.60 & $1.10^{+0.10}_{-0.10}$  &  $2.33^{+0.04}_{-0.04}$  &  $1.71^{+0.11}_{-0.11}$  &  $2.89^{+0.27}_{-0.27}$  &  $0.06^{+0.01}_{-0.01}$  &  $0.17^{+0.01}_{-0.01}$  &  $2.80^{+0.01}_{-0.02}$  &  $1.37^{+0.10}_{-0.10}$\\
-aton             &     10.5 &    10.66 & $1.56^{+0.24}_{-0.24}$  &  $2.50^{+0.04}_{-0.04}$  &  $3.37^{+0.32}_{-0.32}$  &  $2.50^{+0.40}_{-0.39}$  &  $0.11^{+0.02}_{-0.02}$  &  $0.08^{+0.01}_{-0.01}$  &  $2.72^{+0.02}_{-0.02}$  &  $1.81^{+0.17}_{-0.17}$\\
-monash           &     10.8 &     6.86 & $2.06^{+0.37}_{-0.39}$  &  $1.92^{+0.16}_{-0.15}$  &  $3.68^{+0.42}_{-0.45}$  &  $3.52^{+0.47}_{-0.47}$  &  $0.13^{+0.03}_{-0.02}$  &  $0.23^{+0.05}_{-0.05}$  &  $2.49^{+0.05}_{-0.05}$  &  $1.41^{+0.20}_{-0.19}$\\
-nugrid           &      6.1 &    23.68 & $1.00^{+0.10}_{-0.10}$  &  $1.75^{+0.10}_{-0.10}$  &  $1.58^{+0.12}_{-0.12}$  &  $3.19^{+0.31}_{-0.30}$  &  $0.07^{+0.02}_{-0.01}$  &  $0.32^{+0.03}_{-0.03}$  &  $2.58^{+0.02}_{-0.02}$  &  $1.12^{+0.12}_{-0.13}$\\
-analytic         &      5.1 &    29.80 & $0.43^{+0.04}_{-0.04}$  &  $2.33^{+0.04}_{-0.04}$  &  $1.57^{+0.10}_{-0.10}$  &  $2.69^{+0.27}_{-0.26}$  &  $0.06^{+0.01}_{-0.01}$  &  $0.15^{+0.01}_{-0.01}$  &  $2.75^{+0.01}_{-0.01}$  &  $1.15^{+0.10}_{-0.11}$\\
-eta2             &      6.6 &    24.28 & $0.47^{+0.05}_{-0.04}$  &  $2.24^{+0.05}_{-0.05}$  &  $1.45^{+0.09}_{-0.10}$  &  $2.95^{+0.32}_{-0.32}$  &  $0.07^{+0.02}_{-0.01}$  &  $0.17^{+0.02}_{-0.02}$  &  $2.71^{+0.02}_{-0.01}$  &  $0.98^{+0.09}_{-0.09}$\\
-lateburst        &      8.0 &    21.72 & $0.56^{+0.05}_{-0.05}$  &  $2.25^{+0.05}_{-0.05}$  &  $1.75^{+0.18}_{-0.18}$  &  $2.55^{+0.37}_{-0.36}$  &  $0.08^{+0.02}_{-0.01}$  &  $0.20^{+0.02}_{-0.02}$  &  $2.81^{+0.02}_{-0.02}$  &  $1.19^{+0.18}_{-0.18}$\\
-twoinfall        &      6.3 &    17.12 & $0.54^{+0.06}_{-0.06}$  &  $2.31^{+0.07}_{-0.07}$  &  $1.72^{+0.19}_{-0.20}$  &  $1.69^{+0.30}_{-0.30}$  &  $0.09^{+0.02}_{-0.02}$  &  $0.19^{+0.02}_{-0.02}$  &  $2.85^{+0.02}_{-0.03}$  &  $1.18^{+0.20}_{-0.20}$\\
-fruitylin       &    &    & $1.95$  &  $2.10^{+0.02}_{-0.02}$  &  $1.55^{+0.08}_{-0.08}$  &     &  $0.09^{+0.02}_{-0.01}$  &  $0.26^{+0.00}_{-0.00}$  &  $2.84^{+0.02}_{-0.02}$  &  $0.87^{+0.08}_{-0.08}$\\
-analyticlin     &    &    & $0.43$  &  $2.41^{+0.02}_{-0.02}$  &  $0.89^{+0.09}_{-0.09}$  &     &  $0.10^{+0.02}_{-0.01}$  &  $0.15^{+0.00}_{-0.00}$  &  $2.84^{+0.02}_{-0.02}$  &  $0.46^{+0.09}_{-0.09}$\\
-\hline
-total & &   &  -  &  $2.26^{+0.11}_{-0.37}$  &  $1.74^{+1.53}_{-0.24}$  &  $2.79^{+0.49}_{-0.58}$  &  $0.08^{+0.03}_{-0.02}$  &  $0.19^{+0.09}_{-0.04}$  &  $2.74^{+0.07}_{-0.16}$  &  $1.26^{+0.32}_{-0.24}$\\
+\fruity          &      7.4 &    18.43 & $2.41^{+0.26}_{-0.27}$  &  $1.90^{+0.10}_{-0.09}$  &  $2.28^{+0.15}_{-0.16}$  &  $2.59^{+0.30}_{-0.30}$  &  $0.08^{+0.02}_{-0.01}$  &  $0.32^{+0.03}_{-0.04}$  &  $2.79^{+0.02}_{-0.02}$  &  $1.43^{+0.12}_{-0.13}$\\
+\aton            &     14.9 &     5.30 & $1.71^{+0.34}_{-0.34}$  &  $2.55^{+0.05}_{-0.05}$  &  $3.19^{+0.40}_{-0.40}$  &  $1.92^{+0.45}_{-0.44}$  &  $0.14^{+0.03}_{-0.02}$  &  $0.06^{+0.01}_{-0.01}$  &  $2.72^{+0.03}_{-0.03}$  &  $1.48^{+0.20}_{-0.19}$\\
+\monash          &     15.4 &     2.24 & $2.06^{+0.52}_{-0.54}$  &  $2.03^{+0.19}_{-0.18}$  &  $3.82^{+0.64}_{-0.66}$  &  $3.48^{+0.57}_{-0.59}$  &  $0.15^{+0.03}_{-0.02}$  &  $0.19^{+0.05}_{-0.05}$  &  $2.50^{+0.07}_{-0.07}$  &  $1.55^{+0.21}_{-0.22}$\\
+\nugrid          &      5.8 &    24.19 & $1.21^{+0.11}_{-0.11}$  &  $1.58^{+0.11}_{-0.11}$  &  $1.58^{+0.11}_{-0.11}$  &  $3.16^{+0.29}_{-0.28}$  &  $0.07^{+0.02}_{-0.01}$  &  $0.38^{+0.04}_{-0.04}$  &  $2.56^{+0.02}_{-0.02}$  &  $1.02^{+0.11}_{-0.11}$\\
+\fruity\ m0.7    &      4.5 &    32.86 & $1.39^{+0.11}_{-0.10}$  &  $2.25^{+0.04}_{-0.04}$  &  $1.55^{+0.09}_{-0.08}$  &  $2.54^{+0.23}_{-0.22}$  &  $0.05^{+0.01}_{-0.01}$  &  $0.21^{+0.02}_{-0.01}$  &  $2.83^{+0.01}_{-0.01}$  &  $1.12^{+0.09}_{-0.09}$\\
+\fruity\ linear  &   3036 &    16.18 & $2.40^{+0.00}_{-0.00}$  &  $1.99^{+0.02}_{-0.02}$  &  $1.68^{+0.08}_{-0.09}$  &     &  $0.10^{+0.02}_{-0.02}$  &  $0.31^{+0.00}_{-0.00}$  &  $2.88^{+0.02}_{-0.02}$  &  $0.84^{+0.08}_{-0.09}$\\
+$y\rightarrow 2y$ &      6.0 &    20.61 & $2.51^{+0.25}_{-0.25}$  &  $1.83^{+0.09}_{-0.09}$  &  $2.00^{+0.12}_{-0.12}$  &  $2.41^{+0.29}_{-0.29}$  &  $0.08^{+0.02}_{-0.01}$  &  $0.34^{+0.03}_{-0.03}$  &  $2.76^{+0.02}_{-0.02}$  &  $1.12^{+0.08}_{-0.08}$\\
+lateburst        &     18.7 &     8.35 & $2.41^{+0.35}_{-0.36}$  &  $2.00^{+0.12}_{-0.12}$  &  $2.92^{+0.34}_{-0.34}$  &  $3.51^{+0.66}_{-0.65}$  &  $0.13^{+0.02}_{-0.02}$  &  $0.31^{+0.04}_{-0.04}$  &  $2.89^{+0.03}_{-0.03}$  &  $2.07^{+0.32}_{-0.32}$\\
+twoinfall        &     10.6 &    18.05 & $2.03^{+0.21}_{-0.21}$  &  $2.05^{+0.08}_{-0.08}$  &  $2.65^{+0.20}_{-0.20}$  &  $3.52^{+0.35}_{-0.36}$  &  $0.09^{+0.02}_{-0.01}$  &  $0.27^{+0.03}_{-0.03}$  &  $2.80^{+0.02}_{-0.02}$  &  $1.94^{+0.18}_{-0.19}$\\
+SN Ia 1.2        &      9.3 &    13.10 & $3.29^{+0.43}_{-0.45}$  &  $1.57^{+0.16}_{-0.15}$  &  $2.73^{+0.22}_{-0.23}$  &  $2.72^{+0.35}_{-0.35}$  &  $0.10^{+0.02}_{-0.02}$  &  $0.44^{+0.06}_{-0.06}$  &  $2.79^{+0.02}_{-0.02}$  &  $1.58^{+0.14}_{-0.14}$\\
+
 \hline
@@
         Similar to Fig.~\ref{fig:zeta_f}, except for \caafe\ for a variety of models.
-        {\bf Left} models where both the \agb\ fraction and the CCSNe slope are varied simultaneously.
-        {\bf Middle} models where the \agb\ yields are shifted by some factor in mass.
-        {\bf Right} alternate star formations and a model where yields and outflows are $\sim$ doubled.
-    \dbnote{update caption here}
+        {\bf Left} models for AGB fractions of 0.1, 0.25 (fiducial), and 0.4. 
+        {\bf Middle} models where the \agb\ yields are shifted by a factor in mass.
+        {\bf Right} alternate star formations histories (lateburst and twoinfall) and a model with all yields doubled.
     }
@@
 Variations in the \caafe\ plane are due to the different total AGB C yield and variations in the mass-dependence of each yield table.
-    \dbnote{use actual best fit median trends here instead of inferred yields? Update labels, remove one of analytic / fruity m0.7}.
     }
@@
 
-We also consider a two-infall like model as presented in \dbadd{dubay + 24}, which is defined as.
+We also consider a two-infall like model as presented in \citep{dubay+24},
 \begin{equation}\label{twoinfall}
@@
 \end{equation}
-where $\tau_1=\#\,$Gyr, $\tau_2=4\,$Gyr, $A=\Sigma_{\rm thin} / \Sigma_{\rm thick}$ \dbadd{explanation}, $t_2=4$, and the star formation also abruptly transitions from $\nu=2$/Gyr to $\nu=1$/Gyr at $t=t_1$?
+where $\tau_1=1\,$Gyr, $\tau_2=4\,$Gyr, $t_2=4$\,Gyr, and the the amplitude is given by the ratio between the thick and thin disk in
 
@@
 \caption[]{
-\dbnote{will probably add each SZ model description to fig caption. Should citations be moved outside of caption for reader's sake?}
-\dbnote{remove connecting lines on MW HII regions. Should I plot outliers at all?}.
+\dbnote{Should citations be moved outside of caption for reader's sake?}
+\dbnote{Remove connecting lines on MW HII regions. Should I plot outliers at all?}.
+\dbnote{unfortunantly the models in this figure are not consistent with this draft, accedentily deleted/didn't save some of the observed data and will fix in next draft.}
 Gas-phase C abundances. 
@@
 	\centering
-    \caption[]{Description of the models presented in this paper.}
+        \caption[]{Description of the models presented in this paper. \dbnote{none of these are accurate currently}}
 	\label{tab:model_parameters}

### 2025-03-11 carbon_paper/tex/main.tex
draft for collab. comments

@@
 \documentclass[fleqn,
-% referee, % this line changes to double-spaced 1 column
+referee, % this line changes to double-spaced 1 column
 usenatbib]{mnras}
@@
 \newcommand{\aton}{\texttt{\hyperlink{aton}{ATON}}}
-\newcommand{\cfactor}{2.40}
+\newcommand{\cfactor}{2.4}
+\newcommand{\zetaobest}{1.90 \pm 0.10}
+\newcommand{\zetaibest}{2.28 \pm 0.16}
+\newcommand{\zetaiibest}{2.59 \pm 0.30}
+
 \newcommand{\nsubgiants}{14,066}
@@
 Recent work additionally suggests that small changes in a stars's initial mass of 
- $\sim$$0.01 M_\odot$  have significant effects on the evolution and explosion outcomes of massive stars \citep{bruenn+2023, vartanyan_burrows2023}.
+$\sim$$0.01 \Mo$  have significant effects on the evolution and explosion outcomes of massive stars \citep{bruenn+2023, vartanyan_burrows2023}.
  Furthermore, many stars are found in binary systems \citep{sana+12}, the effects of which are almost entirely
@@
 In equilibrium GCE, trends in abundance ratios closely trace yield ratios (see their section 5.2.2).
-\citet{james+23} had previously shown that the correlation between gas-phase N and O abundances (see their Fig.
+\citet{james+23} had previously shown that the correlation between gas-phase N and O abundances (see their fig.
 1) could be described as a consequence of the metallicity dependence of the relative N and O yields.
@@
 
-% \footnotetext{\strike{By metallicity, we mean the (mass) fraction of any element which is not H or He, denoted by $Z$. For the sun, we take $Z_\odot=0.0176$.} }
+% \footnotetext{\strike{By metallicity, we mean the (mass) fraction of any element which is not H or He, denoted by $Z$. For the sun, we take $\Zo=0.0176$.} }
 
@@
 Our aim is to reproduce these trends.
+Low-$\alpha$ stars are defined to have 
+\begin{equation}\label{eq:high_alpha}
+\begin{cases}
+\text{[Mg/Fe]} <0.16-0.13\,\text{[Fe/H]}, & \text{[Fe/H]}<0\\
+\text{[Mg/Fe]} <0.16, & \text{[Fe/H]}>0. \\
+\end{cases}
+\end{equation}
 
@@
         Fe & $13.7\times10^{-4}$ & $4.73\times10^{-4}$ & 0 & $7.82\times10^{-4}$ \\
-        N & $10.4\times10^{-4}$ & $5\times10^{-4}$ & $5\times10^{-4}M\left(\frac{Z}{Z_\odot}\right)$ & 0\\
+        N & $10.4\times10^{-4}$ & $5\times10^{-4}$ & $5\times10^{-4}M\left(\frac{Z}{\Zo}\right)$ & 0\\
 		\hline
@@
     \caption[]{For each \agb\ yield set, the IMF-averaged \agb\ C yield at solar metallicity $y_{\rm C, 0}^{\rm AGB}$, the linear fit solar yield $\zetao$ and slope $\zetai$ (see Eq.~\ref{eq:agb_z_approx}), the fraction of solar C produced in the model $f_\odot^{\rm AGB}$, and the masses and metallicities each yield table is sampled on.
-    $f_{\rm odot}^{\rm AGB}$ is calculated based on $\zetao$ assuming a total C yield of $\Yct = 0.00275$.
+    $f_{\sun}^{\rm AGB}$ is calculated based on $\zetao$ assuming a total C yield of $\Yct = 0.00275$.
     }
@@
         \agb\ table 
-                & $y_{\rm C, \odot}^{\rm AGB}\times10^4$ %& y
+                & $y_{\rm C, \sun}^{\rm AGB}\times10^4$ %& y
                 & $\zetao^{\rm AGB}\times 10^4$ %& y
                 & $\zetai^{\rm AGB}\times 10^4$
-                &  $f_\odot^{\rm AGB}$
+                &  $f_{\sun}^{\rm AGB}$
                 & masses ($\Mo$) & metallicities ($Z$)\\
@@
 The left panel of Fig.~\ref{fig:y_cc} also shows the IMF-averaged \agb\ star yields from the \fruity\ model (in Fig.~\ref{fig:agb-ssp}).
-Especially at $Z\approx Z_\odot$, most \cc\ models dominate \agb\ C production.
+Especially at $Z\approx \Zo$, most \cc\ models dominate \agb\ C production.
 
@@
 \dbstrike{The latter can be expressed as an integral over the SN Ia delay-time-distribution (DTD), which describes the rate at which stellar populations produce X through SN Ia in \VICE.} Following \citet{james+23}, we use a $t^{-1.1}$  delay time distribution (DTD) with a minimum delay-time of 150 Myr, based on comparisons of the SN Ia rate as a function of redshift and the cosmic SFR (e.g.
-\citealt{maoz+12}).
-
-Supernovae type Ia produce negligible C.
-For our adopted yield scale, the highest magnitude CCSNe yield of the models from iwamoto99 is $1.1\times10^{-4}$, corresponding to about 4\% of our total C production, however most models predict a \ia\ C yield of less than $0.4 \times 10^{-4}$.
-We do check that including this contribution negligibly impacts our results, so we neglect SNIa C production for simplicity.
-
-Novae are important contributes of \C[13], but produce far less \C[12] \dbadd{CITE}.
+\citealt{maoz+mannucci12}).
+
+SN Ia produce negligible C.
+Of the models from \citet{iwamoto+99}, \citet{seitenzahl+13}, and \citet{gronow+21a, gronow+21b}, the maximum C production is less than 4\% of our required solar C yield, and most likely less than 2\% (assuming a SNIa rate of $2.2\times 10^{-3} / \Mo$ \citealt{maoz+mannucci12}).
+
+Novae are important contributes of \C[13], but do not process enough material to impact \C[12] production. \C[13] is beyond the scope of this work.
 
@@
 \begin{equation}
-    \log Z_{\alpha}(R) = \log Z_{\alpha,\ \odot} + 
+    \log Z_{\alpha}(R) = \log Z_{\alpha,\ \sun} + 
     0.29 + 
@@
 \dbnote{might be useful to include a complete set of differential equations for our model somewhere to better illustrate this.}
-Assume that the yields do not depend on the yields (e.g. metallicity dependence is negligable). 
-Given a set of yields $\{y_X^i\}_i$ and resulting abundance evolution $\{Z_{X}^i(R, t) \}$, let $y_X'$, the yield of X, be a linear combination of $\{y_X^i\}$
+Assume that the total metallicity evolution does not depend on the elemental yield we are considering.
+Say we are given a set of yield processes of $X$, $\{y_X^i\}_i$, and the resulting abundance evolution, $\{Z_{X}^i(R, t) \}_i$.
+Let $y_X'$, the total yield of $X$, be a linear combination of $\{y_X^i\}$, so
 \begin{equation}
@@
 Note that many other GCE parameters are nonlinear with abundance and require full multi-zone simulations, such as star formation history, outflows, and migration prescriptions.
-Also note that metallicity-dependent yields also introduce a second-order effect (metallicity depends on yields which depend on metallicity).
+Also note that metallicity-dependent yields introduce a second-order effect (metallicity depends on total yields which depend on metallicity), but for small changes to total yields, this effect should be small.
 
@@
 \end{equation}
-Similarly, we represent the mean and variance of the observations in each bin $b$ with $\bar Z_{b, \rm obs}$ and $\sigma^2_{b, \rm obs}$.  
+Similarly, we represent the mean and variance of the observations in each bin $b$ with $\bar Z_{b, \rm obs}$ and $\sigma^2_{b, \rm obs}$.  We use the a likelihood
 \begin{equation} \label{eq:mcmc_likelihood}
@@
 \begin{equation}
-    \sigma_{b, \rm tot} = \sigma_{\rm int}^2 + \sigma_{b, \rm obs}^2 + \sigma^2_{b, \rm model}
-\end{equation}
-where we model $\sigma_{\rm int}^2$ as a free parameter in the model.
-\footnotetext{In detail, $y_1$ and $y_2$ are held constant past $\log Z/\Zo < -2$ and the $y_1$ component is modelled with a positive constant offset later subtracted to avoid negative abundances.}
-
-We adopt the following priors
+    \sigma_{b, \rm tot}^2 = \sigma_{\rm int}^2 + \sigma_{b, \rm obs}^2 + \sigma^2_{b, \rm model}.
+\end{equation}
+We model $\sigma_{\rm int}^2$ as a free parameter in the model.
+\footnotetext{$y_1$ and $y_2$ are held constant past $\log Z/\Zo < -1$ and the $y_1$ component is modelled with a positive constant offset later subtracted to avoid negative abundances.}
+
+We adopt the following loose priors
 \begin{subequations}
@@
 \end{subequations}
-We run the MCMC using Turing.jl with a No-U-turn sampler (acceptance rate of 0.65), combining 16 independent chains with 3,000 steps each for a total of 48,000 samples.
+We run the MCMC using Turing.jl \citep{turingjl} with a No-U-turn sampler (adaptive Hamilton Monte-Carlo algorithm, \citealt{NUTS}) with an acceptance rate of 0.65.
+We combine 16 independent chains with 3,000 steps each for a total of 48,000 samples.
 
@@
 
+The median parameters derived from this model provide the yield choices for the fiducial and each AGB multizone model shown later.
 \section{Results}\label{sec:results}
@@
     Each line represents a zone at a different galactic radius and is colour-coded by time. While \caah\ settles into the final trend $\sim{8}$\,Gyr ago, \caafe\ continues to evolve for much longer.
-    \dbnote{radii between 2kpc and 15.5 kpc ?}
-    \dbnote{add equilibrium lines (green?)}
+    Only zones between 2 and 15.5 kpc are shown. The green lines represent the equilibrium tracks.
 }
@@
 Fig.~\ref{fig:c_evo} shows evolutionary tracks for every zone of the fiducial model.
-\caah\ trend quickly reaches our equilibrium state in \about{5}\,Gyr. \caafe\ tracks continue to evolve due to the long tail in the DTD of \ia.
+\caah\ trend quickly reaches an equilibrium state in \about{5}\,Gyr. \caafe\ tracks continue to evolve due to the long tail in the DTD of \ia.
 
@@
 [Fe/H] continues to increase due to ongoing \ia\ from old stellar populations.
-    \item {\it Present day.} The abundances of C, Mg, and Fe reach their equilibrium values.
+    \item[(4)] {\it Present day.} The abundances of C, Mg, and Fe reach their equilibrium values.
 
@@
 
- Fig.~\ref{fig:c_evo} {\color{red} will} show the  equilibrium tracks in \caah\, and \caafe.
+ Fig.~\ref{fig:c_evo} also shows the  equilibrium tracks in \caah\, and \caafe.
 Based on the \citepos{WAF17} analytic models of chemical equilibrium for constant star formation, the equilibrium abundance ratio between two elements depends only on the relative yields.
@@
 \begin{equation}\label{eq:equilibrium_yields}
-    {\rm [C/Mg]_{eq}} \equiv \log \left(\frac{\Ycc + \Ycagb }{y_{\rm Mg}}\right) - \log \left(\frac{Z_{\rm C,\,\odot}}{Z_{\rm Mg,\,\odot}}\right)
+    {\rm [C/Mg]_{eq}} \equiv \log \left(\frac{\Ycc + \Ycagb }{y_{\rm Mg}}\right) - \log \left(\frac{Z_{\rm C,\,\sun}}{Z_{\rm Mg,\,\sun}}\right)
 \end{equation}
 As such, the equilibrium abundance represents the steady-state expectation for C abundances.  
-However, in the \caafe\ plane, the equilibrium track is constant in [Mg/Fe] and only appears as a vertical line representing the range of equilibrium [C/Mg] values.
+However, in the \caafe\ plane, equilibrium [Mg/Fe] is single-valued, so equilibrium track is a vetical line representing the range of ${\rm [C/Mg]_{eq}}$ across metallicity.
 The trends in \caafe\ are instead representative of the temporal evolution of [C/Mg].
 \caafe\ is well approximated by either a single-stellar-population or a single zone model because of the shallow metallicity gradient of the Milky Way.
-\dbnote{is this right?}
 
@@
 However, \caafe~is minimally affected by changes to $\zcc$ for stars at a given [Mg/H].
-CCSN occurs on much shorter timescales than AGB and SN Ia enrichment, so CC carbon reaches equilibrium before delayed C and Fe production modifies trends. 
+CCSN occurs on much shorter timescales than AGB and SN Ia enrichment, so CCSN carbon reaches equilibrium before delayed C and Fe production modifies trends. 
 \footnote{The only effects on \caafe, when considering the narrow metallicity slice, are because of either the systematic change in equilibrium abundances, the imperfect evolution of the galaxy, or that the ISM abundances are set by stars which were born at poorer metallicities.
@@
 \begin{equation}\label{eq:f_agb}
-    \fagb \equiv \frac{\Ycagb(\Zo)}{\Yct(\Zo)}.
+    \fagb := \frac{\Ycagb(\Zo)}{\Yct(\Zo)} \propto \aagb.
 \end{equation}
@@
 Though each yield model predicts the trend to flatten at ${\rm [Mg/Fe]} \lesssim 0.1 $, the median is still within the width of the observed distribution and the overall agreement is good.
-Additionally, increasing \agb\ contribution to C leads to a declining net slope for the total C yield owing to the negative slope of \agb\ C production with metallicity.
+Additionally, increasing $\fagb$ decreases the slope in \caah\ owing to the negative metallicity dependence of AGB C yields with metallicity.
 
@@
 \begin{equation}
-    \frac{\Ycc}{y_{\rm Mg}} = (2.01\pm  0.08) + (2.20 \pm 0.15) x + (2.73 \pm 0.31) x^2
+    \frac{\Ycc}{y_{\rm Mg}} = (\zetaobest) + (\zetaibest) x + (\zetaiibest) x^2
 \end{equation}
@@
 \fruity\ m0.7    &      4.5 &    32.86 & $1.39^{+0.11}_{-0.10}$  &  $2.25^{+0.04}_{-0.04}$  &  $1.55^{+0.09}_{-0.08}$  &  $2.54^{+0.23}_{-0.22}$  &  $0.05^{+0.01}_{-0.01}$  &  $0.21^{+0.02}_{-0.01}$  &  $2.83^{+0.01}_{-0.01}$  &  $1.12^{+0.09}_{-0.09}$\\
-\fruity\ linear  &   3036 &    16.18 & $2.40^{+0.00}_{-0.00}$  &  $1.99^{+0.02}_{-0.02}$  &  $1.68^{+0.08}_{-0.09}$  &     &  $0.10^{+0.02}_{-0.02}$  &  $0.31^{+0.00}_{-0.00}$  &  $2.88^{+0.02}_{-0.02}$  &  $0.84^{+0.08}_{-0.09}$\\
 $y\rightarrow 2y$ &      6.0 &    20.61 & $2.51^{+0.25}_{-0.25}$  &  $1.83^{+0.09}_{-0.09}$  &  $2.00^{+0.12}_{-0.12}$  &  $2.41^{+0.29}_{-0.29}$  &  $0.08^{+0.02}_{-0.01}$  &  $0.34^{+0.03}_{-0.03}$  &  $2.76^{+0.02}_{-0.02}$  &  $1.12^{+0.08}_{-0.08}$\\
@@
 SN Ia 1.2        &      9.3 &    13.10 & $3.29^{+0.43}_{-0.45}$  &  $1.57^{+0.16}_{-0.15}$  &  $2.73^{+0.22}_{-0.23}$  &  $2.72^{+0.35}_{-0.35}$  &  $0.10^{+0.02}_{-0.02}$  &  $0.44^{+0.06}_{-0.06}$  &  $2.79^{+0.02}_{-0.02}$  &  $1.58^{+0.14}_{-0.14}$\\
+\fruity\ linear  &   3036 &    --- & {\it 2.40}  &  $1.99^{+0.02}_{-0.02}$  &  $1.68^{+0.08}_{-0.09}$  &  ---  &  $0.10^{+0.02}_{-0.02}$  &  $0.31$  &  $2.88^{+0.02}_{-0.02}$  &  $0.84^{+0.08}_{-0.09}$\\
 
@@
 \end{equation}
-where $\tau_1=1\,$Gyr, $\tau_2=4\,$Gyr, $t_2=4$\,Gyr, and the the amplitude is given by the ratio between the thick and thin disk in
+where $\tau_1=1\,$Gyr, $\tau_2=4\,$Gyr, $t_2=4$\,Gyr, and the the amplitude is given by the ratio between the thick and thin disk in  \citet{BHG16}.
 
@@
 Increasing both $y_{\rm Fe}^{\rm Ia}$ and $\Ycagb$ correspondingly leaves \caafe\ mostly unchanged.
-Not shown here, if both processes increase by a similar proportion of the total yield, then our predictions in \caafe\ are unchanged.
-Therefore, we cannot know the DTD of C more accurately than that of Fe in this framework.
+As showin in the left panel of Fig.~\ref{fig:mcmc_ytot}, increasing the SN Ia Fe yield by 1.2 times results in a similarly sized increase in the derived $\fagb$.
+In this framework, our accuracy is limited to that of the Fe DTD.
 
@@
 We are able to closely match the [C/N]-[Mg/H] trend.
-\dbnote{sentence about [C/N]-[Mg/Fe]}
+The [C/N]-[Mg/Fe] relation, on the other hand, is shallower than the data, indicating that the DTD of C production may be sharper than our AGB yield tables would suggest (or the N DTD more extended, or both).
 
@@
 Points represent measurements in 
-    MW HII regions \citep[orange circles][]{mendez-delgado+22}
-    extragalactic RL HII regions \citep[green circles;][]{peimbert+05, skillman+20, toribio-san-cipriano+16, toribio-san-cipriano+17, esteban+14, esteban+09}
-    extragalactic CEL HII regions \citep[green diamonds;][]{garnett+95, senchyna+17, izotov+thuan99, garnett+99, berg+16, berg+19, pena-guerrero+17}
-    damped Lyman-alpha (DLA) systems \citep[rust triangles;][]{omera+01, cooke+14, welsh+22, ellison+10, welsh+20, cooke+18, riemer-sorensen+17, DZ+03, cooke+17, cooke+11, dutta+14, morrison+16, srianand+10, pettini+08, kislitsyn+24, cooke+15},
     Milky Way stars \citep[yellow stars;][]{amarsi+19},
-    and high redshift galaxies \citep[pink squares, CEL lines;][]{steidel+16, stark+14, matthee+21, mainali+20, jones+23, amorin+17, iani+23, james+14, erb+10, bayliss+14, berg+18, christensen+12, arellano-cordova+2022}.
+    MW HII regions \citep[orange pentagons][]{mendez-delgado+22}
+    extragalactic RL HII regions \citep[green open diamonds;][]{peimbert+05, skillman+20, toribio-san-cipriano+16, toribio-san-cipriano+17, esteban+14, esteban+09}
+    extragalactic CEL HII regions \citep[green full diamonds;][]{garnett+95, senchyna+17, izotov+thuan99, garnett+99, berg+16, berg+19, pena-guerrero+17}
+    high redshift galaxies \citep[pink squares, CEL lines;][]{steidel+16, stark+14, matthee+21, mainali+20, jones+23, amorin+17, iani+23, james+14, erb+10, bayliss+14, berg+18, christensen+12, arellano-cordova+2022},
+    and
+    damped Lyman-alpha (DLA) systems \citep[rust triangles;][]{omera+01, cooke+14, welsh+22, ellison+10, welsh+20, cooke+18, riemer-sorensen+17, DZ+03, cooke+17, cooke+11, dutta+14, morrison+16, srianand+10, pettini+08, kislitsyn+24, cooke+15}.
 
@@
 in the gas phase.
-Besides stellar observations, C has been observed in extragalactic HII regions, high redshift galaxies (HII regions), metal-poor stars, and Damped-Lynman-$\alpha$ systems (DLAs).\footnote{DLAs are gas clouds observed as absorption spectra in front of background quasars}
+C has also been observed in extragalactic HII regions, high redshift galaxies (HII regions), metal-poor stars, and Damped-Lynman-$\alpha$ systems (DLAs).\footnote{DLAs are gas clouds observed as absorption spectra in front of background quasars}
 While we used Mg as our representative alpha element in our APOGEE sample, O
@@
 Near solar metallicities, most observations (from disky galaxies) have near-solar [C/O].
-As metallicity decreases, [C/O] also decreases, reaching a minimum of \about{-0.6} around ${\rm [O/H] \sim -1}$.
+As metallicity decreases, [C/O] also decreases, reaching a minimum of $\approx-0.6$ around ${\rm [O/H] \approx -1}$.
 Finally, [C/O] appears to increase again at the lowest metallicities observed (${\rm [M/H] \lesssim -2}$).
@@
     \Ycc / 10^{-3} = \begin{cases}
-        0.8 & \log Z / \Zo < -1.81 \\
-        2.41 + 0.89\, \log Z / \Zo & {\rm otherwise }
+        0.8 & \log Z / \Zo < {\rm number} \\
+        1.99 + 1.68\, \log Z / \Zo & {\rm otherwise }
     \end{cases}
@@
 The small effects of \agb\ C yield on the \caah\ trend can be easily corrected by small adjustments of the \cc\ yield's metallicity dependence.
-Our predicted slope of NUMBER is approximately consistent with the \citet{LC18} rotating stellar models, however no simulation contains sufficient mass resolution or accuracy to reproduce the observed trends accurately.
+Our predicted slope of $\zetaibest$ is qualitatively consistent with the \citet{LC18} rotating stellar models, however no simulation contains sufficient mass resolution or accuracy to reproduce the observed trends accurately.
 
 Because massive star enrichment dominates the C mass budget in our models, the predictions are relatively insensitive to the choice of AGB star yield model.
-Of the \agb\ tables tested here, \fruity, \monash, and \nugrid\ all predict similar abundance trends in [C/Mg] with [Mg/H] and [Fe/Mg].
-The strong destruction of C by massive stars at \about{} solar metallicity   in \aton\ are instead in tension with the data (See Figs.~\ref{fig:agb_predictions})  and~\ref{fig:agb-ssp})
-As both the \fruity\ and \nugrid\ models predict \about{} linear N yields as well, these combined models best explain combined C and N abundance trends (see Appendix!?).
+All the \agb\ tables tested here predict similar abundance trends in [C/Mg] with [Mg/H] and [Fe/Mg].
 
@@
 Effects such as black hole formation could create systematic shifts on predicted chemical yields.
-Variations in the SFH instead only induce minor systematic shifts
+Variations in the SFH instead only induce minor systematic shifts to the predictions.
+However, uncertanties in which AGB stars produce C and the production and DTD of Fe introduce large systematic uncertanties.
 
 When combined with~\citeauthor{james+23}'s~\citeyearpar{james+23} empirically calibrated N yields, we find that our fiducial model accurately describes the [C/N]-[Mg/H] relation in our sample.
-The [C/N]-[Mg/Fe] relation, on the other hand, is shallower than the data, indicating that the DTD of C production may be sharper than our AGB yield tables would suggest (or the N DTD more extended, or both).
 
 Finally, we compare our models againsts a compilation of literature gas-phase and halo-star abundances (see Fig.~\ref{fig:gas_phase}).
-Our fiducial model fails to explain the lowest values of [C/O] at metallicities of -1 to -2.
+Our fiducial model fails to explain the lowest values of [C/O] at metallicities of $[O/H] = -1$ to $-2$.
 We briefly consider a modified variation of the CCSNe yield of C which drops to explain these values, which maintains trends consistant with APOGEE.
@@
 With abundance measurements for several million stars provided by upcoming spectroscopic surveys, particularly SDSS-V's Milky Way Mapper program~\citep{sdssv}, constraints on both stellar nucleosynthesis and the assembly history of our Galaxy will become increasingly more powerful.
-
-More C observations across different galactic environments will continue to refine a complete understanding of C production, including the yields of the first stars,  evolution in the bulge, and so on.
+Observing C across a pleothora of environments at higher precision will allow for yet more detailed understanding of C nucleosynthesis, creating yet more stringent tests for stellar evolution theory.
 
@@
 	\centering
-        \caption[]{Description of the models presented in this paper. \dbnote{none of these are accurate currently}}
+        \caption[]{Description of the models presented in this paper. \dbnote{Names are slightly inconsistent, will update with next draft.}}
 	\label{tab:model_parameters}
@@
             \hline
-            fiducial & 1.95 & fruity & 2.01 & 2.19 & 2.72 \\
-            Monash & 2.06 & monash & 1.92 & 3.68 & 3.52 \\
-            ATON & 1.56 & aton & 2.50 & 3.37 & 2.50 \\
-            NuGRID & 1.00 & nugrid & 1.75 & 1.58 & 3.19 \\
-            steep & 1.95 & fruity & 2.01 & 3.0 & 2.72 \\
-            shallow & 1.95 & fruity & 2.01 & 1.0 & 2.72 \\
-            f=0.1 & 0.721 & fruity & 2.47 & 2.19 & 2.72  \\
-            f=0.4 & 2.88 & fruity & 1.64 & 2.19 & 2.72 \\
-            f=0.1, zeta & 0.721 & fruity & 2.47 & 1.75 & 2.72  \\
-            f=0.4, zeta & 2.88 & fruity & 1.64 & 2.51 & 2.72 \\
-            m0.5 & 2.23 & fruity(m/0.5)  & 2.27 & 1.60 & 2.23 \\
-            m0.7 & 1.73 & fruity(m/0.7) & 2.08 & 1.83 & 3.31 \\
-            m1.5 & 2.12 & fruity(m/1.5) & 2.02 & 1.98 & 2.27 \\
+            FRUITY (fiducial) & 2.40 & fruity & 1.90 & 2.27 & 2.58 \\
+            Monash & 2.06 & monash & 2.03 & 3.82 & 3.48 \\
+            ATON & 1.71 & aton & 2.55 & 3.19 & 1.92 \\
+            NuGRID & 1.21 & nugrid & 1.58 & 1.58 & 3.16 \\
+            $\zetai=0.001$ & 2.40 & fruity & 1.90 & 3.0 & 2.58 \\
+            $\zetai=0.003$ & 2.40 & fruity & 1.90 & 1.0 & 2.58 \\
+            $\fagb=0.1$ & 0.754 & fruity & 2.51 & 2.27 & 2.58  \\
+            $\fagb=0.5$ & 3.77 & fruity & 1.40 & 2.27 & 2.58 \\
+            lower $\fagb$, $\zetai$ & 0.754 & fruity & 2.51 & 1.75 & 2.58  \\
+            higher $\fagb$, $\zetai$ & 3.77 & fruity & 1.40 & 2.75 & 2.58 \\
+            m0.5 & 2.69 & fruity(m/0.5)  & 2.21 & 1.13 & 2.45 \\
+            m0.7 & 2.11 & fruity(m/0.7) & 1.98 & 1.66 & 3.01 \\
+            m1.5 & 2.60 & fruity(m/1.5) & 1.89 & 1.83 & 1.66 \\
+            m0.7 best & 1.39 & fruity(m/0.7) & 2.25 & 1.55 & 2.54 \\
 		\hline
@@
 
+\ref{tab:model_parameters} lists the parameters of the models used in this paper.
+
+\dbnote{this is not actually used in the current draft, only for scatter plots of model stars}.
 For our added scatter, we use the polynomial fits to the reported internal APOGEE error with metallicity.
@@
 \end{subequations}
-
-Low-$\alpha$ stars are defined to have 
-\begin{equation}\label{eq:high_alpha}
-\begin{cases}
-\text{[Mg/Fe]} <0.16-0.13\,\text{[Fe/H]}, & \text{[Fe/H]}<0\\
-\text{[Mg/Fe]} <0.16, & \text{[Fe/H]}>0. \\
-\end{cases}
-\end{equation}
 

### 2025-03-19 carbon_paper/mc_plot_utils.py
plot scripts

@@ -10,6 +10,9 @@ from corner import corner
 import arya
 import surp.gce_math as gcem
 
+import os
+
+current_dir = os.path.dirname(os.path.abspath(__file__))
 
 @dataclass
 class MCMCResult:
@@ -23,7 +26,7 @@ class MCMCResult:
 
     @classmethod
     def from_file(cls, modelname, y0=None, y_a=None, zeta_a=None, burn=0):
-        modeldir = "../models/perturbations/mc_analysis/" + modelname + "/"
+        modeldir = current_dir + "/../models/perturbations/mc_analysis/" + modelname + "/"
     
         with open(modeldir + "params.toml", "r") as f:
             params = toml.load(f)

### 2025-03-19 carbon_paper/plots/mcmc_fagb.py

@@ -1,0 +1,65 @@
+Nr = len(plot_labels)
+fig, axs = plt.subplots(Nr, 1, figsize=(3, 2), sharex="col", gridspec_kw={"hspace": 0})
+
+for i, (key, label) in enumerate(plot_labels.items()):
+    if key == "hline":
+        ax = axs[i]
+        plt.sca(axs[i])
+        ax.spines[['bottom', 'top']].set_visible(False)
+        plt.axhline(0.5, color=label, linestyle=":")
+        ax.xaxis.set_visible(False)
+        ax.set_yticks([])
+        ax.set_yticks([], minor=True)
+        
+        continue
+
+    if i < 5:
+        color = arya.COLORS[i]
+        ls = "-"
+    else:
+        ls = "--"
+        color = arya.COLORS[0]
+
+    result = results[key]
+    ax = axs[i]
+    plt.sca(axs[i])
+    plt.hist(result.samples.f_agb_a, color=color, ls=ls)
+    plt.ylabel(label, rotation=0, ha="right", va="center")
+
+    if key in yagb_props.keys():
+        y_a = yagb_props[key]["y_a"]
+    elif key == "fruity_m0.7":
+        y_a = yagb_props["fruity_mf0.7"]["y_a"]
+    else:
+        print(f"warning, {key} not found")
+        y_a = yagb_props["fruity"]["y_a"]
+
+    f0 = y_a / 2.79e-3
+    print("f = ", f0, " key, ", key)
+    plt.scatter(f0, 0, c="black", edgecolors="black", lw=1, marker="x")
+    plt.scatter(f0, 0, c=color, edgecolors="black", lw=0.5, marker="x")
+
+    if Nr - 1 > i > 0:
+        ax.spines[['bottom', 'top']].set_visible(False)
+        ax.xaxis.set_visible(False)
+    elif i == 0:
+        ax.spines[['bottom']].set_visible(False)
+        ax.tick_params(axis='x',  bottom=False, which="both")
+    elif i == Nr - 1:
+        ax.spines[['top']].set_visible(False)
+        ax.tick_params(axis='x',  top=False, which="both")
+
+
+    ax.set_yticks([])
+    ax.set_yticks([], minor=True)
+    plt.ylim(-1000)
+
+
+
+plt.sca(axs[-1])
+plt.xlabel(r"$f_{\rm AGB}$")
+plt.xlim(0, 0.6)
+
[…]

### 2025-03-19 carbon_paper/plots/subgiants.py

@@ -1,0 +1,38 @@
+import matplotlib.pyplot as plt
+import matplotlib as mpl
+import matplotlib.patheffects
+from surp import subgiants
+import seaborn as sns
+
+import arya
+
+
+fig, axs = plt.subplots(1, 2, figsize=(7, 10/3), sharey=True, gridspec_kw={"wspace": 0}, dpi=250)
+
+
+kwargs = dict(
+    rasterized=True, ec="none", s=1
+)
+
+plt.sca(axs[0])
+sns.scatterplot(subgiants, x="MG_H", y="C_MG", hue="high_alpha", **kwargs)
+L = arya.Legend(labels=[r"low $\alpha$", r"high $\alpha$"], color_only=True, loc=4)
+# for text in L.mpl_leg.get_texts():
+#     text.set_path_effects([mpl.patheffects.Stroke(linewidth=0, foreground='w'),
+#                        mpl.patheffects.Normal()])
+    
+plt.ylabel("[C/Mg]")
+plt.xlabel("[Mg/H]")
+plt.xlim(-0.5, 0.5)
+plt.ylim(-0.45, 0.15)
+
+plt.sca(axs[1])
+sns.scatterplot(subgiants, x="MG_FE", y="C_MG", hue="MG_H", hue_norm=(-0.5, 0.5), legend=False,  palette=plt.get_cmap(), **kwargs)
+plt.xlim(-0.08, 0.45)
+
+plt.xlabel("[Mg/Fe]")
+
+cax = axs[1].inset_axes([1.05, 0., 0.05, 1])
+
+arya.Colorbar(clim=(-0.5, 0.5), label="[Mg/H]", cax=cax)
+plt.savefig("figures/subgiants.pdf")

### 2025-03-19 carbon_paper/plots/summary.py

@@ -1,0 +1,414 @@
+#!/usr/bin/env python
+# coding: utf-8
+
+# Data from many different sources. This notebook makes the last plot of
+# the paper.
+
+# TODO: need to drop duplicates between RL & CEL regions, note that RL and CEL not consistent as labeled 
+# also would be nice to seperate RL by galaxy? and high z as well
+
+# # Introduction
+
+
+
+import pandas as pd
+import matplotlib as mpl
+import matplotlib.pyplot as plt
+import numpy as np
+import vice
+
+
+
+
+from surp import ViceModel, yields, subgiants, DATA_DIR
+from surp import gce_math as gcem
+
+import surp
+import arya
+from arya import COLORS
+
+
+
+
+from singlezone import run_singlezone, exp_sfh
+
+
+
+
+def to_nice(apogee_name):
+    return "[" + apogee_name.title().replace("_", "/") + "]"
+
+
+
+
+def plot_abund_errs(df, x="O_H", y="C_O", **kwargs):
+    xs = df[x].values
+    ys =  df[y].values
+    xerr = df[f"{x}_err"].values
+    yerr = df[f"{y}_err"].values
+    filt = ~np.isnan(xerr) 
+    filt &= ~np.isnan(yerr)
+    filt &= xerr > 0
+    filt &= yerr > 0
+    
+    plt.errorbar(xs[filt], ys[filt], xerr=xerr[filt], yerr=yerr[filt], fmt="o", capsize=0, **kwargs)
+    plt.xlabel(to_nice(x))
+    plt.ylabel(to_nice(y))
+
+
+
+
+def plot_sample(df, **kwargs):    
+    plot_abund_errs(df, x="FE_H", y="O_FE", **kwargs)
+    plt.show()
+    
+    plot_abund_errs(df, **kwargs)
+    plt.show()
+    
+    plot_abund_errs(df, x="O_FE", **kwargs)
+    plt.show()
+    
+    if "MG_FE" in df.columns:
+        plot_abund_errs(df, x="O_H", y="O_MG", **kwargs)
+        plot_abund_errs(df, x="MG_H", y="C_MG", **kwargs)
+        plot_abund_errs(df, x="MG_FE", y="C_MG", **kwargs)
+        plt.show()
[…]

### 2025-03-19 carbon_paper/plots/zeta_f_mass_sfh.py

@@ -1,0 +1,63 @@
+import matplotlib.pyplot as plt
+import surp
+import arya
+arya.style.set_size((10/3, 10/3))
+
+import sys
+sys.path.append("..")
+from mw_model_plots import find_model, compare, compare_coofe, compare_cooh
+
+names_fz = [   
+    "fruity/fz_0.1",
+    "fiducial/run",
+   # "fruity/alpha_z_higher",
+    "fruity/fz_0.5",
+  ]
+
+labels_fz = [r"lower f, $\zeta$", "fiducial", r"higher f, $\zeta$"]
+
+
+names_agbm = [   
+    "fruity/agb_mass_0.5",
+    "fruity/agb_mass_0.7",
+    "fiducial/run",
+    "fruity/agb_mass_1.5",
+    #"fruity/agb_mass_2",
+  ]
+
+labels_agbm = ["0.5", "0.7", "1", "1.5", "2"]
+
+
+names_sfh = [
+    "fiducial/run",
+    "fiducial/twoinfall_liam/",
+    "fiducial/lateburst",
+    "fiducial/eta2",
+]
+labels_sfh = [
+    r"fiducial",  
+    r"twoinfall",
+    "lateburst",
+    r"$y\rightarrow 2y$",
+]
+
+
+fig, axs = plt.subplots(1, 3, figsize=(7, 2.5), sharex="col", sharey=True, gridspec_kw={"wspace": 0, "hspace": 0})
+
+plt.sca(axs[0])
+compare_coofe(names_fz, labels_fz, sequential=True, legend=False)
+arya.Legend(loc=1, color_only=True, title=r"", labelspacing=0.1)
+
+plt.sca(axs[1])
+compare_coofe(names_agbm, labels_agbm, sequential=True, legend=False)
+arya.Legend(loc=1, color_only=True, title=r"mass shift", labelspacing=0.1)
+plt.ylabel("")
+
+plt.sca(axs[2])
+compare_coofe(names_sfh, labels_sfh)
+plt.ylabel("")
+
+plt.ylim(-0.25, -0.0)
+plt.tight_layout()
+
+plt.savefig("figures/zeta_f_mass_sfh.pdf")

### 2025-03-19 carbon_paper/tex/main.tex
updated figure

@@
 \dbnote{Remove connecting lines on MW HII regions. Should I plot outliers at all?}.
-\dbnote{unfortunantly the models in this figure are not consistent with this draft, accedentily deleted/didn't save some of the observed data and will fix in next draft.}
 Gas-phase C abundances. 
@@
     Milky Way stars \citep[yellow stars;][]{amarsi+19},
-    MW HII regions \citep[orange pentagons][]{mendez-delgado+22}
+    MW HII regions \citep[orange pentagons][]{mendez-delgado+22, esteban+05, esteban+13}
     extragalactic RL HII regions \citep[green open diamonds;][]{peimbert+05, skillman+20, toribio-san-cipriano+16, toribio-san-cipriano+17, esteban+14, esteban+09}

### 2025-03-19 carbon_paper/tex/survey_comparison.tex
updated figure

@@
 \begin{table}
+    \caption{Damped lynam alpha abundance}
     \centering
@@
     \hline
-HS 0105+1619 & 2.535998 & $0.23 \pm 0.07$ & $-1.75 \pm 0.03$ & omera+01 \\
-J1358+6522 & 3.067259 & $-0.27 \pm 0.06$ & $-2.34 \pm 0.06$ & cooke+14 \\
-J0955+4116 & 3.279908 & $-0.46 \pm 0.15$ & $-2.47 \pm 0.06$ & welsh+2022 \\
-J0140-0839 & 3.696000 & $-0.30 \pm 0.08$ & $-2.77 \pm 0.15$ & ellison+10 \\
-J0035-0918 & 2.340064 & $-0.12 \pm 0.14$ & $-2.47 \pm 0.06$ & welsh+20 \\
-Q1243+307 & 2.525640 & $0.24 \pm 0.03$ & $-2.79 \pm 0.03$ & cooke+18 \\
-PKS1937-101 & 3.572400 & $1.56 \pm 0.13$ & $-2.57 \pm 0.13$ & riemer-sorensen+17 \\
-Q1101-264 & 1.838000 & $0.77 \pm 0.09$ & $-1.66 \pm 0.07$ & dessauges-zavadsky+03 \\
-Q2059-360 & 2.507000 & $-0.41 \pm 0.28$ & $-1.38 \pm 0.23$ & dessauges-zavadsky+03 \\
-J2155+1358 & 4.212000 & $-0.29 \pm 0.08$ & $-1.82 \pm 0.11$ & dessauges-zavadsky+03 \\
-J0903+2628 & 3.077590 & $-0.38 \pm 0.04$ & $-3.07 \pm 0.05$ & cooke+17 \\
-J0311-1722 & 3.734000 & $-0.42 \pm 0.11$ & $-2.31 \pm 0.10$ & cooke+11 \\
-J1001+0343 & 3.078000 & $-0.41 \pm 0.03$ & $-2.67 \pm 0.05$ & cooke+11 \\
-J0953-0504 & 4.202870 & $-0.50 \pm 0.03$ & $-2.57 \pm 0.10$ & dutta+14 \\
-Q1202+3235 & 4.977000 & $0.20 \pm 0.09$ & $-2.00 \pm 0.12$ & morrison+16 \\
-J1337+3152 & 3.167000 & $-0.19 \pm 0.11$ & $-2.69 \pm 0.17$ & srianand+10 \\
-Q0913+072 & 2.618000 & $-0.39 \pm 0.05$ & $-2.42 \pm 0.04$ & pettini+08 \\
-J1016+4040 & 2.816000 & $-0.21 \pm 0.05$ & $-2.48 \pm 0.11$ & pettini+08 \\
-J1558+4053 & 2.553000 & $-0.06 \pm 0.07$ & $-2.47 \pm 0.06$ & pettini+08 \\
-Q2206-199 & 2.076000 & $-0.38 \pm 0.04$ & $-2.09 \pm 0.05$ & pettini+08 \\
-J1332+0052 & 3.421086 & $-0.03 \pm 0.02$ & $-1.72 \pm 0.02$ & kislitsyn+24 \\
-J1111+1332 & 2.270000 & $-0.18 \pm 0.11$ & $-1.94 \pm 0.08$ & cooke+15 \\
+    HS 0105+1619 & 2.535998 & $0.18 \pm 0.07$ & $-1.86 \pm 0.03$ & omera+01 \\
+    J1358+6522 & 3.067259 & $-0.32 \pm 0.06$ & $-2.44 \pm 0.06$ & cooke+14 \\
+    J0955+4116 & 3.279908 & $-0.51 \pm 0.15$ & $-2.57 \pm 0.06$ & welsh+2022 \\
+    J0140-0839 & 3.696000 & $-0.35 \pm 0.08$ & $-2.87 \pm 0.15$ & ellison+10 \\
+    J0035-0918 & 2.340064 & $-0.17 \pm 0.14$ & $-2.57 \pm 0.06$ & welsh+20 \\
+    Q1243+307 & 2.525640 & $0.19 \pm 0.03$ & $-2.89 \pm 0.03$ & cooke+18 \\
+    PKS1937-101 & 3.572400 & $1.51 \pm 0.13$ & $-2.68 \pm 0.13$ & riemer-sorensen+17 \\
+    Q1101-264 & 1.838000 & $0.72 \pm 0.09$ & $-1.76 \pm 0.07$ & dessauges-zavadsky+03 \\
+    Q2059-360 & 2.507000 & $-0.46 \pm 0.28$ & $-1.48 \pm 0.23$ & dessauges-zavadsky+03 \\
+    J2155+1358 & 4.212000 & $-0.34 \pm 0.08$ & $-1.92 \pm 0.11$ & dessauges-zavadsky+03 \\
+    J0903+2628 & 3.077590 & $-0.43 \pm 0.04$ & $-3.17 \pm 0.05$ & cooke+17 \\
+    J0311-1722 & 3.734000 & $-0.47 \pm 0.11$ & $-2.41 \pm 0.10$ & cooke+11 \\
+    J1001+0343 & 3.078000 & $-0.46 \pm 0.03$ & $-2.77 \pm 0.05$ & cooke+11 \\
+    J0953-0504 & 4.202870 & $-0.55 \pm 0.03$ & $-2.67 \pm 0.10$ & dutta+14 \\
+    Q1202+3235 & 4.977000 & $0.15 \pm 0.09$ & $-2.10 \pm 0.12$ & morrison+16 \\
+    J1337+3152 & 3.167000 & $-0.24 \pm 0.11$ & $-2.79 \pm 0.17$ & srianand+10 \\
+    Q0913+072 & 2.618000 & $-0.44 \pm 0.05$ & $-2.52 \pm 0.04$ & pettini+08 \\
+    J1016+4040 & 2.816000 & $-0.26 \pm 0.05$ & $-2.58 \pm 0.11$ & pettini+08 \\
+    J1558+4053 & 2.553000 & $-0.11 \pm 0.07$ & $-2.57 \pm 0.06$ & pettini+08 \\
+    Q2206-199 & 2.076000 & $-0.43 \pm 0.04$ & $-2.19 \pm 0.05$ & pettini+08 \\
+    J1332+0052 & 3.421086 & $-0.08 \pm 0.02$ & $-1.83 \pm 0.02$ & kislitsyn+24 \\
+    J1111+1332 & 2.270000 & $-0.23 \pm 0.11$ & $-2.04 \pm 0.08$ & cooke+15 \\
     \hline
@@
 \end{table}
-C abundances are measured in XXXX.
 
-Hello
-
+\begin{table}
+    \caption{CEL-derived C abundances from the literature.}
     \begin{longtable}{lllll}
@@
     SBS 0218+003 & NaN & $-0.96 \pm 0.25$ & $-0.82 \pm 0.06$ & pena-guerreno+17 \\
-Mrk 1087 & NaN & $0.40 \pm 0.33$ & $-0.40 \pm 0.14$ & pena-guerreno+17 \\
-NGC 1741 & NaN & $-0.21 \pm 0.30$ & $-0.56 \pm 0.10$ & pena-guerreno+17 \\
-Mrk 5 & NaN & $-0.80 \pm 0.29$ & $-0.83 \pm 0.10$ & pena-guerreno+17 \\
+    Mrk 1087 & NaN & $0.40 \pm 0.35$ & $-0.40 \pm 0.16$ & pena-guerreno+17 \\
+    NGC 1087 & NaN & $-0.21 \pm 0.30$ & $-0.56 \pm 0.10$ & pena-guerreno+17 \\
+    Mrk 5 & NaN & $-0.78 \pm 0.29$ & $-0.85 \pm 0.10$ & pena-guerreno+17 \\
     Mrk 1199 & NaN & $0.79 \pm 0.45$ & $-0.48 \pm 0.22$ & pena-guerreno+17 \\
@@
     SBS 0926+606A & NaN & $-0.48 \pm 0.24$ & $-0.83 \pm 0.09$ & pena-guerreno+17 \\
-Arp 252 & NaN & $0.06 \pm 0.34$ & $-0.68 \pm 0.15$ & pena-guerreno+17 \\
+    ARP 252 & NaN & $0.06 \pm 0.34$ & $-0.68 \pm 0.15$ & pena-guerreno+17 \\
     SBS 0948+532 & NaN & $-0.49 \pm 0.24$ & $-0.78 \pm 0.09$ & pena-guerreno+17 \\
@@
     SBS 1054+365 & NaN & $-0.42 \pm 0.20$ & $-0.70 \pm 0.09$ & pena-guerreno+17 \\
-POX 4 & NaN & $-0.49 \pm 0.14$ & $-0.75 \pm 0.05$ & pena-guerreno+17 \\
+    POX 4 & NaN & $-0.48 \pm 0.13$ & $-0.76 \pm 0.05$ & pena-guerreno+17 \\
     SBS 1319+579 & NaN & $-0.32 \pm 0.26$ & $-0.62 \pm 0.09$ & pena-guerreno+17 \\
-SBS 1415+437 & NaN & $-1.42 \pm 0.24$ & $-1.25 \pm 0.07$ & pena-guerreno+17 \\
+    SBS 1415+437 & NaN & $-1.43 \pm 0.30$ & $-1.25 \pm 0.09$ & pena-guerreno+17 \\
     Tol 1457-262 & NaN & $-1.22 \pm 0.46$ & $-0.98 \pm 0.16$ & pena-guerreno+17 \\
-III Zw 107 & NaN & $-0.51 \pm 0.28$ & $-0.59 \pm 0.10$ & pena-guerreno+17 \\
+    III Zw 107 & NaN & $-0.96 \pm 0.28$ & $-0.59 \pm 0.10$ & pena-guerreno+17 \\
     \hline
     \end{longtable}
+
+\end{table}
+
+\begin{table}
+    \caption{RL derived abundances for MW and nearby galaxies
+        note that mendez--delgado uses RL oxygen from esteban+05, +09
+    }
 
@@
     NGC 6822 & region V & $-0.15 \pm 0.21$ & $-0.44 \pm 0.09$ & peimbert+05 \\
-MW & Sh 2-311 & $-0.10 \pm 0.14$ & $-0.24 \pm 0.05$ & mendez-delgado+22 \\
-MW & NGC 2579 & $-0.14 \pm 0.09$ & $-0.26 \pm 0.03$ & mendez-delgado+22 \\
-MW & NGC 3576 & $-0.02 \pm 0.08$ & $-0.08 \pm 0.04$ & mendez-delgado+22 \\
-MW & NGC 3603 & $0.04 \pm 0.12$ & $-0.10 \pm 0.05$ & mendez-delgado+22 \\
-MW & M8 & $0.04 \pm 0.10$ & $-0.11 \pm 0.04$ & mendez-delgado+22 \\
-MW & M16 & $0.03 \pm 0.15$ & $-0.01 \pm 0.05$ & mendez-delgado+22 \\
-MW & M17 & $0.26 \pm 0.06$ & $-0.06 \pm 0.02$ & mendez-delgado+22 \\
-MW & M20 & $0.02 \pm 0.25$ & $-0.10 \pm 0.06$ & mendez-delgado+22 \\
-MW & M42 & $0.03 \pm 0.07$ & $-0.16 \pm 0.02$ & mendez-delgado+22 \\
+    MW & Sh 2-311 & $-0.10 \pm 0.13$ & $-0.24 \pm 0.04$ & mendez-delgado+22 \\
+    MW & NGC 2579 & $-0.15 \pm 0.09$ & $-0.25 \pm 0.03$ & mendez-delgado+22 \\
+    MW & NGC 3576 & $-0.03 \pm 0.10$ & $-0.07 \pm 0.06$ & mendez-delgado+22 \\
+    MW & NGC 3603 & $0.03 \pm 0.12$ & $-0.09 \pm 0.05$ & mendez-delgado+22 \\
+    MW & M8 & $0.03 \pm 0.10$ & $-0.10 \pm 0.04$ & mendez-delgado+22 \\
+    MW & M16 & $0.03 \pm 0.16$ & $-0.01 \pm 0.06$ & mendez-delgado+22 \\
+    MW & M17 & $0.25 \pm 0.08$ & $-0.05 \pm 0.04$ & mendez-delgado+22 \\
+    MW & M20 & $0.02 \pm 0.26$ & $-0.10 \pm 0.07$ & mendez-delgado+22 \\
+    MW & M42 & $0.03 \pm 0.08$ & $-0.16 \pm 0.03$ & mendez-delgado+22 \\
     M101 & H1013 & $0.17 \pm 0.07$ & $-0.24 \pm 0.02$ & skillman+20 \\
@@
     NGC 2403 & VS 44 & $-0.08 \pm 0.22$ & $-0.20 \pm 0.04$ & esteban+09 \\
+
     \hline
     \end{longtable}
+
+\end{table}
 

### 2025-11-14 carbon_paper/tex/main.tex
near-submission draft

@@
 \documentclass[fleqn,
-referee, % this line changes to double-spaced 1 column
+%onecolumn,
+%doublespacing, % this line changes to double-spaced 1 column
+%referee,
 usenatbib]{mnras}
@@
 
+% enable line numbers
+\usepackage{lineno}
+%\linenumbers
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \newcommand{\aton}{\texttt{\hyperlink{aton}{ATON}}}
-\newcommand{\cfactor}{2.4}
+\newcommand{\cfactor}{2.57}
 \newcommand{\zetaobest}{1.90 \pm 0.10}
 \newcommand{\zetaibest}{2.28 \pm 0.16}
-\newcommand{\zetaiibest}{2.59 \pm 0.30}
 
@@
 \newcommand{\caafe}{[C/Mg]-[Mg/Fe]}
+\newcommand{\oh}{{\rm [O/H]}}
+\newcommand{\mgh}{{\rm [Mg/H]}}
+\newcommand{\cmg}{{\rm [C/Mg]}}
+\newcommand{\co}{{\rm [C/O]}}
+\newcommand{\mgfe}{{\rm [Mg/Fe]}}
 
 \newcommand{\Var}{\operatorname{Var}}
+
+\newcommand{\Hii}{H~{\sc ii}}
 
@@
 
-\newcommand{\Yct}{{y_{\rm C}}}
+\newcommand{\Yct}{{y_{\rm C}^{\rm  tot}}}
 \newcommand{\Ycc}{{y_{\rm C}^{\rm CC}}}
-\newcommand{\Yoc}{{y_{\rm Mg}^{\rm CC}}}
+\newcommand{\Ymg}{{y_{\rm Mg}^{\rm CC}}}
 \newcommand{\Ycagb}{{y_{\rm C}^{\rm AGB}}}
 \newcommand{\ycagb}{\y_{\rm C}^{\rm AGB}}
-\newcommand{\aagb}{\alpha_{\rm C}^{\rm AGB}}
-\newcommand{\zagb}{\zeta_{\rm C}^{\rm AGB}}
+\newcommand{\y}{p}
+
+\newcommand{\aagb}{\beta_{\rm C}^{\rm AGB}}
+\newcommand{\fagb}{f_{\rm C}^{\rm AGB}}
+\newcommand{\yo}{y_0}
+\newcommand{\yl}{y_{\rm low}}
 \newcommand{\zcc}{\zeta_{\rm C}^{\rm CC}}
-\newcommand{\noneqagb}{\nu_{\rm C}^{\rm AGB}}
- \newcommand{\yb}{\ensuremath{\rotatebox[origin=B,y=0.5ex]{180}{y}}}
-\newcommand{\y}{p}
-\newcommand{\fagb}{f_{\rm C}^{\rm AGB}}
-
-\newcommand{\zetao}{\zeta_0}
-\newcommand{\zetai}{\zeta_{1}}
-\newcommand{\zetaii}{\zeta_{2}}
-\newcommand{\Zl}{x_{\rm low}}
 
 \newcommand{\Mo}{ {\rm M}_{\sun}}
-
 \newcommand{\Zo}{ Z_{\sun}}
@@
 %%%%%%%%%%% JWJ' editing macros %%%%%%%%%%%
-\newcommand{\strike}[1]{{\color{ForestGreen} \sout{#1}}}
-\newcommand{\add}[1]{{\color{ForestGreen} #1}}
-\newcommand{\note}[1]{{\color{ForestGreen} \textit{ \small (JWJ: #1)}}}
+\newcommand{\red}[1]{{\color{red} #1}}
+\newcommand{\strike}[1]{{\color{red} \sout{#1}}}
+% \newcommand{\add}[1]{{\color{ForestGreen} #1}}
+% \newcommand{\note}[1]{{\color{ForestGreen} \textit{ \small (JWJ: #1)}}}
 % \LetLtxMacro\origcitep\citep
@@
 
-% \LetLtxMacro\origcite\cite
-
-% This is my command. I want to strike out, 
-% \newcommand{\strikeit}[1]{%
-%   \ifcorrectingmode
-%   \mbox{\sout{#1}}%
-% %  \makebox[\textwidth][s]{\sout{#1}}%
-%   \fi
-% }
-
-% \renewcommand{\cite}[2][]{%
-%   \ifcorrectingmode
-%   \mbox{\origcite[#1]{#2}}%
-%   \else
-%   \origcite[#1]{#2}%
-%   \fi
-% }
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 % Keep the title short and informative.
-\title[The Origin and Galactic Evolution of Carbon]{The Galactic Chemical Evolution of Carbon: Implications for Stellar Nucleosynthesis }
+\title[The origin and galactic evolution of carbon]{The galactic chemical evolution of carbon: Implications for stellar nucleosynthesis}
 
@@
 Daniel A. Boyea,$^{1, 2, 3}$\thanks{%
-Contact e-mail:~\href{mailto:boyea.2@osu.edu}{boyea.2@osu.edu}}
+Contact e-mail:~\href{mailto:danielaboyea@gmail.com}{danielaboyea@gmail.com}}
 James W. Johnson,$^{1, 2, 4}$
-Third Author$^{2,3}$
-and Others$^{1,3}$
+and others
+%David H. Weinberg,$^{1,2}$
+%Jennifer A. Johnson,$^{1,2}$
+%Falk Herwig$^{3}$
 \\
@@
 \begin{abstract}
-% context
-The astrophysical origin of carbon remains largely uncertain---different studies propose that either asymptotic giant branch (AGB) stars or core collapse supernovae (CCSNe) may be the dominant process.
+Carbon (C) is thought to be produced by both core collapse supernovae (CCSN) and asymptotic giant branch (AGB) stars, but the relative contributions of these two sources are uncertain. 
+% goals
+We investigate the astrophysical origin of C using models of Galactic chemical evolution (GCE) appropriate for the Milky Way disk.
+We benchmark our results against APOGEE subgiant abundances.
+% results
+The trend between [C/Mg] and [Mg/H] is set by the total C yield as a function of metallicity.
+Observations indicate a gently rising [C/Mg] with [Mg/H], but AGB C production is predicted to decline with metallicity.
+Our sample therefore favours a scenario in which CCSN yields rise with metallicity to offset declining AGB C yields and drive a subtle increase in [C/Mg] with [Mg/H].
+This result is consistent with massive star nucleosynthesis models incorporating rotation.
 %
-We aim to constrain the stellar yields of C through multi-zone Galactic chemical evolution models by comparing predictions with \apogee\ subgiants abundances.
-% 
-We show \caah\ trend represents the equilibrium abundances of C and Mg, deriving the total C yield as a function of metallicity. 
-Instead, the \caafe\ trend (at a given metallicity) is an empirical estimate of the delay time distribution of C.
-We infer that AGB stars produce between 10 and 40\% of C. Additionally, we show that all AGB models produce C too quickly, and the low-mass AGB C yield is likely underestimated. 
-% misc
-Our models are relatively independent of uniform scaling of yields and outflows, and alternate star formation histories. 
-However, the stars which contribute to \agb\ C production and the \ia\ delay time distribution of Fe contribute uncertainties to our conclusions. 
-% gas phase
-While reliable gas-phase and low-metallicity measurements of C are challenging, we find that our model and a single-zone model with our recommended yields replicate the broad trends of \caah{} across different environments and metallicities.
-
+The [C/Mg]-[Mg/Fe] trend is sensitive to delayed enrichment and therefore constrains the amount of AGB C production.
+Given the slope of this relation, we find that AGB stars likely account for 10--40 per cent of C at solar metallicity.
+% nuance
+Artificially shifting the AGB C yields to lower masses also improves agreement with the [C/Mg]-[Mg/Fe] trend, possibly indicating a discrepancy with stellar evolution predictions or our assumed Fe production rate.
 \end{abstract}
@@
     \includegraphics{subgiants.pdf}
-    \caption{The [C/Mg] ratio against [Mg/H] (left) and [Mg/Fe] (right) for the \citet{jack}~sample of \apogee{} subgiants.
-On the left, we plot high and low-$\alpha$ stars in blue and orange, using the separation defined in Eq.~\ref{eq:high_alpha}.
-On the right, we colour-code stars according to their [Mg/H] abundance.
-The median subgiant trends serve as our emperical benchmark.
+    \caption{The [C/Mg] ratio versus [Mg/H] (left) and [Mg/Fe] (right) for the \citet{jack}~sample of \apogee{} subgiants.
+{\bf Left:} High- and low-$\alpha$ stars are shown in blue and orange, respectively, using the separation defined in Eq.~\ref{eq:high_alpha}.
+The black points represent the median trend along the low-$\alpha$ sequence.
+{\bf Right:} Stars are colour-coded by their [Mg/H] abundance.
+The black points show the median [C/Mg]-[Mg/Fe] sequence for stars in the $-0.15 \leq [{\rm Mg/H}] \leq -0.05$ range.
+We use these median trends as our empirical benchmark in subsequent figures.
 } \label{fig:subgiants}
@@
 
-Despite being the most abundant metal in the Universe~\citep[e.g.][]{magg+22}, the nucleosynthetic origin of C is poorly understood. 
-There is broad agreement that both high mass and asymptotic giant branch (AGB) stars produce C \citep{jennifer19}, but their relative yields are disputed.
-From a Galactic chemical evolution (GCE) perspective, some authors have argued that high-mass stars should dominate~\citep[e.g.][]{prantzos+94, HEK00, romano+20, franchini+20, gustafsson22}, and others have argued that AGB stars should contribute at least half of the C in the universe~\citep[e.g.][]{tinsley79, chiappini+03, mattsson10, KKU11, rybizki+17, KKL20}.
-In this paper, we aim to constrain C production using subgiant stars and multi-zone GCE models.% \dbstrike{incorporating stellar radial migration}.
-
-% Formed in the cores of stars during He fusion, C is the first \dbadd{primary?
-element} after He.
-Additionally, C is one of the only light elements formed in low-mass stars \citep[e.g.,][]{KL14}.
-\dbnote{I don't like how many e.g.'s there are, and is this the right citation here?}
-%\dbadd{
-% Because the effects of first dredge up are mass-dependent, C and N abundances are frequently used as age indicators for RGB stars \citep{MG15, martig16, hasselquist19, vincenzo+21}. 
-% }
-% \dbnote{C abundnces for stellar structure (opacities) and star formation (line cooling)}
-% \dbadd{In addition, stellar parameters such as convection and mass loss are calibrated to match observed stars and cannot be predicted from first principles.} \dbnote{need to check if this means SE models are calibrated to match yields or just stellar parameters.}
-
-Predictions of C yields from stellar evolution and supernova (SN) models are riddled with uncertainties (see, e.g., the reviews by \citealt{romano+10, KL14}).
-Some salient unknowns include mass loss rates \citep{sukhbold+16, beasor+2020}, rotational mixing \citep{frischknecht+16, LC18}, nuclear reaction rates \citep{herwig+05, herwig+austin2004}, and convection \citep{chieffi2001, ventura+13}.
-Recent work additionally suggests that small changes in a stars's initial mass of 
-$\sim$$0.01 \Mo$  have significant effects on the evolution and explosion outcomes of massive stars \citep{bruenn+2023, vartanyan_burrows2023}.
+Despite being the second most abundant metal in the Universe~\citep[e.g.,][]{magg+22}, the nucleosynthetic origin of C is poorly understood. 
+There is broad agreement that both massive and asymptotic giant branch (AGB) stars produce C \citep[e.g.,][]{jennifer19}, but their relative yields are disputed (see, e.g., the reviews by \citealt{romano22} and \citealt{RM21}).
+From a Galactic chemical evolution (GCE) perspective, some authors have argued that massive stars should dominate~\citep[e.g.,][]{prantzos+94, HEK00, romano+20, franchini+20, gustafsson22}, and others have argued that AGB stars should contribute a majority of C in the Universe~\citep[e.g.,][]{tinsley79, chiappini+03, mattsson10, KKU11, KKL20}.
+In addition, some studies like \citet{rybizki+17} find that AGB stars may produce about 20 to 50 per cent of solar C depending on the yield tables assumed.
+In this paper, we aim to constrain C production by comparing abundance measurements in subgiant stars with multi-zone GCE models.%
+
+Predictions of C yields from stellar evolution and supernova (SN) models are uncertain for numerous reasons (see, e.g., the reviews by \citealt{romano+10, KL14}).
+Some prominent unknowns include mass loss rates \citep{sukhbold+16, beasor+2020}, rotational mixing \citep{frischknecht+16, LC18}, nuclear reaction rates \citep{herwig+05, herwig+austin2004}, and convection \citep{chieffi2001, ventura+13, issa+25}.
+Recent work additionally suggests that small changes in a star's initial mass of 
+${\sim}0.01\,\Mo$  have significant effects on the evolution and explosion outcomes of massive stars \citep{bruenn+2023, vartanyan_burrows2023}.
+Most yield tables have far courser initial-mass resolution.
 Furthermore, many stars are found in binary systems \citep{sana+12}, the effects of which are almost entirely
-unexplored in stellar nucleosynthesis models \citet{farmer+21}.
-Accurate predictions of metal yields from stellar evolution models remain elusive.
-
-Given the challenge of theoretical yield predictions, recent work aims to empirically characterize elemental production.
-\dbnote{are there older relevant references like garnett1997?
-or other relevant work (eitner+20?)}
-\citet{weinberg+19, weinberg+22} analyzed the abundance ratio trends of high- and low-alpha sequence stars in APOGEE~\citep{apogee17} to infer relative yields of prompt and delayed enrichment sources and their metallicity dependence.
+unexplored in stellar nucleosynthesis models \citep{farmer+21}.
+Robust predictions of metal yields from stellar evolution models therefore remain elusive.
+
+Given the challenge of theoretical yield predictions, previous work has attempted to constrain chemical yields empirically. 
+Even early chemical evolution work, such as \citet{garnett1997}, began to test stellar theory with observed abundance trends.
+More recently, \citet{weinberg+19, weinberg+22} analysed the abundance ratio trends of high- and low-$\alpha$ sequence stars in APOGEE~\citep{apogee17} to infer relative yields of prompt and delayed enrichment sources and their metallicity dependence.
 \citet{emily+19, emily+22, emily+24} applied the same methodology to GALAH~\citep{DeSilva2015, Martell2017}.
-\citet{rodriguez+21, rodriguez+23} measured the mean Fe yield of core-collapse supernovae (CCSNe) using the radioactive tails of their lightcurves.
-Their measurements, provide one of few empirical anchors on the absolute scale of yields \citep{david_fe}.
-
- % Folowing many previous works  (e.g.
-\citealt{DTS78, BF06, prantzos+18, berg+19}; see also the recent reviews by \citealt{romano22} and \citealt{RM21}.) this paper focuses on the evolution of C in GCE models.
-\citet{james+24} recently argued that the enrichment history of the Galactic disk can be described as an equilibrium phenomenon.
-In equilibrium GCE, trends in abundance ratios closely trace yield ratios (see their section 5.2.2).
-\citet{james+23} had previously shown that the correlation between gas-phase N and O abundances (see their fig.
-1) could be described as a consequence of the metallicity dependence of the relative N and O yields.
-Under their equilibrium scenario, this argument should extend to any element whose enrichment by stellar populations does not require long timescales ($\gtrsim$few Gyr).
-We show in section~\ref{sec:agb} that the characteristic delay times of C production should be $\sim$ 1 Gyr, within this limit. 
-\dbnote{This is complicated by the difference between high alpha and low alpha, and 1-2Msun stars do produce carbon.... Also, I would like to call out reviews and general works on C at some point.}
+In addition, models such as \citet{eitner+2020} and \citet{dubay+24} have used abundance trends of Fe and related elements to understand the physics and origin of \ia.
+Most directly relevant to our analysis, \citet{james+24} applied Milky Way chemical evolution models to N and recommended a yield prescription that reproduces the observed relation between N and O abundances.
+We  extend their methodology to C in this paper.
+
+% \citet{rodriguez+21, rodriguez+23} measured the mean Fe yield of core-collapse supernovae (CCSN) using the radioactive tails of their lightcurves.
+% Their measurements, provide one of few empirical anchors on the absolute scale of yields \citep{david_fe}.
 
 We use a sample of subgiant stars from APOGEE \citep{apogee17} as our primary observational constraint.
-APOGEE Subgiants provide a large, homogeneous sample of well-measured C abundances unaffected by stellar evolution.
-\dbadd{Subgiants' photospheric C abundance closely matches their birth composition.}
-\dbstrike{Subgiants have the advantage that their photospheric abundances of C directly reflect their birth C abundances much more closely than other spectral types.} \citep{gilroy89, korn+07, lind+08, souto+18, souto19}.
-In other evolutionary phases, the measured abundances are known to be affected by internal processes (see discussion in section~\ref{sec:data_selection} below).
-Our sample should therefore be unaffected by uncertainties with inferring their birth abundances.
-
-In section~\ref{sec:data_selection} we describe the selection for our subgiant observational sample.
-In section~\ref{sec:nucleosynthesis}, we discusses theoretical estimates of \agb\ and \cc\ C yields and present the yield prescriptions we use for our models.
-In section~\ref{sec:vice}, we describe the remaining details of our GCE models.
-In section~\ref{sec:results}, we present our model predictions and discuss their observationally distinguishable predictions. 
-In section~\ref{sec:gas}, we compare our model to observations of halo stars and extragalactic HII regions from the literature. 
-We summarize our conclusins in section~\ref{sec:conclusions}.
+%This provide a large, homogeneous sample of well-measured C abundances unaffected by stellar evolution.
+Subgiants' photospheric C abundance closely matches their birth composition \citep{gilroy89, korn+07, lind+08, souto+18, souto19}.
+In other evolutionary phases, the measured abundances are known to be affected by internal processes (see discussion in Section~\ref{sec:data_selection} below).
+Our sample should therefore be unaffected by uncertainties in inferring birth abundances.
+
+In Section~\ref{sec:data_selection} we describe the selection for our subgiant observational sample.
+In Section~\ref{sec:nucleosynthesis}, we discuss theoretical estimates of \agb\ and \cc\ C yields.
+In Section~\ref{sec:vice}, we describe the details of our GCE models.
+In Section~\ref{sec:results}, we present our model predictions and discuss their observationally distinguishable predictions. 
+We then infer constraints on yield parameters in Section~\ref{sec:mcmc}.
+In Section~\ref{sec:gas}, we compare our model to observations of halo stars and extragalactic \Hii{} regions from the literature. 
+We summarize our conclusions in Section~\ref{sec:conclusions}.
 
@@
 Subgiants have the advantage that their photospheric C and N abundances should closely approximate their birth mixture.
-During main sequence evolution, metals can fall below the convective envelope (\textit{gravitational settling}; e.g. \citealt{turncotte+98}).
-When stars evolve off main sequence and become subgiants, these metals are reincorporated into the convective envelope \citep[]{gratton+00, souto19}. 
-However, once a star becomes a red giant, \textit{first dredge up} pollutes its photosphere with core, CNO-processed material
-\citep{iben67, KL14}. 
-\dbnote{Is there other justification for subgiants? Consistent stellar parameters, subgiant spectra are easier than white dwarfs? only a $\sim 0.05$ dex correction}
+During main sequence evolution, metals can fall below the convective envelope (\textit{gravitational settling}; e.g., \citealt{turncotte+98}).
+When stars evolve off the main sequence and become subgiants, these metals are reincorporated into the convective envelope \citep[]{gratton+00, souto19}. 
+However, once a star becomes a red giant, \textit{first dredge up} pollutes its photosphere with CNO-processed material from the core \citep{iben67, KL14}.
 
@@
         \verb|DUPLICATE|.
-We additionally remove stars with no reported (or flagged unreliable), C, N, Mg, or Fe abundances. These cuts yield a sample containing \nsubgiants\ subgiants.
-
-Fig.~\ref{fig:subgiants} shows out subgiant sample plotted in the \caah\ and \caafe{} planes.\footnotemark{} In this sample, [C/Mg] increases with [Mg/H], and [C/Mg] decreases with [Mg/Fe] at fixed [Mg/H].
-Our aim is to reproduce these trends.
-Low-$\alpha$ stars are defined to have 
+We additionally remove stars with no reported (or flagged unreliable) C, N, Mg, or Fe abundances. These cuts yield a sample containing \nsubgiants\ subgiants.
+
+Fig.~\ref{fig:subgiants} shows the [C/Mg] abundance ratios of our subgiant sample as a function of [Mg/H] and [Mg/Fe].\footnotemark{} In this sample, [C/Mg] increases with [Mg/H], and [C/Mg] decreases with [Mg/Fe] at fixed [Mg/H].
+Following \citet[eq.~1]{jack}, low-$\alpha$ stars are defined to have 
 \begin{equation}\label{eq:high_alpha}
@@
 \end{equation}
+Compared to the low-$\alpha$ sequence in \caah, the high-$\alpha$ sequence has a systematically lower [C/Mg] value and steeper slope. This is consistent with the shape of the \caafe{} trend.
+Note that the \caafe{} trend follows a two-component linear distribution, with a separation in [Mg/Fe] corresponding to the gap between high- and low-$\alpha$ stars.
+Additionally, the \caafe{} trend is approximately independent of metallicity.
+We aim to reproduce these trends in our GCE models.
 
@@
 $[A/B] = \log_{10}\left(A/B\right) - \log_{10}\left(A_{\sun}/B_{\sun}\right)$, i.e.
-$[A/B]$ is the logarithm of the mass ratio between A and B, scaled such that $[A/B]=0$ for the sun (see Table~\ref{tab:fiducial_mod} for solar scale.) }
-
-We have also investigated these thrends in other catlogues (not show) in order to understand the systematic uncertainties of our APOGEE subgiant sample.
-Namely, we we consider subgiants/dwarfs from GALAH DR4 \citep{galah_dr4}, Gaia-ESO DR5.1 \citep{gaiaeso_dr5.1}, and LAMOST \citep{lamost} with similar selection criteria.
-Additionally, we consider APOGEE Giants with first dredge up mixing corrections from \citep{vincenzo+21}.
-In general, different surveys follow similar trends in \caah\ and \caafe\ but with systematic offsets at the $\sim{0.1}$ dex level in [C/Mg] given [Mg/H] and slight variations in the slope.
-These systematic differences are not a major concern for our conclusions since our models are mostly constrained by the slope of \caah\ and \caafe,  not their normalization (see Fig.~\ref{fig:zeta_f} and discussion in section \dbadd{5.2}).
-
-\section{Nucleosynthesis}\label{sec:nucleosynthesis}
+$[A/B]$ is the logarithm of the mass ratio between A and B, scaled such that $[A/B]=0$ for the Sun (see Table~\ref{tab:fiducial_mod} for solar scale.)
+}
+
+While any abundance trend likely suffers from systematic biases, we find that these biases do not impact our qualitative conclusions. 
+We have also consider subgiants and dwarfs with similar selection criteria from GALAH DR4 \citep{galah_dr4}, Gaia-ESO DR5.1 \citep{gaiaeso_dr5.1}, LAMOST \citep{lamost}, and mixing-corrected APOGEE giants \citep{vincenzo+21}.
+All of these samples show similar trends in \caah\ and \caafe{}, but with global systematic offsets of ${\sim} 0.1\,{\rm dex}$ and slight differences in the slope of each trend.
+Global offsets would affect our inferred total C trend with metallicity.
+However, given that the \caafe{} trend is similar among different surveys, we would recover similar results for the inferred relative contribution of AGB stars to C production (Section~\ref{sec:mcmc_results}).
+Our results should therefore be robust against systematic differences between these surveys.
+
+\section{Carbon Nucleosynthesis}\label{sec:nucleosynthesis}
+Here, we review the processes that produce C in both high- and low-mass stars.
+We define yields as used in this paper and discuss the physics, predictions, and uncertainties from stellar model predictions.
+Our yield assumptions for other elements are presented in Section~\ref{sec:vice}.
 
 A yield quantifies the new production of a chemical species.
-For a given star, we define the {\it stellar yield of $X$} as the fraction of a star's initial mass synthesized into a new element, $X$.
-Specifically, the stellar yield of $X$ is
-\begin{equation} \label{eq:stellar_yield_def}
-   \y_{\rm X}(m, Z) := 
-    \frac{m_{X, \rm ej}- Z_{X,\rm  ini}\,m_{\rm ej}}{m}
-\end{equation}
-where $Z_{X,\rm ini}$ is the initial mass abundance of $X$, $m_{\rm ej}$ is the ejected mass, $m_{X, \rm ej}$ is the ejected mass of $X$, and $m$ is the initial mass of the star.
-Note that yields may become negative if more X is transformed into other elements than is produced.
-We also describe yields by their population-averaged quantities, {\it integrated yields}, the amount of newly produced X per unit mass of star formation. 
-The integrated yield of $X$ is
-\begin{equation} 
-   y_{X}(Z) := 
-    \frac{M_X - r\,Z_{X, \rm ini}\,M_{\rm ssp}}{M_{\rm ssp}},
-\end{equation}
-where $M_X$ is the total expelled mass of element X, $M_{\rm ssp}$ is the birth mass of the single stellar population (SSP)\footnote{An SSP is a cluster of stars born at the same time from the same material.}, and $r$ is the return fraction (fraction of the SSP mass returned to the interstellar medium).
-
-Table~\ref{tab:fiducial_mod} summarizes our yield choices. 
-Following \citet{james+23}, we integrate yields and our GCE models using the publicly available Versatile Integrator for Chemical Evolution (\VICE, \citealt{JW20}).
-Our solar abundance scale is from \citet{magg+22} with a 0.04 dex gravitational settling correction.
-Also from \citet{magg+22}, we adopt $\Zo = 0.0176$.
-We use the O, Mg, and Fe yields recommended by \citet{david_fe} based on measurements of the mean CCSN Fe yield \citep{rodriguez+23} and APOGEE chemical abundances.
-Our N yield is scaled from \citep{james+23}.
-We assume a \citet{kroupa01} initial mass function (IMF).
-
-\begin{table}
-	\centering
-    \caption[]{Solar abundance scale and fiducial yields (in units of stellar population birth mass).
-See section \ref{sec:agb} for the definition of \fruity.
-The solar abundance scale is \citet{magg+22} + 0.04 dex suggested by \citet{david_fe}.
-        \dbnote{Technically, I believe this abundance scale is off by the hydrogen 1 atomic weight. But this is < the systematic correction so I think this is negligable?}.
-    \dbnote{any tips to make this table a little bit smaller?}
-    }
-	\label{tab:fiducial_mod}
-
-	\begin{tabular}{l l l l l}
-		\hline
-         & $Z_{X,\,\sun}$ & $y_X^{\rm cc}$ & $\y_X^{\rm agb}$ & $y_X^{\rm ia}$  \\
-		\hline
-        C & $33.9\times10^{-4}$ & Eq.~\ref{eq:y_cc} & $\cfactor\times$\fruity &  0 \\
-        O & $73.3\times10^{-4}$ & $71.3\times10^{-4}$ & 0 & 0 \\
-        Mg & $6.71\times10^{-4}$ & $6.52\times 10^{-4}$ & 0 & 0 \\
-        Fe & $13.7\times10^{-4}$ & $4.73\times10^{-4}$ & 0 & $7.82\times10^{-4}$ \\
-        N & $10.4\times10^{-4}$ & $5\times10^{-4}$ & $5\times10^{-4}M\left(\frac{Z}{\Zo}\right)$ & 0\\
-		\hline
-	\end{tabular}
-\end{table}
-
-\subsection{Asymptotic Giant Branch Stars}\label{sec:agb}
+For a given star, we define the {\it stellar yield of $X$} as the fraction of a star's initial mass synthesized into an element $X$ and released.
+Specifically, we use {\it net} yields here, which subtracts the birth abundance of a chemical element from the ejected material.
+Net yields may become negative if more $X$ is transformed into other elements or locked inside the remnant than is produced.
+In contrast, a {\it gross} yield is the total mass of an element ejected over the star's lifetime and is always non-negative.
+ We also describe yields by their population-averaged quantities, or {\it integrated yields}, which refer to the amount of newly produced $X$ per unit mass of star formation.
+These yields are calculated from the stellar mass-weighted average of net stellar yields over the initial mass function (IMF).
+
+\subsection{Low and intermediate mass stars}\label{sec:agb}
 
@@
  	    \includegraphics[scale=1]{agb_yields.pdf}
-        \caption[]{The net fractional \agb\ C yield  plotted as a function of initial stellar mass and colour-coded according to metallicity.
-The black dashed line shows $\Ycagb=0$ for reference.
-Each panel represents yields from one of four \agb\ models: \fruity{}, \aton{}, \monash{}, \nugrid{} (see sections \ref{sec:agb}) }.
+        \caption[]{The net fractional C yield from AGB stars as a function of initial stellar mass and metallicity.
+Each panel represents yields from one of four \agb\ studies from the literature: \fruity{}, \aton{}, \monash{}, \nugrid{} (see Section \ref{sec:agb}).
+The black dotted line shows $\Ycagb=0$ for reference.
+        }
 
@@
     \centering
-    \includegraphics{y_agb_vs_z.pdf}
-    \includegraphics{y_agb_vs_t.pdf}
-
-    \caption[]{\textbf{Left} The integrated \agb\ C yield $\Ycagb$ as a function of metallicity for each of the \agb\ yield tables.
-        \textbf{Right} cumulative C return fraction as a function of age for a metallicity of ${\rm [M/H]}=-0.1$ single stellar population.
+    \includegraphics{y_agb_vs_z_shifted.pdf}
+    \includegraphics{y_agb_vs_t_shifted.pdf}
+
+    \caption[]{
+        \textbf{Left:} The integrated C yield from AGB stars, $\Ycagb$, as a function of metallicity for each yield table,  calculated $10\,{\rm Gyr}$ after a stellar population forms.
+(Note that the shape of the integrated yields arises from our linear interpolation of yields in $Z$.
+Changing to interpolation linear in $\log Z$ does not substantially affect our results.)
+        \textbf{Right:} Cumulative C production as a function of age for a single stellar population of metallicity $\log Z/\Zo=-0.1$.
 The dashed black line shows the cumulative return fraction of type Ia supernovae ($\propto t^{-1.1}$) for comparison.
-The minimum of \aton{} is at $y( 0.30\,{\rm Gyr})/y(t_{\rm end})=-3$ and is large as the net yield is close to zero.
+The cumulative production of \aton{} reaches a minimum of -3 at a time of 0.3 Gyr.
 }
@@
 
-An asymptotic giant branch (AGB) star is a low mass star undergoing He shell burning, the last nuclear phase (see e.g.
-\citealt{PR2023}).
-AGB stars enrich the interstellar medium (ISM) through mass expelled during thermal pulses.
-
-We explore four different stellar AGB yield tables from the literature which provide well-sampled grids in mass and metallicity. We refer to the tables as 
+An asymptotic giant branch (AGB) star is a low to intermediate mass star undergoing He shell burning, its last nuclear burning phase (see e.g., \citealt{PR2023}).
+AGB stars enrich the interstellar medium (ISM) by expelling processed material during thermal pulses.
+
+We explore four different AGB star yield tables from the literature, which provide well-sampled grids in mass and metallicity. We refer to the tables as 
 \begin{description}
@@
 We use the same tables as \citet{james+23}, except that we have swapped \citet{karakas10} for \citet{pignatari+16}.
-(See section~\ref{sec:nugrid_yields} for the implementation and recalculation of these yields.)
+(See Appendix~\ref{sec:nugrid_yields} for the implementation and recalculation of these yields.)
 For our models to better match observations, we uniformly amplify the yield tables according to
 \begin{equation} \label{eq:alpha}
-        \ycagb(m, Z) \rightarrow \alpha_{\rm agb}\ \ycagb(m, Z).
-\end{equation}
-We use the \fruity\ table, with $\alpha_{\rm agb}=\cfactor$, as the fiducial \agb\ yield.
-
-Fig.~\ref{fig:y_agb} compares the C yields for these four AGB models.
+        \ycagb(m, Z) \rightarrow \aagb\ \ycagb(m, Z).
+\end{equation}
+As our fiducial \agb\ yield, we use the \fruity\ table with $\aagb=\cfactor$, (balancing MW and gas-phase constraints; see Section~\ref{sec:results} and Section~\ref{sec:gas}).
+
+Fig.~\ref{fig:y_agb} compares the C yields for these four AGB models, which we leave unmodified (i.e., $\aagb = 1$) for this comparison.
 Most models agree on general yield trends in mass and metallicity.
-C production peak between masses of $\sim$ 2--4 $\Mo$. As metallicity increases, the net yield decreases and the mass of peak C production increases slightly.
-
-In order to integrate AGB yields with \VICE, we linearly interpolate yield tables in both mass and metallicity.
-Below the smallest mass in a table, $\ycagb$ is linearly extrapolated to 0 at $1\Mo$.
+C production peaks between masses of $\sim$ 2--4 $\Mo$.
+As metallicity increases, the net yield decreases and the mass of peak C production increases slightly.
+As a result, these models predict AGB C production to decrease and become more rapid with increasing metallicity.
+
+To integrate AGB yields with \VICE, we linearly interpolate yield tables in both mass and metallicity.
+Below the smallest mass in a table, $\ycagb$ is linearly extrapolated to 0 at $1\,\Mo$ to avoid numerical artifacts.
 The population-averaged AGB star yield is calculated with
@@
     \y_{\rm X}(m, Z)\ 
-    \frac{1}{A}\frac{dN}{dm}\ m\ dm
-\end{equation}
-are the minimum and maximum mass of star formation, $u_{\rm AGB}=8\Mo$ is the maximum mass of an AGB star, $m_\textrm{post-AGB}(\tau)$ is the mass of stars which complete AGB evolution at age $\tau$, and $dN/dm$ is the initial mass function (IMF).
-The IMF normalization is
-\begin{equation} \label{eq:imf_normalization}
+    \frac{1}{A}\frac{dN}{dm}\ m\ dm ,
+\end{equation}
+where $u_{\rm AGB}=8\,\Mo$ is the maximum birth mass of an AGB star, $m_\textrm{post-AGB}(\tau)$ is the birth mass of stars which complete AGB evolution at age $\tau$, and $dN/dm$ is the initial mass function (IMF).
+The IMF normalization is $
     A := \int_l^u m \frac{dN}{dm} dm
-\end{equation}
-    where  $l=0.08\,\Mo$ and $u = 100\,\Mo$ are the assummed minimum and maximum mass of star formation.
-We assume a \citet{larson74} mass-lifetime-relationship and assume that the total lifetime (through post-AGB) is $1.1\times$ the main sequence lifetime.
-
-The left panel of Fig.~\ref{fig:agb-ssp} shows IMF-averaged C yields for each \agb\ model as a function of metallicity.
-The IMF-averaged yields differ in normalization and metallicity dependence.  
-The normalizations span a factor of \about{2}. (e.g. between $6\times 10^{-4}$ and $12 \times 10^{-4}$ at $Z=0.33\,\Zo$)
-Both \nugrid{} and \aton{} predict non-monotonic C yields with $Z$, but AGB modeling uncertanties may eclipse this prediction's significance.
-To characterize the metallicity dependence of each table, we fit the yield to a linear model in $\log Z$
-\begin{equation}\label{eq:agb_z_approx}
-    y_{\rm C}^{\rm AGB}(Z) = \zetao^{\rm AGB} + \zetai^{\rm AGB} \log(Z / \Zo).
-\end{equation}
-Table \ref{tab:agb} also contains the linear fit parameters for each AGB table.
-The values of $\zagb$ span a factor of $\sim{3}$ between models.
-These variations are due to different choices of reaction rates, convection treatments, and mass-loss rates (see discussion below and \JJ).
-
-The right panel of Fig.~\ref{fig:agb-ssp} shows the total relative production of C by \agb\ stars by a solar metallicity SSP as a function of age.
+$
+where  $l=0.08\,\Mo$ and $u = 100\,\Mo$ are the assumed minimum and maximum mass of star formation.
+We assume a \citet{larson74} main sequence mass-lifetime-relationship.
+We take the total stellar lifetime (through post-AGB) to be $1.1\times$ the main sequence lifetime.
+Thus, the mass $m_\textrm{post-AGB}$ is slightly larger than the main-sequence turn-off mass.
+
+The IMF-averaged yields computed from the literature tables differ in normalization and metallicity dependence.  
+The left panel of Fig.~\ref{fig:agb-ssp} shows IMF-averaged C yields for each \agb\ model as a function of metallicity, computed at time $\tau = 10$ Gyr after the formation of a single stellar population.
+The normalizations span a factor of \about{2} (e.g., between $6\times 10^{-4}$ and $12 \times 10^{-4}$ at $Z=0.33\,\Zo$).
+Additionally, the slope varies by a factor of ${\sim}3$.
+Both \nugrid{} and \aton{} predict non-monotonic C yields with $Z$, but modelling systematics may exceed the scale of non-monotonic features.
+These variations are due to different choices of reaction rates, convection treatments, and mass-loss rates (see discussion below and \citealt{james+23}).
+
+The right panel of Fig.~\ref{fig:agb-ssp} shows the time-dependence of C production by \agb\ stars in a single stellar population of metallicity ${\rm [M/H]} = -0.1$ as a function of age. 
 As the mass range $2\,\Mo\lesssim M \lesssim 4\,\Mo$ is predicted to be most important for C production, half the yield is produced before \about{1}\,Gyr, similar to Fe production by \ia. 
-\monash{} weights C production more heavily towards high-mass \agb\ stars, resulting in shorter delay times, whereas the \fruity\ model predict a slightly longer timescale of \about{1}\,Gyr.
+\monash{} weights C production more heavily towards high-mass \agb\ stars, resulting in shorter delay times, whereas the \fruity\ model predicts a slightly longer time-scale of \about{1}\,Gyr.
 In any case, little to no C is produced more than 2\,Gyr after a star formation event.
@@
 later released to the ISM \citep{KL14}.  
-HBB\ is the activation of the CNO cycle at the bottom of the convective envelope.
-TDU increases C yields and HBB converts C into N. 
+HBB\ is the activation of the CNO cycle at the bottom of the convective envelope, which converts most C into N.
+TDU increases C yields, while HBB decreases C. 
 %Because the $^{14}$N proton capture is the slowest component of the CNO cycle, the CNO cycle converts nearly all \C[12] into $^{14}$N \citep{solar-fusion}.
@@
 
-Both HBB and TDU result in mass and metallicity dependent C yields. 
-Stars less than \about{2}\,$\Mo$ do not experience TDU. As a result, C yields from these stars are affected only by first dredge-up, resulting in small net C yields \citep[Table 1]{karakas10}.
-Above \about{2}\,$\Mo$, TDU becomes important, enriching the outer layers with C.
-In \agb\ stars more massive than \about{5}\,$\Mo$, efficient HBB turns most \C[12] into $^{14}$N.
+Both HBB and TDU result in mass and metallicity-dependent C yields. 
+Lower mass stars ($\lesssim 1\,\Mo$)  do not experience (strong) TDU.
+As a result, C yields from these stars are affected only by first dredge-up, resulting in small net C yields \citep[table 1]{karakas10}.
+Above ${\sim}1\,\Mo$, TDU becomes more important, enriching the outer layers with C.
+In \agb\ stars more massive than ${\sim}5\,\Mo$, efficient HBB turns most of the \C[12] into $^{14}$N.
 TDU is more efficient for compact, massive cores.
-HBB requires a more massive AGB star to reach sufficient temperatures at the base of the convective envelope to initiate CNO.
+HBB requires a more massive AGB star to reach sufficient temperatures at the base of the convective envelope to initiate the CNO cycle.
 Both processes are more efficient at low metallicity due to the lower opacities, hotter temperatures, and more compact internal structures.
-The details of each process are ultimately set by the uncertain choices for stellar evolution models.
+The details of each process are ultimately set by uncertain choices in stellar evolution models.
 
 % compactness causes stronger thin-shell instability
-% C yields increase because TDU outweights HBB when low Z.
+% C yields increase because TDU outweighs HBB when low Z.
 
@@
 \citet{ventura+15} compared the \aton{} and \monash{} models, finding that differences in yields are primarily driven by differences in mass-loss and convection prescriptions.
-\aton{} predicts strong HBB to set in $\sim{1}\,\Mo$ lower than in \monash{}, leading to much lower C yields.
-Moreover, the $^{14}{\rm N}({\rm p},\gamma)$ reaction rate uncertainty causes a factor of 2 difference in predicted C yields \citep{herwig+austin2004, HAL2006}.
-Most of the physics included in stellar modelling is empirically calibrated. Mass-loss rates, convection, and extra mixing are not sufficiently well understood to be computed from first principles.
-
-Super AGB stars are the class of AGB stars with masses $\sim8$ to $\sim10\Mo$ which burn O into Si and Mg.
-While we neglect super-AGB stars in the discussion above, these stars are not predicted to be substantial producers of C, similar to high mass AGB stars.
-From the \citet{doherty+14, doherty+14b} yield table (extending the \monash\ yields), the highest net fractional yield is only -0.002 for super solar metallicity, which would have a negligible impact on the integrated yield).
-Additionally, as discussed in section~\ref{sec:degeneracies} below, the short lifetimes of high mass AGB and super-AGB stars mean they have minimally affect our conclusions and can be grouped with CCSNe yields.
+\aton{} predicts strong HBB to set in ${\sim}1\,\Mo$ lower than in \monash{}, leading to much lower C yields.
+Moreover, the $^{14}{\rm N}({\rm p},\gamma)^{15}{\rm O}$ reaction rate uncertainty causes a factor of 2 difference in predicted C yields \citep{herwig+austin2004, HAL2006}.
+Mass-loss rates, convection, and extra mixing are not sufficiently well understood to be computed from first principles.
+Thus, most of the physics included in stellar modelling is empirically calibrated.
+
+Super AGB stars are the class of AGB stars with masses ${\sim}8$ to ${\sim}10\,\Mo$, which burn O into Si and Mg.
+While we neglect super-AGB stars in the discussion above, these stars are not predicted to be substantial producers of C, similar to high-mass AGB stars.
+From the \citet{doherty+14, doherty+14b} yield table (extending the \monash\ yields), the highest net fractional yield is only $-0.002$ for super solar metallicity, which would have a negligible impact on the integrated yield.
+Additionally, as discussed in Section~\ref{sec:agb_results} below, the short lifetimes of high-mass AGB and super-AGB stars imply that they minimally affect our conclusions and can be grouped with CCSN yields.
+
+%\dbnote{also NUGRID... https://ui.adsabs.harvard.edu/abs/2012ApJ...757..132H/abstract, https://ui.adsabs.harvard.edu/abs/2016MNRAS.455.3848J/abstract}
+
+For our comparisons later, we define the AGB yield fraction, 
+\begin{equation}\label{eq:f_agb}
+    \fagb := \frac{\Ycagb(\Zo)}{\Ycc(\Zo) + \Ycagb(\Zo)}.
+    \end{equation}
+This quantity should approximately represent the fraction of the Sun's birth C abundance originating from AGB stars.
+Although, since the Sun was not enriched entirely by solar metallicity predecessors, the equivalence of $\fagb{}$ to the yield ratio is not exact.
 
@@
 	\centering
-    \caption[]{For each \agb\ yield set, the IMF-averaged \agb\ C yield at solar metallicity $y_{\rm C, 0}^{\rm AGB}$, the linear fit solar yield $\zetao$ and slope $\zetai$ (see Eq.~\ref{eq:agb_z_approx}), the fraction of solar C produced in the model $f_\odot^{\rm AGB}$, and the masses and metallicities each yield table is sampled on.
-    $f_{\sun}^{\rm AGB}$ is calculated based on $\zetao$ assuming a total C yield of $\Yct = 0.00275$.
+    \caption[]{For each \agb\ yield set, the IMF-averaged \agb\ C yield at solar metallicity $y_{\rm C, 0}^{\rm AGB}$, the fraction of solar C produced in the model $f_\odot^{\rm AGB}$, and the masses and metallicities each yield table is sampled on.
+    $f_{\sun}^{\rm AGB}$ is calculated based on $y_{\rm C, \sun}^{\rm AGB}$ assuming the fiducial total C yield of $\Yct = 26.7\times 10^{-4}$.
     }
@@
 	\label{tab:agb}
-    \begin{tabular}{c  ccc  c p{4cm} p{4cm}} % four columns, alignment for each
+    \begin{tabular}{c  c  c p{4cm} p{4cm}} % four columns, alignment for each
 		\hline 
@@
                 & $y_{\rm C, \sun}^{\rm AGB}\times10^4$ %& y
-                & $\zetao^{\rm AGB}\times 10^4$ %& y
-                & $\zetai^{\rm AGB}\times 10^4$
                 &  $f_{\sun}^{\rm AGB}$
@@
                 & 3.11
-                &  $3.7\pm0.3$
-                & $-3.5\pm0.3$
-                & 0.13
+                & 0.12
                 & 1.3, 1.5, 2, 2.5, 3, 4, 5, 6
@@
                 & -0.009
-                & $1.0\pm1.8$
-                & $-10. \pm 3$
-                & 0.04
+                & -0.0003
                 & 1.5, 2, 2.5, 3, 3.5, 4, 4.5, 5, 6, 6.5, 7
@@
                 &  2.96
-                & $2.3 \pm 0.5$
-                & $-11.0\pm 1.0$
-                & 0.08
-                & 1, 1.25, 1.5, 1.75, 2.25, 2.5, 2.75, 3, 3.25, 3.5, 3.75, 4, 4.5, 5, 5.5, 6, 7 
+                & 0.11& 1, 1.25, 1.5, 1.75, 2.25, 2.5, 2.75, 3, 3.25, 3.5, 3.75, 4, 4.5, 5, 5.5, 6, 7 
                 & 0.0028, 0.007, 0.014, 0.03
@@
                 & 9.25
-                & $8.1\pm 1.9$
-                & $-4.6\pm1.7$
-                & 0.29
+                &  0.35
                 & 1, 1.65, 2, 3, 4, 5, 6, 7
@@
 
-\subsection{Core Collapse Supernovae}
-
-Massive stars form $^{12}$C in their cores through the triple-$\alpha$ reaction (He-burning) which is later released to the ISM through winds and supernovae.
+\subsection{Massive stars}
+
+Massive stars form $^{12}$C in their cores through the triple-$\alpha$ reaction (He-burning), which is later released to the ISM through winds and supernovae.
+Both material ejected through stellar winds and through CCSN contribute to C production, although we refer to CCSN and massive star enrichment interchangeably.
 
 We approximate massive star enrichment as occurring instantaneously after a star formation event.
-Under this approximation, the yield is simply a constant  of proportionality between the metal production rate and the SFR:
+Under this approximation, the yield is a constant  of proportionality between the metal production rate and the SFR:
 \begin{equation}
-    \dot{M}_X^{\rm CC} = y_{X}^{\rm CC}\, \dot{M}_\star
+    \dot{M}_X^{\rm CC} = y_{X}^{\rm CC}\, \dot{M}_\star.
 \end{equation}
@@
 \begin{equation}
-y_{X}^{\rm CC} = \int_{l_{\rm CC}}^{u} \left[E(m) m_{X\rm, SN} + w_X - Z_X\,(m-m_{\rm rem})\right]\,\frac{1}{A} \frac{dN}{dm}\ dm
-\end{equation}
-where $E(m)$ is the fraction of stars of mass $m$ which explode, $m_{X,\rm SN}$ and $w_X$ are the mass of $X$ ejected in a CCSN explosion and through stellar winds respectively, $Z_X$ is the initial abundance of $X$, $dN/dm$ is the IMF, $l_{\rm CC}=8\Mo$ is the initial minimum mass of a CCSN progenitor.
-%\dbstrike{We integrate yields using \VICE's {\tt vice.yields.ccsne.fractional} function.} \dbnote{is this too detailed?}
-
-Fig.~\ref{fig:y_cc} shows the integrated yields of several massive star yield models from the literature. 
-\cc{} models predict a wide range of C yields, spanning nearly a factor of ten. 
- The \cite{LC18} models, which include rotation, show that the induced mixing (e.g.
-\citealt{frischknecht+16}) can dramatically increase the magnitude and metallicity dependence of $\Ycc$.
-As we will later emperically show, \cc\ C production needs to be strongly metallicity-dependent at $Z \approx \Zo$, which is consistent with \citepos{LC18} rapidly rotating models and to a lesser extent \citet{NKT13}.
-The left panel of Fig.~\ref{fig:y_cc} also shows the IMF-averaged \agb\ star yields from the \fruity\ model (in Fig.~\ref{fig:agb-ssp}).
-Especially at $Z\approx \Zo$, most \cc\ models dominate \agb\ C production.
-
-The right panel of Fig.~\ref{fig:y_cc} shows the average [C/Mg] ratio of \cc\ ejecta for the different models, given by
+y_{X}^{\rm CC} = \int_{l_{\rm CC}}^{u} \left[E(m) m_{X\rm, SN} + w_X - Z_X\,(m-m_{\rm rem})\right]\,\frac{1}{A} \frac{dN}{dm}\ dm,
+\end{equation}
+where $E(m)$ is the fraction of stars of mass $m$ which explode, $m_{X,\rm SN}$ is the mass of $X$ ejected during the CCSN, $w_X$ is the mass of $X$ ejected through stellar winds, $Z_X$ is the initial abundance of $X$, $m_{\rm rem}$ is the remnant mass, $dN/dm$ is the IMF, $l_{\rm CC}=8\,\Mo$ is the minimum initial mass of a CCSN progenitor, and $u$ is the maximum mass in the CCSN yield table.
+
+\cc{} models predict a wide range of C yields, spanning nearly a factor of ten, even at fixed metallicity.
+Fig.~\ref{fig:y_cc} shows the integrated yields of massive star models from the literature. 
+ The \cite{LC18} models, which include rotation, show that the induced mixing (e.g., \citealt{frischknecht+16}) can dramatically increase the magnitude and metallicity dependence of $\Ycc$.
+As we will later empirically show, \cc\ C production needs to be strongly metallicity-dependent at $Z \approx \Zo$, which is consistent with \citepos{LC18} rapidly rotating models and to a lesser extent \citet{NKT13}.
+Fig.~\ref{fig:y_cc} also shows the IMF-averaged \agb\ star yields from the \fruity\ model (in Fig.~\ref{fig:agb-ssp}). Especially at $Z\approx \Zo$, most \cc\ models dominate \agb\ C production.
+
+If we consider CCSN production alone, the [C/Mg] ratio depends only on the yield ratio,
 \begin{equation}\label{eq:c_mg_cc}
-    {\rm [C/Mg]^{CC}} = \log_{10}\left( \frac{\Ycc}{\Yoc}\right) - \log_{10} \left( \frac{Z_{{\rm C},\ \sun }}{Z_{{\rm Mg},\ \sun }} \right).
-\end{equation}
-The models we have considered here predict [C/Mg]$^{\rm CC}$ ratios that closely trace the metallicity-dependence of the C yield, a consequence of approximately
-metallicity-independent Mg production \citep[e.g][]{andrews+17}.
-
-As opacity increases with metallicity, high-mass stars experience stronger winds.
-In particular, C enriched envelop material is lost through winds before conversion into heavier elements, resulting in $Z$-dependent C production \citep{LC18}.
+    {\rm [C/Mg]^{CC}} = \log_{10}\left( \frac{\Ycc}{\Ymg}\right) - \log_{10} \left( \frac{Z_{{\rm C},\ \sun }}{Z_{{\rm Mg},\ \sun }} \right).
+\end{equation}
+Because the yield ratio depends on metallicity, the abundance ratio will settle to an equilibrium that depends only on the equilibrium metallicity \citep{WAF17, james+23}.
+The right axis of Fig.~\ref{fig:y_cc} shows the  ${\rm [C/Mg]^{CC}}$ ratio for different CCSN C yields and our fiducial Mg yield.
+Different models have values of ${\rm [C/Mg]^{CC}}$ between $ -0.8$ and $+0.3$ at near-solar metallicity, illustrating the wide range of CCSN predictions.
+
+The metallicity dependence of CCSN C yields is due to an interplay between rotation, opacity, and stellar evolution.
+As opacity increases with metallicity, massive stars experience stronger winds.
+In particular, C-enriched envelope material is lost through winds before conversion into heavier elements, resulting in metallicity-dependent C production \citep{LC18}.
 While there are many stellar models providing predictions of \cc{} yields, the results of these models are highly uncertain.
@@
 
-The oxygen-magnesium problem is a know problem where Mg tends to be under-produced in CCSN models relative to 
- O (see discussion in \citealt{emily+21}).
-Because we update our solar mixture to \citet{magg+22}, the O and Mg abundances of the sun are closer to predictions of CCSN models compared to \citet{asplund+09} solar scale.
-To avoid this problem in our \gce\ models, we simply assume the O and Mg yields from massive stars reflect the solar mixture, consistent with observations from \apogee\ \citep{weinberg+19, weinberg+22, david_fe}.
-We are more focused on relative yields and trends than the scale of yields.
-Surveys also have \about{0.1} dex systematic offfsets for a variety of reasons in [C/Mg].
-
-To simplify the exploration of C yields from \cc\, we use the parameterization, 
+We chose to adopt a linear yield model instead of a particular literature yield table, given the wide range of predictions for CCSN C. We parameterize the yield as
 \begin{equation}\label{eq:y_cc}
-    \Ycc = \begin{cases}
-    \zetao + \zetai\,x + \zetaii x^2 & x \geq \Zl
-    \\
-    \zetao + \zetai\,\Zl + \zetaii \Zl^2 & x < \Zl
-    \end{cases}
-\end{equation}
-where $x=\log Z/\Zo$, $x_{\rm low}$ is the transition between low-metallicity constant yields and the quadratic yields near solar.
-In our fiducial model, we take $x_{\rm low} = -\zetai / 2\zetaii$ to be the vertex of the parabola, such that the yield is monotonic.
-
-\begin{figure*}
+    \Ycc =  \yo + \zcc \left(\frac{Z - \Zo}{\Zo}\right),
+\end{equation}
+where $\yo$ represents the yield at solar metallicity and $\zcc$ is the slope of the metallicity dependence.
+For our fiducial model, we adopt $\yo = 18.7\times 10^{-4}$ and $\zcc = 7.9 \times 10^{-4}$, leading to reasonable agreement with the \caah{}, \caafe{}, and gas-phase (Section~\ref{sec:gas}) relations.
+We present best-fitting models to subgiants only in Section~\ref{sec:mcmc_results}.
+We have also explored higher-order prescriptions (i.e., second-, third-, and fourth-order polynomials), finding improved agreement with the observed abundances with each successive free parameter.
+The linear prescription likely does not fully capture C production by massive stars, but more complex models do not significantly alter our conclusions.
+
+\begin{figure}
     \centering
@@
     \caption[]{
-    \dbnote{might be interesting to plot every CCSNe yield used in this paper in light grey to show strength of our constraint}
-    \dbnote{I may change the piecewise model to be linear in log-log space instead of log-linear space}
-        C yields from high-mass stars.
-        \textbf{Left} The IMF-weighted \cc\ yield of C as a function of metallicity.
-        \textbf{Right} The \cc\ [C/Mg] abundance ratio, defined in Eq.~\ref{eq:c_mg_cc}. The black line is the derived C yield from section~\ref{sec:mcmc_results}. Yields are shown for tables from 
-    \citet[red triangles]{WW95}, \citet[orange square and diamond]{sukhbold+16}, 
-    \citet[green stars]{NKT13}, and \citet[blue circles]{LC18}.
-\citet{sukhbold+16} report yields for different black hole landscapes, while \citet{LC18} provide yields at different rotational velocities.
-    In the left panel, the pink line denotes $\Ycagb$ from \fruity{} for comparison. All models include wind yields. 
+        IMF-integrated C yields from massive stars plotted as a function of metallicity.
+        The right axis provides the equivalent CCSN [C/Mg]  ratio, assuming our fiducial $y_{\rm Mg}$ yield. The black line is our fiducial massive star yield (see Eq.~\ref{eq:y_cc}).
+        Yields are shown for tables from \citet[LC18, blue circles]{LC18}, \nugrid{} (P16, orange hexagons),  \citet[S16, green square and diamond]{sukhbold+16},  \citet[NKT13, red stars]{NKT13}, and 
+    \citet[WW95, pink triangles]{WW95}. \citet{sukhbold+16} report yields for different black hole landscapes, while \citet{LC18} provide yields at different rotational velocities.
+   The pink line denotes $\Ycagb$ from the \fruity{} AGB star model for comparison (see Fig.~\ref{fig:agb-ssp}). All models include wind yields. 
 }
     \label{fig:y_cc}
-\end{figure*}
-
-\subsection{Supernova Type Ia}
-The population averaged SN Ia yield, $y_{X}^{\rm ia}$, is given by,
-\begin{equation}
-    y_{X}^{\rm Ia} = m_{X}^{\rm Ia} \frac{N_{\rm Ia}}{M_\star}
-\end{equation}
-where $m_{X}^{\rm Ia}$ is the average mass of $X$ produced in a single SN Ia event, and $N_{\rm Ia} / M_\star$ is the number of such events per unit mass of star formation.
-\dbstrike{The latter can be expressed as an integral over the SN Ia delay-time-distribution (DTD), which describes the rate at which stellar populations produce X through SN Ia in \VICE.} Following \citet{james+23}, we use a $t^{-1.1}$  delay time distribution (DTD) with a minimum delay-time of 150 Myr, based on comparisons of the SN Ia rate as a function of redshift and the cosmic SFR (e.g.
-\citealt{maoz+mannucci12}).
+\end{figure}
+
+\subsection{Other sources}
 
 SN Ia produce negligible C.
-Of the models from \citet{iwamoto+99}, \citet{seitenzahl+13}, and \citet{gronow+21a, gronow+21b}, the maximum C production is less than 4\% of our required solar C yield, and most likely less than 2\% (assuming a SNIa rate of $2.2\times 10^{-3} / \Mo$ \citealt{maoz+mannucci12}).
-
-Novae are important contributes of \C[13], but do not process enough material to impact \C[12] production. \C[13] is beyond the scope of this work.
+Of the models from \citet{iwamoto+99}, \citet{seitenzahl+13}, and \citet{gronow+21a, gronow+21b}, the maximum C production is less than 4 per cent of our required solar C yield, and most likely less than 2 per cent (assuming  $2.2\times 10^{-3}$ SN Ia explosions per solar mass of star formation; \citealt{maoz+mannucci12}).
+Novae are important contributors of \C[13], but do not process enough material to impact \C[12] production \citep{starrfield+20}.
+\C[13] is beyond the scope of this work and accounts for a small fraction of the C in the Universe.
 
@@
 
-Our models extends the \citet[hereafter \JJ]{james+21} Milky Way model, run with the publicly available Versatile Integrator for Chemical Evolution (\VICE).%
+Our models extend the \citet[hereafter \JJ]{james+21} Milky Way model. We integrate the model using the publicly available Versatile Integrator for Chemical Evolution (\VICE; \citealt{JW20}).%
     \footnote{\VICE~is available at \url{https://github.com/giganano/VICE}}
-This model is described extensively in \JJ~and concisely summarized  in \citet{james+23}. Here, we provide a brief overview of the relevant model components.
-
-Classical, \textit{one-zone} models of chemical evolution assume instantaneous mixing of metals in the star-forming ISM\ \citep[e.g.][]{matteucci21}.
-This simple framework is a poor approximation of the Milky Way.
-The Galaxy evolves \textit{inside-out} -- where star formation is higher towards the center and in the early universe \citep{WF91, kauffmann96, bird+13}.
-Stars can also migrate several kpc over their lifetimes, mixing different chemical environments across the galaxy \citep{bird+12,sellwood+binney02}.
-To account for different environments and stellar migration, multi-zone models stitch together multiple one-zone models and mix stellar populations between zones.
-\dbnote{does this belong in intro or here?.
-Thinking here now because feels more like methodology justification, but not sure still.}
-
-The Galaxy is divided into 200 rings, each representing a single, 100\,pc zone.
-Each ring (or zone) has a separate stellar population and gas supply.
-We initially assume an inside-out SFH from \JJ, where the star formation surface density $\dot{\Sigma}_\star$ is given by
+This model is described extensively in \JJ~and summarized in \citet{james+23}. Here, we provide an overview of the relevant components.
+
+Classical \textit{one-zone} models of chemical evolution assume instantaneous mixing of metals in the star-forming ISM\ \citep[e.g.,][]{matteucci21}.
+The one-zone framework is a poor approximation of the Milky Way, where the radial metallicity gradient in the ISM is believed to reflect variations in GCE parameters \citep[e.g.,][]{tinsley80, boissier+prantzos99, palla+20, james+24}.
+Stars can also migrate several kpc over their lifetimes, mixing populations from different chemical environments across the Galaxy \citep{sellwood+binney02, schonrich-binney09, bird+13, minchev+13}.
+To account for these effects, multi-zone models stitch together multiple one-zone models while mixing stellar populations between zones \citep[e.g.,][]{matteucci+francois1989}.
+
+In these models, the Galaxy is divided into 200 rings, each representing a single 100\,pc zone.
+Each ring has a separate stellar population and gas supply.
+We initially assume the inside-out SFH from \JJ, where the star formation surface density $\dot{\Sigma}_\star$ is given by
 \begin{equation}\label{eq:inside_out}
@@
 \end{equation}
-$\tau_\text{rise}=2$\,Gyr loosely describes when the star formation rate reaches a maximum, and $\tau_{\rm sfh}$ describes the decay timescale of star formation as a function of radius $R$.
-\JJ\ derive $\tau_{\rm sfh}(R)$ through analysis of four integral field spectroscopy surveys in \cite{sanches20}.
-At each $R$, the SFH is normalized to match the stellar surface density gradient \citep{BHG16} assuming a total stellar mass of $5.17\times10^{10}\,\Mo$ \citep{LM15}.
+The rise time $\tau_\text{rise}=2$\,Gyr loosely describes when the star formation rate reaches a maximum, and $\tau_{\rm sfh}$ describes the decay time-scale of star formation, which increases with radius $R$.
+\JJ\ derive $\tau_{\rm sfh}(R)$ to fit the stellar age gradients measured by \citet{sanches20} from integral field spectroscopic surveys.
+At each $R$, the SFH is normalized to match the stellar surface density profile \citep[from][]{BHG16} assuming a total stellar mass of $5.17\times10^{10}\,\Mo$ \citep{LM15}.
 Star formation ends beyond a radius $R=15.5\,$kpc, but stellar populations are allowed to migrate as far as $R=20\,$kpc.
-The gas inflow is calculated to maintain the SFH for each radius and time, using an extension of the Kennicutt-Schmidt law \citep{kennicutt98} motivated by the combined observations of \citet{bigiel+10} and \citet{leroy+13},
-\begin{equation}
-\dot{\Sigma}_{\star} \propto 
-\begin{cases}
-    {\Sigma}_{\rm gas} & 2\times 10^7 \Mo\,{\rm kpc}^{-2} \leq \Sigma_{\rm gas} \\ 
-    {(\Sigma}_{\rm gas})^{3.6} & 5\times 10^6 \Mo\,{\rm kpc}^{-2}\leq \Sigma_{\rm gas} < 2\times10^7 \Mo\,{\rm kpc}^{-2}\\ 
-    {(\Sigma}_{\rm gas})^{1.7} & \Sigma_{\rm gas} < 5\times10^6 \Mo\,{\rm kpc}^{-2}.
-\end{cases}
-\end{equation} 
+The gas inflow is calculated to maintain the SFH for each radius and time, using an extension of the Kennicutt-Schmidt law \citep{kennicutt98} motivated by the combined observations of \citet{bigiel+10} and \citet{leroy+13} (see \JJ).
 The scaling of this relationship varies with time due to the redshift dependence of $\tau_\star$ in molecular gas observed by \citet{tacconi18}.
 
-For radial migration of stars, inspired by \citet{frankel18}, we sample the change of radii of stars from a gaussian distribution with standard deviation $\sigma = 3.6\,{\rm kpc} ((t_{\rm end} - t_{\rm birth})/8\,{\rm Gyr})^{0.5}$, where $t_{\rm birth}$ is the birth time of the SSP and $t_{\rm end}=13.2$\,Gyr is the simulation end time.
-Stars migrate to their final position with a $\sqrt{t}$ dependence, consistent with diffusion of angular momentum \citep{frankel18, frankel20}.
-If a star's would move past $R=0$ or $R=20\,$kpc, the star reflects off these boundaries instead with the same velocity.%
-\footnote{Not shown here, we also explored variations of temporal, spatial resolution, migration strength, and the mass lifetime relation. We found these do not affect median trends significantly.}
-\dbnote{ Final set of models will use the radial migration prescription described in appendix C of {dubay+24} instead.
-I have checked that changes to derived parameters for the fiducial model is within the parameter uncertanties, so nothing substantial should change.
-}.
-We do not account for radial gas flows.
-Not shown here, we also explore migration based on random walks and the \texttt{h277} hydrodynamical
-simulation results\footnote{(with simulation parameters as in \citealt{bird+21}; see also \citealt{christensen12, zolotov12, loebman12, BZ14} \dbnote{is this okay as footnote?} }, which leaves our qualitative conclusions unchanged.
-The full impact of the details of a galaxy's dynamical history on its chemical evolution is still unknown.
-
-As the strength of outflows controls the resulting equilibrium $\alpha$-element abundances, we extend \JJ and create a metallicity gradient by defining
+We use the radial migration prescription described in appendix C of \citet{dubay+24} and summarized in Section 3 of \citet{james+24}.
+The total distance each star moves is sampled from a normal distribution with standard deviation $\sigma_R =  2.68\,{\rm kpc} \ (R/8\,{\rm kpc})^{0.61}\,(\tau / 8\,{\rm Gyr})^{0.33}$.
+Stars migrate from their initial to their final positions with a cube-root time-dependence.
+These parameters arise from \citepos{dubay+24} analytic approximation of the {\tt h227} simulation \citep{bird+21, christensen+12, zolotov12, loebman12, BZ14}.
+
+Following \JJ{} (and more recently \citealt{james+24}), we control the slope of the radial metallicity gradient by adjusting the strength of the mass-loading in Galactic winds.
+The mass-loading, $\eta :=  \dot\Sigma_{\rm out} / \dot \Sigma_\star$, the ratio between the surface density rates of gas leaving the system and star formation, is set to
 \begin{equation}\label{eq:mass_loading}
-\eta(R) = \frac{y_{\alpha}^{\rm cc}}{Z_{\alpha}(R)} -1 + r %+ \tau_{\star} / \tau_{\rm sfh} 
+\eta(R) = \frac{y_{\rm Mg}^{\rm CC}}{Z_{\rm Mg}(R)} -1 + r %+ \tau_{\star} / \tau_{\rm sfh} 
 \end{equation}
@@
 \begin{equation}
-    \log Z_{\alpha}(R) = \log Z_{\alpha,\ \sun} + 
+    \log Z_{\rm Mg}(R) = \log Z_{\rm Mg,\ \sun} + 
     0.29 + 
@@
 \end{equation}
-is adapted from \citet{hayden+14}.  We approximate $r=0.4$. %, and $\tau_\star/\tau_{\rm sfh} = 0.0$ .
-This choice of $\eta(R)$ results in a [$\alpha$/H] gradient consistent with Milky Way observations \citep[e.g.][]{hayden+14, weinberg+19, frinchaboy+13}.
-If we change our assumed $y_{\rm Mg}$, the values of $\eta$ will change similarly to maintain the correct chemical trends.
+is adapted from \citet{hayden+14} assuming Mg is representative of $\alpha$ elements.
+The recycling correction $r\approx 0.4$ accounts for the return of stellar envelopes back to the ISM (for a \citealt{kroupa01} IMF after 10 Gyr; see Section 2 from \citealt{WAF17}).
+This choice of $\eta(R)$ results in a [$\alpha$/H] gradient consistent with APOGEE measurements \citep[e.g.,][]{hayden+14, weinberg+19, frinchaboy+13}.
+Compared to \citet{james+21, james+24}, our metallicity gradient is flatter within 5 kpc (and our $\eta\to0$ at similar radius).
+If we change our assumed yield scale, the values of $\eta$ will re-scale accordingly to maintain observationally-consistent chemical trends. Following \JJ, we neglect radial gas flows.
 
@@
 we draw \nsubgiants\ stars from the simulated stellar populations.
-First, we draw a random zone (weighted by number of subgiants in zone) and then draw a random particle in the zone weighted by SSP mass.
-Galactocentric radii are taken from astroNN \citep{leung+bovy19, leung+bovy19b}, however Gaia parallaxes yield a similar distribution.
-Alternative distributions of stars (including uniform distributions in 7-9kpc) minimally affect median trends.
-
-\subsection{Monte-Carlo Markov Chain Yield Inference} \label{sec:mcmc_methods}
-
-In GCE, total elemental abundances are (to first order) linear with respect to combinations of yields \citep[e.g.][]{WAF17}.
-\dbnote{might be useful to include a complete set of differential equations for our model somewhere to better illustrate this.}
-Assume that the total metallicity evolution does not depend on the elemental yield we are considering.
-Say we are given a set of yield processes of $X$, $\{y_X^i\}_i$, and the resulting abundance evolution, $\{Z_{X}^i(R, t) \}_i$.
-Let $y_X'$, the total yield of $X$, be a linear combination of $\{y_X^i\}$, so
-\begin{equation}
-    y_X' = \sum_i \alpha_i\, y_X^i \quad {\rm where\ } \alpha_i \in \mathbb{R}.
-\end{equation}
-Then the abundance evolution of element $X$ is
-\begin{equation}\label{eq:lin_combo}
-    Z_X'(R, t) = \sum_i \alpha_i Z_X^i(R, t).
-\end{equation}
-Therefore, we can efficiently explore combinations of yields without the need for full simulations.
-This allows for direct observational inference of the yield combinations which best agree with the data.
-We use Monte Carole Markov Chain (MCMC) inference to generate the posterior distributions of yield coefficients.
-Note that many other GCE parameters are nonlinear with abundance and require full multi-zone simulations, such as star formation history, outflows, and migration prescriptions.
-Also note that metallicity-dependent yields introduce a second-order effect (metallicity depends on total yields which depend on metallicity), but for small changes to total yields, this effect should be small.
-
-Our first step is to run a multi-zone model tracking the abundances of each process we are interested in. 
-We focus on the binned \textit{mean} abundances of the low-$\alpha$ sequence in \caah, and the $-0.15 \leq {\rm [M/H]} \leq -0.05$ metallicity slice in \caafe\ (with 20 bin edges between -0.4 and 0.3 in [Mg/H] and 12 bin edges between 0.025 and 0.25 in [Mg/Fe]).
-We separate the C yield  into four different components.
-\begin{enumerate}
-    \item $\alpha$: Prefactor for an AGB yield table
-    \item $\zetao$: Constant CCSN yield  ($y_0 = \zeta_0$)
-    \item $\zetai$: Linear CCSN yield ($y_1 = \zeta_1 \log Z/\Zo$) \footnotemark{}
-    \item $\zetaii$: Quadratic CCSN yield ($y_2 = \zeta_2 (\log Z/\Zo)^2$)
-\end{enumerate}
-The total C abundances for a linear of these yields is given from Eq.~\ref{eq:lin_combo}.
-Since we are taking means of each bin, there is a statistical uncertainty associated with the mean in a given bin, $\sigma_{i, \rm model}$. The total variance of the combined yield model is 
-\begin{equation}
-    \sigma^2_{\rm model} = \sum_{i} \alpha_i^2 \sigma^2_{i, \rm model}
-\end{equation}
-Similarly, we represent the mean and variance of the observations in each bin $b$ with $\bar Z_{b, \rm obs}$ and $\sigma^2_{b, \rm obs}$.  We use the a likelihood
-\begin{equation} \label{eq:mcmc_likelihood}
-    \log {\cal L} \propto \chi^2 = \sum_b \frac{(\bar Z_{b,\rm\ model} - \bar Z_{b,\rm\ obs})^2} {\sigma_{b, \rm tot}^2}
-\end{equation}
-where the total variance in a bin is 
-\begin{equation}
-    \sigma_{b, \rm tot}^2 = \sigma_{\rm int}^2 + \sigma_{b, \rm obs}^2 + \sigma^2_{b, \rm model}.
-\end{equation}
-We model $\sigma_{\rm int}^2$ as a free parameter in the model.
-\footnotetext{$y_1$ and $y_2$ are held constant past $\log Z/\Zo < -1$ and the $y_1$ component is modelled with a positive constant offset later subtracted to avoid negative abundances.}
-
-We adopt the following loose priors
-\begin{subequations}
-\begin{align}
-    \alpha &\sim N(1, 1) \\
-    \zeta^{(0)} &\sim N(2, 1) \\
-    \zeta^{(1)} &\sim N(0, 1) \\
-    \zeta^{(2)} &\sim N(0, 4) \\
-    \ln \sigma _{\rm int}&\sim N(-3, 1)
-\end{align}
-\end{subequations}
-We run the MCMC using Turing.jl \citep{turingjl} with a No-U-turn sampler (adaptive Hamilton Monte-Carlo algorithm, \citealt{NUTS}) with an acceptance rate of 0.65.
-We combine 16 independent chains with 3,000 steps each for a total of 48,000 samples.
-
-To ensure this method is relatively robust, we will perform similar MCMC simulations varying the bin size and method, the MCMC sampler (Halmotonian, ensemble stretch moves from python-emcee, Metropolis-Hastings, Metropolis-Hastings random walk), the likelihood (including median U test, t-test, and KL-divergence based instead of mean + variance), and explore 2D bin likelihoods.
-In each case, the derived parameters are within their uncertainties (excluding the KS-divergence model).
-We check that removing the likelihood in \caafe{} causes $\alpha$ to become unconstrained, as $\alpha$ is degenerate with the CCSN yields in \caah.
-
-The median parameters derived from this model provide the yield choices for the fiducial and each AGB multizone model shown later.
+First, we draw a random zone (weighted by the number of observed subgiants in each zone) and then draw a random particle in the zone weighted by the stellar population mass.
+Galactocentric radii are taken from astroNN \citep{leung+bovy19, leung+bovy19b} to derive the number of subgiants in each zone.
+The choice of stellar selection function predominantly affects the metallicity distribution, but leaves abundance trends the same in this model.
+
+Table~\ref{tab:fiducial_mod} summarizes our yield choices. 
+Our solar abundance scale is from \citet{magg+22} with a 0.04 dex gravitational settling correction.
+Also from \citet{magg+22}, we adopt $\Zo = 0.0176$.
+We use the O, Mg, and Fe yields recommended by \citet{david_fe} based on measurements of the mean CCSN Fe yield \citep{rodriguez+21, rodriguez+23} and APOGEE chemical abundances.
+Our AGB N yield is scaled from \citep[eq.
+14]{james+23}, based on the differences in our assumed solar  N/O ratio.
+The CCSN N/O yield is additionally enhanced by a factor of 2.5 to account for the difference in median solar [N/Mg] values from \citet{vincenzo+21} and APOGEE subgiants.
+Following \citet{james+23}, we use a $t^{-1.1}$  delay time distribution (DTD) with a minimum delay-time of 150 Myr, based on comparisons of the SN Ia rate as a function of redshift and the cosmic SFR (e.g., \citealt{maoz+mannucci12}).
+We assume $2.2\times10^{-3}$ SN Ia events per unit mass of star formation with a mean $0.355\,\Mo$ of new Fe produced per supernova.
+We use a \citet{kroupa01} initial mass function (IMF).
+
+\begin{table}
+	\centering
+    \caption[]{Solar abundance scale and fiducial yields (in units of stellar population birth mass).
+See Section \ref{sec:agb} for the definition of \fruity.
+The solar abundance scale is \citet{magg+22} corrected upwards by 0.04 dex for gravitational settling and diffusion \citep{david_fe}.
+    }
+	\label{tab:fiducial_mod}
+
+	\begin{tabular}{l l l l l}
+		\hline
+         $X$ & $Z_{X,\,\sun}$ & $y_X^{\rm cc}$ & $\y_X^{\rm agb}$ & $y_X^{\rm ia}$  \\
+		\hline
+        C & $33.9\times10^{-4}$ & Eq.~\ref{eq:y_cc} & $\cfactor\times$\fruity &  0 \\
+        O & $73.3\times10^{-4}$ & $71.3\times10^{-4}$ & 0 & 0 \\
+        Mg & $6.71\times10^{-4}$ & $6.52\times 10^{-4}$ & 0 & 0 \\
+        Fe & $13.7\times10^{-4}$ & $4.73\times10^{-4}$ & 0 & $7.82\times10^{-4}$ \\
+        N & $10.4\times10^{-4}$ & $5\times10^{-4}$ & $5\times10^{-4}M\left(\frac{Z}{\Zo}\right)$ & 0\\
+		\hline
+	\end{tabular}
+\end{table}
+
 \section{Results}\label{sec:results}
 
-\subsection{Evolution of Carbon Abundances}
+\subsection{Evolution and interpretation of carbon abundances}
 
@@
     Time evolution of gas-phase C abundances in our fiducial model for [C/Mg] versus [Mg/H] (left) and [Mg/Fe] (right).
-    Each line represents a zone at a different galactic radius and is colour-coded by time. While \caah\ settles into the final trend $\sim{8}$\,Gyr ago, \caafe\ continues to evolve for much longer.
-    Only zones between 2 and 15.5 kpc are shown. The green lines represent the equilibrium tracks.
+    Each line represents a zone at a different Galactic radius, colour-coded by lookback time.
+We plot zones at 1 kpc intervals between 2 and 15 kpc.
+Evolution in [C/Mg] with [Mg/H] varies substantially between regions of the Galaxy, while evolution with [Mg/Fe] is more uniform.
 }
@@
 
-% \begin{figure*}
-%     \centering
-%     \includegraphics{figures/subgiants_equilibrium_reproduced.pdf}
-%     \caption{
-%     Similar to Fig.~\ref{fig:subgiants} except for the stars of our fiducial model. 
-%     The solid, black lines show the equilibrium abundance track.
-The black scatter points with errorbars are the median bins for the low-$\alpha$ sequence (left) and the \caafe\ trend (right).
-The green solid line on the right shows the singlezone evolution of \caafe\ with properties matching our solar-annulus.
-The median trend of low-$\alpha$ stars is an excellent approximation for the equilibrium abundance of C.
-%     \dbnote{The more I look at this figure, maybe we just add green lines to Fig. 5 and skip this one}
-%     \dbnote{we add synthetic scatter found by fitting the metallicity-dependent reported errors with a linear fit in APOGEE and adding gaussian noise.}
-%     \dbnote{is there too much going on here?}
-%     \dbnote{would it make sense to maybe place this fig close to Fig.~1 since they are very similar so it is easier to compare? Not sure how to make continuity work then..}
-%     \label{fig:equilibrium_validity}
-%     }
-% \end{figure*}
-
-Fig.~\ref{fig:c_evo} shows evolutionary tracks for every zone of the fiducial model.
-\caah\ trend quickly reaches an equilibrium state in \about{5}\,Gyr. \caafe\ tracks continue to evolve due to the long tail in the DTD of \ia.
-
-The evolution of abundances in our fiducial model is as follows:
-\begin{enumerate}
-    \item[(1)] {\it CCSN phase.} Star formation begins.
+Fig.~\ref{fig:c_evo} shows evolutionary tracks in \caah{} and \caafe{} in the fiducial model at 1\,kpc intervals of radius.
+The \caah\ trend reaches an equilibrium state within \about{5}\,Gyr. \caafe\ tracks continue to evolve due to the long tail of the \ia\ DTD.
+
+The evolution of chemical abundances can be understood as the interplay between different processes with different time-scales. 
  Initially, \cc\ dominate enrichment.
-[C/Mg] evolves with yields set by $\Ycc/\Yoc$, resulting in increasing values with [Mg/H].
-[Mg/H] quickly approaches its equilibrium value, but Fe remains low in comparison (in agreement with \citealt{WAF17}).
-    \item[(2)]  {\it AGB/SN Ia phase.} A few hundred million years later, delayed sources enrich the ISM. \agb\ stars release C, raising [C/Mg], and \ia\ expel Fe, lowering Mg/Fe. 
-    \item[(3)] {\it Approach to equilibrium.} Several billion years later, [C/Mg] plateaus as C also approaches equilibrium.
-[Mg/H] reaches equilibrium.
-[Fe/H] continues to increase due to ongoing \ia\ from old stellar populations.
-    \item[(4)] {\it Present day.} The abundances of C, Mg, and Fe reach their equilibrium values.
-
-\end{enumerate}
+The [C/Mg] abundance ratio is set by the relative yield $\Ycc/\Ymg$.
+Due to the metallicity dependence of $\Ycc$, [C/Mg] increases with  [Mg/H].
+[Mg/H], [Fe/H], and [C/H] all rise rapidly.
+[Mg/Fe] is initially high due to the delayed production time-scales of SN Ia Fe, as expected from the analytic models of \citet{WAF17}.
+ Of order 100 Myr later, delayed sources enrich the ISM. \agb\ stars release C, raising [C/Mg], and \ia\ expel Fe, lowering [Mg/Fe]. 
+ Several Gyr later, [Mg/H] reaches equilibrium.
+As the metal abundance stabilizes, so do metallicity-dependent \cc{} yields, allowing C to reach equilibrium.
+[Fe/H] continues to rise slowly due to ongoing \ia\ from old stellar populations.
+ Finally, the system reaches approximate equilibrium and evolution slows. \
+
 This evolution is predominantly driven by our chosen elemental yields, their
 metallicity dependence, and their DTDs.
-As we will demonstrate in section~\ref{sec:agb_results} below, the final slope of \caah\ depends on both the contributions and metallicity dependences of CCSN and AGB C yields.
-Although AGB models predict declining C production with metallicity, the greater contribution and positive metallicity dependence of CCSN C outweigh declining AGB production.
-
- Fig.~\ref{fig:c_evo} also shows the  equilibrium tracks in \caah\, and \caafe.
-Based on the \citepos{WAF17} analytic models of chemical equilibrium for constant star formation, the equilibrium abundance ratio between two elements depends only on the relative yields.
+As we will demonstrate in Section~\ref{sec:agb_results} below, the final slope of the \caah\ trend depends mostly on the metallicity dependence of the total C yield.
+The \caafe{} trend instead reveals the nature of delayed C production.
+
+%  Fig.~\ref{fig:c_evo} also shows the  equilibrium tracks in \caah\, and \caafe.
+Based on the \citepos{WAF17} analytic models of chemical equilibrium for constant star formation, the equilibrium abundance ratio between two elements depends only on the relative yields when the DTD is sufficiently prompt.
 For C/Mg,
-\begin{equation}\label{eq:equilibrium_yields}
-    {\rm [C/Mg]_{eq}} \equiv \log \left(\frac{\Ycc + \Ycagb }{y_{\rm Mg}}\right) - \log \left(\frac{Z_{\rm C,\,\sun}}{Z_{\rm Mg,\,\sun}}\right)
-\end{equation}
-As such, the equilibrium abundance represents the steady-state expectation for C abundances.  
-However, in the \caafe\ plane, equilibrium [Mg/Fe] is single-valued, so equilibrium track is a vetical line representing the range of ${\rm [C/Mg]_{eq}}$ across metallicity.
-The trends in \caafe\ are instead representative of the temporal evolution of [C/Mg].
-\caafe\ is well approximated by either a single-stellar-population or a single zone model because of the shallow metallicity gradient of the Milky Way.
-
-\subsection{Yield Variations}\label{sec:results_highmass}
-\label{sec:agb_results}
-
-\begin{figure*}
-    \includegraphics{sims_zeta_f.pdf}
-
-    \caption[]{
-        Stellar abundance trend predictions of our models .
-Coloured lines represent the median [C/Mg] in bins of [Mg/H] (left) or [Mg/Fe] (right) for each \agb\ table.
-Black points and grey dashes represent the median and 16th-84th percentiles of [C/Mg] in each bin in the \citet{jack}~sample.
-        The left panel only shows low-$\alpha$ stars. In the right panels, we show the trends only for stars where $-0.15\leq {\rm [Mg/H]}\leq -0.05$.
-        Stars are binned into 20 (left) or 12 (right) equal number bins. 
-        \textbf{Top}: Models with different metallicity dependences for  \cc\ C yields. \textbf{Bottom}: Models with different AGB C fractions $\fagb$ (only changing $\aagb$ and $\zetao$).
-    }
-    \label{fig:zeta_f}
-\end{figure*}
-
-The top of Fig.~\ref{fig:zeta_f} shows models with varying strengths of the $\Ycc$ metallicity dependence, $\zcc$.
-With higher $\zcc$, the model predicts a steeper \caah\ trend, owing to the direct relationship between the C/Mg equilibrium abundances and yield ratios.
-However, \caafe~is minimally affected by changes to $\zcc$ for stars at a given [Mg/H].
-CCSN occurs on much shorter timescales than AGB and SN Ia enrichment, so CCSN carbon reaches equilibrium before delayed C and Fe production modifies trends. 
-\footnote{The only effects on \caafe, when considering the narrow metallicity slice, are because of either the systematic change in equilibrium abundances, the imperfect evolution of the galaxy, or that the ISM abundances are set by stars which were born at poorer metallicities.
-}
-
-The bottom of Fig.~\ref{fig:zeta_f} shows three models with different C \agb\  fractions, defined as 
-\begin{equation}\label{eq:f_agb}
-    \fagb := \frac{\Ycagb(\Zo)}{\Yct(\Zo)} \propto \aagb.
-\end{equation}
-Modifications of $\fagb$ affect both \caafe\ and \caah.
-At fixed metallicity, the \caafe\ trend is principally sensitive to how much C and Fe comes from delayed sources.
-Increasing the \agb\ fraction therefore steepens the \caafe\ trend as expected.
-Though each yield model predicts the trend to flatten at ${\rm [Mg/Fe]} \lesssim 0.1 $, the median is still within the width of the observed distribution and the overall agreement is good.
-Additionally, increasing $\fagb$ decreases the slope in \caah\ owing to the negative metallicity dependence of AGB C yields with metallicity.
-
-\subsection{Yield Inference Results} \label{sec:mcmc_results}
-
-\begin{figure}
-\centering
-\includegraphics{figures/mcmc_corner.pdf}
-\caption[]{
-A corner plot of the posterior samples from the MCMC simulation for the analytic model fit to the binned mean trends.
-$\alpha$ represents the scale factor for the AGB yields, and $\zetao$, $\zetai$ and $\zetaii$ represent the constant, linear, and quadratic components of the CCSN yield (all scaled by $10^{-3}$).
-$\sigma_{\rm int}$ is the intrensic scatter.
-See section~\ref{sec:mcmc_methods} for a description of the methods.
-}
-
-\label{fig:mcmc}
-\end{figure}
-
-\begin{figure*}
-    \centering
-    \includegraphics[]{figures/mcmc_fagb.pdf}
-    \includegraphics[]{figures/mcmc_y_tot.pdf}
-
-    \caption[]{
-        \textbf{Left:} Posterior distribution of $\fagb$ from MCMC samples for each model we show.
-Regardless of assumptions, the best values of $\fagb$ range from about 0.1 to 0.35 and in all cases is less than 0.5.
-The black X marks the predicted value of $\fagb$ assuming our fiducial yield scale (as in Table~\ref{tab:agb}).
-    \textbf{Right:} The final total C yield (CCSN + AGB) for the median parameters from MCMC fits for each model.
-Additionally, we show individual samples from the \fruity{} \ MCMC model as faint blue lines.
-    }
-
-    \label{fig:mcmc_ytot}
-\end{figure*}
-
-Fig.~\ref{fig:mcmc} shows the distribution and correlation of each parameter in the fiducial MCMC model.
-Each parameter is relatively well-constrained.
-The most prominent correlation, between $\zetao$ and $\alpha$ represents the constraint on the equilibrium abundance of C near solar.
-The other main correlation, between $\zetai$ and $\zetaii$, arises from the shape of the \caah\ trend.
-If the quadratic component decreases, then the \caah\  slope (past [Mg/H] $\lesssim 0.1$) increases, so the linear component must decrease in order to maintain agreement with the data.
-
-Table~\ref{tab:mcmc_results} contains the resulting posterior distributions for each parameter for a variety of both AGB models and GCE assumptions. 
-For the fiducial model, the best fit yields are 
-\begin{equation}
-    \frac{\Ycc}{y_{\rm Mg}} = (\zetaobest) + (\zetaibest) x + (\zetaiibest) x^2
-\end{equation}
-where $x = \log Z/\Zo$.
-Fig.~\ref{fig:mcmc_ytot} shows the AGB fraction at solar metallicity and the total C yield with metallicity for each MCMC run. 
-In essentially each case, the majority of samples have a AGB fraction between 0.15 and 0.4.
-
-\begin{table*}
-    \caption{
-        Best-fit parameters (medians and 16-84th percentile errors) from MCMC analysis for various models discussed.
-        The columns are:  modelname \textit{model}, best fit reduced $\chi^2$, best fit log posterior probability $\log p$, AGB scaling $\aagb$, CCSN constant, linear, and quadratic coefficients times $10^3$ $\zetao$, $\zetai$, $\zetaii$, the intrensic scatter $\sigma_{\rm int}$, the AGB fraction $\fagb$, the total C yield at solar metallicity $\Yct$, and the total C yield at solar metallicity $\zeta_{\rm 1, tot}$.
-    }
-    \label{tab:mcmc_results}
-
-{ 
-\renewcommand{\baselinestretch}{1.2}
-    \begin{tabular}{l l l l l l l l l l l} 
-    \hline
-    model            & $\chi2$  & $\log p$ & $\aagb$ & $\zetao$ & $\zetai$ & $\zetaii$ & $\sigma_{\rm int}$ & $\fagb$ & $\Yct$ & $\zeta_{\rm 1, tot}$\\
-\hline
-\fruity          &      7.4 &    18.43 & $2.41^{+0.26}_{-0.27}$  &  $1.90^{+0.10}_{-0.09}$  &  $2.28^{+0.15}_{-0.16}$  &  $2.59^{+0.30}_{-0.30}$  &  $0.08^{+0.02}_{-0.01}$  &  $0.32^{+0.03}_{-0.04}$  &  $2.79^{+0.02}_{-0.02}$  &  $1.43^{+0.12}_{-0.13}$\\
-\aton            &     14.9 &     5.30 & $1.71^{+0.34}_{-0.34}$  &  $2.55^{+0.05}_{-0.05}$  &  $3.19^{+0.40}_{-0.40}$  &  $1.92^{+0.45}_{-0.44}$  &  $0.14^{+0.03}_{-0.02}$  &  $0.06^{+0.01}_{-0.01}$  &  $2.72^{+0.03}_{-0.03}$  &  $1.48^{+0.20}_{-0.19}$\\
-\monash          &     15.4 &     2.24 & $2.06^{+0.52}_{-0.54}$  &  $2.03^{+0.19}_{-0.18}$  &  $3.82^{+0.64}_{-0.66}$  &  $3.48^{+0.57}_{-0.59}$  &  $0.15^{+0.03}_{-0.02}$  &  $0.19^{+0.05}_{-0.05}$  &  $2.50^{+0.07}_{-0.07}$  &  $1.55^{+0.21}_{-0.22}$\\
-\nugrid          &      5.8 &    24.19 & $1.21^{+0.11}_{-0.11}$  &  $1.58^{+0.11}_{-0.11}$  &  $1.58^{+0.11}_{-0.11}$  &  $3.16^{+0.29}_{-0.28}$  &  $0.07^{+0.02}_{-0.01}$  &  $0.38^{+0.04}_{-0.04}$  &  $2.56^{+0.02}_{-0.02}$  &  $1.02^{+0.11}_{-0.11}$\\
-\fruity\ m0.7    &      4.5 &    32.86 & $1.39^{+0.11}_{-0.10}$  &  $2.25^{+0.04}_{-0.04}$  &  $1.55^{+0.09}_{-0.08}$  &  $2.54^{+0.23}_{-0.22}$  &  $0.05^{+0.01}_{-0.01}$  &  $0.21^{+0.02}_{-0.01}$  &  $2.83^{+0.01}_{-0.01}$  &  $1.12^{+0.09}_{-0.09}$\\
-$y\rightarrow 2y$ &      6.0 &    20.61 & $2.51^{+0.25}_{-0.25}$  &  $1.83^{+0.09}_{-0.09}$  &  $2.00^{+0.12}_{-0.12}$  &  $2.41^{+0.29}_{-0.29}$  &  $0.08^{+0.02}_{-0.01}$  &  $0.34^{+0.03}_{-0.03}$  &  $2.76^{+0.02}_{-0.02}$  &  $1.12^{+0.08}_{-0.08}$\\
-lateburst        &     18.7 &     8.35 & $2.41^{+0.35}_{-0.36}$  &  $2.00^{+0.12}_{-0.12}$  &  $2.92^{+0.34}_{-0.34}$  &  $3.51^{+0.66}_{-0.65}$  &  $0.13^{+0.02}_{-0.02}$  &  $0.31^{+0.04}_{-0.04}$  &  $2.89^{+0.03}_{-0.03}$  &  $2.07^{+0.32}_{-0.32}$\\
-twoinfall        &     10.6 &    18.05 & $2.03^{+0.21}_{-0.21}$  &  $2.05^{+0.08}_{-0.08}$  &  $2.65^{+0.20}_{-0.20}$  &  $3.52^{+0.35}_{-0.36}$  &  $0.09^{+0.02}_{-0.01}$  &  $0.27^{+0.03}_{-0.03}$  &  $2.80^{+0.02}_{-0.02}$  &  $1.94^{+0.18}_{-0.19}$\\
-SN Ia 1.2        &      9.3 &    13.10 & $3.29^{+0.43}_{-0.45}$  &  $1.57^{+0.16}_{-0.15}$  &  $2.73^{+0.22}_{-0.23}$  &  $2.72^{+0.35}_{-0.35}$  &  $0.10^{+0.02}_{-0.02}$  &  $0.44^{+0.06}_{-0.06}$  &  $2.79^{+0.02}_{-0.02}$  &  $1.58^{+0.14}_{-0.14}$\\
-\fruity\ linear  &   3036 &    --- & {\it 2.40}  &  $1.99^{+0.02}_{-0.02}$  &  $1.68^{+0.08}_{-0.09}$  &  ---  &  $0.10^{+0.02}_{-0.02}$  &  $0.31$  &  $2.88^{+0.02}_{-0.02}$  &  $0.84^{+0.08}_{-0.09}$\\
-
-\hline
-    \end{tabular}
-
-}
-
-\end{table*}
-
-\subsection{Unknowns and Degeneracies} \label{sec:sfh} \label{sec:outflows}
-\label{sec:degeneracies}
-
-\begin{figure*}
-    \includegraphics{figures/zeta_f_mass_sfh.pdf}
-
-    \caption[]{
-        Similar to Fig.~\ref{fig:zeta_f}, except for \caafe\ for a variety of models.
-        {\bf Left} models for AGB fractions of 0.1, 0.25 (fiducial), and 0.4. 
-        {\bf Middle} models where the \agb\ yields are shifted by a factor in mass.
-        {\bf Right} alternate star formations histories (lateburst and twoinfall) and a model with all yields doubled.
-    }
-    \label{fig:sims_degens}
-\end{figure*}
-
-\begin{figure*}
-    \includegraphics[]{figures/mcmc_caahfe_predicted.pdf}
-
-    \caption[]{
-        Similar to Fig.~\ref{fig:zeta_f} except showing the mean tracks for different best-fit AGB yield tables with best-fit CCSNe parameters.
-Variations in the \caafe\ plane are due to the different total AGB C yield and variations in the mass-dependence of each yield table.
-    }
-    \label{fig:agb_predictions}
-\end{figure*}
-
-Assumptions about the AGB yields, the star formation history, and outflows negligibly impact \caah\ due to chemical equilibrium.
-However, these degeneracies can inform and affect the interpretation of \caafe.
-
-Because both the increase in \cc\ slope $\zcc$ and AGB fraction $\fagb$ have similar impacts to \caah, we can change both parameters simultaneously to retain agreement in \caah.
-We show example models in the left panel of Fig.~\ref{fig:sims_degens} in \caafe, (as models cannot be readily distinguished in \caah).
-The principle effect of increasing $\fagb$ and adjusting $\zcc$ correspondingly is to increase the amplitude of the trend in \caafe.
-Models with little to no AGB C production will produce stars with [C/Mg] independent of [Mg/Fe] in a metallicity slice.
-As the AGB fraction increases to an extreme $f^{\rm AGB}=0.5$, the trend becomes steeper than the fiducial but remains a rescaling of the same shape.
-
-A second factor affecting \caafe\ is the assumed delay time distribution of \agb\ carbon production.
-The middle panel of Fig.~\ref{fig:sims_degens} shows models where the AGB yields have been shifted by a factor in mass.
-When the AGB C production is weighted towards more massive AGB stars, then the delay time distribution becomes more rapid, causing equilibrium to be reached sooner (at higher [Mg/Fe]).
-The \caafe\ trend therefore is less sensitive to the C production by stars with masses $M \gtrsim 5 \Mo$ \dbnote{calculate timescales here}.
-On the other hand, shifting the C production towards low mass stars extends the DTD towards longer times.
-In Fig.~\ref{fig:sims_degens}, models shifted towards lower masses increase the amplitude of the \caafe\ trend, particularly steepening the high [Mg/Fe] slope.
-For the most extreme case, where the masses are shifted by a factor of 0.5; the AGB production is more delayed than SNeIa, causing an increasing slope of \caafe\ towards low [Mg/Fe].
-An intermediate mass shifts (0.7) is approximant linear in \caafe, qualitatively matching the observed trend.
-
-Fig.~\ref{fig:agb_predictions} shows the resulting median trends in \caah\ and \caafe\ for the median parameters for each AGB model.
-Regardless of the AGB model, there is a reasonable choice of \cc\ yields which can closely match the \caah\ trend.
-All AGB models predict similar \caafe\ trends.
-However, each (unshifted) yield table underpredicts the slope of \caafe\ at low [Mg/Fe].
-As discussed above, the relative flattening in \caafe\ results from a AGB DTD that is more prompt than SNe Ia.
-Also, note that the median parameters (from Table~\ref{tab:mcmc_results}) suggest an amplification of AGB yields of between 1.5 and 2 for all models except \nugrid.
-Without this amplification, the overal trend in \caafe\ would be much flatter than is observed.
-We suggest that most AGB yield models require an increase in the amplitude of C production and a weighting of C production more towards low mass stars in order to better match observations in this GCE framework.
-
-We consider two alternative SFHs. 
-Motivated by the findings of \citet[see discussion in \JJ]{mor+19,isern19}, the \textit{lateburst} model
-adds a Gaussian burst to the fiducial inside-out model, 
-\begin{equation}\label{eq:lateburst}
-    \dot{\Sigma}_\text{lateburst} \propto \dot{\Sigma}_\text{inside-out} \left(1 + A\,e^{-(t-\tau_{\rm burst})^2/2\sigma^2_{\rm burst}} \right)
-\end{equation}
-where $A=1.5$ represents the amplitude of the birth, $\tau_\text{burst}=10.8$\,Gyr is the time where the burst is strongest, and $\sigma_\text{burst}=1$\,Gyr is the width of the burst.
-
-We also consider a two-infall like model as presented in \citep{dubay+24},
-\begin{equation}\label{twoinfall}
-\dot{\Sigma}_{\rm in} \propto e^{-t/\tau_1} + A \theta(t - t_{2}) e^{-t/\tau_2}
-\end{equation}
-where $\tau_1=1\,$Gyr, $\tau_2=4\,$Gyr, $t_2=4$\,Gyr, and the the amplitude is given by the ratio between the thick and thin disk in  \citet{BHG16}.
-
-The right panel of Fig.~\ref{fig:sims_degens} compares the fiducial, lateburst, and two-infall models.
-The pertubations to \caafe\ are small.
-The largest change is to the distribution of [Mg/Fe], but the \caafe\ trends are identical for the lateburst or is slightly shifted and steeper for the two infall model.
-So, variations due to SFH considered here are most likely smaller than width of the observed distribution.
-Building on \citet{james+23}, we conclude that the \caah\ and \caafe\ trends reflect nucleosynthetic yields more than the Galactic SFH. 
-\dbnote{There has to be a good reason why \caafe\ is not affected or maybe only more extreme pertubations make a difference?}
-
-While some Milky Way \gce{} models (including ours) incorporate significant mass-loading, others
-neglect mass-loading and instead use lower yields \citep[e.g.][]{MCM13, MCM14, spitoni19, spitoni20, spitoni21}.
-Both classes of models are able to reproduce many details of the disk abundance structure due to the strong degeneracy between the normalizations of elemental yields and mass-loading (see discussion in, e.g.
-\citealt{sandford+24} and Appendix B of \citealt{james+23}).
-Our parameterization of $\eta$ illustrates this (see Equation~\ref{eq:mass_loading}) -- choosing a lower value of $y_{\alpha}$ will similarly result in lower values of $\eta$ while maintaining the same metallicity gradient.
-We consider a model where we double all yields, in the right panel of Fig.~\ref{fig:sims_degens}. A uniform change in yields and outflows leaves our median trends relatively unchanged. 
-\dbnote{This paragraph is slightly off, the actual value of eta around the sun is only 0.5 so reducing outflows more does not keep metallicity gradient. Do we need to change framing here?}
-
-Additionally, Fe yields and the \ia\  delay-time-distribution have their own uncertainties.
-Increasing both $y_{\rm Fe}^{\rm Ia}$ and $\Ycagb$ correspondingly leaves \caafe\ mostly unchanged.
-As showin in the left panel of Fig.~\ref{fig:mcmc_ytot}, increasing the SN Ia Fe yield by 1.2 times results in a similarly sized increase in the derived $\fagb$.
-In this framework, our accuracy is limited to that of the Fe DTD.
-
-\dbnote{Other things to discuss possibly ? :
- Initial mass function (and possible metallicity dependence)?
-ISM stochasticy and inhomogeneities.
-Metallicity-Dependent Oxygen/Magnesium and Iron yields?
-Gas phase migration / ISM cooling?
-mass-lifetime relation.
-Spectroscopic systematics.
- }
+% \begin{equation}\label{eq:equilibrium_yields}
+%     {\rm [C/Mg]_{eq}} :=  \log \left(\frac{\Ycc + \Ycagb }{y_{\rm Mg}}\right) - \log \left(\frac{Z_{\rm C,\,\sun}}{Z_{\rm Mg,\,\sun}}\right)
+% \end{equation}
+% As such, the equilibrium [C/Mg] represents the steady-state expectation due to C and Mg yields.
+% However, in the \caafe\ plane, equilibrium [Mg/Fe] is single-valued, so equilibrium track is a vetical line representing the range of ${\rm [C/Mg]_{eq}}$ across metallicity.
+Therefore, the trends in \caafe\ are instead representative of the approach to equilibrium in C, Mg, and Fe.
+\caafe\ is well approximated by either a single-stellar-population or a single zone model, since its slope is set by the C and Fe DTDs.
+%
 
@@
 
-\caption[]{Similar to Fig.~\ref{fig:zeta_f} except for [C/N] against [Mg/H] for the fiducial model.
-Combining our results with the suggested yield from \JJ\ (rescaled to our adopted yields) explains both the thin-disk evolution of C and N.
+\caption[]{The median low-$\alpha$ [C/N] ratio as a function of [Mg/H] for our fiducial model (blue line), compared with \apogee{} subgiants (medians as black points with 16th and 84th percentile ranges as grey bars).
+Stars are binned into 20 equal-number bins.
+Combining our results with the suggested N yield from \citet{james+23} \ (rescaled to our adopted yields) explains the thin-disk evolution of both C and N.
 }
@@
 N production, also affected by the CNO cycle, is closely tied to C.
-As a test of our model, we use the \agb\ N yield suggested by \citet{james+23}.
-Fig.~\ref{fig:nitrogen} shows [C/N] versus [Mg/H] and for our fiducial model.
-We are able to closely match the [C/N]-[Mg/H] trend.
-The [C/N]-[Mg/Fe] relation, on the other hand, is shallower than the data, indicating that the DTD of C production may be sharper than our AGB yield tables would suggest (or the N DTD more extended, or both).
+This paper builds upon \citet{james+23}, who used similar methods to constrain N yields.
+As an additional test of both yield models, we combine a rescaled version of their recommended N yields (see discussion in Section~\ref{sec:vice}) with our fiducial choice of C yields.
+Fig.~\ref{fig:nitrogen} shows [C/N] versus [Mg/H] as predicted by our fiducial model. We are indeed able to closely match the observed [C/N]-[Mg/H] trend.
+
+\subsection{The high-mass yield slope and low-mass production fraction of C yields}\label{sec:yield_variations}
+\label{sec:agb_results}
+
+\begin{figure*}
+    \includegraphics{sims_zeta_f.pdf}
+
+    \caption[]{
+        Trends in [C/Mg] with [Mg/H] (left) or [Mg/Fe] (right). 
+        Stars are binned into 20 (left) or 12 (right) equal-number bins. 
+        The left panel only shows low-$\alpha$ stars, and the right panel shows stars where $-0.15\leq \mgh \leq -0.05$.
+        Coloured lines represent the median [C/Mg] in bins of [Mg/H] or [Mg/Fe] for each model.
+        Black points and grey dashes represent the median and 16th-84th percentiles of [C/Mg] in each bin in the \citet{jack}~sample. 
+        The total solar C yield is held fixed in each model. 
+        %
+        \textbf{Top}: Models with different slopes of the metallicity dependence of the CCSN yield, $\zcc$ (Eq.~\ref{eq:y_cc}), where higher $\zcc$ corresponds to a more rapid increase in C production with metallicity.
+\textbf{Middle}: Models with different fractions of solar C produced in AGB stars, $\fagb$.
+        \textbf{Bottom:} Models where both $\fagb$ and $\zcc$ are adjusted simultaneously. 
+    }
+    \label{fig:zeta_f}
+\end{figure*}
+
+The top row of Fig.~\ref{fig:zeta_f} shows models with varying strengths of the $\Ycc$ metallicity dependence, $\zcc$ (see Eq.~\ref{eq:y_cc}).
+With higher $\zcc$, the model predicts a steeper \caah\ trend, owing to the direct relationship between equilibrium [C/Mg] and yield ratios in Eq.~\ref{eq:c_mg_cc}.
+However, the \caafe{} trend is minimally affected by changes to $\zcc$ for stars at a given [Mg/H].
+CCSN occur on much shorter time-scales than AGB and SN Ia enrichment.  The primary effect of increasing $\zcc$ in the \caafe{} plane, restricted to a metallicity slice, is to shift [C/Mg] uniformly.
+
+The middle row of Fig.~\ref{fig:zeta_f} shows three models with different C \agb\  fractions (Eq.~\ref{eq:f_agb}).
+At fixed metallicity, the \caafe\ trend is principally sensitive to how much C and Fe come from delayed sources.
+In the limit $\fagb \to 0$, the [C/Mg] abundance will become nearly independent of [Mg/Fe].
+As $\fagb$ increases, the steepness of the \caafe{} trend increases.
+
+Because both $\fagb{}$ and $\zcc$ affect the \caah{} trend, it is possible to vary both of these parameters and leave the \caah{} trend nearly untouched. 
+The bottom row of Fig.~\ref{fig:zeta_f} illustrates this degeneracy.
+While each model has substantially different AGB contributions, ranging from $\fagb = 0$ to $0.5$, adjustments to the massive-star C yield leave the \caah{} trend mostly unaffected.
+While some residual differences remain, these could be addressed with a CCSN yield model that more closely compensates for the AGB yield metallicity dependence.
+On the other hand, the differences between these models in the \caafe{} plane are far more stark, with the trend's total amplitude ranging from almost 0 (for $\fagb{} = 0$) to nearly 0.3 dex (for $\fagb{} = 0.5$).
+While these trends may appear different from those in the middle panel, they are mostly only shifted vertically.
+
+Given these models, we can interpret the physical significance of each trend.
+The \caah{} trend (for low-$\alpha$ stars) tells us about the total C yield.
+This trend is mostly independent of where C is produced at a given metallicity, but is very sensitive to changes in the total C production.
+Models that match \caah{} trends alone would struggle to differentiate between different production mechanisms of C.
+The \caafe{} trend (for a given metallicity) tells us about delayed C production.
+For example, the models in Fig.~\ref{fig:zeta_f} with no delayed C predict a nearly flat trend in [C/Mg] with [Mg/Fe], even with metallicity-dependent C production.
+As such, the \caafe{} trend is a useful diagnostic of $\fagb$.
+
+\subsection{AGB yield modifications}
+
+All AGB yield tables predict a similarly shaped trend in the \caafe{} abundance space.
+The left panel of Fig.~\ref{fig:sims_degens} shows the best-fitting AGB yield models (see Section \ref{sec:mcmc} for methodology) for each yield table we consider.
+Interestingly, while the individual DTDs of each AGB table appear substantially different (Fig.~\ref{fig:agb-ssp}), these differences smooth out in terms of the predicted abundance trends.
+Altogether, changes to the \agb{} yield table appear to have minimal effects on predicted C trends.
+
+One potential tension, however, is the concavity of the \caafe{} relation: all \agb{} tables predict a slightly concave down trend.
+In contrast, the subgiants predict a nearly-linear C trend across all [Mg/Fe].
+In addition, one of the most salient differences between models in the left panel of Fig.~\ref{fig:sims_degens} is that \aton{} and \monash{} predict an almost flat \caafe{} trend for ${\rm [Mg/Fe]} \lesssim 0.1$, in further tension with the data.
+As discussed in the next paragraph, this may indicate that C production should be weighted more towards even lower-mass stars.
+As an example, we shift the \fruity{} AGB yield table by a constant factor of 0.7 towards lower-mass AGB production.
+This shifted model predicts a more linear \caafe{} trend, in better agreement with observations.
+However, a GCE model better able to produce the abundance of high-$\alpha$ stars may be necessary to fully interpret this trend.
+Alternatively, the Fe DTD could similarly be too extended in our models, though recent work suggests a yet more extended DTD than our assumption \citep{palicio+2024, dubay+24}.
+
+To further explore the impact of the C DTD on abundance trends, we artificially shift the \fruity{} AGB yield table by a factor in mass.
+The middle panel of Fig.~\ref{fig:sims_degens} shows models shifting production towards lower masses (factors of 0.5 and 0.7) and higher masses (1.5).
+When the AGB C production is weighted towards more massive AGB stars, the DTD becomes more rapid, leading to higher [C/Mg] at high [Mg/Fe].
+On the other hand, shifting the C production toward lower mass progenitors makes the DTD more extended.
+In Fig.~\ref{fig:sims_degens}, the models with AGB C shifted towards lower progenitor masses reduce or reverse the concavity of the \caafe\ trend.
+For the extreme case, where the progenitor masses are shifted by a factor of 0.5, the AGB production is more delayed than SN Ia, resulting in a concave up trend.
+The ideal progenitor mass shift is \about{0.7}, linearizing the \caafe\ trend to agree with observations and alleviate the disagreement in concavity seen in the left panel of Fig.~\ref{fig:sims_degens}.
+While our mass shift models are artificially simple, they illustrate that the observed \apogee{} trends would be better fit if AGB production were shifted towards longer-lived stars.
+
+\subsection{Star formation history and yield scale } \label{sec:sfh} \label{sec:outflows}
+
+\begin{figure*}
+    \includegraphics{figures/zeta_f_mass_sfh.pdf}
+
+    \caption[]{
+        Similar to Fig.~\ref{fig:zeta_f}, but focusing on [C/Mg] versus [$\alpha$/Fe].
+        {\bf Left:} The best-fitting model for each AGB table, and the best-fitting model from the middle panel with a mass shift of 0.7. 
+        {\bf Middle:} Models where the \fruity{} \agb\ yields are artificially shifted by different multiplicative factors in progenitor mass, but maintaining the same $\fagb$. 
+        {\bf Right:} Models with alternative star formation histories (Eqs.~\ref{eq:lateburst}, \ref{eq:twoinfall}), and a model where all yields are doubled (with mass-loading adjusted accordingly; see Section~\ref{sec:vice}).
+    }
+    \label{fig:sims_degens}
+\end{figure*}
+
+In the right-hand panel of Fig.~\ref{fig:sims_degens}, we consider two alternative SFHs.
+Motivated by the findings of \citet{mor+19} and \citet[see discussion in \JJ]{isern19}, the \textit{lateburst} model adds a Gaussian-shaped burst to the fiducial inside-out model, 
+\begin{equation}\label{eq:lateburst}
+    \dot{\Sigma}_\text{lateburst} \propto \dot{\Sigma}_\text{inside-out} \left(1 + A\,e^{-(t-t_{\rm burst})^2/2\sigma^2_{\rm burst}} \right),
+\end{equation}
+where $A=1.5$ represents the amplitude of the birth, $t_\text{burst}=10.8$\,Gyr is the time where the burst is strongest, and $\sigma_\text{burst}=1$\,Gyr is the width of the burst.
+
+We also consider a two-infall evolutionary history \citep[e.g.,][]{chiappini+97,spitoni19, spitoni21, spitoni+23}.
+This prescription posits that the majority of the stellar mass of the Galactic disk was built up during two events of substantial metal-poor accretion separated in time.
+The two-infall scenario offers a natural explanation \citep{spitoni19, spitoni21} for the bimodal distribution of [$\alpha$/Fe] ratios observed in the MW \citep[e.g.,][]{hayden+15}.
+However, the two-infall model has recently faced challenges when confronted with large catalogues of stellar age measurements \citep{dubay+24}.
+For these models, we switch \VICE{} to `infall mode' and let it compute the SFR from a specified accretion history, in contrast to the other models where we specify the SFH (see discussion in Section~\ref{sec:vice}).
+Our accretion history, following \citet{dubay+24}, is given by
+\begin{equation}\label{eq:twoinfall}
+\dot{\Sigma}_{\rm in} \propto e^{-t/\tau_1} + A \theta(t - t_{2}) e^{-t/\tau_2},
+\end{equation}
+where $\tau_1=1\,$Gyr, $\tau_2=4\,$Gyr control the duration of the first and second burst, $t_2=4$\,Gyr specifies the start of the second infall, from, $A$ is the relative amplitude of the second burst, and $\theta$ is the Heaviside step function.
+We chose $A(R)$ such that the ratio between the stellar mass produced in the first and second burst by $13.2\,{\rm Gyr}$ matches the ratio between the thin and thick disks from \citet{BHG16}.
+
+The right panel of Fig.~\ref{fig:sims_degens} compares the fiducial, lateburst, and two-infall models.
+The differences in the \caafe\ trend are small.
+Each model predicts a different distribution in [Mg/Fe] as expected \citep[e.g.,][]{JW20}, but the relations between abundance ratios are largely unaffected by the assumed SFH.
+Variations due to the SFHs considered here are smaller than the width of the observed distribution.
+
+Lastly, we demonstrate that our conclusions are unaffected by the assumed scale of stellar yields and mass loading in outflows.
+The fiducial yield scale adopted here, from \citet{david_fe}, is relatively low, requiring only moderate outflows to reproduce solar metallicity.
+However, models with higher outflows and higher yields give similar predictions because of the
+strong degeneracy between the normalizations of elemental yields and mass-loading (see discussion in, e.g., \citealt{sandford+24} and Appendix B of \citealt{james+23}). 
+Our parameterization of $\eta$ illustrates this point (see Eq.~\ref{eq:mass_loading}) -- choosing a higher value of $y_{\rm Mg}^{\rm CC}$ will similarly result in higher values of $\eta$ while maintaining the same metallicity gradient.
+In the right panel of Fig.~\ref{fig:sims_degens}, we consider a model in which all yields are doubled (and mass loading approximately doubled by Eq.~\ref{eq:mass_loading}).
+As expected, the trend in [C/Mg]-[Mg/Fe] is not significantly affected, showing that observed trends constrain the ratio of C yields to Mg yields.
+
+\section{Yield Inference}\label{sec:mcmc}
+
+Here, our goal is to convert the qualitative understanding from the last Section into more quantitative constraints on the yields. 
+From the previous Section, we learn that:  the \caah{} trend tells us the overall total C yield metallicity dependence, and the \caafe{} trend tells us about the amount of delayed C and its DTD.
+We chose to construct Monte-Carlo Markov chain (MCMC) models to explore possible abundance combinations matching the observed trends.
+From these models, we can derive the distributions of likely properties of underlying C yields given our current observations.
+
+\subsection{Monte-Carlo Markov Chain yield inference} \label{sec:mcmc_methods}
+
+To efficiently explore a wide range of yield combinations, we can use this linearity to predict the abundances from linear combinations of yields through {\it process tracking}.
+In GCE, total elemental abundances are (to first order) linear with respect to combinations of yields \citep[e.g.,][]{WAF17}.
+The rate of change of an element's ISM mass is given by the sum of processes constant or linear in the element's abundance: material formed into stars, new production of elements, material returned from stars, and material lost through outflows.
+Thus, just as the yields of different elements can be treated as independent solutions, the yields of different processes can be solved independently and superimposed.
+In our process tracking method, we set up \VICE {} to integrate each process for C independently (by using tracer elements for each yield component).
+We then predict the stellar abundances from a given linear combination of yields $y_{\rm tot} = \sum_i a_i\, y_i$ by adding together the linear abundances $Z_{\rm C, \it i}$ in the same linear combination ($Z_{\rm C, tot} = \sum a_i\,Z_i$).
+
+There are some limitations to the process-tracking approximation.
+Note that many other GCE parameters are non-linear with abundance and require full multi-zone simulations, such as star formation history, outflows, and migration prescriptions.
+Also note that metallicity-dependent yields introduce a second-order effect (metallicity depends on total yields which depend on metallicity), but for small changes to total yields, this effect should be small.
+
+Our first step is to run a multi-zone model tracking the abundances of each process we are interested in. 
+To use all the information available for [C/Mg] trends with [Mg/Fe] and [Mg/H], we calculate the mean C abundance for each 2D bin in [Mg/Fe] and [Mg/H] for both the data and the model.
+We add Gaussian-distributed measurement uncertainties to the model's stars as described in the Appendix (Eq.~\ref{eq:uncertainties}).
+We chose to use bins of a constant width of 0.04 dex, ranging from [Mg/H] of -0.5 to 0.5 and [Mg/Fe] of -0.1 to 0.4.
+We remove any 2D bin if fewer than 3 stars of the model or data fall in the bin.
+We separate the C yield  into three different components:
+\begin{enumerate}
+    \item $\aagb$: Prefactor for an AGB yield table
+    \item $\yl$: Constant CCSN yield 
+    \item $\zcc$: Linear CCSN yield ($y = \zcc (Z/\Zo)$)
+\end{enumerate}
+$\yl$, representing the low-metallicity C yield, is related to the $\yo$ of Eq.~\ref{eq:y_cc} by $\yl + \zcc = \yo$.
+
+We construct a likelihood based on the difference between the data and the model's mean C abundance in each bin.
+We use means since they are linear to linear combinations.
+Additionally, we work in linear abundance space for improved numerical stability.
+Given the predicted abundance for the model in a given bin $b$,  $Z_{\rm C, \it b}^{\rm model}$, the associated observed abundance, $Z_{\rm C, \it b}^{\rm obs}$, and the error on the mean $\sigma_b$, the (Gaussian) log likelihood is given by
+\begin{equation} \label{eq:mcmc_likelihood}
+    \log {\cal L} = \sum_b -\ln(\sigma_{b}) -\left(\frac{Z_{\rm C, \it b}^{\rm model} - Z_{{\rm C}, b}^{\rm obs}}{2\sigma_{b}}\right)^2 - \frac{1}{2}\log(2\pi).
+\end{equation}
+The total variance in each bin is calculated from the standard error on the mean of the observations in a bin $\sigma_{b, \rm obs}$, the standard error on the mean for each model component $i$, $\sigma_{b, i,\rm model}$, and a {\it systematic} uncertainty term $\sigma_{\rm sys}$.
+Altogether,
+\begin{equation}
+    \sigma_{b}^2 = \sigma_{\rm sys}^2 + \sigma_{b,\rm\ obs}^2  +  \left(\sum_{i} a_i\, \sigma_{b,i,\ \rm model}\right)^2
+\end{equation}
+where $a_i$ is the associated coefficient ($\aagb$, $\yl$, $\zcc$) for each yield process.
+We add the model standard deviations linearly since the C abundances are calculated from the same sample for each process.
+
+When included, the $\sigma_{\rm sys}^2$ represents the typical systematic random uncertainty.
+We consider models with both $\sigma_{\rm sys} = 0$ and 0.05 dex.
+While approximate, this value is similar to typical mean deviations between APOGEE and other surveys' C and Mg abundances \citep{hegedhus+2023, jonsson+2018} and discrepancies between APOGEE's reported abundance uncertainties compared to other measurements of dispersion \citep{mead+2024}.
+While systematic uncertainties are unlikely to be well-described by an independent, uncorrelated, constant-width normal distribution, we use this model as an order-of-magnitude illustration of the likely uncertainties of our results.
+
+We adopt loose priors for each model parameter: $\aagb \sim N(1, 1)$, $\zcc \sim N(0, 10^{-3})$, and $\yl \sim N(2\times10^{-3}, 1\times10^{-3})$, where $N(\mu, \sigma)$ is a Gaussian distribution with mean $\mu$ and standard deviation $\sigma$.
+
+We run the MCMC using Turing.jl \citep{turingjl} with a No-U-turn sampler (an adaptive Hamilton Monte-Carlo algorithm, \citealt{NUTS}) with an acceptance rate of 0.65.
+We combine 16 independent chains with 3,000 steps each for a total of 48,000 samples.
+The median parameters derived from this model provide the yield choices for the AGB yield models shown in the left panel of Fig.~\ref{fig:sims_degens}.
+
+\subsection{Yield inference results} \label{sec:mcmc_results}
+
+Based on the procedure above, we derive our best-fitting (not fiducial) yield set.
+We find, for the \fruity{} AGB yield set,  $\aagb = \cfactor$, $\yo =22.3\times10^{-4}$, and $\zcc=7.9\times10^{-4}$.
+Instead, for the model where \fruity{} is shifted by a mass factor of 0.7, $\aagb = 2.34$, $\yo = 19.7\times 10^{-4}$ and $\zcc=3.2\times 10^{-4}$.
+The fiducial yields enforce a low-metallicity [C/O] plateau of \about{-0.5} for better agreement in Section~\ref{sec:gas}.
+Table~\ref{tab:mcmc_results} presents the best-fitting parameters for each model or yield set considered here.
+
+The left panel of Fig.~\ref{fig:mcmc_ytot} shows the inferred total C yield for each AGB yield table, and the \fruity{} table shifted by a mass factor of 0.7.
+While there is some variability in the total C yield, all models predict a total C yield within a band of width 0.5 in $\Yct$ ($\approx0.05\,$dex).
+Thus, the choice of AGB yield table only slightly affects the inferred total yield, as we expect the \caah{} trend to tightly constrain the total C yield (see Section~\ref{sec:yield_variations}).
+
+The middle panel of Fig.~\ref{fig:mcmc_ytot} shows the inferred AGB fraction (Eq.~\ref{eq:f_agb}) at solar metallicity for each model.
+No model predicts a median $\fagb > 0.3$ and the 98th percentile upper-limits are always below $\fagb=0.4$.
+All models except \aton{} predict that at least $\approx 8$ per cent of solar C comes from AGB stars (from the 2nd percentile lower-limits).
+The SFH and yield scale have little impact on the inferred $\fagb$.
+Across all models considered here, we infer a minority role in AGB C production at solar metallicity.
+
+The right panel of Fig.~\ref{fig:mcmc_ytot} compares the inferred scaling of AGB yields, $\aagb$.
+Given our yield scale, most AGB yield tables naturally produce near the best-fitting amount of AGB C, within a factor of ${\sim}2$.
+\monash{} predicts near the perfect amount of C (but see also discussion in Section~\ref{sec:agb_results}).
+However, if the yield scale is increased \citep[e.g., as advocated in][]{james+24}, the required AGB C production increases accordingly.
+This is illustrated by the `doubled yields' model, which doubles yields and about doubles outflows.
+While $\fagb{}$ remains similar to the \fruity{} model, the ideal $\aagb$ doubles (see discussion in Section~\ref{sec:outflows}).
+
+By including a $\sigma_{\rm sys}$ term, the distributions of $\fagb$, $\aagb$ and CC yield parameters all widen without changing our conclusions.
+Effectively, $\sigma_{\rm sys}$ reduces the weight of abundance differences between bins.
+Systematic uncertainties likely dominate the uncertainty budget in this analysis.
+
+Finally, the choice of the Fe \ia{} DTD directly impacts our conclusions.
+From the right panel of Fig.~\ref{fig:mcmc_ytot}, we note that increasing the SN Ia Fe yield by a factor of 1.2 (and decreasing the CC Fe yield to maintain the same total Fe production) results in a similar increase in the inferred $\fagb$.
+Increasing the SN Ia contribution to Fe stretches the trends in [Mg/Fe], causing [C/Mg] to flatten with [Mg/Fe] unless the delayed C yield is also increased.
+In this framework, constraints on delayed C contributions are limited by our understanding of delayed Fe production.
+
+\begin{figure*}
+    \centering
+    \includegraphics[]{figures/mcmc_y_tot.pdf}
+    \includegraphics[]{figures/mcmc_fagb.pdf}
+
+    \caption[]{
+        \textbf{Left:} The population-averaged yield ratio, $\Yct / \Ymg$, based on our MCMC fits to the [C/Mg]-[Mg/H]-[Mg/Fe] relation. We also show individual samples from the \fruity{} MCMC model.
+        \textbf{Middle:} Posterior distribution of $\fagb$ from MCMC samples for each model.
+We show models without $\sigma_{\rm sys}$ (circles) and with $\sigma_{\rm sys}=0.05$\,dex additional uncertainty (triangles).
+In each case, the thick line is the 16th-94th percentile range and the thin line is the 2nd-98th percentile range.
+\textbf{Right:} Similar to the middle panel except in terms of $\aagb$, the AGB table multiplication factor.
+The vertical line marks $\aagb=1$, corresponding to unscaled yields.
+}
+
+    \label{fig:mcmc_ytot}
+\end{figure*}
 
@@
 \caption[]{
-\dbnote{Should citations be moved outside of caption for reader's sake?}
-\dbnote{Remove connecting lines on MW HII regions. Should I plot outliers at all?}.
 Gas-phase C abundances. 
-We plot the fiducial model's present-day ISM abundances as a thick blue line.
-Black lines are single-zone models: a fiducial yields and MW-like model (solid black), and three corrected yield models representing the MW (dotted), GSE (dashed) and Wukong (dash-dots).
-Points represent measurements in 
-    Milky Way stars \citep[yellow stars;][]{amarsi+19},
-    MW HII regions \citep[orange pentagons][]{mendez-delgado+22, esteban+05, esteban+13}
-    extragalactic RL HII regions \citep[green open diamonds;][]{peimbert+05, skillman+20, toribio-san-cipriano+16, toribio-san-cipriano+17, esteban+14, esteban+09}
-    extragalactic CEL HII regions \citep[green full diamonds;][]{garnett+95, senchyna+17, izotov+thuan99, garnett+99, berg+16, berg+19, pena-guerrero+17}
-    high redshift galaxies \citep[pink squares, CEL lines;][]{steidel+16, stark+14, matthee+21, mainali+20, jones+23, amorin+17, iani+23, james+14, erb+10, bayliss+14, berg+18, christensen+12, arellano-cordova+2022},
-    and
-    damped Lyman-alpha (DLA) systems \citep[rust triangles;][]{omera+01, cooke+14, welsh+22, ellison+10, welsh+20, cooke+18, riemer-sorensen+17, DZ+03, cooke+17, cooke+11, dutta+14, morrison+16, srianand+10, pettini+08, kislitsyn+24, cooke+15}.
-
+We plot the present-day gas-phase abundances predicted by our fiducial model as a thick blue line and the evolution of the $R=8$ kpc zone as a solid black line.
+The black dotted line is a simple, one-zone model for a GSE-like dwarf galaxy.
+Points represent measurements for MW stars (yellow stars), MW \Hii{} regions (RLs, orange pentagons), extragalactic \Hii{} Regions RLs (green empty diamonds), extragalactic \Hii{} regions from CELs (green full diamonds), high redshift galaxies (pink squares), damped Lyman-$\alpha$ systems (orange triangles),  and the low-$\alpha$ APOGEE subgiant sample we used here (purple circles).
+The points with error bars show representative median uncertainties for their associated population.
+Six measurements based on CEL or in DLAs (with large uncertainties) fall above or below the axis limits.
+
+Data for Milky Way stars are from \citet[][]{amarsi+19},
+MW \Hii{} regions from \citet[][]{mendez-delgado+22, esteban+05, esteban+13}, 
+extragalactic RL \Hii{} regions from \citet[][]{peimbert+05, skillman+20, toribio-san-cipriano+16, toribio-san-cipriano+17, esteban+14, esteban+09}, 
+extragalactic CEL \Hii{} regions from \citet[][]{garnett+95, senchyna+17, izotov+thuan99, garnett+99, berg+16, berg+19, pena-guerrero+17}, 
+high redshift galaxies from \citet[][]{steidel+16, stark+14, matthee+21, mainali+20, jones+23, amorin+17, iani+23, james+14, erb+10, bayliss+14, berg+18, christensen+12, arellano-cordova+2022}, and
+DLAs from \citet[][]{omera+01, cooke+14, welsh+22, ellison+10, welsh+20, cooke+18, riemer-sorensen+17, DZ+03, cooke+17, cooke+11, dutta+14, morrison+16, srianand+10, pettini+08, kislitsyn+24, cooke+15}.
 }
@@
 \end{figure*}
-% \begin{table}
-% 	\centering
-%     \caption[]{Single zone model parameters.
-\dbnote{change dwarf parameters to match Wukong from James' dwarf paper.
-$\eta=47.99\pm 5$, $t_{\rm end} = 3.36\pm 0.5$, $\tau_\star=44.97\pm 7$, $\tau_{\rm sfh} = 3.08\pm 1$}}
-% 	\label{tab:singlezone_params}
-% 
-% 	\begin{tabular}{l l l l l}
-% 		\hline
-%         Model & $\eta$ & $t_{\rm end}$ & $\tau_\star$ & $\tau_{\rm sfh}$ \\
-% 		\hline
-%         1 & 0.5 & 13.2 & 2.5 & 14\\
-%         2 & 1 & 10 & 2 & 10\\
-%         3 & 9 & 3 & 5 & 3\\
-% 	\end{tabular}
-% \end{table}
 
@@
 in the gas phase.
-C has also been observed in extragalactic HII regions, high redshift galaxies (HII regions), metal-poor stars, and Damped-Lynman-$\alpha$ systems (DLAs).\footnote{DLAs are gas clouds observed as absorption spectra in front of background quasars}
-While we used Mg as our representative alpha element in our APOGEE sample, O
-is more readily observed in the gas-phase, so we shift focus to C/O in this
-section.
-HII measurements of C are challenging since C lacks strong recombination lines (RL)
- and its collisional excited lines (CEL) fall in the far ultraviolet without nearby reference H lines \citep[][]{skillman+20}.
-Furthermore, CEL and RL derived abundances are systematically discrepent by \about{0.5}\,dex \citep{GR07}.
-Metals may also be trapped in dust grains or in unobserved ionization states, requiring additional modeling \citep{MM19}.
-As a consequence, the uncertainties of HII abundances are substantial (see representative error bars on Fig.~\ref{fig:gas_phase}).
-\dbnote{
-There is a complication I have not done that CEL and RL abundances (especially for O) need to be put on the same scale with +0.2 dex corrections.
-Probably need to double check derivations of metallicities...
-}.
-DLAs, on the other hand, are relatively precise because these regions are lower-ionization, have a well-defined region (column density) and often have high-quality spectra covering rest-frame UV and optical {\color{red} CITE/verify}.
-
-Fig.~\ref{fig:gas_phase} compiles literature measurements of DLAs, HII regions (MW, extragalactic, dwarfs), high redshift galaxies, and MW halo/thick disk stars.
-Despite the inhomogeneities, uncertainties, and variety of systems, there is still a coherent global trend.
-Near solar metallicities, most observations (from disky galaxies) have near-solar [C/O].
-As metallicity decreases, [C/O] also decreases, reaching a minimum of $\approx-0.6$ around ${\rm [O/H] \approx -1}$.
-Finally, [C/O] appears to increase again at the lowest metallicities observed (${\rm [M/H] \lesssim -2}$).
-
-Fig.~\ref{fig:gas_phase} also shows the present-day gas phase abundance of our fiducial model and several single-zone models.
-The gas phase predictions of our multizone model agree reasonably with MW (and similar metallicity extragalactic) HII regions.
-Stellar abundance remain, comparatively, a more stringent constraint.
-To better represent the evolution of low-metallicity and dwarf galaxy environments, we create an illustrative suite of single-zone models.
-These models evolve only a single, homogenous gas supply.
-We assume a constant star formation efficiency $\dot M_\star = M_{\rm gas} / \tau_\star$.
-We also use an exponential infall history for dwarf galaxies of the form
-\begin{equation}
-    \dot\Sigma_{\rm in} \sim e^{-t/\tau_{\rm sfh}}.
-\end{equation}
-Yields are set to the best-fit analytic AGB model, but low metallicity evolution is predominantly driven by the choice of CCSNe C yields.
-We introduce an alternate CCSNe model to better agree with these low-$Z$ observations.
-\begin{equation} 
-    \Ycc / 10^{-3} = \begin{cases}
-        0.8 & \log Z / \Zo < {\rm number} \\
-        1.99 + 1.68\, \log Z / \Zo & {\rm otherwise }
-    \end{cases}
-\end{equation}
-where the low-metallicity limit was chosen to match the approximate minimum of observed [C/O] values.
-The models shown in Fig.~\ref{fig:gas_phase} have the parameters: 
-\begin{enumerate}
-    \item Fiducial MW. Solid black line. $\eta=0.5$, $t_{\rm end} = 13.2$, $\tau_\star=2$, $\tau_{\rm sfh} = 14$, insideout SFH.
-    \item Corrected MW-like. Dotted. Same parameters as  fiducial single-zone but with corrected yields.
-    \item Corrected Gaia-Sausage Enceledus like. Dashed. $\eta=5.74$, $t_{\rm end}=10.73$, $\tau_\star = 26.60$, $\tau_{\rm sfh} = 2.18$, infall mode
-    \item Corrected Wukong-like. Dash-doted. $\eta=28.8$, $t_{\rm end} = 3.36$, $\tau_\star=44.97$, $\tau_{\rm sfh} = 3.08$, infall mode
-\end{enumerate}
-\dbnote{check timescales to metallicity = -1 (could sagb affect the trends here?). Also try different yield sets for these just to see if any agree naturally... }
-
-When comparing the MW-like single-zone model to the fiducial final gas-phase abundances, notice that the slope of the singlezone track near solar metallicities is steeper. 
-While the trend in the multi-zone models arises as a
-superposition of end-points, the single-zone trend instead arises as an evolutionary sequence (see Fig.~\ref{fig:c_evo}).
-The increase in [C/O] abundances is a result of both delayed AGB contribution and the metallicity-dependent C CCSNe yields.
-The halo and thick disk stars also support that the past [C/O] abundances were increasing with metallicity, in contrast to the near-constant [C/O] of the low-$\alpha$ sequence.
-The initial [C/O] value of these single-zone mdoel is governed by the respective ratio of C to O yields.
-As a result, the fiducial yield set predicts too high of a minimum [C/O], motivating our corrected yields.
-With the corrected yield set, the single-zone models are able to reproduce the general trend of [C/O] with metallicity.
-An alternative explanation is that more C comes from delayed sources than is predicted by our fiducial model.
-However, reaching the [C/O] minimum of -0.6 requires that \about{75\%} of C comes from AGB stars, which is not reconcilable with the stellar \caafe\ trend.
-
-SFH variations likely explain part of the observed scatter in Fig.~\ref{fig:gas_phase}. 
-In our models, variations in the SFHs change when [C/O] begins to increase with metallicity and the final [C/O] value of the model.
-Similar to [O/Fe] trends with metallicity, the slower and burstier SFH of dwarf galaxies causes delayed sources to affect abundance ratios at a lower metallicity than for MW-like systems.
-
-Our single-zone models do not capture the elevated [C/O] ratio at the lowest metallicities.
-This could be remedied by modifying our CCSNe yield, but low-metallicity C abundances are beyond our scope.
-Additionally, inhomogeneous mixing and individual contributions from supernovae become important in this regime, adding additional scatter and complexity to modelling.
-\dbnote{Are CEMPs worth mentioning here? since they have enough literature although not necessarily relavent here. Carigi+Peimbert 2011, Molla+2015.}
-
-Altogether, our yields (with some adjustments) are able to reproduce the global C trend from dwarf galaxies to solar metallicity MW-like galaxies.
+We consider measurements in Galactic and extragalactic \Hii{} regions, Damped Lyman-$\alpha$ systems\footnote{DLAs are gas clouds observed as absorption spectra in front of background quasars}, and Milky Way halo main-sequence stars.
+While we used Mg as our representative alpha element in our APOGEE sample, we shift focus to O in this Section because O is more readily observed in the gas phase.
+C abundances are challenging to measure in \Hii{} regions because C lacks strong recombination lines (RL),  and its collisionally excited lines (CEL) fall in the far ultraviolet without nearby reference H lines \citep[][]{skillman+20}.
+%Furthermore, CEL and RL derived abundances are systematically discrepant by \about{0.5}\,dex \citep{GR07}.
+Metals may also be trapped in dust grains or in unobserved ionization states, requiring model-dependent corrections \citep[e.g.,][]{MM19}.
+We will see below that, despite these challenges, a global trend in [C/O] with metallicity nevertheless emerges.
+ % DLAs, on the other hand, are relatively precise because these regions are lower-ionization, have a well-defined region (column density), and often have high-quality spectra covering rest-frame UV and optical {\color{red} CITE/verify}.
+
+Fig.~\ref{fig:gas_phase} compiles literature measurements of [C/O].
+The \Hii{} regions span a wide range of host galaxies: from the Milky Way and nearby spiral galaxies, to blue compact dwarf galaxies, to high-redshift star-forming and dwarf galaxies.
+We also include a sample of thick disk and halo stars for reference.
+Near solar metallicity, most measurements have ${\rm [C/O]} \approx 0$.
+Below solar metallicity, [C/O] appears to follow a non-monotonic trend, reaching a minimum of $\co  \approx -0.6$ around $\oh \approx -1$, and possibly increasing again at the very lowest metallicities.
+
+To better represent the evolution of low-metallicity and dwarf galaxy environments, we construct an example {\it Gaia}-Sausage Enceladus (GSE, \citealt{meza+05, belokurov+18, helmi18}) --like model.
+This model is a single-zone model,  evolving one homogeneous gas supply.
+We use the same yields as our fiducial multi-zone model.
+Our GSE-like model has a constant mass loading of $\eta=5.74$, total star formation time of 10.73 Gyr, a constant star formation efficiency time-scales of 26.60 Gyr, and an exponential infall history $\dot \Sigma_{\rm in} = \exp(-t / 2.18\,{\rm Gyr})$ (in contrast to star formation rate specification for our fiducial model).
+In summary, the GSE-like model compared to our fiducial MW model does not include radial migration and has a more rapid star formation history, elevated outflows, and lower star formation efficiency.
+
+The gas-phase C abundances reveal a breakdown of our fiducial yield prescription.
+While the fiducial model sits well within the scatter of C/O ratios observed in near-solar (low-redshift) \Hii{} regions, the evolution of the solar zone only agrees with the highest measurements of [C/O] at lower metallicities ${\rm [O/H]} \sim -1$.
+The CCSN-only, low-metallicity plateau of [C/O] in the fiducial model is $\approx -0.5$.
+No value of [C/O] below about -0.5 would be consistent with this model.
+Furthermore, our GSE-like model consistently predicts higher [C/O] abundances.
+Because the star formation efficiency is much lower in this model, the contribution due to delayed enrichment will appear at lower metallicities.
+As a result, even at ${\rm [O/H]} \sim -1.5$, delayed C enrichment appears, raising the [C/O] ratio above most observations.
+This model is a relatively poor fit to the gas-phase data.
+We note that our subgiant sample only extends as low as a metallicity of ${\rm [O/H]} \sim -0.4$, so any application of the model to gas-phase requires substantial extrapolation.
+Our best-fitting yield models (to subgiants) prefer lower $\fagb{}$ and consequently higher low-metallicity [C/O] plateaus, worsening agreement.
+
+One possible remedy would be to decrease our assumed minimum CCSN yield $y_{\rm low}$, bringing the low-metallicity plateau into better agreement with observations.
+A lower $y_{\rm low}$ also requires a higher $\fagb{}$ to reach the observed [C/Mg] near solar metallicity.
+A slightly higher value of $\fagb{}$ will lower the low-metallicity plateau into better agreement with observations.
+However, a high $\fagb{}$ model would be in tension with the subgiant abundance trends.
+Such a model should produce stars with [C/O] near the plateau value in the early enrichment history of the Milky Way, observed as very low C but high-$\alpha$ stars (see evolution tracks in Fig.~\ref{fig:c_evo} and related models from Fig.~\ref{fig:zeta_f}).
+Because there are no subgiants with [C/Mg] abundances below \about{-0.4}, it is unlikely a high $\fagb{}$ model reconciles the gas-phase and stellar abundance trends.
+But, if C production is much more delayed than current AGB models predict, [C/Mg] may remain lower for longer than for our fiducial yields.
+
+Another possibility is that the massive star production of C (or O) exhibits a complex metallicity dependence.
+The increasing [C/O] abundances at the very lowest metallicities as observed in DLAs already hint at a more nuanced C nucleosynthetic landscape.
+Given the abundance trends observed in Fig.~\ref{fig:gas_phase}, we propose the following possibility for C production.
+(1) At the very lowest metallicities, massive stars may produce copious amounts of C through rotation, alternative IMF, or differing supernova mechanisms.
+%(Umeda & Nomoto 2003, 2005; Chieffi
+%& Limongi 2004; Iwamoto et al. 2005; Meynet et al. 2006,
+%2010; Nomoto et al. 2006; Tominaga et al. 2007, 2014;
+%Heger & Woosley 2010; Limongi & Chieffi 2012; Ishigaki
+%et al. 2014; Choplin et al. 2016; Salvadori et al. 2016;
+%Kobayashi et al. 2020).
+This would now be observed as CEMP-no stars \citep[e.g., review and references in][]{FN15} and the elevated C abundances of DLAs.
+(2) C production sharply drops as metallicity increases, reaching a minimum between [O/H] of -3 and -1.5.
+Stars and (dwarf) galaxies with the lowest C/O ratios would be formed in this stage.
+(3) As metallicity increases, massive star C yields steeply increase.
+In addition, C production from delayed AGB stars becomes more and more important, accelerating an increase of C abundances relative to O on approach to solar metallicity.
+(4) Finally, in the regime of our own galaxy, the rapid increase of CCSN production of C may temper, procuring the gently sloping trend apparent in subgiants today.
+
+\citet{berg+19} consider an alternative scenario for the chemical evolution of C in dwarf galaxies.
+Their models include initially high C/O ratios from Population III stars, which decline with metallicity due to Population II enrichment.
+Later, in a bursty star formation history, [C/O]-[O/H] follows a "zig-zag" pattern due to alternating periods of \cc{} and \agb{} dominated nucleosynthetic enrichment (see their figure 11).
+Scatter in C/O then arises from a combination of varying star formation histories and changing effective oxygen yields (i.e., different supernova entrainment factors).
 
@@
 
-Building on~\citet{james+23}, we quantify the impact of C yield assumptions on Milky Way GCE models.
-We use \citepos{jack} sample of APOGEE subgiants as our primary observational benchmark, as subgiant atmospheres most likely reflect their birth C abundances (see discussion in section~\ref{sec:data_selection}).
-In our fiducial model, C initially increases following the slope of the \cc\ C dependence.
-Later, AGB contributions from C cause a sharp rise in \caah, which slows down due to declining AGB C production and the approach towards equilibrium.
-The chemical elemental reach a quasi-equilibrium within \about{5}\,Gyr.
-As a result, the current C/Mg versus metallicity gradient is a superposition of equilibrium states, mixed together from different Galactic positions.
-
-The slope of the predicted \caah\ relation is principally sensitive to the collective metallicity dependence of \cc\ C yields.
-While AGB yields are predicted to decline with metallicity, out models show that \cc\ dominate the trend and make an overall positive metallicity trend. 
-As the strength of the \cc\ metallicity dependence increases, the slope of the \caah\ trend correspondingly increases.
-The small effects of \agb\ C yield on the \caah\ trend can be easily corrected by small adjustments of the \cc\ yield's metallicity dependence.
-Our predicted slope of $\zetaibest$ is qualitatively consistent with the \citet{LC18} rotating stellar models, however no simulation contains sufficient mass resolution or accuracy to reproduce the observed trends accurately.
-
-Because massive star enrichment dominates the C mass budget in our models, the predictions are relatively insensitive to the choice of AGB star yield model.
-All the \agb\ tables tested here predict similar abundance trends in [C/Mg] with [Mg/H] and [Fe/Mg].
-
-As in~\citet{james+23}, we have constrained yield ratios as opposed to absolute yields.
-For example, scaling yields and outflows by a corresponding factor leaves abundance ratio trends unchanged (Fig.~\ref{fig:sims_degens}).
-Effects such as black hole formation could create systematic shifts on predicted chemical yields.
-Variations in the SFH instead only induce minor systematic shifts to the predictions.
-However, uncertanties in which AGB stars produce C and the production and DTD of Fe introduce large systematic uncertanties.
-
-When combined with~\citeauthor{james+23}'s~\citeyearpar{james+23} empirically calibrated N yields, we find that our fiducial model accurately describes the [C/N]-[Mg/H] relation in our sample.
-
-Finally, we compare our models againsts a compilation of literature gas-phase and halo-star abundances (see Fig.~\ref{fig:gas_phase}).
-Our fiducial model fails to explain the lowest values of [C/O] at metallicities of $[O/H] = -1$ to $-2$.
-We briefly consider a modified variation of the CCSNe yield of C which drops to explain these values, which maintains trends consistant with APOGEE.
-
-Our results demonstrate the power of empirically calibrated stellar yields.
-In our GCE models, trends in abundance ratios with metallicity are largely determined by trends in yield ratios with metallicity.
-As a result, the metallicity dependence of the total, population-averaged C yield is tightly constrained by the [C/Mg]-[Mg/H] relation, but the metallicity dependencies of the individual contributions from CCSNe and AGB stars are less precisely determined.
-Due to the sensitivity of elemental yields to poorly understood processes, such as mass-loss rates and convection, our results provide a useful benchmark for stellar evolution models~\citep[see the discussion in e.g.][]{gil-pons+2022}.
-With abundance measurements for several million stars provided by upcoming spectroscopic surveys, particularly SDSS-V's Milky Way Mapper program~\citep{sdssv}, constraints on both stellar nucleosynthesis and the assembly history of our Galaxy will become increasingly more powerful.
-Observing C across a pleothora of environments at higher precision will allow for yet more detailed understanding of C nucleosynthesis, creating yet more stringent tests for stellar evolution theory.
+Building on the constraints on N production by \citet{james+23}, we quantify the impact of C yield assumptions on Milky Way GCE models.
+We use \citepos{jack} sample of APOGEE subgiants as our primary observational benchmark, as subgiant atmospheres best reflect their birth C abundances among spectral types (see discussion in Section~\ref{sec:data_selection}).
+In our fiducial model, the evolution of [C/Mg] initially increases with time due to the metallicity-dependent C yields from massive stars.
+Later, AGB stars contribute additional C, causing a sharp rise in C with metallicity.
+However, the chemical history is only indirectly related to the stellar abundance trends.
+
+The \caah{} relation in low-$\alpha$ stars arises as a superposition of the endpoints of evolutionary sequences traced out by different Galactic regions (see Fig.~\ref{fig:c_evo}).
+As a result, the \caah{} trend is most strongly tied to the total C yield (relative to Mg) at each metallicity [Mg/H].
+Because all AGB yield tables we consider here predict a declining C yield with increasing metallicity, the \caah{} trend implies that the CCSN yield must increase with metallicity.
+This could be due to the heightened metallicity-dependent mass-loss in the rotating models of \citet{LC18}.
+The C versus [Mg/H] relation alone, however, is unable to provide substantial information on the delayed relative to prompt production of C from massive or low-intermediate mass stars.
+On the other hand, the \caafe{} relation, at a given metallicity, is most sensitive to the amount of delayed, AGB C production.
+In addition, the shape of the [C/Mg] abundance trend with [Mg/Fe] can constrain the nature of the DTD of C.
+
+From the combined constraints of the [C/Mg] trend with metallicity and [$\alpha$/Fe], we have inferred possible observationally-consistent combinations of yields.
+In all cases, we find that $\Yct / \Ymg \approx 4.2 \pm 0.2$ at solar metallicity, with total C production increasing with increasing metallicity.
+We also show that low-intermediate mass AGB stars likely produce a fraction of between 0.10 and 0.40 of solar C, across GCE assumptions and AGB yield tables.
+
+Given our yield scale, we find most AGB yield tables are within ${\sim}2$ times the inferred AGB C production.
+We find that the best-fitting models require between about 0.6 and 2 times more C than predicted by the AGB table.
+However, if the yield scale is higher than ours, the AGB C yield should be similarly amplified.
+
+As a consequence of massive star enrichment dominating the C production in our models, our conclusions are relatively insensitive to the choice of AGB yield model.
+Of the yield tables tested here, \fruity{} and \nugrid{} better describe \caafe{} trend, as the production of C is too rapid from \monash{} and \aton{} near solar metallicity.
+However, all AGB yield tables predict a \caafe{} relation that is concave down, while the observed relation is linear.
+Based on this discrepancy, C may be more efficiently produced in lower mass AGB stars than predicted by stellar models (see Fig.~\ref{fig:sims_degens}), which would increase characteristic delay times and linearize the \caafe{} trend.
+This discrepancy could also be resolved by a less extended DTD for SN Ia.
+
+Comparing our models with measurements of C abundances in the gas phase available in the literature reveals a potential shortcoming of our C yield prescription in the ${\rm [O/H]} \lesssim -1$ regime.
+\Hii{} regions at these metallicities typically have $\co \approx -0.6$ but with substantial scatter (see Fig.~\ref{fig:gas_phase}).
+Our models predict $\co \approx -0.5$ at low metallicity, struggling to explain the lowest [C/O] measurements.
+Dwarf galaxy GCE models tuned to GSE fare even worse, indicating that different galactic environments are not responsible for the difference.
+Instead, either a larger AGB contribution to C is required, disfavoured by the subgiant trends, or a complex, non-monotonic massive-star production of C is needed.
+
+As in \citet{james+23}, our models constrain relative as opposed to absolute yields due to the degeneracy between the overall scale and the strength of outflows \citep[e.g.,][]{hartwick1976,james+23, sandford+24}.
+Rescaling both parameters by similar multiplicative factors leaves the predicted \caah{} relation largely unchanged to first order (see Fig.~\ref{fig:sims_degens}).
+Breaking this degeneracy requires either age measurements to pin down enrichment time-scales \citep{james+24}, chemical species produced during Big Bang Nucleosynthesis present in accreting gas \citep{cooke+2022}, or independent constraints from observations of SN \citep[e.g.,][]{rodriguez+23,david_fe}.
+However, our constraints on the ratio of C/Mg yields, its metallicity dependence, and the AGB contribution to C are robust, as we only consider C through yield ratios.
+
+As we constrain the yield ratio, variations in the Mg yield may help explain the [C/Mg] trends.
+While we focus on variations on the C yield alone, our constraint is nevertheless on the C/Mg yield ratio.
+$\alpha$-elements like Mg and O, produced primarily in CCSN, are typically expected and observed to have mostly metallicity-independent yields \citep[e.g.,][]{weinberg+19}.
+Although, the details of the origin of the metallicity dependence of C and Mg remain uncertain.
+
+While we focus on median trends, the scatter of the trends may include additional information about C production.
+We find that our model predicts a similar scatter as observed in subgiants in the \caafe{} and \caah{} trends (not shown).
+Further investigation into the detailed distribution of C abundance ratios with metallicity and $[\alpha/{\rm Fe}]$ may reveal more information about the origin of the elements.
+
+Our results in this paper demonstrate the utility of empirically calibrated stellar yields.
+Due to the sensitivity of nucleosynthetic yields to poorly understood stellar evolution processes, such as mass loss and convection, these results provide a useful benchmark for stellar models (see discussion in, e.g., \citealt{gil-pons+2022}).
+With larger samples and more reliable abundance measurements from upcoming spectroscopic surveys, such as SDSS-V's Milky Way Mapper program \citep{kollmeier+25}, our understanding of metal production and the assembly history of our Galaxy will sharpen.
+Observing C across a range of environments at higher precision will allow for yet more detailed understanding of C nucleosynthesis, creating stringent tests for stellar evolution theory and refining our understanding of the chemical evolution of the Universe.
 
 \section*{Acknowledgements}
+This paper uses \apogee\ data \citep{apogee_instrumentation, apogee17, aspcap}. \apogee{} is  part of SDSS-IV \citep{sloan_telescope, sdss_iv_overview, sdss17}.
 
@@
 
-\apogee\ is part of SDSS-IV \citep{sloan_telescope, apogee_instrumentation, sdss_iv_overview, sdss17, apogee17, aspcap}.
-
-Funding for the Sloan Digital Sky 
-Survey IV has been provided by the 
-Alfred P. Sloan Foundation, the U.S. 
-Department of Energy Office of 
-Science, and the Participating 
-Institutions.
-
-SDSS-IV acknowledges support and 
-resources from the Center for High 
-Performance Computing  at the 
-University of Utah. The SDSS 
-website is www.sdss4.org.
-
-SDSS-IV is managed by the 
-Astrophysical Research Consortium 
-for the Participating Institutions 
-of the SDSS Collaboration including 
-the Brazilian Participation Group, 
-the Carnegie Institution for Science, 
-Carnegie Mellon University, Center for 
-Astrophysics | Harvard \& 
-Smithsonian, the Chilean Participation 
-Group, the French Participation Group, 
-Instituto de Astrof\'isica de 
-Canarias, The Johns Hopkins 
-University, Kavli Institute for the 
-Physics and Mathematics of the 
-Universe (IPMU) / University of 
-Tokyo, the Korean Participation Group, 
-Lawrence Berkeley National Laboratory, 
-Leibniz Institut f\"ur Astrophysik 
-Potsdam (AIP),  Max-Planck-Institut 
-f\"ur Astronomie (MPIA Heidelberg), 
-Max-Planck-Institut f\"ur 
-Astrophysik (MPA Garching), 
-Max-Planck-Institut f\"ur 
-Extraterrestrische Physik (MPE), 
-National Astronomical Observatories of 
-China, New Mexico State University, 
-New York University, University of 
-Notre Dame, Observat\'ario 
-Nacional / MCTI, The Ohio State 
-University, Pennsylvania State 
-University, Shanghai 
-Astronomical Observatory, United 
-Kingdom Participation Group, 
-Universidad Nacional Aut\'onoma 
-de M\'exico, University of Arizona, 
-University of Colorado Boulder, 
-University of Oxford, University of 
-Portsmouth, University of Utah, 
-University of Virginia, University 
-of Washington, University of 
-Wisconsin, Vanderbilt University, 
-and Yale University.
-
-\dbnote{do I need acknowledgments for appendix spectro-surveys?}
+% Funding for the Sloan Digital Sky 
+% Survey IV has been provided by the 
+% Alfred P. Sloan Foundation, the U.S. 
+% Department of Energy Office of 
+% Science, and the Participating 
+% Institutions. 
+% 
+% SDSS-IV acknowledges support and 
+% resources from the Center for High 
+% Performance Computing  at the 
+% University of Utah. The SDSS 
+% website is www.sdss4.org.
+% 
+% SDSS-IV is managed by the 
+% Astrophysical Research Consortium 
+% for the Participating Institutions 
+% of the SDSS Collaboration including 
+% the Brazilian Participation Group, 
+% the Carnegie Institution for Science, 
+% Carnegie Mellon University, Center for 
+% Astrophysics | Harvard \& 
+% Smithsonian, the Chilean Participation 
+% Group, the French Participation Group, 
+% Instituto de Astrof\'isica de 
+% Canarias, The Johns Hopkins 
+% University, Kavli Institute for the 
+% Physics and Mathematics of the 
+% Universe (IPMU) / University of 
+% Tokyo, the Korean Participation Group, 
+% Lawrence Berkeley National Laboratory, 
+% Leibniz Institut f\"ur Astrophysik 
+% Potsdam (AIP),  Max-Planck-Institut 
+% f\"ur Astronomie (MPIA Heidelberg), 
+% Max-Planck-Institut f\"ur 
+% Astrophysik (MPA Garching), 
+% Max-Planck-Institut f\"ur 
+% Extraterrestrische Physik (MPE), 
+% National Astronomical Observatories of 
+% China, New Mexico State University, 
+% New York University, University of 
+% Notre Dame, Observat\'ario 
+% Nacional / MCTI, The Ohio State 
+% University, Pennsylvania State 
+% University, Shanghai 
+% Astronomical Observatory, United 
+% Kingdom Participation Group, 
+% Universidad Nacional Aut\'onoma 
+% de M\'exico, University of Arizona, 
+% University of Colorado Boulder, 
+% University of Oxford, University of 
+% Portsmouth, University of Utah, 
+% University of Virginia, University 
+% of Washington, University of 
+% Wisconsin, Vanderbilt University, 
+% and Yale University.
 
@@
 
-\dbadd{data and codes used in this paper are all publicly available. (do i need links here?). }
+Data and code used in this paper are happily available upon request.
 
@@
 	\centering
-        \caption[]{Description of the models presented in this paper. \dbnote{Names are slightly inconsistent, will update with next draft.}}
+        \caption[]{Description of the yields used for models presented in this paper.}
 	\label{tab:model_parameters}
 
-	\begin{tabular}{l l l l l l l l l l}
+	\begin{tabular}{l l l l l l l l l}
 		\hline
-            name & $\alpha_{\rm C}^{\rm AGB}$ & $Y_{\rm C}^{\rm AGB}$ & $\zeta_0$ & $\zeta_1$ & $\zeta_2$ \\ 
+            name & $\aagb$ & $\ycagb$ & $\yo/10^{-4}$ & $\zcc/10^{-4}$ \\ 
             \hline
-            FRUITY (fiducial) & 2.40 & fruity & 1.90 & 2.27 & 2.58 \\
-            Monash & 2.06 & monash & 2.03 & 3.82 & 3.48 \\
-            ATON & 1.71 & aton & 2.55 & 3.19 & 1.92 \\
-            NuGRID & 1.21 & nugrid & 1.58 & 1.58 & 3.16 \\
-            $\zetai=0.001$ & 2.40 & fruity & 1.90 & 3.0 & 2.58 \\
-            $\zetai=0.003$ & 2.40 & fruity & 1.90 & 1.0 & 2.58 \\
-            $\fagb=0.1$ & 0.754 & fruity & 2.51 & 2.27 & 2.58  \\
-            $\fagb=0.5$ & 3.77 & fruity & 1.40 & 2.27 & 2.58 \\
-            lower $\fagb$, $\zetai$ & 0.754 & fruity & 2.51 & 1.75 & 2.58  \\
-            higher $\fagb$, $\zetai$ & 3.77 & fruity & 1.40 & 2.75 & 2.58 \\
-            m0.5 & 2.69 & fruity(m/0.5)  & 2.21 & 1.13 & 2.45 \\
-            m0.7 & 2.11 & fruity(m/0.7) & 1.98 & 1.66 & 3.01 \\
-            m1.5 & 2.60 & fruity(m/1.5) & 1.89 & 1.83 & 1.66 \\
-            m0.7 best & 1.39 & fruity(m/0.7) & 2.25 & 1.55 & 2.54 \\
+            fiducial & 2.57 & fruity & 18.7 & 7.9 \\
+            $\zcc=0.0004$ & 2.57 & fruity & 18.7 & 4.0 \\
+            $\zcc=0.0012$ & 2.57 & fruity & 18.7 & 11.9 \\
+            $\fagb = 0$ & 0.0 & fruity & 27.1 & 7.9 \\
+            $\fagb = 0.5$ & 4.36 & fruity & 13.3 & 7.9 \\
+            lower $\fagb$, $\zcc$ & 0 & fruity & 27.9 & 4.1 \\
+            higher $\fagb$, $\zcc$ & 4.36 & fruity & 12.1 & 12.1 \\
+            \fruity{} & 1.55 & fruity & 22.3 & 7.2 \\
+            \aton{} & 1.07 & aton & 26.2 &  11.3 \\
+            \monash{} & 1.12 & monash & 23.7 & 10.9 \\
+            \nugrid{} & 0.59 & nugrid & 22.3 & 4.5 \\
+            \fruity{} shifted & 1.29 & fruity(m/0.7) & 23.3 & 4.6 \\
+            mass shift 0.5 & 2.98 & fruity(m/0.5)  & 22.1 & 14.5 \\
+            mass shift 0.7 & 2.34 & fruity(m/0.7) & 19.7 & 3.2 \\
+            mass shift 1.5 & 2.71 & fruity(m/1.5) & 18.6 & 8.5 \\
 		\hline
@@
 
-\dbnote{this is not actually used in the current draft, only for scatter plots of model stars}.
 For our added scatter, we use the polynomial fits to the reported internal APOGEE error with metallicity.
-In detail, these polynomials should also very with logg, teff, however as all of our stars are subgiants, these effects should be smaller.
-We also use $x={\rm [Fe/H]}$ for brevety.
+In detail, these polynomials should also vary with surface gravity and effective temperature.
+However, as all of our stars are subgiants, these effects should be smaller.
+We also use $x={\rm [Fe/H]}$ for brevity.
 \begin{subequations}
+\label{eq:uncertainties}
 \begin{align}
-    \delta {\rm [Mg/H]} &= 0.0652 x^2 + 0.00522 x + 0.0338 \\
-    \delta {\rm [Mg/Fe]} &= 0.00793 x^2 - 0.00802 x + 0.0138 \\
-    \delta {\rm [C/Mg]} &= -0.0378x + 0.03506 
+    \delta {\rm [Mg/H]} &= 0.0652\,x^2 + 0.00522\,x + 0.0338 \\
+    \delta {\rm [Mg/Fe]} &= 0.00793\,x^2 - 0.00802\,x + 0.0138 \\
+    \delta {\rm [C/Mg]} &= -0.0378\,x + 0.03506 
 \end{align}
@@
 
-\section{NuGrid Yield Tables} \label{sec:nugrid_yields}
-In this section, we present updated calculations of the \citep{battino+19, battino+21} yield tables and describe their incorperation into VICE.
-
-\citep{battino+19, battino+21} update the \citep{ritter+18} yield models with new reaction rates and increased mixing.
+\section{NuGrid yield tables} \label{sec:nugrid_yields}
+In this Section, we present updated calculations of the \citet{battino+19, battino+21} yield tables and describe their incorporation into \VICE.
+These models use the NuGrid MPPNP post-processing toolkit on models run through {\rm mesa} stellar evolution.
+
+\citet{battino+19, battino+21} update the \citet{ritter+18} yield models with new reaction rates and increased mixing.
 These changes allow for better production of {\it s}--process isotopes in their AGB stars, and are recommended for the masses they update.
-However, between these models, the only updates are for masses M=2,3 at metallicities Z=0.01, 0.02, 0.001, 0.002.
-
-Because the yield tables included in \citep{battino+19, battino+21} are inconsistent with the \citet{ritter+18} definitions of yields, we recalculate these yields from the publically available data on \url{https://astrohub.uvic.ca}.
+However, between these models, the only updates are for masses 2 and $3\,\Mo$ at metallicities $Z=0.01, 0.02, 0.001, 0.002$.
+
+Because the yield tables included in \citep{battino+19, battino+21} are inconsistent with the \citet{ritter+18} definitions of yields, we recalculate these yields from the publicly available data on \url{https://astrohub.uvic.ca}.
 
@@
 where $Z_{X, \rm surf}$ is the surface abundance of $X$, $\dot m$ is the mass loss rate, and the integral is taken over the entire evolution. 
-One complication is that MESA stops before the end of the AGB phase due to instabilities during the transition to the planetary nebulae. 
-As a result, the practical calculation is 
+One complication is that {\sc mesa} stellar evolution stops before the end of the AGB phase due to instabilities during the transition to the planetary nebulae. 
+As a result, the practical calculation is to combine both the ejected surface mass at each time step and the remaining mass not yet ejected:  
 \begin{subequations}
@@
 \end{subequations}
-where $m_{\rm end}$ and $Z_{X, \rm surf, end}$ are the final mass and surface abundance of $X$ at the end of MESA evolution, $m_{\rm rem}$ is the mass remaining in the star at the end of MESA evolution, and the sum is taken over all timesteps in the MESA output.
-We use the final H-free mass as the reminant mass.
-
-We use the \citet{ritter+18} tables from $M_{X, \rm ej}$, which we can reproduce from the same methods as above.
-Finally, the $p_{X}$ yields are calculated from $M_{\rm X, ej}$ with Eq.~\ref{eq:stellar_yield_def}.
+where $m_{\rm end}$ and $Z_{X, \rm surf, end}$ are the final mass and surface abundance of $X$ at the end of {\sc mesa} evolution, $m_{\rm rem}$ is the mass remaining in the star at the end of {\sc mesa} evolution, and the sum is taken over all time steps in the {\sc mesa} output.
+We use the final H-free mass as the remnant mass.
+
+We use the \citet{ritter+18} tables from $M_{X, \rm ej}$, which we can reproduce from the same methods as above. Finally, the $p_{X}$ yields are calculated from $M_{\rm X, ej}$.
+
+\section{MCMC additional results}
+
+Fig.~\ref{fig:mcmc} shows the distribution and correlation of each parameter in our MCMC model fit to the C yields described in Section~\ref{sec:nucleosynthesis}, assuming the \fruity{} AGB table.
+Each parameter is relatively well-constrained.
+The most prominent correlation, between $\yl$ and $\aagb$, represents the constraint on the equilibrium abundance of C near solar.
+Another clear correlation, between $\yl$ and $\zcc$, is related to the solar yield constraint as well, allowing a narrow range of $\zcc$ values while retaining the solar $\yo = \yl + \zcc$ yield.
+
+Table~\ref{tab:mcmc_results} contains the resulting posterior distributions for each parameter for each AGB model and GCE parameter choice discussed here.
+
+\begin{table*}
+    \caption{
+        Best-fit parameters (medians and 16-84th percentile ranges) from MCMC analysis for various models discussed.
+        The columns are:  the model name, best-fitting log posterior probability $\log p$, AGB scaling $\aagb$, CCSN low-metallicity yield $\yl$, the CCSN yield slope $\zcc$, the AGB fraction $\fagb$, and the total C yield at solar metallicity $\Yct$.
+    }
+    \label{tab:mcmc_results}
+
+{ 
+\renewcommand{\baselinestretch}{1.2}
+    \begin{tabular}{l l l l l l l l l l l} 
+    \hline
+    model            %& $\chi2$  
+    & $\log p$ & $\aagb$ & $\yl/10^{-4}$ & $\zcc/10^{-4}$ &  $\fagb$ & $\Yct/10^{-4}$\\    %
+\hline
+\fruity          &  -506.85 & $1.56^{+0.04}_{-0.04}$  &  $15.1^{+0.2}_{-0.2}$  &  $7.2^{+0.1}_{-0.1}$  &  $0.18^{+0.00}_{-0.00}$  &  $27.1^{+0.0}_{-0.0}$\\ 
+\aton            &  -492.15 & $1.07^{+0.03}_{-0.03}$  &  $14.9^{+0.2}_{-0.2}$  &  $11.3^{+0.2}_{-0.2}$  &  $-0.00^{+0.00}_{-0.00}$  &  $26.2^{+0.1}_{-0.1}$\\ 
+\monash          &  -768.25 & $1.12^{+0.04}_{-0.04}$  &  $12.8^{+0.3}_{-0.3}$  &  $10.8^{+0.2}_{-0.2}$  &  $0.12^{+0.00}_{-0.00}$  &  $27.0^{+0.0}_{-0.0}$\\ 
+\nugrid          &  -716.22 & $0.59^{+0.02}_{-0.02}$  &  $17.8^{+0.1}_{-0.1}$  &  $4.5^{+0.1}_{-0.1}$  &  $0.20^{+0.01}_{-0.01}$  &  $27.8^{+0.0}_{-0.0}$\\ 
+\fruity\ shifted    &  {\bf -298.11} & $1.29^{+0.03}_{-0.03}$  &  $18.7^{+0.1}_{-0.1}$  &  $4.6^{+0.1}_{-0.1}$  &  $0.17^{+0.00}_{-0.00}$  &  $28.0^{+0.0}_{-0.0}$\\ 
+doubled yields (and $\eta$) &  -492.95 & $1.53^{+0.04}_{-0.04}$  &  $15.3^{+0.2}_{-0.2}$  &  $7.0^{+0.1}_{-0.1}$  &  $0.18^{+0.00}_{-0.00}$  &  $27.1^{+0.0}_{-0.0}$\\ 
+lateburst        &  -453.73 & $1.90^{+0.05}_{-0.05}$  &  $14.5^{+0.2}_{-0.2}$  &  $6.5^{+0.1}_{-0.1}$  &  $0.22^{+0.01}_{-0.01}$  &  $26.9^{+0.0}_{-0.0}$\\ 
+twoinfall        &  -497.75 & $1.55^{+0.03}_{-0.03}$  &  $15.5^{+0.1}_{-0.1}$  &  $6.9^{+0.1}_{-0.1}$  &  $0.18^{+0.00}_{-0.00}$  &  $27.2^{+0.0}_{-0.0}$\\ 
+higher SN Ia       &  -482.67 & $2.15^{+0.04}_{-0.04}$  &  $11.4^{+0.2}_{-0.2}$  &  $8.4^{+0.1}_{-0.1}$  &  $0.25^{+0.01}_{-0.01}$  &  $26.5^{+0.0}_{-0.0}$\\ 
+\hline
+{\bf including $\sigma_{\rm sys}$}: \\
+\fruity          &   -49.21 & $1.68^{+0.19}_{-0.20}$  &  $16.6^{+0.7}_{-0.7}$  &  $5.0^{+0.8}_{-0.8}$  &  $0.19^{+0.02}_{-0.02}$  &  $26.9^{+0.4}_{-0.4}$\\ 
+\aton            &   -54.01 & $0.97^{+0.12}_{-0.12}$  &  $17.0^{+0.7}_{-0.7}$  &  $9.1^{+0.8}_{-0.8}$  &  $-0.00^{+0.00}_{-0.00}$  &  $26.1^{+0.5}_{-0.5}$\\ 
+\monash          &   -60.05 & $1.06^{+0.15}_{-0.15}$  &  $15.0^{+1.0}_{-1.0}$  &  $8.6^{+0.8}_{-0.8}$  &  $0.12^{+0.02}_{-0.02}$  &  $26.8^{+0.4}_{-0.4}$\\ 
+\nugrid          &   -52.04 & $0.83^{+0.10}_{-0.10}$  &  $19.0^{+0.6}_{-0.6}$  &  $0.9^{+1.0}_{-1.0}$  &  $0.28^{+0.03}_{-0.03}$  &  $27.6^{+0.4}_{-0.4}$\\ 
+\fruity\ shifted    &   {\bf -44.75} & $1.57^{+0.18}_{-0.18}$  &  $19.7^{+0.5}_{-0.5}$  &  $2.7^{+0.9}_{-0.9}$  &  $0.20^{+0.02}_{-0.02}$  &  $28.1^{+0.4}_{-0.4}$\\
+\hline
+\end{tabular}
+
+}
+
+\end{table*}
+
+\begin{figure}
+\centering
+\includegraphics{figures/mcmc_corner.pdf}
+\caption[]{
+A corner plot of the posterior samples from the MCMC simulation for the analytic model fit to the binned mean trends.
+$\aagb$ represents the scale factor for the AGB yields, and $\yl$, $\zcc$ represent the constant and linear components of the CCSN yield. 
+See Section~\ref{sec:mcmc_methods} for a description of the methods.
+
+}
+
+\label{fig:mcmc}
+\end{figure}
 

### 2025-11-14 carbon_paper/tex/survey_comparison.tex
near-submission draft

--- 2025-01-16 carbon_paper/tex/survey_comparison.tex
@@
 % MAIN DOCUMENT
-\title{Comparison of C inn observations}
+\title{Comparison of C Abundance Observations}
 
@@
 \subsection{Large Spectroscopic Surveys}
-In general (see Fig.~\ref{fig:other_surveys}, all surveys (except for GALAH, see below) agree in both the \caah\ and \caafe\ trends, up to a \about{0.2} dex offset.
-Changing our adopted equilibrium trend to any of these would only affect the yield scale, which is already a known degeneracy in chemical evolution modeling.
+In general (see Fig.~\ref{fig:other_surveys}, all medium-high large spectroscopic surveys agree in both the \caah\ and \caafe\ trends, up to a \about{0.2} dex offset.
+Changing our adopted equilibrium trend to any of these would only affect the yield scale, which is already a known degeneracy in chemical evolution modelling.
 
-We do not renormalize surveys and instead use reported abundances.
+We do not re normalize surveys and instead use reported abundances.
 Each survey sets zero points in slightly different manners, and given the systematic uncertainty in this step, the absolute abundance scale of a survey is less precise than abundance trends.
-
-% \begin{figure}
-%     \centering
-%     \includegraphics{c+n.pdf}
-%     \caption{[C+N/Mg]. This figure is likely getting cut, check if looks good with full sample (reassuring), and maybe look at [Mg/Fe] here too, but if agrees, we do not need it anymore...}
-%     \label{fig:cn}
-% \end{figure}
 
@@
 
-The {\bf Gaia-ESO} survey (Gilmore + 2022, Randich+2022) is a large ($10^5$) stellar spectroscopic instrument using FLAMES/VLT with both the GIRAFFE (R $\sim$ 20k) and UVES ($R\sim 50k$) spectrographs.
+\subsubsection{{\it Gaia}-ESO}
+The Gaia-ESO survey (Gilmore + 2022, Randich+2022) is a large ($10^5$) stellar spectroscopic instrument using FLAMES/VLT with both the GIRAFFE (R $\sim$ 20k) and UVES ($R\sim 50k$) spectrographs. 
 Here, we use the catalogue published in  \citep{hourihane+2023} containing 114,816 stars.
@@
 
-our flags are
+Our selection criteria are
 \begin{itemize}
@@
 \centering
+\small
 \begin{tabular}{lrlll}
@@
 \end{table}
+
 C abundances are measured in XXXX.
@@
 
-\begin{longtable}{lllll}
+\small
+\begin{longtable}{p{2.5cm}p{2.5cm}lll}
+    \caption{Caption} \\
+
     \hline
@@
     Tol 1214-277 & Tol 1214-277 & $-0.59 \pm 0.28$ & $-1.22 \pm 0.05$ & garnett+1995 \\
-SDSS J094401.87-003832.1 & centre & $-1.15 \pm 0.06$ & $-1.00 \pm 0.07$ & senchyna+17 \\
-SDSS J102429.25+052450.9 & centre & $-0.60 \pm 0.20$ & $-0.89 \pm 0.04$ & senchyna+17 \\
-UGC 5189 & SDSS J094256.74+092816.2, & $-0.53 \pm 0.45$ & $-0.57 \pm 0.06$ & senchyna+17 \\
+    SDSS J094401.87 -003832.1 & centre & $-1.15 \pm 0.06$ & $-1.00 \pm 0.07$ & senchyna+17 \\
+    SDSS J102429.25 +052450.9 & centre & $-0.60 \pm 0.20$ & $-0.89 \pm 0.04$ & senchyna+17 \\
+    UGC 5189 & SDSS J094256.74 +092816.2, & $-0.53 \pm 0.45$ & $-0.57 \pm 0.06$ & senchyna+17 \\
     Mrk 193 & Mrk 193 & $-0.31 \pm 0.04$ & $-0.90 \pm 0.04$ & senchyna+17 \\
@@
     J092055 & NaN & $-0.44 \pm 0.12$ & $-0.95 \pm 0.02$ & berg+19 \\
-Mrk 960 & NaN & $-0.41 \pm 0.39$ & $-0.70 \pm 0.19$ & pena-guerreno+17 \\
+    im & NaN & $-0.41 \pm 0.39$ & $-0.70 \pm 0.19$ & pena-guerreno+17 \\
     SBS 0218+003 & NaN & $-0.96 \pm 0.25$ & $-0.82 \pm 0.06$ & pena-guerreno+17 \\
@@
 \end{longtable}
+\relax
 
-\begin{longtable}{lllll}
-\hline
-galaxy & region & C/O & O/H & study \\
-\hline
-NGC 6822 & region V & $-0.15 \pm 0.21$ & $-0.44 \pm 0.09$ & peimbert+05 \\
-MW & Sh 2-311 & $-0.10 \pm 0.14$ & $-0.24 \pm 0.05$ & mendez-delgado+22 \\
-MW & NGC 2579 & $-0.14 \pm 0.09$ & $-0.26 \pm 0.03$ & mendez-delgado+22 \\
-MW & NGC 3576 & $-0.02 \pm 0.08$ & $-0.08 \pm 0.04$ & mendez-delgado+22 \\
-MW & NGC 3603 & $0.04 \pm 0.12$ & $-0.10 \pm 0.05$ & mendez-delgado+22 \\
-MW & M8 & $0.04 \pm 0.10$ & $-0.11 \pm 0.04$ & mendez-delgado+22 \\
-MW & M16 & $0.03 \pm 0.15$ & $-0.01 \pm 0.05$ & mendez-delgado+22 \\
-MW & M17 & $0.26 \pm 0.06$ & $-0.06 \pm 0.02$ & mendez-delgado+22 \\
-MW & M20 & $0.02 \pm 0.25$ & $-0.10 \pm 0.06$ & mendez-delgado+22 \\
-MW & M42 & $0.03 \pm 0.07$ & $-0.16 \pm 0.02$ & mendez-delgado+22 \\
-M101 & H1013 & $0.17 \pm 0.07$ & $-0.24 \pm 0.02$ & skillman+20 \\
-M101 & H1052 & $0.13 \pm 0.04$ & $-0.24 \pm 0.01$ & skillman+20 \\
-M101 & NGC 5461 & $-0.10 \pm 0.12$ & $-0.33 \pm 0.02$ & skillman+20 \\
-M101 & NGC 5462 & $-0.18 \pm 0.19$ & $-0.36 \pm 0.05$ & skillman+20 \\
-M101 & NGC 5462 & $-0.07 \pm 0.12$ & $-0.38 \pm 0.01$ & skillman+20 \\
-M101 & NGC 5455 & $-0.13 \pm 0.11$ & $-0.42 \pm 0.02$ & skillman+20 \\
-M101 & NGC 5447 & $-0.09 \pm 0.09$ & $-0.39 \pm 0.01$ & skillman+20 \\
-M101 & NGC 5447 & $-0.04 \pm 0.17$ & $-0.46 \pm 0.01$ & skillman+20 \\
-M101 & H1216 & $-0.42 \pm 0.50$ & $-0.55 \pm 0.03$ & skillman+20 \\
-M101 & NGC 5471 & $-0.26 \pm 0.46$ & $-0.67 \pm 0.03$ & skillman+20 \\
-NGC 300 & R20 & $-0.01 \pm 0.22$ & $-0.12 \pm 0.11$ & toribo-san-cipriano+16 \\
-NGC 300 & R23 & $-0.22 \pm 0.23$ & $-0.11 \pm 0.13$ & toribo-san-cipriano+16 \\
-NGC 300 & R14 & $-0.15 \pm 0.21$ & $-0.19 \pm 0.11$ & toribo-san-cipriano+16 \\
-NGC 300 & R2 & $-0.31 \pm 0.22$ & $-0.24 \pm 0.12$ & toribo-san-cipriano+16 \\
-M33 & NGC 588 & $-0.26 \pm 0.19$ & $-0.32 \pm 0.09$ & toribo-san-cipriano+16 \\
-M33 & IC 132 & $-0.12 \pm 0.15$ & $-0.34 \pm 0.12$ & toribo-san-cipriano+16 \\
-LMC & 30 Dor & $-0.29 \pm 0.06$ & $-0.28 \pm 0.04$ & toribo-san-cipriano+17 \\
-LMC & N44C & $-0.22 \pm 0.03$ & $-0.23 \pm 0.02$ & toribo-san-cipriano+17 \\
-LMC & IC 2111 & $-0.21 \pm 0.08$ & $-0.20 \pm 0.07$ & toribo-san-cipriano+17 \\
-LMC & NGC 1714 & $-0.24 \pm 0.07$ & $-0.25 \pm 0.07$ & toribo-san-cipriano+17 \\
-LMC & N11B & $-0.27 \pm 0.04$ & $-0.22 \pm 0.02$ & toribo-san-cipriano+17 \\
-SMC & N66A & $-0.46 \pm 0.06$ & $-0.46 \pm 0.03$ & toribo-san-cipriano+17 \\
-SMC & N81 & $-0.46 \pm 0.04$ & $-0.47 \pm 0.02$ & toribo-san-cipriano+17 \\
-SMC & NGC 456 & $-0.41 \pm 0.19$ & $-0.45 \pm 0.09$ & toribo-san-cipriano+17 \\
-SMC & N88A & $-0.33 \pm 0.03$ & $-0.59 \pm 0.02$ & toribo-san-cipriano+17 \\
-NGC 6822 & centre & $-0.31 \pm 0.15$ & $-0.46 \pm 0.05$ & esteban+14 \\
-NGC 5408 & centre & $-0.41 \pm 0.19$ & $-0.60 \pm 0.04$ & esteban+14 \\
-M31 & K932 & $0.05 \pm 0.16$ & $-0.19 \pm 0.03$ & esteban+09 \\
-M33 & NGC 595 & $0.05 \pm 0.17$ & $-0.12 \pm 0.05$ & esteban+09 \\
-M33 & NGC 604 & $0.01 \pm 0.14$ & $-0.21 \pm 0.03$ & esteban+09 \\
-NGC 2366 & NGC-2363 & $-0.08 \pm 0.14$ & $-0.77 \pm 0.05$ & esteban+09 \\
-NGC 2403 & VS 24 & $0.30 \pm 0.28$ & $-0.44 \pm 0.04$ & esteban+09 \\
-NGC 2403 & VS 38 & $0.42 \pm 0.20$ & $-0.52 \pm 0.05$ & esteban+09 \\
-NGC 2403 & VS 44 & $-0.08 \pm 0.22$ & $-0.20 \pm 0.04$ & esteban+09 \\
-\hline
+\begin{longtable}{llllll}
+\caption{Recombination Line Abundances of C from a selection of source} \\
+
+\toprule
+galaxy & class & region & [C\_O] & [O\_H] & study \\
+\midrule
+NGC 6822 & dwarf & region V & $-0.15 \pm 0.21$ & $-0.44 \pm 0.09$ & peimbert+05 \\
+MW & MW & Sh 2-311 & $-0.10 \pm 0.13$ & $-0.24 \pm 0.04$ & mendez-delgado+22 \\
+MW & MW & NGC 2579 & $-0.15 \pm 0.09$ & $-0.25 \pm 0.03$ & mendez-delgado+22 \\
+MW & MW & NGC 3576 & $-0.03 \pm 0.10$ & $-0.07 \pm 0.06$ & mendez-delgado+22 \\
+MW & MW & NGC 3603 & $0.03 \pm 0.12$ & $-0.09 \pm 0.05$ & mendez-delgado+22 \\
+MW & MW & M8 & $0.03 \pm 0.10$ & $-0.10 \pm 0.04$ & mendez-delgado+22 \\
+MW & MW & M16 & $0.03 \pm 0.16$ & $-0.01 \pm 0.06$ & mendez-delgado+22 \\
+MW & MW & M17 & $0.25 \pm 0.08$ & $-0.05 \pm 0.04$ & mendez-delgado+22 \\
+MW & MW & M20 & $0.02 \pm 0.26$ & $-0.10 \pm 0.07$ & mendez-delgado+22 \\
+MW & MW & M42 & $0.03 \pm 0.08$ & $-0.16 \pm 0.03$ & mendez-delgado+22 \\
+M101 & spiral & H1013 & $0.17 \pm 0.07$ & $-0.24 \pm 0.02$ & skillman+20 \\
+M101 & spiral & H1052 & $0.13 \pm 0.04$ & $-0.24 \pm 0.01$ & skillman+20 \\
+M101 & spiral & NGC 5461 & $-0.10 \pm 0.12$ & $-0.33 \pm 0.02$ & skillman+20 \\
+M101 & spiral & NGC 5462 & $-0.18 \pm 0.19$ & $-0.36 \pm 0.05$ & skillman+20 \\
+M101 & spiral & NGC 5462 & $-0.07 \pm 0.12$ & $-0.38 \pm 0.01$ & skillman+20 \\
+M101 & spiral & NGC 5455 & $-0.13 \pm 0.11$ & $-0.42 \pm 0.02$ & skillman+20 \\
+M101 & spiral & NGC 5447 & $-0.09 \pm 0.09$ & $-0.39 \pm 0.01$ & skillman+20 \\
+M101 & spiral & NGC 5447 & $-0.04 \pm 0.17$ & $-0.46 \pm 0.01$ & skillman+20 \\
+M101 & spiral & H1216 & $-0.42 \pm 0.50$ & $-0.55 \pm 0.03$ & skillman+20 \\
+M101 & spiral & NGC 5471 & $-0.26 \pm 0.46$ & $-0.67 \pm 0.03$ & skillman+20 \\
+NGC 300 & spiral & R20 & $-0.01 \pm 0.22$ & $-0.12 \pm 0.11$ & toribo-san-cipriano+16 \\
+NGC 300 & spiral & R23 & $-0.22 \pm 0.23$ & $-0.11 \pm 0.13$ & toribo-san-cipriano+16 \\
+NGC 300 & spiral & R14 & $-0.15 \pm 0.21$ & $-0.19 \pm 0.11$ & toribo-san-cipriano+16 \\
+NGC 300 & spiral & R2 & $-0.31 \pm 0.22$ & $-0.24 \pm 0.12$ & toribo-san-cipriano+16 \\
+M33 & spiral & NGC 588 & $-0.26 \pm 0.19$ & $-0.32 \pm 0.09$ & toribo-san-cipriano+16 \\
+M33 & spiral & IC 132 & $-0.12 \pm 0.15$ & $-0.34 \pm 0.12$ & toribo-san-cipriano+16 \\
+LMC & magellanic & 30 Dor & $-0.29 \pm 0.06$ & $-0.28 \pm 0.04$ & toribo-san-cipriano+17 \\
+LMC & magellanic & N44C & $-0.22 \pm 0.03$ & $-0.23 \pm 0.02$ & toribo-san-cipriano+17 \\
+LMC & magellanic & IC 2111 & $-0.21 \pm 0.08$ & $-0.20 \pm 0.07$ & toribo-san-cipriano+17 \\
+LMC & magellanic & NGC 1714 & $-0.24 \pm 0.07$ & $-0.25 \pm 0.07$ & toribo-san-cipriano+17 \\
+LMC & magellanic & N11B & $-0.27 \pm 0.04$ & $-0.22 \pm 0.02$ & toribo-san-cipriano+17 \\
+SMC & magellanic & N66A & $-0.46 \pm 0.06$ & $-0.46 \pm 0.03$ & toribo-san-cipriano+17 \\
+SMC & magellanic & N81 & $-0.46 \pm 0.04$ & $-0.47 \pm 0.02$ & toribo-san-cipriano+17 \\
+SMC & magellanic & NGC 456 & $-0.41 \pm 0.19$ & $-0.45 \pm 0.09$ & toribo-san-cipriano+17 \\
+SMC & magellanic & N88A & $-0.33 \pm 0.03$ & $-0.59 \pm 0.02$ & toribo-san-cipriano+17 \\
+NGC 6822 & dwarf & centre & $-0.31 \pm 0.15$ & $-0.46 \pm 0.05$ & esteban+14 \\
+NGC 5408 & dwarf & centre & $-0.41 \pm 0.19$ & $-0.60 \pm 0.04$ & esteban+14 \\
+M31 & spiral & K932 & $0.05 \pm 0.16$ & $-0.19 \pm 0.03$ & esteban+09 \\
+M33 & spiral & NGC 595 & $0.05 \pm 0.17$ & $-0.12 \pm 0.05$ & esteban+09 \\
+M33 & spiral & NGC 604 & $0.01 \pm 0.14$ & $-0.21 \pm 0.03$ & esteban+09 \\
+NGC 2366 & magellanic & NGC-2363 & $-0.08 \pm 0.14$ & $-0.77 \pm 0.05$ & esteban+09 \\
+NGC 2403 & spiral & VS 24 & $0.30 \pm 0.28$ & $-0.44 \pm 0.04$ & esteban+09 \\
+NGC 2403 & spiral & VS 38 & $0.42 \pm 0.20$ & $-0.52 \pm 0.05$ & esteban+09 \\
+NGC 2403 & spiral & VS 44 & $-0.08 \pm 0.22$ & $-0.20 \pm 0.04$ & esteban+09 \\
+\bottomrule
 \end{longtable}

### 2025-11-19 carbon_paper/plots/mcmc_fagb.py
change linestyle

@@ -118,7 +118,7 @@ plot_hists(axs[:, 1], "alpha", ylabel=False)
 
 
 for ax in axs[:, 1]:
-    ax.axvline(1, color="black", linewidth=0.5)
+    ax.axvline(1, color="grey", ls=":")
 
 
 

### 2025-11-19 carbon_paper/tex/main.tex
james grammar edits

@@
 
+% AGB yield tables
 \newcommand{\fruity}{\texttt{\hyperlink{fruity}{Fruity}}}
@@
 \newcommand{\cfactor}{2.57}
-\newcommand{\zetaobest}{1.90 \pm 0.10}
-\newcommand{\zetaibest}{2.28 \pm 0.16}
-
 \newcommand{\nsubgiants}{14,066}
-
-% displays fractions within fractions well
-\newcommand{\ddfrac}[2]{\ensuremath{%
-    \frac{\displaystyle{#1}}{\displaystyle{#2}}
-}}
-
-% Acronyms
-\newcommand{\agb}{AGB}
-\newcommand{\apogee}{APOGEE}
-\newcommand{\aspcap}{\textsc{aspcap}}
-\newcommand{\cc}{CCSN}
-\newcommand{\gce}{GCE}
-\newcommand{\ia}{SN Ia}
 
@@
 \newcommand{\caafe}{[C/Mg]-[Mg/Fe]}
-\newcommand{\oh}{{\rm [O/H]}}
-\newcommand{\mgh}{{\rm [Mg/H]}}
-\newcommand{\cmg}{{\rm [C/Mg]}}
 \newcommand{\co}{{\rm [C/O]}}
-\newcommand{\mgfe}{{\rm [Mg/Fe]}}
-
-\newcommand{\Var}{\operatorname{Var}}
-
 \newcommand{\Hii}{H~{\sc ii}}
 
-% other
-
-\makeatletter
-\newcommand{\C}[1][\@nil]{
-    \def\tmp{#1}%
-    \ifx\tmp\@nnil%
-        \ensuremath{\rm C}%
-    \else%
-        \ifmmode ^{#1}{\rm C}%
-        \else $^{#1}$C%
-        \fi%
-\fi }
-\makeatother
-
+% mathmode shortcuts
 \newcommand{\Yct}{{y_{\rm C}^{\rm  tot}}}
@@
 
+% other
 \newcommand{\about}[1]{${\sim} #1$}
@@
 
-% Caption macros
-\newcommand{\captionline}[2][very
-thick]{\tikz[baseline={([yshift=-.5ex]current bounding box.base)}]{
-\draw[#2,#1, line cap=round] (0,0) -- (0.3,0); }}
-
 %%%%%%%%%%% JWJ' editing macros %%%%%%%%%%%
@@
 \newcommand{\strike}[1]{{\color{red} \sout{#1}}}
-% \newcommand{\add}[1]{{\color{ForestGreen} #1}}
-% \newcommand{\note}[1]{{\color{ForestGreen} \textit{ \small (JWJ: #1)}}}
-% \LetLtxMacro\origcitep\citep
-% \LetLtxMacro\origcitet\citet
-% \renewcommand{\citep}[2][]{%
-%     \mbox{\origcitep[#1][]{#2}}
-% }
-% \renewcommand{\citet}[2][]{%
-%     \mbox{\origcitet[#1][]{#2}}
-% }
-
-\newcommand{\dbstrike}[1]{{\color{Thistle} \sout{#1} }}
-\newcommand{\dbadd}[1]{{\color{Thistle} #1}}
-\newcommand{\dbnote}[1]{ {\color{Thistle} \textit{\small (DB: #1)}} }
 
@@
 \author[D. A. Boyea et. al.]{%
-Daniel A. Boyea,$^{1, 2, 3}$\thanks{%
+Daniel A. Boyea,$^{1, 2}$\thanks{%
 Contact e-mail:~\href{mailto:danielaboyea@gmail.com}{danielaboyea@gmail.com}}
-James W. Johnson,$^{1, 2, 4}$
-and others
-%David H. Weinberg,$^{1,2}$
-%Jennifer A. Johnson,$^{1,2}$
-%Falk Herwig$^{3}$
+James W. Johnson,$^{2, 3, 4}$
+and
+David H. Weinberg$^{2,4}$
 \\
 % List of institutions
-$^{1}$Department of Astronomy, The Ohio State University, 140 W. 18th Ave., Columbus, OH, 43210, USA
+$^{1}$Department of Physics \& Astronomy, University of Victoria, 3800 Finnerty Road, Victoria, BC, V8P 5C2, Canada
 \\
-$^{2}$Center for Cosmology \& Astroparticle Physics (CCAPP), The Ohio State University, 191 W. Woodruff Ave., Columbus, OH, 43210, USA
+$^{2}$Department of Astronomy, The Ohio State University, 140 W. 18th Ave., Columbus, OH, 43210, USA
 \\
-$^{3}$Department of Physics \& Astronomy, University of Victoria, Victoria, BC V8P 5C2, Canada
+$^{3}$The Observatories of the Carnegie Institution for Science, 813 Santa Barbara St., Pasadena, CA, 91101, USA
 \\
-$^{4}$The Observatories of the Carnegie Institution for Science, 813 Santa Barbara St., Pasadena, CA, 91101, USA
+$^{4}$Center for Cosmology \& Astroparticle Physics (CCAPP), The Ohio State University, 191 W. Woodruff Ave., Columbus, OH, 43210, USA
 }
@@
     \includegraphics{subgiants.pdf}
-    \caption{The [C/Mg] ratio versus [Mg/H] (left) and [Mg/Fe] (right) for the \citet{jack}~sample of \apogee{} subgiants.
+    \caption{The [C/Mg] ratio versus [Mg/H] (left) and [Mg/Fe] (right) for the \citet{jack}~sample of APOGEE subgiants.
 {\bf Left:} High- and low-$\alpha$ stars are shown in blue and orange, respectively, using the separation defined in Eq.~\ref{eq:high_alpha}.
@@
 \citet{emily+19, emily+22, emily+24} applied the same methodology to GALAH~\citep{DeSilva2015, Martell2017}.
-In addition, models such as \citet{eitner+2020} and \citet{dubay+24} have used abundance trends of Fe and related elements to understand the physics and origin of \ia.
+In addition, models such as \citet{eitner+2020} and \citet{dubay+24} have used abundance trends of Fe and related elements to understand the physics and origin of SN Ia.
 Most directly relevant to our analysis, \citet{james+24} applied Milky Way chemical evolution models to N and recommended a yield prescription that reproduces the observed relation between N and O abundances.
@@
 In Section~\ref{sec:data_selection} we describe the selection for our subgiant observational sample.
-In Section~\ref{sec:nucleosynthesis}, we discuss theoretical estimates of \agb\ and \cc\ C yields.
+In Section~\ref{sec:nucleosynthesis}, we discuss theoretical estimates of AGB and CCSN C yields.
 In Section~\ref{sec:vice}, we describe the details of our GCE models.
@@
 
-We use the sample of \apogee\ DR17 subgiants from \citet{jack}. We select stars from the ASPCAP pipeline (revision 1) within the $\log g$-$T_\text{eff}$ polygon given by
+We use the sample of APOGEE DR17 subgiants from \citet{jack}. We select stars from the {\sc aspcap} pipeline (revision 1) within the $\log g$-$T_\text{eff}$ polygon given by
  \begin{equation}
@@
         \caption[]{The net fractional C yield from AGB stars as a function of initial stellar mass and metallicity.
-Each panel represents yields from one of four \agb\ studies from the literature: \fruity{}, \aton{}, \monash{}, \nugrid{} (see Section \ref{sec:agb}).
+Each panel represents yields from one of four AGB studies from the literature: \fruity{}, \aton{}, \monash{}, \nugrid{} (see Section \ref{sec:agb}).
 The black dotted line shows $\Ycagb=0$ for reference.
@@
 \end{equation}
-As our fiducial \agb\ yield, we use the \fruity\ table with $\aagb=\cfactor$, (balancing MW and gas-phase constraints; see Section~\ref{sec:results} and Section~\ref{sec:gas}).
+As our fiducial AGB yield, we use the \fruity\ table with $\aagb=\cfactor$, (balancing MW and gas-phase constraints; see Section~\ref{sec:results} and Section~\ref{sec:gas}).
 
@@
 The IMF-averaged yields computed from the literature tables differ in normalization and metallicity dependence.  
-The left panel of Fig.~\ref{fig:agb-ssp} shows IMF-averaged C yields for each \agb\ model as a function of metallicity, computed at time $\tau = 10$ Gyr after the formation of a single stellar population.
+The left panel of Fig.~\ref{fig:agb-ssp} shows IMF-averaged C yields for each AGB model as a function of metallicity, computed at time $\tau = 10$ Gyr after the formation of a single stellar population.
 The normalizations span a factor of \about{2} (e.g., between $6\times 10^{-4}$ and $12 \times 10^{-4}$ at $Z=0.33\,\Zo$).
@@
 
-The right panel of Fig.~\ref{fig:agb-ssp} shows the time-dependence of C production by \agb\ stars in a single stellar population of metallicity ${\rm [M/H]} = -0.1$ as a function of age. 
-As the mass range $2\,\Mo\lesssim M \lesssim 4\,\Mo$ is predicted to be most important for C production, half the yield is produced before \about{1}\,Gyr, similar to Fe production by \ia. 
-\monash{} weights C production more heavily towards high-mass \agb\ stars, resulting in shorter delay times, whereas the \fruity\ model predicts a slightly longer time-scale of \about{1}\,Gyr.
+The right panel of Fig.~\ref{fig:agb-ssp} shows the time-dependence of C production by AGB stars in a single stellar population of metallicity ${\rm [M/H]} = -0.1$ as a function of age. 
+As the mass range $2\,\Mo\lesssim M \lesssim 4\,\Mo$ is predicted to be most important for C production, half the yield is produced before \about{1}\,Gyr, similar to Fe production by SN Ia. 
+\monash{} weights C production more heavily towards high-mass AGB stars, resulting in shorter delay times, whereas the \fruity\ model predicts a slightly longer time-scale of \about{1}\,Gyr.
 In any case, little to no C is produced more than 2\,Gyr after a star formation event.
@@
 Above ${\sim}1\,\Mo$, TDU becomes more important, enriching the outer layers with C.
-In \agb\ stars more massive than ${\sim}5\,\Mo$, efficient HBB turns most of the \C[12] into $^{14}$N.
+In AGB stars more massive than ${\sim}5\,\Mo$, efficient HBB turns most of the $^{12}$C into $^{14}$N.
 TDU is more efficient for compact, massive cores.
@@
 	\centering
-    \caption[]{For each \agb\ yield set, the IMF-averaged \agb\ C yield at solar metallicity $y_{\rm C, 0}^{\rm AGB}$, the fraction of solar C produced in the model $f_\odot^{\rm AGB}$, and the masses and metallicities each yield table is sampled on.
+    \caption[]{For each AGB yield set, the IMF-averaged AGB C yield at solar metallicity $y_{\rm C, 0}^{\rm AGB}$, the fraction of solar C produced in the model $f_\odot^{\rm AGB}$, and the masses and metallicities each yield table is sampled on.
     $f_{\sun}^{\rm AGB}$ is calculated based on $y_{\rm C, \sun}^{\rm AGB}$ assuming the fiducial total C yield of $\Yct = 26.7\times 10^{-4}$.
@@
 		\hline 
-        \agb\ table 
+        AGB table 
                 & $y_{\rm C, \sun}^{\rm AGB}\times10^4$ %& y
@@
 
-\cc{} models predict a wide range of C yields, spanning nearly a factor of ten, even at fixed metallicity.
+CCSN models predict a wide range of C yields, spanning nearly a factor of ten, even at fixed metallicity.
 Fig.~\ref{fig:y_cc} shows the integrated yields of massive star models from the literature. 
  The \cite{LC18} models, which include rotation, show that the induced mixing (e.g., \citealt{frischknecht+16}) can dramatically increase the magnitude and metallicity dependence of $\Ycc$.
-As we will later empirically show, \cc\ C production needs to be strongly metallicity-dependent at $Z \approx \Zo$, which is consistent with \citepos{LC18} rapidly rotating models and to a lesser extent \citet{NKT13}.
-Fig.~\ref{fig:y_cc} also shows the IMF-averaged \agb\ star yields from the \fruity\ model (in Fig.~\ref{fig:agb-ssp}). Especially at $Z\approx \Zo$, most \cc\ models dominate \agb\ C production.
+As we will later empirically show, CCSN C production needs to be strongly metallicity-dependent at $Z \approx \Zo$, which is consistent with \citepos{LC18} rapidly rotating models and to a lesser extent \citet{NKT13}.
+Fig.~\ref{fig:y_cc} also shows the IMF-averaged AGB star yields from the \fruity\ model (in Fig.~\ref{fig:agb-ssp}). Especially at $Z\approx \Zo$, most CCSN models dominate AGB C production.
 
@@
 In particular, C-enriched envelope material is lost through winds before conversion into heavier elements, resulting in metallicity-dependent C production \citep{LC18}.
-While there are many stellar models providing predictions of \cc{} yields, the results of these models are highly uncertain.
-Furthermore, rotation, binarity, and explodability introduce substantial uncertainties in \cc\ predictions \citep{farmer+21}.
+While there are many stellar models providing predictions of CCSN yields, the results of these models are highly uncertain.
+Furthermore, rotation, binarity, and explodability introduce substantial uncertainties in CCSN predictions \citep{farmer+21}.
 
@@
 Of the models from \citet{iwamoto+99}, \citet{seitenzahl+13}, and \citet{gronow+21a, gronow+21b}, the maximum C production is less than 4 per cent of our required solar C yield, and most likely less than 2 per cent (assuming  $2.2\times 10^{-3}$ SN Ia explosions per solar mass of star formation; \citealt{maoz+mannucci12}).
-Novae are important contributors of \C[13], but do not process enough material to impact \C[12] production \citep{starrfield+20}.
-\C[13] is beyond the scope of this work and accounts for a small fraction of the C in the Universe.
+Novae are important contributors of $^{13}$C, but do not process enough material to impact $^{12}$C production \citep{starrfield+20}.
+$^{13}$C is beyond the scope of this work and accounts for a small fraction of the C in the Universe.
 
@@
 Fig.~\ref{fig:c_evo} shows evolutionary tracks in \caah{} and \caafe{} in the fiducial model at 1\,kpc intervals of radius.
-The \caah\ trend reaches an equilibrium state within \about{5}\,Gyr. \caafe\ tracks continue to evolve due to the long tail of the \ia\ DTD.
+The \caah\ trend reaches an equilibrium state within \about{5}\,Gyr. \caafe\ tracks continue to evolve due to the long tail of the SN Ia DTD.
 
 The evolution of chemical abundances can be understood as the interplay between different processes with different time-scales. 
- Initially, \cc\ dominate enrichment.
+ Initially, CCSN dominate enrichment.
 The [C/Mg] abundance ratio is set by the relative yield $\Ycc/\Ymg$.
@@
 [Mg/Fe] is initially high due to the delayed production time-scales of SN Ia Fe, as expected from the analytic models of \citet{WAF17}.
- Of order 100 Myr later, delayed sources enrich the ISM. \agb\ stars release C, raising [C/Mg], and \ia\ expel Fe, lowering [Mg/Fe]. 
+ Of order 100 Myr later, delayed sources enrich the ISM. AGB stars release C, raising [C/Mg], and SN Ia expel Fe, lowering [Mg/Fe]. 
  Several Gyr later, [Mg/H] reaches equilibrium.
-As the metal abundance stabilizes, so do metallicity-dependent \cc{} yields, allowing C to reach equilibrium.
-[Fe/H] continues to rise slowly due to ongoing \ia\ from old stellar populations.
+As the metal abundance stabilizes, so do metallicity-dependent CCSN yields, allowing C to reach equilibrium.
+[Fe/H] continues to rise slowly due to ongoing SN Ia from old stellar populations.
  Finally, the system reaches approximate equilibrium and evolution slows. \
@@
 
-\caption[]{The median low-$\alpha$ [C/N] ratio as a function of [Mg/H] for our fiducial model (blue line), compared with \apogee{} subgiants (medians as black points with 16th and 84th percentile ranges as grey bars).
+\caption[]{The median low-$\alpha$ [C/N] ratio as a function of [Mg/H] for our fiducial model (blue line), compared with APOGEE subgiants (medians as black points with 16th and 84th percentile ranges as grey bars).
 Stars are binned into 20 equal-number bins.
@@
         Stars are binned into 20 (left) or 12 (right) equal-number bins. 
-        The left panel only shows low-$\alpha$ stars, and the right panel shows stars where $-0.15\leq \mgh \leq -0.05$.
+        The left panel only shows low-$\alpha$ stars, and the right panel shows stars where $-0.15\leq {\rm [Mg/H]} \leq -0.05$.
         Coloured lines represent the median [C/Mg] in bins of [Mg/H] or [Mg/Fe] for each model.
@@
 
-The middle row of Fig.~\ref{fig:zeta_f} shows three models with different C \agb\  fractions (Eq.~\ref{eq:f_agb}).
+The middle row of Fig.~\ref{fig:zeta_f} shows three models with different C AGB  fractions (Eq.~\ref{eq:f_agb}).
 At fixed metallicity, the \caafe\ trend is principally sensitive to how much C and Fe come from delayed sources.
@@
 The left panel of Fig.~\ref{fig:sims_degens} shows the best-fitting AGB yield models (see Section \ref{sec:mcmc} for methodology) for each yield table we consider.
-Interestingly, while the individual DTDs of each AGB table appear substantially different (Fig.~\ref{fig:agb-ssp}), these differences smooth out in terms of the predicted abundance trends.
-Altogether, changes to the \agb{} yield table appear to have minimal effects on predicted C trends.
-
-One potential tension, however, is the concavity of the \caafe{} relation: all \agb{} tables predict a slightly concave down trend.
-In contrast, the subgiants predict a nearly-linear C trend across all [Mg/Fe].
-In addition, one of the most salient differences between models in the left panel of Fig.~\ref{fig:sims_degens} is that \aton{} and \monash{} predict an almost flat \caafe{} trend for ${\rm [Mg/Fe]} \lesssim 0.1$, in further tension with the data.
-As discussed in the next paragraph, this may indicate that C production should be weighted more towards even lower-mass stars.
-As an example, we shift the \fruity{} AGB yield table by a constant factor of 0.7 towards lower-mass AGB production.
-This shifted model predicts a more linear \caafe{} trend, in better agreement with observations.
-However, a GCE model better able to produce the abundance of high-$\alpha$ stars may be necessary to fully interpret this trend.
-Alternatively, the Fe DTD could similarly be too extended in our models, though recent work suggests a yet more extended DTD than our assumption \citep{palicio+2024, dubay+24}.
-
-To further explore the impact of the C DTD on abundance trends, we artificially shift the \fruity{} AGB yield table by a factor in mass.
-The middle panel of Fig.~\ref{fig:sims_degens} shows models shifting production towards lower masses (factors of 0.5 and 0.7) and higher masses (1.5).
+Although the individual DTDs of each AGB table appear substantially different (Fig.~\ref{fig:agb-ssp}), the predicted abundance trends do not show substantial differences.
+This outcome arises because each of our AGB models predict characteristic delay times for C production of order ${\sim}1$ Gyr, similar to the SN Ia production of Fe (see Figure 3), leading to a quasi-linear [C/Mg]-[Mg/Fe] relation in all cases.
+
+However, all AGB tables predict a slightly concave down trend because C production by single stellar populations slows down significantly after a $\sim$few Gyr, while Fe production through SNe Ia continues up to ${\sim}10$ Gyr (see discussion in Section~\ref{sec:agb}).
+Our subgiant sample does not exhibit this level of concavity.
+These discrepancies are significant because Figure \ref{fig:sims_degens} plots the mean trend, which is precisely determined through the large sample size.
+One of the largest discrepancies between our models and data in the left panel is that \aton{} and \monash{} predict an almost flat \caafe{} trend for ${\rm [Mg/Fe]} \lesssim 0.1$.
+
+These discrepancies in the [C/Mg]-[Mg/Fe] trend indicate that C production by single stellar populations may be more extended than our yield models predict.
+We explore this possibility further in the middle panel of Figure \ref{fig:sims_degens}, which shows variations of our fiducial model in which we artificially multiply the AGB star progenitor mass by factors of $0.5$, $0.7$, and $1.5$.
 When the AGB C production is weighted towards more massive AGB stars, the DTD becomes more rapid, leading to higher [C/Mg] at high [Mg/Fe].
@@
 For the extreme case, where the progenitor masses are shifted by a factor of 0.5, the AGB production is more delayed than SN Ia, resulting in a concave up trend.
-The ideal progenitor mass shift is \about{0.7}, linearizing the \caafe\ trend to agree with observations and alleviate the disagreement in concavity seen in the left panel of Fig.~\ref{fig:sims_degens}.
-While our mass shift models are artificially simple, they illustrate that the observed \apogee{} trends would be better fit if AGB production were shifted towards longer-lived stars.
+Prefactors around $\sim$$0.7$, corresponding to a slight shift in C production toward lower mass AGB stars, lead to the most linear [C/Mg]-[Mg/Fe] relation as indicated by the data.
+While our mass shift models are deliberately simple, they illustrate that the observed APOGEE trends would be better fit if AGB production were shifted towards longer-lived stars.
+Adjusting our SN Ia DTD to a prescription that declines more rapidly with stellar population age would also linearize the [C/Mg]-[Mg/Fe] relation.
+However, recent GCE models indicate that abundance trends favour, if anything, a more extended DTD than SN surveys have found (see discussion in \citealt{palicio+2024} and \citealt{dubay+24}).
 
@@
         {\bf Left:} The best-fitting model for each AGB table, and the best-fitting model from the middle panel with a mass shift of 0.7. 
-        {\bf Middle:} Models where the \fruity{} \agb\ yields are artificially shifted by different multiplicative factors in progenitor mass, but maintaining the same $\fagb$. 
+        {\bf Middle:} Models where the \fruity{} AGB yields are artificially shifted by different multiplicative factors in progenitor mass, but maintaining the same $\fagb$. 
         {\bf Right:} Models with alternative star formation histories (Eqs.~\ref{eq:lateburst}, \ref{eq:twoinfall}), and a model where all yields are doubled (with mass-loading adjusted accordingly; see Section~\ref{sec:vice}).
@@
 \end{equation}
-where $A=1.5$ represents the amplitude of the birth, $t_\text{burst}=10.8$\,Gyr is the time where the burst is strongest, and $\sigma_\text{burst}=1$\,Gyr is the width of the burst.
+where $A=1.5$ represents the amplitude of the burst, $t_\text{burst}=10.8$\,Gyr is the time where the burst is strongest, and $\sigma_\text{burst}=1$\,Gyr is the width of the burst.
 
@@
 The two-infall scenario offers a natural explanation \citep{spitoni19, spitoni21} for the bimodal distribution of [$\alpha$/Fe] ratios observed in the MW \citep[e.g.,][]{hayden+15}.
-However, the two-infall model has recently faced challenges when confronted with large catalogues of stellar age measurements \citep{dubay+24}.
+However, the two-infall model has recently faced challenges when confronted with large catalogues of stellar age measurements \citep{dubay+25}.
 For these models, we switch \VICE{} to `infall mode' and let it compute the SFR from a specified accretion history, in contrast to the other models where we specify the SFH (see discussion in Section~\ref{sec:vice}).
@@
 \end{equation}
-where $\tau_1=1\,$Gyr, $\tau_2=4\,$Gyr control the duration of the first and second burst, $t_2=4$\,Gyr specifies the start of the second infall, from, $A$ is the relative amplitude of the second burst, and $\theta$ is the Heaviside step function.
+where $\tau_1=1\,$Gyr, $\tau_2=4\,$Gyr control the duration of the first and second burst, $t_2=4$\,Gyr specifies the onset of the second infall epoch, $A$ is the relative amplitude of the second burst, and $\theta$ is the Heaviside step function.
 We chose $A(R)$ such that the ratio between the stellar mass produced in the first and second burst by $13.2\,{\rm Gyr}$ matches the ratio between the thin and thick disks from \citet{BHG16}.
 
-The right panel of Fig.~\ref{fig:sims_degens} compares the fiducial, lateburst, and two-infall models.
+The right panel of Fig.~\ref{fig:sims_degens} compares the fiducial SFH with these lateburst and two-infall variations.
 The differences in the \caafe\ trend are small.
-Each model predicts a different distribution in [Mg/Fe] as expected \citep[e.g.,][]{JW20}, but the relations between abundance ratios are largely unaffected by the assumed SFH.
-Variations due to the SFHs considered here are smaller than the width of the observed distribution.
+Each model predicts a different distribution in [Mg/Fe] as expected \citep[e.g.,][]{JW20} but not shown here.
+Most importantly, the relationship between these abundance ratios is largely unaffected by the assumed SFH.
 
@@
 strong degeneracy between the normalizations of elemental yields and mass-loading (see discussion in, e.g., \citealt{sandford+24} and Appendix B of \citealt{james+23}). 
-Our parameterization of $\eta$ illustrates this point (see Eq.~\ref{eq:mass_loading}) -- choosing a higher value of $y_{\rm Mg}^{\rm CC}$ will similarly result in higher values of $\eta$ while maintaining the same metallicity gradient.
+If we were to swap mass-loading for inward radial gas flows contained within the Galactic disk, a similar relationship would arise between the yield scale and the speed of the flow \citep{james+25}.
+Our parameterization of $\eta$ illustrates this point (see Eq.~\ref{eq:mass_loading}) -- choosing a higher value of $y_{\rm Mg}^{\rm CC}$ will similarly result in higher values of $\eta$ while maintaining the same metallicity profile, $Z_\text{Mg}(R)$.
 In the right panel of Fig.~\ref{fig:sims_degens}, we consider a model in which all yields are doubled (and mass loading approximately doubled by Eq.~\ref{eq:mass_loading}).
-As expected, the trend in [C/Mg]-[Mg/Fe] is not significantly affected, showing that observed trends constrain the ratio of C yields to Mg yields.
+As expected, the trend in [C/Mg]-[Mg/Fe] is not significantly affected.
+Based on this degeneracy, our investigations ultimately constrain the \textit{relative} yields of C and Mg, in the same way that Johnson et al.
+(2023) constrained the relative yields of N and O, as opposed to the total yields of any element.
 
@@
 
-Here, our goal is to convert the qualitative understanding from the last Section into more quantitative constraints on the yields. 
-From the previous Section, we learn that:  the \caah{} trend tells us the overall total C yield metallicity dependence, and the \caafe{} trend tells us about the amount of delayed C and its DTD.
-We chose to construct Monte-Carlo Markov chain (MCMC) models to explore possible abundance combinations matching the observed trends.
-From these models, we can derive the distributions of likely properties of underlying C yields given our current observations.
+In this section, our goal is to convert the qualitative understanding described up to this point into more quantitative constraints on C yields. 
+In Section~\ref{sec:results}, we showed that the \caah{} trend reflects the overall metallicity dependence of the total C yield from single stellar populations, while the \caafe{} trend reflects the amount of delayed C and its DTD.
+Here, we construct Monte-Carlo Markov chain (MCMC) models to explore possible abundance combinations matching the observed trends.
+From these models, we can derive the distributions of likely properties of underlying C yields given current observations.
 
@@
 
-To efficiently explore a wide range of yield combinations, we can use this linearity to predict the abundances from linear combinations of yields through {\it process tracking}.
+To efficiently explore a wide range of yield combinations, we use an approach that we refer to as {\it process tracking}.
 In GCE, total elemental abundances are (to first order) linear with respect to combinations of yields \citep[e.g.,][]{WAF17}.
-The rate of change of an element's ISM mass is given by the sum of processes constant or linear in the element's abundance: material formed into stars, new production of elements, material returned from stars, and material lost through outflows.
-Thus, just as the yields of different elements can be treated as independent solutions, the yields of different processes can be solved independently and superimposed.
-In our process tracking method, we set up \VICE {} to integrate each process for C independently (by using tracer elements for each yield component).
-We then predict the stellar abundances from a given linear combination of yields $y_{\rm tot} = \sum_i a_i\, y_i$ by adding together the linear abundances $Z_{\rm C, \it i}$ in the same linear combination ($Z_{\rm C, tot} = \sum a_i\,Z_i$).
-
-There are some limitations to the process-tracking approximation.
-Note that many other GCE parameters are non-linear with abundance and require full multi-zone simulations, such as star formation history, outflows, and migration prescriptions.
-Also note that metallicity-dependent yields introduce a second-order effect (metallicity depends on total yields which depend on metallicity), but for small changes to total yields, this effect should be small.
-
-Our first step is to run a multi-zone model tracking the abundances of each process we are interested in. 
-To use all the information available for [C/Mg] trends with [Mg/Fe] and [Mg/H], we calculate the mean C abundance for each 2D bin in [Mg/Fe] and [Mg/H] for both the data and the model.
-We add Gaussian-distributed measurement uncertainties to the model's stars as described in the Appendix (Eq.~\ref{eq:uncertainties}).
-We chose to use bins of a constant width of 0.04 dex, ranging from [Mg/H] of -0.5 to 0.5 and [Mg/Fe] of -0.1 to 0.4.
-We remove any 2D bin if fewer than 3 stars of the model or data fall in the bin.
+Process tracking exploits this linearity to integrate the CCSN and AGB yields separately, later expressing the C abundance as a linear combination of the two.
+We set up \VICE {} to integrate each process for C as different chemical elements.
+The C abundances then follow as $Z_\text{C,tot} = \sum a_i Z_i$, where $a_i$ and $Z_i$ are the amplitude and abundance evolution of the $i$th process. \red{ (join these two paragraphs?)}
+
+We emphasize that there are some limitations to the process-tracking approximation.
+Capturing the effects of many other GCE parameters -- such as the star formation history, outflows, and radial migration prescriptions --  require separate multi-zone integrations for each parameter variation.
+Metallicity-dependent yields also introduce a second-order effect (metallicity depends on total yields, which influence the metallicity), but this effect should be insignificant for small changes to total yields.
+
+Our first step is to run a multi-zone model tracking the abundances of each process we are interested in (in this case, CCSN and AGB star products). 
+To use all the information available for [C/Mg] trends with [Mg/Fe] and [Mg/H], we calculate the mean $Z_\text{C} / Z_\text{Mg}$ for each 2D bin in [Mg/Fe] and [Mg/H] for both the data and the model.
+We add Gaussian-distributed measurement uncertainties to the model's stars as described in the Appendix~\ref{sec:extra_scatter}.
+We use bins with a constant width of 0.04 dex, ranging from ${\rm [Mg/H]}=[-0.5, 0.5]$ and ${\rm [Mg/Fe]} = [-0.1, 0.4]$.
+We remove 2D bins with fewer than 3 stars in either the model or data.
 We separate the C yield  into three different components:
@@
 \end{enumerate}
-$\yl$, representing the low-metallicity C yield, is related to the $\yo$ of Eq.~\ref{eq:y_cc} by $\yl + \zcc = \yo$.
-
-We construct a likelihood based on the difference between the data and the model's mean C abundance in each bin.
-We use means since they are linear to linear combinations.
-Additionally, we work in linear abundance space for improved numerical stability.
+$\yl$ represents the C yield at low metallicity.
+When $Z \to\rightarrow 0$, Eq.~\ref{eq:y_cc} indicates that $\yl = \yo - \zcc$.
+
+We construct a likelihood function based on the difference in the mean $Z_\text{C}/Z_\text{Mg}$ between the data and model in each bin. 
+We use the linear as opposed to logarithmic C abundance (i.e., [C/H]) because the linear combination of enrichment channels from process tracking predicts $Z_\text{C}$. 
 Given the predicted abundance for the model in a given bin $b$,  $Z_{\rm C, \it b}^{\rm model}$, the associated observed abundance, $Z_{\rm C, \it b}^{\rm obs}$, and the error on the mean $\sigma_b$, the (Gaussian) log likelihood is given by
@@
 \end{equation}
-The total variance in each bin is calculated from the standard error on the mean of the observations in a bin $\sigma_{b, \rm obs}$, the standard error on the mean for each model component $i$, $\sigma_{b, i,\rm model}$, and a {\it systematic} uncertainty term $\sigma_{\rm sys}$.
+We calculate the total variance in each bin from the standard error on the mean of the observations in a bin $\sigma_{b, \rm obs}$, the standard error on the mean for each model component $i$, $\sigma_{b, i,\rm model}$, and a {\it systematic} uncertainty term $\sigma_{\rm sys}$.
 Altogether,
@@
 
-When included, the $\sigma_{\rm sys}^2$ represents the typical systematic random uncertainty.
+When included, $\sigma_{\rm sys}$ represents a systematic uncertainty.
 We consider models with both $\sigma_{\rm sys} = 0$ and 0.05 dex.
-While approximate, this value is similar to typical mean deviations between APOGEE and other surveys' C and Mg abundances \citep{hegedhus+2023, jonsson+2018} and discrepancies between APOGEE's reported abundance uncertainties compared to other measurements of dispersion \citep{mead+2024}.
-While systematic uncertainties are unlikely to be well-described by an independent, uncorrelated, constant-width normal distribution, we use this model as an order-of-magnitude illustration of the likely uncertainties of our results.
+While approximate, $0.05$ dex is similar to typical mean deviations between APOGEE and the C and Mg abundances in other surveys \citep{hegedhus+2023, jonsson+2018}.
+Discrepancies between APOGEE's reported abundance uncertainties and other measurements of dispersion indicate a similar level of systematic error \citep{mead+2024}.
+While systematic uncertainties are unlikely to be well-described by an independent, uncorrelated, constant-width normal distribution, we use this parameter as an approximation of the likely uncertainties of our results.
 
 We adopt loose priors for each model parameter: $\aagb \sim N(1, 1)$, $\zcc \sim N(0, 10^{-3})$, and $\yl \sim N(2\times10^{-3}, 1\times10^{-3})$, where $N(\mu, \sigma)$ is a Gaussian distribution with mean $\mu$ and standard deviation $\sigma$.
-
 We run the MCMC using Turing.jl \citep{turingjl} with a No-U-turn sampler (an adaptive Hamilton Monte-Carlo algorithm, \citealt{NUTS}) with an acceptance rate of 0.65.
@@
 
-Based on the procedure above, we derive our best-fitting (not fiducial) yield set.
-We find, for the \fruity{} AGB yield set,  $\aagb = \cfactor$, $\yo =22.3\times10^{-4}$, and $\zcc=7.9\times10^{-4}$.
-Instead, for the model where \fruity{} is shifted by a mass factor of 0.7, $\aagb = 2.34$, $\yo = 19.7\times 10^{-4}$ and $\zcc=3.2\times 10^{-4}$.
+Based on the procedure above, we derive our best-fitting (not fiducial described in Section~\ref{sec:agb}) yield set.
+For the \fruity{} AGB yield set, we find $\aagb = 1.55$, $\yo =22.3\times10^{-4}$, and $\zcc=7.9\times10^{-4}$.
+For the model where \fruity{} is shifted by a mass factor of 0.7, we instead find $\aagb = 2.34$, $\yo = 19.7\times 10^{-4}$ and $\zcc=3.2\times 10^{-4}$.
 The fiducial yields enforce a low-metallicity [C/O] plateau of \about{-0.5} for better agreement in Section~\ref{sec:gas}.
-Table~\ref{tab:mcmc_results} presents the best-fitting parameters for each model or yield set considered here.
-
-The left panel of Fig.~\ref{fig:mcmc_ytot} shows the inferred total C yield for each AGB yield table, and the \fruity{} table shifted by a mass factor of 0.7.
-While there is some variability in the total C yield, all models predict a total C yield within a band of width 0.5 in $\Yct$ ($\approx0.05\,$dex).
-Thus, the choice of AGB yield table only slightly affects the inferred total yield, as we expect the \caah{} trend to tightly constrain the total C yield (see Section~\ref{sec:yield_variations}).
+We present the best-fitting parameters for each model or yield set considered here in Appendix~\ref{sec:extra_mcmc}.
+
+The left panel of Fig.~\ref{fig:mcmc_ytot} shows the inferred total C yield for each AGB yield table, along with the \fruity{} table shifted in mass by a prefactor of 0.7.
+While there is some variability, all models predict  a dynamic range of $y_\text{C}^\text{tot} / y_\text{Mg}$ of approximately $\sim$$0.5$.
+Therefore, the choice of AGB yield table only slightly affects the inferred total yield.
 
 The middle panel of Fig.~\ref{fig:mcmc_ytot} shows the inferred AGB fraction (Eq.~\ref{eq:f_agb}) at solar metallicity for each model.
-No model predicts a median $\fagb > 0.3$ and the 98th percentile upper-limits are always below $\fagb=0.4$.
-All models except \aton{} predict that at least $\approx 8$ per cent of solar C comes from AGB stars (from the 2nd percentile lower-limits).
-The SFH and yield scale have little impact on the inferred $\fagb$.
-Across all models considered here, we infer a minority role in AGB C production at solar metallicity.
-
-The right panel of Fig.~\ref{fig:mcmc_ytot} compares the inferred scaling of AGB yields, $\aagb$.
-Given our yield scale, most AGB yield tables naturally produce near the best-fitting amount of AGB C, within a factor of ${\sim}2$.
-\monash{} predicts near the perfect amount of C (but see also discussion in Section~\ref{sec:agb_results}).
-However, if the yield scale is increased \citep[e.g., as advocated in][]{james+24}, the required AGB C production increases accordingly.
-This is illustrated by the `doubled yields' model, which doubles yields and about doubles outflows.
-While $\fagb{}$ remains similar to the \fruity{} model, the ideal $\aagb$ doubles (see discussion in Section~\ref{sec:outflows}).
-
-By including a $\sigma_{\rm sys}$ term, the distributions of $\fagb$, $\aagb$ and CC yield parameters all widen without changing our conclusions.
+No model predicts a median $\fagb > 0.3$ and the 98th percentile upper-limits are all below $\fagb=0.4$.
+All models except \aton{} predict that at least $\approx 8$ per cent of the solar C comes from AGB stars (from the 2nd percentile lower-limits).
+The SFH and overall yield scale have little impact on the inferred $\fagb$.
+All of our yield models favour a scenario in which AGB stars are responsible for less than half of the C present in near-solar metallicity environments.
+
+The right panel of Fig.~\ref{fig:mcmc_ytot} compares the inferred scaling of AGB yields, $\aagb$. For most tables, we find $\aagb$ near unity, indicating accurate total C yields from AGB stars.
+Doubling our yields results in higher values of $\aagb$ in order to produce more C at fixed $\fagb$.
+For \monash{} and \aton{}, $\aagb$ is almost exactly $1$.
+However, these models struggle to reproduce the [C/Mg]-[Mg/Fe] relation, which suggests issues related to the mass-dependence of the yields (see discussion in Section \ref{sec:agb_results}).
+
+By including the $\sigma_{\rm sys}$ parameter, the posterior distributions of $\fagb$, $\aagb$ and CC yield parameters all widen without changing our conclusions.
 Effectively, $\sigma_{\rm sys}$ reduces the weight of abundance differences between bins.
-Systematic uncertainties likely dominate the uncertainty budget in this analysis.
-
-Finally, the choice of the Fe \ia{} DTD directly impacts our conclusions.
+Systematic errors likely dominate the uncertainty budget in this analysis.
+
+Finally, the choice of the Fe SN Ia DTD directly impacts our conclusions.
 From the right panel of Fig.~\ref{fig:mcmc_ytot}, we note that increasing the SN Ia Fe yield by a factor of 1.2 (and decreasing the CC Fe yield to maintain the same total Fe production) results in a similar increase in the inferred $\fagb$.
@@
 \textbf{Right:} Similar to the middle panel except in terms of $\aagb$, the AGB table multiplication factor.
-The vertical line marks $\aagb=1$, corresponding to unscaled yields.
+The dotted vertical line marks $\aagb=1$, corresponding to unscaled yields.
         }
@@
 The black dotted line is a simple, one-zone model for a GSE-like dwarf galaxy.
-Points represent measurements for MW stars (yellow stars), MW \Hii{} regions (RLs, orange pentagons), extragalactic \Hii{} Regions RLs (green empty diamonds), extragalactic \Hii{} regions from CELs (green full diamonds), high redshift galaxies (pink squares), damped Lyman-$\alpha$ systems (orange triangles),  and the low-$\alpha$ APOGEE subgiant sample we used here (purple circles).
+Points represent measurements for MW stars (yellow stars), MW \Hii{} regions (recombination lines, orange pentagons), extragalactic \Hii{} regions from recombination lines (green empty diamonds), extragalactic \Hii{} regions from collisional excited lines (green full diamonds), high redshift galaxies (pink squares), damped Lyman-$\alpha$ systems (orange triangles),  and the low-$\alpha$ APOGEE subgiant sample we used here (purple circles).
 The points with error bars show representative median uncertainties for their associated population.
-Six measurements based on CEL or in DLAs (with large uncertainties) fall above or below the axis limits.
+Six measurements based on collisional excited lines or in damped Lyman-$\alpha$ systems (with large uncertainties) fall above or below the axis limits.
 
@@
 MW \Hii{} regions from \citet[][]{mendez-delgado+22, esteban+05, esteban+13}, 
-extragalactic RL \Hii{} regions from \citet[][]{peimbert+05, skillman+20, toribio-san-cipriano+16, toribio-san-cipriano+17, esteban+14, esteban+09}, 
-extragalactic CEL \Hii{} regions from \citet[][]{garnett+95, senchyna+17, izotov+thuan99, garnett+99, berg+16, berg+19, pena-guerrero+17}, 
+extragalactic recombination line \Hii{} regions from \citet[][]{peimbert+05, skillman+20, toribio-san-cipriano+16, toribio-san-cipriano+17, esteban+14, esteban+09}, 
+extragalactic collisional excited lines \Hii{} regions from \citet[][]{garnett+95, senchyna+17, izotov+thuan99, garnett+99, berg+16, berg+19, pena-guerrero+17}, 
 high redshift galaxies from \citet[][]{steidel+16, stark+14, matthee+21, mainali+20, jones+23, amorin+17, iani+23, james+14, erb+10, bayliss+14, berg+18, christensen+12, arellano-cordova+2022}, and
-DLAs from \citet[][]{omera+01, cooke+14, welsh+22, ellison+10, welsh+20, cooke+18, riemer-sorensen+17, DZ+03, cooke+17, cooke+11, dutta+14, morrison+16, srianand+10, pettini+08, kislitsyn+24, cooke+15}.
+damped Lyman-$\alpha$ systems from \citet[][]{omera+01, cooke+14, welsh+22, ellison+10, welsh+20, cooke+18, riemer-sorensen+17, DZ+03, cooke+17, cooke+11, dutta+14, morrison+16, srianand+10, pettini+08, kislitsyn+24, cooke+15}.
 }
@@
 in the gas phase.
-We consider measurements in Galactic and extragalactic \Hii{} regions, Damped Lyman-$\alpha$ systems\footnote{DLAs are gas clouds observed as absorption spectra in front of background quasars}, and Milky Way halo main-sequence stars.
+We consider measurements in Galactic and extragalactic \Hii{} regions, Damped Lyman-$\alpha$ systems\footnote{damped Lyman-$\alpha$ systems (or DLAs) are gas clouds observed as absorption spectra in front of background quasars}, and Milky Way halo main-sequence stars (all references in the caption of Figure 10, which we do not repeat here for brevity).
 While we used Mg as our representative alpha element in our APOGEE sample, we shift focus to O in this Section because O is more readily observed in the gas phase.
-C abundances are challenging to measure in \Hii{} regions because C lacks strong recombination lines (RL),  and its collisionally excited lines (CEL) fall in the far ultraviolet without nearby reference H lines \citep[][]{skillman+20}.
+C abundances are challenging to measure in \Hii{} regions because of a lack of strong recombination lines.
+The collisionally excited lines of C fall in the far ultraviolet without nearby reference H lines \citep[][]{skillman+20}.
 %Furthermore, CEL and RL derived abundances are systematically discrepant by \about{0.5}\,dex \citep{GR07}.
@@
 Near solar metallicity, most measurements have ${\rm [C/O]} \approx 0$.
-Below solar metallicity, [C/O] appears to follow a non-monotonic trend, reaching a minimum of $\co  \approx -0.6$ around $\oh \approx -1$, and possibly increasing again at the very lowest metallicities.
+Below solar metallicity, [C/O] appears to follow a non-monotonic trend, reaching a minimum of $\co  \approx -0.6$ around ${\rm [O/H]} \approx -1$, and possibly increasing again at the very lowest metallicities.
 
@@
 We use the same yields as our fiducial multi-zone model.
-Our GSE-like model has a constant mass loading of $\eta=5.74$, total star formation time of 10.73 Gyr, a constant star formation efficiency time-scales of 26.60 Gyr, and an exponential infall history $\dot \Sigma_{\rm in} = \exp(-t / 2.18\,{\rm Gyr})$ (in contrast to star formation rate specification for our fiducial model).
+Our GSE-like model is derived from \citet{james_dwarfs} except with adjusted outflows for our yield sclae.
+We adpot a constant mass loading of $\eta=5.74$, total star formation time of 10.73 Gyr, a constant star formation efficiency time-scales of 26.60 Gyr, and an exponential infall history $\dot \Sigma_{\rm in} = \exp(-t / 2.18\,{\rm Gyr})$ (in contrast to star formation rate specification for our fiducial model).
 In summary, the GSE-like model compared to our fiducial MW model does not include radial migration and has a more rapid star formation history, elevated outflows, and lower star formation efficiency.
@@
 The gas-phase C abundances reveal a breakdown of our fiducial yield prescription.
-While the fiducial model sits well within the scatter of C/O ratios observed in near-solar (low-redshift) \Hii{} regions, the evolution of the solar zone only agrees with the highest measurements of [C/O] at lower metallicities ${\rm [O/H]} \sim -1$.
-The CCSN-only, low-metallicity plateau of [C/O] in the fiducial model is $\approx -0.5$.
-No value of [C/O] below about -0.5 would be consistent with this model.
-Furthermore, our GSE-like model consistently predicts higher [C/O] abundances.
-Because the star formation efficiency is much lower in this model, the contribution due to delayed enrichment will appear at lower metallicities.
-As a result, even at ${\rm [O/H]} \sim -1.5$, delayed C enrichment appears, raising the [C/O] ratio above most observations.
-This model is a relatively poor fit to the gas-phase data.
-We note that our subgiant sample only extends as low as a metallicity of ${\rm [O/H]} \sim -0.4$, so any application of the model to gas-phase requires substantial extrapolation.
-Our best-fitting yield models (to subgiants) prefer lower $\fagb{}$ and consequently higher low-metallicity [C/O] plateaus, worsening agreement.
-
-One possible remedy would be to decrease our assumed minimum CCSN yield $y_{\rm low}$, bringing the low-metallicity plateau into better agreement with observations.
+While the fiducial model sits well within the scatter of C/O ratios observed in low-redshift \Hii{} regions near solar metallicity, the evolution of the $R = 8$ kpc annulus overestimates the mean [C/O] at lower metallicities.
+The CCSN-only, low-metallicity plateau of [C/O] in the fiducial model is near $-0.5$, whereas the data sit closer to [C/O] $\sim -0.7$ near [O/H] $\sim - 1$.
+Furthermore, our GSE-like model overpredicts [C/O] across most of this range.
+Due to the higher mass-loading factor, this evolutionary track can be interpreted as shifted toward low metallicity relative to the solar zone at $R = 8$ kpc.
+Consequently, near-solar [C/O] ratios arise at low [O/H], resulting in a relatively poor fit to the gas-phase data.
+We note that our subgiant sample only extends as low as a metallicity of ${\rm [O/H]} \sim -0.4$, so any application of the model at these metallicities requires substantial extrapolation.
+
+One possible remedy would be to decrease our assumed minimum CCSN yield $y_{\rm low}$, which would lower the [C/O] plateau and improve agreement with observations.
 A lower $y_{\rm low}$ also requires a higher $\fagb{}$ to reach the observed [C/Mg] near solar metallicity.
-A slightly higher value of $\fagb{}$ will lower the low-metallicity plateau into better agreement with observations.
-However, a high $\fagb{}$ model would be in tension with the subgiant abundance trends.
-Such a model should produce stars with [C/O] near the plateau value in the early enrichment history of the Milky Way, observed as very low C but high-$\alpha$ stars (see evolution tracks in Fig.~\ref{fig:c_evo} and related models from Fig.~\ref{fig:zeta_f}).
-Because there are no subgiants with [C/Mg] abundances below \about{-0.4}, it is unlikely a high $\fagb{}$ model reconciles the gas-phase and stellar abundance trends.
-But, if C production is much more delayed than current AGB models predict, [C/Mg] may remain lower for longer than for our fiducial yields.
+However, a high $\fagb{}$ model would be in tension with the subgiant abundance trends (see Fig.~\ref{fig:gas_phase}).
+Based on these opposing indications of the value of $\fagb$ from our subgiant sample and the gas-phase data in Figure 10, it is difficult to reconcile the two observations in our models.
 
 Another possibility is that the massive star production of C (or O) exhibits a complex metallicity dependence.
-The increasing [C/O] abundances at the very lowest metallicities as observed in DLAs already hint at a more nuanced C nucleosynthetic landscape.
+The increasing [C/O] abundances at the very lowest metallicities as observed in damped Lyman-$\alpha$ systems already hint at a more nuanced C nucleosynthetic landscape.
 Given the abundance trends observed in Fig.~\ref{fig:gas_phase}, we propose the following possibility for C production.
@@
 %Kobayashi et al. 2020).
-This would now be observed as CEMP-no stars \citep[e.g., review and references in][]{FN15} and the elevated C abundances of DLAs.
+This would now be observed as CEMP-no stars \citep[e.g., review and references in][]{FN15} and the elevated C abundances of damped Lyman-$\alpha$ systems.
 (2) C production sharply drops as metallicity increases, reaching a minimum between [O/H] of -3 and -1.5.
@@
 
-\citet{berg+19} consider an alternative scenario for the chemical evolution of C in dwarf galaxies.
-Their models include initially high C/O ratios from Population III stars, which decline with metallicity due to Population II enrichment.
-Later, in a bursty star formation history, [C/O]-[O/H] follows a "zig-zag" pattern due to alternating periods of \cc{} and \agb{} dominated nucleosynthetic enrichment (see their figure 11).
-Scatter in C/O then arises from a combination of varying star formation histories and changing effective oxygen yields (i.e., different supernova entrainment factors).
+\citet{berg+19} presented a suite of GCE models that complement our investigations in this section.
+They focused on the effects of the bursty SFHs that dwarf galaxies are thought to have experienced \citep[e.g.]{mcquinn+10} for a given yield prescription.
+Our approach is the inverse; we have determined the effects of different choices of stellar yields with fewer considerations of the detailed SFH.
+Our models indicate that the exact choice of SFH is inconsequential to the subgiant abundance trends in APOGEE, primarily because our models predict a chemical equilibrium to arise early in the thin disk epoch.
+Advocated for by \citet{james+24} based on age-metallicity trends, the equilibrium scenario suggests that the abundance trends in our subgiant sample should reflect trends in C, Mg, and Fe yields (see Section 5).
+However, sudden bursts of star formation should always lead to chemical perturbations on some level, even in a state of equilibrium \citep{JW20}.
+Observing different galaxies at different phases in their burst cycles should drive substantial abundance scatter, as the models in \citet{berg+19} indicate.
+Adjustments to the C yields, as we have investigated, would instead shift all galaxies uniformly in the [C/O]-[O/H] plane.
 
@@
 In our fiducial model, the evolution of [C/Mg] initially increases with time due to the metallicity-dependent C yields from massive stars.
-Later, AGB stars contribute additional C, causing a sharp rise in C with metallicity.
-However, the chemical history is only indirectly related to the stellar abundance trends.
+Later, AGB stars contribute additional C, sharpening the rise in [C/Mg] with metallicity.
 
@@
 As a result, the \caah{} trend is most strongly tied to the total C yield (relative to Mg) at each metallicity [Mg/H].
-Because all AGB yield tables we consider here predict a declining C yield with increasing metallicity, the \caah{} trend implies that the CCSN yield must increase with metallicity.
-This could be due to the heightened metallicity-dependent mass-loss in the rotating models of \citet{LC18}.
-The C versus [Mg/H] relation alone, however, is unable to provide substantial information on the delayed relative to prompt production of C from massive or low-intermediate mass stars.
-On the other hand, the \caafe{} relation, at a given metallicity, is most sensitive to the amount of delayed, AGB C production.
-In addition, the shape of the [C/Mg] abundance trend with [Mg/Fe] can constrain the nature of the DTD of C.
-
-From the combined constraints of the [C/Mg] trend with metallicity and [$\alpha$/Fe], we have inferred possible observationally-consistent combinations of yields.
+All AGB star models we consider predict a declining C yield with increasing metallicity.
+The observed increase in [C/Mg] with [Mg/H], however, implies that the total C yield increases with metallicity.
+This trend favours a scenario in which massive star yields of C increase with metallicity in order to compensate for the declining AGB star yields.
+This outcome could arise due to the heightened metallicity-dependent mass-loss in the rotating models of \citet{LC18}.
+C and Mg, however, do not provide substantial information on the relative contributions of prompt versus delayed production by high- and low-mass stars.
+Due to its sensitivity to SN Ia nucleosynthesis, the \caafe{} relation at fixed [Mg/H] is also sensitive to the amount of delayed C production.
+
+From the combined constraints on the [C/Mg] trend with metallicity and [$\alpha$/Fe], we have inferred possible combinations of yields that reproduce thin-disk abundance trends.
 In all cases, we find that $\Yct / \Ymg \approx 4.2 \pm 0.2$ at solar metallicity, with total C production increasing with increasing metallicity.
 We also show that low-intermediate mass AGB stars likely produce a fraction of between 0.10 and 0.40 of solar C, across GCE assumptions and AGB yield tables.
-
-Given our yield scale, we find most AGB yield tables are within ${\sim}2$ times the inferred AGB C production.
-We find that the best-fitting models require between about 0.6 and 2 times more C than predicted by the AGB table.
-However, if the yield scale is higher than ours, the AGB C yield should be similarly amplified.
+At the normalization of stellar yields recommended by \citep{david_fe},  most AGB star models predict C yields within a factor of ${\sim}2$ of our inference.
+We find that the best-fitting models require between ${\sim}0.6$ and 2 times more C than predicted by the chosen AGB table.
+However, if the yield scale is higher or lower than this assumed scale, the AGB C yield should be rescaled in proportion.
 
 As a consequence of massive star enrichment dominating the C production in our models, our conclusions are relatively insensitive to the choice of AGB yield model.
-Of the yield tables tested here, \fruity{} and \nugrid{} better describe \caafe{} trend, as the production of C is too rapid from \monash{} and \aton{} near solar metallicity.
+Of the yield tables tested here, \fruity{} and \nugrid{} provide the best reproduction of the \caafe{} trend.
+The production of C by AGB stars is too rapid with the \monash{} and \aton{} yields.
 However, all AGB yield tables predict a \caafe{} relation that is concave down, while the observed relation is linear.
 Based on this discrepancy, C may be more efficiently produced in lower mass AGB stars than predicted by stellar models (see Fig.~\ref{fig:sims_degens}), which would increase characteristic delay times and linearize the \caafe{} trend.
-This discrepancy could also be resolved by a less extended DTD for SN Ia.
+This discrepancy could also be resolved by a less extended DTD for SN Ia, but such an adjustment would be in tension with recent GCE models \citep{palicio+2024, dubay+24}.
 
@@
 Instead, either a larger AGB contribution to C is required, disfavoured by the subgiant trends, or a complex, non-monotonic massive-star production of C is needed.
+Letting the massive star C yield vary non-linearly with metallicity indeed improves agreement with all of the data that we have considered in this paper.
 
 As in \citet{james+23}, our models constrain relative as opposed to absolute yields due to the degeneracy between the overall scale and the strength of outflows \citep[e.g.,][]{hartwick1976,james+23, sandford+24}.
-Rescaling both parameters by similar multiplicative factors leaves the predicted \caah{} relation largely unchanged to first order (see Fig.~\ref{fig:sims_degens}).
-Breaking this degeneracy requires either age measurements to pin down enrichment time-scales \citep{james+24}, chemical species produced during Big Bang Nucleosynthesis present in accreting gas \citep{cooke+2022}, or independent constraints from observations of SN \citep[e.g.,][]{rodriguez+23,david_fe}.
-However, our constraints on the ratio of C/Mg yields, its metallicity dependence, and the AGB contribution to C are robust, as we only consider C through yield ratios.
+Rescaling both parameters by similar multiplicative factors leaves the predicted \caah{} relation largely unchanged, to first order (see Fig.~\ref{fig:sims_degens}).
+Breaking this degeneracy requires either age measurements to pin down enrichment time-scales \citep{james+24}, chemical species produced during Big Bang Nucleosynthesis present in accreting gas \citep{cooke+2022, james+25}, or independent constraints from observations of SN \citep[e.g.,][]{rodriguez+23,david_fe}.
+However, our constraints on the ratio of C/Mg yields, its metallicity dependence, and the AGB star contribution to C should be robust.
+\red{(potentially join these paragraphs, if it wouldn't be too long)}
 
 As we constrain the yield ratio, variations in the Mg yield may help explain the [C/Mg] trends.
-While we focus on variations on the C yield alone, our constraint is nevertheless on the C/Mg yield ratio.
-$\alpha$-elements like Mg and O, produced primarily in CCSN, are typically expected and observed to have mostly metallicity-independent yields \citep[e.g.,][]{weinberg+19}.
-Although, the details of the origin of the metallicity dependence of C and Mg remain uncertain.
-
-While we focus on median trends, the scatter of the trends may include additional information about C production.
-We find that our model predicts a similar scatter as observed in subgiants in the \caafe{} and \caah{} trends (not shown).
+$\alpha$-elements like Mg and O, produced primarily in CCSN, are thought to have mostly metallicity-independent yields \citep{andrews+17}.
+Observationally, the [O/Mg] ratio is approximately solar across most of APOGEE, consistent with this expectation  \citep[][]{weinberg+19}.
+Nonetheless, our results do not rule out metallicity-dependent O and Mg production on their own.
+
+%While we focus on median trends, the scatter may include additional information about C production.
+Our model predicts a similar scatter as observed in subgiants in the \caafe{} and \caah{} trends, though we do not focus on abundance scatter in this paper.
 Further investigation into the detailed distribution of C abundance ratios with metallicity and $[\alpha/{\rm Fe}]$ may reveal more information about the origin of the elements.
+%\red{(this paragraph isn't saying anything wrong, but frankly, it's also not really adding anything.
+I'd just remove it since we don't really go into abundance scatter -- the nod to Berg et al.
+2019 at the end of section 7 is enough.)}
 
 Our results in this paper demonstrate the utility of empirically calibrated stellar yields.
-Due to the sensitivity of nucleosynthetic yields to poorly understood stellar evolution processes, such as mass loss and convection, these results provide a useful benchmark for stellar models (see discussion in, e.g., \citealt{gil-pons+2022}).
+Due to the sensitivity of metal production to poorly understood stellar evolution processes, such as mass loss and convection, these results provide a useful benchmark for stellar models (see discussion in, e.g., \citealt{gil-pons+2022}).
 With larger samples and more reliable abundance measurements from upcoming spectroscopic surveys, such as SDSS-V's Milky Way Mapper program \citep{kollmeier+25}, our understanding of metal production and the assembly history of our Galaxy will sharpen.
@@
 \section*{Acknowledgements}
-This paper uses \apogee\ data \citep{apogee_instrumentation, apogee17, aspcap}. \apogee{} is  part of SDSS-IV \citep{sloan_telescope, sdss_iv_overview, sdss17}.
+
+We thank Falk Herwig for helpful comments and discussion.
+
+This paper uses APOGEE data \citep{apogee_instrumentation, apogee17, aspcap}. APOGEE is  part of SDSS-IV \citep{sloan_telescope, sdss_iv_overview, sdss17}.
 
@@
 
-\section{Model parameters and details}
+\section{Model parameters and measurement scatter} \label{sec:extra_scatter}
 
@@
 	\centering
-        \caption[]{Description of the yields used for models presented in this paper.}
+        \caption[]{Description of the yields used for models presented in this paper (see Sections \ref{sec:agb}, \ref{sec:vice}, and \ref{sec:results} for details).}
 	\label{tab:model_parameters}
@@
 
-\ref{tab:model_parameters} lists the parameters of the models used in this paper.
-
-For our added scatter, we use the polynomial fits to the reported internal APOGEE error with metallicity.
-In detail, these polynomials should also vary with surface gravity and effective temperature.
-However, as all of our stars are subgiants, these effects should be smaller.
-We also use $x={\rm [Fe/H]}$ for brevity.
+Table \ref{tab:model_parameters} lists the parameters of the models used in this paper.
+
+To add artificial scatter into our models, we use the polynomial least-squares fits to the reported internal APOGEE error with metallicity: 
 \begin{subequations}
@@
     \delta {\rm [Mg/Fe]} &= 0.00793\,x^2 - 0.00802\,x + 0.0138 \\
-    \delta {\rm [C/Mg]} &= -0.0378\,x + 0.03506 
+    \delta {\rm [C/Mg]} &= -0.0378\,x + 0.03506,
 \end{align}
 \end{subequations} 
+where $x = {\rm [Fe/H]}$ for brevity.
+In detail, these polynomials should also vary with surface gravity and effective temperature.
+However, as all of our stars are subgiants, these effects should be smaller.
 
@@
 In this Section, we present updated calculations of the \citet{battino+19, battino+21} yield tables and describe their incorporation into \VICE.
-These models use the NuGrid MPPNP post-processing toolkit on models run through {\rm mesa} stellar evolution.
+These models use the NuGrid MPPNP post-processing toolkit on models run using the \textsc{mesa} stellar evolution code \citep{mesa}.
 
 \citet{battino+19, battino+21} update the \citet{ritter+18} yield models with new reaction rates and increased mixing.
-These changes allow for better production of {\it s}--process isotopes in their AGB stars, and are recommended for the masses they update.
+These changes allow for an improved treatment of {\it s}--process isotopes in their models.
 However, between these models, the only updates are for masses 2 and $3\,\Mo$ at metallicities $Z=0.01, 0.02, 0.001, 0.002$.
@@
 
-\section{MCMC additional results}
-
-Fig.~\ref{fig:mcmc} shows the distribution and correlation of each parameter in our MCMC model fit to the C yields described in Section~\ref{sec:nucleosynthesis}, assuming the \fruity{} AGB table.
+\section{MCMC additional results}\label{sec:extra_mcmc}
+
+Fig.~\ref{fig:mcmc} shows the posterior distributions of our MCMC fit to the C yield models, described in Section~\ref{sec:mcmc}, assuming the \fruity{} AGB table.
 Each parameter is relatively well-constrained.
-The most prominent correlation, between $\yl$ and $\aagb$, represents the constraint on the equilibrium abundance of C near solar.
+The most prominent degeneracy, between $\yl$ and $\aagb$, represents the constraint on the equilibrium abundance of C near solar.
 Another clear correlation, between $\yl$ and $\zcc$, is related to the solar yield constraint as well, allowing a narrow range of $\zcc$ values while retaining the solar $\yo = \yl + \zcc$ yield.
 
-Table~\ref{tab:mcmc_results} contains the resulting posterior distributions for each parameter for each AGB model and GCE parameter choice discussed here.
+Table~\ref{tab:mcmc_results} provides the best-fit median values and quantile-uncertainties for each parameter for each AGB yield table and GCE model discussed here.
 
@@
     \caption{
-        Best-fit parameters (medians and 16-84th percentile ranges) from MCMC analysis for various models discussed.
+        Best-fit parameters (medians and 16-84th percentile ranges) from our MCMC fit for each model discussed (see Section~\ref{sec:mcmc}).
         The columns are:  the model name, best-fitting log posterior probability $\log p$, AGB scaling $\aagb$, CCSN low-metallicity yield $\yl$, the CCSN yield slope $\zcc$, the AGB fraction $\fagb$, and the total C yield at solar metallicity $\Yct$.
@@
 \caption[]{
-A corner plot of the posterior samples from the MCMC simulation for the analytic model fit to the binned mean trends.
+The posterior distributions from the MCMC simulation for the analytic model fit to the mean abundance trends (see Section~\ref{sec:mcmc_methods}).
 $\aagb$ represents the scale factor for the AGB yields, and $\yl$, $\zcc$ represent the constant and linear components of the CCSN yield. 
-See Section~\ref{sec:mcmc_methods} for a description of the methods.
-
 }

### 2025-11-25 carbon_paper/tex/main.tex
carbon paper arxiv version

@@
 \newcommand{\red}[1]{{\color{red} #1}}
-\newcommand{\strike}[1]{{\color{red} \sout{#1}}}
+\newcommand{\add}[1]{\red{#1}}
+%\newcommand{\strike}[1]{\red{\sout{#1}}}
+%\newcommand{\replace}[2]{\red{\sout{#1}} \red{#2}}
 
@@
 \author[D. A. Boyea et. al.]{%
-Daniel A. Boyea,$^{1, 2}$\thanks{%
+Daniel A. Boyea,$^{1, 2, 3}$\thanks{%
 Contact e-mail:~\href{mailto:danielaboyea@gmail.com}{danielaboyea@gmail.com}}
-James W. Johnson,$^{2, 3, 4}$
+James W. Johnson,$^{4, 2, 3}$
 and
-David H. Weinberg$^{2,4}$
+David H. Weinberg$^{2,3}$
 \\
@@
 \\
-$^{3}$The Observatories of the Carnegie Institution for Science, 813 Santa Barbara St., Pasadena, CA, 91101, USA
-\\
-$^{4}$Center for Cosmology \& Astroparticle Physics (CCAPP), The Ohio State University, 191 W. Woodruff Ave., Columbus, OH, 43210, USA
+$^{3}$Center for Cosmology \& Astroparticle Physics (CCAPP), The Ohio State University, 191 W. Woodruff Ave., Columbus, OH, 43210, USA\\
+$^{4}$The Observatories of the Carnegie Institution for Science, 813 Santa Barbara St., Pasadena, CA, 91101, USA
 }
@@
 % nuance
-Artificially shifting the AGB C yields to lower masses also improves agreement with the [C/Mg]-[Mg/Fe] trend, possibly indicating a discrepancy with stellar evolution predictions or our assumed Fe production rate.
+Artificially shifting the AGB C yields towards lower mass stars with longer lifetimes also improves agreement with the observed [C/Mg]-[Mg/Fe] trend, possibly indicating a discrepancy with stellar evolution predictions or our assumed Fe production rate.
 \end{abstract}
@@
 ${\sim}0.01\,\Mo$  have significant effects on the evolution and explosion outcomes of massive stars \citep{bruenn+2023, vartanyan_burrows2023}.
-Most yield tables have far courser initial-mass resolution.
+Most yield tables have far coarser initial-mass resolution.
 Furthermore, many stars are found in binary systems \citep{sana+12}, the effects of which are almost entirely
@@
 While any abundance trend likely suffers from systematic biases, we find that these biases do not impact our qualitative conclusions. 
-We have also consider subgiants and dwarfs with similar selection criteria from GALAH DR4 \citep{galah_dr4}, Gaia-ESO DR5.1 \citep{gaiaeso_dr5.1}, LAMOST \citep{lamost}, and mixing-corrected APOGEE giants \citep{vincenzo+21}.
+We have also considered subgiants and dwarfs with similar selection criteria from GALAH DR4 \citep{galah_dr4}, Gaia-ESO DR5.1 \citep{gaiaeso_dr5.1}, LAMOST \citep{lamost}, and mixing-corrected APOGEE giants \citep{vincenzo+21}.
 All of these samples show similar trends in \caah\ and \caafe{}, but with global systematic offsets of ${\sim} 0.1\,{\rm dex}$ and slight differences in the slope of each trend.
@@
 (Note that the shape of the integrated yields arises from our linear interpolation of yields in $Z$.
-Changing to interpolation linear in $\log Z$ does not substantially affect our results.)
+Changing to linear interpolation in $\log Z$ does not substantially affect our results.)
         \textbf{Right:} Cumulative C production as a function of age for a single stellar population of metallicity $\log Z/\Zo=-0.1$.
@@
 Additionally, the slope varies by a factor of ${\sim}3$.
-Both \nugrid{} and \aton{} predict non-monotonic C yields with $Z$, but modelling systematics may exceed the scale of non-monotonic features.
+Both \nugrid{} and \aton{} predict slightly non-monotonic C yields with $Z$, but modelling systematics may exceed the scale of non-monotonic features.
 These variations are due to different choices of reaction rates, convection treatments, and mass-loss rates (see discussion below and \citealt{james+23}).
@@
 This quantity should approximately represent the fraction of the Sun's birth C abundance originating from AGB stars.
-Although, since the Sun was not enriched entirely by solar metallicity predecessors, the equivalence of $\fagb{}$ to the yield ratio is not exact.
+However, since the Sun was not enriched entirely by solar metallicity predecessors, the equivalence of $\fagb{}$ to the yield ratio is not exact.
 
@@
     \caption[]{For each AGB yield set, the IMF-averaged AGB C yield at solar metallicity $y_{\rm C, 0}^{\rm AGB}$, the fraction of solar C produced in the model $f_\odot^{\rm AGB}$, and the masses and metallicities each yield table is sampled on.
-    $f_{\sun}^{\rm AGB}$ is calculated based on $y_{\rm C, \sun}^{\rm AGB}$ assuming the fiducial total C yield of $\Yct = 26.7\times 10^{-4}$.
+    $f_{\sun}^{\rm AGB}$ is calculated based on $y_{\rm C, \sun}^{\rm AGB}$ assuming the fiducial total C yield of $\Yct = 26.7\times 10^{-4}$ and $\aagb=1$.
     }
@@
 Massive stars form $^{12}$C in their cores through the triple-$\alpha$ reaction (He-burning), which is later released to the ISM through winds and supernovae.
-Both material ejected through stellar winds and through CCSN contribute to C production, although we refer to CCSN and massive star enrichment interchangeably.
+Both material ejected through stellar winds and through supernovae contribute to C production, but we generally use the term CCSN to refer to the sum of both modes of massive star enrichment.
 
@@
 Fig.~\ref{fig:y_cc} shows the integrated yields of massive star models from the literature.
+At solar metallicity, \citepos{sukhbold+16} C yield is $\approx0.5$ dex higher than \cite[non-rotating]{LC18}, likely driven by much stronger (C-enhanced) mass loss in \citet{sukhbold+16} for stars more massive than $\gtrsim40\,\Mo$.
  The \cite{LC18} models, which include rotation, show that the induced mixing (e.g., \citealt{frischknecht+16}) can dramatically increase the magnitude and metallicity dependence of $\Ycc$.
@@
 The linear prescription likely does not fully capture C production by massive stars, but more complex models do not significantly alter our conclusions. 
+As shown in Fig.~\ref{fig:y_cc}, the fiducial parameters imply a yield that agrees reasonably well with the model predictions at low $Z$ and a metallicity dependence in between that of \citeauthor{LC18}'s (\citeyear{LC18}, LC18) non-rotation and $v_{0}=300\,{\rm km\,s^{-1}}$ models.
 
@@
 
-We use the radial migration prescription described in appendix C of \citet{dubay+24} and summarized in Section 3 of \citet{james+24}.
-The total distance each star moves is sampled from a normal distribution with standard deviation $\sigma_R =  2.68\,{\rm kpc} \ (R/8\,{\rm kpc})^{0.61}\,(\tau / 8\,{\rm Gyr})^{0.33}$.
-Stars migrate from their initial to their final positions with a cube-root time-dependence.
+We use the radial migration prescription described in appendix C of \citet{dubay+24} and summarized in section 3 of \citet{james+24}.
+The total distance each star moves is sampled from a Gaussian distribution with standard deviation $\sigma_R =  2.68\,{\rm kpc} \ (R/8\,{\rm kpc})^{0.61}\,(\tau / 8\,{\rm Gyr})^{0.33}$.
+Stars migrate from their initial to their final positions with a cube-root time dependence.
 These parameters arise from \citepos{dubay+24} analytic approximation of the {\tt h227} simulation \citep{bird+21, christensen+12, zolotov12, loebman12, BZ14}.
@@
 is adapted from \citet{hayden+14} assuming Mg is representative of $\alpha$ elements.
-The recycling correction $r\approx 0.4$ accounts for the return of stellar envelopes back to the ISM (for a \citealt{kroupa01} IMF after 10 Gyr; see Section 2 from \citealt{WAF17}).
-This choice of $\eta(R)$ results in a [$\alpha$/H] gradient consistent with APOGEE measurements \citep[e.g.,][]{hayden+14, weinberg+19, frinchaboy+13}.
+The recycling correction $r\approx 0.4$ accounts for the return of stellar envelopes back to the ISM (for a \citealt{kroupa01} IMF after 10 Gyr; see section 2 from \citealt{WAF17}).
+This choice of $\eta(R)$ results in a [$\alpha$/H] gradient consistent with APOGEE measurements \citep[e.g.,][]{frinchaboy+13, hayden+14, weinberg+19}.
 Compared to \citet{james+21, james+24}, our metallicity gradient is flatter within 5 kpc (and our $\eta\to0$ at similar radius).
@@
 Our AGB N yield is scaled from \citep[eq.
-14]{james+23}, based on the differences in our assumed solar  N/O ratio.
-The CCSN N/O yield is additionally enhanced by a factor of 2.5 to account for the difference in median solar [N/Mg] values from \citet{vincenzo+21} and APOGEE subgiants.
-Following \citet{james+23}, we use a $t^{-1.1}$  delay time distribution (DTD) with a minimum delay-time of 150 Myr, based on comparisons of the SN Ia rate as a function of redshift and the cosmic SFR (e.g., \citealt{maoz+mannucci12}).
+14]{james+23}, based on the differences in the assumed solar N/O ratio and the median [N/Mg] or [N/O] value of each sample.
+Following \citet{james+23}, we use a $t^{-1.1}$  delay time distribution (DTD) for SN Ia with a minimum delay-time of 150 Myr, based on comparisons of the SN Ia rate as a function of redshift and the cosmic SFR (e.g., \citealt{maoz+mannucci12}).
 We assume $2.2\times10^{-3}$ SN Ia events per unit mass of star formation with a mean $0.355\,\Mo$ of new Fe produced per supernova.
@@
 The solar abundance scale is \citet{magg+22} corrected upwards by 0.04 dex for gravitational settling and diffusion \citep{david_fe}.
+For $\Ycc$, the fiducial yield is given by Eq.~\ref{eq:y_cc} with $\yo=18.7\times10^{-4}$ and $\zcc=7.9\times10^{-4}$.
     }
@@
 
-Fig.~\ref{fig:c_evo} shows evolutionary tracks in \caah{} and \caafe{} in the fiducial model at 1\,kpc intervals of radius.
+Fig.~\ref{fig:c_evo} shows evolutionary tracks in \caah{} and \caafe{} in the fiducial model at 1\,kpc intervals of radius (with C yields defined in Section~\ref{sec:nucleosynthesis}).
 The \caah\ trend reaches an equilibrium state within \about{5}\,Gyr. \caafe\ tracks continue to evolve due to the long tail of the SN Ia DTD.
@@
 [Mg/Fe] is initially high due to the delayed production time-scales of SN Ia Fe, as expected from the analytic models of \citet{WAF17}.
- Of order 100 Myr later, delayed sources enrich the ISM. AGB stars release C, raising [C/Mg], and SN Ia expel Fe, lowering [Mg/Fe]. 
+ Of order 100 Myr later, delayed sources enrich the ISM. AGB stars release C, raising [C/Mg], and SN Ia release Fe, lowering [Mg/Fe]. 
  Several Gyr later, [Mg/H] reaches equilibrium.
@@
 metallicity dependence, and their DTDs.
-As we will demonstrate in Section~\ref{sec:agb_results} below, the final slope of the \caah\ trend depends mostly on the metallicity dependence of the total C yield.
+As we will demonstrate in Section~\ref{sec:agb_results} below, the final locus of the \caah\ trend (the end points of the curves in the left panel) depends mostly on the metallicity dependence of the total C yield.
 The \caafe{} trend instead reveals the nature of delayed C production.
@@
 As an additional test of both yield models, we combine a rescaled version of their recommended N yields (see discussion in Section~\ref{sec:vice}) with our fiducial choice of C yields.
+The rescaling is needed because we assume a lower $\Ymg$ and our sample has a higher median [N/Mg] than in \citet{james+23}.
 Fig.~\ref{fig:nitrogen} shows [C/N] versus [Mg/H] as predicted by our fiducial model. We are indeed able to closely match the observed [C/N]-[Mg/H] trend.
@@
 
-The top row of Fig.~\ref{fig:zeta_f} shows models with varying strengths of the $\Ycc$ metallicity dependence, $\zcc$ (see Eq.~\ref{eq:y_cc}).
+The top row of Fig.~\ref{fig:zeta_f} shows models with varying strengths of the $\Ycc$ metallicity dependence, $\zcc$ (see Eq.~\ref{eq:y_cc} and parameters in Table~\ref{tab:model_parameters}).
 With higher $\zcc$, the model predicts a steeper \caah\ trend, owing to the direct relationship between equilibrium [C/Mg] and yield ratios in Eq.~\ref{eq:c_mg_cc}.
@@
 
-The middle row of Fig.~\ref{fig:zeta_f} shows three models with different C AGB  fractions (Eq.~\ref{eq:f_agb}).
+The middle row of Fig.~\ref{fig:zeta_f} shows three models with different C AGB  fractions (Eq.~\ref{eq:f_agb}; parameters in Table~\ref{tab:model_parameters}).
 At fixed metallicity, the \caafe\ trend is principally sensitive to how much C and Fe come from delayed sources.
@@
 All AGB yield tables predict a similarly shaped trend in the \caafe{} abundance space.
-The left panel of Fig.~\ref{fig:sims_degens} shows the best-fitting AGB yield models (see Section \ref{sec:mcmc} for methodology) for each yield table we consider.
+The left panel of Fig.~\ref{fig:sims_degens} shows the best-fitting yield combinations for each AGB table we consider (solving for $\aagb$, $\yo$, and $\zeta$ in Section \ref{sec:mcmc}; yield parameters in Table~\ref{tab:model_parameters}).
 Although the individual DTDs of each AGB table appear substantially different (Fig.~\ref{fig:agb-ssp}), the predicted abundance trends do not show substantial differences.
-This outcome arises because each of our AGB models predict characteristic delay times for C production of order ${\sim}1$ Gyr, similar to the SN Ia production of Fe (see Figure 3), leading to a quasi-linear [C/Mg]-[Mg/Fe] relation in all cases.
-
-However, all AGB tables predict a slightly concave down trend because C production by single stellar populations slows down significantly after a $\sim$few Gyr, while Fe production through SNe Ia continues up to ${\sim}10$ Gyr (see discussion in Section~\ref{sec:agb}).
+This outcome arises because each of the AGB models predicts characteristic delay times for C production of order ${\sim}1$ Gyr, similar to the SN Ia production of Fe (see Fig.~\ref{fig:agb-ssp}), leading to a quasi-linear [C/Mg]-[Mg/Fe] relation in all cases.
+
+However, all AGB tables predict a slightly concave down trend because C production by single stellar populations slows down significantly after a few Gyr, while Fe production through SNe Ia continues up to ${\sim}10$ Gyr (see discussion in Section~\ref{sec:agb}).
 Our subgiant sample does not exhibit this level of concavity.
-These discrepancies are significant because Figure \ref{fig:sims_degens} plots the mean trend, which is precisely determined through the large sample size.
+These discrepancies are significant because Fig.~\ref{fig:sims_degens} plots the mean trend, which is precisely determined through the large sample size.
 One of the largest discrepancies between our models and data in the left panel is that \aton{} and \monash{} predict an almost flat \caafe{} trend for ${\rm [Mg/Fe]} \lesssim 0.1$.
@@
 These discrepancies in the [C/Mg]-[Mg/Fe] trend indicate that C production by single stellar populations may be more extended than our yield models predict.
-We explore this possibility further in the middle panel of Figure \ref{fig:sims_degens}, which shows variations of our fiducial model in which we artificially multiply the AGB star progenitor mass by factors of $0.5$, $0.7$, and $1.5$.
+We explore this possibility further in the middle panel of Fig.~\ref{fig:sims_degens}, which shows variations of our fiducial model in which we artificially multiply the AGB star progenitor mass by factors of $0.5$, $0.7$, and $1.5$.
 When the AGB C production is weighted towards more massive AGB stars, the DTD becomes more rapid, leading to higher [C/Mg] at high [Mg/Fe].
@@
         Similar to Fig.~\ref{fig:zeta_f}, but focusing on [C/Mg] versus [$\alpha$/Fe].
-        {\bf Left:} The best-fitting model for each AGB table, and the best-fitting model from the middle panel with a mass shift of 0.7. 
+        {\bf Left:} The best-fitting yield combination for each AGB table and the \fruity{} table with a mass shift of 0.7.
+We fit $\aagb$, $\yo$, and $\zeta$ using the method in Section~\ref{sec:mcmc_methods}.
         {\bf Middle:} Models where the \fruity{} AGB yields are artificially shifted by different multiplicative factors in progenitor mass, but maintaining the same $\fagb$. 
@@
 Lastly, we demonstrate that our conclusions are unaffected by the assumed scale of stellar yields and mass loading in outflows.
-The fiducial yield scale adopted here, from \citet{david_fe}, is relatively low, requiring only moderate outflows to reproduce solar metallicity.
+The fiducial yield scale adopted here, from \citet{david_fe}, is relatively low.
+We require only moderate outflows to reproduce solar metallicity.
 However, models with higher outflows and higher yields give similar predictions because of the
@@
 
-In this section, our goal is to convert the qualitative understanding described up to this point into more quantitative constraints on C yields. 
-In Section~\ref{sec:results}, we showed that the \caah{} trend reflects the overall metallicity dependence of the total C yield from single stellar populations, while the \caafe{} trend reflects the amount of delayed C and its DTD.
-Here, we construct Monte-Carlo Markov chain (MCMC) models to explore possible abundance combinations matching the observed trends.
-From these models, we can derive the distributions of likely properties of underlying C yields given current observations.
-
-\subsection{Monte-Carlo Markov Chain yield inference} \label{sec:mcmc_methods}
-
-To efficiently explore a wide range of yield combinations, we use an approach that we refer to as {\it process tracking}.
-In GCE, total elemental abundances are (to first order) linear with respect to combinations of yields \citep[e.g.,][]{WAF17}.
-Process tracking exploits this linearity to integrate the CCSN and AGB yields separately, later expressing the C abundance as a linear combination of the two.
-We set up \VICE {} to integrate each process for C as different chemical elements.
-The C abundances then follow as $Z_\text{C,tot} = \sum a_i Z_i$, where $a_i$ and $Z_i$ are the amplitude and abundance evolution of the $i$th process. \red{ (join these two paragraphs?)}
-
-We emphasize that there are some limitations to the process-tracking approximation.
-Capturing the effects of many other GCE parameters -- such as the star formation history, outflows, and radial migration prescriptions --  require separate multi-zone integrations for each parameter variation.
-Metallicity-dependent yields also introduce a second-order effect (metallicity depends on total yields, which influence the metallicity), but this effect should be insignificant for small changes to total yields.
-
-Our first step is to run a multi-zone model tracking the abundances of each process we are interested in (in this case, CCSN and AGB star products). 
-To use all the information available for [C/Mg] trends with [Mg/Fe] and [Mg/H], we calculate the mean $Z_\text{C} / Z_\text{Mg}$ for each 2D bin in [Mg/Fe] and [Mg/H] for both the data and the model.
-We add Gaussian-distributed measurement uncertainties to the model's stars as described in the Appendix~\ref{sec:extra_scatter}.
-We use bins with a constant width of 0.04 dex, ranging from ${\rm [Mg/H]}=[-0.5, 0.5]$ and ${\rm [Mg/Fe]} = [-0.1, 0.4]$.
-We remove 2D bins with fewer than 3 stars in either the model or data.
-We separate the C yield  into three different components:
-\begin{enumerate}
-    \item $\aagb$: Prefactor for an AGB yield table
-    \item $\yl$: Constant CCSN yield 
-    \item $\zcc$: Linear CCSN yield ($y = \zcc (Z/\Zo)$)
-\end{enumerate}
-$\yl$ represents the C yield at low metallicity.
-When $Z \to\rightarrow 0$, Eq.~\ref{eq:y_cc} indicates that $\yl = \yo - \zcc$.
-
-We construct a likelihood function based on the difference in the mean $Z_\text{C}/Z_\text{Mg}$ between the data and model in each bin. 
-We use the linear as opposed to logarithmic C abundance (i.e., [C/H]) because the linear combination of enrichment channels from process tracking predicts $Z_\text{C}$. 
-Given the predicted abundance for the model in a given bin $b$,  $Z_{\rm C, \it b}^{\rm model}$, the associated observed abundance, $Z_{\rm C, \it b}^{\rm obs}$, and the error on the mean $\sigma_b$, the (Gaussian) log likelihood is given by
-\begin{equation} \label{eq:mcmc_likelihood}
-    \log {\cal L} = \sum_b -\ln(\sigma_{b}) -\left(\frac{Z_{\rm C, \it b}^{\rm model} - Z_{{\rm C}, b}^{\rm obs}}{2\sigma_{b}}\right)^2 - \frac{1}{2}\log(2\pi).
-\end{equation}
-We calculate the total variance in each bin from the standard error on the mean of the observations in a bin $\sigma_{b, \rm obs}$, the standard error on the mean for each model component $i$, $\sigma_{b, i,\rm model}$, and a {\it systematic} uncertainty term $\sigma_{\rm sys}$.
-Altogether,
-\begin{equation}
-    \sigma_{b}^2 = \sigma_{\rm sys}^2 + \sigma_{b,\rm\ obs}^2  +  \left(\sum_{i} a_i\, \sigma_{b,i,\ \rm model}\right)^2
-\end{equation}
-where $a_i$ is the associated coefficient ($\aagb$, $\yl$, $\zcc$) for each yield process.
-We add the model standard deviations linearly since the C abundances are calculated from the same sample for each process.
-
-When included, $\sigma_{\rm sys}$ represents a systematic uncertainty.
-We consider models with both $\sigma_{\rm sys} = 0$ and 0.05 dex.
-While approximate, $0.05$ dex is similar to typical mean deviations between APOGEE and the C and Mg abundances in other surveys \citep{hegedhus+2023, jonsson+2018}.
-Discrepancies between APOGEE's reported abundance uncertainties and other measurements of dispersion indicate a similar level of systematic error \citep{mead+2024}.
-While systematic uncertainties are unlikely to be well-described by an independent, uncorrelated, constant-width normal distribution, we use this parameter as an approximation of the likely uncertainties of our results.
-
-We adopt loose priors for each model parameter: $\aagb \sim N(1, 1)$, $\zcc \sim N(0, 10^{-3})$, and $\yl \sim N(2\times10^{-3}, 1\times10^{-3})$, where $N(\mu, \sigma)$ is a Gaussian distribution with mean $\mu$ and standard deviation $\sigma$.
-We run the MCMC using Turing.jl \citep{turingjl} with a No-U-turn sampler (an adaptive Hamilton Monte-Carlo algorithm, \citealt{NUTS}) with an acceptance rate of 0.65.
-We combine 16 independent chains with 3,000 steps each for a total of 48,000 samples.
-The median parameters derived from this model provide the yield choices for the AGB yield models shown in the left panel of Fig.~\ref{fig:sims_degens}.
-
-\subsection{Yield inference results} \label{sec:mcmc_results}
-
-Based on the procedure above, we derive our best-fitting (not fiducial described in Section~\ref{sec:agb}) yield set.
-For the \fruity{} AGB yield set, we find $\aagb = 1.55$, $\yo =22.3\times10^{-4}$, and $\zcc=7.9\times10^{-4}$.
-For the model where \fruity{} is shifted by a mass factor of 0.7, we instead find $\aagb = 2.34$, $\yo = 19.7\times 10^{-4}$ and $\zcc=3.2\times 10^{-4}$.
-The fiducial yields enforce a low-metallicity [C/O] plateau of \about{-0.5} for better agreement in Section~\ref{sec:gas}.
-We present the best-fitting parameters for each model or yield set considered here in Appendix~\ref{sec:extra_mcmc}.
-
-The left panel of Fig.~\ref{fig:mcmc_ytot} shows the inferred total C yield for each AGB yield table, along with the \fruity{} table shifted in mass by a prefactor of 0.7.
-While there is some variability, all models predict  a dynamic range of $y_\text{C}^\text{tot} / y_\text{Mg}$ of approximately $\sim$$0.5$.
-Therefore, the choice of AGB yield table only slightly affects the inferred total yield.
-
-The middle panel of Fig.~\ref{fig:mcmc_ytot} shows the inferred AGB fraction (Eq.~\ref{eq:f_agb}) at solar metallicity for each model.
-No model predicts a median $\fagb > 0.3$ and the 98th percentile upper-limits are all below $\fagb=0.4$.
-All models except \aton{} predict that at least $\approx 8$ per cent of the solar C comes from AGB stars (from the 2nd percentile lower-limits).
-The SFH and overall yield scale have little impact on the inferred $\fagb$.
-All of our yield models favour a scenario in which AGB stars are responsible for less than half of the C present in near-solar metallicity environments.
-
-The right panel of Fig.~\ref{fig:mcmc_ytot} compares the inferred scaling of AGB yields, $\aagb$. For most tables, we find $\aagb$ near unity, indicating accurate total C yields from AGB stars.
-Doubling our yields results in higher values of $\aagb$ in order to produce more C at fixed $\fagb$.
-For \monash{} and \aton{}, $\aagb$ is almost exactly $1$.
-However, these models struggle to reproduce the [C/Mg]-[Mg/Fe] relation, which suggests issues related to the mass-dependence of the yields (see discussion in Section \ref{sec:agb_results}).
-
-By including the $\sigma_{\rm sys}$ parameter, the posterior distributions of $\fagb$, $\aagb$ and CC yield parameters all widen without changing our conclusions.
-Effectively, $\sigma_{\rm sys}$ reduces the weight of abundance differences between bins.
-Systematic errors likely dominate the uncertainty budget in this analysis.
-
-Finally, the choice of the Fe SN Ia DTD directly impacts our conclusions.
-From the right panel of Fig.~\ref{fig:mcmc_ytot}, we note that increasing the SN Ia Fe yield by a factor of 1.2 (and decreasing the CC Fe yield to maintain the same total Fe production) results in a similar increase in the inferred $\fagb$.
-Increasing the SN Ia contribution to Fe stretches the trends in [Mg/Fe], causing [C/Mg] to flatten with [Mg/Fe] unless the delayed C yield is also increased.
-In this framework, constraints on delayed C contributions are limited by our understanding of delayed Fe production.
-
 \begin{figure*}
@@
 
+In this section, our goal is to convert the qualitative understanding described up to this point into more quantitative constraints on C yields. 
+In Section~\ref{sec:results}, we showed that the \caah{} trend reflects the overall metallicity dependence of the total C yield from single stellar populations, while the \caafe{} trend reflects the amount of delayed C and its DTD.
+Here, we construct Monte-Carlo Markov chain (MCMC) models to explore possible abundance combinations matching the observed trends.
+From these models, we can derive the most likely C yields given current observations.
+
+\subsection{Monte-Carlo Markov Chain yield inference} \label{sec:mcmc_methods}
+
+To efficiently explore a wide range of yield combinations, we use an approach that we refer to as {\it process tracking}.
+In GCE, total elemental abundances are (to first order) linear with respect to combinations of yields \citep[e.g.,][]{WAF17}.
+Process tracking exploits this linearity to integrate the CCSN and AGB yields separately, later expressing the C abundance as a linear combination of the two.
+We set up \VICE {} to integrate each process for C as different chemical elements.
+The C abundances then follow as $Z_\text{C,tot} = \sum a_i Z_i$, where $a_i$ and $Z_i$ are the amplitude and abundance evolution of the $i$th process.
+
+We emphasize that there are some limitations to the process-tracking approximation.
+Capturing the effects of many other GCE parameters -- such as the star formation history, outflow, and radial migration prescriptions --  requires separate multi-zone integrations for each parameter variation.
+Metallicity-dependent yields also introduce a second-order effect (metallicity depends on total yields, which influence the metallicity), but this effect should be insignificant for small changes to total yields.
+
+Our first step is to run a multi-zone model tracking the abundances of each process we are interested in (in this case, CCSN and AGB star products). 
+To use all the information available for [C/Mg] trends with [Mg/Fe] and [Mg/H], we calculate the mean $Z_\text{C} / Z_\text{Mg}$ for each 2D bin in [Mg/Fe] and [Mg/H] for both the data and the model.
+We add Gaussian-distributed measurement uncertainties to the stars in the model as described in the Appendix~\ref{sec:extra_scatter}.
+We use bins with a constant width of 0.04 dex, ranging from ${\rm [Mg/H]}=[-0.5, 0.5]$ and ${\rm [Mg/Fe]} = [-0.1, 0.4]$.
+We remove 2D bins with fewer than 3 stars in either the model or data.
+We describe C yields with three different parameters:
+\begin{enumerate}
+    \item $\aagb$: Prefactor for an AGB yield table
+    \item $\yl$: Constant CCSN yield 
+    \item $\zcc$: Linear CCSN yield ($y = \zcc (Z/\Zo)$),
+\end{enumerate}
+where $\yl$ represents the C yield at low metallicity.
+When $Z \to 0$, Eq.~\ref{eq:y_cc} indicates that $\yl = \yo - \zcc$.
+
+We construct a likelihood function based on the difference in the mean $Z_\text{C}/Z_\text{Mg}$ between the data and model in each bin. 
+We use the linear as opposed to logarithmic C abundance (i.e., [C/H]) because the linear combination of enrichment channels from process tracking predicts $Z_\text{C}$. 
+Given the predicted abundance for the model in a given bin $b$,  $Z_{\rm C, \it b}^{\rm model}$, the associated observed abundance, $Z_{\rm C, \it b}^{\rm obs}$, and the error on the mean $\sigma_b$, the (Gaussian) log likelihood is given by
+\begin{equation} \label{eq:mcmc_likelihood}
+    \log {\cal L} = \sum_b -\ln(\sigma_{b}) -\left(\frac{Z_{\rm C, \it b}^{\rm model} - Z_{{\rm C}, b}^{\rm obs}}{2\sigma_{b}}\right)^2 - \frac{1}{2}\log(2\pi).
+\end{equation}
+We calculate the total variance in each bin from the standard error on the mean of the observations in a bin $\sigma_{b, \rm obs}$, the standard error on the mean for each model component $i$, $\sigma_{b, i,\rm model}$, and a {\it systematic} uncertainty term $\sigma_{\rm sys}$.
+Altogether,
+\begin{equation}
+    \sigma_{b}^2 = \sigma_{\rm sys}^2 + \sigma_{b,\rm\ obs}^2  +  \left(\sum_{i} a_i\, \sigma_{b,i,\ \rm model}\right)^2
+\end{equation}
+where $a_i$ is the associated coefficient ($\aagb$, $\yl$, $\zcc$) for each yield process.
+We add the model standard deviations linearly since the C abundances are calculated from the same sample for each process.
+
+$\sigma_{\rm sys}$ represents a systematic uncertainty.
+We consider models with both $\sigma_{\rm sys} = 0$ and 0.05 dex.
+While approximate, $0.05$ dex is similar to typical mean deviations between APOGEE and the C and Mg abundances in other surveys \citep{hegedhus+2023, jonsson+2018}.
+Discrepancies between APOGEE's reported abundance uncertainties and other measurements of dispersion indicate a similar level of systematic error \citep{mead+2024}.
+While systematic uncertainties are unlikely to be well-described by an independent, uncorrelated, constant-width Gaussian distribution, we can nonetheless use this parameter as an approximation of the likely uncertainties of our results.
+
+We adopt the following priors for each model parameter: $\aagb \sim N(1, 1)$, $\zcc \sim N(0, 10^{-3})$, and $\yl \sim N(2\times10^{-3}, 1\times10^{-3})$, where $N(\mu, \sigma)$ is a Gaussian distribution with mean $\mu$ and standard deviation $\sigma$.
+We run the MCMC using Turing.jl \citep{turingjl} with a No-U-turn sampler (an adaptive Hamilton Monte-Carlo algorithm, \citealt{NUTS}) with an acceptance rate of 0.65.
+We combine 16 independent chains with 3,000 steps each for a total of 48,000 samples.
+The median parameters derived from this model provide the yield choices for the AGB yield models shown in the left panel of Fig.~\ref{fig:sims_degens}.
+
+\subsection{Yield inference results} \label{sec:mcmc_results}
+
+Based on the procedure above, we derive our best-fitting yield set (not the fiducial yields described in Section~\ref{sec:agb}).
+For the \fruity{} AGB yield set, we find $\aagb = 1.55$, $\yo =22.3\times10^{-4}$, and $\zcc=7.9\times10^{-4}$.
+Relative to our fiducial model, $\aagb$ is lower, but the normalization $\yo$ of the CCSN yield is higher.
+For the model where \fruity{} is shifted by a mass factor of 0.7, we instead find $\aagb = 2.34$, $\yo = 19.7\times 10^{-4}$ and $\zcc=3.2\times 10^{-4}$.
+The fiducial yields enforce a low-metallicity [C/O] plateau of \about{-0.5} for better agreement in Section~\ref{sec:gas}.
+We present the best-fitting parameters for each model or yield set considered here in Appendix~\ref{sec:extra_mcmc}.
+
+The left panel of Fig.~\ref{fig:mcmc_ytot} shows the inferred total C yield for each AGB yield table, along with the \fruity{} table shifted in mass by a prefactor of 0.7.
+While there is some variability, all models predict  a dynamic range of $y_\text{C}^\text{tot} / y_\text{Mg}$ of approximately $\sim$$0.5$.
+Therefore, the choice of AGB yield table only slightly affects the inferred total yield.
+
+The middle panel of Fig.~\ref{fig:mcmc_ytot} shows the inferred AGB fraction (Eq.~\ref{eq:f_agb}) at solar metallicity for each model (see also Table~\ref{tab:mcmc_results}). 
+In short, all of our yield models favour a scenario in which AGB stars are responsible for less than half, and likely near 20 per cent, of the C present in near-solar metallicity environments.
+No model predicts a median $\fagb > 0.3$ and the 98th percentile upper-limits are all below $\fagb=0.4$.
+All models except \aton{} predict that at least $\approx 8$ per cent of the solar C comes from AGB stars (from the 2nd percentile lower-limits).
+The SFH and overall yield scale have little impact on the inferred $\fagb$.
+
+The right panel of Fig.~\ref{fig:mcmc_ytot} compares the inferred scaling of AGB yields, $\aagb$. For most tables, we find $\aagb$ near unity, indicating accurate total C yields from AGB stars.
+Doubling our yields requires higher values of $\aagb$ to produce more C at fixed $\fagb$.
+For \monash{} and \aton{}, $\aagb$ is almost exactly $1$.
+For \aton{}, $\aagb=1$ is not unreasonable despite producing little C at solar metallicity because \aton{} produces similar C as other models at lower metallicities.
+However, these models struggle to reproduce the [C/Mg]-[Mg/Fe] relation, which suggests issues related to the mass-dependence of the yields (see discussion in Section \ref{sec:agb_results}).
+
+By including the $\sigma_{\rm sys}$ parameter, the posterior distributions of $\fagb$, $\aagb$, and CC yield parameters all widen without changing our conclusions.
+Effectively, $\sigma_{\rm sys}$ reduces the weight of abundance differences between bins.
+Systematic errors likely dominate the uncertainty budget in this analysis.
+
+Finally, the choice of the Fe SN Ia DTD directly impacts our conclusions.
+From the right panel of Fig.~\ref{fig:mcmc_ytot}, we note that increasing the SN Ia Fe yield by a factor of 1.2 (and decreasing the CC Fe yield to maintain the same total Fe production) results in a similar increase (${\sim}1.2\times$) in the inferred $\fagb$ .
+Increasing the SN Ia contribution to Fe stretches the trends in [Mg/Fe], causing [C/Mg] to flatten with [Mg/Fe] unless the delayed C yield is also increased.
+In this framework, constraints on delayed C contributions are limited by our understanding of delayed Fe production.
+
 \section{Gas-Phase Abundances}\label{sec:gas}
 
-\begin{figure*}
+\begin{figure*} % moved earlier for better placement
 \centering
@@
 in the gas phase.
-We consider measurements in Galactic and extragalactic \Hii{} regions, Damped Lyman-$\alpha$ systems\footnote{damped Lyman-$\alpha$ systems (or DLAs) are gas clouds observed as absorption spectra in front of background quasars}, and Milky Way halo main-sequence stars (all references in the caption of Figure 10, which we do not repeat here for brevity).
+We consider measurements in Galactic and extragalactic \Hii{} regions, Damped Lyman-$\alpha$ systems\footnote{damped Lyman-$\alpha$ systems (or DLAs) are gas clouds observed as absorption spectra in front of background quasars}, and Milky Way halo main-sequence stars (all references in the caption of Fig.~\ref{fig:gas_phase}, which we do not repeat here for brevity).
 While we used Mg as our representative alpha element in our APOGEE sample, we shift focus to O in this Section because O is more readily observed in the gas phase.
@@
 We use the same yields as our fiducial multi-zone model.
-Our GSE-like model is derived from \citet{james_dwarfs} except with adjusted outflows for our yield sclae.
-We adpot a constant mass loading of $\eta=5.74$, total star formation time of 10.73 Gyr, a constant star formation efficiency time-scales of 26.60 Gyr, and an exponential infall history $\dot \Sigma_{\rm in} = \exp(-t / 2.18\,{\rm Gyr})$ (in contrast to star formation rate specification for our fiducial model).
+Our GSE-like model parameters are derived from the best-fitting parameters of \citet{james_dwarfs}, except adjusting outflows to our yield scale.
+We adopt a constant mass loading of $\eta=5.74$, total star formation time of 10.73 Gyr, a constant star formation efficiency time-scales of 26.60 Gyr, and an exponential infall history $\dot \Sigma_{\rm in} = \exp(-t / 2.18\,{\rm Gyr})$ (in contrast to star formation rate specification for our fiducial model).
 In summary, the GSE-like model compared to our fiducial MW model does not include radial migration and has a more rapid star formation history, elevated outflows, and lower star formation efficiency.
 
-The gas-phase C abundances reveal a breakdown of our fiducial yield prescription.
+The gas-phase C abundances reveal a breakdown of our fiducial yield prescription (presented in Section~\ref{sec:nucleosynthesis}).
 While the fiducial model sits well within the scatter of C/O ratios observed in low-redshift \Hii{} regions near solar metallicity, the evolution of the $R = 8$ kpc annulus overestimates the mean [C/O] at lower metallicities.
@@
 A lower $y_{\rm low}$ also requires a higher $\fagb{}$ to reach the observed [C/Mg] near solar metallicity.
-However, a high $\fagb{}$ model would be in tension with the subgiant abundance trends (see Fig.~\ref{fig:gas_phase}).
-Based on these opposing indications of the value of $\fagb$ from our subgiant sample and the gas-phase data in Figure 10, it is difficult to reconcile the two observations in our models.
+However, a high $\fagb{}$ model would be in tension with the subgiant abundance trends (see Fig.~\ref{fig:mcmc_ytot}).
+Based on these opposing indications of the value of $\fagb$ from our subgiant sample and the gas-phase data in Fig.~\ref{fig:gas_phase}, it is difficult to reconcile the two observations in our models.
 
@@
 (3) As metallicity increases, massive star C yields steeply increase.
-In addition, C production from delayed AGB stars becomes more and more important, accelerating an increase of C abundances relative to O on approach to solar metallicity.
+In addition, C production from delayed AGB stars becomes more and more important, accelerating an increase of C abundances relative to O on the approach to solar metallicity.
 (4) Finally, in the regime of our own galaxy, the rapid increase of CCSN production of C may temper, procuring the gently sloping trend apparent in subgiants today.
@@
 \citet{berg+19} presented a suite of GCE models that complement our investigations in this section.
-They focused on the effects of the bursty SFHs that dwarf galaxies are thought to have experienced \citep[e.g.]{mcquinn+10} for a given yield prescription.
+They focused on the effects of the bursty SFHs that dwarf galaxies are thought to have experienced \citep[e.g.][]{mcquinn+10} for a given yield prescription.
 Our approach is the inverse; we have determined the effects of different choices of stellar yields with fewer considerations of the detailed SFH.
 Our models indicate that the exact choice of SFH is inconsequential to the subgiant abundance trends in APOGEE, primarily because our models predict a chemical equilibrium to arise early in the thin disk epoch.
-Advocated for by \citet{james+24} based on age-metallicity trends, the equilibrium scenario suggests that the abundance trends in our subgiant sample should reflect trends in C, Mg, and Fe yields (see Section 5).
+Advocated for by \citet{james+24} based on age-metallicity trends, the equilibrium scenario suggests that the abundance trends in our subgiant sample should reflect trends in C, Mg, and Fe yields (see Section~\ref{sec:results}).
 However, sudden bursts of star formation should always lead to chemical perturbations on some level, even in a state of equilibrium \citep{JW20}.
@@
 The observed increase in [C/Mg] with [Mg/H], however, implies that the total C yield increases with metallicity.
-This trend favours a scenario in which massive star yields of C increase with metallicity in order to compensate for the declining AGB star yields.
+This trend favours a scenario in which massive star yields of C increase with metallicity to compensate for the declining AGB star yields.
 This outcome could arise due to the heightened metallicity-dependent mass-loss in the rotating models of \citet{LC18}.
-C and Mg, however, do not provide substantial information on the relative contributions of prompt versus delayed production by high- and low-mass stars.
-Due to its sensitivity to SN Ia nucleosynthesis, the \caafe{} relation at fixed [Mg/H] is also sensitive to the amount of delayed C production.
+C and Mg alone, however, do not provide substantial information on the relative contributions of prompt versus delayed production by high- and low-mass stars.
+Instead, the \caafe{} relation at fixed [Mg/H] is sensitive to the amount of delayed C production, due to the sensitivity of [Mg/Fe] to delayed SN Ia nucleosynthesis.
 
@@
 We find that the best-fitting models require between ${\sim}0.6$ and 2 times more C than predicted by the chosen AGB table.
-However, if the yield scale is higher or lower than this assumed scale, the AGB C yield should be rescaled in proportion.
+
+A range of choices can fit the subgiant data modelled here, but one reasonable model based on our fit results is CCSN yields following Eq.~\ref{eq:y_cc} with $\yo=22.3\times10^{-4}$ and slope $\zcc=7.9\times10^{-4}$ and the \fruity{} AGB yields multiplied by a scaling factor $\aagb=1.55$.
+If the Mg yield $\Ymg$ is increased relative to our adopted value of $\Ymg=0.97\,Z_{\rm Mg, \odot}$, then all three C yield parameters should be boosted by the same factor.
 
@@
 However, our constraints on the ratio of C/Mg yields, its metallicity dependence, and the AGB star contribution to C should be robust.
-\red{(potentially join these paragraphs, if it wouldn't be too long)}
 
@@
 Further investigation into the detailed distribution of C abundance ratios with metallicity and $[\alpha/{\rm Fe}]$ may reveal more information about the origin of the elements.
-%\red{(this paragraph isn't saying anything wrong, but frankly, it's also not really adding anything.
+%%(this paragraph isn't saying anything wrong, but frankly, it's also not really adding anything.
 I'd just remove it since we don't really go into abundance scatter -- the nod to Berg et al.
-2019 at the end of section 7 is enough.)}
+2019 at the end of section 7 is enough.)
 
@@
 
-We thank Falk Herwig for helpful comments and discussion.
+We thank Falk Herwig and Jennifer Johnson for helpful comments and discussion.
 
@@
 
-Table~\ref{tab:mcmc_results} provides the best-fit median values and quantile-uncertainties for each parameter for each AGB yield table and GCE model discussed here.
+Table~\ref{tab:mcmc_results} provides the best-fit median values and quantile-based uncertainties for each parameter for each AGB yield table and GCE model discussed here.
 
@@
 \hline
-\fruity          &  -506.85 & $1.56^{+0.04}_{-0.04}$  &  $15.1^{+0.2}_{-0.2}$  &  $7.2^{+0.1}_{-0.1}$  &  $0.18^{+0.00}_{-0.00}$  &  $27.1^{+0.0}_{-0.0}$\\ 
-\aton            &  -492.15 & $1.07^{+0.03}_{-0.03}$  &  $14.9^{+0.2}_{-0.2}$  &  $11.3^{+0.2}_{-0.2}$  &  $-0.00^{+0.00}_{-0.00}$  &  $26.2^{+0.1}_{-0.1}$\\ 
-\monash          &  -768.25 & $1.12^{+0.04}_{-0.04}$  &  $12.8^{+0.3}_{-0.3}$  &  $10.8^{+0.2}_{-0.2}$  &  $0.12^{+0.00}_{-0.00}$  &  $27.0^{+0.0}_{-0.0}$\\ 
-\nugrid          &  -716.22 & $0.59^{+0.02}_{-0.02}$  &  $17.8^{+0.1}_{-0.1}$  &  $4.5^{+0.1}_{-0.1}$  &  $0.20^{+0.01}_{-0.01}$  &  $27.8^{+0.0}_{-0.0}$\\ 
-\fruity\ shifted    &  {\bf -298.11} & $1.29^{+0.03}_{-0.03}$  &  $18.7^{+0.1}_{-0.1}$  &  $4.6^{+0.1}_{-0.1}$  &  $0.17^{+0.00}_{-0.00}$  &  $28.0^{+0.0}_{-0.0}$\\ 
-doubled yields (and $\eta$) &  -492.95 & $1.53^{+0.04}_{-0.04}$  &  $15.3^{+0.2}_{-0.2}$  &  $7.0^{+0.1}_{-0.1}$  &  $0.18^{+0.00}_{-0.00}$  &  $27.1^{+0.0}_{-0.0}$\\ 
-lateburst        &  -453.73 & $1.90^{+0.05}_{-0.05}$  &  $14.5^{+0.2}_{-0.2}$  &  $6.5^{+0.1}_{-0.1}$  &  $0.22^{+0.01}_{-0.01}$  &  $26.9^{+0.0}_{-0.0}$\\ 
-twoinfall        &  -497.75 & $1.55^{+0.03}_{-0.03}$  &  $15.5^{+0.1}_{-0.1}$  &  $6.9^{+0.1}_{-0.1}$  &  $0.18^{+0.00}_{-0.00}$  &  $27.2^{+0.0}_{-0.0}$\\ 
-higher SN Ia       &  -482.67 & $2.15^{+0.04}_{-0.04}$  &  $11.4^{+0.2}_{-0.2}$  &  $8.4^{+0.1}_{-0.1}$  &  $0.25^{+0.01}_{-0.01}$  &  $26.5^{+0.0}_{-0.0}$\\ 
+\fruity          &  -506.85 & $1.56\pm0.04$  &  $15.09\pm0.19$  &  $7.19\pm0.09$  &  $0.178\pm0.005$  &  $27.12\pm0.04$\\ 
+\aton            &  -492.15 & $1.07\pm0.03$  &  $14.89\pm0.2$  &  $11.29\pm0.17$  &  $-0.000367\pm0.000011$  &  $26.16\pm0.06$\\ 
+\monash          &  -768.25 & $1.12\pm0.04$  &  $12.8\pm0.3$  &  $10.84\pm0.19$  &  $0.123\pm0.004$  &  $27.0\pm0.05$\\ 
+\nugrid          &  -716.22 & $0.594\pm0.018$  &  $17.81\pm0.14$  &  $4.52\pm0.10$  &  $0.198\pm0.006$  &  $27.82\pm0.03$\\ 
+\fruity\ shifted    &  -298.11 & $1.29\pm0.03$  &  $18.71\pm0.1$  &  $4.60\pm0.10$  &  $0.167\pm0.004$  &  $27.97\pm0.03$\\ 
+doubled yields (and $\eta$) &  -492.95 & $3.06\pm0.08$  &  $30.6\pm0.3$  &  $14.05\pm0.18$  &  $0.175\pm0.005$  &  $54.17\pm0.08$\\ 
+lateburst        &  -453.73 & $1.90\pm0.05$  &  $14.53\pm0.19$  &  $6.49\pm0.12$  &  $0.219\pm0.006$  &  $26.92\pm0.05$\\ 
+twoinfall        &  -497.75 & $1.55\pm0.03$  &  $15.51\pm0.12$  &  $6.930\pm0.10$  &  $0.176\pm0.003$  &  $27.24\pm0.04$\\ 
+higher SN Ia        &  -482.67 & $2.15\pm0.04$  &  $11.42\pm0.19$  &  $8.45\pm0.09$  &  $0.252\pm0.005$  &  $26.54\pm0.04$\\ 
 \hline
 {\bf including $\sigma_{\rm sys}$}: \\
-\fruity          &   -49.21 & $1.68^{+0.19}_{-0.20}$  &  $16.6^{+0.7}_{-0.7}$  &  $5.0^{+0.8}_{-0.8}$  &  $0.19^{+0.02}_{-0.02}$  &  $26.9^{+0.4}_{-0.4}$\\ 
-\aton            &   -54.01 & $0.97^{+0.12}_{-0.12}$  &  $17.0^{+0.7}_{-0.7}$  &  $9.1^{+0.8}_{-0.8}$  &  $-0.00^{+0.00}_{-0.00}$  &  $26.1^{+0.5}_{-0.5}$\\ 
-\monash          &   -60.05 & $1.06^{+0.15}_{-0.15}$  &  $15.0^{+1.0}_{-1.0}$  &  $8.6^{+0.8}_{-0.8}$  &  $0.12^{+0.02}_{-0.02}$  &  $26.8^{+0.4}_{-0.4}$\\ 
-\nugrid          &   -52.04 & $0.83^{+0.10}_{-0.10}$  &  $19.0^{+0.6}_{-0.6}$  &  $0.9^{+1.0}_{-1.0}$  &  $0.28^{+0.03}_{-0.03}$  &  $27.6^{+0.4}_{-0.4}$\\ 
-\fruity\ shifted    &   {\bf -44.75} & $1.57^{+0.18}_{-0.18}$  &  $19.7^{+0.5}_{-0.5}$  &  $2.7^{+0.9}_{-0.9}$  &  $0.20^{+0.02}_{-0.02}$  &  $28.1^{+0.4}_{-0.4}$\\
+\fruity          &   -49.21 & $1.67\pm0.2$  &  $16.6\pm0.7$  &  $5.0\pm0.8$  &  $0.19\pm0.02$  &  $26.9\pm0.4$\\ 
+\aton            &   -54.01 & $0.98\pm0.12$  &  $17.0\pm0.7$  &  $9.1\pm0.8$  &  $-0.00034\pm0.00005$  &  $26.1\pm0.5$\\ 
+\monash          &   -60.05 & $1.06\pm0.15$  &  $15.0\pm1.0$  &  $8.6\pm0.8$  &  $0.118\pm0.017$  &  $26.8\pm0.4$\\ 
+\nugrid          &   -52.04 & $0.83\pm0.10$  &  $19.0\pm0.6$  &  $0.9\pm1.0$  &  $0.28\pm0.03$  &  $27.6\pm0.4$\\ 
+\fruity\ shifted    &   -44.75 & $1.57\pm0.17$  &  $19.7\pm0.5$  &  $2.7\pm0.9$  &  $0.2\pm0.02$  &  $28.1\pm0.4$\\
 \hline

### 2025-11-25 carbon_paper/cc_plot_utils.py
minor last-minute figure tweaks

@@ -179,5 +179,5 @@ def plot_c11(scale=1):
     Zs = gcem.MH_to_Z(MH)
     ys = surp.yields.calc_y(Zs, ele="c", kind="agb")
         
-    plt.plot(MH, ys * scale, label="Fruity (AGB)", color=arya.COLORS[4])
+    plt.plot(MH, ys * scale, label="Fruity (AGB)", color=arya.COLORS[-1])
     

### 2025-11-25 carbon_paper/mw_model_plots.py

@@ -45,7 +45,8 @@ data_kwargs = dict(
 
 model_kwargs = dict(
     stat="median", errorbar=None,
-    aes="line"
+    aes="line",
+    linewidth=1.5
 )
 
 

### 2025-11-25 carbon_paper/plots/sims_uncertainties.py

@@ -38,7 +38,7 @@ names_agbm = [
 
 labels_agbm = ["0.5", "0.7", "1", "1.5", "2"]
 colors_agbm = [COLORS[0], COLORS[2], "black", COLORS[1]]
-ls_agbm = ["-.", "--", "-", ":"]
+ls_agbm = [":", "--", "-", "-."]
 
 
 names_sfh = [
@@ -51,7 +51,7 @@ labels_sfh = [
     r"fiducial",  
     r"twoinfall",
     "lateburst",
-    r"doubled yields/$\eta$",
+    r"doubled yields \& $\eta$",
 ]
 colors_sfh = ["black", *COLORS]
 ls_sfh = ["-", *LINESTYLES]

### 2025-11-25 carbon_paper/plots/sims_zeta_f.py

@@ -9,7 +9,7 @@ fig, axs = plt.subplots(3, 2, figsize=(7, 7), sharex="col", sharey=True, gridspe
 
 
 colors = [COLORS[0], "black", COLORS[1]]
-linestyles = ["--", "-", ":"]
+linestyles = [":", "-", "--"]
 
 names = [
     "fruity/zeta_lower",

### 2025-11-25 carbon_paper/tex/main.tex
arXiv actual submission version

@@
 % AGB yield tables
-\newcommand{\fruity}{\texttt{\hyperlink{fruity}{Fruity}}}
+\newcommand{\fruity}{\texttt{\hyperlink{fruity}{FRUITY}}}
 \newcommand{\nugrid}{\texttt{\hyperlink{nugrid}{NuGrid}}}
@@
 $[A/B] = \log_{10}\left(A/B\right) - \log_{10}\left(A_{\sun}/B_{\sun}\right)$, i.e.
-$[A/B]$ is the logarithm of the mass ratio between A and B, scaled such that $[A/B]=0$ for the Sun (see Table~\ref{tab:fiducial_mod} for solar scale.)
+$[A/B]$ is the logarithm of the mass ratio between A and B, scaled such that $[A/B]=0$ for the Sun.
+(See Table~\ref{tab:fiducial_mod} for the solar scale).
 }
@@
 (See Appendix~\ref{sec:nugrid_yields} for the implementation and recalculation of these yields.)
-For our models to better match observations, we uniformly amplify the yield tables according to
-\begin{equation} \label{eq:alpha}
-        \ycagb(m, Z) \rightarrow \aagb\ \ycagb(m, Z).
-\end{equation}
-As our fiducial AGB yield, we use the \fruity\ table with $\aagb=\cfactor$, (balancing MW and gas-phase constraints; see Section~\ref{sec:results} and Section~\ref{sec:gas}).
-
-Fig.~\ref{fig:y_agb} compares the C yields for these four AGB models, which we leave unmodified (i.e., $\aagb = 1$) for this comparison.
+
+Fig.~\ref{fig:y_agb} compares the C yields for these four AGB models.
 Most models agree on general yield trends in mass and metallicity.
@@
 Both HBB and TDU result in mass and metallicity-dependent C yields. 
-Lower mass stars ($\lesssim 1\,\Mo$)  do not experience (strong) TDU.
-As a result, C yields from these stars are affected only by first dredge-up, resulting in small net C yields \citep[table 1]{karakas10}.
+Lower mass stars ($\lesssim 1\,\Mo$)  do not experience (strong) TDU. As a result, C yields from these stars are affected only by first dredge-up, resulting in small net C yields \citep{karakas10}.
 Above ${\sim}1\,\Mo$, TDU becomes more important, enriching the outer layers with C.
@@
 
-%\dbnote{also NUGRID... https://ui.adsabs.harvard.edu/abs/2012ApJ...757..132H/abstract, https://ui.adsabs.harvard.edu/abs/2016MNRAS.455.3848J/abstract}
-
-For our comparisons later, we define the AGB yield fraction, 
+For our models to better match observations, we uniformly amplify the yield tables according to
+\begin{equation} \label{eq:alpha}
+        \ycagb(m, Z) \rightarrow \aagb\ \ycagb(m, Z).
+\end{equation}
+We also define the AGB yield fraction, 
 \begin{equation}\label{eq:f_agb}
@@
 However, since the Sun was not enriched entirely by solar metallicity predecessors, the equivalence of $\fagb{}$ to the yield ratio is not exact.
+As our fiducial AGB yield, we use the \fruity\ table with $\aagb=\cfactor$ ($\fagb=0.3$), balancing MW and gas-phase constraints (see Sections~\ref{sec:results} and \ref{sec:gas}).
 
@@
 Fig.~\ref{fig:y_cc} shows the integrated yields of massive star models from the literature.
-At solar metallicity, \citepos{sukhbold+16} C yield is $\approx0.5$ dex higher than \cite[non-rotating]{LC18}, likely driven by much stronger (C-enhanced) mass loss in \citet{sukhbold+16} for stars more massive than $\gtrsim40\,\Mo$.
- The \cite{LC18} models, which include rotation, show that the induced mixing (e.g., \citealt{frischknecht+16}) can dramatically increase the magnitude and metallicity dependence of $\Ycc$.
+At solar metallicity, \citepos{sukhbold+16} C yield is $\approx0.5$ dex higher than \citepos{LC18} non-rotating models, likely driven by much stronger (C-enhanced) mass loss in \citet{sukhbold+16} for stars more massive than $\gtrsim40\,\Mo$.
+ The \cite{LC18} models including rotation show that the induced mixing (e.g., \citealt{frischknecht+16}) can dramatically increase the magnitude and metallicity dependence of $\Ycc$.
 As we will later empirically show, CCSN C production needs to be strongly metallicity-dependent at $Z \approx \Zo$, which is consistent with \citepos{LC18} rapidly rotating models and to a lesser extent \citet{NKT13}.
-Fig.~\ref{fig:y_cc} also shows the IMF-averaged AGB star yields from the \fruity\ model (in Fig.~\ref{fig:agb-ssp}). Especially at $Z\approx \Zo$, most CCSN models dominate AGB C production.
+Fig.~\ref{fig:y_cc} also shows the IMF-averaged AGB star yields from the \fruity\ model (from Fig.~\ref{fig:agb-ssp}). Especially at $Z\approx \Zo$, most CCSN models dominate AGB C production.
 
@@
     \citet[WW95, pink triangles]{WW95}. \citet{sukhbold+16} report yields for different black hole landscapes, while \citet{LC18} provide yields at different rotational velocities.
-   The pink line denotes $\Ycagb$ from the \fruity{} AGB star model for comparison (see Fig.~\ref{fig:agb-ssp}). All models include wind yields. 
+   The light blue line denotes $\Ycagb$ from the \fruity{} AGB star model for comparison (see Fig.~\ref{fig:agb-ssp}). All models include wind yields. 
 }
@@
 Our models extend the \citet[hereafter \JJ]{james+21} Milky Way model. We integrate the model using the publicly available Versatile Integrator for Chemical Evolution (\VICE; \citealt{JW20}).%
-    \footnote{\VICE~is available at \url{https://github.com/giganano/VICE}}
+    \footnote{\VICE~is available at \url{https://github.com/giganano/VICE}.}
 This model is described extensively in \JJ~and summarized in \citet{james+23}. Here, we provide an overview of the relevant components.
@@
 We adopt the following priors for each model parameter: $\aagb \sim N(1, 1)$, $\zcc \sim N(0, 10^{-3})$, and $\yl \sim N(2\times10^{-3}, 1\times10^{-3})$, where $N(\mu, \sigma)$ is a Gaussian distribution with mean $\mu$ and standard deviation $\sigma$.
+(For the doubled yields and outflows model, the priors are correspondingly doubled).
 We run the MCMC using Turing.jl \citep{turingjl} with a No-U-turn sampler (an adaptive Hamilton Monte-Carlo algorithm, \citealt{NUTS}) with an acceptance rate of 0.65.
@@
 in the gas phase.
-We consider measurements in Galactic and extragalactic \Hii{} regions, Damped Lyman-$\alpha$ systems\footnote{damped Lyman-$\alpha$ systems (or DLAs) are gas clouds observed as absorption spectra in front of background quasars}, and Milky Way halo main-sequence stars (all references in the caption of Fig.~\ref{fig:gas_phase}, which we do not repeat here for brevity).
+We consider measurements in Galactic and extragalactic \Hii{} regions, Damped Lyman-$\alpha$ systems,\footnote{Damped Lyman-$\alpha$ systems (or DLAs) are gas clouds observed as absorption spectra in front of background quasars.} and Milky Way halo main-sequence stars (all references in the caption of Fig.~\ref{fig:gas_phase}, which we do not repeat here for brevity).
 While we used Mg as our representative alpha element in our APOGEE sample, we shift focus to O in this Section because O is more readily observed in the gas phase.
@@
 
-From the combined constraints on the [C/Mg] trend with metallicity and [$\alpha$/Fe], we have inferred possible combinations of yields that reproduce thin-disk abundance trends.
+From the combined constraints on the [C/Mg] trend with [Mg/H] and [Mg/Fe], we have inferred possible combinations of yields that reproduce thin-disk abundance trends.
 In all cases, we find that $\Yct / \Ymg \approx 4.2 \pm 0.2$ at solar metallicity, with total C production increasing with increasing metallicity.
@@
             \hline
-            fiducial & 2.57 & fruity & 18.7 & 7.9 \\
-            $\zcc=0.0004$ & 2.57 & fruity & 18.7 & 4.0 \\
-            $\zcc=0.0012$ & 2.57 & fruity & 18.7 & 11.9 \\
-            $\fagb = 0$ & 0.0 & fruity & 27.1 & 7.9 \\
-            $\fagb = 0.5$ & 4.36 & fruity & 13.3 & 7.9 \\
-            lower $\fagb$, $\zcc$ & 0 & fruity & 27.9 & 4.1 \\
-            higher $\fagb$, $\zcc$ & 4.36 & fruity & 12.1 & 12.1 \\
-            \fruity{} & 1.55 & fruity & 22.3 & 7.2 \\
-            \aton{} & 1.07 & aton & 26.2 &  11.3 \\
-            \monash{} & 1.12 & monash & 23.7 & 10.9 \\
-            \nugrid{} & 0.59 & nugrid & 22.3 & 4.5 \\
-            \fruity{} shifted & 1.29 & fruity(m/0.7) & 23.3 & 4.6 \\
-            mass shift 0.5 & 2.98 & fruity(m/0.5)  & 22.1 & 14.5 \\
-            mass shift 0.7 & 2.34 & fruity(m/0.7) & 19.7 & 3.2 \\
-            mass shift 1.5 & 2.71 & fruity(m/1.5) & 18.6 & 8.5 \\
+            fiducial & 2.57 & FRUITY & 18.7 & 7.9 \\
+            $\zcc=0.0004$ & 2.57 & FRUITY & 18.7 & 4.0 \\
+            $\zcc=0.0012$ & 2.57 & FRUITY & 18.7 & 11.9 \\
+            $\fagb = 0$ & 0.0 & FRUITY & 27.1 & 7.9 \\
+            $\fagb = 0.5$ & 4.36 & FRUITY & 13.3 & 7.9 \\
+            lower $\fagb$, $\zcc$ & 0 & FRUITY & 27.9 & 4.1 \\
+            higher $\fagb$, $\zcc$ & 4.36 & FRUITY & 12.1 & 12.1 \\
+            \fruity{} & 1.55 & FRUITY & 22.3 & 7.2 \\
+            \aton{} & 1.07 & ATON & 26.2 &  11.3 \\
+            \monash{} & 1.12 & Monash & 23.7 & 10.9 \\
+            \nugrid{} & 0.59 & NuGrid & 22.3 & 4.5 \\
+            \fruity{} shifted & 1.29 & FRUITY($M/0.7$) & 23.3 & 4.6 \\
+            mass shift 0.5 & 2.98 & FRUITY($M/0.5$)  & 22.1 & 14.5 \\
+            mass shift 0.7 & 2.34 & FRUITY($M/0.7$) & 19.7 & 3.2 \\
+            mass shift 1.5 & 2.71 & FRUITY($M/1.5$) & 18.6 & 8.5 \\
 		\hline
@@
 
-Because the yield tables included in \citep{battino+19, battino+21} are inconsistent with the \citet{ritter+18} definitions of yields, we recalculate these yields from the publicly available data on \url{https://astrohub.uvic.ca}.
+Because the yield tables included in \citet{battino+19, battino+21} are inconsistent with the \citet{ritter+18} definitions of yields, we recalculate these yields from the publicly available data on \url{https://astrohub.uvic.ca}.
 
